### 2020-04-09 paper/dcpo_demsupport.Rmd
add paper/

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms2.tex
title: "[dcpo_demsupport]"
thanks: "Corresponding author: [yuehong-tai@uiowa.edu](mailto:yuehong-tai@uiowa.edu). Current version: `r format(Sys.time(), '%B %d, %Y')`."
author:
- name: Yuehong 'Cassandra' Tai
  affiliation: University of Iowa
- name: Yue Hu
  affiliation: Tsinghua University
- name: Frederick Solt
  affiliation: University of Iowa
abstract: ""
keywords: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
spacing: double
bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$"))`}
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
nocite: |
  @Solt2020a
---

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
# load all the packages you will use below 
library(huxtable)
library(kableExtra)
library(DCPOtools)
library(tidyverse)
library(latex2exp)
```

<!-- The following text is all cribbed from `fsolt/dcpo_article` and obviously needs heavy revision -->

# Incorporating Uncertainty
This means not simply employing the point estimates, that is, the means of the posterior distributions [_contra_ @Claassen2020a; @Claassen2020b].

Instead, researchers should follow the recommendations of work using other latent variables [e.g., @Schnakenberg2014; @Crabtree2015] and other measures incorporating uncertainty, such as the Standardized World Income Inequality Database [@Solt2020]: generate many duplicate versions of the analysis dataset, assign to each a different random draw from the posterior distributions of the variables measured with uncertainty, perform the analyses repeatedly on each of these multiple versions of the dataset, and combine the results following the rules set out in @Rubin1987.
The functional programming tools in the `purrr` package [@Henry2019] make this a matter of just a few additional lines of code.

# A Better Measure of Democratic Support
The DCPO model is estimated using the `DCPO` package for R [@Solt2020a], which is written in the Stan probabilistic programming language [@StanDevTeam2019a; @StanDevTeam2019b].

## Relative Fit
<!-- We'll only compare Model 5 and DCPO and save ourselves the heartache of dealing with dgirt, but the comparison needs updated with the full dataset -->
To assess the ability of the DCPO model to fit public opinion data relative to the two alternative approaches, I use the set of survey questions on support for democracy employed in @Claassen2019 [, 7-8].

The first three columns of Table \ref{tab:validation_table} present the results of an internal validation test, that is, a test that uses the same data that was used to fit the model [see, e.g., @Claassen2019, 9].
In column 1, the mean absolute error (MAE) measures the average difference between the observed proportion of survey respondents in country $k$ in year $t$ with replies to question $q$ with a response at least as positive as response $r$ (or with an affirmative response, in the case of Claassen's [-@Claassen2019] Model 5) and the model's predicted proportion across all countries, years, questions, and response categories.
Given, however, that Claassen's [-@Claassen2019] Model 5 is fit to dichotomized data, while the @Caughey2019 and DCPO models are fit to the original, possibly ordinal, survey data, which have higher variance, comparing the MAE across all three models can be somewhat misleading.
Therefore, the MAE of the country means---the average proportions answering affirmatively (for Claassen's [-@Claassen2019] Model 5) or with a response at least as positive as response $r$ (for @Caughey2019 and DCPO) in each country across all years and all questions---serve as a baseline [see @Claassen2019, 11-12]; these appear in column 2.
The percentage reduction in MAE achieved by each model, listed in column 3, represents the improvement in fit compared to this baseline.

The last three columns of Table \ref{tab:validation_table} present the results of an external validation test, a test of the models' ability to predict out-of-sample survey responses.
This test employs $k$-fold validation with 10 folds, that is, it randomly divides the available country-year-questions into tenths and then sequentially treats each tenth as a test set to be predicted while fitting the model on a training set consisting of the other nine tenths of the data.
Column 4 shows the mean of the MAEs of the ten resulting sets of out-of-sample predictions, while column 5 presents the mean improvement over of these ten MAEs over their respective ten country-mean MAEs.
Column 6 reports the discrepancy between the percentage of all response proportions that fall within their corresponding predictions' 80% confidence intervals and the expected 80%; it therefore provides a gauge of the accuracy of the models' estimates of uncertainty.
A negative value in this column indicate that less than 80% of the observed out-of-sample survey proportions are included with the model's predictions' nominal 80% credible intervals, and so its uncertainty estimates are overconfident, while a positive value indicates the opposite, that more than 80% of the observed proportions fall within the credible intervals and so the model's uncertainty estimates are overly conservative.

```{r validation}
# load(here::here("data", "validation_table.rda"))
# 
# validation_table
```

Comparing first the results for Claassen's [-@Claassen2019] Model 5 with those for the @Caughey2019 model reveals that, at least for this set of survey questions, while the former has a smaller MAE, the latter accounts for a larger percentage of the variation in its source data left unexplained by its respective country-means model.
This is true both in the internal validation test and on average across the ten folds of the external validation test.
Again, this discrepancy is possible due to the greater variance in the survey data when its ordinal nature is preserved, as in the @Caughey2019 model, rather than dichotomized, as in Claassen's [-@Claassen2019] approach.
An examination of column 6 reveals that the @Caughey2019 model yielded predictions with credible intervals that are much too narrow, encompassing only about 13% of the actual sample observations, while those for Claassen's [-@Claassen2019] Model 5 were slightly too conservative.^[
The relatively poor uncertainty estimates of the @Caughey2019 model are similar to those found for the dichotomous version presented in @Caughey2015 by @Claassen2019 [, 12].]

However, it is the DCPO model that provides what is unambiguously the best fit.
It features the smallest mean absolute error: on average, in the internal validation test its predictions are just over 3 percentage points away from the actual sample observations, and in the external validation test they are only 5.5 percentage points away from the actual out-of-sample observations.
In both cases, these represent the largest percentage improvement over the country-means MAE.
Further, in the external validation test, the DCPO credible intervals come closest to matching the nominal 80% level of any of the three models.

## Results
DCPO results here

# Conclusion

\pagebreak

### 2020-04-09 R/argon/dcpo_demsup_kfold/R/processing.R
add R/argon/

@@ -1,0 +1,27 @@
+remotes::install_github("fsolt/DCPOtools")
+remotes::install_github("fsolt/DCPO")
+
+library(tidyverse)
+library(DCPOtools)
+library(DCPO)
+
+fold <- commandArgs(trailingOnly=TRUE) %>%
+  as.numeric()
+
+demsup <- read_csv(system.file("extdata", "all_data_demsupport.csv", package = "DCPOtools"))
+
+print(fold)
+
+demsup_data <- format_dcpo(demsup %>% with_min_yrs(3),
+                       scale_q = "church_21",
+                       scale_cp = 2)
+
+demsup_kfold <- dcpo_xvt(demsup_data,
+                          fold_number = fold, 
+			  number_of_folds = 10,
+                          iter = 500)
+
+save(demsup_kfold, 
+     file = str_c("data/fold_",
+		  fold,
+                  ".rda"))

### 2020-04-09 R/argon/dcpo_demsupport/R/claassen_m5.R

@@ -1,0 +1,28 @@
+remotes::install_github("fsolt/DCPOtools")
+remotes::install_github("stan-dev/rstantools")
+remotes::install_github("fsolt/DCPO")
+
+library(tidyverse)
+library(DCPOtools)
+library(rstan)
+
+demsup <- read_csv("https://github.com/fsolt/DCPOtools/raw/master/inst/extdata/all_data_demsupport.csv")
+
+demsup_claassen <- format_claassen(demsup)
+
+claassen_m5 <- stan(file = 'R/supdem.stan.mod5.stan',
+                       data = demsup_claassen,
+                       iter = 2000,
+                       chains= 4,
+                       cores = 4,
+		       thin = 2,
+                       pars = c("mu_lambda","sigma_lambda","sigma_delta","sigma_theta","phi","lambda","delta","theta",
+            "x_pred","log_lik"),
+                       control = list(adapt_delta=0.99, stepsize=0.02, max_treedepth=11))
+
+save(demsup_claassen, claassen_m5, 
+     file = str_c("data/claassen_m5_2k_", 
+                  str_replace_all(Sys.time(), "[ :]", "-") %>%
+                    str_replace("2019-", "") %>%
+                    str_replace("-\\d{2}$", ""),
+                  ".rda"))

### 2020-04-09 R/argon/dcpo_demsupport/R/claassen_m5.sh

@@ -1,0 +1,4 @@
+#!/bin/sh
+
+module load R/3.5.1_gcc-5.4.0
+Rscript R/claassen_m5.R

### 2020-04-09 R/argon/dcpo_demsupport/R/processing.R

@@ -1,0 +1,25 @@
+remotes::install_github("fsolt/DCPOtools")
+remotes::install_github("fsolt/DCPO")
+
+library(tidyverse)
+library(DCPOtools)
+library(DCPO)
+
+demsup <- read_csv("https://github.com/fsolt/DCPOtools/raw/master/inst/extdata/all_data_demsupport.csv")
+
+demsup_data <- format_dcpo(demsup %>% with_min_yrs(2),
+                       scale_q = "church_21",
+                       scale_cp = 2)
+
+out1 <- dcpo(demsup_data,
+                 iter = 2000,
+		 chains = 4,
+		 thin = 2,
+                 pars = c("sd_delta","sd_theta_evolve", "sd_sigma_evolve", "sigma","phi","beta","alpha","delta","theta","y_r_pred","log_lik"))
+
+save(demsup_data, out1,
+     file = str_c("data/church_21_2k_",
+                  str_replace_all(Sys.time(), "[ :]", "-") %>%
+                    str_replace("2019-", "") %>%
+                    str_replace("-\\d{2}$", ""),
+                  ".rda"))

### 2020-04-09 R/argon/dcpo_demsupport/R/processing.sh

@@ -1,0 +1,4 @@
+#!/bin/sh
+
+module load R/3.5.1_gcc-5.4.0
+Rscript R/processing.R

### 2020-05-31 paper/dcpo_demsupport.Rmd
adding replication codes for model 5; improve the replicability of the rmd

@@
     latex_engine: pdflatex
-    template: svm-latex-ms2.tex
+    template: https://raw.githubusercontent.com/junkpolisci/website/master/working_content/svm-latex-ms2.tex
 title: "[dcpo_demsupport]"
@@
 spacing: double
-bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$"))`}
-biblio-style: apsr
+bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
+csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl
+# biblio-style: apsr
 citecolor: black
@@
 
-```{r, include=FALSE}
+```{r setup, include=FALSE}
 options(tinytex.verbose = TRUE)
-```
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, dpi = 300)
+
+# If you haven't install `DCPOtools`
+# remotes::install_github("fsolt/DCPOtools")
+
+if (!require(pacman)) install.packages("pacman")
+library(pacman)
+
 # load all the packages you will use below 
-library(huxtable)
-library(kableExtra)
-library(DCPOtools)
-library(tidyverse)
-library(latex2exp)
+p_load(
+  dataverse, # data scraping
+  DCPOtools, # analysis
+  huxtable, kableExtra, # tabulation
+  latex2exp, # visualization
+  purrr, broom, tidyverse
+) # data wrangling # data wrangling
+
+# Functions preload
+set.seed(313)
 ```
@@
 The functional programming tools in the `purrr` package [@Henry2019] make this a matter of just a few additional lines of code.
+
+```{r replication-model5, eval = FALSE}
+# Before running the following lines, one should set their personal token and server in their system environment first: 
+# Sys.setenv("DATAVERSE_KEY" = "exampleToken")
+# Sys.setenv("DATAVERSE_SERVER" = "dataverse.harvard.edu")
+
+supdem <- get_file("Support for democracy.tab", "doi:10.7910/DVN/A47LUM") %>% 
+  read_csv
+
+# Required by the replication file
+p_load(
+  countrycode,
+  MASS,
+  psych,
+  arm,
+  loo,
+  rstanarm,
+  RColorBrewer,
+  devtools,
+  dgo
+)
+
+sddem1 = gather(data=supdem, key="Item", value="Response", 6:33, na.rm=TRUE) 
+sddem1$Sample = 0
+sddem1[sddem1$Project=="AfB", "Sample"] = sddem1[sddem1$Project=="AfB", "AfB_sample"]
+sddem1[sddem1$Project=="ArB", "Sample"] = sddem1[sddem1$Project=="ArB", "ArB_sample"]
+sddem1[sddem1$Project=="AsB", "Sample"] = sddem1[sddem1$Project=="AsB", "AsB_sample"]
+sddem1[sddem1$Project=="AsnB", "Sample"] = sddem1[sddem1$Project=="AsnB", "AsnB_sample"]
+sddem1[sddem1$Project=="ESS", "Sample"] = sddem1[sddem1$Project=="ESS", "ESS_sample"]
+sddem1[sddem1$Project=="LAPOP", "Sample"] = sddem1[sddem1$Project=="LAPOP", "LAPOP_sample"]
+sddem1[sddem1$Project=="LB", "Sample"] = sddem1[sddem1$Project=="LB", "LB_sample"]
+sddem1[sddem1$Project=="NDB", "Sample"] = sddem1[sddem1$Project=="NDB", "NDB_sample"]
+sddem1[sddem1$Project=="Pew", "Sample"] = sddem1[sddem1$Project=="Pew", "Pew_sample"]
+sddem1[sddem1$Project=="WVS", "Sample"] = sddem1[sddem1$Project=="WVS", "WVS_sample"]
+sddem1[sddem1$Project=="CSES", "Sample"] = sddem1[sddem1$Project=="CSES", "CSES_sample"]
+
+# trim stacked dataset
+sddem1 = sddem1[, -c(6:16)]
+sddem1$Response = ifelse(sddem1$Response==0, NA, sddem1$Response)
+sddem1 = sddem1[!is.na(sddem1$Response), ]
+
+# create item by project indicators
+sddem1 = unite(sddem1, ItemProj, c(Project, Item), sep = "_", remove = FALSE)
+sddem1$ItemProj = as.factor(sddem1$ItemProj)
+
+# create year by country indicators
+year0 = 1990
+sddem1 = sddem1[sddem1$Year > year0,]
+sddem1 = unite(sddem1, YearCountry, c(Year, Country), sep = "_", remove = FALSE)
+sddem1$YearCountry = as.factor(sddem1$YearCountry)
+
+# create item by project by country indicators
+sddem1 = unite(sddem1, ItemProjCnt, c(ItemProj, Country), sep = "_", remove = FALSE)
+sddem1$ItemProjCnt = as.factor(sddem1$ItemProjCnt)
+
+# create item by country indicators
+sddem1 = unite(sddem1, ItemCnt, c(Item, Country), sep = "_", remove = FALSE)
+sddem1$ItemCnt = as.factor(sddem1$ItemCnt)
+
+# create year by project indicators
+sddem1 = unite(sddem1, YrProj, c(Year, Project), sep = "_", remove = FALSE)
+sddem1$YrProj = as.factor(sddem1$YrProj)
+
+# create year by project by country indicators
+sddem1 = unite(sddem1, YrProjCnt, c(YrProj, Country), sep = "_", remove = FALSE)
+sddem1$YrProjCnt = as.factor(sddem1$YrProjCnt)
+
+# factorise
+sddem1$Country = as.factor(as.character(sddem1$Country))
+sddem1$Item = as.factor(as.character(sddem1$Item))
+sddem1$ItemProj = as.factor(as.character(sddem1$ItemProj))
+sddem1$ItemCnt = as.factor(as.character(sddem1$ItemCnt))
+sddem1$ItemProjCnt = as.factor(as.character(sddem1$ItemProjCnt))
+sddem1$Project = as.factor(as.character(sddem1$Project))
+sddem1$YrProj = as.factor(as.character(sddem1$YrProj))
+sddem1$YrProjCnt = as.factor(as.character(sddem1$YrProjCnt))
+sddem1$Year = as.factor(sddem1$Year-year0)
+
+# drop countries with less than 2 years of data
+cnt.obs.years = rowSums(table(sddem1$Country, sddem1$Year) > 0)
+sddem2 = sddem1[sddem1$Country %in% levels(sddem1$Country)[cnt.obs.years > 1], ]
+
+## Stan estimation
+
+# prepare data for stan
+
+n.items = length(unique(sddem2$Item))
+n.cntrys = length(unique(sddem2$Country))
+n.yrs = 2015-year0
+n.proj = length(unique(sddem2$Project))
+n.resp = dim(sddem2)[1]
+n.itm.prj = length(unique(sddem2$ItemProj))
+n.itm.cnt = length(unique(sddem2$ItemCnt))
+n.cntry.yrs = n.cntrys * n.yrs
+n.itm.prj.cnt = length(unique(sddem2$ItemProjCnt))
+n.yr.proj.cnt = length(unique(sddem2$YrProjCnt))
+cntrys = as.numeric(factor(sddem2$Country))
+cnt.names = sort(unique(sddem2$Country))
+cnt.ccode = sddem2[match(cnt.names, sddem2$Country), "COWCode"]
+items = as.numeric(factor(sddem2$Item))
+yrs = as.numeric(sddem2$Year)
+projs = as.numeric(factor(sddem2$Project))
+itm.prjs = as.numeric(factor(sddem2$ItemProj))
+itm.prj.cnts = as.numeric(factor(sddem2$ItemProjCnt))
+itm.cnts = as.numeric(factor(sddem2$ItemCnt))
+cntry.yrs = as.numeric(sddem2$YearCountry)
+
+# specify data for stan
+dat.2 = list(N=n.resp, K=n.itm.prj, T=n.yrs, J=n.cntrys, P=n.itm.prj.cnt, jj=cntrys, tt=yrs, 
+             pp=itm.prj.cnts, kk=itm.prjs, x=sddem2$Response, samp=sddem2$Sample)
+
+# pars
+pars.5 = c("mu_lambda","sigma_lambda","sigma_delta","sigma_theta","phi","lambda","delta","theta","x_pred","log_lik")
+
+# set pars for final run (time-consuming; reduce iterations for trial run)
+n.iter = 1000
+n.warm = 500
+n.chn = 4
+n.thin = 2
+
+## supdem.stan.mod5.stan obtained from dataverse replication files
+stan.mod.5 <- stan(file = "supdem.stan.mod5.stan", data=dat.2, pars=pars.5, 
+                   iter=n.iter, warmup=n.warm, chains=n.chn, thin=n.thin, 
+                   control=list(adapt_delta=0.99, stepsize=0.02, max_treedepth=11))
+```
 

### 2020-06-05 paper/dcpo_demsupport.Rmd
host svm-latex-ms2.tex locally for improved replicability

@@
     latex_engine: pdflatex
-    template: https://raw.githubusercontent.com/junkpolisci/website/master/working_content/svm-latex-ms2.tex
+    template: svm-latex-ms2.tex
 title: "[dcpo_demsupport]"
@@
 bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
-csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl
-# biblio-style: apsr
+# csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl
+biblio-style: apsr
 citecolor: black

### 2020-06-06 paper/dcpo_demsupport.Rmd
fuss with packages: add modelsummary for tables, drop purrr (in tidyverse) and broom (in modelsummary)

@@
   DCPOtools, # analysis
-  huxtable, kableExtra, # tabulation
+  huxtable, kableExtra, modelsummary, # tabulation
   latex2exp, # visualization
-  purrr, broom, tidyverse
-) # data wrangling # data wrangling
+  tidyverse # data wrangling
+)
 

### 2020-06-06 paper/dcpo_demsupport.Rmd
add data/claassen_input.csv

@@
 The functional programming tools in the `purrr` package [@Henry2019] make this a matter of just a few additional lines of code.
+
+```{r replication-data-prep, eval=FALSE}
+claassen_input_raw <- DCPOtools:::claassen_setup(vars = read_csv("data-raw/mood_dem.csv"),
+                                       file = "data/claassen_input_raw.csv")
+
+claassen_input <- format_claassen(claassen_input_raw)
+
+claassen_m5 <- stan(file = 'R/supdem.stan.mod5.stan',
+                       data = claassen_input,
+                    iter = 2000,
+                    chains= 4,
+                    cores = 4,
+                    thin = 2,
+                    pars = c("mu_lambda", "sigma_lambda", "sigma_delta", "sigma_theta", "phi", "lambda", "delta", "theta", "x_pred","log_lik"),
+                    control = list(adapt_delta=0.99, stepsize=0.02, max_treedepth=11))
+
+```
 

### 2020-06-07 paper/dcpo_demsupport.Rmd
exclude problematic WVS country-years; format data for Model 5; run Model 5; save output

--- 2020-06-06 paper/dcpo_demsupport.Rmd
@@
   latex2exp, # visualization
+  rstan, # Bayesian estimation
   tidyverse # data wrangling
@@
 The functional programming tools in the `purrr` package [@Henry2019] make this a matter of just a few additional lines of code.
+
+```{r replication-data-prep, eval=FALSE}
+# claassen_input_raw <- DCPOtools:::claassen_setup(vars = read_csv("data-raw/mood_dem.csv"),
+#                                        file = "data/claassen_input_raw.csv")
+
+claassen_input_raw <- read_csv("data/claassen_input_raw.csv") %>% 
+  filter(!(str_detect(item, "army") & # WVS obs identified as problematic by Claassen 
+    ((country=="Albania" & year==1998) |
+         (country=="Indonesia" & (year==2001 | year==2006)) |
+         (country=="Iran" & year==2000) |
+         (country=="Pakistan" & (year==1996 | year==2001)) |
+         (country=="Vietnam" & year==2001)) |
+    (str_detect(item, "strong") &
+         ((country=="Egypt" & year==2012) |
+              (country=="Iran" & (year==2000 | year==2005)) |
+              (country=="India") |
+              (country=="Pakistan" & (year==1996 | year==2001)) |
+              (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
+              (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
+              (country=="Vietnam" & year==2001)))))
+
+claassen_input <- DCPOtools::format_claassen(claassen_input_raw)
+
+claassen_m5 <- rstan::stan(file = 'R/argon/dcpo_demsupport/R/supdem.stan.mod5.stan',
+                           data = claassen_input,
+                           iter = 2000,
+                           warmup = 1000,
+                           chains = 4,
+                           cores = 4,
+                           thin = 2,
+                           pars = c("mu_lambda", "sigma_lambda", "sigma_delta", "sigma_theta", "phi", "lambda", "delta", "theta", "x_pred","log_lik"),
+                           control = list(adapt_delta=0.99, stepsize=0.02, max_treedepth=15))
+
+save(claassen_m5, file = "data/claassen_m5.RData")
+```
 

### 2020-06-11 paper/dcpo_demsupport.Rmd
divide claassen_input chunks for caching; filter cases per @Tyhcass' dcpo_dem_mood.R (but using tidyverse for legibility); get replication data from AJPS (not PA) Dataverse

--- 2020-06-06 paper/dcpo_demsupport.Rmd
@@
 
+```{r claassen_input_raw}
+claassen_input_raw <- DCPOtools:::claassen_setup(vars = read_csv("data-raw/mood_dem.csv"),
+                                       file = "data/claassen_input_raw.csv")
+```
+
+```{r claassen_input}
+claassen_input_raw1 <- read_csv("data/claassen_input_raw.csv") %>% 
+  filter(!(str_detect(item, "army") & # WVS obs identified as problematic by Claassen 
+    ((country=="Albania" & year==1998) |
+         (country=="Indonesia" & (year==2001 | year==2006)) |
+         (country=="Iran" & year==2000) |
+         (country=="Pakistan" & (year==1996 | year==2001)) |
+         (country=="Vietnam" & year==2001)) |
+    (str_detect(item, "strong") &
+         ((country=="Egypt" & year==2012) |
+              (country=="Iran" & (year==2000 | year==2005)) |
+              (country=="India") |
+              (country=="Pakistan" & (year==1996 | year==2001)) |
+              (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
+              (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
+              (country=="Vietnam" & year==2001))))) %>% 
+  filter(!(survey=="evs2017" | survey == "arabb5" | survey == "eb47")) %>%  # surveys unused by Claassen
+  mutate(item = if_else(item == "strong_amb_1" & year == 2004, "strong_amb_2", item)) # items conflated in amb_combo file
+
+claassen_input <- DCPOtools::format_claassen(claassen_input_raw)
+```
+
+```{r claassen_m5, eval=FALSE}
+claassen_m5 <- rstan::stan(file = 'R/argon/dcpo_demsupport/R/supdem.stan.mod5.stan',
+                           data = claassen_input,
+                           iter = 2000,
+                           warmup = 1000,
+                           chains = 4,
+                           cores = 4,
+                           thin = 2,
+                           pars = c("mu_lambda", "sigma_lambda", "sigma_delta", "sigma_theta", "phi", "lambda", "delta", "theta", "x_pred","log_lik"),
+                           control = list(adapt_delta=0.99, stepsize=0.02, max_treedepth=15))
+
+save(claassen_m5, file = "data/claassen_m5.RData")
+```
+
 ```{r replication-model5, eval = FALSE}
@@
 
-supdem <- get_file("Support for democracy.tab", "doi:10.7910/DVN/A47LUM") %>% 
-  read_csv
+supdem <- get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>% 
+  read_csv(col_types = cols(.default = col_double(), 
+                            Country = col_character(),
+                            CAbb = col_character(),
+                            Project = col_character()))
 

### 2020-06-12 R/cy_crosswalk.R
add cy_crosswalk.R; start towards #5 (I'm still working on this, @Tyhcass)

@@ -1,0 +1,37 @@
+library(DCPOtools)
+library(tidyverse)
+
+supdem <- dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>% 
+    read_csv(col_types = "cdcddcdc")
+
+supdem_cy <- supdem %>%                                             # 1390 obs
+    janitor::clean_names() %>% 
+    mutate(old_country = country,
+           country = countrycode::countryname(old_country)) %>%
+    dplyr::select(country, year, project) %>% 
+    unique()
+
+claassen_input_cy <- read_csv("data/claassen_input_raw.csv") %>%    # 1504 obs
+    mutate(p_dcpo = str_extract(survey, "^[a-z]+"), 
+           project = case_when(p_dcpo == "afrob" ~ "afb",
+                               p_dcpo == "amb" ~ "lapop",
+                               p_dcpo == "arabb" ~ "arb",
+                               p_dcpo == "asiab" ~ "asb",
+                               p_dcpo == "asianb" ~ "asnb",
+                               p_dcpo == "neb" ~ "ndb",
+                               p_dcpo == "sasianb" ~ "sab",
+                               TRUE ~ p_dcpo),
+           y_dcpo = year,
+           old_country = country,
+           country = countrycode::countryname(old_country)) %>%
+    dplyr::select(country, year, y_dcpo, survey, project) %>% 
+    unique()
+
+no_problems <- inner_join(supdem_cy, claassen_input_cy)             # 1259 obs
+
+needed <- anti_join(supdem_cy, claassen_input_cy)                   # 131 obs
+
+available <- anti_join(claassen_input_cy, supdem_cy)                # 245 obs
+
+try <- left_join(needed, available, by = c("country", "project"))
+

### 2020-06-12 paper/dcpo_demsupport.Rmd
In line 99, it should be eb471 instead of 47. Filter Iran and Pakistan by the survey year in DCPO rather than Claassen's year. @fsolt.

@@
          (country=="Iran" & year==2000) |
-         (country=="Pakistan" & (year==1996 | year==2001)) |
+         (country=="Pakistan" & (year==1997 | year==2001)) | #in DCPO,it is 1997 instead of 1996
          (country=="Vietnam" & year==2001)) |
@@
          ((country=="Egypt" & year==2012) |
-              (country=="Iran" & (year==2000 | year==2005)) |
+              (country=="Iran" & (year==2000 | year==2007)) | #in DCPO, the year is 2007 rather than 2005
               (country=="India") |
-              (country=="Pakistan" & (year==1996 | year==2001)) |
+              (country=="Pakistan" & (year==1997 | year==2001)) | #in DCPO,it is 1997 instead of 1996
               (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
@@
               (country=="Vietnam" & year==2001))))) %>% 
-  filter(!(survey=="evs2017" | survey == "arabb5" | survey == "eb47")) %>%  # surveys unused by Claassen
+  filter(!(survey=="evs2017" | survey == "arabb5" | survey == "eb471")) %>%  # surveys unused by Claassen
   mutate(item = if_else(item == "strong_amb_1" & year == 2004, "strong_amb_2", item)) # items conflated in amb_combo file

### 2020-06-12 paper/dcpo_demsupport.Rmd
add note and fix per @Tyhcass re claassen_input_raw1; paste in AJPS (not PA) replication script (still messy at the moment)

--- 2020-06-11 paper/dcpo_demsupport.Rmd
@@
 claassen_input_raw1 <- read_csv("data/claassen_input_raw.csv") %>% 
-  filter(!(str_detect(item, "army") & # WVS obs identified as problematic by Claassen 
+  filter(!(str_detect(item, "army") & # WVS obs identified as problematic by Claassen (note: these are his years right now)
     ((country=="Albania" & year==1998) |
@@
 supdem <- get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>% 
-  read_csv(col_types = cols(.default = col_double(), 
-                            Country = col_character(),
-                            CAbb = col_character(),
-                            Project = col_character()))
+  read_csv(col_types = "cdcddcdc")
 
@@
 
-sddem1 = gather(data=supdem, key="Item", value="Response", 6:33, na.rm=TRUE) 
-sddem1$Sample = 0
-sddem1[sddem1$Project=="AfB", "Sample"] = sddem1[sddem1$Project=="AfB", "AfB_sample"]
-sddem1[sddem1$Project=="ArB", "Sample"] = sddem1[sddem1$Project=="ArB", "ArB_sample"]
-sddem1[sddem1$Project=="AsB", "Sample"] = sddem1[sddem1$Project=="AsB", "AsB_sample"]
-sddem1[sddem1$Project=="AsnB", "Sample"] = sddem1[sddem1$Project=="AsnB", "AsnB_sample"]
-sddem1[sddem1$Project=="ESS", "Sample"] = sddem1[sddem1$Project=="ESS", "ESS_sample"]
-sddem1[sddem1$Project=="LAPOP", "Sample"] = sddem1[sddem1$Project=="LAPOP", "LAPOP_sample"]
-sddem1[sddem1$Project=="LB", "Sample"] = sddem1[sddem1$Project=="LB", "LB_sample"]
-sddem1[sddem1$Project=="NDB", "Sample"] = sddem1[sddem1$Project=="NDB", "NDB_sample"]
-sddem1[sddem1$Project=="Pew", "Sample"] = sddem1[sddem1$Project=="Pew", "Pew_sample"]
-sddem1[sddem1$Project=="WVS", "Sample"] = sddem1[sddem1$Project=="WVS", "WVS_sample"]
-sddem1[sddem1$Project=="CSES", "Sample"] = sddem1[sddem1$Project=="CSES", "CSES_sample"]
+library(MASS)
+library(arm)
+library(dplyr)
+library(tidyr)
+library(rstan)
+library(loo)
+library(ggplot2)
+library(RColorBrewer)
 
-# trim stacked dataset
-sddem1 = sddem1[, -c(6:16)]
-sddem1$Response = ifelse(sddem1$Response==0, NA, sddem1$Response)
-sddem1 = sddem1[!is.na(sddem1$Response), ]
+# options
+rstan_options(auto_write = TRUE)
+options(mc.cores = parallel::detectCores())
 
-# create item by project indicators
-sddem1 = unite(sddem1, ItemProj, c(Project, Item), sep = "_", remove = FALSE)
-sddem1$ItemProj = as.factor(sddem1$ItemProj)
+# working directory
+WD = getwd()
+setwd(WD)
+
+# read support for dem data
+sddem1 = read.csv("supdem raw survey marginals.csv")
+
+# remove NAs
+sddem1 = sddem1[!sddem1$Response==0, ]
 
 # create year by country indicators
-year0 = 1990
+year0 = 1987
 sddem1 = sddem1[sddem1$Year > year0,]
 sddem1 = unite(sddem1, YearCountry, c(Year, Country), sep = "_", remove = FALSE)
-sddem1$YearCountry = as.factor(sddem1$YearCountry)
-
-# create item by project by country indicators
-sddem1 = unite(sddem1, ItemProjCnt, c(ItemProj, Country), sep = "_", remove = FALSE)
-sddem1$ItemProjCnt = as.factor(sddem1$ItemProjCnt)
 
@@
 sddem1 = unite(sddem1, ItemCnt, c(Item, Country), sep = "_", remove = FALSE)
-sddem1$ItemCnt = as.factor(sddem1$ItemCnt)
 
@@
 sddem1 = unite(sddem1, YrProj, c(Year, Project), sep = "_", remove = FALSE)
-sddem1$YrProj = as.factor(sddem1$YrProj)
 
@@
 sddem1 = unite(sddem1, YrProjCnt, c(YrProj, Country), sep = "_", remove = FALSE)
-sddem1$YrProjCnt = as.factor(sddem1$YrProjCnt)
 
@@
 sddem1$Item = as.factor(as.character(sddem1$Item))
-sddem1$ItemProj = as.factor(as.character(sddem1$ItemProj))
 sddem1$ItemCnt = as.factor(as.character(sddem1$ItemCnt))
-sddem1$ItemProjCnt = as.factor(as.character(sddem1$ItemProjCnt))
 sddem1$Project = as.factor(as.character(sddem1$Project))
@@
 sddem1$YrProjCnt = as.factor(as.character(sddem1$YrProjCnt))
-sddem1$Year = as.factor(sddem1$Year-year0)
+sddem1$Year = sddem1$Year-year0
+
+# count data
+dim(sddem1)[1]                   # 3765 national responses
+length(unique(sddem1$Country))   # 150 countries
+length(unique(sddem1$Project))   # 14 projects
+length(unique(sddem1$Item))      # 52 items
+length(unique(sddem1$ItemCnt))   # 1453 item-country
+length(unique(sddem1$YrProjCnt)) # 1390 national surveys
+length(unique(sddem1$Year))      # 27 unique years (out of 30)
+sum(sddem1$Sample) / dim(sddem1)[1] * length(unique(sddem1$YrProjCnt))   # 1,804,450 respondents
 
@@
 cnt.obs.years = rowSums(table(sddem1$Country, sddem1$Year) > 0)
+sort(cnt.obs.years)
 sddem2 = sddem1[sddem1$Country %in% levels(sddem1$Country)[cnt.obs.years > 1], ]
+length(unique(sddem2$Country))   # 137 countries with 2+ years of data
 
-## Stan estimation
+#### Stan estimation
 
 # prepare data for stan
-
 n.items = length(unique(sddem2$Item))
 n.cntrys = length(unique(sddem2$Country))
-n.yrs = 2015-year0
+n.yrs = 2017-year0
 n.proj = length(unique(sddem2$Project))
 n.resp = dim(sddem2)[1]
-n.itm.prj = length(unique(sddem2$ItemProj))
 n.itm.cnt = length(unique(sddem2$ItemCnt))
 n.cntry.yrs = n.cntrys * n.yrs
-n.itm.prj.cnt = length(unique(sddem2$ItemProjCnt))
 n.yr.proj.cnt = length(unique(sddem2$YrProjCnt))
 cntrys = as.numeric(factor(sddem2$Country))
-cnt.names = sort(unique(sddem2$Country))
-cnt.ccode = sddem2[match(cnt.names, sddem2$Country), "COWCode"]
+cnt.names = as.character(sort(unique(sddem2$Country)))
+cnt.code = as.character(sddem2[match(cnt.names, sddem2$Country), "CAbb"])
+cnt.code[83] = "MNE"
+cnt.code[106] = "SRB"
 items = as.numeric(factor(sddem2$Item))
-yrs = as.numeric(sddem2$Year)
+yrs = sddem2$Year
 projs = as.numeric(factor(sddem2$Project))
-itm.prjs = as.numeric(factor(sddem2$ItemProj))
-itm.prj.cnts = as.numeric(factor(sddem2$ItemProjCnt))
 itm.cnts = as.numeric(factor(sddem2$ItemCnt))
-cntry.yrs = as.numeric(sddem2$YearCountry)
 
 # specify data for stan
-dat.2 = list(N=n.resp, K=n.itm.prj, T=n.yrs, J=n.cntrys, P=n.itm.prj.cnt, jj=cntrys, tt=yrs, 
-             pp=itm.prj.cnts, kk=itm.prjs, x=sddem2$Response, samp=sddem2$Sample)
+dat.1 = list(N=n.resp, K=n.items, T=n.yrs, J=n.cntrys, jj=cntrys, tt=yrs, kk=items, 
+             x=sddem2$Response, samp=sddem2$Sample)
+dat.2 = list(N=n.resp, K=n.items, T=n.yrs, J=n.cntrys, P=n.itm.cnt, jj=cntrys, tt=yrs, 
+             pp=itm.cnts, kk=items, x=sddem2$Response, samp=sddem2$Sample)
+sapply(dat.2, summary)
 
 # pars
-pars.5 = c("mu_lambda","sigma_lambda","sigma_delta","sigma_theta","phi","lambda","delta","theta","x_pred","log_lik")
+pars.4 = c("mu_lambda","sigma_lambda","sigma_theta","phi","lambda","theta","x_pred","log_lik")
+pars.5 = c("mu_lambda","sigma_lambda","sigma_delta","sigma_theta","phi","lambda","delta","theta",
+            "x_pred","log_lik")
+pars.6 = c("Sigma","Omega","sigma_delta","sigma_theta","phi","lambda","gamm","delta","theta",
+           "x_pred","log_lik")
 
-# set pars for final run (time-consuming; reduce iterations for trial run)
-n.iter = 1000
-n.warm = 500
+# iterations
+n.iter = 500
+n.warm = 250
 n.chn = 4
-n.thin = 2
+n.thin = 1
 
-## supdem.stan.mod5.stan obtained from dataverse replication files
-stan.mod.5 <- stan(file = "supdem.stan.mod5.stan", data=dat.2, pars=pars.5, 
+# best model from PA article (model 5)
+stan.mod.5 = stan(file='supdem.stan.mod5.stan', data=dat.2, pars=pars.5, 
                    iter=n.iter, warmup=n.warm, chains=n.chn, thin=n.thin, 
                    control=list(adapt_delta=0.99, stepsize=0.02, max_treedepth=11))
+
+# model 5 with different priors
+stan.mod.5.2 = stan(file='supdem.stan.mod5.2.stan', data=dat.2, pars=pars.5, 
+                  iter=n.iter, warmup=n.warm, chains=n.chn, thin=n.thin, 
+                  control=list(adapt_delta=0.99, stepsize=0.02, max_treedepth=11))
+
+# model 5 with item slopes
+stan.mod.6 = stan(file='supdem.stan.mod6.2.stan', data=dat.2, pars=pars.6, 
+                   iter=n.iter, warmup=n.warm, chains=n.chn, thin=n.thin, 
+                   control=list(adapt_delta=0.99, stepsize=0.01, max_treedepth=13))
 ```

### 2020-06-12 paper/dcpo_demsupport.Rmd

@@
 claassen_input_raw1 <- read_csv("data/claassen_input_raw.csv") %>% 
-  filter(!(str_detect(item, "army") & # WVS obs identified as problematic by Claassen (note: these are his years right now)
+  filter(!(str_detect(item, "army") & # WVS obs identified as problematic by Claassen 
     ((country=="Albania" & year==1998) |
@@
 supdem <- get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>% 
-  read_csv(col_types = "cdcddcdc")
+  read_csv(col_types = cols(.default = col_double(), 
+                            Country = col_character(),
+                            CAbb = col_character(),
+                            Project = col_character()))
 
 # Required by the replication file
-p_load(
-  countrycode,
-  MASS,
-  psych,
-  arm,
-  loo,
-  rstanarm,
-  RColorBrewer,
-  devtools,
-  dgo
-)
-
 library(MASS)

### 2020-06-13 R/cy_crosswalk.R
finish cys_crosswalk; save data/cys_crosswalk.RData

@@ -33,5 +33,22 @@ needed <- anti_join(supdem_cy, claassen_input_cy)                   # 131 obs
 
 available <- anti_join(claassen_input_cy, supdem_cy)                # 245 obs
 
-try <- left_join(needed, available, by = c("country", "project"))
+year_fixes <- left_join(needed, available, by = c("country", "project")) %>% # 90 obs
+    mutate(diff = year.x - year.y) %>% 
+    group_by(country, project, year.x) %>% 
+    mutate(closest_to_claassen = min(abs(diff))) %>% 
+    ungroup() %>% 
+    group_by(country, project, year.y) %>% 
+    mutate(closest_to_dcpo = min(abs(diff))) %>% 
+    ungroup() %>% 
+    filter(closest_to_claassen == abs(diff) & closest_to_dcpo == abs(diff) & abs(diff) <= 3) %>% 
+    filter(!(country == "Egypt" & year.x == 2014 & survey == "afrob5")) # double match (it's really afrob6)
+
+cys_crosswalk <- year_fixes %>% 
+    select(country, y_dcpo, y_claassen = year.x, survey)
+
+save(cys_crosswalk,
+     file = "data/cys_crosswalk.RData")
+
+still_needed <- anti_join(needed, year_fixes,  by = c("country", "year" = "year.x", "project")) # 41 obs; listed in issue #5 
 

### 2020-06-13 R/cy_crosswalk.R
add cys_to_drop to data/cys_crosswalk.RData

@@ -47,8 +47,10 @@ year_fixes <- left_join(needed, available, by = c("country", "project")) %>% # 9
 cys_crosswalk <- year_fixes %>% 
     select(country, y_dcpo, y_claassen = year.x, survey)
 
-save(cys_crosswalk,
-     file = "data/cys_crosswalk.RData")
-
 still_needed <- anti_join(needed, year_fixes,  by = c("country", "year" = "year.x", "project")) # 41 obs; listed in issue #5 
 
+cys_to_drop <- anti_join(available, year_fixes, by = c("country", "year" = "year.y", "project")) %>% 
+    select(-y_dcpo)
+
+save(cys_crosswalk, cys_to_drop,
+     file = "data/cys_crosswalk.RData")

### 2020-06-13 paper/dcpo_demsupport.Rmd
fix years in claassen_input_raw1 to match Claassen's; exclude surveys Claassen omits (this doesn't work perfectly yet pending https://github.com/fsolt/DCPOtools/issues/35)

@@
 ```{r claassen_input}
-claassen_input_raw1 <- read_csv("data/claassen_input_raw.csv") %>% 
-  filter(!(str_detect(item, "army") & # WVS obs identified as problematic by Claassen 
+load("data/cys_crosswalk.RData")
+
+claassen_input_raw1 <- read_csv("data/claassen_input_raw.csv", col_types = "cdcddcd") %>% 
+  filter(!(str_detect(item, "army_wvs") & # WVS obs identified as problematic by Claassen 
     ((country=="Albania" & year==1998) |
@@
          (country=="Vietnam" & year==2001)) |
-    (str_detect(item, "strong") &
+    (str_detect(item, "strong_wvs") &
          ((country=="Egypt" & year==2012) |
@@
               (country=="Vietnam" & year==2001))))) %>% 
-  filter(!(survey=="evs2017" | survey == "arabb5" | survey == "eb471")) %>%  # surveys unused by Claassen
+  anti_join(cys_to_drop, by = c("country", "year", "survey")) %>% # surveys unused by Claassen
+  left_join(cys_crosswalk, by = c("country", "year" = "y_dcpo", "survey")) %>% 
+  mutate(year = if_else(!is.na(y_claassen), y_claassen, year)) %>% # use Claassen's year codings
   mutate(item = if_else(item == "strong_amb_1" & year == 2004, "strong_amb_2", item)) # items conflated in amb_combo file

### 2020-06-16 paper/dcpo_demsupport.Rmd
clean up

@@
 ```{r claassen_input_raw}
-claassen_input_raw <- DCPOtools:::claassen_setup(vars = read_csv("data-raw/mood_dem.csv"),
+claassen_input_raw <- DCPOtools:::claassen_setup(vars = read_csv("data-raw/mood_dem.csv",
+                                                                 col_types = "ccccc"),
                                        file = "data/claassen_input_raw.csv")

### 2020-06-19 R/cy_crosswalk.R
use countrycode::countrycode (not countryname) to match DCPOtools:::claassen_setup().  Fixes https://github.com/fsolt/dcpo_dem_mood/commit/1d78156719f3c886ff07831d119a034c97ba9f59#commitcomment-40014819

@@ -7,7 +7,7 @@ supdem <- dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DV
 supdem_cy <- supdem %>%                                             # 1390 obs
     janitor::clean_names() %>% 
     mutate(old_country = country,
-           country = countrycode::countryname(old_country)) %>%
+           country = countrycode::countrycode(old_country, "country.name", "country.name")) %>%
     dplyr::select(country, year, project) %>% 
     unique()
 
@@ -22,9 +22,7 @@ claassen_input_cy <- read_csv("data/claassen_input_raw.csv",
                                p_dcpo == "neb" ~ "ndb",
                                p_dcpo == "sasianb" ~ "sab",
                                TRUE ~ p_dcpo),
-           y_dcpo = year,
-           old_country = country,
-           country = countrycode::countryname(old_country)) %>%
+           y_dcpo = year) %>%
     dplyr::select(country, year, y_dcpo, survey, project) %>% 
     unique()
 

### 2020-06-25 R/cy_crosswalk.R
update

@@ -12,7 +12,7 @@ supdem_cy <- supdem %>%                                             # 1390 obs
     unique()
 
 claassen_input_cy <- read_csv("data/claassen_input_raw.csv",
-                              col_types = "cdcddcd") %>%    # 1560 obs
+                              col_types = "cdcddcd") %>%    # 1578 obs
     mutate(p_dcpo = str_extract(survey, "^[a-z]+"), 
            project = case_when(p_dcpo == "afrob" ~ "afb",
                                p_dcpo == "amb" ~ "lapop",
@@ -30,7 +30,7 @@ no_problems <- inner_join(supdem_cy, claassen_input_cy)             # 1297 obs
 
 needed <- anti_join(supdem_cy, claassen_input_cy)                   # 93 obs
 
-available <- anti_join(claassen_input_cy, supdem_cy)                # 263 obs
+available <- anti_join(claassen_input_cy, supdem_cy)                # 281 obs
 
 year_fixes <- left_join(needed, available, by = c("country", "project")) %>% # 89 obs
     mutate(diff = year.x - year.y) %>% 
@@ -48,7 +48,7 @@ cys_crosswalk <- year_fixes %>%
 
 still_needed <- anti_join(needed, year_fixes,  by = c("country", "year" = "year.x", "project")) # 4 obs; listed in issue #5 
 
-cys_to_drop <- anti_join(available, year_fixes, by = c("country", "year" = "year.y", "project")) %>% 
+cys_to_drop <- anti_join(available, year_fixes, by = c("country", "year" = "year.y", "project")) %>% # 192 obs
     select(-y_dcpo)
 
 save(cys_crosswalk, cys_to_drop,

### 2020-06-25 paper/dcpo_demsupport.Rmd
clean up
incorporate cys_crosswalk into Rmd file (so that updates propagate automatically)

@@
 ```{r claassen_input}
-load("data/cys_crosswalk.RData")
+supdem <- dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>% 
+    read_csv(col_types = "cdcddcdc")
+
+supdem_cy <- supdem %>%                                             # 1390 obs
+    janitor::clean_names() %>% 
+    mutate(old_country = country,
+           country = countrycode::countrycode(old_country, "country.name", "country.name")) %>%
+    dplyr::select(country, year, project) %>% 
+    unique()
+
+claassen_input_cy <- read_csv("data/claassen_input_raw.csv",
+                              col_types = "cdcddcd") %>%           # 1578 obs
+    mutate(p_dcpo = str_extract(survey, "^[a-z]+"), 
+           project = case_when(p_dcpo == "afrob" ~ "afb",
+                               p_dcpo == "amb" ~ "lapop",
+                               p_dcpo == "arabb" ~ "arb",
+                               p_dcpo == "asiab" ~ "asb",
+                               p_dcpo == "asianb" ~ "asnb",
+                               p_dcpo == "neb" ~ "ndb",
+                               p_dcpo == "sasianb" ~ "sab",
+                               TRUE ~ p_dcpo),
+           y_dcpo = year) %>%
+    dplyr::select(country, year, y_dcpo, survey, project) %>% 
+    unique()
+
+no_problems <- inner_join(supdem_cy, claassen_input_cy)             # 1297 obs
+
+needed <- anti_join(supdem_cy, claassen_input_cy)                   # 93 obs
+
+available <- anti_join(claassen_input_cy, supdem_cy)                # 281 obs
+
+year_fixes <- left_join(needed, available, by = c("country", "project")) %>% # 89 obs
+    mutate(diff = year.x - year.y) %>% 
+    group_by(country, project, year.x) %>% 
+    mutate(closest_to_claassen = min(abs(diff))) %>% 
+    ungroup() %>% 
+    group_by(country, project, year.y) %>% 
+    mutate(closest_to_dcpo = min(abs(diff))) %>% 
+    ungroup() %>% 
+    filter(closest_to_claassen == abs(diff) & closest_to_dcpo == abs(diff) & abs(diff) <= 3) %>% 
+    filter(!(country == "Egypt" & year.x == 2014 & survey == "afrob5")) # double match (it's really afrob6)
+
+cys_crosswalk <- year_fixes %>% 
+    select(country, y_dcpo, y_claassen = year.x, survey)
+
+missing_cyps <- anti_join(needed, year_fixes,  by = c("country", "year" = "year.x", "project")) # 4 obs; listed in issue #5
+
+cys_to_drop <- anti_join(available, year_fixes, by = c("country", "year" = "year.y", "project")) %>% # 192 obs
+    select(-y_dcpo)
 
@@
 
-claassen_input <- DCPOtools::format_claassen(claassen_input_raw)
+claassen_input <- DCPOtools::format_claassen(claassen_input_raw1)
+save(claassen_input, file = "data/claassen_input.Rda")
 ```
@@
                            pars = c("mu_lambda", "sigma_lambda", "sigma_delta", "sigma_theta", "phi", "lambda", "delta", "theta", "x_pred","log_lik"),
-                           control = list(adapt_delta=0.99, stepsize=0.02, max_treedepth=15))
+                           control = list(adapt_delta=0.99, stepsize=0.02, max_treedepth=11))
 

### 2020-06-25 R/argon/dcpo_demsupport/R/claassen_m5.R
use data/claassen_input.Rda; this converged on argon in 1h:36m:20s  👀@Tyhcass

@@ -1,31 +1,23 @@
-# remotes::install_github("fsolt/DCPOtools")
-# remotes::install_github("stan-dev/rstantools")
-# remotes::install_github("fsolt/DCPO")
-
 library(tidyverse)
-library(DCPOtools)
 library(rstan)
 
-rstan_options(auto_write = TRUE)
+download.file("https://github.com/fsolt/dcpo_dem_mood/raw/master/data/claassen_input.Rda", "data/claassen_input.Rda")
 
-demsup <-
-    read_csv("data/claassen_replication.csv", col_types = "dcdcddcdd")
+load("data/claassen_input.Rda")
 
-demsup_claassen <- format_claassen(demsup)
-
-claassen_m5 <- stan(file = "R/argon/dcpo_demsupport/R/supdem.stan.mod5.stan",
-                       data = demsup_claassen,
-                       iter = 2000,
-                       chains= 4,
-                       cores = 4,
-		       thin = 2,
-                       pars = c("mu_lambda","sigma_lambda","sigma_delta","sigma_theta","phi","lambda","delta","theta",
-            "x_pred","log_lik"),
-                       control = list(adapt_delta=0.99, stepsize=0.02, max_treedepth=11))
+claassen_m5 <- stan(file = 'R/supdem.stan.mod5.stan',
+                    data = claassen_input,
+                    iter = 2000,
+                    chains= 4,
+                    cores = 4,
+                    thin = 2,
+                    pars = c("mu_lambda","sigma_lambda","sigma_delta","sigma_theta","phi","lambda","delta","theta",
+                             "x_pred","log_lik"),
+                    control = list(adapt_delta=0.99, stepsize=0.02, max_treedepth=11))
 
 save(demsup_claassen, claassen_m5, 
      file = str_c("data/claassen_m5_2k_", 
                   str_replace_all(Sys.time(), "[ :]", "-") %>%
-                    str_replace("2019-", "") %>%
-                    str_replace("-\\d{2}$", ""),
+                      str_replace("20\\d{2}-", "") %>%
+                      str_replace("-\\d{2}$", ""),
                   ".rda"))

### 2020-06-25 paper/dcpo_demsupport.Rmd
extract x_pred from claassen_m5 and save for (a) comparison table 👀@Tyhcass and (b) analysis replication 👀@sammo3182

@@
 ```{r claassen_input}
+# Note that before running `dataverse::get_file()` below, one should set their personal token and server in their system environment first: 
+# Sys.setenv("DATAVERSE_KEY" = "exampleToken")
+# Sys.setenv("DATAVERSE_SERVER" = "dataverse.harvard.edu")
+# These values can be set to persist across R sessions using `usethis::edit_r_environ()`
+
 supdem <- dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>% 
@@
                            iter = 2000,
-                           warmup = 1000,
                            chains = 4,
@@
 
-save(claassen_m5, file = "data/claassen_m5.RData")
+save(claassen_m5, file = "data/claassen_m5.rda")
+
+claassen_m5_x_pred <- rstan::extract(claassen_m5, pars = "x_pred")
+
+save(claassen_input, claassen_m5_x_pred, file = "data/claassen_m5_x_pred.rda")
 ```
 
-```{r replication-model5, eval = FALSE}
-# Before running the following lines, one should set their personal token and server in their system environment first: 
-# Sys.setenv("DATAVERSE_KEY" = "exampleToken")
-# Sys.setenv("DATAVERSE_SERVER" = "dataverse.harvard.edu")
+```{r comparison_table}
 
-supdem <- get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>% 
-  read_csv(col_types = cols(.default = col_double(), 
-                            Country = col_character(),
-                            CAbb = col_character(),
-                            Project = col_character()))
-
-# Required by the replication file
-library(MASS)
-library(arm)
-library(dplyr)
-library(tidyr)
-library(rstan)
-library(loo)
-library(ggplot2)
-library(RColorBrewer)
-
-# options
-rstan_options(auto_write = TRUE)
-options(mc.cores = parallel::detectCores())
-
-# working directory
-WD = getwd()
-setwd(WD)
-
-# read support for dem data
-sddem1 = read.csv("supdem raw survey marginals.csv")
-
-# remove NAs
-sddem1 = sddem1[!sddem1$Response==0, ]
-
-# create year by country indicators
-year0 = 1987
-sddem1 = sddem1[sddem1$Year > year0,]
-sddem1 = unite(sddem1, YearCountry, c(Year, Country), sep = "_", remove = FALSE)
-
-# create item by country indicators
-sddem1 = unite(sddem1, ItemCnt, c(Item, Country), sep = "_", remove = FALSE)
-
-# create year by project indicators
-sddem1 = unite(sddem1, YrProj, c(Year, Project), sep = "_", remove = FALSE)
-
-# create year by project by country indicators
-sddem1 = unite(sddem1, YrProjCnt, c(YrProj, Country), sep = "_", remove = FALSE)
-
-# factorise
-sddem1$Country = as.factor(as.character(sddem1$Country))
-sddem1$Item = as.factor(as.character(sddem1$Item))
-sddem1$ItemCnt = as.factor(as.character(sddem1$ItemCnt))
-sddem1$Project = as.factor(as.character(sddem1$Project))
-sddem1$YrProj = as.factor(as.character(sddem1$YrProj))
-sddem1$YrProjCnt = as.factor(as.character(sddem1$YrProjCnt))
-sddem1$Year = sddem1$Year-year0
-
-# count data
-dim(sddem1)[1]                   # 3765 national responses
-length(unique(sddem1$Country))   # 150 countries
-length(unique(sddem1$Project))   # 14 projects
-length(unique(sddem1$Item))      # 52 items
-length(unique(sddem1$ItemCnt))   # 1453 item-country
-length(unique(sddem1$YrProjCnt)) # 1390 national surveys
-length(unique(sddem1$Year))      # 27 unique years (out of 30)
-sum(sddem1$Sample) / dim(sddem1)[1] * length(unique(sddem1$YrProjCnt))   # 1,804,450 respondents
-
-# drop countries with less than 2 years of data
-cnt.obs.years = rowSums(table(sddem1$Country, sddem1$Year) > 0)
-sort(cnt.obs.years)
-sddem2 = sddem1[sddem1$Country %in% levels(sddem1$Country)[cnt.obs.years > 1], ]
-length(unique(sddem2$Country))   # 137 countries with 2+ years of data
-
-#### Stan estimation
-
-# prepare data for stan
-n.items = length(unique(sddem2$Item))
-n.cntrys = length(unique(sddem2$Country))
-n.yrs = 2017-year0
-n.proj = length(unique(sddem2$Project))
-n.resp = dim(sddem2)[1]
-n.itm.cnt = length(unique(sddem2$ItemCnt))
-n.cntry.yrs = n.cntrys * n.yrs
-n.yr.proj.cnt = length(unique(sddem2$YrProjCnt))
-cntrys = as.numeric(factor(sddem2$Country))
-cnt.names = as.character(sort(unique(sddem2$Country)))
-cnt.code = as.character(sddem2[match(cnt.names, sddem2$Country), "CAbb"])
-cnt.code[83] = "MNE"
-cnt.code[106] = "SRB"
-items = as.numeric(factor(sddem2$Item))
-yrs = sddem2$Year
-projs = as.numeric(factor(sddem2$Project))
-itm.cnts = as.numeric(factor(sddem2$ItemCnt))
-
-# specify data for stan
-dat.1 = list(N=n.resp, K=n.items, T=n.yrs, J=n.cntrys, jj=cntrys, tt=yrs, kk=items, 
-             x=sddem2$Response, samp=sddem2$Sample)
-dat.2 = list(N=n.resp, K=n.items, T=n.yrs, J=n.cntrys, P=n.itm.cnt, jj=cntrys, tt=yrs, 
-             pp=itm.cnts, kk=items, x=sddem2$Response, samp=sddem2$Sample)
-sapply(dat.2, summary)
-
-# pars
-pars.4 = c("mu_lambda","sigma_lambda","sigma_theta","phi","lambda","theta","x_pred","log_lik")
-pars.5 = c("mu_lambda","sigma_lambda","sigma_delta","sigma_theta","phi","lambda","delta","theta",
-            "x_pred","log_lik")
-pars.6 = c("Sigma","Omega","sigma_delta","sigma_theta","phi","lambda","gamm","delta","theta",
-           "x_pred","log_lik")
-
-# iterations
-n.iter = 500
-n.warm = 250
-n.chn = 4
-n.thin = 1
-
-# best model from PA article (model 5)
-stan.mod.5 = stan(file='supdem.stan.mod5.stan', data=dat.2, pars=pars.5, 
-                   iter=n.iter, warmup=n.warm, chains=n.chn, thin=n.thin, 
-                   control=list(adapt_delta=0.99, stepsize=0.02, max_treedepth=11))
-
-# model 5 with different priors
-stan.mod.5.2 = stan(file='supdem.stan.mod5.2.stan', data=dat.2, pars=pars.5, 
-                  iter=n.iter, warmup=n.warm, chains=n.chn, thin=n.thin, 
-                  control=list(adapt_delta=0.99, stepsize=0.02, max_treedepth=11))
-
-# model 5 with item slopes
-stan.mod.6 = stan(file='supdem.stan.mod6.2.stan', data=dat.2, pars=pars.6, 
-                   iter=n.iter, warmup=n.warm, chains=n.chn, thin=n.thin, 
-                   control=list(adapt_delta=0.99, stepsize=0.01, max_treedepth=13))
 ```

### 2020-06-26 paper/dcpo_demsupport.Rmd
add claassen_m5_theta, what @sammo3182 *really* needs to replicate the analysis

@@
 
+claassen_m5_theta <- rstan::extract(claassen_m5, pars = "theta")
+
+save(claassen_m5_theta, file = "data/claassen_m5_theta.rda")
+
 claassen_m5_x_pred <- rstan::extract(claassen_m5, pars = "x_pred")
@@
 ```{r comparison_table}
+load("data/claassen_m5_x_pred.rda")
+
+ivt_claassen <- DCPOtools::internal_validation_tests(claassen_input, claassen_m5_x_pred, "claassen")
+
+# see https://github.com/fsolt/dcpo_article/blob/master/R/validation_table.R for more to add when we have it
 

### 2020-06-26 R/setupcls.R
update

@@ -1,355 +1,0 @@
-
-library(tidyverse)
-library(countrycode)
-library(DCPOtools)
-
-wd <- getwd()
-#surveys_data <- rio::import("https://github.com/fsolt/DCPOtools/blob/master/data/surveys_data.rda") # cannot work
-
-load(paste(wd, '/data-raw/surveys_data.rda',sep = ''))  #load dcpo data
-
-
-##mood_dem_cls deletes evs2017, arob5, eb47 which are not in original data. 
-surveys_demmood <- read_csv("data/mood_dem_cls.csv")  
-##non-respone need to 99
-surveys_demmood$variable <- tolower(surveys_demmood$variable)
-##convert to lowercase with clean replication.
-surveys_demmood <- surveys_demmood %>% drop_na()
-
-surveys_data$subfile[surveys_data$survey == "pew2005_6"] <- NA
-
-########Function for claassen_setup from https://github.com/fsolt/DCPOtools/blob/master/R/claassen_setup.R
-claassen_setup <- function(vars,
-                           datapath = "../data/dcpo_surveys",
-                           file = "",
-                           chime = TRUE) {
-  if ("data.frame" %in% class(vars)) {
-    vars_table <- vars
-  } else {
-    vars_table <- readr::read_csv(vars, col_types = "ccccc")
-  }
-  
-  # Revise countrycode::countrycode to work better with custom names in cc_dcpo
-  body(countrycode)[[2]] <- substitute(
-    if (is.null(custom_dict) | as.list(match.call())[["custom_dict"]] == "cc_dcpo") {
-      if (origin == "country.name") {
-        origin <- "country.name.en"
-      }
-      if (destination == "country.name") {
-        destination <- "country.name.en"
-      }
-      if (origin %in% c("country.name.en", "country.name.de")) {
-        origin <- paste0(origin, ".regex")
-        origin_regex <- TRUE
-      }
-      else {
-        origin_regex <- FALSE
-      }
-    }
-  )
-  
-  # loop rather than purrr to avoid reloading datasets (some are big and slow)
-  all_sets <- list()
-  for (i in seq(nrow(vars_table))) {
-    cat(i, " ")
-    v <- vars_table[i, ]
-    ds <- surveys_data[surveys_data$survey==v$survey, ]
-    
-    # Import dataset (if necessary)
-    if (vars_table[["survey"]][i] != c(0, head(vars_table[["survey"]], -1))[i]) {
-      dataset_path <- file.path(datapath,
[…]

### 2020-06-26 R/argon/dcpo_demsupport/R/claassen_m5.R
save claasen_input with claassen_m5

@@ -15,7 +15,7 @@ claassen_m5 <- stan(file = 'R/supdem.stan.mod5.stan',
                              "x_pred","log_lik"),
                     control = list(adapt_delta=0.99, stepsize=0.02, max_treedepth=11))
 
-save(demsup_claassen, claassen_m5, 
+save(claassen_input, claassen_m5, 
      file = str_c("data/claassen_m5_2k_", 
                   str_replace_all(Sys.time(), "[ :]", "-") %>%
                       str_replace("20\\d{2}-", "") %>%

### 2020-06-26 R/argon/dcpo_demsupport/R/claassen_m5.R
clean up

@@ -1,9 +1,9 @@
 library(tidyverse)
 library(rstan)
 
-download.file("https://github.com/fsolt/dcpo_dem_mood/raw/master/data/claassen_input.Rda", "data/claassen_input.Rda")
+download.file("https://github.com/fsolt/dcpo_dem_mood/raw/master/data/claassen_input.rda", "data/claassen_input.rda")
 
-load("data/claassen_input.Rda")
+load("data/claassen_input.rda")
 
 claassen_m5 <- stan(file = 'R/supdem.stan.mod5.stan',
                     data = claassen_input,

### 2020-06-26 paper/dcpo_demsupport.Rmd
add data/dcpo_replication_input.rda; clean up

@@
 claassen_input <- DCPOtools::format_claassen(claassen_input_raw1)
-save(claassen_input, file = "data/claassen_input.Rda")
+save(claassen_input, file = here::here("data", "claassen_input.rda"))
+
+dcpo_replication_input <- DCPOtools::format_dcpo(claassen_input_raw1)
+save(dcpo_replication_input, file = here::here("data", "dcpo_replication_input.rda"))
 ```

### 2020-06-26 R/argon/dcpo_demsupport/R/processing.R
install DCPO from CRAN; download data/dcpo_replication_input.rda

@@ -1,25 +1,21 @@
-remotes::install_github("fsolt/DCPOtools")
-remotes::install_github("fsolt/DCPO")
+install.packages("DCPO", repos = "https://cloud.r-project.org/")
 
 library(tidyverse)
-library(DCPOtools)
 library(DCPO)
 
-demsup <- read_csv("https://github.com/fsolt/DCPOtools/raw/master/inst/extdata/all_data_demsupport.csv")
+download.file("https://github.com/fsolt/dcpo_dem_mood/raw/master/data/dcpo_replication_input.rda", "data/dcpo_replication_input.rda")
 
-demsup_data <- format_dcpo(demsup %>% with_min_yrs(2),
-                       scale_q = "church_21",
-                       scale_cp = 2)
+load("data/dcpo_replication_input.rda")
 
-out1 <- dcpo(demsup_data,
-                 iter = 2000,
-		 chains = 4,
-		 thin = 2,
-                 pars = c("sd_delta","sd_theta_evolve", "sd_sigma_evolve", "sigma","phi","beta","alpha","delta","theta","y_r_pred","log_lik"))
+dcpo_replication <- dcpo(dcpo_replication_input,
+                         iter = 2000,
+                         chains = 4,
+                         thin = 2,
+                         pars = c("sd_delta","sd_theta_evolve", "sd_sigma_evolve", "sigma","phi","beta","alpha","delta","theta","y_r_pred","log_lik"))
 
-save(demsup_data, out1,
-     file = str_c("data/church_21_2k_",
+save(dcpo_replication_input, dcpo_replication,
+     file = str_c("data/church_lb2_2k_",
                   str_replace_all(Sys.time(), "[ :]", "-") %>%
-                    str_replace("2019-", "") %>%
-                    str_replace("-\\d{2}$", ""),
+                      str_replace("20\\d{2}-", "") %>%
+                      str_replace("-\\d{2}$", ""),
                   ".rda"))

### 2020-06-27 paper/dcpo_demsupport.Rmd
specify arguments correctly for dcpo_replication_input

@@
 
-dcpo_replication_input <- DCPOtools::format_dcpo(claassen_input_raw1)
+dcpo_replication_input <- DCPOtools::format_dcpo(claassen_input_raw1,
+                                                 scale_q = "church_lb",
+                                                 scale_cp = 2)
 save(dcpo_replication_input, file = here::here("data", "dcpo_replication_input.rda"))
@@
 ```{r comparison_table}
-load("data/claassen_m5_x_pred.rda")
+load(here::here("data", "claassen_m5_x_pred.rda"))
 
@@
 
-```{r validation}
-# load(here::here("data", "validation_table.rda"))
-# 
-# validation_table
-```
+<!-- We will probably want to just want to summarize results in writing instead of a table, given that we're comparing just two models, rather than three, and space constraints -->
 
@@
 ## Results
-DCPO results here
+
+### Claassen with uncertainty
+
+### DCPO replication (with uncertainty, of course)
+
+### DCPO, with lots more data
 

### 2020-06-27 paper/dcpo_demsupport.Rmd
add ivt_dcpo

@@
 
+load(here::here("data", "dcpo_replication_y_r_pred.rda"))
+
+ivt_dcpo <- DCPOtools::internal_validation_tests(dcpo_replication_input, dcpo_replication_y_r_pred)
 # see https://github.com/fsolt/dcpo_article/blob/master/R/validation_table.R for more to add when we have it

### 2020-06-27 R/argon/dcpo_demsup_kfold/R/processing.R
install DCPO from CRAN; use data/dcpo_replication_input.rda

@@ -1,27 +1,24 @@
-remotes::install_github("fsolt/DCPOtools")
-remotes::install_github("fsolt/DCPO")
+install.packages("DCPO", repos = "https://cloud.r-project.org/")
 
 library(tidyverse)
-library(DCPOtools)
 library(DCPO)
 
 fold <- commandArgs(trailingOnly=TRUE) %>%
-  as.numeric()
-
-demsup <- read_csv(system.file("extdata", "all_data_demsupport.csv", package = "DCPOtools"))
+    as.numeric()
 
 print(fold)
 
-demsup_data <- format_dcpo(demsup %>% with_min_yrs(3),
-                       scale_q = "church_21",
-                       scale_cp = 2)
+download.file("https://github.com/fsolt/dcpo_dem_mood/raw/master/data/dcpo_replication_input.rda", "data/dcpo_replication_input.rda")
 
-demsup_kfold <- dcpo_xvt(demsup_data,
-                          fold_number = fold, 
-			  number_of_folds = 10,
-                          iter = 500)
+load("data/dcpo_replication_input.rda")
 
-save(demsup_kfold, 
+
+dcpo_kfold <- dcpo_xvt(dcpo_replication_input,
+                       fold_number = fold, 
+                       number_of_folds = 10,
+                       iter = 2000)
+
+save(dcpo_kfold, 
      file = str_c("data/fold_",
-		  fold,
+                  fold,
                   ".rda"))

### 2020-06-27 R/argon/dcpo_demsup_kfold/R/processing.R
save to dcpo_fold_X.rda

@@ -19,6 +19,6 @@ dcpo_kfold <- dcpo_xvt(dcpo_replication_input,
                        iter = 2000)
 
 save(dcpo_kfold, 
-     file = str_c("data/fold_",
+     file = str_c("data/dcpo_fold_",
                   fold,
                   ".rda"))

### 2020-06-29 R/argon/dcpo_demsupport/R/claassen_m5.R
set iter to 3000 and thin to 3

@@ -7,16 +7,16 @@ load("data/claassen_input.rda")
 
 claassen_m5 <- stan(file = 'R/supdem.stan.mod5.stan',
                     data = claassen_input,
-                    iter = 2000,
+                    iter = 3000,
                     chains= 4,
                     cores = 4,
-                    thin = 2,
+                    thin = 3,
                     pars = c("mu_lambda","sigma_lambda","sigma_delta","sigma_theta","phi","lambda","delta","theta",
                              "x_pred","log_lik"),
                     control = list(adapt_delta=0.99, stepsize=0.02, max_treedepth=11))
 
-save(claassen_input, claassen_m5, 
-     file = str_c("data/claassen_m5_2k_", 
+save(claassen_input, claassen_m5,
+     file = str_c("data/claassen_m5_3k_",
                   str_replace_all(Sys.time(), "[ :]", "-") %>%
                       str_replace("20\\d{2}-", "") %>%
                       str_replace("-\\d{2}$", ""),

### 2020-06-29 R/argon/dcpo_demsupport/R/processing.R

@@ -8,13 +8,13 @@ download.file("https://github.com/fsolt/dcpo_dem_mood/raw/master/data/dcpo_repli
 load("data/dcpo_replication_input.rda")
 
 dcpo_replication <- dcpo(dcpo_replication_input,
-                         iter = 2000,
+                         iter = 3000,
                          chains = 4,
-                         thin = 2,
+                         thin = 3,
                          pars = c("sd_delta","sd_theta_evolve", "sd_sigma_evolve", "sigma","phi","beta","alpha","delta","theta","y_r_pred","log_lik"))
 
 save(dcpo_replication_input, dcpo_replication,
-     file = str_c("data/church_lb2_2k_",
+     file = str_c("data/church_lb2_3k_",
                   str_replace_all(Sys.time(), "[ :]", "-") %>%
                       str_replace("20\\d{2}-", "") %>%
                       str_replace("-\\d{2}$", ""),

### 2020-06-29 R/claassen_kfold.R
input claassen_input.rda

@@ -6,23 +6,20 @@ source("R/claassen_xvt.R")
 
 rstan_options(auto_write = TRUE)
 
-demsup <-
-    read_csv("data/claassen_replication.csv", col_types = "dcdcddcdd")
+download.file("https://github.com/fsolt/dcpo_dem_mood/raw/master/data/claassen_input.rda", "data/claassen_input.rda")
 
-demsup_data <- DCPOtools::format_claassen(demsup %>%
-                                              DCPOtools::with_min_yrs(3))
-
+load("data/claassen_input.rda")
 
 claassen_demsup_kfold <- purrr::map(1:10, function(x) {
-    claassen_xvt(demsup_data,
-                 fold_number = 10, # number_of_folds = 10 is the default，
-                 iter = 500)
+  claassen_xvt(claassen_input,
+               fold_number = 10, # number_of_folds = 10 is the default,
+               iter = 500)
 })
 
 xvt_claassen_kfold <-
-    get_claassen_xvt_results(claassen_demsup_kfold)
+  get_claassen_xvt_results(claassen_demsup_kfold)
 
 save(
-    list = ls() %>% str_subset("^(?!demsup)"),
-    file = file.path("data", "kfold", "claassen_demsup_kfold.rda")
+  list = ls() %>% str_subset("^(?!demsup)"),
+  file = file.path("data", "kfold", "claassen_demsup_kfold.rda")
 )

### 2020-06-29 paper/dcpo_demsupport.Rmd
update estimation of claassen_m5 w/ iter = 3000, thin = 3 to ensure convergence

@@
                            data = claassen_input,
-                           iter = 2000,
+                           iter = 3000,
                            chains = 4,
                            cores = 4,
-                           thin = 2,
+                           thin = 3,
                            pars = c("mu_lambda", "sigma_lambda", "sigma_delta", "sigma_theta", "phi", "lambda", "delta", "theta", "x_pred","log_lik"),

### 2020-07-03 paper/dcpo_demsupport_appendix.Rmd
add chunks for dcpo_input_raw and dcpo_input; move replication to appendix

--- 2020-06-29 paper/dcpo_demsupport.Rmd
@@
 claassen_input_cy <- read_csv("data/claassen_input_raw.csv",
-                              col_types = "cdcddcd") %>%           # 1578 obs
+                              col_types = "cdcddcd") %>%           # 1784 obs
     mutate(p_dcpo = str_extract(survey, "^[a-z]+"), 

### 2020-07-03 R/argon/dcpo_demsupport/R/processing.R
update

@@ -3,17 +3,17 @@ install.packages("DCPO", repos = "https://cloud.r-project.org/")
 library(tidyverse)
 library(DCPO)
 
-download.file("https://github.com/fsolt/dcpo_dem_mood/raw/master/data/dcpo_replication_input.rda", "data/dcpo_replication_input.rda")
+download.file("https://github.com/fsolt/dcpo_dem_mood/raw/master/data/dcpo_input.rda", "data/dcpo_input.rda")
 
-load("data/dcpo_replication_input.rda")
+load("data/dcpo_input.rda")
 
-dcpo_replication <- dcpo(dcpo_replication_input,
-                         iter = 3000,
-                         chains = 4,
-                         thin = 3,
-                         pars = c("sd_delta","sd_theta_evolve", "sd_sigma_evolve", "sigma","phi","beta","alpha","delta","theta","y_r_pred","log_lik"))
+dcpo_output <- dcpo(dcpo_input,
+                    iter = 2000,
+                    chains = 4,
+                    thin = 4,
+                    pars = c("sd_delta","sd_theta_evolve", "sd_sigma_evolve", "sigma","phi","beta","alpha","delta","theta","y_r_pred","log_lik"))
 
-save(dcpo_replication_input, dcpo_replication,
+save(dcpo_input, dcpo_output,
      file = str_c("data/church_lb2_3k_",
                   str_replace_all(Sys.time(), "[ :]", "-") %>%
                       str_replace("20\\d{2}-", "") %>%

### 2020-07-03 paper/dcpo_demsupport_appendix.Rmd
with_min_yrs(2) for claassen_input and dcpo_replication_input

@@
     template: svm-latex-ms2.tex
-title: "[dcpo_demsupport]"
+title: "[dcpo_demsupport] Appendix"
 thanks: "Corresponding author: [yuehong-tai@uiowa.edu](mailto:yuehong-tai@uiowa.edu). Current version: `r format(Sys.time(), '%B %d, %Y')`."
@@
 
-<!-- The following text is all cribbed from `fsolt/dcpo_article` and obviously needs heavy revision -->
-
-# Incorporating Uncertainty
-This means not simply employing the point estimates, that is, the means of the posterior distributions [_contra_ @Claassen2020a; @Claassen2020b].
-
-Instead, researchers should follow the recommendations of work using other latent variables [e.g., @Schnakenberg2014; @Crabtree2015] and other measures incorporating uncertainty, such as the Standardized World Income Inequality Database [@Solt2020]: generate many duplicate versions of the analysis dataset, assign to each a different random draw from the posterior distributions of the variables measured with uncertainty, perform the analyses repeatedly on each of these multiple versions of the dataset, and combine the results following the rules set out in @Rubin1987.
-The functional programming tools in the `purrr` package [@Henry2019] make this a matter of just a few additional lines of code.
-
 ```{r claassen_input_raw}
@@
 
-available <- anti_join(claassen_input_cy, supdem_cy)                # 281 obs
+available <- anti_join(claassen_input_cy, supdem_cy)                # 487 obs
 
@@
 
-cys_to_drop <- anti_join(available, year_fixes, by = c("country", "year" = "year.y", "project")) %>% # 192 obs
+cys_to_drop <- anti_join(available, year_fixes, by = c("country", "year" = "year.y", "project")) %>% # 398 obs
     select(-y_dcpo)
@@
   mutate(year = if_else(!is.na(y_claassen), y_claassen, year)) %>% # use Claassen's year codings
-  mutate(item = if_else(item == "strong_amb_1" & year == 2004, "strong_amb_2", item)) # items conflated in amb_combo file
+  mutate(item = if_else(item == "strong_amb_1" & year == 2004, "strong_amb_2", item)) %>% # items conflated in amb_combo file
+  with_min_yrs(2)
 
@@
 
-# A Better Measure of Democratic Support
-The DCPO model is estimated using the `DCPO` package for R [@Solt2020a], which is written in the Stan probabilistic programming language [@StanDevTeam2019a; @StanDevTeam2019b].
-
-## Relative Fit
-<!-- We'll only compare Model 5 and DCPO and save ourselves the heartache of dealing with dgirt, but the comparison needs updated with the full dataset -->
-To assess the ability of the DCPO model to fit public opinion data relative to the two alternative approaches, I use the set of survey questions on support for democracy employed in @Claassen2019 [, 7-8].
-
-The first three columns of Table \ref{tab:validation_table} present the results of an internal validation test, that is, a test that uses the same data that was used to fit the model [see, e.g., @Claassen2019, 9].
-In column 1, the mean absolute error (MAE) measures the average difference between the observed proportion of survey respondents in country $k$ in year $t$ with replies to question $q$ with a response at least as positive as response $r$ (or with an affirmative response, in the case of Claassen's [-@Claassen2019] Model 5) and the model's predicted proportion across all countries, years, questions, and response categories.
-Given, however, that Claassen's [-@Claassen2019] Model 5 is fit to dichotomized data, while the @Caughey2019 and DCPO models are fit to the original, possibly ordinal, survey data, which have higher variance, comparing the MAE across all three models can be somewhat misleading.
-Therefore, the MAE of the country means---the average proportions answering affirmatively (for Claassen's [-@Claassen2019] Model 5) or with a response at least as positive as response $r$ (for @Caughey2019 and DCPO) in each country across all years and all questions---serve as a baseline [see @Claassen2019, 11-12]; these appear in column 2.
-The percentage reduction in MAE achieved by each model, listed in column 3, represents the improvement in fit compared to this baseline.
-
-The last three columns of Table \ref{tab:validation_table} present the results of an external validation test, a test of the models' ability to predict out-of-sample survey responses.
-This test employs $k$-fold validation with 10 folds, that is, it randomly divides the available country-year-questions into tenths and then sequentially treats each tenth as a test set to be predicted while fitting the model on a training set consisting of the other nine tenths of the data.
-Column 4 shows the mean of the MAEs of the ten resulting sets of out-of-sample predictions, while column 5 presents the mean improvement over of these ten MAEs over their respective ten country-mean MAEs.
-Column 6 reports the discrepancy between the percentage of all response proportions that fall within their corresponding predictions' 80% confidence intervals and the expected 80%; it therefore provides a gauge of the accuracy of the models' estimates of uncertainty.
-A negative value in this column indicate that less than 80% of the observed out-of-sample survey proportions are included with the model's predictions' nominal 80% credible intervals, and so its uncertainty estimates are overconfident, while a positive value indicates the opposite, that more than 80% of the observed proportions fall within the credible intervals and so the model's uncertainty estimates are overly conservative.
-
-<!-- We will probably want to just want to summarize results in writing instead of a table, given that we're comparing just two models, rather than three, and space constraints -->
-
-Comparing first the results for Claassen's [-@Claassen2019] Model 5 with those for the @Caughey2019 model reveals that, at least for this set of survey questions, while the former has a smaller MAE, the latter accounts for a larger percentage of the variation in its source data left unexplained by its respective country-means model.
-This is true both in the internal validation test and on average across the ten folds of the external validation test.
-Again, this discrepancy is possible due to the greater variance in the survey data when its ordinal nature is preserved, as in the @Caughey2019 model, rather than dichotomized, as in Claassen's [-@Claassen2019] approach.
-An examination of column 6 reveals that the @Caughey2019 model yielded predictions with credible intervals that are much too narrow, encompassing only about 13% of the actual sample observations, while those for Claassen's [-@Claassen2019] Model 5 were slightly too conservative.^[
-The relatively poor uncertainty estimates of the @Caughey2019 model are similar to those found for the dichotomous version presented in @Caughey2015 by @Claassen2019 [, 12].]
-
-However, it is the DCPO model that provides what is unambiguously the best fit.
-It features the smallest mean absolute error: on average, in the internal validation test its predictions are just over 3 percentage points away from the actual sample observations, and in the external validation test they are only 5.5 percentage points away from the actual out-of-sample observations.
-In both cases, these represent the largest percentage improvement over the country-means MAE.
-Further, in the external validation test, the DCPO credible intervals come closest to matching the nominal 80% level of any of the three models.
-
-## Results
-
-### Claassen with uncertainty
-
-### DCPO replication (with uncertainty, of course)
-
-### DCPO, with lots more data
-
 # Conclusion

### 2020-07-03 paper/dcpo_demsupport.Rmd
clean up

--- 2020-06-27 paper/dcpo_demsupport.Rmd
@@
   affiliation: University of Iowa
-abstract: ""
+abstract: "Public opinion’s effect on democratic institutions is important and long-studied topic.
+Claassen (2020) renewed attention to this question by using a Bayesian latent variable approach to measure mass democratic support from survey data and concluded such support has a positive effect on subsequent democratic change and especially on democracy’s endurance once in place.
+In this article, we reexamine the question, bringing more survey data on democratic support; a superior measure, Dynamic Comparative Public Opinion (DCPO); and an improved methodological approach that takes the uncertainty in this measure into account.
+Our results [further reinforce/contradict] the long-held view that democracies depend on public support to survive."
 keywords: ""
@@
 
+# More Data
+
+```{r dcpo_input_raw}
+dcpo_input_raw <- DCPOtools::dcpo_setup(vars = read_csv("data-raw/mood_dem.csv",
+                                                          col_types = "cccccc"),
+                                          file = "data/dcpo_input_raw.csv")
+```
+
+```{r dcpo_input}
+dcpo_input_raw2 <- read_csv("data/dcpo_input_raw.csv", col_types = "cdcddcd") %>% 
+  filter(!(str_detect(item, "army_wvs") & # WVS obs identified as problematic by Claassen 
+    ((country=="Albania" & year==1998) |
+         (country=="Indonesia" & (year==2001 | year==2006)) |
+         (country=="Iran" & year==2000) |
+         (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
+         (country=="Vietnam" & year==2001)) |
+    (str_detect(item, "strong_wvs") &
+         ((country=="Egypt" & year==2012) |
+              (country=="Iran" & (year==2000 | year==2007)) | # 2005 in Claassen
+              (country=="India") |
+              (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
+              (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
+              (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
+              (country=="Vietnam" & year==2001))))) %>%
+  with_min_yrs(2)
+
+dcpo_input <- DCPOtools::format_dcpo(dcpo_input_raw1,
+                                     scale_q = "church_lb",
+                                     scale_cp = 2)
+save(dcpo_input, file = here::here("data", "dcpo_input.rda"))
+```
+
+# A Better Measure of Democratic Support
+The DCPO model is estimated using the `DCPO` package for R [@Solt2020a], which is written in the Stan probabilistic programming language [@StanDevTeam2019a; @StanDevTeam2019b].
+
 # Incorporating Uncertainty
@@
 
-```{r claassen_input_raw}
-claassen_input_raw <- DCPOtools:::claassen_setup(vars = read_csv("data-raw/mood_dem.csv",
-                                                                 col_types = "ccccc"),
-                                       file = "data/claassen_input_raw.csv")
-```
-
-```{r claassen_input}
-# Note that before running `dataverse::get_file()` below, one should set their personal token and server in their system environment first: 
-# Sys.setenv("DATAVERSE_KEY" = "exampleToken")
-# Sys.setenv("DATAVERSE_SERVER" = "dataverse.harvard.edu")
-# These values can be set to persist across R sessions using `usethis::edit_r_environ()`
-
-supdem <- dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>% 
-    read_csv(col_types = "cdcddcdc")
-
-supdem_cy <- supdem %>%                                             # 1390 obs
-    janitor::clean_names() %>% 
-    mutate(old_country = country,
-           country = countrycode::countrycode(old_country, "country.name", "country.name")) %>%
-    dplyr::select(country, year, project) %>% 
-    unique()
-
-claassen_input_cy <- read_csv("data/claassen_input_raw.csv",
-                              col_types = "cdcddcd") %>%           # 1578 obs
-    mutate(p_dcpo = str_extract(survey, "^[a-z]+"), 
-           project = case_when(p_dcpo == "afrob" ~ "afb",
-                               p_dcpo == "amb" ~ "lapop",
-                               p_dcpo == "arabb" ~ "arb",
-                               p_dcpo == "asiab" ~ "asb",
-                               p_dcpo == "asianb" ~ "asnb",
-                               p_dcpo == "neb" ~ "ndb",
-                               p_dcpo == "sasianb" ~ "sab",
-                               TRUE ~ p_dcpo),
-           y_dcpo = year) %>%
-    dplyr::select(country, year, y_dcpo, survey, project) %>% 
-    unique()
-
-no_problems <- inner_join(supdem_cy, claassen_input_cy)             # 1297 obs
-
-needed <- anti_join(supdem_cy, claassen_input_cy)                   # 93 obs
-
-available <- anti_join(claassen_input_cy, supdem_cy)                # 281 obs
-
-year_fixes <- left_join(needed, available, by = c("country", "project")) %>% # 89 obs
-    mutate(diff = year.x - year.y) %>% 
-    group_by(country, project, year.x) %>% 
-    mutate(closest_to_claassen = min(abs(diff))) %>% 
-    ungroup() %>% 
-    group_by(country, project, year.y) %>% 
-    mutate(closest_to_dcpo = min(abs(diff))) %>% 
-    ungroup() %>% 
-    filter(closest_to_claassen == abs(diff) & closest_to_dcpo == abs(diff) & abs(diff) <= 3) %>% 
-    filter(!(country == "Egypt" & year.x == 2014 & survey == "afrob5")) # double match (it's really afrob6)
-
-cys_crosswalk <- year_fixes %>% 
-    select(country, y_dcpo, y_claassen = year.x, survey)
-
-missing_cyps <- anti_join(needed, year_fixes,  by = c("country", "year" = "year.x", "project")) # 4 obs; listed in issue #5
-
-cys_to_drop <- anti_join(available, year_fixes, by = c("country", "year" = "year.y", "project")) %>% # 192 obs
-    select(-y_dcpo)
-
-claassen_input_raw1 <- read_csv("data/claassen_input_raw.csv", col_types = "cdcddcd") %>% 
-  filter(!(str_detect(item, "army_wvs") & # WVS obs identified as problematic by Claassen 
-    ((country=="Albania" & year==1998) |
-         (country=="Indonesia" & (year==2001 | year==2006)) |
-         (country=="Iran" & year==2000) |
-         (country=="Pakistan" & (year==1997 | year==2001)) | #in DCPO,it is 1997 instead of 1996
-         (country=="Vietnam" & year==2001)) |
-    (str_detect(item, "strong_wvs") &
-         ((country=="Egypt" & year==2012) |
-              (country=="Iran" & (year==2000 | year==2007)) | #in DCPO, the year is 2007 rather than 2005
-              (country=="India") |
-              (country=="Pakistan" & (year==1997 | year==2001)) | #in DCPO,it is 1997 instead of 1996
-              (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
-              (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
-              (country=="Vietnam" & year==2001))))) %>% 
-  anti_join(cys_to_drop, by = c("country", "year", "survey")) %>% # surveys unused by Claassen
-  left_join(cys_crosswalk, by = c("country", "year" = "y_dcpo", "survey")) %>% 
-  mutate(year = if_else(!is.na(y_claassen), y_claassen, year)) %>% # use Claassen's year codings
-  mutate(item = if_else(item == "strong_amb_1" & year == 2004, "strong_amb_2", item)) # items conflated in amb_combo file
-
-claassen_input <- DCPOtools::format_claassen(claassen_input_raw1)
-save(claassen_input, file = here::here("data", "claassen_input.rda"))
-
-dcpo_replication_input <- DCPOtools::format_dcpo(claassen_input_raw1,
-                                                 scale_q = "church_lb",
-                                                 scale_cp = 2)
-save(dcpo_replication_input, file = here::here("data", "dcpo_replication_input.rda"))
-```
-
-```{r claassen_m5, eval=FALSE}
-claassen_m5 <- rstan::stan(file = 'R/argon/dcpo_demsupport/R/supdem.stan.mod5.stan',
-                           data = claassen_input,
-                           iter = 2000,
-                           chains = 4,
-                           cores = 4,
-                           thin = 2,
-                           pars = c("mu_lambda", "sigma_lambda", "sigma_delta", "sigma_theta", "phi", "lambda", "delta", "theta", "x_pred","log_lik"),
-                           control = list(adapt_delta=0.99, stepsize=0.02, max_treedepth=11))
-
-save(claassen_m5, file = "data/claassen_m5.rda")
-
-claassen_m5_theta <- rstan::extract(claassen_m5, pars = "theta")
-
-save(claassen_m5_theta, file = "data/claassen_m5_theta.rda")
-
-claassen_m5_x_pred <- rstan::extract(claassen_m5, pars = "x_pred")
-
-save(claassen_input, claassen_m5_x_pred, file = "data/claassen_m5_x_pred.rda")
-```
-
-```{r comparison_table}
-load(here::here("data", "claassen_m5_x_pred.rda"))
-
-ivt_claassen <- DCPOtools::internal_validation_tests(claassen_input, claassen_m5_x_pred, "claassen")
-
-# see https://github.com/fsolt/dcpo_article/blob/master/R/validation_table.R for more to add when we have it
-
-```
-
-# A Better Measure of Democratic Support
-The DCPO model is estimated using the `DCPO` package for R [@Solt2020a], which is written in the Stan probabilistic programming language [@StanDevTeam2019a; @StanDevTeam2019b].
-
-## Relative Fit
-<!-- We'll only compare Model 5 and DCPO and save ourselves the heartache of dealing with dgirt, but the comparison needs updated with the full dataset -->
-To assess the ability of the DCPO model to fit public opinion data relative to the two alternative approaches, I use the set of survey questions on support for democracy employed in @Claassen2019 [, 7-8].
-
-The first three columns of Table \ref{tab:validation_table} present the results of an internal validation test, that is, a test that uses the same data that was used to fit the model [see, e.g., @Claassen2019, 9].
-In column 1, the mean absolute error (MAE) measures the average difference between the observed proportion of survey respondents in country $k$ in year $t$ with replies to question $q$ with a response at least as positive as response $r$ (or with an affirmative response, in the case of Claassen's [-@Claassen2019] Model 5) and the model's predicted proportion across all countries, years, questions, and response categories.
-Given, however, that Claassen's [-@Claassen2019] Model 5 is fit to dichotomized data, while the @Caughey2019 and DCPO models are fit to the original, possibly ordinal, survey data, which have higher variance, comparing the MAE across all three models can be somewhat misleading.
-Therefore, the MAE of the country means---the average proportions answering affirmatively (for Claassen's [-@Claassen2019] Model 5) or with a response at least as positive as response $r$ (for @Caughey2019 and DCPO) in each country across all years and all questions---serve as a baseline [see @Claassen2019, 11-12]; these appear in column 2.
-The percentage reduction in MAE achieved by each model, listed in column 3, represents the improvement in fit compared to this baseline.
-
-The last three columns of Table \ref{tab:validation_table} present the results of an external validation test, a test of the models' ability to predict out-of-sample survey responses.
-This test employs $k$-fold validation with 10 folds, that is, it randomly divides the available country-year-questions into tenths and then sequentially treats each tenth as a test set to be predicted while fitting the model on a training set consisting of the other nine tenths of the data.
-Column 4 shows the mean of the MAEs of the ten resulting sets of out-of-sample predictions, while column 5 presents the mean improvement over of these ten MAEs over their respective ten country-mean MAEs.
-Column 6 reports the discrepancy between the percentage of all response proportions that fall within their corresponding predictions' 80% confidence intervals and the expected 80%; it therefore provides a gauge of the accuracy of the models' estimates of uncertainty.
-A negative value in this column indicate that less than 80% of the observed out-of-sample survey proportions are included with the model's predictions' nominal 80% credible intervals, and so its uncertainty estimates are overconfident, while a positive value indicates the opposite, that more than 80% of the observed proportions fall within the credible intervals and so the model's uncertainty estimates are overly conservative.
-
-<!-- We will probably want to just want to summarize results in writing instead of a table, given that we're comparing just two models, rather than three, and space constraints -->
-
-Comparing first the results for Claassen's [-@Claassen2019] Model 5 with those for the @Caughey2019 model reveals that, at least for this set of survey questions, while the former has a smaller MAE, the latter accounts for a larger percentage of the variation in its source data left unexplained by its respective country-means model.
-This is true both in the internal validation test and on average across the ten folds of the external validation test.
-Again, this discrepancy is possible due to the greater variance in the survey data when its ordinal nature is preserved, as in the @Caughey2019 model, rather than dichotomized, as in Claassen's [-@Claassen2019] approach.
-An examination of column 6 reveals that the @Caughey2019 model yielded predictions with credible intervals that are much too narrow, encompassing only about 13% of the actual sample observations, while those for Claassen's [-@Claassen2019] Model 5 were slightly too conservative.^[
-The relatively poor uncertainty estimates of the @Caughey2019 model are similar to those found for the dichotomous version presented in @Caughey2015 by @Claassen2019 [, 12].]
-
-However, it is the DCPO model that provides what is unambiguously the best fit.
-It features the smallest mean absolute error: on average, in the internal validation test its predictions are just over 3 percentage points away from the actual sample observations, and in the external validation test they are only 5.5 percentage points away from the actual out-of-sample observations.
-In both cases, these represent the largest percentage improvement over the country-means MAE.
-Further, in the external validation test, the DCPO credible intervals come closest to matching the nominal 80% level of any of the three models.
-
-## Results
-
-### Claassen with uncertainty
-
-### DCPO replication (with uncertainty, of course)
-
-### DCPO, with lots more data
+# Results
 

### 2020-07-03 paper/dcpo_demsupport.Rmd
compare n

@@
 ```{r dcpo_input}
-dcpo_input_raw2 <- read_csv("data/dcpo_input_raw.csv", col_types = "cdcddcd") %>% 
+dcpo_input_raw1 <- read_csv("data/dcpo_input_raw.csv", col_types = "cdcddcd") %>% 
   filter(!(str_detect(item, "army_wvs") & # WVS obs identified as problematic by Claassen 
@@
 
+```{r compare_n}
+supdem <- dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>%
+  read_csv(col_types = "cdcddcdc")
+
+supdem_ncy <- supdem %>%
+  dplyr::select(Country, Year) %>% 
+  unique() %>% 
+  nrow()
+
+supdem_ncyi <- supdem %>%
+  dplyr::select(Country, Year, Item) %>% 
+  unique() %>% 
+  nrow()
+
+dcpo_input_ncy <- dcpo_input_raw1 %>% 
+  dplyr::select(country, year) %>% 
+  unique() %>% 
+  nrow()
+
+dcpo_input_ncyi <- dcpo_input_raw1 %>% 
+  dplyr::select(country, year, item) %>% 
+  unique() %>% 
+  nrow()
+
+increase_cy <- round((dcpo_input_ncy/supdem_ncy - 1) * 100, 1)
+increase_cyi <- round((dcpo_input_ncyi/supdem_ncyi - 1) * 100, 1)
+```
+
 # A Better Measure of Democratic Support

### 2020-07-03 paper/dcpo_demsupport.Rmd
clean up

@@
               (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
-              (country=="Vietnam" & year==2001))))) %>%
+              (country=="Vietnam" & year==2001))) |
+      (country %in% c("Puerto Rico", "Northern Ireland", 
+                      "SrpSka Republic", "Hong Kong SAR China")))) %>%
   with_min_yrs(2)
@@
 supdem <- dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>%
-  read_csv(col_types = "cdcddcdc")
+  read_csv(col_types = "cdcddcdc") %>% 
+  janitor::clean_names() %>% 
+  with_min_yrs(2)
 
 supdem_ncy <- supdem %>%
-  dplyr::select(Country, Year) %>% 
+  dplyr::select(country, year) %>% 
   unique() %>% 
@@
 supdem_ncyi <- supdem %>%
-  dplyr::select(Country, Year, Item) %>% 
+  dplyr::select(country, year, item) %>% 
   unique() %>% 

### 2020-07-03 R/argon/dcpo_demsupport/R/processing.R
only install DCPO if not installed

@@ -1,7 +1,6 @@
-install.packages("DCPO", repos = "https://cloud.r-project.org/")
-
 library(tidyverse)
-library(DCPO)
+if (!require("DCPO")) install.packages("DCPO", repos = "https://cloud.r-project.org/"); library(DCPO)
+
 
 download.file("https://github.com/fsolt/dcpo_dem_mood/raw/master/data/dcpo_input.rda", "data/dcpo_input.rda")
 

### 2020-07-04 R/argon/dcpo_demsupport/R/processing.R
use object to set iter; use iter to set thin and filename

@@ -6,14 +6,16 @@ download.file("https://github.com/fsolt/dcpo_dem_mood/raw/master/data/dcpo_input
 
 load("data/dcpo_input.rda")
 
+iter <- 3000
+
 dcpo_output <- dcpo(dcpo_input,
-                    iter = 2000,
+                    iter = iter,
                     chains = 4,
-                    thin = 4,
+                    thin = iter/500, # this yields 250 draws per chain, 1000 draws total
                     pars = c("sd_delta","sd_theta_evolve", "sd_sigma_evolve", "sigma","phi","beta","alpha","delta","theta","y_r_pred","log_lik"))
 
 save(dcpo_input, dcpo_output,
-     file = str_c("data/church_lb2_3k_",
+     file = str_c("data/church_lb2_", round(iter/1000), "k_",
                   str_replace_all(Sys.time(), "[ :]", "-") %>%
                       str_replace("20\\d{2}-", "") %>%
                       str_replace("-\\d{2}$", ""),

### 2020-07-04 paper/dcpo_demsupport.Rmd
clean up

@@
 dcpo_input_raw1 <- read_csv("data/dcpo_input_raw.csv", col_types = "cdcddcd") %>% 
-  filter(!(str_detect(item, "army_wvs") & # WVS obs identified as problematic by Claassen 
+  filter(!(str_detect(survey, "army_wvs") & # WVS obs identified as problematic by Claassen 
                  ((country=="Albania" & year==1998) |
@@
 
+```{r country_years}
+dcpo_input_cy <- dcpo_input_raw1 %>% 
+  dplyr::select(country, year) %>% 
+  unique()
+
+save(dcpo_input_cy, file = here::here("data", "dcpo_input_cy.rda"))
+```
+
 # Incorporating Uncertainty

### 2020-07-04 R/argon/dcpo_demsupport_kfold/R/processing.R
rename R/argon/dcpo_demsupport_kfold/*

@@ -1,19 +1,17 @@
-install.packages("DCPO", repos = "https://cloud.r-project.org/")
-
 library(tidyverse)
-library(DCPO)
+if (!require("DCPO")) install.packages("DCPO", repos = "https://cloud.r-project.org/"); library(DCPO)
 
 fold <- commandArgs(trailingOnly=TRUE) %>%
     as.numeric()
 
 print(fold)
 
-download.file("https://github.com/fsolt/dcpo_dem_mood/raw/master/data/dcpo_replication_input.rda", "data/dcpo_replication_input.rda")
+download.file("https://github.com/fsolt/dcpo_dem_mood/raw/master/data/dcpo_input.rda", "data/dcpo_input.rda")
 
-load("data/dcpo_replication_input.rda")
+load("data/dcpo_input.rda")
 
 
-dcpo_kfold <- dcpo_xvt(dcpo_replication_input,
+dcpo_kfold <- dcpo_xvt(dcpo_input,
                        fold_number = fold, 
                        number_of_folds = 10,
                        iter = 2000)

### 2020-07-04 paper/dcpo_demsupport_appendix.Rmd
save claassen_replication_input.rda

@@
 
-claassen_input <- DCPOtools::format_claassen(claassen_input_raw1)
-save(claassen_input, file = here::here("data", "claassen_input.rda"))
+claassen_replication_input <- DCPOtools::format_claassen(claassen_input_raw1)
+save(claassen_replication_input, file = here::here("data", "claassen_replication_input.rda"))
 

### 2020-07-04 R/argon/dcpo_demsupport_rep/R/claassen_m5_rep.R
add R/argon/dcpo_demsupport_rep/

@@ -1,0 +1,25 @@
+library(tidyverse)
+library(rstan)
+
+download.file("https://github.com/fsolt/dcpo_dem_mood/raw/master/data/claassen_replication_input.rda", "data/claassen_replication_input.rda")
+
+load("data/claassen_replication_input.rda")
+
+iter <- 3000
+
+claassen_m5 <- stan(file = 'R/supdem.stan.mod5.stan',
+                    data = claassen_replication_input,
+                    iter = iter,
+                    chains= 4,
+                    cores = 4,
+                    thin = iter/500,
+                    pars = c("mu_lambda","sigma_lambda","sigma_delta","sigma_theta","phi","lambda","delta","theta",
+                             "x_pred","log_lik"),
+                    control = list(adapt_delta=0.99, stepsize=0.02, max_treedepth=11))
+
+save(claassen_replication_input, claassen_m5,
+     file = str_c("data/claassen_m5_rep_", round(iter/1000), "k_",
+                  str_replace_all(Sys.time(), "[ :]", "-") %>%
+                      str_replace("20\\d{2}-", "") %>%
+                      str_replace("-\\d{2}$", ""),
+                  ".rda"))

### 2020-07-04 R/argon/dcpo_demsupport_rep/R/claassen_m5_rep.sh

@@ -1,0 +1,4 @@
+#!/bin/sh
+
+module load R/3.5.1_gcc-5.4.0
+Rscript R/claassen_m5_rep.R

### 2020-07-04 R/argon/dcpo_demsupport_rep/R/processing_rep.R

@@ -1,0 +1,22 @@
+library(tidyverse)
+if (!require("DCPO")) install.packages("DCPO", repos = "https://cloud.r-project.org/"); library(DCPO)
+
+
+download.file("https://github.com/fsolt/dcpo_dem_mood/raw/master/data/dcpo_replication_input.rda", "data/dcpo_replication_input.rda")
+
+load("data/dcpo_replication_input.rda")
+
+iter <- 3000
+
+dcpo_output <- dcpo(dcpo_replication_input,
+                    iter = iter,
+                    chains = 4,
+                    thin = iter/500, # this yields 250 draws per chain, 1000 draws total
+                    pars = c("sd_delta","sd_theta_evolve", "sd_sigma_evolve", "sigma","phi","beta","alpha","delta","theta","y_r_pred","log_lik"))
+
+save(dcpo_replication_input, dcpo_replication_output,
+     file = str_c("data/church_lb2_rep_", round(iter/1000), "k_",
+                  str_replace_all(Sys.time(), "[ :]", "-") %>%
+                      str_replace("20\\d{2}-", "") %>%
+                      str_replace("-\\d{2}$", ""),
+                  ".rda"))

### 2020-07-04 R/argon/dcpo_demsupport_rep/R/processing_rep.sh

@@ -1,0 +1,4 @@
+#!/bin/sh
+
+module load R/3.5.1_gcc-5.4.0
+Rscript R/processing_rep.R

### 2020-07-04 R/argon/dcpo_demsupport/R/processing_con.R
add R/argon/dcpo_demsupport/R/processing_con*

@@ -1,0 +1,22 @@
+library(tidyverse)
+if (!require("DCPO")) install.packages("DCPO", repos = "https://cloud.r-project.org/"); library(DCPO)
+
+
+download.file("https://github.com/fsolt/dcpo_dem_mood/raw/master/data/dcpo_input_con.rda", "data/dcpo_input_con.rda")
+
+load("data/dcpo_input_con.rda")
+
+iter <- 3000
+
+dcpo_output_con <- dcpo(dcpo_input_con,
+                    iter = iter,
+                    chains = 4,
+                    thin = iter/500,
+                    pars = c("sd_delta","sd_theta_evolve", "sd_sigma_evolve", "sigma","phi","beta","alpha","delta","theta","y_r_pred","log_lik"))
+
+save(dcpo_input_con, dcpo_output_con,
+     file = str_c("data/church4_", round(iter/1000), "k_",
+                  str_replace_all(Sys.time(), "[ :]", "-") %>%
+                      str_replace("20\\d{2}-", "") %>%
+                      str_replace("-\\d{2}$", ""),
+                  ".rda"))

### 2020-07-04 R/argon/dcpo_demsupport/R/processing_con.sh

@@ -1,0 +1,4 @@
+#!/bin/sh
+
+module load R/3.5.1_gcc-5.4.0
+Rscript R/processing_con.R

### 2020-07-06 R/argon/dcpo_demsupport_con_kfold/R/processing.R
add R/argon/dcpo_demsupport_con_kfold/ (lumped version of item coding)

@@ -1,0 +1,23 @@
+library(tidyverse)
+if (!require("DCPO")) install.packages("DCPO", repos = "https://cloud.r-project.org/"); library(DCPO)
+
+fold <- commandArgs(trailingOnly=TRUE) %>%
+    as.numeric()
+
+print(fold)
+
+
+download.file("https://github.com/fsolt/dcpo_dem_mood/raw/master/data/dcpo_input_con.rda", "data/dcpo_input_con.rda")
+
+load("data/dcpo_input_con.rda")
+
+
+dcpo_con_kfold <- dcpo_xvt(dcpo_input_con,
+                           fold_number = fold, 
+                           number_of_folds = 10,
+                           iter = 2000)
+
+save(dcpo_con_kfold, 
+     file = str_c("data/dcpo_con_fold_",
+                  fold,
+                  ".rda"))

### 2020-07-06 R/argon/dcpo_demsupport_con_kfold/R/processing.sh

@@ -1,0 +1,4 @@
+#!/bin/sh
+
+module load R/3.5.1_gcc-5.4.0
+Rscript R/processing.R $SGE_TASK_ID

### 2020-07-06 R/argon/dcpo_demsupport_rep/R/processing_rep.R
clean up

@@ -8,11 +8,11 @@ load("data/dcpo_replication_input.rda")
 
 iter <- 3000
 
-dcpo_output <- dcpo(dcpo_replication_input,
-                    iter = iter,
-                    chains = 4,
-                    thin = iter/500, # this yields 250 draws per chain, 1000 draws total
-                    pars = c("sd_delta","sd_theta_evolve", "sd_sigma_evolve", "sigma","phi","beta","alpha","delta","theta","y_r_pred","log_lik"))
+dcpo_replication_output <- dcpo(dcpo_replication_input,
+                                iter = iter,
+                                chains = 4,
+                                thin = iter/500, # this yields 250 draws per chain, 1000 draws total
+                                pars = c("sd_delta","sd_theta_evolve", "sd_sigma_evolve", "sigma","phi","beta","alpha","delta","theta","y_r_pred","log_lik"))
 
 save(dcpo_replication_input, dcpo_replication_output,
      file = str_c("data/church_lb2_rep_", round(iter/1000), "k_",

### 2020-07-06 R/argon/dcpo_demsupport/R/claassen_m5.R
use object to set iter

@@ -5,18 +5,20 @@ download.file("https://github.com/fsolt/dcpo_dem_mood/raw/master/data/claassen_i
 
 load("data/claassen_input.rda")
 
+iter <- 3000
+
 claassen_m5 <- stan(file = 'R/supdem.stan.mod5.stan',
                     data = claassen_input,
-                    iter = 3000,
+                    iter = iter,
                     chains= 4,
                     cores = 4,
-                    thin = 3,
+                    thin = iter/500,
                     pars = c("mu_lambda","sigma_lambda","sigma_delta","sigma_theta","phi","lambda","delta","theta",
                              "x_pred","log_lik"),
                     control = list(adapt_delta=0.99, stepsize=0.02, max_treedepth=11))
 
 save(claassen_input, claassen_m5,
-     file = str_c("data/claassen_m5_3k_",
+     file = str_c("data/claassen_m5_", round(iter/1000), "k_",
                   str_replace_all(Sys.time(), "[ :]", "-") %>%
                       str_replace("20\\d{2}-", "") %>%
                       str_replace("-\\d{2}$", ""),

### 2020-07-06 paper/dcpo_demsupport_appendix.Rmd
generate claassen_input.rda

@@
 
-```{r claassen_input}
+```{r claassen_replication_input}
 # Note that before running `dataverse::get_file()` below, one should set their personal token and server in their system environment first: 
@@
 
-claassen_input_raw1 <- read_csv("data/claassen_input_raw.csv", col_types = "cdcddcd") %>% 
+claassen_replication_input_raw1 <- read_csv("data/claassen_input_raw.csv", col_types = "cdcddcd") %>% 
   filter(!(str_detect(item, "army_wvs") & # WVS obs identified as problematic by Claassen 
@@
 
+```{r claassen_input}
+claassen_input_raw1 <- read_csv("data/dcpo_input_raw.csv", col_types = "cdcddcd") %>% 
+  filter(!(str_detect(survey, "army_wvs") & # WVS obs identified as problematic by Claassen 
+                 ((country=="Albania" & year==1998) |
+                      (country=="Indonesia" & (year==2001 | year==2006)) |
+                      (country=="Iran" & year==2000) |
+                      (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
+                      (country=="Vietnam" & year==2001)) |
+                 (str_detect(item, "strong_wvs") &
+                      ((country=="Egypt" & year==2012) |
+                           (country=="Iran" & (year==2000 | year==2007)) | # 2005 in Claassen
+                           (country=="India") |
+                           (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
+                           (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
+                           (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
+                           (country=="Vietnam" & year==2001))) |
+                 (country %in% c("Puerto Rico", "Northern Ireland", 
+                                 "SrpSka Republic", "Hong Kong SAR China")))) %>%
+  with_min_yrs(2)
+
+claassen_input <- DCPOtools::format_claassen(claassen_input_raw1)
+save(claassen_input, file = here::here("data", "claassen_input.rda"))
+
+```
+
 # Conclusion

### 2020-07-06 paper/dcpo_demsupport.Rmd
add data/dcpo_theta.rda and data/dcpo_y_r_pred.rda

@@
 
+```{r dcpo, eval=FALSE}
+iter <- 3000
+
+dcpo_output <- dcpo(dcpo_input,
+                    iter = iter,
+                    chains = 4,
+                    thin = iter/500, # this yields 250 draws per chain, 1000 draws total
+                    pars = c("sd_delta","sd_theta_evolve", "sd_sigma_evolve", "sigma","phi","beta","alpha","delta","theta","y_r_pred","log_lik"))
+
+save(dcpo_output, file = here::here("data", "dcpo_output.rda"))
+
+dcpo_theta <- rstan::extract(dcpo_output, pars = "theta")
+
+save(dcpo_theta, file = here::here("data", "dcpo_theta.rda"))
+
+dcpo_y_r_pred <- rstan::extract(dcpo_output, pars = "y_r_pred")
+
+save(dcpo_input, dcpo_x_pred, file = here::here("data", "dcpo_y_r_pred.rda"))
+```
+
 # A Better Measure of Democratic Support

### 2020-07-12 paper/dcpo_demsupport.Rmd
clean up
address #3, uncertainty embedded.

@@
 
+# A Better Measure of Democratic Support
+The DCPO model is estimated using the `DCPO` package for R [@Solt2020a], which is written in the Stan probabilistic programming language [@StanDevTeam2019a; @StanDevTeam2019b].
+
 ```{r dcpo, eval=FALSE}
@@
 
-# A Better Measure of Democratic Support
-The DCPO model is estimated using the `DCPO` package for R [@Solt2020a], which is written in the Stan probabilistic programming language [@StanDevTeam2019a; @StanDevTeam2019b].
-
-```{r country_years}
-dcpo_input_cy <- dcpo_input_raw1 %>% 
-  dplyr::select(country, year) %>% 
-  unique()
-
-save(dcpo_input_cy, file = here::here("data", "dcpo_input_cy.rda"))
-```
-
 # Incorporating Uncertainty
@@
 
+```{r country_years}
+path_df <-
+  list.files(
+    "../data",
+    pattern = ".*_theta.rda",
+    recursive = TRUE,
+    full.names = TRUE
+  ) %>%
+  .[str_which(., "claassen")]
+
+load(path_df)
+
+df_thetaDraw <- map_df(seq(claassen_m5_theta$theta[1, , 1]),
+       function(year) {
+         map_df(seq(claassen_m5_theta$theta[1, 1, ]),
+                function(country) {
+                  df_temp <-
+                    sample(claassen_m5_theta$theta[, year, country],
+                           size = 100,
+                           replace = TRUE) %>%
+                    matrix(ncol = 100) %>%
+                    as_tibble()
+                  df_temp$yearID <- year
+                  df_temp$countryID <- country
+                  return(df_temp)
+                })
+       }) %>% 
+  pivot_longer(
+    df_temp,
+    cols = starts_with("V"),
+    names_to = "draw",
+    values_to = "theta"
+  ) %>% 
+  group_split(draw)
+```
+
 # Results

### 2020-07-12 paper/dcpo_demsupport_appendix.Rmd
address #3, uncertainty embedded.

@@
   DCPOtools, # analysis
+  plm,
   huxtable, kableExtra, modelsummary, # tabulation
@@
 
+```{r claassenWUncertainty}
+load("../data/claassen_replication_input.rda")
+load("../data/claassen_m5_theta.rda")
+
+ls_year <- 1988:2017
+ls_country <- claassen_replication_input$data$country %>% unique
+
+df_thetaDraw <- map_df(seq(ls_year), # year2
+       function(oneYear) {
+         map_df(seq(ls_country),
+                function(oneCountry) {
+                  df_temp <-
+                    sample(claassen_m5_theta$theta[, oneYear, oneCountry],
+                           size = 100, #draw 100 from the distribution
+                           replace = TRUE) %>%
+                    matrix(ncol = 100) %>%
+                    as_tibble()
+                  df_temp$year <- ls_year[oneYear]
+                  df_temp$country <- ls_country[oneCountry]
+                  return(df_temp)
+                })
+       }) %>% 
+  pivot_longer(
+    cols = starts_with("V"),
+    names_to = "draw",
+    values_to = "theta"
+  ) %>% 
+  group_split(draw)
+
+df_controls <- read_csv("../data/Support_democracy_ajps.csv")
+
+df_thetaDraw <- map(df_thetaDraw, function(oneDraw){
+  left_join(oneDraw, df_controls, by = c("country" = "Country", "year" = "Year")) %>% 
+    pdata.frame(index = c("country", "year"))
+})
+
+result_m5O <- plm(Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + plm::lag(SupDem_trim, 1) + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1), pdata.frame(df_controls, index = c("Country", "Year")), model="pooling")
+
+result_m5N <- map(df_thetaDraw, function(aDataset){
+  plm(Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + plm::lag(theta, 1) + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1), model="pooling", data = aDataset)
+})
+
+vcovBK_se <- function(x){
+  vcovBK(x, cluster = "time") %>% 
+    sqrt(diag(.))}
+
+result_betas_m5 <- MIextract(result_m5, fun = coef)
+result_vars_m5 <- MIextract(result_m5, fun = vcovBK_time)
+
+summary(result_m5O)
+summary(MIcombine(results = result_betas_m5, 
+                  variance = result_vars_m5))
+```
+
 # Conclusion

### 2020-07-12 paper/dcpo_demsupport_appendix.Rmd
clean up; use here::here for claassen_input

--- 2020-07-06 paper/dcpo_demsupport_appendix.Rmd
@@
 
-```{r claassen_input_raw}
-claassen_input_raw <- DCPOtools:::claassen_setup(vars = read_csv("data-raw/mood_dem.csv",
-                                                                 col_types = "ccccc"),
-                                       file = "data/claassen_input_raw.csv")
+```{r claassen_input}
+dcpo_input_raw1 <- read_csv("data/dcpo_input_raw.csv", col_types = "cdcddcd") %>% 
+  filter(!(str_detect(survey, "army_wvs") & # WVS obs identified as problematic by Claassen 
+                 ((country=="Albania" & year==1998) |
+                      (country=="Indonesia" & (year==2001 | year==2006)) |
+                      (country=="Iran" & year==2000) |
+                      (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
+                      (country=="Vietnam" & year==2001)) |
+                 (str_detect(item, "strong_wvs") &
+                      ((country=="Egypt" & year==2012) |
+                           (country=="Iran" & (year==2000 | year==2007)) | # 2005 in Claassen
+                           (country=="India") |
+                           (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
+                           (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
+                           (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
+                           (country=="Vietnam" & year==2001))) |
+                 (country %in% c("Puerto Rico", "Northern Ireland", 
+                                 "SrpSka Republic", "Hong Kong SAR China")))) %>%
+  with_min_yrs(2)
+
+claassen_input <- DCPOtools::format_claassen(dcpo_input_raw1)
+save(claassen_input, file = here::here("data", "claassen_input.rda"))
 ```
@@
 
-claassen_input_cy <- read_csv("data/claassen_input_raw.csv",
-                              col_types = "cdcddcd") %>%           # 1784 obs
+claassen_input_cy <- read_csv("data/dcpo_input_raw.csv",
+                              col_types = "cdcddcd") %>%           # 1813 obs
   mutate(p_dcpo = str_extract(survey, "^[a-z]+"), 
@@
 
-available <- anti_join(claassen_input_cy, supdem_cy)                # 487 obs
+available <- anti_join(claassen_input_cy, supdem_cy)                # 516 obs
 
@@
 
-cys_to_drop <- anti_join(available, year_fixes, by = c("country", "year" = "year.y", "project")) %>% # 398 obs
+cys_to_drop <- anti_join(available, year_fixes, by = c("country", "year" = "year.y", "project")) %>% # 427 obs
     select(-y_dcpo)

### 2020-07-12 paper/dcpo_demsupport_appendix.Rmd
clean up: use vcovBK_se in result_vars_m5; specify plm and mitools pkgs; use here::here; specify col_types for df_controls

@@
 ```{r claassenWUncertainty}
-load("../data/claassen_replication_input.rda")
-load("../data/claassen_m5_theta.rda")
+load(here::here("data", "claassen_replication_input.rda"))
+load(here::here("data", "claassen_m5_theta.rda"))
 
 ls_year <- 1988:2017
-ls_country <- claassen_replication_input$data$country %>% unique
+ls_country <- claassen_replication_input$data$country %>% unique()
 
@@
 
-df_controls <- read_csv("../data/Support_democracy_ajps.csv")
+df_controls <- read_csv(here::here("data", "Support_democracy_ajps.csv"),
+                        col_types = cols(
+                          .default = col_double(),
+                          Country = col_character(),
+                          Cnt_code = col_character(),
+                          ISO_code = col_character(),
+                          Region_UN = col_character()))
 
@@
   left_join(oneDraw, df_controls, by = c("country" = "Country", "year" = "Year")) %>% 
-    pdata.frame(index = c("country", "year"))
+    plm::pdata.frame(index = c("country", "year"))
 })
@@
   vcovBK(x, cluster = "time") %>% 
-    sqrt(diag(.))}
+    diag() %>% 
+    sqrt()}
 
-result_betas_m5 <- MIextract(result_m5, fun = coef)
-result_vars_m5 <- MIextract(result_m5, fun = vcovBK_time)
+result_betas_m5 <- mitools::MIextract(result_m5N, fun = coef)
+result_vars_m5 <- mitools::MIextract(result_m5N, fun = vcovBK_se)
 
 summary(result_m5O)
-summary(MIcombine(results = result_betas_m5, 
+summary(mitools::MIcombine(results = result_betas_m5, 
                            variance = result_vars_m5))

### 2020-07-15 paper/dcpo_demsupport_appendix.Rmd
clean up

@@
 
-vcovBK_se <- function(x){
+vcovBK_se <- function(x) {
   vcovBK(x, cluster = "time") %>% 
     diag() %>% 
-    sqrt()}
+    sqrt()
+}
 
@@
                            variance = result_vars_m5))
+
+first_year <- min(claassen_replication_input$data$year)
+
+df_theta <- purrr::map(1:1000, function(x) {
+  claassen_m5_theta$theta[x,,] %>% 
+    as_tibble() %>% 
+    rename_with(~ls_country, .cols = starts_with("V")) %>% 
+    mutate(year = first_year + row_number() - 1) %>% 
+    pivot_longer(cols = ls_country,
+                 names_to = "country",
+                 values_to = "theta") %>%
+    arrange(country, year) %>% 
+    left_join(df_controls, by = c("country" = "Country", "year" = "Year")) %>% 
+    plm::pdata.frame(index = c("country", "year"))
+})
+
+result_m5_1k <- map(df_theta, function(aDataset) {
+  plm(Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + plm::lag(theta, 1) + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1), model="pooling", data = aDataset)
+})
+
+result_betas_m5_1k <- mitools::MIextract(result_m5N_1k, fun = coef)
+result_vars_m5_1k <- mitools::MIextract(result_m5N_1k, fun = vcovBK_se)
+
+summary(mitools::MIcombine(results = result_betas_m5_1k, 
+                           variance = result_vars_m5_1k))
 ```

### 2020-07-15 paper/dcpo_demsupport_appendix.Rmd
add analysis of all 1000 draws (per https://github.com/fsolt/dcpo_dem_mood/issues/3#issuecomment-658743777); clean up

@@
 df_theta <- purrr::map(1:1000, function(x) {
-  claassen_m5_theta$theta[x,,] %>% 
+  claassen_m5_theta$theta[1,,] %>% 
     as_tibble() %>% 

### 2020-07-22 paper/dcpo_demsupport.Rmd

@@
 
+```{r dcpo-uncertainty}
+# Preload function ----
+vcovBK_se <- function(x) {
+  vcovBK(x, cluster = "time") %>% 
+    diag() %>% 
+    sqrt()
+}
+
+# Data input ----
+
+load(here::here("data", "dcpo_input_update.rda"))
+load(here::here("data", "dcpo_theta.rda"))
+
+ls_year <- 1988:2017
+ls_country <- dcpo_input$data$country %>% 
+  unique
+
+df_controls <- read_csv(here::here("data", "control_variables.csv"),
+                        col_types = cols(
+                          .default = col_double(),
+                          Country = col_character(),
+                          Cnt_code = col_character(),
+                          ISO_code = col_character(),
+                          Region_UN = col_character()))
+
+first_year <- min(dcpo_input$data$year)
+
+df_theta <- purrr::map(1:1000, function(anEntry) {
+  dcpo_theta$theta[anEntry,,] %>% 
+    as_tibble() %>% 
+    rename_with(~ ls_country, .cols = starts_with("V")) %>% 
+    mutate(year = first_year + row_number() - 1) %>% 
+    pivot_longer(cols = ls_country,
+                 names_to = "country",
+                 values_to = "theta") %>%
+    arrange(country, year) %>% 
+    left_join(df_controls, by = c("country", "year")) %>% 
+    plm::pdata.frame(index = c("country", "year"))
+})
+
+result_dcpo_1k <- map(df_theta, function(aDataset) {
+  plm(
+    Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + plm::lag(theta, 1) + plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_UN, 1) + plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1),
+    model = "pooling",
+    data = aDataset
+  )
+})
+
+result_betas_dcpo_1k <- mitools::MIextract(result_dcpo_1k, fun = coef)
+result_vars_dcpo_1k <- mitools::MIextract(result_dcpo_1k, fun = vcovBK_se)
+
+summary(mitools::MIcombine(results = result_betas_dcpo_1k, 
+                           variance = result_vars_dcpo_1k))
+
+```
+
 # Conclusion

### 2020-07-26 paper/dcpo_demsupport.Rmd
download supdem from dataverse just one time

@@
 ```{r compare_n}
-supdem <- dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>%
+if (!file.exists("data/supdem raw survey marginals.tab")) {
+  dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>% 
     read_csv(col_types = "cdcddcdc") %>% 
+    write_csv("data/supdem raw survey marginals.tab")
+}
+
+supdem <- read_csv("data/supdem raw survey marginals.tab",
+                   col_types = "cdcddcdc") %>% 
   janitor::clean_names() %>% 

### 2020-07-28 paper/dcpo_demsupport.Rmd
use sprintf not round for increase_cy and increase_cyi
clean up

@@
 
-increase_cy <- round((dcpo_input_ncy/supdem_ncy - 1) * 100, 1)
-increase_cyi <- round((dcpo_input_ncyi/supdem_ncyi - 1) * 100, 1)
+increase_cy <- sprintf("%2.1f", (dcpo_input_ncy/supdem_ncy - 1) * 100, 1)
+increase_cyi <- sprintf("%2.1f", (dcpo_input_ncyi/supdem_ncyi - 1) * 100, 1)
 ```
@@
 
-save(dcpo_input, dcpo_x_pred, file = here::here("data", "dcpo_y_r_pred.rda"))
+save(dcpo_input, dcpo_y_r_pred, file = here::here("data", "dcpo_y_r_pred.rda"))
 ```

### 2020-07-30 paper/dcpo_demsupport.Rmd
fix df_controls encoding issue; fix for painful change in v2.0 as_tibble behavior

@@
 title: "[dcpo_demsupport]"
-thanks: "Corresponding author: [yuehong-tai@uiowa.edu](mailto:yuehong-tai@uiowa.edu). Current version: `r format(Sys.time(), '%B %d, %Y')`."
+thanks: "The authors contributed equally to this work.  Corresponding author: [yuehong-tai@uiowa.edu](mailto:yuehong-tai@uiowa.edu).  Current version: `r format(Sys.time(), '%B %d, %Y')`."
 author:
@@
 
-ls_year <- 1988:2017
-ls_country <- dcpo_input$data$country %>% 
-  unique
+df_controls <- read_csv(here::here("data", "control_variables.csv"),
+                        col_types = cols(.default = col_double(),
+                                         country = col_character(),
+                                         country_name = col_character(),
+                                         ISO = col_character(),
+                                         Region_UN = col_character(),
+                                         Region_UN.1 = col_character())) %>% 
+  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
+         country = countrycode::countrycode(country0, "country.name", "country.name"))
 
-df_controls <- read_csv(here::here("data", "control_variables.csv"),
-                        col_types = cols(
-                          .default = col_double(),
-                          Country = col_character(),
-                          Cnt_code = col_character(),
-                          ISO_code = col_character(),
-                          Region_UN = col_character()))
-
+ls_country <- levels(dcpo_input$data$kk)
 first_year <- min(dcpo_input$data$year)
@@
   dcpo_theta$theta[anEntry,,] %>% 
-    as_tibble() %>% 
-    rename_with(~ ls_country, .cols = starts_with("V")) %>% 
+    as_tibble(.name_repair = ~make.names(., unique = TRUE)) %>% 
+    rename_with(~ ls_country, .cols = everything()) %>% 
     mutate(year = first_year + row_number() - 1) %>% 
-    pivot_longer(cols = ls_country,
+    pivot_longer(cols = all_of(ls_country),
                  names_to = "country",

### 2020-07-30 paper/dcpo_demsupport.Rmd
use better fix for new as_tibble()

@@
   dcpo_theta$theta[anEntry,,] %>% 
-    as_tibble(.name_repair = ~make.names(., unique = TRUE)) %>% 
-    rename_with(~ ls_country, .cols = everything()) %>% 
+    as_tibble(.name_repair = ~ls_country) %>% 
     mutate(year = first_year + row_number() - 1) %>% 

### 2020-08-02 paper/dcpo_demsupport.Rmd
clean up

@@
 
-load(here::here("data", "dcpo_input_update.rda"))
+# load(here::here("data", "dcpo_input_update.rda"))
 load(here::here("data", "dcpo_theta.rda"))
@@
                                          ISO = col_character(),
-                                         Region_UN = col_character(),
-                                         Region_UN.1 = col_character())) %>% 
+                                         Region_UN = col_character())) %>% 
   mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
@@
 result_dcpo_1k <- map(df_theta, function(aDataset) {
-  plm(
-    Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + plm::lag(theta, 1) + plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_UN, 1) + plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1),
+  plm(Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + plm::lag(theta, 1) +
+        plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) +
+        plm::lag(Region_UN, 1) + plm::lag(muslism_prop_2010, 1) +
+        plm::lag(dependence_pc_di, 1),
     model = "pooling",

### 2020-08-02 paper/dcpo_demsupport.Rmd
finishing the visualization of dcpo outcomes, task of #4

@@
   dataverse, # data scraping
-  DCPOtools, # analysis
+  DCPOtools,
+  plm, # analysis
   huxtable, kableExtra, modelsummary, # tabulation
@@
 
-```{r dcpo-uncertainty}
+```{r dcpo-uncertainty, cache=TRUE}
 # Preload function ----
@@
 
-# load(here::here("data", "dcpo_input_update.rda"))
+load(here::here("data", "dcpo_input.rda"))
 load(here::here("data", "dcpo_theta.rda"))
@@
     left_join(df_controls, by = c("country", "year")) %>% 
-    plm::pdata.frame(index = c("country", "year"))
+    pdata.frame(index = c("country", "year"))
 })
@@
         plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) +
-        plm::lag(Region_UN, 1) + plm::lag(muslism_prop_2010, 1) +
+        plm::lag(Region_libdem, 1) + plm::lag(muslism_prop_2010, 1) +
         plm::lag(dependence_pc_di, 1),
@@
 
-summary(mitools::MIcombine(results = result_betas_dcpo_1k, 
-                           variance = result_vars_dcpo_1k))
+df_result_dcpo <- summary(mitools::MIcombine(results = result_betas_dcpo_1k, variance = result_vars_dcpo_1k)) %>% rownames_to_column(var = "term") %>% 
+  rename(conf.low = `(lower`,
+         conf.high = `upper)`, 
+         estimate = results) %>% 
+  filter(!str_detect(term, "(Intercept)"))
+
+```
+
+```{r dcpoVisualization, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO"}
+
+(dwplot(df_result_dcpo, by_2sd = FALSE)) %>% 
+  relabel_predictors(c(`plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
+`plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
+`plm::lag(theta, 1)` = "Democratic Mood(t-1)",
+`plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
+`plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
+`plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
+`plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)", #there's a lag in the replication file
+`plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)")) +
+  geom_vline(xintercept = 0, colour = "grey80", linetype = 2) +
+  theme_minimal() +
+  ggtitle("Dependent Variable: Level of Democracy") + 
+  xlab("Coefficient Estimate") +
+  theme(axis.title.y = element_blank(),
+        legend.position = "none")
 

### 2020-08-02 paper/dcpo_demsupport.Rmd
adding dotwhisker preload

@@
   rstan, # Bayesian estimation
-  tidyverse # data wrangling
+  tidyverse, # data wrangling
+  dotwhisker # visualization
 )
@@
 
-(dwplot(df_result_dcpo, by_2sd = FALSE)) %>% 
-  relabel_predictors(c(`plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
+dwplot(df_result_dcpo, by_2sd = FALSE) %>% 
+  relabel_predictors(
+    c(
+      `plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
       `plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
@@
       `plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
-`plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)", #there's a lag in the replication file
-`plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)")) +
-  geom_vline(xintercept = 0, colour = "grey80", linetype = 2) +
+      `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
+      #there's a lag in the replication file
+      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)"
+    )
+  ) +
+  geom_vline(xintercept = 0,
+             colour = "grey80",
+             linetype = 2) +
   theme_minimal() +

### 2020-08-04 paper/dcpo_demsupport.Rmd
clean up

--- 2020-08-02 paper/dcpo_demsupport.Rmd
@@
 
-# load(here::here("data", "dcpo_input_update.rda"))
 load(here::here("data", "dcpo_theta.rda"))
@@
 result_dcpo_1k <- map(df_theta, function(aDataset) {
-  plm(Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + plm::lag(theta, 1) +
+  plm::plm(Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + plm::lag(theta, 1) +
         plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) +
-        plm::lag(Region_UN, 1) + plm::lag(muslism_prop_2010, 1) +
+        plm::lag(Region_libdem, 1) + plm::lag(muslism_prop_2010, 1) +
         plm::lag(dependence_pc_di, 1),
     model = "pooling",
-    data = aDataset
-  )
+    data = aDataset)
 })

### 2020-08-04 paper/dcpo_demsupport.Rmd
add {plm} to dependencies

@@
   rstan, # Bayesian estimation
+  plm,
   tidyverse # data wrangling
@@
 vcovBK_se <- function(x) {
-  vcovBK(x, cluster = "time") %>% 
+  plm::vcovBK(x, cluster = "time") %>% 
     diag() %>% 

### 2020-08-04 paper/dcpo_demsupport.Rmd

--- 2020-08-02 paper/dcpo_demsupport.Rmd
@@
 
-load(here::here("data", "dcpo_input.rda"))
 load(here::here("data", "dcpo_theta.rda"))
@@
     left_join(df_controls, by = c("country", "year")) %>% 
-    pdata.frame(index = c("country", "year"))
+    plm::pdata.frame(index = c("country", "year"))
 })
@@
 result_dcpo_1k <- map(df_theta, function(aDataset) {
-  plm(Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + plm::lag(theta, 1) +
+  plm::plm(Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + plm::lag(theta, 1) +
         plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) +
@@
     model = "pooling",
-    data = aDataset
-  )
+    data = aDataset)
 })

### 2020-08-04 paper/dcpo_demsupport_appendix.Rmd

--- 2020-07-15 paper/dcpo_demsupport_appendix.Rmd
@@
 
-df_thetaDraw <- map_df(seq(ls_year), # year2
-                       function(oneYear) {
-                         map_df(seq(ls_country),
-                                function(oneCountry) {
-                                  df_temp <-
-                                    sample(claassen_m5_theta$theta[, oneYear, oneCountry],
-                                           size = 100, #draw 100 from the distribution
-                                           replace = TRUE) %>%
-                                    matrix(ncol = 100) %>%
-                                    as_tibble()
-                                  df_temp$year <- ls_year[oneYear]
-                                  df_temp$country <- ls_country[oneCountry]
-                                  return(df_temp)
-                                })
-                       }) %>% 
-  pivot_longer(
-    cols = starts_with("V"),
-    names_to = "draw",
-    values_to = "theta"
-  ) %>% 
-  group_split(draw)
-
-df_controls <- read_csv(here::here("data", "Support_democracy_ajps.csv"),
-                        col_types = cols(
-                          .default = col_double(),
-                          Country = col_character(),
-                          Cnt_code = col_character(),
-                          ISO_code = col_character(),
-                          Region_UN = col_character()))
-
-df_thetaDraw <- map(df_thetaDraw, function(oneDraw){
-  left_join(oneDraw, df_controls, by = c("country" = "Country", "year" = "Year")) %>% 
-    plm::pdata.frame(index = c("country", "year"))
-})
-
-result_m5O <- plm(Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + plm::lag(SupDem_trim, 1) + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1), pdata.frame(df_controls, index = c("Country", "Year")), model="pooling")
-
-result_m5N <- map(df_thetaDraw, function(aDataset){
-  plm(Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + plm::lag(theta, 1) + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1), model="pooling", data = aDataset)
-})
-
 vcovBK_se <- function(x) {
@@
 }
-
-result_betas_m5 <- mitools::MIextract(result_m5N, fun = coef)
-result_vars_m5 <- mitools::MIextract(result_m5N, fun = vcovBK_se)
-
-summary(result_m5O)
-summary(mitools::MIcombine(results = result_betas_m5, 
-                           variance = result_vars_m5))
 
@@
 
-summary(mitools::MIcombine(results = result_betas_m5_1k, 
-                           variance = result_vars_m5_1k))
+df_result_cls <- summary(mitools::MIcombine(results = result_betas_m5_1k, variance = result_vars_m5_1k))%>% rownames_to_column(var = "term") %>% 
+  rename(conf.low = `(lower`,
+         conf.high = `upper)`, 
+         estimate = results) %>% 
+  filter(!str_detect(term, "(Intercept)"))
+```
+
+```{r dcpoVisualization, fig.cap= "Replication of Model 5 in Claassen's AJPS 2019"}
+
+(dwplot(df_result_cls, by_2sd = FALSE)) %>% 
+  relabel_predictors(c(`plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
+`plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
+`plm::lag(theta, 1)` = "Democratic Mood(t-1)",
+`plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
+`plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
+`plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
+`plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)", #there's a lag in the replication file
+`plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)")) +
+  geom_vline(xintercept = 0, colour = "grey80", linetype = 2) +
+  theme_minimal() +
+  ggtitle("Dependent Variable: Level of Democracy") + 
+  xlab("Coefficient Estimate") +
+  theme(axis.title.y = element_blank(),
+        legend.position = "none")
+
 ```

### 2020-08-05 paper/dcpo_demsupport.Rmd
add data/dcpo_sigma.rda and include sigma in model 1.  Closes #8

@@
 ---
+
+intro
+
+More data, better method, superior measure
+
+review models
+
+results
 
@@
 
+dcpo_sigma <- rstan::extract(dcpo_output, pars = "sigma")
+
+save(dcpo_theta, file = here::here("data", "dcpo_sigma.rda"))
+
 dcpo_y_r_pred <- rstan::extract(dcpo_output, pars = "y_r_pred")
@@
 
-df_theta <- purrr::map(1:1000, function(anEntry) {
-  dcpo_theta$theta[anEntry,,] %>% 
+reformat_dcpo_output <- function(x, parameter_name) {
+  df_temp <- x %>% 
     as_tibble(.name_repair = ~ls_country) %>% 
@@
                  names_to = "country",
-                 values_to = "theta") %>%
-    arrange(country, year) %>% 
+                 values_to = parameter_name) %>%
+    arrange(country, year)
+  return(df_temp)
+}
+
+df_dcpo <- purrr::map(1:1000, function(anEntry) {
+  dcpo_theta$theta[anEntry,,] %>% 
+    reformat_dcpo_output("theta") %>% 
+    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
+              by = c("year", "country")) %>% 
     left_join(df_controls, by = c("country", "year")) %>% 
@@
 
-result_dcpo_1k <- map(df_theta, function(aDataset) {
+result_dcpo_1k <- map(df_dcpo, function(aDataset) {
   plm::plm(Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + plm::lag(theta, 1) +
-        plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) +
-        plm::lag(Region_libdem, 1) + plm::lag(muslism_prop_2010, 1) +
-        plm::lag(dependence_pc_di, 1),
+             plm::lag(sigma, 1) + plm::lag(lg_imp_mdpgdp, 1) +
+             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
+             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1),
     model = "pooling",
@@
       `plm::lag(theta, 1)` = "Democratic Mood(t-1)",
+      `plm::lag(sigma, 1)` = "Democratic Mood(t-1)",
       `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",

### 2020-08-05 paper/dcpo_demsupport.Rmd
finish labeling lag(sigma, 1) in dotwhisker plot

@@
       `plm::lag(theta, 1)` = "Democratic Mood(t-1)",
-      `plm::lag(sigma, 1)` = "Democratic Mood(t-1)",
+      `plm::lag(sigma, 1)` = "Democratic Mood Polarization(t-1)",
       `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",

### 2020-08-07 paper/dcpo_demsupport.Rmd
fix for dcpo_sigma.rda (per https://github.com/fsolt/dcpo_dem_mood/issues/8#issuecomment-670502645)
intro/theory + more data

@@
 
-intro
+One of the classic but disputable questions in comparative politics is whether mass democratic support stabilizes democracy.
+A long-standing and widely accepted theory is that the level of mass democratic support determines the stability of a democratic system [e.g., @lipset_social_1959; @norris_democratic_2011], but findings from empirical analyses still remain inconclusive [@inglehart_modernization_2005; @fails_changing_2010; @qi_how_2011].
+One reason for the mixed results is the approaches to measure public democratic support.
+One concern is whether self-report attitude toward democracy could transfer to behaviorally democratic commitments when the democratic system is in economic or societal crisis.
+Recent studies show that although the public understands and supports democratic principles, their support is elastic, especially in the context of polarization [@graham_democracy_2020].
+Voters sometimes are willing to subordinate democratic norms to their partisan and policy preferences [@nyhan_who_2020] and subsequently support their elected leaders to take anti-democratic measures [@mccoy_democratic_2020].
+However, before considering whether public opinion could transfer to public behavior, one more essential concern is whether and how we capture and measure the latent public opinion accurately, especially comparative public opinion.
+The sparse and incomparable comparative public opinion data has perplexed the study of comparative politics for a long time [@Solt2020a].
+Recently, a few pioneering studies are contributing to the latent public opinion measurement in comparative studies [@Caughey2019,@Claassen2019,@Solt2020a].
+A prominent study by @Claassen2020a applied an advanced Bayesian Item Response Model to measure dynamic public democratic support for 135 countries for up to 29 years.
+It found that mass democratic support had a positive impact on democratic change, especially the endurance of democracy.
+@Claassen2020a's study reignites the debate on the relationship between public opinion and democracy
 
-More data, better method, superior measure
+To adjudicate/contribute to the ongoing debate, this article applies a superior measure, Dynamic Comparative Public Opinion (DCPO) model developed by @Solt2020a, to estimate democratic support for a larger data with 144 countries for up to 32 years between 1988 and 2019.
+Next, we employ a better method to incorporate uncertainty by using random draws from the posterior distributions and following @Rubin1987's rules.
+In addition to account for item response bias across countries and the extent of polarization by generating estimates on bounded scales,  the DCPO model has superiority in dealing with both binominal and ordinal survey data cross countries over time.
+Both internal and external k-fold validation tests corroborate that the DCPO model yields more accurate results than other latent variable measurements, either of @Claassen2019 Model 5 and @Caughey2019 model.
 
-review models
-
-results
+We first replicated Claassen's model but including uncertainty.
+Next, we replicate Claassen's analysis using the DCPO model with more data and uncertainty.
+Surprisingly, our study reveals that there is no significant relationship between public support and democratic change in both the replication analysis of @Claassen2020a model and DCPO analysis when uncertainty is included.
 
@@
 # More Data
+We collected available data from 62 survey questions in 120 surveys across 159 countries for up to 33 years between 1988 and 2020.
+Survey data was extracted automatically through DCPO package.
+DCPO package also automatically identifies survey conducted year, which captures more accurate correspondence between public opinion and democracy level.
+Compared to Claassen's (2019) 1178 available country-years, our data consists of 1406 country-years, which is a 19.4% increase.
+The mass support for democracy is estimated for 144 countries with at least 2 country-years observed.
+Since V-Dem does not have data for small countries and data for 2020, xx countries are filtered from our final data set.
+The dataset in our analysis consists of xxxx estimates, drawn from 144 countries.
 
@@
 The DCPO model is estimated using the `DCPO` package for R [@Solt2020a], which is written in the Stan probabilistic programming language [@StanDevTeam2019a; @StanDevTeam2019b].
+The DCPO shows its superiority in several significant ways.
+First, the model permits to treat the data as their originial scales, either dichotomou or ordinal. 
+Second, the model generates estimates on a bounded scale. Bounded scales serve to both theoretical and methodologoical needs [@Linzer2015]. 
+Third, the model takes into account item response bias across countries.
+Results from validation tests in @Solt2020a.
+In validation tests, @Solt2020a employs k-fold validation with 10 folds, which reduces the misrepresentation of the model due to the chosen data from single cross-validation.
+The validation tests corroborate that DCPO not only features the smallest mean absolute error and largest improvement over the country-means MAE but also provides a more stable and efficient prediction on out-of-sample data than either of @Claassen2019 Model 5 and @Caughey2019 model.
 
@@
 
-save(dcpo_theta, file = here::here("data", "dcpo_sigma.rda"))
+save(dcpo_sigma, file = here::here("data", "dcpo_sigma.rda"))
 

### 2020-08-07 paper/dcpo_demsupport.Rmd
intro

@@
+<<<<<<< HEAD
 ---
@@
 \pagebreak
+=======
+---
+output: 
+  pdf_document:
+    citation_package: natbib
+    keep_tex: true
+    fig_caption: true
+    latex_engine: pdflatex
+    template: svm-latex-ms2.tex
+title: "[dcpo_demsupport]"
+thanks: "The authors contributed equally to this work.  Corresponding author: [yuehong-tai@uiowa.edu](mailto:yuehong-tai@uiowa.edu).  Current version: `r format(Sys.time(), '%B %d, %Y')`."
+author:
+- name: Yuehong 'Cassandra' Tai
+  affiliation: University of Iowa
+- name: Yue Hu
+  affiliation: Tsinghua University
+- name: Frederick Solt
+  affiliation: University of Iowa
+abstract: "Public opinion’s effect on democratic institutions is important and long-studied topic.
+Claassen (2020) renewed attention to this question by using a Bayesian latent variable approach to measure mass democratic support from survey data and concluded such support has a positive effect on subsequent democratic change and especially on democracy’s endurance once in place.
+In this article, we reexamine the question, bringing more survey data on democratic support; a superior measure, Dynamic Comparative Public Opinion (DCPO); and an improved methodological approach that takes the uncertainty in this measure into account.
+Our results [further reinforce/contradict] the long-held view that democracies depend on public support to survive."
+keywords: ""
+date: "`r format(Sys.time(), '%B %d, %Y')`"
+fontsize: 11pt
+spacing: double
+bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
+# csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl
+biblio-style: apsr
+citecolor: black
+linkcolor: black
+endnote: no
+header-includes:
+      - \usepackage{array}
+      - \usepackage{caption}
+      - \usepackage{graphicx}
+      - \usepackage{siunitx}
+      - \usepackage{colortbl}
+      - \usepackage{multirow}
+      - \usepackage{hhline}
+      - \usepackage{calc}
+      - \usepackage{tabularx}
+      - \usepackage{threeparttable}
+      - \usepackage{wrapfig}
+nocite: |
+  @Solt2020a
+---
+
+intro
+
+More data, better method, superior measure
+
+review models
+
+results
+
+```{r setup, include=FALSE}
+options(tinytex.verbose = TRUE)
+
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, dpi = 300)
+
+# If you haven't install `DCPOtools`
+# remotes::install_github("fsolt/DCPOtools")
+
+if (!require(pacman)) install.packages("pacman")
+library(pacman)
+
+# load all the packages you will use below 
+p_load(
+  dataverse, # data scraping
+  DCPOtools,
+  plm, # analysis
+  huxtable, kableExtra, modelsummary, # tabulation
+  latex2exp, # visualization
+  rstan, # Bayesian estimation
+  tidyverse, # data wrangling
+  dotwhisker # visualization
+)
+
+# Functions preload
+set.seed(313)
+```
+
+<!-- The following text is all cribbed from `fsolt/dcpo_article` and obviously needs heavy revision -->
+
+# More Data
+
+```{r dcpo_input_raw}
+dcpo_input_raw <- DCPOtools::dcpo_setup(vars = read_csv("data-raw/mood_dem.csv",
+                                                          col_types = "cccccc"),
+                                          file = "data/dcpo_input_raw.csv")
+```
+
+```{r dcpo_input}
+dcpo_input_raw1 <- read_csv("data/dcpo_input_raw.csv", col_types = "cdcddcd") %>% 
+  filter(!(str_detect(survey, "army_wvs") & # WVS obs identified as problematic by Claassen 
+                 ((country=="Albania" & year==1998) |
+                      (country=="Indonesia" & (year==2001 | year==2006)) |
+                      (country=="Iran" & year==2000) |
+                      (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
+                      (country=="Vietnam" & year==2001)) |
+                 (str_detect(item, "strong_wvs") &
+                      ((country=="Egypt" & year==2012) |
+                           (country=="Iran" & (year==2000 | year==2007)) | # 2005 in Claassen
+                           (country=="India") |
+                           (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
+                           (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
+                           (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
+                           (country=="Vietnam" & year==2001))) |
+                 (country %in% c("Puerto Rico", "Northern Ireland", 
+                                 "SrpSka Republic", "Hong Kong SAR China")))) %>%
+  with_min_yrs(2)
+
+dcpo_input <- DCPOtools::format_dcpo(dcpo_input_raw1,
+                                     scale_q = "church_lb",
+                                     scale_cp = 2)
+save(dcpo_input, file = here::here("data", "dcpo_input.rda"))
+```
+
+```{r compare_n}
+if (!file.exists("data/supdem raw survey marginals.tab")) {
+  dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>% 
+    read_csv(col_types = "cdcddcdc") %>% 
+    write_csv("data/supdem raw survey marginals.tab")
+}
+
+supdem <- read_csv("data/supdem raw survey marginals.tab",
+                   col_types = "cdcddcdc") %>% 
+  janitor::clean_names() %>% 
+  with_min_yrs(2)
+
+supdem_ncy <- supdem %>%
+  dplyr::select(country, year) %>% 
+  unique() %>% 
+  nrow()
+
+supdem_ncyi <- supdem %>%
+  dplyr::select(country, year, item) %>% 
+  unique() %>% 
+  nrow()
+
+dcpo_input_ncy <- dcpo_input_raw1 %>% 
+  dplyr::select(country, year) %>% 
+  unique() %>% 
+  nrow()
+
+dcpo_input_ncyi <- dcpo_input_raw1 %>% 
+  dplyr::select(country, year, item) %>% 
+  unique() %>% 
+  nrow()
+
+increase_cy <- sprintf("%2.1f", (dcpo_input_ncy/supdem_ncy - 1) * 100, 1)
+increase_cyi <- sprintf("%2.1f", (dcpo_input_ncyi/supdem_ncyi - 1) * 100, 1)
+```
+
+# A Better Measure of Democratic Support
+The DCPO model is estimated using the `DCPO` package for R [@Solt2020a], which is written in the Stan probabilistic programming language [@StanDevTeam2019a; @StanDevTeam2019b].
+
+```{r dcpo, eval=FALSE}
+iter <- 3000
+
+dcpo_output <- dcpo(dcpo_input,
+                    iter = iter,
+                    chains = 4,
+                    thin = iter/500, # this yields 250 draws per chain, 1000 draws total
+                    pars = c("sd_delta","sd_theta_evolve", "sd_sigma_evolve", "sigma","phi","beta","alpha","delta","theta","y_r_pred","log_lik"))
+
+save(dcpo_output, file = here::here("data", "dcpo_output.rda"))
+
+dcpo_theta <- rstan::extract(dcpo_output, pars = "theta")
+
+save(dcpo_theta, file = here::here("data", "dcpo_theta.rda"))
+
+dcpo_sigma <- rstan::extract(dcpo_output, pars = "sigma")
+
+save(dcpo_sigma, file = here::here("data", "dcpo_sigma.rda"))
+
+dcpo_y_r_pred <- rstan::extract(dcpo_output, pars = "y_r_pred")
+
+save(dcpo_input, dcpo_y_r_pred, file = here::here("data", "dcpo_y_r_pred.rda"))
+```
+
+# Incorporating Uncertainty
+This means not simply employing the point estimates, that is, the means of the posterior distributions [_contra_ @Claassen2020a; @Claassen2020b].
+
+Instead, researchers should follow the recommendations of work using other latent variables [e.g., @Schnakenberg2014; @Crabtree2015] and other measures incorporating uncertainty, such as the Standardized World Income Inequality Database [@Solt2020]: generate many duplicate versions of the analysis dataset, assign to each a different random draw from the posterior distributions of the variables measured with uncertainty, perform the analyses repeatedly on each of these multiple versions of the dataset, and combine the results following the rules set out in @Rubin1987.
+The functional programming tools in the `purrr` package [@Henry2019] make this a matter of just a few additional lines of code.
+
+```{r country_years}
+path_df <-
+  list.files(
+    "../data",
+    pattern = ".*_theta.rda",
+    recursive = TRUE,
+    full.names = TRUE
+  ) %>%
+  .[str_which(., "claassen")]
+
+load(path_df)
+
+df_thetaDraw <- map_df(seq(claassen_m5_theta$theta[1, , 1]),
+       function(year) {
+         map_df(seq(claassen_m5_theta$theta[1, 1, ]),
+                function(country) {
+                  df_temp <-
+                    sample(claassen_m5_theta$theta[, year, country],
+                           size = 100,
+                           replace = TRUE) %>%
+                    matrix(ncol = 100) %>%
+                    as_tibble()
+                  df_temp$yearID <- year
+                  df_temp$countryID <- country
+                  return(df_temp)
+                })
+       }) %>% 
+  pivot_longer(
+    df_temp,
+    cols = starts_with("V"),
+    names_to = "draw",
+    values_to = "theta"
+  ) %>% 
+  group_split(draw)
+```
+
+# Results
+
+```{r dcpo-uncertainty, cache=TRUE}
+# Preload function ----
+vcovBK_se <- function(x) {
+  plm::vcovBK(x, cluster = "time") %>% 
+    diag() %>% 
+    sqrt()
+}
+
+# Data input ----
+
+load(here::here("data", "dcpo_theta.rda"))
+
+df_controls <- read_csv(here::here("data", "control_variables.csv"),
+                        col_types = cols(.default = col_double(),
+                                         country = col_character(),
+                                         country_name = col_character(),
+                                         ISO = col_character(),
+                                         Region_UN = col_character())) %>% 
+  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
+         country = countrycode::countrycode(country0, "country.name", "country.name"))
+
+ls_country <- levels(dcpo_input$data$kk)
+first_year <- min(dcpo_input$data$year)
+
+reformat_dcpo_output <- function(x, parameter_name) {
+  df_temp <- x %>% 
+    as_tibble(.name_repair = ~ls_country) %>% 
+    mutate(year = first_year + row_number() - 1) %>% 
+    pivot_longer(cols = all_of(ls_country),
+                 names_to = "country",
+                 values_to = parameter_name) %>%
+    arrange(country, year)
+  return(df_temp)
+}
+
+df_dcpo <- purrr::map(1:1000, function(anEntry) {
+  dcpo_theta$theta[anEntry,,] %>% 
+    reformat_dcpo_output("theta") %>% 
+    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
+              by = c("year", "country")) %>% 
+    left_join(df_controls, by = c("country", "year")) %>% 
+    plm::pdata.frame(index = c("country", "year"))
+})
+
+result_dcpo_1k <- map(df_dcpo, function(aDataset) {
+  plm::plm(Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + plm::lag(theta, 1) +
+             plm::lag(sigma, 1) + plm::lag(lg_imp_mdpgdp, 1) +
+             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
+             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1),
+    model = "pooling",
+    data = aDataset)
+})
+
+result_betas_dcpo_1k <- mitools::MIextract(result_dcpo_1k, fun = coef)
+result_vars_dcpo_1k <- mitools::MIextract(result_dcpo_1k, fun = vcovBK_se)
+
+df_result_dcpo <- summary(mitools::MIcombine(results = result_betas_dcpo_1k, variance = result_vars_dcpo_1k)) %>% rownames_to_column(var = "term") %>% 
+  rename(conf.low = `(lower`,
+         conf.high = `upper)`, 
+         estimate = results) %>% 
+  filter(!str_detect(term, "(Intercept)"))
+
+```
+
+```{r dcpoVisualization, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO"}
+
+dwplot(df_result_dcpo, by_2sd = FALSE) %>% 
+  relabel_predictors(
+    c(
+      `plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
+      `plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
+      `plm::lag(theta, 1)` = "Democratic Mood(t-1)",
+      `plm::lag(sigma, 1)` = "Democratic Mood Polarization(t-1)",
+      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
+      `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
+      `plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
+      `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
+      #there's a lag in the replication file
+      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)"
+    )
+  ) +
+  geom_vline(xintercept = 0,
+             colour = "grey80",
+             linetype = 2) +
+  theme_minimal() +
+  ggtitle("Dependent Variable: Level of Democracy") +
+  xlab("Coefficient Estimate") +
+  theme(axis.title.y = element_blank(),
+        legend.position = "none")
+
+```
+
+# Conclusion
+
+\pagebreak
+>>>>>>> e804bffe869cdef06565e4d4a674715965eea46e

### 2020-08-07 paper/dcpo_demsupport.Rmd
resolve conflicts per https://github.com/fsolt/dcpo_dem_mood/issues/10#issuecomment-670695515
per #9

--- 2020-08-05 paper/dcpo_demsupport.Rmd
@@
 
-```{r dcpo_input_raw}
+```{r dcpo_input_raw, eval = FALSE}
 dcpo_input_raw <- DCPOtools::dcpo_setup(vars = read_csv("data-raw/mood_dem.csv",
@@
 
-```{r dcpo_input}
+```{r dcpo_input, eval = FALSE}
 dcpo_input_raw1 <- read_csv("data/dcpo_input_raw.csv", col_types = "cdcddcd") %>% 
@@
 
-```{r compare_n}
+```{r compare_n, eval = FALSE}
 if (!file.exists("data/supdem raw survey marginals.tab")) {
@@
 
-```{r country_years}
+```{r country-years, eval=FALSE}
 path_df <-
@@
 
-```{r dcpo-uncertainty, cache=TRUE}
-# Preload function ----
+```{r claassen-replication}
+# Data input ----
+
+supdem <- read.csv("../data/Support_democracy_ajps.csv")
+v_dem <- read.csv("../data/vdem15.csv")
+
+sd.plm <- pdata.frame(supdem, index = c("Country", "Year"))
+
+# Pooled model -----
+
+## Beck-Katz panel-corrected standard errors
 vcovBK_se <- function(x) {
@@
 
+# regime = ifelse(sd2$Regime_VD > 1, 1, 0)
+
+ls_mod <-
+  paste0(
+    "Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + ",
+    c(
+      "plm::lag(SupDem_trim, 1)",
+      "plm::lag(SupDem_Democ, 1) + plm::lag(SupDem_Autoc, 1)"
+    ),
+    "+ plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)"
+  )
+
+result_cls <- map(ls_mod, function(mod){
+  result <- plm(ls_mod, model = "pooling", data = sd.plm)
+  df_result <- tidy(result) %>%
+    mutate(std.error = vcovBK_se(result))
+})
+
+# GMM ----
+
+## Windmeijer corrected standard errors
+vcovHC_se <- function(x) {
+  plm::vcovHC(x, cluster = "time") %>% 
+    diag() %>% 
+    sqrt()
+}
+
+ls_mod <- 
+  paste0(
+    "Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + ",
+    c(
+      "plm::lag(SupDem_trim, 1)",
+      "plm::lag(SupDem_Democ, 1) + plm::lag(SupDem_Autoc, 1)"
+    ),
+    "+ plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)",
+    " | plm::lag(Libdem_VD, 3:5)"
+  )
+
+result_cls[3:4] <- map(ls_mod, function(mod){
+  result <- pgmm(as.formula(ls_mod), effect="individual", model="onestep", transformation="ld", indexes=c("Country", "Year"), data = sd.plm)
+  df_result <- coef(result) %>% 
+    tibble::enframe(name = "term", value = "estimate") %>% 
+    mutate(std.error = vcovHC_se(result))
+})
+
+```
+
+```{r dcpo-uncertainty, cache=TRUE}
+
 # Data input ----
-
+load(here::here("data", "dcpo_input.rda"))
+load(here::here("data", "dcpo_sigma.rda"))
 load(here::here("data", "dcpo_theta.rda"))
@@
   mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
-         country = countrycode::countrycode(country0, "country.name", "country.name"))
+         country = countrycode::countrycode(country0, "country.name", "country.name"),
+         regime = Vdem_libdem > 1)
 
@@
     left_join(df_controls, by = c("country", "year")) %>% 
+    mutate(theta_dem = theta * regime,
+           theta_aut = theta * (1 - regime)) %>% 
     plm::pdata.frame(index = c("country", "year"))
@@
 
+estimate_dcpo_pooled <- function(aModel) {
   result_dcpo_1k <- map(df_dcpo, function(aDataset) {
-  plm::plm(Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + plm::lag(theta, 1) +
-             plm::lag(sigma, 1) + plm::lag(lg_imp_mdpgdp, 1) +
-             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
-             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1),
+    plm::plm(aModel,
              model = "pooling",
@@
 
-result_betas_dcpo_1k <- mitools::MIextract(result_dcpo_1k, fun = coef)
-result_vars_dcpo_1k <- mitools::MIextract(result_dcpo_1k, fun = vcovBK_se)
+  result_betas_dcpo_1k <-
+    mitools::MIextract(result_dcpo_1k, fun = coef)
+  result_vars_dcpo_1k <-
+    mitools::MIextract(result_dcpo_1k, fun = vcovBK_se)
 
-df_result_dcpo <- summary(mitools::MIcombine(results = result_betas_dcpo_1k, variance = result_vars_dcpo_1k)) %>% rownames_to_column(var = "term") %>% 
+  df_result_dcpo <-
+    summary(
+      mitools::MIcombine(results = result_betas_dcpo_1k, variance = result_vars_dcpo_1k)
+    ) %>% rownames_to_column(var = "term") %>%
     rename(conf.low = `(lower`,
@@
     filter(!str_detect(term, "(Intercept)"))
+}
+
+mod_ls <- paste0(
+  "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
+  c("plm::lag(theta, 1)", 
+    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
+  " + plm::lag(lg_imp_mdpgdp, 1) +
+             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
+             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)"
+)
+
+df_result_dcpo <- map(mod_ls, estimate_dcpo_pooled)
+
+estimate_dcpo_gmm <- function(aModel) {
+  result_dcpo_1k <- map(df_dcpo, function(aDataset) {
+    pgmm(as.formula(aModel), effect="individual", model="onestep", transformation="ld", indexes=c("Country", "Year"), data = aDataset)
+  })
+
+  result_betas_dcpo_1k <-
+    mitools::MIextract(result_dcpo_1k, fun = coef)
+  result_vars_dcpo_1k <-
+    mitools::MIextract(result_dcpo_1k, fun = vcovHC_se)
+
+  df_result_dcpo <-
+    summary(
+      mitools::MIcombine(results = result_betas_dcpo_1k, variance = result_vars_dcpo_1k)
+    ) %>% rownames_to_column(var = "term") %>%
+    rename(conf.low = `(lower`,
+           conf.high = `upper)`,
+           estimate = results) %>%
+    filter(!str_detect(term, "(Intercept)"))
+}
+
+mod_ls <- paste0(
+  "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
+  c("plm::lag(theta, 1)", 
+    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
+  " + plm::lag(lg_imp_mdpgdp, 1) +
+             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
+             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)",
+    " | plm::lag(Vdem_libdem, 3:5)"
+)
+
+df_result_dcpo[3:4] <- map(mod_ls, estimate_dcpo_gmm)
 

### 2020-08-07 paper/dcpo_demsupport.Rmd
revised the `estimated_dcpo`

@@
 
-estimate_dcpo_pooled <- function(aModel) {
+estimate_dcpo <- function(aModel, aType = "pooling") {
+  if (aType == "gmm") {
+    result_dcpo_1k <- map(df_dcpo, function(aDataset) {
+      pgmm(
+        as.formula(aModel),
+        effect = "individual",
+        model = "onestep",
+        transformation = "ld",
+        indexes = c("Country", "Year"),
+        data = aDataset
+      )
+    })
+
+    result_vars_dcpo_1k <-
+      mitools::MIextract(result_dcpo_1k, fun = vcovHC_se)
+
+  } else {
     result_dcpo_1k <- map(df_dcpo, function(aDataset) {
@@
 
-  result_betas_dcpo_1k <-
-    mitools::MIextract(result_dcpo_1k, fun = coef)
     result_vars_dcpo_1k <-
       mitools::MIextract(result_dcpo_1k, fun = vcovBK_se)
+  }
 
@@
 
-df_result_dcpo <- map(mod_ls, estimate_dcpo_pooled)
-
-estimate_dcpo_gmm <- function(aModel) {
-  result_dcpo_1k <- map(df_dcpo, function(aDataset) {
-    pgmm(as.formula(aModel), effect="individual", model="onestep", transformation="ld", indexes=c("Country", "Year"), data = aDataset)
-  })
-
-  result_betas_dcpo_1k <-
-    mitools::MIextract(result_dcpo_1k, fun = coef)
-  result_vars_dcpo_1k <-
-    mitools::MIextract(result_dcpo_1k, fun = vcovHC_se)
-
-  df_result_dcpo <-
-    summary(
-      mitools::MIcombine(results = result_betas_dcpo_1k, variance = result_vars_dcpo_1k)
-    ) %>% rownames_to_column(var = "term") %>%
-    rename(conf.low = `(lower`,
-           conf.high = `upper)`,
-           estimate = results) %>%
-    filter(!str_detect(term, "(Intercept)"))
-}
+df_result_dcpo <- map(mod_ls, estimate_dcpo)
 
@@
 
-df_result_dcpo[3:4] <- map(mod_ls, estimate_dcpo_gmm)
+df_result_dcpo[3] <- map(mod_ls[[1]], estimate_dcpo, aType = "gmm")
 

### 2020-08-08 paper/dcpo_demsupport.Rmd
format.

@@
 It found that mass democratic support had a positive impact on democratic change, especially the endurance of democracy.
-@Claassen2020a's study reignites the debate on the relationship between public opinion and democracy
+@Claassen2020a's study reignites the debate on the relationship between public opinion and democracy.
 
@@
 We collected available data from 62 survey questions in 120 surveys across 159 countries for up to 33 years between 1988 and 2020.
-Survey data was extracted automatically through DCPO package.
-DCPO package also automatically identifies survey conducted year, which captures more accurate correspondence between public opinion and democracy level.
-Compared to Claassen's (2019) 1178 available country-years, our data consists of 1406 country-years, which is a 19.4% increase.
-The mass support for democracy is estimated for 144 countries with at least 2 country-years observed.
-Since V-Dem does not have data for small countries and data for 2020, xx countries are filtered from our final data set.
-The dataset in our analysis consists of xxxx estimates, drawn from 144 countries.
+Survey data was extracted automatically through the DCPO package.
+Survey years identified by the DCPO package were the years when respondents were contacted.
+This identification facilitates correspondence between public opinion and democracy level.
+Compared to Claassen's (2019) 1178 available country-years, our data consists of 1465 country-years, which is a 24.4% increase.
+Then, the mass support for democracy is estimated for 144 countries with at least 2 country-years observed.
+After dropping 2020 data and countries without V-Dem index, our final data set in models have 4538 country-years.
 
@@
 The DCPO shows its superiority in several significant ways.
-First, the model permits to treat the data as their originial scales, either dichotomou or ordinal. 
-Second, the model generates estimates on a bounded scale. Bounded scales serve to both theoretical and methodologoical needs [@Linzer2015]. 
+
+First, the model permits to treat the data as their originial scales, either dichotomous or ordinal.
+
+Second, the model generates estimates on a bounded scale. Bounded scales serve to both theoretical and methodological needs [@Linzer2015].
+
 Third, the model takes into account item response bias across countries.
-Results from validation tests in @Solt2020a.
+
+results from validation tests in @Solt2020a.
 In validation tests, @Solt2020a employs k-fold validation with 10 folds, which reduces the misrepresentation of the model due to the chosen data from single cross-validation.

### 2020-08-08 paper/dcpo_demsupport.Rmd
estimates of model 1-4; per #9

--- 2020-08-07 paper/dcpo_demsupport.Rmd
@@
 vcovHC_se <- function(x) {
-  plm::vcovHC(x, cluster = "time") %>% 
+  plm::vcovHC(x) %>% 
     diag() %>% 
@@
 
+save(df_result_dcpo, file = here::here("output", "estimates_cls.RDS"))
 ```
@@
 
+  result_betas_dcpo_1k <-
+    mitools::MIextract(result_dcpo_1k, fun = coef)
+
   df_result_dcpo <-
@@
 
+df_result_dcpo[4] <- map(mod_ls[[2]], estimate_dcpo, aType = "gmm")
+
+save(df_result_dcpo, file = here::here("output", "estimates_dcpo.RDS"))
 ```

### 2020-08-08 paper/dcpo_demsupport.Rmd
visualization of polarization

@@
 
-```{r dcpo-uncertainty, cache=TRUE}
+```{r dcpo-uncertainty, eval = FALSE}
 
@@
 
+```{r polarizationVisualization, eval = FALSE}
+# Bootstrap to get confidence intervals
+
+library(boot)
+
+## function to obtain the mean
+Bmean <- function(data, indices) {
+  d <- data[indices] # allows boot to select sample 
+    return(mean(d))
+}
+
+# bootstrapping with 1000 replications 
+bootstrapCI_sigma <- function(aData) {
+  aSigma <- aData$sigma
+  result_temp <- boot(data = aSigma,
+                      statistic = Bmean,
+                      R = 1000) %>%
+    boot.ci(type = "bca")
+  tibble(
+    mean = mean(aSigma),
+    conf.low = result_temp$bca[4],
+    conf.high = result_temp$bca[5]
+  )
+}
+
+df_sigma <- purrr::map(1:1000, function(anEntry) {
+  dcpo_sigma$sigma[anEntry, , ] %>%
+  reformat_dcpo_output("sigma")
+})
+
+df_sigma_us <- map_df(df_sigma, function(aCountry){
+  filter(aCountry, country == "United States")
+})
+
+df_sigma_usCI <- map_df(unique(df_sigma_us$year), function(aYear){
+  dataAYear <- filter(df_sigma_us, year == aYear)
+  bootstrapCI_sigma(dataAYear)
+}) %>% 
+  mutate(year = unique(df_sigma_us$year))
+
+df_sigma_2019 <- map_df(df_sigma, function(aCountry){
+  filter(aCountry, year == 2019)
+})
+
+df_sigma_2019CI <- map_df(unique(df_sigma_2019$country), function(aCountry){
+  dataACountry <- filter(df_sigma_2019, country == aCountry)
+  bootstrapCI_sigma(dataACountry)
+}) %>% 
+  mutate(country = unique(df_sigma_2019$country))
+
+plot_us <- ggplot(df_sigma_usCI, aes(x = mean, y = year, xmin = conf.low, xmax = conf.high)) +
+  geom_point() +
+  geom_errorbarh(height=.2) + 
+  scale_y_reverse(breaks = unique(df_sigma_us$year)) +
+  xlab(expression("Polarization Estimates, "~sigma)) + 
+  ggtitle("Polarization of the U.S. from 1988--2020") +
+  theme_minimal() +
+  theme(axis.title.y = element_blank())
+
+plot_2019 <- ggplot(df_sigma_2019CI, aes(x = mean, y = country, xmin = conf.low, xmax = conf.high)) +
+  geom_point() +
+  geom_errorbarh(height=.2) + 
+  xlab(expression("Polarization Estimates, "~sigma)) + 
+  ggtitle("Polarization around the World in 2019") +
+  theme_minimal() +
+  theme(axis.title.y = element_blank())
+
+gridExtra::grid.arrange(plot_us, plot_2019, nrow = 1)
+```
+
 ```{r dcpoVisualization, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO"}

### 2020-08-08 paper/dcpo_demsupport.Rmd
including sigma in 1--4

@@
     "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
-  " + plm::lag(lg_imp_mdpgdp, 1) +
+  " + plm::lag(sigma, 1) + plm::lag(lg_imp_mdpgdp, 1) +
              plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
@@
 
-df_result_dcpo[4] <- map(mod_ls[[2]], estimate_dcpo, aType = "gmm")
+# df_result_dcpo[4] <- map(mod_ls[[2]], estimate_dcpo, aType = "gmm")
 

### 2020-08-08 paper/dcpo_demsupport.Rmd
estimate results

@@
 
-result_cls <- map(ls_mod, function(mod){
+df_result_cls <- map(ls_mod, function(mod){
   result <- plm(ls_mod, model = "pooling", data = sd.plm)
@@
 
-result_cls[3:4] <- map(ls_mod, function(mod){
+df_result_cls[3:4] <- map(ls_mod, function(mod){
   result <- pgmm(as.formula(ls_mod), effect="individual", model="onestep", transformation="ld", indexes=c("Country", "Year"), data = sd.plm)
@@
 
-save(df_result_dcpo, file = here::here("output", "estimates_cls.RDS"))
+save(df_result_cls, file = here::here("output", "estimates_cls.RDS"))
 ```

### 2020-08-08 paper/dcpo_demsupport.Rmd
ggarrange version, not ideal

@@
   DCPOtools,
-  plm, # analysis
+  boot, plm, # analysis
   huxtable, kableExtra, modelsummary, # tabulation
@@
 
-```{r polarizationVisualization, eval = FALSE}
-# Bootstrap to get confidence intervals
-
-library(boot)
+```{r polarizationVisualization, fig.cap="Variance of Polarization"}
+# Bootstrap to get confidence intervals----
 
@@
 
-# bootstrapping with 1000 replications 
+## bootstrapping with 1000 replications 
 bootstrapCI_sigma <- function(aData) {
@@
 
-dwplot(df_result_dcpo, by_2sd = FALSE) %>% 
+load(here::here("output", "estimates_dcpo.RDS"))
+load(here::here("output", "estimates_cls.RDS"))
+
+df_plot <- df_result_cls[[1]] %>% 
+  mutate(model = "Uncertainty\n Ignored",
+         type = "Pooled OLS")
+
+df_plot <- df_result_dcpo[[1]] %>% 
+  mutate(model = "DCPO",
+         type = "Pooled OLS") %>% 
+  rename(std.error = se) %>% 
+  bind_rows(df_plot)
+
+df_plot <- df_result_cls[[3]] %>% 
+  mutate(model = "Uncertainty\n Ignored",
+         type = "System GMM") %>% 
+  bind_rows(df_plot)
+
+df_plot <- df_result_dcpo[[3]] %>% 
+  mutate(model = "DCPO",
+         type = "System GMM") %>% 
+  rename(std.error = se) %>% 
+  bind_rows(df_plot) %>% 
+  select(term, estimate, std.error, model, type)
+
+## Facet cause NA column, very weird. 
+plot_estimate <- map(c("Pooled OLS", "System GMM"), function(aType) {
+  filter(df_plot, type == aType) %>%
+    dwplot(by_2sd = FALSE) %>%
     relabel_predictors(
@@
         `plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
+        `plm::lag(Libdem_VD, 1:2)1` = "Democracy(t-1)",
         `plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
+        `plm::lag(Libdem_VD, 1:2)2` = "Democracy(t-2)",
         `plm::lag(theta, 1)` = "Democratic Mood(t-1)",
-      `plm::lag(sigma, 1)` = "Democratic Mood Polarization(t-1)",
+        `plm::lag(SupDem_trim, 1)` = "Democratic Mood(t-1)",
         `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
+        `plm::lag(lnGDP_imp, 1)` = "Log GDP per capita(t−1)",
         `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
+        `plm::lag(GDP_imp_grth, 1)` = "GDP per capita Growth(t−1)",
         `plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
+        `plm::lag(Libdem_regUN, 1)` = "Regional democracy(t−1)",
         `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
-      #there's a lag in the replication file
-      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)"
+        `plm::lag(Pr_Muslim, 1)` = "Percent Muslim (t-1)",
+        `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)",
+        `plm::lag(Res_cp_WDI_di, 1)` = "Resource Dependence(t−1)",
+        `plm::lag(sigma, 1)` = "Democratic Mood Polarization(t-1)"
       )
@@
     theme_minimal() +
-  ggtitle("Dependent Variable: Level of Democracy") +
+    ggtitle(aType) +
     xlab("Coefficient Estimate") +
-  theme(axis.title.y = element_blank(),
-        legend.position = "none")
+    theme(axis.title.y = element_blank())
+})
+
+library(ggpubr)
+ggarrange(plotlist = plot_estimate, common.legend = TRUE)
 

### 2020-08-08 paper/dcpo_demsupport.Rmd
facet version, why it isn't work! Very annoying!

@@
 
-## Facet cause NA column, very weird. 
-plot_estimate <- map(c("Pooled OLS", "System GMM"), function(aType) {
-  filter(df_plot, type == aType) %>%
-    dwplot(by_2sd = FALSE) %>%
+plot_wNA <- dwplot(df_plot, by_2sd = FALSE) %>% 
   relabel_predictors(
@@
   theme_minimal() +
-    ggtitle(aType) +
+  ggtitle("Dependent Variable: Level of Democracy") +
   xlab("Coefficient Estimate") +
-    theme(axis.title.y = element_blank())
-})
-
-library(ggpubr)
-ggarrange(plotlist = plot_estimate, common.legend = TRUE)
+  theme(axis.title.y = element_blank()) + 
+  facet_wrap(~ type)
 

### 2020-08-08 paper/dcpo_demsupport.Rmd
visualization that can be used. Per #4 and #9

@@
 
-plot_wNA <- dwplot(df_plot, by_2sd = FALSE) %>% 
+# the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
+plot_pooled <- filter(df_plot, type == "Pooled OLS") %>% 
+  dwplot(by_2sd = FALSE) %>% 
   relabel_predictors(
@@
   theme_minimal() +
-  ggtitle("Dependent Variable: Level of Democracy") +
+  ggtitle("Pooled OLS") +
   xlab("Coefficient Estimate") +
-  theme(axis.title.y = element_blank()) + 
-  facet_wrap(~ type)
+  theme(axis.title.y = element_blank(),
+        legend.position = "none")
 
+plot_gmm <- filter(df_plot, type == "System GMM") %>% 
+  dwplot(by_2sd = FALSE) %>% 
+  relabel_predictors(
+    c(
+`plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
+`plm::lag(Libdem_VD, 1:2)1` = "Democracy(t-1)",
+`plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
+`plm::lag(Libdem_VD, 1:2)2` = "Democracy(t-2)",
+`plm::lag(theta, 1)` = "Democratic Mood(t-1)",
+`plm::lag(SupDem_trim, 1)` = "Democratic Mood(t-1)",
+`plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
+`plm::lag(lnGDP_imp, 1)` = "Log GDP per capita(t−1)",
+`plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
+`plm::lag(GDP_imp_grth, 1)` = "GDP per capita Growth(t−1)",
+`plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
+`plm::lag(Libdem_regUN, 1)` = "Regional democracy(t−1)",
+`plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
+`plm::lag(Pr_Muslim, 1)` = "Percent Muslim (t-1)",
+`plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)",
+`plm::lag(Res_cp_WDI_di, 1)` = "Resource Dependence(t−1)",
+`plm::lag(sigma, 1)` = "Democratic Mood Polarization(t-1)"
+    )
+  ) +
+  geom_vline(xintercept = 0,
+             colour = "grey80",
+             linetype = 2) +
+  theme_minimal() +
+  ggtitle("System GMM") +
+  xlab("Coefficient Estimate") +
+  theme(axis.title.y = element_blank(),
+        axis.text.y = element_blank(),
+        legend.title = element_blank())
+
+gridExtra::grid.arrange(plot_pooled, plot_gmm, ncol = 2)
 ```

### 2020-08-08 paper/dcpo_demsupport.Rmd
formating

@@
 # the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
+
 plot_pooled <- filter(df_plot, type == "Pooled OLS") %>% 

### 2020-08-25 paper/dcpo_demsupport.Rmd
edit uncertainty part.

@@
 One of the classic but disputable questions in comparative politics is whether mass democratic support stabilizes democracy.
-A long-standing and widely accepted theory is that the level of mass democratic support determines the stability of a democratic system [e.g., @lipset_social_1959; @norris_democratic_2011], but findings from empirical analyses still remain inconclusive [@inglehart_modernization_2005; @fails_changing_2010; @qi_how_2011].
-One reason for the mixed results is the approaches to measure public democratic support.
-One concern is whether self-report attitude toward democracy could transfer to behaviorally democratic commitments when the democratic system is in economic or societal crisis.
+A long-standing and widely accepted theory is that the level of mass democratic support determines the stability of a democratic system [e.g., @lipset_social_1959; @norris_democratic_2011], but findings from empirical analyses still remain inconclusive [@inglehart_modernization_2005; @fails_changing_2010; @qi_how_2011, see @Claassen2020a for a review in this literature].
+One reason for the mixed results is the measurement of public democratic support.
+Measuring democratic support by using self-report survey data is still the dominant approach.
+However, it is questionable that whether self-report attitude toward democracy could transfer to behaviorally democratic commitments when the democratic system is in economic or societal crisis.
 Recent studies show that although the public understands and supports democratic principles, their support is elastic, especially in the context of polarization [@graham_democracy_2020].
 Voters sometimes are willing to subordinate democratic norms to their partisan and policy preferences [@nyhan_who_2020] and subsequently support their elected leaders to take anti-democratic measures [@mccoy_democratic_2020].
-However, before considering whether public opinion could transfer to public behavior, one more essential concern is whether and how we capture and measure the latent public opinion accurately, especially comparative public opinion.
+However, one more essential concern is whether and how we can measure the latent public opinion correctly, especially for comparative public opinion survey data.
 The sparse and incomparable comparative public opinion data has perplexed the study of comparative politics for a long time [@Solt2020a].
+Public support for democracy is a latent variable and the incorrect measurement of it may conceal the real relationship between public opinion and democratic insitution development.
 Recently, a few pioneering studies are contributing to the latent public opinion measurement in comparative studies [@Caughey2019,@Claassen2019,@Solt2020a].
@@
 It found that mass democratic support had a positive impact on democratic change, especially the endurance of democracy.
-@Claassen2020a's study reignites the debate on the relationship between public opinion and democracy
+@Claassen2020a's study reignites the debate on the relationship between public opinion and democracy.
 
-To adjudicate/contribute to the ongoing debate, this article applies a superior measure, Dynamic Comparative Public Opinion (DCPO) model developed by @Solt2020a, to estimate democratic support for a larger data with 144 countries for up to 32 years between 1988 and 2019.
-Next, we employ a better method to incorporate uncertainty by using random draws from the posterior distributions and following @Rubin1987's rules.
+To adjudicate/contribute to the ongoing debate, this research note reexamines the relationship between public democratic support and democracy stability by applying a superior measure and incorporating a larger data and uncertainty.
+We use a superior measure, Dynamic Comparative Public Opinion (DCPO) model developed by @Solt2020a, to estimate democratic support for a larger data with 144 countries for up to 32 years between 1988 and 2019.
 In addition to account for item response bias across countries and the extent of polarization by generating estimates on bounded scales, the DCPO model has superiority in dealing with both binominal and ordinal survey data cross countries over time.
 Both internal and external k-fold validation tests corroborate that the DCPO model yields more accurate results than other latent variable measurements, either of @Claassen2019 Model 5 and @Caughey2019 model.
+Next, we incorporate uncertainty by using random draws from the posterior distributions and following @Rubin1987's rules.
+A latent construct should be measured with uncertainty because it is impossible to measure the complex concept perfectly and uncertainty is substantively necessary for “comparing relationship between complex theoretical concepts across political contexts and over time" [@Crabtree2015,p2].
 
-We first replicated Claassen's model but including uncertainty.
-Next, we replicate Claassen's analysis using the DCPO model with more data and uncertainty.
 Surprisingly, our study reveals that there is no significant relationship between public support and democratic change in both the replication analysis of @Claassen2020a model and DCPO analysis when uncertainty is included.
@@
 # Incorporating Uncertainty
-This means not simply employing the point estimates, that is, the means of the posterior distributions [_contra_ @Claassen2020a; @Claassen2020b].
-
-Instead, researchers should follow the recommendations of work using other latent variables [e.g., @Schnakenberg2014; @Crabtree2015] and other measures incorporating uncertainty, such as the Standardized World Income Inequality Database [@Solt2020]: generate many duplicate versions of the analysis dataset, assign to each a different random draw from the posterior distributions of the variables measured with uncertainty, perform the analyses repeatedly on each of these multiple versions of the dataset, and combine the results following the rules set out in @Rubin1987.
+Instead of simply employing the point estimates, that is, the means of the posterior distributions [_contra_ @Claassen2020a; @Claassen2020b], it is recommended to incorporate uncertainty in using latent variables [e.g., @Schnakenberg2014; @Crabtree2015] and other measures, such as the Standardized World Income Inequality Database [@Solt2020].
+In this study, we generate 1,000 duplicate versions of the analysis dataset, assign to each a different random draw from the posterior distributions of public democratic support, perform the analyses repeatedly on each of these 1,000 versions of the dataset, and combine the results following the rules set out in @Rubin1987.
 The functional programming tools in the `purrr` package [@Henry2019] make this a matter of just a few additional lines of code.

### 2020-08-26 paper/dcpo_demsupport.Rmd
fixed #12

@@
   pivot_longer(
-    df_temp,
     cols = starts_with("V"),
@@
 df_result_cls <- map(ls_mod, function(mod){
-  result <- plm(ls_mod, model = "pooling", data = sd.plm)
+  result <- plm(mod, model = "pooling", data = sd.plm)
   df_result <- tidy(result) %>%
     mutate(std.error = vcovBK_se(result))
-})
-
-# GMM ----
-
-## Windmeijer corrected standard errors
-vcovHC_se <- function(x) {
-  plm::vcovHC(x) %>% 
-    diag() %>% 
-    sqrt()
-}
-
-ls_mod <- 
-  paste0(
-    "Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + ",
-    c(
-      "plm::lag(SupDem_trim, 1)",
-      "plm::lag(SupDem_Democ, 1) + plm::lag(SupDem_Autoc, 1)"
-    ),
-    "+ plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)",
-    " | plm::lag(Libdem_VD, 3:5)"
-  )
-
-df_result_cls[3:4] <- map(ls_mod, function(mod){
-  result <- pgmm(as.formula(ls_mod), effect="individual", model="onestep", transformation="ld", indexes=c("Country", "Year"), data = sd.plm)
-  df_result <- coef(result) %>% 
-    tibble::enframe(name = "term", value = "estimate") %>% 
-    mutate(std.error = vcovHC_se(result))
 })
@@
 
-```{r dcpo-uncertainty, eval = FALSE}
-
-# Data input ----
+```{r dcpo-point}
 load(here::here("data", "dcpo_input.rda"))
+load(here::here("data", "dcpo_theta.rda"))
 load(here::here("data", "dcpo_sigma.rda"))
-load(here::here("data", "dcpo_theta.rda"))
 
@@
          country = countrycode::countrycode(country0, "country.name", "country.name"),
-         regime = Vdem_libdem > 1)
+         regime = Vdem_regime > 1)
 
@@
 
+df_dcpoMean <- purrr::map_df(1:1000, function(anEntry) {
+  dcpo_theta$theta[anEntry,,] %>% 
+    reformat_dcpo_output("theta") %>% 
+    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
+              by = c("year", "country"))
+}) %>% 
+  group_by(country, year) %>% 
+  summarise(theta = mean(theta), 
+            sigma = mean(sigma))
+
+df_dcpoMean <- df_dcpoMean %>% 
+  left_join(df_controls, by = c("country", "year")) %>% 
+  mutate(theta_dem = theta * regime,
+         theta_aut = theta * (1 - regime)) %>% 
+    plm::pdata.frame(index = c("country", "year"))
+
+ls_mod <- paste0(
+  "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
+  c("plm::lag(theta, 1)", 
+    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
+  " + plm::lag(lg_imp_mdpgdp, 1) +
+             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
+             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)"
+)
+
+df_result_dcpoMean <- map(ls_mod, function(mod){
+  result <- plm(mod, model = "pooling", data = df_dcpoMean)
+  df_result <- tidy(result) %>%
+    mutate(std.error = vcovBK_se(result))
+})
+
+save(df_result_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))
+```
+
+```{r dcpo-uncertainty, eval = FALSE}
 df_dcpo <- purrr::map(1:1000, function(anEntry) {
@@
     "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
-  " + plm::lag(sigma, 1) + plm::lag(lg_imp_mdpgdp, 1) +
+  " + plm::lag(lg_imp_mdpgdp, 1) +
              plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
@@
 
-mod_ls <- paste0(
-  "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
-  c("plm::lag(theta, 1)", 
-    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
-  " + plm::lag(sigma, 1) + plm::lag(lg_imp_mdpgdp, 1) +
-             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
-             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)",
-    " | plm::lag(Vdem_libdem, 3:5)"
-)
-
-df_result_dcpo[3] <- map(mod_ls[[1]], estimate_dcpo, aType = "gmm")
-
-# df_result_dcpo[4] <- map(mod_ls[[2]], estimate_dcpo, aType = "gmm")
-
 save(df_result_dcpo, file = here::here("output", "estimates_dcpo.RDS"))
@@
 
-```{r polarizationVisualization, fig.cap="Variance of Polarization"}
-# Bootstrap to get confidence intervals----
+```{r visualizedMood, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO"}
 
-## function to obtain the mean
-Bmean <- function(data, indices) {
-  d <- data[indices] # allows boot to select sample 
-    return(mean(d))
-}
+load(here::here("output", "estimates_cls.RDS"))
+load(here::here("output", "estimates_dcpoMean.RDS"))
+load(here::here("output", "estimates_dcpo.RDS"))
 
-## bootstrapping with 1000 replications 
-bootstrapCI_sigma <- function(aData) {
-  aSigma <- aData$sigma
-  result_temp <- boot(data = aSigma,
-                      statistic = Bmean,
-                      R = 1000) %>%
-    boot.ci(type = "bca")
-  tibble(
-    mean = mean(aSigma),
-    conf.low = result_temp$bca[4],
-    conf.high = result_temp$bca[5]
+df_plot <- df_result_cls[[1]] %>% 
+  mutate(model = "Claassen 2019")
+
+df_plot <- df_result_dcpoMean[[1]] %>% 
+  mutate(model = "DCPO\n (Point Estimates)") %>%  
+  bind_rows(df_plot)
+
+df_plotS <- df_plot %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democracy\n (t-1)",
+        "Democracy\n (t-2)",
+      "Democratic\n Mood\n (t-1)",
+      "Log GDP\n per capita\n (t−1)",
+      "GDP per\n capita Growth\n (t−1)",
+      "Regional\n Democracy\n (t−1)",
+      "Percent\n Muslim\n (t-1)",
+      "Resource\n Dependence\n (t−1)"),
+    time = 2)
   )
-}
 
-df_sigma <- purrr::map(1:1000, function(anEntry) {
-  dcpo_sigma$sigma[anEntry, , ] %>%
-  reformat_dcpo_output("sigma")
-})
+# the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
 
-df_sigma_us <- map_df(df_sigma, function(aCountry){
-  filter(aCountry, country == "United States")
-})
+plot_clsVsDCPO <- small_multiple(df_plotS) +
+  theme_minimal() +
+  ggtitle("DV: Liberal Democracy (Vdem)")+
+  theme(legend.position = "none")
 
-df_sigma_usCI <- map_df(unique(df_sigma_us$year), function(aYear){
-  dataAYear <- filter(df_sigma_us, year == aYear)
-  bootstrapCI_sigma(dataAYear)
-}) %>% 
-  mutate(year = unique(df_sigma_us$year))
+df_plot <- df_result_cls[[2]] %>% 
+  mutate(model = "Claassen 2019")
 
-df_sigma_2019 <- map_df(df_sigma, function(aCountry){
-  filter(aCountry, year == 2019)
-})
+df_plot <- df_result_dcpoMean[[2]] %>% 
+  mutate(model = "DCPO\n (Point Estimates)") %>%  
+  bind_rows(df_plot)
 
-df_sigma_2019CI <- map_df(unique(df_sigma_2019$country), function(aCountry){
-  dataACountry <- filter(df_sigma_2019, country == aCountry)
-  bootstrapCI_sigma(dataACountry)
-}) %>% 
-  mutate(country = unique(df_sigma_2019$country))
+df_plotS <- df_plot %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democracy\n (t-1)",
+        "Democracy\n (t-2)",
+      "Democratic\n Demo Only\n (t-1)",
+      "Democratic\n Auto Only\n (t-1)",
+      "Log GDP\n per capita\n (t−1)",
+      "GDP per\n capita Growth\n (t−1)",
+      "Regional\n Democracy\n (t−1)",
+      "Percent\n Muslim\n (t-1)",
+      "Resource\n Dependence\n (t−1)"),
+    time = 2)
+  )
 
-plot_us <- ggplot(df_sigma_usCI, aes(x = mean, y = year, xmin = conf.low, xmax = conf.high)) +
-  geom_point() +
-  geom_errorbarh(height=.2) + 
-  scale_y_reverse(breaks = unique(df_sigma_us$year)) +
-  xlab(expression("Polarization Estimates, "~sigma)) + 
-  ggtitle("Polarization of the U.S. from 1988--2020") +
+plot_clsVsDCPO2 <- small_multiple(df_plotS) +
   theme_minimal() +
-  theme(axis.title.y = element_blank())
+  ggtitle("DV: Liberal Democracy (Vdem)")+
+  theme(legend.position = "none")
 
-plot_2019 <- ggplot(df_sigma_2019CI, aes(x = mean, y = country, xmin = conf.low, xmax = conf.high)) +
-  geom_point() +
-  geom_errorbarh(height=.2) + 
-  xlab(expression("Polarization Estimates, "~sigma)) + 
-  ggtitle("Polarization around the World in 2019") +
-  theme_minimal() +
-  theme(axis.title.y = element_blank())
-
-gridExtra::grid.arrange(plot_us, plot_2019, nrow = 1)
+gridExtra::grid.arrange(plot_clsVsDCPO, plot_clsVsDCPO2, ncol = 2)
 ```
 
-```{r dcpoVisualization, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO"}
+```{r visualizedSep, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO"}
 
-load(here::here("output", "estimates_dcpo.RDS"))
-load(here::here("output", "estimates_cls.RDS"))
-
-df_plot <- df_result_cls[[1]] %>% 
-  mutate(model = "Uncertainty\n Ignored",
-         type = "Pooled OLS")
+df_plot <- df_result_dcpoMean[[1]] %>% 
+  mutate(model = "DCPO\n (Point Estimates)")
 
 df_plot <- df_result_dcpo[[1]] %>%
-  mutate(model = "DCPO",
-         type = "Pooled OLS") %>% 
+  mutate(model = "DCPO\n (w. Uncertainty)") %>%
   rename(std.error = se) %>%
@@
 
-df_plot <- df_result_cls[[3]] %>% 
-  mutate(model = "Uncertainty\n Ignored",
-         type = "System GMM") %>% 
-  bind_rows(df_plot)
-
-df_plot <- df_result_dcpo[[3]] %>% 
-  mutate(model = "DCPO",
-         type = "System GMM") %>% 
-  rename(std.error = se) %>% 
-  bind_rows(df_plot) %>% 
-  select(term, estimate, std.error, model, type)
-
-# the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
-
-plot_pooled <- filter(df_plot, type == "Pooled OLS") %>% 
+plot_pooled <- filter(df_plot, model != "Claassen 2019") %>% 
   dwplot(by_2sd = FALSE) %>%
@@
       `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)",
-`plm::lag(Res_cp_WDI_di, 1)` = "Resource Dependence(t−1)",
-`plm::lag(sigma, 1)` = "Democratic Mood Polarization(t-1)"
+      `plm::lag(Res_cp_WDI_di, 1)` = "Resource Dependence(t−1)"
     )
@@
   theme_minimal() +
-  ggtitle("Pooled OLS") +
+  ggtitle("DV: Liberal Democracy (Vdem)") +
   xlab("Coefficient Estimate") +
-  theme(axis.title.y = element_blank(),
-        legend.position = "none")
+  theme(
+    axis.title.y = element_blank(),
+    legend.position = "bottom",
+    legend.title = element_blank()
+  )
 
-plot_gmm <- filter(df_plot, type == "System GMM") %>% 
+df_plot <- df_result_dcpoMean[[2]] %>% 
+  mutate(model = "DCPO\n (Point Estimates)")
+
+df_plot <- df_result_dcpo[[2]] %>%
+  mutate(model = "DCPO\n (w. Uncertainty)") %>%
+  rename(std.error = se) %>%
+  bind_rows(df_plot)
+
+plot_pooled2 <- filter(df_plot, model != "Claassen 2019") %>% 
   dwplot(by_2sd = FALSE) %>%
@@
       `plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
-`plm::lag(Libdem_VD, 1:2)1` = "Democracy(t-1)",
       `plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
-`plm::lag(Libdem_VD, 1:2)2` = "Democracy(t-2)",
-`plm::lag(theta, 1)` = "Democratic Mood(t-1)",
-`plm::lag(SupDem_trim, 1)` = "Democratic Mood(t-1)",
+      `plm::lag(theta_dem, 1)` = "Mood Democracy(t-1)",
+      `plm::lag(theta_aut, 1)` = "Mood Autocracy(t-1)",
       `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
-`plm::lag(lnGDP_imp, 1)` = "Log GDP per capita(t−1)",
       `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
-`plm::lag(GDP_imp_grth, 1)` = "GDP per capita Growth(t−1)",
       `plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
-`plm::lag(Libdem_regUN, 1)` = "Regional democracy(t−1)",
       `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
-`plm::lag(Pr_Muslim, 1)` = "Percent Muslim (t-1)",
-`plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)",
-`plm::lag(Res_cp_WDI_di, 1)` = "Resource Dependence(t−1)",
-`plm::lag(sigma, 1)` = "Democratic Mood Polarization(t-1)"
+      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)"
     )
@@
   theme_minimal() +
-  ggtitle("System GMM") +
+  ggtitle("DV: Liberal Democracy (Vdem)") +
   xlab("Coefficient Estimate") +
-  theme(axis.title.y = element_blank(),
-        axis.text.y = element_blank(),
-        legend.title = element_blank())
+  theme(
+    axis.title.y = element_blank(),
+    legend.position = "bottom",
+    legend.title = element_blank()
+  )
 
-gridExtra::grid.arrange(plot_pooled, plot_gmm, ncol = 2)
+gridExtra::grid.arrange(plot_pooled,plot_pooled2, ncol = 2)
 ```

### 2020-08-26 R/supdem+democracy+ajps+replication.R

@@ -1,0 +1,714 @@
+#### Does Public Support Help Democracy Survive?
+#### Christopher Claassen
+#### AJPS Replication file: main tables and figures
+
+# install.packages(c('xtable','texreg','plm','pss','arm','dplyr','tidyr','ggplot2','RColorBrewer','rworldmap','rworldmap','statmod','AER','phtt','gtools','rgdal'))
+
+library(xtable)
+library(texreg)
+library(plm)
+library(pss)
+library(arm)
+library(dplyr)
+library(tidyr)
+library(ggplot2)
+library(RColorBrewer)
+library(rworldmap)
+library(statmod)
+library(AER)
+library(phtt)
+library(gtools)
+library(rgdal)
+
+# Working directory
+WD = getwd()
+setwd(WD)
+
+# Get data
+supdem = read.csv("Support_democracy_ajps.csv")
+v_dem = read.csv("vdem15.csv")
+
+# Create panel datasets
+sd.plm = pdata.frame(supdem, index = c("Country", "Year")) # full dataset 
+
+# Summary table
+vars = c("Libdem_VD", "SupDem_m1", "Year", "lnGDP_imp_m1", "GDP_imp_grth_m1", "Libdem_regUN_m1", "Res_cp_WDI_di_m1", 
+         "Pr_Muslim", "Satis_m1", "lnInflat_imp", "Corrup_TI")
+supdem.trim = supdem[complete.cases(supdem[, c("Libdem_VD", "SupDem_m1")]),]
+sum.table = data.frame(
+  Mean=sapply(supdem.trim[,vars], mean, na.rm=TRUE),
+  SD=sapply(supdem.trim[,vars], sd, na.rm=TRUE),
+  Min=sapply(supdem.trim[,vars], min, na.rm=TRUE),
+  Max=sapply(supdem.trim[,vars], max, na.rm=TRUE),
+  NAs=sapply(supdem.trim[,vars], function(x) sum(is.na(x))))
+print(xtable(sum.table, digits=2), type="html", file="table_S1.html")
+
+
+##### Models
+
+
+## Full dynamic ADL models 
+
[…]

### 2020-08-28 paper/dcpo_demsupport.Rmd
starting APSR analysis

@@
 
-```{r claassen-replication}
+```{r claassenAJPS}
 # Data input ----
@@
 
-save(df_result_cls, file = here::here("output", "estimates_cls.RDS"))
+save(df_result_cls, file = here::here("output", "estimates_clsAJPS.RDS"))
 ```
 
-```{r dcpo-point}
+```{r dcpoPointAJPS}
 load(here::here("data", "dcpo_input.rda"))
@@
 load(here::here("data", "dcpo_sigma.rda"))
-
-df_controls <- read_csv(here::here("data", "control_variables.csv"),
-                        col_types = cols(.default = col_double(),
-                                         country = col_character(),
-                                         country_name = col_character(),
-                                         ISO = col_character(),
-                                         Region_UN = col_character())) %>% 
-  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
-         country = countrycode::countrycode(country0, "country.name", "country.name"),
-         regime = Vdem_regime > 1)
 
@@
 
-df_dcpoMean <- df_dcpoMean %>% 
+df_controls <- read_csv(here::here("data", "control_variables.csv"),
+                        col_types = cols(.default = col_double(),
+                                         country = col_character(),
+                                         country_name = col_character(),
+                                         ISO = col_character(),
+                                         Region_UN = col_character())) %>% 
+  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
+         country = countrycode::countrycode(country0, "country.name", "country.name"),
+         regime = Vdem_regime > 1)
+
+df_dcpoMeanAJPS <- df_dcpoMean %>% 
   left_join(df_controls, by = c("country", "year")) %>% 
@@
 
-df_result_dcpoMean <- map(ls_mod, function(mod){
-  result <- plm(mod, model = "pooling", data = df_dcpoMean)
+df_result_dcpoMeanAJPS <- map(ls_mod, function(mod){
+  result <- plm(mod, model = "pooling", data = df_dcpoMeanAJPS)
   df_result <- tidy(result) %>%
@@
 
-save(df_result_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))
+save(df_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))
+save(df_result_dcpoMeanAJPS, file = here::here("output", "estimates_dcpoMeanAJPS.RDS"))
 ```
 
-```{r dcpo-uncertainty, eval = FALSE}
+```{r dcpoUncertaintyAJPS, eval = FALSE}
 df_dcpo <- purrr::map(1:1000, function(anEntry) {
@@
 
-```{r visualizedMood, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO"}
+```{r visualizedMood, fig.cap= "The Effect of Democratic Mood on Institutional Democratization"}
 
-load(here::here("output", "estimates_cls.RDS"))
-load(here::here("output", "estimates_dcpoMean.RDS"))
+load(here::here("output", "estimates_clsAJPS.RDS"))
+load(here::here("output", "estimates_dcpoMeanAJPS.RDS"))
 load(here::here("output", "estimates_dcpo.RDS"))
@@
   ggtitle("DV: Liberal Democracy (Vdem)")+
+  theme(legend.position = "none")
+
+gridExtra::grid.arrange(plot_clsVsDCPO, plot_clsVsDCPO2, ncol = 2)
+```
+
+```{r visualizedUncertain, fig.cap= "The Effect of Democratic Mood on Institutional Democratization Accounting for Uncertainty"}
+
+df_plot <- df_result_dcpoMean[[1]] %>% 
+  mutate(model = "DCPO\n (Point Estimates)")
+
+df_plot <- df_result_dcpo[[1]] %>%
+  mutate(model = "DCPO\n (w. Uncertainty)") %>%
+  rename(std.error = se) %>%
+  bind_rows(df_plot)
+
+plot_pooled <- filter(df_plot, model != "Claassen 2019") %>% 
+  dwplot(by_2sd = FALSE) %>%
+  relabel_predictors(
+    c(
+      `plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
+      `plm::lag(Libdem_VD, 1:2)1` = "Democracy(t-1)",
+      `plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
+      `plm::lag(Libdem_VD, 1:2)2` = "Democracy(t-2)",
+      `plm::lag(theta, 1)` = "Democratic Mood(t-1)",
+      `plm::lag(SupDem_trim, 1)` = "Democratic Mood(t-1)",
+      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
+      `plm::lag(lnGDP_imp, 1)` = "Log GDP per capita(t−1)",
+      `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
+      `plm::lag(GDP_imp_grth, 1)` = "GDP per capita Growth(t−1)",
+      `plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
+      `plm::lag(Libdem_regUN, 1)` = "Regional democracy(t−1)",
+      `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
+      `plm::lag(Pr_Muslim, 1)` = "Percent Muslim (t-1)",
+      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)",
+      `plm::lag(Res_cp_WDI_di, 1)` = "Resource Dependence(t−1)"
+    )
+  ) +
+  geom_vline(xintercept = 0,
+             colour = "grey80",
+             linetype = 2) +
+  theme_minimal() +
+  ggtitle("DV: Liberal Democracy (Vdem)") +
+  xlab("Coefficient Estimate") +
+  theme(
+    axis.title.y = element_blank(),
+    legend.position = "bottom",
+    legend.title = element_blank()
+  )
+
+df_plot <- df_result_dcpoMean[[2]] %>% 
+  mutate(model = "DCPO\n (Point Estimates)")
+
+df_plot <- df_result_dcpo[[2]] %>%
+  mutate(model = "DCPO\n (w. Uncertainty)") %>%
+  rename(std.error = se) %>%
+  bind_rows(df_plot)
+
+plot_pooled2 <- filter(df_plot, model != "Claassen 2019") %>% 
+  dwplot(by_2sd = FALSE) %>%
+  relabel_predictors(
+    c(
+      `plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
+      `plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
+      `plm::lag(theta_dem, 1)` = "Mood Democracy(t-1)",
+      `plm::lag(theta_aut, 1)` = "Mood Autocracy(t-1)",
+      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
+      `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
+      `plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
+      `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
+      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)"
+    )
+  ) +
+  geom_vline(xintercept = 0,
+             colour = "grey80",
+             linetype = 2) +
+  theme_minimal() +
+  ggtitle("DV: Liberal Democracy (Vdem)") +
+  xlab("Coefficient Estimate") +
+  theme(
+    axis.title.y = element_blank(),
+    legend.position = "bottom",
+    legend.title = element_blank()
+  )
+
+gridExtra::grid.arrange(plot_pooled,plot_pooled2, ncol = 2)
+```
+
+```{r claassenAPSR}
+load("../data/dem_mood_apsr.RData")
+sd.plm <- pdata.frame(x, index = c("Country", "Year"))
+
+mods <- vector(mode = "list")
+
+mods[[1]] <- plm(
+  diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Libdem_z, lag = 1)
+  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1),
+  sd.plm,
+  model = "pooling"
+)
+mods[[2]] <- plm(
+  diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Libdem_z, lag = 1)
+  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)
+  + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1),
+  sd.plm,
+  model = "pooling"
+)
+
+vcovHC_se <-  function(x) {
+  plm::vcovBK(x, cluster = "time") %>% 
+    diag() %>% 
+    sqrt()
+}
+
+df_result_clsAPSR <- map(mods, function(aMod){
+  tidy(aMod) %>%
+    mutate(std.error = vcovHC_se(aMod))
+})
+
+save(df_result_clsAPSR, file = here::here("output", "estimates_clsAPSR.RDS"))
+```
+
+```{r dcpoPointAPSR}
+df_controls <- read_csv(here::here("data", "APSRctlv.csv"),
+                        col_types = cols(.default = col_double(),
+                                         country = col_character(),
+                                         country_name = col_character(),
+                                         ISO = col_character(),
+                                         Region_UN = col_character())) %>% 
+  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
+         country = countrycode::countrycode(country0, "country.name", "country.name"))
+
+df_dcpoMeanAPSR <- df_dcpoMean %>% 
+  left_join(df_controls, by = c("country", "year")) %>% 
+  plm::pdata.frame(index = c("country", "year"))
+
+mods <- vector(mode = "list")
+mods[[1]] <-
+  plm(
+    diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1)
+    + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1),
+    data = df_dcpoMeanAPSR,
+    model = "pooling"
+  )
+
+mods[[2]] <-
+  plm(
+    diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1) + diff(cpi_sd, lag = 1) + plm::lag(cpi_sd, 1),
+    data = df_dcpoMeanAPSR,
+    model = "pooling"
+  )
+
+df_result_dcpoMeanAPSR <- map(mods, function(aMod){
+  aMod %>% 
+    tidy %>%
+    mutate(std.error = vcovHC_se(aMod))
+})
+
+save(df_result_dcpoMeanAPSR, file = here::here("output", "estimates_dcpoMeanAPSR.RDS"))
+```
+
+```{r dcpoUncertaintyAPSR, eval = FALSE}
+df_dcpo <- purrr::map(1:1000, function(anEntry) {
+  dcpo_theta$theta[anEntry,,] %>% 
+    reformat_dcpo_output("theta") %>% 
+    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
+              by = c("year", "country")) %>%
+    left_join(df_controls, by = c("country", "year")) %>% 
+    plm::pdata.frame(index = c("country", "year"))
+})
+
+estimate_dcpo <- function(aDataset) {
+
+    result_dcpo_1k <- vector(mode = "list")
+
+    result_dcpo_1k[[1]] <- plm(diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1)
+    + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1), model = "pooling", data = aDataset)
+    result_dcpo_1k[[2]] <- plm(diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1) + diff(cpi_sd, lag = 1) + plm::lag(cpi_sd, 1), model = "pooling", data = aDataset)
+
+    result_vars_dcpo_1k <- map(result_dcpo_1k, function(aFit){
+      mitools::MIextract(aFit, fun = vcovHC_se)
+    })
+
+    result_betas_dcpo_1k <- map(result_dcpo_1k, function(aFit){
+      mitools::MIextract(aFit, fun = coef)
+    })
+
+  df_result_dcpo <- map2(result_vars_dcpo_1k, result_betas_dcpo_1k, function(aVar, aBeta){
+    summary(
+      mitools::MIcombine(results = aBeta, variance = aVar)
+    ) %>% rownames_to_column(var = "term") %>%
+    rename(conf.low = `(lower`,
+           conf.high = `upper)`,
+           estimate = results) %>%
+    filter(!str_detect(term, "(Intercept)"))
+  })
+}
+
+df_result_dcpoAPSR <- map(df_dcpo, estimate_dcpo)
+
+save(df_result_dcpoAPSR, file = here::here("output", "estimates_dcpoAPSR.RDS"))
+```
+
+```{r visualizedMood, fig.cap= "Effects of Democracy on Change in Mood"}
+
+load(here::here("output", "estimates_clsAPSR.RDS"))
+load(here::here("output", "estimates_dcpoMeanAPSR.RDS"))
+load(here::here("output", "estimates_dcpoAPSR.RDS"))
+
+df_plot <- df_result_clsAPSR[[1]] %>% 
+  mutate(model = "Claassen 2020")
+
+df_plot <- df_result_dcpoMeanAPSR[[1]] %>% 
+  mutate(model = "DCPO\n (Point Estimates)") %>%  
+  bind_rows(df_plot)
+
+df_plotS <- df_plot %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+      "Liberal Democracy\n (Difference)",
+      "Liberal Democracy\n (t-1)",
+      "Log GDP\n per capita\n (Difference)",
+      "Log GDP\n (t−1)"),
+    time = 2)
+  )
+
+# the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
+
+plot_clsVsDCPO <- small_multiple(df_plotS) +
+  theme_minimal() +
+  ggtitle("DV: Democracy Mood")+
+  theme(legend.position = "none")
+
+df_plot <- df_result_clsAPSR[[2]] %>% 
+  mutate(model = "Claassen 2020")
+
+df_plot <- df_result_dcpoMeanAPSR[[2]] %>% 
+  mutate(model = "DCPO\n (Point Estimates)") %>%  
+  bind_rows(df_plot)
+
+df_plotS <- df_plot %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+      "Liberal Democracy\n (Difference)",
+      "Liberal Democracy\n (t-1)",
+      "Log GDP\n per capita\n (Difference)",
+      "Log GDP\n (t−1)",
+      "Corruption\n (Difference)",
+      "Corruption\n (t−1)"
+      ),time = 2)
+  )
+
+plot_clsVsDCPO2 <- small_multiple(df_plotS) +
+  theme_minimal() +
+  ggtitle("DV: Democracy Mood")+
   theme(legend.position = "none")

### 2020-08-28 R/democratic+mood+APSR+replication.R

@@ -1,0 +1,983 @@
+#### In the Mood for Democracy
+#### Christopher Claassen
+#### APSR Replication file: main tables and figures
+
+# install.packages(c('xtable','texreg','plm','dplyr','tidyr','ggplot2','RColorBrewer','AER','MASS','lme4'))
+
+library(xtable)
+library(texreg)
+library(plm)
+library(dplyr)
+library(tidyr)
+library(ggplot2)
+library(RColorBrewer)
+library(AER)
+library(MASS)
+library(lme4)
+
+
+# Setup working directory
+
+WD = getwd()
+setwd(WD)
+
+# Get data
+
+supdem = read.csv("dem_mood_apsr.csv")
+sd.plm = pdata.frame(supdem, index = c("Country", "Year")) 
+
+
+
+##### Models
+
+
+# ECM models with Lib Dem index
+
+mod1 = plm(diff(SupDem_trim, lag=1) ~ plm::lag(SupDem_trim, 1:2) + diff(Libdem_z, lag=1) 
+           + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag=1) + plm::lag(lnGDP_imp, 1), 
+           sd.plm, model="pooling")
+mod2 = plm(diff(SupDem_trim, lag=1) ~ plm::lag(SupDem_trim, 1:2) + diff(Libdem_z, lag=1) 
+           + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag=1) + plm::lag(lnGDP_imp, 1) 
+           + diff(Corrup_TI_z, lag=1) + plm::lag(Corrup_TI_z, 1), sd.plm, model="pooling")
+
+mods = list(mod1, mod2)
+vcm = lapply(mods, function(x) plm::vcovHC(x, method="arellano", cluster="group"))
+rse = lapply(vcm, function(x) sqrt(diag(x)))
+pval = list()
+for(i in 1:length(mods)) {pval[[i]] = pt(abs(coef(mods[[i]]) / rse[[i]]), df=2500, lower.tail=FALSE) * 2}
+screenreg(mods, override.se=rse, override.pvalues=pval, digits=3, single.row=FALSE, leading.zero=FALSE, 
+          stars=c(0.05))
+
+# FD models with Lib Dem index
+
[…]

### 2020-08-28 paper/dcpo_demsupport.Rmd
apsr with uncertainty

@@
 
-    result_dcpo_1k[[1]] <- plm(diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1)
-    + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1), model = "pooling", data = aDataset)
-    result_dcpo_1k[[2]] <- plm(diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1) + diff(cpi_sd, lag = 1) + plm::lag(cpi_sd, 1), model = "pooling", data = aDataset)
+    result_dcpo_1k[[1]] <-
+      plm(
+        diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1)
+        + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1),
+        model = "pooling",
+        data = aDataset
+      )
 
-    result_vars_dcpo_1k <- map(result_dcpo_1k, function(aFit){
+    result_dcpo_1k[[2]] <-
+      plm(
+        diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1) + diff(cpi_sd, lag = 1) + plm::lag(cpi_sd, 1),
+        model = "pooling",
+        data = aDataset
+      )
+
+}
+
+df_result_dcpoAPSR <- map(df_dcpo, estimate_dcpo)
+
+result_vars_dcpo_1k <- map(df_result_dcpoAPSR, function(aFit){
       mitools::MIextract(aFit, fun = vcovHC_se)
@@
 
-    result_betas_dcpo_1k <- map(result_dcpo_1k, function(aFit){
+result_betas_dcpo_1k <- map(df_result_dcpoAPSR, function(aFit){
       mitools::MIextract(aFit, fun = coef)
@@
 
-  df_result_dcpo <- map2(result_vars_dcpo_1k, result_betas_dcpo_1k, function(aVar, aBeta){
+df_result_dcpoAPSR <- map2(result_vars_dcpo_1k, result_betas_dcpo_1k, function(aVar, aBeta){
     summary(
@@
   })
-}
-
-df_result_dcpoAPSR <- map(df_dcpo, estimate_dcpo)
 

### 2020-08-28 paper/dcpo_demsupport.Rmd
HC_se fixed
adding the apsr fully reproduction, #13

--- 2020-08-28 paper/dcpo_demsupport.Rmd
@@
 vcovHC_se <-  function(x) {
-  plm::vcovBK(x, cluster = "time") %>% 
+  plm::vcovHC(x, method="arellano", cluster="group") %>% 
     diag() %>% 
@@
 
-estimate_dcpo <- function(aDataset) {
+estimate_dcpo <- vector(mode = "list")
 
-    result_dcpo_1k <- vector(mode = "list")
+estimate_dcpo[[1]] <- function(aDataset) {
+  plm(
+      diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1)
+      + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1),
+      model = "pooling",
+      data = aDataset
+    )
+}
 
-    result_dcpo_1k[[1]] <- plm(diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1)
-    + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1), model = "pooling", data = aDataset)
-    result_dcpo_1k[[2]] <- plm(diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1) + diff(cpi_sd, lag = 1) + plm::lag(cpi_sd, 1), model = "pooling", data = aDataset)
+estimate_dcpo[[2]] <- function(aDataset) {
+  plm(
+      diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1) + diff(cpi_sd, lag = 1) + plm::lag(cpi_sd, 1),
+      model = "pooling",
+      data = aDataset
+    )
+}
 
-    result_vars_dcpo_1k <- map(result_dcpo_1k, function(aFit){
-      mitools::MIextract(aFit, fun = vcovHC_se)
-    })
+df_result_dcpoAPSR <- map(estimate_dcpo, function(aModel){
+  aFit <- map(df_dcpo, aModel)
 
-    result_betas_dcpo_1k <- map(result_dcpo_1k, function(aFit){
-      mitools::MIextract(aFit, fun = coef)
-    })
+  result_vars_dcpo_1k <- mitools::MIextract(aFit, fun = vcovHC_se)
+  result_betas_dcpo_1k <- mitools::MIextract(aFit, fun = coef)
 
-  df_result_dcpo <- map2(result_vars_dcpo_1k, result_betas_dcpo_1k, function(aVar, aBeta){
   summary(
-      mitools::MIcombine(results = aBeta, variance = aVar)
+      mitools::MIcombine(results = result_betas_dcpo_1k, 
+                         variance = result_vars_dcpo_1k)
     ) %>% rownames_to_column(var = "term") %>%
@@
     filter(!str_detect(term, "(Intercept)"))
+
 })
-}
-
-df_result_dcpoAPSR <- map(df_dcpo, estimate_dcpo)
 

### 2020-08-28 paper/dcpo_demsupport.Rmd
clean the chunk names

@@
 
-```{r visualizedMood, fig.cap= "The Effect of Democratic Mood on Institutional Democratization"}
+```{r visualizedMoodAJPS, fig.cap= "The Effect of Democratic Mood on Institutional Democratization"}
 
@@
 
-```{r visualizedUncertain, fig.cap= "The Effect of Democratic Mood on Institutional Democratization Accounting for Uncertainty"}
+```{r visualizedUncertainAJPS, fig.cap= "The Effect of Democratic Mood on Institutional Democratization Accounting for Uncertainty"}
 
@@
 
+load(here::here("output", "estimates_dcpoMean.RDS"))
+
 df_dcpoMeanAPSR <- df_dcpoMean %>% 
@@
 
-```{r visualizedMood, fig.cap= "Effects of Democracy on Change in Mood"}
+```{r visualizedMoodAPSR, fig.cap= "Effects of Democracy on Change in Mood"}
 
@@
 load(here::here("output", "estimates_dcpoMeanAPSR.RDS"))
-load(here::here("output", "estimates_dcpoAPSR.RDS"))
 
@@
 
-```{r visualizedSep, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO"}
+```{r visualizedUncertaintyAPSR, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO"}
 
-df_plot <- df_result_dcpoMean[[1]] %>% 
+load(here::here("output", "estimates_dcpoAPSR.RDS"))
+
+df_plot <- df_result_dcpoMeanAPSR[[1]] %>% 
   mutate(model = "DCPO\n (Point Estimates)")
 
-df_plot <- df_result_dcpo[[1]] %>%
+df_plot <- df_result_dcpoAPSR[[1]] %>%
   mutate(model = "DCPO\n (w. Uncertainty)") %>%
@@
     c(
-      `plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
-      `plm::lag(Libdem_VD, 1:2)1` = "Democracy(t-1)",
-      `plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
-      `plm::lag(Libdem_VD, 1:2)2` = "Democracy(t-2)",
-      `plm::lag(theta, 1)` = "Democratic Mood(t-1)",
-      `plm::lag(SupDem_trim, 1)` = "Democratic Mood(t-1)",
+      `plm::lag(theta, 1:2)1` = "Democracy Mood(t-1)",
+      `plm::lag(theta, 1:2)2` = "Democracy Mood(t-2)",
+      `diff(Vdem_libdem_z, lag = 1)` = "Liberal Democracy (Diff)",
+      `plm::lag(Vdem_libdem_z, 1)` = "Liberal Democracy (t-1)",
+      `diff(lg_imp_mdpgdp, lag = 1)` = "Log GDP per capita(Diff)", 
       `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
-      `plm::lag(lnGDP_imp, 1)` = "Log GDP per capita(t−1)",
-      `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
-      `plm::lag(GDP_imp_grth, 1)` = "GDP per capita Growth(t−1)",
-      `plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
-      `plm::lag(Libdem_regUN, 1)` = "Regional democracy(t−1)",
-      `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
-      `plm::lag(Pr_Muslim, 1)` = "Percent Muslim (t-1)",
-      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)",
-      `plm::lag(Res_cp_WDI_di, 1)` = "Resource Dependence(t−1)"
+      `plm::lag(mdprgdp_grwth, 1)` = "Corruption (Difference)"
     )
@@
 
-df_plot <- df_result_dcpoMean[[2]] %>% 
+df_plot <- df_result_dcpoMeanAPSR[[2]] %>% 
   mutate(model = "DCPO\n (Point Estimates)")
 
-df_plot <- df_result_dcpo[[2]] %>%
+df_plot <- df_result_dcpoAPSR[[2]] %>%
   mutate(model = "DCPO\n (w. Uncertainty)") %>%
@@
     c(
-      `plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
-      `plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
-      `plm::lag(theta_dem, 1)` = "Mood Democracy(t-1)",
-      `plm::lag(theta_aut, 1)` = "Mood Autocracy(t-1)",
+      `plm::lag(theta, 1:2)1` = "Democracy Mood(t-1)",
+      `plm::lag(theta, 1:2)2` = "Democracy Mood(t-2)",
+      `diff(Vdem_libdem_z, lag = 1)` = "Liberal Democracy (Diff)",
+      `plm::lag(Vdem_libdem_z, 1)` = "Liberal Democracy (t-1)",
+      `diff(lg_imp_mdpgdp, lag = 1)` = "Log GDP per capita(Diff)", 
       `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
-      `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
-      `plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
-      `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
-      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)"
+      `diff(cpi_sd, lag = 1)` = "Corruption (Difference)",
+      `plm::lag(cpi_sd, 1)` = "Corruption (t-1)"
     )

### 2020-09-03 paper/dcpo_demsupport.Rmd
trimmed data updating

@@
 
-```{r claassenAJPS}
-# Data input ----
+```{r dataInput, eval = FALSE}
 
@@
 v_dem <- read.csv("../data/vdem15.csv")
-
 sd.plm <- pdata.frame(supdem, index = c("Country", "Year"))
 
+load(here::here("data", "claassen_m5_theta.rda"))
+load(here::here("data", "dcpo_input.rda"))
+load(here::here("data", "dcpo_theta.rda"))
+load(here::here("data", "dcpo_sigma.rda"))
+load(here::here("data", "dem_mood_apsr.RData"))
+
+```
+
+```{r claassenAJPS}
 # Pooled model -----
@@
 
+```{r claassenUncertainty}
+
+ls_country <- levels(dcpo_input$data$kk)
+first_year <- min(dcpo_input$data$year)
+
+df_claassen <- purrr::map(1:1000, function(anEntry) {
+  claassen_m5_theta$theta[anEntry,,] %>% 
+    reformat_dcpo_output("theta") %>% 
+    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
+              by = c("year", "country")) %>%
+    left_join(df_controls, by = c("country", "year")) %>% 
+    mutate(theta_dem = theta * regime,
+           theta_aut = theta * (1 - regime)) %>% 
+    plm::pdata.frame(index = c("country", "year"))
+})
+
+estimate_dcpo <- function(aModel, aType = "pooling") {
+  if (aType == "gmm") {
+    result_dcpo_1k <- map(df_dcpo, function(aDataset) {
+      pgmm(
+        as.formula(aModel),
+        effect = "individual",
+        model = "onestep",
+        transformation = "ld",
+        indexes = c("Country", "Year"),
+        data = aDataset
+      )
+    })
+
+    result_vars_dcpo_1k <-
+      mitools::MIextract(result_dcpo_1k, fun = vcovHC_se)
+
+  } else {
+    result_dcpo_1k <- map(df_dcpo, function(aDataset) {
+      plm::plm(aModel,
+               model = "pooling",
+               data = aDataset)
+    })
+
+    result_vars_dcpo_1k <-
+      mitools::MIextract(result_dcpo_1k, fun = vcovBK_se)
+  }
+
+  result_betas_dcpo_1k <-
+    mitools::MIextract(result_dcpo_1k, fun = coef)
+
+  df_result_dcpo <-
+    summary(
+      mitools::MIcombine(results = result_betas_dcpo_1k, variance = result_vars_dcpo_1k)
+    ) %>% rownames_to_column(var = "term") %>%
+    rename(conf.low = `(lower`,
+           conf.high = `upper)`,
+           estimate = results) %>%
+    filter(!str_detect(term, "(Intercept)"))
+}
+
+mod_ls <- paste0(
+  "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
+  c("plm::lag(theta, 1)", 
+    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
+  " + plm::lag(lg_imp_mdpgdp, 1) +
+             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
+             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)"
+)
+
+df_result_dcpo <- map(mod_ls, estimate_dcpo)
+
+save(df_result_dcpo, file = here::here("output", "estimates_dcpo.RDS"))
+```
+
 ```{r dcpoPointAJPS}
-load(here::here("data", "dcpo_input.rda"))
-load(here::here("data", "dcpo_theta.rda"))
-load(here::here("data", "dcpo_sigma.rda"))
-
 ls_country <- levels(dcpo_input$data$kk)
@@
 ```{r claassenAPSR}
-load("../data/dem_mood_apsr.RData")
 sd.plm <- pdata.frame(x, index = c("Country", "Year"))

### 2020-09-03 paper/dcpo_demsupport.Rmd
loading data in the front
results with the trimmed data

@@
 
-df_controls <- read_csv(here::here("data", "control_variables.csv"),
+save(df_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))
+
+df_controls <- read_csv(here::here("data", "control_variables_ajps.csv"),
                         col_types = cols(.default = col_double(),
@@
          country = countrycode::countrycode(country0, "country.name", "country.name"),
-         regime = Vdem_regime > 1)
+         regime = Vdem_regime > 1) %>% 
+  filter(year >= first_year) # using trimmed data as Claassen
 
 df_dcpoMeanAJPS <- df_dcpoMean %>% 
-  left_join(df_controls, by = c("country", "year")) %>% 
+  right_join(df_controls, by = c("country", "year")) %>% 
   mutate(theta_dem = theta * regime,
@@
 
-save(df_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))
 save(df_result_dcpoMeanAJPS, file = here::here("output", "estimates_dcpoMeanAJPS.RDS"))
@@
 
-df_result_dcpo <- map(mod_ls, estimate_dcpo)
+df_result_dcpoAJPS <- map(mod_ls, estimate_dcpo)
 
-save(df_result_dcpo, file = here::here("output", "estimates_dcpo.RDS"))
+save(df_result_dcpoAJPS, file = here::here("output", "estimates_dcpoAJPS.RDS"))
 ```
@@
 load(here::here("output", "estimates_dcpoMeanAJPS.RDS"))
-load(here::here("output", "estimates_dcpo.RDS"))
+load(here::here("output", "estimates_dcpoAJPS.RDS"))
 
@@
 
-df_plot <- df_result_dcpoMean[[1]] %>% 
+df_plot <- df_result_dcpoMeanAJPS[[1]] %>% 
   mutate(model = "DCPO\n (Point Estimates)") %>%  
@@
 
-df_plot <- df_result_dcpoMean[[2]] %>% 
+df_plot <- df_result_dcpoMeanAJPS[[2]] %>% 
   mutate(model = "DCPO\n (Point Estimates)") %>%  

### 2020-09-03 paper/dcpo_demsupport.Rmd
apsr with trimmed data

@@
          regime = Vdem_regime > 1) %>% 
-  filter(year >= first_year) # using trimmed data as Claassen
+  filter(year >= firstyear) # using trimmed data as Claassen
 
@@
 
-df_plot <- df_result_dcpoMean[[1]] %>% 
+df_plot <- df_result_dcpoMeanAJPS[[1]] %>% 
   mutate(model = "DCPO\n (Point Estimates)")
 
-df_plot <- df_result_dcpo[[1]] %>%
+df_plot <- df_result_dcpoAJPS[[1]] %>%
   mutate(model = "DCPO\n (w. Uncertainty)") %>%
@@
 
-df_plot <- df_result_dcpoMean[[2]] %>% 
+df_plot <- df_result_dcpoMeanAJPS[[2]] %>% 
   mutate(model = "DCPO\n (Point Estimates)")
 
-df_plot <- df_result_dcpo[[2]] %>%
+df_plot <- df_result_dcpoAJPS[[2]] %>%
   mutate(model = "DCPO\n (w. Uncertainty)") %>%
@@
 ```{r dcpoPointAPSR}
-df_controls <- read_csv(here::here("data", "APSRctlv.csv"),
+df_controls <- read_csv(here::here("data", "control_variables_apsr.csv"),
                         col_types = cols(.default = col_double(),
@@
   mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
-         country = countrycode::countrycode(country0, "country.name", "country.name"))
+         country = countrycode::countrycode(country0, "country.name", "country.name")) %>% 
+  filter(year >= firstyear)
 
@@
   plm(
-    diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1) + diff(cpi_sd, lag = 1) + plm::lag(cpi_sd, 1),
+    diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1) + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1),
     data = df_dcpoMeanAPSR,
@@
   plm(
-      diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1) + diff(cpi_sd, lag = 1) + plm::lag(cpi_sd, 1),
+      diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1) + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1),
       model = "pooling",
@@
     term = rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-      "Liberal Democracy\n (Difference)",
-      "Liberal Democracy\n (t-1)",
+      c("Democratic\n Mood\n (t-1)",
+        "Democratic\n Mood\n (t-2)",
+      "Liberal\n Democracy\n (Difference)",
+      "Liberal\n Democracy\n (t-1)",
       "Log GDP\n per capita\n (Difference)",

### 2020-09-08 paper/dcpo_demsupport.Rmd
draft

@@
 ---
-
-One of the classic but disputable questions in comparative politics is whether mass democratic support stabilizes democracy.
+One of the classic but disputable questions in comparative politics is the relationship between mass democratic support and countries' level of democracy.
 A long-standing and widely accepted theory is that the level of mass democratic support determines the stability of a democratic system [e.g., @lipset_social_1959; @norris_democratic_2011], but findings from empirical analyses still remain inconclusive [@inglehart_modernization_2005; @fails_changing_2010; @qi_how_2011, see @Claassen2020a for a review in this literature].
@@
 Measuring democratic support by using self-report survey data is still the dominant approach.
-However, it is questionable that whether self-report attitude toward democracy could transfer to behaviorally democratic commitments when the democratic system is in economic or societal crisis.
-Recent studies show that although the public understands and supports democratic principles, their support is elastic, especially in the context of polarization [@graham_democracy_2020].
-Voters sometimes are willing to subordinate democratic norms to their partisan and policy preferences [@nyhan_who_2020] and subsequently support their elected leaders to take anti-democratic measures [@mccoy_democratic_2020].
-However, one more essential concern is whether and how we can measure the latent public opinion correctly, especially for comparative public opinion survey data.
+However, one essential concern is whether and how we can measure the latent public opinion correctly, especially for comparative public opinion survey data.
 The sparse and incomparable comparative public opinion data has perplexed the study of comparative politics for a long time [@Solt2020a].
-Public support for democracy is a latent variable and the incorrect measurement of it may conceal the real relationship between public opinion and democratic insitution development.
-Recently, a few pioneering studies are contributing to the latent public opinion measurement in comparative studies [@Caughey2019,@Claassen2019,@Solt2020a].
+Public support for democracy is a latent variable and the incorrect measurement of it may conceal the real relationship between public opinion and democratic institution development.
+Recently, a few pioneering studies are contributing to the latent public opinion measurement in comparative studies[@Caughey2019,@Claassen2019,@Solt2020a].     
 A prominent study by @Claassen2020a applied an advanced Bayesian Item Response Model to measure dynamic public democratic support for 135 countries for up to 29 years.
@@
 @Claassen2020a's study reignites the debate on the relationship between public opinion and democracy.
-
-To adjudicate/contribute to the ongoing debate, this research note reexamines the relationship between public democratic support and democracy stability by applying a superior measure and incorporating a larger data and uncertainty.
-We use a superior measure, Dynamic Comparative Public Opinion (DCPO) model developed by @Solt2020a, to estimate democratic support for a larger data with 144 countries for up to 32 years between 1988 and 2019.
+To adjudicate/contribute to the ongoing debate, by using a superior measurement, bigger data, and incorporating uncertainty, our study presents a thorough reexamination of the relationship between mass democratic support and democracy survival across counties and over time.
+We use a superior measure, Dynamic Comparative Public Opinion (DCPO) model developed by@Solt2020a, to estimate democratic support for a larger dataset with 144 countries for up to 33 years between 1988 and 2020.
 In addition to account for item response bias across countries and the extent of polarization by generating estimates on bounded scales, the DCPO model has superiority in dealing with both binominal and ordinal survey data cross countries over time.
 Both internal and external k-fold validation tests corroborate that the DCPO model yields more accurate results than other latent variable measurements, either of @Claassen2019 Model 5 and @Caughey2019 model.
-Next, we incorporate uncertainty by using random draws from the posterior distributions and following @Rubin1987's rules.
-A latent construct should be measured with uncertainty because it is impossible to measure the complex concept perfectly and uncertainty is substantively necessary for “comparing relationship between complex theoretical concepts across political contexts and over time" [@Crabtree2015,p2].
-
+The nature of latent variables' unobservability decides that the estimates of latent variables are inherently accompanied with measurement uncertainty. 
+Omitting to account for measurement error distorts both statistical and substantive inference (See Juhl 2019for review in this literature). 
+Since the measurement uncertainty could have consequential (propagated) effects on inferences about the relationship of substantive interests, it is strongly recommended to incorporate the measurement uncertainty in analysis models (Treier and Jackman 2008, Crabtree and Fariss 2015).
+Many scholars have taken the account for measurement error in analyses as a final crucial part in their empirical studies (Schnakenberg and Fariss 2014, Caughey and Warshaw 2018), and recent studies on latent variable measurement emphasized the incorporation of measurement uncertainty when using their measures ( Solis and Waggoner 2020, Gandhi and Sumner 2020).
+However, in comparative public opinion field, previous efforts on measuring comparative public opinion didn’t account for measurement uncertainty in their analysis.  
+To address the uncertainty, the inherent trail of latent constructs, in addition to employ the DCPO which reduces uncertainty in measurement, we also incorporated uncertainty in our analysis by using random draws from the posterior distributions and following @Rubin1987's rules.
 Surprisingly, our study reveals that there is no significant relationship between public support and democratic change in both the replication analysis of @Claassen2020a model and DCPO analysis when uncertainty is included.
+Our study reaffirms Fariss 2014, Juhl (2019) and Solt (2020)'s suggestion that given the latent character of variables in political science, scholars should be vigilant in measurement uncertainty. 
+In addition to methodological concerns, our reanalysis echoes recent studies about public’s behavioral commitment to democracy.  
+It is questionable that whether self-report based conventional measures of support for democracy could transfer to behaviorally democratic commitments when the democratic system is in economic or societal crisis.
+Recent studies show that although the public understands and supports democratic principles, their support is elastic, especially in the context of polarization [@graham_democracy_2020].
+Voters sometimes are willing to subordinate democratic norms to their partisan and policy preferences [@nyhan_who_2020] and subsequently support their elected leaders to take anti-democratic measures [@mccoy_democratic_2020].
 
@@
 # More Data
-We collected available data from 62 survey questions in 120 surveys across 159 countries for up to 33 years between 1988 and 2020.
-Survey data was extracted automatically through DCPO package.
-DCPO package also automatically identifies survey conducted year, which captures more accurate correspondence between public opinion and democracy level.
-Compared to Claassen's (2019) 1178 available country-years, our data consists of 1406 country-years, which is a 19.4% increase.
-The mass support for democracy is estimated for 144 countries with at least 2 country-years observed.
-Since V-Dem does not have data for small countries and data for 2020, xx countries are filtered from our final data set.
-The dataset in our analysis consists of xxxx estimates, drawn from 144 countries.
+We collected data on 62 items from 17 survey projects in 159 countries covering years from 1988 to 2020.
+Survey data was extracted automatically through the `DCPO` package for R [@Solt2020a], which is written in the Stan probabilistic programming language [@StanDevTeam2019a; @StanDevTeam2019b].
+The DCPO package also automatically identifies the year in which the survey was conducted, which contributes to the capture of the real relationship between public opinion and the level of democracy.
+Our data consists of 1,465 country-years and 1,861 national surveys, which is a 24.4% and 33.9% increase respectively over 1,178 country-years and 1,390 national surveys used in Claassen's study [-@Claassen2020a; -@Claassen2020b].
 
@@
 # A Better Measure of Democratic Support
-The DCPO model is estimated using the `DCPO` package for R [@Solt2020a], which is written in the Stan probabilistic programming language [@StanDevTeam2019a; @StanDevTeam2019b].
-The DCPO shows its superiority in several significant ways. 
-First, the model permits to treat the data as their originial scales, either dichotomou or ordinal.
-Second, the model generates estimates on a bounded scale. Bounded scales serve to both theoretical and methodologoical needs [@Linzer2015]. 
-Third, the model takes into account item response bias across countries.
-Results from validation tests in @Solt2020a.
-In validation tests, @Solt2020a employs k-fold validation with 10 folds, which reduces the misrepresentation of the model due to the chosen data from single cross-validation.
-The validation tests corroborate that DCPO not only features the smallest mean absolute error and largest improvement over the country-means MAE but also provides a more stable and efficient prediction on out-of-sample data than either of @Claassen2019 Model 5 and @Caughey2019 model.
+Using the DCPO model in the `DCPO` package, we attained 4,752 estimates for mass support for democracy, drawn from 144 countries with at least 2 country-years observed.
+The DCPO model has methodological superiority in significant ways. 
+First, the DCPO model allows us to treat the data as their original scales, either dichotomous or ordinal, to avoid information missing due to the potential scale change.
+For example, our data consists of 20885 national responses as the result of measuring public attitude at ordinal scales, which has potential to give us more nuances about public demcratic support. 
+Second, to reduce the uncertainty in estimating countries which lie at the extreme ends of the public opinion spectrum[@Linzer2015], the estimates of mean public opinion are bounded and the extent of polarization is included in the DCPO model.
+The capture of the extent of polarization is more meaningful in this era, since the respondents from countries with more polarized opinions are more likely to give negative responses even though these countries may have the similar mean estimates of public opinion.
+It is worth noticing that the small number of extreme opinions in countries may have a louder voice and bigger effects on actual politics. 
+Third, to address the differences in item response across countries, caused by factors other than public attitude or preference, a country-specific item bias is modelled as "a country-specific bias in the difficulty of each question" [@Solt2020a, 6].
+This approach allows us to keep information embeded in questions rather than discarding them directly. 
+In sum, the DCPO model has methodological advantages in keeping as much as available information, reducing uncertainty by bounding scales and capturing the extent of polarization. 
+The validation tests in @Solt2020a's paper corroborate that DCPO not only features the smallest mean absolute error(MAE) and largest improvement over the country-means MAE but also provides a more stable and efficient prediction on out-of-sample data than either of @Claassen2019 Model 5 and @Caughey2019 model.
+Following @Solt2020a's apporoach, our validation test employ k-fold validation with 10 folds, which reduces the misrepresentation of the model due to the chosen data from single cross-validation (See details of the validation test in Appendix).
 
@@
 # Incorporating Uncertainty
-Instead of simply employing the point estimates, that is, the means of the posterior distributions [_contra_ @Claassen2020a; @Claassen2020b], it is recommended to incorporate uncertainty in using latent variables [e.g., @Schnakenberg2014; @Crabtree2015] and other measures, such as the Standardized World Income Inequality Database [@Solt2020].
-In this study, we generate 1,000 duplicate versions of the analysis dataset, assign to each a different random draw from the posterior distributions of public democratic support, perform the analyses repeatedly on each of these 1,000 versions of the dataset, and combine the results following the rules set out in @Rubin1987.
-The functional programming tools in the `purrr` package [@Henry2019] make this a matter of just a few additional lines of code.
+The latent constructs are inherently accompanied with amount of measurement uncertainty due to the unobservability of variables.
+The measurement is more far away from prefection when concepts are complex. 
+With a strong assumption that latent variables are measured perfectly, the omittance to incorporate measurement error might obscure the true relationship between theoretical concepts and invalidates findings.
+Therefore, incorporating uncertainty is substantively necessary for “comparing relationship between complex theoretical concepts across political contexts and over time"[@Crabtree2015,p2]. 
+In our reexamination, instead of employing the point estimates, we relax the implausible assumption of perfect measurment of latent variables, we followed the recommendation and the approach of incorporating uncertainty in using latent variables [e.g., @Schnakenberg2014; @Crabtree2015] and other measures, such as the Standardized World Income Inequality Database [@Solt2020].
+Specifically, we generated 1,000 duplicate versions of the analysis dataset, assigned to each a different random draw from the posterior distributions of public democratic support, performed the analyses repeatedly on each of these 1,000 versions of the dataset, and then combined the results following the rules set out in @Rubin1987.
+This process can be achieved by using the `purrr` package [@Henry2019] and adding only a few lines of code.
 
@@
 # Results
+Our reanalysis follows the following steps. Frist, we replicated Claassen's  (2019,2020)  studies by using his measurement and analysis models.
+Results here.
+Next, adding measurement uncertainty into Claassen's analysis models, we found xxxx.
+Tables and results here.
+We then reanalyzed the relationship between public democratic attitude and democracy institution in both directions, using more data, the DCPO measurement model and measurement uncertainty incorporated.
+Results here. indistinguishable from zero.
+In short, the main empirical findings about the estimated effect of public democratic support on democracy or vice versa are not replicable when measurement uncertainty is accounted, even using better measurement and more data.
+There are potential causes for the null results.
+First, the survey items we used might not capture real public democratic support, given the complexity of this concept and limited indicators compared to other concepts like gender egalitarian (Solt, 2021??).
+Second, these survey items do capture public democratic support, but we still don’t have enough data to compensate the fragmentation and incomparability of the available comparative public opinion data, which is doomed to accompany with high uncertainty.
+Methodologically, given the nature trail of latent variables and specific characters of comparative public opinion, performing analyses based on the strong assumption that comparative public attitudes are perfectly measured might exaggerate scholars' certainty methodologically and obscure a proper substantive evaluation of theoretical claims.
+In addition to the potentially methodological cause, the measurement errors, there are some potentially substantive causes for the disappearing relationship.
+First, democratic backsliding might be mainly caused by elites.
+Elites are thought to play a critical role in preserving democratic stability by respecting the limits on their behaviors (Weingast 1997).
+After the Cold War, many democracies backslided and imperiled in the worldwide because elected leaders lack of commitment to democratic norms when the public even did not notice that (Bermeo 2016; Levtsky and Ziblatt 2018, Waldner and Lust 2018).
+Second, there has been a gulf between public perception and elites’ perception on important democratic principles (McClosky, 1959).
+A recent study shown that polarized public cannot get a consensus on democratic erosion which experts preserved (Carey et al 2018).
+Given the measures for democratic development are from experts, there could be a gap between public perception on democracy and the measures of the levels of democracy.
+Third, since there is a difference between the public support for democracy in the abstract and under specific propositions (Bartels 2020), recent studies questioned whether conventional measures of public support for democracy could capture public realistic commitment to democracy.
+By using survey experiments, Graham an Svolik (2020) pointed out a " fundamental blind spot" in traditional measures of public democratic support: the questions regarding the support for an abstract democracy cannot capture public willingness and behavioral commitment to democratic principles when voters have to choose between democratic norms and their partisan identification or policy preference.
+It turned out that voters subordinated democratic norms to their partisan preference by not electorally penalizing their candidates who endorse measures that violate norms.
+Furthermore, McCoy et al (2020) found that rather than only tolerate anti-democratic policies, voters support/encourage these policies when their co-partisans are in power. 
+This increasing substantial literature emphasizes the eroding effect of polarization on democracy worldwide (McCoy et al 2019). 
+Regarding the polarization, the sigma in our measurement model captures the polarization.
+The figure xx shows the varying polarization in public support for democracy across countries. 
+Given the uncertainty in measures of public support, it is unsurprising that we did not find the statistically significant effect of polarization.
+However, the estimated effect of the interaction term between public support and polarization was negative, which referred to the attenuation effect of polarization on the impact of public support on democracy.
+Specifically, the big polarization in the U.S. implies that political polarization exists not only in partisan politics but also in more general democracy values.
+Future studies could take advantage of the DCPO’s polarization measurement in their analysis, given the necessity to analyze traditional relationships under the environment of polarization.
 
@@
 # Conclusion
+In this reexamination, we show how the measurement uncertainty of public attitude causes inferential errors regardless of public attitude as an independent variable or dependent variable, even using more data and a sophisticated DCPO model which reduces the noises in measures for extreme countries.
+Our study has important implications in several aspects. 
+In terms of data, although democracy and democratization are the primary theme in comparative politics, the indicators of public democratic attitude are limited compared to other concepts, like gender egalitarian (Solt 2020?).
+More data and more indicators could serve to reduce the uncertainty in measuring public democratic attitude.
+Employing a more reliable statistical measurement model could not only make public opinion across countries comparable and but also reduce the uncertainty in the measurement stage. 
+Given the inherent uncertainty accompanying latent public opinion, and its propagated effects in analysis, we especially recommend that incorporating measurement uncertainty in analysis models is a safer way to infer the relationship between public opinion and other substantive interest especially for comparative politics, in which the measurement uncertainty of public opinion is further exacerbated by the sparse and incomparability of indicators.
+Substantively, the association between public democratic attitude and democratic development might be not robust especially in the era of political polarization within countries. 
+A strong estimated effect of public attitude might endure the propagated effect from the measurement uncertainty. 
+However, if the effect itself is not robust enough, any theoretical inference could be easily wiped out due to the imperfect measurement of public opinion. 
+It suggests that the relationship between public opinion and institution or policy making should be considered in the environment of polarization where people might subordinate their behaviorally commitment to democracy to their partisan loyalty or policy preference.
 

### 2020-09-25 paper/dcpo_demsupport.Rmd
word changes.

@@
 The sparse and incomparable comparative public opinion data has perplexed the study of comparative politics for a long time [@Solt2020a].
-Public support for democracy is a latent variable and the incorrect measurement of it may conceal the real relationship between public opinion and democratic institution development.
+Public support for democracy is a latent variable and the incorrect measurement of it may conceal the real relationship between public opinion and democratic institutional development.
 Recently, a few pioneering studies are contributing to the latent public opinion measurement in comparative studies[@Caughey2019,@Claassen2019,@Solt2020a].     
@@
 To adjudicate/contribute to the ongoing debate, by using a superior measurement, bigger data, and incorporating uncertainty, our study presents a thorough reexamination of the relationship between mass democratic support and democracy survival across counties and over time.
-We use a superior measure, Dynamic Comparative Public Opinion (DCPO) model developed by@Solt2020a, to estimate democratic support for a larger dataset with 144 countries for up to 33 years between 1988 and 2020.
-In addition to account for item response bias across countries and the extent of polarization by generating estimates on bounded scales, the DCPO model has superiority in dealing with both binominal and ordinal survey data cross countries over time.
+We use a superior measure, the Dynamic Comparative Public Opinion (DCPO) model developed by@Solt2020a, to estimate democratic support for a larger dataset with 144 countries for up to 33 years between 1988 and 2020.
+In addition to accounting for item response bias across countries and the extent of polarization by generating estimates on bounded scales, the DCPO model has superiority in dealing with both binominal and ordinal survey data across countries over time.
 Both internal and external k-fold validation tests corroborate that the DCPO model yields more accurate results than other latent variable measurements, either of @Claassen2019 Model 5 and @Caughey2019 model.
 The nature of latent variables' unobservability decides that the estimates of latent variables are inherently accompanied with measurement uncertainty. 
-Omitting to account for measurement error distorts both statistical and substantive inference (See Juhl 2019for review in this literature). 
+Omitting measurement error distorts both statistical and substantive inference (See Juhl 2019for review in this literature). 
 Since the measurement uncertainty could have consequential (propagated) effects on inferences about the relationship of substantive interests, it is strongly recommended to incorporate the measurement uncertainty in analysis models (Treier and Jackman 2008, Crabtree and Fariss 2015).
 Many scholars have taken the account for measurement error in analyses as a final crucial part in their empirical studies (Schnakenberg and Fariss 2014, Caughey and Warshaw 2018), and recent studies on latent variable measurement emphasized the incorporation of measurement uncertainty when using their measures ( Solis and Waggoner 2020, Gandhi and Sumner 2020).
-However, in comparative public opinion field, previous efforts on measuring comparative public opinion didn’t account for measurement uncertainty in their analysis.  
-To address the uncertainty, the inherent trail of latent constructs, in addition to employ the DCPO which reduces uncertainty in measurement, we also incorporated uncertainty in our analysis by using random draws from the posterior distributions and following @Rubin1987's rules.
-Surprisingly, our study reveals that there is no significant relationship between public support and democratic change in both the replication analysis of @Claassen2020a model and DCPO analysis when uncertainty is included.
+However, in the comparative public opinion field, previous efforts on measuring comparative public opinion didn’t account for measurement uncertainty in their analyses.  
+To address the uncertainty (caused by the inherent trail of latent constructs), in addition to employing the DCPO which reduces uncertainty in measurement, we also incorporated uncertainty in our analysis by using random draws from the posterior distributions and following @Rubin1987's rules.
+Surprisingly, our study reveals that there is no significant relationship between public support and democratic change in both the replication analysis of @Claassen2020a model and the DCPO analysis when uncertainty is included.
 Our study reaffirms Fariss 2014, Juhl (2019) and Solt (2020)'s suggestion that given the latent character of variables in political science, scholars should be vigilant in measurement uncertainty. 
-In addition to methodological concerns, our reanalysis echoes recent studies about public’s behavioral commitment to democracy.  
-It is questionable that whether self-report based conventional measures of support for democracy could transfer to behaviorally democratic commitments when the democratic system is in economic or societal crisis.
+In addition to methodological concerns, our reanalysis echoes recent studies about the public’s behavioral commitment to democracy.  
+It is questionable whether self-report based conventional measures of support for democracy could transfer to behaviorally democratic commitments when the democratic system is in economic or societal crisis.
 Recent studies show that although the public understands and supports democratic principles, their support is elastic, especially in the context of polarization [@graham_democracy_2020].
@@
 First, the DCPO model allows us to treat the data as their original scales, either dichotomous or ordinal, to avoid information missing due to the potential scale change.
-For example, our data consists of 20885 national responses as the result of measuring public attitude at ordinal scales, which has potential to give us more nuances about public demcratic support. 
+For example, our data consists of 20,885 national responses as the result of measuring public attitude at ordinal scales, which has the potential to give us more nuances about public democratic support.
 Second, to reduce the uncertainty in estimating countries which lie at the extreme ends of the public opinion spectrum[@Linzer2015], the estimates of mean public opinion are bounded and the extent of polarization is included in the DCPO model.
@@
 Third, to address the differences in item response across countries, caused by factors other than public attitude or preference, a country-specific item bias is modelled as "a country-specific bias in the difficulty of each question" [@Solt2020a, 6].
-This approach allows us to keep information embeded in questions rather than discarding them directly. 
-In sum, the DCPO model has methodological advantages in keeping as much as available information, reducing uncertainty by bounding scales and capturing the extent of polarization. 
-The validation tests in @Solt2020a's paper corroborate that DCPO not only features the smallest mean absolute error(MAE) and largest improvement over the country-means MAE but also provides a more stable and efficient prediction on out-of-sample data than either of @Claassen2019 Model 5 and @Caughey2019 model.
-Following @Solt2020a's apporoach, our validation test employ k-fold validation with 10 folds, which reduces the misrepresentation of the model due to the chosen data from single cross-validation (See details of the validation test in Appendix).
+This approach allows us to keep information embedded in questions rather than discarding them directly. 
+In sum, the DCPO model has methodological advantages in keeping as much available information as possible, reducing uncertainty by bounding scales and capturing the extent of polarization. 
+The validation tests in @Solt2020a's paper corroborate that DCPO not only features the smallest mean absolute error (MAE) and largest improvement over the country-means MAE but also provides a more stable and efficient prediction on out-of-sample data than either the @Claassen2019's Model 5 or the @Caughey2019's model.
+Following @Solt2020a's approach, our validation test employs k-fold validation with 10 folds, which reduces the misrepresentation of the model due to the chosen data from single cross-validation (See details of the validation test in Appendix).
 
@@
 # Incorporating Uncertainty
-The latent constructs are inherently accompanied with amount of measurement uncertainty due to the unobservability of variables.
-The measurement is more far away from prefection when concepts are complex. 
-With a strong assumption that latent variables are measured perfectly, the omittance to incorporate measurement error might obscure the true relationship between theoretical concepts and invalidates findings.
+The latent constructs are inherently accompanied by amount of measurement uncertainty due to the unobservability of variables.
+The measurement is more far away from perfection when concepts are complex. 
+With a strong assumption that latent variables are measured perfectly, the omittance of measurement error might obscure the true relationship between theoretical concepts and invalidates findings.
 Therefore, incorporating uncertainty is substantively necessary for “comparing relationship between complex theoretical concepts across political contexts and over time"[@Crabtree2015,p2]. 
-In our reexamination, instead of employing the point estimates, we relax the implausible assumption of perfect measurment of latent variables, we followed the recommendation and the approach of incorporating uncertainty in using latent variables [e.g., @Schnakenberg2014; @Crabtree2015] and other measures, such as the Standardized World Income Inequality Database [@Solt2020].
+In our reexamination, instead of employing the point estimates, we relax the implausible assumption of perfect measurement of latent variables.
+We followed the recommendation and the approach of incorporating uncertainty in using latent variables [e.g., @Schnakenberg2014; @Crabtree2015] and other measures, such as the Standardized World Income Inequality Database [@Solt2020].
 Specifically, we generated 1,000 duplicate versions of the analysis dataset, assigned to each a different random draw from the posterior distributions of public democratic support, performed the analyses repeatedly on each of these 1,000 versions of the dataset, and then combined the results following the rules set out in @Rubin1987.
@@
 First, the survey items we used might not capture real public democratic support, given the complexity of this concept and limited indicators compared to other concepts like gender egalitarian (Solt, 2021??).
-Second, these survey items do capture public democratic support, but we still don’t have enough data to compensate the fragmentation and incomparability of the available comparative public opinion data, which is doomed to accompany with high uncertainty.
+Second, these survey items do capture public democratic support, but we still don’t have enough data to compensate the fragmentation and incomparability of the available comparative public opinion data, which is doomed to high uncertainty.
 Methodologically, given the nature trail of latent variables and specific characters of comparative public opinion, performing analyses based on the strong assumption that comparative public attitudes are perfectly measured might exaggerate scholars' certainty methodologically and obscure a proper substantive evaluation of theoretical claims.
-In addition to the potentially methodological cause, the measurement errors, there are some potentially substantive causes for the disappearing relationship.
+In addition to the potentially methodological cause (the measurement errors), the measurement errors, there are some potentially substantive causes for the disappearing relationship.
 First, democratic backsliding might be mainly caused by elites.
 Elites are thought to play a critical role in preserving democratic stability by respecting the limits on their behaviors (Weingast 1997).
-After the Cold War, many democracies backslided and imperiled in the worldwide because elected leaders lack of commitment to democratic norms when the public even did not notice that (Bermeo 2016; Levtsky and Ziblatt 2018, Waldner and Lust 2018).
+After the Cold War, many democracies backslid and were imperiled worldwide because elected leaders lack commitment to democratic norms when the public even did not notice that (Bermeo 2016; Levtsky and Ziblatt 2018, Waldner and Lust 2018).
 Second, there has been a gulf between public perception and elites’ perception on important democratic principles (McClosky, 1959).
-A recent study shown that polarized public cannot get a consensus on democratic erosion which experts preserved (Carey et al 2018).
-Given the measures for democratic development are from experts, there could be a gap between public perception on democracy and the measures of the levels of democracy.
+A recent study showed that polarized public cannot get a consensus on democratic erosion which experts preserved (Carey et al 2018).
+Given that the measures for democratic development are from experts, there could be a gap between public perception on democracy and the measures of the levels of democracy.
 Third, since there is a difference between the public support for democracy in the abstract and under specific propositions (Bartels 2020), recent studies questioned whether conventional measures of public support for democracy could capture public realistic commitment to democracy.
-By using survey experiments, Graham an Svolik (2020) pointed out a " fundamental blind spot" in traditional measures of public democratic support: the questions regarding the support for an abstract democracy cannot capture public willingness and behavioral commitment to democratic principles when voters have to choose between democratic norms and their partisan identification or policy preference.
+By using survey experiments, Graham and Svolik (2020) pointed out a " fundamental blind spot" in traditional measures of public democratic support: the questions regarding the support for an abstract democracy cannot capture public willingness and behavioral commitment to democratic principles when voters have to choose between democratic norms and their partisan identification or policy preference.
 It turned out that voters subordinated democratic norms to their partisan preference by not electorally penalizing their candidates who endorse measures that violate norms.

### 2020-09-27 paper/dcpo_demsupport.Rmd
plot updated: adding cls uncertainty

--- 2020-09-08 paper/dcpo_demsupport.Rmd
@@
   huxtable, kableExtra, modelsummary, # tabulation
+  gridExtra,
   latex2exp, # visualization
@@
 set.seed(313)
+
+get_legend<-function(myggplot){
+  tmp <- ggplot_gtable(ggplot_build(myggplot))
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
+  legend <- tmp$grobs[[leg]]
+  return(legend)
+}
+
+# Theme setup
+theme_set(theme_minimal())
+source("../R/uiowa_palette.R")
 ```
@@
 
+load(here::here("data", "claassen_replication_input.rda"))
 load(here::here("data", "claassen_m5_theta.rda"))
@@
 
-```
-
-```{r claassenAJPS}
-# Pooled model -----
-
 ## Beck-Katz panel-corrected standard errors
@@
 
+vcovHC_se <-  function(x) {
+  plm::vcovHC(x, method="arellano", cluster="group") %>% 
+    diag() %>% 
+    sqrt()
+}
+
+reformat_dcpo_output <- function(x, parameter_name) {
+  df_temp <- x %>% 
+    as_tibble(.name_repair = ~ls_country) %>% 
+    mutate(year = first_year + row_number() - 1) %>% 
+    pivot_longer(cols = all_of(ls_country),
+                 names_to = "country",
+                 values_to = parameter_name) %>%
+    arrange(country, year)
+  return(df_temp)
+}
+```
+
+```{r claassenAJPS}
+# Pooled model -----
 # regime = ifelse(sd2$Regime_VD > 1, 1, 0)
@@
 
-save(df_result_cls, file = here::here("output", "estimates_clsAJPS.RDS"))
-```
-
-```{r claassenUncertainty}
-
+save(df_result_cls, file = here::here("output", "estimates_clsMeanAJPS.RDS"))
+```
+
+```{r claassenUncertaintyAJPS,eval=FALSE}
+
+ls_country <- unique(claassen_replication_input$data$country)
+first_year <- min(claassen_replication_input$data$year)
+
+sd_control <- sd.plm %>%
+  mutate(
+    country = as.character(Country),
+    year = as.numeric(as.character(Year)),
+    regime = ifelse(Regime_VD > 1, 1, 0)
+  )
+
+df_cls <- purrr::map(1:1000, function(anEntry) {
+  claassen_m5_theta$theta[anEntry,,] %>% 
+    reformat_dcpo_output("theta") %>% 
+    # left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
+    #           by = c("year", "country")) %>%
+    left_join(sd_control, by = c("country", "year")) %>% 
+    mutate(theta_dem = theta * regime,
+           theta_aut = theta * (1 - regime)) %>% 
+    plm::pdata.frame(index = c("country", "year"))
+})
+
+estimate_cls <- function(aModel, aType = "pooling") {
+  if (aType == "gmm") {
+    result_cls_1k <- map(df_cls, function(aDataset) {
+      pgmm(
+        as.formula(aModel),
+        effect = "individual",
+        model = "onestep",
+        transformation = "ld",
+        indexes = c("Country", "Year"),
+        data = aDataset
+      )
+    })
+
+    result_vars_cls_1k <-
+      mitools::MIextract(result_cls_1k, fun = vcovHC_se)
+
+  } else {
+    result_cls_1k <- map(df_cls, function(aDataset) {
+      plm::plm(aModel,
+               model = "pooling",
+               data = aDataset)
+    })
+
+    result_vars_cls_1k <-
+      mitools::MIextract(result_cls_1k, fun = vcovBK_se)
+  }
+
+  result_betas_cls_1k <-
+    mitools::MIextract(result_cls_1k, fun = coef)
+
+  df_result_cls <-
+    summary(
+      mitools::MIcombine(results = result_betas_cls_1k, variance = result_vars_cls_1k)
+    ) %>% rownames_to_column(var = "term") %>%
+    rename(conf.low = `(lower`,
+           conf.high = `upper)`,
+           estimate = results) %>%
+    filter(!str_detect(term, "(Intercept)"))
+}
+
+mod_ls <- paste0(
+  "Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + ",
+  c("plm::lag(theta, 1)", 
+    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
+  " + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)"
+)
+
+df_result_clsUncertain <- map(mod_ls, estimate_cls)
+
+save(df_result_clsUncertain, file = here::here("output", "estimates_clsAJPS.RDS"))
+```
+
+```{r dcpoPointAJPS, eval=FALSE}
 ls_country <- levels(dcpo_input$data$kk)
@@
 
-df_claassen <- purrr::map(1:1000, function(anEntry) {
-  claassen_m5_theta$theta[anEntry,,] %>% 
+df_dcpoMean <- purrr::map_df(1:1000, function(anEntry) {
+  dcpo_theta$theta[anEntry,,] %>% 
+    reformat_dcpo_output("theta") %>% 
+    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
+              by = c("year", "country"))
+}) %>% 
+  group_by(country, year) %>% 
+  summarise(theta = mean(theta), 
+            sigma = mean(sigma))
+
+save(df_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))
+
+df_controls <- read_csv(here::here("data", "control_variables_ajps.csv"),
+                        col_types = cols(.default = col_double(),
+                                         country = col_character(),
+                                         country_name = col_character(),
+                                         ISO = col_character(),
+                                         Region_UN = col_character())) %>% 
+  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
+         country = countrycode::countrycode(country0, "country.name", "country.name"),
+         regime = Vdem_regime > 1) %>% 
+  filter(year >= firstyear) # using trimmed data as Claassen
+
+df_dcpoMeanAJPS <- df_dcpoMean %>% 
+  right_join(df_controls, by = c("country", "year")) %>% 
+  mutate(theta_dem = theta * regime,
+         theta_aut = theta * (1 - regime)) %>% 
+    plm::pdata.frame(index = c("country", "year"))
+
+ls_mod <- paste0(
+  "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
+  c("plm::lag(theta, 1)", 
+    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
+  " + plm::lag(lg_imp_mdpgdp, 1) +
+             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
+             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)"
+)
+
+df_result_dcpoMeanAJPS <- map(ls_mod, function(mod){
+  result <- plm(mod, model = "pooling", data = df_dcpoMeanAJPS)
+  df_result <- tidy(result) %>%
+    mutate(std.error = vcovBK_se(result))
+})
+
+save(df_result_dcpoMeanAJPS, file = here::here("output", "estimates_dcpoMeanAJPS.RDS"))
+```
+
+```{r dcpoUncertaintyAJPS, eval = FALSE}
+df_dcpo <- purrr::map(1:1000, function(anEntry) {
+  dcpo_theta$theta[anEntry,,] %>% 
     reformat_dcpo_output("theta") %>% 
@@
 
-df_result_dcpo <- map(mod_ls, estimate_dcpo)
-
-save(df_result_dcpo, file = here::here("output", "estimates_dcpo.RDS"))
-```
-
-```{r dcpoPointAJPS}
-ls_country <- levels(dcpo_input$data$kk)
-first_year <- min(dcpo_input$data$year)
-
-reformat_dcpo_output <- function(x, parameter_name) {
-  df_temp <- x %>% 
-    as_tibble(.name_repair = ~ls_country) %>% 
-    mutate(year = first_year + row_number() - 1) %>% 
-    pivot_longer(cols = all_of(ls_country),
-                 names_to = "country",
-                 values_to = parameter_name) %>%
-    arrange(country, year)
-  return(df_temp)
-}
-
-df_dcpoMean <- purrr::map_df(1:1000, function(anEntry) {
-  dcpo_theta$theta[anEntry,,] %>% 
-    reformat_dcpo_output("theta") %>% 
-    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
-              by = c("year", "country"))
-}) %>% 
-  group_by(country, year) %>% 
-  summarise(theta = mean(theta), 
-            sigma = mean(sigma))
-
-save(df_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))
-
-df_controls <- read_csv(here::here("data", "control_variables_ajps.csv"),
-                        col_types = cols(.default = col_double(),
-                                         country = col_character(),
-                                         country_name = col_character(),
-                                         ISO = col_character(),
-                                         Region_UN = col_character())) %>% 
-  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
-         country = countrycode::countrycode(country0, "country.name", "country.name"),
-         regime = Vdem_regime > 1) %>% 
-  filter(year >= firstyear) # using trimmed data as Claassen
-
-df_dcpoMeanAJPS <- df_dcpoMean %>% 
-  right_join(df_controls, by = c("country", "year")) %>% 
-  mutate(theta_dem = theta * regime,
-         theta_aut = theta * (1 - regime)) %>% 
-    plm::pdata.frame(index = c("country", "year"))
-
-ls_mod <- paste0(
-  "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
-  c("plm::lag(theta, 1)", 
-    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
-  " + plm::lag(lg_imp_mdpgdp, 1) +
-             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
-             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)"
-)
-
-df_result_dcpoMeanAJPS <- map(ls_mod, function(mod){
-  result <- plm(mod, model = "pooling", data = df_dcpoMeanAJPS)
-  df_result <- tidy(result) %>%
-    mutate(std.error = vcovBK_se(result))
-})
-
-save(df_result_dcpoMeanAJPS, file = here::here("output", "estimates_dcpoMeanAJPS.RDS"))
-```
-
-```{r dcpoUncertaintyAJPS, eval = FALSE}
-df_dcpo <- purrr::map(1:1000, function(anEntry) {
-  dcpo_theta$theta[anEntry,,] %>% 
-    reformat_dcpo_output("theta") %>% 
-    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
-              by = c("year", "country")) %>%
-    left_join(df_controls, by = c("country", "year")) %>% 
-    mutate(theta_dem = theta * regime,
-           theta_aut = theta * (1 - regime)) %>% 
-    plm::pdata.frame(index = c("country", "year"))
-})
-
-estimate_dcpo <- function(aModel, aType = "pooling") {
-  if (aType == "gmm") {
-    result_dcpo_1k <- map(df_dcpo, function(aDataset) {
-      pgmm(
-        as.formula(aModel),
-        effect = "individual",
-        model = "onestep",
-        transformation = "ld",
-        indexes = c("Country", "Year"),
-        data = aDataset
-      )
-    })
-
-    result_vars_dcpo_1k <-
-      mitools::MIextract(result_dcpo_1k, fun = vcovHC_se)
-
-  } else {
-    result_dcpo_1k <- map(df_dcpo, function(aDataset) {
-      plm::plm(aModel,
-               model = "pooling",
-               data = aDataset)
-    })
-
-    result_vars_dcpo_1k <-
-      mitools::MIextract(result_dcpo_1k, fun = vcovBK_se)
-  }
-
-  result_betas_dcpo_1k <-
-    mitools::MIextract(result_dcpo_1k, fun = coef)
-
-  df_result_dcpo <-
-    summary(
-      mitools::MIcombine(results = result_betas_dcpo_1k, variance = result_vars_dcpo_1k)
-    ) %>% rownames_to_column(var = "term") %>%
-    rename(conf.low = `(lower`,
-           conf.high = `upper)`,
-           estimate = results) %>%
-    filter(!str_detect(term, "(Intercept)"))
-}
-
-mod_ls <- paste0(
-  "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
-  c("plm::lag(theta, 1)", 
-    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
-  " + plm::lag(lg_imp_mdpgdp, 1) +
-             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
-             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)"
-)
-
 df_result_dcpoAJPS <- map(mod_ls, estimate_dcpo)
@@
 
+load(here::here("output", "estimates_clsMeanAJPS.RDS"))
 load(here::here("output", "estimates_clsAJPS.RDS"))
-load(here::here("output", "estimates_dcpoMeanAJPS.RDS"))
 load(here::here("output", "estimates_dcpoAJPS.RDS"))
@@
 
-df_plot <- df_result_dcpoMeanAJPS[[1]] %>% 
-  mutate(model = "DCPO\n (Point Estimates)") %>%  
+df_plot <- df_result_clsUncertain[[1]] %>% 
+  mutate(model = "Claassen w. Uncertainty") %>%  
+  bind_rows(df_plot)
+
+df_plot <- df_result_dcpoAJPS[[1]] %>% 
+  mutate(model = "DCPO") %>%  
   bind_rows(df_plot)
@@
       "Resource\n Dependence\n (t−1)"),
-    time = 2)
-  )
+    time = 3)
+  )
+
+plot_AJPS1 <- dwplot(df_plotS, dodge_size = 0.8) +
+  scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "DV: Institutional Democracy (Vdem)",
+    subtitle = "Pooled"
+  ) +
+  theme(legend.position = "none")
 
 # the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
-
-plot_clsVsDCPO <- small_multiple(df_plotS) +
-  theme_minimal() +
-  ggtitle("DV: Liberal Democracy (Vdem)")+
-  theme(legend.position = "none")
 
@@
 
-df_plot <- df_result_dcpoMeanAJPS[[2]] %>% 
-  mutate(model = "DCPO\n (Point Estimates)") %>%  
+df_plot <- df_result_clsUncertain[[2]] %>% 
+  mutate(model = "Claassen w. Uncertainty") %>%  
+  bind_rows(df_plot)
+
+df_plot <- df_result_dcpoAJPS[[2]] %>% 
+  mutate(model = "DCPO") %>%  
   bind_rows(df_plot)
@@
       "Resource\n Dependence\n (t−1)"),
-    time = 2)
-  )
-
-plot_clsVsDCPO2 <- small_multiple(df_plotS) +
-  theme_minimal() +
-  ggtitle("DV: Liberal Democracy (Vdem)")+
-  theme(legend.position = "none")
-
-gridExtra::grid.arrange(plot_clsVsDCPO, plot_clsVsDCPO2, ncol = 2)
-```
-
-```{r visualizedUncertainAJPS, fig.cap= "The Effect of Democratic Mood on Institutional Democratization Accounting for Uncertainty"}
+    time = 3)
+  )
+
+plot_AJPS2 <- dwplot(df_plotS, dodge_size = 0.8) +
+  scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "",
+    subtitle = "Regime Specific"
+  ) +
+  theme(legend.position = "bottom")
+
+legend <- get_legend(plot_AJPS2)
+
+plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
+
+grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol=2, nrow = 2, 
+             layout_matrix = rbind(c(1,2), c(3,3)),
+             widths = c(2.7, 2.7), heights = c(2.5, 0.2))
+
+```
+
+```{r visualizedUncertainAJPS, fig.cap= "The Effect of Democratic Mood on Institutional Democratization Accounting for Uncertainty", eval=FALSE}
 
@@
 
-vcovHC_se <-  function(x) {
-  plm::vcovHC(x, method="arellano", cluster="group") %>% 
-    diag() %>% 
-    sqrt()
-}
-
 df_result_clsAPSR <- map(mods, function(aMod){
@@
 
-save(df_result_clsAPSR, file = here::here("output", "estimates_clsAPSR.RDS"))
-```
-
-```{r dcpoPointAPSR}
+save(df_result_clsAPSR, file = here::here("output", "estimates_clsMeanAPSR.RDS"))
+```
+
+```{r claassenAPSRUncertainty}
+ls_country <- unique(claassen_replication_input$data$country)
+first_year <- min(claassen_replication_input$data$year)
+
+sd_control <- sd.plm %>%
+  mutate(
+    country = as.character(Country),
+    year = as.numeric(as.character(Year))
+  )
+
+df_clsAPSR <- purrr::map(1:1000, function(anEntry) {
+  claassen_m5_theta$theta[anEntry,,] %>% 
+    reformat_dcpo_output("theta") %>% 
+    # left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
+    #           by = c("year", "country")) %>%
+    left_join(sd_control, by = c("country", "year")) %>% 
+    plm::pdata.frame(index = c("country", "year"))
+})
+
+estimate_cls <- vector(mode = "list")
+
+estimate_cls[[1]] <- function(aDataset) {
+  plm(
+      diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Libdem_z, lag = 1)
+  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1),
+      model = "pooling",
+      data = aDataset
+    )
+}
+
+estimate_cls[[2]] <- function(aDataset) {
+  plm(
+      diff(theta, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Libdem_z, lag = 1)
+  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)
+  + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1),
+      model = "pooling",
+      data = aDataset
+    )
+}
+
+df_result_clsUncertainAPSR <- map(estimate_cls, function(aModel){
+  aFit <- map(df_clsAPSR, aModel)
+
+  result_vars_cls_1k <- mitools::MIextract(aFit, fun = vcovHC_se)
+  result_betas_cls_1k <- mitools::MIextract(aFit, fun = coef)
+
+  summary(
+      mitools::MIcombine(results = result_betas_cls_1k, 
+                         variance = result_vars_cls_1k)
+    ) %>% rownames_to_column(var = "term") %>%
+    rename(conf.low = `(lower`,
+           conf.high = `upper)`,
+           estimate = results) %>%
+    filter(!str_detect(term, "(Intercept)"))
+
+})
+
+save(df_result_clsUncertainAPSR, file = here::here("output", "estimates_clsAPSR.RDS"))
+```
+
+```{r dcpoPointAPSR, eval = FALSE}
 df_controls <- read_csv(here::here("data", "control_variables_apsr.csv"),
@@
 
+load(here::here("output", "estimates_clsMeanAPSR.RDS"))
 load(here::here("output", "estimates_clsAPSR.RDS"))
-load(here::here("output", "estimates_dcpoMeanAPSR.RDS"))
+load(here::here("output", "estimates_dcpoAPSR.RDS"))
 
@@
 
-df_plot <- df_result_dcpoMeanAPSR[[1]] %>% 
-  mutate(model = "DCPO\n (Point Estimates)") %>%  
+df_plot <- df_result_clsUncertainAPSR[[1]] %>% 
+  mutate(model = "Claassen w. Uncertainty") %>%  
+  bind_rows(df_plot)
+
+df_plot <- df_result_dcpoAPSR[[1]] %>% 
+  mutate(model = "DCPO") %>%  
   bind_rows(df_plot)
@@
       "Log GDP\n (t−1)"),
-    time = 2)
-  )
-
-# the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
-
-plot_clsVsDCPO <- small_multiple(df_plotS) +
-  theme_minimal() +
-  ggtitle("DV: Democracy Mood")+
+    time = 3)
+  )
+
+plot_APSR1 <- dwplot(df_plotS, dodge_size = 0.8) +
+  scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "DV: Democratic Mood",
+    subtitle = "Basic"
+  ) +
   theme(legend.position = "none")
@@
 
-df_plot <- df_result_dcpoMeanAPSR[[2]] %>% 
-  mutate(model = "DCPO\n (Point Estimates)") %>%  
+df_plot <- df_result_clsUncertainAPSR[[2]] %>% 
+  mutate(model = "Claassen w. Uncertainty") %>%  
+  bind_rows(df_plot)
+
+df_plot <- df_result_dcpoAPSR[[2]] %>% 
+  mutate(model = "DCPO") %>%  
   bind_rows(df_plot)
@@
       "Corruption\n (t−1)"
-      ),time = 2)
-  )
-
-plot_clsVsDCPO2 <- small_multiple(df_plotS) +
-  theme_minimal() +
-  ggtitle("DV: Democracy Mood")+
+      ),time = 3)
+  )
+
+plot_APSR2 <- dwplot(df_plotS, dodge_size = 0.8) +
+  scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "",
+    subtitle = "w. Corruption"
+  )
+
+legend <- get_legend(plot_AJPS2)
+
+plot_APSR2 <- plot_APSR2 +
   theme(legend.position = "none")
 
-gridExtra::grid.arrange(plot_clsVsDCPO, plot_clsVsDCPO2, ncol = 2)
-```
-
-```{r visualizedUncertaintyAPSR, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO"}
+gridExtra::grid.arrange(plot_APSR1, plot_APSR2, legend, ncol=2, nrow = 2, 
+             layout_matrix = rbind(c(1,2), c(3,3)),
+             widths = c(2.7, 2.7), heights = c(2.5, 0.2))
+```
+
+```{r visualizedUncertaintyAPSR, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO", eval = FALSE}
 

### 2020-09-29 paper/dcpo_demsupport.Rmd
starting the result

@@
 
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, dpi = 300)
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, eval = FALSE, dpi = 300)
 
@@
   boot, plm, # analysis
-  huxtable, kableExtra, modelsummary, # tabulation
+  flextable, kableExtra, modelsummary, # tabulation
   gridExtra,
@@
   tidyverse, # data wrangling
-  dotwhisker # visualization
+  dotwhisker, # visualization
 )
@@
 
-```{r country-years, eval=FALSE}
+```{r country-years}
 path_df <-
@@
 # Results
-Our reanalysis follows the following steps. Frist, we replicated Claassen's  (2019,2020)  studies by using his measurement and analysis models.
-Results here.
-Next, adding measurement uncertainty into Claassen's analysis models, we found xxxx.
-Tables and results here.
-We then reanalyzed the relationship between public democratic attitude and democracy institution in both directions, using more data, the DCPO measurement model and measurement uncertainty incorporated.
-Results here. indistinguishable from zero.
+
+<!-- I may suggest to move this paragraph to the beginning of the previous section or a separate section of research design -->
+
+**To examine the influence of empirical uncertainty, we conducted a three-step test. 
+We first reproduced @Claassen2019.
+Then applying the method he described in the article, we replicated his IRT-based measurement of democratic mood and maintain the entire distribution of the predicted outcome, instead of aggregating to a single point estimate.
+Utilizing the estimated distribution, we involved uncertainty to the analysis of the influence of democratic mood on institutional democracy cross-nationally.
+In the third step, we applied an advanced method and added one-third more data to the analysis to reduce potential effects of measurement biases and data spareness.
+We compared the outcomes of the three steps and showed as below that uncertainty is an critical factor in the studies of mass democratic attitude, which may alter the analytic conclusions. 
+We further show that accounting for uncertainty is at least equivalently important when the latent-variable estimates plays as the dependent variable in a study by replicating Claassen2020b. **
+
+```{r dataInput}
+
+supdem <- read.csv("../data/Support_democracy_ajps.csv")
+v_dem <- read.csv("../data/vdem15.csv")
+sd.plm <- pdata.frame(supdem, index = c("Country", "Year"))
+
+load(here::here("data", "claassen_replication_input.rda"))
+load(here::here("data", "claassen_m5_theta.rda"))
+load(here::here("data", "dcpo_input.rda"))
+load(here::here("data", "dcpo_theta.rda"))
+load(here::here("data", "dcpo_sigma.rda"))
+load(here::here("data", "dem_mood_apsr.RData"))
+
+## Beck-Katz panel-corrected standard errors
+vcovBK_se <- function(x) {
+  plm::vcovBK(x, cluster = "time") %>% 
+    diag() %>% 
+    sqrt()
+}
+
+vcovHC_se <-  function(x) {
+  plm::vcovHC(x, method="arellano", cluster="group") %>% 
+    diag() %>% 
+    sqrt()
+}
+
+reformat_dcpo_output <- function(x, parameter_name) {
+  df_temp <- x %>% 
+    as_tibble(.name_repair = ~ls_country) %>% 
+    mutate(year = first_year + row_number() - 1) %>% 
+    pivot_longer(cols = all_of(ls_country),
+                 names_to = "country",
+                 values_to = parameter_name) %>%
+    arrange(country, year)
+  return(df_temp)
+}
+```
+
+```{r claassenAJPS}
+# Pooled model -----
+# regime = ifelse(sd2$Regime_VD > 1, 1, 0)
+
+ls_mod <-
+  paste0(
+    "Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + ",
+    c(
+      "plm::lag(SupDem_trim, 1)",
+      "plm::lag(SupDem_Democ, 1) + plm::lag(SupDem_Autoc, 1)"
+    ),
+    "+ plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)"
+  )
+
+df_result_cls <- map(ls_mod, function(mod){
+  result <- plm(mod, model = "pooling", data = sd.plm)
+  df_result <- tidy(result) %>%
+    mutate(std.error = vcovBK_se(result))
+})
+
+save(df_result_cls, file = here::here("output", "estimates_clsMeanAJPS.RDS"))
+```
+
+```{r claassenUncertaintyAJPS}
+
+ls_country <- unique(claassen_replication_input$data$country)
+first_year <- min(claassen_replication_input$data$year)
+
+sd_control <- sd.plm %>%
+  mutate(
+    country = as.character(Country),
+    year = as.numeric(as.character(Year)),
+    regime = ifelse(Regime_VD > 1, 1, 0)
+  )
+
+df_cls <- purrr::map(1:1000, function(anEntry) {
+  claassen_m5_theta$theta[anEntry,,] %>% 
+    reformat_dcpo_output("theta") %>% 
+    # left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
+    #           by = c("year", "country")) %>%
+    left_join(sd_control, by = c("country", "year")) %>% 
+    mutate(theta_dem = theta * regime,
+           theta_aut = theta * (1 - regime)) %>% 
+    plm::pdata.frame(index = c("country", "year"))
+})
+
+estimate_cls <- function(aModel, aType = "pooling") {
+  if (aType == "gmm") {
+    result_cls_1k <- map(df_cls, function(aDataset) {
+      pgmm(
+        as.formula(aModel),
+        effect = "individual",
+        model = "onestep",
+        transformation = "ld",
+        indexes = c("Country", "Year"),
+        data = aDataset
+      )
+    })
+
+    result_vars_cls_1k <-
+      mitools::MIextract(result_cls_1k, fun = vcovHC_se)
+
+  } else {
+    result_cls_1k <- map(df_cls, function(aDataset) {
+      plm::plm(aModel,
+               model = "pooling",
+               data = aDataset)
+    })
+
+    result_vars_cls_1k <-
+      mitools::MIextract(result_cls_1k, fun = vcovBK_se)
+  }
+
+  result_betas_cls_1k <-
+    mitools::MIextract(result_cls_1k, fun = coef)
+
+  df_result_cls <-
+    summary(
+      mitools::MIcombine(results = result_betas_cls_1k, variance = result_vars_cls_1k)
+    ) %>% rownames_to_column(var = "term") %>%
+    rename(conf.low = `(lower`,
+           conf.high = `upper)`,
+           estimate = results) %>%
+    filter(!str_detect(term, "(Intercept)"))
+}
+
+mod_ls <- paste0(
+  "Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + ",
+  c("plm::lag(theta, 1)", 
+    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
+  " + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)"
+)
+
+df_result_clsUncertain <- map(mod_ls, estimate_cls)
+
+save(df_result_clsUncertain, file = here::here("output", "estimates_clsAJPS.RDS"))
+```
+
+```{r dcpoPointAJPS}
+ls_country <- levels(dcpo_input$data$kk)
+first_year <- min(dcpo_input$data$year)
+
+df_dcpoMean <- purrr::map_df(1:1000, function(anEntry) {
+  dcpo_theta$theta[anEntry,,] %>% 
+    reformat_dcpo_output("theta") %>% 
+    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
+              by = c("year", "country"))
+}) %>% 
+  group_by(country, year) %>% 
+  summarise(theta = mean(theta), 
+            sigma = mean(sigma))
+
+save(df_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))
+
+df_controls <- read_csv(here::here("data", "control_variables_ajps.csv"),
+                        col_types = cols(.default = col_double(),
+                                         country = col_character(),
+                                         country_name = col_character(),
+                                         ISO = col_character(),
+                                         Region_UN = col_character())) %>% 
+  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
+         country = countrycode::countrycode(country0, "country.name", "country.name"),
+         regime = Vdem_regime > 1) %>% 
+  filter(year >= firstyear) # using trimmed data as Claassen
+
+df_dcpoMeanAJPS <- df_dcpoMean %>% 
+  right_join(df_controls, by = c("country", "year")) %>% 
+  mutate(theta_dem = theta * regime,
+         theta_aut = theta * (1 - regime)) %>% 
+    plm::pdata.frame(index = c("country", "year"))
+
+ls_mod <- paste0(
+  "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
+  c("plm::lag(theta, 1)", 
+    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
+  " + plm::lag(lg_imp_mdpgdp, 1) +
+             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
+             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)"
+)
+
+df_result_dcpoMeanAJPS <- map(ls_mod, function(mod){
+  result <- plm(mod, model = "pooling", data = df_dcpoMeanAJPS)
+  df_result <- tidy(result) %>%
+    mutate(std.error = vcovBK_se(result))
+})
+
+save(df_result_dcpoMeanAJPS, file = here::here("output", "estimates_dcpoMeanAJPS.RDS"))
+```
+
+```{r dcpoUncertaintyAJPS}
+df_dcpo <- purrr::map(1:1000, function(anEntry) {
+  dcpo_theta$theta[anEntry,,] %>% 
+    reformat_dcpo_output("theta") %>% 
+    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
+              by = c("year", "country")) %>%
+    left_join(df_controls, by = c("country", "year")) %>% 
+    mutate(theta_dem = theta * regime,
+           theta_aut = theta * (1 - regime)) %>% 
+    plm::pdata.frame(index = c("country", "year"))
+})
+
+estimate_dcpo <- function(aModel, aType = "pooling") {
+  if (aType == "gmm") {
+    result_dcpo_1k <- map(df_dcpo, function(aDataset) {
+      pgmm(
+        as.formula(aModel),
+        effect = "individual",
+        model = "onestep",
+        transformation = "ld",
+        indexes = c("Country", "Year"),
+        data = aDataset
+      )
+    })
+
+    result_vars_dcpo_1k <-
+      mitools::MIextract(result_dcpo_1k, fun = vcovHC_se)
+
+  } else {
+    result_dcpo_1k <- map(df_dcpo, function(aDataset) {
+      plm::plm(aModel,
+               model = "pooling",
+               data = aDataset)
+    })
+
+    result_vars_dcpo_1k <-
+      mitools::MIextract(result_dcpo_1k, fun = vcovBK_se)
+  }
+
+  result_betas_dcpo_1k <-
+    mitools::MIextract(result_dcpo_1k, fun = coef)
+
+  df_result_dcpo <-
+    summary(
+      mitools::MIcombine(results = result_betas_dcpo_1k, variance = result_vars_dcpo_1k)
+    ) %>% rownames_to_column(var = "term") %>%
+    rename(conf.low = `(lower`,
+           conf.high = `upper)`,
+           estimate = results) %>%
+    filter(!str_detect(term, "(Intercept)"))
+}
+
+mod_ls <- paste0(
+  "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
+  c("plm::lag(theta, 1)", 
+    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
+  " + plm::lag(lg_imp_mdpgdp, 1) +
+             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
+             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)"
+)
+
+df_result_dcpoAJPS <- map(mod_ls, estimate_dcpo)
+
+save(df_result_dcpoAJPS, file = here::here("output", "estimates_dcpoAJPS.RDS"))
+```
+
+```{r visualizeAJPS, fig.cap= "The Effect of Democratic Mood on Institutional Democratization", eval = TRUE}
+
+load(here::here("output", "estimates_clsMeanAJPS.RDS"))
+load(here::here("output", "estimates_clsAJPS.RDS"))
+load(here::here("output", "estimates_dcpoAJPS.RDS"))
+
+df_plot <- df_result_cls[[1]] %>% 
+  mutate(model = "Claassen 2019")
+
+df_plot <- df_result_clsUncertain[[1]] %>% 
+  mutate(model = "Claassen w. Uncertainty") %>%  
+  bind_rows(df_plot)
+
+df_plot <- df_result_dcpoAJPS[[1]] %>% 
+  mutate(model = "DCPO") %>%  
+  bind_rows(df_plot)
+
+df_plotS <- df_plot %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democracy\n (t-1)",
+        "Democracy\n (t-2)",
+      "Democratic\n Mood\n (t-1)",
+      "Log GDP\n per capita\n (t−1)",
+      "GDP per\n capita Growth\n (t−1)",
+      "Regional\n Democracy\n (t−1)",
+      "Percent\n Muslim\n (t-1)",
+      "Resource\n Dependence\n (t−1)"),
+    time = 3)
+  )
+
+df_tableAJPS <- df_plotS %>% mutate(
+  std.error = ifelse(is.na(std.error), se, std.error)
+) %>% 
+  select(term, estimate, std.error, model)
+
+plot_AJPS1 <- dwplot(df_plotS, dodge_size = 0.8) +
+  scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "DV: Institutional Democracy (Vdem)",
+    subtitle = "Pooled"
+  ) +
+  theme(legend.position = "none")
+
+# the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
+
+df_plot <- df_result_cls[[2]] %>% 
+  mutate(model = "Claassen 2019")
+
+df_plot <- df_result_clsUncertain[[2]] %>% 
+  mutate(model = "Claassen w. Uncertainty") %>%  
+  bind_rows(df_plot)
+
+df_plot <- df_result_dcpoAJPS[[2]] %>% 
+  mutate(model = "DCPO") %>%  
+  bind_rows(df_plot)
+
+df_plotS <- df_plot %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democracy\n (t-1)",
+        "Democracy\n (t-2)",
+      "Democratic\n Demo Only\n (t-1)",
+      "Democratic\n Auto Only\n (t-1)",
+      "Log GDP\n per capita\n (t−1)",
+      "GDP per\n capita Growth\n (t−1)",
+      "Regional\n Democracy\n (t−1)",
+      "Percent\n Muslim\n (t-1)",
+      "Resource\n Dependence\n (t−1)"),
+    time = 3)
+  )
+
+plot_AJPS2 <- dwplot(df_plotS, dodge_size = 0.8) +
+  scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "",
+    subtitle = "Regime Specific"
+  ) +
+  theme(legend.position = "bottom")
+
+legend <- get_legend(plot_AJPS2)
+
+plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
+
+grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol=2, nrow = 2, 
+             layout_matrix = rbind(c(1,2), c(3,3)),
+             widths = c(2.7, 2.7), heights = c(2.5, 0.2))
+
+```
+
+```{r visualizedUncertainAJPS, fig.cap= "The Effect of Democratic Mood on Institutional Democratization Accounting for Uncertainty"}
+
+df_plot <- df_result_dcpoMeanAJPS[[1]] %>% 
+  mutate(model = "DCPO\n (Point Estimates)")
+
+df_plot <- df_result_dcpoAJPS[[1]] %>%
+  mutate(model = "DCPO\n (w. Uncertainty)") %>%
+  rename(std.error = se) %>%
+  bind_rows(df_plot)
+
+plot_pooled <- filter(df_plot, model != "Claassen 2019") %>% 
+  dwplot(by_2sd = FALSE) %>%
+  relabel_predictors(
+    c(
+      `plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
+      `plm::lag(Libdem_VD, 1:2)1` = "Democracy(t-1)",
+      `plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
+      `plm::lag(Libdem_VD, 1:2)2` = "Democracy(t-2)",
+      `plm::lag(theta, 1)` = "Democratic Mood(t-1)",
+      `plm::lag(SupDem_trim, 1)` = "Democratic Mood(t-1)",
+      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
+      `plm::lag(lnGDP_imp, 1)` = "Log GDP per capita(t−1)",
+      `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
+      `plm::lag(GDP_imp_grth, 1)` = "GDP per capita Growth(t−1)",
+      `plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
+      `plm::lag(Libdem_regUN, 1)` = "Regional democracy(t−1)",
+      `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
+      `plm::lag(Pr_Muslim, 1)` = "Percent Muslim (t-1)",
+      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)",
+      `plm::lag(Res_cp_WDI_di, 1)` = "Resource Dependence(t−1)"
+    )
+  ) +
+  geom_vline(xintercept = 0,
+             colour = "grey80",
+             linetype = 2) +
+  theme_minimal() +
+  ggtitle("DV: Liberal Democracy (Vdem)") +
+  xlab("Coefficient Estimate") +
+  theme(
+    axis.title.y = element_blank(),
+    legend.position = "bottom",
+    legend.title = element_blank()
+  )
+
+df_plot <- df_result_dcpoMeanAJPS[[2]] %>% 
+  mutate(model = "DCPO\n (Point Estimates)")
+
+df_plot <- df_result_dcpoAJPS[[2]] %>%
+  mutate(model = "DCPO\n (w. Uncertainty)") %>%
+  rename(std.error = se) %>%
+  bind_rows(df_plot)
+
+plot_pooled2 <- filter(df_plot, model != "Claassen 2019") %>% 
+  dwplot(by_2sd = FALSE) %>%
+  relabel_predictors(
+    c(
+      `plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
+      `plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
+      `plm::lag(theta_dem, 1)` = "Mood Democracy(t-1)",
+      `plm::lag(theta_aut, 1)` = "Mood Autocracy(t-1)",
+      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
+      `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
+      `plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
+      `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
+      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)"
+    )
+  ) +
+  geom_vline(xintercept = 0,
+             colour = "grey80",
+             linetype = 2) +
+  theme_minimal() +
+  ggtitle("DV: Liberal Democracy (Vdem)") +
+  xlab("Coefficient Estimate") +
+  theme(
+    axis.title.y = element_blank(),
+    legend.position = "bottom",
+    legend.title = element_blank()
+  )
+
+gridExtra::grid.arrange(plot_pooled,plot_pooled2, ncol = 2)
+```
+
+```{r claassenAPSR}
+sd.plm <- pdata.frame(x, index = c("Country", "Year"))
+
+mods <- vector(mode = "list")
+
+mods[[1]] <- plm(
+  diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Libdem_z, lag = 1)
+  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1),
+  sd.plm,
+  model = "pooling"
+)
+mods[[2]] <- plm(
+  diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Libdem_z, lag = 1)
+  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)
+  + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1),
+  sd.plm,
+  model = "pooling"
+)
+
+df_result_clsAPSR <- map(mods, function(aMod){
+  tidy(aMod) %>%
+    mutate(std.error = vcovHC_se(aMod))
+})
+
+save(df_result_clsAPSR, file = here::here("output", "estimates_clsMeanAPSR.RDS"))
+```
+
+```{r claassenAPSRUncertainty}
+ls_country <- unique(claassen_replication_input$data$country)
+first_year <- min(claassen_replication_input$data$year)
+
+sd_control <- sd.plm %>%
+  mutate(
+    country = as.character(Country),
+    year = as.numeric(as.character(Year))
+  )
+
+df_clsAPSR <- purrr::map(1:1000, function(anEntry) {
+  claassen_m5_theta$theta[anEntry,,] %>% 
+    reformat_dcpo_output("theta") %>% 
+    # left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
+    #           by = c("year", "country")) %>%
+    left_join(sd_control, by = c("country", "year")) %>% 
+    plm::pdata.frame(index = c("country", "year"))
+})
+
+estimate_cls <- vector(mode = "list")
+
+estimate_cls[[1]] <- function(aDataset) {
+  plm(
+      diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Libdem_z, lag = 1)
+  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1),
+      model = "pooling",
+      data = aDataset
+    )
+}
+
+estimate_cls[[2]] <- function(aDataset) {
+  plm(
+      diff(theta, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Libdem_z, lag = 1)
+  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)
+  + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1),
+      model = "pooling",
+      data = aDataset
+    )
+}
+
+df_result_clsUncertainAPSR <- map(estimate_cls, function(aModel){
+  aFit <- map(df_clsAPSR, aModel)
+
+  result_vars_cls_1k <- mitools::MIextract(aFit, fun = vcovHC_se)
+  result_betas_cls_1k <- mitools::MIextract(aFit, fun = coef)
+
+  summary(
+      mitools::MIcombine(results = result_betas_cls_1k, 
+                         variance = result_vars_cls_1k)
+    ) %>% rownames_to_column(var = "term") %>%
+    rename(conf.low = `(lower`,
+           conf.high = `upper)`,
+           estimate = results) %>%
+    filter(!str_detect(term, "(Intercept)"))
+
+})
+
+save(df_result_clsUncertainAPSR, file = here::here("output", "estimates_clsAPSR.RDS"))
+```
+
+```{r dcpoPointAPSR}
+df_controls <- read_csv(here::here("data", "control_variables_apsr.csv"),
+                        col_types = cols(.default = col_double(),
+                                         country = col_character(),
+                                         country_name = col_character(),
+                                         ISO = col_character(),
+                                         Region_UN = col_character())) %>% 
+  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
+         country = countrycode::countrycode(country0, "country.name", "country.name")) %>% 
+  filter(year >= firstyear)
+
+load(here::here("output", "estimates_dcpoMean.RDS"))
+
+df_dcpoMeanAPSR <- df_dcpoMean %>% 
+  left_join(df_controls, by = c("country", "year")) %>% 
+  plm::pdata.frame(index = c("country", "year"))
+
+mods <- vector(mode = "list")
+mods[[1]] <-
+  plm(
+    diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1)
+    + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1),
+    data = df_dcpoMeanAPSR,
+    model = "pooling"
+  )
+
+mods[[2]] <-
+  plm(
+    diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1) + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1),
+    data = df_dcpoMeanAPSR,
+    model = "pooling"
+  )
+
+df_result_dcpoMeanAPSR <- map(mods, function(aMod){
+  aMod %>% 
+    tidy %>%
+    mutate(std.error = vcovHC_se(aMod))
+})
+
+save(df_result_dcpoMeanAPSR, file = here::here("output", "estimates_dcpoMeanAPSR.RDS"))
+```
+
+```{r dcpoUncertaintyAPSR}
+df_dcpo <- purrr::map(1:1000, function(anEntry) {
+  dcpo_theta$theta[anEntry,,] %>% 
+    reformat_dcpo_output("theta") %>% 
+    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
+              by = c("year", "country")) %>%
+    left_join(df_controls, by = c("country", "year")) %>% 
+    plm::pdata.frame(index = c("country", "year"))
+})
+
+estimate_dcpo <- vector(mode = "list")
+
+estimate_dcpo[[1]] <- function(aDataset) {
+  plm(
+      diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1)
+      + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1),
+      model = "pooling",
+      data = aDataset
+    )
+}
+
+estimate_dcpo[[2]] <- function(aDataset) {
+  plm(
+      diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1) + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1),
+      model = "pooling",
+      data = aDataset
+    )
+}
+
+df_result_dcpoAPSR <- map(estimate_dcpo, function(aModel){
+  aFit <- map(df_dcpo, aModel)
+
+  result_vars_dcpo_1k <- mitools::MIextract(aFit, fun = vcovHC_se)
+  result_betas_dcpo_1k <- mitools::MIextract(aFit, fun = coef)
+
+  summary(
+      mitools::MIcombine(results = result_betas_dcpo_1k, 
+                         variance = result_vars_dcpo_1k)
+    ) %>% rownames_to_column(var = "term") %>%
+    rename(conf.low = `(lower`,
+           conf.high = `upper)`,
+           estimate = results) %>%
+    filter(!str_detect(term, "(Intercept)"))
+
+})
+
+save(df_result_dcpoAPSR, file = here::here("output", "estimates_dcpoAPSR.RDS"))
+```
+
+```{r visualizedAPSR, fig.cap= "Effects of Democracy on Change in Mood", eval = TRUE}
+
+load(here::here("output", "estimates_clsMeanAPSR.RDS"))
+load(here::here("output", "estimates_clsAPSR.RDS"))
+load(here::here("output", "estimates_dcpoAPSR.RDS"))
+
+df_plot <- df_result_clsAPSR[[1]] %>% 
+  mutate(model = "Claassen 2020")
+
+df_plot <- df_result_clsUncertainAPSR[[1]] %>% 
+  mutate(model = "Claassen w. Uncertainty") %>%  
+  bind_rows(df_plot)
+
+df_plot <- df_result_dcpoAPSR[[1]] %>% 
+  mutate(model = "DCPO") %>%  
+  bind_rows(df_plot)
+
+df_plotS <- df_plot %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+      "Liberal Democracy\n (Difference)",
+      "Liberal Democracy\n (t-1)",
+      "Log GDP\n per capita\n (Difference)",
+      "Log GDP\n (t−1)"),
+    time = 3)
+  )
+
+plot_APSR1 <- dwplot(df_plotS, dodge_size = 0.8) +
+  scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "DV: Democratic Mood",
+    subtitle = "Basic"
+  ) +
+  theme(legend.position = "none")
+
+df_plot <- df_result_clsAPSR[[2]] %>% 
+  mutate(model = "Claassen 2020")
+
+df_plot <- df_result_clsUncertainAPSR[[2]] %>% 
+  mutate(model = "Claassen w. Uncertainty") %>%  
+  bind_rows(df_plot)
+
+df_plot <- df_result_dcpoAPSR[[2]] %>% 
+  mutate(model = "DCPO") %>%  
+  bind_rows(df_plot)
+
+df_plotS <- df_plot %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democratic\n Mood\n (t-1)",
+        "Democratic\n Mood\n (t-2)",
+      "Liberal\n Democracy\n (Difference)",
+      "Liberal\n Democracy\n (t-1)",
+      "Log GDP\n per capita\n (Difference)",
+      "Log GDP\n (t−1)",
+      "Corruption\n (Difference)",
+      "Corruption\n (t−1)"
+      ),time = 3)
+  )
+
+plot_APSR2 <- dwplot(df_plotS, dodge_size = 0.8) +
+  scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "",
+    subtitle = "w. Corruption"
+  )
+
+legend <- get_legend(plot_AJPS2)
+
+plot_APSR2 <- plot_APSR2 +
+  theme(legend.position = "none")
+
+gridExtra::grid.arrange(plot_APSR1, plot_APSR2, legend, ncol=2, nrow = 2, 
+             layout_matrix = rbind(c(1,2), c(3,3)),
+             widths = c(2.7, 2.7), heights = c(2.5, 0.2))
+```
+
+```{r visualizedUncertaintyAPSR, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO"}
+
+load(here::here("output", "estimates_dcpoAPSR.RDS"))
+
+df_plot <- df_result_dcpoMeanAPSR[[1]] %>% 
+  mutate(model = "DCPO\n (Point Estimates)")
+
+df_plot <- df_result_dcpoAPSR[[1]] %>%
+  mutate(model = "DCPO\n (w. Uncertainty)") %>%
+  rename(std.error = se) %>%
+  bind_rows(df_plot)
+
+plot_pooled <- filter(df_plot, model != "Claassen 2019") %>% 
+  dwplot(by_2sd = FALSE) %>%
+  relabel_predictors(
+    c(
+      `plm::lag(theta, 1:2)1` = "Democracy Mood(t-1)",
+      `plm::lag(theta, 1:2)2` = "Democracy Mood(t-2)",
+      `diff(Vdem_libdem_z, lag = 1)` = "Liberal Democracy (Diff)",
+      `plm::lag(Vdem_libdem_z, 1)` = "Liberal Democracy (t-1)",
+      `diff(lg_imp_mdpgdp, lag = 1)` = "Log GDP per capita(Diff)", 
+      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
+      `plm::lag(mdprgdp_grwth, 1)` = "Corruption (Difference)"
+    )
+  ) +
+  geom_vline(xintercept = 0,
+             colour = "grey80",
+             linetype = 2) +
+  theme_minimal() +
+  ggtitle("DV: Liberal Democracy (Vdem)") +
+  xlab("Coefficient Estimate") +
+  theme(
+    axis.title.y = element_blank(),
+    legend.position = "bottom",
+    legend.title = element_blank()
+  )
+
+df_plot <- df_result_dcpoMeanAPSR[[2]] %>% 
+  mutate(model = "DCPO\n (Point Estimates)")
+
+df_plot <- df_result_dcpoAPSR[[2]] %>%
+  mutate(model = "DCPO\n (w. Uncertainty)") %>%
+  rename(std.error = se) %>%
+  bind_rows(df_plot)
+
+plot_pooled2 <- filter(df_plot, model != "Claassen 2019") %>% 
+  dwplot(by_2sd = FALSE) %>%
+  relabel_predictors(
+    c(
+      `plm::lag(theta, 1:2)1` = "Democracy Mood(t-1)",
+      `plm::lag(theta, 1:2)2` = "Democracy Mood(t-2)",
+      `diff(Vdem_libdem_z, lag = 1)` = "Liberal Democracy (Diff)",
+      `plm::lag(Vdem_libdem_z, 1)` = "Liberal Democracy (t-1)",
+      `diff(lg_imp_mdpgdp, lag = 1)` = "Log GDP per capita(Diff)", 
+      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
+      `diff(cpi_sd, lag = 1)` = "Corruption (Difference)",
+      `plm::lag(cpi_sd, 1)` = "Corruption (t-1)"
+    )
+  ) +
+  geom_vline(xintercept = 0,
+             colour = "grey80",
+             linetype = 2) +
+  theme_minimal() +
+  ggtitle("DV: Liberal Democracy (Vdem)") +
+  xlab("Coefficient Estimate") +
+  theme(
+    axis.title.y = element_blank(),
+    legend.position = "bottom",
+    legend.title = element_blank()
+  )
+
+gridExtra::grid.arrange(plot_pooled,plot_pooled2, ncol = 2)
+```
+
+The results are presented in Figure \@ref(fig:visualizeAJPS)
+
+# Discussion
+
 In short, the main empirical findings about the estimated effect of public democratic support on democracy or vice versa are not replicable when measurement uncertainty is accounted, even using better measurement and more data.
@@
 
-```{r dataInput, eval = FALSE}
-
-supdem <- read.csv("../data/Support_democracy_ajps.csv")
-v_dem <- read.csv("../data/vdem15.csv")
-sd.plm <- pdata.frame(supdem, index = c("Country", "Year"))
-
-load(here::here("data", "claassen_replication_input.rda"))
-load(here::here("data", "claassen_m5_theta.rda"))
-load(here::here("data", "dcpo_input.rda"))
-load(here::here("data", "dcpo_theta.rda"))
-load(here::here("data", "dcpo_sigma.rda"))
-load(here::here("data", "dem_mood_apsr.RData"))
-
-## Beck-Katz panel-corrected standard errors
-vcovBK_se <- function(x) {
-  plm::vcovBK(x, cluster = "time") %>% 
-    diag() %>% 
-    sqrt()
-}
-
-vcovHC_se <-  function(x) {
-  plm::vcovHC(x, method="arellano", cluster="group") %>% 
-    diag() %>% 
-    sqrt()
-}
-
-reformat_dcpo_output <- function(x, parameter_name) {
-  df_temp <- x %>% 
-    as_tibble(.name_repair = ~ls_country) %>% 
-    mutate(year = first_year + row_number() - 1) %>% 
-    pivot_longer(cols = all_of(ls_country),
-                 names_to = "country",
-                 values_to = parameter_name) %>%
-    arrange(country, year)
-  return(df_temp)
-}
-```
-
-```{r claassenAJPS}
-# Pooled model -----
-# regime = ifelse(sd2$Regime_VD > 1, 1, 0)
-
-ls_mod <-
-  paste0(
-    "Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + ",
-    c(
-      "plm::lag(SupDem_trim, 1)",
-      "plm::lag(SupDem_Democ, 1) + plm::lag(SupDem_Autoc, 1)"
-    ),
-    "+ plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)"
-  )
-
-df_result_cls <- map(ls_mod, function(mod){
-  result <- plm(mod, model = "pooling", data = sd.plm)
-  df_result <- tidy(result) %>%
-    mutate(std.error = vcovBK_se(result))
-})
-
-save(df_result_cls, file = here::here("output", "estimates_clsMeanAJPS.RDS"))
-```
-
-```{r claassenUncertaintyAJPS,eval=FALSE}
-
-ls_country <- unique(claassen_replication_input$data$country)
-first_year <- min(claassen_replication_input$data$year)
-
-sd_control <- sd.plm %>%
-  mutate(
-    country = as.character(Country),
-    year = as.numeric(as.character(Year)),
-    regime = ifelse(Regime_VD > 1, 1, 0)
-  )
-
-df_cls <- purrr::map(1:1000, function(anEntry) {
-  claassen_m5_theta$theta[anEntry,,] %>% 
-    reformat_dcpo_output("theta") %>% 
-    # left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
-    #           by = c("year", "country")) %>%
-    left_join(sd_control, by = c("country", "year")) %>% 
-    mutate(theta_dem = theta * regime,
-           theta_aut = theta * (1 - regime)) %>% 
-    plm::pdata.frame(index = c("country", "year"))
-})
-
-estimate_cls <- function(aModel, aType = "pooling") {
-  if (aType == "gmm") {
-    result_cls_1k <- map(df_cls, function(aDataset) {
-      pgmm(
-        as.formula(aModel),
-        effect = "individual",
-        model = "onestep",
-        transformation = "ld",
-        indexes = c("Country", "Year"),
-        data = aDataset
-      )
-    })
-
-    result_vars_cls_1k <-
-      mitools::MIextract(result_cls_1k, fun = vcovHC_se)
-
-  } else {
-    result_cls_1k <- map(df_cls, function(aDataset) {
-      plm::plm(aModel,
-               model = "pooling",
-               data = aDataset)
-    })
-
-    result_vars_cls_1k <-
-      mitools::MIextract(result_cls_1k, fun = vcovBK_se)
-  }
-
-  result_betas_cls_1k <-
-    mitools::MIextract(result_cls_1k, fun = coef)
-
-  df_result_cls <-
-    summary(
-      mitools::MIcombine(results = result_betas_cls_1k, variance = result_vars_cls_1k)
-    ) %>% rownames_to_column(var = "term") %>%
-    rename(conf.low = `(lower`,
-           conf.high = `upper)`,
-           estimate = results) %>%
-    filter(!str_detect(term, "(Intercept)"))
-}
-
-mod_ls <- paste0(
-  "Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + ",
-  c("plm::lag(theta, 1)", 
-    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
-  " + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)"
-)
-
-df_result_clsUncertain <- map(mod_ls, estimate_cls)
-
-save(df_result_clsUncertain, file = here::here("output", "estimates_clsAJPS.RDS"))
-```
-
-```{r dcpoPointAJPS, eval=FALSE}
-ls_country <- levels(dcpo_input$data$kk)
-first_year <- min(dcpo_input$data$year)
-
-df_dcpoMean <- purrr::map_df(1:1000, function(anEntry) {
-  dcpo_theta$theta[anEntry,,] %>% 
-    reformat_dcpo_output("theta") %>% 
-    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
-              by = c("year", "country"))
-}) %>% 
-  group_by(country, year) %>% 
-  summarise(theta = mean(theta), 
-            sigma = mean(sigma))
-
-save(df_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))
-
-df_controls <- read_csv(here::here("data", "control_variables_ajps.csv"),
-                        col_types = cols(.default = col_double(),
-                                         country = col_character(),
-                                         country_name = col_character(),
-                                         ISO = col_character(),
-                                         Region_UN = col_character())) %>% 
-  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
-         country = countrycode::countrycode(country0, "country.name", "country.name"),
-         regime = Vdem_regime > 1) %>% 
-  filter(year >= firstyear) # using trimmed data as Claassen
-
-df_dcpoMeanAJPS <- df_dcpoMean %>% 
-  right_join(df_controls, by = c("country", "year")) %>% 
-  mutate(theta_dem = theta * regime,
-         theta_aut = theta * (1 - regime)) %>% 
-    plm::pdata.frame(index = c("country", "year"))
-
-ls_mod <- paste0(
-  "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
-  c("plm::lag(theta, 1)", 
-    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
-  " + plm::lag(lg_imp_mdpgdp, 1) +
-             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
-             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)"
-)
-
-df_result_dcpoMeanAJPS <- map(ls_mod, function(mod){
-  result <- plm(mod, model = "pooling", data = df_dcpoMeanAJPS)
-  df_result <- tidy(result) %>%
-    mutate(std.error = vcovBK_se(result))
-})
-
-save(df_result_dcpoMeanAJPS, file = here::here("output", "estimates_dcpoMeanAJPS.RDS"))
-```
-
-```{r dcpoUncertaintyAJPS, eval = FALSE}
-df_dcpo <- purrr::map(1:1000, function(anEntry) {
-  dcpo_theta$theta[anEntry,,] %>% 
-    reformat_dcpo_output("theta") %>% 
-    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
-              by = c("year", "country")) %>%
-    left_join(df_controls, by = c("country", "year")) %>% 
-    mutate(theta_dem = theta * regime,
-           theta_aut = theta * (1 - regime)) %>% 
-    plm::pdata.frame(index = c("country", "year"))
-})
-
-estimate_dcpo <- function(aModel, aType = "pooling") {
-  if (aType == "gmm") {
-    result_dcpo_1k <- map(df_dcpo, function(aDataset) {
-      pgmm(
-        as.formula(aModel),
-        effect = "individual",
-        model = "onestep",
-        transformation = "ld",
-        indexes = c("Country", "Year"),
-        data = aDataset
-      )
-    })
-
-    result_vars_dcpo_1k <-
-      mitools::MIextract(result_dcpo_1k, fun = vcovHC_se)
-
-  } else {
-    result_dcpo_1k <- map(df_dcpo, function(aDataset) {
-      plm::plm(aModel,
-               model = "pooling",
-               data = aDataset)
-    })
-
-    result_vars_dcpo_1k <-
-      mitools::MIextract(result_dcpo_1k, fun = vcovBK_se)
-  }
-
-  result_betas_dcpo_1k <-
-    mitools::MIextract(result_dcpo_1k, fun = coef)
-
-  df_result_dcpo <-
-    summary(
-      mitools::MIcombine(results = result_betas_dcpo_1k, variance = result_vars_dcpo_1k)
-    ) %>% rownames_to_column(var = "term") %>%
-    rename(conf.low = `(lower`,
-           conf.high = `upper)`,
-           estimate = results) %>%
-    filter(!str_detect(term, "(Intercept)"))
-}
-
-mod_ls <- paste0(
-  "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
-  c("plm::lag(theta, 1)", 
-    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
-  " + plm::lag(lg_imp_mdpgdp, 1) +
-             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
-             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)"
-)
-
-df_result_dcpoAJPS <- map(mod_ls, estimate_dcpo)
-
-save(df_result_dcpoAJPS, file = here::here("output", "estimates_dcpoAJPS.RDS"))
-```
-
-```{r visualizedMoodAJPS, fig.cap= "The Effect of Democratic Mood on Institutional Democratization"}
-
-load(here::here("output", "estimates_clsMeanAJPS.RDS"))
-load(here::here("output", "estimates_clsAJPS.RDS"))
-load(here::here("output", "estimates_dcpoAJPS.RDS"))
-
-df_plot <- df_result_cls[[1]] %>% 
-  mutate(model = "Claassen 2019")
-
-df_plot <- df_result_clsUncertain[[1]] %>% 
-  mutate(model = "Claassen w. Uncertainty") %>%  
-  bind_rows(df_plot)
-
-df_plot <- df_result_dcpoAJPS[[1]] %>% 
-  mutate(model = "DCPO") %>%  
-  bind_rows(df_plot)
-
-df_plotS <- df_plot %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = rep(
-      c("Democracy\n (t-1)",
-        "Democracy\n (t-2)",
-      "Democratic\n Mood\n (t-1)",
-      "Log GDP\n per capita\n (t−1)",
-      "GDP per\n capita Growth\n (t−1)",
-      "Regional\n Democracy\n (t−1)",
-      "Percent\n Muslim\n (t-1)",
-      "Resource\n Dependence\n (t−1)"),
-    time = 3)
-  )
-
-plot_AJPS1 <- dwplot(df_plotS, dodge_size = 0.8) +
-  scale_color_uiowa(name = "", palette = "digitMixed") +
-  labs(
-    title = "DV: Institutional Democracy (Vdem)",
-    subtitle = "Pooled"
-  ) +
-  theme(legend.position = "none")
-
-# the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
-
-df_plot <- df_result_cls[[2]] %>% 
-  mutate(model = "Claassen 2019")
-
-df_plot <- df_result_clsUncertain[[2]] %>% 
-  mutate(model = "Claassen w. Uncertainty") %>%  
-  bind_rows(df_plot)
-
-df_plot <- df_result_dcpoAJPS[[2]] %>% 
-  mutate(model = "DCPO") %>%  
-  bind_rows(df_plot)
-
-df_plotS <- df_plot %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = rep(
-      c("Democracy\n (t-1)",
-        "Democracy\n (t-2)",
-      "Democratic\n Demo Only\n (t-1)",
-      "Democratic\n Auto Only\n (t-1)",
-      "Log GDP\n per capita\n (t−1)",
-      "GDP per\n capita Growth\n (t−1)",
-      "Regional\n Democracy\n (t−1)",
-      "Percent\n Muslim\n (t-1)",
-      "Resource\n Dependence\n (t−1)"),
-    time = 3)
-  )
-
-plot_AJPS2 <- dwplot(df_plotS, dodge_size = 0.8) +
-  scale_color_uiowa(name = "", palette = "digitMixed") +
-  labs(
-    title = "",
-    subtitle = "Regime Specific"
-  ) +
-  theme(legend.position = "bottom")
-
-legend <- get_legend(plot_AJPS2)
-
-plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
-
-grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol=2, nrow = 2, 
-             layout_matrix = rbind(c(1,2), c(3,3)),
-             widths = c(2.7, 2.7), heights = c(2.5, 0.2))
-
-```
-
-```{r visualizedUncertainAJPS, fig.cap= "The Effect of Democratic Mood on Institutional Democratization Accounting for Uncertainty", eval=FALSE}
-
-df_plot <- df_result_dcpoMeanAJPS[[1]] %>% 
-  mutate(model = "DCPO\n (Point Estimates)")
-
-df_plot <- df_result_dcpoAJPS[[1]] %>%
-  mutate(model = "DCPO\n (w. Uncertainty)") %>%
-  rename(std.error = se) %>%
-  bind_rows(df_plot)
-
-plot_pooled <- filter(df_plot, model != "Claassen 2019") %>% 
-  dwplot(by_2sd = FALSE) %>%
-  relabel_predictors(
-    c(
-      `plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
-      `plm::lag(Libdem_VD, 1:2)1` = "Democracy(t-1)",
-      `plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
-      `plm::lag(Libdem_VD, 1:2)2` = "Democracy(t-2)",
-      `plm::lag(theta, 1)` = "Democratic Mood(t-1)",
-      `plm::lag(SupDem_trim, 1)` = "Democratic Mood(t-1)",
-      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
-      `plm::lag(lnGDP_imp, 1)` = "Log GDP per capita(t−1)",
-      `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
-      `plm::lag(GDP_imp_grth, 1)` = "GDP per capita Growth(t−1)",
-      `plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
-      `plm::lag(Libdem_regUN, 1)` = "Regional democracy(t−1)",
-      `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
-      `plm::lag(Pr_Muslim, 1)` = "Percent Muslim (t-1)",
-      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)",
-      `plm::lag(Res_cp_WDI_di, 1)` = "Resource Dependence(t−1)"
-    )
-  ) +
-  geom_vline(xintercept = 0,
-             colour = "grey80",
-             linetype = 2) +
-  theme_minimal() +
-  ggtitle("DV: Liberal Democracy (Vdem)") +
-  xlab("Coefficient Estimate") +
-  theme(
-    axis.title.y = element_blank(),
-    legend.position = "bottom",
-    legend.title = element_blank()
-  )
-
-df_plot <- df_result_dcpoMeanAJPS[[2]] %>% 
-  mutate(model = "DCPO\n (Point Estimates)")
-
-df_plot <- df_result_dcpoAJPS[[2]] %>%
-  mutate(model = "DCPO\n (w. Uncertainty)") %>%
-  rename(std.error = se) %>%
-  bind_rows(df_plot)
-
-plot_pooled2 <- filter(df_plot, model != "Claassen 2019") %>% 
-  dwplot(by_2sd = FALSE) %>%
-  relabel_predictors(
-    c(
-      `plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
-      `plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
-      `plm::lag(theta_dem, 1)` = "Mood Democracy(t-1)",
-      `plm::lag(theta_aut, 1)` = "Mood Autocracy(t-1)",
-      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
-      `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
-      `plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
-      `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
-      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)"
-    )
-  ) +
-  geom_vline(xintercept = 0,
-             colour = "grey80",
-             linetype = 2) +
-  theme_minimal() +
-  ggtitle("DV: Liberal Democracy (Vdem)") +
-  xlab("Coefficient Estimate") +
-  theme(
-    axis.title.y = element_blank(),
-    legend.position = "bottom",
-    legend.title = element_blank()
-  )
-
-gridExtra::grid.arrange(plot_pooled,plot_pooled2, ncol = 2)
-```
-
-```{r claassenAPSR}
-sd.plm <- pdata.frame(x, index = c("Country", "Year"))
-
-mods <- vector(mode = "list")
-
-mods[[1]] <- plm(
-  diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Libdem_z, lag = 1)
-  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1),
-  sd.plm,
-  model = "pooling"
-)
-mods[[2]] <- plm(
-  diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Libdem_z, lag = 1)
-  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)
-  + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1),
-  sd.plm,
-  model = "pooling"
-)
-
-df_result_clsAPSR <- map(mods, function(aMod){
-  tidy(aMod) %>%
-    mutate(std.error = vcovHC_se(aMod))
-})
-
-save(df_result_clsAPSR, file = here::here("output", "estimates_clsMeanAPSR.RDS"))
-```
-
-```{r claassenAPSRUncertainty}
-ls_country <- unique(claassen_replication_input$data$country)
-first_year <- min(claassen_replication_input$data$year)
-
-sd_control <- sd.plm %>%
-  mutate(
-    country = as.character(Country),
-    year = as.numeric(as.character(Year))
-  )
-
-df_clsAPSR <- purrr::map(1:1000, function(anEntry) {
-  claassen_m5_theta$theta[anEntry,,] %>% 
-    reformat_dcpo_output("theta") %>% 
-    # left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
-    #           by = c("year", "country")) %>%
-    left_join(sd_control, by = c("country", "year")) %>% 
-    plm::pdata.frame(index = c("country", "year"))
-})
-
-estimate_cls <- vector(mode = "list")
-
-estimate_cls[[1]] <- function(aDataset) {
-  plm(
-      diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Libdem_z, lag = 1)
-  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1),
-      model = "pooling",
-      data = aDataset
-    )
-}
-
-estimate_cls[[2]] <- function(aDataset) {
-  plm(
-      diff(theta, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Libdem_z, lag = 1)
-  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)
-  + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1),
-      model = "pooling",
-      data = aDataset
-    )
-}
-
-df_result_clsUncertainAPSR <- map(estimate_cls, function(aModel){
-  aFit <- map(df_clsAPSR, aModel)
-
-  result_vars_cls_1k <- mitools::MIextract(aFit, fun = vcovHC_se)
-  result_betas_cls_1k <- mitools::MIextract(aFit, fun = coef)
-
-  summary(
-      mitools::MIcombine(results = result_betas_cls_1k, 
-                         variance = result_vars_cls_1k)
-    ) %>% rownames_to_column(var = "term") %>%
-    rename(conf.low = `(lower`,
-           conf.high = `upper)`,
-           estimate = results) %>%
-    filter(!str_detect(term, "(Intercept)"))
-
-})
-
-save(df_result_clsUncertainAPSR, file = here::here("output", "estimates_clsAPSR.RDS"))
-```
-
-```{r dcpoPointAPSR, eval = FALSE}
-df_controls <- read_csv(here::here("data", "control_variables_apsr.csv"),
-                        col_types = cols(.default = col_double(),
-                                         country = col_character(),
-                                         country_name = col_character(),
-                                         ISO = col_character(),
-                                         Region_UN = col_character())) %>% 
-  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
-         country = countrycode::countrycode(country0, "country.name", "country.name")) %>% 
-  filter(year >= firstyear)
-
-load(here::here("output", "estimates_dcpoMean.RDS"))
-
-df_dcpoMeanAPSR <- df_dcpoMean %>% 
-  left_join(df_controls, by = c("country", "year")) %>% 
-  plm::pdata.frame(index = c("country", "year"))
-
-mods <- vector(mode = "list")
-mods[[1]] <-
-  plm(
-    diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1)
-    + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1),
-    data = df_dcpoMeanAPSR,
-    model = "pooling"
-  )
-
-mods[[2]] <-
-  plm(
-    diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1) + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1),
-    data = df_dcpoMeanAPSR,
-    model = "pooling"
-  )
-
-df_result_dcpoMeanAPSR <- map(mods, function(aMod){
-  aMod %>% 
-    tidy %>%
-    mutate(std.error = vcovHC_se(aMod))
-})
-
-save(df_result_dcpoMeanAPSR, file = here::here("output", "estimates_dcpoMeanAPSR.RDS"))
-```
-
-```{r dcpoUncertaintyAPSR, eval = FALSE}
-df_dcpo <- purrr::map(1:1000, function(anEntry) {
-  dcpo_theta$theta[anEntry,,] %>% 
-    reformat_dcpo_output("theta") %>% 
-    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
-              by = c("year", "country")) %>%
-    left_join(df_controls, by = c("country", "year")) %>% 
-    plm::pdata.frame(index = c("country", "year"))
-})
-
-estimate_dcpo <- vector(mode = "list")
-
-estimate_dcpo[[1]] <- function(aDataset) {
-  plm(
-      diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1)
-      + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1),
-      model = "pooling",
-      data = aDataset
-    )
-}
-
-estimate_dcpo[[2]] <- function(aDataset) {
-  plm(
-      diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1) + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1),
-      model = "pooling",
-      data = aDataset
-    )
-}
-
-df_result_dcpoAPSR <- map(estimate_dcpo, function(aModel){
-  aFit <- map(df_dcpo, aModel)
-
-  result_vars_dcpo_1k <- mitools::MIextract(aFit, fun = vcovHC_se)
-  result_betas_dcpo_1k <- mitools::MIextract(aFit, fun = coef)
-
-  summary(
-      mitools::MIcombine(results = result_betas_dcpo_1k, 
-                         variance = result_vars_dcpo_1k)
-    ) %>% rownames_to_column(var = "term") %>%
-    rename(conf.low = `(lower`,
-           conf.high = `upper)`,
-           estimate = results) %>%
-    filter(!str_detect(term, "(Intercept)"))
-
-})
-
-save(df_result_dcpoAPSR, file = here::here("output", "estimates_dcpoAPSR.RDS"))
-```
-
-```{r visualizedMoodAPSR, fig.cap= "Effects of Democracy on Change in Mood"}
-
-load(here::here("output", "estimates_clsMeanAPSR.RDS"))
-load(here::here("output", "estimates_clsAPSR.RDS"))
-load(here::here("output", "estimates_dcpoAPSR.RDS"))
-
-df_plot <- df_result_clsAPSR[[1]] %>% 
-  mutate(model = "Claassen 2020")
-
-df_plot <- df_result_clsUncertainAPSR[[1]] %>% 
-  mutate(model = "Claassen w. Uncertainty") %>%  
-  bind_rows(df_plot)
-
-df_plot <- df_result_dcpoAPSR[[1]] %>% 
-  mutate(model = "DCPO") %>%  
-  bind_rows(df_plot)
-
-df_plotS <- df_plot %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-      "Liberal Democracy\n (Difference)",
-      "Liberal Democracy\n (t-1)",
-      "Log GDP\n per capita\n (Difference)",
-      "Log GDP\n (t−1)"),
-    time = 3)
-  )
-
-plot_APSR1 <- dwplot(df_plotS, dodge_size = 0.8) +
-  scale_color_uiowa(name = "", palette = "digitMixed") +
-  labs(
-    title = "DV: Democratic Mood",
-    subtitle = "Basic"
-  ) +
-  theme(legend.position = "none")
-
-df_plot <- df_result_clsAPSR[[2]] %>% 
-  mutate(model = "Claassen 2020")
-
-df_plot <- df_result_clsUncertainAPSR[[2]] %>% 
-  mutate(model = "Claassen w. Uncertainty") %>%  
-  bind_rows(df_plot)
-
-df_plot <- df_result_dcpoAPSR[[2]] %>% 
-  mutate(model = "DCPO") %>%  
-  bind_rows(df_plot)
-
-df_plotS <- df_plot %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = rep(
-      c("Democratic\n Mood\n (t-1)",
-        "Democratic\n Mood\n (t-2)",
-      "Liberal\n Democracy\n (Difference)",
-      "Liberal\n Democracy\n (t-1)",
-      "Log GDP\n per capita\n (Difference)",
-      "Log GDP\n (t−1)",
-      "Corruption\n (Difference)",
-      "Corruption\n (t−1)"
-      ),time = 3)
-  )
-
-plot_APSR2 <- dwplot(df_plotS, dodge_size = 0.8) +
-  scale_color_uiowa(name = "", palette = "digitMixed") +
-  labs(
-    title = "",
-    subtitle = "w. Corruption"
-  )
-
-legend <- get_legend(plot_AJPS2)
-
-plot_APSR2 <- plot_APSR2 +
-  theme(legend.position = "none")
-
-gridExtra::grid.arrange(plot_APSR1, plot_APSR2, legend, ncol=2, nrow = 2, 
-             layout_matrix = rbind(c(1,2), c(3,3)),
-             widths = c(2.7, 2.7), heights = c(2.5, 0.2))
-```
-
-```{r visualizedUncertaintyAPSR, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO", eval = FALSE}
-
-load(here::here("output", "estimates_dcpoAPSR.RDS"))
-
-df_plot <- df_result_dcpoMeanAPSR[[1]] %>% 
-  mutate(model = "DCPO\n (Point Estimates)")
-
-df_plot <- df_result_dcpoAPSR[[1]] %>%
-  mutate(model = "DCPO\n (w. Uncertainty)") %>%
-  rename(std.error = se) %>%
-  bind_rows(df_plot)
-
-plot_pooled <- filter(df_plot, model != "Claassen 2019") %>% 
-  dwplot(by_2sd = FALSE) %>%
-  relabel_predictors(
-    c(
-      `plm::lag(theta, 1:2)1` = "Democracy Mood(t-1)",
-      `plm::lag(theta, 1:2)2` = "Democracy Mood(t-2)",
-      `diff(Vdem_libdem_z, lag = 1)` = "Liberal Democracy (Diff)",
-      `plm::lag(Vdem_libdem_z, 1)` = "Liberal Democracy (t-1)",
-      `diff(lg_imp_mdpgdp, lag = 1)` = "Log GDP per capita(Diff)", 
-      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
-      `plm::lag(mdprgdp_grwth, 1)` = "Corruption (Difference)"
-    )
-  ) +
-  geom_vline(xintercept = 0,
-             colour = "grey80",
-             linetype = 2) +
-  theme_minimal() +
-  ggtitle("DV: Liberal Democracy (Vdem)") +
-  xlab("Coefficient Estimate") +
-  theme(
-    axis.title.y = element_blank(),
-    legend.position = "bottom",
-    legend.title = element_blank()
-  )
-
-df_plot <- df_result_dcpoMeanAPSR[[2]] %>% 
-  mutate(model = "DCPO\n (Point Estimates)")
-
-df_plot <- df_result_dcpoAPSR[[2]] %>%
-  mutate(model = "DCPO\n (w. Uncertainty)") %>%
-  rename(std.error = se) %>%
-  bind_rows(df_plot)
-
-plot_pooled2 <- filter(df_plot, model != "Claassen 2019") %>% 
-  dwplot(by_2sd = FALSE) %>%
-  relabel_predictors(
-    c(
-      `plm::lag(theta, 1:2)1` = "Democracy Mood(t-1)",
-      `plm::lag(theta, 1:2)2` = "Democracy Mood(t-2)",
-      `diff(Vdem_libdem_z, lag = 1)` = "Liberal Democracy (Diff)",
-      `plm::lag(Vdem_libdem_z, 1)` = "Liberal Democracy (t-1)",
-      `diff(lg_imp_mdpgdp, lag = 1)` = "Log GDP per capita(Diff)", 
-      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
-      `diff(cpi_sd, lag = 1)` = "Corruption (Difference)",
-      `plm::lag(cpi_sd, 1)` = "Corruption (t-1)"
-    )
-  ) +
-  geom_vline(xintercept = 0,
-             colour = "grey80",
-             linetype = 2) +
-  theme_minimal() +
-  ggtitle("DV: Liberal Democracy (Vdem)") +
-  xlab("Coefficient Estimate") +
-  theme(
-    axis.title.y = element_blank(),
-    legend.position = "bottom",
-    legend.title = element_blank()
-  )
-
-gridExtra::grid.arrange(plot_pooled,plot_pooled2, ncol = 2)
-```
-
 # Conclusion
@@
 \pagebreak
+
+# (APPENDIX) Appendix {-},
+
+## Models of Effect of Democratic Mood on Institutional Democratization
+
+```{r tableAJPS}
+
+```
+
+## Models of Effects of Democracy on Change in Mood

### 2020-09-29 paper/dcpo_demsupport.Rmd
getting the ns from the point estimations

@@
   df_result <- tidy(result) %>%
-    mutate(std.error = vcovBK_se(result))
+    mutate(std.error = vcovBK_se(result),
+           n = nobs(result))
 })
@@
   tidy(aMod) %>%
-    mutate(std.error = vcovHC_se(aMod))
+    mutate(std.error = vcovHC_se(aMod),
+           n = nobs(aMod))
 })
@@
     tidy %>%
-    mutate(std.error = vcovHC_se(aMod))
+    mutate(std.error = vcovHC_se(aMod),
+           n = nobs(aMod))
 })
@@
 
-The results are presented in Figure \@ref(fig:visualizeAJPS)
+The results are presented in Figure \@ref(fig:visualizeAJPS) (and numerically in the Appendix \@ref(replicateAJPS))
 
@@
 
-## Models of Effect of Democratic Mood on Institutional Democratization
+## Models of Effect of Democratic Mood on Institutional Democratization {#replicateAJPS}
 

### 2020-09-30 paper/dcpo_demsupport.Rmd
finish drafting the result section; correct the CIs in the plot

@@
   rstan, # Bayesian estimation
-  tidyverse, # data wrangling
+  broom, tidyverse, # data wrangling
   dotwhisker, # visualization
@@
   result <- plm(mod, model = "pooling", data = sd.plm)
-  df_result <- tidy(result) %>%
+  df_result <- tidy(result, conf.int = TRUE) %>%
     mutate(std.error = vcovBK_se(result),
@@
 
-plot_AJPS1 <- dwplot(df_plotS, dodge_size = 0.8) +
+plot_AJPS1 <- dwplot(df_plotS, dodge_size = 0.8, by_2sd = FALSE) +
   scale_color_uiowa(name = "", palette = "digitMixed") +
   labs(
-    title = "DV: Institutional Democracy (Vdem)",
+    title = "DV: Institutional Democratization",
     subtitle = "Pooled"
@@
 
-plot_AJPS2 <- dwplot(df_plotS, dodge_size = 0.8) +
+plot_AJPS2 <- dwplot(df_plotS, dodge_size = 0.8, by_2sd = FALSE) +
   scale_color_uiowa(name = "", palette = "digitMixed") +
@@
 
+The results are presented in Figure \@ref(fig:visualizeAJPS) (and numerically in Appendix \@ref(replicateAJPS)).
+In the pooled model (left panel), the aggregated measurement of democratic mood shows a positive effect on the institutional democratization in Claassen's original model, and the effect is statistically significant at the 0.05 level.
+However, when accounting for the uncertainty of the latent variable measurement of the mood, the significance disappears.
+We added one-third more data and applied a more efficient measurement (DCPO), resulting a saliently shrink of the range of measurement uncertainty, but the confidence intervals still cut zero---that is, remaining statistically insignificant.^[The point estimates also alters.
+We attribute it to additional more information and better measuring method by DCPO.]
+Similar phenomenon also happens on the estimates of, for example, the second-time-unit lag of democratization and resouce dependency.
+
+We further examined Claassen's regime specific model [@Claassen2019: Model 2].
+The originally significant contribution of democratic mood in democratic regimes disappears as well, regardless whether more information and better method are applied.
+
 ```{r claassenAPSR}
@@
 df_result_clsAPSR <- map(mods, function(aMod){
-  tidy(aMod) %>%
+  tidy(aMod, conf.int = TRUE) %>%
     mutate(std.error = vcovHC_se(aMod),
@@
     mutate(std.error = vcovHC_se(aMod),
-           n = nobs(aMod))
+           n = nobs(aMod`))
 })
@@
 
-plot_APSR1 <- dwplot(df_plotS, dodge_size = 0.8) +
+plot_APSR1 <- dwplot(df_plotS, dodge_size = 0.8, by_2sd = FALSE) +
   scale_color_uiowa(name = "", palette = "digitMixed") +
@@
 
-plot_APSR2 <- dwplot(df_plotS, dodge_size = 0.8) +
+plot_APSR2 <- dwplot(df_plotS, dodge_size = 0.8, by_2sd = FALSE) +
   scale_color_uiowa(name = "", palette = "digitMixed") +
@@
     subtitle = "w. Corruption"
-  )
-
-legend <- get_legend(plot_AJPS2)
+  ) +
+  theme(legend.position = "bottom")
+
+legend <- get_legend(plot_APSR2)
 
@@
 
-The results are presented in Figure \@ref(fig:visualizeAJPS) (and numerically in the Appendix \@ref(replicateAJPS))
+The importance of accounting for the measurement uncertainty appear more evident when the relevant variable plays as the dependent variable. 
+In Figure \@ref(fig:visualizedAPSR), we examine the thermostatic model of democratic mood [@Claassen2020b]. 
+The estimates without taking uncertainty into account imply that democatic mood decreases along with the progress of democratization. 
+Nevertheless, this effect no longer holds when the measurement uncertainty is involved.
+
+As previous operation, we tested if this alteration is caused by the data scarcity or estimating inefficiency. 
+When more data and better method are applied, the confidence intervals do shrink yet remaining statistically insignificant. 
+We observed the similar changes after adjusting the effect of domestic corruption [@Claassen2020b: 41].
 

### 2020-09-30 paper/dcpo_demsupport.Rmd
finish the appendix tables

@@
 df_tableAJPS <- df_plotS %>% mutate(
-  std.error = ifelse(is.na(std.error), se, std.error)
+  conf = paste0("[", round(conf.low, digits = 2), ", ", round(conf.high, digits = 2), "]"),
+  group = "Pooled"
 ) %>% 
-  select(term, estimate, std.error, model)
+  select(term, estimate, conf, n, model, group) %>% 
+  fill(n, .direction = "up")
 
@@
   )
+
+df_tableAJPS <- df_plotS %>% mutate(
+  conf = paste0("[", round(conf.low, digits = 2), ", ", round(conf.high, digits = 2), "]"),
+  group = "Regime Spec."
+) %>% 
+  select(term, estimate, conf, n, model, group) %>% 
+  fill(n, .direction = "up") %>% 
+  bind_rows(df_tableAJPS) %>% 
+  mutate(estimate = round(estimate, digits = 3))
 
@@
 
+df_tableAPSR <- df_plotS %>% mutate(
+  conf = paste0("[", round(conf.low, digits = 2), ", ", round(conf.high, digits = 2), "]"),
+  group = "Basic"
+) %>% 
+  select(term, estimate, conf, n, model, group) %>% 
+  fill(n, .direction = "up")
+
 plot_APSR1 <- dwplot(df_plotS, dodge_size = 0.8, by_2sd = FALSE) +
@@
   )
+
+df_tableAPSR <- df_plotS %>% mutate(
+  conf = paste0("[", round(conf.low, digits = 2), ", ", round(conf.high, digits = 2), "]"),
+  group = "W. Corruption"
+) %>% 
+  select(term, estimate, conf, n, model, group) %>% 
+  fill(n, .direction = "up") %>% 
+  bind_rows(df_tableAPSR) %>% 
+  mutate(estimate = round(estimate, digits = 3))
 
@@
 ```{r tableAJPS}
-
+df_tableAJPS %>% 
+  mutate(estimate = paste0(estimate, "\n ", conf),
+         group = paste0(group, "\n (n: ", n, ")")) %>% 
+  arrange(group, model) %>% 
+  select(group, model, term, estimate) %>% 
+  group_by(group) %>% 
+  pivot_wider(names_from = model, values_from = estimate) %>% 
+  mutate(term = str_replace_all(term, "\\n", " ")) %>% 
+  arrange(group) %>% 
+  flextable %>% 
+  set_header_labels(group = "Model",
+                    term = "Variable") %>% 
+  merge_v(j = c("group")) %>% 
+  hline(i = 8, border = officer::fp_border()) %>% 
+  autofit() %>% 
+  add_header_lines(values = paste0("Number of Observations: ", unique(df_tableAJPS$n)))
 ```
@@
 ## Models of Effects of Democracy on Change in Mood
+
+```{r table APSR}
+df_tableAPSR %>% 
+  mutate(estimate = paste0(estimate, "\n ", conf),
+         group = paste0(group, "\n (n: ", n, ")")) %>% 
+  arrange(group, model) %>% 
+  select(group, model, term, estimate) %>% 
+  group_by(group) %>% 
+  pivot_wider(names_from = model, values_from = estimate) %>% 
+  mutate(term = str_replace_all(term, "\\n", " ")) %>% 
+  arrange(group) %>% 
+  flextable %>% 
+  set_header_labels(group = "Model",
+                    term = "Variable") %>% 
+  merge_v(j = c("group")) %>% 
+  hline(i = 8, border = officer::fp_border()) %>% 
+  autofit() 
+```

### 2020-10-05 paper/dcpo_demsupport.Rmd
reorganize the structure.

@@
 ---
+# Introduction
+
 One of the classic but disputable questions in comparative politics is the relationship between mass democratic support and countries' level of democracy.
 A long-standing and widely accepted theory is that the level of mass democratic support determines the stability of a democratic system [e.g., @lipset_social_1959; @norris_democratic_2011], but findings from empirical analyses still remain inconclusive [@inglehart_modernization_2005; @fails_changing_2010; @qi_how_2011, see @Claassen2020a for a review in this literature].
-One reason for the mixed results is the measurement of public democratic support.
-Measuring democratic support by using self-report survey data is still the dominant approach.
-However, one essential concern is whether and how we can measure the latent public opinion correctly, especially for comparative public opinion survey data.
-The sparse and incomparable comparative public opinion data has perplexed the study of comparative politics for a long time [@Solt2020a].
+
+One reason for the mixed results is the difficulities in measuring comparative public democratic support.
 Public support for democracy is a latent variable and the incorrect measurement of it may conceal the real relationship between public opinion and democratic institutional development.
+However, the sparsity and incomparability of public opinion data across countries over time have perplexed the study of comparative politics for a long time [@Solt2020a].
 Recently, a few pioneering studies are contributing to the latent public opinion measurement in comparative studies[@Caughey2019,@Claassen2019,@Solt2020a].
+
 A prominent study by @Claassen2020a applied an advanced Bayesian Item Response Model to measure dynamic public democratic support for 135 countries for up to 29 years.
 It found that mass democratic support had a positive impact on democratic change, especially the endurance of democracy.
-@Claassen2020a's study reignites the debate on the relationship between public opinion and democracy.
-To adjudicate/contribute to the ongoing debate, by using a superior measurement, bigger data, and incorporating uncertainty, our study presents a thorough reexamination of the relationship between mass democratic support and democracy survival across counties and over time.
-We use a superior measure, the Dynamic Comparative Public Opinion (DCPO) model developed by@Solt2020a, to estimate democratic support for a larger dataset with 144 countries for up to 33 years between 1988 and 2020.
-In addition to accounting for item response bias across countries and the extent of polarization by generating estimates on bounded scales, the DCPO model has superiority in dealing with both binominal and ordinal survey data across countries over time.
-Both internal and external k-fold validation tests corroborate that the DCPO model yields more accurate results than other latent variable measurements, either of @Claassen2019 Model 5 and @Caughey2019 model.
-The nature of latent variables' unobservability decides that the estimates of latent variables are inherently accompanied with measurement uncertainty. 
-Omitting measurement error distorts both statistical and substantive inference (See Juhl 2019for review in this literature). 
-Since the measurement uncertainty could have consequential (propagated) effects on inferences about the relationship of substantive interests, it is strongly recommended to incorporate the measurement uncertainty in analysis models (Treier and Jackman 2008, Crabtree and Fariss 2015).
-Many scholars have taken the account for measurement error in analyses as a final crucial part in their empirical studies (Schnakenberg and Fariss 2014, Caughey and Warshaw 2018), and recent studies on latent variable measurement emphasized the incorporation of measurement uncertainty when using their measures ( Solis and Waggoner 2020, Gandhi and Sumner 2020).
-However, in the comparative public opinion field, previous efforts on measuring comparative public opinion didn’t account for measurement uncertainty in their analyses.  
-To address the uncertainty (caused by the inherent trail of latent constructs), in addition to employing the DCPO which reduces uncertainty in measurement, we also incorporated uncertainty in our analysis by using random draws from the posterior distributions and following @Rubin1987's rules.
-Surprisingly, our study reveals that there is no significant relationship between public support and democratic change in both the replication analysis of @Claassen2020a model and the DCPO analysis when uncertainty is included.
-Our study reaffirms Fariss 2014, Juhl (2019) and Solt (2020)'s suggestion that given the latent character of variables in political science, scholars should be vigilant in measurement uncertainty. 
-In addition to methodological concerns, our reanalysis echoes recent studies about the public’s behavioral commitment to democracy.  
-It is questionable whether self-report based conventional measures of support for democracy could transfer to behaviorally democratic commitments when the democratic system is in economic or societal crisis.
-Recent studies show that although the public understands and supports democratic principles, their support is elastic, especially in the context of polarization [@graham_democracy_2020].
-Voters sometimes are willing to subordinate democratic norms to their partisan and policy preferences [@nyhan_who_2020] and subsequently support their elected leaders to take anti-democratic measures [@mccoy_democratic_2020].
+The analysis models he used do not accout, though, for measurement uncertainty.
+The latent constructs are inherently accompanied by amount of measurement uncertainty due to the unobservability of variables.
+Left unacknowledged, with a strong assumption that latent variables are measured perfectly, measurement error could distort both statistical and substantive inference [@Crabtree2015,@Juhl2019].
+
+In this paper, we reexamined the relationship between public support for democracy and democratic changes thoroughly, by using a superior measurement, bigger data, and incorporating uncertainty.
+To reduce the uncertainty, we used a superior measurement, the Dynamic Comparative Public Opinion (DCPO) model developed by@Solt2020a, to estimate democratic support for a larger dataset with 144 countries for up to 33 years between 1988 and 2020.
+Surprisingly, our study revealed that the significant relationship between public support and democratic change disappeared when uncertainty was included in the replication analysis of @Claassen2020a modelwith his original data and the DCPO analysis with more data.
+
+The underlying reasons for the uncertainty could be the ineffectiveness of survey questions in capturing public attitude compared to rich indicators for other concept,like gender egalitarianism [Solt, 2021??], the shortage of indicators for public support worldwide, or the gap between self-reported democratic attitude and behaviorally democratic commitments [@graham_democracy_2020,@nyhan_who_2020,@mccoy_democratic_2020].
+There could be some potentially substantive explanations for the disappearing relationship: the elite-driven democratic backsliding (Weingast 1997,Levtsky and Ziblatt 2018), the lack of a consensus on democratic erosion between the public and experts (Carey et al 2018), and the difference between the public support in abstract and public commitments in context (Bartels 2020,Graham and Svolik 2020,McCoy et al 2020).
+
+Although we could not exclude or identify any of them in this study, our reexamination reaffirmed Fariss (2014), Juhl (2019), and Solt (2020)'s suggestion that given the latent character of variables in political science, scholars should be vigilant in measurement uncertainty.
 
@@
 
-<!-- The following text is all cribbed from `fsolt/dcpo_article` and obviously needs heavy revision -->
-
-# More Data
-We collected data on 62 items from 17 survey projects in 159 countries covering years from 1988 to 2020.
-Survey data was extracted automatically through the `DCPO` package for R [@Solt2020a], which is written in the Stan probabilistic programming language [@StanDevTeam2019a; @StanDevTeam2019b].
-The DCPO package also automatically identifies the year in which the survey was conducted, which contributes to the capture of the real relationship between public opinion and the level of democracy.
-Our data consists of 1,465 country-years and 1,861 national surveys, which is a 24.4% and 33.9% increase respectively over 1,178 country-years and 1,390 national surveys used in Claassen's study [-@Claassen2020a; -@Claassen2020b].
+# Model Specification 
+To examine the influence of empirical uncertainty, we conducted a three-step test. 
+The first step we made is to reproduced @Claassen2019.
+Then applying the method he described in the article, we replicated his IRT-based measurement of democratic mood and maintained the entire distribution of the predicted outcome, instead of aggregating to a single point estimate.
+Utilizing the estimated distribution, we involved uncertainty to the analysis of the influence of democratic mood on institutional democracy cross-nationally.
+In the third step, we applied an advanced method and added one-third more data to the analysis to reduce potential effects of measurement biases and data spareness.
+We compared the outcomes of the three steps and showed as below that uncertainty is an critical factor in the studies of mass democratic attitude, which may alter the analytic conclusions. 
+We further showed that accounting for uncertainty is at least equivalently important when the latent-variable estimates plays as the dependent variable in a study by replicating Claassen2020b.
+
+## Incorporating Uncertainty
+Given the measurement uncertainty caused by the inherent trail of latent constructs and the consequential (propagated) effects of measurement uncertainty on inferences about the relationship of substantive interests, it is strongly recommended to incorporate the measurement uncertainty in analysis models (Treier and Jackman 2008, Crabtree and Fariss 2015).
+Many scholars have taken the account for measurement error in analyses as a final crucial part in their empirical studies (Schnakenberg and Fariss 2014, Caughey and Warshaw 2018), and recent studies on latent variable measurement emphasized the incorporation of measurement uncertainty when using their measures ( Solis and Waggoner 2020, Gandhi and Sumner 2020).
+However, in the comparative public opinion field, previous efforts on measuring comparative public opinion didn’t account for measurement uncertainty in their analyses.
+
+In our reexamination, instead of employing the point estimates, we followed the recommendation and the approach of incorporating uncertainty in using latent variables [e.g., @Schnakenberg2014; @Crabtree2015] and other measures, such as the Standardized World Income Inequality Database [@Solt2020].
+Specifically, in our replication of Claassen2020a's analysis models, we incorporated uncertainty by using random draws from the posterior distributions. 
+We generated 1,000 duplicate versions of the analysis dataset, assigned to each a different random draw from the posterior distributions of public democratic support, performed the analyses repeatedly on each of these 1,000 versions of the dataset, and then combined the results following the rules set out in @Rubin1987.
 
@@
 
-# A Better Measure of Democratic Support
-Using the DCPO model in the `DCPO` package, we attained 4,752 estimates for mass support for democracy, drawn from 144 countries with at least 2 country-years observed.
-The DCPO model has methodological superiority in significant ways. 
-First, the DCPO model allows us to treat the data as their original scales, either dichotomous or ordinal, to avoid information missing due to the potential scale change.
+## A Better Measure of Democratic Support and More Data
+To reduce the uncertainty, we applied a more valid measurement, the DCPO model, to a bigger data set.
+The validation tests in @Solt2020a's paper corroborate that the DCPO model yields more accurate results than other latent variable measurements, either of @Claassen2019 Model 5 and @Caughey2019 model.
+The flexibility of the DCPO model in treating the data as their original scales, either dichotomous or ordinal, decreases information missing due to the potential scale change.
 For example, our data consists of 20,885 national responses as the result of measuring public attitude at ordinal scales, which has the potential to give us more nuances about public democratic support.
-Second, to reduce the uncertainty in estimating countries which lie at the extreme ends of the public opinion spectrum[@Linzer2015], the estimates of mean public opinion are bounded and the extent of polarization is included in the DCPO model.
-The capture of the extent of polarization is more meaningful in this era, since the respondents from countries with more polarized opinions are more likely to give negative responses even though these countries may have the similar mean estimates of public opinion.
-It is worth noticing that the small number of extreme opinions in countries may have a louder voice and bigger effects on actual politics. 
+Second, to reduce the uncertainty in estimating countries which lie at the extreme ends of the public opinion spectrum [@Linzer2015], the estimates of mean public opinion are bounded and the extent of polarization is included in the DCPO model.
 Third, to address the differences in item response across countries, caused by factors other than public attitude or preference, a country-specific item bias is modelled as "a country-specific bias in the difficulty of each question" [@Solt2020a, 6].
-This approach allows us to keep information embedded in questions rather than discarding them directly. 
-In sum, the DCPO model has methodological advantages in keeping as much available information as possible, reducing uncertainty by bounding scales and capturing the extent of polarization. 
-The validation tests in @Solt2020a's paper corroborate that DCPO not only features the smallest mean absolute error (MAE) and largest improvement over the country-means MAE but also provides a more stable and efficient prediction on out-of-sample data than either the @Claassen2019's Model 5 or the @Caughey2019's model.
-Following @Solt2020a's approach, our validation test employs k-fold validation with 10 folds, which reduces the misrepresentation of the model due to the chosen data from single cross-validation (See details of the validation test in Appendix).
+In short, the DCPO model has methodological advantages in keeping as much available information as possible, reducing uncertainty by bounding scales and capturing the extent of polarization.
+
+In addition to applying the advanced measurement, we also collected as much available data as possible.
+We collected data on 62 items from 17 survey projects in 159 countries covering years from 1988 to 2020.
+Survey data was extracted automatically through the `DCPO` package for R [@Solt2020a].
+The DCPO package also automatically identifies the year in which the survey was conducted, which contributes to the capture of the real relationship between public opinion and the level of democracy.
+Our data consists of 1,465 country-years and 1,861 national surveys, which is a 24.4% and 33.9% increase respectively over 1,178 country-years and 1,390 national surveys used in Claassen's studies [-@Claassen2020a; -@Claassen2020b].
+Finally, using the DCPO model in the `DCPO` package, we attained 4,752 estimates for mass support for democracy, drawn from 144 countries with at least 2 country-years observed.
 
@@
 ```
-
-# Incorporating Uncertainty
-The latent constructs are inherently accompanied by amount of measurement uncertainty due to the unobservability of variables.
-The measurement is more far away from perfection when concepts are complex. 
-With a strong assumption that latent variables are measured perfectly, the omittance of measurement error might obscure the true relationship between theoretical concepts and invalidates findings.
-Therefore, incorporating uncertainty is substantively necessary for “comparing relationship between complex theoretical concepts across political contexts and over time"[@Crabtree2015,p2]. 
-In our reexamination, instead of employing the point estimates, we relax the implausible assumption of perfect measurement of latent variables.
-We followed the recommendation and the approach of incorporating uncertainty in using latent variables [e.g., @Schnakenberg2014; @Crabtree2015] and other measures, such as the Standardized World Income Inequality Database [@Solt2020].
-Specifically, we generated 1,000 duplicate versions of the analysis dataset, assigned to each a different random draw from the posterior distributions of public democratic support, performed the analyses repeatedly on each of these 1,000 versions of the dataset, and then combined the results following the rules set out in @Rubin1987.
-This process can be achieved by using the `purrr` package [@Henry2019] and adding only a few lines of code.
 
@@
 
-<!-- I may suggest to move this paragraph to the beginning of the previous section or a separate section of research design -->
-
-**To examine the influence of empirical uncertainty, we conducted a three-step test. 
-We first reproduced @Claassen2019.
-Then applying the method he described in the article, we replicated his IRT-based measurement of democratic mood and maintain the entire distribution of the predicted outcome, instead of aggregating to a single point estimate.
-Utilizing the estimated distribution, we involved uncertainty to the analysis of the influence of democratic mood on institutional democracy cross-nationally.
-In the third step, we applied an advanced method and added one-third more data to the analysis to reduce potential effects of measurement biases and data spareness.
-We compared the outcomes of the three steps and showed as below that uncertainty is an critical factor in the studies of mass democratic attitude, which may alter the analytic conclusions. 
-We further show that accounting for uncertainty is at least equivalently important when the latent-variable estimates plays as the dependent variable in a study by replicating Claassen2020b. **
+The results are presented in Figure \@ref(fig:visualizeAJPS) (and numerically in Appendix \@ref(replicateAJPS)).
+In the pooled model (left panel), the aggregated measurement of democratic mood shows a positive effect on the institutional democratization in Claassen's original model, and the effect is statistically significant at the 0.05 level.
 
@@
 
-The results are presented in Figure \@ref(fig:visualizeAJPS) (and numerically in Appendix \@ref(replicateAJPS)).
-In the pooled model (left panel), the aggregated measurement of democratic mood shows a positive effect on the institutional democratization in Claassen's original model, and the effect is statistically significant at the 0.05 level.
 However, when accounting for the uncertainty of the latent variable measurement of the mood, the significance disappears.
@@
 # Discussion
-
 In short, the main empirical findings about the estimated effect of public democratic support on democracy or vice versa are not replicable when measurement uncertainty is accounted, even using better measurement and more data.
+
 There are potential causes for the null results.
@@
 Methodologically, given the nature trail of latent variables and specific characters of comparative public opinion, performing analyses based on the strong assumption that comparative public attitudes are perfectly measured might exaggerate scholars' certainty methodologically and obscure a proper substantive evaluation of theoretical claims.
-In addition to the potentially methodological cause (the measurement errors), the measurement errors, there are some potentially substantive causes for the disappearing relationship.
+
+In addition to the potentially methodological cause (the measurement errors), there are some potentially substantive causes for the disappearing relationship.
 First, democratic backsliding might be mainly caused by elites.
@@
 After the Cold War, many democracies backslid and were imperiled worldwide because elected leaders lack commitment to democratic norms when the public even did not notice that (Bermeo 2016; Levtsky and Ziblatt 2018, Waldner and Lust 2018).
+
 Second, there has been a gulf between public perception and elites’ perception on important democratic principles (McClosky, 1959).
@@
 Given that the measures for democratic development are from experts, there could be a gap between public perception on democracy and the measures of the levels of democracy.
+
 Third, since there is a difference between the public support for democracy in the abstract and under specific propositions (Bartels 2020), recent studies questioned whether conventional measures of public support for democracy could capture public realistic commitment to democracy.
-By using survey experiments, Graham and Svolik (2020) pointed out a " fundamental blind spot" in traditional measures of public democratic support: the questions regarding the support for an abstract democracy cannot capture public willingness and behavioral commitment to democratic principles when voters have to choose between democratic norms and their partisan identification or policy preference.
+By using survey experiments, Graham and Svolik (2020) pointed out a "fundamental blind spot" in traditional measures of public democratic support: the questions regarding the support for an abstract democracy cannot capture public willingness and behavioral commitment to democratic principles when voters have to choose between democratic norms and their partisan identification or policy preference.
 It turned out that voters subordinated democratic norms to their partisan preference by not electorally penalizing their candidates who endorse measures that violate norms.
-Furthermore, McCoy et al (2020) found that rather than only tolerate anti-democratic policies, voters support/encourage these policies when their co-partisans are in power. 
-This increasing substantial literature emphasizes the eroding effect of polarization on democracy worldwide (McCoy et al 2019). 
-Regarding the polarization, the sigma in our measurement model captures the polarization.
-The figure xx shows the varying polarization in public support for democracy across countries. 
-Given the uncertainty in measures of public support, it is unsurprising that we did not find the statistically significant effect of polarization.
-However, the estimated effect of the interaction term between public support and polarization was negative, which referred to the attenuation effect of polarization on the impact of public support on democracy.
-Specifically, the big polarization in the U.S. implies that political polarization exists not only in partisan politics but also in more general democracy values.
-Future studies could take advantage of the DCPO’s polarization measurement in their analysis, given the necessity to analyze traditional relationships under the environment of polarization.
+Furthermore, McCoy et al (2020) found that rather than only tolerate anti-democratic policies, voters support/encourage democratic norm-eroding policies when their co-partisans are in power.
 
 # Conclusion
-In this reexamination, we show how the measurement uncertainty of public attitude causes inferential errors regardless of public attitude as an independent variable or dependent variable, even using more data and a sophisticated DCPO model which reduces the noises in measures for extreme countries.
-Our study has important implications in several aspects. 
-In terms of data, although democracy and democratization are the primary theme in comparative politics, the indicators of public democratic attitude are limited compared to other concepts, like gender egalitarian (Solt 2020?).
-More data and more indicators could serve to reduce the uncertainty in measuring public democratic attitude.
-Employing a more reliable statistical measurement model could not only make public opinion across countries comparable and but also reduce the uncertainty in the measurement stage. 
-Given the inherent uncertainty accompanying latent public opinion, and its propagated effects in analysis, we especially recommend that incorporating measurement uncertainty in analysis models is a safer way to infer the relationship between public opinion and other substantive interest especially for comparative politics, in which the measurement uncertainty of public opinion is further exacerbated by the sparse and incomparability of indicators.
-Substantively, the association between public democratic attitude and democratic development might be not robust especially in the era of political polarization within countries. 
-A strong estimated effect of public attitude might endure the propagated effect from the measurement uncertainty. 
-However, if the effect itself is not robust enough, any theoretical inference could be easily wiped out due to the imperfect measurement of public opinion. 
-It suggests that the relationship between public opinion and institution or policy making should be considered in the environment of polarization where people might subordinate their behaviorally commitment to democracy to their partisan loyalty or policy preference.
+In this note, we reexamined the findings from Claassens'(2019, 2020) that public support helps the survival of democarcy and democratic development has a thermostatic effect on public support for democracy.
+We demonstrated that the relationships between public support and democratic development depends on the incorporation of uncertainty in the measurement of latent variables.
+Even using more data and a sophisticated DCPO model, the measurement uncertainty made the relationships irreplicable irrespective of whether public support is an independent variable or dependent variable.
+
+There could be several potential reasons for this no relationship: the self-report survey data that could not capture the public attitude, the scarce data on the complex concept of democratic support,  and the gap between the public attitude and public commitment.
+Any one of these could lead to this no relationship.
+
+Although we could not exclude any one of these, a basic lesson from this reexamination is simple: given the inherent uncertainty accompanying latent public opinion, and its propagated effects in analysis, incorporating measurement uncertainty in analysis models is a safer way to infer the relationship between public opinion and other substantive interest especially for comparative politics, in which the measurement uncertainty of public opinion is further exacerbated by the sparse and incomparability of indicators.
 

### 2020-10-13 paper/dcpo_demsupport.Rmd
citation update

@@
 The underlying reasons for the uncertainty could be the ineffectiveness of survey questions in capturing public attitude compared to rich indicators for other concept,like gender egalitarianism [Solt, 2021??], the shortage of indicators for public support worldwide, or the gap between self-reported democratic attitude and behaviorally democratic commitments [@graham_democracy_2020,@nyhan_who_2020,@mccoy_democratic_2020].
-There could be some potentially substantive explanations for the disappearing relationship: the elite-driven democratic backsliding (Weingast 1997,Levtsky and Ziblatt 2018), the lack of a consensus on democratic erosion between the public and experts (Carey et al 2018), and the difference between the public support in abstract and public commitments in context (Bartels 2020,Graham and Svolik 2020,McCoy et al 2020).
-
-Although we could not exclude or identify any of them in this study, our reexamination reaffirmed Fariss (2014), Juhl (2019), and Solt (2020)'s suggestion that given the latent character of variables in political science, scholars should be vigilant in measurement uncertainty.
+There could be some potentially substantive explanations for the disappearing relationship: the elite-driven democratic backsliding [@weingast_political_1997,@levitsky_how_2018], the lack of a consensus on democratic erosion between the public and experts [@carey_searching_2019], and the difference between the public support in abstract and public commitments in context [@bartels_ethnic_2020,@graham_democracy_2020,@mccoy_democratic_2020].
+
+Although we could not exclude or identify any of them in this study, our reexamination reaffirmed @fariss_respect_2014, @juhl_measurement_2019, and Solt (2020)'s suggestion that given the latent character of variables in political science, scholars should be vigilant in measurement uncertainty.
 
@@
 ## Incorporating Uncertainty
-Given the measurement uncertainty caused by the inherent trail of latent constructs and the consequential (propagated) effects of measurement uncertainty on inferences about the relationship of substantive interests, it is strongly recommended to incorporate the measurement uncertainty in analysis models (Treier and Jackman 2008, Crabtree and Fariss 2015).
-Many scholars have taken the account for measurement error in analyses as a final crucial part in their empirical studies (Schnakenberg and Fariss 2014, Caughey and Warshaw 2018), and recent studies on latent variable measurement emphasized the incorporation of measurement uncertainty when using their measures ( Solis and Waggoner 2020, Gandhi and Sumner 2020).
+Given the measurement uncertainty caused by the inherent trail of latent constructs and the consequential (propagated) effects of measurement uncertainty on inferences about the relationship of substantive interests, it is strongly recommended to incorporate the measurement uncertainty in analysis models [@treier_democracy_2008,@Crabtree2015].
+Many scholars have taken the account for measurement error in analyses as a final crucial part in their empirical studies [@Schnakenberg2014,@caughey_policy_2018], and recent studies on latent variable measurement emphasized the incorporation of measurement uncertainty when using their measures [@solis_measuring_2020,@gandhi_measuring_2020].
 However, in the comparative public opinion field, previous efforts on measuring comparative public opinion didn’t account for measurement uncertainty in their analyses.
@@
 First, democratic backsliding might be mainly caused by elites.
-Elites are thought to play a critical role in preserving democratic stability by respecting the limits on their behaviors (Weingast 1997).
-After the Cold War, many democracies backslid and were imperiled worldwide because elected leaders lack commitment to democratic norms when the public even did not notice that (Bermeo 2016; Levtsky and Ziblatt 2018, Waldner and Lust 2018).
-
-Second, there has been a gulf between public perception and elites’ perception on important democratic principles (McClosky, 1959).
-A recent study showed that polarized public cannot get a consensus on democratic erosion which experts preserved (Carey et al 2018).
+Elites are thought to play a critical role in preserving democratic stability by respecting the limits on their behaviors [@weingast_political_1997].
+After the Cold War, many democracies backslid and were imperiled worldwide because elected leaders lack commitment to democratic norms when the public even did not notice that [@bermeo_democratic_2016,@levitsky_how_2018, @waldner_unwelcome_2018].
+
+Second, there has been a gulf between public perception and elites’ perception on important democratic principles [@mcclosky_consensus_1964].
+A recent study showed that polarized public cannot get a consensus on democratic erosion which experts preserved [@carey_searching_2019].
 Given that the measures for democratic development are from experts, there could be a gap between public perception on democracy and the measures of the levels of democracy.
 
-Third, since there is a difference between the public support for democracy in the abstract and under specific propositions (Bartels 2020), recent studies questioned whether conventional measures of public support for democracy could capture public realistic commitment to democracy.
-By using survey experiments, Graham and Svolik (2020) pointed out a "fundamental blind spot" in traditional measures of public democratic support: the questions regarding the support for an abstract democracy cannot capture public willingness and behavioral commitment to democratic principles when voters have to choose between democratic norms and their partisan identification or policy preference.
+Third, since there is a difference between the public support for democracy in the abstract and under specific propositions [@bartels_ethnic_2020], recent studies questioned whether conventional measures of public support for democracy could capture public realistic commitment to democracy.
+By using survey experiments, @graham_democracy_2020 pointed out a "fundamental blind spot" in traditional measures of public democratic support: the questions regarding the support for an abstract democracy cannot capture public willingness and behavioral commitment to democratic principles when voters have to choose between democratic norms and their partisan identification or policy preference.
 It turned out that voters subordinated democratic norms to their partisan preference by not electorally penalizing their candidates who endorse measures that violate norms.
-Furthermore, McCoy et al (2020) found that rather than only tolerate anti-democratic policies, voters support/encourage democratic norm-eroding policies when their co-partisans are in power.
+Furthermore, @Carey2020 found that rather than only tolerate anti-democratic policies, voters support/encourage democratic norm-eroding policies when their co-partisans are in power.
 
 # Conclusion
-In this note, we reexamined the findings from Claassens'(2019, 2020) that public support helps the survival of democarcy and democratic development has a thermostatic effect on public support for democracy.
+In this note, we reexamined the findings from Claassens'[-@Claassen2019,-@Claassen2020b] paper that public support helps the survival of democarcy and democratic development has a thermostatic effect on public support for democracy.
 We demonstrated that the relationships between public support and democratic development depends on the incorporation of uncertainty in the measurement of latent variables.

### 2020-10-26 paper/dcpo_demsupport.Rmd
fix citations; clean up plots (use plotmath for varnames, reverse legend); fix cross-references; dynamic results for country-year counts

@@
 One of the classic but disputable questions in comparative politics is the relationship between mass democratic support and countries' level of democracy.
-A long-standing and widely accepted theory is that the level of mass democratic support determines the stability of a democratic system [e.g., @lipset_social_1959; @norris_democratic_2011], but findings from empirical analyses still remain inconclusive [@inglehart_modernization_2005; @fails_changing_2010; @qi_how_2011, see @Claassen2020a for a review in this literature].
-
-One reason for the mixed results is the difficulities in measuring comparative public democratic support.
+A long-standing and widely accepted theory is that the level of mass democratic support determines the stability of a democratic system [e.g., @lipset_social_1959; @norris_democratic_2011], but findings from empirical analyses still remain inconclusive [@inglehart_modernization_2005; @fails_changing_2010; @qi_how_2011; for a review in this literature, see @Claassen2020a].
+
+One reason for the mixed results is the difficulties in measuring comparative public democratic support.
 Public support for democracy is a latent variable and the incorrect measurement of it may conceal the real relationship between public opinion and democratic institutional development.
 However, the sparsity and incomparability of public opinion data across countries over time have perplexed the study of comparative politics for a long time [@Solt2020a].
-Recently, a few pioneering studies are contributing to the latent public opinion measurement in comparative studies[@Caughey2019,@Claassen2019,@Solt2020a].
+Recently, a few pioneering studies are contributing to the latent public opinion measurement in comparative studies [@Caughey2019; @Claassen2019; @Solt2020a].
 
@@
 It found that mass democratic support had a positive impact on democratic change, especially the endurance of democracy.
-The analysis models he used do not accout, though, for measurement uncertainty.
+The analysis models he used do not account, though, for measurement uncertainty.
 The latent constructs are inherently accompanied by amount of measurement uncertainty due to the unobservability of variables.
-Left unacknowledged, with a strong assumption that latent variables are measured perfectly, measurement error could distort both statistical and substantive inference [@Crabtree2015,@Juhl2019].
+Left unacknowledged, with a strong assumption that latent variables are measured perfectly, measurement error could distort both statistical and substantive inference [@Crabtree2015; @juhl_measurement_2019].
 
 In this paper, we reexamined the relationship between public support for democracy and democratic changes thoroughly, by using a superior measurement, bigger data, and incorporating uncertainty.
-To reduce the uncertainty, we used a superior measurement, the Dynamic Comparative Public Opinion (DCPO) model developed by@Solt2020a, to estimate democratic support for a larger dataset with 144 countries for up to 33 years between 1988 and 2020.
-Surprisingly, our study revealed that the significant relationship between public support and democratic change disappeared when uncertainty was included in the replication analysis of @Claassen2020a modelwith his original data and the DCPO analysis with more data.
-
-The underlying reasons for the uncertainty could be the ineffectiveness of survey questions in capturing public attitude compared to rich indicators for other concept,like gender egalitarianism [Solt, 2021??], the shortage of indicators for public support worldwide, or the gap between self-reported democratic attitude and behaviorally democratic commitments [@graham_democracy_2020,@nyhan_who_2020,@mccoy_democratic_2020].
-There could be some potentially substantive explanations for the disappearing relationship: the elite-driven democratic backsliding [@weingast_political_1997,@levitsky_how_2018], the lack of a consensus on democratic erosion between the public and experts [@carey_searching_2019], and the difference between the public support in abstract and public commitments in context [@bartels_ethnic_2020,@graham_democracy_2020,@mccoy_democratic_2020].
-
-Although we could not exclude or identify any of them in this study, our reexamination reaffirmed @fariss_respect_2014, @juhl_measurement_2019, and Solt (2020)'s suggestion that given the latent character of variables in political science, scholars should be vigilant in measurement uncertainty.
+To reduce the uncertainty, we used a superior measurement, the Dynamic Comparative Public Opinion (DCPO) model developed by @Solt2020a, to estimate democratic support for a larger dataset with 144 countries for up to 33 years between 1988 and 2020.
+Surprisingly, our study revealed that the significant relationship between public support and democratic change disappeared when uncertainty was included in the replication analysis of @Claassen2020a model with his original data and the DCPO analysis with more data.
+
+The underlying reasons for the uncertainty could be the ineffectiveness of survey questions in capturing public attitude compared to rich indicators for other concept, like gender egalitarianism [Solt, 2021??], the shortage of indicators for public support worldwide, or the gap between self-reported democratic attitude and behaviorally democratic commitments [@graham_democracy_2020; @Carey2020; @McCoy2020].
+There could be some potentially substantive explanations for the disappearing relationship: the elite-driven democratic backsliding [@weingast_political_1997; @levitsky_how_2018], the lack of a consensus on democratic erosion between the public and experts [@carey_searching_2019], and the difference between the public support in abstract and public commitments in context [@bartels_ethnic_2020; @graham_democracy_2020; @McCoy2020].
+
+Although we could not exclude or identify any of them in this study, our reexamination reaffirmed @fariss_respect_2014, @juhl_measurement_2019, and Solt's [-@Solt2020a] suggestion that given the latent character of variables in political science, scholars should be vigilant in measurement uncertainty.
 
@@
   rstan, # Bayesian estimation
-  broom, tidyverse, # data wrangling
-  dotwhisker, # visualization
+  broom, tidyverse, janitor, # data wrangling
+  dotwhisker # visualization
 )
@@
 theme_set(theme_minimal())
-source("../R/uiowa_palette.R")
+source(here::here("R", "uiowa_palette.R"))
 ```
@@
 To examine the influence of empirical uncertainty, we conducted a three-step test. 
-The first step we made is to reproduced @Claassen2019.
+The first step we made is to reproduce @Claassen2020a.
 Then applying the method he described in the article, we replicated his IRT-based measurement of democratic mood and maintained the entire distribution of the predicted outcome, instead of aggregating to a single point estimate.
@@
 We compared the outcomes of the three steps and showed as below that uncertainty is an critical factor in the studies of mass democratic attitude, which may alter the analytic conclusions. 
-We further showed that accounting for uncertainty is at least equivalently important when the latent-variable estimates plays as the dependent variable in a study by replicating Claassen2020b.
+We further showed that accounting for uncertainty is at least equivalently important when the latent-variable estimates plays as the dependent variable in a study by replicating @Claassen2020b.
 
 ## Incorporating Uncertainty
-Given the measurement uncertainty caused by the inherent trail of latent constructs and the consequential (propagated) effects of measurement uncertainty on inferences about the relationship of substantive interests, it is strongly recommended to incorporate the measurement uncertainty in analysis models [@treier_democracy_2008,@Crabtree2015].
-Many scholars have taken the account for measurement error in analyses as a final crucial part in their empirical studies [@Schnakenberg2014,@caughey_policy_2018], and recent studies on latent variable measurement emphasized the incorporation of measurement uncertainty when using their measures [@solis_measuring_2020,@gandhi_measuring_2020].
+Given the measurement uncertainty caused by the inherent trail of latent constructs and the consequential (propagated) effects of measurement uncertainty on inferences about the relationship of substantive interests, it is strongly recommended to incorporate the measurement uncertainty in analysis models [@treier_democracy_2008; @Crabtree2015].
+Many scholars have taken the account for measurement error in analyses as a final crucial part in their empirical studies [@Schnakenberg2014; @caughey_policy_2018], and recent studies on latent variable measurement emphasized the incorporation of measurement uncertainty when using their measures [@solis_measuring_2020; @gandhi_measuring_2020].
 However, in the comparative public opinion field, previous efforts on measuring comparative public opinion didn’t account for measurement uncertainty in their analyses.
@@
 In our reexamination, instead of employing the point estimates, we followed the recommendation and the approach of incorporating uncertainty in using latent variables [e.g., @Schnakenberg2014; @Crabtree2015] and other measures, such as the Standardized World Income Inequality Database [@Solt2020].
-Specifically, in our replication of Claassen2020a's analysis models, we incorporated uncertainty by using random draws from the posterior distributions. 
+Specifically, in our replication of Claassen's [-@Claassen2020a] analysis models, we incorporated uncertainty by using random draws from the posterior distributions. 
 We generated 1,000 duplicate versions of the analysis dataset, assigned to each a different random draw from the posterior distributions of public democratic support, performed the analyses repeatedly on each of these 1,000 versions of the dataset, and then combined the results following the rules set out in @Rubin1987.
 
-```{r dcpo_input_raw, eval = FALSE}
-dcpo_input_raw <- DCPOtools::dcpo_setup(vars = read_csv("data-raw/mood_dem.csv",
+```{r dcpo_input_raw}
+dcpo_input_raw <- DCPOtools::dcpo_setup(vars = read_csv(here::here("data-raw", "mood_dem.csv"),
                                                           col_types = "cccccc"),
@@
 
-```{r dcpo_input, eval = FALSE}
-dcpo_input_raw1 <- read_csv("data/dcpo_input_raw.csv", col_types = "cdcddcd") %>% 
+```{r dcpo_input, eval=TRUE}
+dcpo_input_raw1 <- read_csv(here::here("data", "dcpo_input_raw.csv"), col_types = "cdcddcd") %>% 
   filter(!(str_detect(survey, "army_wvs") & # WVS obs identified as problematic by Claassen 
@@
 
-```{r compare_n, eval = FALSE}
-if (!file.exists("data/supdem raw survey marginals.tab")) {
+```{r compare_n, eval=TRUE}
+if (!file.exists(here::here("data", "supdem raw survey marginals.tab"))) {
   dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>% 
@@
 
-supdem <- read_csv("data/supdem raw survey marginals.tab",
+supdem <- read_csv(here::here("data", "supdem raw survey marginals.tab"),
                    col_types = "cdcddcdc") %>% 
   janitor::clean_names() %>% 
-  with_min_yrs(2)
+  DCPOtools::with_min_yrs(2)
 
@@
 Third, to address the differences in item response across countries, caused by factors other than public attitude or preference, a country-specific item bias is modelled as "a country-specific bias in the difficulty of each question" [@Solt2020a, 6].
-In short, the DCPO model has methodological advantages in keeping as much available information as possible, reducing uncertainty by bounding scales and capturing the extent of polarization.
+In short, the DCPO model has methodological advantages in keeping as much available information as possible, reducing uncertainty by bounding scales, and in capturing the extent of polarization in the public.
 
@@
 We collected data on 62 items from 17 survey projects in 159 countries covering years from 1988 to 2020.
-Survey data was extracted automatically through the `DCPO` package for R [@Solt2020a].
+Survey data was extracted automatically through the `DCPO` package for R [@Solt2020b].
 The DCPO package also automatically identifies the year in which the survey was conducted, which contributes to the capture of the real relationship between public opinion and the level of democracy.
-Our data consists of 1,465 country-years and 1,861 national surveys, which is a 24.4% and 33.9% increase respectively over 1,178 country-years and 1,390 national surveys used in Claassen's studies [-@Claassen2020a; -@Claassen2020b].
+Our data consists of `r dcpo_input_ncy` country-years and 1,861 national surveys, which is a `r increase_cy`% and 33.9% increase respectively over `r supdem_ncy` country-years and 1,390 national surveys used in Claassen's studies [-@Claassen2020a; -@Claassen2020b].
 Finally, using the DCPO model in the `DCPO` package, we attained 4,752 estimates for mass support for democracy, drawn from 144 countries with at least 2 country-years observed.
 
-```{r dcpo, eval=FALSE}
+```{r dcpo}
 iter <- 3000
@@
 
-The results are presented in Figure \@ref(fig:visualizeAJPS) (and numerically in Appendix \@ref(replicateAJPS)).
+The results are presented in Figure&nbsp;\ref{fig:visualizeAJPS} (and numerically in Appendix Table&nbsp;[A1](#AJPSreplication)).
 In the pooled model (left panel), the aggregated measurement of democratic mood shows a positive effect on the institutional democratization in Claassen's original model, and the effect is statistically significant at the 0.05 level.
@@
 
-```{r visualizeAJPS, fig.cap= "The Effect of Democratic Mood on Institutional Democratization", eval = TRUE}
+```{r visualizeAJPS, fig.cap= "\\label{fig:visualizeAJPS}The Effect of Democratic Support on Democratic Institutions", eval = TRUE, fig.width=7.5, fig.height=5}
 
@@
 df_plot <- df_result_cls[[1]] %>% 
-  mutate(model = "Claassen 2019")
+  mutate(model = "Claassen 2020a")
 
 df_plot <- df_result_clsUncertain[[1]] %>% 
-  mutate(model = "Claassen w. Uncertainty") %>%  
+  mutate(model = "Claassen w/ Uncertainty") %>%  
   bind_rows(df_plot)
@@
         "Democracy\n (t-2)",
-      "Democratic\n Mood\n (t-1)",
-      "Log GDP\n per capita\n (t−1)",
-      "GDP per\n capita Growth\n (t−1)",
-      "Regional\n Democracy\n (t−1)",
+      "Support\n (t-1)",
+      "Log GDP\n per capita\n (t-1)",
+      "GDP per\n capita growth\n (t-1)",
+      "Regional\n democracy\n (t-1)",
       "Percent\n Muslim\n (t-1)",
-      "Resource\n Dependence\n (t−1)"),
-    time = 3)
-  )
+      "Resource\n dependence\n (t-1)"),
+    time = 3))
+
+terms <- factor(rev(c("Democracy[t-1]",
+        "Democracy[t-2]",
+      "Support[t-1]",
+      "Log~GDP~per~capita[t-1]",
+      "GDP~per~capita~growth[t-1]",
+      "Regional~democracy[t-1]",
+      "Percent~Muslim[t-1]",
+      "Resource~dependence[t-1]")), levels =
+      rev(c("Democracy[t-1]",
+        "Democracy[t-2]",
+      "Support[t-1]",
+      "Log~GDP~per~capita[t-1]",
+      "GDP~per~capita~growth[t-1]",
+      "Regional~democracy[t-1]",
+      "Percent~Muslim[t-1]",
+      "Resource~dependence[t-1]")))
 
@@
 plot_AJPS1 <- dwplot(df_plotS, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_color_uiowa(name = "", palette = "digitMixed") +
+  scale_y_discrete(labels = parse(text = levels(terms))) +
+  # scale_color_uiowa(name = "", palette = "digitMixed") +
+  scale_color_grey(start = 0.4, end = 0.8) +
   labs(
@@
 # the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
+# The trick is  to use guide = guide_legend(reverse = TRUE) within scale_color_*(); see below in plotAJPS2. --FS
 
 df_plot <- df_result_cls[[2]] %>% 
-  mutate(model = "Claassen 2019")
+  mutate(model = "Claassen 2020a")
 
 df_plot <- df_result_clsUncertain[[2]] %>% 
-  mutate(model = "Claassen w. Uncertainty") %>%  
+  mutate(model = "Claassen w/ Uncertainty") %>%  
   bind_rows(df_plot)
@@
         "Democracy\n (t-2)",
-      "Democratic\n Demo Only\n (t-1)",
-      "Democratic\n Auto Only\n (t-1)",
-      "Log GDP\n per capita\n (t−1)",
-      "GDP per\n capita Growth\n (t−1)",
-      "Regional\n Democracy\n (t−1)",
+      "Support\n demo only\n (t-1)",
+      "Support\n auto only\n (t-1)",
+      "Log GDP\n per capita\n (t-1)",
+      "GDP per\n capita growth\n (t-1)",
+      "Regional\n democracy\n (t-1)",
       "Percent\n Muslim\n (t-1)",
-      "Resource\n Dependence\n (t−1)"),
+      "Resource\n dependence\n (t-1)"),
     time = 3)
   )
+
+terms2 <- factor(rev(c("Democracy[t-1]",
+                       "Democracy[t-2]",
+                       "Support[t-1] (democracies~only)",
+                       "Support[t-1] (autocracies~only)",
+                       "Log~GDP~per~capita[t-1]",
+                       "GDP~per~capita~growth[t-1]",
+                       "Regional~democracy[t-1]",
+                       "Percent~Muslim[t-1]",
+                       "Resource~dependence[t-1]")), levels =
+                   rev(c("Democracy[t-1]",
+                         "Democracy[t-2]",
+                         "Support[t-1] (democracies~only)",
+                         "Support[t-1] (autocracies~only)",
+                         "Log~GDP~per~capita[t-1]",
+                         "GDP~per~capita~growth[t-1]",
+                         "Regional~democracy[t-1]",
+                         "Percent~Muslim[t-1]",
+                         "Resource~dependence[t-1]")))
 
@@
 plot_AJPS2 <- dwplot(df_plotS, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_color_uiowa(name = "", palette = "digitMixed") +
+    scale_y_discrete(labels = parse(text = levels(terms2))) +
+  # scale_color_uiowa(name = "", palette = "digitMixed") +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
   labs(
@@
   ) +
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom", 
+        legend.title = element_blank())
 
@@
       `plm::lag(SupDem_trim, 1)` = "Democratic Mood(t-1)",
-      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
-      `plm::lag(lnGDP_imp, 1)` = "Log GDP per capita(t−1)",
-      `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
-      `plm::lag(GDP_imp_grth, 1)` = "GDP per capita Growth(t−1)",
-      `plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
-      `plm::lag(Libdem_regUN, 1)` = "Regional democracy(t−1)",
+      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t-1)",
+      `plm::lag(lnGDP_imp, 1)` = "Log GDP per capita(t-1)",
+      `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t-1)",
+      `plm::lag(GDP_imp_grth, 1)` = "GDP per capita Growth(t-1)",
+      `plm::lag(Region_libdem, 1)` = "Regional democracy(t-1)",
+      `plm::lag(Libdem_regUN, 1)` = "Regional democracy(t-1)",
       `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
       `plm::lag(Pr_Muslim, 1)` = "Percent Muslim (t-1)",
-      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)",
-      `plm::lag(Res_cp_WDI_di, 1)` = "Resource Dependence(t−1)"
+      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t-1)",
+      `plm::lag(Res_cp_WDI_di, 1)` = "Resource Dependence(t-1)"
     )
@@
       `plm::lag(theta_aut, 1)` = "Mood Autocracy(t-1)",
-      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
-      `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
-      `plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
+      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t-1)",
+      `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t-1)",
+      `plm::lag(Region_libdem, 1)` = "Regional democracy(t-1)",
       `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
-      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)"
+      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t-1)"
     )
@@
 
-We further examined Claassen's regime specific model [@Claassen2019: Model 2].
+We further examined Claassen's regime specific model [@Claassen2020a: Model 2].
 The originally significant contribution of democratic mood in democratic regimes disappears as well, regardless whether more information and better method are applied.
@@
 
-```{r visualizedAPSR, fig.cap= "Effects of Democracy on Change in Mood", eval = TRUE}
+```{r visualizedAPSR, fig.cap= "\\label{fig:visualizedAPSR} Effects of Democracy on Change in Mood", eval = TRUE, fig.width=7, fig.height=5}
 
@@
 df_plot <- df_result_clsAPSR[[1]] %>% 
-  mutate(model = "Claassen 2020")
+  mutate(model = "Claassen 2020b")
 
 df_plot <- df_result_clsUncertainAPSR[[1]] %>% 
-  mutate(model = "Claassen w. Uncertainty") %>%  
+  mutate(model = "Claassen w/ Uncertainty") %>%  
   bind_rows(df_plot)
@@
       "Log GDP\n per capita\n (Difference)",
-      "Log GDP\n (t−1)"),
+      "Log GDP\n (t-1)"),
     time = 3)
   )
+
+terms <- factor(rev(c("Support[t-1]",
+                      "Support[t-2]",
+                      "Delta~Liberal~democracy",
+                      "Liberal~democracy[t-1]",
+                      "Delta~Log~GDP~per~capita",
+                      "Log~GDP[t-1]")),
+                levels = rev(c("Support[t-1]",
+                               "Support[t-2]",
+                               "Delta~Liberal~democracy",
+                               "Liberal~democracy[t-1]",
+                               "Delta~Log~GDP~per~capita",
+                               "Log~GDP[t-1]")))
 
@@
 plot_APSR1 <- dwplot(df_plotS, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_color_uiowa(name = "", palette = "digitMixed") +
+  scale_y_discrete(labels = parse(text = levels(terms))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  # scale_color_uiowa(name = "", palette = "digitMixed") +
   labs(
@@
 df_plot <- df_result_clsUncertainAPSR[[2]] %>% 
-  mutate(model = "Claassen w. Uncertainty") %>%  
+  mutate(model = "Claassen w/ Uncertainty") %>%  
   bind_rows(df_plot)
@@
       "Log GDP\n per capita\n (Difference)",
-      "Log GDP\n (t−1)",
+      "Log GDP\n (t-1)",
       "Corruption\n (Difference)",
-      "Corruption\n (t−1)"
+      "Corruption\n (t-1)"
       ),time = 3)
   )
+
+terms2 <- factor(rev(c("Support[t-1]",
+                      "Support[t-2]",
+                      "Delta~Liberal~democracy",
+                      "Liberal~democracy[t-1]",
+                      "Delta~Log~GDP~per~capita",
+                      "Log~GDP[t-1]",
+                      "Delta~Corruption",
+                      "Corruption[t-1]")),
+                levels = rev(c("Support[t-1]",
+                               "Support[t-2]",
+                               "Delta~Liberal~democracy",
+                               "Liberal~democracy[t-1]",
+                               "Delta~Log~GDP~per~capita",
+                               "Log~GDP[t-1]",
+                               "Delta~Corruption",
+                               "Corruption[t-1]")))
 
@@
 plot_APSR2 <- dwplot(df_plotS, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_color_uiowa(name = "", palette = "digitMixed") +
+  scale_y_discrete(labels = parse(text = levels(terms2))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  # scale_color_uiowa(name = "", palette = "digitMixed") +
   labs(
     title = "",
-    subtitle = "w. Corruption"
+    subtitle = "w/ Corruption"
   ) +
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom", legend.title = element_blank())
 
@@
       `diff(lg_imp_mdpgdp, lag = 1)` = "Log GDP per capita(Diff)", 
-      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
+      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t-1)",
       `plm::lag(mdprgdp_grwth, 1)` = "Corruption (Difference)"
@@
       `diff(lg_imp_mdpgdp, lag = 1)` = "Log GDP per capita(Diff)", 
-      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
+      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t-1)",
       `diff(cpi_sd, lag = 1)` = "Corruption (Difference)",
@@
 The importance of accounting for the measurement uncertainty appear more evident when the relevant variable plays as the dependent variable. 
-In Figure \@ref(fig:visualizedAPSR), we examine the thermostatic model of democratic mood [@Claassen2020b]. 
+In Figure&nbsp;\ref{fig:visualizedAPSR}, we examine the thermostatic model of democratic mood [@Claassen2020b]. 
 The estimates without taking uncertainty into account imply that democatic mood decreases along with the progress of democratization. 
@@
 # Conclusion
-In this note, we reexamined the findings from Claassens'[-@Claassen2019,-@Claassen2020b] paper that public support helps the survival of democarcy and democratic development has a thermostatic effect on public support for democracy.
+In this note, we reexamined the findings from Claassens'[-@Claassen2019; -@Claassen2020b] paper that public support helps the survival of democracy and democratic development has a thermostatic effect on public support for democracy.
 We demonstrated that the relationships between public support and democratic development depends on the incorporation of uncertainty in the measurement of latent variables.
@@
 
-# (APPENDIX) Appendix {-},
-
-## Models of Effect of Democratic Mood on Institutional Democratization {#replicateAJPS}
-
-```{r tableAJPS}
+\newpage
+# APPENDIX A: Tabular Results
+
+# Table A1. Democratic Support on Democratic Institutions{#AJPSreplication}
+<!-- ## Models of Effect of Democratic Support on Institutional Democratization {#replicateAJPS} -->
+
+```{r tableAJPS, eval=TRUE}
 df_tableAJPS %>% 
@@
   hline(i = 8, border = officer::fp_border()) %>% 
-  autofit() %>% 
-  add_header_lines(values = paste0("Number of Observations: ", unique(df_tableAJPS$n)))
-```
-
-## Models of Effects of Democracy on Change in Mood
-
-```{r table APSR}
+  add_header_lines(values = paste0("Number of Observations: ", unique(df_tableAJPS$n))) %>% 
+  autofit() 
+```
+
+# Table A2. Democratic Institutions on Democratic Support{#APSRreplication}
+
+```{r table APSR, eval=TRUE}
 df_tableAPSR %>% 
@@
   autofit()
-```
+
+```

### 2020-10-27 paper/appendix.Rmd
split off appendix

---
title: "[dcpo_demsupport] Appendix"
classoption: landscape
output:
  pdf_document
---

```{r setup, include=FALSE}
options(tinytex.verbose = TRUE)

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, eval = FALSE, dpi = 300)

if (!require(pacman)) install.packages("pacman")
library(pacman)

# load all the packages you will use below 
p_load(
  flextable, kableExtra, modelsummary, # tabulation
  latex2exp, # visualization
  broom, tidyverse, janitor, # data wrangling
  dotwhisker # visualization
)

# Functions preload
set.seed(313)

# Theme setup
theme_set(theme_minimal())
```

\renewcommand{\thepage}{A\arabic{page}}
# APPENDIX A: Tabular Results

# Table A1. Estimates of Democratic Support on Democratic Institutions{#AJPSreplication}
<!-- ## Models of Effect of Democratic Support on Institutional Democratization {#replicateAJPS} -->

```{r tableAJPS, eval=TRUE}
load(here::here("output", "df_tables.rda"))

df_tableAJPS %>% 
  mutate(estimate = paste0(estimate, "\n ", conf),
         group = paste0(group, "\n (n: ", n, ")")) %>% 
  arrange(group, model) %>% 
  select(group, model, term, estimate) %>% 
  group_by(group) %>% 
  pivot_wider(names_from = model, values_from = estimate) %>% 
  mutate(term = str_replace_all(term, "\\n", " ")) %>% 
  arrange(group) %>% 
  flextable %>% 
  set_header_labels(group = "Model",
                    term = "Variable") %>% 
  merge_v(j = c("group")) %>% 
  hline(i = 8, border = officer::fp_border()) %>% 
  add_header_lines(values = paste0("Number of Observations: ", unique(df_tableAJPS$n))) %>% 
  autofit() 
```

# Table A2. Estimates of Democratic Institutions on Democratic Support{#APSRreplication}

```{r table APSR, eval=TRUE}
df_tableAPSR %>% 
  mutate(estimate = paste0(estimate, "\n ", conf),
         group = paste0(group, "\n (n: ", n, ")")) %>% 
  arrange(group, model) %>% 
  select(group, model, term, estimate) %>% 
  group_by(group) %>% 
  pivot_wider(names_from = model, values_from = estimate) %>% 
  mutate(term = str_replace_all(term, "\\n", " ")) %>% 
  arrange(group) %>% 
  flextable %>% 
  set_header_labels(group = "Model",
                    term = "Variable") %>% 
  merge_v(j = c("group")) %>% 
  hline(i = 6, border = officer::fp_border()) %>% 
  autofit()

```

### 2020-10-27 paper/dcpo_demsupport.Rmd
split off appendix

@@
 df_plot <- df_result_clsAPSR[[2]] %>% 
-  mutate(model = "Claassen 2020")
+  mutate(model = "Claassen 2020b")
 
@@
 
+```{r save_tables, eval=TRUE}
+save(df_tableAJPS, df_tableAPSR, file = here::here("output", "df_tables.rda"))
+
+```
+
 The importance of accounting for the measurement uncertainty appear more evident when the relevant variable plays as the dependent variable. 
@@
 
-\newpage
-# APPENDIX A: Tabular Results
-
-# Table A1. Democratic Support on Democratic Institutions{#AJPSreplication}
-<!-- ## Models of Effect of Democratic Support on Institutional Democratization {#replicateAJPS} -->
-
-```{r tableAJPS, eval=TRUE}
-df_tableAJPS %>% 
-  mutate(estimate = paste0(estimate, "\n ", conf),
-         group = paste0(group, "\n (n: ", n, ")")) %>% 
-  arrange(group, model) %>% 
-  select(group, model, term, estimate) %>% 
-  group_by(group) %>% 
-  pivot_wider(names_from = model, values_from = estimate) %>% 
-  mutate(term = str_replace_all(term, "\\n", " ")) %>% 
-  arrange(group) %>% 
-  flextable %>% 
-  set_header_labels(group = "Model",
-                    term = "Variable") %>% 
-  merge_v(j = c("group")) %>% 
-  hline(i = 8, border = officer::fp_border()) %>% 
-  add_header_lines(values = paste0("Number of Observations: ", unique(df_tableAJPS$n))) %>% 
-  autofit() 
-```
-
-# Table A2. Democratic Institutions on Democratic Support{#APSRreplication}
-
-```{r table APSR, eval=TRUE}
-df_tableAPSR %>% 
-  mutate(estimate = paste0(estimate, "\n ", conf),
-         group = paste0(group, "\n (n: ", n, ")")) %>% 
-  arrange(group, model) %>% 
-  select(group, model, term, estimate) %>% 
-  group_by(group) %>% 
-  pivot_wider(names_from = model, values_from = estimate) %>% 
-  mutate(term = str_replace_all(term, "\\n", " ")) %>% 
-  arrange(group) %>% 
-  flextable %>% 
-  set_header_labels(group = "Model",
-                    term = "Variable") %>% 
-  merge_v(j = c("group")) %>% 
-  hline(i = 8, border = officer::fp_border()) %>% 
-  autofit()
-
-```
+# References
+
+<div id="refs"></div>

### 2020-10-28 paper/dcpo_demsupport.Rmd
revise abstract, try out a very tentative title

@@
     template: svm-latex-ms2.tex
-title: "[dcpo_demsupport]"
+title: "Public Support for Democracy, Regime Change, and the Importance of Incorporating Measurement Uncertainty"
 thanks: "The authors contributed equally to this work.  Corresponding author: [yuehong-tai@uiowa.edu](mailto:yuehong-tai@uiowa.edu).  Current version: `r format(Sys.time(), '%B %d, %Y')`."
@@
   affiliation: University of Iowa
-abstract: "Public opinion’s effect on democratic institutions is important and long-studied topic.
-Claassen (2020) renewed attention to this question by using a Bayesian latent variable approach to measure mass democratic support from survey data and concluded such support has a positive effect on subsequent democratic change and especially on democracy’s endurance once in place.
-In this article, we reexamine the question, bringing more survey data on democratic support; a superior measure, Dynamic Comparative Public Opinion (DCPO); and an improved methodological approach that takes the uncertainty in this measure into account.
-Our results [further reinforce/contradict] the long-held view that democracies depend on public support to survive."
+abstract: "Do democratic regimes depend on public support to avoid backsliding?
+Does public support, in turn, respond thermostatically to changes in regime?
+Two recent prominent studies (Claassen 2020a, 2020b) have reinvigorated the classic hypothesis on the positive relationship between public support for democracy and regime survival--and challenged its reciprocal counterpart--by using a Bayesian latent variable approach to measure mass democratic support from cross-national survey data.
+But such approaches come with concomitant measurement uncertainty, and neither study incorporated this error into its analyses.
+Here we correctly take this uncertainty in account and show that there is no support for the conclusion of either study.
+We then work to minimize the measurement uncertainty in public support by bringing additional survey data and a superior model of public opinion.
+Even with these improvements, however, our analyses fail to yield evidence in support of either hypothesis."
 keywords: ""
@@
 
-df_result_dcpoMeanAPSR <- map(mods, function(aMod){
+df_result_dcpoMeanAPSR <- map(mods, function(aMod) {
   aMod %>% 
@@
 In Figure&nbsp;\ref{fig:visualizedAPSR}, we examine the thermostatic model of democratic mood [@Claassen2020b]. 
-The estimates without taking uncertainty into account imply that democatic mood decreases along with the progress of democratization. 
+The estimates without taking uncertainty into account imply that democratic mood decreases along with the progress of democratization. 
 Nevertheless, this effect no longer holds when the measurement uncertainty is involved.

### 2020-11-16 paper/dcpo_demsupport.Rmd
make Hu corresponding author; revise some citations

@@
 title: "Public Support for Democracy, Regime Change, and the Importance of Incorporating Measurement Uncertainty"
-thanks: "The authors contributed equally to this work.  Corresponding author: [yuehong-tai@uiowa.edu](mailto:yuehong-tai@uiowa.edu).  Current version: `r format(Sys.time(), '%B %d, %Y')`."
+thanks: "The authors contributed equally to this work.  Corresponding author: [yuehu@mail.tsinghua.edu.cn](mailto:yuehu@mail.tsinghua.edu.cn).  Current version: `r format(Sys.time(), '%B %d, %Y')`."
 author:
@@
 Does public support, in turn, respond thermostatically to changes in regime?
-Two recent prominent studies (Claassen 2020a, 2020b) have reinvigorated the classic hypothesis on the positive relationship between public support for democracy and regime survival--and challenged its reciprocal counterpart--by using a Bayesian latent variable approach to measure mass democratic support from cross-national survey data.
-But such approaches come with concomitant measurement uncertainty, and neither study incorporated this error into its analyses.
+Two prominent recent studies (Claassen 2020_a_, Claassen 2020_b_) have reinvigorated the classic hypothesis on the positive relationship between public support for democracy and regime survival--and challenged its reciprocal counterpart--by using a Bayesian latent variable approach to measure mass democratic support from cross-national survey data.
+But such approaches come with concomitant measurement uncertainty, and neither study incorporated this uncertainty into its analyses.
 Here we correctly take this uncertainty in account and show that there is no support for the conclusion of either study.
 We then work to minimize the measurement uncertainty in public support by bringing additional survey data and a superior model of public opinion.
-Even with these improvements, however, our analyses fail to yield evidence in support of either hypothesis."
+Even with these improvements, however, our analyses fail to yield evidence in support of either hypothesis.
+[142/150 words]"
 keywords: ""
@@
       - \usepackage{wrapfig}
-nocite: |
-  @Solt2020a
 ---
@@
 One of the classic but disputable questions in comparative politics is the relationship between mass democratic support and countries' level of democracy.
-A long-standing and widely accepted theory is that the level of mass democratic support determines the stability of a democratic system [e.g., @lipset_social_1959; @norris_democratic_2011], but findings from empirical analyses still remain inconclusive [@inglehart_modernization_2005; @fails_changing_2010; @qi_how_2011; for a review in this literature, see @Claassen2020a].
+A long-standing and widely accepted theory is that the level of mass democratic support determines the stability of a democratic system [e.g., @lipset_social_1959; @norris_democratic_2011], but findings from empirical analyses still remain inconclusive [@inglehart_modernization_2005; @fails_changing_2010; @qi_how_2011; for a review of this literature, see @Claassen2020a].
 
@@
 
-In our reexamination, instead of employing the point estimates, we followed the recommendation and the approach of incorporating uncertainty in using latent variables [e.g., @Schnakenberg2014; @Crabtree2015] and other measures, such as the Standardized World Income Inequality Database [@Solt2020].
+In our reexamination, instead of employing the point estimates, we followed the recommendation and the approach of incorporating uncertainty in using latent variables [e.g., @Schnakenberg2014; @Crabtree2015].
 Specifically, in our replication of Claassen's [-@Claassen2020a] analysis models, we incorporated uncertainty by using random draws from the posterior distributions. 
@@
 When more data and better method are applied, the confidence intervals do shrink yet remaining statistically insignificant. 
-We observed the similar changes after adjusting the effect of domestic corruption [@Claassen2020b: 41].
+We observed the similar changes after adjusting the effect of domestic corruption [@Claassen2020b, 41].
 
@@
 Elites are thought to play a critical role in preserving democratic stability by respecting the limits on their behaviors [@weingast_political_1997].
-After the Cold War, many democracies backslid and were imperiled worldwide because elected leaders lack commitment to democratic norms when the public even did not notice that [@bermeo_democratic_2016,@levitsky_how_2018, @waldner_unwelcome_2018].
+After the Cold War, many democracies backslid and were imperiled worldwide because elected leaders lack commitment to democratic norms when the public even did not notice that [@bermeo_democratic_2016; @levitsky_how_2018; @waldner_unwelcome_2018].
 
@@
 # Conclusion
-In this note, we reexamined the findings from Claassens'[-@Claassen2019; -@Claassen2020b] paper that public support helps the survival of democracy and democratic development has a thermostatic effect on public support for democracy.
+In this note, we reexamined the findings from Claassens' [-@Claassen2020a; -@Claassen2020b] paper that public support helps the survival of democracy and democratic development has a thermostatic effect on public support for democracy.
 We demonstrated that the relationships between public support and democratic development depends on the incorporation of uncertainty in the measurement of latent variables.

### 2020-11-23 paper/dcpo_demsupport.Rmd
add lit Van et al. 2017 and wuttke2020.

@@
 
-The underlying reasons for the uncertainty could be the ineffectiveness of survey questions in capturing public attitude compared to rich indicators for other concept, like gender egalitarianism [Solt, 2021??], the shortage of indicators for public support worldwide, or the gap between self-reported democratic attitude and behaviorally democratic commitments [@graham_democracy_2020; @Carey2020; @McCoy2020].
-There could be some potentially substantive explanations for the disappearing relationship: the elite-driven democratic backsliding [@weingast_political_1997; @levitsky_how_2018], the lack of a consensus on democratic erosion between the public and experts [@carey_searching_2019], and the difference between the public support in abstract and public commitments in context [@bartels_ethnic_2020; @graham_democracy_2020; @McCoy2020].
+The underlying reasons for the uncertainty could be the ineffectiveness of survey questions in capturing public attitude.
+For example, compared to rich indicators for other concept, like gender egalitarianism [Solt, 2021??], there is a shortage of indicators for public support worldwide.
+Also, the existing standard questions are not sufficient to capture either the multi-faceted democratic support [@wuttke2020have] or behaviorally democratic commitments [@graham_democracy_2020; @Carey2020; @McCoy2020].
+There could be some potentially substantive explanations for the disappearing relationship: the elite-driven democratic backsliding [@weingast_political_1997; @levitsky_how_2018], the lack of a consensus on democratic erosion between the public and experts [@carey_searching_2019], and the difference between the public support in abstract and public commitments in context [@bartels_ethnic_2020; @graham_democracy_2020; @McCoy2020;@prothro_fundamental_1960;@van2017myth
+].
 
@@
 First, the survey items we used might not capture real public democratic support, given the complexity of this concept and limited indicators compared to other concepts like gender egalitarian (Solt, 2021??).
-Second, these survey items do capture public democratic support, but we still don’t have enough data to compensate the fragmentation and incomparability of the available comparative public opinion data, which is doomed to high uncertainty.
+Second, the standard questions capture the support for the generic concept of democracy, but
+are not sophisticated to capture the multi-faceted feature of democratic support due to the variation in understanding the concept across countries or over time or within country [@wuttke2020have;@van2017myth].
+As @van2017myth pointed out, without considering the varying understanding of democracy due to political and social development, the unchanged survey questions decrease the comparability of time series data.
+Third, these survey items might capture public democratic support, but we still don’t have enough data to compensate the fragmentation and incomparability of the available comparative public opinion data, which is doomed to high uncertainty.
 Methodologically, given the nature trail of latent variables and specific characters of comparative public opinion, performing analyses based on the strong assumption that comparative public attitudes are perfectly measured might exaggerate scholars' certainty methodologically and obscure a proper substantive evaluation of theoretical claims.
@@
 
-Third, since there is a difference between the public support for democracy in the abstract and under specific propositions [@bartels_ethnic_2020], recent studies questioned whether conventional measures of public support for democracy could capture public realistic commitment to democracy.
+Third, the study of democratic support is suffered from "inputism" ignoring the output-side, however, the output-side better predicts democratic support [@van2017myth].
+
+Lastly, verbal support in pro-democratic stance is usually higher than behavioral commitments [@prothro_fundamental_1960]. 
+since there is a difference between the public support for democracy in the abstract and under specific propositions [@bartels_ethnic_2020], recent studies questioned whether conventional measures of public support for democracy could capture public realistic commitment to democracy.
 By using survey experiments, @graham_democracy_2020 pointed out a "fundamental blind spot" in traditional measures of public democratic support: the questions regarding the support for an abstract democracy cannot capture public willingness and behavioral commitment to democratic principles when voters have to choose between democratic norms and their partisan identification or policy preference.

### 2020-12-16 paper/dcpo_demsupport.Rmd
Edit words and structure.

--- 2020-11-16 paper/dcpo_demsupport.Rmd
@@
 
-One of the classic but disputable questions in comparative politics is the relationship between mass democratic support and countries' level of democracy.
-A long-standing and widely accepted theory is that the level of mass democratic support determines the stability of a democratic system [e.g., @lipset_social_1959; @norris_democratic_2011], but findings from empirical analyses still remain inconclusive [@inglehart_modernization_2005; @fails_changing_2010; @qi_how_2011; for a review of this literature, see @Claassen2020a].
+One classic but disputable question in comparative politics is the relationship between mass democratic support and countries' level of democracy.
+A long-standing and widely accepted theory is that the level of mass democratic support determines the stability of a democratic system [e.g., @lipset_social_1959; @easton1965systems; @norris_democratic_2011], but empirical findings remain inconclusive [@inglehart_modernization_2005; @fails_changing_2010; @qi_how_2011; for a review of this literature, see @Claassen2020a].
 
 One reason for the mixed results is the difficulties in measuring comparative public democratic support.
-Public support for democracy is a latent variable and the incorrect measurement of it may conceal the real relationship between public opinion and democratic institutional development.
-However, the sparsity and incomparability of public opinion data across countries over time have perplexed the study of comparative politics for a long time [@Solt2020a].
-Recently, a few pioneering studies are contributing to the latent public opinion measurement in comparative studies [@Caughey2019; @Claassen2019; @Solt2020a].
+Public support for democracy is a latent variable, and the incorrect measurement of it may limit inferences about relationship between public opinion and democratic institutional development.
+However, the sparsity and incomparability of public opinion data across countries over time have always been perplexing comparative studies for a long time [@Solt2020a].
+Recently, a few pioneering studies have contributed to comparative public opinion studies using advanced latent variable measurement [@Caughey2019; @Claassen2019; @Solt2020a].
 
 A prominent study by @Claassen2020a applied an advanced Bayesian Item Response Model to measure dynamic public democratic support for 135 countries for up to 29 years.
-It found that mass democratic support had a positive impact on democratic change, especially the endurance of democracy.
+It found that mass support had a positive impact on democratic change, especially the endurance of democracy.
 The analysis models he used do not account, though, for measurement uncertainty.
-The latent constructs are inherently accompanied by amount of measurement uncertainty due to the unobservability of variables.
+The latent constructs are inherently accompanied by a quantity  of measurement uncertainty due to the unobservability of variables.
 Left unacknowledged, with a strong assumption that latent variables are measured perfectly, measurement error could distort both statistical and substantive inference [@Crabtree2015; @juhl_measurement_2019].
 
-In this paper, we reexamined the relationship between public support for democracy and democratic changes thoroughly, by using a superior measurement, bigger data, and incorporating uncertainty.
-To reduce the uncertainty, we used a superior measurement, the Dynamic Comparative Public Opinion (DCPO) model developed by @Solt2020a, to estimate democratic support for a larger dataset with 144 countries for up to 33 years between 1988 and 2020.
-Surprisingly, our study revealed that the significant relationship between public support and democratic change disappeared when uncertainty was included in the replication analysis of @Claassen2020a model with his original data and the DCPO analysis with more data.
-
-The underlying reasons for the uncertainty could be the ineffectiveness of survey questions in capturing public attitude compared to rich indicators for other concept, like gender egalitarianism [Solt, 2021??], the shortage of indicators for public support worldwide, or the gap between self-reported democratic attitude and behaviorally democratic commitments [@graham_democracy_2020; @Carey2020; @McCoy2020].
-There could be some potentially substantive explanations for the disappearing relationship: the elite-driven democratic backsliding [@weingast_political_1997; @levitsky_how_2018], the lack of a consensus on democratic erosion between the public and experts [@carey_searching_2019], and the difference between the public support in abstract and public commitments in context [@bartels_ethnic_2020; @graham_democracy_2020; @McCoy2020].
+This paper reexamined the classic claim about public democratic attitude and democratic changes thoroughly through both sophisticated methods and bigger data.
+In addition to incorporating uncertainty, we employed a more sophisticated measurement, the Dynamic Comparative Public Opinion (DCPO) model developed by @Solt2020a, to estimate democratic support for a larger dataset with 144 countries for up to 33 years between 1988 and 2020.
+Surprisingly, our study revealed that the significant relationship between public support and democratic change disappeared once uncertainty was included in the replication analysis of @Claassen2020a model with his original data and the DCPO analysis with more data.
+To be cautious, we then also reexamined @Claassen2020b analyses by following the same operations. 
+Again, when uncertainty was incorporated, the significant relationship between democratic changes and public democratic attitude disappeared.
+
+The disappearing relationship might be caused by theoretical, methodological reasons, or both.
+Methodologically, the existing survey questions might not be able to capture mass democratic attitude due to a shortage of indicators [Solt, 2021??] and the ineffectiveness of indicators in measuring the multi-faceted democratic support [@wuttke2020have] and behaviorally democratic commitments [@graham_democracy_2020; @Carey2020; @McCoy2020].
+Substantive explanations might also account for the insignificant relationship: the elite-driven democratic backsliding [@weingast_political_1997; @levitsky_how_2018], the lack of a consensus on democratic erosion between the public and experts [@carey_searching_2019], and the difference between the public support in abstract and public commitments in context [@bartels_ethnic_2020; @graham_democracy_2020; @McCoy2020;@prothro_fundamental_1960;@van2017myth
+].
 
@@
 The first step we made is to reproduce @Claassen2020a.
-Then applying the method he described in the article, we replicated his IRT-based measurement of democratic mood and maintained the entire distribution of the predicted outcome, instead of aggregating to a single point estimate.
-Utilizing the estimated distribution, we involved uncertainty to the analysis of the influence of democratic mood on institutional democracy cross-nationally.
-In the third step, we applied an advanced method and added one-third more data to the analysis to reduce potential effects of measurement biases and data spareness.
-We compared the outcomes of the three steps and showed as below that uncertainty is an critical factor in the studies of mass democratic attitude, which may alter the analytic conclusions. 
-We further showed that accounting for uncertainty is at least equivalently important when the latent-variable estimates plays as the dependent variable in a study by replicating @Claassen2020b.
+Then applying the method he described in the article, we replicated his IRT-based measurement of democratic mood and maintained the entire distribution of the predicted outcome instead of aggregating it to a single point estimate.
+Utilizing the estimated distribution, we involved uncertainty in the analysis of the influence of democratic mood on institutional democracy cross-nationally.
+In the third step, we applied the DCPO measurement and added one-third more data to the analysis to reduce potential effects of measurement biases and data spareness.
+We compared the outcomes of the three steps and showed as below that uncertainty is a critical factor in the studies of mass democratic attitude, which may alter the analytic conclusions. 
+We further showed that accounting for uncertainty is equivalently important when the latent-variable estimates play as a dependent variable in a study by replicating @Claassen2020b.
 
 ## Incorporating Uncertainty
-Given the measurement uncertainty caused by the inherent trail of latent constructs and the consequential (propagated) effects of measurement uncertainty on inferences about the relationship of substantive interests, it is strongly recommended to incorporate the measurement uncertainty in analysis models [@treier_democracy_2008; @Crabtree2015].
-Many scholars have taken the account for measurement error in analyses as a final crucial part in their empirical studies [@Schnakenberg2014; @caughey_policy_2018], and recent studies on latent variable measurement emphasized the incorporation of measurement uncertainty when using their measures [@solis_measuring_2020; @gandhi_measuring_2020].
-However, in the comparative public opinion field, previous efforts on measuring comparative public opinion didn’t account for measurement uncertainty in their analyses.
-
-In our reexamination, instead of employing the point estimates, we followed the recommendation and the approach of incorporating uncertainty in using latent variables [e.g., @Schnakenberg2014; @Crabtree2015].
-Specifically, in our replication of Claassen's [-@Claassen2020a] analysis models, we incorporated uncertainty by using random draws from the posterior distributions. 
+Given the measurement uncertainty derived by the inherent trail of latent constructs and its propagated effects on inferences about the relationship of substantive interests, it is strongly recommended to incorporate the measurement uncertainty in analysis models [@treier_democracy_2008; @Crabtree2015].
+Many scholars have accounted for measurement error in analyses as a final crucial part in their empirical studies [@Schnakenberg2014; @caughey_policy_2018].
+Moreover, recent studies on latent variable measurement highlighted the incorporation of measurement uncertainty when using their measures [@solis_measuring_2020; @gandhi_measuring_2020]. 
+However, measurement uncertainty has not attracted attention in the comparative public opinion field.
+Previous efforts on measuring dynamic comparative public opinion did not account for measurement uncertainty in analyses.
+
+Instead of employing the point estimates, we followed the recommendation and the approach of incorporating uncertainty in using latent variables [e.g., @Schnakenberg2014; @Crabtree2015].
+Specifically, in our replication of Claassen's [-@Claassen2020a] analysis models, we incorporated uncertainty using random draws from the posterior distributions. 
 We generated 1,000 duplicate versions of the analysis dataset, assigned to each a different random draw from the posterior distributions of public democratic support, performed the analyses repeatedly on each of these 1,000 versions of the dataset, and then combined the results following the rules set out in @Rubin1987.
@@
 The validation tests in @Solt2020a's paper corroborate that the DCPO model yields more accurate results than other latent variable measurements, either of @Claassen2019 Model 5 and @Caughey2019 model.
+The DCPO is superior to other measurements in several ways.
 The flexibility of the DCPO model in treating the data as their original scales, either dichotomous or ordinal, decreases information missing due to the potential scale change.
-For example, our data consists of 20,885 national responses as the result of measuring public attitude at ordinal scales, which has the potential to give us more nuances about public democratic support.
-Second, to reduce the uncertainty in estimating countries which lie at the extreme ends of the public opinion spectrum [@Linzer2015], the estimates of mean public opinion are bounded and the extent of polarization is included in the DCPO model.
-Third, to address the differences in item response across countries, caused by factors other than public attitude or preference, a country-specific item bias is modelled as "a country-specific bias in the difficulty of each question" [@Solt2020a, 6].
-In short, the DCPO model has methodological advantages in keeping as much available information as possible, reducing uncertainty by bounding scales, and in capturing the extent of polarization in the public.
-
-In addition to applying the advanced measurement, we also collected as much available data as possible.
+For example, our data consists of 20,885 national responses as the result of measuring public attitude at ordinal scales, which can give us more nuances about public democratic support. 
+Second, to reduce the uncertainty in estimating countries that lie at the extreme ends of the public opinion spectrum [@Linzer2015], the estimates of mean public opinion are bounded, and the extent of polarization is included in the DCPO model.
+Third, to address the differences in item response across countries caused by factors other than public attitude or preference, a country-specific item bias is modelled as "a country-specific bias in the difficulty of each question" [@Solt2020a, 6].
+In short, the DCPO model has methodological advantages in keeping as much available information as possible, reducing uncertainty by bounding scales, and capturing the extent of polarization in public.
+
+In addition to applying the advanced DCPO measurement, we also collected as much available data as possible.
 We collected data on 62 items from 17 survey projects in 159 countries covering years from 1988 to 2020.
 Survey data was extracted automatically through the `DCPO` package for R [@Solt2020b].
-The DCPO package also automatically identifies the year in which the survey was conducted, which contributes to the capture of the real relationship between public opinion and the level of democracy.
+The DCPO package also automatically identifies the year in which the survey was conducted, which contributes to capturing the real relationship between public opinion and the level of democracy.
 Our data consists of `r dcpo_input_ncy` country-years and 1,861 national surveys, which is a `r increase_cy`% and 33.9% increase respectively over `r supdem_ncy` country-years and 1,390 national surveys used in Claassen's studies [-@Claassen2020a; -@Claassen2020b].
@@
 However, when accounting for the uncertainty of the latent variable measurement of the mood, the significance disappears.
-We added one-third more data and applied a more efficient measurement (DCPO), resulting a saliently shrink of the range of measurement uncertainty, but the confidence intervals still cut zero---that is, remaining statistically insignificant.^[The point estimates also alters.
-We attribute it to additional more information and better measuring method by DCPO.]
-Similar phenomenon also happens on the estimates of, for example, the second-time-unit lag of democratization and resouce dependency.
+We applied the DCPO and added one-third more data, resulting in a saliently shrink of the range of measurement uncertainty, but the confidence intervals still cut zero---that is, remaining statistically insignificant.^[The point estimates also alters.
+We attribute it to more information and better measuring method by DCPO.]
+A similar phenomenon also happens on the estimates of, for example, the second-time-unit lag of democratization and resource dependency.
 
 We further examined Claassen's regime specific model [@Claassen2020a: Model 2].
-The originally significant contribution of democratic mood in democratic regimes disappears as well, regardless whether more information and better method are applied.
+The originally significant contribution of democratic mood in democratic regimes disappears, regardless whether more information and better method are applied.
 
@@
 The importance of accounting for the measurement uncertainty appear more evident when the relevant variable plays as the dependent variable. 
-In Figure&nbsp;\ref{fig:visualizedAPSR}, we examine the thermostatic model of democratic mood [@Claassen2020b]. 
+In Figure&nbsp;\ref{fig:visualizedAPSR}, we examined the thermostatic model of democratic mood [@Claassen2020b]. 
 The estimates without taking uncertainty into account imply that democratic mood decreases along with the progress of democratization. 
@@
 
-As previous operation, we tested if this alteration is caused by the data scarcity or estimating inefficiency. 
-When more data and better method are applied, the confidence intervals do shrink yet remaining statistically insignificant. 
-We observed the similar changes after adjusting the effect of domestic corruption [@Claassen2020b, 41].
+As previous operations, we tested if this alteration is caused by the data scarcity or estimating inefficiency. 
+When more data and better method are applied, the confidence intervals do shrink yet remain statistically insignificant. 
+We observed similar changes after adjusting the effect of domestic corruption [@Claassen2020b, 41].
 
 # Discussion
-In short, the main empirical findings about the estimated effect of public democratic support on democracy or vice versa are not replicable when measurement uncertainty is accounted, even using better measurement and more data.
-
-There are potential causes for the null results.
-First, the survey items we used might not capture real public democratic support, given the complexity of this concept and limited indicators compared to other concepts like gender egalitarian (Solt, 2021??).
-Second, these survey items do capture public democratic support, but we still don’t have enough data to compensate the fragmentation and incomparability of the available comparative public opinion data, which is doomed to high uncertainty.
-Methodologically, given the nature trail of latent variables and specific characters of comparative public opinion, performing analyses based on the strong assumption that comparative public attitudes are perfectly measured might exaggerate scholars' certainty methodologically and obscure a proper substantive evaluation of theoretical claims.
-
-In addition to the potentially methodological cause (the measurement errors), there are some potentially substantive causes for the disappearing relationship.
-First, democratic backsliding might be mainly caused by elites.
+In short, the main empirical findings about the estimated effect of public democratic support on democracy or vice versa are not replicable when measurement uncertainty is accounted for, even using better measurement and more data.
+
+There are several potential causes for the null results.
+First, the survey items we used might not capture real public democratic attitudes since the number of indicators of democratic support is limited compared to indicators of other concepts like gender-egalitarianism (Solt, 2021??).
+Second, even if survey questions capture the support for the generic concept of democracy, they might still not be sufficient to capture the multi-faceted feature of democratic support due to the variation in understanding the concept across countries or over time or within country [@wuttke2020have;@van2017myth].
+As @van2017myth pointed out, without considering the varying understanding of democracy due to political and social development, the unchanged survey questions decrease the comparability of time series data.
+Third, these survey items might capture public democratic support, but we do not have enough data to compensate for the fragmentation and sparseness of available comparative public opinion data, which is doomed to high uncertainty.
+Given the nature trail of latent variables and specific characters of comparative public opinion data, performing analyses based on the strong assumption that comparative public attitudes are perfectly measured might exaggerate scholars' certainty methodologically and obscure a proper substantive evaluation of theoretical claims.
+
+In addition, there are alternative explanations about the relationship between public attitude and democratic changes.
+First, democratic changes might be more associated with elites than with the public.
 Elites are thought to play a critical role in preserving democratic stability by respecting the limits on their behaviors [@weingast_political_1997].
-After the Cold War, many democracies backslid and were imperiled worldwide because elected leaders lack commitment to democratic norms when the public even did not notice that [@bermeo_democratic_2016; @levitsky_how_2018; @waldner_unwelcome_2018].
-
-Second, there has been a gulf between public perception and elites’ perception on important democratic principles [@mcclosky_consensus_1964].
-A recent study showed that polarized public cannot get a consensus on democratic erosion which experts preserved [@carey_searching_2019].
-Given that the measures for democratic development are from experts, there could be a gap between public perception on democracy and the measures of the levels of democracy.
-
-Third, since there is a difference between the public support for democracy in the abstract and under specific propositions [@bartels_ethnic_2020], recent studies questioned whether conventional measures of public support for democracy could capture public realistic commitment to democracy.
-By using survey experiments, @graham_democracy_2020 pointed out a "fundamental blind spot" in traditional measures of public democratic support: the questions regarding the support for an abstract democracy cannot capture public willingness and behavioral commitment to democratic principles when voters have to choose between democratic norms and their partisan identification or policy preference.
+However, after the Cold War, many democracies backslid and were imperiled worldwide because elected leaders lacked commitment to democratic norms and the public even did not notice that [@bermeo_democratic_2016; @levitsky_how_2018; @waldner_unwelcome_2018].
+
+Second, given that the measures for democratic development are from experts, the gulf between public perception and elites' perception on important democratic principles [@mcclosky_consensus_1964] might result in the disconnection between public perception of democracy and experts' measures of the levels of democracy.
+A recent study also lent support to that claim by demonstrating the polarized public cannot reach a consensus with experts on democratic erosion [@carey_searching_2019].
+
+Third, the study of democratic support is suffered from "inputism," which focuses on public evaluations of input-side, institutional designs, but ignores the output-side, policy outcome or implementation; however, the output-side better predicts democratic support [@van2017myth].
+
+Lastly, verbal support in a pro-democratic stance is usually higher than behavioral commitments [@prothro_fundamental_1960]. 
+Since there is a difference in public support for democracy between "in the abstract" and "under specific propositions" [@bartels_ethnic_2020], recent studies questioned whether conventional measures of public support for democracy could capture real public commitment to democracy.
+By using survey experiments, @graham_democracy_2020 pointed out a "fundamental blind spot" in traditional measures of public democratic support: general survey questions cannot capture voters' willingness and behavioral commitment to democratic principles in specific context where voters need to choose between democratic norms and their partisan identification or policy preference.
 It turned out that voters subordinated democratic norms to their partisan preference by not electorally penalizing their candidates who endorse measures that violate norms.
-Furthermore, @Carey2020 found that rather than only tolerate anti-democratic policies, voters support/encourage democratic norm-eroding policies when their co-partisans are in power.
+Furthermore, voters support/encourage democratic norm-eroding policies when their co-partisans are in power rather than only tolerating anti-democratic policies [@Carey2020].
 
@@
 In this note, we reexamined the findings from Claassens' [-@Claassen2020a; -@Claassen2020b] paper that public support helps the survival of democracy and democratic development has a thermostatic effect on public support for democracy.
-We demonstrated that the relationships between public support and democratic development depends on the incorporation of uncertainty in the measurement of latent variables.
-Even using more data and a sophisticated DCPO model, the measurement uncertainty made the relationships irreplicable irrespective of whether public support is an independent variable or dependent variable.
-
-There could be several potential reasons for this no relationship: the self-report survey data that could not capture the public attitude, the scarce data on the complex concept of democratic support,  and the gap between the public attitude and public commitment.
-Any one of these could lead to this no relationship.
-
-Although we could not exclude any one of these, a basic lesson from this reexamination is simple: given the inherent uncertainty accompanying latent public opinion, and its propagated effects in analysis, incorporating measurement uncertainty in analysis models is a safer way to infer the relationship between public opinion and other substantive interest especially for comparative politics, in which the measurement uncertainty of public opinion is further exacerbated by the sparse and incomparability of indicators.
+We demonstrated the importance of incorporating measurement uncertainty in analyzing the relationship between public support and democratic development.
+Even using more data and the sophisticated DCPO model, the measurement uncertainty made the original positive relationships irreplicable regardless whether public support was an independent or dependent variable.
+
+The high uncertainty might come from several sources: the problems of self-report survey data that might not capture the public attitude, the sparse data on the complex concept of democratic support, the relationship between democratic changes and elites, the different public understanding of democracy, and the gap between the public attitude and public commitment.
+
+Although we could not identify or exclude any one of these possible sources in this paper, a basic lesson from this reexamination is simple: given the inherent uncertainty accompanying latent public opinion and its propagated effects in analyses, incorporating measurement uncertainty is a safer way to infer the relationship between public opinion and other substantive interest especially in comparative politics, in which the measurement uncertainty of public opinion is further exacerbated by the sparse and incomparability of indicators.
 

### 2020-12-29 paper/dcpo_demsupport.Rmd
work toward revising introduction

@@
 
-One classic but disputable question in comparative politics is the relationship between mass democratic support and countries' level of democracy.
-A long-standing and widely accepted theory is that the level of mass democratic support determines the stability of a democratic system [e.g., @lipset_social_1959; @easton1965systems; @norris_democratic_2011], but empirical findings remain inconclusive [@inglehart_modernization_2005; @fails_changing_2010; @qi_how_2011; for a review of this literature, see @Claassen2020a].
-
-One reason for the mixed results is the difficulties in measuring comparative public democratic support.
-Public support for democracy is a latent variable, and the incorrect measurement of it may limit inferences about relationship between public opinion and democratic institutional development.
-However, the sparsity and incomparability of public opinion data across countries over time have always been perplexing comparative studies for a long time [@Solt2020a].
-Recently, a few pioneering studies have contributed to comparative public opinion studies using advanced latent variable measurement [@Caughey2019; @Claassen2019; @Solt2020a].
-
-A prominent study by @Claassen2020a applied an advanced Bayesian Item Response Model to measure dynamic public democratic support for 135 countries for up to 29 years.
+One classic but unresolved question in comparative politics is the relationships between mass democratic support and countries' levels of democracy.
+A long-standing and widely accepted theory is that the extent of mass democratic support determines the stability of a democratic system [e.g., @lipset_social_1959; @easton1965systems; @norris_democratic_2011], but empirical findings remain inconclusive [@inglehart_modernization_2005; @fails_changing_2010; @qi_how_2011; for a review of this literature, see @Claassen2020a].
+
+One important reason for these mixed results is the difficulty in measuring comparative public democratic support.
+Public support for democracy cannot be directly observed, and its incorrect measurement will limit inferences about the relationship between public opinion and democratic institutional development.
+However, the survey data available across countries and over time on support for democracy--or indeed nearly any topic in public opinion---are sparse and incomparable, greatly hindering the broadly comparative research needed to reach sound conclusions.
+Recently, a few pioneering studies have sought to overcome the hurdle of sparse and incomparable data and further broadly comparative research by developing latent variable measurement models of public opinion [see @Caughey2019; @Claassen2019; @Solt2020a].
+One prominent study, @Claassen2020a took advantage of this approach to measure dynamic public democratic support for 135 countries for up to 29 years and to then assess its relationship to democratic change.
+
 It found that mass support had a positive impact on democratic change, especially the endurance of democracy.
+
 The analysis models he used do not account, though, for measurement uncertainty.

### 2020-12-31 paper/dcpo_demsupport.Rmd
rewrite first paragraph for balance; minimalist title per https://github.com/fsolt/dcpo_dem_mood/issues/11#issuecomment-752794638

--- 2020-12-16 paper/dcpo_demsupport.Rmd
@@
     template: svm-latex-ms2.tex
-title: "Public Support for Democracy, Regime Change, and the Importance of Incorporating Measurement Uncertainty"
+title: "Democracy, Public Support, and Measurement Uncertainty"
 thanks: "The authors contributed equally to this work.  Corresponding author: [yuehu@mail.tsinghua.edu.cn](mailto:yuehu@mail.tsinghua.edu.cn).  Current version: `r format(Sys.time(), '%B %d, %Y')`."
@@
 abstract: "Do democratic regimes depend on public support to avoid backsliding?
-Does public support, in turn, respond thermostatically to changes in regime?
-Two prominent recent studies (Claassen 2020_a_, Claassen 2020_b_) have reinvigorated the classic hypothesis on the positive relationship between public support for democracy and regime survival--and challenged its reciprocal counterpart--by using a Bayesian latent variable approach to measure mass democratic support from cross-national survey data.
+Does public support, in turn, respond thermostatically to changes in democracy?
+Two prominent recent studies (Claassen 2020a, Claassen 2020b) have reinvigorated the classic hypothesis on the positive relationship between public support for democracy and regime survival--and challenged its reciprocal counterpart--by using a Bayesian latent variable approach to measure mass democratic support from cross-national survey data.
 But such approaches come with concomitant measurement uncertainty, and neither study incorporated this uncertainty into its analyses.
@@
 
-One classic but disputable question in comparative politics is the relationship between mass democratic support and countries' level of democracy.
-A long-standing and widely accepted theory is that the level of mass democratic support determines the stability of a democratic system [e.g., @lipset_social_1959; @easton1965systems; @norris_democratic_2011], but empirical findings remain inconclusive [@inglehart_modernization_2005; @fails_changing_2010; @qi_how_2011; for a review of this literature, see @Claassen2020a].
-
-One reason for the mixed results is the difficulties in measuring comparative public democratic support.
-Public support for democracy is a latent variable, and the incorrect measurement of it may limit inferences about relationship between public opinion and democratic institutional development.
-However, the sparsity and incomparability of public opinion data across countries over time have always been perplexing comparative studies for a long time [@Solt2020a].
-Recently, a few pioneering studies have contributed to comparative public opinion studies using advanced latent variable measurement [@Caughey2019; @Claassen2019; @Solt2020a].
-
-A prominent study by @Claassen2020a applied an advanced Bayesian Item Response Model to measure dynamic public democratic support for 135 countries for up to 29 years.
-It found that mass support had a positive impact on democratic change, especially the endurance of democracy.
-The analysis models he used do not account, though, for measurement uncertainty.
-The latent constructs are inherently accompanied by a quantity  of measurement uncertainty due to the unobservability of variables.
-Left unacknowledged, with a strong assumption that latent variables are measured perfectly, measurement error could distort both statistical and substantive inference [@Crabtree2015; @juhl_measurement_2019].
-
-This paper reexamined the classic claim about public democratic attitude and democratic changes thoroughly through both sophisticated methods and bigger data.
+It has long been argued that democratic regimes and public support for them are mutually reinforcing: that high levels of public support ensure democracies remain strong, and that experience with democratic governance generates robust public support [see, e.g., @lipset_social_1959; @Easton1965].
+But the evidence for either side of this claim has been decidedly mixed.
+Countries with greater democratic support have been found to become stronger and more stable democracies [e.g., @Inglehart2005, 251-254] and just the opposite [@Fails2010, 182-183].
+Similarly, studies have alternately found that more experience with democracy yields more democratic support [e.g., @Fails2010, 183; @Wuttke2020a, 5-6] or instead that long-established democracies are suffering from democratic fatigue [e.g., @Denemark2016; @Foa2017].
+
+One important reason for these mixed results is the difficulty in measuring democratic support over time and across many countries.
+Public support for democracy cannot be directly observed, and its incorrect measurement will limit inferences about the relationships between public opinion and institutional development.
+Further, the survey data available across countries and over time on support for democracy--or indeed most topics in public opinion---are sparse and incomparable, greatly hindering the broadly comparative research needed to reach sound conclusions.
+Recently, a few pioneering studies have sought to overcome the hurdle of sparse and incomparable data and advance broadly comparative research by developing latent variable measurement models of public opinion [see @Caughey2019; @Claassen2019; @Solt2020a].
+A pair of prominent recent works took advantage of this latent variable approach to measure dynamic public democratic support for 135 countries for up to 29 years and to then assess its consequences for democratic change.
+It concluded that mass support had a positive impact on democratic change, especially the endurance of democracy.
+
+The models employed in this study's analyses, though, do not account for measurement uncertainty.
+Because they are unobserved, latent variables are inherently accompanied by a quantity of measurement uncertainty.
+To leave this uncertainty unacknowledged is to make the implausible assumption that the latent variables are measured perfectly, an assumption which distorts both statistical and substantive inference [@Crabtree2015; @juhl_measurement_2019].
+
+This paper reexamines the classic claim about public democratic attitude and democratic changes thoroughly through both sophisticated methods and bigger data.
 In addition to incorporating uncertainty, we employed a more sophisticated measurement, the Dynamic Comparative Public Opinion (DCPO) model developed by @Solt2020a, to estimate democratic support for a larger dataset with 144 countries for up to 33 years between 1988 and 2020.
@@
 Methodologically, the existing survey questions might not be able to capture mass democratic attitude due to a shortage of indicators [Solt, 2021??] and the ineffectiveness of indicators in measuring the multi-faceted democratic support [@wuttke2020have] and behaviorally democratic commitments [@graham_democracy_2020; @Carey2020; @McCoy2020].
-Substantive explanations might also account for the insignificant relationship: the elite-driven democratic backsliding [@weingast_political_1997; @levitsky_how_2018], the lack of a consensus on democratic erosion between the public and experts [@carey_searching_2019], and the difference between the public support in abstract and public commitments in context [@bartels_ethnic_2020; @graham_democracy_2020; @McCoy2020;@prothro_fundamental_1960;@van2017myth
+Substantive explanations might also account for the insignificant relationship: the elite-driven democratic backsliding [@weingast_political_1997; @levitsky_how_2018], the lack of a consensus on democratic erosion between the public and experts [@carey_searching_2019], and the difference between the public support in abstract and public commitments in context [@bartels_ethnic_2020; @graham_democracy_2020; @McCoy2020; @prothro_fundamental_1960; @van2017myth
 ].

### 2021-01-01 paper/dcpo_demsupport.Rmd
replace "Here" with "In this letter" to stress to reviewers that this is a short article with 4k wordcount limit
revise introduction further

@@
 Does public support, in turn, respond thermostatically to changes in democracy?
-Two prominent recent studies (Claassen 2020a, Claassen 2020b) have reinvigorated the classic hypothesis on the positive relationship between public support for democracy and regime survival--and challenged its reciprocal counterpart--by using a Bayesian latent variable approach to measure mass democratic support from cross-national survey data.
+Two prominent recent studies (Claassen 2020a,b) have reinvigorated the classic hypothesis on the positive relationship between public support for democracy and regime survival--and challenged its reciprocal counterpart--by using a Bayesian latent variable approach to measure mass democratic support from cross-national survey data.
 But such approaches come with concomitant measurement uncertainty, and neither study incorporated this uncertainty into its analyses.
-Here we correctly take this uncertainty in account and show that there is no support for the conclusion of either study.
+In this letter, we correctly take this uncertainty in account and show that there is no support for the conclusion of either study.
 We then work to minimize the measurement uncertainty in public support by bringing additional survey data and a superior model of public opinion.
 Even with these improvements, however, our analyses fail to yield evidence in support of either hypothesis.
-[142/150 words]"
+[141/150 words]"
 keywords: ""
@@
 Public support for democracy cannot be directly observed, and its incorrect measurement will limit inferences about the relationships between public opinion and institutional development.
-Further, the survey data available across countries and over time on support for democracy--or indeed most topics in public opinion---are sparse and incomparable, greatly hindering the broadly comparative research needed to reach sound conclusions.
-Recently, a few pioneering studies have sought to overcome the hurdle of sparse and incomparable data and advance broadly comparative research by developing latent variable measurement models of public opinion [see @Caughey2019; @Claassen2019; @Solt2020a].
-A pair of prominent recent works took advantage of this latent variable approach to measure dynamic public democratic support for 135 countries for up to 29 years and to then assess its consequences for democratic change.
-It concluded that mass support had a positive impact on democratic change, especially the endurance of democracy.
-
-The models employed in this study's analyses, though, do not account for measurement uncertainty.
+Further, the survey data available across countries and over time on support for democracy--or indeed most topics in public opinion---are sparse and incomparable, greatly hindering broadly comparative research.
+Recently, a few pioneering studies have sought to overcome the hurdle of sparse and incomparable data by developing latent variable measurement models of public opinion [see @Caughey2019; @Claassen2019; @Solt2020a].
+A pair of prominent recent works took advantage of this latent variable approach to measure democratic support for over one hundred countries for up to nearly three decades and to then assess, respectively, its consequences for and roots in democratic change [@Claassen2020a; @Claassen2020b].
+These works concluded, first and supporting the classic argument, that mass support had a positive impact on democratic change, especially the endurance of democracy [@Claassen2020a, 127-130], and, second and directly contrary to it, democratic change has a thermostatic effect on public support, that is, that rather than generating their own support, deepening democracies provoke a backlash [@Claassen2020b, 46-50].
+
+The models employed in these studies' analyses, though, do not account for uncertainty in their measurement of democratic support.
 Because they are unobserved, latent variables are inherently accompanied by a quantity of measurement uncertainty.
@@
 
-This paper reexamines the classic claim about public democratic attitude and democratic changes thoroughly through both sophisticated methods and bigger data.
-In addition to incorporating uncertainty, we employed a more sophisticated measurement, the Dynamic Comparative Public Opinion (DCPO) model developed by @Solt2020a, to estimate democratic support for a larger dataset with 144 countries for up to 33 years between 1988 and 2020.
-Surprisingly, our study revealed that the significant relationship between public support and democratic change disappeared once uncertainty was included in the replication analysis of @Claassen2020a model with his original data and the DCPO analysis with more data.
-To be cautious, we then also reexamined @Claassen2020b analyses by following the same operations. 
-Again, when uncertainty was incorporated, the significant relationship between democratic changes and public democratic attitude disappeared.
-
-The disappearing relationship might be caused by theoretical, methodological reasons, or both.
+In this letter, we reexamine the classic arguments about support for democracy and democratic change tested in these two pieces while correcting this oversight.
+In addition to incorporating the measurement uncertainty, we also sought to reduce it by employing a superior model of public opinion, the Dynamic Comparative Public Opinion (DCPO) model developed by @Solt2020a, and more data to estimate democratic support for 144 countries for up to 33 years between 1988 and 2020.
+Our analyses reveal that the significant relationships between public support and democratic change disappear once measurement uncertainty is taken into account, both in replications of @Claassen2020a and @Claassen2020b with the studies' original data and in our extension DCPO analyses that incorporate additional data.
+That is, once measurement uncertainty is accounted for, there is no empirical support for either claim: declining democratic support does not appear important to subsequent democratic backsliding, and changes in democracy do not spur a thermostatic response in democratic support.
+
+These null results might be caused by theoretical, methodological reasons, or both.
 Methodologically, the existing survey questions might not be able to capture mass democratic attitude due to a shortage of indicators [Solt, 2021??] and the ineffectiveness of indicators in measuring the multi-faceted democratic support [@wuttke2020have] and behaviorally democratic commitments [@graham_democracy_2020; @Carey2020; @McCoy2020].
@@
 The first step we made is to reproduce @Claassen2020a.
-Then applying the method he described in the article, we replicated his IRT-based measurement of democratic mood and maintained the entire distribution of the predicted outcome instead of aggregating it to a single point estimate.
+Then, applying the method he described in the article, we replicated his IRT-based measurement of democratic mood and maintained the entire distribution of the predicted outcome instead of aggregating it to a single point estimate.
 Utilizing the estimated distribution, we involved uncertainty in the analysis of the influence of democratic mood on institutional democracy cross-nationally.

### 2021-01-03 paper/dcpo_demsupport.Rmd
add more work on intro

@@
 A pair of prominent recent works took advantage of this latent variable approach to measure democratic support for over one hundred countries for up to nearly three decades and to then assess, respectively, its consequences for and roots in democratic change [@Claassen2020a; @Claassen2020b].
-These works concluded, first and supporting the classic argument, that mass support had a positive impact on democratic change, especially the endurance of democracy [@Claassen2020a, 127-130], and, second and directly contrary to it, democratic change has a thermostatic effect on public support, that is, that rather than generating their own support, deepening democracies provoke a backlash [@Claassen2020b, 46-50].
+These works concluded, first and supporting the classic argument, that mass support had a positive impact on democratic change, especially the endurance of democracy [@Claassen2020a, 127-130], and, second and directly contrary to it, democratic change has a thermostatic effect on public support, that is that, rather than generating their own support, deepening democracies provoke a backlash and it is instead the erosion of democracy that calls forth greater public support [@Claassen2020b, 46-50].
 
 The models employed in these studies' analyses, though, do not account for uncertainty in their measurement of democratic support.
-Because they are unobserved, latent variables are inherently accompanied by a quantity of measurement uncertainty.
-To leave this uncertainty unacknowledged is to make the implausible assumption that the latent variables are measured perfectly, an assumption which distorts both statistical and substantive inference [@Crabtree2015; @juhl_measurement_2019].
+Because they are unobserved, latent variables are inherently accompanied by measurement uncertainty.
+To leave this uncertainty unacknowledged is to make the implausible assumption that the latent variables are measured perfectly, an assumption which distorts both statistical and substantive inference [see, e.g., @Crabtree2015; @juhl_measurement_2019].
 
@@
 Our analyses reveal that the significant relationships between public support and democratic change disappear once measurement uncertainty is taken into account, both in replications of @Claassen2020a and @Claassen2020b with the studies' original data and in our extension DCPO analyses that incorporate additional data.
-That is, once measurement uncertainty is accounted for, there is no empirical support for either claim: declining democratic support does not appear important to subsequent democratic backsliding, and changes in democracy do not spur a thermostatic response in democratic support.
-
-These null results might be caused by theoretical, methodological reasons, or both.
-Methodologically, the existing survey questions might not be able to capture mass democratic attitude due to a shortage of indicators [Solt, 2021??] and the ineffectiveness of indicators in measuring the multi-faceted democratic support [@wuttke2020have] and behaviorally democratic commitments [@graham_democracy_2020; @Carey2020; @McCoy2020].
-Substantive explanations might also account for the insignificant relationship: the elite-driven democratic backsliding [@weingast_political_1997; @levitsky_how_2018], the lack of a consensus on democratic erosion between the public and experts [@carey_searching_2019], and the difference between the public support in abstract and public commitments in context [@bartels_ethnic_2020; @graham_democracy_2020; @McCoy2020; @prothro_fundamental_1960; @van2017myth
-].
+That is, once measurement uncertainty is accounted for, there is no empirical support for either claim put forward in these two pieces: declining democratic support does not signal subsequent democratic backsliding, and changes in democracy do not spur a thermostatic response in democratic support.
+
+There are many plausible explanations for these null results, both methodological and theoretical.
+One possible methodological issue is that support for democracy is multidimensional, and the survey questions used to measure it---which ask respondents to assess the desirability or appropriateness of democracy, to compare democracy to some undemocratic alternative, or to assess one of these alternatives---simply do not capture all of the dimensions relevant to democratic change, such as commitments to political equality and freedom of expression [see @Schedler2007; @Wuttke2020].
+Another is that the relationships among these survey items have varied substantially over time [see @wuttke2020have]; this would violate the assumptions of the public opinion models used and would yield faulty estimates of democratic support.
+A third is that these survey questions do not ask respondents to prioritize democracy with regard to other values with which it may come into conflict, such as their partisanship, and so miss capturing the actual extent of support democracy would find among the public when it actually needed public support [see @Carey2020; @graham_democracy_2020; @McCoy2020].
+
+From a theoretical perspective, the effect of democracy on public support may depend not on its mere existence but on its effectiveness [see, e.g., @Magalhaes2014] and particularly with regard to redistribution [see, e.g., @Krieckhaus2014].
+Similarly, the effect of public support on democracy may depend on the extent to which those who support democracy are also dissatisfied with the current regime's performance; that is, that it is not democratic support that is important to democratic change, but rather unsatisfied democratic demand [see, e.g., @Qi2011].
+Of course, it could in fact be that democratic change does not actually depend on public opinion of any sort at all, but rather is an elite-driven phenomenon [see, e.g., Przeworski1991, @levitsky_how_2018].
 
 Although we could not exclude or identify any of them in this study, our reexamination reaffirmed @fariss_respect_2014, @juhl_measurement_2019, and Solt's [-@Solt2020a] suggestion that given the latent character of variables in political science, scholars should be vigilant in measurement uncertainty.
+
+At a time when democracy as seen as under threat around the world [e.g., @Diamond2015], taken together, Claassen (2020_a_,_b_) send what is ultimately a reassuring message: the fate of democracy rests with us, the public, and when democratic institutions are undermined, we will swing to their support and constitute "an obstacle to democratic backsliding" [@Claassen2020b, 51].
+Both of these conclusions may well be true, but the evidence we have, properly assessed, does not provide support for them.
+There can be no room for complacency.
 
@@
 By using survey experiments, @graham_democracy_2020 pointed out a "fundamental blind spot" in traditional measures of public democratic support: general survey questions cannot capture voters' willingness and behavioral commitment to democratic principles in specific context where voters need to choose between democratic norms and their partisan identification or policy preference.
+"fail to capture voters’ willingness to act on their commitment to democracy precisely when democracy is at stake"
 It turned out that voters subordinated democratic norms to their partisan preference by not electorally penalizing their candidates who endorse measures that violate norms.

### 2021-01-03 paper/dcpo_demsupport.Rmd
clean up revisions to intro

@@
 ---
-# Introduction
 
@@
 Public support for democracy cannot be directly observed, and its incorrect measurement will limit inferences about the relationships between public opinion and institutional development.
-Further, the survey data available across countries and over time on support for democracy--or indeed most topics in public opinion---are sparse and incomparable, greatly hindering broadly comparative research.
+Further, the survey data available across countries and over time on support for democracy---or indeed most topics in public opinion---are sparse and incomparable, greatly hindering broadly comparative research.
 Recently, a few pioneering studies have sought to overcome the hurdle of sparse and incomparable data by developing latent variable measurement models of public opinion [see @Caughey2019; @Claassen2019; @Solt2020a].
 A pair of prominent recent works took advantage of this latent variable approach to measure democratic support for over one hundred countries for up to nearly three decades and to then assess, respectively, its consequences for and roots in democratic change [@Claassen2020a; @Claassen2020b].
-These works concluded, first and supporting the classic argument, that mass support had a positive impact on democratic change, especially the endurance of democracy [@Claassen2020a, 127-130], and, second and directly contrary to it, democratic change has a thermostatic effect on public support, that is that, rather than generating their own support, deepening democracies provoke a backlash and it is instead the erosion of democracy that calls forth greater public support [@Claassen2020b, 46-50].
+These works concluded, first and supporting the classic argument, that mass support had a positive impact on democratic change, especially the endurance of democracy [@Claassen2020a, 127-130], and, second and directly contrary to it, democratic change has a thermostatic effect on public support, that is that, rather than generating their own support, deepening democracy provokes a backlash and it is instead democratic backsliding that calls forth greater public support [@Claassen2020b, 46-50].
 
@@
 In addition to incorporating the measurement uncertainty, we also sought to reduce it by employing a superior model of public opinion, the Dynamic Comparative Public Opinion (DCPO) model developed by @Solt2020a, and more data to estimate democratic support for 144 countries for up to 33 years between 1988 and 2020.
-Our analyses reveal that the significant relationships between public support and democratic change disappear once measurement uncertainty is taken into account, both in replications of @Claassen2020a and @Claassen2020b with the studies' original data and in our extension DCPO analyses that incorporate additional data.
-That is, once measurement uncertainty is accounted for, there is no empirical support for either claim put forward in these two pieces: declining democratic support does not signal subsequent democratic backsliding, and changes in democracy do not spur a thermostatic response in democratic support.
+Our analyses reveal that the significant relationships between public support and democratic change disappear once measurement uncertainty is taken into account, both in replications with the studies' original data and in our extension DCPO analyses that incorporate additional data.
+That is, once measurement uncertainty is accounted for, there is no empirical support for either claim put forward in these two works: declining democratic support does not signal subsequent democratic backsliding, and changes in democracy do not spur a thermostatic response in democratic support.
 
 There are many plausible explanations for these null results, both methodological and theoretical.
-One possible methodological issue is that support for democracy is multidimensional, and the survey questions used to measure it---which ask respondents to assess the desirability or appropriateness of democracy, to compare democracy to some undemocratic alternative, or to assess one of these alternatives---simply do not capture all of the dimensions relevant to democratic change, such as commitments to political equality and freedom of expression [see @Schedler2007; @Wuttke2020].
-Another is that the relationships among these survey items have varied substantially over time [see @wuttke2020have]; this would violate the assumptions of the public opinion models used and would yield faulty estimates of democratic support.
-A third is that these survey questions do not ask respondents to prioritize democracy with regard to other values with which it may come into conflict, such as their partisanship, and so miss capturing the actual extent of support democracy would find among the public when it actually needed public support [see @Carey2020; @graham_democracy_2020; @McCoy2020].
+Methodologically, one possible issue is that support for democracy is multidimensional, and the survey questions used to measure it---which ask respondents to assess the desirability or appropriateness of democracy, to compare democracy to some undemocratic alternative, or to assess one of these alternatives---simply do not capture all of the dimensions relevant to democratic change, such as commitments to political equality and freedom of expression [see @Schedler2007; @Wuttke2020].
+Another is that the relationships among these survey items have varied substantially over time [see @Wuttke2021]; this would violate the assumptions of the public opinion models used and would yield faulty estimates of democratic support.
+A third is that these survey questions do not ask respondents how they prioritize democracy relative to other values with which it may come into conflict, such as their partisanship, and so miss capturing the true extent of support democracy would find among the public when public support was actually needed [see @Carey2020; @graham_democracy_2020; @McCoy2020].
 
@@
 Similarly, the effect of public support on democracy may depend on the extent to which those who support democracy are also dissatisfied with the current regime's performance; that is, that it is not democratic support that is important to democratic change, but rather unsatisfied democratic demand [see, e.g., @Qi2011].
-Of course, it could in fact be that democratic change does not actually depend on public opinion of any sort at all, but rather is an elite-driven phenomenon [see, e.g., Przeworski1991, @levitsky_how_2018].
-
-Although we could not exclude or identify any of them in this study, our reexamination reaffirmed @fariss_respect_2014, @juhl_measurement_2019, and Solt's [-@Solt2020a] suggestion that given the latent character of variables in political science, scholars should be vigilant in measurement uncertainty.
-
-At a time when democracy as seen as under threat around the world [e.g., @Diamond2015], taken together, Claassen (2020_a_,_b_) send what is ultimately a reassuring message: the fate of democracy rests with us, the public, and when democratic institutions are undermined, we will swing to their support and constitute "an obstacle to democratic backsliding" [@Claassen2020b, 51].
-Both of these conclusions may well be true, but the evidence we have, properly assessed, does not provide support for them.
-There can be no room for complacency.
+Of course, it could in fact be that democratic change does not actually depend on public opinion of any sort at all but instead is an elite-driven phenomenon [see, e.g., @levitsky_how_2018].
+
+We draw two conclusions.
+First, as latent variable measurement models become more commonly used, that it is absolutely necessary for researchers employing them to incorporate the associated uncertainty into analyses.
+Second, at a time when democracy as seen as under threat around the world [e.g., @Diamond2015], taken together, Claassen (2020$a$,_b_) send what is ultimately a reassuring message: the fate of democracy rests with us, the public, and when democratic institutions are undermined, we will swing to their support and constitute "an obstacle to democratic backsliding" [@Claassen2020b, 51].
+Both of these assertions may well be true, but the evidence we have, properly assessed, does not provide support for them.
+There is no room for complacency.
 
@@
 
-# Model Specification 
+# Method
 To examine the influence of empirical uncertainty, we conducted a three-step test. 
@@
 First, the survey items we used might not capture real public democratic attitudes since the number of indicators of democratic support is limited compared to indicators of other concepts like gender-egalitarianism (Solt, 2021??).
-Second, even if survey questions capture the support for the generic concept of democracy, they might still not be sufficient to capture the multi-faceted feature of democratic support due to the variation in understanding the concept across countries or over time or within country [@wuttke2020have;@van2017myth].
+Second, even if survey questions capture the support for the generic concept of democracy, they might still not be sufficient to capture the multi-faceted feature of democratic support due to the variation in understanding the concept across countries or over time or within country [@Wuttke2021;@van2017myth].
 As @van2017myth pointed out, without considering the varying understanding of democracy due to political and social development, the unchanged survey questions decrease the comparability of time series data.

### 2021-01-03 paper/dcpo_demsupport.Rmd
add take-home message to abstract

@@
 Does public support, in turn, respond thermostatically to changes in democracy?
-Two prominent recent studies (Claassen 2020a,b) have reinvigorated the classic hypothesis on the positive relationship between public support for democracy and regime survival--and challenged its reciprocal counterpart--by using a Bayesian latent variable approach to measure mass democratic support from cross-national survey data.
+Two prominent recent studies (Claassen 2020a,b) reinvigorated the classic hypothesis on the positive relationship between public support for democracy and regime survival--and challenged its reciprocal counterpart--by using a latent variable approach to measure mass democratic support from cross-national survey data.
 But such approaches come with concomitant measurement uncertainty, and neither study incorporated this uncertainty into its analyses.
@@
 Even with these improvements, however, our analyses fail to yield evidence in support of either hypothesis.
-[141/150 words]"
+These findings underscore the necessity of accounting for measurement uncertainty.
+[150/150 words]"
 keywords: ""

### 2021-01-04 paper/dcpo_demsupport.Rmd
revise methods section

@@
 # Method
-To examine the influence of empirical uncertainty, we conducted a three-step test. 
-The first step we made is to reproduce @Claassen2020a.
-Then, applying the method he described in the article, we replicated his IRT-based measurement of democratic mood and maintained the entire distribution of the predicted outcome instead of aggregating it to a single point estimate.
-Utilizing the estimated distribution, we involved uncertainty in the analysis of the influence of democratic mood on institutional democracy cross-nationally.
-In the third step, we applied the DCPO measurement and added one-third more data to the analysis to reduce potential effects of measurement biases and data spareness.
-We compared the outcomes of the three steps and showed as below that uncertainty is a critical factor in the studies of mass democratic attitude, which may alter the analytic conclusions. 
-We further showed that accounting for uncertainty is equivalently important when the latent-variable estimates play as a dependent variable in a study by replicating @Claassen2020b.
+We proceed in three steps.
+In our first step, we reproduce the original analyses of Claassen (2020$a$,_b_), which included only the point estimates of the latent variable of democratic support and so exclude its measurement uncertainty.
+In the second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.
+As our third step, we collect even more survey data---increasing these source data observations by one-fourth---and re-estimate democratic support using the superior DCPO measurement model, then conduct the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.
 
 ## Incorporating Uncertainty
-Given the measurement uncertainty derived by the inherent trail of latent constructs and its propagated effects on inferences about the relationship of substantive interests, it is strongly recommended to incorporate the measurement uncertainty in analysis models [@treier_democracy_2008; @Crabtree2015].
-Many scholars have accounted for measurement error in analyses as a final crucial part in their empirical studies [@Schnakenberg2014; @caughey_policy_2018].
-Moreover, recent studies on latent variable measurement highlighted the incorporation of measurement uncertainty when using their measures [@solis_measuring_2020; @gandhi_measuring_2020]. 
-However, measurement uncertainty has not attracted attention in the comparative public opinion field.
-Previous efforts on measuring dynamic comparative public opinion did not account for measurement uncertainty in analyses.
-
-Instead of employing the point estimates, we followed the recommendation and the approach of incorporating uncertainty in using latent variables [e.g., @Schnakenberg2014; @Crabtree2015].
-Specifically, in our replication of Claassen's [-@Claassen2020a] analysis models, we incorporated uncertainty using random draws from the posterior distributions. 
-We generated 1,000 duplicate versions of the analysis dataset, assigned to each a different random draw from the posterior distributions of public democratic support, performed the analyses repeatedly on each of these 1,000 versions of the dataset, and then combined the results following the rules set out in @Rubin1987.
+Although measurement uncertainty has yet not attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can bias coefficient estimates and standard errors.
+In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey_policy_2018, 254].
+
+Therefore, after we replicate the original analyses that used only the point estimates of democratic support, we incorporate the full distribution of the latent variable estimates.
+To do this, we replicate the latent variable estimation from the original survey data, duplicate each article's analysis dataset 1,000 times, and assign to each a different random draw from the posterior distribution of public democratic support.
+Then we perform each analysis repeatedly on its respective collection of datasets, and combine the results following the rules set out in @Rubin1987 [see, e.g., @Schnakenberg2014; @Crabtree2015].
 
@@
   dplyr::select(country, year) %>% 
-  unique() %>% 
+  distinct() %>% 
+  nrow()
+
+supdem_surv <- supdem %>%
+  dplyr::select(country, year, project) %>%
+  distinct() %>%
   nrow()
@@
   dplyr::select(country, year, item) %>% 
-  unique() %>% 
+  distinct() %>% 
+  nrow()
+
+dcpo_input_nc <- dcpo_input_raw1 %>% 
+  dplyr::select(country) %>% 
+  distinct() %>% 
+  nrow()
+
+dcpo_input_surv <- dcpo_input_raw1 %>%
+  dplyr::select(country, year, survey) %>%
+  distinct() %>%
+  separate(survey, c("surv1", "surv2"), sep=",", fill = "left") %>%
+  pivot_longer(cols = starts_with("surv")) %>%
+  filter(!is.na(value)) %>% 
   nrow()
@@
   dplyr::select(country, year) %>% 
-  unique() %>% 
+  distinct() %>% 
   nrow()
@@
 dcpo_input_ncyi <- dcpo_input_raw1 %>% 
-  dplyr::select(country, year, item) %>% 
-  unique() %>% 
+  dplyr::select(country, year, item, survey) %>% 
+  distinct() %>% 
+  separate(survey, c("surv1", "surv2"), sep=",", fill = "left") %>%
+  pivot_longer(cols = starts_with("surv")) %>%
+  filter(!is.na(value)) %>% 
   nrow()
@@
 increase_cyi <- sprintf("%2.1f", (dcpo_input_ncyi/supdem_ncyi - 1) * 100, 1)
+increase_surv <- sprintf("%2.1f", (dcpo_input_surv/supdem_surv - 1) * 100, 1)
 ```
@@
 ## A Better Measure of Democratic Support and More Data
-To reduce the uncertainty, we applied a more valid measurement, the DCPO model, to a bigger data set.
-The validation tests in @Solt2020a's paper corroborate that the DCPO model yields more accurate results than other latent variable measurements, either of @Claassen2019 Model 5 and @Caughey2019 model.
-The DCPO is superior to other measurements in several ways.
-The flexibility of the DCPO model in treating the data as their original scales, either dichotomous or ordinal, decreases information missing due to the potential scale change.
-For example, our data consists of 20,885 national responses as the result of measuring public attitude at ordinal scales, which can give us more nuances about public democratic support. 
-Second, to reduce the uncertainty in estimating countries that lie at the extreme ends of the public opinion spectrum [@Linzer2015], the estimates of mean public opinion are bounded, and the extent of polarization is included in the DCPO model.
-Third, to address the differences in item response across countries caused by factors other than public attitude or preference, a country-specific item bias is modelled as "a country-specific bias in the difficulty of each question" [@Solt2020a, 6].
-In short, the DCPO model has methodological advantages in keeping as much available information as possible, reducing uncertainty by bounding scales, and capturing the extent of polarization in public.
-
-In addition to applying the advanced DCPO measurement, we also collected as much available data as possible.
-We collected data on 62 items from 17 survey projects in 159 countries covering years from 1988 to 2020.
-Survey data was extracted automatically through the `DCPO` package for R [@Solt2020b].
-The DCPO package also automatically identifies the year in which the survey was conducted, which contributes to capturing the real relationship between public opinion and the level of democracy.
-Our data consists of `r dcpo_input_ncy` country-years and 1,861 national surveys, which is a `r increase_cy`% and 33.9% increase respectively over `r supdem_ncy` country-years and 1,390 national surveys used in Claassen's studies [-@Claassen2020a; -@Claassen2020b].
-Finally, using the DCPO model in the `DCPO` package, we attained 4,752 estimates for mass support for democracy, drawn from 144 countries with at least 2 country-years observed.
+As a further test of the classic arguments on democracy and public support, we apply the superior DCPO model to a bigger data set.
+The DCPO model has several advantages over the @Claassen2019 model used in Claassen (2020$a$,$b$).
+First, while the @Claassen2019 model dichotomizes responses and so discards some information provided by 50 of the 52 survey items employed in Claassen (2020$a$,_b_), the DCPO model makes use of all of the information available from these ordinal items [@Solt2020a, 5].
+Second, as the DCPO model includes both parameters for the dispersion of each survey item and for the standard deviation of aggregate public opinion in each country-year, it is a complete population-level item-response model and so, unlike the @Claassen2019 model, is explicitly derived from an individual-level model of survey responses [@Solt2020a, 3-4; see also @McGann2014].
+Third, to produce more sensible estimates of uncertainty for observations at the extremes of the scale [see @Linzer2015, 229], the DCPO model places bounds on its estimates of public opinion [@Solt2020a, 8].
+Further commending the DCPO model to us---and demonstrating that its advantages make a difference---the validation tests in @Solt2020a [, 10-12] reveal that it fits survey data on democratic support better than the @Claassen2019 model does.
+
+In addition to applying the superior DCPO model, we also assembled as much available data on democratic support as possible.
+We employed `r dcpo_input_ncyi` national opinions on democracy from `r dcpo_input_surv` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncy` opinions and `r supdem_surv` national surveys used in Claassen (2020$a$,_b_).^[These figures represent the survey data actually used in estimating public support for democracy; as in Claassen (2020$a$,_b_), countries for which two separate years of survey data were not available were excluded.]
+We used the `DCPO` package for R [@Solt2020b] to estimate the DCPO model on this expanded dataset.
 

### 2021-01-04 paper/dcpo_demsupport.Rmd
fuss with intro

@@
 
-We draw two conclusions.
-First, as latent variable measurement models become more commonly used, that it is absolutely necessary for researchers employing them to incorporate the associated uncertainty into analyses.
-Second, at a time when democracy as seen as under threat around the world [e.g., @Diamond2015], taken together, Claassen (2020$a$,_b_) send what is ultimately a reassuring message: the fate of democracy rests with us, the public, and when democratic institutions are undermined, we will swing to their support and constitute "an obstacle to democratic backsliding" [@Claassen2020b, 51].
+We draw two conclusions, one methodological, and one substantive.
+As latent variable measurement models become more commonly used, it is absolutely necessary for researchers employing them to incorporate the associated uncertainty into analyses.
+And, at a time when democracy as seen as under threat around the world [e.g., @Diamond2015], taken together, Claassen (2020$a$,$b$) send what is ultimately a reassuring message: the fate of democracy rests with us, the public, and when democratic institutions are undermined, we will swing to their support and constitute "an obstacle to democratic backsliding" [@Claassen2020b, 51].
 Both of these assertions may well be true, but the evidence we have, properly assessed, does not provide support for them.
@@
 We proceed in three steps.
-In our first step, we reproduce the original analyses of Claassen (2020$a$,_b_), which included only the point estimates of the latent variable of democratic support and so exclude its measurement uncertainty.
+In our first step, we reproduce the original analyses of Claassen (2020$a$,$b$), which included only the point estimates of the latent variable of democratic support and so exclude its measurement uncertainty.
 In the second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.
@@
 The DCPO model has several advantages over the @Claassen2019 model used in Claassen (2020$a$,$b$).
-First, while the @Claassen2019 model dichotomizes responses and so discards some information provided by 50 of the 52 survey items employed in Claassen (2020$a$,_b_), the DCPO model makes use of all of the information available from these ordinal items [@Solt2020a, 5].
+First, while the @Claassen2019 model dichotomizes responses and so discards some information provided by 50 of the 52 survey items employed in Claassen (2020$a$,$b$), the DCPO model makes use of all of the information available from these ordinal items [@Solt2020a, 5].
 Second, as the DCPO model includes both parameters for the dispersion of each survey item and for the standard deviation of aggregate public opinion in each country-year, it is a complete population-level item-response model and so, unlike the @Claassen2019 model, is explicitly derived from an individual-level model of survey responses [@Solt2020a, 3-4; see also @McGann2014].
@@
 In addition to applying the superior DCPO model, we also assembled as much available data on democratic support as possible.
-We employed `r dcpo_input_ncyi` national opinions on democracy from `r dcpo_input_surv` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncy` opinions and `r supdem_surv` national surveys used in Claassen (2020$a$,_b_).^[These figures represent the survey data actually used in estimating public support for democracy; as in Claassen (2020$a$,_b_), countries for which two separate years of survey data were not available were excluded.]
+We employed `r dcpo_input_ncyi` national opinions on democracy from `r dcpo_input_surv` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncy` opinions and `r supdem_surv` national surveys used in Claassen (2020$a$,$b$).^[These figures represent the survey data actually used in estimating public support for democracy; as in Claassen (2020$a$,$b$), countries for which two separate years of survey data were not available were excluded.]
 We used the `DCPO` package for R [@Solt2020b] to estimate the DCPO model on this expanded dataset.

### 2021-01-04 paper/dcpo_demsupport.Rmd
revise discussion and conclusion

@@
 Does public support, in turn, respond thermostatically to changes in democracy?
-Two prominent recent studies (Claassen 2020a,b) reinvigorated the classic hypothesis on the positive relationship between public support for democracy and regime survival--and challenged its reciprocal counterpart--by using a latent variable approach to measure mass democratic support from cross-national survey data.
+Two prominent recent studies (Claassen 2020a, 2020b) reinvigorated the classic hypothesis on the positive relationship between public support for democracy and regime survival---and challenged its reciprocal counterpart---by using a latent variable approach to measure mass democratic support from cross-national survey data.
 But such approaches come with concomitant measurement uncertainty, and neither study incorporated this uncertainty into its analyses.
@@
 We then work to minimize the measurement uncertainty in public support by bringing additional survey data and a superior model of public opinion.
-Even with these improvements, however, our analyses fail to yield evidence in support of either hypothesis.
-These findings underscore the necessity of accounting for measurement uncertainty.
-[150/150 words]"
+Even with these improvements, however, our analyses fail to yield evidence in support of either hypothesis, underscoring the necessity of accounting for measurement uncertainty.
+[149/150 words]"
 keywords: ""
@@
 ---
+Word count: 3920
 
 It has long been argued that democratic regimes and public support for them are mutually reinforcing: that high levels of public support ensure democracies remain strong, and that experience with democratic governance generates robust public support [see, e.g., @lipset_social_1959; @Easton1965].
-But the evidence for either side of this claim has been decidedly mixed.
+But the evidence for either part of this claim has been decidedly mixed.
 Countries with greater democratic support have been found to become stronger and more stable democracies [e.g., @Inglehart2005, 251-254] and just the opposite [@Fails2010, 182-183].
@@
 There are many plausible explanations for these null results, both methodological and theoretical.
-Methodologically, one possible issue is that support for democracy is multidimensional, and the survey questions used to measure it---which ask respondents to assess the desirability or appropriateness of democracy, to compare democracy to some undemocratic alternative, or to assess one of these alternatives---simply do not capture all of the dimensions relevant to democratic change, such as commitments to political equality and freedom of expression [see @Schedler2007; @Wuttke2020].
+Methodologically, one possible issue is that support for democracy is multidimensional, and the survey questions used to measure it simply do not capture all of the dimensions relevant to democratic change, such as commitments to political equality and freedom of expression [see @Schedler2007; @Wuttke2020].
 Another is that the relationships among these survey items have varied substantially over time [see @Wuttke2021]; this would violate the assumptions of the public opinion models used and would yield faulty estimates of democratic support.
@@
 
-From a theoretical perspective, the effect of democracy on public support may depend not on its mere existence but on its effectiveness [see, e.g., @Magalhaes2014] and particularly with regard to redistribution [see, e.g., @Krieckhaus2014].
-Similarly, the effect of public support on democracy may depend on the extent to which those who support democracy are also dissatisfied with the current regime's performance; that is, that it is not democratic support that is important to democratic change, but rather unsatisfied democratic demand [see, e.g., @Qi2011].
+From a theoretical perspective, the effect of democracy on public support may depend not on its mere existence but on its effectiveness [see @Magalhaes2014] and particularly with regard to redistribution [see @Krieckhaus2014].
+Similarly, the effect of public support on democracy may depend on the extent to which those who support democracy are also dissatisfied with the current regime's performance; that is, that it is not democratic support that is important to democratic change, but rather unsatisfied democratic demand [see @Qi2011].
 Of course, it could in fact be that democratic change does not actually depend on public opinion of any sort at all but instead is an elite-driven phenomenon [see, e.g., @levitsky_how_2018].
 
-We draw two conclusions, one methodological, and one substantive.
+We draw two conclusions, one methodological and one substantive.
 As latent variable measurement models become more commonly used, it is absolutely necessary for researchers employing them to incorporate the associated uncertainty into analyses.
-And, at a time when democracy as seen as under threat around the world [e.g., @Diamond2015], taken together, Claassen (2020$a$,$b$) send what is ultimately a reassuring message: the fate of democracy rests with us, the public, and when democratic institutions are undermined, we will swing to their support and constitute "an obstacle to democratic backsliding" [@Claassen2020b, 51].
+And, at a time when democracy as seen as under threat around the world [e.g., @Diamond2015], taken together, Claassen [-@Claassen2020a; -@Claassen2020b] send what is ultimately a reassuring message: the fate of democracy rests with us, the public, and when democratic institutions are undermined, we will swing to their support and constitute "an obstacle to democratic backsliding" [@Claassen2020b, 51].
 Both of these assertions may well be true, but the evidence we have, properly assessed, does not provide support for them.
@@
 We proceed in three steps.
-In our first step, we reproduce the original analyses of Claassen (2020$a$,$b$), which included only the point estimates of the latent variable of democratic support and so exclude its measurement uncertainty.
+In our first step, we reproduce the original analyses of Claassen [-@Claassen2020a; -@Claassen2020b], which included only the point estimates of the latent variable of democratic support and so exclude its measurement uncertainty.
 In the second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.
@@
 
-## A Better Measure of Democratic Support and More Data
+## Better Estimates of Democratic Support and More Data
 As a further test of the classic arguments on democracy and public support, we apply the superior DCPO model to a bigger data set.
-The DCPO model has several advantages over the @Claassen2019 model used in Claassen (2020$a$,$b$).
-First, while the @Claassen2019 model dichotomizes responses and so discards some information provided by 50 of the 52 survey items employed in Claassen (2020$a$,$b$), the DCPO model makes use of all of the information available from these ordinal items [@Solt2020a, 5].
+The DCPO model has several advantages over the @Claassen2019 model used in Claassen [-@Claassen2020a; -@Claassen2020b].
+First, while the @Claassen2019 model dichotomizes responses and so discards some information provided by 50 of the 52 survey items employed in Claassen [-@Claassen2020a; -@Claassen2020b], the DCPO model makes use of all of the information available from these ordinal items [@Solt2020a, 5].
 Second, as the DCPO model includes both parameters for the dispersion of each survey item and for the standard deviation of aggregate public opinion in each country-year, it is a complete population-level item-response model and so, unlike the @Claassen2019 model, is explicitly derived from an individual-level model of survey responses [@Solt2020a, 3-4; see also @McGann2014].
@@
 In addition to applying the superior DCPO model, we also assembled as much available data on democratic support as possible.
-We employed `r dcpo_input_ncyi` national opinions on democracy from `r dcpo_input_surv` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncy` opinions and `r supdem_surv` national surveys used in Claassen (2020$a$,$b$).^[These figures represent the survey data actually used in estimating public support for democracy; as in Claassen (2020$a$,$b$), countries for which two separate years of survey data were not available were excluded.]
+We employed `r dcpo_input_ncyi` national opinions on democracy from `r dcpo_input_surv` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncy` opinions and `r supdem_surv` national surveys used in Claassen [-@Claassen2020a; -@Claassen2020b].^[These figures represent the survey data actually used in estimating public support for democracy; as in Claassen [-@Claassen2020a; -@Claassen2020b], countries for which two separate years of survey data were not available were excluded.]
 We used the `DCPO` package for R [@Solt2020b] to estimate the DCPO model on this expanded dataset.
@@
 
-The results are presented in Figure&nbsp;\ref{fig:visualizeAJPS} (and numerically in Appendix Table&nbsp;[A1](#AJPSreplication)).
-In the pooled model (left panel), the aggregated measurement of democratic mood shows a positive effect on the institutional democratization in Claassen's original model, and the effect is statistically significant at the 0.05 level.
+Figure&nbsp;\ref{fig:visualizeAJPS} presents the reanalyses of the hypothesis that public support influences the level of democracy, with democratic support pooled for all countries (Claassen's 2020$a$, 128, Model 1) in the right panel and democratic support separated by regime type (Model 2) on the left.
+The uppermost set of results replicate @Claassen2020a, including by excluding measurement uncertainty, and reproduce that article's findings.
+The middle results introduce a single change: the uncertainty in the measurement of public support is taken into account.
+In both models, the positive coefficients for democratic support are no longer statistically significant.
+The bottom results also incorporate uncertainty but additionally replace the @Claassen2019 estimates of support with those based on DCPO and the expanded dataset; this change works to increase the number of observations analyzed as well.
+Although the confidence intervals shrink considerably, the coefficient estimates move much closer to zero; the hypothesis remains unsupported.
 
@@
 
-```{r visualizeAJPS, fig.cap= "\\label{fig:visualizeAJPS}The Effect of Democratic Support on Democratic Institutions", eval = TRUE, fig.width=7.5, fig.height=5}
+```{r visualizeAJPS, fig.cap= "\\label{fig:visualizeAJPS}The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=5}
 
@@
   labs(
-    title = "DV: Institutional Democratization",
+    title = "DV: V-Dem Liberal Democracy Index",
     subtitle = "Pooled"
@@
 
-```{r visualizedUncertainAJPS, fig.cap= "The Effect of Democratic Mood on Institutional Democratization Accounting for Uncertainty"}
+```{r visualizedUncertainAJPS, fig.cap= "The Effect of Public Support on Democracy with Uncertainty"}
 
@@
 
-However, when accounting for the uncertainty of the latent variable measurement of the mood, the significance disappears.
-We applied the DCPO and added one-third more data, resulting in a saliently shrink of the range of measurement uncertainty, but the confidence intervals still cut zero---that is, remaining statistically insignificant.^[The point estimates also alters.
-We attribute it to more information and better measuring method by DCPO.]
-A similar phenomenon also happens on the estimates of, for example, the second-time-unit lag of democratization and resource dependency.
-
-We further examined Claassen's regime specific model [@Claassen2020a: Model 2].
-The originally significant contribution of democratic mood in democratic regimes disappears, regardless whether more information and better method are applied.
-
 ```{r claassenAPSR}
@@
 
-```{r visualizedAPSR, fig.cap= "\\label{fig:visualizedAPSR} Effects of Democracy on Change in Mood", eval = TRUE, fig.width=7, fig.height=5}
+The importance of accounting for the measurement uncertainty appear more evident when the relevant variable plays as the dependent variable. 
+In Figure&nbsp;\ref{fig:visualizedAPSR}, we examine the thermostatic model of democratic support per @Claassen2020b [, 47, Models 1.1 and 1.2]. 
+The negative coefficient estimates of change in liberal democracy in the top set of results, which do not take uncertainty into account, imply that democratic mood decreases as democracy increases and vice versa.
+However, the middle results demonstrate that this thermostatic effect, too, no longer holds after the measurement uncertainty is accounted for. 
+And again, the bottom results reveal that the additional data and superior DCPO measurement model of our extension do not recover the original finding.
+
+```{r visualizedAPSR, fig.cap= "\\label{fig:visualizedAPSR} The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=5}
 
@@
   labs(
-    title = "DV: Democratic Mood",
+    title = "DV: Public Support for Democracy",
     subtitle = "Basic"
@@
 
-The importance of accounting for the measurement uncertainty appear more evident when the relevant variable plays as the dependent variable. 
-In Figure&nbsp;\ref{fig:visualizedAPSR}, we examined the thermostatic model of democratic mood [@Claassen2020b]. 
-The estimates without taking uncertainty into account imply that democratic mood decreases along with the progress of democratization. 
-Nevertheless, this effect no longer holds when the measurement uncertainty is involved.
-
-As previous operations, we tested if this alteration is caused by the data scarcity or estimating inefficiency. 
-When more data and better method are applied, the confidence intervals do shrink yet remain statistically insignificant. 
-We observed similar changes after adjusting the effect of domestic corruption [@Claassen2020b, 41].
-
 # Discussion
-In short, the main empirical findings about the estimated effect of public democratic support on democracy or vice versa are not replicable when measurement uncertainty is accounted for, even using better measurement and more data.
-
-There are several potential causes for the null results.
-First, the survey items we used might not capture real public democratic attitudes since the number of indicators of democratic support is limited compared to indicators of other concepts like gender-egalitarianism (Solt, 2021??).
-Second, even if survey questions capture the support for the generic concept of democracy, they might still not be sufficient to capture the multi-faceted feature of democratic support due to the variation in understanding the concept across countries or over time or within country [@Wuttke2021;@van2017myth].
-As @van2017myth pointed out, without considering the varying understanding of democracy due to political and social development, the unchanged survey questions decrease the comparability of time series data.
-Third, these survey items might capture public democratic support, but we do not have enough data to compensate for the fragmentation and sparseness of available comparative public opinion data, which is doomed to high uncertainty.
-Given the nature trail of latent variables and specific characters of comparative public opinion data, performing analyses based on the strong assumption that comparative public attitudes are perfectly measured might exaggerate scholars' certainty methodologically and obscure a proper substantive evaluation of theoretical claims.
-
-In addition, there are alternative explanations about the relationship between public attitude and democratic changes.
-First, democratic changes might be more associated with elites than with the public.
-Elites are thought to play a critical role in preserving democratic stability by respecting the limits on their behaviors [@weingast_political_1997].
-However, after the Cold War, many democracies backslid and were imperiled worldwide because elected leaders lacked commitment to democratic norms and the public even did not notice that [@bermeo_democratic_2016; @levitsky_how_2018; @waldner_unwelcome_2018].
-
-Second, given that the measures for democratic development are from experts, the gulf between public perception and elites' perception on important democratic principles [@mcclosky_consensus_1964] might result in the disconnection between public perception of democracy and experts' measures of the levels of democracy.
-A recent study also lent support to that claim by demonstrating the polarized public cannot reach a consensus with experts on democratic erosion [@carey_searching_2019].
-
-Third, the study of democratic support is suffered from "inputism," which focuses on public evaluations of input-side, institutional designs, but ignores the output-side, policy outcome or implementation; however, the output-side better predicts democratic support [@van2017myth].
-
-Lastly, verbal support in a pro-democratic stance is usually higher than behavioral commitments [@prothro_fundamental_1960]. 
-Since there is a difference in public support for democracy between "in the abstract" and "under specific propositions" [@bartels_ethnic_2020], recent studies questioned whether conventional measures of public support for democracy could capture real public commitment to democracy.
-By using survey experiments, @graham_democracy_2020 pointed out a "fundamental blind spot" in traditional measures of public democratic support: general survey questions cannot capture voters' willingness and behavioral commitment to democratic principles in specific context where voters need to choose between democratic norms and their partisan identification or policy preference.
-"fail to capture voters’ willingness to act on their commitment to democracy precisely when democracy is at stake"
-It turned out that voters subordinated democratic norms to their partisan preference by not electorally penalizing their candidates who endorse measures that violate norms.
-Furthermore, voters support/encourage democratic norm-eroding policies when their co-partisans are in power rather than only tolerating anti-democratic policies [@Carey2020].
+In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support has a positive effect on democracy and democracy a negative effect on support are not empirically supported once measurement uncertainty is taken into account, even when a superior estimate of public support and more data are used.
+
+There are several potential methodological explanations for these null results.
+One issue is that the survey items employed---which ask respondents to assess the desirability or appropriateness of democracy, to compare democracy to some undemocratic alternative, or to assess one of these alternatives---may not capture every aspect of democratic support necessary for it to play its hypothesized roles in the classic theory.
+If only those who profess to prefer democracy to its alternatives _and also_ value freedom of expression, freedom of association, and pluralism of opinion will take appropriate action when democracy is threatened, then this measure is inadequate to its purpose [see, e.g., @Schedler2007].
+Moreover, given the multi-faceted nature of democratic attitudes, even the inclusion of such questions in unidimensional public opinion models such as those provided by @Claassen2019 or @Solt2020a are unlikely to be sufficient [see, e.g., @Wuttke2020].
+Another issue is that even if these survey questions do capture support for the generic concept of democracy, these measurement models might still be incapable of suitably capturing democratic support due to the variation in understanding the concept across countries or over time within countries [@Wuttke2021].
+Yet another is that this measure provides no assessment of the _relative_ importance the public affords democracy.
+It provides no information on the extent to which other values, such as policy preferences or partisanship, weigh more heavily---and there is growing evidence that, at least in the United States, there are many for whom these other considerations excuse substantial transgressions against democracy [see @bartels_ethnic_2020; @Carey2020; @graham_democracy_2020; @McCoy2020].
+
+There are theoretical explanations for the null results as well.
+With regard to how levels of democracy affect public support, we note that even the proponents of the classic argument did not contend that the mere existence of democratic institutions, no matter how consistently feckless and ineffective, would generate support among the public: instead, they maintained, public support would be gained through experience with government performance that was generally effective [@lipset_social_1959, 86-89; @Easton1965, 119-120].
+There is some empirical support for this, with government effectiveness positively related to public support among democracies and negatively related in non-democracies [@Magalhaes2014]. 
+The finding of @Krieckhaus2014 that income inequality is strongly negatively related to public support in democracies suggests that performance regarding redistribution is particularly important.
+Relatedly, on the reverse part of the classic argument, @Qi2011 suggests that democratic support alone cannot be expected to generate democratic change and oppose backsliding.
+Instead, that work contends, it is the combination of democratic support and dissatisfaction with current regime performance that generates demand for greater democracy.
+And we must be open to the possibility that no theoretical elaboration, no respecification of these models will reveal relationships between public opinion and democracy.
+Democratic backsliding may simply be primarily a matter of elite decisionmaking [see, e.g., @levitsky_how_2018].
+Regardless, these explanations indicate that there remains much work to be done in the empirical study of public support and democracy.
 
 # Conclusion
-In this note, we reexamined the findings from Claassens' [-@Claassen2020a; -@Claassen2020b] paper that public support helps the survival of democracy and democratic development has a thermostatic effect on public support for democracy.
-We demonstrated the importance of incorporating measurement uncertainty in analyzing the relationship between public support and democratic development.
-Even using more data and the sophisticated DCPO model, the measurement uncertainty made the original positive relationships irreplicable regardless whether public support was an independent or dependent variable.
-
-The high uncertainty might come from several sources: the problems of self-report survey data that might not capture the public attitude, the sparse data on the complex concept of democratic support, the relationship between democratic changes and elites, the different public understanding of democracy, and the gap between the public attitude and public commitment.
-
-Although we could not identify or exclude any one of these possible sources in this paper, a basic lesson from this reexamination is simple: given the inherent uncertainty accompanying latent public opinion and its propagated effects in analyses, incorporating measurement uncertainty is a safer way to infer the relationship between public opinion and other substantive interest especially in comparative politics, in which the measurement uncertainty of public opinion is further exacerbated by the sparse and incomparability of indicators.
+In this letter, we reexamined the findings from Claassen [-@Claassen2020a; -@Claassen2020b], two articles that maintain that public support helps the survival of democracy and democratic development has a thermostatic effect on public support.
+We demonstrated the importance of incorporating measurement uncertainty in analyzing the relationship between public support and democracy.
+Taking uncertainty into account rendered both articles' conclusions without empirical support, even when we employed the more sophisticated DCPO measurement model and additional data.
+
+This points to the absolute necessity of incorporating measurement uncertainty into analyses that include latent variables.
+As the use of latent variables grows more common in political science, both researchers and readers should be aware that these variables' concomitant measurement uncertainty cannot be neglected.
+
+The null results reached in this letter could arise from several sources.
+We identified a number of potential shortcomings in the measurement of democratic support and ways in which the analysis models might be underspecified.
+All of these could and should be explored in future research, though there are also theoretically grounded reasons to suspect that the relationships are in fact negligible.
+In any event, the sanguine assessment that readers may draw from Claassen [-@Claassen2020a; -@Claassen2020b]---that the fate of democracies depend on public support, and when eroded, their publics will rally to them---is not supported by the current evidence.
+Those who would defend democracy have no grounds to be complacent.
 

### 2021-01-05 paper/dcpo_demsupport.Rmd
fuss a bit with discussion of dem->support results

@@
 ---
-Word count: 3920
+Word count: 3923
 
@@
 The negative coefficient estimates of change in liberal democracy in the top set of results, which do not take uncertainty into account, imply that democratic mood decreases as democracy increases and vice versa.
-However, the middle results demonstrate that this thermostatic effect, too, no longer holds after the measurement uncertainty is accounted for. 
-And again, the bottom results reveal that the additional data and superior DCPO measurement model of our extension do not recover the original finding.
+However, the middle results demonstrate that this thermostatic effect, too, does not  hold after the measurement uncertainty is accounted for. 
+And again, the bottom results reveal that the additional data and superior DCPO measurement model of our extension do not provide support for the original conclusion.
 
@@
 # Discussion
-In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support has a positive effect on democracy and democracy a negative effect on support are not empirically supported once measurement uncertainty is taken into account, even when a superior estimate of public support and more data are used.
+In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support has a positive effect on democracy and democracy a negative effect on support are not empirically supported when measurement uncertainty is correctly taken into account, even when a superior estimate of public support and more data are used.
 

### 2021-01-07 paper/dcpo_demsupport.Rmd
Adding key words; typo correction

--- 2021-01-04 paper/dcpo_demsupport.Rmd
@@
 [149/150 words]"
-keywords: ""
+keywords: "Democratization, public support, regime survival, measurement uncertainty, IRT"
 date: "`r format(Sys.time(), '%B %d, %Y')`"
@@
 
-Figure&nbsp;\ref{fig:visualizeAJPS} presents the reanalyses of the hypothesis that public support influences the level of democracy, with democratic support pooled for all countries (Claassen's 2020$a$, 128, Model 1) in the right panel and democratic support separated by regime type (Model 2) on the left.
+Figure&nbsp;\ref{fig:visualizeAJPS} presents the reanalyses of the hypothesis that public support influences the level of democracy, with democratic support pooled for all countries (Claassen's 2020$a$, 128, Model 1) in the left panel and democratic support separated by regime type (Model 2) on the right.
 The uppermost set of results replicate @Claassen2020a, including by excluding measurement uncertainty, and reproduce that article's findings.
@@
 # Discussion
-In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support has a positive effect on democracy and democracy a negative effect on support are not empirically supported once measurement uncertainty is taken into account, even when a superior estimate of public support and more data are used.
+In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support has a positive effect on democracy and that democracy has a negative effect on support are not empirically supported once measurement uncertainty is taken into account, even when a superior estimate of public support and more data are used.
 

### 2021-01-11 paper/dcpo_demsupport.Rmd
revised 1201

@@
 # Discussion
-In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support has a positive effect on democracy and that democracy has a negative effect on support are not empirically supported once measurement uncertainty is taken into account, even when a superior estimate of public support and more data are used.
+In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support has a positive effect on democracy and democracy a negative effect on support are not empirically supported once measurement uncertainty is taken into account, even when a superior estimate of public support and more data are used.
 

### 2021-01-13 paper/dcpo_demsupport.Rmd
removing the names from the manuscript

@@
 title: "Democracy, Public Support, and Measurement Uncertainty"
-thanks: "The authors contributed equally to this work.  Corresponding author: [yuehu@mail.tsinghua.edu.cn](mailto:yuehu@mail.tsinghua.edu.cn).  Current version: `r format(Sys.time(), '%B %d, %Y')`."
-author:
-- name: Yuehong 'Cassandra' Tai
-  affiliation: University of Iowa
-- name: Yue Hu
-  affiliation: Tsinghua University
-- name: Frederick Solt
-  affiliation: University of Iowa
+# thanks: "The authors contributed equally to this work.  Corresponding author: [yuehu@mail.tsinghua.edu.cn](mailto:yuehu@mail.tsinghua.edu.cn).  Current version: `r format(Sys.time(), '%B %d, %Y')`."
+# author:
+# - name: Yuehong 'Cassandra' Tai
+#   affiliation: University of Iowa
+# - name: Yue Hu
+#   affiliation: Tsinghua University
+# - name: Frederick Solt
+#   affiliation: University of Iowa
 abstract: "Do democratic regimes depend on public support to avoid backsliding?
@@
 [149/150 words]"
-keywords: "Democratization, public support, regime survival, measurement uncertainty, IRT"
+keywords: "Democratization, public support, regime survival, measurement uncertainty, IRT."
 date: "`r format(Sys.time(), '%B %d, %Y')`"
@@
 ```{r compare_n, eval=TRUE}
-if (!file.exists(here::here("data", "supdem raw survey marginals.tab"))) {
-  dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>% 
-    read_csv(col_types = "cdcddcdc") %>% 
-    write_csv("data/supdem raw survey marginals.tab")
-}
+# if (!file.exists(here::here("data", "supdem raw survey marginals.tab"))) {
+#   dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>% 
+#     read_csv(col_types = "cdcddcdc") %>% 
+#     write_csv("data/supdem raw survey marginals.tab")
+# }
 

### 2021-01-14 paper/appendix.Rmd
add title and adjust width

@@
 ---
-title: "[dcpo_demsupport] Appendix"
+title: "Democracy, Public Support, and Measurement Uncertainty: Appendix"
 classoption: landscape
@@
   pdf_document
+
 ---
@@
   hline(i = 8, border = officer::fp_border()) %>% 
-  add_header_lines(values = paste0("Number of Observations: ", unique(df_tableAJPS$n))) %>% 
-  autofit() 
+  add_header_lines(values = "Estimates of Democratic Support on Democratic Institutions") %>% 
+  autofit() %>% 
+  fit_to_width(8.5)
+
 ```
@@
   hline(i = 6, border = officer::fp_border()) %>% 
-  autofit()
+  add_header_lines(values = "Estimates of Democratic Institutions on Democratic Support") %>% 
+  autofit() %>% 
+  fit_to_width(8.5)
 

### 2021-04-22 paper/appendix.Rmd

--- 2020-10-27 paper/appendix.Rmd
@@
 ---
-title: "[dcpo_demsupport] Appendix"
+title: "Democracy, Public Support, and Measurement Uncertainty: Appendix"
 classoption: landscape
 output:
-  pdf_document
+  pdf_document:
+    fig_caption: true
+    latex_engine: xelatex
 ---
@@
 \renewcommand{\thepage}{A\arabic{page}}
-# APPENDIX A: Tabular Results
-
-# Table A1. Estimates of Democratic Support on Democratic Institutions{#AJPSreplication}
-<!-- ## Models of Effect of Democratic Support on Institutional Democratization {#replicateAJPS} -->
 
@@
   hline(i = 8, border = officer::fp_border()) %>% 
-  add_header_lines(values = paste0("Number of Observations: ", unique(df_tableAJPS$n))) %>% 
-  autofit() 
+  autofit() %>% 
+  fit_to_width(8.5) %>% 
+  set_caption("Estimates of Democratic Support on Democratic Institutions")
+
 ```
-
-# Table A2. Estimates of Democratic Institutions on Democratic Support{#APSRreplication}
 
@@
   hline(i = 6, border = officer::fp_border()) %>% 
-  autofit()
+  autofit() %>% 
+  fit_to_width(8.5) %>% 
+  set_caption("Estimates of Democratic Institutions on Democratic Support")
 

### 2021-04-22 paper/dcpo_demsupport.Rmd

@@
 ---
-Word count: 3923
+
+(Word count: 3628)
 

### 2021-04-22 paper/dcpo_demsupport_appendix.Rmd
trimmed data updating

@@
     template: svm-latex-ms2.tex
-title: "[dcpo_demsupport] Appendix"
-thanks: "Corresponding author: [yuehong-tai@uiowa.edu](mailto:yuehong-tai@uiowa.edu). Current version: `r format(Sys.time(), '%B %d, %Y')`."
+title: "Democracy, Public Support, and Measurement Uncertainty"
+subtitle: "Online Appendix"
+# thanks: "Corresponding author: [yuehong-tai@uiowa.edu](mailto:yuehong-tai@uiowa.edu). Current version: `r format(Sys.time(), '%B %d, %Y')`."
 author:
-- name: Yuehong 'Cassandra' Tai
-  affiliation: University of Iowa
-- name: Yue Hu
-  affiliation: Tsinghua University
-- name: Frederick Solt
-  affiliation: University of Iowa
+# - name: Yuehong 'Cassandra' Tai
+#   affiliation: University of Iowa
+# - name: Yue Hu
+#   affiliation: Tsinghua University
+# - name: Frederick Solt
+#   affiliation: University of Iowa
 abstract: ""
@@
 
-```{r claassen_input}
-dcpo_input_raw1 <- read_csv("data/dcpo_input_raw.csv", col_types = "cdcddcd") %>% 
+## Numeric Results of the Visualized Results
+
+```{r claassen_input_APSR}
+dcpo_input_raw1 <- read_csv("../data/dcpo_input_raw.csv", col_types = "cdcddcd") %>% 
   filter(!(str_detect(survey, "army_wvs") & # WVS obs identified as problematic by Claassen 
@@
 
+```{r claassen_input_AJPS}
+claassen_input_raw1 <- read_csv("../data/dcpo_input_raw.csv", col_types = "cdcddcd") %>% 
+  filter(!(str_detect(survey, "army_wvs") & # WVS obs identified as problematic by Claassen 
+             ((country=="Albania" & year==1998) |
+                (country=="Indonesia" & (year==2001 | year==2006)) |
+                (country=="Iran" & year==2000) |
+                (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
+                (country=="Vietnam" & year==2001)) |
+             (str_detect(item, "strong_wvs") &
+                ((country=="Egypt" & year==2012) |
+                   (country=="Iran" & (year==2000 | year==2007)) | # 2005 in Claassen
+                   (country=="India") |
+                   (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
+                   (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
+                   (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
+                   (country=="Vietnam" & year==2001))) |
+             (country %in% c("Puerto Rico", "Northern Ireland", 
+                             "SrpSka Republic", "Hong Kong SAR China")))) %>%
+  with_min_yrs(2)
+
+claassen_input <- DCPOtools::format_claassen(claassen_input_raw1)
+save(claassen_input, file = here::here("data", "claassen_input.rda"))
+
+```
+
 ```{r claassen_replication_input}
@@
 
-claassen_input_cy <- read_csv("data/dcpo_input_raw.csv",
+claassen_input_cy <- read_csv("../data/dcpo_input_raw.csv",
                               col_types = "cdcddcd") %>%           # 1813 obs
@@
 
-claassen_replication_input_raw1 <- read_csv("data/claassen_input_raw.csv", col_types = "cdcddcd") %>% 
+claassen_replication_input_raw1 <- read_csv("../data/claassen_input_raw.csv", col_types = "cdcddcd") %>% 
   filter(!(str_detect(item, "army_wvs") & # WVS obs identified as problematic by Claassen 
@@
 
-```{r claassen_input}
-claassen_input_raw1 <- read_csv("data/dcpo_input_raw.csv", col_types = "cdcddcd") %>% 
-  filter(!(str_detect(survey, "army_wvs") & # WVS obs identified as problematic by Claassen 
-             ((country=="Albania" & year==1998) |
-                (country=="Indonesia" & (year==2001 | year==2006)) |
-                (country=="Iran" & year==2000) |
-                (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
-                (country=="Vietnam" & year==2001)) |
-             (str_detect(item, "strong_wvs") &
-                ((country=="Egypt" & year==2012) |
-                   (country=="Iran" & (year==2000 | year==2007)) | # 2005 in Claassen
-                   (country=="India") |
-                   (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
-                   (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
-                   (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
-                   (country=="Vietnam" & year==2001))) |
-             (country %in% c("Puerto Rico", "Northern Ireland", 
-                             "SrpSka Republic", "Hong Kong SAR China")))) %>%
-  with_min_yrs(2)
-
-claassen_input <- DCPOtools::format_claassen(claassen_input_raw1)
-save(claassen_input, file = here::here("data", "claassen_input.rda"))
-
-```
-
-```{r claassenWUncertainty}
+```{r claassenUncertainty, cache=TRUE}
 load(here::here("data", "claassen_replication_input.rda"))
@@
 
+df_controls <- read_csv(here::here("data", "control_variables_ajps.csv"),
+                        col_types = cols(.default = col_double(),
+                                         country = col_character(),
+                                         country_name = col_character(),
+                                         ISO = col_character(),
+                                         Region_UN = col_character())) %>% 
+  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
+         country = countrycode::countrycode(country0, "country.name", "country.name"),
+         regime = Vdem_regime > 1) %>% 
+  filter(year >= firstyear) # using trimmed data as Claassen
+
 df_theta <- purrr::map(1:1000, function(x) {
@@
     mutate(year = first_year + row_number() - 1) %>% 
-    pivot_longer(cols = ls_country,
+    pivot_longer(cols = !year,
                  names_to = "country",
@@
     arrange(country, year) %>% 
-    left_join(df_controls, by = c("country" = "Country", "year" = "Year")) %>% 
+    left_join(df_controls, by = c("country", "year")) %>% 
     plm::pdata.frame(index = c("country", "year"))
@@
 
-# Conclusion
-
 \pagebreak

### 2021-04-23 paper/memo/memo.Rmd
add /paper/memo/memo.Rmd and .pdf

---
title: |
    | Democracy, Public Support, and Measurement Uncertainty:
    | Memo to Reviewers
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2021-04-24 paper/dcpo_demsupport.Rmd
prevent conflict

@@
 title: "Democracy, Public Support, and Measurement Uncertainty"
-# thanks: "The authors contributed equally to this work.  Corresponding author: [yuehu@mail.tsinghua.edu.cn](mailto:yuehu@mail.tsinghua.edu.cn).  Current version: `r format(Sys.time(), '%B %d, %Y')`."
-# author:
-# - name: Yuehong 'Cassandra' Tai
-#   affiliation: University of Iowa
-# - name: Yue Hu
-#   affiliation: Tsinghua University
-# - name: Frederick Solt
-#   affiliation: University of Iowa
+thanks: "The authors contributed equally to this work.  Corresponding author: [yuehu@mail.tsinghua.edu.cn](mailto:yuehu@mail.tsinghua.edu.cn).  Current version: `r format(Sys.time(), '%B %d, %Y')`."
+author:
+- name: Yuehong 'Cassandra' Tai
+  affiliation: University of Iowa
+- name: Yue Hu
+  affiliation: Tsinghua University
+- name: Frederick Solt
+  affiliation: University of Iowa
 abstract: "Do democratic regimes depend on public support to avoid backsliding?

### 2021-04-24 paper/memo/memo.Rmd

@@
 ---
+output: 
+  pdf_document:
+    citation_package: natbib
+    keep_tex: true
+    fig_caption: true
+    latex_engine: pdflatex
+    template: ../svm-latex-ms2.tex
 title: |
-    | Democracy, Public Support, and Measurement Uncertainty:
+    | Democracy, Public Support, and Measurement Uncertainty
     | Memo to Reviewers
 date: "`r format(Sys.time(), '%B %d, %Y')`"
-output: pdf_document
+fontsize: 11pt
+spacing: double
+bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
+biblio-style: apsr
+citecolor: black
+linkcolor: black
+endnote: no
+header-includes:
+      - \usepackage{array}
+      - \usepackage{caption}
+      - \usepackage{graphicx}
+      - \usepackage{siunitx}
+      - \usepackage{colortbl}
+      - \usepackage{multirow}
+      - \usepackage{hhline}
+      - \usepackage{calc}
+      - \usepackage{tabularx}
+      - \usepackage{threeparttable}
+      - \usepackage{wrapfig}
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+options(tinytex.verbose = TRUE)
+
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, eval = FALSE, dpi = 300)
+
+# If you haven't install `DCPOtools`
+# remotes::install_github("fsolt/DCPOtools")
+
+if (!require(pacman)) install.packages("pacman")
+library(pacman)
+
+# load all the packages you will use below 
+p_load(
+  dataverse, # data scraping
+  DCPOtools,
+  boot, plm, # analysis
+  flextable, kableExtra, modelsummary, # tabulation
+  gridExtra,
+  latex2exp, # visualization
+  rstan, # Bayesian estimation
+  broom, tidyverse, janitor, # data wrangling
+  dotwhisker # visualization
+)
+
+# Functions preload
+set.seed(313)
+
+get_legend<-function(myggplot){
+  tmp <- ggplot_gtable(ggplot_build(myggplot))
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
+  legend <- tmp$grobs[[leg]]
+  return(legend)
+}
+
+# Theme setup
+theme_set(theme_minimal())
+source(here::here("R", "uiowa_palette.R"))
 ```
 
-## R Markdown
+Again, this is things to do only.
+Remember to go back to the reviews and mine them for compliments when writing the memo.
+Temporarily(?) listed by reviewer; reordering later to match the sequence of the article will likely be more effective, given the overlap and conversation among reviewers.
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+## Reviewer #1
+[Issue 17](https://github.com/fsolt/dcpo_dem_mood/issues/17) My primary concern is that the method by which measurement error is included / added is not sufficiently explicated and demonstrated to be valid (e.g., using Monte Carlo experiments), especially in the time-series, cross-sectional context which is of interest.
+The authors cite several applied articles - none of which appears to be methodological in nature - as well as a classic book by Rubin on multiple imputation in surveys - which is a distinct topic.
+This is unfortunate because I have several concerns with the method as used and the results which are produced, as described below.
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
+[Issue 16](https://github.com/fsolt/dcpo_dem_mood/issues/16) First, I believe that the measurement error of variables included in the model should be factored in.
+Many of these variables (democracy, corruption, economic output) cannot be directly observed and are therefore prone to measurement error.
+If one believes that (a) estimating the effect of one variable on another requires incorporating measurement error; and (b) control variable Z needs to be included because it likely has an effect on both X and Y, then to accurately adjust for the effects of Z requires that X, Y and Z all have included measurement error.
 
-```{r cars}
-summary(cars)
-```
+[Issue 24](https://github.com/fsolt/dcpo_dem_mood/issues/23) Second, the results in Figure 2, based on models using democratic support as a dependent variable, are puzzling.
+They appear to show that democratic support is entirely disconnected from such prominent features of the political environment as the level of democracy and economic development.
+Not only are these effects insignificant, but their point estimates are almost exactly zero in magnitude.
+The effects of lagged democratic support are also zero, which is even more implausible because it suggests that democratic support in one year is entirely disconnected from its levels in previous years.
+In other words, Denmark is as likely to have a low value next year as China is likely to have a high value.
+This stands in contrast with much of existing research on democratic support and political culture.
 
-## Including Plots
+[Issue 23](https://github.com/fsolt/dcpo_dem_mood/issues/23) Alternatively, the authors might use a different method for factoring in the error due to measurement: structural equation models, which, in essence, combine a measurement model and the subsequent regression model in one step.
+In contrast to the method proposed in the present paper, SEMs benefits from a substantial methodological literature (e.g., Bollen & Noble 2011; Skrondal & Rabe-Hesketh 2004).
+Indeed, one of the articles cited by the current paper (Juhl 2019) adopts exactly this approach.
+Bollen & Noble.
+2011.
+Structural Equation Models and The Quantification of Behavior.
+Proceedings of the National Academy of Sciences 108: 15639-15646; Skrondal & Rabe-Hesketh.
+2004.
+Generalized Latent Variable Modeling: Multilevel, Longitudinal, and Structural Equation Models.
+Taylor & Francis.
 
-You can also embed plots, for example:
+[Issue 22](https://github.com/fsolt/dcpo_dem_mood/issues/22) I have two additional concerns with the paper.
+First, the authors have not replicated all of Claassen's main results.
+Claassen 2020a argues that within-country analyses are desirable and uses generalized method of moments (GMM) estimators to obtain these.
+Claassen (2020b) uses first difference models; he also focuses on the separate effects of the electoral and liberal components of democracy.
+I suggest that the authors replicate all the main results from Claassen (2020a; 2020b), rather than an ad hoc subset of these.
 
-```{r pressure, echo=FALSE}
-plot(pressure)
-```
+[Issue 18](https://github.com/fsolt/dcpo_dem_mood/issues/18) Second, in addition to the results obtained from the latent variable model developed and used by Claassen, the authors present the results obtained from an entirely different latent variable model.
+Although intriguing, no evidence at all is presented to support the claim (repeated throughout) that this method is "superior" to Claassen's (reference is made to an unpublished working paper).
+Indeed, it would appear from the short summary of this model that it adds additional parameters to Claassen's model.
+Yet more complicated models may overfit the data and are not necessarily more accurate.
+I propose that evidence supporting the superiority of this method be supplied, or alternatively, the authors just focus on replicating Claassen's models.
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+## Reviewer #2
+[Issue 17](https://github.com/fsolt/dcpo_dem_mood/issues/17) The MS deals with measurement error by treating mismeasured variables as if they were fully imputed, and following Rubin's standard multiple imputation rules.
+If I understand correctly, this is what Blackwell, Honaker, and King (2017) call "multiple overimputation" (MO)—a fact that should probably be noted in the MS, given that Blackwell et al.
+provide the most comprehensive exposition of this method that I am aware of.
+...
+More can be done, however, to show that this critique itself is robust.
+First, the MS should provide more detail on the theoretical justification for MO and the conditions under which it performs well.
+How does it perform when measurement error is strongly correlated across variables, as is likely to be the case in the models with lagged DVs?
+
+[Issue 23](https://github.com/fsolt/dcpo_dem_mood/issues/23) It would be useful to show that the critique still holds with an alternative measurement-error approach, such as Treier and Jackman's (2008) method of composition.
+
+[Issue 16](https://github.com/fsolt/dcpo_dem_mood/issues/16) Despite the MS's assertion of the "absolute necessity" of accounting for measurement error, the MS does not do so for any of the other variables in the analysis.
+Given that Treier and Jackman's analysis focused on uncertainty in measures of democracy, the most obvious omission is the V-DEM democracy measure itself (which, according to the V-DEM documentation, does appear to have associated uncertainty estimates).
+
+[Issue 24](https://github.com/fsolt/dcpo_dem_mood/issues/24) Also, I could not help but be struck by the extreme attenuation of the coefficient estimates in Figure 2, which almost suggest that the variables were generated from independent distributions.
+In particular, can it really be the case that lagged support has no conditional association with current support?
+If so, then I think some explanation is required, or else readers will think that some mistake has been made.
+
+[Issue 20](https://github.com/fsolt/dcpo_dem_mood/issues/20) Finally, I am concerned about the over-time smoothing induced by the random-walk prior in measurement model.
+In county-years without survey data, this prior will impute the latent variable by interpolating between adjacent years, and in years with data it may still make over-time changes smoother than the raw data suggest.
+From a descriptive perspective this is largely a virtue, but in models that rely for causal identification on sharp over-time shifts, such as the thermostatic model, it can be a big problem.
+There is no magic fix for this problem, but readers should still be given more information on how much "work" the prior is doing—what proportion of country-years are missing data, how informative is the prior relative to the likelihood, and so on.
+
+## Reviewer #3
+
+[Issue 19](https://github.com/fsolt/dcpo_dem_mood/issues/19) I, for my part, however, have been left in disbelief by this mechanistic model of the link between public opinion and regime qualities.
+Although I am quite confident that policy preferences and policy change react thermostatically to each other in yearly rhythms, I find it hard to believe that such fundamental things as regime preferences and regime qualities underly such short-term cycles.
+Regime preferences and regime qualities are more enduring, inert and their changes are too glacial for a thermostatic model of short-term cycles to plausibly capture the underlying dynamic in the co-evolution of public opinion and regime qualities.
+Since Claassen uses V-Dem data to measure democratic regime qualities, which are entirely expert judgements, his models demonstrate at best that expert and lay assessments of democracy react thermostatically to each other.
+
+[Issue 19](https://github.com/fsolt/dcpo_dem_mood/issues/19) Another reason why I doubt Claassen's findings is evidence showing that the same level of support for democracy hides over firmly encultured differences in how people in different countries understand democracy (Kirsch & Welzel 2018), which often leads people to mis-estimate their own countries' democraticness (Kruse, Ravlik & Welzel 2018).
+Hence, levels of support for democracy are strictly speaking incomparable across culturally diverse sets of societies.
+Also relevant in this context are findings showing that what matters for democratic regime stability and change is not how much people say that they support democracy but what values motivate them to do so.
+Specifically, mass support for democracy operates in favor of democracy only in conjunction with emancipative values but not in disconnection from these values (Brunkert, Kruse & Welzel 2018).
+Hence, to establish the regime-relevance of public opinion, looking merely at levels of democratic mass support is misleading.
+Instead, it is more promising to use value priorities to distinguish different types of democracy supporters and estimate their demographic distribution.
+
+Kirsch, H. & C. Welzel (2018). "Democracy Misunderstood: Authoritarian Notions of Democracy around the Globe." Social Forces 91: 1-33 (DOI: 10.1093/sf/soy114).
+
+Kruse, S., M.
+Ravlik & C.
+Welzel (2018).
+"Democracy Confused: When People Mistake the Absence of Democracy for Its Presence." Journal of Cross-Cultural Psychology 49: 1-21 (DOI: 10.1177/0022022118821437).
+
+Brunkert, L., S.
+Kruse & C.
+Welzel (2018).
+"A Tale of Culture-bound Regime Evolution: The Centennial Democratic Trend and Its Recent Reversal." Democratization 25: 1-23 (DOI: 10.1080/13510347.2018.1542430).
+
+## Reviewer #4
+
+[Issue 19](https://github.com/fsolt/dcpo_dem_mood/issues/19) First, I found the 'Discussion' section somewhat underwhelming.
+The discussion is mainly about data issues that could explain the lack of a relationship, not the substantive question.
+If that is the case, the letter makes a negligible contribution because it only finds that the findings of two specific studies are not robust (not that there is no relationship between public support for democracy and regime survival).
+I would like the author to engage a bit more in substantive debates.
+
+[Issue 15](https://github.com/fsolt/dcpo_dem_mood/issues/15) Second, I was a bit confused by Figures 1 and 2.
+My understanding is that accounting for uncertainty should only affect the standard errors, but in the figures it also affects the point estimates.
+This is the case even in the models 'Claassen W/Uncertainty.'
+
+[Issue 18](https://github.com/fsolt/dcpo_dem_mood/issues/18) Third, the author should provide more information on the differences between the models employed by Claassen and those that she/he employs (perhaps in an appendix).
+
+[Issue 17](https://github.com/fsolt/dcpo_dem_mood/issues/17) We need more information on (1) how uncertainty is integrated into the models of Claassen, and (2) the DCPO models.
+
+## Editor
+Both Reviewers 1 and 2 want more evidence, explanation, and/or justification of the alternative method used to incorporate measurement error.
+Reviewer 1 seems to specifically suggest a simulation study.
+If such a study already addresses the performance of the method (either analytically or with simulations) in a context with temporally and serially correlated errors, it would make sense to reference that work in the main text.
+Reviewer 2 also asks for clarification and/or justification of the imputation and smoothing processes used in the analysis. 
+Reviewers 1 & 2 also ask why measurement error in other variables are not included in the analysis.
+Reviewers 1 & 2 also ask why lagged support is unrelated to current support.
+
+Reviewers 1, 2, and 4 all ask why the results for Claassen's model but accounting for measurement error (second set of results) also yield different point estimates.
+The revised version should address this directly, including by better explaining the method(s) used.
+If the different in point estimates is due to multiple deviations from Claassen's approach (e.g., in both the smoothing _and_ the use of the errors), I would suggest introducing and presenting each intermediate modification of the research design incrementally to avoid confusion and help readers assess how much of the change in results is due to the incorporation of measurement error vs.
+other modelling or measurement decisions.
+Analytical transparency is key.
+
+Evidence to address these various methodological questions and issues issues may be included in the response to reviewers and/or the Supplemental Information (if it would help readers appreciate the methods used) as needed.
+For instance, I could imagine some readers benefitting from having the estimating equations included in the Supplemental Information in order to appreciate how measurement error is incorporated into the estimates as well as more information about the levels of measurement used (mentioned as an important difference by Reviewer 3).
+While Reviewer 1 asks for all results from the original two studies be replicated as well, these additional replications need only be included in the paper or SI to the extent that they are relevant to the relationship between support and democracy at the core of this Letter's focus.
+
+As you expand the SI, please keep in mind our limit of 25 pages. Material solely for editors and reviewers that would not be relevant for readers can remain in the response to reviewers.
+
+Finally, Reviewers 2, 3, and 4 offer various suggestions for how to more effectively frame or discuss the substantive or theoretical (rather than measurement or methodological) implications of your contribution.
+We hope their feedback is useful as you revise your Letter.
+
+\pagebreak
+
+# References
+
+<div id="refs"></div>

### 2021-04-27 paper/dcpo_demsupport.Rmd
getting the tidy version of pgmm for the AJPS replication

@@
     fig_caption: true
-    latex_engine: pdflatex
+    latex_engine: xelatex
     template: svm-latex-ms2.tex
@@
   rstan, # Bayesian estimation
-  broom, tidyverse, janitor, # data wrangling
+  glue,
+  broomExtra, tidyverse, janitor, # data wrangling
+  drhutools,
   dotwhisker # visualization
@@
 set.seed(313)
+
+source("../R/tidy_pgmm.r")
 
@@
 theme_set(theme_minimal())
-source(here::here("R", "uiowa_palette.R"))
 ```
@@
 ```{r dcpo_input_raw}
-dcpo_input_raw <- DCPOtools::dcpo_setup(vars = read_csv(here::here("data-raw", "mood_dem.csv"),
+dcpo_input_raw <-
+  DCPOtools::dcpo_setup(vars = read_csv(here::here("data-raw", "mood_dem.csv"),
                                         col_types = "cccccc"),
@@
 ```{r dcpo_input, eval=TRUE}
-dcpo_input_raw1 <- read_csv(here::here("data", "dcpo_input_raw.csv"), col_types = "cdcddcd") %>% 
-  filter(!(str_detect(survey, "army_wvs") & # WVS obs identified as problematic by Claassen 
-                 ((country=="Albania" & year==1998) |
-                      (country=="Indonesia" & (year==2001 | year==2006)) |
-                      (country=="Iran" & year==2000) |
-                      (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
-                      (country=="Vietnam" & year==2001)) |
+dcpo_input_raw1 <-
+  read_csv(here::here("data", "dcpo_input_raw.csv"), col_types = "cdcddcd") %>%
+  filter(!(
+    str_detect(survey, "army_wvs") &
+      # WVS obs identified as problematic by Claassen
+      ((country == "Albania" & year == 1998) |
+         (country == "Indonesia" &
+            (year == 2001 | year == 2006)) |
+         (country == "Iran" & year == 2000) |
+         (country == "Pakistan" &
+            (year == 1997 | year == 2001)) | # 1996 in Claassen
+         (country == "Vietnam" & year == 2001)
+      ) |
       (str_detect(item, "strong_wvs") &
-                      ((country=="Egypt" & year==2012) |
-                           (country=="Iran" & (year==2000 | year==2007)) | # 2005 in Claassen
-                           (country=="India") |
-                           (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
-                           (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
-                           (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
-                           (country=="Vietnam" & year==2001))) |
-                 (country %in% c("Puerto Rico", "Northern Ireland", 
-                                 "SrpSka Republic", "Hong Kong SAR China")))) %>%
+         ((country == "Egypt" & year == 2012) |
+            (country == "Iran" &
+               (year == 2000 | year == 2007)) | # 2005 in Claassen
+            (country == "India") |
+            (country == "Pakistan" &
+               (year == 1997 | year == 2001)) | # 1996 in Claassen
+            (country == "Kyrgyzstan" &
+               (year == 2003 | year == 2011)) |
+            (country == "Romania" &
+               (year == 1998 | year == 2005 | year == 2012)) |
+            (country == "Vietnam" & year == 2001)
+         )) |
+      (
+        country %in% c(
+          "Puerto Rico",
+          "Northern Ireland",
+          "SrpSka Republic",
+          "Hong Kong SAR China"
+        )
+      )
+  )) %>%
   with_min_yrs(2)
@@
 vcovHC_se <-  function(x) {
-  plm::vcovHC(x, method="arellano", cluster="group") %>% 
+  plm::vcovHC(x, method="arellano", cluster="group") %>%  #default setting
     diag() %>% 
@@
 
-df_result_cls <- map(ls_mod, function(mod){
-  result <- plm(mod, model = "pooling", data = sd.plm)
-  df_result <- tidy(result, conf.int = TRUE) %>%
+ls_iv <- c("plm::lag(SupDem_trim, 1)",
+           "plm::lag(SupDem_Democ, 1) + plm::lag(SupDem_Autoc, 1)")
+
+ls_method <- c("plm", "pgmm")
+
+ls_eq <- glue("Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + {ls_iv} + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)")
+
+ls_mod <- c(
+  glue("plm({ls_eq}, model = 'pooling', data = sd.plm)"),
+  glue(
+    "pgmm({ls_eq} | plm::lag(Libdem_VD, 3:5), data = sd.plm, effect='individual', model='onestep', transformation='ld', indexes=c('Country', 'Year'))"
+  )
+)
+
+df_result_cls <- map(ls_mod, function(mod) {
+  result <- eval(parse(text = mod))
+
+  if (class(result) == "plm") {
+    tidy(result, conf.int = TRUE) %>%
       mutate(std.error = vcovBK_se(result),
              n = nobs(result))
+  } else{
+    tidy(result, conf.int = TRUE) %>%
+      mutate(std.error = vcovHC_se(result),
+             n = nobs(result))
+  }
+
 })

### 2021-04-27 R/broom_utilities.R

@@ -1,0 +1,604 @@
+# Rename only those columns in a data frame that are present. Example:
+#
+# rename2(
+#   tibble(dog = 1),
+#   cat = dog,
+#   mouse = gerbil
+# )
+#
+rename2 <- function(.data, ...) {
+    dots <- quos(...)
+    present <- purrr::keep(dots, ~ quo_name(.x) %in% colnames(.data))
+    rename(.data, !!!present)
+}
+
+exponentiate <- function(data) {
+    data <- mutate_at(data, vars(estimate), exp)
+    
+    if ("conf.low" %in% colnames(data)) {
+        data <- mutate_at(data, vars(conf.low, conf.high), exp)
+    }
+    
+    data
+}
+
+#' Coerce a data frame to a tibble
+#'
+#' A thin wrapper around [tibble::as_tibble()], except checks for
+#' rownames and adds them to a new column `.rownames` if they are
+#' interesting (i.e. more than `1, 2, 3, ...`). This function is
+#' meant for use inside of `augment.*` methods.
+#'
+#' @param data A [base::data.frame()] or [tibble::tibble()].
+#'
+#' @return A `tibble` potentially with a `.rownames` column
+#' @noRd
+#'
+as_augment_tibble <- function(data) {
+    
+    if (inherits(data, "matrix") & is.null(colnames(data))) {
+        stop("The supplied `data`/`newdata` argument was an unnamed matrix. ",
+             "Please supply a matrix or dataframe with column names.")
+    }
+    
+    tryCatch(
+        df <- as_tibble(data),
+        error = function(cnd) {
+            stop("Could not coerce data to `tibble`. Try explicitly passing a",
+                 "dataset to either the `data` or `newdata` argument.",
+                 call. = FALSE
+            )
+        }
+    )
+    
+    if (has_rownames(data)) {
+        df <- tibble::add_column(df, 
+                                 .rownames = rownames(data), 
+                                 .before = TRUE)
+    }
+    df
+}
+
+#' Convert a data.frame or matrix to a tibble
+#' 
+#' This function is meant for use inside `tidy.*` methods.
+#'
+#' @param x a data.frame or matrix
+#' @param new_names new column names, not including the rownames
+#' @param new_col the name of the new rownames column
+#'
+#' @return a tibble with rownames moved into a column and new column
+#' names assigned
+#' @noRd
+as_tidy_tibble <- function(x, new_names = NULL, new_column = "term") {
+    
+    if (!is.null(new_names) && length(new_names) != ncol(x)) {
[…]

### 2021-04-27 R/tidy_pgmm.r

@@ -1,0 +1,43 @@
+source("../R/broom_utilities.R")
+
+tidy.pgmm <- function(x,
+                      conf.int = FALSE,
+                      conf.level = 0.95,
+                      ...) {
+    result <- summary(x)$coefficients %>%
+        tibble::as_tibble(rownames = "term") %>%
+        dplyr::rename(
+            estimate = Estimate,
+            std.error = `Std. Error`,
+            statistic = `z-value`,
+            p.value = `Pr(>|z|)`
+        )
+    
+    if (conf.int) {
+        ci <- confint(x, level = conf.level) %>% 
+            as.data.frame() %>% 
+            rownames_to_column(var = "term") %>% 
+            dplyr::rename(
+                conf.low = `2.5 %`,
+                conf.high = `97.5 %`
+            )
+        result <- dplyr::left_join(result, ci, by = "term")
+    }
+    
+    result
+}
+
+
+glance.pgmm <- function(x, ...) {
+    s <- summary(x)
+    as_glance_tibble(
+        chisq.sargan = unname(s$sargan$statistic),
+        df.sargan = unname(s$sargan$parameter),
+        p.sargan = unname(s$sargan$p.value),
+        chisq.wald = unname(s$wald.coef$statistic),
+        df.wald = unname(s$wald.coef$parameter),
+        p.wald = unname(s$wald.coef$p.value),
+        nobs = stats::nobs(x),
+        na_types = "rrrrrii"
+    )
+}

### 2021-04-27 paper/dcpo_demsupport.Rmd
issues in num of country name at 434

@@
                  values_to = parameter_name) %>%
-    arrange(country, year)
+    dplyr::arrange(country, year)
   return(df_temp)
@@
     #           by = c("year", "country")) %>%
-    left_join(sd_control, by = c("country", "year")) %>% 
-    mutate(theta_dem = theta * regime,
+    dplyr::left_join(sd_control, by = c("country", "year")) %>% 
+    dplyr::mutate(theta_dem = theta * regime,
            theta_aut = theta * (1 - regime)) %>% 

### 2021-04-28 paper/dcpo_demsupport.Rmd
presenting the orginal works in a table in the appendix

--- 2021-04-27 paper/dcpo_demsupport.Rmd
@@
 output: 
-  pdf_document:
-    citation_package: natbib
-    keep_tex: true
-    fig_caption: true
+  bookdown::pdf_document2:
+    fig_caption: yes
+    keep_tex: yes
+    toc: FALSE
     latex_engine: xelatex
-    template: svm-latex-ms2.tex
+    # template: svm-latex-ms2.tex
+
 title: "Democracy, Public Support, and Measurement Uncertainty"
 thanks: "The authors contributed equally to this work.  Corresponding author: [yuehu@mail.tsinghua.edu.cn](mailto:yuehu@mail.tsinghua.edu.cn).  Current version: `r format(Sys.time(), '%B %d, %Y')`."
-author:
-- name: Yuehong 'Cassandra' Tai
-  affiliation: University of Iowa
-- name: Yue Hu
-  affiliation: Tsinghua University
-- name: Frederick Solt
-  affiliation: University of Iowa
+
+# author:
+# - name: Yuehong 'Cassandra' Tai
+#   affiliation: University of Iowa
+# - name: Yue Hu
+#   affiliation: Tsinghua University
+# - name: Frederick Solt
+#   affiliation: University of Iowa
+
 abstract: "Do democratic regimes depend on public support to avoid backsliding?
@@
 keywords: "Democratization, public support, regime survival, measurement uncertainty, IRT."
+
 date: "`r format(Sys.time(), '%B %d, %Y')`"
+editor_options: 
+  markdown: 
+    wrap: sentence
+tables: true # enable longtable and booktabs
+citation_package: natbib
 fontsize: 11pt
-spacing: double
-bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
+linestretch: 1.5 # double spacing using linestretch 1.5
+bibliography: dcpo_demsupport.bib
+# bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
 # csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl
@@
 
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, eval = FALSE, dpi = 300)
+knitr::opts_chunk$set(
+  echo = FALSE,
+  message = FALSE,
+  warning = FALSE,
+  eval = FALSE,
+  dpi = 300
+)
 
@@
   rstan, # Bayesian estimation
-  glue,
-  broomExtra, tidyverse, janitor, # data wrangling
+  broomExtra, tidyverse, janitor, glue, # data wrangling
   drhutools,
@@
 
-```{r dataInput}
+```{r dataInput, eval=TRUE}
 
@@
 
-```{r claassenAJPS}
+```{r claassenAJPS, eval=TRUE}
 # Pooled model -----
@@
   result <- eval(parse(text = mod))
+})
+
+tidy_result_cls <- map(df_result_cls, function(result) {
+  df_result <- tidy(result, conf.int = TRUE)
 
   if (class(result) == "plm") {
-    tidy(result, conf.int = TRUE) %>%
-      mutate(std.error = vcovBK_se(result),
-             n = nobs(result))
+     mutate(df_result, std.error = vcovBK_se(result))
   } else{
-    tidy(result, conf.int = TRUE) %>%
-      mutate(std.error = vcovHC_se(result),
-             n = nobs(result))
+    mutate(df_result, std.error = vcovHC_se(result))
   }
@@
 
-save(df_result_cls, file = here::here("output", "estimates_clsMeanAJPS.RDS"))
+glance_result_cls <- map(df_result_cls, glance)
+
+#save(df_result_cls, file = here::here("output", "estimates_clsMeanAJPS.RDS"))
 ```
@@
 
+# References  {-}
+
+<div id = 'refs'></div>
+
 \pagebreak
 
-# References
-
-<div id="refs"></div>
+# Online Supplementary Materials {-}
+# (APPENDIX) Appendix {-}
+# Numeric Results for Replicating @Claassen2020a
+
+```{r cls2020a, results='asis', eval = TRUE}
+ls_result_cls <-
+  map2(tidy_result_cls, glance_result_cls, function(aTidy, aGlance) {
+    ls_sum <- list(tidy = aTidy,
+                   glance = aGlance)
+
+    class(ls_sum) <- "modelsummary_list"
+
+    return(ls_sum)
+  })
+
+names(ls_result_cls) <- c("Pooled OLS 1", "Pooled OLS 2", "GMM 1", "GMM 2")
+
+names_coef <- c(
+  "(Intercept)" = "(Intercept)",
+  "plm::lag(Libdem_VD, 1:2)1" = "Democracy[t-1]",
+  "plm::lag(Libdem_VD, 1:2)2"  = "Democracy[t-2]",
+  "plm::lag(SupDem_trim, 1)" = "Support[t-1]",
+  "plm::lag(lnGDP_imp, 1)" = "Log~GDP~per~capita[t-1]",
+  "plm::lag(GDP_imp_grth, 1)"  = "GDP~per~capita~growth[t-1]",
+  "plm::lag(Libdem_regUN, 1)" = "Regional~democracy[t-1]",
+  "plm::lag(Pr_Muslim, 1)" = "Percent~Muslim[t-1]",
+  "plm::lag(Res_cp_WDI_di, 1)" = "Resource~dependence[t-1]"
+)
+
+modelsummary(ls_result_cls, 
+             stars = TRUE,
+             coef_map = names_coef, 
+             output = "latex") %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+\pagebreak
+
+# Numeric Results for Replicating @Claassen2020b

### 2021-04-28 R/tidy_pgmm.r

@@ -31,13 +31,17 @@ tidy.pgmm <- function(x,
 glance.pgmm <- function(x, ...) {
     s <- summary(x)
     as_glance_tibble(
-        chisq.sargan = unname(s$sargan$statistic),
-        df.sargan = unname(s$sargan$parameter),
-        p.sargan = unname(s$sargan$p.value),
-        chisq.wald = unname(s$wald.coef$statistic),
-        df.wald = unname(s$wald.coef$parameter),
-        p.wald = unname(s$wald.coef$p.value),
+        # chisq.sargan = unname(s$sargan$statistic),
+        # df.sargan = unname(s$sargan$parameter),
+        # p.sargan = unname(s$sargan$p.value),
+        # chisq.wald = unname(s$wald.coef$statistic),
+        # df.wald = unname(s$wald.coef$parameter),
+        # p.wald = unname(s$wald.coef$p.value),
+        # arellano.bond1 = unname(x$m1$statistic[1,]),
+        # arellano.bond2 = unname(x$m2$statistic[1,]),
         nobs = stats::nobs(x),
-        na_types = "rrrrrii"
+        # n.country = length(x$residuals),
+        n.inst = dim(x$W[[1]])[2],
+        na_types = "ii"
     )
 }

### 2021-04-29 paper/dcpo_demsupport.Rmd
figuring the country-year matching in `claassenUnicertaintyAJPS`

@@
 
-ls_mod <-
-  paste0(
-    "Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + ",
-    c(
-      "plm::lag(SupDem_trim, 1)",
-      "plm::lag(SupDem_Democ, 1) + plm::lag(SupDem_Autoc, 1)"
-    ),
-    "+ plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)"
-  )
-
 ls_iv <- c("plm::lag(SupDem_trim, 1)",
@@
 ```{r claassenUncertaintyAJPS}
+claassen_replication_input$data <- claassen_replication_input$data %>% 
+  janitor::clean_names() %>% 
+  DCPOtools::with_min_yrs(2)
 
@@
 ```{r dcpoPointAJPS}
+
 ls_country <- levels(dcpo_input$data$kk)
@@
 ```{r claassenAPSR}
+df_result_cls <- map(ls_mod, function(mod) {
+  result <- eval(parse(text = mod))
+})
+
 sd.plm <- pdata.frame(x, index = c("Country", "Year"))
 
-mods <- vector(mode = "list")
-
-mods[[1]] <- plm(
+ls_mods <- vector(mode = "list")
+
+ls_mods[["ECM1.1"]] <- plm(
   diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Libdem_z, lag = 1)
   + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1),
-  sd.plm,
+  data = sd.plm,
   model = "pooling"
 )
-mods[[2]] <- plm(
+
+ls_mods[["ECM1.2"]] <- plm(
   diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Libdem_z, lag = 1)
@@
   + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1),
+  data = sd.plm,
+  model = "pooling"
+)
+
+ls_mods[["FD1.1"]] <-
+  plm(
+    SupDem_trim ~ Libdem_z + lnGDP_imp,
+    model = "fd",
+    data = sd.plm,
+    index = "Country"
+  )
+
+ls_mods[["FD1.2"]] <-
+  plm(
+    SupDem_trim ~ Libdem_z + lnGDP_imp + Corrup_TI_z,
+    model = "fd",
+    data = sd.plm,
+    index = "Country"
+  )
+
+ls_mods[["ECM2.1"]] <-
+  plm(
+    diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Polyarchy_z, lag = 1)
+    + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)
+    + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1),
     sd.plm,
     model = "pooling"
+  )
+ls_mods[["FD2.1"]] <-
+  plm(
+    diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Polyarchy_z, lag = 1)
+    + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)
+    + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1) + diff(Corrup_TI_z, lag = 1)
+    + plm::lag(Corrup_TI_z, 1),
+    sd.plm,
+    model = "pooling"
+  )
+
+# FD models
+
+ls_mods[["ECM2.2"]] <-
+  plm(
+    SupDem_trim ~ Polyarchy_z + Liberal_z + lnGDP_imp,
+    model = "fd",
+    data = sd.plm,
+    index = "Country"
+  )
+ls_mods[["FD2.2"]] <-
+  plm(
+    SupDem_trim ~ Polyarchy_z + Liberal_z + lnGDP_imp + Corrup_TI_z,
+    model = "fd",
+    data = sd.plm,
+    index = "Country"
   )
@@
 
-save(df_result_clsAPSR, file = here::here("output", "estimates_clsMeanAPSR.RDS"))
+#save(df_result_clsAPSR, file = here::here("output", "estimates_clsMeanAPSR.RDS"))
 ```

### 2021-04-29 paper/dcpo_demsupport.Rmd
clean claassen_replication and get country number

@@
 ```{r claassenUncertaintyAJPS}
-claassen_replication_input$data <- claassen_replication_input$data %>% 
+claassen_replication <- read_csv(here::here("data", "claassen_replication.csv"),
+                   col_types = "cdcddcdc") %>% 
   janitor::clean_names() %>% 
   DCPOtools::with_min_yrs(2)
+
+length(unique(claassen_replication$country))
 

### 2021-04-29 paper/dcpo_demsupport.Rmd
original analysis in nice table

--- 2021-04-29 paper/dcpo_demsupport.Rmd
@@
 
-```{r claassenAPSR}
-df_result_cls <- map(ls_mod, function(mod) {
-  result <- eval(parse(text = mod))
-})
+```{r claassenAPSR, eval = TRUE}
 
@@
   )
-ls_mods[["FD2.1"]] <-
+ls_mods[["ECM2.2"]] <-
   plm(
@@
 
-ls_mods[["ECM2.2"]] <-
+ls_mods[["FD2.1"]] <-
   plm(
@@
 
-df_result_clsAPSR <- map(mods, function(aMod){
+df_result_clsAPSR <- map(ls_mods, function(aMod){
   tidy(aMod, conf.int = TRUE) %>%
-    mutate(std.error = vcovHC_se(aMod),
-           n = nobs(aMod))
+    mutate(std.error = vcovHC_se(aMod))
 })
@@
 
-```{r cls2020a, results='asis', eval = TRUE}
+```{r num-cls2020a, results='asis', eval = TRUE}
 ls_result_cls <-
@@
 # Numeric Results for Replicating @Claassen2020b
+
+```{r num-cls2020b, results='asis', eval = TRUE}
+names_coef <- c(
+  "(Intercept)" = "(Intercept)",
+  "plm::lag(SupDem_trim, 1:2)1" = "Democratic\n Mood\n (t-1)",
+  "plm::lag(SupDem_trim, 1:2)2" = "Democratic\n Mood\n (t-2)",
+  "diff(Libdem_z, lag = 1)" = "Liberal\n Democracy\n (Difference)",
+  "Libdem_z" = "Liberal\n Democracy\n (Difference)",
+  "plm::lag(Libdem_z, 1)" = "Liberal\n Democracy\n (t-1)",
+  "diff(Polyarchy_z, lag = 1)" = "Electoral\n Democracy\n (Difference)",
+  "Polyarchy_z" = "Electoral\n Democracy\n (Difference)",
+  "plm::lag(Polyarchy_z, 1)" = "Electoral\n Democracy\n (t-1)",
+  "diff(Liberal_z, lag = 1)" = "Minoritarian\n Democracy\n (Difference)",
+  "Liberal_z" = "Minoritarian\n Democracy\n (Difference)",
+  "plm::lag(Liberal_z, 1)" = "Minoritarian\n Democracy\n (t-1)",
+  "diff(lnGDP_imp, lag = 1)" = "Log GDP\n per capita\n (Difference)",
+  "lnGDP_imp" = "Log GDP\n per capita\n (Difference)",
+  "plm::lag(lnGDP_imp, 1)" = "Log GDP\n (t-1)",
+  "diff(Corrup_TI_z, lag = 1)" = "Corruption\n (Difference)",
+  "Corrup_TI_z" = "Corruption\n (Difference)",
+  "plm::lag(Corrup_TI_z, 1)" = "Corruption\n (t-1)"
+)
+
+modelsummary(ls_mods, 
+             stars = TRUE,
+             coef_map = names_coef, 
+             output = "latex") %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```

### 2021-04-29 paper/dcpo_demsupport.Rmd
landscape

@@
       - \usepackage{wrapfig}
+      - \usepackage{fullpage}
+      - \usepackage{lscape} #better for printing, page displayed vertically, content in landscape mode, \usepackage{pdflscape} better for screen, page displayed horizontally, content in landscape mode
 ---
@@
 
-length(unique(claassen_replication$country))
-
-ls_country <- unique(claassen_replication_input$data$country)
-first_year <- min(claassen_replication_input$data$year)
+# length(unique(claassen_replication$country))
+# 
+# ls_country <- unique(claassen_replication_input$data$country)
+# first_year <- min(claassen_replication_input$data$year)
+
+ls_country <- unique(claassen_replication$country)
+first_year <- min(claassen_replication$year)
 
@@
 # (APPENDIX) Appendix {-}
-# Numeric Results for Replicating @Claassen2020a
+# Numeric Results for Replicating Claassen 2020a
 
@@
 
-# Numeric Results for Replicating @Claassen2020b
+# Numeric Results for Replicating Claassen 2020b
+
+\begin{landscape}
 
@@
 ```
+
+\end{landscape}

### 2021-05-03 paper/dcpo_demsupport.Rmd
cls uncertain

@@
 
+names(tidy_result_cls) <- names(glance_result_cls) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
+
 #save(df_result_cls, file = here::here("output", "estimates_clsMeanAJPS.RDS"))
@@
 ```{r claassenUncertaintyAJPS}
-claassen_replication <- read_csv(here::here("data", "claassen_replication.csv"),
-                   col_types = "cdcddcdc") %>% 
+claassen_replication <- readRDS("../data/claassen_replication.rds") %>% 
   janitor::clean_names() %>% 
   DCPOtools::with_min_yrs(2)
-
-# length(unique(claassen_replication$country))
-# 
-# ls_country <- unique(claassen_replication_input$data$country)
-# first_year <- min(claassen_replication_input$data$year)
 
@@
 
-df_result_clsUncertain <- map(mod_ls, estimate_cls)
-
-save(df_result_clsUncertain, file = here::here("output", "estimates_clsAJPS.RDS"))
+ls_iv <- c("plm::lag(theta, 1)", 
+    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) ")
+
+ls_method <- c("plm", "pgmm")
+
+ls_eq <- glue("Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + {ls_iv} + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)")
+
+ls_mod <- c(
+    glue("plm({ls_eq}, model = 'pooling', data = aData)"),
+    glue(
+        "pgmm({ls_eq} | plm::lag(Libdem_VD, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('Country', 'Year'))"
+    )
+)
+
+tidy_result_clsUncertain <- map(ls_mod, possibly(function(aMod){ # reading a model
+  result <- map(df_cls, function(aData){ # applying to the 1000 datasets
+    eval(parse(text = aMod))
+  })
+
+  result_vars <- ifelse(class(result[[1]])[1] == "plm", 
+                        mitools::MIextract(result, fun = vcovBK_se),
+                        mitools::MIextract(result, fun = vcovHC_se))
+  result_betas <- mitools::MIextract(result, fun = coef)
+
+  summary(mitools::MIcombine(results = result_betas, 
+                             variance = result_vars)) %>% 
+    rownames_to_column(var = "term") %>%
+        rename(conf.low = `(lower`,
+               conf.high = `upper)`,
+               estimate = results) %>%
+        filter(!str_detect(term, "(Intercept)"))
+}, otherwise = NA_real_))
+
+save(tidy_result_clsUncertain, file = here::here("output", "estimates_clsAJPS.RDS"))
 ```

### 2021-05-03 paper/dcpo_demsupport.Rmd
ifelse doesn't work for mi weirdly, trying if_else perhaps

@@
 
-tidy_result_clsUncertain <- map(ls_mod, possibly(function(aMod){ # reading a model
+tidy_result_clsUncertain <- map(ls_mod, function(aMod){ # reading a model
   result <- map(df_cls, function(aData){ # applying to the 1000 datasets
@@
 
+  result_betas <- mitools::MIextract(result, fun = coef)
+
+  ## Not work with ifelse
   result_vars <- ifelse(class(result[[1]])[1] == "plm", 
-                        mitools::MIextract(result, fun = vcovBK_se),
-                        mitools::MIextract(result, fun = vcovHC_se))
-  result_betas <- mitools::MIextract(result, fun = coef)
+                        eval(mitools::MIextract(result, fun = vcovBK_se)),
+                        eval(mitools::MIextract(result, fun = vcovHC_se)))
 
@@
         filter(!str_detect(term, "(Intercept)"))
-}, otherwise = NA_real_))
+})
 

### 2021-05-04 paper/dcpo_demsupport.Rmd
replicated the gmm for ajps

@@
   boot, plm, # analysis
-  flextable, kableExtra, modelsummary, # tabulation
+  flextable, 
+  kableExtra, modelsummary, # tabulation
   gridExtra,
@@
 
-estimate_cls <- function(aModel, aType = "pooling") {
-  if (aType == "gmm") {
-    result_cls_1k <- map(df_cls, function(aDataset) {
-      pgmm(
-        as.formula(aModel),
-        effect = "individual",
-        model = "onestep",
-        transformation = "ld",
-        indexes = c("Country", "Year"),
-        data = aDataset
-      )
-    })
-
-    result_vars_cls_1k <-
-      mitools::MIextract(result_cls_1k, fun = vcovHC_se)
-
-  } else {
-    result_cls_1k <- map(df_cls, function(aDataset) {
-      plm::plm(aModel,
-               model = "pooling",
-               data = aDataset)
-    })
-
-    result_vars_cls_1k <-
-      mitools::MIextract(result_cls_1k, fun = vcovBK_se)
-  }
-
-  result_betas_cls_1k <-
-    mitools::MIextract(result_cls_1k, fun = coef)
-
-  df_result_cls <-
-    summary(
-      mitools::MIcombine(results = result_betas_cls_1k, variance = result_vars_cls_1k)
-    ) %>% rownames_to_column(var = "term") %>%
-    rename(conf.low = `(lower`,
-           conf.high = `upper)`,
-           estimate = results) %>%
-    filter(!str_detect(term, "(Intercept)"))
-}
-
-mod_ls <- paste0(
-  "Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + ",
-  c("plm::lag(theta, 1)", 
-    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
-  " + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)"
-)
-
 ls_iv <- c("plm::lag(theta, 1)", 
@@
   ## Not work with ifelse
-  result_vars <- ifelse(class(result[[1]])[1] == "plm", 
-                        eval(mitools::MIextract(result, fun = vcovBK_se)),
-                        eval(mitools::MIextract(result, fun = vcovHC_se)))
+  if(class(result[[1]])[1] == "plm"){
+      result_vars <- mitools::MIextract(result, fun = vcovBK_se)
+  }else{
+      result_vars <- mitools::MIextract(result, fun = vcovHC_se)
+  }
 
@@
 
-save(tidy_result_clsUncertain, file = here::here("output", "estimates_clsAJPS.RDS"))
+save(tidy_result_clsUncertain, file = "estimates_clsAJPS.RDS")
 ```
@@
 ```{r dcpoPointAJPS}
-
+# Not showing in the final result
 ls_country <- levels(dcpo_input$data$kk)
@@
 
-estimate_dcpo <- function(aModel, aType = "pooling") {
-  if (aType == "gmm") {
-    result_dcpo_1k <- map(df_dcpo, function(aDataset) {
-      pgmm(
-        as.formula(aModel),
-        effect = "individual",
-        model = "onestep",
-        transformation = "ld",
-        indexes = c("Country", "Year"),
-        data = aDataset
-      )
-    })
-
-    result_vars_dcpo_1k <-
-      mitools::MIextract(result_dcpo_1k, fun = vcovHC_se)
-
-  } else {
-    result_dcpo_1k <- map(df_dcpo, function(aDataset) {
-      plm::plm(aModel,
-               model = "pooling",
-               data = aDataset)
-    })
-
-    result_vars_dcpo_1k <-
-      mitools::MIextract(result_dcpo_1k, fun = vcovBK_se)
+# estimate_dcpo <- function(aModel, aType = "pooling") {
+#   if (aType == "gmm") {
+#     result_dcpo_1k <- map(df_dcpo, function(aDataset) {
+#       pgmm(
+#         as.formula(aModel),
+#         effect = "individual",
+#         model = "onestep",
+#         transformation = "ld",
+#         indexes = c("Country", "Year"),
+#         data = aDataset
+#       )
+#     })
+#     
+#     result_vars_dcpo_1k <-
+#       mitools::MIextract(result_dcpo_1k, fun = vcovHC_se)
+#     
+#   } else {
+#     result_dcpo_1k <- map(df_dcpo, function(aDataset) {
+#       plm::plm(aModel,
+#                model = "pooling",
+#                data = aDataset)
+#     })
+#     
+#     result_vars_dcpo_1k <-
+#       mitools::MIextract(result_dcpo_1k, fun = vcovBK_se)
+#   }
+#   
+#   result_betas_dcpo_1k <-
+#     mitools::MIextract(result_dcpo_1k, fun = coef)
+#   
+#   df_result_dcpo <-
+#     summary(
+#       mitools::MIcombine(results = result_betas_dcpo_1k, variance = result_vars_dcpo_1k)
+#     ) %>% rownames_to_column(var = "term") %>%
+#     rename(conf.low = `(lower`,
+#            conf.high = `upper)`,
+#            estimate = results) %>%
+#     filter(!str_detect(term, "(Intercept)"))
+# }
+# 
+# mod_ls <- paste0(
+#   "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
+#   c("plm::lag(theta, 1)", 
+#     "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
+#   " + plm::lag(lg_imp_mdpgdp, 1) +
+#              plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
+#              plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)"
+# )
+# 
+# df_result_dcpoAJPS <- map(mod_ls, estimate_dcpo)
+
+ls_iv <- c("plm::lag(theta, 1)", 
+    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) ")
+
+ls_method <- c("plm", "pgmm")
+
+ls_eq <- glue("Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + {ls_iv} + plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) + plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)")
+
+ls_mod <- c(
+    glue("plm({ls_eq}, model = 'pooling', data = aData)"),
+    glue(
+        "pgmm({ls_eq} | plm::lag(Vdem_libdem, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('Country', 'Year'))"
+    )
+)
+
+tidy_result_dcpoUncertain <- map(ls_mod, function(aMod){ # reading a model
+  result <- map(df_dcpo, function(aData){ # applying to the 1000 datasets
+    eval(parse(text = aMod))
+  })
+
+  result_betas <- mitools::MIextract(result, fun = coef)
+
+  ## Not work with ifelse
+  if(class(result[[1]])[1] == "plm"){
+      result_vars <- mitools::MIextract(result, fun = vcovBK_se)
+  }else{
+      result_vars <- mitools::MIextract(result, fun = vcovHC_se)
   }
 
-  result_betas_dcpo_1k <-
-    mitools::MIextract(result_dcpo_1k, fun = coef)
-
-  df_result_dcpo <-
-    summary(
-      mitools::MIcombine(results = result_betas_dcpo_1k, variance = result_vars_dcpo_1k)
-    ) %>% rownames_to_column(var = "term") %>%
+  summary(mitools::MIcombine(results = result_betas, 
+                             variance = result_vars)) %>% 
+    rownames_to_column(var = "term") %>%
         rename(conf.low = `(lower`,
@@
         filter(!str_detect(term, "(Intercept)"))
-}
-
-mod_ls <- paste0(
-  "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
-  c("plm::lag(theta, 1)", 
-    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
-  " + plm::lag(lg_imp_mdpgdp, 1) +
-             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
-             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)"
-)
-
-df_result_dcpoAJPS <- map(mod_ls, estimate_dcpo)
-
-save(df_result_dcpoAJPS, file = here::here("output", "estimates_dcpoAJPS.RDS"))
+})
+
+save(tidy_result_dcpoUncertain, file = here::here("output", "estimates_dcpoAJPS.RDS"))
 ```

### 2021-05-04 paper/dcpo_demsupport.Rmd
writing a customized version of glance for plm

@@
   dataverse, # data scraping
-  DCPOtools,
+  DCPOtools, mitools,
   boot, plm, # analysis
   flextable, 
-  kableExtra, modelsummary, # tabulation
+  broomExtra, kableExtra, modelsummary, # tabulation
   gridExtra,
@@
   rstan, # Bayesian estimation
-  broomExtra, tidyverse, janitor, glue, # data wrangling
+  tidyverse, janitor, glue, # data wrangling
   drhutools,
@@
 
-glance_result_cls <- map(df_result_cls, glance)
+glance_result_cls <- map(df_result_cls, function(aResult){
+  if(class(aResult) == "plm"){ 
+    glance.plm(aResult) # using the customized glance function
+  }else{
+      glance(aResult)
+    }
+})
 
@@
 
-#save(df_result_cls, file = here::here("output", "estimates_clsMeanAJPS.RDS"))
+save(tidy_result_cls, glance_result_cls, file = here::here("output", "estimates_clsMeanAJPS.RDA"))
 ```
@@
 
-# estimate_dcpo <- function(aModel, aType = "pooling") {
-#   if (aType == "gmm") {
-#     result_dcpo_1k <- map(df_dcpo, function(aDataset) {
-#       pgmm(
-#         as.formula(aModel),
-#         effect = "individual",
-#         model = "onestep",
-#         transformation = "ld",
-#         indexes = c("Country", "Year"),
-#         data = aDataset
-#       )
-#     })
-#     
-#     result_vars_dcpo_1k <-
-#       mitools::MIextract(result_dcpo_1k, fun = vcovHC_se)
-#     
-#   } else {
-#     result_dcpo_1k <- map(df_dcpo, function(aDataset) {
-#       plm::plm(aModel,
-#                model = "pooling",
-#                data = aDataset)
-#     })
-#     
-#     result_vars_dcpo_1k <-
-#       mitools::MIextract(result_dcpo_1k, fun = vcovBK_se)
-#   }
-#   
-#   result_betas_dcpo_1k <-
-#     mitools::MIextract(result_dcpo_1k, fun = coef)
-#   
-#   df_result_dcpo <-
-#     summary(
-#       mitools::MIcombine(results = result_betas_dcpo_1k, variance = result_vars_dcpo_1k)
-#     ) %>% rownames_to_column(var = "term") %>%
-#     rename(conf.low = `(lower`,
-#            conf.high = `upper)`,
-#            estimate = results) %>%
-#     filter(!str_detect(term, "(Intercept)"))
-# }
-# 
-# mod_ls <- paste0(
-#   "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
-#   c("plm::lag(theta, 1)", 
-#     "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
-#   " + plm::lag(lg_imp_mdpgdp, 1) +
-#              plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
-#              plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)"
-# )
-# 
-# df_result_dcpoAJPS <- map(mod_ls, estimate_dcpo)
-
 ls_iv <- c("plm::lag(theta, 1)", 
@@
 
-load(here::here("output", "estimates_clsMeanAJPS.RDS"))
+load(here::here("output", "estimates_clsMeanAJPS.RDA"))
 load(here::here("output", "estimates_clsAJPS.RDS"))

### 2021-05-04 R/tidy_pgmm.r

@@ -40,8 +40,26 @@ glance.pgmm <- function(x, ...) {
         # arellano.bond1 = unname(x$m1$statistic[1,]),
         # arellano.bond2 = unname(x$m2$statistic[1,]),
         nobs = stats::nobs(x),
-        # n.country = length(x$residuals),
-        n.inst = dim(x$W[[1]])[2],
+        n.country = length(x$residuals),
+        # n.inst = dim(x$W[[1]])[2],
+        na_types = "ii"
+    )
+}
+
+glance.plm <- function(x, ...) {
+    s <- summary(x)
+    as_glance_tibble(
+        # chisq.sargan = unname(s$sargan$statistic),
+        # df.sargan = unname(s$sargan$parameter),
+        # p.sargan = unname(s$sargan$p.value),
+        # chisq.wald = unname(s$wald.coef$statistic),
+        # df.wald = unname(s$wald.coef$parameter),
+        # p.wald = unname(s$wald.coef$p.value),
+        # arellano.bond1 = unname(x$m1$statistic[1,]),
+        # arellano.bond2 = unname(x$m2$statistic[1,]),
+        nobs = stats::nobs(x),
+        n.country = attr(x$residuals, "index")$Country %>% nlevels,
+        # n.inst = dim(x$W[[1]])[2],
         na_types = "ii"
     )
 }

### 2021-05-04 paper/dcpo_demsupport.Rmd
uncertaint claasseen

@@
 ```{r claassenAJPS, eval=TRUE}
-# Pooled model -----
-# regime = ifelse(sd2$Regime_VD > 1, 1, 0)
-
 ls_iv <- c("plm::lag(SupDem_trim, 1)",
@@
 
-tidy_result_cls <- map(df_result_cls, function(result) {
+tidy_cls <- map(df_result_cls, function(result) {
   df_result <- tidy(result, conf.int = TRUE)
@@
 
-glance_result_cls <- map(df_result_cls, function(aResult){
+glance_cls <- map(df_result_cls, function(aResult){
   if(class(aResult) == "plm"){ 
@@
 
-names(tidy_result_cls) <- names(glance_result_cls) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
-
-save(tidy_result_cls, glance_result_cls, file = here::here("output", "estimates_clsMeanAJPS.RDA"))
+result_cls <- map2(tidy_cls, glance_cls, ~ list(.x, .y))
+names(result_cls) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
+
+save(result_cls, file = here::here("output", "estimates_clsMeanAJPS.RDS"))
 ```
@@
     glue(
-        "pgmm({ls_eq} | plm::lag(Libdem_VD, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('Country', 'Year'))"
-    )
-)
-
-tidy_result_clsUncertain <- map(ls_mod, function(aMod){ # reading a model
+        "pgmm({ls_eq} | plm::lag(Libdem_VD, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
+    )
+)
+
+result_clsUncertain <- map(ls_mod, function(aMod){ # reading a model
   result <- map(df_cls, function(aData){ # applying to the 1000 datasets
@@
 
-  summary(mitools::MIcombine(results = result_betas, 
+  tidy_clsUncertain <- summary(mitools::MIcombine(results = result_betas, 
                              variance = result_vars)) %>% 
@@
         filter(!str_detect(term, "(Intercept)"))
-})
-
-save(tidy_result_clsUncertain, file = "estimates_clsAJPS.RDS")
-```
-
-```{r dcpoPointAJPS}
-# Not showing in the final result
-ls_country <- levels(dcpo_input$data$kk)
-first_year <- min(dcpo_input$data$year)
-
-df_dcpoMean <- purrr::map_df(1:1000, function(anEntry) {
-  dcpo_theta$theta[anEntry,,] %>% 
-    reformat_dcpo_output("theta") %>% 
-    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
-              by = c("year", "country"))
-}) %>% 
-  group_by(country, year) %>% 
-  summarise(theta = mean(theta), 
-            sigma = mean(sigma))
-
-save(df_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))
+
+  if(class(result[[1]]) == "plm"){ 
+    glance_clsUncertain <- glance.plm(result[[1]]) # using the customized glance function
+  }else{
+    glance_clsUncertain <- glance(result[[1]])
+  }
+
+  result_clsUncertain <- list(tidy_clsUncertain, glance_clsUncertain)
+})
+
+names(result_clsUncertain) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
+
+save(result_clsUncertain, file = "estimates_clsAJPS.RDS")
+```
+
+```{r dcpoPointAJPS, eval = TRUE}
+# ls_country <- levels(dcpo_input$data$kk)
+# first_year <- min(dcpo_input$data$year)
+# 
+# df_dcpoMean <- purrr::map_df(1:1000, function(anEntry) {
+#   dcpo_theta$theta[anEntry,,] %>% 
+#     reformat_dcpo_output("theta") %>% 
+#     left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
+#               by = c("year", "country"))
+# }) %>% 
+#   group_by(country, year) %>% 
+#   summarise(theta = mean(theta), 
+#             sigma = mean(sigma))
+# 
+# save(df_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))
+df_dcpoMean <- readRDS(here::here("output", "estimates_dcpoMean.RDS"))
 
@@
 
-ls_mod <- paste0(
-  "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
-  c("plm::lag(theta, 1)", 
-    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
-  " + plm::lag(lg_imp_mdpgdp, 1) +
-             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
-             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)"
-)
-
-df_result_dcpoMeanAJPS <- map(ls_mod, function(mod){
-  result <- plm(mod, model = "pooling", data = df_dcpoMeanAJPS)
-  df_result <- tidy(result) %>%
-    mutate(std.error = vcovBK_se(result),
-           n = nobs(result))
-})
-
-save(df_result_dcpoMeanAJPS, file = here::here("output", "estimates_dcpoMeanAJPS.RDS"))
+ls_iv <- c("plm::lag(theta, 1)", 
+           "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) ")
+
+ls_method <- c("plm", "pgmm")
+
+ls_eq <- glue("Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + {ls_iv} + plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) + plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)")
+
+ls_mod <- c(
+  glue("plm({ls_eq}, model = 'pooling', data = df_dcpoMeanAJPS)"),
+  glue(
+    "pgmm({ls_eq} | plm::lag(Vdem_libdem, 3:5), data = df_dcpoMeanAJPS, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
+  )
+)
+
+df_result_dcpo <- map(ls_mod, function(mod) {
+  result <- eval(parse(text = mod))
+})
+
+tidy_dcpo <- map(df_result_cls, function(result) {
+  df_result <- tidy(result, conf.int = TRUE)
+
+  if (class(result) == "plm") {
+     mutate(df_result, std.error = vcovBK_se(result))
+  } else{
+    mutate(df_result, std.error = vcovHC_se(result))
+  }
+
+})
+
+glance_dcpo <- map(df_result_cls, function(aResult){
+  if(class(aResult) == "plm"){ 
+    glance.plm(aResult) # using the customized glance function
+  }else{
+      glance(aResult)
+    }
+})
+
+result_dcpo <- map2(tidy_dcpo, glance_dcpo, ~ list(.x, .y))
+names(result_dcpo) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
+
+save(result_dcpo, file = here::here("output", "estimates_dcpoMeanAJPS.RDS"))
 ```
@@
     glue(
-        "pgmm({ls_eq} | plm::lag(Vdem_libdem, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('Country', 'Year'))"
-    )
-)
-
-tidy_result_dcpoUncertain <- map(ls_mod, function(aMod){ # reading a model
+        "pgmm({ls_eq} | plm::lag(Vdem_libdem, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
+    )
+)
+
+result_dcpoUncertain <- map(ls_mod, function(aMod){ # reading a model
   result <- map(df_dcpo, function(aData){ # applying to the 1000 datasets
@@
 
-  summary(mitools::MIcombine(results = result_betas, 
+  tidy_dcpoUncertain <- summary(mitools::MIcombine(results = result_betas, 
                              variance = result_vars)) %>% 
@@
         filter(!str_detect(term, "(Intercept)"))
-})
-
-save(tidy_result_dcpoUncertain, file = here::here("output", "estimates_dcpoAJPS.RDS"))
+
+  if(class(result[[1]]) == "plm"){ 
+    glance_dcpoUncertain <- glance.plm(result[[1]]) # using the customized glance function
+  }else{
+    glance_dcpoUncertain <- glance(result[[1]])
+  }
+
+  result_dcpoUncertain <- list(tidy_dcpoUncertain, glance_dcpoUncertain)
+})
+
+names(result_dcpoUncertain) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
+
+save(result_dcpoUncertain, file = here::here("output", "estimates_dcpoAJPS.RDS"))
 ```
@@
 
-load(here::here("output", "estimates_clsMeanAJPS.RDA"))
+load(here::here("output", "estimates_clsMeanAJPS.RDS"))
 load(here::here("output", "estimates_clsAJPS.RDS"))
@@
 
-df_plot <- df_result_cls[[1]] %>% 
-  mutate(model = "Claassen 2020a")
-
-df_plot <- df_result_clsUncertain[[1]] %>% 
-  mutate(model = "Claassen w/ Uncertainty") %>%  
-  bind_rows(df_plot)
-
-df_plot <- df_result_dcpoAJPS[[1]] %>% 
-  mutate(model = "DCPO") %>%  
-  bind_rows(df_plot)
+result_pooled <- bind_rows(
+  mutate(result_cls$pooled[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertain$pooled[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertain$pooled[[1]], model = "DCPO")
+)
 

### 2021-05-04 R/tidy_pgmm.r

@@ -58,7 +58,7 @@ glance.plm <- function(x, ...) {
         # arellano.bond1 = unname(x$m1$statistic[1,]),
         # arellano.bond2 = unname(x$m2$statistic[1,]),
         nobs = stats::nobs(x),
-        n.country = attr(x$residuals, "index")$Country %>% nlevels,
+        n.country = attr(x$residuals, "index")[,1] %>% nlevels,
         # n.inst = dim(x$W[[1]])[2],
         na_types = "ii"
     )

### 2021-05-04 paper/dcpo_demsupport.Rmd
corrected the output path
dcpo results

@@
 
-save(result_clsUncertain, file = "estimates_clsAJPS.RDS")
+save(result_clsUncertain, file = here::here("output", "estimates_clsAJPS.RDS"))
 ```
@@
 ```{r dcpoPointAJPS, eval = TRUE}
-# ls_country <- levels(dcpo_input$data$kk)
-# first_year <- min(dcpo_input$data$year)
-# 
-# df_dcpoMean <- purrr::map_df(1:1000, function(anEntry) {
-#   dcpo_theta$theta[anEntry,,] %>% 
-#     reformat_dcpo_output("theta") %>% 
-#     left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
-#               by = c("year", "country"))
-# }) %>% 
-#   group_by(country, year) %>% 
-#   summarise(theta = mean(theta), 
-#             sigma = mean(sigma))
-# 
+ls_country <- levels(dcpo_input$data$kk)
+first_year <- min(dcpo_input$data$year)
+
+df_dcpoMean <- purrr::map_df(1:1000, function(anEntry) {
+  dcpo_theta$theta[anEntry,,] %>%
+    reformat_dcpo_output("theta") %>%
+    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
+              by = c("year", "country"))
+}) %>%
+  group_by(country, year) %>%
+  summarise(theta = mean(theta),
+            sigma = mean(sigma))
+
+# the readRDS produced "unknown format" error, very weild
 # save(df_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))
-df_dcpoMean <- readRDS(here::here("output", "estimates_dcpoMean.RDS"))
+# df_dcpoMean <- readRDS(here::here("output", "estimates_dcpoMean.RDS"))
 
@@
 
-tidy_dcpo <- map(df_result_cls, function(result) {
+tidy_dcpo <- map(df_result_dcpo, function(result) {
   df_result <- tidy(result, conf.int = TRUE)
@@
 
-glance_dcpo <- map(df_result_cls, function(aResult){
+glance_dcpo <- map(df_result_dcpo, function(aResult){
   if(class(aResult) == "plm"){ 

### 2021-05-05 paper/dcpo_demsupport.Rmd
dcpo uncertain done

@@
 
-load(here::here("data", "claassen_replication_input.rda"))
+claassen_replication <- readRDS("../data/claassen_replication.rds") %>% 
+  janitor::clean_names() %>% 
+  DCPOtools::with_min_yrs(2)
+
 load(here::here("data", "claassen_m5_theta.rda"))
@@
 ```{r claassenUncertaintyAJPS}
-claassen_replication <- readRDS("../data/claassen_replication.rds") %>% 
-  janitor::clean_names() %>% 
-  DCPOtools::with_min_yrs(2)
-
 ls_country <- unique(claassen_replication$country)
@@
 ```{r claassenAPSR, eval = TRUE}
-
+load(here::here("data", "dem_mood_apsr.RData"))
 sd.plm <- pdata.frame(x, index = c("Country", "Year"))
 
-ls_mods <- vector(mode = "list")
-
-ls_mods[["ECM1.1"]] <- plm(
-  diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Libdem_z, lag = 1)
-  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1),
-  data = sd.plm,
-  model = "pooling"
-)
-
-ls_mods[["ECM1.2"]] <- plm(
-  diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Libdem_z, lag = 1)
-  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)
-  + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1),
-  data = sd.plm,
-  model = "pooling"
-)
-
-ls_mods[["FD1.1"]] <-
-  plm(
-    SupDem_trim ~ Libdem_z + lnGDP_imp,
-    model = "fd",
-    data = sd.plm,
-    index = "Country"
-  )
-
-ls_mods[["FD1.2"]] <-
-  plm(
-    SupDem_trim ~ Libdem_z + lnGDP_imp + Corrup_TI_z,
-    model = "fd",
-    data = sd.plm,
-    index = "Country"
-  )
-
-ls_mods[["ECM2.1"]] <-
-  plm(
-    diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Polyarchy_z, lag = 1)
-    + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)
-    + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1),
-    sd.plm,
-    model = "pooling"
-  )
-ls_mods[["ECM2.2"]] <-
-  plm(
-    diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Polyarchy_z, lag = 1)
-    + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)
-    + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1) + diff(Corrup_TI_z, lag = 1)
-    + plm::lag(Corrup_TI_z, 1),
-    sd.plm,
-    model = "pooling"
-  )
-
-# FD models
-
-ls_mods[["FD2.1"]] <-
-  plm(
-    SupDem_trim ~ Polyarchy_z + Liberal_z + lnGDP_imp,
-    model = "fd",
-    data = sd.plm,
-    index = "Country"
-  )
-ls_mods[["FD2.2"]] <-
-  plm(
-    SupDem_trim ~ Polyarchy_z + Liberal_z + lnGDP_imp + Corrup_TI_z,
-    model = "fd",
-    data = sd.plm,
-    index = "Country"
-  )
-
-df_result_clsAPSR <- map(ls_mods, function(aMod){
-  tidy(aMod, conf.int = TRUE) %>%
-    mutate(std.error = vcovHC_se(aMod))
-})
-
-#save(df_result_clsAPSR, file = here::here("output", "estimates_clsMeanAPSR.RDS"))
+ls_ivECM <- c("diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)", 
+              "diff(Polyarchy_z, lag = 1) + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)")
+ls_ctrlECM <- c("", " + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1)")
+
+ls_eqECM <- glue("diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)") %>% 
+  outer(ls_ctrlECM, paste0) %>% 
+  as.vector()
+
+ls_ivFD <- c("Libdem_z",
+             "Polyarchy_z + Liberal_z")
+
+ls_ctrlFD <- c("", " + Corrup_TI_z")
+
+ls_eqFD <- glue("SupDem_trim ~ {ls_ivFD} + lnGDP_imp") %>% 
+  outer(ls_ctrlFD, paste0) %>% 
+  as.vector()
+
+ls_mod <- c(
+  glue("plm({ls_eqECM}, model = 'pooling', data = sd.plm)"),
+  glue("plm({ls_eqFD}, model = 'fd', index = 'Country', data = sd.plm)")
+)
+
+df_result_clsAPSR <- map(ls_mod, function(mod) {
+  result <- eval(parse(text = mod))
+})
+
+result_clsAPSR <- map(df_result_clsAPSR, function(aResult) {
+  tidy_result <- tidy(aResult, conf.int = TRUE) %>% 
+    mutate(std.error = vcovHC_se(aResult))
+
+  glance_result <- glance.plm(aResult)
+
+  ls_result <- list(tidy_result, glance_result)
+})
+
+names(result_clsAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", 
+                           "fd1", "fd-regime1", "fd2", "fd-regime2")
+
+#save(result_clsAPSR, file = here::here("output", "estimates_clsMeanAPSR.RDS"))
 ```
@@
 ```{r claassenAPSRUncertainty}
-ls_country <- unique(claassen_replication_input$data$country)
-first_year <- min(claassen_replication_input$data$year)
+ls_country <- unique(claassen_replication$country)
+first_year <- min(claassen_replication$year)
 
@@
 
-estimate_cls <- vector(mode = "list")
-
-estimate_cls[[1]] <- function(aDataset) {
-  plm(
-      diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Libdem_z, lag = 1)
-  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1),
-      model = "pooling",
-      data = aDataset
-    )
-}
-
-estimate_cls[[2]] <- function(aDataset) {
-  plm(
-      diff(theta, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Libdem_z, lag = 1)
-  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)
-  + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1),
-      model = "pooling",
-      data = aDataset
-    )
-}
-
-df_result_clsUncertainAPSR <- map(estimate_cls, function(aModel){
-  aFit <- map(df_clsAPSR, aModel)
-
-  result_vars_cls_1k <- mitools::MIextract(aFit, fun = vcovHC_se)
-  result_betas_cls_1k <- mitools::MIextract(aFit, fun = coef)
-
-  summary(
-      mitools::MIcombine(results = result_betas_cls_1k, 
-                         variance = result_vars_cls_1k)
-    ) %>% rownames_to_column(var = "term") %>%
+ls_ivECM <- c("diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)", 
+              "diff(Polyarchy_z, lag = 1) + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)")
+ls_ctrlECM <- c("", " + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1)")
+
+ls_eqECM <- glue("diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)") %>% 
+  outer(ls_ctrlECM, paste0) %>% 
+  as.vector()
+
+ls_ivFD <- c("Libdem_z",
+             "Polyarchy_z + Liberal_z")
+
+ls_ctrlFD <- c("", " + Corrup_TI_z")
+
+ls_eqFD <- glue("diff(theta, lag = 1) ~ {ls_ivFD} + lnGDP_imp") %>% 
+  outer(ls_ctrlFD, paste0) %>% 
+  as.vector()
+
+ls_mod <- c(
+  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
+  glue("plm({ls_eqFD}, model = 'fd', index = 'Country', data = aData)")
+)
+
+result_clsUncertainAPSR <- map(ls_mod, function(aMod){ # reading a model
+  result <- map(df_clsAPSR, function(aData){ # applying to the 1000 datasets
+    eval(parse(text = aMod))
+  })
+
+  result_betas <- mitools::MIextract(result, fun = coef)
+
+  result_vars <- mitools::MIextract(result, fun = vcovHC_se)
+
+  tidy_clsUncertainAPSR <- summary(mitools::MIcombine(results = result_betas, 
+                             variance = result_vars)) %>% 
+    rownames_to_column(var = "term") %>%
         rename(conf.low = `(lower`,
@@
 
-})
-
-save(df_result_clsUncertainAPSR, file = here::here("output", "estimates_clsAPSR.RDS"))
+  glance_clsUncertainAPSR <- glance.plm(result[[1]])
+
+  result_clsUncertainAPSR <- list(tidy_clsUncertainAPSR, glance_clsUncertainAPSR)
+})
+
+names(result_clsUncertainAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", "fd1", "fd-regime1", "fd2", "fd-regime2")
+
+save(result_clsUncertainAPSR, file = here::here("output", "estimates_clsAPSR.RDS"))
+
 ```
@@
 
-mods <- vector(mode = "list")
-mods[[1]] <-
-  plm(
-    diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1)
-    + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1),
-    data = df_dcpoMeanAPSR,
-    model = "pooling"
-  )
-
-mods[[2]] <-
-  plm(
-    diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1) + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1),
-    data = df_dcpoMeanAPSR,
-    model = "pooling"
-  )
-
-df_result_dcpoMeanAPSR <- map(mods, function(aMod) {
-  aMod %>% 
-    tidy %>%
-    mutate(std.error = vcovHC_se(aMod),
-           n = nobs(aMod`))
-})
-
-save(df_result_dcpoMeanAPSR, file = here::here("output", "estimates_dcpoMeanAPSR.RDS"))
+ls_ivECM <- c("diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1)", 
+              "diff(Vdem_polyarchy_z, lag = 1) + plm::lag(Vdem_polyarchy_z, 1) + diff(Vdem_liberal_z, lag = 1) + plm::lag(Vdem_liberal_z, 1)")
+ls_ctrlECM <- c("", " + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1)")
+
+ls_eqECM <- glue("diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + {ls_ivECM} + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1)") %>% 
+  outer(ls_ctrlECM, paste0) %>% 
+  as.vector()
+
+ls_ivFD <- c("Vdem_libdem_z",
+             "Vdem_polyarchy_z + Vdem_liberal_z")
+
+ls_ctrlFD <- c("", " + corruption_z")
+
+ls_eqFD <- glue("theta ~ {ls_ivFD} + lg_imp_mdpgdp") %>% 
+  outer(ls_ctrlFD, paste0) %>% 
+  as.vector()
+
+ls_mod <- c(
+  glue("plm({ls_eqECM}, model = 'pooling', data = df_dcpoMeanAPSR)"),
+  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = df_dcpoMeanAPSR)")
+)
+
+df_result_dcpoMeanAPSR <- map(ls_mod, function(mod) {
+  result <- eval(parse(text = mod))
+})
+
+result_dcpoMeanAPSR <- map(df_result_dcpoMeanAPSR, function(aResult) {
+  tidy_result <- tidy(aResult, conf.int = TRUE) %>% 
+    mutate(std.error = vcovHC_se(aResult))
+
+  glance_result <- glance.plm(aResult)
+
+  ls_result <- list(tidy_result, glance_result)
+})
+
+names(result_dcpoMeanAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",  "fd1", "fd-regime1", "fd2", "fd-regime2")
+
+save(result_dcpoMeanAPSR, file = here::here("output", "estimates_dcpoMeanAPSR.RDS"))
 ```
@@
 ```{r dcpoUncertaintyAPSR}
-df_dcpo <- purrr::map(1:1000, function(anEntry) {
+ls_country <- levels(dcpo_input$data$kk)
+first_year <- min(dcpo_input$data$year)
+
+df_dcpoUncertainAPSR <- purrr::map(1:1000, function(anEntry) {
   dcpo_theta$theta[anEntry,,] %>% 
@@
 
-estimate_dcpo <- vector(mode = "list")
-
-estimate_dcpo[[1]] <- function(aDataset) {
-  plm(
-      diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1)
-      + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1),
-      model = "pooling",
-      data = aDataset
-    )
-}
-
-estimate_dcpo[[2]] <- function(aDataset) {
-  plm(
-      diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1) + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1),
-      model = "pooling",
-      data = aDataset
-    )
-}
-
-df_result_dcpoAPSR <- map(estimate_dcpo, function(aModel){
-  aFit <- map(df_dcpo, aModel)
-
-  result_vars_dcpo_1k <- mitools::MIextract(aFit, fun = vcovHC_se)
-  result_betas_dcpo_1k <- mitools::MIextract(aFit, fun = coef)
-
-  summary(
-      mitools::MIcombine(results = result_betas_dcpo_1k, 
-                         variance = result_vars_dcpo_1k)
-    ) %>% rownames_to_column(var = "term") %>%
+## The same as in the previous chunk
+
+ls_ivECM <- c("diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1)", 
+              "diff(Vdem_polyarchy_z, lag = 1) + plm::lag(Vdem_polyarchy_z, 1) + diff(Vdem_liberal_z, lag = 1) + plm::lag(Vdem_liberal_z, 1)")
+ls_ctrlECM <- c("", " + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1)")
+
+ls_eqECM <- glue("diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + {ls_ivECM} + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1)") %>% 
+  outer(ls_ctrlECM, paste0) %>% 
+  as.vector()
+
+ls_ivFD <- c("Vdem_libdem_z",
+             "Vdem_polyarchy_z + Vdem_liberal_z")
+
+ls_ctrlFD <- c("", " + corruption_z")
+
+ls_eqFD <- glue("theta ~ {ls_ivFD} + lg_imp_mdpgdp") %>% 
+  outer(ls_ctrlFD, paste0) %>% 
+  as.vector()
+
+### Different datasets
+
+ls_mod <- c(
+  glue("plm({ls_eqECM}, model = 'pooling', data = df_dcpoUncertainAPSR)"),
+  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = df_dcpoUncertainAPSR)")
+)
+
+result_dcpoUncertainAPSR <- map(ls_mod, function(aMod){ # reading a model
+  result <- map(df_dcpoUncertainAPSR, function(aData){ # applying to the 1000 datasets
+    eval(parse(text = aMod))
+  })
+
+  result_betas <- mitools::MIextract(result, fun = coef)
+
+  result_vars <- mitools::MIextract(result, fun = vcovHC_se)
+
+  tidy_dcpoUncertainAPSR <- summary(mitools::MIcombine(results = result_betas, 
+                             variance = result_vars)) %>% 
+    rownames_to_column(var = "term") %>%
         rename(conf.low = `(lower`,
@@
 
-})
-
-save(df_result_dcpoAPSR, file = here::here("output", "estimates_dcpoAPSR.RDS"))
+  glance_dcpoUncertainAPSR <- glance.plm(result[[1]])
+
+  result_dcpoUncertainAPSR <- list(tidy_dcpoUncertainAPSR, glance_dcpoUncertainAPSR)
+})
+
+names(result_dcpoUncertainAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",  "fd1", "fd-regime1", "fd2", "fd-regime2")
+
+save(result_dcpoUncertainAPSR, file = here::here("output", "estimates_dcpoAPSR.RDS"))
 ```

### 2021-05-05 R/tidy_pgmm.r

@@ -40,7 +40,7 @@ glance.pgmm <- function(x, ...) {
         # arellano.bond1 = unname(x$m1$statistic[1,]),
         # arellano.bond2 = unname(x$m2$statistic[1,]),
         nobs = stats::nobs(x),
-        n.country = length(x$residuals),
+        n.country = pdim(x)$nT$n,
         # n.inst = dim(x$W[[1]])[2],
         na_types = "ii"
     )
@@ -58,7 +58,7 @@ glance.plm <- function(x, ...) {
         # arellano.bond1 = unname(x$m1$statistic[1,]),
         # arellano.bond2 = unname(x$m2$statistic[1,]),
         nobs = stats::nobs(x),
-        n.country = attr(x$residuals, "index")[,1] %>% nlevels,
+        n.country = pdim(x)$nT$n,
         # n.inst = dim(x$W[[1]])[2],
         na_types = "ii"
     )

### 2021-05-05 paper/dcpo_demsupport.Rmd
using saveRDS to prevent unsuccessful saving

@@
 
-save(result_cls, file = here::here("output", "estimates_clsMeanAJPS.RDS"))
+saveRDS(result_cls, file = here::here("output", "estimates_clsMeanAJPS.RDS"))
 ```
@@
 
-save(result_clsUncertain, file = here::here("output", "estimates_clsAJPS.RDS"))
+saveRDS(result_clsUncertain, file = here::here("output", "estimates_clsAJPS.RDS"))
 ```
@@
 # the readRDS produced "unknown format" error, very weild
-# save(df_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))
+# saveRDS(df_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))
 # df_dcpoMean <- readRDS(here::here("output", "estimates_dcpoMean.RDS"))
@@
 
-save(result_dcpo, file = here::here("output", "estimates_dcpoMeanAJPS.RDS"))
+saveRDS(result_dcpo, file = here::here("output", "estimates_dcpoMeanAJPS.RDS"))
 ```
@@
 
-save(result_dcpoUncertain, file = here::here("output", "estimates_dcpoAJPS.RDS"))
+saveRDS(result_dcpoUncertain, file = here::here("output", "estimates_dcpoAJPS.RDS"))
 ```
@@
 
-#save(result_clsAPSR, file = here::here("output", "estimates_clsMeanAPSR.RDS"))
+#saveRDS(result_clsAPSR, file = here::here("output", "estimates_clsMeanAPSR.RDS"))
 ```
@@
 
-save(result_clsUncertainAPSR, file = here::here("output", "estimates_clsAPSR.RDS"))
+saveRDS(result_clsUncertainAPSR, file = here::here("output", "estimates_clsAPSR.RDS"))
 
@@
 
-save(result_dcpoMeanAPSR, file = here::here("output", "estimates_dcpoMeanAPSR.RDS"))
+saveRDS(result_dcpoMeanAPSR, file = here::here("output", "estimates_dcpoMeanAPSR.RDS"))
 ```
@@
 
-save(result_dcpoUncertainAPSR, file = here::here("output", "estimates_dcpoAPSR.RDS"))
+saveRDS(result_dcpoUncertainAPSR, file = here::here("output", "estimates_dcpoAPSR.RDS"))
 ```

### 2021-05-12 paper/dcpo_demsupport.Rmd
visualized results for AJPS; coefficent order issue, #27

@@
 
-```{r visualizeAJPS, fig.cap= "\\label{fig:visualizeAJPS}The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=5}
-
+```{r visualizeAJPS, fig.cap= "\\label{fig:visualizeAJPS}The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=8}
+
+# Very weird phenomenon that the same type of rds files needs different ways to read
+# Suggesting using the qs or csv data type in future.
 load(here::here("output", "estimates_clsMeanAJPS.RDS"))
-load(here::here("output", "estimates_clsAJPS.RDS"))
+result_clsUncertain <- readRDS(here::here("output", "estimates_clsAJPS.RDS"))
 load(here::here("output", "estimates_dcpoAJPS.RDS"))
@@
   mutate(result_dcpoUncertain$pooled[[1]], model = "DCPO")
-)
-
-df_plotS <- df_plot %>%
+) %>% 
+  mutate(type = "Pooled")
+
+result_gmm <- bind_rows(
+  mutate(result_cls$gmm[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertain$gmm[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertain$gmm[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "GMM")
+
+result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
   filter(term != "(Intercept)") %>%
@@
       "Resource\n dependence\n (t-1)"),
-    time = 3))
+    time = 6), 
+    type = factor(type, levels = c("Pooled", "GMM")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
 
@@
 
-df_tableAJPS <- df_plotS %>% mutate(
-  conf = paste0("[", round(conf.low, digits = 2), ", ", round(conf.high, digits = 2), "]"),
-  group = "Pooled"
-) %>% 
-  select(term, estimate, conf, n, model, group) %>% 
-  fill(n, .direction = "up")
-
-plot_AJPS1 <- dwplot(df_plotS, dodge_size = 0.8, by_2sd = FALSE) +
+# ggplot produces reversed plot, and embarrassed to say, I can't fix, again. Any thought?
+# What I've tried
+# 1. using guide_legend(reverse = TRUE) will change the legend's order not the plot.
+# 2. ordering models with factor levels using the original names or even c("1", "2", "3")
+# 2. redefining the order of model in the dataframe or in dwplot 
+# 3. checking the dwplot codes, model works in line 453, but nothing looks helpful
+# 4. Every post online is to reverse
+
+plot_AJPS1 <- dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
   scale_y_discrete(labels = parse(text = levels(terms))) +
-  # scale_color_uiowa(name = "", palette = "digitMixed") +
   scale_color_grey(start = 0.4, end = 0.8) +
@@
     title = "DV: V-Dem Liberal Democracy Index",
-    subtitle = "Pooled"
+    subtitle = "Regime Compacted"
   ) +
+  facet_wrap(~type, scales = "free_x") + 
   theme(legend.position = "none")
@@
 
-df_plot <- df_result_cls[[2]] %>% 
-  mutate(model = "Claassen 2020a")
-
-df_plot <- df_result_clsUncertain[[2]] %>% 
-  mutate(model = "Claassen w/ Uncertainty") %>%  
-  bind_rows(df_plot)
-
-df_plot <- df_result_dcpoAJPS[[2]] %>% 
-  mutate(model = "DCPO") %>%  
-  bind_rows(df_plot)
-
-df_plotS <- df_plot %>%
+result_regime <- bind_rows(
+  mutate(result_cls$`pooled-regime`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertain$`pooled-regime`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertain$`pooled-regime`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "Pooled")
+
+result_regimeGmm <- bind_rows(
+  mutate(result_cls$`gmm-regime`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertain$`gmm-regime`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertain$`gmm-regime`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "GMM")
+
+result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
   filter(term != "(Intercept)") %>%
@@
       "Resource\n dependence\n (t-1)"),
-    time = 3)
-  )
+    time = 6), 
+    type = factor(type, levels = c("Pooled", "GMM")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
 
@@
 
-df_tableAJPS <- df_plotS %>% mutate(
-  conf = paste0("[", round(conf.low, digits = 2), ", ", round(conf.high, digits = 2), "]"),
-  group = "Regime Spec."
-) %>% 
-  select(term, estimate, conf, n, model, group) %>% 
-  fill(n, .direction = "up") %>% 
-  bind_rows(df_tableAJPS) %>% 
-  mutate(estimate = round(estimate, digits = 3))
-
-plot_AJPS2 <- dwplot(df_plotS, dodge_size = 0.8, by_2sd = FALSE) +
+plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
     scale_y_discrete(labels = parse(text = levels(terms2))) +
-  # scale_color_uiowa(name = "", palette = "digitMixed") +
   scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
@@
   ) +
+  facet_wrap(~type, scales = "free_x") +
   theme(legend.position = "bottom", 
@@
 
-grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol=2, nrow = 2, 
-             layout_matrix = rbind(c(1,2), c(3,3)),
-             widths = c(2.7, 2.7), heights = c(2.5, 0.2))
+grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
 
@@
 ```{r num-cls2020a, results='asis', eval = TRUE}
-ls_result_cls <-
-  map2(tidy_result_cls, glance_result_cls, function(aTidy, aGlance) {
-    ls_sum <- list(tidy = aTidy,
-                   glance = aGlance)
-
-    class(ls_sum) <- "modelsummary_list"
-
-    return(ls_sum)
-  })
-
-names(ls_result_cls) <- c("Pooled OLS 1", "Pooled OLS 2", "GMM 1", "GMM 2")
+tb_result_cls <- map(result_cls, ~ {
+  names(.) <- c("tidy", "glance")
+  class(.) <- "modelsummary_list"
+  return(.)})
+
+names(tb_result_cls) <- c("Pooled", "Pooled-Regime", 
+                          "GMM", "GMM-Regime")
 
@@
   "plm::lag(SupDem_trim, 1)" = "Support[t-1]",
+  "plm::lag(SupDem_Democ, 1)" = "Support in Democracy",
+  "plm::lag(SupDem_Autoc, 1)" = "Support in Autocracy",
   "plm::lag(lnGDP_imp, 1)" = "Log~GDP~per~capita[t-1]",
@@
 
-modelsummary(ls_result_cls, 
-             stars = TRUE,
+modelsummary(tb_result_cls,  
+             statistic = "conf.int",
              coef_map = names_coef, 
-             output = "latex") %>% 
+             output = "latex", 
+             title = "Original") %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+```{r num-cls2020aUncertain, results='asis', eval = TRUE}
+tb_result_clsUncertain <- map(result_clsUncertain, ~ {
+  names(.) <- c("tidy", "glance")
+  class(.) <- "modelsummary_list"
+  return(.)})
+
+names(tb_result_cls) <- c("Pooled", "Pooled-Regime", 
+                          "GMM", "GMM-Regime")
+
+names_coef <- c(
+  "plm::lag(Libdem_VD, 1:2)1" = "Democracy[t-1]",
+  "plm::lag(Libdem_VD, 1:2)2"  = "Democracy[t-2]",
+  "plm::lag(theta, 1)" = "Support[t-1]",
+  "plm::lag(theta_dem, 1)" = "Support in Democracy",
+  "plm::lag(theta_aut, 1)" = "Support in Autocracy",
+  "plm::lag(lnGDP_imp, 1)" = "Log~GDP~per~capita[t-1]",
+  "plm::lag(GDP_imp_grth, 1)"  = "GDP~per~capita~growth[t-1]",
+  "plm::lag(Libdem_regUN, 1)" = "Regional~democracy[t-1]",
+  "plm::lag(Pr_Muslim, 1)" = "Percent~Muslim[t-1]",
+  "plm::lag(Res_cp_WDI_di, 1)" = "Resource~dependence[t-1]"
+)
+
+modelsummary(tb_result_clsUncertain, 
+             statistic = "conf.int",
+             coef_map = names_coef, 
+             output = "latex", 
+             title = "W. Uncertainty") %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+```{r num-cls2020aDCPO, results='asis', eval = TRUE}
+tb_result_DCPO <- map(result_dcpoUncertain, ~ {
+  names(.) <- c("tidy", "glance")
+  class(.) <- "modelsummary_list"
+  return(.)})
+
+names(tb_result_DCPO) <- c("Pooled", "Pooled-Regime", 
+                          "GMM", "GMM-Regime")
+
+names_coef <- c(
+  "plm::lag(Vdem_libdem, 1:2)1" = "Democracy[t-1]",
+  "plm::lag(Vdem_libdem, 1:2)2"  = "Democracy[t-2]",
+  "plm::lag(theta, 1)" = "Support[t-1]",
+  "plm::lag(theta_dem, 1)" = "Support in Democracy",
+  "plm::lag(theta_aut, 1)" = "Support in Autocracy",
+  "plm::lag(lg_imp_mdpgdp, 1)" = "Log~GDP~per~capita[t-1]",
+  "plm::lag(mdprgdp_grwth, 1)"  = "GDP~per~capita~growth[t-1]",
+  "plm::lag(Region_libdem, 1)" = "Regional~democracy[t-1]",
+  "plm::lag(muslism_prop_2010, 1)" = "Percent~Muslim[t-1]",
+  "plm::lag(dependence_pc_di, 1)" = "Resource~dependence[t-1]"
+)
+
+modelsummary(tb_result_DCPO, 
+             statistic = "conf.int",
+             coef_map = names_coef, 
+             output = "latex", 
+             title = "W. Uncertainty") %>% 
   kableExtra::kable_styling(latex_options = "HOLD_position")

### 2021-05-12 paper/dcpo_demsupport.Rmd
version with all the models

@@
 
-```{r dcpoPointAJPS, eval = TRUE}
+```{r dcpoPointAJPS}
 ls_country <- levels(dcpo_input$data$kk)
@@
 
-```{r visualizeAJPS, fig.cap= "\\label{fig:visualizeAJPS}The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=8}
+```{r visualizeAJPS, fig.cap= "\\label{fig:visualizeAJPS}The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=10}
 
@@
 # Suggesting using the qs or csv data type in future.
-load(here::here("output", "estimates_clsMeanAJPS.RDS"))
+result_cls <- readRDS(here::here("output", "estimates_clsMeanAJPS.RDS"))
 result_clsUncertain <- readRDS(here::here("output", "estimates_clsAJPS.RDS"))
@@
 
-```{r visualizedAPSR, fig.cap= "\\label{fig:visualizedAPSR} The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=5}
+```{r visualizedAPSR, fig.cap= "\\label{fig:visualizedAPSR} The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}
 
@@
 load(here::here("output", "estimates_clsAPSR.RDS"))
-load(here::here("output", "estimates_dcpoAPSR.RDS"))
-
-df_plot <- df_result_clsAPSR[[1]] %>% 
-  mutate(model = "Claassen 2020b")
-
-df_plot <- df_result_clsUncertainAPSR[[1]] %>% 
-  mutate(model = "Claassen w/ Uncertainty") %>%  
-  bind_rows(df_plot)
-
-df_plot <- df_result_dcpoAPSR[[1]] %>% 
-  mutate(model = "DCPO") %>%  
-  bind_rows(df_plot)
-
-df_plotS <- df_plot %>%
+result_dcpoAPSR <- readRDS(here::here("output", "estimates_dcpoAPSR.RDS"))
+
+# Regime compacted ####
+
+result_ecm1 <- bind_rows(
+  mutate(result_clsAPSR$pooled1[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainAPSR$pooled1[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoAPSR$pooled1[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "ECM")
+
+result_fd1 <- bind_rows(
+  mutate(result_clsAPSR$fd1[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainAPSR$fd1[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoAPSR$fd1[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "First Difference")
+
+result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
   filter(term != "(Intercept)") %>%
   mutate(
-    term = rep(
+    term = c(rep(
       c("Democratic Mood\n (t-1)",
@@
       "Log GDP\n (t-1)"),
-    time = 3)
-  )
-
-terms <- factor(rev(c("Support[t-1]",
+    time = 3),
+    rep(
+      c("Liberal Democracy\n (Difference)", 
+        "Log GDP\n per capita\n (Difference)"), 
+      time = 3
+    )),
+    type = factor(type, levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
+  )
+
+terms1 <- factor(rev(c("Support[t-1]",
                       "Support[t-2]",
@@
 
-df_tableAPSR <- df_plotS %>% mutate(
-  conf = paste0("[", round(conf.low, digits = 2), ", ", round(conf.high, digits = 2), "]"),
-  group = "Basic"
-) %>% 
-  select(term, estimate, conf, n, model, group) %>% 
-  fill(n, .direction = "up")
-
-plot_APSR1 <- dwplot(df_plotS, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms))) +
+plot_APSR1 <- dwplot(result_APSR1, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms1))) +
   scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
@@
     title = "DV: Public Support for Democracy",
-    subtitle = "Basic"
+    subtitle = "Regime Compacted"
   ) +
+  facet_wrap(~type, scales = "free_x") + 
   theme(legend.position = "none")
 
-df_plot <- df_result_clsAPSR[[2]] %>% 
-  mutate(model = "Claassen 2020b")
-
-df_plot <- df_result_clsUncertainAPSR[[2]] %>% 
-  mutate(model = "Claassen w/ Uncertainty") %>%  
-  bind_rows(df_plot)
-
-df_plot <- df_result_dcpoAPSR[[2]] %>% 
-  mutate(model = "DCPO") %>%  
-  bind_rows(df_plot)
-
-df_plotS <- df_plot %>%
+result_ecm2 <- bind_rows(
+  mutate(result_clsAPSR$pooled2[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainAPSR$pooled2[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoAPSR$pooled2[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "ECM")
+
+result_fd2 <- bind_rows(
+  mutate(result_clsAPSR$fd2[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainAPSR$fd2[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoAPSR$fd2[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "First Difference")
+
+result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
   filter(term != "(Intercept)") %>%
   mutate(
-    term = rep(
-      c("Democratic\n Mood\n (t-1)",
-        "Democratic\n Mood\n (t-2)",
-      "Liberal\n Democracy\n (Difference)",
-      "Liberal\n Democracy\n (t-1)",
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+      "Liberal Democracy\n (Difference)",
+      "Liberal Democracy\n (t-1)",
       "Log GDP\n per capita\n (Difference)",
@@
       "Corruption\n (t-1)"
-      ),time = 3)
+      ),
+    time = 3),
+    rep(
+      c("Liberal Democracy\n (Difference)", 
+        "Log GDP\n per capita\n (Difference)",
+        "Corruption\n (Difference)"), 
+      time = 3
+    )),
+    type = factor(type, levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
   )
@@
 
-df_tableAPSR <- df_plotS %>% mutate(
-  conf = paste0("[", round(conf.low, digits = 2), ", ", round(conf.high, digits = 2), "]"),
-  group = "W. Corruption"
-) %>% 
-  select(term, estimate, conf, n, model, group) %>% 
-  fill(n, .direction = "up") %>% 
-  bind_rows(df_tableAPSR) %>% 
-  mutate(estimate = round(estimate, digits = 3))
-
-plot_APSR2 <- dwplot(df_plotS, dodge_size = 0.8, by_2sd = FALSE) +
+plot_APSR2 <- dwplot(result_APSR2, dodge_size = 0.8, by_2sd = FALSE) +
   scale_y_discrete(labels = parse(text = levels(terms2))) +
@@
     title = "",
-    subtitle = "w/ Corruption"
+    subtitle = "W. Corruption"
   ) +
-  theme(legend.position = "bottom", legend.title = element_blank())
-
-legend <- get_legend(plot_APSR2)
-
-plot_APSR2 <- plot_APSR2 +
+  facet_wrap(~type, scales = "free_x") +
   theme(legend.position = "none")
 
-gridExtra::grid.arrange(plot_APSR1, plot_APSR2, legend, ncol=2, nrow = 2, 
-             layout_matrix = rbind(c(1,2), c(3,3)),
-             widths = c(2.7, 2.7), heights = c(2.5, 0.2))
+# Regime specified ####
+
+result_ecmReg1 <- bind_rows(
+  mutate(result_clsAPSR$`pooled-regime1`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainAPSR$`pooled-regime1`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoAPSR$`pooled-regime1`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "ECM")
+
+result_fdReg1 <- bind_rows(
+  mutate(result_clsAPSR$`fd-regime1`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainAPSR$`fd-regime1`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoAPSR$`fd-regime1`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "First Difference")
+
+result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+      "Electoral Democracy\n (Difference)",
+      "Electoral Democracy\n (t-1)",
+      "Minoritarian Democracy\n (Difference)",
+      "Minoritarian Democracy\n (t-1)",
+      "Log GDP\n per capita\n (Difference)",
+      "Log GDP\n (t-1)"),
+    time = 3),
+    rep(
+      c("Electoral Democracy\n (Difference)", 
+        "Minoritarian Democracy\n (Difference)",
+        "Log GDP\n per capita\n (Difference)"), 
+      time = 3
+    )),
+    type = factor(type, levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
+  )
+
+terms3 <- factor(rev(c("Support[t-1]",
+                      "Support[t-2]",
+                      "Delta~Electoral~democracy",
+                      "Electoral~democracy[t-1]",
+                      "Delta~Minoritarian~democracy",
+                      "Minoritarian~democracy[t-1]",
+                      "Delta~Log~GDP~per~capita",
+                      "Log~GDP[t-1]")),
+                levels = rev(c("Support[t-1]",
+                      "Support[t-2]",
+                      "Delta~Electoral~democracy",
+                      "Electoral~democracy[t-1]",
+                      "Delta~Minoritarian~democracy",
+                      "Minoritarian~democracy[t-1]",
+                      "Delta~Log~GDP~per~capita",
+                      "Log~GDP[t-1]")))
+
+plot_RegAPSR1 <- dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms3))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  # scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "",
+    subtitle = "Regime Specified"
+  ) +
+  facet_wrap(~type, scales = "free_x") + 
+  theme(legend.position = "none")
+
+result_ecmReg2 <- bind_rows(
+  mutate(result_clsAPSR$`pooled-regime2`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainAPSR$`pooled-regime2`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoAPSR$`pooled-regime2`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "ECM")
+
+result_fdReg2 <- bind_rows(
+  mutate(result_clsAPSR$`fd-regime2`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainAPSR$`fd-regime2`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoAPSR$`fd-regime2`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "First Difference")
+
+result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+      "Electoral Democracy\n (Difference)",
+      "Electoral Democracy\n (t-1)",
+      "Minoritarian Democracy\n (Difference)",
+      "Minoritarian Democracy\n (t-1)",
+      "Log GDP\n per capita\n (Difference)",
+      "Log GDP\n (t-1)",
+      "Corruption\n (Difference)",
+      "Corruption\n (t-1)"
+      ),
+    time = 3),
+    rep(
+      c("Electoral Democracy\n (Difference)", 
+        "Minoritarian Democracy\n (Difference)",
+        "Log GDP\n per capita\n (Difference)",
+        "Corruption\n (Difference)"), 
+      time = 3
+    )),
+    type = factor(type, levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
+  )
+
+terms4 <- factor(rev(c("Support[t-1]",
+                      "Support[t-2]",
+                      "Delta~Electoral~democracy",
+                      "Electoral~democracy[t-1]",
+                      "Delta~Minoritarian~democracy",
+                      "Minoritarian~democracy[t-1]",
+                      "Delta~Log~GDP",
+                      "Log~GDP[t-1]",
+                      "Delta~Corruption",
+                      "Corruption[t-1]")),
+                levels = rev(c("Support[t-1]",
+                               "Support[t-2]",
+                               "Delta~Electoral~democracy",
+                               "Electoral~democracy[t-1]",
+                               "Delta~Minoritarian~democracy",
+                               "Minoritarian~democracy[t-1]",
+                               "Delta~Log~GDP",
+                               "Log~GDP[t-1]",
+                               "Delta~Corruption",
+                               "Corruption[t-1]")))
+
+plot_RegAPSR2 <- dwplot(result_RegAPSR2, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms4))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  # scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "",
+    subtitle = "Regime Specified w. Corruption"
+  ) +
+  facet_wrap(~type, scales = "free_x") +
+  theme(legend.position = "bottom", 
+        legend.title = element_blank())
+
+legend <- get_legend(plot_RegAPSR2)
+
+plot_RegAPSR2 <- plot_RegAPSR2 + theme(legend.position = "none")
+
+grid.arrange(plot_APSR1, plot_APSR2, plot_RegAPSR1, plot_RegAPSR2, legend, ncol = 1)
 ```
@@
 
-```{r save_tables, eval=TRUE}
-save(df_tableAJPS, df_tableAPSR, file = here::here("output", "df_tables.rda"))
-
-```
-
 # Discussion
@@
 ```{r num-cls2020b, results='asis', eval = TRUE}
+tb_result_clsAPSR <- map(result_clsAPSR, ~ {
+  names(.) <- c("tidy", "glance")
+  class(.) <- "modelsummary_list"
+  return(.)}) %>% 
+  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
+      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]
+
+names(tb_result_clsAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM w. Corruption", "ECM w. Corruption-Regime", "FD w. Corruption", "FD w. Corruption-Regime")
+
 names_coef <- c(
@@
 
-modelsummary(ls_mods, 
+modelsummary(tb_result_clsAPSR, 
              stars = TRUE,
@@
 
+\pagebreak
+
+```{r num-cls2020bUncertain, results='asis', eval = TRUE}
+tb_result_clsUncertainAPSR <- map(result_clsUncertainAPSR, ~ {
+  names(.) <- c("tidy", "glance")
+  class(.) <- "modelsummary_list"
+  return(.)}) %>% 
+  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
+      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]
+
+names(tb_result_clsUncertainAPSR) <- c("ECM", "ECM-Regime", 
+                          "FD", "FD-Regime", 
+                          "ECM w. Corruption", "ECM w. Corruption-Regime", 
+                          "FD w. Corruption", "FD w. Corruption-Regime")
+
+names_coef <- c(
+  "(Intercept)" = "(Intercept)",
+  "plm::lag(SupDem_trim, 1:2)1" = "Democratic\n Mood\n (t-1)",
+  "plm::lag(SupDem_trim, 1:2)2" = "Democratic\n Mood\n (t-2)",
+  "diff(Libdem_z, lag = 1)" = "Liberal\n Democracy\n (Difference)",
+  "Libdem_z" = "Liberal\n Democracy\n (Difference)",
+  "plm::lag(Libdem_z, 1)" = "Liberal\n Democracy\n (t-1)",
+  "diff(Polyarchy_z, lag = 1)" = "Electoral\n Democracy\n (Difference)",
+  "Polyarchy_z" = "Electoral\n Democracy\n (Difference)",
+  "plm::lag(Polyarchy_z, 1)" = "Electoral\n Democracy\n (t-1)",
+  "diff(Liberal_z, lag = 1)" = "Minoritarian\n Democracy\n (Difference)",
+  "Liberal_z" = "Minoritarian\n Democracy\n (Difference)",
+  "plm::lag(Liberal_z, 1)" = "Minoritarian\n Democracy\n (t-1)",
+  "diff(lnGDP_imp, lag = 1)" = "Log GDP\n per capita\n (Difference)",
+  "lnGDP_imp" = "Log GDP\n per capita\n (Difference)",
+  "plm::lag(lnGDP_imp, 1)" = "Log GDP\n (t-1)",
+  "diff(Corrup_TI_z, lag = 1)" = "Corruption\n (Difference)",
+  "Corrup_TI_z" = "Corruption\n (Difference)",
+  "plm::lag(Corrup_TI_z, 1)" = "Corruption\n (t-1)"
+)
+
+modelsummary(tb_result_clsUncertainAPSR, 
+             statistic = "conf.int",
+             coef_map = names_coef, 
+             output = "latex") %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+\pagebreak
+
+```{r num-cls2020bDCPO, results='asis', eval = TRUE}
+tb_result_dcpoAPSR <- map(result_dcpoAPSR, ~ {
+  names(.) <- c("tidy", "glance")
+  class(.) <- "modelsummary_list"
+  return(.)}) %>% 
+  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
+      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]
+
+names(tb_result_dcpoAPSR) <- c("ECM", "ECM-Regime", 
+                          "FD", "FD-Regime", 
+                          "ECM w. Corruption", "ECM w. Corruption-Regime", 
+                          "FD w. Corruption", "FD w. Corruption-Regime")
+
+names_coef <- c(
+  "(Intercept)" = "(Intercept)",
+  "plm::lag(theta, 1:2)1" = "Democratic\n Mood\n (t-1)",
+  "plm::lag(theta, 1:2)2" = "Democratic\n Mood\n (t-2)",
+
+  "diff(Vdem_libdem_z, lag = 1)" = "Liberal\n Democracy\n (Difference)",
+  "Vdem_libdem_z" = "Liberal\n Democracy\n (Difference)",
+  "plm::lag(Vdem_libdem_z, 1)" = "Liberal\n Democracy\n (t-1)",
+
+  "diff(Vdem_polyarchy_z, lag = 1)" = "Electoral\n Democracy\n (Difference)",
+  "Vdem_polyarchy_z" = "Electoral\n Democracy\n (Difference)",
+  "plm::lag(Vdem_polyarchy_z, 1)" = "Electoral\n Democracy\n (t-1)",
+  "diff(Vdem_liberal_z, lag = 1)" = "Minoritarian\n Democracy\n (Difference)",
+  "Vdem_liberal_z" = "Minoritarian\n Democracy\n (Difference)",
+  "plm::lag(Vdem_liberal_z, 1)" = "Minoritarian\n Democracy\n (t-1)",
+  "diff(lg_imp_mdpgdp, lag = 1)" = "Log GDP\n per capita\n (Difference)",
+  "lg_imp_mdpgdp" = "Log GDP\n per capita\n (Difference)",
+  "plm::lag(lg_imp_mdpgdp, 1)" = "Log GDP\n (t-1)",
+  "diff(corruption_z, lag = 1)" = "Corruption\n (Difference)",
+  "corruption_z" = "Corruption\n (Difference)",
+  "plm::lag(corruption_z, 1)" = "Corruption\n (t-1)"
+)
+
+modelsummary(tb_result_dcpoAPSR, 
+             statistic = "conf.int",
+             coef_map = names_coef, 
+             output = "latex") %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
 \end{landscape}

### 2021-05-13 paper/dcpo_demsupport.Rmd
theta with errors

@@
 
+\pagebreak
+```{r datawitherrors}
+
+ls_country <- unique(claassen_replication$country)
+first_year <- min(claassen_replication$year)
+
+df_cls_errors <- purrr::map(1:900, function(anEntry) {
+  claassen_m5_theta$theta[anEntry,,] %>%
+    reformat_dcpo_output("theta")  %>%
+    mutate(iter = anEntry) 
+  }
+  )
+
+cls_theta_uncertainty <- bind_rows(df_cls_errors)
+saveRDS(cls_theta_uncertainty,"data/cls_theta_uncertainty.rds")
+
+ls_country <- levels(dcpo_input$data$kk)
+first_year <- min(dcpo_input$data$year)
+
+df_dcpo <- purrr::map_df(1:900, function(anEntry) {
+  dcpo_theta$theta[anEntry,,] %>%
+    reformat_dcpo_output("theta") %>%
+    mutate(iter = anEntry) %>%
+    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
+              by = c("year", "country"))
+})
+
+saveRDS(df_dcpo,"dcpo_theta_uncertainty.rds")
+
+```
+
 \end{landscape}

### 2021-05-13 paper/dcpo_demsupport.Rmd
codes for combining theta and control variables

@@
 
+cntrl_ajps_uncertainty <- readRDS("data/cntrl_ajps_uncertainty.rds")
+
+dcpo_analysis <- left_join(df_dcpo,cntrl_ajps_uncertainty, by=c("country","year","iter"="iter_se") )
+saveRDS(dcpo_analysis, "data/dcpo_analysis_ajps.rds")
+
+cls_ajps_uncertainty <- readRDS("data/cls_ajps_uncertainty.rds")
+
+cls_analysis <- left_join(cls_theta_uncertainty,cls_ajps_uncertainty, by=c("country","year"="Year","iter"="iter_se") )
+saveRDS(cls_analysis, "data/cls_analysis_ajps.rds")
+
 ```

### 2021-05-17 R/dcpo_apsr_uncertainty.R
codes for apsr control variables with uncertainty

@@ -1,0 +1,104 @@
+###cpi_uncertainty
+
+library(tidyverse)
+library(countrycode)
+library(haven)
+library(readxl)
+library(janitor)
+library(stringr)
+
+set.seed(313)
+
+cntrl_apsr_z <- readRds("data/cntrl_apsr_z.rds")
+cpi_95_19_update <- readRDS("data/cpi95_19_update.rds")
+cpi_2012error <- read_excel("data/CPI2019.xlsx", sheet ="CPI Timeseries 2012 - 2019")
+
+cpi_2012error_clean <- cpi_2012error %>%
+  row_to_names(row_number = 2) %>%
+  select(-contains("Rank"),-contains("Source"),-Region, -contains("CPI"),-ISO3) %>%
+  rename(country = Country) %>%
+  gather("year", "cpi_error", 2:9) %>%
+  mutate(year = str_replace_all(year, "[A-Za-z,]",""),
+         year = as.numeric(year),
+         cpi_error = as.numeric(cpi_error)) %>%
+  mutate(ISO = countrycode(country, origin = 'country.name', destination = 'iso3c')) %>%
+  mutate(country_name = countrycode::countrycode(ISO, "iso3c","country.name")) %>%
+  mutate(country_name = ifelse(country == "Kosovo","Kosovo",
+                               ifelse(country == "Yugoslavia","Yugoslavia",country_name))) %>%
+  rename(country_text = country,
+         country = country_name) %>%
+  select(-country_text,-ISO)
+
+cpi_95_19_error <- left_join(cpi_95_19_update,cpi_2012error_clean, by= c("country","year"))
+
+cpi_95_19_error <- cpi_95_19_error %>%
+  mutate(relative_error = cpi_error/cpi_100) %>%
+  select(-cpi) %>%
+  group_by(country) %>%
+  mutate(h_re = max(relative_error,na.rm = T),
+         h_re = ifelse(h_re =="-Inf",NA,h_re)) %>%
+  ungroup() %>%
+  mutate(cpi_error = ifelse(is.na(cpi_error), cpi_100*h_re,cpi_error)) %>%
+  group_by(country) %>%
+  mutate(cpi_100_m1 = lag(cpi_100)) %>%
+  arrange(country,year)
+
+cpi_pdist <- cpi_95_19_error %>%
[…]

### 2021-05-18 R/moc_function.R
modify data$iter_se to iter

@@ -35,4 +35,4 @@ methodComposition <- function (data, iter, model, vcov=plmHC, rsq=TRUE) {
 
 
 ###for analysis
-iter <- sort(sample(unique(data$iter_se), min(900, length(unique(data$iter)))))
+iter <- sort(sample(unique(data$iter), min(900, length(unique(data$iter)))))

### 2021-05-18 R/moc_function.R
delete analysis codes

@@ -32,7 +32,3 @@ methodComposition <- function (data, iter, model, vcov=plmHC, rsq=TRUE) {
   }
   return(coefdf)
 }
-
-
-###for analysis
-iter <- sort(sample(unique(data$iter), min(900, length(unique(data$iter)))))

### 2021-05-18 paper/dcpo_demsupport.Rmd
adding moc into the manuscript

@@
   drhutools,
-  dotwhisker # visualization
+  dotwhisker, # visualization
+  qs
 )
@@
 
-source("../R/tidy_pgmm.r")
+source(here::here("R", "tidy_pgmm.r"))
+source(here::here("R", "moc_function.R"))
 
@@
   DCPOtools::with_min_yrs(2)
-
 load(here::here("data", "claassen_m5_theta.rda"))
-load(here::here("data", "dcpo_input.rda"))
-load(here::here("data", "dcpo_theta.rda"))
-load(here::here("data", "dcpo_sigma.rda"))
 load(here::here("data", "dem_mood_apsr.RData"))
+# load(here::here("data", "dcpo_input.rda"))
+# load(here::here("data", "dcpo_theta.rda"))
+# load(here::here("data", "dcpo_sigma.rda"))
 
@@
 
+dcpo_apsr_cntrl <- readRDS("data/cntrl_apsr_uncertainty.rds")
+dcpo_apsr_analysis <- left_join(df_dcpo,dcpo_apsr_cntrl, by=c("country","year","iter"="iter_se") )
+saveRDS(dcpo_apsr_analysis, "data/dcpo_analysis_apsr.rds")
+qsave(dcpo_apsr_analysis, "data/dcpo_analysis_apsr_compress")
+
 cls_ajps_uncertainty <- readRDS("data/cls_ajps_uncertainty.rds")
@@
 \end{landscape}
+# Replication with Alternative Methods Accounting for Uncertainty
+
+```{r moc}
+
+```

### 2021-05-18 R/moc_function.R
moc conflict

@@ -12,7 +12,7 @@ methodComposition <- function (data, iter, model, vcov=plmHC, rsq=TRUE) {
   for (s in seq_along(iter)) {
     ## (1) Sample from p(x)
     it <- iter[s]
-    data_sample <- subset(data, iter_se == it)
+    data_sample <- subset(data, iter == it)
     ## (2) Sample from p(B|x,y):
     ##     (a) Estimate B_s and Cov(B_s) conditional on x_s.
     mod_sample <- update(model, data=data_sample)
@@ -35,4 +35,4 @@ methodComposition <- function (data, iter, model, vcov=plmHC, rsq=TRUE) {
 
 
 ###for analysis
-iter <- sort(sample(unique(data$iter_se), min(900, length(unique(data$iter)))))
+iter <- sort(sample(unique(data$iter), min(900, length(unique(data$iter)))))

### 2021-05-19 R/dcpo_ajps_rubin.R
R for creating dcpo_ajps_rubin analysis data

@@ -1,0 +1,34 @@
+###dcpo_rubin
+
+library(tidyverse)
+
+set.seed(313)
+
+#####analysis for rubin's rule
+cntrl_ajps_uncertainty <- readRDS("data/cntrl_ajps_uncertainty.rds")
+temp_df <- cntrl_ajps_uncertainty %>%
+  filter(iter_se == 1) %>%
+  select(country, year, Vdem_regime,muslism_prop_2010,dependence_pc_di,
+         lg_imp_mdpgdp,mdprgdp_grwth) %>%
+  mutate(regime = Vdem_regime > 1)
+
+libdem_list_temp <- readRDS("data/libdem_list.rda")
+
+load("data/theta_sigma_list.rda")
+
+list_temp <- theta_list %>%
+  map(~.x %>%
+        left_join(temp_df, by=c("country","year")) 
+  )
+
+dcpo_ajps_rubin <- list()
+dcpo_ajps_rubin <- purrr::map(1:900, function(anEntry) {
+  dcpo_ajps_rubin[[anEntry]] <- list_temp[[anEntry]] %>%
+    left_join(libdem_list_temp[[anEntry]],by = c("year", "country"))
+  return(dcpo_ajps_rubin)
+}) 
+
+save(dcpo_ajps_rubin, file = "data/dcpo_ajps_rubin.rda")
+
+
+

### 2021-05-19 R/dcpo_ajps_rubin.R
modify codes for the list

@@ -21,11 +21,11 @@ list_temp <- theta_list %>%
         left_join(temp_df, by=c("country","year")) 
   )
 
-dcpo_ajps_rubin <- list()
+
 dcpo_ajps_rubin <- purrr::map(1:900, function(anEntry) {
-  dcpo_ajps_rubin[[anEntry]] <- list_temp[[anEntry]] %>%
-    left_join(libdem_list_temp[[anEntry]],by = c("year", "country"))
-  return(dcpo_ajps_rubin)
+  list_temp[[anEntry]] %>% 
+    left_join(libdem_list[[anEntry]],by = c("year", "country")) %>% 
+    list()
 }) 
 
 save(dcpo_ajps_rubin, file = "data/dcpo_ajps_rubin.rda")

### 2021-05-19 R/moc_function.R
try purrr::map

@@ -32,3 +32,20 @@ methodComposition <- function (data, iter, model, vcov=plmHC, rsq=TRUE) {
   }
   return(coefdf)
 }
+
+methodComposition2 <- function (data, model, vcov=plmHC) {
+  coefdf <- purrr::map(data, function(data_sample) {
+    ## (2) Sample from p(B|x,y):
+    ##     (a) Estimate B_s and Cov(B_s) conditional on x_s.
+    mod_sample <- update(model, data=data_sample)
+    hatB_sample <- coef(mod_sample)
+    hatV_sample <- vcov(mod_sample)
+    ##     (b) Sample \data_sample{B_s} from MV(\hat{B_sample}, \hat{Cov(B_sample)}).
+    coefdf0 <- MASS::mvrnorm(n = 1, mu = hatB_sample, Sigma = hatV_sample)
+    return(coefdf0)
+  })
+  
+  
+  names(coefdf) <- names(coef(model))
+  return(coefdf)
+}

### 2021-05-19 R/moc_function.R
use Hu's idiom

@@ -34,13 +34,13 @@ methodComposition <- function (data, iter, model, vcov=plmHC, rsq=TRUE) {
 }
 
 methodComposition2 <- function (data, model, vcov=plmHC) {
-  coefdf <- purrr::map(data, function(data_sample) {
+  coefdf <- purrr::map(data, function(aData) {
     ## (2) Sample from p(B|x,y):
     ##     (a) Estimate B_s and Cov(B_s) conditional on x_s.
-    mod_sample <- update(model, data=data_sample)
-    hatB_sample <- coef(mod_sample)
-    hatV_sample <- vcov(mod_sample)
-    ##     (b) Sample \data_sample{B_s} from MV(\hat{B_sample}, \hat{Cov(B_sample)}).
+    aMod <- update(model, data=aData)
+    hatB_sample <- coef(aMod)
+    hatV_sample <- vcov(aMod)
+    ##     (b) Sample \aData{B_s} from MV(\hat{B_sample}, \hat{Cov(B_sample)}).
     coefdf0 <- MASS::mvrnorm(n = 1, mu = hatB_sample, Sigma = hatV_sample)
     return(coefdf0)
   })

### 2021-05-19 R/dcpo_ajps_rubin.R
make dcpo_ajps_rubin a list of dataframes

@@ -24,8 +24,7 @@ list_temp <- theta_list %>%
 
 dcpo_ajps_rubin <- purrr::map(1:900, function(anEntry) {
   list_temp[[anEntry]] %>% 
-    left_join(libdem_list[[anEntry]],by = c("year", "country")) %>% 
-    list()
+    left_join(libdem_list[[anEntry]],by = c("year", "country"))
 }) 
 
 save(dcpo_ajps_rubin, file = "data/dcpo_ajps_rubin.rda")

### 2021-05-31 R/dcpo_apsr_uncertainty.R
changes made during meeting with @Tyhcass on 5/26

@@ -9,7 +9,7 @@ library(stringr)
 
 set.seed(313)
 
-cntrl_apsr_z <- readRds("data/cntrl_apsr_z.rds")
+cntrl_apsr_z <- readRDS("data/cntrl_apsr_z.rds")
 cpi_95_19_update <- readRDS("data/cpi95_19_update.rds")
 cpi_2012error <- read_excel("data/CPI2019.xlsx", sheet ="CPI Timeseries 2012 - 2019")
 

### 2021-05-31 R/moc_summary.R

@@ -1,4 +1,3 @@
-<<<<<<< HEAD
 ###Moc summary
 
 pEmp <- function (x) {
@@ -22,9 +21,16 @@ MOCsumm <- function (moc, digits=3,
     var_names <- names(moc) %>% 
         str_c(collapse = "|")
     
-    summarise_at(moc, .vars=vars(matches(var_names)), .funs=ff) %>%
+    summarise_all(moc, .funs=ff) %>%
         mutate_all(funs(round(., digits=digits))) %>%
-        reshape2::melt(measure.vars=names(.))
+        reshape2::melt(measure.vars=names(.)) %>% 
+        separate(variable, into = c("term", "temp"), sep = "_(?=est|se|z|pnorm|pemp)") %>% 
+        pivot_wider(names_from = "temp", values_from = "value") %>% 
+        transmute(term = term,
+                  estimate = est,
+                  std.error = se) %>% 
+        filter(!term=="rsq"&!term=="adjrsq")
+        
 }
 
 MOCmean <- function (mod.ls) {
@@ -37,41 +43,3 @@ MOCsd <- function (mod.ls) {
 
 
 MOCsumm(model.ls[[]])
-=======
-###Moc summary
-
-pEmp <- function (x) {
-    p_pos <- mean(x < 0)
-    p_neg <- mean(x > 0)
-    p2side <- 2 * min(p_pos, p_neg)
-    p2side
-}
-
-pNorm <- function (x) {
-    z <- abs(mean(x)/sd(x))
-    p2side <- 2*(1 - pnorm(z))
-    p2side
-}
-
-
-MOCsumm <- function (moc, regex=var_names, digits=3,
-                     ff=funs(est = mean, se = sd, z = mean(.)/sd(.),
-                             pnorm = pNorm(.),
-                             pemp = pEmp(.))) {
-    summarise_at(moc, .vars=var_names, .funs=ff) %>%
-        mutate_all(funs(round(., digits=digits))) %>%
-        reshape2::melt(measure.vars=names(.))
-}
-
-
-MOCmean <- function (mod.ls) {
-    plyr::llply(mod.ls, function (x) apply(x, 2, mean))
-}
-
-MOCsd <- function (mod.ls) {
-    plyr::llply(mod.ls, function (x) apply(x, 2, sd))
-}
-
-
-MOCsumm(model.ls[[]])
->>>>>>> 4dac44d45c2ae215a5086ef9f3c2e3d497d0aeaf

### 2021-06-01 paper/dcpo_demsupport.Rmd
fixed the table format

@@
       - \usepackage{fullpage}
-      - \usepackage{lscape} #better for printing, page displayed vertically, content in landscape mode, \usepackage{pdflscape} better for screen, page displayed horizontally, content in landscape mode
+      - \usepackage{pdflscape} #\usepackage{lscape} better for printing, page displayed vertically, content in landscape mode, \usepackage{pdflscape} better for screen, page displayed horizontally, content in landscape mode
+      - \newcommand{\blandscape}{\begin{landscape}}
+      - \newcommand{\elandscape}{\end{landscape}}
 ---
@@
 p_load(
-  dataverse, # data scraping
+  # data scrapping
+  dataverse, 
   DCPOtools, mitools,
-  boot, plm, # analysis
+  boot, 
+  here,
+  # analysis
+  plm, 
+  rstan, 
+  # presentation
   flextable, 
-  broomExtra, kableExtra, modelsummary, # tabulation
+  broomExtra, 
+  kableExtra, 
+  modelsummary, 
   gridExtra,
-  latex2exp, # visualization
-  rstan, # Bayesian estimation
-  tidyverse, janitor, glue, # data wrangling
+  latex2exp,
   drhutools,
-  dotwhisker, # visualization
+  dotwhisker, 
+  # data wrangling
+  tidyverse, 
+  janitor, 
+  glue, 
   qs
@@
 
-source(here::here("R", "tidy_pgmm.r"))
-source(here::here("R", "moc_function.R"))
+source(here("R", "tidy_pgmm.r"))
+source(here("R", "moc_function.R"))
 
@@
 theme_set(theme_minimal())
+
+# Data input
+
+supdem <- read.csv("../data/Support_democracy_ajps.csv")
+v_dem <- read.csv("../data/vdem15.csv")
+sd.plm <- pdata.frame(supdem, index = c("Country", "Year"))
+
+claassen_replication <- readRDS("../data/claassen_replication.rds") %>% 
+  janitor::clean_names() %>% 
+  DCPOtools::with_min_yrs(2)
+load(here("data", "claassen_m5_theta.rda"))
+load(here("data", "dem_mood_apsr.RData"))
+load(here("data", "dcpo_input.rda"))
+# load(here::here("data", "dcpo_theta.rda"))
+# load(here::here("data", "dcpo_sigma.rda"))
+# load(here("data", "dcpo_ajps_rubin.rda"))
+
+## Beck-Katz panel-corrected standard errors
+vcovBK_se <- function(x) {
+  plm::vcovBK(x, cluster = "time") %>% 
+    diag() %>% 
+    sqrt()
+}
+
+vcovHC_se <-  function(x) {
+  plm::vcovHC(x, method="arellano", cluster="group") %>%  #default setting
+    diag() %>% 
+    sqrt()
+}
+
+reformat_dcpo_output <- function(x, parameter_name) {
+  df_temp <- x %>% 
+    as_tibble(.name_repair = ~ls_country) %>% 
+    mutate(year = first_year + row_number() - 1) %>% 
+    pivot_longer(cols = all_of(ls_country),
+                 names_to = "country",
+                 values_to = parameter_name) %>%
+    arrange(country, year)
+  return(df_temp)
+}
 ```
@@
 
-```{r dataInput, eval=TRUE}
-
-supdem <- read.csv("../data/Support_democracy_ajps.csv")
-v_dem <- read.csv("../data/vdem15.csv")
-sd.plm <- pdata.frame(supdem, index = c("Country", "Year"))
-
-claassen_replication <- readRDS("../data/claassen_replication.rds") %>% 
-  janitor::clean_names() %>% 
-  DCPOtools::with_min_yrs(2)
-load(here::here("data", "claassen_m5_theta.rda"))
-load(here::here("data", "dem_mood_apsr.RData"))
-# load(here::here("data", "dcpo_input.rda"))
-# load(here::here("data", "dcpo_theta.rda"))
-# load(here::here("data", "dcpo_sigma.rda"))
-
-## Beck-Katz panel-corrected standard errors
-vcovBK_se <- function(x) {
-  plm::vcovBK(x, cluster = "time") %>% 
-    diag() %>% 
-    sqrt()
-}
-
-vcovHC_se <-  function(x) {
-  plm::vcovHC(x, method="arellano", cluster="group") %>%  #default setting
-    diag() %>% 
-    sqrt()
-}
-
-reformat_dcpo_output <- function(x, parameter_name) {
-  df_temp <- x %>% 
-    as_tibble(.name_repair = ~ls_country) %>% 
-    mutate(year = first_year + row_number() - 1) %>% 
-    pivot_longer(cols = all_of(ls_country),
-                 names_to = "country",
-                 values_to = parameter_name) %>%
-    arrange(country, year)
-  return(df_temp)
-}
-```
-
 ```{r claassenAJPS, eval=TRUE}
@@
 ```{r dcpoUncertaintyAJPS}
-df_dcpo <- purrr::map(1:1000, function(anEntry) {
-  dcpo_theta$theta[anEntry,,] %>% 
-    reformat_dcpo_output("theta") %>% 
-    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
-              by = c("year", "country")) %>%
-    left_join(df_controls, by = c("country", "year")) %>% 
-    mutate(theta_dem = theta * regime,
-           theta_aut = theta * (1 - regime)) %>% 
-    plm::pdata.frame(index = c("country", "year"))
-})
+df_dcpo <- dcpo_ajps_rubin %>% map(~ .)
+
+# df_dcpo <- purrr::map(1:1000, function(anEntry) {
+#   dcpo_theta$theta[anEntry,,] %>% 
+#     reformat_dcpo_output("theta") %>% 
+#     left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
+#               by = c("year", "country")) %>%
+#     left_join(df_controls, by = c("country", "year")) %>% 
+#     mutate(theta_dem = theta * regime,
+#            theta_aut = theta * (1 - regime)) %>% 
+#     plm::pdata.frame(index = c("country", "year"))
+# })
 
@@
 
-```{r visualizeAJPS, fig.cap= "\\label{fig:visualizeAJPS}The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=10}
+```{r visualizeAJPS, fig.cap= "The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=10}
 
@@
 ```{r dcpoUncertaintyAPSR}
-ls_country <- levels(dcpo_input$data$kk)
-first_year <- min(dcpo_input$data$year)
-
-df_dcpoUncertainAPSR <- purrr::map(1:1000, function(anEntry) {
-  dcpo_theta$theta[anEntry,,] %>% 
-    reformat_dcpo_output("theta") %>% 
-    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
-              by = c("year", "country")) %>%
-    left_join(df_controls, by = c("country", "year")) %>% 
-    plm::pdata.frame(index = c("country", "year"))
-})
+# ls_country <- levels(dcpo_input$data$kk)
+# first_year <- min(dcpo_input$data$year)
+# 
+# df_dcpoUncertainAPSR <- purrr::map(1:1000, function(anEntry) {
+#   dcpo_theta$theta[anEntry,,] %>% 
+#     reformat_dcpo_output("theta") %>% 
+#     left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
+#               by = c("year", "country")) %>%
+#     left_join(df_controls, by = c("country", "year")) %>% 
+#     plm::pdata.frame(index = c("country", "year"))
+# })
 
@@
 
+###Duble check the dataset--------------
 ls_mod <- c(
@@
 
-```{r visualizedAPSR, fig.cap= "\\label{fig:visualizedAPSR} The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}
-
-load(here::here("output", "estimates_clsMeanAPSR.RDS"))
-load(here::here("output", "estimates_clsAPSR.RDS"))
-result_dcpoAPSR <- readRDS(here::here("output", "estimates_dcpoAPSR.RDS"))
+```{r visualizedAPSR, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}
+
+load(here("output", "estimates_clsMeanAPSR.RDS"))
+result_clsUncertainAPSR <- readRDS(here("output", "estimates_clsAPSR.RDS"))
+result_dcpoAPSR <- readRDS(here("output", "estimates_dcpoAPSR.RDS"))
 
@@
              title = "Original") %>%
+
+  kableExtra::kable_styling(font_size = 8) %>% 
   kableExtra::kable_styling(latex_options = "HOLD_position")
@@
 
-\pagebreak
+\blandscape
 
 # Numeric Results for Replicating Claassen 2020b
-
-\begin{landscape}
 
@@
 
-names(tb_result_clsAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM w. Corruption", "ECM w. Corruption-Regime", "FD w. Corruption", "FD w. Corruption-Regime")
+names(tb_result_clsAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
 
@@
              output = "latex") %>% 
+  kableExtra::kable_styling(font_size = 7) %>% 
   kableExtra::kable_styling(latex_options = "HOLD_position")
@@
 
-\pagebreak
+\elandscape
+
+\blandscape
 
@@
 
-names(tb_result_clsUncertainAPSR) <- c("ECM", "ECM-Regime", 
-                          "FD", "FD-Regime", 
-                          "ECM w. Corruption", "ECM w. Corruption-Regime", 
-                          "FD w. Corruption", "FD w. Corruption-Regime")
+names(tb_result_clsUncertainAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
 
@@
 
-names(tb_result_dcpoAPSR) <- c("ECM", "ECM-Regime", 
-                          "FD", "FD-Regime", 
-                          "ECM w. Corruption", "ECM w. Corruption-Regime", 
-                          "FD w. Corruption", "FD w. Corruption-Regime")
+names(tb_result_dcpoAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
 
@@
 
-\pagebreak
+\elandscape
+
 ```{r datawitherrors}
@@
 
-\end{landscape}
+# Results Accounting for the Uncertainty in Both the Outcome and Explanatory Variables
+
+```{r claassenFullUncertaintyAJPS}
+
+load(here("data", "cls_ajps.rda")) # produced by cls_ajps_apsr_uncertain.R
+
+ls_iv <- c("plm::lag(theta, 1)", 
+    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) ")
+
+ls_method <- c("plm", "pgmm")
+
+ls_eq <- glue("Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + {ls_iv} + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)")
+
+ls_mod <- c(
+    glue("plm({ls_eq}, model = 'pooling', data = aData)"),
+    glue(
+        "pgmm({ls_eq} | plm::lag(Libdem_VD, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
+    )
+)
+
+result_clsUncertainFull <- map(ls_mod, function(aMod){ # reading a model
+  result <- map(cls_ajps, function(aData){ # applying to the 1000 datasets
+    eval(parse(text = aMod))
+  })
+
+  result_betas <- mitools::MIextract(result, fun = coef)
+
+  ## Not work with ifelse
+  if(class(result[[1]])[1] == "plm"){
+      result_vars <- mitools::MIextract(result, fun = vcovBK_se)
+  }else{
+      result_vars <- mitools::MIextract(result, fun = vcovHC_se)
+  }
+
+  tidy_clsUncertain <- summary(mitools::MIcombine(results = result_betas, 
+                             variance = result_vars)) %>% 
+    rownames_to_column(var = "term") %>%
+        rename(conf.low = `(lower`,
+               conf.high = `upper)`,
+               estimate = results) %>%
+        filter(!str_detect(term, "(Intercept)"))
+
+  if(class(result[[1]]) == "plm"){ 
+    glance_clsUncertain <- glance.plm(result[[1]]) # using the customized glance function
+  }else{
+    glance_clsUncertain <- glance(result[[1]])
+  }
+
+  result_clsUncertain <- list(tidy_clsUncertain, glance_clsUncertain)
+})
+
+names(result_clsUncertainFull) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
+
+saveRDS(result_clsUncertainFull, file = here::here("output", "estimates_clsAJPSfullUncertain.RDS"))
+```
+
+```{r dcpoFullUncertaintyAJPS}
+load(here("data", "dcpo_ajps.rda")) # produced by dcpo_ajps_apsr_uncertain.R
+
+ls_iv <- c("plm::lag(theta, 1)", 
+    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) ")
+
+ls_method <- c("plm", "pgmm")
+
+ls_eq <- glue("Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + {ls_iv} + plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) + plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)")
+
+ls_mod <- c(
+    glue("plm({ls_eq}, model = 'pooling', data = aData)"),
+    glue(
+        "pgmm({ls_eq} | plm::lag(Vdem_libdem, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
+    )
+)
+
+result_dcpoUncertainFull <- map(ls_mod, function(aMod){ # reading a model
+  result <- map(dcpo_ajps, function(aData){ # applying to the 1000 datasets
+    eval(parse(text = aMod))
+  })
+
+  result_betas <- mitools::MIextract(result, fun = coef)
+
+  ## Not work with ifelse
+  if(class(result[[1]])[1] == "plm"){
+      result_vars <- mitools::MIextract(result, fun = vcovBK_se)
+  }else{
+      result_vars <- mitools::MIextract(result, fun = vcovHC_se)
+  }
+
+  tidy_dcpoUncertain <- summary(mitools::MIcombine(results = result_betas, 
+                             variance = result_vars)) %>% 
+    rownames_to_column(var = "term") %>%
+        rename(conf.low = `(lower`,
+               conf.high = `upper)`,
+               estimate = results) %>%
+        filter(!str_detect(term, "(Intercept)"))
+
+  if(class(result[[1]]) == "plm"){ 
+    glance_dcpoUncertain <- glance.plm(result[[1]]) # using the customized glance function
+  }else{
+    glance_dcpoUncertain <- glance(result[[1]])
+  }
+
+  result_dcpoUncertain <- list(tidy_dcpoUncertain, glance_dcpoUncertain)
+})
+
+names(result_dcpoUncertainFull) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
+
+saveRDS(result_dcpoUncertainFull, file = here::here("output", "estimates_dcpoAJPSfullUncertain.RDS"))
+```
+
+```{r visualizeFullUncertainAJPS, fig.cap= "The Effect of Public Support on Democracy", eval = FALSE, fig.width=7.5, fig.height=10}
+
+# Very weird phenomenon that the same type of rds files needs different ways to read
+# Suggesting using the qs or csv data type in future.
+result_cls <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
+result_clsUncertainFull <- readRDS(here("output", "estimates_clsAJPSfullUncertain.RDS"))
+result_dcpoUncertainFull <- readRDS(here("output", "estimates_dcpoAJPSfullUncertain.RDS"))
+
+result_pooled <- bind_rows(
+  mutate(result_cls$pooled[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainFull$pooled[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertainFull$pooled[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "Pooled")
+
+result_gmm <- bind_rows(
+  mutate(result_cls$gmm[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainFull$gmm[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertainFull$gmm[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "GMM")
+
+result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democracy\n (t-1)",
+        "Democracy\n (t-2)",
+      "Support\n (t-1)",
+      "Log GDP\n per capita\n (t-1)",
+      "GDP per\n capita growth\n (t-1)",
+      "Regional\n democracy\n (t-1)",
+      "Percent\n Muslim\n (t-1)",
+      "Resource\n dependence\n (t-1)"),
+    time = 6), 
+    type = factor(type, levels = c("Pooled", "GMM")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
+
+terms <- factor(rev(c("Democracy[t-1]",
+        "Democracy[t-2]",
+      "Support[t-1]",
+      "Log~GDP~per~capita[t-1]",
+      "GDP~per~capita~growth[t-1]",
+      "Regional~democracy[t-1]",
+      "Percent~Muslim[t-1]",
+      "Resource~dependence[t-1]")), levels =
+      rev(c("Democracy[t-1]",
+        "Democracy[t-2]",
+      "Support[t-1]",
+      "Log~GDP~per~capita[t-1]",
+      "GDP~per~capita~growth[t-1]",
+      "Regional~democracy[t-1]",
+      "Percent~Muslim[t-1]",
+      "Resource~dependence[t-1]")))
+
+# ggplot produces reversed plot, and embarrassed to say, I can't fix, again. Any thought?
+# What I've tried
+# 1. using guide_legend(reverse = TRUE) will change the legend's order not the plot.
+# 2. ordering models with factor levels using the original names or even c("1", "2", "3")
+# 2. redefining the order of model in the dataframe or in dwplot 
+# 3. checking the dwplot codes, model works in line 453, but nothing looks helpful
+# 4. Every post online is to reverse
+
+plot_AJPS1 <- dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms))) +
+  scale_color_grey(start = 0.4, end = 0.8) +
+  labs(
+    title = "DV: V-Dem Liberal Democracy Index",
+    subtitle = "Regime Compacted"
+  ) +
+  facet_wrap(~type, scales = "free_x") + 
+  theme(legend.position = "none")
+
+# the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
+# The trick is  to use guide = guide_legend(reverse = TRUE) within scale_color_*(); see below in plotAJPS2. --FS
+
+result_regime <- bind_rows(
+  mutate(result_cls$`pooled-regime`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainFull$`pooled-regime`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertainFull$`pooled-regime`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "Pooled")
+
+result_regimeGmm <- bind_rows(
+  mutate(result_cls$`gmm-regime`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainFull$`gmm-regime`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertainFull$`gmm-regime`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "GMM")
+
+result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democracy\n (t-1)",
+        "Democracy\n (t-2)",
+      "Support\n demo only\n (t-1)",
+      "Support\n auto only\n (t-1)",
+      "Log GDP\n per capita\n (t-1)",
+      "GDP per\n capita growth\n (t-1)",
+      "Regional\n democracy\n (t-1)",
+      "Percent\n Muslim\n (t-1)",
+      "Resource\n dependence\n (t-1)"),
+    time = 6), 
+    type = factor(type, levels = c("Pooled", "GMM")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
+
+terms2 <- factor(rev(c("Democracy[t-1]",
+                       "Democracy[t-2]",
+                       "Support[t-1] (democracies~only)",
+                       "Support[t-1] (autocracies~only)",
+                       "Log~GDP~per~capita[t-1]",
+                       "GDP~per~capita~growth[t-1]",
+                       "Regional~democracy[t-1]",
+                       "Percent~Muslim[t-1]",
+                       "Resource~dependence[t-1]")), levels =
+                   rev(c("Democracy[t-1]",
+                         "Democracy[t-2]",
+                         "Support[t-1] (democracies~only)",
+                         "Support[t-1] (autocracies~only)",
+                         "Log~GDP~per~capita[t-1]",
+                         "GDP~per~capita~growth[t-1]",
+                         "Regional~democracy[t-1]",
+                         "Percent~Muslim[t-1]",
+                         "Resource~dependence[t-1]")))
+
+plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
+    scale_y_discrete(labels = parse(text = levels(terms2))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  labs(
+    title = "",
+    subtitle = "Regime Specific"
+  ) +
+  facet_wrap(~type, scales = "free_x") +
+  theme(legend.position = "bottom", 
+        legend.title = element_blank())
+
+legend <- get_legend(plot_AJPS2)
+
+plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
+
+grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
+
+```
+
+```{r claassenFullUncertaintyAPSR}
+
+load(here("data", "cls_apsr.rda")) # produced by cls_ajps_apsr_uncertain.R
+
+ls_ivECM <- c("diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)", 
+              "diff(Polyarchy_z, lag = 1) + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)")
+ls_ctrlECM <- c("", " + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1)")
+
+ls_eqECM <- glue("diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)") %>% 
+  outer(ls_ctrlECM, paste0) %>% 
+  as.vector()
+
+ls_ivFD <- c("Libdem_z",
+             "Polyarchy_z + Liberal_z")
+
+ls_ctrlFD <- c("", " + Corrup_TI_z")
+
+ls_eqFD <- glue("diff(theta, lag = 1) ~ {ls_ivFD} + lnGDP_imp") %>% 
+  outer(ls_ctrlFD, paste0) %>% 
+  as.vector()
+
+ls_mod <- c(
+  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
+  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
+)
+
+result_clsFullUncertainAPSR <- map(ls_mod, function(aMod){ # reading a model
+  result <- map(cls_apsr, function(aData){ # applying to the 1000 datasets
+    eval(parse(text = aMod))
+  })
+
+  result_betas <- mitools::MIextract(result, fun = coef)
+
+  result_vars <- mitools::MIextract(result, fun = vcovHC_se)
+
+  tidy_clsUncertainAPSR <- summary(mitools::MIcombine(results = result_betas, 
+                             variance = result_vars)) %>% 
+    rownames_to_column(var = "term") %>%
+        rename(conf.low = `(lower`,
+               conf.high = `upper)`,
+               estimate = results) %>%
+        filter(!str_detect(term, "(Intercept)"))
+
+  glance_clsUncertainAPSR <- glance.plm(result[[1]])
+
+  result_clsUncertainAPSR <- list(tidy_clsUncertainAPSR, glance_clsUncertainAPSR)
+})
+
+names(result_clsFullUncertainAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", "fd1", "fd-regime1", "fd2", "fd-regime2")
+
+saveRDS(result_clsFullUncertainAPSR, file = here::here("output", "estimates_clsAPSR.RDS"))
+
+```
+
+```{r dcpoFullUncertaintyAPSR}
+load(here("data", "dcpo_apsr.rda")) # produced by cls_ajps_apsr_uncertain.R
+
+ls_ivECM <- c("diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1)", 
+              "diff(Vdem_polyarchy_z, lag = 1) + plm::lag(Vdem_polyarchy_z, 1) + diff(Vdem_liberal_z, lag = 1) + plm::lag(Vdem_liberal_z, 1)")
+ls_ctrlECM <- c("", " + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1)")
+
+ls_eqECM <- glue("diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + {ls_ivECM} + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1)") %>% 
+  outer(ls_ctrlECM, paste0) %>% 
+  as.vector()
+
+ls_ivFD <- c("Vdem_libdem_z",
+             "Vdem_polyarchy_z + Vdem_liberal_z")
+
+ls_ctrlFD <- c("", " + corruption_z")
+
+ls_eqFD <- glue("theta ~ {ls_ivFD} + lg_imp_mdpgdp") %>% 
+  outer(ls_ctrlFD, paste0) %>% 
+  as.vector()
+
+### Different datasets
+
+###Duble check the dataset--------------
+ls_mod <- c(
+  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
+  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
+)
+
+result_dcpoUncertainAPSR <- map(ls_mod, function(aMod){ # reading a model
+  result <- map(dcpo_apsr, function(aData){ # applying to the 1000 datasets
+    eval(parse(text = aMod))
+  })
+
+  result_betas <- mitools::MIextract(result, fun = coef)
+
+  result_vars <- mitools::MIextract(result, fun = vcovHC_se)
+
+  tidy_dcpoUncertainAPSR <- summary(mitools::MIcombine(results = result_betas, 
+                             variance = result_vars)) %>% 
+    rownames_to_column(var = "term") %>%
+        rename(conf.low = `(lower`,
+               conf.high = `upper)`,
+               estimate = results) %>%
+        filter(!str_detect(term, "(Intercept)"))
+
+  glance_dcpoUncertainAPSR <- glance.plm(result[[1]])
+
+  result_dcpoUncertainAPSR <- list(tidy_dcpoUncertainAPSR, glance_dcpoUncertainAPSR)
+})
+
+names(result_dcpoUncertainAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",  "fd1", "fd-regime1", "fd2", "fd-regime2")
+
+saveRDS(result_dcpoUncertainAPSR, file = here::here("output", "estimates_dcpoAPSR.RDS"))
+```
+
 # Replication with Alternative Methods Accounting for Uncertainty
-
-```{r moc}
-
-```

### 2021-06-01 paper/dcpo_demsupport.Rmd
adding visualization for full uncertain

@@
 
-```{r visualizeFullUncertainAJPS, fig.cap= "The Effect of Public Support on Democracy", eval = FALSE, fig.width=7.5, fig.height=10}
+```{r visualizeFullUncertainAJPS, fig.cap= "The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=10}
 
@@
 
+```{r visualizedAPSR, fig.cap= "The Effect of Democracy on Public Support", eval = FALSE, fig.width=7, fig.height=10}
+
+result_cls <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
+result_clsUncertainFull <- readRDS(here("output", "estimates_clsAJPSfullUncertain.RDS"))
+result_dcpoUncertainFull <- readRDS(here("output", "estimates_dcpoAJPSfullUncertain.RDS"))
+
+result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
+result_clsFullUncertainAPSR <- readRDS(here("output", "estimates_clsAPSRfullUncertain.RDS"))
+result_dcpoFullUncertainAPSR <- readRDS(here("output", "estimates_dcpoAPSRfullUncertain.RDS"))
+
+# Regime compacted ####
+
+result_ecm1 <- bind_rows(
+  mutate(result_clsAPSR$pooled1[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainAPSR$pooled1[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoAPSR$pooled1[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "ECM")
+
+result_fd1 <- bind_rows(
+  mutate(result_clsAPSR$fd1[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainAPSR$fd1[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoAPSR$fd1[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "First Difference")
+
+result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+      "Liberal Democracy\n (Difference)",
+      "Liberal Democracy\n (t-1)",
+      "Log GDP\n per capita\n (Difference)",
+      "Log GDP\n (t-1)"),
+    time = 3),
+    rep(
+      c("Liberal Democracy\n (Difference)", 
+        "Log GDP\n per capita\n (Difference)"), 
+      time = 3
+    )),
+    type = factor(type, levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
+  )
+
+terms1 <- factor(rev(c("Support[t-1]",
+                      "Support[t-2]",
+                      "Delta~Liberal~democracy",
+                      "Liberal~democracy[t-1]",
+                      "Delta~Log~GDP~per~capita",
+                      "Log~GDP[t-1]")),
+                levels = rev(c("Support[t-1]",
+                               "Support[t-2]",
+                               "Delta~Liberal~democracy",
+                               "Liberal~democracy[t-1]",
+                               "Delta~Log~GDP~per~capita",
+                               "Log~GDP[t-1]")))
+
+plot_APSR1 <- dwplot(result_APSR1, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms1))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  # scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "DV: Public Support for Democracy",
+    subtitle = "Regime Compacted"
+  ) +
+  facet_wrap(~type, scales = "free_x") + 
+  theme(legend.position = "none")
+
+result_ecm2 <- bind_rows(
+  mutate(result_clsAPSR$pooled2[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainAPSR$pooled2[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoAPSR$pooled2[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "ECM")
+
+result_fd2 <- bind_rows(
+  mutate(result_clsAPSR$fd2[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainAPSR$fd2[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoAPSR$fd2[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "First Difference")
+
+result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+      "Liberal Democracy\n (Difference)",
+      "Liberal Democracy\n (t-1)",
+      "Log GDP\n per capita\n (Difference)",
+      "Log GDP\n (t-1)",
+      "Corruption\n (Difference)",
+      "Corruption\n (t-1)"
+      ),
+    time = 3),
+    rep(
+      c("Liberal Democracy\n (Difference)", 
+        "Log GDP\n per capita\n (Difference)",
+        "Corruption\n (Difference)"), 
+      time = 3
+    )),
+    type = factor(type, levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
+  )
+
+terms2 <- factor(rev(c("Support[t-1]",
+                      "Support[t-2]",
+                      "Delta~Liberal~democracy",
+                      "Liberal~democracy[t-1]",
+                      "Delta~Log~GDP~per~capita",
+                      "Log~GDP[t-1]",
+                      "Delta~Corruption",
+                      "Corruption[t-1]")),
+                levels = rev(c("Support[t-1]",
+                               "Support[t-2]",
+                               "Delta~Liberal~democracy",
+                               "Liberal~democracy[t-1]",
+                               "Delta~Log~GDP~per~capita",
+                               "Log~GDP[t-1]",
+                               "Delta~Corruption",
+                               "Corruption[t-1]")))
+
+plot_APSR2 <- dwplot(result_APSR2, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms2))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  # scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "",
+    subtitle = "W. Corruption"
+  ) +
+  facet_wrap(~type, scales = "free_x") +
+  theme(legend.position = "none")
+
+# Regime specified ####
+
+result_ecmReg1 <- bind_rows(
+  mutate(result_clsAPSR$`pooled-regime1`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainAPSR$`pooled-regime1`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoAPSR$`pooled-regime1`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "ECM")
+
+result_fdReg1 <- bind_rows(
+  mutate(result_clsAPSR$`fd-regime1`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainAPSR$`fd-regime1`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoAPSR$`fd-regime1`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "First Difference")
+
+result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+      "Electoral Democracy\n (Difference)",
+      "Electoral Democracy\n (t-1)",
+      "Minoritarian Democracy\n (Difference)",
+      "Minoritarian Democracy\n (t-1)",
+      "Log GDP\n per capita\n (Difference)",
+      "Log GDP\n (t-1)"),
+    time = 3),
+    rep(
+      c("Electoral Democracy\n (Difference)", 
+        "Minoritarian Democracy\n (Difference)",
+        "Log GDP\n per capita\n (Difference)"), 
+      time = 3
+    )),
+    type = factor(type, levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
+  )
+
+terms3 <- factor(rev(c("Support[t-1]",
+                      "Support[t-2]",
+                      "Delta~Electoral~democracy",
+                      "Electoral~democracy[t-1]",
+                      "Delta~Minoritarian~democracy",
+                      "Minoritarian~democracy[t-1]",
+                      "Delta~Log~GDP~per~capita",
+                      "Log~GDP[t-1]")),
+                levels = rev(c("Support[t-1]",
+                      "Support[t-2]",
+                      "Delta~Electoral~democracy",
+                      "Electoral~democracy[t-1]",
+                      "Delta~Minoritarian~democracy",
+                      "Minoritarian~democracy[t-1]",
+                      "Delta~Log~GDP~per~capita",
+                      "Log~GDP[t-1]")))
+
+plot_RegAPSR1 <- dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms3))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  # scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "",
+    subtitle = "Regime Specified"
+  ) +
+  facet_wrap(~type, scales = "free_x") + 
+  theme(legend.position = "none")
+
+result_ecmReg2 <- bind_rows(
+  mutate(result_clsAPSR$`pooled-regime2`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainAPSR$`pooled-regime2`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoAPSR$`pooled-regime2`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "ECM")
+
+result_fdReg2 <- bind_rows(
+  mutate(result_clsAPSR$`fd-regime2`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainAPSR$`fd-regime2`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoAPSR$`fd-regime2`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "First Difference")
+
+result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+      "Electoral Democracy\n (Difference)",
+      "Electoral Democracy\n (t-1)",
+      "Minoritarian Democracy\n (Difference)",
+      "Minoritarian Democracy\n (t-1)",
+      "Log GDP\n per capita\n (Difference)",
+      "Log GDP\n (t-1)",
+      "Corruption\n (Difference)",
+      "Corruption\n (t-1)"
+      ),
+    time = 3),
+    rep(
+      c("Electoral Democracy\n (Difference)", 
+        "Minoritarian Democracy\n (Difference)",
+        "Log GDP\n per capita\n (Difference)",
+        "Corruption\n (Difference)"), 
+      time = 3
+    )),
+    type = factor(type, levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
+  )
+
+terms4 <- factor(rev(c("Support[t-1]",
+                      "Support[t-2]",
+                      "Delta~Electoral~democracy",
+                      "Electoral~democracy[t-1]",
+                      "Delta~Minoritarian~democracy",
+                      "Minoritarian~democracy[t-1]",
+                      "Delta~Log~GDP",
+                      "Log~GDP[t-1]",
+                      "Delta~Corruption",
+                      "Corruption[t-1]")),
+                levels = rev(c("Support[t-1]",
+                               "Support[t-2]",
+                               "Delta~Electoral~democracy",
+                               "Electoral~democracy[t-1]",
+                               "Delta~Minoritarian~democracy",
+                               "Minoritarian~democracy[t-1]",
+                               "Delta~Log~GDP",
+                               "Log~GDP[t-1]",
+                               "Delta~Corruption",
+                               "Corruption[t-1]")))
+
+plot_RegAPSR2 <- dwplot(result_RegAPSR2, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms4))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  # scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "",
+    subtitle = "Regime Specified w. Corruption"
+  ) +
+  facet_wrap(~type, scales = "free_x") +
+  theme(legend.position = "bottom", 
+        legend.title = element_blank())
+
+legend <- get_legend(plot_RegAPSR2)
+
+plot_RegAPSR2 <- plot_RegAPSR2 + theme(legend.position = "none")
+
+grid.arrange(plot_APSR1, plot_APSR2, plot_RegAPSR1, plot_RegAPSR2, legend, ncol = 1)
+```
+
 # Replication with Alternative Methods Accounting for Uncertainty

### 2021-06-01 paper/dcpo_demsupport.Rmd
corrected the saving files
uncertain for apsr analyses

--- 2021-06-01 paper/dcpo_demsupport.Rmd
@@
 
-saveRDS(result_clsFullUncertainAPSR, file = here::here("output", "estimates_clsAPSR.RDS"))
+saveRDS(result_clsFullUncertainAPSR, file = here::here("output", "estimates_clsFullUncertainAPSR.RDS"))
 
@@
 
-saveRDS(result_dcpoUncertainAPSR, file = here::here("output", "estimates_dcpoAPSR.RDS"))
+saveRDS(result_dcpoUncertainAPSR, file = here::here("output", "estimates_dcpoUncertainAPSR.RDS"))
+```
+
+```{r visualizedFullUncertainAPSR, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}
+
+result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
+result_clsFullUncertainAPSR <- readRDS(here("output", "estimates_clsFullUncertainAPSR.RDS"))
+result_dcpoFullUncertainAPSR <- readRDS(here("output", "estimates_dcpoUncertainAPSR.RDS"))
+
+# Regime compacted ####
+
+result_ecm1 <- bind_rows(
+  mutate(result_clsAPSR$pooled1[[1]], model = "Claassen 2020a"),
+  mutate(result_clsFullUncertainAPSR$pooled1[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoFullUncertainAPSR$pooled1[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "ECM")
+
+result_fd1 <- bind_rows(
+  mutate(result_clsAPSR$fd1[[1]], model = "Claassen 2020a"),
+  mutate(result_clsFullUncertainAPSR$fd1[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoFullUncertainAPSR$fd1[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "First Difference")
+
+result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+      "Liberal Democracy\n (Difference)",
+      "Liberal Democracy\n (t-1)",
+      "Log GDP\n per capita\n (Difference)",
+      "Log GDP\n (t-1)"),
+    time = 3),
+    rep(
+      c("Liberal Democracy\n (Difference)", 
+        "Log GDP\n per capita\n (Difference)"), 
+      time = 3
+    )),
+    type = factor(type, levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
+  )
+
+terms1 <- factor(rev(c("Support[t-1]",
+                      "Support[t-2]",
+                      "Delta~Liberal~democracy",
+                      "Liberal~democracy[t-1]",
+                      "Delta~Log~GDP~per~capita",
+                      "Log~GDP[t-1]")),
+                levels = rev(c("Support[t-1]",
+                               "Support[t-2]",
+                               "Delta~Liberal~democracy",
+                               "Liberal~democracy[t-1]",
+                               "Delta~Log~GDP~per~capita",
+                               "Log~GDP[t-1]")))
+
+plot_APSR1 <- dwplot(result_APSR1, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms1))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  # scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "DV: Public Support for Democracy",
+    subtitle = "Regime Compacted"
+  ) +
+  facet_wrap(~type, scales = "free_x") + 
+  theme(legend.position = "none")
+
+result_ecm2 <- bind_rows(
+  mutate(result_clsAPSR$pooled2[[1]], model = "Claassen 2020a"),
+  mutate(result_clsFullUncertainAPSR$pooled2[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoFullUncertainAPSR$pooled2[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "ECM")
+
+result_fd2 <- bind_rows(
+  mutate(result_clsAPSR$fd2[[1]], model = "Claassen 2020a"),
+  mutate(result_clsFullUncertainAPSR$fd2[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoFullUncertainAPSR$fd2[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "First Difference")
+
+result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+      "Liberal Democracy\n (Difference)",
+      "Liberal Democracy\n (t-1)",
+      "Log GDP\n per capita\n (Difference)",
+      "Log GDP\n (t-1)",
+      "Corruption\n (Difference)",
+      "Corruption\n (t-1)"
+      ),
+    time = 3),
+    rep(
+      c("Liberal Democracy\n (Difference)", 
+        "Log GDP\n per capita\n (Difference)",
+        "Corruption\n (Difference)"), 
+      time = 3
+    )),
+    type = factor(type, levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
+  )
+
+terms2 <- factor(rev(c("Support[t-1]",
+                      "Support[t-2]",
+                      "Delta~Liberal~democracy",
+                      "Liberal~democracy[t-1]",
+                      "Delta~Log~GDP~per~capita",
+                      "Log~GDP[t-1]",
+                      "Delta~Corruption",
+                      "Corruption[t-1]")),
+                levels = rev(c("Support[t-1]",
+                               "Support[t-2]",
+                               "Delta~Liberal~democracy",
+                               "Liberal~democracy[t-1]",
+                               "Delta~Log~GDP~per~capita",
+                               "Log~GDP[t-1]",
+                               "Delta~Corruption",
+                               "Corruption[t-1]")))
+
+plot_APSR2 <- dwplot(result_APSR2, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms2))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  # scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "",
+    subtitle = "W. Corruption"
+  ) +
+  facet_wrap(~type, scales = "free_x") +
+  theme(legend.position = "none")
+
+# Regime specified ####
+
+result_ecmReg1 <- bind_rows(
+  mutate(result_clsAPSR$`pooled-regime1`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsFullUncertainAPSR$`pooled-regime1`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoFullUncertainAPSR$`pooled-regime1`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "ECM")
+
+result_fdReg1 <- bind_rows(
+  mutate(result_clsAPSR$`fd-regime1`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsFullUncertainAPSR$`fd-regime1`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoFullUncertainAPSR$`fd-regime1`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "First Difference")
+
+result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+      "Electoral Democracy\n (Difference)",
+      "Electoral Democracy\n (t-1)",
+      "Minoritarian Democracy\n (Difference)",
+      "Minoritarian Democracy\n (t-1)",
+      "Log GDP\n per capita\n (Difference)",
+      "Log GDP\n (t-1)"),
+    time = 3),
+    rep(
+      c("Electoral Democracy\n (Difference)", 
+        "Minoritarian Democracy\n (Difference)",
+        "Log GDP\n per capita\n (Difference)"), 
+      time = 3
+    )),
+    type = factor(type, levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
+  )
+
+terms3 <- factor(rev(c("Support[t-1]",
+                      "Support[t-2]",
+                      "Delta~Electoral~democracy",
+                      "Electoral~democracy[t-1]",
+                      "Delta~Minoritarian~democracy",
+                      "Minoritarian~democracy[t-1]",
+                      "Delta~Log~GDP~per~capita",
+                      "Log~GDP[t-1]")),
+                levels = rev(c("Support[t-1]",
+                      "Support[t-2]",
+                      "Delta~Electoral~democracy",
+                      "Electoral~democracy[t-1]",
+                      "Delta~Minoritarian~democracy",
+                      "Minoritarian~democracy[t-1]",
+                      "Delta~Log~GDP~per~capita",
+                      "Log~GDP[t-1]")))
+
+plot_RegAPSR1 <- dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms3))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  # scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "",
+    subtitle = "Regime Specified"
+  ) +
+  facet_wrap(~type, scales = "free_x") + 
+  theme(legend.position = "none")
+
+result_ecmReg2 <- bind_rows(
+  mutate(result_clsAPSR$`pooled-regime2`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsFullUncertainAPSR$`pooled-regime2`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoFullUncertainAPSR$`pooled-regime2`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "ECM")
+
+result_fdReg2 <- bind_rows(
+  mutate(result_clsAPSR$`fd-regime2`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsFullUncertainAPSR$`fd-regime2`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoFullUncertainAPSR$`fd-regime2`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "First Difference")
+
+result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+      "Electoral Democracy\n (Difference)",
+      "Electoral Democracy\n (t-1)",
+      "Minoritarian Democracy\n (Difference)",
+      "Minoritarian Democracy\n (t-1)",
+      "Log GDP\n per capita\n (Difference)",
+      "Log GDP\n (t-1)",
+      "Corruption\n (Difference)",
+      "Corruption\n (t-1)"
+      ),
+    time = 3),
+    rep(
+      c("Electoral Democracy\n (Difference)", 
+        "Minoritarian Democracy\n (Difference)",
+        "Log GDP\n per capita\n (Difference)",
+        "Corruption\n (Difference)"), 
+      time = 3
+    )),
+    type = factor(type, levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
+  )
+
+terms4 <- factor(rev(c("Support[t-1]",
+                      "Support[t-2]",
+                      "Delta~Electoral~democracy",
+                      "Electoral~democracy[t-1]",
+                      "Delta~Minoritarian~democracy",
+                      "Minoritarian~democracy[t-1]",
+                      "Delta~Log~GDP",
+                      "Log~GDP[t-1]",
+                      "Delta~Corruption",
+                      "Corruption[t-1]")),
+                levels = rev(c("Support[t-1]",
+                               "Support[t-2]",
+                               "Delta~Electoral~democracy",
+                               "Electoral~democracy[t-1]",
+                               "Delta~Minoritarian~democracy",
+                               "Minoritarian~democracy[t-1]",
+                               "Delta~Log~GDP",
+                               "Log~GDP[t-1]",
+                               "Delta~Corruption",
+                               "Corruption[t-1]")))
+
+plot_RegAPSR2 <- dwplot(result_RegAPSR2, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms4))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  # scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "",
+    subtitle = "Regime Specified w. Corruption"
+  ) +
+  facet_wrap(~type, scales = "free_x") +
+  theme(legend.position = "bottom", 
+        legend.title = element_blank())
+
+legend <- get_legend(plot_RegAPSR2)
+
+plot_RegAPSR2 <- plot_RegAPSR2 + theme(legend.position = "none")
+
+grid.arrange(plot_APSR1, plot_APSR2, plot_RegAPSR1, plot_RegAPSR2, legend, ncol = 1)
 ```

### 2021-06-01 paper/dcpo_demsupport.Rmd
full result presented; need rerun the uncertains to measure everything works correctly

@@
 
-#saveRDS(result_clsAPSR, file = here::here("output", "estimates_clsMeanAPSR.RDS"))
+saveRDS(result_clsAPSR, file = here::here("output", "estimates_clsMeanAPSR.RDS"))
 ```
@@
 
-load(here("output", "estimates_clsMeanAPSR.RDS"))
-result_clsUncertainAPSR <- readRDS(here("output", "estimates_clsAPSR.RDS"))
+result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
+load(here("output", "estimates_clsAPSR.RDS"))
 result_dcpoAPSR <- readRDS(here("output", "estimates_dcpoAPSR.RDS"))
@@
 
-```{r visualizeFullUncertainAJPS, fig.cap= "The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=10}
+```{r visualizeFullUncertainAJPS, fig.cap= "The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=7}
 
@@
 
+\pagebreak
+
 # Replication with Alternative Methods Accounting for Uncertainty

### 2021-06-01 paper/dcpo_demsupport.Rmd
fixed the issue of dcpomean

@@
 load(here("data", "dcpo_input.rda"))
-# load(here::here("data", "dcpo_theta.rda"))
-# load(here::here("data", "dcpo_sigma.rda"))
-# load(here("data", "dcpo_ajps_rubin.rda"))
+load(here("data", "dcpo_theta.rda"))
+load(here("data", "dcpo_sigma.rda"))
+load(here("data", "dcpo_ajps_rubin.rda"))
 
@@
 # the readRDS produced "unknown format" error, very weild
-# saveRDS(df_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))
-# df_dcpoMean <- readRDS(here::here("output", "estimates_dcpoMean.RDS"))
 
@@
                                          Region_UN = col_character())) %>% 
-  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
-         country = countrycode::countrycode(country0, "country.name", "country.name"),
+  mutate(
+         country = countrycode::countrycode(country, "country.name", "country.name"),
          regime = Vdem_regime > 1) %>% 
-  filter(year >= firstyear) # using trimmed data as Claassen
+  filter(year >= first_year) # using trimmed data as Claassen
 
@@
 )
+
+#There's a problem to run this part---------------------
 
@@
 ```{r dcpoUncertaintyAJPS}
+load(here("data", "dcpo_ajps_rubin.rda"))
+
 df_dcpo <- dcpo_ajps_rubin %>% map(~ .)

### 2021-06-02 paper/dcpo_demsupport.Rmd
analysis all going through

@@
 
-```{r dcpoPointAJPS}
+```{r dcpoMean}
 ls_country <- levels(dcpo_input$data$kk)
@@
 
-# the readRDS produced "unknown format" error, very weild
-
-df_controls <- read_csv(here::here("data", "control_variables_ajps.csv"),
-                        col_types = cols(.default = col_double(),
-                                         country = col_character(),
-                                         country_name = col_character(),
-                                         ISO = col_character(),
-                                         Region_UN = col_character())) %>% 
-  mutate(
-         country = countrycode::countrycode(country, "country.name", "country.name"),
+saveRDS(df_dcpoMean, file = here("data", "df_dcpoMean.RDS"))
+```
+
+```{r dcpoPointAJPS}
+df_controls <- readRDS(here("data", "control_variables_ajps.rds")) %>% 
+  mutate(country = countrycode::countrycode(country, "country.name", "country.name"),
          regime = Vdem_regime > 1) %>% 
@@
 ```{r dcpoUncertaintyAJPS}
-load(here("data", "dcpo_ajps_rubin.rda"))
-
-df_dcpo <- dcpo_ajps_rubin %>% map(~ .)
+df_dcpo <- dcpo_ajps_rubin %>% map2(1:length(dcpo_ajps_rubin), ~ {
+  .x[[.y]] %>%
+    mutate(theta_dem = theta * regime,
+           theta_aut = theta * (1 - regime)) %>%
+    plm::pdata.frame(index = c("country", "year"))
+}) # The code is to fit the embedded format of dcpo_ajps_rubin
 
@@
 result_dcpoUncertain <- map(ls_mod, function(aMod){ # reading a model
-  result <- map(df_dcpo, function(aData){ # applying to the 1000 datasets
-    eval(parse(text = aMod))
-  })
+  mod_eval <- function(aData) eval(parse(text = aMod))
+
+  result <- map(df_dcpo, mod_eval)
 
@@
 result_clsUncertain <- readRDS(here::here("output", "estimates_clsAJPS.RDS"))
-load(here::here("output", "estimates_dcpoAJPS.RDS"))
+result_dcpoUncertain <- readRDS(here::here("output", "estimates_dcpoAJPS.RDS"))
 
@@
 ```{r dcpoPointAPSR}
-df_controls <- read_csv(here::here("data", "control_variables_apsr.csv"),
-                        col_types = cols(.default = col_double(),
-                                         country = col_character(),
-                                         country_name = col_character(),
-                                         ISO = col_character(),
-                                         Region_UN = col_character())) %>% 
-  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
-         country = countrycode::countrycode(country0, "country.name", "country.name")) %>% 
-  filter(year >= firstyear)
-
-load(here::here("output", "estimates_dcpoMean.RDS"))
+
+df_dcpoMean <- readRDS(here("data", "df_dcpoMean.RDS"))
+
+df_controls <- readRDS(here("data", "control_variables_apsr.rds")) %>% 
+  mutate(country = countrycode::countrycode(country, "country.name", "country.name")) %>% 
+  filter(year >= first_year)
 
@@
 
+```{r data-dcpoUncertainAPSR}
+ls_country <- levels(dcpo_input$data$kk)
+first_year <- min(dcpo_input$data$year)
+
+df_dcpoUncertainAPSR <- purrr::map(1:1000, function(anEntry) {
+  dcpo_theta$theta[anEntry,,] %>%
+    reformat_dcpo_output("theta") %>%
+    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
+              by = c("year", "country")) %>%
+    left_join(df_controls, by = c("country", "year")) %>%
+    plm::pdata.frame(index = c("country", "year"))
+})
+
+saveRDS(df_dcpoUncertainAPSR, here("data", "df_dcpoUncertainAPSR.rds"))
+```
+
 ```{r dcpoUncertaintyAPSR}
-# ls_country <- levels(dcpo_input$data$kk)
-# first_year <- min(dcpo_input$data$year)
-# 
-# df_dcpoUncertainAPSR <- purrr::map(1:1000, function(anEntry) {
-#   dcpo_theta$theta[anEntry,,] %>% 
-#     reformat_dcpo_output("theta") %>% 
-#     left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
-#               by = c("year", "country")) %>%
-#     left_join(df_controls, by = c("country", "year")) %>% 
-#     plm::pdata.frame(index = c("country", "year"))
-# })
-
 ## The same as in the previous chunk
@@
 
-###Duble check the dataset--------------
 ls_mod <- c(
-  glue("plm({ls_eqECM}, model = 'pooling', data = df_dcpoUncertainAPSR)"),
-  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = df_dcpoUncertainAPSR)")
+  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
+  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
 )
@@
 result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
-load(here("output", "estimates_clsAPSR.RDS"))
+result_clsUncertainAPSR <- readRDS(here("output", "estimates_clsAPSR.RDS"))
 result_dcpoAPSR <- readRDS(here("output", "estimates_dcpoAPSR.RDS"))

### 2021-06-02 R/moc_summary.R
moc summary for ajps and apsr seperately

@@ -1,4 +1,4 @@
-<<<<<<< HEAD
+
 ###Moc summary
 
 pEmp <- function (x) {
@@ -14,6 +14,7 @@ pNorm <- function (x) {
 }
 
 
+##For AJPS model summary. 
 MOCsumm <- function (moc, digits=3,
                      ff=funs(est = mean, se = sd, z = mean(.)/sd(.),
                              pnorm = pNorm(.),
@@ -22,56 +23,32 @@ MOCsumm <- function (moc, digits=3,
     var_names <- names(moc) %>% 
         str_c(collapse = "|")
     
-    summarise_at(moc, .vars=vars(matches(var_names)), .funs=ff) %>%
+    summarise_all(moc, .funs=ff) %>%
         mutate_all(funs(round(., digits=digits))) %>%
-        reshape2::melt(measure.vars=names(.))
-}
-
-MOCmean <- function (mod.ls) {
-    plyr::llply(mod.ls, function (x) apply(x, 2, mean))
-}
-
-MOCsd <- function (mod.ls) {
-    plyr::llply(mod.ls, function (x) apply(x, 2, sd))
-}
-
-
-MOCsumm(model.ls[[]])
-=======
-###Moc summary
-
-pEmp <- function (x) {
-    p_pos <- mean(x < 0)
-    p_neg <- mean(x > 0)
-    p2side <- 2 * min(p_pos, p_neg)
-    p2side
-}
-
-pNorm <- function (x) {
-    z <- abs(mean(x)/sd(x))
-    p2side <- 2*(1 - pnorm(z))
-    p2side
+        reshape2::melt(measure.vars=names(.)) %>%
+        separate(variable, into = c("term","temp"),sep ="_(?=est|se|z|pnorm|pemp)") %>%
+        pivot_wider(names_from = "temp",values_from = "value") %>%
+        transmute(term = term,
+                  estimate = est,
+                  std.error = se) %>%
+        filter(!term =="rsq"&!term =="adjrsq" )
 }
 
 
-MOCsumm <- function (moc, regex=var_names, digits=3,
-                     ff=funs(est = mean, se = sd, z = mean(.)/sd(.),
-                             pnorm = pNorm(.),
-                             pemp = pEmp(.))) {
-    summarise_at(moc, .vars=var_names, .funs=ff) %>%
+##For APSR model Summaries
+MOCsumm2 <- function (moc, digits=3,
+                      ff=funs(est = mean, se = sd)) {
[…]

### 2021-06-02 paper/dcpo_demsupport.Rmd
add moc and result in appendix

@@
 source(here("R", "moc_function.R")) 
+source(here("R", "moc_summary.R"))
 
@@
 # Replication with Alternative Methods Accounting for Uncertainty
+```{r  MocclaassenUncertaintyAJPS}
+load("data/cls_ajps.rda")
+df_cls <- purrr::map(1:900, function(anEntry) {
+  cls_ajps[[anEntry]] %>% 
+    plm::pdata.frame(index = c("country", "year"))
+})
+
+ls_iv <- c("plm::lag(SupDem_trim, 1)",                         ##sumpdem_trim, our model did not use trim
+           "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) ")
+ls_method <- c("plm", "pgmm")
+ls_eq <- glue("Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + {ls_iv} + 
+              plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + 
+              plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)")
+
+ls_mod <- c(
+  glue("plm({ls_eq}, model = 'pooling', data = aData)"),
+  glue(
+    "pgmm({ls_eq} | plm::lag(Libdem_VD, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
+  )
+)
+
+result_clsUncertain  <- map(ls_mod[1:2], function(aMod){
+  result <- methodComposition1(df_cls,aMod)
+})
+
+names(result_clsUncertain) <- c("pooled", "pooled-regime")
+
+result_clsUncertain_gmm  <- map(ls_mod[3:4], function(aMod){
+  result <- methodComposition2(df_cls,aMod)
+})
+names(result_clsUncertain_gmm) <- c("gmm", "gmm-regime")
+
+result_clsUncertain_whole <- append(result_clsUncertain, result_clsUncertain_gmm)
+
+saveRDS(result_clsUncertain_whole, file ="output/clsAJPS_uncertainty.RDS")
+
+```
+
+```{r MocdcpoUncertaintyAJPS}
+load("data/dcpo_ajps.rda")
+
+df_dcpo <- purrr::map(1:900, function(anEntry) {
+  dcpo_ajps[[anEntry]] %>% 
+    mutate(theta_dem = ifelse(is.na(theta_trim),NA,theta_dem),
+           theta_aut = ifelse(is.na(theta_trim),NA,theta_aut)) %>% 
+    plm::pdata.frame(index = c("country", "year"))
+})
+
+ls_iv <- c("plm::lag(theta_trim, 1)", 
+           "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1)") 
+ls_method <- c("plm", "pgmm")
+ls_eq <- glue("Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + {ls_iv} + plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) + plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)")
+ls_mod <- c(
+  glue("plm({ls_eq}, model = 'pooling', data = aData)"),
+  glue(
+    "pgmm({ls_eq} | plm::lag(Vdem_libdem, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
+  )
+)
+
+result_dcpoUncertain  <- map(ls_mod[1:2], function(aMod){
+  result <- methodComposition1(df_dcpo,aMod)
+})
+
+names(result_dcpoUncertain) <- c("pooled", "pooled-regime")
+
+result_dcpoUncertain_gmm  <- map(ls_mod[3:4], function(aMod){
+  result <- methodComposition2(df_dcpo,aMod)
+})
+
+names(result_dcpoUncertain_gmm) <- c("gmm", "gmm-regime")
+
+result_dcpoUncertain_whole <- append(result_dcpoUncertain, result_dcpoUncertain_gmm)
+
+saveRDS(result_dcpoUncertain_whole, file ="output/dcpoAJPS_uncertainty.RDS")
+
+```
+
+```{r visualizedMocUncertainAJPS, fig.cap= "The Effect of Public Support on Democracy ", eval = TRUE, fig.width=7, fig.height=10}
+
+result_clsAJPS <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
+result_clsUncertain_whole <- readRDS(here("output", "clsAJPS_uncertainty.RDS"))
+result_dcpoUncertain_whole <- readRDS(here("output", "dcpoAJPS_uncertainty.RDS"))
+
+result_pooled <- bind_rows(
+  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Claassen 2020a"),
+  mutate(MOCsumm(result_clsUncertain_whole[["pooled"]]), model = "Claassen w/uncertainty"),
+  mutate(MOCsumm(result_dcpoUncertain_whole[[1]]), model = "DCPO")
+) %>% 
+  mutate(type = "Pooled")
+
+result_gmm <- bind_rows(
+  mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Claassen 2020a"),
+  mutate(MOCsumm(result_clsUncertain_whole[["gmm"]]), model = "Claassen w/uncertainty"),
+  mutate(MOCsumm(result_dcpoUncertain_whole[["gmm"]]), model = "DCPO")
+) %>% 
+  mutate(type = "GMM")
+
+result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democracy\n (t-1)",
+        "Democracy\n (t-2)",
+        "Support\n (t-1)",
+        "Log GDP\n per capita\n (t-1)",
+        "GDP per\n capita growth\n (t-1)",
+        "Regional\n democracy\n (t-1)",
+        "Percent\n Muslim\n (t-1)",
+        "Resource\n dependence\n (t-1)"),
+      time = 6), 
+    type = factor(type, levels = c("Pooled", "GMM")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/uncertainty", "DCPO")))
+
+terms <- factor(rev(c("Democracy[t-1]",
+                      "Democracy[t-2]",
+                      "Support[t-1]",
+                      "Log~GDP~per~capita[t-1]",
+                      "GDP~per~capita~growth[t-1]",
+                      "Regional~democracy[t-1]",
+                      "Percent~Muslim[t-1]",
+                      "Resource~dependence[t-1]")), levels =
+                  rev(c("Democracy[t-1]",
+                        "Democracy[t-2]",
+                        "Support[t-1]",
+                        "Log~GDP~per~capita[t-1]",
+                        "GDP~per~capita~growth[t-1]",
+                        "Regional~democracy[t-1]",
+                        "Percent~Muslim[t-1]",
+                        "Resource~dependence[t-1]")))
+
+plot_AJPS1 <- dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms))) +
+  scale_color_grey(start = 0.4, end = 0.8) +
+  labs(
+    title = "DV: V-Dem Liberal Democracy Index",
+    subtitle = "Regime Compacted"
+  ) +
+  facet_wrap(~type, scales = "free_x") + 
+  theme(legend.position = "none")
+
+###########Regime
+result_regime <- bind_rows(
+  mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Claassen 2020a"),
+  mutate(MOCsumm(result_clsUncertain_whole[["pooled-regime"]]), model = "Claassen w/uncertainty"),
+  mutate(MOCsumm(result_dcpoUncertain_whole[[2]]), model = "DCPO")
+) %>% 
+  mutate(type = "Pooled")
+
+result_regimeGmm <- bind_rows(
+  mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Claassen 2020a"),
+  mutate(MOCsumm(result_clsUncertain_whole[["gmm-regime"]]), model = "Claassen w/uncertainty"),
+    mutate(MOCsumm(result_dcpoUncertain_whole[["gmm-regime"]]), model = "DCPO")
+)%>% 
+  mutate(type = "GMM")
+
+result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democracy\n (t-1)",
+        "Democracy\n (t-2)",
+        "Support\n demo only\n (t-1)",
+        "Support\n auto only\n (t-1)",
+        "Log GDP\n per capita\n (t-1)",
+        "GDP per\n capita growth\n (t-1)",
+        "Regional\n democracy\n (t-1)",
+        "Percent\n Muslim\n (t-1)",
+        "Resource\n dependence\n (t-1)"),
+      time = 6), 
+    type = factor(type, levels = c("Pooled", "GMM")),
+    model = factor(model, levels = c("Claassen 2020a","Claassen w/uncertainty", "DCPO")))
+terms2 <- factor(rev(c("Democracy[t-1]",
+                       "Democracy[t-2]",
+                       "Support[t-1] (democracies~only)",
+                       "Support[t-1] (autocracies~only)",
+                       "Log~GDP~per~capita[t-1]",
+                       "GDP~per~capita~growth[t-1]",
+                       "Regional~democracy[t-1]",
+                       "Percent~Muslim[t-1]",
+                       "Resource~dependence[t-1]")), levels =
+                   rev(c("Democracy[t-1]",
+                         "Democracy[t-2]",
+                         "Support[t-1] (democracies~only)",
+                         "Support[t-1] (autocracies~only)",
+                         "Log~GDP~per~capita[t-1]",
+                         "GDP~per~capita~growth[t-1]",
+                         "Regional~democracy[t-1]",
+                         "Percent~Muslim[t-1]",
+                         "Resource~dependence[t-1]")))
+plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms2))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  labs(
+    title = "",
+    subtitle = "Regime Specific"
+  ) +
+  facet_wrap(~type, scales = "free_x") +
+  theme(legend.position = "bottom", 
+        legend.title = element_blank())
+legend <- get_legend(plot_AJPS2)
+plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
+grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
+
+```
+
+```{r claassenMocUncertaintyAPSR}
+load(here("data", "cls_apsr.rda"))
+
+df_clsAPSR <- purrr::map(1:900, function(anEntry) {
+  cls_apsr[[anEntry]] %>% 
+    plm::pdata.frame(index = c("country", "year"))
+}
+)
+
+ls_ivECM <- c("diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)", 
+              "diff(Polyarchy_z, lag = 1) + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)")
+ls_ctrlECM <- c("", " + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1)")
+
+ls_eqECM <- glue("diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)") %>% 
+  outer(ls_ctrlECM, paste0) %>% 
+  as.vector() ##Change theta to SupDem_trim
+
+ls_ivFD <- c("Libdem_z",
+             "Polyarchy_z + Liberal_z")
+ls_ctrlFD <- c("", " + Corrup_TI_z")
+ls_eqFD <- glue("SupDem_trim ~ {ls_ivFD} + lnGDP_imp") %>% 
+  outer(ls_ctrlFD, paste0) %>% 
+  as.vector()
+ls_mod <- c(
+  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
+  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
+)
+
+result_clsUncertain  <- map(ls_mod, function(aMod){
+  result <- methodComposition3(df_clsAPSR,aMod)
+})
+
+names(result_clsUncertain) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
+                                "fd1", "fd-regime1", "fd2", "fd-regime2")
+
+saveRDS(result_clsUncertain, file = "ouput/clsAPSR_uncertainty.RDS")
+
+```
+
+```{r  dcpoMocUncertaintyAPSR}
+load("dcpo_apsr.rda")
+df_dcpoUncertainAPSR <- purrr::map(1:900, function(anEntry) {
+  dcpo_apsr[[anEntry]] %>% 
+    plm::pdata.frame(index = c("country", "year"))
+})
+
+ls_ivECM <- c("diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1)", 
+              "diff(Vdem_polyarchy_z, lag = 1) + plm::lag(Vdem_polyarchy_z, 1) + diff(Vdem_liberal_z, lag = 1) + plm::lag(Vdem_liberal_z, 1)")
+ls_ctrlECM <- c("", " + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1)")
+ls_eqECM <- glue("diff(theta_trim, lag = 1) ~ plm::lag(theta_trim, 1:2) + {ls_ivECM} + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1)") %>% 
+  outer(ls_ctrlECM, paste0) %>% 
+  as.vector()
+
+ls_ivFD <- c("Vdem_libdem_z",
+             "Vdem_polyarchy_z + Vdem_liberal_z")
+ls_ctrlFD <- c("", " + corruption_z")
+ls_eqFD <- glue("theta_trim ~ {ls_ivFD} + lg_imp_mdpgdp") %>% 
+  outer(ls_ctrlFD, paste0) %>% 
+  as.vector()
+
+ls_mod <- c(
+  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
+  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
+)
+
+result_dcpoUncertain  <- map(ls_mod, function(aMod){
+  result <- methodComposition3(df_dcpoUncertainAPSR,aMod)
+})
+
+names(result_dcpoUncertain) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
+                                "fd1", "fd-regime1", "fd2", "fd-regime2")
+
+saveRDS(result_dcpoUncertain, file ="output/dcpoAPSR_uncertainty.RDS")
+
+```
+
+```{r visualizedMocUncertainAPSR, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}
+
+result_clsUncertain <- readRDS(here("output","clsAPSR_uncertainty.RDS"))
+result_dcpoUncertain <- readRDS(here("output","dcpoAPSR_uncertainty.RDS"))
+result_clsAPSR <- readRDS(here("output","estimates_clsMeanAPSR.RDS"))
+
+result_ecm1 <- bind_rows(
+  mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], model = "Claassen 2020b"),
+  mutate(MOCsumm2(result_clsUncertain[["pooled1"]]), model = "Claassen w/uncertainty"),
+  mutate(MOCsumm2(result_dcpoUncertain[["pooled1"]]), model = "DCPO")
+) %>% 
+  mutate(type = "ECM")
+
+result_fd1 <- bind_rows(
+  mutate(result_clsAPSR[["fd1"]][[1]][,1:3], model = "Claassen 2020b"),
+  mutate(MOCsumm2(result_clsUncertain[["fd1"]]), model = "Claassen w/uncertainty"),
+  mutate(MOCsumm2(result_dcpoUncertain[["fd1"]]), model = "DCPO")
+) %>% 
+  mutate(type = "First Difference")
+
+result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+        "Liberal Democracy\n (Difference)",
+        "Liberal Democracy\n (t-1)",
+        "Log GDP\n per capita\n (Difference)",
+        "Log GDP\n (t-1)"),
+      time = 3),
+      rep(
+        c("Liberal Democracy\n (Difference)", 
+          "Log GDP\n per capita\n (Difference)"), 
+        time = 3
+      )),
+    type = factor(type,  levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Claassen 2020b","Claassen w/uncertainty", "DCPO"))
+  )
+
+terms1 <- factor(rev(c("Support[t-1]",
+                       "Support[t-2]",
+                       "Delta~Liberal~democracy",
+                       "Liberal~democracy[t-1]",
+                       "Delta~Log~GDP~per~capita",
+                       "Log~GDP[t-1]")),
+                 levels = rev(c("Support[t-1]",
+                                "Support[t-2]",
+                                "Delta~Liberal~democracy",
+                                "Liberal~democracy[t-1]",
+                                "Delta~Log~GDP~per~capita",
+                                "Log~GDP[t-1]")))
+plot_APSR1 <- dwplot(result_APSR1, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms1))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  # scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "DV: Public Support for Democracy",
+    subtitle = "Regime Compacted"
+  ) +
+  facet_wrap(~type, drop=T,scales = "free_x") +
+  theme(legend.position = "none")
+
+############################ Regime specified####
+result_ecmReg1 <- bind_rows(
+  mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], model = "Claassen 2020b"),
+  mutate(MOCsumm2(result_clsUncertain[["pooled-regime1"]]), model = "Claassen w/uncertainty"),
+  mutate(MOCsumm2(result_dcpoUncertain[["pooled-regime1"]]), model = "DCPO")
+) %>% 
+  mutate(type = "ECM")
+
+result_fdReg1 <- bind_rows(
+  mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], model = "Claassen 2020b"),
+  mutate(MOCsumm2(result_clsUncertain[["fd-regime1"]]), model = "Claassen w/uncertainty"),
+  mutate(MOCsumm2(result_dcpoUncertain[["fd-regime1"]]), model = "DCPO")
+) %>% 
+  mutate(type = "First Difference")
+
+result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+        "Electoral Democracy\n (Difference)",
+        "Electoral Democracy\n (t-1)",
+        "Minoritarian Democracy\n (Difference)",
+        "Minoritarian Democracy\n (t-1)",
+        "Log GDP\n per capita\n (Difference)",
+        "Log GDP\n (t-1)"),
+      time = 3),
+      rep(
+        c("Electoral Democracy\n (Difference)", 
+          "Minoritarian Democracy\n (Difference)",
+          "Log GDP\n per capita\n (Difference)"), 
+        time = 3
+      )),
+    type = factor(type,  levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Claassen 2020b","Claassen w/uncertainty", "DCPO"))
+  )
+terms3 <- factor(rev(c("Support[t-1]",
+                       "Support[t-2]",
+                       "Delta~Electoral~democracy",
+                       "Electoral~democracy[t-1]",
+                       "Delta~Minoritarian~democracy",
+                       "Minoritarian~democracy[t-1]",
+                       "Delta~Log~GDP~per~capita",
+                       "Log~GDP[t-1]")),
+                 levels = rev(c("Support[t-1]",
+                                "Support[t-2]",
+                                "Delta~Electoral~democracy",
+                                "Electoral~democracy[t-1]",
+                                "Delta~Minoritarian~democracy",
+                                "Minoritarian~democracy[t-1]",
+                                "Delta~Log~GDP~per~capita",
+                                "Log~GDP[t-1]")))
+plot_RegAPSR1 <- dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms3))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  # scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "",
+    subtitle = "Regime Specified"
+  ) +
+  facet_wrap(~type, scales = "free_x") + 
+  theme(legend.position = "none")
+
+#########Corruption
+
+result_ecm2 <- bind_rows(
+  mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], model = "Claassen 2020b"),
+  mutate(MOCsumm2(result_clsUncertain[["pooled2"]]), model = "Claassen w/uncertainty"),
+  mutate(MOCsumm2(result_dcpoUncertain[["pooled2"]]), model = "DCPO")
+) %>% 
+  mutate(type = "ECM")
+
+result_fd2 <- bind_rows(
+  mutate(result_clsAPSR[["fd2"]][[1]][,1:3], model = "Claassen 2020b"),
+  mutate(MOCsumm2(result_clsUncertain[["fd2"]]), model = "Claassen w/uncertainty"),
+  mutate(MOCsumm2(result_dcpoUncertain[["fd2"]]), model = "DCPO")
+) %>% 
+  mutate(type = "First Difference")
+
+result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+        "Liberal Democracy\n (Difference)",
+        "Liberal Democracy\n (t-1)",
+        "Log GDP\n per capita\n (Difference)",
+        "Log GDP\n (t-1)",
+        "Corruption\n (Difference)",
+        "Corruption\n (t-1)"
+      ),
+      time = 3),
+      rep(
+        c("Liberal Democracy\n (Difference)", 
+          "Log GDP\n per capita\n (Difference)",
+          "Corruption\n (Difference)"), 
+        time = 3
+      )),
+    type = factor(type,  levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Claassen 2020b", "Claassen w/uncertainty","DCPO"))
+  )
+terms2 <- factor(rev(c("Support[t-1]",
+                       "Support[t-2]",
+                       "Delta~Liberal~democracy",
+                       "Liberal~democracy[t-1]",
+                       "Delta~Log~GDP~per~capita",
+                       "Log~GDP[t-1]",
+                       "Delta~Corruption",
+                       "Corruption[t-1]")),
+                 levels = rev(c("Support[t-1]",
+                                "Support[t-2]",
+                                "Delta~Liberal~democracy",
+                                "Liberal~democracy[t-1]",
+                                "Delta~Log~GDP~per~capita",
+                                "Log~GDP[t-1]",
+                                "Delta~Corruption",
+                                "Corruption[t-1]")))
+plot_APSR2 <- dwplot(result_APSR2, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms2))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  # scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "",
+    subtitle = "W. Corruption"
+  ) +
+  facet_wrap(~type, scales = "free_x") +
+  theme(legend.position = "none")
+
+#########Regime + Corruption
+
+result_ecmReg2 <- bind_rows(
+  mutate(result_clsAPSR[["pooled-regime2"]][[1]][,1:3], model = "Claassen 2020b"),
+  mutate(MOCsumm2(result_clsUncertain[["pooled-regime2"]]), model = "Claassen w/uncertainty"),
+  mutate(MOCsumm2(result_dcpoUncertain[["pooled-regime2"]]), model = "DCPO")) %>% 
+  mutate(type = "ECM")
+
+result_fdReg2 <- bind_rows(
+  mutate(result_clsAPSR[["fd-regime2"]][[1]][,1:3], model = "Claassen 2020b"),
+  mutate(MOCsumm2(result_clsUncertain[["fd-regime2"]]), model = "Claassen w/uncertainty"),
+  mutate(MOCsumm2(result_dcpoUncertain[["fd-regime2"]]), model = "DCPO")) %>% 
+  mutate(type = "First Difference")
+
+result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+        "Electoral Democracy\n (Difference)",
+        "Electoral Democracy\n (t-1)",
+        "Minoritarian Democracy\n (Difference)",
+        "Minoritarian Democracy\n (t-1)",
+        "Log GDP\n per capita\n (Difference)",
+        "Log GDP\n (t-1)",
+        "Corruption\n (Difference)",
+        "Corruption\n (t-1)"
+      ),
+      time = 3),
+      rep(
+        c("Electoral Democracy\n (Difference)", 
+          "Minoritarian Democracy\n (Difference)",
+          "Log GDP\n per capita\n (Difference)",
+          "Corruption\n (Difference)"), 
+        time = 3
+      )),
+    type = factor(type,  levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Claassen 2020b", "Claassen w/uncertainty","DCPO"))
+  )
+terms4 <- factor(rev(c("Support[t-1]",
+                       "Support[t-2]",
+                       "Delta~Electoral~democracy",
+                       "Electoral~democracy[t-1]",
+                       "Delta~Minoritarian~democracy",
+                       "Minoritarian~democracy[t-1]",
+                       "Delta~Log~GDP",
+                       "Log~GDP[t-1]",
+                       "Delta~Corruption",
+                       "Corruption[t-1]")),
+                 levels = rev(c("Support[t-1]",
+                                "Support[t-2]",
+                                "Delta~Electoral~democracy",
+                                "Electoral~democracy[t-1]",
+                                "Delta~Minoritarian~democracy",
+                                "Minoritarian~democracy[t-1]",
+                                "Delta~Log~GDP",
+                                "Log~GDP[t-1]",
+                                "Delta~Corruption",
+                                "Corruption[t-1]")))
+plot_RegAPSR2 <- dwplot(result_RegAPSR2, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms4))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  # scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "",
+    subtitle = "Regime Specified w. Corruption"
+  ) +
+  facet_wrap(~type, scales = "free_x") +
+  theme(legend.position = "bottom", 
+        legend.title = element_blank())
+
+legend <- get_legend(plot_RegAPSR2)
+
+plot_RegAPSR2 <- plot_RegAPSR2 + theme(legend.position = "none")
+
+grid.arrange(plot_APSR1, plot_APSR2, plot_RegAPSR1, plot_RegAPSR2, legend, ncol = 1)
+
+```

### 2021-06-02 paper/dcpo_demsupport.Rmd
change path in moc

@@
 
-saveRDS(result_clsUncertain_whole, file ="output/clsAJPS_uncertainty.RDS")
+saveRDS(result_clsUncertain_whole, file =here("output","clsAJPS_uncertainty.RDS"))
 
@@
 ```{r MocdcpoUncertaintyAJPS}
-load("data/dcpo_ajps.rda")
+load(here("data","dcpo_ajps.rda"))
 
@@
 
-saveRDS(result_dcpoUncertain_whole, file ="output/dcpoAJPS_uncertainty.RDS")
+saveRDS(result_dcpoUncertain_whole, file =here("output","dcpoAJPS_uncertainty.RDS"))
 
@@
   mutate(MOCsumm(result_clsUncertain_whole[["pooled"]]), model = "Claassen w/uncertainty"),
-  mutate(MOCsumm(result_dcpoUncertain_whole[[1]]), model = "DCPO")
+  mutate(MOCsumm(result_dcpoUncertain_whole[["pooled"]]), model = "DCPO")
 ) %>% 
@@
   mutate(MOCsumm(result_clsUncertain_whole[["pooled-regime"]]), model = "Claassen w/uncertainty"),
-  mutate(MOCsumm(result_dcpoUncertain_whole[[2]]), model = "DCPO")
+  mutate(MOCsumm(result_dcpoUncertain_whole[["pooled-regime"]]), model = "DCPO")
 ) %>% 
@@
 
-saveRDS(result_clsUncertain, file = "ouput/clsAPSR_uncertainty.RDS")
+saveRDS(result_clsUncertain, file = here("ouput","clsAPSR_uncertainty.RDS"))
 
@@
 ```{r  dcpoMocUncertaintyAPSR}
-load("dcpo_apsr.rda")
+load(here("data","dcpo_apsr.rda"))
 df_dcpoUncertainAPSR <- purrr::map(1:900, function(anEntry) {
@@
 
-saveRDS(result_dcpoUncertain, file ="output/dcpoAPSR_uncertainty.RDS")
+saveRDS(result_dcpoUncertain, file =here("output","dcpoAPSR_uncertainty.RDS"))
 

### 2021-06-02 paper/dcpo_demsupport.Rmd

--- 2021-06-02 paper/dcpo_demsupport.Rmd
@@
       - \usepackage{fullpage}
-      - \usepackage{pdflscape} #\usepackage{lscape} better for printing, page displayed vertically, content in landscape mode, \usepackage{pdflscape} better for screen, page displayed horizontally, content in landscape mode
-      - \newcommand{\blandscape}{\begin{landscape}}
-      - \newcommand{\elandscape}{\end{landscape}}
+      - \usepackage{lscape} #better for printing, page displayed vertically, content in landscape mode, \usepackage{pdflscape} better for screen, page displayed horizontally, content in landscape mode
 ---
@@
 
-source(here("R", "tidy_pgmm.r"))
-source(here("R", "moc_function.R"))
+source(here::here("R", "tidy_pgmm.r"))
+source(here::here("R", "moc_function.R"))
 
@@
   DCPOtools::with_min_yrs(2)
-load(here("data", "claassen_m5_theta.rda"))
-load(here("data", "dem_mood_apsr.RData"))
-load(here("data", "dcpo_input.rda"))
-load(here("data", "dcpo_theta.rda"))
-load(here("data", "dcpo_sigma.rda"))
-load(here("data", "dcpo_ajps_rubin.rda"))
+load(here::here("data", "claassen_m5_theta.rda"))
+load(here::here("data", "dem_mood_apsr.RData"))
+load(here::here("data", "dcpo_input.rda"))
+# load(here::here("data", "dcpo_theta.rda"))
+# load(here::here("data", "dcpo_sigma.rda"))
+load("../data/dcpo_ajps_rubin.rda")
 
@@
 
-```{r dcpoMean}
+```{r dcpoPointAJPS}
 ls_country <- levels(dcpo_input$data$kk)
@@
 
-saveRDS(df_dcpoMean, file = here("data", "df_dcpoMean.RDS"))
-```
-
-```{r dcpoPointAJPS}
-df_controls <- readRDS(here("data", "control_variables_ajps.rds")) %>% 
-  mutate(country = countrycode::countrycode(country, "country.name", "country.name"),
+# the readRDS produced "unknown format" error, very weild
+# saveRDS(df_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))
+# df_dcpoMean <- readRDS(here::here("output", "estimates_dcpoMean.RDS"))
+
+df_controls <- read_csv(here::here("data", "control_variables_ajps.csv"),
+                        col_types = cols(.default = col_double(),
+                                         country = col_character(),
+                                         country_name = col_character(),
+                                         ISO = col_character(),
+                                         Region_UN = col_character())) %>% 
+  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
+         country = countrycode::countrycode(country0, "country.name", "country.name"),
          regime = Vdem_regime > 1) %>% 
-  filter(year >= first_year) # using trimmed data as Claassen
+  filter(year >= firstyear) # using trimmed data as Claassen
 
@@
 )
-
-#There's a problem to run this part---------------------
 
@@
 ```{r dcpoUncertaintyAJPS}
-df_dcpo <- dcpo_ajps_rubin %>% map2(1:length(dcpo_ajps_rubin), ~ {
-  .x[[.y]] %>%
-    mutate(theta_dem = theta * regime,
-           theta_aut = theta * (1 - regime)) %>%
-    plm::pdata.frame(index = c("country", "year"))
-}) # The code is to fit the embedded format of dcpo_ajps_rubin
+df_dcpo <- dcpo_ajps_rubin %>% map(~ .)
 
@@
 result_dcpoUncertain <- map(ls_mod, function(aMod){ # reading a model
-  mod_eval <- function(aData) eval(parse(text = aMod))
-
-  result <- map(df_dcpo, mod_eval)
+  result <- map(df_dcpo, function(aData){ # applying to the 1000 datasets
+    eval(parse(text = aMod))
+  })
 
@@
 
-```{r visualizeAJPS, fig.cap= "The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=10}
+```{r visualizeAJPS, fig.cap= "\\label{fig:visualizeAJPS}The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=10}
 
@@
 result_clsUncertain <- readRDS(here::here("output", "estimates_clsAJPS.RDS"))
-result_dcpoUncertain <- readRDS(here::here("output", "estimates_dcpoAJPS.RDS"))
+load(here::here("output", "estimates_dcpoAJPS.RDS"))
 
@@
 
-saveRDS(result_clsAPSR, file = here::here("output", "estimates_clsMeanAPSR.RDS"))
+#saveRDS(result_clsAPSR, file = here::here("output", "estimates_clsMeanAPSR.RDS"))
 ```
@@
 ```{r dcpoPointAPSR}
-
-df_dcpoMean <- readRDS(here("data", "df_dcpoMean.RDS"))
-
-df_controls <- readRDS(here("data", "control_variables_apsr.rds")) %>% 
-  mutate(country = countrycode::countrycode(country, "country.name", "country.name")) %>% 
-  filter(year >= first_year)
+df_controls <- read_csv(here::here("data", "control_variables_apsr.csv"),
+                        col_types = cols(.default = col_double(),
+                                         country = col_character(),
+                                         country_name = col_character(),
+                                         ISO = col_character(),
+                                         Region_UN = col_character())) %>% 
+  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
+         country = countrycode::countrycode(country0, "country.name", "country.name")) %>% 
+  filter(year >= firstyear)
+
+load(here::here("output", "estimates_dcpoMean.RDS"))
 
@@
 
-```{r data-dcpoUncertainAPSR}
-ls_country <- levels(dcpo_input$data$kk)
-first_year <- min(dcpo_input$data$year)
-
-df_dcpoUncertainAPSR <- purrr::map(1:1000, function(anEntry) {
-  dcpo_theta$theta[anEntry,,] %>%
-    reformat_dcpo_output("theta") %>%
-    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
-              by = c("year", "country")) %>%
-    left_join(df_controls, by = c("country", "year")) %>%
-    plm::pdata.frame(index = c("country", "year"))
-})
-
-saveRDS(df_dcpoUncertainAPSR, here("data", "df_dcpoUncertainAPSR.rds"))
-```
-
 ```{r dcpoUncertaintyAPSR}
+# ls_country <- levels(dcpo_input$data$kk)
+# first_year <- min(dcpo_input$data$year)
+# 
+# df_dcpoUncertainAPSR <- purrr::map(1:1000, function(anEntry) {
+#   dcpo_theta$theta[anEntry,,] %>% 
+#     reformat_dcpo_output("theta") %>% 
+#     left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
+#               by = c("year", "country")) %>%
+#     left_join(df_controls, by = c("country", "year")) %>% 
+#     plm::pdata.frame(index = c("country", "year"))
+# })
+
 ## The same as in the previous chunk
@@
 
+###Duble check the dataset--------------
 ls_mod <- c(
-  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
-  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
+  glue("plm({ls_eqECM}, model = 'pooling', data = df_dcpoUncertainAPSR)"),
+  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = df_dcpoUncertainAPSR)")
 )
@@
 
-```{r visualizedAPSR, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}
-
-result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
-result_clsUncertainAPSR <- readRDS(here("output", "estimates_clsAPSR.RDS"))
-result_dcpoAPSR <- readRDS(here("output", "estimates_dcpoAPSR.RDS"))
+```{r visualizedAPSR, fig.cap= "\\label{fig:visualizedAPSR} The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}
+
+load(here::here("output", "estimates_clsMeanAPSR.RDS"))
+load(here::here("output", "estimates_clsAPSR.RDS"))
+result_dcpoAPSR <- readRDS(here::here("output", "estimates_dcpoAPSR.RDS"))
 
@@
              title = "Original") %>% 
-
-  kableExtra::kable_styling(font_size = 8) %>% 
   kableExtra::kable_styling(latex_options = "HOLD_position")
@@
 
-\blandscape
+\pagebreak
 
 # Numeric Results for Replicating Claassen 2020b
+
+\begin{landscape}
 
@@
 
-names(tb_result_clsAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
+names(tb_result_clsAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM w. Corruption", "ECM w. Corruption-Regime", "FD w. Corruption", "FD w. Corruption-Regime")
 
@@
              output = "latex") %>% 
-  kableExtra::kable_styling(font_size = 7) %>% 
   kableExtra::kable_styling(latex_options = "HOLD_position")
@@
 
-\elandscape
-
-\blandscape
+\pagebreak
 
@@
 
-names(tb_result_clsUncertainAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
+names(tb_result_clsUncertainAPSR) <- c("ECM", "ECM-Regime", 
+                          "FD", "FD-Regime", 
+                          "ECM w. Corruption", "ECM w. Corruption-Regime", 
+                          "FD w. Corruption", "FD w. Corruption-Regime")
 
@@
 
-names(tb_result_dcpoAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
+names(tb_result_dcpoAPSR) <- c("ECM", "ECM-Regime", 
+                          "FD", "FD-Regime", 
+                          "ECM w. Corruption", "ECM w. Corruption-Regime", 
+                          "FD w. Corruption", "FD w. Corruption-Regime")
 
@@
 
-\elandscape
-
+\pagebreak
 ```{r datawitherrors}
@@
 ```
+
+\end{landscape}
 
@@
 
-```{r visualizeFullUncertainAJPS, fig.cap= "The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=7}
-
-# Very weird phenomenon that the same type of rds files needs different ways to read
-# Suggesting using the qs or csv data type in future.
-result_cls <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
-result_clsUncertainFull <- readRDS(here("output", "estimates_clsAJPSfullUncertain.RDS"))
-result_dcpoUncertainFull <- readRDS(here("output", "estimates_dcpoAJPSfullUncertain.RDS"))
-
-result_pooled <- bind_rows(
-  mutate(result_cls$pooled[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainFull$pooled[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainFull$pooled[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "Pooled")
-
-result_gmm <- bind_rows(
-  mutate(result_cls$gmm[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainFull$gmm[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainFull$gmm[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "GMM")
-
-result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = rep(
-      c("Democracy\n (t-1)",
-        "Democracy\n (t-2)",
-      "Support\n (t-1)",
-      "Log GDP\n per capita\n (t-1)",
-      "GDP per\n capita growth\n (t-1)",
-      "Regional\n democracy\n (t-1)",
-      "Percent\n Muslim\n (t-1)",
-      "Resource\n dependence\n (t-1)"),
-    time = 6), 
-    type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
-
-terms <- factor(rev(c("Democracy[t-1]",
-        "Democracy[t-2]",
-      "Support[t-1]",
-      "Log~GDP~per~capita[t-1]",
-      "GDP~per~capita~growth[t-1]",
-      "Regional~democracy[t-1]",
-      "Percent~Muslim[t-1]",
-      "Resource~dependence[t-1]")), levels =
-      rev(c("Democracy[t-1]",
-        "Democracy[t-2]",
-      "Support[t-1]",
-      "Log~GDP~per~capita[t-1]",
-      "GDP~per~capita~growth[t-1]",
-      "Regional~democracy[t-1]",
-      "Percent~Muslim[t-1]",
-      "Resource~dependence[t-1]")))
-
-# ggplot produces reversed plot, and embarrassed to say, I can't fix, again. Any thought?
-# What I've tried
-# 1. using guide_legend(reverse = TRUE) will change the legend's order not the plot.
-# 2. ordering models with factor levels using the original names or even c("1", "2", "3")
-# 2. redefining the order of model in the dataframe or in dwplot 
-# 3. checking the dwplot codes, model works in line 453, but nothing looks helpful
-# 4. Every post online is to reverse
-
-plot_AJPS1 <- dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms))) +
-  scale_color_grey(start = 0.4, end = 0.8) +
-  labs(
-    title = "DV: V-Dem Liberal Democracy Index",
-    subtitle = "Regime Compacted"
-  ) +
-  facet_wrap(~type, scales = "free_x") + 
-  theme(legend.position = "none")
-
-# the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
-# The trick is  to use guide = guide_legend(reverse = TRUE) within scale_color_*(); see below in plotAJPS2. --FS
-
-result_regime <- bind_rows(
-  mutate(result_cls$`pooled-regime`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainFull$`pooled-regime`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainFull$`pooled-regime`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "Pooled")
-
-result_regimeGmm <- bind_rows(
-  mutate(result_cls$`gmm-regime`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainFull$`gmm-regime`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainFull$`gmm-regime`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "GMM")
-
-result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = rep(
-      c("Democracy\n (t-1)",
-        "Democracy\n (t-2)",
-      "Support\n demo only\n (t-1)",
-      "Support\n auto only\n (t-1)",
-      "Log GDP\n per capita\n (t-1)",
-      "GDP per\n capita growth\n (t-1)",
-      "Regional\n democracy\n (t-1)",
-      "Percent\n Muslim\n (t-1)",
-      "Resource\n dependence\n (t-1)"),
-    time = 6), 
-    type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
-
-terms2 <- factor(rev(c("Democracy[t-1]",
-                       "Democracy[t-2]",
-                       "Support[t-1] (democracies~only)",
-                       "Support[t-1] (autocracies~only)",
-                       "Log~GDP~per~capita[t-1]",
-                       "GDP~per~capita~growth[t-1]",
-                       "Regional~democracy[t-1]",
-                       "Percent~Muslim[t-1]",
-                       "Resource~dependence[t-1]")), levels =
-                   rev(c("Democracy[t-1]",
-                         "Democracy[t-2]",
-                         "Support[t-1] (democracies~only)",
-                         "Support[t-1] (autocracies~only)",
-                         "Log~GDP~per~capita[t-1]",
-                         "GDP~per~capita~growth[t-1]",
-                         "Regional~democracy[t-1]",
-                         "Percent~Muslim[t-1]",
-                         "Resource~dependence[t-1]")))
-
-plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms2))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  labs(
-    title = "",
-    subtitle = "Regime Specific"
-  ) +
-  facet_wrap(~type, scales = "free_x") +
-  theme(legend.position = "bottom", 
-        legend.title = element_blank())
-
-legend <- get_legend(plot_AJPS2)
-
-plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
-
-grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
-
-```
-
 ```{r claassenFullUncertaintyAPSR}
@@
 
-saveRDS(result_clsFullUncertainAPSR, file = here::here("output", "estimates_clsFullUncertainAPSR.RDS"))
-
-```
-
-```{r dcpoFullUncertaintyAPSR}
+saveRDS(result_clsFullUncertainAPSR, file = here::here("output", "estimates_clsAPSR.RDS"))
+
+```
+
+```{r dcpoUncertaintyAPSR}
 load(here("data", "dcpo_apsr.rda")) # produced by cls_ajps_apsr_uncertain.R
@@
 
-saveRDS(result_dcpoUncertainAPSR, file = here::here("output", "estimates_dcpoUncertainAPSR.RDS"))
-```
-
-```{r visualizedFullUncertainAPSR, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}
-
-result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
-result_clsFullUncertainAPSR <- readRDS(here("output", "estimates_clsFullUncertainAPSR.RDS"))
-result_dcpoFullUncertainAPSR <- readRDS(here("output", "estimates_dcpoUncertainAPSR.RDS"))
-
-# Regime compacted ####
-
-result_ecm1 <- bind_rows(
-  mutate(result_clsAPSR$pooled1[[1]], model = "Claassen 2020a"),
-  mutate(result_clsFullUncertainAPSR$pooled1[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoFullUncertainAPSR$pooled1[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "ECM")
-
-result_fd1 <- bind_rows(
-  mutate(result_clsAPSR$fd1[[1]], model = "Claassen 2020a"),
-  mutate(result_clsFullUncertainAPSR$fd1[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoFullUncertainAPSR$fd1[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "First Difference")
-
-result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-      "Liberal Democracy\n (Difference)",
-      "Liberal Democracy\n (t-1)",
-      "Log GDP\n per capita\n (Difference)",
-      "Log GDP\n (t-1)"),
-    time = 3),
-    rep(
-      c("Liberal Democracy\n (Difference)", 
-        "Log GDP\n per capita\n (Difference)"), 
-      time = 3
-    )),
-    type = factor(type, levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
-  )
-
-terms1 <- factor(rev(c("Support[t-1]",
-                      "Support[t-2]",
-                      "Delta~Liberal~democracy",
-                      "Liberal~democracy[t-1]",
-                      "Delta~Log~GDP~per~capita",
-                      "Log~GDP[t-1]")),
-                levels = rev(c("Support[t-1]",
-                               "Support[t-2]",
-                               "Delta~Liberal~democracy",
-                               "Liberal~democracy[t-1]",
-                               "Delta~Log~GDP~per~capita",
-                               "Log~GDP[t-1]")))
-
-plot_APSR1 <- dwplot(result_APSR1, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms1))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  # scale_color_uiowa(name = "", palette = "digitMixed") +
-  labs(
-    title = "DV: Public Support for Democracy",
-    subtitle = "Regime Compacted"
-  ) +
-  facet_wrap(~type, scales = "free_x") + 
-  theme(legend.position = "none")
-
-result_ecm2 <- bind_rows(
-  mutate(result_clsAPSR$pooled2[[1]], model = "Claassen 2020a"),
-  mutate(result_clsFullUncertainAPSR$pooled2[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoFullUncertainAPSR$pooled2[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "ECM")
-
-result_fd2 <- bind_rows(
-  mutate(result_clsAPSR$fd2[[1]], model = "Claassen 2020a"),
-  mutate(result_clsFullUncertainAPSR$fd2[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoFullUncertainAPSR$fd2[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "First Difference")
-
-result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-      "Liberal Democracy\n (Difference)",
-      "Liberal Democracy\n (t-1)",
-      "Log GDP\n per capita\n (Difference)",
-      "Log GDP\n (t-1)",
-      "Corruption\n (Difference)",
-      "Corruption\n (t-1)"
-      ),
-    time = 3),
-    rep(
-      c("Liberal Democracy\n (Difference)", 
-        "Log GDP\n per capita\n (Difference)",
-        "Corruption\n (Difference)"), 
-      time = 3
-    )),
-    type = factor(type, levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
-  )
-
-terms2 <- factor(rev(c("Support[t-1]",
-                      "Support[t-2]",
-                      "Delta~Liberal~democracy",
-                      "Liberal~democracy[t-1]",
-                      "Delta~Log~GDP~per~capita",
-                      "Log~GDP[t-1]",
-                      "Delta~Corruption",
-                      "Corruption[t-1]")),
-                levels = rev(c("Support[t-1]",
-                               "Support[t-2]",
-                               "Delta~Liberal~democracy",
-                               "Liberal~democracy[t-1]",
-                               "Delta~Log~GDP~per~capita",
-                               "Log~GDP[t-1]",
-                               "Delta~Corruption",
-                               "Corruption[t-1]")))
-
-plot_APSR2 <- dwplot(result_APSR2, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms2))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  # scale_color_uiowa(name = "", palette = "digitMixed") +
-  labs(
-    title = "",
-    subtitle = "W. Corruption"
-  ) +
-  facet_wrap(~type, scales = "free_x") +
-  theme(legend.position = "none")
-
-# Regime specified ####
-
-result_ecmReg1 <- bind_rows(
-  mutate(result_clsAPSR$`pooled-regime1`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsFullUncertainAPSR$`pooled-regime1`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoFullUncertainAPSR$`pooled-regime1`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "ECM")
-
-result_fdReg1 <- bind_rows(
-  mutate(result_clsAPSR$`fd-regime1`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsFullUncertainAPSR$`fd-regime1`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoFullUncertainAPSR$`fd-regime1`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "First Difference")
-
-result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-      "Electoral Democracy\n (Difference)",
-      "Electoral Democracy\n (t-1)",
-      "Minoritarian Democracy\n (Difference)",
-      "Minoritarian Democracy\n (t-1)",
-      "Log GDP\n per capita\n (Difference)",
-      "Log GDP\n (t-1)"),
-    time = 3),
-    rep(
-      c("Electoral Democracy\n (Difference)", 
-        "Minoritarian Democracy\n (Difference)",
-        "Log GDP\n per capita\n (Difference)"), 
-      time = 3
-    )),
-    type = factor(type, levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
-  )
-
-terms3 <- factor(rev(c("Support[t-1]",
-                      "Support[t-2]",
-                      "Delta~Electoral~democracy",
-                      "Electoral~democracy[t-1]",
-                      "Delta~Minoritarian~democracy",
-                      "Minoritarian~democracy[t-1]",
-                      "Delta~Log~GDP~per~capita",
-                      "Log~GDP[t-1]")),
-                levels = rev(c("Support[t-1]",
-                      "Support[t-2]",
-                      "Delta~Electoral~democracy",
-                      "Electoral~democracy[t-1]",
-                      "Delta~Minoritarian~democracy",
-                      "Minoritarian~democracy[t-1]",
-                      "Delta~Log~GDP~per~capita",
-                      "Log~GDP[t-1]")))
-
-plot_RegAPSR1 <- dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms3))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  # scale_color_uiowa(name = "", palette = "digitMixed") +
-  labs(
-    title = "",
-    subtitle = "Regime Specified"
-  ) +
-  facet_wrap(~type, scales = "free_x") + 
-  theme(legend.position = "none")
-
-result_ecmReg2 <- bind_rows(
-  mutate(result_clsAPSR$`pooled-regime2`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsFullUncertainAPSR$`pooled-regime2`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoFullUncertainAPSR$`pooled-regime2`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "ECM")
-
-result_fdReg2 <- bind_rows(
-  mutate(result_clsAPSR$`fd-regime2`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsFullUncertainAPSR$`fd-regime2`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoFullUncertainAPSR$`fd-regime2`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "First Difference")
-
-result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-      "Electoral Democracy\n (Difference)",
-      "Electoral Democracy\n (t-1)",
-      "Minoritarian Democracy\n (Difference)",
-      "Minoritarian Democracy\n (t-1)",
-      "Log GDP\n per capita\n (Difference)",
-      "Log GDP\n (t-1)",
-      "Corruption\n (Difference)",
-      "Corruption\n (t-1)"
-      ),
-    time = 3),
-    rep(
-      c("Electoral Democracy\n (Difference)", 
-        "Minoritarian Democracy\n (Difference)",
-        "Log GDP\n per capita\n (Difference)",
-        "Corruption\n (Difference)"), 
-      time = 3
-    )),
-    type = factor(type, levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
-  )
-
-terms4 <- factor(rev(c("Support[t-1]",
-                      "Support[t-2]",
-                      "Delta~Electoral~democracy",
-                      "Electoral~democracy[t-1]",
-                      "Delta~Minoritarian~democracy",
-                      "Minoritarian~democracy[t-1]",
-                      "Delta~Log~GDP",
-                      "Log~GDP[t-1]",
-                      "Delta~Corruption",
-                      "Corruption[t-1]")),
-                levels = rev(c("Support[t-1]",
-                               "Support[t-2]",
-                               "Delta~Electoral~democracy",
-                               "Electoral~democracy[t-1]",
-                               "Delta~Minoritarian~democracy",
-                               "Minoritarian~democracy[t-1]",
-                               "Delta~Log~GDP",
-                               "Log~GDP[t-1]",
-                               "Delta~Corruption",
-                               "Corruption[t-1]")))
-
-plot_RegAPSR2 <- dwplot(result_RegAPSR2, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms4))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  # scale_color_uiowa(name = "", palette = "digitMixed") +
-  labs(
-    title = "",
-    subtitle = "Regime Specified w. Corruption"
-  ) +
-  facet_wrap(~type, scales = "free_x") +
-  theme(legend.position = "bottom", 
-        legend.title = element_blank())
-
-legend <- get_legend(plot_RegAPSR2)
-
-plot_RegAPSR2 <- plot_RegAPSR2 + theme(legend.position = "none")
-
-grid.arrange(plot_APSR1, plot_APSR2, plot_RegAPSR1, plot_RegAPSR2, legend, ncol = 1)
-```
-
-\pagebreak
+saveRDS(result_dcpoUncertainAPSR, file = here::here("output", "estimates_dcpoAPSR.RDS"))
+```
 

### 2021-06-06 dcpo_demsupport.R
reorganized and renamed chunks; removing the point estimation for dcpo; #16

@@ -1,99 +1,4 @@
----
-output: 
-  bookdown::pdf_document2:
-    fig_caption: yes
-    keep_tex: yes
-    toc: FALSE
-    latex_engine: xelatex
-    # template: svm-latex-ms2.tex
-    
-title: "Democracy, Public Support, and Measurement Uncertainty"
-thanks: "The authors contributed equally to this work.  Corresponding author: [yuehu@mail.tsinghua.edu.cn](mailto:yuehu@mail.tsinghua.edu.cn).  Current version: `r format(Sys.time(), '%B %d, %Y')`."
-
-# author:
-# - name: Yuehong 'Cassandra' Tai
-#   affiliation: University of Iowa
-# - name: Yue Hu
-#   affiliation: Tsinghua University
-# - name: Frederick Solt
-#   affiliation: University of Iowa
-  
-abstract: "Do democratic regimes depend on public support to avoid backsliding? Does public support, in turn, respond thermostatically to changes in democracy? Two prominent recent studies (Claassen 2020a, 2020b) reinvigorated the classic hypothesis on the positive relationship between public support for democracy and regime survival---and challenged its reciprocal counterpart---by using a latent variable approach to measure mass democratic support from cross-national survey data. But such approaches come with concomitant measurement uncertainty, and neither study incorporated this uncertainty into its analyses. In this letter, we correctly take this uncertainty in account and show that there is no support for the conclusion of either study. We then work to minimize the measurement uncertainty in public support by bringing additional survey data and a superior model of public opinion. Even with these improvements, however, our analyses fail to yield evidence in support of either hypothesis, underscoring the necessity of accounting for measurement uncertainty. [149/150 words]"
-keywords: "Democratization, public support, regime survival, measurement uncertainty, IRT."
-
-date: "`r format(Sys.time(), '%B %d, %Y')`"
-editor_options: 
-  markdown: 
-    wrap: sentence
-tables: true # enable longtable and booktabs
-citation_package: natbib
-fontsize: 11pt
-linestretch: 1.5 # double spacing using linestretch 1.5
-bibliography: dcpo_demsupport.bib
-# bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
-# csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl
-biblio-style: apsr
-citecolor: black
-linkcolor: black
[…]

### 2021-06-06 paper/dcpo_demsupport.Rmd
use theta_dem_trim and theta_aut_trim in dcpo ajps models and cls ajps models. The previous ones also usded trimmed data but named as "theta_dem" and theta_aut". @sammo3182.

--- 2021-06-02 paper/dcpo_demsupport.Rmd
@@
 source(here("R", "moc_summary.R")) 
-
-get_legend<-function(myggplot){
-  tmp <- ggplot_gtable(ggplot_build(myggplot))
-  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
-  legend <- tmp$grobs[[leg]]
-  return(legend)
-}
+source(here("R", "customFunctions.R"))
 
@@
 
-supdem <- read.csv("../data/Support_democracy_ajps.csv")
-v_dem <- read.csv("../data/vdem15.csv")
+supdem <- read.csv(here("data", "Support_democracy_ajps.csv"))
+v_dem <- read.csv(here("data", "vdem15.csv"))    ######????????? why we need this one? for graph?  in the following analysis, we never use v_dem
 sd.plm <- pdata.frame(supdem, index = c("Country", "Year"))
 
-claassen_replication <- readRDS("../data/claassen_replication.rds") %>% 
+# produced by cls_ajps_apsr_uncertain.R and dcpo_ajps_apsr_uncertain.R
+load(here("data", "cls_ajps.rda")) 
+load(here("data", "dcpo_ajps.rda")) 
+load(here("data", "cls_apsr.rda"))
+load(here("data", "dcpo_apsr.rda"))
+
+claassen_replication <- readRDS(here("data", "claassen_replication.rds")) %>% 
   janitor::clean_names() %>% 
@@
 load(here("data", "dcpo_ajps_rubin.rda"))
-
-## Beck-Katz panel-corrected standard errors
-vcovBK_se <- function(x) {
-  plm::vcovBK(x, cluster = "time") %>% 
-    diag() %>% 
-    sqrt()
-}
-
-vcovHC_se <-  function(x) {
-  plm::vcovHC(x, method="arellano", cluster="group") %>%  #default setting
-    diag() %>% 
-    sqrt()
-}
-
-reformat_dcpo_output <- function(x, parameter_name) {
-  df_temp <- x %>% 
-    as_tibble(.name_repair = ~ls_country) %>% 
-    mutate(year = first_year + row_number() - 1) %>% 
-    pivot_longer(cols = all_of(ls_country),
-                 names_to = "country",
-                 values_to = parameter_name) %>%
-    arrange(country, year)
-  return(df_temp)
-}
+df_dcpoUncertainAPSR <- readRDS(here("data", "df_dcpoUncertainAPSR.rds"))
+
 ```
@@
 
-```{r dcpo_input_raw}
-dcpo_input_raw <-
-  DCPOtools::dcpo_setup(vars = read_csv(here::here("data-raw", "mood_dem.csv"),
-                                        col_types = "cccccc"),
-                        file = "data/dcpo_input_raw.csv")
-```
-
-```{r dcpo_input, eval=TRUE}
+```{r compare_n, eval = TRUE}
 dcpo_input_raw1 <-
@@
 
-dcpo_input <- DCPOtools::format_dcpo(dcpo_input_raw1,
-                                     scale_q = "church_lb",
-                                     scale_cp = 2)
-save(dcpo_input, file = here::here("data", "dcpo_input.rda"))
-```
-
-```{r compare_n, eval=TRUE}
 # if (!file.exists(here::here("data", "supdem raw survey marginals.tab"))) {
@@
 
-```{r dcpo}
-iter <- 3000
-
-dcpo_output <- dcpo(dcpo_input,
-                    iter = iter,
-                    chains = 4,
-                    thin = iter/500, # this yields 250 draws per chain, 1000 draws total
-                    pars = c("sd_delta","sd_theta_evolve", "sd_sigma_evolve", "sigma","phi","beta","alpha","delta","theta","y_r_pred","log_lik"))
-
-save(dcpo_output, file = here::here("data", "dcpo_output.rda"))
-
-dcpo_theta <- rstan::extract(dcpo_output, pars = "theta")
-
-save(dcpo_theta, file = here::here("data", "dcpo_theta.rda"))
-
-dcpo_sigma <- rstan::extract(dcpo_output, pars = "sigma")
-
-save(dcpo_sigma, file = here::here("data", "dcpo_sigma.rda"))
-
-dcpo_y_r_pred <- rstan::extract(dcpo_output, pars = "y_r_pred")
-
-save(dcpo_input, dcpo_y_r_pred, file = here::here("data", "dcpo_y_r_pred.rda"))
-```
-
-```{r country-years}
-path_df <-
-  list.files(
-    "../data",
-    pattern = ".*_theta.rda",
-    recursive = TRUE,
-    full.names = TRUE
-  ) %>%
-  .[str_which(., "claassen")]
-
-load(path_df)
-
-df_thetaDraw <- map_df(seq(claassen_m5_theta$theta[1, , 1]),
-       function(year) {
-         map_df(seq(claassen_m5_theta$theta[1, 1, ]),
-                function(country) {
-                  df_temp <-
-                    sample(claassen_m5_theta$theta[, year, country],
-                           size = 100,
-                           replace = TRUE) %>%
-                    matrix(ncol = 100) %>%
-                    as_tibble()
-                  df_temp$yearID <- year
-                  df_temp$countryID <- country
-                  return(df_temp)
-                })
-       }) %>% 
-  pivot_longer(
-    cols = starts_with("V"),
-    names_to = "draw",
-    values_to = "theta"
-  ) %>% 
-  group_split(draw)
-```
-
 # Results
@@
 
-```{r claassenAJPS, eval=TRUE}
+```{r cls-pointAJPS}
 ls_iv <- c("plm::lag(SupDem_trim, 1)",
@@
 
-```{r claassenUncertaintyAJPS}
-ls_country <- unique(claassen_replication$country)
-first_year <- min(claassen_replication$year)
-
-sd_control <- sd.plm %>%
-  mutate(
-    country = as.character(Country),
-    year = as.numeric(as.character(Year)),
-    regime = ifelse(Regime_VD > 1, 1, 0)
-  )
-
-df_cls <- purrr::map(1:1000, function(anEntry) {
-  claassen_m5_theta$theta[anEntry,,] %>% 
-    reformat_dcpo_output("theta") %>% 
-    # left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
-    #           by = c("year", "country")) %>%
-    left_join(sd_control, by = c("country", "year")) %>% 
-    mutate(theta_dem = theta * regime,
-           theta_aut = theta * (1 - regime)) %>% 
-    plm::pdata.frame(index = c("country", "year"))
-})
+```{r cls-modelAJPS}
 
@@
 
-ls_mod <- c(
+ls_mod_ajpsCLS <- c(
     glue("plm({ls_eq}, model = 'pooling', data = aData)"),
@@
 
-result_clsUncertain <- map(ls_mod, function(aMod){ # reading a model
-  result <- map(df_cls, function(aData){ # applying to the 1000 datasets
+```
+
+```{r cls-uncertainAJPSfull, eval=FALSE}
+result_clsUncertainFull <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
+  result <- map(cls_ajps, function(aData){ # applying to the 1000 datasets
     eval(parse(text = aMod))
@@
 
-names(result_clsUncertain) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
-
-saveRDS(result_clsUncertain, file = here::here("output", "estimates_clsAJPS.RDS"))
-```
-
-```{r dcpoMean}
-ls_country <- levels(dcpo_input$data$kk)
-first_year <- min(dcpo_input$data$year)
-
-df_dcpoMean <- purrr::map_df(1:1000, function(anEntry) {
-  dcpo_theta$theta[anEntry,,] %>%
-    reformat_dcpo_output("theta") %>%
-    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
-              by = c("year", "country"))
-}) %>%
-  group_by(country, year) %>%
-  summarise(theta = mean(theta),
-            sigma = mean(sigma))
-
-saveRDS(df_dcpoMean, file = here("data", "df_dcpoMean.RDS"))
-```
-
-```{r dcpoPointAJPS}
-df_controls <- readRDS(here("data", "control_variables_ajps.rds")) %>% 
-  mutate(country = countrycode::countrycode(country, "country.name", "country.name"),
-         regime = Vdem_regime > 1) %>% 
-  filter(year >= first_year) # using trimmed data as Claassen
-
-df_dcpoMeanAJPS <- df_dcpoMean %>% 
-  right_join(df_controls, by = c("country", "year")) %>% 
-  mutate(theta_dem = theta * regime,
-         theta_aut = theta * (1 - regime)) %>% 
-    plm::pdata.frame(index = c("country", "year"))
-
+names(result_clsUncertainFull) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
+
+saveRDS(result_clsUncertainFull, file = here::here("output", "estimates_clsAJPSfullUncertain.RDS"))
+```
+
+```{r dcpo-modelAJPS}
 ls_iv <- c("plm::lag(theta, 1)", 
@@
 
-ls_mod <- c(
-  glue("plm({ls_eq}, model = 'pooling', data = df_dcpoMeanAJPS)"),
-  glue(
-    "pgmm({ls_eq} | plm::lag(Vdem_libdem, 3:5), data = df_dcpoMeanAJPS, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
-  )
-)
-
-#There's a problem to run this part---------------------
-
-df_result_dcpo <- map(ls_mod, function(mod) {
-  result <- eval(parse(text = mod))
-})
-
-tidy_dcpo <- map(df_result_dcpo, function(result) {
-  df_result <- tidy(result, conf.int = TRUE)
-
-  if (class(result) == "plm") {
-     mutate(df_result, std.error = vcovBK_se(result))
-  } else{
-    mutate(df_result, std.error = vcovHC_se(result))
-  }
-
-})
-
-glance_dcpo <- map(df_result_dcpo, function(aResult){
-  if(class(aResult) == "plm"){ 
-    glance.plm(aResult) # using the customized glance function
-  }else{
-      glance(aResult)
-    }
-})
-
-result_dcpo <- map2(tidy_dcpo, glance_dcpo, ~ list(.x, .y))
-names(result_dcpo) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
-
-saveRDS(result_dcpo, file = here::here("output", "estimates_dcpoMeanAJPS.RDS"))
-```
-
-```{r dcpoUncertaintyAJPS}
-df_dcpo <- dcpo_ajps_rubin %>% map2(1:length(dcpo_ajps_rubin), ~ {
-  .x[[.y]] %>%
-    mutate(theta_dem = theta * regime,
-           theta_aut = theta * (1 - regime)) %>%
-    plm::pdata.frame(index = c("country", "year"))
-}) # The code is to fit the embedded format of dcpo_ajps_rubin
-
-# df_dcpo <- purrr::map(1:1000, function(anEntry) {
-#   dcpo_theta$theta[anEntry,,] %>% 
-#     reformat_dcpo_output("theta") %>% 
-#     left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
-#               by = c("year", "country")) %>%
-#     left_join(df_controls, by = c("country", "year")) %>% 
-#     mutate(theta_dem = theta * regime,
-#            theta_aut = theta * (1 - regime)) %>% 
-#     plm::pdata.frame(index = c("country", "year"))
-# })
-
-ls_iv <- c("plm::lag(theta, 1)", 
-    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) ")
-
-ls_method <- c("plm", "pgmm")
-
-ls_eq <- glue("Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + {ls_iv} + plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) + plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)")
-
-ls_mod <- c(
+ls_mod_ajpsDCPO <- c(
     glue("plm({ls_eq}, model = 'pooling', data = aData)"),
@@
 )
-
-result_dcpoUncertain <- map(ls_mod, function(aMod){ # reading a model
-  mod_eval <- function(aData) eval(parse(text = aMod))
-
-  result <- map(df_dcpo, mod_eval)
+```
+
+```{r dcpo-uncertainAJPSfull, eval=FALSE}
+result_dcpoUncertainFull <- map(ls_mod_ajpsDCPO, function(aMod){ # reading a model
+  result <- map(dcpo_ajps, function(aData){ # applying to the 1000 datasets
+    eval(parse(text = aMod))
+  })
 
@@
 
-names(result_dcpoUncertain) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
-
-saveRDS(result_dcpoUncertain, file = here::here("output", "estimates_dcpoAJPS.RDS"))
-```
-
-```{r visualizeAJPS, fig.cap= "The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=10}
-
-# Very weird phenomenon that the same type of rds files needs different ways to read
-# Suggesting using the qs or csv data type in future.
-result_cls <- readRDS(here::here("output", "estimates_clsMeanAJPS.RDS"))
-result_clsUncertain <- readRDS(here::here("output", "estimates_clsAJPS.RDS"))
-result_dcpoUncertain <- readRDS(here::here("output", "estimates_dcpoAJPS.RDS"))
-
-result_pooled <- bind_rows(
-  mutate(result_cls$pooled[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertain$pooled[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertain$pooled[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "Pooled")
-
-result_gmm <- bind_rows(
-  mutate(result_cls$gmm[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertain$gmm[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertain$gmm[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "GMM")
-
-result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = rep(
-      c("Democracy\n (t-1)",
-        "Democracy\n (t-2)",
-      "Support\n (t-1)",
-      "Log GDP\n per capita\n (t-1)",
-      "GDP per\n capita growth\n (t-1)",
-      "Regional\n democracy\n (t-1)",
-      "Percent\n Muslim\n (t-1)",
-      "Resource\n dependence\n (t-1)"),
-    time = 6), 
-    type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
-
-terms <- factor(rev(c("Democracy[t-1]",
-        "Democracy[t-2]",
-      "Support[t-1]",
-      "Log~GDP~per~capita[t-1]",
-      "GDP~per~capita~growth[t-1]",
-      "Regional~democracy[t-1]",
-      "Percent~Muslim[t-1]",
-      "Resource~dependence[t-1]")), levels =
-      rev(c("Democracy[t-1]",
-        "Democracy[t-2]",
-      "Support[t-1]",
-      "Log~GDP~per~capita[t-1]",
-      "GDP~per~capita~growth[t-1]",
-      "Regional~democracy[t-1]",
-      "Percent~Muslim[t-1]",
-      "Resource~dependence[t-1]")))
-
-# ggplot produces reversed plot, and embarrassed to say, I can't fix, again. Any thought?
-# What I've tried
-# 1. using guide_legend(reverse = TRUE) will change the legend's order not the plot.
-# 2. ordering models with factor levels using the original names or even c("1", "2", "3")
-# 2. redefining the order of model in the dataframe or in dwplot 
-# 3. checking the dwplot codes, model works in line 453, but nothing looks helpful
-# 4. Every post online is to reverse
-
-plot_AJPS1 <- dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms))) +
-  scale_color_grey(start = 0.4, end = 0.8) +
-  labs(
-    title = "DV: V-Dem Liberal Democracy Index",
-    subtitle = "Regime Compacted"
-  ) +
-  facet_wrap(~type, scales = "free_x") + 
-  theme(legend.position = "none")
-
-# the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
-# The trick is  to use guide = guide_legend(reverse = TRUE) within scale_color_*(); see below in plotAJPS2. --FS
-
-result_regime <- bind_rows(
-  mutate(result_cls$`pooled-regime`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertain$`pooled-regime`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertain$`pooled-regime`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "Pooled")
-
-result_regimeGmm <- bind_rows(
-  mutate(result_cls$`gmm-regime`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertain$`gmm-regime`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertain$`gmm-regime`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "GMM")
-
-result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = rep(
-      c("Democracy\n (t-1)",
-        "Democracy\n (t-2)",
-      "Support\n demo only\n (t-1)",
-      "Support\n auto only\n (t-1)",
-      "Log GDP\n per capita\n (t-1)",
-      "GDP per\n capita growth\n (t-1)",
-      "Regional\n democracy\n (t-1)",
-      "Percent\n Muslim\n (t-1)",
-      "Resource\n dependence\n (t-1)"),
-    time = 6), 
-    type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
-
-terms2 <- factor(rev(c("Democracy[t-1]",
-                       "Democracy[t-2]",
-                       "Support[t-1] (democracies~only)",
-                       "Support[t-1] (autocracies~only)",
-                       "Log~GDP~per~capita[t-1]",
-                       "GDP~per~capita~growth[t-1]",
-                       "Regional~democracy[t-1]",
-                       "Percent~Muslim[t-1]",
-                       "Resource~dependence[t-1]")), levels =
-                   rev(c("Democracy[t-1]",
-                         "Democracy[t-2]",
-                         "Support[t-1] (democracies~only)",
-                         "Support[t-1] (autocracies~only)",
-                         "Log~GDP~per~capita[t-1]",
-                         "GDP~per~capita~growth[t-1]",
-                         "Regional~democracy[t-1]",
-                         "Percent~Muslim[t-1]",
-                         "Resource~dependence[t-1]")))
-
-plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms2))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  labs(
-    title = "",
-    subtitle = "Regime Specific"
-  ) +
-  facet_wrap(~type, scales = "free_x") +
-  theme(legend.position = "bottom", 
-        legend.title = element_blank())
-
-legend <- get_legend(plot_AJPS2)
-
-plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
-
-grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
-
-```
-
-```{r visualizedUncertainAJPS, fig.cap= "The Effect of Public Support on Democracy with Uncertainty"}
+names(result_dcpoUncertainFull) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
+
+saveRDS(result_dcpoUncertainFull, file = here::here("output", "estimates_dcpoAJPSfullUncertain.RDS"))
+```
+
+```{r plot-mainAJPS, fig.cap= "The Effect of Public Support on Democracy with Uncertainty", eval=FALSE}
 
@@
 
-```{r claassenAPSR, eval = TRUE}
+```{r cls-pointAPSR}
 load(here::here("data", "dem_mood_apsr.RData"))
@@
 
-```{r claassenAPSRUncertainty}
-ls_country <- unique(claassen_replication$country)
-first_year <- min(claassen_replication$year)
-
-sd_control <- sd.plm %>%
-  mutate(
-    country = as.character(Country),
-    year = as.numeric(as.character(Year))
-  )
-
-df_clsAPSR <- purrr::map(1:1000, function(anEntry) {
-  claassen_m5_theta$theta[anEntry,,] %>% 
-    reformat_dcpo_output("theta") %>% 
-    # left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
-    #           by = c("year", "country")) %>%
-    left_join(sd_control, by = c("country", "year")) %>% 
-    plm::pdata.frame(index = c("country", "year"))
-})
-
+```{r cls-modelAPSR}
 ls_ivECM <- c("diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)", 
@@
 
-ls_mod <- c(
+ls_mod_apsrCLS <- c(
   glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
@@
 )
-
-result_clsUncertainAPSR <- map(ls_mod, function(aMod){ # reading a model
-  result <- map(df_clsAPSR, function(aData){ # applying to the 1000 datasets
+```
+
+```{r cls-uncertainAPSRfull, eval=FALSE}
+result_clsFullUncertainAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
+  result <- map(cls_apsr, function(aData){ # applying to the 1000 datasets
     eval(parse(text = aMod))
@@
 
-names(result_clsUncertainAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", "fd1", "fd-regime1", "fd2", "fd-regime2")
-
-saveRDS(result_clsUncertainAPSR, file = here::here("output", "estimates_clsAPSR.RDS"))
-
-```
-
-```{r dcpoPointAPSR}
-
-df_dcpoMean <- readRDS(here("data", "df_dcpoMean.RDS"))
-
-df_controls <- readRDS(here("data", "control_variables_apsr.rds")) %>% 
-  mutate(country = countrycode::countrycode(country, "country.name", "country.name")) %>% 
-  filter(year >= first_year)
-
-df_dcpoMeanAPSR <- df_dcpoMean %>% 
-  left_join(df_controls, by = c("country", "year")) %>% 
-  plm::pdata.frame(index = c("country", "year"))
-
+names(result_clsFullUncertainAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", "fd1", "fd-regime1", "fd2", "fd-regime2")
+
+saveRDS(result_clsFullUncertainAPSR, file = here::here("output", "estimates_clsFullUncertainAPSR.RDS"))
+```
+
+```{r dcpo-modelAPSR}
 ls_ivECM <- c("diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1)", 
@@
 
-ls_mod <- c(
-  glue("plm({ls_eqECM}, model = 'pooling', data = df_dcpoMeanAPSR)"),
-  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = df_dcpoMeanAPSR)")
-)
-
-df_result_dcpoMeanAPSR <- map(ls_mod, function(mod) {
-  result <- eval(parse(text = mod))
-})
-
-result_dcpoMeanAPSR <- map(df_result_dcpoMeanAPSR, function(aResult) {
-  tidy_result <- tidy(aResult, conf.int = TRUE) %>% 
-    mutate(std.error = vcovHC_se(aResult))
-
-  glance_result <- glance.plm(aResult)
-
-  ls_result <- list(tidy_result, glance_result)
-})
-
-names(result_dcpoMeanAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",  "fd1", "fd-regime1", "fd2", "fd-regime2")
-
-saveRDS(result_dcpoMeanAPSR, file = here::here("output", "estimates_dcpoMeanAPSR.RDS"))
-```
-
-```{r data-dcpoUncertainAPSR}
-ls_country <- levels(dcpo_input$data$kk)
-first_year <- min(dcpo_input$data$year)
-
-df_dcpoUncertainAPSR <- purrr::map(1:1000, function(anEntry) {
-  dcpo_theta$theta[anEntry,,] %>%
-    reformat_dcpo_output("theta") %>%
-    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
-              by = c("year", "country")) %>%
-    left_join(df_controls, by = c("country", "year")) %>%
-    plm::pdata.frame(index = c("country", "year"))
-})
-
-saveRDS(df_dcpoUncertainAPSR, here("data", "df_dcpoUncertainAPSR.rds"))
-```
-
-```{r dcpoUncertaintyAPSR}
-## The same as in the previous chunk
-
-ls_ivECM <- c("diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1)", 
-              "diff(Vdem_polyarchy_z, lag = 1) + plm::lag(Vdem_polyarchy_z, 1) + diff(Vdem_liberal_z, lag = 1) + plm::lag(Vdem_liberal_z, 1)")
-ls_ctrlECM <- c("", " + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1)")
-
-ls_eqECM <- glue("diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + {ls_ivECM} + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1)") %>% 
-  outer(ls_ctrlECM, paste0) %>% 
-  as.vector()
-
-ls_ivFD <- c("Vdem_libdem_z",
-             "Vdem_polyarchy_z + Vdem_liberal_z")
-
-ls_ctrlFD <- c("", " + corruption_z")
-
-ls_eqFD <- glue("theta ~ {ls_ivFD} + lg_imp_mdpgdp") %>% 
-  outer(ls_ctrlFD, paste0) %>% 
-  as.vector()
-
-### Different datasets
-
-ls_mod <- c(
+ls_mod_apsrDCPO <- c(
   glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
@@
 )
-
-result_dcpoUncertainAPSR <- map(ls_mod, function(aMod){ # reading a model
-  result <- map(df_dcpoUncertainAPSR, function(aData){ # applying to the 1000 datasets
+```
+
+```{r dcpo-uncertainAPSRfull, eval=FALSE}
+result_dcpoUncertainAPSR <- map(ls_mod_apsrDCPO, function(aMod){ # reading a model
+  result <- map(dcpo_apsr, function(aData){ # applying to the 1000 datasets
     eval(parse(text = aMod))
@@
 
-saveRDS(result_dcpoUncertainAPSR, file = here::here("output", "estimates_dcpoAPSR.RDS"))
+saveRDS(result_dcpoUncertainAPSR, file = here::here("output", "estimates_dcpoUncertainAPSR.RDS"))
 ```
@@
 
-```{r visualizedAPSR, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}
+```{r plot-mainAPSR, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10, eval=FALSE}
 
@@
 
-```{r visualizedUncertaintyAPSR, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO"}
-
-load(here::here("output", "estimates_dcpoAPSR.RDS"))
-
-df_plot <- df_result_dcpoMeanAPSR[[1]] %>% 
-  mutate(model = "DCPO\n (Point Estimates)")
-
-df_plot <- df_result_dcpoAPSR[[1]] %>%
-  mutate(model = "DCPO\n (w. Uncertainty)") %>%
-  rename(std.error = se) %>%
-  bind_rows(df_plot)
-
-plot_pooled <- filter(df_plot, model != "Claassen 2019") %>% 
-  dwplot(by_2sd = FALSE) %>%
-  relabel_predictors(
-    c(
-      `plm::lag(theta, 1:2)1` = "Democracy Mood(t-1)",
-      `plm::lag(theta, 1:2)2` = "Democracy Mood(t-2)",
-      `diff(Vdem_libdem_z, lag = 1)` = "Liberal Democracy (Diff)",
-      `plm::lag(Vdem_libdem_z, 1)` = "Liberal Democracy (t-1)",
-      `diff(lg_imp_mdpgdp, lag = 1)` = "Log GDP per capita(Diff)", 
-      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t-1)",
-      `plm::lag(mdprgdp_grwth, 1)` = "Corruption (Difference)"
-    )
-  ) +
-  geom_vline(xintercept = 0,
-             colour = "grey80",
-             linetype = 2) +
-  theme_minimal() +
-  ggtitle("DV: Liberal Democracy (Vdem)") +
-  xlab("Coefficient Estimate") +
-  theme(
-    axis.title.y = element_blank(),
-    legend.position = "bottom",
-    legend.title = element_blank()
-  )
-
-df_plot <- df_result_dcpoMeanAPSR[[2]] %>% 
-  mutate(model = "DCPO\n (Point Estimates)")
-
-df_plot <- df_result_dcpoAPSR[[2]] %>%
-  mutate(model = "DCPO\n (w. Uncertainty)") %>%
-  rename(std.error = se) %>%
-  bind_rows(df_plot)
-
-plot_pooled2 <- filter(df_plot, model != "Claassen 2019") %>% 
-  dwplot(by_2sd = FALSE) %>%
-  relabel_predictors(
-    c(
-      `plm::lag(theta, 1:2)1` = "Democracy Mood(t-1)",
-      `plm::lag(theta, 1:2)2` = "Democracy Mood(t-2)",
-      `diff(Vdem_libdem_z, lag = 1)` = "Liberal Democracy (Diff)",
-      `plm::lag(Vdem_libdem_z, 1)` = "Liberal Democracy (t-1)",
-      `diff(lg_imp_mdpgdp, lag = 1)` = "Log GDP per capita(Diff)", 
-      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t-1)",
-      `diff(cpi_sd, lag = 1)` = "Corruption (Difference)",
-      `plm::lag(cpi_sd, 1)` = "Corruption (t-1)"
-    )
-  ) +
-  geom_vline(xintercept = 0,
-             colour = "grey80",
-             linetype = 2) +
-  theme_minimal() +
-  ggtitle("DV: Liberal Democracy (Vdem)") +
-  xlab("Coefficient Estimate") +
-  theme(
-    axis.title.y = element_blank(),
-    legend.position = "bottom",
-    legend.title = element_blank()
-  )
-
-gridExtra::grid.arrange(plot_pooled,plot_pooled2, ncol = 2)
-```
-
 # Discussion
@@
 
-```{r claassenFullUncertaintyAJPS}
-
-load(here("data", "cls_ajps.rda")) # produced by cls_ajps_apsr_uncertain.R
-
-ls_iv <- c("plm::lag(theta, 1)", 
-    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) ")
-
-ls_method <- c("plm", "pgmm")
-
-ls_eq <- glue("Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + {ls_iv} + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)")
-
-ls_mod <- c(
-    glue("plm({ls_eq}, model = 'pooling', data = aData)"),
-    glue(
-        "pgmm({ls_eq} | plm::lag(Libdem_VD, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
-    )
-)
-
-result_clsUncertainFull <- map(ls_mod, function(aMod){ # reading a model
-  result <- map(cls_ajps, function(aData){ # applying to the 1000 datasets
+```{r cls-uncertainAJPSmain, eval=FALSE}
+ls_country <- unique(claassen_replication$country)
+first_year <- min(claassen_replication$year)
+
+sd_control <- sd.plm %>%
+  mutate(
+    country = as.character(Country),
+    year = as.numeric(as.character(Year)),
+    regime = ifelse(Regime_VD > 1, 1, 0)
+  )
+
+df_cls <- purrr::map(1:1000, function(anEntry) {
+  claassen_m5_theta$theta[anEntry,,] %>% 
+    reformat_dcpo_output("theta") %>% 
+    left_join(sd_control, by = c("country", "year")) %>% 
+    mutate(theta_dem = theta * regime,
+           theta_aut = theta * (1 - regime)) %>% 
+    plm::pdata.frame(index = c("country", "year"))
+})
+
+result_clsUncertain <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
+  result <- map(df_cls, function(aData){ # applying to the 1000 datasets
     eval(parse(text = aMod))
@@
 
-names(result_clsUncertainFull) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
-
-saveRDS(result_clsUncertainFull, file = here::here("output", "estimates_clsAJPSfullUncertain.RDS"))
-```
-
-```{r dcpoFullUncertaintyAJPS}
-load(here("data", "dcpo_ajps.rda")) # produced by dcpo_ajps_apsr_uncertain.R
-
-ls_iv <- c("plm::lag(theta, 1)", 
-    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) ")
-
-ls_method <- c("plm", "pgmm")
-
-ls_eq <- glue("Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + {ls_iv} + plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) + plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)")
-
-ls_mod <- c(
-    glue("plm({ls_eq}, model = 'pooling', data = aData)"),
-    glue(
-        "pgmm({ls_eq} | plm::lag(Vdem_libdem, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
-    )
-)
-
-result_dcpoUncertainFull <- map(ls_mod, function(aMod){ # reading a model
-  result <- map(dcpo_ajps, function(aData){ # applying to the 1000 datasets
-    eval(parse(text = aMod))
-  })
+names(result_clsUncertain) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
+
+saveRDS(result_clsUncertain, file = here::here("output", "estimates_clsAJPS.RDS"))
+```
+
+```{r dcpo-uncertainAJPSmain, eval=FALSE}
+df_dcpo <- dcpo_ajps_rubin %>% map2(1:length(dcpo_ajps_rubin), ~ {
+  .x[[.y]] %>%
+    mutate(theta_dem = theta * regime,
+           theta_aut = theta * (1 - regime)) %>%
+    plm::pdata.frame(index = c("country", "year"))
+}) # The code is to fit the embedded format of dcpo_ajps_rubin
+
+# df_dcpo <- purrr::map(1:1000, function(anEntry) {
+#   dcpo_theta$theta[anEntry,,] %>% 
+#     reformat_dcpo_output("theta") %>% 
+#     left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
+#               by = c("year", "country")) %>%
+#     left_join(df_controls, by = c("country", "year")) %>% 
+#     mutate(theta_dem = theta * regime,
+#            theta_aut = theta * (1 - regime)) %>% 
+#     plm::pdata.frame(index = c("country", "year"))
+# })
+
+result_dcpoUncertain <- map(ls_mod_ajpsDCPO, function(aMod){ # reading a model
+  mod_eval <- function(aData) eval(parse(text = aMod))
+
+  result <- map(df_dcpo, mod_eval)
 
@@
 
-names(result_dcpoUncertainFull) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
-
-saveRDS(result_dcpoUncertainFull, file = here::here("output", "estimates_dcpoAJPSfullUncertain.RDS"))
-```
-
-```{r visualizeFullUncertainAJPS, fig.cap= "The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=7}
+names(result_dcpoUncertain) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
+
+saveRDS(result_dcpoUncertain, file = here::here("output", "estimates_dcpoAJPS.RDS"))
+```
+
+```{r cls-undertainAPSRmain, eval=FALSE}
+ls_country <- unique(claassen_replication$country)
+first_year <- min(claassen_replication$year)
+
+sd_control <- sd.plm %>%
+  mutate(
+    country = as.character(Country),
+    year = as.numeric(as.character(Year))
+  )
+
+df_clsAPSR <- purrr::map(1:1000, function(anEntry) {
+  claassen_m5_theta$theta[anEntry,,] %>% 
+    reformat_dcpo_output("theta") %>% 
+    # left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
+    #           by = c("year", "country")) %>%
+    left_join(sd_control, by = c("country", "year")) %>% 
+    plm::pdata.frame(index = c("country", "year"))
+})
+
+result_clsUncertainAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
+  result <- map(df_clsAPSR, function(aData){ # applying to the 1000 datasets
+    eval(parse(text = aMod))
+  })
+
+  result_betas <- mitools::MIextract(result, fun = coef)
+
+  result_vars <- mitools::MIextract(result, fun = vcovHC_se)
+
+  tidy_clsUncertainAPSR <- summary(mitools::MIcombine(results = result_betas, 
+                             variance = result_vars)) %>% 
+    rownames_to_column(var = "term") %>%
+        rename(conf.low = `(lower`,
+               conf.high = `upper)`,
+               estimate = results) %>%
+        filter(!str_detect(term, "(Intercept)"))
+
+  glance_clsUncertainAPSR <- glance.plm(result[[1]])
+
+  result_clsUncertainAPSR <- list(tidy_clsUncertainAPSR, glance_clsUncertainAPSR)
+})
+
+names(result_clsUncertainAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", "fd1", "fd-regime1", "fd2", "fd-regime2")
+
+saveRDS(result_clsUncertainAPSR, file = here::here("output", "estimates_clsAPSR.RDS"))
+
+```
+
+```{r dcpo-uncertainAPSRmain, eval=FALSE}
+result_dcpoUncertainAPSR <- map(ls_mod_apsrDCPO, function(aMod){ # reading a model
+  result <- map(df_dcpoUncertainAPSR, function(aData){ # applying to the 1000 datasets
+    eval(parse(text = aMod))
+  })
+
+  result_betas <- mitools::MIextract(result, fun = coef)
+
+  result_vars <- mitools::MIextract(result, fun = vcovHC_se)
+
+  tidy_dcpoUncertainAPSR <- summary(mitools::MIcombine(results = result_betas, 
+                             variance = result_vars)) %>% 
+    rownames_to_column(var = "term") %>%
+        rename(conf.low = `(lower`,
+               conf.high = `upper)`,
+               estimate = results) %>%
+        filter(!str_detect(term, "(Intercept)"))
+
+  glance_dcpoUncertainAPSR <- glance.plm(result[[1]])
+
+  result_dcpoUncertainAPSR <- list(tidy_dcpoUncertainAPSR, glance_dcpoUncertainAPSR)
+})
+
+names(result_dcpoUncertainAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",  "fd1", "fd-regime1", "fd2", "fd-regime2")
+
+saveRDS(result_dcpoUncertainAPSR, file = here::here("output", "estimates_dcpoAPSR.RDS"))
+```
+
+# Replications of Full Pack of Models in Claassen 2020a,b
+
+```{r plot-fullpackAJPS, fig.cap= "The Effect of Public Support on Democracy", fig.width=7.5, fig.height=10}
 
@@
 # Suggesting using the qs or csv data type in future.
-result_cls <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
-result_clsUncertainFull <- readRDS(here("output", "estimates_clsAJPSfullUncertain.RDS"))
-result_dcpoUncertainFull <- readRDS(here("output", "estimates_dcpoAJPSfullUncertain.RDS"))
+result_cls <- readRDS(here::here("output", "estimates_clsMeanAJPS.RDS"))
+result_clsUncertain <- readRDS(here::here("output", "estimates_clsAJPS.RDS"))
+result_dcpoUncertain <- readRDS(here::here("output", "estimates_dcpoAJPS.RDS"))
 
@@
   mutate(result_cls$pooled[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainFull$pooled[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainFull$pooled[[1]], model = "DCPO")
+  mutate(result_clsUncertain$pooled[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertain$pooled[[1]], model = "DCPO")
 ) %>% 
@@
   mutate(result_cls$gmm[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainFull$gmm[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainFull$gmm[[1]], model = "DCPO")
+  mutate(result_clsUncertain$gmm[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertain$gmm[[1]], model = "DCPO")
 ) %>% 
@@
   mutate(result_cls$`pooled-regime`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainFull$`pooled-regime`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainFull$`pooled-regime`[[1]], model = "DCPO")
+  mutate(result_clsUncertain$`pooled-regime`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertain$`pooled-regime`[[1]], model = "DCPO")
 ) %>% 
@@
   mutate(result_cls$`gmm-regime`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainFull$`gmm-regime`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainFull$`gmm-regime`[[1]], model = "DCPO")
+  mutate(result_clsUncertain$`gmm-regime`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertain$`gmm-regime`[[1]], model = "DCPO")
 ) %>% 
@@
 
-```{r claassenFullUncertaintyAPSR}
-
-load(here("data", "cls_apsr.rda")) # produced by cls_ajps_apsr_uncertain.R
-
-ls_ivECM <- c("diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)", 
-              "diff(Polyarchy_z, lag = 1) + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)")
-ls_ctrlECM <- c("", " + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1)")
-
-ls_eqECM <- glue("diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)") %>% 
-  outer(ls_ctrlECM, paste0) %>% 
-  as.vector()
-
-ls_ivFD <- c("Libdem_z",
-             "Polyarchy_z + Liberal_z")
-
-ls_ctrlFD <- c("", " + Corrup_TI_z")
-
-ls_eqFD <- glue("diff(theta, lag = 1) ~ {ls_ivFD} + lnGDP_imp") %>% 
-  outer(ls_ctrlFD, paste0) %>% 
-  as.vector()
-
-ls_mod <- c(
-  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
-  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
-)
-
-result_clsFullUncertainAPSR <- map(ls_mod, function(aMod){ # reading a model
-  result <- map(cls_apsr, function(aData){ # applying to the 1000 datasets
-    eval(parse(text = aMod))
-  })
-
-  result_betas <- mitools::MIextract(result, fun = coef)
-
-  result_vars <- mitools::MIextract(result, fun = vcovHC_se)
-
-  tidy_clsUncertainAPSR <- summary(mitools::MIcombine(results = result_betas, 
-                             variance = result_vars)) %>% 
-    rownames_to_column(var = "term") %>%
-        rename(conf.low = `(lower`,
-               conf.high = `upper)`,
-               estimate = results) %>%
-        filter(!str_detect(term, "(Intercept)"))
-
-  glance_clsUncertainAPSR <- glance.plm(result[[1]])
-
-  result_clsUncertainAPSR <- list(tidy_clsUncertainAPSR, glance_clsUncertainAPSR)
-})
-
-names(result_clsFullUncertainAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", "fd1", "fd-regime1", "fd2", "fd-regime2")
-
-saveRDS(result_clsFullUncertainAPSR, file = here::here("output", "estimates_clsFullUncertainAPSR.RDS"))
-
-```
-
-```{r dcpoFullUncertaintyAPSR}
-load(here("data", "dcpo_apsr.rda")) # produced by cls_ajps_apsr_uncertain.R
-
-ls_ivECM <- c("diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1)", 
-              "diff(Vdem_polyarchy_z, lag = 1) + plm::lag(Vdem_polyarchy_z, 1) + diff(Vdem_liberal_z, lag = 1) + plm::lag(Vdem_liberal_z, 1)")
-ls_ctrlECM <- c("", " + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1)")
-
-ls_eqECM <- glue("diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + {ls_ivECM} + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1)") %>% 
-  outer(ls_ctrlECM, paste0) %>% 
-  as.vector()
-
-ls_ivFD <- c("Vdem_libdem_z",
-             "Vdem_polyarchy_z + Vdem_liberal_z")
-
-ls_ctrlFD <- c("", " + corruption_z")
-
-ls_eqFD <- glue("theta ~ {ls_ivFD} + lg_imp_mdpgdp") %>% 
-  outer(ls_ctrlFD, paste0) %>% 
-  as.vector()
-
-### Different datasets
-
-###Duble check the dataset--------------
-ls_mod <- c(
-  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
-  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
-)
-
-result_dcpoUncertainAPSR <- map(ls_mod, function(aMod){ # reading a model
-  result <- map(dcpo_apsr, function(aData){ # applying to the 1000 datasets
-    eval(parse(text = aMod))
-  })
-
-  result_betas <- mitools::MIextract(result, fun = coef)
-
-  result_vars <- mitools::MIextract(result, fun = vcovHC_se)
-
-  tidy_dcpoUncertainAPSR <- summary(mitools::MIcombine(results = result_betas, 
-                             variance = result_vars)) %>% 
-    rownames_to_column(var = "term") %>%
-        rename(conf.low = `(lower`,
-               conf.high = `upper)`,
-               estimate = results) %>%
-        filter(!str_detect(term, "(Intercept)"))
-
-  glance_dcpoUncertainAPSR <- glance.plm(result[[1]])
-
-  result_dcpoUncertainAPSR <- list(tidy_dcpoUncertainAPSR, glance_dcpoUncertainAPSR)
-})
-
-names(result_dcpoUncertainAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",  "fd1", "fd-regime1", "fd2", "fd-regime2")
-
-saveRDS(result_dcpoUncertainAPSR, file = here::here("output", "estimates_dcpoUncertainAPSR.RDS"))
-```
-
-```{r visualizedFullUncertainAPSR, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}
+```{r plot-fullpackAJPSfull, fig.cap= "The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=7}
+
+# Very weird phenomenon that the same type of rds files needs different ways to read
+# Suggesting using the qs or csv data type in future.
+result_cls <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
+result_clsUncertainFull <- readRDS(here("output", "estimates_clsAJPSfullUncertain.RDS"))
+result_dcpoUncertainFull <- readRDS(here("output", "estimates_dcpoAJPSfullUncertain.RDS"))
+
+result_pooled <- bind_rows(
+  mutate(result_cls$pooled[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainFull$pooled[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertainFull$pooled[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "Pooled")
+
+result_gmm <- bind_rows(
+  mutate(result_cls$gmm[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainFull$gmm[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertainFull$gmm[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "GMM")
+
+result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democracy\n (t-1)",
+        "Democracy\n (t-2)",
+      "Support\n (t-1)",
+      "Log GDP\n per capita\n (t-1)",
+      "GDP per\n capita growth\n (t-1)",
+      "Regional\n democracy\n (t-1)",
+      "Percent\n Muslim\n (t-1)",
+      "Resource\n dependence\n (t-1)"),
+    time = 6), 
+    type = factor(type, levels = c("Pooled", "GMM")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
+
+terms <- factor(rev(c("Democracy[t-1]",
+        "Democracy[t-2]",
+      "Support[t-1]",
+      "Log~GDP~per~capita[t-1]",
+      "GDP~per~capita~growth[t-1]",
+      "Regional~democracy[t-1]",
+      "Percent~Muslim[t-1]",
+      "Resource~dependence[t-1]")), levels =
+      rev(c("Democracy[t-1]",
+        "Democracy[t-2]",
+      "Support[t-1]",
+      "Log~GDP~per~capita[t-1]",
+      "GDP~per~capita~growth[t-1]",
+      "Regional~democracy[t-1]",
+      "Percent~Muslim[t-1]",
+      "Resource~dependence[t-1]")))
+
+# ggplot produces reversed plot, and embarrassed to say, I can't fix, again. Any thought?
+# What I've tried
+# 1. using guide_legend(reverse = TRUE) will change the legend's order not the plot.
+# 2. ordering models with factor levels using the original names or even c("1", "2", "3")
+# 2. redefining the order of model in the dataframe or in dwplot 
+# 3. checking the dwplot codes, model works in line 453, but nothing looks helpful
+# 4. Every post online is to reverse
+
+plot_AJPS1 <- dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms))) +
+  scale_color_grey(start = 0.4, end = 0.8) +
+  labs(
+    title = "DV: V-Dem Liberal Democracy Index",
+    subtitle = "Regime Compacted"
+  ) +
+  facet_wrap(~type, scales = "free_x") + 
+  theme(legend.position = "none")
+
+# the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
+# The trick is  to use guide = guide_legend(reverse = TRUE) within scale_color_*(); see below in plotAJPS2. --FS
+
+result_regime <- bind_rows(
+  mutate(result_cls$`pooled-regime`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainFull$`pooled-regime`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertainFull$`pooled-regime`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "Pooled")
+
+result_regimeGmm <- bind_rows(
+  mutate(result_cls$`gmm-regime`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainFull$`gmm-regime`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertainFull$`gmm-regime`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "GMM")
+
+result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democracy\n (t-1)",
+        "Democracy\n (t-2)",
+      "Support\n demo only\n (t-1)",
+      "Support\n auto only\n (t-1)",
+      "Log GDP\n per capita\n (t-1)",
+      "GDP per\n capita growth\n (t-1)",
+      "Regional\n democracy\n (t-1)",
+      "Percent\n Muslim\n (t-1)",
+      "Resource\n dependence\n (t-1)"),
+    time = 6), 
+    type = factor(type, levels = c("Pooled", "GMM")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
+
+terms2 <- factor(rev(c("Democracy[t-1]",
+                       "Democracy[t-2]",
+                       "Support[t-1] (democracies~only)",
+                       "Support[t-1] (autocracies~only)",
+                       "Log~GDP~per~capita[t-1]",
+                       "GDP~per~capita~growth[t-1]",
+                       "Regional~democracy[t-1]",
+                       "Percent~Muslim[t-1]",
+                       "Resource~dependence[t-1]")), levels =
+                   rev(c("Democracy[t-1]",
+                         "Democracy[t-2]",
+                         "Support[t-1] (democracies~only)",
+                         "Support[t-1] (autocracies~only)",
+                         "Log~GDP~per~capita[t-1]",
+                         "GDP~per~capita~growth[t-1]",
+                         "Regional~democracy[t-1]",
+                         "Percent~Muslim[t-1]",
+                         "Resource~dependence[t-1]")))
+
+plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
+    scale_y_discrete(labels = parse(text = levels(terms2))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  labs(
+    title = "",
+    subtitle = "Regime Specific"
+  ) +
+  facet_wrap(~type, scales = "free_x") +
+  theme(legend.position = "bottom", 
+        legend.title = element_blank())
+
+legend <- get_legend(plot_AJPS2)
+
+plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
+
+grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
+
+```
+
+```{r plot-fullpackAPSR, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO"}
+
+load(here::here("output", "estimates_dcpoAPSR.RDS"))
+
+df_plot <- df_result_dcpoMeanAPSR[[1]] %>% 
+  mutate(model = "DCPO\n (Point Estimates)")
+
+df_plot <- df_result_dcpoAPSR[[1]] %>%
+  mutate(model = "DCPO\n (w. Uncertainty)") %>%
+  rename(std.error = se) %>%
+  bind_rows(df_plot)
+
+plot_pooled <- filter(df_plot, model != "Claassen 2019") %>% 
+  dwplot(by_2sd = FALSE) %>%
+  relabel_predictors(
+    c(
+      `plm::lag(theta, 1:2)1` = "Democracy Mood(t-1)",
+      `plm::lag(theta, 1:2)2` = "Democracy Mood(t-2)",
+      `diff(Vdem_libdem_z, lag = 1)` = "Liberal Democracy (Diff)",
+      `plm::lag(Vdem_libdem_z, 1)` = "Liberal Democracy (t-1)",
+      `diff(lg_imp_mdpgdp, lag = 1)` = "Log GDP per capita(Diff)", 
+      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t-1)",
+      `plm::lag(mdprgdp_grwth, 1)` = "Corruption (Difference)"
+    )
+  ) +
+  geom_vline(xintercept = 0,
+             colour = "grey80",
+             linetype = 2) +
+  theme_minimal() +
+  ggtitle("DV: Liberal Democracy (Vdem)") +
+  xlab("Coefficient Estimate") +
+  theme(
+    axis.title.y = element_blank(),
+    legend.position = "bottom",
+    legend.title = element_blank()
+  )
+
+df_plot <- df_result_dcpoMeanAPSR[[2]] %>% 
+  mutate(model = "DCPO\n (Point Estimates)")
+
+df_plot <- df_result_dcpoAPSR[[2]] %>%
+  mutate(model = "DCPO\n (w. Uncertainty)") %>%
+  rename(std.error = se) %>%
+  bind_rows(df_plot)
+
+plot_pooled2 <- filter(df_plot, model != "Claassen 2019") %>% 
+  dwplot(by_2sd = FALSE) %>%
+  relabel_predictors(
+    c(
+      `plm::lag(theta, 1:2)1` = "Democracy Mood(t-1)",
+      `plm::lag(theta, 1:2)2` = "Democracy Mood(t-2)",
+      `diff(Vdem_libdem_z, lag = 1)` = "Liberal Democracy (Diff)",
+      `plm::lag(Vdem_libdem_z, 1)` = "Liberal Democracy (t-1)",
+      `diff(lg_imp_mdpgdp, lag = 1)` = "Log GDP per capita(Diff)", 
+      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t-1)",
+      `diff(cpi_sd, lag = 1)` = "Corruption (Difference)",
+      `plm::lag(cpi_sd, 1)` = "Corruption (t-1)"
+    )
+  ) +
+  geom_vline(xintercept = 0,
+             colour = "grey80",
+             linetype = 2) +
+  theme_minimal() +
+  ggtitle("DV: Liberal Democracy (Vdem)") +
+  xlab("Coefficient Estimate") +
+  theme(
+    axis.title.y = element_blank(),
+    legend.position = "bottom",
+    legend.title = element_blank()
+  )
+
+gridExtra::grid.arrange(plot_pooled,plot_pooled2, ncol = 2)
+```
+
+```{r plot-fullpackAPSRfull, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}
 
@@
 ```{r MocclaassenUncertaintyAJPS}
-load("data/cls_ajps.rda")
+load(here("data","cls_ajps.rda"))
+
 df_cls <- purrr::map(1:900, function(anEntry) {
@@
 
-ls_iv <- c("plm::lag(SupDem_trim, 1)",                         ##sumpdem_trim, our model did not use trim
-           "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) ")
+ls_iv <- c("plm::lag(SupDem_trim, 1)",                         
+           "plm::lag(theta_dem_trim, 1) + plm::lag(theta_aut_trim, 1) ") ##all use trim
 ls_method <- c("plm", "pgmm")
@@
 df_dcpo <- purrr::map(1:900, function(anEntry) {
-  dcpo_ajps[[anEntry]] %>% 
-    mutate(theta_dem = ifelse(is.na(theta_trim),NA,theta_dem),
-           theta_aut = ifelse(is.na(theta_trim),NA,theta_aut)) %>% 
+  dcpo_ajps[[anEntry]] %>%     #original data has include theta_dem_trim
     plm::pdata.frame(index = c("country", "year"))
@@
 ls_iv <- c("plm::lag(theta_trim, 1)", 
-           "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1)") 
+           "plm::lag(theta_dem_trim, 1) + plm::lag(theta_aut_trim, 1)") #use trimed data
 ls_method <- c("plm", "pgmm")

### 2021-06-06 paper/dcpo_demsupport.Rmd
changed theta to theta_trim for apsr models. The results should yield the same x_scale with MOC now. @sammo3182

@@
 load(here("data", "dcpo_sigma.rda"))
-load(here("data", "dcpo_ajps_rubin.rda"))
+#load(here("data", "dcpo_ajps_rubin.rda"))
+# df_controls <- readRDS(here("data", "control_variables_ajps.rds"))   #use control file for merging with 
 df_dcpoUncertainAPSR <- readRDS(here("data", "df_dcpoUncertainAPSR.rds"))
@@
 
-ls_eqECM <- glue("diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)") %>% 
+ls_eqECM <- glue("diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)") %>% 
   outer(ls_ctrlECM, paste0) %>% 
@@
 
-ls_eqFD <- glue("diff(theta, lag = 1) ~ {ls_ivFD} + lnGDP_imp") %>% 
+ls_eqFD <- glue("diff(SupDem_trim, lag = 1) ~ {ls_ivFD} + lnGDP_imp") %>% 
   outer(ls_ctrlFD, paste0) %>% 
@@
   glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
-  glue("plm({ls_eqFD}, model = 'fd', index = 'Country', data = aData)")
+  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
 )
@@
 
-ls_eqECM <- glue("diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + {ls_ivECM} + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1)") %>% 
+ls_eqECM <- glue("diff(theta_trim, lag = 1) ~ plm::lag(theta_trim, 1:2) + {ls_ivECM} + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1)") %>% 
   outer(ls_ctrlECM, paste0) %>% 
@@
 
-ls_eqFD <- glue("theta ~ {ls_ivFD} + lg_imp_mdpgdp") %>% 
+ls_eqFD <- glue("theta_trim ~ {ls_ivFD} + lg_imp_mdpgdp") %>% 
   outer(ls_ctrlFD, paste0) %>% 
@@
 ```{r dcpo-uncertainAJPSmain, eval=FALSE}
-df_dcpo <- dcpo_ajps_rubin %>% map2(1:length(dcpo_ajps_rubin), ~ {
-  .x[[.y]] %>%
-    mutate(theta_dem = theta * regime,
-           theta_aut = theta * (1 - regime)) %>%
-    plm::pdata.frame(index = c("country", "year"))
-}) # The code is to fit the embedded format of dcpo_ajps_rubin
+# df_dcpo <- dcpo_ajps_rubin %>% map2(1:length(dcpo_ajps_rubin), ~ {
+#  .x[[.y]] %>%
+#    mutate(theta_dem = theta * regime,
+#           theta_aut = theta * (1 - regime)) %>%
+#    plm::pdata.frame(index = c("country", "year"))
+# }) # The code is to fit the embedded format of dcpo_ajps_rubin
 

### 2021-06-06 paper/dcpo_demsupport.Rmd
change theta, theta_aut and theta_dem to SupDem_trim, theta_aut_trim, and theta_dem_trim. @sammo3182

@@
 
-ls_iv <- c("plm::lag(theta, 1)", 
-    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) ")
+#ls_iv <- c("plm::lag(theta, 1)", 
+#    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) ")
+
+ls_iv <- c("plm::lag(SupDem_trim, 1)", 
+    "plm::lag(theta_dem_trim, 1) + plm::lag(theta_aut_trim, 1) ") #use trimmed data
 
@@
 ```{r dcpo-modelAJPS}
-ls_iv <- c("plm::lag(theta, 1)", 
-    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) ")
+#ls_iv <- c("plm::lag(theta, 1)", 
+#    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) ")
+
+ls_iv <- c("plm::lag(theta_trim, 1)", 
+    "plm::lag(theta_dem_trim, 1) + plm::lag(theta_aut_trim, 1) ") #use trimmed data
 

### 2021-06-07 R/cls_ajps_apsr_uncertainty.R
rename theta_dem and theta_aut to theta_dem_trim and theta_aut_trim

@@ -47,11 +47,13 @@ cls_ajps <- purrr::map(1:900, function(anEntry) {
     cls_theta_list[[anEntry]] %>% 
         left_join(cls_ajps_cntrl_list[[anEntry]],by = c("year", "country"))  %>% 
         mutate(SupDem_trim = ifelse(year<firstyear, NA, theta),
-               theta_dem = ifelse(is.na(SupDem_trim),NA,
+               theta_dem_trim = ifelse(is.na(SupDem_trim),NA,
                                   ifelse(Regime_VD > 1 & !is.na(SupDem_trim), theta, 0)),
-               theta_aut = ifelse(is.na(SupDem_trim),NA,
-                                  ifelse(Regime_VD < 2& !is.na(SupDem_trim), theta, 0)))
+               theta_aut_trim = ifelse(is.na(SupDem_trim),NA,
+                                  ifelse(Regime_VD < 2& !is.na(SupDem_trim), theta, 0))) %>%
+        select(country, year, theta, contains("trim"), everything())
 }) 
+
 #merge with cls_theta and create trim variables. 
 
 save(cls_ajps, file = "data/cls_ajps.rda")

### 2021-06-07 R/dcpo_ajps_apsr_uncertainty.R
created trimmed data and used here

@@ -16,15 +16,15 @@ set.seed(313)
 ####################### libdem_cntrl_list     ##################
 
 
-load("data/dcpo_input.rda")
-load("data/dcpo_theta.rda")
-load("data/dcpo_sigma.rda")
-load("data/dcpo_ajps_cntrl.rda")
-load("data/dcpo_apsr_cntrl.rda")
-cntrl_ajps_se <- readRDS("data/cntrl_ajps_se_1985.rds")
-load("data/country_regionUN.rda")  ##this file can be used when we need region variables
+load(here("data","dcpo_input.rda"))
+load(here("data","dcpo_theta.rda"))
+load(here("data","dcpo_sigma.rda"))
+load(here("data","dcpo_ajps_cntrl.rda"))
+load(here("data","dcpo_apsr_cntrl.rda"))
+cntrl_ajps_se <- readRDS(here("data","cntrl_ajps_se_1985.rds"))
+load(here("data","country_regionUN.rda"))  ##this file can be used when we need region variables
 
-#cpi_post <- readRDS("data/cpi_post.rds") created in R/cpi_error.R. 
+#cpi_post <- readRDS(here("data","cpi_post.rds")) created in R/cpi_error.R. 
 # For the convenience, create cpi_post here too.  
 
 
@@ -50,7 +50,7 @@ theta_sigma_list <- purrr::map(1:900, function(anEntry) {
               by = c("year", "country"))
 }) 
 
-#save(theta_sigma_list,file = "data/theta_sigma_list.rda")
+save(theta_sigma_list,file = here::here("data","theta_sigma_list.rda"))
 
 
 ########libdem_list
@@ -74,7 +74,7 @@ cntrl_ajps_se_pdist <- data.frame(cntrl_ajps_se_pdist)
 cntrl_ajps_libdem <- cbind(cntrl_ajps_se_pdist, pdist_df)
 identical(cntrl_ajps_libdem$iter_cn,cntrl_ajps_libdem$iter_se)
 
-#saveRDS(cntrl_ajps_libdem, "data/cntrl_ajps_libdem.rds")
+saveRDS(cntrl_ajps_libdem, file = here::here("data", "cntrl_ajps_libdem.rds"))
 
 data_temp <- cntrl_ajps_libdem %>% 
   group_by(iter_cn,country) %>%
@@ -86,8 +86,8 @@ for (i in 1:900) {
     filter(iter_cn ==  i)
 }
 
-#save(libdem_list, file = "data/libdem_list.rda")
[…]

### 2021-06-07 R/cls_ajps_apsr_uncertainty.R
use here

@@ -8,10 +8,10 @@ set.seed(313)
 ######## Create lists for elements in analysis data  ###########
 ########### AJPS: cls_libdem_ajps_list,cls_ajps  ###############
 ################################################################
-load("data/cls_ajps_cntrl.rda")  #cls ajps variables without errors. 
-load("data/cls_theta_list.rda")  #cls's theta list
-load("data/cls_libdem_list.rda")  #vdem8 libdem list
-load("data/country_regionUN.rda") 
+load(here("data","cls_ajps_cntrl.rda"))  #cls ajps variables without errors. 
+load(here("data","cls_theta_list.rda"))  #cls's theta list
+load(here("data","cls_libdem_list.rda"))  #vdem8 libdem list
+load(here("data","country_regionUN.rda"))
 
 libdem_ajps_list <- cls_libdem_list %>%
     map(~.x %>%
@@ -34,7 +34,7 @@ libdem_ajps_list <- cls_libdem_list %>%
             mutate(Libdem_regUN_m1 = lag(Libdem_regUN))
     ) 
 
-saveRDS(libdem_ajps_list, "data/cls_libdem_ajps_list.rds")
+saveRDS(libdem_ajps_list, file = here("data","cls_libdem_ajps_list.rds"))
 #include vdem8 libdem related variables such Libdem, Region_libdem, ChDem
 
 cls_ajps_cntrl_list <-  purrr::map(1:900, function(anEntry) {
@@ -56,19 +56,19 @@ cls_ajps <- purrr::map(1:900, function(anEntry) {
 
 #merge with cls_theta and create trim variables. 
 
-save(cls_ajps, file = "data/cls_ajps.rda")
+save(cls_ajps, file = here("data","cls_ajps.rda"))
 
 ################################################################
 ######## Create lists for elements in analysis data  ###########
 ########### APSR: cls_libdem_ajps_list,cls_ajps  ###############
 ################################################################
-#load("data/cls_ajps_cntrl.rda")
-#load("data/cls_theta_list.rda")
-#load("data/cls_libdem_list.rda")
-load("data/cls_apsr_cntrl.rda")
-load("data/cls_poly_list.rda")
-load("data/cls_liberal_list.rda")
-load("data/cpi_list.rda")
+#load(here("data","cls_ajps_cntrl.rda"))
+#load(here("data","cls_theta_list.rda"))
[…]

### 2021-06-07 paper/dcpo_demsupport.Rmd
outcome updated; #16 and d #23

@@
               "diff(Vdem_polyarchy_z, lag = 1) + plm::lag(Vdem_polyarchy_z, 1) + diff(Vdem_liberal_z, lag = 1) + plm::lag(Vdem_liberal_z, 1)")
-ls_ctrlECM <- c("", " + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1)")
+ls_ctrlECM <- c("", " + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1)")
 
@@
 
-ls_ctrlFD <- c("", " + corruption_z")
+ls_ctrlFD <- c("", " + Corrup_TI_z")
 

### 2021-06-07 R/cls_ajps_apsr_uncertainty.R

@@ -1,17 +1,26 @@
-library(tidyverse)
-library(dplyr)
-library(purrr)
-library(countrycode)
+if (!require(pacman)) install.packages("pacman")
+library(pacman)
+
+# load all the packages you will use below 
+p_load(
+    here,
+    purrr,
+    countrycode,
+    tidyverse
+) 
+
+# Functions preload
 set.seed(313)
+
 
 ################################################################
 ######## Create lists for elements in analysis data  ###########
 ########### AJPS: cls_libdem_ajps_list,cls_ajps  ###############
 ################################################################
-load("data/cls_ajps_cntrl.rda")  #cls ajps variables without errors. 
-load("data/cls_theta_list.rda")  #cls's theta list
-load("data/cls_libdem_list.rda")  #vdem8 libdem list
-load("data/country_regionUN.rda") 
+load(here("data","cls_ajps_cntrl.rda"))  #cls ajps variables without errors. 
+load(here("data","cls_theta_list.rda"))  #cls's theta list
+load(here("data","cls_libdem_list.rda"))  #vdem8 libdem list
+load(here("data","country_regionUN.rda"))
 
 libdem_ajps_list <- cls_libdem_list %>%
     map(~.x %>%
@@ -34,7 +43,7 @@ libdem_ajps_list <- cls_libdem_list %>%
             mutate(Libdem_regUN_m1 = lag(Libdem_regUN))
     ) 
 
-saveRDS(libdem_ajps_list, "data/cls_libdem_ajps_list.rds")
+saveRDS(libdem_ajps_list, file = here("data","cls_libdem_ajps_list.rds"))
 #include vdem8 libdem related variables such Libdem, Region_libdem, ChDem
 
 cls_ajps_cntrl_list <-  purrr::map(1:900, function(anEntry) {
@@ -47,26 +56,28 @@ cls_ajps <- purrr::map(1:900, function(anEntry) {
     cls_theta_list[[anEntry]] %>% 
         left_join(cls_ajps_cntrl_list[[anEntry]],by = c("year", "country"))  %>% 
         mutate(SupDem_trim = ifelse(year<firstyear, NA, theta),
-               theta_dem = ifelse(is.na(SupDem_trim),NA,
+               theta_dem_trim = ifelse(is.na(SupDem_trim),NA,
                                   ifelse(Regime_VD > 1 & !is.na(SupDem_trim), theta, 0)),
-               theta_aut = ifelse(is.na(SupDem_trim),NA,
[…]

### 2021-06-07 R/dcpo_ajps_apsr_uncertainty.R

@@ -1,13 +1,22 @@
-###Posterior distribution: codes from R/v10_posterior.R
-library(tidyverse)
-library(dplyr)
-library(tidyr)
-library(purrr)
-library(readxl)
-library(janitor)
-library(countrycode)
-library(stringr)
+if (!require(pacman)) install.packages("pacman")
+library(pacman)
+
+# load all the packages you will use below 
+p_load(
+  here,
+  tidyr,
+  purrr,
+  readxl,
+  janitor,
+  countrycode,
+  stringr,
+  tidyverse
+) 
+
+# Functions preload
 set.seed(313)
+
+
 
 ################################################################
 ######## Create lists for elements in analysis data  ###########
@@ -16,15 +25,15 @@ set.seed(313)
 ####################### libdem_cntrl_list     ##################
 
 
-load("data/dcpo_input.rda")
-load("data/dcpo_theta.rda")
-load("data/dcpo_sigma.rda")
-load("data/dcpo_ajps_cntrl.rda")
-load("data/dcpo_apsr_cntrl.rda")
-cntrl_ajps_se <- readRDS("data/cntrl_ajps_se_1985.rds")
-load("data/country_regionUN.rda")  ##this file can be used when we need region variables
+load(here("data","dcpo_input.rda"))
+load(here("data","dcpo_theta.rda"))
+load(here("data","dcpo_sigma.rda"))
+load(here("data","dcpo_ajps_cntrl.rda"))
+load(here("data","dcpo_apsr_cntrl.rda"))
+cntrl_ajps_se <- readRDS(here("data","cntrl_ajps_se_1985.rds"))
+load(here("data","country_regionUN.rda"))  ##this file can be used when we need region variables
 
-#cpi_post <- readRDS("data/cpi_post.rds") created in R/cpi_error.R. 
+#cpi_post <- readRDS(here("data","cpi_post.rds")) created in R/cpi_error.R. 
 # For the convenience, create cpi_post here too.  
 
 
@@ -50,7 +59,7 @@ theta_sigma_list <- purrr::map(1:900, function(anEntry) {
               by = c("year", "country"))
 }) 
 
-#save(theta_sigma_list,file = "data/theta_sigma_list.rda")
[…]

### 2021-06-08 paper/dcpo_demsupport.Rmd
clean up intro

--- 2021-06-06 paper/dcpo_demsupport.Rmd
@@
     latex_engine: xelatex
-    # template: svm-latex-ms2.tex
 
@@
 A pair of prominent recent works took advantage of this latent variable approach to measure democratic support for over one hundred countries for up to nearly three decades and to then assess, respectively, its consequences for and roots in democratic change [@Claassen2020a; @Claassen2020b].
-These works concluded, first and supporting the classic argument, that mass support had a positive impact on democratic change, especially the endurance of democracy [@Claassen2020a, 127-130], and, second and directly contrary to it, democratic change has a thermostatic effect on public support, that is that, rather than generating their own support, deepening democracy provokes a backlash and it is instead democratic backsliding that calls forth greater public support [@Claassen2020b, 46-50].
+These works concluded, first and supporting the classic argument, that mass support had a positive impact on democratic change, especially the endurance of democracy [@Claassen2020a, 127-130], and, second and directly contrary to it, democratic change has a thermostatic effect on public support, that is that, rather than generating its own support, deepening democracy provokes a backlash and it is instead democratic backsliding that calls forth greater public support [@Claassen2020b, 46-50].
 
@@
 As latent variable measurement models become more commonly used, it is absolutely necessary for researchers employing them to incorporate the associated uncertainty into analyses.
-And, at a time when democracy as seen as under threat around the world [e.g., @Diamond2015], taken together, Claassen [-@Claassen2020a; -@Claassen2020b] send what is ultimately a reassuring message: the fate of democracy rests with us, the public, and when democratic institutions are undermined, we will swing to their support and constitute "an obstacle to democratic backsliding" [@Claassen2020b, 51].
+And, at a time when democracy is seen as under threat around the world [e.g., @Diamond2015], taken together, Claassen [-@Claassen2020a; -@Claassen2020b] send what is ultimately a reassuring message: the fate of democracy rests with us, the public, and when democratic institutions are undermined, we will swing to their support and constitute "an obstacle to democratic backsliding" [@Claassen2020b, 51].
 Both of these assertions may well be true, but the evidence we have, properly assessed, does not provide support for them.

### 2021-06-09 R/dcpo_ajps_apsr_uncertainty.R
code correction

@@ -190,7 +190,7 @@ save(lib_list, file = here::here("data","lib_list.rda"))
 
 ############create cpi_post and Cpi_list
 cpi_95_19_update <- readRDS(here("data","cpi95_19_update.rds"))
-cpi_2012error <- read_excel(here("data","CPI2019.xlsx", sheet ="CPI Timeseries 2012 - 2019"))
+cpi_2012error <- read_xlsx(here("data","CPI2019.xlsx"), sheet ="CPI Timeseries 2012 - 2019")
 
 cpi_2012error_clean <- cpi_2012error %>%
   row_to_names(row_number = 2) %>%

### 2021-06-09 paper/dcpo_demsupport_appendix.Rmd
cls uncertain

@@
   plm,
+  glue,
   huxtable, kableExtra, modelsummary, # tabulation
@@
 set.seed(313)
+
+parse_na_types <- function(s) {
+
+    positions <- purrr::map(
+        stringr::str_split(s, pattern = ""), 
+        match,
+        table = names(na_types_dict)
+    ) %>%
+        unlist()
+
+    na_types_dict[positions] %>%
+        unlist() %>%
+        unname()
+}
+
+na_types_dict <- list("r" = NA_real_,
+                      "i" = rlang::na_int,
+                      "c" = NA_character_,
+                      "l" = rlang::na_lgl)
+
+as_glance_tibble <- function(..., na_types) {
+
+    cols <- list(...)
+
+    if (length(cols) != stringr::str_length(na_types)) {
+        stop(
+            "The number of columns provided does not match the number of ",
+            "column types provided."
+        )
+    }
+
+    na_types_long <- parse_na_types(na_types)
+
+    entries <- purrr::map2(cols, 
+                           na_types_long, 
+                           function(.x, .y) {if (length(.x) == 0) .y else .x})
+
+    tibble::as_tibble_row(entries)
+
+}
+
+tidy.pgmm <- function(x,
+                      conf.int = FALSE,
+                      conf.level = 0.95,
+                      ...) {
+    result <- summary(x)$coefficients %>%
+        tibble::as_tibble(rownames = "term") %>%
+        dplyr::rename(
+            estimate = Estimate,
+            std.error = `Std. Error`,
+            statistic = `z-value`,
+            p.value = `Pr(>|z|)`
+        )
+
+    if (conf.int) {
+        ci <- confint(x, level = conf.level) %>% 
+            as.data.frame() %>% 
+            rownames_to_column(var = "term") %>% 
+            dplyr::rename(
+                conf.low = `2.5 %`,
+                conf.high = `97.5 %`
+            )
+        result <- dplyr::left_join(result, ci, by = "term")
+    }
+
+    result
+}
+
+glance.pgmm <- function(x, ...) {
+    s <- summary(x)
+    as_glance_tibble(
+        nobs = stats::nobs(x),
+        n.country = pdim(x)$nT$n,
+        na_types = "ii"
+    )
+}
+
+glance.plm <- function(x, ...) {
+    s <- summary(x)
+    as_glance_tibble(
+        nobs = stats::nobs(x),
+        n.country = pdim(x)$nT$n,
+        na_types = "ii"
+    )
+}
+
 ```
 
-## Numeric Results of the Visualized Results
+## Claassen Replication Input
 
-```{r claassen_input_APSR}
-dcpo_input_raw1 <- read_csv("../data/dcpo_input_raw.csv", col_types = "cdcddcd") %>% 
+```{r claassen_replication_input, eval=FALSE}
+dcpo_input_raw1 <- read_csv(here::here("data", "dcpo_input_raw.csv"), col_types = "cdcddcd") %>% 
   filter(!(str_detect(survey, "army_wvs") & # WVS obs identified as problematic by Claassen 
@@
 
-claassen_input <- DCPOtools::format_claassen(dcpo_input_raw1)
-save(claassen_input, file = here::here("data", "claassen_input.rda"))
-```
-
-```{r claassen_input_AJPS}
-claassen_input_raw1 <- read_csv("../data/dcpo_input_raw.csv", col_types = "cdcddcd") %>% 
-  filter(!(str_detect(survey, "army_wvs") & # WVS obs identified as problematic by Claassen 
-             ((country=="Albania" & year==1998) |
-                (country=="Indonesia" & (year==2001 | year==2006)) |
-                (country=="Iran" & year==2000) |
-                (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
-                (country=="Vietnam" & year==2001)) |
-             (str_detect(item, "strong_wvs") &
-                ((country=="Egypt" & year==2012) |
-                   (country=="Iran" & (year==2000 | year==2007)) | # 2005 in Claassen
-                   (country=="India") |
-                   (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
-                   (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
-                   (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
-                   (country=="Vietnam" & year==2001))) |
-             (country %in% c("Puerto Rico", "Northern Ireland", 
-                             "SrpSka Republic", "Hong Kong SAR China")))) %>%
-  with_min_yrs(2)
-
-claassen_input <- DCPOtools::format_claassen(claassen_input_raw1)
-save(claassen_input, file = here::here("data", "claassen_input.rda"))
-
-```
-
-```{r claassen_replication_input}
 # Note that before running `dataverse::get_file()` below, one should set their personal token and server in their system environment first: 
@@
 
-supdem <- dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>% 
-  read_csv(col_types = "cdcddcdc")
+if (!file.exists(here::here("data", "supdem raw survey marginals.tab"))) {
+  tempfile <- dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") # AJPS replication file
+
+  writeBin(tempfile, here::here("data", "supdem raw survey marginals.tab"))
+}
+
+supdem <- read_csv(here::here("data", "supdem raw survey marginals.tab"), col_types = "cdcddcdc")
 
@@
 
-claassen_input_cy <- read_csv("../data/dcpo_input_raw.csv",
-                              col_types = "cdcddcd") %>%           # 1813 obs
+claassen_input_cy <- read_csv(here::here("data", "dcpo_input_raw.csv"),
+                              col_types = "cdcddcd") %>%           # 1861 obs
   mutate(p_dcpo = str_extract(survey, "^[a-z]+"), 
@@
 
-available <- anti_join(claassen_input_cy, supdem_cy)                # 516 obs
+available <- anti_join(claassen_input_cy, supdem_cy)                # 564 obs
 
@@
 
-cys_to_drop <- anti_join(available, year_fixes, by = c("country", "year" = "year.y", "project")) %>% # 427 obs
+cys_to_drop <- anti_join(available, year_fixes, by = c("country", "year" = "year.y", "project")) %>% # 475 obs
   select(-y_dcpo)
 
-claassen_replication_input_raw1 <- read_csv("../data/claassen_input_raw.csv", col_types = "cdcddcd") %>% 
+claassen_replication_input_raw1 <- read_csv(here::here("data", "claassen_input_raw.csv"), col_types = "cdcddcd") %>% 
   filter(!(str_detect(item, "army_wvs") & # WVS obs identified as problematic by Claassen 
@@
 
-claassen_replication_input <- DCPOtools::format_claassen(claassen_input_raw1)
+claassen_replication_input <- DCPOtools::format_claassen(claassen_replication_input_raw1)
 save(claassen_replication_input, file = here::here("data", "claassen_replication_input.rda"))
-
-dcpo_replication_input <- DCPOtools::format_dcpo(claassen_input_raw1,
-                                                 scale_q = "church_lb",
-                                                 scale_cp = 2)
-save(dcpo_replication_input, file = here::here("data", "dcpo_replication_input.rda"))
 ```
@@
 ```{r claassen_m5, eval=FALSE}
+load(here::here("data", "claassen_replication_input.rda"))
+
 claassen_m5 <- rstan::stan(file = 'R/argon/dcpo_demsupport/R/supdem.stan.mod5.stan',
-                           data = claassen_input,
+                           data = claassen_replication_input,
                            iter = 3000,
@@
 
-save(claassen_m5, file = "data/claassen_m5.rda")
+save(claassen_m5, file = load(here::here("data", "claassen_m5.rda")))
+```
+
+```{r claassen_m5_theta}
+load(here::here("data", "claassen_m5.rda"))
 
@@
 
-save(claassen_input, claassen_m5_x_pred, file = "data/claassen_m5_x_pred.rda")
-```
-
-```{r comparison_table}
-load(here::here("data", "claassen_m5_x_pred.rda"))
-
-ivt_claassen <- DCPOtools::internal_validation_tests(claassen_input, claassen_m5_x_pred, "claassen")
-
-load(here::here("data", "dcpo_replication_y_r_pred.rda"))
-
-ivt_dcpo <- DCPOtools::internal_validation_tests(dcpo_replication_input, dcpo_replication_y_r_pred)
-# see https://github.com/fsolt/dcpo_article/blob/master/R/validation_table.R for more to add when we have it
-
+save(claassen_replication_input, claassen_m5_x_pred, file = "data/claassen_m5_x_pred.rda")
 ```
@@
 ```{r claassenUncertainty, cache=TRUE}
-load(here::here("data", "claassen_replication_input.rda"))
-load(here::here("data", "claassen_m5_theta.rda"))
+load(here::here("data", "claassen_m5_3k_07-05-11-16.rda")) # ours
+
+claassen_m5_theta <- rstan::extract(claassen_m5, pars = "theta")
 
 ls_year <- 1988:2017
-ls_country <- claassen_replication_input$data$country %>% unique()
+ls_country <- claassen_input$data$country %>% unique()
 
@@
 
-first_year <- min(claassen_replication_input$data$year)
+first_year <- min(claassen_input$data$year)
 
-df_controls <- read_csv(here::here("data", "control_variables_ajps.csv"),
+first_years <- claassen_input$data %>% 
+  group_by(country) %>% 
+  summarize(first_year = min(year))
+
+sd_controls <- read_csv(here::here("data", "Support_democracy_ajps.csv"),
                         col_types = cols(.default = col_double(),
-                                         country = col_character(),
-                                         country_name = col_character(),
-                                         ISO = col_character(),
+                                         Country = col_character(),
+                                         Cnt_code = col_character(),
+                                         ISO_code = col_character(),
                                          Region_UN = col_character())) %>% 
-  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
-         country = countrycode::countrycode(country0, "country.name", "country.name"),
-         regime = Vdem_regime > 1) %>% 
-  filter(year >= firstyear) # using trimmed data as Claassen
+  mutate(country = countrycode::countrycode(as.character(Country), "country.name", "country.name"),
+         year = as.numeric(as.character(Year)),
+         regime = ifelse(Regime_VD > 1, 1, 0)) %>% 
+  left_join(first_years, by = "country") %>% 
+  filter(year >= first_year)
+
+claassen_m5_theta_std = (claassen_m5_theta[[1]] - mean(as.vector(claassen_m5_theta[[1]]))) / sd(as.vector(claassen_m5_theta[[1]]))
 
 df_theta <- purrr::map(1:1000, function(x) {
-  claassen_m5_theta$theta[x,,] %>% 
+  claassen_m5_theta_std[x,,] %>% 
     as_tibble() %>% 
@@
     arrange(country, year) %>% 
-    left_join(df_controls, by = c("country", "year")) %>% 
+    left_join(sd_controls, by = c("country", "year")) %>% 
     plm::pdata.frame(index = c("country", "year"))
@@
 
-result_m5_1k <- map(df_theta, function(aDataset) {
-  plm(Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + plm::lag(theta, 1) + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1), model="pooling", data = aDataset)
+df_theta_mean <- purrr::map_df(1:1000, function(x) {
+  claassen_m5_theta_std[x,,] %>% 
+    as_tibble() %>% 
+    rename_with(~ls_country, .cols = starts_with("V")) %>% 
+    mutate(year = first_year + row_number() - 1) %>% 
+    pivot_longer(cols = !year,
+                 names_to = "country",
+                 values_to = "theta") %>%
+    arrange(country, year)
+}) %>% 
+  group_by(country, year) %>% 
+  summarize(theta_mean = mean(theta)) %>% 
+  right_join(sd_controls, by = c("country", "year")) %>% 
+  plm::pdata.frame(index = c("country", "year"))
+
+df_theta_mean %>% summarize(corr = cor(theta_mean, SupDem_trim))
+
+corrs <- df_theta_mean %>%
+    group_by(country) %>% 
+    summarize(corr = cor(theta_mean, SupDem_trim))
+
+ls_iv <- c("plm::lag(theta_mean, 1)",
+           "plm::lag(SupDem_trim, 1)")
+           #"plm::lag(SupDem_Democ, 1) + plm::lag(SupDem_Autoc, 1)")
+
+ls_method <- c("plm", "pgmm")
+
+ls_eq <- glue::glue("Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + {ls_iv} + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)")
+
+ls_mod <- c(
+  glue::glue("plm({ls_eq}, model = 'pooling', data = df_theta_mean)")# ,
+  # glue(
+  #   "pgmm({ls_eq} | plm::lag(Libdem_VD, 3:5), data = df_theta_mean, effect='individual', model='onestep', transformation='ld', indexes=c('Country', 'Year'))"
+  # )
+)
+
+df_result_cls <- map(ls_mod, function(mod) {
+  result <- eval(parse(text = mod))
 })
 
-result_betas_m5_1k <- mitools::MIextract(result_m5N_1k, fun = coef)
-result_vars_m5_1k <- mitools::MIextract(result_m5N_1k, fun = vcovBK_se)
+tidy_cls <- map(df_result_cls, function(result) {
+  df_result <- tidy(result, conf.int = TRUE)
 
-df_result_cls <- summary(mitools::MIcombine(results = result_betas_m5_1k, variance = result_vars_m5_1k))%>% rownames_to_column(var = "term") %>% 
-  rename(conf.low = `(lower`,
-         conf.high = `upper)`, 
-         estimate = results) %>% 
+  if (class(result)[[1]] == "plm") {
+     mutate(df_result, std.error = vcovBK_se(result))
+  } else{
+    mutate(df_result, std.error = vcovHC_se(result))
+  }
+
+})
+
+glance_cls <- map(df_result_cls, function(aResult) {
+  if (class(aResult)[[1]] == "plm") { 
+    glance.plm(aResult) # using the customized glance function
+  } else {
+    glance(aResult)
+  }
+})
+
+result_cls <- map2(tidy_cls, glance_cls, ~ list(.x, .y))
+#names(result_cls) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
+
+map_df(1:2, function(a) {
+  result_cls[[a]][[1]] %>% 
+    mutate(model = if_else(a==1, "Ours", "Claassen's"),
+           term = str_replace(term, "SupDem_trim", "theta_mean")) %>% 
     filter(!str_detect(term, "(Intercept)"))
-```
-
-```{r dcpoVisualization, fig.cap= "Replication of Model 5 in Claassen's AJPS 2019"}
-
-(dwplot(df_result_cls, by_2sd = FALSE)) %>% 
-  relabel_predictors(c(`plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
-`plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
-`plm::lag(theta, 1)` = "Democratic Mood(t-1)",
-`plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
-`plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
-`plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
-`plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)", #there's a lag in the replication file
-`plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)")) +
+}) %>% 
+  dotwhisker::dwplot() %>% 
+  relabel_predictors(c(`plm::lag(Libdem_VD, 1:2)1` = "Democracy(t-1)",
+                       `plm::lag(Libdem_VD, 1:2)2` = "Democracy(t-2)",
+                       `plm::lag(theta_mean, 1)` = "Democratic Mood(t-1)",
+                       `plm::lag(lnGDP_imp, 1)` = "Log GDP per capita(t-1)",
+                       `plm::lag(GDP_imp_grth, 1)` = "GDP per capita Growth(t-1)",
+                       `plm::lag(Libdem_regUN, 1)` = "Regional Democracy(t-1)",
+                       `plm::lag(Pr_Muslim, 1)` = "Percent Muslim (t-1)", #there's a lag in the replication file
+                       `plm::lag(Res_cp_WDI_di, 1)` = "Resource Dependence(t-1)")) +
   geom_vline(xintercept = 0, colour = "grey80", linetype = 2) +
@@
   xlab("Coefficient Estimate") +
-  theme(axis.title.y = element_blank(),
-        legend.position = "none")
+  scale_color_discrete(name="Dataset")
 
+ggsave("paper/ours_vs_claassens_mean.pdf")
+
+result_m5_1k <- map(df_theta, function(aDataset) {
+  plm(Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + plm::lag(theta, 1) + plm::lag(lnGDP_imp, 1) +
+        plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) +
+        plm::lag(Res_cp_WDI_di, 1), model="pooling", data = aDataset)
+})
+
+result_betas_m5_1k <- mitools::MIextract(result_m5_1k, fun = coef)
+result_vars_m5_1k <- mitools::MIextract(result_m5_1k, fun = vcovBK_se)
+
+load(here::here("data", "pure_claassen_1k_result.rda"))
+
+df_result_cls_1k <- summary(mitools::MIcombine(results = result_betas_m5_1k, 
+                                               variance = result_vars_m5_1k)) %>%
+  rownames_to_column(var = "term") %>% 
+  rename(conf.low = `(lower`,
+         conf.high = `upper)`, 
+         estimate = results) %>% 
+  filter(!str_detect(term, "(Intercept)")) %>% 
+  mutate(model = "Ours")
+
+bind_rows(df_result_cls_1k, mod.1_df_result_cls_1k) %>% 
+  dotwhisker::dwplot() %>% 
+  relabel_predictors(c(`plm::lag(Libdem_VD, 1:2)1` = "Democracy(t-1)",
+                       `plm::lag(Libdem_VD, 1:2)2` = "Democracy(t-2)",
+                       `plm::lag(theta, 1)` = "Democratic Mood(t-1)",
+                       `plm::lag(lnGDP_imp, 1)` = "Log GDP per capita(t-1)",
+                       `plm::lag(GDP_imp_grth, 1)` = "GDP per capita Growth(t-1)",
+                       `plm::lag(Libdem_regUN, 1)` = "Regional Democracy(t-1)",
+                       `plm::lag(Pr_Muslim, 1)` = "Percent Muslim (t-1)", #there's a lag in the replication file
+                       `plm::lag(Res_cp_WDI_di, 1)` = "Resource Dependence(t-1)")) +
+  geom_vline(xintercept = 0, colour = "grey80", linetype = 2) +
+  theme_minimal() +
+  ggtitle("Dependent Variable: Level of Democracy") + 
+  xlab("Coefficient Estimate") +
+  scale_color_discrete(name="1k Samples\nDataset", breaks=c("Claassen's","Ours"))
+
+ggsave("paper/ours_vs_claassens_1k.pdf")
 ```

### 2021-06-09 paper/dcpo_demsupport.Rmd
plot code revised

--- 2021-06-06 paper/dcpo_demsupport.Rmd
@@
 supdem <- read.csv(here("data", "Support_democracy_ajps.csv"))
-v_dem <- read.csv(here("data", "vdem15.csv"))    ######????????? why we need this one? for graph?  in the following analysis, we never use v_dem
 sd.plm <- pdata.frame(supdem, index = c("Country", "Year"))
@@
 
-```{r cls-uncertainAJPSfull, eval=FALSE}
+```{r cls-uncertainAJPSfull}
 result_clsUncertainFull <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
@@
 
-```{r dcpo-uncertainAJPSfull, eval=FALSE}
+```{r dcpo-uncertainAJPSfull}
 result_dcpoUncertainFull <- map(ls_mod_ajpsDCPO, function(aMod){ # reading a model
@@
 
-```{r plot-mainAJPS, fig.cap= "The Effect of Public Support on Democracy with Uncertainty", eval=FALSE}
-
-df_plot <- df_result_dcpoMeanAJPS[[1]] %>% 
-  mutate(model = "DCPO\n (Point Estimates)")
-
-df_plot <- df_result_dcpoAJPS[[1]] %>%
-  mutate(model = "DCPO\n (w. Uncertainty)") %>%
-  rename(std.error = se) %>%
-  bind_rows(df_plot)
-
-plot_pooled <- filter(df_plot, model != "Claassen 2019") %>% 
-  dwplot(by_2sd = FALSE) %>%
-  relabel_predictors(
-    c(
-      `plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
-      `plm::lag(Libdem_VD, 1:2)1` = "Democracy(t-1)",
-      `plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
-      `plm::lag(Libdem_VD, 1:2)2` = "Democracy(t-2)",
-      `plm::lag(theta, 1)` = "Democratic Mood(t-1)",
-      `plm::lag(SupDem_trim, 1)` = "Democratic Mood(t-1)",
-      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t-1)",
-      `plm::lag(lnGDP_imp, 1)` = "Log GDP per capita(t-1)",
-      `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t-1)",
-      `plm::lag(GDP_imp_grth, 1)` = "GDP per capita Growth(t-1)",
-      `plm::lag(Region_libdem, 1)` = "Regional democracy(t-1)",
-      `plm::lag(Libdem_regUN, 1)` = "Regional democracy(t-1)",
-      `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
-      `plm::lag(Pr_Muslim, 1)` = "Percent Muslim (t-1)",
-      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t-1)",
-      `plm::lag(Res_cp_WDI_di, 1)` = "Resource Dependence(t-1)"
-    )
-  ) +
+```{r coefName-AJPS, eval=TRUE}
+index_coefName <- c(
+  `plm::lag(Libdem_VD, 1:2)1` = "Democracy[t-1]",
+  `plm::lag(Libdem_VD, 1:2)2` = "Democracy[t-2]",
+  `plm::lag(Vdem_libdem, 1:2)1` = "Democracy[t-1]",
+  `plm::lag(Vdem_libdem, 1:2)2` = "Democracy[t-2]",
+  `plm::lag(SupDem_trim, 1)` = "Support[t-1]",
+  `plm::lag(theta_trim, 1)` = "Support[t-1]",
+  `plm::lag(SupDem_Democ, 1)` = "Support[t-1](demo~only)",
+  `plm::lag(SupDem_Autoc, 1)` = "Support[t-1](auto~only)",
+  `plm::lag(theta_dem_trim, 1)` = "Support[t-1](demo~only)",
+  `plm::lag(theta_aut_trim, 1)` = "Support[t-1](auto~only)",
+  `plm::lag(lnGDP_imp, 1)` = "Log~GDP~per~capita[t-1]",
+  `plm::lag(lg_imp_mdpgdp, 1)` = "Log~GDP~per~capita[t-1]",
+  `plm::lag(GDP_imp_grth, 1)` = "GDP~per~capita~growth[t-1]",
+  `plm::lag(mdprgdp_grwth, 1)` = "GDP~per~capita~growth[t-1]",
+  `plm::lag(Libdem_regUN, 1)` = "Regional~democracy[t-1]",
+  `plm::lag(Region_libdem, 1)` = "Regional~democracy[t-1]",
+  `plm::lag(Pr_Muslim, 1)` = "Percent~Muslim[t-1]",
+  `plm::lag(muslism_prop_2010, 1)` = "Percent~Muslim[t-1]",
+  `plm::lag(Res_cp_WDI_di, 1)` = "Resource~dependence[t-1]",
+  `plm::lag(dependence_pc_di, 1)` = "Resource~dependence[t-1]"
+)
+```
+
+```{r plot-mainAJPS, fig.cap= "The Effect of Public Support on Democracy with Uncertainty", fig.width=7, fig.height=10, fig.align='center', eval=TRUE}
+
+result_cls <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
+result_clsUncertainFull <- readRDS(here("output", "estimates_clsAJPSfullUncertain.RDS"))
+result_dcpoUncertainFull <- readRDS(here("output", "estimates_dcpoAJPSfullUncertain.RDS"))
+
+type_model <-
+  c("Claassen 2019", "Claassen Uncertainty", "DCPO Uncertainty")
+
+result_ajpsPooled <-
+  list(result_cls,
+       result_clsUncertainFull,
+       result_dcpoUncertainFull) %>%
+  map2_df(type_model, ~ {
+    .x$pooled[[1]] %>%
+      filter(term != "(Intercept)") %>%
+      select(term, estimate, conf.low, conf.high) %>%
+      mutate(model = .y)
+  }) %>% 
+  mutate(type = "Pooled")
+
+result_ajpsRegime <-
+  list(result_cls,
+       result_clsUncertainFull,
+       result_dcpoUncertainFull) %>%
+  map2_df(type_model, ~ {
+    .x$`pooled-regime`[[1]] %>%
+      filter(term != "(Intercept)") %>%
+      select(term, estimate, conf.low, conf.high) %>%
+      mutate(model = .y)
+  }) %>% 
+  mutate(type = "Regime Specified")
+
+df_plot <- bind_rows(result_ajpsPooled, result_ajpsRegime) %>% 
+    mutate(term = index_coefName[term],
+           term = factor(term, levels = unique(index_coefName)))
+
+dwplot(df_plot) +
     geom_vline(xintercept = 0,
@@
         legend.title = element_blank()
-  )
-
-df_plot <- df_result_dcpoMeanAJPS[[2]] %>% 
-  mutate(model = "DCPO\n (Point Estimates)")
-
-df_plot <- df_result_dcpoAJPS[[2]] %>%
-  mutate(model = "DCPO\n (w. Uncertainty)") %>%
-  rename(std.error = se) %>%
-  bind_rows(df_plot)
-
-plot_pooled2 <- filter(df_plot, model != "Claassen 2019") %>% 
-  dwplot(by_2sd = FALSE) %>%
-  relabel_predictors(
-    c(
-      `plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
-      `plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
-      `plm::lag(theta_dem, 1)` = "Mood Democracy(t-1)",
-      `plm::lag(theta_aut, 1)` = "Mood Autocracy(t-1)",
-      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t-1)",
-      `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t-1)",
-      `plm::lag(Region_libdem, 1)` = "Regional democracy(t-1)",
-      `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
-      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t-1)"
-    )
     ) +
-  geom_vline(xintercept = 0,
-             colour = "grey80",
-             linetype = 2) +
-  theme_minimal() +
-  ggtitle("DV: Liberal Democracy (Vdem)") +
-  xlab("Coefficient Estimate") +
-  theme(
-    axis.title.y = element_blank(),
-    legend.position = "bottom",
-    legend.title = element_blank()
-  )
-
-gridExtra::grid.arrange(plot_pooled,plot_pooled2, ncol = 2)
+    scale_y_discrete(labels = parse(text = rev(levels(df_plot$term)))) +
+    # Using expressions of underscore and greek letters
+    scale_color_gb(palette = "digitMixed") +
+    facet_wrap(~ type)
+
 ```
@@
 
-saveRDS(result_clsAPSR, file = here::here("output", "estimates_clsMeanAPSR.RDS"))
+saveRDS(result_clsAPSR, file = here("output", "estimates_clsMeanAPSR.RDS"))
 ```
@@
 
-```{r cls-uncertainAPSRfull, eval=FALSE}
+```{r cls-uncertainAPSRfull}
 result_clsFullUncertainAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
@@
 
-saveRDS(result_clsFullUncertainAPSR, file = here::here("output", "estimates_clsFullUncertainAPSR.RDS"))
+saveRDS(result_clsFullUncertainAPSR, file = here("output", "estimates_clsFullUncertainAPSR.RDS"))
 ```
@@
 
-```{r dcpo-uncertainAPSRfull, eval=FALSE}
+```{r dcpo-uncertainAPSRfull}
 result_dcpoUncertainAPSR <- map(ls_mod_apsrDCPO, function(aMod){ # reading a model
@@
 
-saveRDS(result_dcpoUncertainAPSR, file = here::here("output", "estimates_dcpoUncertainAPSR.RDS"))
+saveRDS(result_dcpoUncertainAPSR, file = here("output", "estimates_dcpoUncertainAPSR.RDS"))
 ```
@@
 
-```{r plot-mainAPSR, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10, eval=FALSE}
+```{r coefName-APSR, eval=TRUE}
+index_coefName <- c(
+    `plm::lag(SupDem_trim, 1:2)1` = "Support[t-1]",
+    `plm::lag(SupDem_trim, 1:2)2` = "Support[t-2]",
+    `plm::lag(theta_trim, 1:2)1` = "Support[t-1]",
+    `plm::lag(theta_trim, 1:2)2` = "Support[t-2]",
+    `diff(Liberal_z, lag = 1)` = "Delta~Support(demo~only)",
+    `diff(Vdem_liberal_z, lag = 1)` = "Delta~Support(demo~only)",
+    `plm::lag(Liberal_z, 1)` = "Support[t-1](demo~only)",
+    `plm::lag(Vdem_liberal_z, 1)` = "Support[t-1](demo~only)",
+    `diff(Polyarchy_z, lag = 1)` = "Delta~Support(auto~only)",
+    `diff(Vdem_polyarchy_z, lag = 1)` = "Delta~Support(auto~only)",
+    `plm::lag(Polyarchy_z, 1)` = "Support[t-1](auto~only)",
+    `plm::lag(Vdem_polyarchy_z, 1)` = "Support[t-1](auto~only)",
+    `diff(Libdem_z, lag = 1)` = "Delta~Liberal~democracy",
+    `diff(Vdem_libdem_z, lag = 1)` = "Delta~Liberal~democracy",
+    `plm::lag(Libdem_z, 1)` = "Liberal~democracy[t-1]",
+    `plm::lag(Vdem_libdem_z, 1)` = "Liberal~democracy[t-1]",
+    `diff(lnGDP_imp, lag = 1)` = "Delta~Log~GDP~per~capita",
+    `diff(lg_imp_mdpgdp, lag = 1)` = "Delta~Log~GDP~per~capita",
+    `plm::lag(lnGDP_imp, 1)` = "Log~GDP[t-1]",
+    `plm::lag(lg_imp_mdpgdp, 1)` = "Log~GDP[t-1]"
+)
+```
+
+```{r plot-mainAPSR, fig.cap= "The Effect of Democracy on Public Support", fig.width=7, fig.height=10, eval = TRUE}
+result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
+result_clsFullUncertainAPSR <- readRDS(here("output", "estimates_clsFullUncertainAPSR.RDS"))
+result_dcpoUncertainAPSR <- readRDS(here("output", "estimates_dcpoUncertainAPSR.RDS"))
+
+type_model <-
+  c("Claassen 2020", "Claassen Uncertainty", "DCPO Uncertainty")
+
+result_apsrPooled <-
+  list(result_clsAPSR,
+       result_clsFullUncertainAPSR,
+       result_dcpoUncertainAPSR) %>%
+  map2_df(type_model, ~ {
+    .x$pooled1[[1]] %>%
+      filter(term != "(Intercept)") %>%
+      select(term, estimate, conf.low, conf.high) %>%
+      mutate(model = .y)
+  }) %>% 
+  mutate(type = "Pooled")
+
+result_apsrRegime <-
+  list(result_clsAPSR,
+       result_clsFullUncertainAPSR,
+       result_dcpoUncertainAPSR) %>%
+  map2_df(type_model, ~ {
+    .x$`pooled-regime1`[[1]] %>%
+      filter(term != "(Intercept)") %>%
+      select(term, estimate, conf.low, conf.high) %>%
+      mutate(model = .y)
+  }) %>% 
+  mutate(type = "Regime Specified")
+
+df_plot <- bind_rows(result_apsrPooled, result_apsrRegime) %>% 
+    mutate(term = index_coefName[term],
+           term = factor(term, levels = unique(index_coefName)))
+
+dwplot(df_plot) +
+    geom_vline(xintercept = 0,
+               colour = "grey80",
+               linetype = 2) +
+    theme_minimal() +
+    ggtitle("DV: Public Support for Democracy") +
+    xlab("Coefficient Estimate") +
+    theme(
+        axis.title.y = element_blank(),
+        legend.position = "bottom",
+        legend.title = element_blank()
+    ) +
+    scale_y_discrete(labels = parse(text = rev(levels(df_plot$term)))) +
+    # Using expressions of underscore and greek letters
+    scale_color_gb(palette = "digitMixed") +
+    facet_wrap( ~ type)
+
+```
+
+# Discussion
+In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support has a positive effect on democracy and democracy a negative effect on support are not empirically supported once measurement uncertainty is taken into account, even when a superior estimate of public support and more data are used.
+
+There are several potential methodological explanations for these null results.
+One issue is that the survey items employed---which ask respondents to assess the desirability or appropriateness of democracy, to compare democracy to some undemocratic alternative, or to assess one of these alternatives---may not capture every aspect of democratic support necessary for it to play its hypothesized roles in the classic theory.
+If only those who profess to prefer democracy to its alternatives _and also_ value freedom of expression, freedom of association, and pluralism of opinion will take appropriate action when democracy is threatened, then this measure is inadequate to its purpose [see, e.g., @Schedler2007].
+Moreover, given the multi-faceted nature of democratic attitudes, even the inclusion of such questions in unidimensional public opinion models such as those provided by @Claassen2019 or @Solt2020a are unlikely to be sufficient [see, e.g., @Wuttke2020].
+Another issue is that even if these survey questions do capture support for the generic concept of democracy, these measurement models might still be incapable of suitably capturing democratic support due to the variation in understanding the concept across countries or over time within countries [@Wuttke2021].
+Yet another is that this measure provides no assessment of the _relative_ importance the public affords democracy.
+It provides no information on the extent to which other values, such as policy preferences or partisanship, weigh more heavily---and there is growing evidence that, at least in the United States, there are many for whom these other considerations excuse substantial transgressions against democracy [see @bartels_ethnic_2020; @Carey2020; @graham_democracy_2020; @McCoy2020].
+
+There are theoretical explanations for the null results as well.
+With regard to how levels of democracy affect public support, we note that even the proponents of the classic argument did not contend that the mere existence of democratic institutions, no matter how consistently feckless and ineffective, would generate support among the public: instead, they maintained, public support would be gained through experience with government performance that was generally effective [@lipset_social_1959, 86-89; @Easton1965, 119-120].
+There is some empirical support for this, with government effectiveness positively related to public support among democracies and negatively related in non-democracies [@Magalhaes2014]. 
+The finding of @Krieckhaus2014 that income inequality is strongly negatively related to public support in democracies suggests that performance regarding redistribution is particularly important.
+Relatedly, on the reverse part of the classic argument, @Qi2011 suggests that democratic support alone cannot be expected to generate democratic change and oppose backsliding.
+Instead, that work contends, it is the combination of democratic support and dissatisfaction with current regime performance that generates demand for greater democracy.
+And we must be open to the possibility that no theoretical elaboration, no respecification of these models will reveal relationships between public opinion and democracy.
+Democratic backsliding may simply be primarily a matter of elite decisionmaking [see, e.g., @levitsky_how_2018].
+Regardless, these explanations indicate that there remains much work to be done in the empirical study of public support and democracy.
+
+# Conclusion
+In this letter, we reexamined the findings from Claassen [-@Claassen2020a; -@Claassen2020b], two articles that maintain that public support helps the survival of democracy and democratic development has a thermostatic effect on public support.
+We demonstrated the importance of incorporating measurement uncertainty in analyzing the relationship between public support and democracy.
+Taking uncertainty into account rendered both articles' conclusions without empirical support, even when we employed the more sophisticated DCPO measurement model and additional data.
+
+This points to the absolute necessity of incorporating measurement uncertainty into analyses that include latent variables.
+As the use of latent variables grows more common in political science, both researchers and readers should be aware that these variables' concomitant measurement uncertainty cannot be neglected.
+
+The null results reached in this letter could arise from several sources.
+We identified a number of potential shortcomings in the measurement of democratic support and ways in which the analysis models might be underspecified.
+All of these could and should be explored in future research, though there are also theoretically grounded reasons to suspect that the relationships are in fact negligible.
+In any event, the sanguine assessment that readers may draw from Claassen [-@Claassen2020a; -@Claassen2020b]---that the fate of democracies depend on public support, and when eroded, their publics will rally to them---is not supported by the current evidence.
+Those who would defend democracy have no grounds to be complacent.
+
+# References  {-}
+
+<div id = 'refs'></div>
+
+\pagebreak
+
+# Online Supplementary Materials {-}
+# (APPENDIX) Appendix {-}
+# Numeric Results for Replicating Claassen 2020a
+
+```{r num-cls2020a, results='asis'}
+tb_result_cls <- map(result_cls, ~ {
+  names(.) <- c("tidy", "glance")
+  class(.) <- "modelsummary_list"
+  return(.)})
+
+names(tb_result_cls) <- c("Pooled", "Pooled-Regime", 
+                          "GMM", "GMM-Regime")
+
+names_coef <- c(
+  "(Intercept)" = "(Intercept)",
+  "plm::lag(Libdem_VD, 1:2)1" = "Democracy[t-1]",
+  "plm::lag(Libdem_VD, 1:2)2"  = "Democracy[t-2]",
+  "plm::lag(SupDem_trim, 1)" = "Support[t-1]",
+  "plm::lag(SupDem_Democ, 1)" = "Support in Democracy",
+  "plm::lag(SupDem_Autoc, 1)" = "Support in Autocracy",
+  "plm::lag(lnGDP_imp, 1)" = "Log~GDP~per~capita[t-1]",
+  "plm::lag(GDP_imp_grth, 1)"  = "GDP~per~capita~growth[t-1]",
+  "plm::lag(Libdem_regUN, 1)" = "Regional~democracy[t-1]",
+  "plm::lag(Pr_Muslim, 1)" = "Percent~Muslim[t-1]",
+  "plm::lag(Res_cp_WDI_di, 1)" = "Resource~dependence[t-1]"
+)
+
+modelsummary(tb_result_cls,  
+             statistic = "conf.int",
+             coef_map = names_coef, 
+             output = "latex", 
+             title = "Original") %>%
+
+  kableExtra::kable_styling(font_size = 8) %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+```{r num-cls2020aUncertain, results='asis'}
+tb_result_clsUncertain <- map(result_clsUncertain, ~ {
+  names(.) <- c("tidy", "glance")
+  class(.) <- "modelsummary_list"
+  return(.)})
+
+names(tb_result_cls) <- c("Pooled", "Pooled-Regime", 
+                          "GMM", "GMM-Regime")
+
+names_coef <- c(
+  "plm::lag(Libdem_VD, 1:2)1" = "Democracy[t-1]",
+  "plm::lag(Libdem_VD, 1:2)2"  = "Democracy[t-2]",
+  "plm::lag(theta, 1)" = "Support[t-1]",
+  "plm::lag(theta_dem, 1)" = "Support in Democracy",
+  "plm::lag(theta_aut, 1)" = "Support in Autocracy",
+  "plm::lag(lnGDP_imp, 1)" = "Log~GDP~per~capita[t-1]",
+  "plm::lag(GDP_imp_grth, 1)"  = "GDP~per~capita~growth[t-1]",
+  "plm::lag(Libdem_regUN, 1)" = "Regional~democracy[t-1]",
+  "plm::lag(Pr_Muslim, 1)" = "Percent~Muslim[t-1]",
+  "plm::lag(Res_cp_WDI_di, 1)" = "Resource~dependence[t-1]"
+)
+
+modelsummary(tb_result_clsUncertain, 
+             statistic = "conf.int",
+             coef_map = names_coef, 
+             output = "latex", 
+             title = "W. Uncertainty") %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+```{r num-cls2020aDCPO, results='asis'}
+tb_result_DCPO <- map(result_dcpoUncertain, ~ {
+  names(.) <- c("tidy", "glance")
+  class(.) <- "modelsummary_list"
+  return(.)})
+
+names(tb_result_DCPO) <- c("Pooled", "Pooled-Regime", 
+                          "GMM", "GMM-Regime")
+
+names_coef <- c(
+  "plm::lag(Vdem_libdem, 1:2)1" = "Democracy[t-1]",
+  "plm::lag(Vdem_libdem, 1:2)2"  = "Democracy[t-2]",
+  "plm::lag(theta, 1)" = "Support[t-1]",
+  "plm::lag(theta_dem, 1)" = "Support in Democracy",
+  "plm::lag(theta_aut, 1)" = "Support in Autocracy",
+  "plm::lag(lg_imp_mdpgdp, 1)" = "Log~GDP~per~capita[t-1]",
+  "plm::lag(mdprgdp_grwth, 1)"  = "GDP~per~capita~growth[t-1]",
+  "plm::lag(Region_libdem, 1)" = "Regional~democracy[t-1]",
+  "plm::lag(muslism_prop_2010, 1)" = "Percent~Muslim[t-1]",
+  "plm::lag(dependence_pc_di, 1)" = "Resource~dependence[t-1]"
+)
+
+modelsummary(tb_result_DCPO, 
+             statistic = "conf.int",
+             coef_map = names_coef, 
+             output = "latex", 
+             title = "W. Uncertainty") %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+\blandscape
+
+# Numeric Results for Replicating Claassen 2020b
+
+```{r num-cls2020b, results='asis'}
+tb_result_clsAPSR <- map(result_clsAPSR, ~ {
+  names(.) <- c("tidy", "glance")
+  class(.) <- "modelsummary_list"
+  return(.)}) %>% 
+  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
+      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]
+
+names(tb_result_clsAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
+
+names_coef <- c(
+  "(Intercept)" = "(Intercept)",
+  "plm::lag(SupDem_trim, 1:2)1" = "Democratic\n Mood\n (t-1)",
+  "plm::lag(SupDem_trim, 1:2)2" = "Democratic\n Mood\n (t-2)",
+  "diff(Libdem_z, lag = 1)" = "Liberal\n Democracy\n (Difference)",
+  "Libdem_z" = "Liberal\n Democracy\n (Difference)",
+  "plm::lag(Libdem_z, 1)" = "Liberal\n Democracy\n (t-1)",
+  "diff(Polyarchy_z, lag = 1)" = "Electoral\n Democracy\n (Difference)",
+  "Polyarchy_z" = "Electoral\n Democracy\n (Difference)",
+  "plm::lag(Polyarchy_z, 1)" = "Electoral\n Democracy\n (t-1)",
+  "diff(Liberal_z, lag = 1)" = "Minoritarian\n Democracy\n (Difference)",
+  "Liberal_z" = "Minoritarian\n Democracy\n (Difference)",
+  "plm::lag(Liberal_z, 1)" = "Minoritarian\n Democracy\n (t-1)",
+  "diff(lnGDP_imp, lag = 1)" = "Log GDP\n per capita\n (Difference)",
+  "lnGDP_imp" = "Log GDP\n per capita\n (Difference)",
+  "plm::lag(lnGDP_imp, 1)" = "Log GDP\n (t-1)",
+  "diff(Corrup_TI_z, lag = 1)" = "Corruption\n (Difference)",
+  "Corrup_TI_z" = "Corruption\n (Difference)",
+  "plm::lag(Corrup_TI_z, 1)" = "Corruption\n (t-1)"
+)
+
+modelsummary(tb_result_clsAPSR, 
+             stars = TRUE,
+             coef_map = names_coef, 
+             output = "latex") %>% 
+  kableExtra::kable_styling(font_size = 7) %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+\elandscape
+
+\blandscape
+
+```{r num-cls2020bUncertain, results='asis'}
+tb_result_clsUncertainAPSR <- map(result_clsUncertainAPSR, ~ {
+  names(.) <- c("tidy", "glance")
+  class(.) <- "modelsummary_list"
+  return(.)}) %>% 
+  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
+      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]
+
+names(tb_result_clsUncertainAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
+
+names_coef <- c(
+  "(Intercept)" = "(Intercept)",
+  "plm::lag(SupDem_trim, 1:2)1" = "Democratic\n Mood\n (t-1)",
+  "plm::lag(SupDem_trim, 1:2)2" = "Democratic\n Mood\n (t-2)",
+  "diff(Libdem_z, lag = 1)" = "Liberal\n Democracy\n (Difference)",
+  "Libdem_z" = "Liberal\n Democracy\n (Difference)",
+  "plm::lag(Libdem_z, 1)" = "Liberal\n Democracy\n (t-1)",
+  "diff(Polyarchy_z, lag = 1)" = "Electoral\n Democracy\n (Difference)",
+  "Polyarchy_z" = "Electoral\n Democracy\n (Difference)",
+  "plm::lag(Polyarchy_z, 1)" = "Electoral\n Democracy\n (t-1)",
+  "diff(Liberal_z, lag = 1)" = "Minoritarian\n Democracy\n (Difference)",
+  "Liberal_z" = "Minoritarian\n Democracy\n (Difference)",
+  "plm::lag(Liberal_z, 1)" = "Minoritarian\n Democracy\n (t-1)",
+  "diff(lnGDP_imp, lag = 1)" = "Log GDP\n per capita\n (Difference)",
+  "lnGDP_imp" = "Log GDP\n per capita\n (Difference)",
+  "plm::lag(lnGDP_imp, 1)" = "Log GDP\n (t-1)",
+  "diff(Corrup_TI_z, lag = 1)" = "Corruption\n (Difference)",
+  "Corrup_TI_z" = "Corruption\n (Difference)",
+  "plm::lag(Corrup_TI_z, 1)" = "Corruption\n (t-1)"
+)
+
+modelsummary(tb_result_clsUncertainAPSR, 
+             statistic = "conf.int",
+             coef_map = names_coef, 
+             output = "latex") %>% 
+  kableExtra::kable_styling(font_size = 7) %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+\elandscape
+
+\blandscape
+
+```{r num-cls2020bDCPO, results='asis'}
+tb_result_dcpoAPSR <- map(result_dcpoAPSR, ~ {
+  names(.) <- c("tidy", "glance")
+  class(.) <- "modelsummary_list"
+  return(.)}) %>% 
+  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
+      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]
+
+names(tb_result_dcpoAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
+
+names_coef <- c(
+  "(Intercept)" = "(Intercept)",
+  "plm::lag(theta, 1:2)1" = "Democratic\n Mood\n (t-1)",
+  "plm::lag(theta, 1:2)2" = "Democratic\n Mood\n (t-2)",
+
+  "diff(Vdem_libdem_z, lag = 1)" = "Liberal\n Democracy\n (Difference)",
+  "Vdem_libdem_z" = "Liberal\n Democracy\n (Difference)",
+  "plm::lag(Vdem_libdem_z, 1)" = "Liberal\n Democracy\n (t-1)",
+
+  "diff(Vdem_polyarchy_z, lag = 1)" = "Electoral\n Democracy\n (Difference)",
+  "Vdem_polyarchy_z" = "Electoral\n Democracy\n (Difference)",
+  "plm::lag(Vdem_polyarchy_z, 1)" = "Electoral\n Democracy\n (t-1)",
+  "diff(Vdem_liberal_z, lag = 1)" = "Minoritarian\n Democracy\n (Difference)",
+  "Vdem_liberal_z" = "Minoritarian\n Democracy\n (Difference)",
+  "plm::lag(Vdem_liberal_z, 1)" = "Minoritarian\n Democracy\n (t-1)",
+  "diff(lg_imp_mdpgdp, lag = 1)" = "Log GDP\n per capita\n (Difference)",
+  "lg_imp_mdpgdp" = "Log GDP\n per capita\n (Difference)",
+  "plm::lag(lg_imp_mdpgdp, 1)" = "Log GDP\n (t-1)",
+  "diff(corruption_z, lag = 1)" = "Corruption\n (Difference)",
+  "corruption_z" = "Corruption\n (Difference)",
+  "plm::lag(corruption_z, 1)" = "Corruption\n (t-1)"
+)
+
+modelsummary(tb_result_dcpoAPSR, 
+             statistic = "conf.int",
+             coef_map = names_coef, 
+             output = "latex") %>% 
+  kableExtra::kable_styling(font_size = 7) %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+\elandscape
+
+```{r datawitherrors}
+
+ls_country <- unique(claassen_replication$country)
+first_year <- min(claassen_replication$year)
+
+df_cls_errors <- purrr::map(1:900, function(anEntry) {
+  claassen_m5_theta$theta[anEntry,,] %>%
+    reformat_dcpo_output("theta")  %>%
+    mutate(iter = anEntry) 
+  }
+  )
+
+cls_theta_uncertainty <- bind_rows(df_cls_errors)
+saveRDS(cls_theta_uncertainty,"data/cls_theta_uncertainty.rds")
+
+ls_country <- levels(dcpo_input$data$kk)
+first_year <- min(dcpo_input$data$year)
+
+df_dcpo <- purrr::map_df(1:900, function(anEntry) {
+  dcpo_theta$theta[anEntry,,] %>%
+    reformat_dcpo_output("theta") %>%
+    mutate(iter = anEntry) %>%
+    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
+              by = c("year", "country"))
+})
+
+saveRDS(df_dcpo,"dcpo_theta_uncertainty.rds")
+
+cntrl_ajps_uncertainty <- readRDS("data/cntrl_ajps_uncertainty.rds")
+
+dcpo_analysis <- left_join(df_dcpo,cntrl_ajps_uncertainty, by=c("country","year","iter"="iter_se") )
+saveRDS(dcpo_analysis, "data/dcpo_analysis_ajps.rds")
+
+dcpo_apsr_cntrl <- readRDS("data/cntrl_apsr_uncertainty.rds")
+dcpo_apsr_analysis <- left_join(df_dcpo,dcpo_apsr_cntrl, by=c("country","year","iter"="iter_se") )
+saveRDS(dcpo_apsr_analysis, "data/dcpo_analysis_apsr.rds")
+qsave(dcpo_apsr_analysis, "data/dcpo_analysis_apsr_compress")
+
+cls_ajps_uncertainty <- readRDS("data/cls_ajps_uncertainty.rds")
+
+cls_analysis <- left_join(cls_theta_uncertainty,cls_ajps_uncertainty, by=c("country","year"="Year","iter"="iter_se") )
+saveRDS(cls_analysis, "data/cls_analysis_ajps.rds")
+
+```
+
+# Results Accounting for the Uncertainty in Both the Outcome and Explanatory Variables
+
+```{r cls-uncertainAJPSmain, eval=FALSE}
+ls_country <- unique(claassen_replication$country)
+first_year <- min(claassen_replication$year)
+
+sd_control <- sd.plm %>%
+  mutate(
+    country = as.character(Country),
+    year = as.numeric(as.character(Year)),
+    regime = ifelse(Regime_VD > 1, 1, 0)
+  )
+
+df_cls <- purrr::map(1:1000, function(anEntry) {
+  claassen_m5_theta$theta[anEntry,,] %>% 
+    reformat_dcpo_output("theta") %>% 
+    left_join(sd_control, by = c("country", "year")) %>% 
+    mutate(theta_dem = theta * regime,
+           theta_aut = theta * (1 - regime)) %>% 
+    plm::pdata.frame(index = c("country", "year"))
+})
+
+result_clsUncertain <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
+  result <- map(df_cls, function(aData){ # applying to the 1000 datasets
+    eval(parse(text = aMod))
+  })
+
+  result_betas <- mitools::MIextract(result, fun = coef)
+
+  ## Not work with ifelse
+  if(class(result[[1]])[1] == "plm"){
+      result_vars <- mitools::MIextract(result, fun = vcovBK_se)
+  }else{
+      result_vars <- mitools::MIextract(result, fun = vcovHC_se)
+  }
+
+  tidy_clsUncertain <- summary(mitools::MIcombine(results = result_betas, 
+                             variance = result_vars)) %>% 
+    rownames_to_column(var = "term") %>%
+        rename(conf.low = `(lower`,
+               conf.high = `upper)`,
+               estimate = results) %>%
+        filter(!str_detect(term, "(Intercept)"))
+
+  if(class(result[[1]]) == "plm"){ 
+    glance_clsUncertain <- glance.plm(result[[1]]) # using the customized glance function
+  }else{
+    glance_clsUncertain <- glance(result[[1]])
+  }
+
+  result_clsUncertain <- list(tidy_clsUncertain, glance_clsUncertain)
+})
+
+names(result_clsUncertain) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
+
+saveRDS(result_clsUncertain, file = here::here("output", "estimates_clsAJPS.RDS"))
+```
+
+```{r dcpo-uncertainAJPSmain, eval=FALSE}
+# df_dcpo <- dcpo_ajps_rubin %>% map2(1:length(dcpo_ajps_rubin), ~ {
+#  .x[[.y]] %>%
+#    mutate(theta_dem = theta * regime,
+#           theta_aut = theta * (1 - regime)) %>%
+#    plm::pdata.frame(index = c("country", "year"))
+# }) # The code is to fit the embedded format of dcpo_ajps_rubin
+
+# df_dcpo <- purrr::map(1:1000, function(anEntry) {
+#   dcpo_theta$theta[anEntry,,] %>% 
+#     reformat_dcpo_output("theta") %>% 
+#     left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
+#               by = c("year", "country")) %>%
+#     left_join(df_controls, by = c("country", "year")) %>% 
+#     mutate(theta_dem = theta * regime,
+#            theta_aut = theta * (1 - regime)) %>% 
+#     plm::pdata.frame(index = c("country", "year"))
+# })
+
+result_dcpoUncertain <- map(ls_mod_ajpsDCPO, function(aMod){ # reading a model
+  mod_eval <- function(aData) eval(parse(text = aMod))
+
+  result <- map(df_dcpo, mod_eval)
+
+  result_betas <- mitools::MIextract(result, fun = coef)
+
+  ## Not work with ifelse
+  if(class(result[[1]])[1] == "plm"){
+      result_vars <- mitools::MIextract(result, fun = vcovBK_se)
+  }else{
+      result_vars <- mitools::MIextract(result, fun = vcovHC_se)
+  }
+
+  tidy_dcpoUncertain <- summary(mitools::MIcombine(results = result_betas,
+                             variance = result_vars)) %>%
+    rownames_to_column(var = "term") %>%
+        rename(conf.low = `(lower`,
+               conf.high = `upper)`,
+               estimate = results) %>%
+        filter(!str_detect(term, "(Intercept)"))
+
+  if(class(result[[1]]) == "plm"){
+    glance_dcpoUncertain <- glance.plm(result[[1]]) # using the customized glance function
+  }else{
+    glance_dcpoUncertain <- glance(result[[1]])
+  }
+
+  result_dcpoUncertain <- list(tidy_dcpoUncertain, glance_dcpoUncertain)
+})
+
+names(result_dcpoUncertain) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
+
+saveRDS(result_dcpoUncertain, file = here::here("output", "estimates_dcpoAJPS.RDS"))
+```
+
+```{r cls-undertainAPSRmain, eval=FALSE}
+ls_country <- unique(claassen_replication$country)
+first_year <- min(claassen_replication$year)
+
+sd_control <- sd.plm %>%
+  mutate(
+    country = as.character(Country),
+    year = as.numeric(as.character(Year))
+  )
+
+df_clsAPSR <- purrr::map(1:1000, function(anEntry) {
+  claassen_m5_theta$theta[anEntry,,] %>% 
+    reformat_dcpo_output("theta") %>% 
+    # left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
+    #           by = c("year", "country")) %>%
+    left_join(sd_control, by = c("country", "year")) %>% 
+    plm::pdata.frame(index = c("country", "year"))
+})
+
+result_clsUncertainAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
+  result <- map(df_clsAPSR, function(aData){ # applying to the 1000 datasets
+    eval(parse(text = aMod))
+  })
+
+  result_betas <- mitools::MIextract(result, fun = coef)
+
+  result_vars <- mitools::MIextract(result, fun = vcovHC_se)
+
+  tidy_clsUncertainAPSR <- summary(mitools::MIcombine(results = result_betas, 
+                             variance = result_vars)) %>% 
+    rownames_to_column(var = "term") %>%
+        rename(conf.low = `(lower`,
+               conf.high = `upper)`,
+               estimate = results) %>%
+        filter(!str_detect(term, "(Intercept)"))
+
+  glance_clsUncertainAPSR <- glance.plm(result[[1]])
+
+  result_clsUncertainAPSR <- list(tidy_clsUncertainAPSR, glance_clsUncertainAPSR)
+})
+
+names(result_clsUncertainAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", "fd1", "fd-regime1", "fd2", "fd-regime2")
+
+saveRDS(result_clsUncertainAPSR, file = here::here("output", "estimates_clsAPSR.RDS"))
+
+```
+
+```{r dcpo-uncertainAPSRmain, eval=FALSE}
+result_dcpoUncertainAPSR <- map(ls_mod_apsrDCPO, function(aMod){ # reading a model
+  result <- map(df_dcpoUncertainAPSR, function(aData){ # applying to the 1000 datasets
+    eval(parse(text = aMod))
+  })
+
+  result_betas <- mitools::MIextract(result, fun = coef)
+
+  result_vars <- mitools::MIextract(result, fun = vcovHC_se)
+
+  tidy_dcpoUncertainAPSR <- summary(mitools::MIcombine(results = result_betas, 
+                             variance = result_vars)) %>% 
+    rownames_to_column(var = "term") %>%
+        rename(conf.low = `(lower`,
+               conf.high = `upper)`,
+               estimate = results) %>%
+        filter(!str_detect(term, "(Intercept)"))
+
+  glance_dcpoUncertainAPSR <- glance.plm(result[[1]])
+
+  result_dcpoUncertainAPSR <- list(tidy_dcpoUncertainAPSR, glance_dcpoUncertainAPSR)
+})
+
+names(result_dcpoUncertainAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",  "fd1", "fd-regime1", "fd2", "fd-regime2")
+
+saveRDS(result_dcpoUncertainAPSR, file = here::here("output", "estimates_dcpoAPSR.RDS"))
+```
+
+# Replications of Full Pack of Models in Claassen 2020a,b
+
+```{r plot-fullpackAJPS, fig.cap= "The Effect of Public Support on Democracy", fig.width=7.5, fig.height=10, eval=TRUE}
+
+# Very weird phenomenon that the same type of rds files needs different ways to read
+# Suggesting using the qs or csv data type in future.
+result_cls <- readRDS(here::here("output", "estimates_clsMeanAJPS.RDS"))
+result_clsUncertain <- readRDS(here::here("output", "estimates_clsAJPS.RDS"))
+result_dcpoUncertain <- readRDS(here::here("output", "estimates_dcpoAJPS.RDS"))
+
+result_pooled <- bind_rows(
+  mutate(result_cls$pooled[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertain$pooled[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertain$pooled[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "Pooled")
+
+result_gmm <- bind_rows(
+  mutate(result_cls$gmm[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertain$gmm[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertain$gmm[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "GMM")
+
+result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democracy\n (t-1)",
+        "Democracy\n (t-2)",
+      "Support\n (t-1)",
+      "Log GDP\n per capita\n (t-1)",
+      "GDP per\n capita growth\n (t-1)",
+      "Regional\n democracy\n (t-1)",
+      "Percent\n Muslim\n (t-1)",
+      "Resource\n dependence\n (t-1)"),
+    time = 6), 
+    type = factor(type, levels = c("Pooled", "GMM")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
+
+terms <- factor(rev(c("Democracy[t-1]",
+        "Democracy[t-2]",
+      "Support[t-1]",
+      "Log~GDP~per~capita[t-1]",
+      "GDP~per~capita~growth[t-1]",
+      "Regional~democracy[t-1]",
+      "Percent~Muslim[t-1]",
+      "Resource~dependence[t-1]")), levels =
+      rev(c("Democracy[t-1]",
+        "Democracy[t-2]",
+      "Support[t-1]",
+      "Log~GDP~per~capita[t-1]",
+      "GDP~per~capita~growth[t-1]",
+      "Regional~democracy[t-1]",
+      "Percent~Muslim[t-1]",
+      "Resource~dependence[t-1]")))
+
+# ggplot produces reversed plot, and embarrassed to say, I can't fix, again. Any thought?
+# What I've tried
+# 1. using guide_legend(reverse = TRUE) will change the legend's order not the plot.
+# 2. ordering models with factor levels using the original names or even c("1", "2", "3")
+# 2. redefining the order of model in the dataframe or in dwplot 
+# 3. checking the dwplot codes, model works in line 453, but nothing looks helpful
+# 4. Every post online is to reverse
+
+plot_AJPS1 <- dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms))) +
+  scale_color_grey(start = 0.4, end = 0.8) +
+  labs(
+    title = "DV: V-Dem Liberal Democracy Index",
+    subtitle = "Regime Compacted"
+  ) +
+  facet_wrap(~type, scales = "free_x") + 
+  theme(legend.position = "none")
+
+# the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
+# The trick is  to use guide = guide_legend(reverse = TRUE) within scale_color_*(); see below in plotAJPS2. --FS
+
+result_regime <- bind_rows(
+  mutate(result_cls$`pooled-regime`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertain$`pooled-regime`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertain$`pooled-regime`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "Pooled")
+
+result_regimeGmm <- bind_rows(
+  mutate(result_cls$`gmm-regime`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertain$`gmm-regime`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertain$`gmm-regime`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "GMM")
+
+result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democracy\n (t-1)",
+        "Democracy\n (t-2)",
+      "Support\n demo only\n (t-1)",
+      "Support\n auto only\n (t-1)",
+      "Log GDP\n per capita\n (t-1)",
+      "GDP per\n capita growth\n (t-1)",
+      "Regional\n democracy\n (t-1)",
+      "Percent\n Muslim\n (t-1)",
+      "Resource\n dependence\n (t-1)"),
+    time = 6), 
+    type = factor(type, levels = c("Pooled", "GMM")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
+
+terms2 <- factor(rev(c("Democracy[t-1]",
+                       "Democracy[t-2]",
+                       "Support[t-1] (democracies~only)",
+                       "Support[t-1] (autocracies~only)",
+                       "Log~GDP~per~capita[t-1]",
+                       "GDP~per~capita~growth[t-1]",
+                       "Regional~democracy[t-1]",
+                       "Percent~Muslim[t-1]",
+                       "Resource~dependence[t-1]")), levels =
+                   rev(c("Democracy[t-1]",
+                         "Democracy[t-2]",
+                         "Support[t-1] (democracies~only)",
+                         "Support[t-1] (autocracies~only)",
+                         "Log~GDP~per~capita[t-1]",
+                         "GDP~per~capita~growth[t-1]",
+                         "Regional~democracy[t-1]",
+                         "Percent~Muslim[t-1]",
+                         "Resource~dependence[t-1]")))
+
+plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
+    scale_y_discrete(labels = parse(text = levels(terms2))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  labs(
+    title = "",
+    subtitle = "Regime Specific"
+  ) +
+  facet_wrap(~type, scales = "free_x") +
+  theme(legend.position = "bottom", 
+        legend.title = element_blank())
+
+legend <- get_legend(plot_AJPS2)
+
+plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
+
+grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
+
+```
+
+```{r plot-fullpackAJPSfull, fig.cap= "The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=7, eval=TRUE}
+
+# Very weird phenomenon that the same type of rds files needs different ways to read
+# Suggesting using the qs or csv data type in future.
+result_cls <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
+result_clsUncertainFull <- readRDS(here("output", "estimates_clsAJPSfullUncertain.RDS"))
+result_dcpoUncertainFull <- readRDS(here("output", "estimates_dcpoAJPSfullUncertain.RDS"))
+
+result_pooled <- bind_rows(
+  mutate(result_cls$pooled[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainFull$pooled[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertainFull$pooled[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "Pooled")
+
+result_gmm <- bind_rows(
+  mutate(result_cls$gmm[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainFull$gmm[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertainFull$gmm[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "GMM")
+
+result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democracy\n (t-1)",
+        "Democracy\n (t-2)",
+      "Support\n (t-1)",
+      "Log GDP\n per capita\n (t-1)",
+      "GDP per\n capita growth\n (t-1)",
+      "Regional\n democracy\n (t-1)",
+      "Percent\n Muslim\n (t-1)",
+      "Resource\n dependence\n (t-1)"),
+    time = 6), 
+    type = factor(type, levels = c("Pooled", "GMM")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
+
+terms <- factor(rev(c("Democracy[t-1]",
+        "Democracy[t-2]",
+      "Support[t-1]",
+      "Log~GDP~per~capita[t-1]",
+      "GDP~per~capita~growth[t-1]",
+      "Regional~democracy[t-1]",
+      "Percent~Muslim[t-1]",
+      "Resource~dependence[t-1]")), levels =
+      rev(c("Democracy[t-1]",
+        "Democracy[t-2]",
+      "Support[t-1]",
+      "Log~GDP~per~capita[t-1]",
+      "GDP~per~capita~growth[t-1]",
+      "Regional~democracy[t-1]",
+      "Percent~Muslim[t-1]",
+      "Resource~dependence[t-1]")))
+
+# ggplot produces reversed plot, and embarrassed to say, I can't fix, again. Any thought?
+# What I've tried
+# 1. using guide_legend(reverse = TRUE) will change the legend's order not the plot.
+# 2. ordering models with factor levels using the original names or even c("1", "2", "3")
+# 2. redefining the order of model in the dataframe or in dwplot 
+# 3. checking the dwplot codes, model works in line 453, but nothing looks helpful
+# 4. Every post online is to reverse
+
+plot_AJPS1 <- dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms))) +
+  scale_color_grey(start = 0.4, end = 0.8) +
+  labs(
+    title = "DV: V-Dem Liberal Democracy Index",
+    subtitle = "Regime Compacted"
+  ) +
+  facet_wrap(~type, scales = "free_x") + 
+  theme(legend.position = "none")
+
+# the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
+# The trick is  to use guide = guide_legend(reverse = TRUE) within scale_color_*(); see below in plotAJPS2. --FS
+
+result_regime <- bind_rows(
+  mutate(result_cls$`pooled-regime`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainFull$`pooled-regime`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertainFull$`pooled-regime`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "Pooled")
+
+result_regimeGmm <- bind_rows(
+  mutate(result_cls$`gmm-regime`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainFull$`gmm-regime`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertainFull$`gmm-regime`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "GMM")
+
+result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democracy\n (t-1)",
+        "Democracy\n (t-2)",
+      "Support\n demo only\n (t-1)",
+      "Support\n auto only\n (t-1)",
+      "Log GDP\n per capita\n (t-1)",
+      "GDP per\n capita growth\n (t-1)",
+      "Regional\n democracy\n (t-1)",
+      "Percent\n Muslim\n (t-1)",
+      "Resource\n dependence\n (t-1)"),
+    time = 6), 
+    type = factor(type, levels = c("Pooled", "GMM")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
+
+terms2 <- factor(rev(c("Democracy[t-1]",
+                       "Democracy[t-2]",
+                       "Support[t-1] (democracies~only)",
+                       "Support[t-1] (autocracies~only)",
+                       "Log~GDP~per~capita[t-1]",
+                       "GDP~per~capita~growth[t-1]",
+                       "Regional~democracy[t-1]",
+                       "Percent~Muslim[t-1]",
+                       "Resource~dependence[t-1]")), levels =
+                   rev(c("Democracy[t-1]",
+                         "Democracy[t-2]",
+                         "Support[t-1] (democracies~only)",
+                         "Support[t-1] (autocracies~only)",
+                         "Log~GDP~per~capita[t-1]",
+                         "GDP~per~capita~growth[t-1]",
+                         "Regional~democracy[t-1]",
+                         "Percent~Muslim[t-1]",
+                         "Resource~dependence[t-1]")))
+
+plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
+    scale_y_discrete(labels = parse(text = levels(terms2))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  labs(
+    title = "",
+    subtitle = "Regime Specific"
+  ) +
+  facet_wrap(~type, scales = "free_x") +
+  theme(legend.position = "bottom", 
+        legend.title = element_blank())
+
+legend <- get_legend(plot_AJPS2)
+
+plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
+
+grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
+
+```
+
+```{r plot-fullpackAPSR, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO", fig.width=7.5, fig.height=10, eval=TRUE}
 
@@
 result_clsUncertainAPSR <- readRDS(here("output", "estimates_clsAPSR.RDS"))
-result_dcpoAPSR <- readRDS(here("output", "estimates_dcpoAPSR.RDS"))
+result_dcpoUncertainAPSR <- readRDS(here("output", "estimates_dcpoAPSR.RDS"))
 
@@
   mutate(result_clsUncertainAPSR$pooled1[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoAPSR$pooled1[[1]], model = "DCPO")
+  mutate(result_dcpoUncertainAPSR$pooled1[[1]], model = "DCPO")
 ) %>% 
@@
   mutate(result_clsUncertainAPSR$fd1[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoAPSR$fd1[[1]], model = "DCPO")
+  mutate(result_dcpoUncertainAPSR$fd1[[1]], model = "DCPO")
 ) %>% 
@@
   mutate(result_clsUncertainAPSR$pooled2[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoAPSR$pooled2[[1]], model = "DCPO")
+  mutate(result_dcpoUncertainAPSR$pooled2[[1]], model = "DCPO")
 ) %>% 
@@
   mutate(result_clsUncertainAPSR$fd2[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoAPSR$fd2[[1]], model = "DCPO")
+  mutate(result_dcpoUncertainAPSR$fd2[[1]], model = "DCPO")
 ) %>% 
@@
   mutate(result_clsUncertainAPSR$`pooled-regime1`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoAPSR$`pooled-regime1`[[1]], model = "DCPO")
+  mutate(result_dcpoUncertainAPSR$`pooled-regime1`[[1]], model = "DCPO")
 ) %>% 
@@
   mutate(result_clsUncertainAPSR$`fd-regime1`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoAPSR$`fd-regime1`[[1]], model = "DCPO")
+  mutate(result_dcpoUncertainAPSR$`fd-regime1`[[1]], model = "DCPO")
 ) %>% 
@@
   mutate(result_clsUncertainAPSR$`pooled-regime2`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoAPSR$`pooled-regime2`[[1]], model = "DCPO")
+  mutate(result_dcpoUncertainAPSR$`pooled-regime2`[[1]], model = "DCPO")
 ) %>% 
@@
   mutate(result_clsUncertainAPSR$`fd-regime2`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoAPSR$`fd-regime2`[[1]], model = "DCPO")
+  mutate(result_dcpoUncertainAPSR$`fd-regime2`[[1]], model = "DCPO")
 ) %>% 
@@
 
-# Discussion
-In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support has a positive effect on democracy and democracy a negative effect on support are not empirically supported once measurement uncertainty is taken into account, even when a superior estimate of public support and more data are used.
-
-There are several potential methodological explanations for these null results.
-One issue is that the survey items employed---which ask respondents to assess the desirability or appropriateness of democracy, to compare democracy to some undemocratic alternative, or to assess one of these alternatives---may not capture every aspect of democratic support necessary for it to play its hypothesized roles in the classic theory.
-If only those who profess to prefer democracy to its alternatives _and also_ value freedom of expression, freedom of association, and pluralism of opinion will take appropriate action when democracy is threatened, then this measure is inadequate to its purpose [see, e.g., @Schedler2007].
-Moreover, given the multi-faceted nature of democratic attitudes, even the inclusion of such questions in unidimensional public opinion models such as those provided by @Claassen2019 or @Solt2020a are unlikely to be sufficient [see, e.g., @Wuttke2020].
-Another issue is that even if these survey questions do capture support for the generic concept of democracy, these measurement models might still be incapable of suitably capturing democratic support due to the variation in understanding the concept across countries or over time within countries [@Wuttke2021].
-Yet another is that this measure provides no assessment of the _relative_ importance the public affords democracy.
-It provides no information on the extent to which other values, such as policy preferences or partisanship, weigh more heavily---and there is growing evidence that, at least in the United States, there are many for whom these other considerations excuse substantial transgressions against democracy [see @bartels_ethnic_2020; @Carey2020; @graham_democracy_2020; @McCoy2020].
-
-There are theoretical explanations for the null results as well.
-With regard to how levels of democracy affect public support, we note that even the proponents of the classic argument did not contend that the mere existence of democratic institutions, no matter how consistently feckless and ineffective, would generate support among the public: instead, they maintained, public support would be gained through experience with government performance that was generally effective [@lipset_social_1959, 86-89; @Easton1965, 119-120].
-There is some empirical support for this, with government effectiveness positively related to public support among democracies and negatively related in non-democracies [@Magalhaes2014]. 
-The finding of @Krieckhaus2014 that income inequality is strongly negatively related to public support in democracies suggests that performance regarding redistribution is particularly important.
-Relatedly, on the reverse part of the classic argument, @Qi2011 suggests that democratic support alone cannot be expected to generate democratic change and oppose backsliding.
-Instead, that work contends, it is the combination of democratic support and dissatisfaction with current regime performance that generates demand for greater democracy.
-And we must be open to the possibility that no theoretical elaboration, no respecification of these models will reveal relationships between public opinion and democracy.
-Democratic backsliding may simply be primarily a matter of elite decisionmaking [see, e.g., @levitsky_how_2018].
-Regardless, these explanations indicate that there remains much work to be done in the empirical study of public support and democracy.
-
-# Conclusion
-In this letter, we reexamined the findings from Claassen [-@Claassen2020a; -@Claassen2020b], two articles that maintain that public support helps the survival of democracy and democratic development has a thermostatic effect on public support.
-We demonstrated the importance of incorporating measurement uncertainty in analyzing the relationship between public support and democracy.
-Taking uncertainty into account rendered both articles' conclusions without empirical support, even when we employed the more sophisticated DCPO measurement model and additional data.
-
-This points to the absolute necessity of incorporating measurement uncertainty into analyses that include latent variables.
-As the use of latent variables grows more common in political science, both researchers and readers should be aware that these variables' concomitant measurement uncertainty cannot be neglected.
-
-The null results reached in this letter could arise from several sources.
-We identified a number of potential shortcomings in the measurement of democratic support and ways in which the analysis models might be underspecified.
-All of these could and should be explored in future research, though there are also theoretically grounded reasons to suspect that the relationships are in fact negligible.
-In any event, the sanguine assessment that readers may draw from Claassen [-@Claassen2020a; -@Claassen2020b]---that the fate of democracies depend on public support, and when eroded, their publics will rally to them---is not supported by the current evidence.
-Those who would defend democracy have no grounds to be complacent.
-
-# References  {-}
-
-<div id = 'refs'></div>
-
-\pagebreak
-
-# Online Supplementary Materials {-}
-# (APPENDIX) Appendix {-}
-# Numeric Results for Replicating Claassen 2020a
-
-```{r num-cls2020a, results='asis', eval = TRUE}
-tb_result_cls <- map(result_cls, ~ {
-  names(.) <- c("tidy", "glance")
-  class(.) <- "modelsummary_list"
-  return(.)})
-
-names(tb_result_cls) <- c("Pooled", "Pooled-Regime", 
-                          "GMM", "GMM-Regime")
-
-names_coef <- c(
-  "(Intercept)" = "(Intercept)",
-  "plm::lag(Libdem_VD, 1:2)1" = "Democracy[t-1]",
-  "plm::lag(Libdem_VD, 1:2)2"  = "Democracy[t-2]",
-  "plm::lag(SupDem_trim, 1)" = "Support[t-1]",
-  "plm::lag(SupDem_Democ, 1)" = "Support in Democracy",
-  "plm::lag(SupDem_Autoc, 1)" = "Support in Autocracy",
-  "plm::lag(lnGDP_imp, 1)" = "Log~GDP~per~capita[t-1]",
-  "plm::lag(GDP_imp_grth, 1)"  = "GDP~per~capita~growth[t-1]",
-  "plm::lag(Libdem_regUN, 1)" = "Regional~democracy[t-1]",
-  "plm::lag(Pr_Muslim, 1)" = "Percent~Muslim[t-1]",
-  "plm::lag(Res_cp_WDI_di, 1)" = "Resource~dependence[t-1]"
-)
-
-modelsummary(tb_result_cls,  
-             statistic = "conf.int",
-             coef_map = names_coef, 
-             output = "latex", 
-             title = "Original") %>%
-
-  kableExtra::kable_styling(font_size = 8) %>% 
-  kableExtra::kable_styling(latex_options = "HOLD_position")
-```
-
-```{r num-cls2020aUncertain, results='asis', eval = TRUE}
-tb_result_clsUncertain <- map(result_clsUncertain, ~ {
-  names(.) <- c("tidy", "glance")
-  class(.) <- "modelsummary_list"
-  return(.)})
-
-names(tb_result_cls) <- c("Pooled", "Pooled-Regime", 
-                          "GMM", "GMM-Regime")
-
-names_coef <- c(
-  "plm::lag(Libdem_VD, 1:2)1" = "Democracy[t-1]",
-  "plm::lag(Libdem_VD, 1:2)2"  = "Democracy[t-2]",
-  "plm::lag(theta, 1)" = "Support[t-1]",
-  "plm::lag(theta_dem, 1)" = "Support in Democracy",
-  "plm::lag(theta_aut, 1)" = "Support in Autocracy",
-  "plm::lag(lnGDP_imp, 1)" = "Log~GDP~per~capita[t-1]",
-  "plm::lag(GDP_imp_grth, 1)"  = "GDP~per~capita~growth[t-1]",
-  "plm::lag(Libdem_regUN, 1)" = "Regional~democracy[t-1]",
-  "plm::lag(Pr_Muslim, 1)" = "Percent~Muslim[t-1]",
-  "plm::lag(Res_cp_WDI_di, 1)" = "Resource~dependence[t-1]"
-)
-
-modelsummary(tb_result_clsUncertain, 
-             statistic = "conf.int",
-             coef_map = names_coef, 
-             output = "latex", 
-             title = "W. Uncertainty") %>% 
-  kableExtra::kable_styling(latex_options = "HOLD_position")
-```
-
-```{r num-cls2020aDCPO, results='asis', eval = TRUE}
-tb_result_DCPO <- map(result_dcpoUncertain, ~ {
-  names(.) <- c("tidy", "glance")
-  class(.) <- "modelsummary_list"
-  return(.)})
-
-names(tb_result_DCPO) <- c("Pooled", "Pooled-Regime", 
-                          "GMM", "GMM-Regime")
-
-names_coef <- c(
-  "plm::lag(Vdem_libdem, 1:2)1" = "Democracy[t-1]",
-  "plm::lag(Vdem_libdem, 1:2)2"  = "Democracy[t-2]",
-  "plm::lag(theta, 1)" = "Support[t-1]",
-  "plm::lag(theta_dem, 1)" = "Support in Democracy",
-  "plm::lag(theta_aut, 1)" = "Support in Autocracy",
-  "plm::lag(lg_imp_mdpgdp, 1)" = "Log~GDP~per~capita[t-1]",
-  "plm::lag(mdprgdp_grwth, 1)"  = "GDP~per~capita~growth[t-1]",
-  "plm::lag(Region_libdem, 1)" = "Regional~democracy[t-1]",
-  "plm::lag(muslism_prop_2010, 1)" = "Percent~Muslim[t-1]",
-  "plm::lag(dependence_pc_di, 1)" = "Resource~dependence[t-1]"
-)
-
-modelsummary(tb_result_DCPO, 
-             statistic = "conf.int",
-             coef_map = names_coef, 
-             output = "latex", 
-             title = "W. Uncertainty") %>% 
-  kableExtra::kable_styling(latex_options = "HOLD_position")
-```
-
-\blandscape
-
-# Numeric Results for Replicating Claassen 2020b
-
-```{r num-cls2020b, results='asis', eval = TRUE}
-tb_result_clsAPSR <- map(result_clsAPSR, ~ {
-  names(.) <- c("tidy", "glance")
-  class(.) <- "modelsummary_list"
-  return(.)}) %>% 
-  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
-      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]
-
-names(tb_result_clsAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
-
-names_coef <- c(
-  "(Intercept)" = "(Intercept)",
-  "plm::lag(SupDem_trim, 1:2)1" = "Democratic\n Mood\n (t-1)",
-  "plm::lag(SupDem_trim, 1:2)2" = "Democratic\n Mood\n (t-2)",
-  "diff(Libdem_z, lag = 1)" = "Liberal\n Democracy\n (Difference)",
-  "Libdem_z" = "Liberal\n Democracy\n (Difference)",
-  "plm::lag(Libdem_z, 1)" = "Liberal\n Democracy\n (t-1)",
-  "diff(Polyarchy_z, lag = 1)" = "Electoral\n Democracy\n (Difference)",
-  "Polyarchy_z" = "Electoral\n Democracy\n (Difference)",
-  "plm::lag(Polyarchy_z, 1)" = "Electoral\n Democracy\n (t-1)",
-  "diff(Liberal_z, lag = 1)" = "Minoritarian\n Democracy\n (Difference)",
-  "Liberal_z" = "Minoritarian\n Democracy\n (Difference)",
-  "plm::lag(Liberal_z, 1)" = "Minoritarian\n Democracy\n (t-1)",
-  "diff(lnGDP_imp, lag = 1)" = "Log GDP\n per capita\n (Difference)",
-  "lnGDP_imp" = "Log GDP\n per capita\n (Difference)",
-  "plm::lag(lnGDP_imp, 1)" = "Log GDP\n (t-1)",
-  "diff(Corrup_TI_z, lag = 1)" = "Corruption\n (Difference)",
-  "Corrup_TI_z" = "Corruption\n (Difference)",
-  "plm::lag(Corrup_TI_z, 1)" = "Corruption\n (t-1)"
-)
-
-modelsummary(tb_result_clsAPSR, 
-             stars = TRUE,
-             coef_map = names_coef, 
-             output = "latex") %>% 
-  kableExtra::kable_styling(font_size = 7) %>% 
-  kableExtra::kable_styling(latex_options = "HOLD_position")
-```
-
-\elandscape
-
-\blandscape
-
-```{r num-cls2020bUncertain, results='asis', eval = TRUE}
-tb_result_clsUncertainAPSR <- map(result_clsUncertainAPSR, ~ {
-  names(.) <- c("tidy", "glance")
-  class(.) <- "modelsummary_list"
-  return(.)}) %>% 
-  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
-      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]
-
-names(tb_result_clsUncertainAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
-
-names_coef <- c(
-  "(Intercept)" = "(Intercept)",
-  "plm::lag(SupDem_trim, 1:2)1" = "Democratic\n Mood\n (t-1)",
-  "plm::lag(SupDem_trim, 1:2)2" = "Democratic\n Mood\n (t-2)",
-  "diff(Libdem_z, lag = 1)" = "Liberal\n Democracy\n (Difference)",
-  "Libdem_z" = "Liberal\n Democracy\n (Difference)",
-  "plm::lag(Libdem_z, 1)" = "Liberal\n Democracy\n (t-1)",
-  "diff(Polyarchy_z, lag = 1)" = "Electoral\n Democracy\n (Difference)",
-  "Polyarchy_z" = "Electoral\n Democracy\n (Difference)",
-  "plm::lag(Polyarchy_z, 1)" = "Electoral\n Democracy\n (t-1)",
-  "diff(Liberal_z, lag = 1)" = "Minoritarian\n Democracy\n (Difference)",
-  "Liberal_z" = "Minoritarian\n Democracy\n (Difference)",
-  "plm::lag(Liberal_z, 1)" = "Minoritarian\n Democracy\n (t-1)",
-  "diff(lnGDP_imp, lag = 1)" = "Log GDP\n per capita\n (Difference)",
-  "lnGDP_imp" = "Log GDP\n per capita\n (Difference)",
-  "plm::lag(lnGDP_imp, 1)" = "Log GDP\n (t-1)",
-  "diff(Corrup_TI_z, lag = 1)" = "Corruption\n (Difference)",
-  "Corrup_TI_z" = "Corruption\n (Difference)",
-  "plm::lag(Corrup_TI_z, 1)" = "Corruption\n (t-1)"
-)
-
-modelsummary(tb_result_clsUncertainAPSR, 
-             statistic = "conf.int",
-             coef_map = names_coef, 
-             output = "latex") %>% 
-  kableExtra::kable_styling(font_size = 7) %>% 
-  kableExtra::kable_styling(latex_options = "HOLD_position")
-```
-
-\elandscape
-
-\blandscape
-
-```{r num-cls2020bDCPO, results='asis', eval = TRUE}
-tb_result_dcpoAPSR <- map(result_dcpoAPSR, ~ {
-  names(.) <- c("tidy", "glance")
-  class(.) <- "modelsummary_list"
-  return(.)}) %>% 
-  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
-      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]
-
-names(tb_result_dcpoAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
-
-names_coef <- c(
-  "(Intercept)" = "(Intercept)",
-  "plm::lag(theta, 1:2)1" = "Democratic\n Mood\n (t-1)",
-  "plm::lag(theta, 1:2)2" = "Democratic\n Mood\n (t-2)",
-
-  "diff(Vdem_libdem_z, lag = 1)" = "Liberal\n Democracy\n (Difference)",
-  "Vdem_libdem_z" = "Liberal\n Democracy\n (Difference)",
-  "plm::lag(Vdem_libdem_z, 1)" = "Liberal\n Democracy\n (t-1)",
-
-  "diff(Vdem_polyarchy_z, lag = 1)" = "Electoral\n Democracy\n (Difference)",
-  "Vdem_polyarchy_z" = "Electoral\n Democracy\n (Difference)",
-  "plm::lag(Vdem_polyarchy_z, 1)" = "Electoral\n Democracy\n (t-1)",
-  "diff(Vdem_liberal_z, lag = 1)" = "Minoritarian\n Democracy\n (Difference)",
-  "Vdem_liberal_z" = "Minoritarian\n Democracy\n (Difference)",
-  "plm::lag(Vdem_liberal_z, 1)" = "Minoritarian\n Democracy\n (t-1)",
-  "diff(lg_imp_mdpgdp, lag = 1)" = "Log GDP\n per capita\n (Difference)",
-  "lg_imp_mdpgdp" = "Log GDP\n per capita\n (Difference)",
-  "plm::lag(lg_imp_mdpgdp, 1)" = "Log GDP\n (t-1)",
-  "diff(corruption_z, lag = 1)" = "Corruption\n (Difference)",
-  "corruption_z" = "Corruption\n (Difference)",
-  "plm::lag(corruption_z, 1)" = "Corruption\n (t-1)"
-)
-
-modelsummary(tb_result_dcpoAPSR, 
-             statistic = "conf.int",
-             coef_map = names_coef, 
-             output = "latex") %>% 
-  kableExtra::kable_styling(font_size = 7) %>% 
-  kableExtra::kable_styling(latex_options = "HOLD_position")
-```
-
-\elandscape
-
-```{r datawitherrors}
-
-ls_country <- unique(claassen_replication$country)
-first_year <- min(claassen_replication$year)
-
-df_cls_errors <- purrr::map(1:900, function(anEntry) {
-  claassen_m5_theta$theta[anEntry,,] %>%
-    reformat_dcpo_output("theta")  %>%
-    mutate(iter = anEntry) 
-  }
-  )
-
-cls_theta_uncertainty <- bind_rows(df_cls_errors)
-saveRDS(cls_theta_uncertainty,"data/cls_theta_uncertainty.rds")
-
-ls_country <- levels(dcpo_input$data$kk)
-first_year <- min(dcpo_input$data$year)
-
-df_dcpo <- purrr::map_df(1:900, function(anEntry) {
-  dcpo_theta$theta[anEntry,,] %>%
-    reformat_dcpo_output("theta") %>%
-    mutate(iter = anEntry) %>%
-    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
-              by = c("year", "country"))
-})
-
-saveRDS(df_dcpo,"dcpo_theta_uncertainty.rds")
-
-cntrl_ajps_uncertainty <- readRDS("data/cntrl_ajps_uncertainty.rds")
-
-dcpo_analysis <- left_join(df_dcpo,cntrl_ajps_uncertainty, by=c("country","year","iter"="iter_se") )
-saveRDS(dcpo_analysis, "data/dcpo_analysis_ajps.rds")
-
-dcpo_apsr_cntrl <- readRDS("data/cntrl_apsr_uncertainty.rds")
-dcpo_apsr_analysis <- left_join(df_dcpo,dcpo_apsr_cntrl, by=c("country","year","iter"="iter_se") )
-saveRDS(dcpo_apsr_analysis, "data/dcpo_analysis_apsr.rds")
-qsave(dcpo_apsr_analysis, "data/dcpo_analysis_apsr_compress")
-
-cls_ajps_uncertainty <- readRDS("data/cls_ajps_uncertainty.rds")
-
-cls_analysis <- left_join(cls_theta_uncertainty,cls_ajps_uncertainty, by=c("country","year"="Year","iter"="iter_se") )
-saveRDS(cls_analysis, "data/cls_analysis_ajps.rds")
-
-```
-
-# Results Accounting for the Uncertainty in Both the Outcome and Explanatory Variables
-
-```{r cls-uncertainAJPSmain, eval=FALSE}
-ls_country <- unique(claassen_replication$country)
-first_year <- min(claassen_replication$year)
-
-sd_control <- sd.plm %>%
-  mutate(
-    country = as.character(Country),
-    year = as.numeric(as.character(Year)),
-    regime = ifelse(Regime_VD > 1, 1, 0)
-  )
-
-df_cls <- purrr::map(1:1000, function(anEntry) {
-  claassen_m5_theta$theta[anEntry,,] %>% 
-    reformat_dcpo_output("theta") %>% 
-    left_join(sd_control, by = c("country", "year")) %>% 
-    mutate(theta_dem = theta * regime,
-           theta_aut = theta * (1 - regime)) %>% 
-    plm::pdata.frame(index = c("country", "year"))
-})
-
-result_clsUncertain <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
-  result <- map(df_cls, function(aData){ # applying to the 1000 datasets
-    eval(parse(text = aMod))
-  })
-
-  result_betas <- mitools::MIextract(result, fun = coef)
-
-  ## Not work with ifelse
-  if(class(result[[1]])[1] == "plm"){
-      result_vars <- mitools::MIextract(result, fun = vcovBK_se)
-  }else{
-      result_vars <- mitools::MIextract(result, fun = vcovHC_se)
-  }
-
-  tidy_clsUncertain <- summary(mitools::MIcombine(results = result_betas, 
-                             variance = result_vars)) %>% 
-    rownames_to_column(var = "term") %>%
-        rename(conf.low = `(lower`,
-               conf.high = `upper)`,
-               estimate = results) %>%
-        filter(!str_detect(term, "(Intercept)"))
-
-  if(class(result[[1]]) == "plm"){ 
-    glance_clsUncertain <- glance.plm(result[[1]]) # using the customized glance function
-  }else{
-    glance_clsUncertain <- glance(result[[1]])
-  }
-
-  result_clsUncertain <- list(tidy_clsUncertain, glance_clsUncertain)
-})
-
-names(result_clsUncertain) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
-
-saveRDS(result_clsUncertain, file = here::here("output", "estimates_clsAJPS.RDS"))
-```
-
-```{r dcpo-uncertainAJPSmain, eval=FALSE}
-# df_dcpo <- dcpo_ajps_rubin %>% map2(1:length(dcpo_ajps_rubin), ~ {
-#  .x[[.y]] %>%
-#    mutate(theta_dem = theta * regime,
-#           theta_aut = theta * (1 - regime)) %>%
-#    plm::pdata.frame(index = c("country", "year"))
-# }) # The code is to fit the embedded format of dcpo_ajps_rubin
-
-# df_dcpo <- purrr::map(1:1000, function(anEntry) {
-#   dcpo_theta$theta[anEntry,,] %>% 
-#     reformat_dcpo_output("theta") %>% 
-#     left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
-#               by = c("year", "country")) %>%
-#     left_join(df_controls, by = c("country", "year")) %>% 
-#     mutate(theta_dem = theta * regime,
-#            theta_aut = theta * (1 - regime)) %>% 
-#     plm::pdata.frame(index = c("country", "year"))
-# })
-
-result_dcpoUncertain <- map(ls_mod_ajpsDCPO, function(aMod){ # reading a model
-  mod_eval <- function(aData) eval(parse(text = aMod))
-
-  result <- map(df_dcpo, mod_eval)
-
-  result_betas <- mitools::MIextract(result, fun = coef)
-
-  ## Not work with ifelse
-  if(class(result[[1]])[1] == "plm"){
-      result_vars <- mitools::MIextract(result, fun = vcovBK_se)
-  }else{
-      result_vars <- mitools::MIextract(result, fun = vcovHC_se)
-  }
-
-  tidy_dcpoUncertain <- summary(mitools::MIcombine(results = result_betas,
-                             variance = result_vars)) %>%
-    rownames_to_column(var = "term") %>%
-        rename(conf.low = `(lower`,
-               conf.high = `upper)`,
-               estimate = results) %>%
-        filter(!str_detect(term, "(Intercept)"))
-
-  if(class(result[[1]]) == "plm"){
-    glance_dcpoUncertain <- glance.plm(result[[1]]) # using the customized glance function
-  }else{
-    glance_dcpoUncertain <- glance(result[[1]])
-  }
-
-  result_dcpoUncertain <- list(tidy_dcpoUncertain, glance_dcpoUncertain)
-})
-
-names(result_dcpoUncertain) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
-
-saveRDS(result_dcpoUncertain, file = here::here("output", "estimates_dcpoAJPS.RDS"))
-```
-
-```{r cls-undertainAPSRmain, eval=FALSE}
-ls_country <- unique(claassen_replication$country)
-first_year <- min(claassen_replication$year)
-
-sd_control <- sd.plm %>%
-  mutate(
-    country = as.character(Country),
-    year = as.numeric(as.character(Year))
-  )
-
-df_clsAPSR <- purrr::map(1:1000, function(anEntry) {
-  claassen_m5_theta$theta[anEntry,,] %>% 
-    reformat_dcpo_output("theta") %>% 
-    # left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
-    #           by = c("year", "country")) %>%
-    left_join(sd_control, by = c("country", "year")) %>% 
-    plm::pdata.frame(index = c("country", "year"))
-})
-
-result_clsUncertainAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
-  result <- map(df_clsAPSR, function(aData){ # applying to the 1000 datasets
-    eval(parse(text = aMod))
-  })
-
-  result_betas <- mitools::MIextract(result, fun = coef)
-
-  result_vars <- mitools::MIextract(result, fun = vcovHC_se)
-
-  tidy_clsUncertainAPSR <- summary(mitools::MIcombine(results = result_betas, 
-                             variance = result_vars)) %>% 
-    rownames_to_column(var = "term") %>%
-        rename(conf.low = `(lower`,
-               conf.high = `upper)`,
-               estimate = results) %>%
-        filter(!str_detect(term, "(Intercept)"))
-
-  glance_clsUncertainAPSR <- glance.plm(result[[1]])
-
-  result_clsUncertainAPSR <- list(tidy_clsUncertainAPSR, glance_clsUncertainAPSR)
-})
-
-names(result_clsUncertainAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", "fd1", "fd-regime1", "fd2", "fd-regime2")
-
-saveRDS(result_clsUncertainAPSR, file = here::here("output", "estimates_clsAPSR.RDS"))
-
-```
-
-```{r dcpo-uncertainAPSRmain, eval=FALSE}
-result_dcpoUncertainAPSR <- map(ls_mod_apsrDCPO, function(aMod){ # reading a model
-  result <- map(df_dcpoUncertainAPSR, function(aData){ # applying to the 1000 datasets
-    eval(parse(text = aMod))
-  })
-
-  result_betas <- mitools::MIextract(result, fun = coef)
-
-  result_vars <- mitools::MIextract(result, fun = vcovHC_se)
-
-  tidy_dcpoUncertainAPSR <- summary(mitools::MIcombine(results = result_betas, 
-                             variance = result_vars)) %>% 
-    rownames_to_column(var = "term") %>%
-        rename(conf.low = `(lower`,
-               conf.high = `upper)`,
-               estimate = results) %>%
-        filter(!str_detect(term, "(Intercept)"))
-
-  glance_dcpoUncertainAPSR <- glance.plm(result[[1]])
-
-  result_dcpoUncertainAPSR <- list(tidy_dcpoUncertainAPSR, glance_dcpoUncertainAPSR)
-})
-
-names(result_dcpoUncertainAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",  "fd1", "fd-regime1", "fd2", "fd-regime2")
-
-saveRDS(result_dcpoUncertainAPSR, file = here::here("output", "estimates_dcpoAPSR.RDS"))
-```
-
-# Replications of Full Pack of Models in Claassen 2020a,b
-
-```{r plot-fullpackAJPS, fig.cap= "The Effect of Public Support on Democracy", fig.width=7.5, fig.height=10}
-
-# Very weird phenomenon that the same type of rds files needs different ways to read
-# Suggesting using the qs or csv data type in future.
-result_cls <- readRDS(here::here("output", "estimates_clsMeanAJPS.RDS"))
-result_clsUncertain <- readRDS(here::here("output", "estimates_clsAJPS.RDS"))
-result_dcpoUncertain <- readRDS(here::here("output", "estimates_dcpoAJPS.RDS"))
-
-result_pooled <- bind_rows(
-  mutate(result_cls$pooled[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertain$pooled[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertain$pooled[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "Pooled")
-
-result_gmm <- bind_rows(
-  mutate(result_cls$gmm[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertain$gmm[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertain$gmm[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "GMM")
-
-result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = rep(
-      c("Democracy\n (t-1)",
-        "Democracy\n (t-2)",
-      "Support\n (t-1)",
-      "Log GDP\n per capita\n (t-1)",
-      "GDP per\n capita growth\n (t-1)",
-      "Regional\n democracy\n (t-1)",
-      "Percent\n Muslim\n (t-1)",
-      "Resource\n dependence\n (t-1)"),
-    time = 6), 
-    type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
-
-terms <- factor(rev(c("Democracy[t-1]",
-        "Democracy[t-2]",
-      "Support[t-1]",
-      "Log~GDP~per~capita[t-1]",
-      "GDP~per~capita~growth[t-1]",
-      "Regional~democracy[t-1]",
-      "Percent~Muslim[t-1]",
-      "Resource~dependence[t-1]")), levels =
-      rev(c("Democracy[t-1]",
-        "Democracy[t-2]",
-      "Support[t-1]",
-      "Log~GDP~per~capita[t-1]",
-      "GDP~per~capita~growth[t-1]",
-      "Regional~democracy[t-1]",
-      "Percent~Muslim[t-1]",
-      "Resource~dependence[t-1]")))
-
-# ggplot produces reversed plot, and embarrassed to say, I can't fix, again. Any thought?
-# What I've tried
-# 1. using guide_legend(reverse = TRUE) will change the legend's order not the plot.
-# 2. ordering models with factor levels using the original names or even c("1", "2", "3")
-# 2. redefining the order of model in the dataframe or in dwplot 
-# 3. checking the dwplot codes, model works in line 453, but nothing looks helpful
-# 4. Every post online is to reverse
-
-plot_AJPS1 <- dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms))) +
-  scale_color_grey(start = 0.4, end = 0.8) +
-  labs(
-    title = "DV: V-Dem Liberal Democracy Index",
-    subtitle = "Regime Compacted"
-  ) +
-  facet_wrap(~type, scales = "free_x") + 
-  theme(legend.position = "none")
-
-# the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
-# The trick is  to use guide = guide_legend(reverse = TRUE) within scale_color_*(); see below in plotAJPS2. --FS
-
-result_regime <- bind_rows(
-  mutate(result_cls$`pooled-regime`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertain$`pooled-regime`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertain$`pooled-regime`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "Pooled")
-
-result_regimeGmm <- bind_rows(
-  mutate(result_cls$`gmm-regime`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertain$`gmm-regime`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertain$`gmm-regime`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "GMM")
-
-result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = rep(
-      c("Democracy\n (t-1)",
-        "Democracy\n (t-2)",
-      "Support\n demo only\n (t-1)",
-      "Support\n auto only\n (t-1)",
-      "Log GDP\n per capita\n (t-1)",
-      "GDP per\n capita growth\n (t-1)",
-      "Regional\n democracy\n (t-1)",
-      "Percent\n Muslim\n (t-1)",
-      "Resource\n dependence\n (t-1)"),
-    time = 6), 
-    type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
-
-terms2 <- factor(rev(c("Democracy[t-1]",
-                       "Democracy[t-2]",
-                       "Support[t-1] (democracies~only)",
-                       "Support[t-1] (autocracies~only)",
-                       "Log~GDP~per~capita[t-1]",
-                       "GDP~per~capita~growth[t-1]",
-                       "Regional~democracy[t-1]",
-                       "Percent~Muslim[t-1]",
-                       "Resource~dependence[t-1]")), levels =
-                   rev(c("Democracy[t-1]",
-                         "Democracy[t-2]",
-                         "Support[t-1] (democracies~only)",
-                         "Support[t-1] (autocracies~only)",
-                         "Log~GDP~per~capita[t-1]",
-                         "GDP~per~capita~growth[t-1]",
-                         "Regional~democracy[t-1]",
-                         "Percent~Muslim[t-1]",
-                         "Resource~dependence[t-1]")))
-
-plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms2))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  labs(
-    title = "",
-    subtitle = "Regime Specific"
-  ) +
-  facet_wrap(~type, scales = "free_x") +
-  theme(legend.position = "bottom", 
-        legend.title = element_blank())
-
-legend <- get_legend(plot_AJPS2)
-
-plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
-
-grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
-
-```
-
-```{r plot-fullpackAJPSfull, fig.cap= "The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=7}
-
-# Very weird phenomenon that the same type of rds files needs different ways to read
-# Suggesting using the qs or csv data type in future.
-result_cls <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
-result_clsUncertainFull <- readRDS(here("output", "estimates_clsAJPSfullUncertain.RDS"))
-result_dcpoUncertainFull <- readRDS(here("output", "estimates_dcpoAJPSfullUncertain.RDS"))
-
-result_pooled <- bind_rows(
-  mutate(result_cls$pooled[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainFull$pooled[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainFull$pooled[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "Pooled")
-
-result_gmm <- bind_rows(
-  mutate(result_cls$gmm[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainFull$gmm[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainFull$gmm[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "GMM")
-
-result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = rep(
-      c("Democracy\n (t-1)",
-        "Democracy\n (t-2)",
-      "Support\n (t-1)",
-      "Log GDP\n per capita\n (t-1)",
-      "GDP per\n capita growth\n (t-1)",
-      "Regional\n democracy\n (t-1)",
-      "Percent\n Muslim\n (t-1)",
-      "Resource\n dependence\n (t-1)"),
-    time = 6), 
-    type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
-
-terms <- factor(rev(c("Democracy[t-1]",
-        "Democracy[t-2]",
-      "Support[t-1]",
-      "Log~GDP~per~capita[t-1]",
-      "GDP~per~capita~growth[t-1]",
-      "Regional~democracy[t-1]",
-      "Percent~Muslim[t-1]",
-      "Resource~dependence[t-1]")), levels =
-      rev(c("Democracy[t-1]",
-        "Democracy[t-2]",
-      "Support[t-1]",
-      "Log~GDP~per~capita[t-1]",
-      "GDP~per~capita~growth[t-1]",
-      "Regional~democracy[t-1]",
-      "Percent~Muslim[t-1]",
-      "Resource~dependence[t-1]")))
-
-# ggplot produces reversed plot, and embarrassed to say, I can't fix, again. Any thought?
-# What I've tried
-# 1. using guide_legend(reverse = TRUE) will change the legend's order not the plot.
-# 2. ordering models with factor levels using the original names or even c("1", "2", "3")
-# 2. redefining the order of model in the dataframe or in dwplot 
-# 3. checking the dwplot codes, model works in line 453, but nothing looks helpful
-# 4. Every post online is to reverse
-
-plot_AJPS1 <- dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms))) +
-  scale_color_grey(start = 0.4, end = 0.8) +
-  labs(
-    title = "DV: V-Dem Liberal Democracy Index",
-    subtitle = "Regime Compacted"
-  ) +
-  facet_wrap(~type, scales = "free_x") + 
-  theme(legend.position = "none")
-
-# the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
-# The trick is  to use guide = guide_legend(reverse = TRUE) within scale_color_*(); see below in plotAJPS2. --FS
-
-result_regime <- bind_rows(
-  mutate(result_cls$`pooled-regime`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainFull$`pooled-regime`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainFull$`pooled-regime`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "Pooled")
-
-result_regimeGmm <- bind_rows(
-  mutate(result_cls$`gmm-regime`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainFull$`gmm-regime`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainFull$`gmm-regime`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "GMM")
-
-result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = rep(
-      c("Democracy\n (t-1)",
-        "Democracy\n (t-2)",
-      "Support\n demo only\n (t-1)",
-      "Support\n auto only\n (t-1)",
-      "Log GDP\n per capita\n (t-1)",
-      "GDP per\n capita growth\n (t-1)",
-      "Regional\n democracy\n (t-1)",
-      "Percent\n Muslim\n (t-1)",
-      "Resource\n dependence\n (t-1)"),
-    time = 6), 
-    type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
-
-terms2 <- factor(rev(c("Democracy[t-1]",
-                       "Democracy[t-2]",
-                       "Support[t-1] (democracies~only)",
-                       "Support[t-1] (autocracies~only)",
-                       "Log~GDP~per~capita[t-1]",
-                       "GDP~per~capita~growth[t-1]",
-                       "Regional~democracy[t-1]",
-                       "Percent~Muslim[t-1]",
-                       "Resource~dependence[t-1]")), levels =
-                   rev(c("Democracy[t-1]",
-                         "Democracy[t-2]",
-                         "Support[t-1] (democracies~only)",
-                         "Support[t-1] (autocracies~only)",
-                         "Log~GDP~per~capita[t-1]",
-                         "GDP~per~capita~growth[t-1]",
-                         "Regional~democracy[t-1]",
-                         "Percent~Muslim[t-1]",
-                         "Resource~dependence[t-1]")))
-
-plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms2))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  labs(
-    title = "",
-    subtitle = "Regime Specific"
-  ) +
-  facet_wrap(~type, scales = "free_x") +
-  theme(legend.position = "bottom", 
-        legend.title = element_blank())
-
-legend <- get_legend(plot_AJPS2)
-
-plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
-
-grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
-
-```
-
-```{r plot-fullpackAPSR, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO"}
-
-load(here::here("output", "estimates_dcpoAPSR.RDS"))
-
-df_plot <- df_result_dcpoMeanAPSR[[1]] %>% 
-  mutate(model = "DCPO\n (Point Estimates)")
-
-df_plot <- df_result_dcpoAPSR[[1]] %>%
-  mutate(model = "DCPO\n (w. Uncertainty)") %>%
-  rename(std.error = se) %>%
-  bind_rows(df_plot)
-
-plot_pooled <- filter(df_plot, model != "Claassen 2019") %>% 
-  dwplot(by_2sd = FALSE) %>%
-  relabel_predictors(
-    c(
-      `plm::lag(theta, 1:2)1` = "Democracy Mood(t-1)",
-      `plm::lag(theta, 1:2)2` = "Democracy Mood(t-2)",
-      `diff(Vdem_libdem_z, lag = 1)` = "Liberal Democracy (Diff)",
-      `plm::lag(Vdem_libdem_z, 1)` = "Liberal Democracy (t-1)",
-      `diff(lg_imp_mdpgdp, lag = 1)` = "Log GDP per capita(Diff)", 
-      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t-1)",
-      `plm::lag(mdprgdp_grwth, 1)` = "Corruption (Difference)"
-    )
-  ) +
-  geom_vline(xintercept = 0,
-             colour = "grey80",
-             linetype = 2) +
-  theme_minimal() +
-  ggtitle("DV: Liberal Democracy (Vdem)") +
-  xlab("Coefficient Estimate") +
-  theme(
-    axis.title.y = element_blank(),
-    legend.position = "bottom",
-    legend.title = element_blank()
-  )
-
-df_plot <- df_result_dcpoMeanAPSR[[2]] %>% 
-  mutate(model = "DCPO\n (Point Estimates)")
-
-df_plot <- df_result_dcpoAPSR[[2]] %>%
-  mutate(model = "DCPO\n (w. Uncertainty)") %>%
-  rename(std.error = se) %>%
-  bind_rows(df_plot)
-
-plot_pooled2 <- filter(df_plot, model != "Claassen 2019") %>% 
-  dwplot(by_2sd = FALSE) %>%
-  relabel_predictors(
-    c(
-      `plm::lag(theta, 1:2)1` = "Democracy Mood(t-1)",
-      `plm::lag(theta, 1:2)2` = "Democracy Mood(t-2)",
-      `diff(Vdem_libdem_z, lag = 1)` = "Liberal Democracy (Diff)",
-      `plm::lag(Vdem_libdem_z, 1)` = "Liberal Democracy (t-1)",
-      `diff(lg_imp_mdpgdp, lag = 1)` = "Log GDP per capita(Diff)", 
-      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t-1)",
-      `diff(cpi_sd, lag = 1)` = "Corruption (Difference)",
-      `plm::lag(cpi_sd, 1)` = "Corruption (t-1)"
-    )
-  ) +
-  geom_vline(xintercept = 0,
-             colour = "grey80",
-             linetype = 2) +
-  theme_minimal() +
-  ggtitle("DV: Liberal Democracy (Vdem)") +
-  xlab("Coefficient Estimate") +
-  theme(
-    axis.title.y = element_blank(),
-    legend.position = "bottom",
-    legend.title = element_blank()
-  )
-
-gridExtra::grid.arrange(plot_pooled,plot_pooled2, ncol = 2)
-```
-
-```{r plot-fullpackAPSRfull, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}
+```{r plot-fullpackAPSRfull, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10, eval=TRUE}
 

### 2021-06-09 paper/dcpo_demsupport.Rmd
merge conflict avoid

--- 2021-06-08 paper/dcpo_demsupport.Rmd
@@
 load(here("data", "cls_apsr.rda"))
-load(here("data", "dcpo_apsr.rda"))
+load(here("data","dcpo_apsr.rda"))
 

### 2021-06-11 paper/dcpo_demsupport_appendix.Rmd
finish comparison plots

@@
 
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, dpi = 300)
+knitr::opts_chunk$set(cache = TRUE, echo = FALSE, message = FALSE, warning = FALSE, dpi = 300, include = FALSE)
 
@@
   plm,
-  glue,
+  glue, dotwhisker,
   huxtable, kableExtra, modelsummary, # tabulation
-  latex2exp, # visualization
+  latex2exp, patchwork, # visualization
   rstan, # Bayesian estimation
@@
 
-## Claassen Replication Input
+## Claassen Replication
 
@@
 
-```{r claassen_m5_theta}
-load(here::here("data", "claassen_m5.rda"))
+```{r ajps_mean}
+load(here::here("data", "claassen_m5_3k_07-05-11-16.rda")) # our dataset of estimates, from surveys & DCPOtools, as generated in above (unrun) chunks
 
-claassen_m5_theta <- rstan::extract(claassen_m5, pars = "theta")
-
-save(claassen_m5_theta, file = "data/claassen_m5_theta.rda")
-
-claassen_m5_x_pred <- rstan::extract(claassen_m5, pars = "x_pred")
-
-save(claassen_replication_input, claassen_m5_x_pred, file = "data/claassen_m5_x_pred.rda")
-```
-
-```{r claassenUncertainty, cache=TRUE}
-load(here::here("data", "claassen_m5_3k_07-05-11-16.rda")) # ours
-
-claassen_m5_theta <- rstan::extract(claassen_m5, pars = "theta")
+claassen_m5_theta <- rstan::extract(claassen_m5, pars = "theta") %>% 
+  first()
 
 ls_year <- 1988:2017
-ls_country <- claassen_input$data$country %>% unique()
+ls_country <- unique(claassen_input$data$country)
 
@@
 
-claassen_m5_theta_std = (claassen_m5_theta[[1]] - mean(as.vector(claassen_m5_theta[[1]]))) / sd(as.vector(claassen_m5_theta[[1]]))
-
-df_theta <- purrr::map(1:1000, function(x) {
-  claassen_m5_theta_std[x,,] %>% 
-    as_tibble() %>% 
-    rename_with(~ls_country, .cols = starts_with("V")) %>% 
-    mutate(year = first_year + row_number() - 1) %>% 
-    pivot_longer(cols = !year,
-                 names_to = "country",
-                 values_to = "theta") %>%
-    arrange(country, year) %>% 
-    left_join(sd_controls, by = c("country", "year")) %>% 
-    plm::pdata.frame(index = c("country", "year"))
-})
+# standardize, exactly as in 'supdem stan estimation ajps.R' at L192
+claassen_m5_theta_std = (claassen_m5_theta - mean(as.vector(claassen_m5_theta))) / sd(as.vector(claassen_m5_theta))
 
@@
      mutate(df_result, std.error = vcovBK_se(result))
-  } else{
+  } else {
     mutate(df_result, std.error = vcovHC_se(result))
@@
 
-map_df(1:2, function(a) {
+ajps_mean_plot <- map_df(1:2, function(a) {
   result_cls[[a]][[1]] %>% 
@@
   xlab("Coefficient Estimate") +
-  scale_color_discrete(name="Dataset")
+  scale_color_discrete(name="Dataset", breaks=c("Claassen's","Ours"))
+```
 
-ggsave("paper/ours_vs_claassens_mean.pdf")
+```{r our_ajps_1k}
+df_theta <- purrr::map(1:1000, function(x) {
+  claassen_m5_theta_std[x,,] %>% 
+    as_tibble() %>% 
+    rename_with(~ls_country, .cols = starts_with("V")) %>% 
+    mutate(year = first_year + row_number() - 1) %>% 
+    pivot_longer(cols = !year,
+                 names_to = "country",
+                 values_to = "theta") %>%
+    arrange(country, year) %>% 
+    left_join(sd_controls, by = c("country", "year")) %>% 
+    plm::pdata.frame(index = c("country", "year"))
+})
 
@@
 
-load(here::here("data", "pure_claassen_1k_result.rda"))
-
 df_result_cls_1k <- summary(mitools::MIcombine(results = result_betas_m5_1k, 
@@
   mutate(model = "Ours")
+```
 
-bind_rows(df_result_cls_1k, mod.1_df_result_cls_1k) %>% 
+```{r pure_claassen_ajps_1k}
+load(here::here("data", "pure_claassen_1k_result.rda")) # from pure_claassen.R
+# Replicate Claassen AJPS thetas, using his input data and his code
+# light revision of 'supdem stan estimation ajps.R'
+
+# options
+rstan_options(auto_write = TRUE)
+options(mc.cores = parallel::detectCores())
+
+# read support for dem data
+sddem1 = read.csv(here::here("data", "supdem raw survey marginals.tab"))
+
+# remove NAs
+sddem1 = sddem1[!sddem1$Response==0, ]
+
+# create year by country indicators
+year0 = 1987
+sddem1 = sddem1[sddem1$Year > year0,]
+sddem1 = unite(sddem1, YearCountry, c(Year, Country), sep = "_", remove = FALSE)
+
+# create item by country indicators
+sddem1 = unite(sddem1, ItemCnt, c(Item, Country), sep = "_", remove = FALSE)
+
+# create year by project indicators
+sddem1 = unite(sddem1, YrProj, c(Year, Project), sep = "_", remove = FALSE)
+
+# create year by project by country indicators
+sddem1 = unite(sddem1, YrProjCnt, c(YrProj, Country), sep = "_", remove = FALSE)
+
+# factorise
+sddem1$Country = as.factor(as.character(sddem1$Country))
+sddem1$Item = as.factor(as.character(sddem1$Item))
+sddem1$ItemCnt = as.factor(as.character(sddem1$ItemCnt))
+sddem1$Project = as.factor(as.character(sddem1$Project))
+sddem1$YrProj = as.factor(as.character(sddem1$YrProj))
+sddem1$YrProjCnt = as.factor(as.character(sddem1$YrProjCnt))
+sddem1$Year = sddem1$Year-year0
+
+# count data
+dim(sddem1)[1]                   # 3765 national responses
+length(unique(sddem1$Country))   # 150 countries
+length(unique(sddem1$Project))   # 14 projects
+length(unique(sddem1$Item))      # 52 items
+length(unique(sddem1$ItemCnt))   # 1453 item-country
+length(unique(sddem1$YrProjCnt)) # 1390 national surveys
+length(unique(sddem1$Year))      # 27 unique years (out of 30)
+sum(sddem1$Sample) / dim(sddem1)[1] * length(unique(sddem1$YrProjCnt))   # 1,804,450 respondents
+
+# drop countries with less than 2 years of data
+cnt.obs.years = rowSums(table(sddem1$Country, sddem1$Year) > 0)
+sort(cnt.obs.years)
+sddem2 = sddem1[sddem1$Country %in% levels(sddem1$Country)[cnt.obs.years > 1], ]
+length(unique(sddem2$Country))   # 137 countries with 2+ years of data
+
+#### Stan estimation
+# prepare data for stan
+n.items = length(unique(sddem2$Item))
+n.cntrys = length(unique(sddem2$Country))
+n.yrs = 2017-year0
+n.proj = length(unique(sddem2$Project))
+n.resp = dim(sddem2)[1]
+n.itm.cnt = length(unique(sddem2$ItemCnt))
+n.cntry.yrs = n.cntrys * n.yrs
+n.yr.proj.cnt = length(unique(sddem2$YrProjCnt))
+cntrys = as.numeric(factor(sddem2$Country))
+cnt.names = as.character(sort(unique(sddem2$Country)))
+cnt.code = as.character(sddem2[match(cnt.names, sddem2$Country), "CAbb"])
+cnt.code[83] = "MNE"
+cnt.code[106] = "SRB"
+items = as.numeric(factor(sddem2$Item))
+yrs = sddem2$Year
+projs = as.numeric(factor(sddem2$Project))
+itm.cnts = as.numeric(factor(sddem2$ItemCnt))
+
+# specify data for stan
+dat.2 = list(N=n.resp, K=n.items, T=n.yrs, J=n.cntrys, P=n.itm.cnt, jj=cntrys, tt=yrs, 
+             pp=itm.cnts, kk=items, x=sddem2$Response, samp=sddem2$Sample)
+sapply(dat.2, summary)
+
+# pars
+pars.5 = c("mu_lambda","sigma_lambda","sigma_delta","sigma_theta","phi","lambda","delta","theta",
+           "x_pred","log_lik")
+
+save(dat.2, pars.5, file = here::here("R", "argon", "dcpo_demsupport_rep", "data", "pure_claassen.rda"))
+
+# run 'R/argon/dcpo_demsupport_rep/R/pure_claassen_m5.R'
+stan.mod.5 <- rio::import(here::here("R", "argon", "dcpo_demsupport_rep", "data", "pure_claassen_m5.rda"))
+
+#### Extract theta estimates
+
+theta.out = rstan::extract(stan.mod.5, pars = c("theta"))[[1]]
+theta.std = (theta.out - mean(as.vector(theta.out))) / sd(as.vector(theta.out)) # standardize
+theta.out.t = apply( theta.std, 1, function(x) t(x) )
+theta.out.df = data.frame(Country=rep(cnt.names, length.out=n.cntrys*30), 
+                          ISO_code=rep(cnt.code, length.out=n.cntrys*30),
+                          Year=rep(1988:2017, each=n.cntrys), theta.out.t)
+theta.pe = theta.out.df[,1:3]
+theta.dim = dim(theta.out.df)[2]
+theta.pe$SupDem_trim = apply(theta.out.df[,4:theta.dim], 1, mean)
+
+first.yr = data.frame(Country=levels(sddem2$Country),
+                      First_yr = as.vector(by(sddem2, sddem2$Country, function(x) min(as.numeric(x$Year))+1987)))
+
+theta.pe = merge(theta.pe, first.yr, by="Country", all.x=TRUE)
+cnts = theta.pe[theta.pe$Year==2008, "Country"]
+frst.yr = theta.pe[theta.pe$Year==2008, "First_yr"]
+for(i in 1:length(cnts)) {
+    theta.pe[theta.pe$Country==cnts[i] & theta.pe$Year<frst.yr[i], "SupDem_trim"] = NA
+}
+
+sd_controls <- read_csv(here::here("data", "Support_democracy_ajps.csv"),
+                        col_types = cols(.default = col_double(),
+                                         Country = col_character(),
+                                         Cnt_code = col_character(),
+                                         ISO_code = col_character(),
+                                         Region_UN = col_character()))
+
+theta.out.df_list <- map(1:1000, function(x) {
+    theta.pe %>% 
+        mutate(theta0 = theta.out.t[,x],
+               theta = if_else(!is.na(SupDem_trim), theta0, NA_real_)) %>% 
+        left_join(sd_controls, by = c("Country", "Year")) %>% 
+        plm::pdata.frame(index = c("Country", "Year"))
+})
+
+mod.1_1k <- map(theta.out.df_list, function(aDataset) {
+    plm(Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + plm::lag(theta, 1) + plm::lag(lnGDP_imp, 1) +
+            plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) +
+            plm::lag(Res_cp_WDI_di, 1), model="pooling", data = aDataset)
+})
+
+result_betas_mod.1_1k <- mitools::MIextract(mod.1_1k, fun = coef)
+result_vars_mod.1_1k <- mitools::MIextract(mod.1_1k, fun = vcovBK_se)
+
+mod.1_df_result_cls_1k <- summary(mitools::MIcombine(results = result_betas_mod.1_1k,
+                                            variance = result_vars_mod.1_1k)) %>%
+    rownames_to_column(var = "term") %>% 
+    rename(conf.low = `(lower`,
+           conf.high = `upper)`, 
+           estimate = results) %>% 
+    filter(!str_detect(term, "(Intercept)")) %>% 
+    mutate(model = "Claassen's")
+```
+
+```{r ajps_1k_plot}
+ajps_1k_plot <- bind_rows(df_result_cls_1k, mod.1_df_result_cls_1k) %>% 
   dotwhisker::dwplot() %>% 
@@
   scale_color_discrete(name="1k Samples\nDataset", breaks=c("Claassen's","Ours"))
-
-ggsave("paper/ours_vs_claassens_1k.pdf")
 ```
 
+```{r apsr_mean}
+if (!file.exists(here::here("data", "dem_mood_apsr.csv"))) {
+  tempfile <- dataverse::get_file("dem_mood_apsr.tab", "doi:10.7910/DVN/FECIO3", 
+                                  format = "original") # Claassen's APSR replication file
+
+  writeBin(tempfile, here::here("data", "dem_mood_apsr.csv"))
+}
+
+sd_controls_apsr <- read_csv(here::here("data", "dem_mood_apsr.csv"), 
+                        col_types = cols(.default = col_double(),
+                                         Country = col_character(),
+                                         ISO_code = col_character(),
+                                         Region_UN = col_character())) %>% 
+  mutate(country = countrycode::countrycode(as.character(Country), "country.name", "country.name"),
+         year = as.numeric(as.character(Year))) %>% 
+  left_join(first_years, by = "country") %>% 
+  filter(year >= first_year)
+
+df_theta_mean_apsr <- purrr::map_df(1:1000, function(x) {
+  claassen_m5_theta_std[x,,] %>% 
+    as_tibble() %>% 
+    rename_with(~ls_country, .cols = starts_with("V")) %>% 
+    mutate(year = first_year + row_number() - 1) %>% 
+    pivot_longer(cols = !year,
+                 names_to = "country",
+                 values_to = "theta") %>%
+    arrange(country, year)
+}) %>% 
+  group_by(country, year) %>% 
+  summarize(theta_mean = mean(theta)) %>% 
+  right_join(sd_controls_apsr, by = c("country", "year")) %>% 
+  plm::pdata.frame(index = c("country", "year"))
+
+cor(df_theta_mean$theta_mean, df_theta_mean_apsr$theta_mean) # 1
+
+ls_dv_apsr <- c("theta_mean", "SupDem_trim")
+
+ls_eq_apsr <- glue::glue("diff({ls_dv_apsr}, lag=1) ~ plm::lag({ls_dv_apsr}, 1:2) + diff(Libdem_z, lag=1) + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag=1) + plm::lag(lnGDP_imp, 1)")
+
+ls_mod_apsr <- glue::glue("plm({ls_eq_apsr}, model = 'pooling', data = df_theta_mean_apsr)")
+
+df_result_cls_apsr <- map(ls_mod_apsr, function(mod) {
+  result <- eval(parse(text = mod))
+})
+
+tidy_cls_apsr <- map(df_result_cls_apsr, function(result) {
+  df_result <- tidy(result, conf.int = TRUE)
+
+  if (class(result)[[1]] == "plm") {
+     mutate(df_result, std.error = vcovBK_se(result))
+  } else {
+    mutate(df_result, std.error = vcovHC_se(result))
+  }
+})
+
+glance_cls_apsr <- map(df_result_cls_apsr, function(aResult) {
+  if (class(aResult)[[1]] == "plm") { 
+    glance.plm(aResult) # using the customized glance function
+  } else {
+    glance(aResult)
+  }
+})
+
+result_cls_apsr <- map2(tidy_cls_apsr, glance_cls_apsr, ~ list(.x, .y))
+#names(result_cls) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
+
+apsr_mean_plot <- map_df(1:2, function(a) {
+  result_cls_apsr[[a]][[1]] %>% 
+    mutate(model = if_else(a==1, "Ours", "Claassen's")) %>% 
+    filter(!str_detect(term, "(Intercept)"))
+}) %>% 
+  dotwhisker::dwplot() %>% 
+  relabel_predictors(c(`plm::lag(theta_mean, 1:2)1` = "Support[t-1]",
+                       `plm::lag(theta_mean, 1:2)2` = "Support[t-2]",
+                       `plm::lag(SupDem_trim, 1:2)1` = "Support[t-1]",
+                       `plm::lag(SupDem_trim, 1:2)2` = "Support[t-2]",
+                       `diff(Libdem_z, lag = 1)` = "Delta~Liberal~democracy",
+                       `plm::lag(Libdem_z, 1)` = "Liberal~democracy[t-1]",
+                       `diff(lnGDP_imp, lag = 1)` = "Delta~Log GDP per capita",
+                       `plm::lag(lnGDP_imp, 1)` = "Log GDP per capita[t-1]")) +
+  geom_vline(xintercept = 0, colour = "grey80", linetype = 2) +
+  theme_minimal() +
+  ggtitle("Dependent Variable: Delta Support for Democracy") + 
+  xlab("Coefficient Estimate") +
+  scale_color_discrete(name="Dataset", breaks=c("Claassen's","Ours"))
+```
+
+```{r apsr_1k}
+df_theta_apsr <- purrr::map(1:1000, function(x) {
+  claassen_m5_theta_std[x,,] %>% 
+    as_tibble() %>% 
+    rename_with(~ls_country, .cols = starts_with("V")) %>% 
+    mutate(year = first_year + row_number() - 1) %>% 
+    pivot_longer(cols = !year,
+                 names_to = "country",
+                 values_to = "theta") %>%
+    arrange(country, year) %>% 
+    left_join(sd_controls_apsr, by = c("country", "year")) %>% 
+    plm::pdata.frame(index = c("country", "year"))
+})
+
+result_m5_1k_apsr <- map(df_theta_apsr, function(aDataset) {
+  plm(diff(theta, lag=1) ~ plm::lag(theta, 1:2) + diff(Libdem_z, lag=1) 
+           + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag=1) + plm::lag(lnGDP_imp, 1), 
+           aDataset, model="pooling")
+})
+
+result_betas_m5_1k_apsr <- mitools::MIextract(result_m5_1k_apsr, fun = coef)
+result_vars_m5_1k_apsr <- mitools::MIextract(result_m5_1k_apsr, fun = vcovBK_se)
+
+df_result_cls_1k_apsr <- summary(mitools::MIcombine(results = result_betas_m5_1k_apsr, 
+                                                    variance = result_vars_m5_1k_apsr)) %>%
+  rownames_to_column(var = "term") %>% 
+  rename(conf.low = `(lower`,
+         conf.high = `upper)`, 
+         estimate = results) %>% 
+  filter(!str_detect(term, "(Intercept)")) %>% 
+  mutate(model = "Ours")
+```
+
+```{r pure_claassen_apsr_1k}
+sd.apsr = read.csv(here::here("data", "dem_mood_apsr.csv")) %>% 
+    select(-starts_with("SupDem"))
+
+theta.out.df_list_apsr <- map(1:1000, function(x) {
+    theta.pe %>% 
+        mutate(theta0 = theta.out.t[,x],
+               theta = if_else(!is.na(SupDem_trim), theta0, NA_real_)) %>% 
+        left_join(sd.apsr, by = c("Country", "Year")) %>% 
+        plm::pdata.frame(index = c("Country", "Year"))
+})
+
+mod.1_apsr_1k <- map(theta.out.df_list_apsr, function(aDataset) {
+    plm(diff(theta, lag=1) ~ plm::lag(theta, 1:2) + diff(Libdem_z, lag=1) 
+        + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag=1) + plm::lag(lnGDP_imp, 1), 
+        data = aDataset, model="pooling")
+})
+
+result_betas_mod.1_apsr_1k <- mitools::MIextract(mod.1_apsr_1k, fun = coef)
+result_vars_mod.1_apsr_1k <- mitools::MIextract(mod.1_apsr_1k, fun = vcovBK_se)
+
+mod.1_df_result_cls_apsr_1k <- summary(mitools::MIcombine(results = result_betas_mod.1_apsr_1k,
+                                                     variance = result_vars_mod.1_apsr_1k)) %>%
+    rownames_to_column(var = "term") %>% 
+    rename(conf.low = `(lower`,
+           conf.high = `upper)`, 
+           estimate = results) %>% 
+    filter(!str_detect(term, "(Intercept)")) %>% 
+    mutate(model = "Claassen's")
+```
+
+```{r apsr_1k_plot}
+apsr_1k_plot <- bind_rows(df_result_cls_1k_apsr, mod.1_df_result_cls_apsr_1k) %>% 
+  dotwhisker::dwplot() %>% 
+  relabel_predictors(c(
+    `plm::lag(SupDem_trim, 1:2)1` = "Support[t-1]",
+    `plm::lag(SupDem_trim, 1:2)2` = "Support[t-2]",
+    `plm::lag(theta, 1:2)1` = "Support[t-1]",
+    `plm::lag(theta, 1:2)2` = "Support[t-2]",
+    `diff(Liberal_z, lag = 1)` = "Delta~Support(demo~only)",
+    `diff(Vdem_liberal_z, lag = 1)` = "Delta~Support(demo~only)",
+    `plm::lag(Liberal_z, 1)` = "Support[t-1](demo~only)",
+    `plm::lag(Vdem_liberal_z, 1)` = "Support[t-1](demo~only)",
+    `diff(Polyarchy_z, lag = 1)` = "Delta~Support(auto~only)",
+    `diff(Vdem_polyarchy_z, lag = 1)` = "Delta~Support(auto~only)",
+    `plm::lag(Polyarchy_z, 1)` = "Support[t-1](auto~only)",
+    `plm::lag(Vdem_polyarchy_z, 1)` = "Support[t-1](auto~only)",
+    `diff(Libdem_z, lag = 1)` = "Delta~Liberal~democracy",
+    `diff(Vdem_libdem_z, lag = 1)` = "Delta~Liberal~democracy",
+    `plm::lag(Libdem_z, 1)` = "Liberal~democracy[t-1]",
+    `plm::lag(Vdem_libdem_z, 1)` = "Liberal~democracy[t-1]",
+    `diff(lnGDP_imp, lag = 1)` = "Delta~Log~GDP~per~capita",
+    `diff(lg_imp_mdpgdp, lag = 1)` = "Delta~Log~GDP~per~capita",
+    `plm::lag(lnGDP_imp, 1)` = "Log~GDP[t-1]",
+    `plm::lag(lg_imp_mdpgdp, 1)` = "Log~GDP[t-1]"
+)) +
+  geom_vline(xintercept = 0, colour = "grey80", linetype = 2) +
+  theme_minimal() +
+  ggtitle("Dependent Variable: Delta Support for Democracy") + 
+  xlab("Coefficient Estimate") +
+  scale_color_discrete(name="1k Samples\nDataset", breaks=c("Claassen's","Ours"))
+
+```
+
+```{r results_comparison_plots, include=TRUE, fig.width=7}
+ajps_mean_plot 
+ajps_1k_plot
+apsr_mean_plot
+apsr_1k_plot
+
+```
 \pagebreak

### 2021-06-15 paper/dcpo_demsupport_appendix.Rmd
add expanded_claassen for ajps and apsr

@@
 
+vcovBK_se <- function(x) {
+  plm::vcovBK(x, cluster = "time") %>% 
+    diag() %>% 
+    sqrt()
+}
 ```
@@
 ```{r claassen_replication_input, eval=FALSE}
+
+# dcpo_input_raw <- DCPOtools::dcpo_setup(vars = read_csv(here::here("data-raw", "mood_dem.csv"),
+#                                                         col_types = "cccccc"),
+#                                         file = "data/dcpo_input_raw.csv")
+
 dcpo_input_raw1 <- read_csv(here::here("data", "dcpo_input_raw.csv"), col_types = "cdcddcd") %>% 
@@
 claassen_input_cy <- read_csv(here::here("data", "dcpo_input_raw.csv"),
-                              col_types = "cdcddcd") %>%           # 1861 obs
+                              col_types = "cdcddcd") %>%           # 1864 obs
   mutate(p_dcpo = str_extract(survey, "^[a-z]+"), 
@@
 
-no_problems <- inner_join(supdem_cy, claassen_input_cy)             # 1297 obs
+no_problems <- inner_join(supdem_cy, claassen_input_cy)             # 1298 obs
 
@@
 
-available <- anti_join(claassen_input_cy, supdem_cy)                # 564 obs
+available <- anti_join(claassen_input_cy, supdem_cy)                # 566 obs
 
@@
 
-cys_to_drop <- anti_join(available, year_fixes, by = c("country", "year" = "year.y", "project")) %>% # 475 obs
+cys_to_drop <- anti_join(available, year_fixes, by = c("country", "year" = "year.y", "project")) %>% # 477 obs
   select(-y_dcpo)
@@
 ls_country <- unique(claassen_input$data$country)
-
-vcovBK_se <- function(x) {
-  vcovBK(x, cluster = "time") %>% 
-    diag() %>% 
-    sqrt()
-}
 
@@
 ```
+
+```{r expanded_claassen}
+# these are estimates based on Claassen's original dataset, plus all additional country-year-item observations we found; see
+
+load(here::here("data", "exp_claassen_m5_3k_06-13-17-09.rda")) #  dataset of estimates, based on Claassen's original dataset, plus all additional country-year-item observations we found, as generated in (at the moment) expanded_claassen_input.R
+
+exp_claassen_m5_theta <- rstan::extract(exp_claassen_m5, pars = "theta") %>% 
+  first()
+
+ls_ec_year <- min(expanded_claassen_input$data$year):max(expanded_claassen_input$data$year)
+ls_ec_country <- unique(expanded_claassen_input$data$country)
+
+ec_first_year <- min(expanded_claassen_input$data$year)
+
+ec_controls <- read_csv(here::here("data", "control_variables_ajps.csv"),
+                        col_types = cols(.default = col_double(),
+                                         country = col_character(),
+                                         ISO = col_character(),
+                                         Region_UN = col_character(),
+                                         regime = col_logical())) %>% 
+  mutate(country = countrycode::countrycode(as.character(country), "country.name", "country.name"),
+         year = as.numeric(as.character(year))) %>% 
+  filter(year >= first_year)
+
+# standardize, exactly as in 'supdem stan estimation ajps.R' at L192 (= for assignment and all)
+exp_claassen_m5_theta_std = (exp_claassen_m5_theta - mean(as.vector(exp_claassen_m5_theta))) / sd(as.vector(exp_claassen_m5_theta))
+
+ec_df_theta <- purrr::map(1:1000, function(x) {
+  exp_claassen_m5_theta_std[x,,] %>% 
+    as_tibble() %>% 
+    rename_with(~ls_ec_country, .cols = starts_with("V")) %>% 
+    mutate(year = ec_first_year + row_number() - 1) %>% 
+    pivot_longer(cols = !year,
+                 names_to = "country",
+                 values_to = "theta") %>%
+    arrange(country, year) %>% 
+    left_join(ec_controls, by = c("country", "year")) %>% 
+    plm::pdata.frame(index = c("country", "year"))
+})
+
+ec_result_m5_1k <- map(ec_df_theta, function(aDataset) {
+  plm::plm(Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + plm::lag(theta, 1) + plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) + plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1), model="pooling", data = aDataset)
+})
+
+ec_result_betas_m5_1k <- mitools::MIextract(ec_result_m5_1k, fun = coef)
+ec_result_vars_m5_1k <- mitools::MIextract(ec_result_m5_1k, fun = vcovBK_se)
+
+ec_df_result_cls_1k <- summary(mitools::MIcombine(results = ec_result_betas_m5_1k, 
+                                               variance = ec_result_vars_m5_1k)) %>%
+  rownames_to_column(var = "term") %>% 
+  rename(conf.low = `(lower`,
+         conf.high = `upper)`, 
+         estimate = results) %>% 
+  filter(!str_detect(term, "(Intercept)"))
+```
+
+```{r all_claassen_res_ajps_plot, include=TRUE, fig.width=7}
+all_claassen_res_ajps <- ec_df_result_cls_1k %>% 
+              mutate(model = "Expanded Dataset\nw/ Uncertainty") %>% 
+  bind_rows(mod.1_df_result_cls_1k %>% 
+              mutate(model = "Claassen w/ Uncertainty")) %>% 
+  bind_rows(result_cls[[2]][[1]] %>% 
+    mutate(model = "Claassen 2020a",
+           term = str_replace(term, "SupDem_trim", "theta_mean"))) %>% 
+  filter(!str_detect(term, "(Intercept)"))
+
+all_claassen_res_ajps_plot <- dotwhisker::dwplot(all_claassen_res_ajps) %>% 
+  relabel_predictors(c(
+    `plm::lag(Libdem_VD, 1:2)1` = "Democracy[t-1]",
+    `plm::lag(Libdem_VD, 1:2)2` = "Democracy[t-2]",
+    `plm::lag(Vdem_libdem, 1:2)1` = "Democracy[t-1]",
+    `plm::lag(Vdem_libdem, 1:2)2` = "Democracy[t-2]",
+    `plm::lag(theta_mean, 1)` = "Support[t-1]",
+    `plm::lag(theta, 1)` = "Support[t-1]",
+    `plm::lag(SupDem_Democ, 1)` = "Support[t-1](demo~only)",
+    `plm::lag(SupDem_Autoc, 1)` = "Support[t-1](auto~only)",
+    `plm::lag(theta_dem_trim, 1)` = "Support[t-1](demo~only)",
+    `plm::lag(theta_aut_trim, 1)` = "Support[t-1](auto~only)",
+    `plm::lag(lnGDP_imp, 1)` = "Log~GDP~per~capita[t-1]",
+    `plm::lag(lg_imp_mdpgdp, 1)` = "Log~GDP~per~capita[t-1]",
+    `plm::lag(GDP_imp_grth, 1)` = "GDP~per~capita~growth[t-1]",
+    `plm::lag(mdprgdp_grwth, 1)` = "GDP~per~capita~growth[t-1]",
+    `plm::lag(Libdem_regUN, 1)` = "Regional~democracy[t-1]",
+    `plm::lag(Region_libdem, 1)` = "Regional~democracy[t-1]",
+    `plm::lag(Pr_Muslim, 1)` = "Percent~Muslim[t-1]",
+    `plm::lag(muslism_prop_2010, 1)` = "Percent~Muslim[t-1]",
+    `plm::lag(Res_cp_WDI_di, 1)` = "Resource~dependence[t-1]",
+    `plm::lag(dependence_pc_di, 1)` = "Resource~dependence[t-1]"
+  )
+  ) +
+  geom_vline(xintercept = 0, colour = "grey80", linetype = 2) +
+  theme_minimal() +
+  ggtitle("Dependent Variable: Level of Democracy") + 
+  xlab("Coefficient Estimate") +
+  scale_color_discrete(name="Dataset", guide = guide_legend(reverse = TRUE))
+
+all_claassen_res_ajps_plot
+```
+
+```{r apsr_1k}
+ec_df_theta_apsr <- purrr::map(1:1000, function(x) {
+  exp_claassen_m5_theta_std[x,,] %>% 
+    as_tibble() %>% 
+    rename_with(~ls_ec_country, .cols = starts_with("V")) %>% 
+    mutate(year = ec_first_year + row_number() - 1) %>% 
+    pivot_longer(cols = !year,
+                 names_to = "country",
+                 values_to = "theta") %>%
+    arrange(country, year) %>% 
+    left_join(sd_controls_apsr, by = c("country", "year")) %>% 
+    plm::pdata.frame(index = c("country", "year"))
+})
+
+ec_result_m5_1k_apsr <- map(ec_df_theta_apsr, function(aDataset) {
+  plm(diff(theta, lag=1) ~ plm::lag(theta, 1:2) + diff(Libdem_z, lag=1) 
+           + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag=1) + plm::lag(lnGDP_imp, 1), 
+           aDataset, model="pooling")
+})
+
+ec_result_betas_m5_1k_apsr <- mitools::MIextract(ec_result_m5_1k_apsr, fun = coef)
+ec_result_vars_m5_1k_apsr <- mitools::MIextract(ec_result_m5_1k_apsr, fun = vcovBK_se)
+
+ec_df_result_cls_1k_apsr <- summary(mitools::MIcombine(results = ec_result_betas_m5_1k_apsr, 
+                                                    variance = ec_result_vars_m5_1k_apsr)) %>%
+  rownames_to_column(var = "term") %>% 
+  rename(conf.low = `(lower`,
+         conf.high = `upper)`, 
+         estimate = results) %>% 
+  filter(!str_detect(term, "(Intercept)"))
+```
+
 \pagebreak

### 2021-06-20 R/cls_ajps_apsr_uncertainty.R
using pure/exp_claassen_m5.rda to create uncertainty list.

@@ -6,20 +6,65 @@ p_load(
     here,
     purrr,
     countrycode,
-    tidyverse
+    tidyverse,
+    rstan
 ) 
 
 # Functions preload
 set.seed(313)
 
 
+reformat_dcpo_output <- function(x, parameter_name) {
+    df_temp <- x %>% 
+        as_tibble(.name_repair = ~ls_country) %>% 
+        mutate(year = first_year + row_number() - 1) %>% 
+        pivot_longer(cols = all_of(ls_country),
+                     names_to = "country",
+                     values_to = parameter_name) %>%
+        arrange(country, year)
+    return(df_temp)
+}
+
+
+load(here::here("data", "exp_claassen_m5_3k_06-13-17-09.rda")) 
+
+load(here("data", "pure_claassen_m5.rda")) 
+
+claassen_m5_theta <- rstan::extract(pure_claassen_m5, pars = "theta")
+
+cnt.names = as.character(sort(unique(sddem2$Country)))
+
+supdem <- read_csv(here::here("data", "supdem raw survey marginals.tab"), col_types = "cdcddcdc")
+pure_claassen_input <- supdem %>%                                             # 1390 obs
+    janitor::clean_names() %>% 
+    mutate(old_country = country,
+           country = countrycode::countrycode(old_country, "country.name", "country.name")) %>%
+    DCPOtools::with_min_yrs(2) %>% 
+    dplyr::select(country, year, project) %>% 
+    unique()
+
+length(unique(pure_claassen_input$country))
+
+ls_year <- 1988:2017
+ls_country <- pure_claassen_input$country %>% unique()
+first_year <- min(pure_claassen_input$year)
+
+pure_cls_theta_list <- purrr::map(1:900, function(anEntry) {
+    claassen_m5_theta$theta[anEntry,,] %>%
+        reformat_dcpo_output("theta") 
+}
+)
+#year 30, country 137
+save(pure_cls_theta_list,file = here("data","pure_cls_theta_list.rda"))
+
 ################################################################
 ######## Create lists for elements in analysis data  ###########
-########### AJPS: cls_libdem_ajps_list,cls_ajps  ###############
+########### AJPS: cls_libdem_ajps_list,pure_cls_ajps ############
 ################################################################
 
[…]

### 2021-06-20 paper/dcpo_demsupport.Rmd
use pure/exp_cls_ajps/apsr to execute moc.

--- 2021-06-09 paper/dcpo_demsupport.Rmd
@@
 ```{r claassenMocUncertaintyAPSR}
-load(here("data", "cls_apsr.rda"))
+load(here("data", "pure_cls_apsr.rda")) #use pure_cls_apsr instead of cls_apsr
+load(here("data", "exp_cls_apsr.rda")) #use exp_cls_apsr instead of cls_apsr
 
 df_clsAPSR <- purrr::map(1:900, function(anEntry) {
-  cls_apsr[[anEntry]] %>% 
+  pure_cls_apsr[[anEntry]] %>% 
+    plm::pdata.frame(index = c("country", "year"))
+}
+)
+
+df_our_clsAPSR <- purrr::map(1:900, function(anEntry) {
+  exp_cls_apsr[[anEntry]] %>% 
     plm::pdata.frame(index = c("country", "year"))
@@
   result <- methodComposition3(df_clsAPSR,aMod)
-})
+})  #claassen's data
+
+result_our_clsUncertain  <- map(ls_mod, function(aMod){
+  result <- methodComposition3(df_our_clsAPSR,aMod)
+})   ##our expanded data
 
@@
 
-saveRDS(result_clsUncertain, file = here("ouput","clsAPSR_uncertainty.RDS"))
+names(result_our_clsUncertain) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
+                                "fd1", "fd-regime1", "fd2", "fd-regime2")
+
+saveRDS(result_clsUncertain, file = here::here("ouput","clsAPSR_uncertainty.RDS"))
+
+saveRDS(result_our_clsUncertain, file = here::here("ouput","our_clsAPSR_uncertainty.RDS"))
 
@@
 
-result_clsUncertain <- readRDS(here("output","clsAPSR_uncertainty.RDS"))
+#result_clsUncertain <- readRDS(here("output","clsAPSR_uncertainty.RDS"))
+result_clsUncertain <- readRDS(here("output","our_clsAPSR_uncertainty.RDS"))
 result_dcpoUncertain <- readRDS(here("output","dcpoAPSR_uncertainty.RDS"))

### 2021-06-24 paper/dcpo_demsupport.Rmd
downloading data from the osf

@@
   dataverse, 
-  DCPOtools, mitools,
+  osfr,
+  # DCPOtools, 
+  mitools,
   boot, 
@@
 
-# produced by cls_ajps_apsr_uncertain.R and dcpo_ajps_apsr_uncertain.R
-load(here("data", "cls_ajps.rda")) 
-load(here("data", "dcpo_ajps.rda")) 
-load(here("data", "cls_apsr.rda"))
-load(here("data", "dcpo_apsr.rda"))
-
-claassen_replication <- readRDS(here("data", "claassen_replication.rds")) %>% 
-  janitor::clean_names() %>% 
-  DCPOtools::with_min_yrs(2)
-load(here("data", "claassen_m5_theta.rda"))
-load(here("data", "dem_mood_apsr.RData"))
-load(here("data", "dcpo_input.rda"))
-load(here("data", "dcpo_theta.rda"))
-load(here("data", "dcpo_sigma.rda"))
-#load(here("data", "dcpo_ajps_rubin.rda"))
-# df_controls <- readRDS(here("data", "control_variables_ajps.rds"))   #use control file for merging with 
-df_dcpoUncertainAPSR <- readRDS(here("data", "df_dcpoUncertainAPSR.rds"))
+# Removed the comments for the final replication file
+## Claasseen and extend data
+
+# osf_retrieve_file("hczmf") %>% 
+#     osf_download(path = "../data")
+# 
+# osf_retrieve_file("wbu6m") %>% 
+#     osf_download(path = "../data")
+# 
+# osf_retrieve_file("2jhbc") %>% 
+#     osf_download(path = "../data")
+# 
+# osf_retrieve_file("u96m8") %>% 
+#     osf_download(path = "../data")
+
+load(here("data", "pure_cls_ajps.rda")) 
+load(here("data", "pure_cls_apsr.rda")) 
+load(here("data", "exp_cls_ajps.rda"))
+load(here("data", "exp_cls_apsr.rda"))
 

### 2021-06-25 paper/dcpo_demsupport.Rmd
Add literature summary for Blackwell2017 and Blackwell2017a

@@
 The models employed in these studies' analyses, though, do not account for uncertainty in their measurement of democratic support.
+Measurement error challenges statistical analyses, especially when it is correlated with a dependent variable which is the case of democratic support, but it is often ignored in the analysis [@Blackwell2017; @Blackwell2017a].
 Because they are unobserved, latent variables are inherently accompanied by measurement uncertainty.
@@
 Although measurement uncertainty has yet not attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can bias coefficient estimates and standard errors.
+Especially when measurement error is correlated with the dependent variable, the resulting bias could either attentuate or exaggerate the magnitude of the estimated effects [see, e.g., @Blackwell2017, 360].
 In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey_policy_2018, 254].
@@
 Then we perform each analysis repeatedly on its respective collection of datasets, and combine the results following the rules set out in @Rubin1987 [see, e.g., @Schnakenberg2014; @Crabtree2015].
+Our approach of incorporating uncertainty is similar in the logic of @Blackwell2017a's multiple overimputation, that is, creating multiple data set from the posterior distribution of the true latent value, applying analysis model for each dataset, and then averaging results by using Rubin's rule.
 

### 2021-06-26 paper/dcpo_demsupport.Rmd

--- 2021-06-20 paper/dcpo_demsupport.Rmd
@@
 saveRDS(result_dcpoUncertainAPSR, file = here::here("output", "estimates_dcpoAPSR.RDS"))
-```
-
-# Replications of Full Pack of Models in Claassen 2020a,b
-
-```{r plot-fullpackAJPS, fig.cap= "The Effect of Public Support on Democracy", fig.width=7.5, fig.height=10, eval=TRUE}
-
-# Very weird phenomenon that the same type of rds files needs different ways to read
-# Suggesting using the qs or csv data type in future.
-result_cls <- readRDS(here::here("output", "estimates_clsMeanAJPS.RDS"))
-result_clsUncertain <- readRDS(here::here("output", "estimates_clsAJPS.RDS"))
-result_dcpoUncertain <- readRDS(here::here("output", "estimates_dcpoAJPS.RDS"))
-
-result_pooled <- bind_rows(
-  mutate(result_cls$pooled[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertain$pooled[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertain$pooled[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "Pooled")
-
-result_gmm <- bind_rows(
-  mutate(result_cls$gmm[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertain$gmm[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertain$gmm[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "GMM")
-
-result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = rep(
-      c("Democracy\n (t-1)",
-        "Democracy\n (t-2)",
-      "Support\n (t-1)",
-      "Log GDP\n per capita\n (t-1)",
-      "GDP per\n capita growth\n (t-1)",
-      "Regional\n democracy\n (t-1)",
-      "Percent\n Muslim\n (t-1)",
-      "Resource\n dependence\n (t-1)"),
-    time = 6), 
-    type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
-
-terms <- factor(rev(c("Democracy[t-1]",
-        "Democracy[t-2]",
-      "Support[t-1]",
-      "Log~GDP~per~capita[t-1]",
-      "GDP~per~capita~growth[t-1]",
-      "Regional~democracy[t-1]",
-      "Percent~Muslim[t-1]",
-      "Resource~dependence[t-1]")), levels =
-      rev(c("Democracy[t-1]",
-        "Democracy[t-2]",
-      "Support[t-1]",
-      "Log~GDP~per~capita[t-1]",
-      "GDP~per~capita~growth[t-1]",
-      "Regional~democracy[t-1]",
-      "Percent~Muslim[t-1]",
-      "Resource~dependence[t-1]")))
-
-# ggplot produces reversed plot, and embarrassed to say, I can't fix, again. Any thought?
-# What I've tried
-# 1. using guide_legend(reverse = TRUE) will change the legend's order not the plot.
-# 2. ordering models with factor levels using the original names or even c("1", "2", "3")
-# 2. redefining the order of model in the dataframe or in dwplot 
-# 3. checking the dwplot codes, model works in line 453, but nothing looks helpful
-# 4. Every post online is to reverse
-
-plot_AJPS1 <- dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms))) +
-  scale_color_grey(start = 0.4, end = 0.8) +
-  labs(
-    title = "DV: V-Dem Liberal Democracy Index",
-    subtitle = "Regime Compacted"
-  ) +
-  facet_wrap(~type, scales = "free_x") + 
-  theme(legend.position = "none")
-
-# the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
-# The trick is  to use guide = guide_legend(reverse = TRUE) within scale_color_*(); see below in plotAJPS2. --FS
-
-result_regime <- bind_rows(
-  mutate(result_cls$`pooled-regime`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertain$`pooled-regime`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertain$`pooled-regime`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "Pooled")
-
-result_regimeGmm <- bind_rows(
-  mutate(result_cls$`gmm-regime`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertain$`gmm-regime`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertain$`gmm-regime`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "GMM")
-
-result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = rep(
-      c("Democracy\n (t-1)",
-        "Democracy\n (t-2)",
-      "Support\n demo only\n (t-1)",
-      "Support\n auto only\n (t-1)",
-      "Log GDP\n per capita\n (t-1)",
-      "GDP per\n capita growth\n (t-1)",
-      "Regional\n democracy\n (t-1)",
-      "Percent\n Muslim\n (t-1)",
-      "Resource\n dependence\n (t-1)"),
-    time = 6), 
-    type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
-
-terms2 <- factor(rev(c("Democracy[t-1]",
-                       "Democracy[t-2]",
-                       "Support[t-1] (democracies~only)",
-                       "Support[t-1] (autocracies~only)",
-                       "Log~GDP~per~capita[t-1]",
-                       "GDP~per~capita~growth[t-1]",
-                       "Regional~democracy[t-1]",
-                       "Percent~Muslim[t-1]",
-                       "Resource~dependence[t-1]")), levels =
-                   rev(c("Democracy[t-1]",
-                         "Democracy[t-2]",
-                         "Support[t-1] (democracies~only)",
-                         "Support[t-1] (autocracies~only)",
-                         "Log~GDP~per~capita[t-1]",
-                         "GDP~per~capita~growth[t-1]",
-                         "Regional~democracy[t-1]",
-                         "Percent~Muslim[t-1]",
-                         "Resource~dependence[t-1]")))
-
-plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms2))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  labs(
-    title = "",
-    subtitle = "Regime Specific"
-  ) +
-  facet_wrap(~type, scales = "free_x") +
-  theme(legend.position = "bottom", 
-        legend.title = element_blank())
-
-legend <- get_legend(plot_AJPS2)
-
-plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
-
-grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
-
-```
-
-```{r plot-fullpackAJPSfull, fig.cap= "The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=7, eval=TRUE}
-
-# Very weird phenomenon that the same type of rds files needs different ways to read
-# Suggesting using the qs or csv data type in future.
-result_cls <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
-result_clsUncertainFull <- readRDS(here("output", "estimates_clsAJPSfullUncertain.RDS"))
-result_dcpoUncertainFull <- readRDS(here("output", "estimates_dcpoAJPSfullUncertain.RDS"))
-
-result_pooled <- bind_rows(
-  mutate(result_cls$pooled[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainFull$pooled[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainFull$pooled[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "Pooled")
-
-result_gmm <- bind_rows(
-  mutate(result_cls$gmm[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainFull$gmm[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainFull$gmm[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "GMM")
-
-result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = rep(
-      c("Democracy\n (t-1)",
-        "Democracy\n (t-2)",
-      "Support\n (t-1)",
-      "Log GDP\n per capita\n (t-1)",
-      "GDP per\n capita growth\n (t-1)",
-      "Regional\n democracy\n (t-1)",
-      "Percent\n Muslim\n (t-1)",
-      "Resource\n dependence\n (t-1)"),
-    time = 6), 
-    type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
-
-terms <- factor(rev(c("Democracy[t-1]",
-        "Democracy[t-2]",
-      "Support[t-1]",
-      "Log~GDP~per~capita[t-1]",
-      "GDP~per~capita~growth[t-1]",
-      "Regional~democracy[t-1]",
-      "Percent~Muslim[t-1]",
-      "Resource~dependence[t-1]")), levels =
-      rev(c("Democracy[t-1]",
-        "Democracy[t-2]",
-      "Support[t-1]",
-      "Log~GDP~per~capita[t-1]",
-      "GDP~per~capita~growth[t-1]",
-      "Regional~democracy[t-1]",
-      "Percent~Muslim[t-1]",
-      "Resource~dependence[t-1]")))
-
-# ggplot produces reversed plot, and embarrassed to say, I can't fix, again. Any thought?
-# What I've tried
-# 1. using guide_legend(reverse = TRUE) will change the legend's order not the plot.
-# 2. ordering models with factor levels using the original names or even c("1", "2", "3")
-# 2. redefining the order of model in the dataframe or in dwplot 
-# 3. checking the dwplot codes, model works in line 453, but nothing looks helpful
-# 4. Every post online is to reverse
-
-plot_AJPS1 <- dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms))) +
-  scale_color_grey(start = 0.4, end = 0.8) +
-  labs(
-    title = "DV: V-Dem Liberal Democracy Index",
-    subtitle = "Regime Compacted"
-  ) +
-  facet_wrap(~type, scales = "free_x") + 
-  theme(legend.position = "none")
-
-# the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
-# The trick is  to use guide = guide_legend(reverse = TRUE) within scale_color_*(); see below in plotAJPS2. --FS
-
-result_regime <- bind_rows(
-  mutate(result_cls$`pooled-regime`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainFull$`pooled-regime`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainFull$`pooled-regime`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "Pooled")
-
-result_regimeGmm <- bind_rows(
-  mutate(result_cls$`gmm-regime`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainFull$`gmm-regime`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainFull$`gmm-regime`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "GMM")
-
-result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = rep(
-      c("Democracy\n (t-1)",
-        "Democracy\n (t-2)",
-      "Support\n demo only\n (t-1)",
-      "Support\n auto only\n (t-1)",
-      "Log GDP\n per capita\n (t-1)",
-      "GDP per\n capita growth\n (t-1)",
-      "Regional\n democracy\n (t-1)",
-      "Percent\n Muslim\n (t-1)",
-      "Resource\n dependence\n (t-1)"),
-    time = 6), 
-    type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
-
-terms2 <- factor(rev(c("Democracy[t-1]",
-                       "Democracy[t-2]",
-                       "Support[t-1] (democracies~only)",
-                       "Support[t-1] (autocracies~only)",
-                       "Log~GDP~per~capita[t-1]",
-                       "GDP~per~capita~growth[t-1]",
-                       "Regional~democracy[t-1]",
-                       "Percent~Muslim[t-1]",
-                       "Resource~dependence[t-1]")), levels =
-                   rev(c("Democracy[t-1]",
-                         "Democracy[t-2]",
-                         "Support[t-1] (democracies~only)",
-                         "Support[t-1] (autocracies~only)",
-                         "Log~GDP~per~capita[t-1]",
-                         "GDP~per~capita~growth[t-1]",
-                         "Regional~democracy[t-1]",
-                         "Percent~Muslim[t-1]",
-                         "Resource~dependence[t-1]")))
-
-plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms2))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  labs(
-    title = "",
-    subtitle = "Regime Specific"
-  ) +
-  facet_wrap(~type, scales = "free_x") +
-  theme(legend.position = "bottom", 
-        legend.title = element_blank())
-
-legend <- get_legend(plot_AJPS2)
-
-plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
-
-grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
-
-```
-
-```{r plot-fullpackAPSR, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO", fig.width=7.5, fig.height=10, eval=TRUE}
-
-result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
-result_clsUncertainAPSR <- readRDS(here("output", "estimates_clsAPSR.RDS"))
-result_dcpoUncertainAPSR <- readRDS(here("output", "estimates_dcpoAPSR.RDS"))
-
-# Regime compacted ####
-
-result_ecm1 <- bind_rows(
-  mutate(result_clsAPSR$pooled1[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainAPSR$pooled1[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainAPSR$pooled1[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "ECM")
-
-result_fd1 <- bind_rows(
-  mutate(result_clsAPSR$fd1[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainAPSR$fd1[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainAPSR$fd1[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "First Difference")
-
-result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-      "Liberal Democracy\n (Difference)",
-      "Liberal Democracy\n (t-1)",
-      "Log GDP\n per capita\n (Difference)",
-      "Log GDP\n (t-1)"),
-    time = 3),
-    rep(
-      c("Liberal Democracy\n (Difference)", 
-        "Log GDP\n per capita\n (Difference)"), 
-      time = 3
-    )),
-    type = factor(type, levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
-  )
-
-terms1 <- factor(rev(c("Support[t-1]",
-                      "Support[t-2]",
-                      "Delta~Liberal~democracy",
-                      "Liberal~democracy[t-1]",
-                      "Delta~Log~GDP~per~capita",
-                      "Log~GDP[t-1]")),
-                levels = rev(c("Support[t-1]",
-                               "Support[t-2]",
-                               "Delta~Liberal~democracy",
-                               "Liberal~democracy[t-1]",
-                               "Delta~Log~GDP~per~capita",
-                               "Log~GDP[t-1]")))
-
-plot_APSR1 <- dwplot(result_APSR1, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms1))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  # scale_color_uiowa(name = "", palette = "digitMixed") +
-  labs(
-    title = "DV: Public Support for Democracy",
-    subtitle = "Regime Compacted"
-  ) +
-  facet_wrap(~type, scales = "free_x") + 
-  theme(legend.position = "none")
-
-result_ecm2 <- bind_rows(
-  mutate(result_clsAPSR$pooled2[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainAPSR$pooled2[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainAPSR$pooled2[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "ECM")
-
-result_fd2 <- bind_rows(
-  mutate(result_clsAPSR$fd2[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainAPSR$fd2[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainAPSR$fd2[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "First Difference")
-
-result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-      "Liberal Democracy\n (Difference)",
-      "Liberal Democracy\n (t-1)",
-      "Log GDP\n per capita\n (Difference)",
-      "Log GDP\n (t-1)",
-      "Corruption\n (Difference)",
-      "Corruption\n (t-1)"
-      ),
-    time = 3),
-    rep(
-      c("Liberal Democracy\n (Difference)", 
-        "Log GDP\n per capita\n (Difference)",
-        "Corruption\n (Difference)"), 
-      time = 3
-    )),
-    type = factor(type, levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
-  )
-
-terms2 <- factor(rev(c("Support[t-1]",
-                      "Support[t-2]",
-                      "Delta~Liberal~democracy",
-                      "Liberal~democracy[t-1]",
-                      "Delta~Log~GDP~per~capita",
-                      "Log~GDP[t-1]",
-                      "Delta~Corruption",
-                      "Corruption[t-1]")),
-                levels = rev(c("Support[t-1]",
-                               "Support[t-2]",
-                               "Delta~Liberal~democracy",
-                               "Liberal~democracy[t-1]",
-                               "Delta~Log~GDP~per~capita",
-                               "Log~GDP[t-1]",
-                               "Delta~Corruption",
-                               "Corruption[t-1]")))
-
-plot_APSR2 <- dwplot(result_APSR2, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms2))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  # scale_color_uiowa(name = "", palette = "digitMixed") +
-  labs(
-    title = "",
-    subtitle = "W. Corruption"
-  ) +
-  facet_wrap(~type, scales = "free_x") +
-  theme(legend.position = "none")
-
-# Regime specified ####
-
-result_ecmReg1 <- bind_rows(
-  mutate(result_clsAPSR$`pooled-regime1`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainAPSR$`pooled-regime1`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainAPSR$`pooled-regime1`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "ECM")
-
-result_fdReg1 <- bind_rows(
-  mutate(result_clsAPSR$`fd-regime1`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainAPSR$`fd-regime1`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainAPSR$`fd-regime1`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "First Difference")
-
-result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-      "Electoral Democracy\n (Difference)",
-      "Electoral Democracy\n (t-1)",
-      "Minoritarian Democracy\n (Difference)",
-      "Minoritarian Democracy\n (t-1)",
-      "Log GDP\n per capita\n (Difference)",
-      "Log GDP\n (t-1)"),
-    time = 3),
-    rep(
-      c("Electoral Democracy\n (Difference)", 
-        "Minoritarian Democracy\n (Difference)",
-        "Log GDP\n per capita\n (Difference)"), 
-      time = 3
-    )),
-    type = factor(type, levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
-  )
-
-terms3 <- factor(rev(c("Support[t-1]",
-                      "Support[t-2]",
-                      "Delta~Electoral~democracy",
-                      "Electoral~democracy[t-1]",
-                      "Delta~Minoritarian~democracy",
-                      "Minoritarian~democracy[t-1]",
-                      "Delta~Log~GDP~per~capita",
-                      "Log~GDP[t-1]")),
-                levels = rev(c("Support[t-1]",
-                      "Support[t-2]",
-                      "Delta~Electoral~democracy",
-                      "Electoral~democracy[t-1]",
-                      "Delta~Minoritarian~democracy",
-                      "Minoritarian~democracy[t-1]",
-                      "Delta~Log~GDP~per~capita",
-                      "Log~GDP[t-1]")))
-
-plot_RegAPSR1 <- dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms3))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  # scale_color_uiowa(name = "", palette = "digitMixed") +
-  labs(
-    title = "",
-    subtitle = "Regime Specified"
-  ) +
-  facet_wrap(~type, scales = "free_x") + 
-  theme(legend.position = "none")
-
-result_ecmReg2 <- bind_rows(
-  mutate(result_clsAPSR$`pooled-regime2`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainAPSR$`pooled-regime2`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainAPSR$`pooled-regime2`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "ECM")
-
-result_fdReg2 <- bind_rows(
-  mutate(result_clsAPSR$`fd-regime2`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainAPSR$`fd-regime2`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainAPSR$`fd-regime2`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "First Difference")
-
-result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-      "Electoral Democracy\n (Difference)",
-      "Electoral Democracy\n (t-1)",
-      "Minoritarian Democracy\n (Difference)",
-      "Minoritarian Democracy\n (t-1)",
-      "Log GDP\n per capita\n (Difference)",
-      "Log GDP\n (t-1)",
-      "Corruption\n (Difference)",
-      "Corruption\n (t-1)"
-      ),
-    time = 3),
-    rep(
-      c("Electoral Democracy\n (Difference)", 
-        "Minoritarian Democracy\n (Difference)",
-        "Log GDP\n per capita\n (Difference)",
-        "Corruption\n (Difference)"), 
-      time = 3
-    )),
-    type = factor(type, levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
-  )
-
-terms4 <- factor(rev(c("Support[t-1]",
-                      "Support[t-2]",
-                      "Delta~Electoral~democracy",
-                      "Electoral~democracy[t-1]",
-                      "Delta~Minoritarian~democracy",
-                      "Minoritarian~democracy[t-1]",
-                      "Delta~Log~GDP",
-                      "Log~GDP[t-1]",
-                      "Delta~Corruption",
-                      "Corruption[t-1]")),
-                levels = rev(c("Support[t-1]",
-                               "Support[t-2]",
-                               "Delta~Electoral~democracy",
-                               "Electoral~democracy[t-1]",
-                               "Delta~Minoritarian~democracy",
-                               "Minoritarian~democracy[t-1]",
-                               "Delta~Log~GDP",
-                               "Log~GDP[t-1]",
-                               "Delta~Corruption",
-                               "Corruption[t-1]")))
-
-plot_RegAPSR2 <- dwplot(result_RegAPSR2, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms4))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  # scale_color_uiowa(name = "", palette = "digitMixed") +
-  labs(
-    title = "",
-    subtitle = "Regime Specified w. Corruption"
-  ) +
-  facet_wrap(~type, scales = "free_x") +
-  theme(legend.position = "bottom", 
-        legend.title = element_blank())
-
-legend <- get_legend(plot_RegAPSR2)
-
-plot_RegAPSR2 <- plot_RegAPSR2 + theme(legend.position = "none")
-
-grid.arrange(plot_APSR1, plot_APSR2, plot_RegAPSR1, plot_RegAPSR2, legend, ncol = 1)
-```
-
-```{r plot-fullpackAPSRfull, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10, eval=TRUE}
-
-result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
-result_clsFullUncertainAPSR <- readRDS(here("output", "estimates_clsFullUncertainAPSR.RDS"))
-result_dcpoFullUncertainAPSR <- readRDS(here("output", "estimates_dcpoUncertainAPSR.RDS"))
-
-# Regime compacted ####
-
-result_ecm1 <- bind_rows(
-  mutate(result_clsAPSR$pooled1[[1]], model = "Claassen 2020a"),
-  mutate(result_clsFullUncertainAPSR$pooled1[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoFullUncertainAPSR$pooled1[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "ECM")
-
-result_fd1 <- bind_rows(
-  mutate(result_clsAPSR$fd1[[1]], model = "Claassen 2020a"),
-  mutate(result_clsFullUncertainAPSR$fd1[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoFullUncertainAPSR$fd1[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "First Difference")
-
-result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-      "Liberal Democracy\n (Difference)",
-      "Liberal Democracy\n (t-1)",
-      "Log GDP\n per capita\n (Difference)",
-      "Log GDP\n (t-1)"),
-    time = 3),
-    rep(
-      c("Liberal Democracy\n (Difference)", 
-        "Log GDP\n per capita\n (Difference)"), 
-      time = 3
-    )),
-    type = factor(type, levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
-  )
-
-terms1 <- factor(rev(c("Support[t-1]",
-                      "Support[t-2]",
-                      "Delta~Liberal~democracy",
-                      "Liberal~democracy[t-1]",
-                      "Delta~Log~GDP~per~capita",
-                      "Log~GDP[t-1]")),
-                levels = rev(c("Support[t-1]",
-                               "Support[t-2]",
-                               "Delta~Liberal~democracy",
-                               "Liberal~democracy[t-1]",
-                               "Delta~Log~GDP~per~capita",
-                               "Log~GDP[t-1]")))
-
-plot_APSR1 <- dwplot(result_APSR1, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms1))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  # scale_color_uiowa(name = "", palette = "digitMixed") +
-  labs(
-    title = "DV: Public Support for Democracy",
-    subtitle = "Regime Compacted"
-  ) +
-  facet_wrap(~type, scales = "free_x") + 
-  theme(legend.position = "none")
-
-result_ecm2 <- bind_rows(
-  mutate(result_clsAPSR$pooled2[[1]], model = "Claassen 2020a"),
-  mutate(result_clsFullUncertainAPSR$pooled2[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoFullUncertainAPSR$pooled2[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "ECM")
-
-result_fd2 <- bind_rows(
-  mutate(result_clsAPSR$fd2[[1]], model = "Claassen 2020a"),
-  mutate(result_clsFullUncertainAPSR$fd2[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoFullUncertainAPSR$fd2[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "First Difference")
-
-result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-      "Liberal Democracy\n (Difference)",
-      "Liberal Democracy\n (t-1)",
-      "Log GDP\n per capita\n (Difference)",
-      "Log GDP\n (t-1)",
-      "Corruption\n (Difference)",
-      "Corruption\n (t-1)"
-      ),
-    time = 3),
-    rep(
-      c("Liberal Democracy\n (Difference)", 
-        "Log GDP\n per capita\n (Difference)",
-        "Corruption\n (Difference)"), 
-      time = 3
-    )),
-    type = factor(type, levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
-  )
-
-terms2 <- factor(rev(c("Support[t-1]",
-                      "Support[t-2]",
-                      "Delta~Liberal~democracy",
-                      "Liberal~democracy[t-1]",
-                      "Delta~Log~GDP~per~capita",
-                      "Log~GDP[t-1]",
-                      "Delta~Corruption",
-                      "Corruption[t-1]")),
-                levels = rev(c("Support[t-1]",
-                               "Support[t-2]",
-                               "Delta~Liberal~democracy",
-                               "Liberal~democracy[t-1]",
-                               "Delta~Log~GDP~per~capita",
-                               "Log~GDP[t-1]",
-                               "Delta~Corruption",
-                               "Corruption[t-1]")))
-
-plot_APSR2 <- dwplot(result_APSR2, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms2))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  # scale_color_uiowa(name = "", palette = "digitMixed") +
-  labs(
-    title = "",
-    subtitle = "W. Corruption"
-  ) +
-  facet_wrap(~type, scales = "free_x") +
-  theme(legend.position = "none")
-
-# Regime specified ####
-
-result_ecmReg1 <- bind_rows(
-  mutate(result_clsAPSR$`pooled-regime1`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsFullUncertainAPSR$`pooled-regime1`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoFullUncertainAPSR$`pooled-regime1`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "ECM")
-
-result_fdReg1 <- bind_rows(
-  mutate(result_clsAPSR$`fd-regime1`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsFullUncertainAPSR$`fd-regime1`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoFullUncertainAPSR$`fd-regime1`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "First Difference")
-
-result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-      "Electoral Democracy\n (Difference)",
-      "Electoral Democracy\n (t-1)",
-      "Minoritarian Democracy\n (Difference)",
-      "Minoritarian Democracy\n (t-1)",
-      "Log GDP\n per capita\n (Difference)",
-      "Log GDP\n (t-1)"),
-    time = 3),
-    rep(
-      c("Electoral Democracy\n (Difference)", 
-        "Minoritarian Democracy\n (Difference)",
-        "Log GDP\n per capita\n (Difference)"), 
-      time = 3
-    )),
-    type = factor(type, levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
-  )
-
-terms3 <- factor(rev(c("Support[t-1]",
-                      "Support[t-2]",
-                      "Delta~Electoral~democracy",
-                      "Electoral~democracy[t-1]",
-                      "Delta~Minoritarian~democracy",
-                      "Minoritarian~democracy[t-1]",
-                      "Delta~Log~GDP~per~capita",
-                      "Log~GDP[t-1]")),
-                levels = rev(c("Support[t-1]",
-                      "Support[t-2]",
-                      "Delta~Electoral~democracy",
-                      "Electoral~democracy[t-1]",
-                      "Delta~Minoritarian~democracy",
-                      "Minoritarian~democracy[t-1]",
-                      "Delta~Log~GDP~per~capita",
-                      "Log~GDP[t-1]")))
-
-plot_RegAPSR1 <- dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms3))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  # scale_color_uiowa(name = "", palette = "digitMixed") +
-  labs(
-    title = "",
-    subtitle = "Regime Specified"
-  ) +
-  facet_wrap(~type, scales = "free_x") + 
-  theme(legend.position = "none")
-
-result_ecmReg2 <- bind_rows(
-  mutate(result_clsAPSR$`pooled-regime2`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsFullUncertainAPSR$`pooled-regime2`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoFullUncertainAPSR$`pooled-regime2`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "ECM")
-
-result_fdReg2 <- bind_rows(
-  mutate(result_clsAPSR$`fd-regime2`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsFullUncertainAPSR$`fd-regime2`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoFullUncertainAPSR$`fd-regime2`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "First Difference")
-
-result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-      "Electoral Democracy\n (Difference)",
-      "Electoral Democracy\n (t-1)",
-      "Minoritarian Democracy\n (Difference)",
-      "Minoritarian Democracy\n (t-1)",
-      "Log GDP\n per capita\n (Difference)",
-      "Log GDP\n (t-1)",
-      "Corruption\n (Difference)",
-      "Corruption\n (t-1)"
-      ),
-    time = 3),
-    rep(
-      c("Electoral Democracy\n (Difference)", 
-        "Minoritarian Democracy\n (Difference)",
-        "Log GDP\n per capita\n (Difference)",
-        "Corruption\n (Difference)"), 
-      time = 3
-    )),
-    type = factor(type, levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
-  )
-
-terms4 <- factor(rev(c("Support[t-1]",
-                      "Support[t-2]",
-                      "Delta~Electoral~democracy",
-                      "Electoral~democracy[t-1]",
-                      "Delta~Minoritarian~democracy",
-                      "Minoritarian~democracy[t-1]",
-                      "Delta~Log~GDP",
-                      "Log~GDP[t-1]",
-                      "Delta~Corruption",
-                      "Corruption[t-1]")),
-                levels = rev(c("Support[t-1]",
-                               "Support[t-2]",
-                               "Delta~Electoral~democracy",
-                               "Electoral~democracy[t-1]",
-                               "Delta~Minoritarian~democracy",
-                               "Minoritarian~democracy[t-1]",
-                               "Delta~Log~GDP",
-                               "Log~GDP[t-1]",
-                               "Delta~Corruption",
-                               "Corruption[t-1]")))
-
-plot_RegAPSR2 <- dwplot(result_RegAPSR2, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms4))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  # scale_color_uiowa(name = "", palette = "digitMixed") +
-  labs(
-    title = "",
-    subtitle = "Regime Specified w. Corruption"
-  ) +
-  facet_wrap(~type, scales = "free_x") +
-  theme(legend.position = "bottom", 
-        legend.title = element_blank())
-
-legend <- get_legend(plot_RegAPSR2)
-
-plot_RegAPSR2 <- plot_RegAPSR2 + theme(legend.position = "none")
-
-grid.arrange(plot_APSR1, plot_APSR2, plot_RegAPSR1, plot_RegAPSR2, legend, ncol = 1)
 ```
@@
 ```
+
+>>>>>>> 7257990cf1c7c4951fc068aacaa22c22bc503a86

### 2021-06-26 paper/dcpo_demsupport_appendix.Rmd

@@
 
-```{r expanded_claassen}
+```{r expanded_claassen_ajps}
 # these are estimates based on Claassen's original dataset, plus all additional country-year-item observations we found; see
@@
 
-```{r apsr_1k}
+```{r expanded_claassen_apsr}
 ec_df_theta_apsr <- purrr::map(1:1000, function(x) {

### 2021-06-29 paper/dcpo_demsupport.Rmd

--- 2021-06-25 paper/dcpo_demsupport.Rmd
@@
 ## Claasseen and extend data
-
+# 
 # osf_retrieve_file("hczmf") %>%
@@
 # osf_retrieve_file("u96m8") %>%
-#     osf_download(path = "../data")
+#     osf_download(path = "../data", conflicts = "overwrite")
 
@@
 
-```{r cls-pointAJPS}
+```{r pointAJPS}
 ls_iv <- c("plm::lag(SupDem_trim, 1)",
@@
 
-```{r cls-modelAJPS}
+```{r model-AJPS}
 
@@
 
-```{r cls-uncertainAJPSfull}
-result_clsUncertainFull <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
-  result <- map(cls_ajps, function(aData){ # applying to the 1000 datasets
+```{r result-pureAJPS}
+result_pureAJPS <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
+  result <- map(pure_cls_ajps, function(aData){ # applying to the 1000 datasets
     eval(parse(text = aMod))
@@
 
-names(result_clsUncertainFull) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
-
-saveRDS(result_clsUncertainFull, file = here::here("output", "estimates_clsAJPSfullUncertain.RDS"))
-```
-
-```{r dcpo-modelAJPS}
-#ls_iv <- c("plm::lag(theta, 1)", 
-#    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) ")
-
-ls_iv <- c("plm::lag(theta_trim, 1)", 
-    "plm::lag(theta_dem_trim, 1) + plm::lag(theta_aut_trim, 1) ") #use trimmed data
-
-ls_method <- c("plm", "pgmm")
-
-ls_eq <- glue("Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + {ls_iv} + plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) + plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)")
-
-ls_mod_ajpsDCPO <- c(
-    glue("plm({ls_eq}, model = 'pooling', data = aData)"),
-    glue(
-        "pgmm({ls_eq} | plm::lag(Vdem_libdem, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
-    )
-)
-```
-
-```{r dcpo-uncertainAJPSfull}
-result_dcpoUncertainFull <- map(ls_mod_ajpsDCPO, function(aMod){ # reading a model
-  result <- map(dcpo_ajps, function(aData){ # applying to the 1000 datasets
+names(result_pureAJPS) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
+
+saveRDS(result_pureAJPS, file = here::here("output", "estimates_clsPureAJPS.RDS"))
+```
+
+```{r result-expAJPS}
+result_expAJPS <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
+  result <- map(exp_cls_ajps, function(aData){ # applying to the 1000 datasets
     eval(parse(text = aMod))
@@
 
-names(result_dcpoUncertainFull) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
-
-saveRDS(result_dcpoUncertainFull, file = here::here("output", "estimates_dcpoAJPSfullUncertain.RDS"))
+names(result_expAJPS) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
+
+saveRDS(result_expAJPS, file = here::here("output", "estimates_clsExpAJPS.RDS"))
 ```
@@
   `plm::lag(SupDem_trim, 1)` = "Support[t-1]",
-  `plm::lag(theta_trim, 1)` = "Support[t-1]",
+  `plm::lag(theta, 1)` = "Support[t-1]",
   `plm::lag(SupDem_Democ, 1)` = "Support[t-1](demo~only)",
@@
 result_cls <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
-result_clsUncertainFull <- readRDS(here("output", "estimates_clsAJPSfullUncertain.RDS"))
-result_dcpoUncertainFull <- readRDS(here("output", "estimates_dcpoAJPSfullUncertain.RDS"))
+result_pureAJPS <- readRDS(here("output", "estimates_clsPureAJPS.RDS"))
+result_expAJPS <- readRDS(here("output", "estimates_clsExpAJPS.RDS"))
 
 type_model <-
-  c("Claassen 2019", "Claassen Uncertainty", "DCPO Uncertainty")
+  c("Original", "Uncertainty", "Uncertainty+Expanded Data")
 
@@
   list(result_cls,
-       result_clsUncertainFull,
-       result_dcpoUncertainFull) %>%
+       result_pureAJPS,
+       result_expAJPS) %>%
   map2_df(type_model, ~ {
@@
 
-```{r cls-pointAPSR}
+```{r pointAPSR}
 load(here::here("data", "dem_mood_apsr.RData"))
@@
 
-```{r cls-modelAPSR}
+```{r model-APSR}
 ls_ivECM <- c("diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)", 
@@
 
-```{r cls-uncertainAPSRfull}
-result_clsFullUncertainAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
-  result <- map(cls_apsr, function(aData){ # applying to the 1000 datasets
+```{r result-pureAPSR}
+result_pureAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
+  result <- map(pure_cls_apsr, function(aData){ # applying to the 1000 datasets
     eval(parse(text = aMod))
@@
 
-names(result_clsFullUncertainAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", "fd1", "fd-regime1", "fd2", "fd-regime2")
-
-saveRDS(result_clsFullUncertainAPSR, file = here("output", "estimates_clsFullUncertainAPSR.RDS"))
-```
-
-```{r dcpo-modelAPSR}
-ls_ivECM <- c("diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1)", 
-              "diff(Vdem_polyarchy_z, lag = 1) + plm::lag(Vdem_polyarchy_z, 1) + diff(Vdem_liberal_z, lag = 1) + plm::lag(Vdem_liberal_z, 1)")
-ls_ctrlECM <- c("", " + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1)")
-
-ls_eqECM <- glue("diff(theta_trim, lag = 1) ~ plm::lag(theta_trim, 1:2) + {ls_ivECM} + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1)") %>% 
-  outer(ls_ctrlECM, paste0) %>% 
-  as.vector()
-
-ls_ivFD <- c("Vdem_libdem_z",
-             "Vdem_polyarchy_z + Vdem_liberal_z")
-
-ls_ctrlFD <- c("", " + corruption_z")
-
-ls_eqFD <- glue("theta_trim ~ {ls_ivFD} + lg_imp_mdpgdp") %>% 
-  outer(ls_ctrlFD, paste0) %>% 
-  as.vector()
-
-ls_mod_apsrDCPO <- c(
-  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
-  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
-)
-```
-
-```{r dcpo-uncertainAPSRfull}
-result_dcpoUncertainAPSR <- map(ls_mod_apsrDCPO, function(aMod){ # reading a model
-  result <- map(dcpo_apsr, function(aData){ # applying to the 1000 datasets
+names(result_pureAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", "fd1", "fd-regime1", "fd2", "fd-regime2")
+
+saveRDS(result_pureAPSR, file = here("output", "estimates_clsPureAPSR.RDS"))
+```
+
+```{r result-expAPSR}
+result_expAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
+  result <- map(exp_cls_apsr, function(aData){ # applying to the 1000 datasets
     eval(parse(text = aMod))
@@
 
-  result_dcpoUncertainAPSR <- list(tidy_dcpoUncertainAPSR, glance_dcpoUncertainAPSR)
-})
-
-names(result_dcpoUncertainAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",  "fd1", "fd-regime1", "fd2", "fd-regime2")
-
-saveRDS(result_dcpoUncertainAPSR, file = here("output", "estimates_dcpoUncertainAPSR.RDS"))
+  result_expAPSR <- list(tidy_dcpoUncertainAPSR, glance_dcpoUncertainAPSR)
+})
+
+names(result_expAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",  "fd1", "fd-regime1", "fd2", "fd-regime2")
+
+saveRDS(result_expAPSR, file = here("output", "estimates_clsExpAPSR.RDS"))
 ```
@@
 result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
-result_clsFullUncertainAPSR <- readRDS(here("output", "estimates_clsFullUncertainAPSR.RDS"))
-result_dcpoUncertainAPSR <- readRDS(here("output", "estimates_dcpoUncertainAPSR.RDS"))
+result_pureAPSR <- readRDS(here("output", "estimates_clsFullUncertainAPSR.RDS"))
+result_expAPSR <- readRDS(here("output", "estimates_clsExpAPSR.RDS"))
 
@@
   list(result_clsAPSR,
-       result_clsFullUncertainAPSR,
-       result_dcpoUncertainAPSR) %>%
+       result_pureAPSR,
+       result_expAPSR) %>%
   map2_df(type_model, ~ {
@@
 
-```{r num-cls2020a, results='asis'}
-tb_result_cls <- map(result_cls, ~ {
-  names(.) <- c("tidy", "glance")
-  class(.) <- "modelsummary_list"
-  return(.)})
-
-names(tb_result_cls) <- c("Pooled", "Pooled-Regime", 
-                          "GMM", "GMM-Regime")
-
+```{r num-labelAJPS}
 names_coef <- c(
@@
 )
+```
+
+```{r num-pointAJPS, results='asis'}
+tb_result_cls <- map(result_cls, ~ {
+  names(.) <- c("tidy", "glance")
+  class(.) <- "modelsummary_list"
+  return(.)})
+
+names(tb_result_cls) <- c("Pooled", "Pooled-Regime", 
+                          "GMM", "GMM-Regime")
 
@@
 
-```{r num-cls2020aUncertain, results='asis'}
-tb_result_clsUncertain <- map(result_clsUncertain, ~ {
+```{r num-pureAJPS, results='asis'}
+tb_result_pureAJPS <- map(result_pureAJPS, ~ {
   names(.) <- c("tidy", "glance")
@@
 
-names_coef <- c(
-  "plm::lag(Libdem_VD, 1:2)1" = "Democracy[t-1]",
-  "plm::lag(Libdem_VD, 1:2)2"  = "Democracy[t-2]",
-  "plm::lag(theta, 1)" = "Support[t-1]",
-  "plm::lag(theta_dem, 1)" = "Support in Democracy",
-  "plm::lag(theta_aut, 1)" = "Support in Autocracy",
-  "plm::lag(lnGDP_imp, 1)" = "Log~GDP~per~capita[t-1]",
-  "plm::lag(GDP_imp_grth, 1)"  = "GDP~per~capita~growth[t-1]",
-  "plm::lag(Libdem_regUN, 1)" = "Regional~democracy[t-1]",
-  "plm::lag(Pr_Muslim, 1)" = "Percent~Muslim[t-1]",
-  "plm::lag(Res_cp_WDI_di, 1)" = "Resource~dependence[t-1]"
-)
-
-modelsummary(tb_result_clsUncertain, 
+modelsummary(tb_result_pureAJPS, 
              statistic = "conf.int",
@@
 
-```{r num-cls2020aDCPO, results='asis'}
-tb_result_DCPO <- map(result_dcpoUncertain, ~ {
+```{r num-expAJPS, results='asis'}
+tb_result_expAJPS <- map(result_expAJPS, ~ {
   names(.) <- c("tidy", "glance")
@@
 
-names(tb_result_DCPO) <- c("Pooled", "Pooled-Regime", 
+names(tb_result_expAJPS) <- c("Pooled", "Pooled-Regime", 
                           "GMM", "GMM-Regime")
 
-names_coef <- c(
-  "plm::lag(Vdem_libdem, 1:2)1" = "Democracy[t-1]",
-  "plm::lag(Vdem_libdem, 1:2)2"  = "Democracy[t-2]",
-  "plm::lag(theta, 1)" = "Support[t-1]",
-  "plm::lag(theta_dem, 1)" = "Support in Democracy",
-  "plm::lag(theta_aut, 1)" = "Support in Autocracy",
-  "plm::lag(lg_imp_mdpgdp, 1)" = "Log~GDP~per~capita[t-1]",
-  "plm::lag(mdprgdp_grwth, 1)"  = "GDP~per~capita~growth[t-1]",
-  "plm::lag(Region_libdem, 1)" = "Regional~democracy[t-1]",
-  "plm::lag(muslism_prop_2010, 1)" = "Percent~Muslim[t-1]",
-  "plm::lag(dependence_pc_di, 1)" = "Resource~dependence[t-1]"
-)
-
-modelsummary(tb_result_DCPO, 
+modelsummary(tb_result_expAJPS, 
              statistic = "conf.int",
@@
 
-```{r num-cls2020b, results='asis'}
-tb_result_clsAPSR <- map(result_clsAPSR, ~ {
-  names(.) <- c("tidy", "glance")
-  class(.) <- "modelsummary_list"
-  return(.)}) %>% 
-  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
-      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]
-
-names(tb_result_clsAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
-
+```{r num-labelAPSR}
 names_coef <- c(
@@
 )
+```
+
+```{r num-pointAPSR, results='asis'}
+tb_result_clsAPSR <- map(result_clsAPSR, ~ {
+  names(.) <- c("tidy", "glance")
+  class(.) <- "modelsummary_list"
+  return(.)}) %>% 
+  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
+      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]
+
+names(tb_result_clsAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
 
@@
 
-```{r num-cls2020bUncertain, results='asis'}
-tb_result_clsUncertainAPSR <- map(result_clsUncertainAPSR, ~ {
+```{r num-pureAPSR, results='asis'}
+tb_result_pureAPSR <- map(result_pureAPSR, ~ {
   names(.) <- c("tidy", "glance")
@@
 
-names(tb_result_clsUncertainAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
-
-names_coef <- c(
-  "(Intercept)" = "(Intercept)",
-  "plm::lag(SupDem_trim, 1:2)1" = "Democratic\n Mood\n (t-1)",
-  "plm::lag(SupDem_trim, 1:2)2" = "Democratic\n Mood\n (t-2)",
-  "diff(Libdem_z, lag = 1)" = "Liberal\n Democracy\n (Difference)",
-  "Libdem_z" = "Liberal\n Democracy\n (Difference)",
-  "plm::lag(Libdem_z, 1)" = "Liberal\n Democracy\n (t-1)",
-  "diff(Polyarchy_z, lag = 1)" = "Electoral\n Democracy\n (Difference)",
-  "Polyarchy_z" = "Electoral\n Democracy\n (Difference)",
-  "plm::lag(Polyarchy_z, 1)" = "Electoral\n Democracy\n (t-1)",
-  "diff(Liberal_z, lag = 1)" = "Minoritarian\n Democracy\n (Difference)",
-  "Liberal_z" = "Minoritarian\n Democracy\n (Difference)",
-  "plm::lag(Liberal_z, 1)" = "Minoritarian\n Democracy\n (t-1)",
-  "diff(lnGDP_imp, lag = 1)" = "Log GDP\n per capita\n (Difference)",
-  "lnGDP_imp" = "Log GDP\n per capita\n (Difference)",
-  "plm::lag(lnGDP_imp, 1)" = "Log GDP\n (t-1)",
-  "diff(Corrup_TI_z, lag = 1)" = "Corruption\n (Difference)",
-  "Corrup_TI_z" = "Corruption\n (Difference)",
-  "plm::lag(Corrup_TI_z, 1)" = "Corruption\n (t-1)"
-)
-
-modelsummary(tb_result_clsUncertainAPSR, 
+names(tb_result_pureAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
+
+modelsummary(tb_result_pureAPSR, 
              statistic = "conf.int",
@@
 
-```{r num-cls2020bDCPO, results='asis'}
-tb_result_dcpoAPSR <- map(result_dcpoAPSR, ~ {
+```{r num-expAPSR, results='asis'}
+tb_result_expAPSR <- map(result_expAPSR, ~ {
   names(.) <- c("tidy", "glance")
@@
 
-names(tb_result_dcpoAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
-
-names_coef <- c(
-  "(Intercept)" = "(Intercept)",
-  "plm::lag(theta, 1:2)1" = "Democratic\n Mood\n (t-1)",
-  "plm::lag(theta, 1:2)2" = "Democratic\n Mood\n (t-2)",
-
-  "diff(Vdem_libdem_z, lag = 1)" = "Liberal\n Democracy\n (Difference)",
-  "Vdem_libdem_z" = "Liberal\n Democracy\n (Difference)",
-  "plm::lag(Vdem_libdem_z, 1)" = "Liberal\n Democracy\n (t-1)",
-
-  "diff(Vdem_polyarchy_z, lag = 1)" = "Electoral\n Democracy\n (Difference)",
-  "Vdem_polyarchy_z" = "Electoral\n Democracy\n (Difference)",
-  "plm::lag(Vdem_polyarchy_z, 1)" = "Electoral\n Democracy\n (t-1)",
-  "diff(Vdem_liberal_z, lag = 1)" = "Minoritarian\n Democracy\n (Difference)",
-  "Vdem_liberal_z" = "Minoritarian\n Democracy\n (Difference)",
-  "plm::lag(Vdem_liberal_z, 1)" = "Minoritarian\n Democracy\n (t-1)",
-  "diff(lg_imp_mdpgdp, lag = 1)" = "Log GDP\n per capita\n (Difference)",
-  "lg_imp_mdpgdp" = "Log GDP\n per capita\n (Difference)",
-  "plm::lag(lg_imp_mdpgdp, 1)" = "Log GDP\n (t-1)",
-  "diff(corruption_z, lag = 1)" = "Corruption\n (Difference)",
-  "corruption_z" = "Corruption\n (Difference)",
-  "plm::lag(corruption_z, 1)" = "Corruption\n (t-1)"
-)
-
-modelsummary(tb_result_dcpoAPSR, 
+names(tb_result_expAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
+
+modelsummary(tb_result_expAPSR, 
              statistic = "conf.int",
@@
 \elandscape
-
-```{r datawitherrors}
-
-ls_country <- unique(claassen_replication$country)
-first_year <- min(claassen_replication$year)
-
-df_cls_errors <- purrr::map(1:900, function(anEntry) {
-  claassen_m5_theta$theta[anEntry,,] %>%
-    reformat_dcpo_output("theta")  %>%
-    mutate(iter = anEntry) 
-  }
-  )
-
-cls_theta_uncertainty <- bind_rows(df_cls_errors)
-saveRDS(cls_theta_uncertainty,"data/cls_theta_uncertainty.rds")
-
-ls_country <- levels(dcpo_input$data$kk)
-first_year <- min(dcpo_input$data$year)
-
-df_dcpo <- purrr::map_df(1:900, function(anEntry) {
-  dcpo_theta$theta[anEntry,,] %>%
-    reformat_dcpo_output("theta") %>%
-    mutate(iter = anEntry) %>%
-    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
-              by = c("year", "country"))
-})
-
-saveRDS(df_dcpo,"dcpo_theta_uncertainty.rds")
-
-cntrl_ajps_uncertainty <- readRDS("data/cntrl_ajps_uncertainty.rds")
-
-dcpo_analysis <- left_join(df_dcpo,cntrl_ajps_uncertainty, by=c("country","year","iter"="iter_se") )
-saveRDS(dcpo_analysis, "data/dcpo_analysis_ajps.rds")
-
-dcpo_apsr_cntrl <- readRDS("data/cntrl_apsr_uncertainty.rds")
-dcpo_apsr_analysis <- left_join(df_dcpo,dcpo_apsr_cntrl, by=c("country","year","iter"="iter_se") )
-saveRDS(dcpo_apsr_analysis, "data/dcpo_analysis_apsr.rds")
-qsave(dcpo_apsr_analysis, "data/dcpo_analysis_apsr_compress")
-
-cls_ajps_uncertainty <- readRDS("data/cls_ajps_uncertainty.rds")
-
-cls_analysis <- left_join(cls_theta_uncertainty,cls_ajps_uncertainty, by=c("country","year"="Year","iter"="iter_se") )
-saveRDS(cls_analysis, "data/cls_analysis_ajps.rds")
-
-```
 
@@
 
-result_dcpoUncertain <- map(ls_mod_ajpsDCPO, function(aMod){ # reading a model
+result_dcpoUncertain <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
   mod_eval <- function(aData) eval(parse(text = aMod))
@@
 ```{r dcpo-uncertainAPSRmain, eval=FALSE}
-result_dcpoUncertainAPSR <- map(ls_mod_apsrDCPO, function(aMod){ # reading a model
+result_expAPSR <- map(ls_mod_apsrDCPO, function(aMod){ # reading a model
   result <- map(df_dcpoUncertainAPSR, function(aData){ # applying to the 1000 datasets
@@
 
-  result_dcpoUncertainAPSR <- list(tidy_dcpoUncertainAPSR, glance_dcpoUncertainAPSR)
-})
-
-names(result_dcpoUncertainAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",  "fd1", "fd-regime1", "fd2", "fd-regime2")
-
-saveRDS(result_dcpoUncertainAPSR, file = here::here("output", "estimates_dcpoAPSR.RDS"))
+  result_expAPSR <- list(tidy_dcpoUncertainAPSR, glance_dcpoUncertainAPSR)
+})
+
+names(result_expAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",  "fd1", "fd-regime1", "fd2", "fd-regime2")
+
+saveRDS(result_expAPSR, file = here::here("output", "estimates_dcpoAPSR.RDS"))
 ```
@@
 result_cls <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
-result_clsUncertainFull <- readRDS(here("output", "estimates_clsAJPSfullUncertain.RDS"))
-result_dcpoUncertainFull <- readRDS(here("output", "estimates_dcpoAJPSfullUncertain.RDS"))
+result_pureAJPS <- readRDS(here("output", "estimates_clsPureAJPS.RDS"))
+result_expAJPS <- readRDS(here("output", "estimates_clsExpAJPS.RDS"))
 
@@
   mutate(result_cls$pooled[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainFull$pooled[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainFull$pooled[[1]], model = "DCPO")
+  mutate(result_pureAJPS$pooled[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_expAJPS$pooled[[1]], model = "DCPO")
 ) %>% 
@@
   mutate(result_cls$gmm[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainFull$gmm[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainFull$gmm[[1]], model = "DCPO")
+  mutate(result_pureAJPS$gmm[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_expAJPS$gmm[[1]], model = "DCPO")
 ) %>% 
@@
   mutate(result_cls$`pooled-regime`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainFull$`pooled-regime`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainFull$`pooled-regime`[[1]], model = "DCPO")
+  mutate(result_pureAJPS$`pooled-regime`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_expAJPS$`pooled-regime`[[1]], model = "DCPO")
 ) %>% 
@@
   mutate(result_cls$`gmm-regime`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainFull$`gmm-regime`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainFull$`gmm-regime`[[1]], model = "DCPO")
+  mutate(result_pureAJPS$`gmm-regime`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_expAJPS$`gmm-regime`[[1]], model = "DCPO")
 ) %>% 
@@
 result_clsUncertainAPSR <- readRDS(here("output", "estimates_clsAPSR.RDS"))
-result_dcpoUncertainAPSR <- readRDS(here("output", "estimates_dcpoAPSR.RDS"))
+result_expAPSR <- readRDS(here("output", "estimates_dcpoAPSR.RDS"))
 
@@
   mutate(result_clsUncertainAPSR$pooled1[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainAPSR$pooled1[[1]], model = "DCPO")
+  mutate(result_expAPSR$pooled1[[1]], model = "DCPO")
 ) %>% 
@@
   mutate(result_clsUncertainAPSR$fd1[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainAPSR$fd1[[1]], model = "DCPO")
+  mutate(result_expAPSR$fd1[[1]], model = "DCPO")
 ) %>% 
@@
   mutate(result_clsUncertainAPSR$pooled2[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainAPSR$pooled2[[1]], model = "DCPO")
+  mutate(result_expAPSR$pooled2[[1]], model = "DCPO")
 ) %>% 
@@
   mutate(result_clsUncertainAPSR$fd2[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainAPSR$fd2[[1]], model = "DCPO")
+  mutate(result_expAPSR$fd2[[1]], model = "DCPO")
 ) %>% 
@@
   mutate(result_clsUncertainAPSR$`pooled-regime1`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainAPSR$`pooled-regime1`[[1]], model = "DCPO")
+  mutate(result_expAPSR$`pooled-regime1`[[1]], model = "DCPO")
 ) %>% 
@@
   mutate(result_clsUncertainAPSR$`fd-regime1`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainAPSR$`fd-regime1`[[1]], model = "DCPO")
+  mutate(result_expAPSR$`fd-regime1`[[1]], model = "DCPO")
 ) %>% 
@@
   mutate(result_clsUncertainAPSR$`pooled-regime2`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainAPSR$`pooled-regime2`[[1]], model = "DCPO")
+  mutate(result_expAPSR$`pooled-regime2`[[1]], model = "DCPO")
 ) %>% 
@@
   mutate(result_clsUncertainAPSR$`fd-regime2`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertainAPSR$`fd-regime2`[[1]], model = "DCPO")
+  mutate(result_expAPSR$`fd-regime2`[[1]], model = "DCPO")
 ) %>% 
@@
 result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
-result_clsFullUncertainAPSR <- readRDS(here("output", "estimates_clsFullUncertainAPSR.RDS"))
-result_dcpoFullUncertainAPSR <- readRDS(here("output", "estimates_dcpoUncertainAPSR.RDS"))
+result_pureAPSR <- readRDS(here("output", "estimates_clsFullUncertainAPSR.RDS"))
+result_dcpoFullUncertainAPSR <- readRDS(here("output", "estimates_clsExpAPSR.RDS"))
 
@@
   mutate(result_clsAPSR$pooled1[[1]], model = "Claassen 2020a"),
-  mutate(result_clsFullUncertainAPSR$pooled1[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_pureAPSR$pooled1[[1]], model = "Claassen w/ Uncertainty"),
   mutate(result_dcpoFullUncertainAPSR$pooled1[[1]], model = "DCPO")
@@
   mutate(result_clsAPSR$fd1[[1]], model = "Claassen 2020a"),
-  mutate(result_clsFullUncertainAPSR$fd1[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_pureAPSR$fd1[[1]], model = "Claassen w/ Uncertainty"),
   mutate(result_dcpoFullUncertainAPSR$fd1[[1]], model = "DCPO")
@@
   mutate(result_clsAPSR$pooled2[[1]], model = "Claassen 2020a"),
-  mutate(result_clsFullUncertainAPSR$pooled2[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_pureAPSR$pooled2[[1]], model = "Claassen w/ Uncertainty"),
   mutate(result_dcpoFullUncertainAPSR$pooled2[[1]], model = "DCPO")
@@
   mutate(result_clsAPSR$fd2[[1]], model = "Claassen 2020a"),
-  mutate(result_clsFullUncertainAPSR$fd2[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_pureAPSR$fd2[[1]], model = "Claassen w/ Uncertainty"),
   mutate(result_dcpoFullUncertainAPSR$fd2[[1]], model = "DCPO")
@@
   mutate(result_clsAPSR$`pooled-regime1`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsFullUncertainAPSR$`pooled-regime1`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_pureAPSR$`pooled-regime1`[[1]], model = "Claassen w/ Uncertainty"),
   mutate(result_dcpoFullUncertainAPSR$`pooled-regime1`[[1]], model = "DCPO")
@@
   mutate(result_clsAPSR$`fd-regime1`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsFullUncertainAPSR$`fd-regime1`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_pureAPSR$`fd-regime1`[[1]], model = "Claassen w/ Uncertainty"),
   mutate(result_dcpoFullUncertainAPSR$`fd-regime1`[[1]], model = "DCPO")
@@
   mutate(result_clsAPSR$`pooled-regime2`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsFullUncertainAPSR$`pooled-regime2`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_pureAPSR$`pooled-regime2`[[1]], model = "Claassen w/ Uncertainty"),
   mutate(result_dcpoFullUncertainAPSR$`pooled-regime2`[[1]], model = "DCPO")
@@
   mutate(result_clsAPSR$`fd-regime2`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsFullUncertainAPSR$`fd-regime2`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_pureAPSR$`fd-regime2`[[1]], model = "Claassen w/ Uncertainty"),
   mutate(result_dcpoFullUncertainAPSR$`fd-regime2`[[1]], model = "DCPO")
@@
 ```{r MocclaassenUncertaintyAJPS}
-load(here("data","cls_ajps.rda"))
+load(here("data","pure_cls_ajps.rda"))
 
 df_cls <- purrr::map(1:900, function(anEntry) {
-  cls_ajps[[anEntry]] %>% 
+  pure_cls_ajps[[anEntry]] %>% 
     plm::pdata.frame(index = c("country", "year"))
@@
 ```{r MocdcpoUncertaintyAJPS}
-load(here("data","dcpo_ajps.rda"))
+load(here("data","exp_cls_ajps.rda"))
 
 df_dcpo <- purrr::map(1:900, function(anEntry) {
-  dcpo_ajps[[anEntry]] %>%     #original data has include theta_dem_trim
+  exp_cls_ajps[[anEntry]] %>%     #original data has include theta_dem_trim
     plm::pdata.frame(index = c("country", "year"))
@@
 ```{r  dcpoMocUncertaintyAPSR}
-load(here("data","dcpo_apsr.rda"))
+load(here("data","exp_cls_apsr.rda"))
 df_dcpoUncertainAPSR <- purrr::map(1:900, function(anEntry) {
-  dcpo_apsr[[anEntry]] %>% 
+  exp_cls_apsr[[anEntry]] %>% 
     plm::pdata.frame(index = c("country", "year"))

### 2021-06-29 paper/dcpo_demsupport.Rmd
Clean the scripts for everything except for moc

@@
   osfr,
-  # DCPOtools, 
+  DCPOtools,
   mitools,
@@
 load(here("data", "exp_cls_apsr.rda"))
+
+result_clsAJPS <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
+result_pureAJPS <- readRDS(here("output", "estimates_clsPureAJPS.RDS"))
+result_expAJPS <- readRDS(here("output", "estimates_clsExpAJPS.RDS"))
+
+result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
+result_pureAPSR <- readRDS(here("output", "estimates_clsPureAPSR.RDS"))
+result_expAPSR <- readRDS(here("output", "estimates_clsExpAPSR.RDS"))
 
@@
     )) %>%
-    with_min_yrs(2)
+    DCPOtools::with_min_yrs(2)
 
@@
 
-```{r pointAJPS}
+```{r pointAJPS, eval=TRUE}
 ls_iv <- c("plm::lag(SupDem_trim, 1)",
@@
 
-result_cls <- map2(tidy_cls, glance_cls, ~ list(.x, .y))
-names(result_cls) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
-
-saveRDS(result_cls, file = here::here("output", "estimates_clsMeanAJPS.RDS"))
+result_clsAJPS <- map2(tidy_cls, glance_cls, ~ list(.x, .y))
+names(result_clsAJPS) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
+
+saveRDS(result_clsAJPS, file = here::here("output", "estimates_clsMeanAJPS.RDS"))
 ```
@@
 
-  result_clsUncertain <- list(tidy_clsUncertain, glance_clsUncertain)
+  result_apsrAJPS <- list(tidy_clsUncertain, glance_clsUncertain)
 })
@@
 
-  result_dcpoUncertain <- list(tidy_dcpoUncertain, glance_dcpoUncertain)
+  result_expAJPS <- list(tidy_dcpoUncertain, glance_dcpoUncertain)
 })
@@
 
-result_cls <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
-result_pureAJPS <- readRDS(here("output", "estimates_clsPureAJPS.RDS"))
-result_expAJPS <- readRDS(here("output", "estimates_clsExpAJPS.RDS"))
-
 type_model <-
@@
 result_ajpsPooled <-
-  list(result_cls,
+  list(result_clsAJPS,
        result_pureAJPS,
@@
 result_ajpsRegime <-
-  list(result_cls,
+  list(result_clsAJPS,
        result_pureAJPS,
@@
 
-```{r pointAPSR}
+```{r pointAPSR, eval=TRUE}
 load(here::here("data", "dem_mood_apsr.RData"))
@@
 
-  result_clsUncertainAPSR <- list(tidy_clsUncertainAPSR, glance_clsUncertainAPSR)
+  result_apsrAJPSAPSR <- list(tidy_clsUncertainAPSR, glance_clsUncertainAPSR)
 })
@@
 ```{r num-pointAJPS, results='asis'}
-tb_result_cls <- map(result_cls, ~ {
+tb_result_cls <- map(result_clsAJPS, ~ {
   names(.) <- c("tidy", "glance")
@@
 
-# Results Accounting for the Uncertainty in Both the Outcome and Explanatory Variables
-
-```{r cls-uncertainAJPSmain, eval=FALSE}
-ls_country <- unique(claassen_replication$country)
-first_year <- min(claassen_replication$year)
-
-sd_control <- sd.plm %>%
-  mutate(
-    country = as.character(Country),
-    year = as.numeric(as.character(Year)),
-    regime = ifelse(Regime_VD > 1, 1, 0)
-  )
-
-df_cls <- purrr::map(1:1000, function(anEntry) {
-  claassen_m5_theta$theta[anEntry,,] %>% 
-    reformat_dcpo_output("theta") %>% 
-    left_join(sd_control, by = c("country", "year")) %>% 
-    mutate(theta_dem = theta * regime,
-           theta_aut = theta * (1 - regime)) %>% 
-    plm::pdata.frame(index = c("country", "year"))
-})
-
-result_clsUncertain <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
-  result <- map(df_cls, function(aData){ # applying to the 1000 datasets
-    eval(parse(text = aMod))
-  })
-
-  result_betas <- mitools::MIextract(result, fun = coef)
-
-  ## Not work with ifelse
-  if(class(result[[1]])[1] == "plm"){
-      result_vars <- mitools::MIextract(result, fun = vcovBK_se)
-  }else{
-      result_vars <- mitools::MIextract(result, fun = vcovHC_se)
-  }
-
-  tidy_clsUncertain <- summary(mitools::MIcombine(results = result_betas, 
-                             variance = result_vars)) %>% 
-    rownames_to_column(var = "term") %>%
-        rename(conf.low = `(lower`,
-               conf.high = `upper)`,
-               estimate = results) %>%
-        filter(!str_detect(term, "(Intercept)"))
-
-  if(class(result[[1]]) == "plm"){ 
-    glance_clsUncertain <- glance.plm(result[[1]]) # using the customized glance function
-  }else{
-    glance_clsUncertain <- glance(result[[1]])
-  }
-
-  result_clsUncertain <- list(tidy_clsUncertain, glance_clsUncertain)
-})
-
-names(result_clsUncertain) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
-
-saveRDS(result_clsUncertain, file = here::here("output", "estimates_clsAJPS.RDS"))
-```
-
-```{r dcpo-uncertainAJPSmain, eval=FALSE}
-# df_dcpo <- dcpo_ajps_rubin %>% map2(1:length(dcpo_ajps_rubin), ~ {
-#  .x[[.y]] %>%
-#    mutate(theta_dem = theta * regime,
-#           theta_aut = theta * (1 - regime)) %>%
-#    plm::pdata.frame(index = c("country", "year"))
-# }) # The code is to fit the embedded format of dcpo_ajps_rubin
-
-# df_dcpo <- purrr::map(1:1000, function(anEntry) {
-#   dcpo_theta$theta[anEntry,,] %>% 
-#     reformat_dcpo_output("theta") %>% 
-#     left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
-#               by = c("year", "country")) %>%
-#     left_join(df_controls, by = c("country", "year")) %>% 
-#     mutate(theta_dem = theta * regime,
-#            theta_aut = theta * (1 - regime)) %>% 
-#     plm::pdata.frame(index = c("country", "year"))
-# })
-
-result_dcpoUncertain <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
-  mod_eval <- function(aData) eval(parse(text = aMod))
-
-  result <- map(df_dcpo, mod_eval)
-
-  result_betas <- mitools::MIextract(result, fun = coef)
-
-  ## Not work with ifelse
-  if(class(result[[1]])[1] == "plm"){
-      result_vars <- mitools::MIextract(result, fun = vcovBK_se)
-  }else{
-      result_vars <- mitools::MIextract(result, fun = vcovHC_se)
-  }
-
-  tidy_dcpoUncertain <- summary(mitools::MIcombine(results = result_betas,
-                             variance = result_vars)) %>%
-    rownames_to_column(var = "term") %>%
-        rename(conf.low = `(lower`,
-               conf.high = `upper)`,
-               estimate = results) %>%
-        filter(!str_detect(term, "(Intercept)"))
-
-  if(class(result[[1]]) == "plm"){
-    glance_dcpoUncertain <- glance.plm(result[[1]]) # using the customized glance function
-  }else{
-    glance_dcpoUncertain <- glance(result[[1]])
-  }
-
-  result_dcpoUncertain <- list(tidy_dcpoUncertain, glance_dcpoUncertain)
-})
-
-names(result_dcpoUncertain) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
-
-saveRDS(result_dcpoUncertain, file = here::here("output", "estimates_dcpoAJPS.RDS"))
-```
-
-```{r cls-undertainAPSRmain, eval=FALSE}
-ls_country <- unique(claassen_replication$country)
-first_year <- min(claassen_replication$year)
-
-sd_control <- sd.plm %>%
-  mutate(
-    country = as.character(Country),
-    year = as.numeric(as.character(Year))
-  )
-
-df_clsAPSR <- purrr::map(1:1000, function(anEntry) {
-  claassen_m5_theta$theta[anEntry,,] %>% 
-    reformat_dcpo_output("theta") %>% 
-    # left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
-    #           by = c("year", "country")) %>%
-    left_join(sd_control, by = c("country", "year")) %>% 
-    plm::pdata.frame(index = c("country", "year"))
-})
-
-result_clsUncertainAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
-  result <- map(df_clsAPSR, function(aData){ # applying to the 1000 datasets
-    eval(parse(text = aMod))
-  })
-
-  result_betas <- mitools::MIextract(result, fun = coef)
-
-  result_vars <- mitools::MIextract(result, fun = vcovHC_se)
-
-  tidy_clsUncertainAPSR <- summary(mitools::MIcombine(results = result_betas, 
-                             variance = result_vars)) %>% 
-    rownames_to_column(var = "term") %>%
-        rename(conf.low = `(lower`,
-               conf.high = `upper)`,
-               estimate = results) %>%
-        filter(!str_detect(term, "(Intercept)"))
-
-  glance_clsUncertainAPSR <- glance.plm(result[[1]])
-
-  result_clsUncertainAPSR <- list(tidy_clsUncertainAPSR, glance_clsUncertainAPSR)
-})
-
-names(result_clsUncertainAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", "fd1", "fd-regime1", "fd2", "fd-regime2")
-
-saveRDS(result_clsUncertainAPSR, file = here::here("output", "estimates_clsAPSR.RDS"))
-
-```
-
-```{r dcpo-uncertainAPSRmain, eval=FALSE}
-result_expAPSR <- map(ls_mod_apsrDCPO, function(aMod){ # reading a model
-  result <- map(df_dcpoUncertainAPSR, function(aData){ # applying to the 1000 datasets
-    eval(parse(text = aMod))
-  })
-
-  result_betas <- mitools::MIextract(result, fun = coef)
-
-  result_vars <- mitools::MIextract(result, fun = vcovHC_se)
-
-  tidy_dcpoUncertainAPSR <- summary(mitools::MIcombine(results = result_betas, 
-                             variance = result_vars)) %>% 
-    rownames_to_column(var = "term") %>%
-        rename(conf.low = `(lower`,
-               conf.high = `upper)`,
-               estimate = results) %>%
-        filter(!str_detect(term, "(Intercept)"))
-
-  glance_dcpoUncertainAPSR <- glance.plm(result[[1]])
-
-  result_expAPSR <- list(tidy_dcpoUncertainAPSR, glance_dcpoUncertainAPSR)
-})
-
-names(result_expAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",  "fd1", "fd-regime1", "fd2", "fd-regime2")
-
-saveRDS(result_expAPSR, file = here::here("output", "estimates_dcpoAPSR.RDS"))
-```
-
-# Replications of Full Pack of Models in Claassen 2020a,b
-
-```{r plot-fullpackAJPS, fig.cap= "The Effect of Public Support on Democracy", fig.width=7.5, fig.height=10, eval=TRUE}
-
-# Very weird phenomenon that the same type of rds files needs different ways to read
-# Suggesting using the qs or csv data type in future.
-result_cls <- readRDS(here::here("output", "estimates_clsMeanAJPS.RDS"))
-result_clsUncertain <- readRDS(here::here("output", "estimates_clsAJPS.RDS"))
-result_dcpoUncertain <- readRDS(here::here("output", "estimates_dcpoAJPS.RDS"))
-
-result_pooled <- bind_rows(
-  mutate(result_cls$pooled[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertain$pooled[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertain$pooled[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "Pooled")
-
-result_gmm <- bind_rows(
-  mutate(result_cls$gmm[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertain$gmm[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertain$gmm[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "GMM")
-
-result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = rep(
-      c("Democracy\n (t-1)",
-        "Democracy\n (t-2)",
-      "Support\n (t-1)",
-      "Log GDP\n per capita\n (t-1)",
-      "GDP per\n capita growth\n (t-1)",
-      "Regional\n democracy\n (t-1)",
-      "Percent\n Muslim\n (t-1)",
-      "Resource\n dependence\n (t-1)"),
-    time = 6), 
-    type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
-
-terms <- factor(rev(c("Democracy[t-1]",
-        "Democracy[t-2]",
-      "Support[t-1]",
-      "Log~GDP~per~capita[t-1]",
-      "GDP~per~capita~growth[t-1]",
-      "Regional~democracy[t-1]",
-      "Percent~Muslim[t-1]",
-      "Resource~dependence[t-1]")), levels =
-      rev(c("Democracy[t-1]",
-        "Democracy[t-2]",
-      "Support[t-1]",
-      "Log~GDP~per~capita[t-1]",
-      "GDP~per~capita~growth[t-1]",
-      "Regional~democracy[t-1]",
-      "Percent~Muslim[t-1]",
-      "Resource~dependence[t-1]")))
-
-# ggplot produces reversed plot, and embarrassed to say, I can't fix, again. Any thought?
-# What I've tried
-# 1. using guide_legend(reverse = TRUE) will change the legend's order not the plot.
-# 2. ordering models with factor levels using the original names or even c("1", "2", "3")
-# 2. redefining the order of model in the dataframe or in dwplot 
-# 3. checking the dwplot codes, model works in line 453, but nothing looks helpful
-# 4. Every post online is to reverse
-
-plot_AJPS1 <- dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms))) +
-  scale_color_grey(start = 0.4, end = 0.8) +
-  labs(
-    title = "DV: V-Dem Liberal Democracy Index",
-    subtitle = "Regime Compacted"
-  ) +
-  facet_wrap(~type, scales = "free_x") + 
-  theme(legend.position = "none")
-
-# the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
-# The trick is  to use guide = guide_legend(reverse = TRUE) within scale_color_*(); see below in plotAJPS2. --FS
-
-result_regime <- bind_rows(
-  mutate(result_cls$`pooled-regime`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertain$`pooled-regime`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertain$`pooled-regime`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "Pooled")
-
-result_regimeGmm <- bind_rows(
-  mutate(result_cls$`gmm-regime`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertain$`gmm-regime`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoUncertain$`gmm-regime`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "GMM")
-
-result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = rep(
-      c("Democracy\n (t-1)",
-        "Democracy\n (t-2)",
-      "Support\n demo only\n (t-1)",
-      "Support\n auto only\n (t-1)",
-      "Log GDP\n per capita\n (t-1)",
-      "GDP per\n capita growth\n (t-1)",
-      "Regional\n democracy\n (t-1)",
-      "Percent\n Muslim\n (t-1)",
-      "Resource\n dependence\n (t-1)"),
-    time = 6), 
-    type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
-
-terms2 <- factor(rev(c("Democracy[t-1]",
-                       "Democracy[t-2]",
-                       "Support[t-1] (democracies~only)",
-                       "Support[t-1] (autocracies~only)",
-                       "Log~GDP~per~capita[t-1]",
-                       "GDP~per~capita~growth[t-1]",
-                       "Regional~democracy[t-1]",
-                       "Percent~Muslim[t-1]",
-                       "Resource~dependence[t-1]")), levels =
-                   rev(c("Democracy[t-1]",
-                         "Democracy[t-2]",
-                         "Support[t-1] (democracies~only)",
-                         "Support[t-1] (autocracies~only)",
-                         "Log~GDP~per~capita[t-1]",
-                         "GDP~per~capita~growth[t-1]",
-                         "Regional~democracy[t-1]",
-                         "Percent~Muslim[t-1]",
-                         "Resource~dependence[t-1]")))
-
-plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms2))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  labs(
-    title = "",
-    subtitle = "Regime Specific"
-  ) +
-  facet_wrap(~type, scales = "free_x") +
-  theme(legend.position = "bottom", 
-        legend.title = element_blank())
-
-legend <- get_legend(plot_AJPS2)
-
-plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
-
-grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
-
-```
-
-```{r plot-fullpackAJPSfull, fig.cap= "The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=7, eval=TRUE}
-
-# Very weird phenomenon that the same type of rds files needs different ways to read
-# Suggesting using the qs or csv data type in future.
-result_cls <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
-result_pureAJPS <- readRDS(here("output", "estimates_clsPureAJPS.RDS"))
-result_expAJPS <- readRDS(here("output", "estimates_clsExpAJPS.RDS"))
-
-result_pooled <- bind_rows(
-  mutate(result_cls$pooled[[1]], model = "Claassen 2020a"),
-  mutate(result_pureAJPS$pooled[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_expAJPS$pooled[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "Pooled")
-
-result_gmm <- bind_rows(
-  mutate(result_cls$gmm[[1]], model = "Claassen 2020a"),
-  mutate(result_pureAJPS$gmm[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_expAJPS$gmm[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "GMM")
-
-result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = rep(
-      c("Democracy\n (t-1)",
-        "Democracy\n (t-2)",
-      "Support\n (t-1)",
-      "Log GDP\n per capita\n (t-1)",
-      "GDP per\n capita growth\n (t-1)",
-      "Regional\n democracy\n (t-1)",
-      "Percent\n Muslim\n (t-1)",
-      "Resource\n dependence\n (t-1)"),
-    time = 6), 
-    type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
-
-terms <- factor(rev(c("Democracy[t-1]",
-        "Democracy[t-2]",
-      "Support[t-1]",
-      "Log~GDP~per~capita[t-1]",
-      "GDP~per~capita~growth[t-1]",
-      "Regional~democracy[t-1]",
-      "Percent~Muslim[t-1]",
-      "Resource~dependence[t-1]")), levels =
-      rev(c("Democracy[t-1]",
-        "Democracy[t-2]",
-      "Support[t-1]",
-      "Log~GDP~per~capita[t-1]",
-      "GDP~per~capita~growth[t-1]",
-      "Regional~democracy[t-1]",
-      "Percent~Muslim[t-1]",
-      "Resource~dependence[t-1]")))
-
-# ggplot produces reversed plot, and embarrassed to say, I can't fix, again. Any thought?
-# What I've tried
-# 1. using guide_legend(reverse = TRUE) will change the legend's order not the plot.
-# 2. ordering models with factor levels using the original names or even c("1", "2", "3")
-# 2. redefining the order of model in the dataframe or in dwplot 
-# 3. checking the dwplot codes, model works in line 453, but nothing looks helpful
-# 4. Every post online is to reverse
-
-plot_AJPS1 <- dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms))) +
-  scale_color_grey(start = 0.4, end = 0.8) +
-  labs(
-    title = "DV: V-Dem Liberal Democracy Index",
-    subtitle = "Regime Compacted"
-  ) +
-  facet_wrap(~type, scales = "free_x") + 
-  theme(legend.position = "none")
-
-# the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
-# The trick is  to use guide = guide_legend(reverse = TRUE) within scale_color_*(); see below in plotAJPS2. --FS
-
-result_regime <- bind_rows(
-  mutate(result_cls$`pooled-regime`[[1]], model = "Claassen 2020a"),
-  mutate(result_pureAJPS$`pooled-regime`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_expAJPS$`pooled-regime`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "Pooled")
-
-result_regimeGmm <- bind_rows(
-  mutate(result_cls$`gmm-regime`[[1]], model = "Claassen 2020a"),
-  mutate(result_pureAJPS$`gmm-regime`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_expAJPS$`gmm-regime`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "GMM")
-
-result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = rep(
-      c("Democracy\n (t-1)",
-        "Democracy\n (t-2)",
-      "Support\n demo only\n (t-1)",
-      "Support\n auto only\n (t-1)",
-      "Log GDP\n per capita\n (t-1)",
-      "GDP per\n capita growth\n (t-1)",
-      "Regional\n democracy\n (t-1)",
-      "Percent\n Muslim\n (t-1)",
-      "Resource\n dependence\n (t-1)"),
-    time = 6), 
-    type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
-
-terms2 <- factor(rev(c("Democracy[t-1]",
-                       "Democracy[t-2]",
-                       "Support[t-1] (democracies~only)",
-                       "Support[t-1] (autocracies~only)",
-                       "Log~GDP~per~capita[t-1]",
-                       "GDP~per~capita~growth[t-1]",
-                       "Regional~democracy[t-1]",
-                       "Percent~Muslim[t-1]",
-                       "Resource~dependence[t-1]")), levels =
-                   rev(c("Democracy[t-1]",
-                         "Democracy[t-2]",
-                         "Support[t-1] (democracies~only)",
-                         "Support[t-1] (autocracies~only)",
-                         "Log~GDP~per~capita[t-1]",
-                         "GDP~per~capita~growth[t-1]",
-                         "Regional~democracy[t-1]",
-                         "Percent~Muslim[t-1]",
-                         "Resource~dependence[t-1]")))
-
-plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms2))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  labs(
-    title = "",
-    subtitle = "Regime Specific"
-  ) +
-  facet_wrap(~type, scales = "free_x") +
-  theme(legend.position = "bottom", 
-        legend.title = element_blank())
-
-legend <- get_legend(plot_AJPS2)
-
-plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
-
-grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
-
-```
-
-```{r plot-fullpackAPSR, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO", fig.width=7.5, fig.height=10, eval=TRUE}
-
-result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
-result_clsUncertainAPSR <- readRDS(here("output", "estimates_clsAPSR.RDS"))
-result_expAPSR <- readRDS(here("output", "estimates_dcpoAPSR.RDS"))
-
-# Regime compacted ####
-
-result_ecm1 <- bind_rows(
-  mutate(result_clsAPSR$pooled1[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainAPSR$pooled1[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_expAPSR$pooled1[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "ECM")
-
-result_fd1 <- bind_rows(
-  mutate(result_clsAPSR$fd1[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainAPSR$fd1[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_expAPSR$fd1[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "First Difference")
-
-result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-      "Liberal Democracy\n (Difference)",
-      "Liberal Democracy\n (t-1)",
-      "Log GDP\n per capita\n (Difference)",
-      "Log GDP\n (t-1)"),
-    time = 3),
-    rep(
-      c("Liberal Democracy\n (Difference)", 
-        "Log GDP\n per capita\n (Difference)"), 
-      time = 3
-    )),
-    type = factor(type, levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
-  )
-
-terms1 <- factor(rev(c("Support[t-1]",
-                      "Support[t-2]",
-                      "Delta~Liberal~democracy",
-                      "Liberal~democracy[t-1]",
-                      "Delta~Log~GDP~per~capita",
-                      "Log~GDP[t-1]")),
-                levels = rev(c("Support[t-1]",
-                               "Support[t-2]",
-                               "Delta~Liberal~democracy",
-                               "Liberal~democracy[t-1]",
-                               "Delta~Log~GDP~per~capita",
-                               "Log~GDP[t-1]")))
-
-plot_APSR1 <- dwplot(result_APSR1, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms1))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  # scale_color_uiowa(name = "", palette = "digitMixed") +
-  labs(
-    title = "DV: Public Support for Democracy",
-    subtitle = "Regime Compacted"
-  ) +
-  facet_wrap(~type, scales = "free_x") + 
-  theme(legend.position = "none")
-
-result_ecm2 <- bind_rows(
-  mutate(result_clsAPSR$pooled2[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainAPSR$pooled2[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_expAPSR$pooled2[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "ECM")
-
-result_fd2 <- bind_rows(
-  mutate(result_clsAPSR$fd2[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainAPSR$fd2[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_expAPSR$fd2[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "First Difference")
-
-result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-      "Liberal Democracy\n (Difference)",
-      "Liberal Democracy\n (t-1)",
-      "Log GDP\n per capita\n (Difference)",
-      "Log GDP\n (t-1)",
-      "Corruption\n (Difference)",
-      "Corruption\n (t-1)"
-      ),
-    time = 3),
-    rep(
-      c("Liberal Democracy\n (Difference)", 
-        "Log GDP\n per capita\n (Difference)",
-        "Corruption\n (Difference)"), 
-      time = 3
-    )),
-    type = factor(type, levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
-  )
-
-terms2 <- factor(rev(c("Support[t-1]",
-                      "Support[t-2]",
-                      "Delta~Liberal~democracy",
-                      "Liberal~democracy[t-1]",
-                      "Delta~Log~GDP~per~capita",
-                      "Log~GDP[t-1]",
-                      "Delta~Corruption",
-                      "Corruption[t-1]")),
-                levels = rev(c("Support[t-1]",
-                               "Support[t-2]",
-                               "Delta~Liberal~democracy",
-                               "Liberal~democracy[t-1]",
-                               "Delta~Log~GDP~per~capita",
-                               "Log~GDP[t-1]",
-                               "Delta~Corruption",
-                               "Corruption[t-1]")))
-
-plot_APSR2 <- dwplot(result_APSR2, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms2))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  # scale_color_uiowa(name = "", palette = "digitMixed") +
-  labs(
-    title = "",
-    subtitle = "W. Corruption"
-  ) +
-  facet_wrap(~type, scales = "free_x") +
-  theme(legend.position = "none")
-
-# Regime specified ####
-
-result_ecmReg1 <- bind_rows(
-  mutate(result_clsAPSR$`pooled-regime1`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainAPSR$`pooled-regime1`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_expAPSR$`pooled-regime1`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "ECM")
-
-result_fdReg1 <- bind_rows(
-  mutate(result_clsAPSR$`fd-regime1`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainAPSR$`fd-regime1`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_expAPSR$`fd-regime1`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "First Difference")
-
-result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-      "Electoral Democracy\n (Difference)",
-      "Electoral Democracy\n (t-1)",
-      "Minoritarian Democracy\n (Difference)",
-      "Minoritarian Democracy\n (t-1)",
-      "Log GDP\n per capita\n (Difference)",
-      "Log GDP\n (t-1)"),
-    time = 3),
-    rep(
-      c("Electoral Democracy\n (Difference)", 
-        "Minoritarian Democracy\n (Difference)",
-        "Log GDP\n per capita\n (Difference)"), 
-      time = 3
-    )),
-    type = factor(type, levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
-  )
-
-terms3 <- factor(rev(c("Support[t-1]",
-                      "Support[t-2]",
-                      "Delta~Electoral~democracy",
-                      "Electoral~democracy[t-1]",
-                      "Delta~Minoritarian~democracy",
-                      "Minoritarian~democracy[t-1]",
-                      "Delta~Log~GDP~per~capita",
-                      "Log~GDP[t-1]")),
-                levels = rev(c("Support[t-1]",
-                      "Support[t-2]",
-                      "Delta~Electoral~democracy",
-                      "Electoral~democracy[t-1]",
-                      "Delta~Minoritarian~democracy",
-                      "Minoritarian~democracy[t-1]",
-                      "Delta~Log~GDP~per~capita",
-                      "Log~GDP[t-1]")))
-
-plot_RegAPSR1 <- dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms3))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  # scale_color_uiowa(name = "", palette = "digitMixed") +
-  labs(
-    title = "",
-    subtitle = "Regime Specified"
-  ) +
-  facet_wrap(~type, scales = "free_x") + 
-  theme(legend.position = "none")
-
-result_ecmReg2 <- bind_rows(
-  mutate(result_clsAPSR$`pooled-regime2`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainAPSR$`pooled-regime2`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_expAPSR$`pooled-regime2`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "ECM")
-
-result_fdReg2 <- bind_rows(
-  mutate(result_clsAPSR$`fd-regime2`[[1]], model = "Claassen 2020a"),
-  mutate(result_clsUncertainAPSR$`fd-regime2`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_expAPSR$`fd-regime2`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "First Difference")
-
-result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-      "Electoral Democracy\n (Difference)",
-      "Electoral Democracy\n (t-1)",
-      "Minoritarian Democracy\n (Difference)",
-      "Minoritarian Democracy\n (t-1)",
-      "Log GDP\n per capita\n (Difference)",
-      "Log GDP\n (t-1)",
-      "Corruption\n (Difference)",
-      "Corruption\n (t-1)"
-      ),
-    time = 3),
-    rep(
-      c("Electoral Democracy\n (Difference)", 
-        "Minoritarian Democracy\n (Difference)",
-        "Log GDP\n per capita\n (Difference)",
-        "Corruption\n (Difference)"), 
-      time = 3
-    )),
-    type = factor(type, levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
-  )
-
-terms4 <- factor(rev(c("Support[t-1]",
-                      "Support[t-2]",
-                      "Delta~Electoral~democracy",
-                      "Electoral~democracy[t-1]",
-                      "Delta~Minoritarian~democracy",
-                      "Minoritarian~democracy[t-1]",
-                      "Delta~Log~GDP",
-                      "Log~GDP[t-1]",
-                      "Delta~Corruption",
-                      "Corruption[t-1]")),
-                levels = rev(c("Support[t-1]",
-                               "Support[t-2]",
-                               "Delta~Electoral~democracy",
-                               "Electoral~democracy[t-1]",
-                               "Delta~Minoritarian~democracy",
-                               "Minoritarian~democracy[t-1]",
-                               "Delta~Log~GDP",
-                               "Log~GDP[t-1]",
-                               "Delta~Corruption",
-                               "Corruption[t-1]")))
-
-plot_RegAPSR2 <- dwplot(result_RegAPSR2, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms4))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  # scale_color_uiowa(name = "", palette = "digitMixed") +
-  labs(
-    title = "",
-    subtitle = "Regime Specified w. Corruption"
-  ) +
-  facet_wrap(~type, scales = "free_x") +
-  theme(legend.position = "bottom", 
-        legend.title = element_blank())
-
-legend <- get_legend(plot_RegAPSR2)
-
-plot_RegAPSR2 <- plot_RegAPSR2 + theme(legend.position = "none")
-
-grid.arrange(plot_APSR1, plot_APSR2, plot_RegAPSR1, plot_RegAPSR2, legend, ncol = 1)
-```
-
-```{r plot-fullpackAPSRfull, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10, eval=TRUE}
-
-result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
-result_pureAPSR <- readRDS(here("output", "estimates_clsFullUncertainAPSR.RDS"))
-result_dcpoFullUncertainAPSR <- readRDS(here("output", "estimates_clsExpAPSR.RDS"))
-
-# Regime compacted ####
-
-result_ecm1 <- bind_rows(
-  mutate(result_clsAPSR$pooled1[[1]], model = "Claassen 2020a"),
-  mutate(result_pureAPSR$pooled1[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoFullUncertainAPSR$pooled1[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "ECM")
-
-result_fd1 <- bind_rows(
-  mutate(result_clsAPSR$fd1[[1]], model = "Claassen 2020a"),
-  mutate(result_pureAPSR$fd1[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoFullUncertainAPSR$fd1[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "First Difference")
-
-result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-      "Liberal Democracy\n (Difference)",
-      "Liberal Democracy\n (t-1)",
-      "Log GDP\n per capita\n (Difference)",
-      "Log GDP\n (t-1)"),
-    time = 3),
-    rep(
-      c("Liberal Democracy\n (Difference)", 
-        "Log GDP\n per capita\n (Difference)"), 
-      time = 3
-    )),
-    type = factor(type, levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
-  )
-
-terms1 <- factor(rev(c("Support[t-1]",
-                      "Support[t-2]",
-                      "Delta~Liberal~democracy",
-                      "Liberal~democracy[t-1]",
-                      "Delta~Log~GDP~per~capita",
-                      "Log~GDP[t-1]")),
-                levels = rev(c("Support[t-1]",
-                               "Support[t-2]",
-                               "Delta~Liberal~democracy",
-                               "Liberal~democracy[t-1]",
-                               "Delta~Log~GDP~per~capita",
-                               "Log~GDP[t-1]")))
-
-plot_APSR1 <- dwplot(result_APSR1, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms1))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  # scale_color_uiowa(name = "", palette = "digitMixed") +
-  labs(
-    title = "DV: Public Support for Democracy",
-    subtitle = "Regime Compacted"
-  ) +
-  facet_wrap(~type, scales = "free_x") + 
-  theme(legend.position = "none")
-
-result_ecm2 <- bind_rows(
-  mutate(result_clsAPSR$pooled2[[1]], model = "Claassen 2020a"),
-  mutate(result_pureAPSR$pooled2[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoFullUncertainAPSR$pooled2[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "ECM")
-
-result_fd2 <- bind_rows(
-  mutate(result_clsAPSR$fd2[[1]], model = "Claassen 2020a"),
-  mutate(result_pureAPSR$fd2[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoFullUncertainAPSR$fd2[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "First Difference")
-
-result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-      "Liberal Democracy\n (Difference)",
-      "Liberal Democracy\n (t-1)",
-      "Log GDP\n per capita\n (Difference)",
-      "Log GDP\n (t-1)",
-      "Corruption\n (Difference)",
-      "Corruption\n (t-1)"
-      ),
-    time = 3),
-    rep(
-      c("Liberal Democracy\n (Difference)", 
-        "Log GDP\n per capita\n (Difference)",
-        "Corruption\n (Difference)"), 
-      time = 3
-    )),
-    type = factor(type, levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
-  )
-
-terms2 <- factor(rev(c("Support[t-1]",
-                      "Support[t-2]",
-                      "Delta~Liberal~democracy",
-                      "Liberal~democracy[t-1]",
-                      "Delta~Log~GDP~per~capita",
-                      "Log~GDP[t-1]",
-                      "Delta~Corruption",
-                      "Corruption[t-1]")),
-                levels = rev(c("Support[t-1]",
-                               "Support[t-2]",
-                               "Delta~Liberal~democracy",
-                               "Liberal~democracy[t-1]",
-                               "Delta~Log~GDP~per~capita",
-                               "Log~GDP[t-1]",
-                               "Delta~Corruption",
-                               "Corruption[t-1]")))
-
-plot_APSR2 <- dwplot(result_APSR2, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms2))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  # scale_color_uiowa(name = "", palette = "digitMixed") +
-  labs(
-    title = "",
-    subtitle = "W. Corruption"
-  ) +
-  facet_wrap(~type, scales = "free_x") +
-  theme(legend.position = "none")
-
-# Regime specified ####
-
-result_ecmReg1 <- bind_rows(
-  mutate(result_clsAPSR$`pooled-regime1`[[1]], model = "Claassen 2020a"),
-  mutate(result_pureAPSR$`pooled-regime1`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoFullUncertainAPSR$`pooled-regime1`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "ECM")
-
-result_fdReg1 <- bind_rows(
-  mutate(result_clsAPSR$`fd-regime1`[[1]], model = "Claassen 2020a"),
-  mutate(result_pureAPSR$`fd-regime1`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoFullUncertainAPSR$`fd-regime1`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "First Difference")
-
-result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-      "Electoral Democracy\n (Difference)",
-      "Electoral Democracy\n (t-1)",
-      "Minoritarian Democracy\n (Difference)",
-      "Minoritarian Democracy\n (t-1)",
-      "Log GDP\n per capita\n (Difference)",
-      "Log GDP\n (t-1)"),
-    time = 3),
-    rep(
-      c("Electoral Democracy\n (Difference)", 
-        "Minoritarian Democracy\n (Difference)",
-        "Log GDP\n per capita\n (Difference)"), 
-      time = 3
-    )),
-    type = factor(type, levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
-  )
-
-terms3 <- factor(rev(c("Support[t-1]",
-                      "Support[t-2]",
-                      "Delta~Electoral~democracy",
-                      "Electoral~democracy[t-1]",
-                      "Delta~Minoritarian~democracy",
-                      "Minoritarian~democracy[t-1]",
-                      "Delta~Log~GDP~per~capita",
-                      "Log~GDP[t-1]")),
-                levels = rev(c("Support[t-1]",
-                      "Support[t-2]",
-                      "Delta~Electoral~democracy",
-                      "Electoral~democracy[t-1]",
-                      "Delta~Minoritarian~democracy",
-                      "Minoritarian~democracy[t-1]",
-                      "Delta~Log~GDP~per~capita",
-                      "Log~GDP[t-1]")))
-
-plot_RegAPSR1 <- dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms3))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  # scale_color_uiowa(name = "", palette = "digitMixed") +
-  labs(
-    title = "",
-    subtitle = "Regime Specified"
-  ) +
-  facet_wrap(~type, scales = "free_x") + 
-  theme(legend.position = "none")
-
-result_ecmReg2 <- bind_rows(
-  mutate(result_clsAPSR$`pooled-regime2`[[1]], model = "Claassen 2020a"),
-  mutate(result_pureAPSR$`pooled-regime2`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoFullUncertainAPSR$`pooled-regime2`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "ECM")
-
-result_fdReg2 <- bind_rows(
-  mutate(result_clsAPSR$`fd-regime2`[[1]], model = "Claassen 2020a"),
-  mutate(result_pureAPSR$`fd-regime2`[[1]], model = "Claassen w/ Uncertainty"),
-  mutate(result_dcpoFullUncertainAPSR$`fd-regime2`[[1]], model = "DCPO")
-) %>% 
-  mutate(type = "First Difference")
-
-result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-      "Electoral Democracy\n (Difference)",
-      "Electoral Democracy\n (t-1)",
-      "Minoritarian Democracy\n (Difference)",
-      "Minoritarian Democracy\n (t-1)",
-      "Log GDP\n per capita\n (Difference)",
-      "Log GDP\n (t-1)",
-      "Corruption\n (Difference)",
-      "Corruption\n (t-1)"
-      ),
-    time = 3),
-    rep(
-      c("Electoral Democracy\n (Difference)", 
-        "Minoritarian Democracy\n (Difference)",
-        "Log GDP\n per capita\n (Difference)",
-        "Corruption\n (Difference)"), 
-      time = 3
-    )),
-    type = factor(type, levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
-  )
-
-terms4 <- factor(rev(c("Support[t-1]",
-                      "Support[t-2]",
-                      "Delta~Electoral~democracy",
-                      "Electoral~democracy[t-1]",
-                      "Delta~Minoritarian~democracy",
-                      "Minoritarian~democracy[t-1]",
-                      "Delta~Log~GDP",
-                      "Log~GDP[t-1]",
-                      "Delta~Corruption",
-                      "Corruption[t-1]")),
-                levels = rev(c("Support[t-1]",
-                               "Support[t-2]",
-                               "Delta~Electoral~democracy",
-                               "Electoral~democracy[t-1]",
-                               "Delta~Minoritarian~democracy",
-                               "Minoritarian~democracy[t-1]",
-                               "Delta~Log~GDP",
-                               "Log~GDP[t-1]",
-                               "Delta~Corruption",
-                               "Corruption[t-1]")))
-
-plot_RegAPSR2 <- dwplot(result_RegAPSR2, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms4))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  # scale_color_uiowa(name = "", palette = "digitMixed") +
-  labs(
-    title = "",
-    subtitle = "Regime Specified w. Corruption"
-  ) +
-  facet_wrap(~type, scales = "free_x") +
-  theme(legend.position = "bottom", 
-        legend.title = element_blank())
-
-legend <- get_legend(plot_RegAPSR2)
-
-plot_RegAPSR2 <- plot_RegAPSR2 + theme(legend.position = "none")
-
-grid.arrange(plot_APSR1, plot_APSR2, plot_RegAPSR1, plot_RegAPSR2, legend, ncol = 1)
-```
-
-\pagebreak
-
 # Replication with Alternative Methods Accounting for Uncertainty
 ```{r MocclaassenUncertaintyAJPS}
-load(here("data","pure_cls_ajps.rda"))
+load(here("data","cls_ajps.rda"))
 
 df_cls <- purrr::map(1:900, function(anEntry) {
-  pure_cls_ajps[[anEntry]] %>% 
+  cls_ajps[[anEntry]] %>% 
     plm::pdata.frame(index = c("country", "year"))
@@
 ```{r MocdcpoUncertaintyAJPS}
-load(here("data","exp_cls_ajps.rda"))
+load(here("data","dcpo_ajps.rda"))
 
 df_dcpo <- purrr::map(1:900, function(anEntry) {
-  exp_cls_ajps[[anEntry]] %>%     #original data has include theta_dem_trim
+  dcpo_ajps[[anEntry]] %>%     #original data has include theta_dem_trim
     plm::pdata.frame(index = c("country", "year"))
@@
 ```{r  dcpoMocUncertaintyAPSR}
-load(here("data","exp_cls_apsr.rda"))
+load(here("data","dcpo_apsr.rda"))
 df_dcpoUncertainAPSR <- purrr::map(1:900, function(anEntry) {
-  exp_cls_apsr[[anEntry]] %>% 
+  dcpo_apsr[[anEntry]] %>% 
     plm::pdata.frame(index = c("country", "year"))

### 2021-07-07 paper/dcpo_demsupport.Rmd
avoid conflict

--- 2021-06-26 paper/dcpo_demsupport.Rmd
@@
 
-# produced by cls_ajps_apsr_uncertain.R and dcpo_ajps_apsr_uncertain.R
-load(here("data", "cls_ajps.rda")) 
-load(here("data", "dcpo_ajps.rda")) 
-load(here("data", "cls_apsr.rda"))
-load(here("data","dcpo_apsr.rda"))
-
-claassen_replication <- readRDS(here("data", "claassen_replication.rds")) %>% 
-  janitor::clean_names() %>% 
-  DCPOtools::with_min_yrs(2)
-load(here("data", "claassen_m5_theta.rda"))
-load(here("data", "dem_mood_apsr.RData"))
-load(here("data", "dcpo_input.rda"))
-load(here("data", "dcpo_theta.rda"))
-load(here("data", "dcpo_sigma.rda"))
-#load(here("data", "dcpo_ajps_rubin.rda"))
-# df_controls <- readRDS(here("data", "control_variables_ajps.rds"))   #use control file for merging with 
-df_dcpoUncertainAPSR <- readRDS(here("data", "df_dcpoUncertainAPSR.rds"))
+# Removed the comments for the final replication file
+## Claasseen and extend data
+
+# osf_retrieve_file("hczmf") %>% 
+#     osf_download(path = "../data")
+# 
+# osf_retrieve_file("wbu6m") %>% 
+#     osf_download(path = "../data")
+# 
+# osf_retrieve_file("2jhbc") %>% 
+#     osf_download(path = "../data")
+# 
+# osf_retrieve_file("u96m8") %>% 
+#     osf_download(path = "../data")
+
+load(here("data", "pure_cls_ajps.rda")) 
+load(here("data", "pure_cls_apsr.rda")) 
+load(here("data", "exp_cls_ajps.rda"))
+load(here("data", "exp_cls_apsr.rda"))
 
@@
 
-```{r cls-uncertainAJPSfull}
-result_clsUncertainFull <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
-  result <- map(cls_ajps, function(aData){ # applying to the 1000 datasets
+```{r cls-AJPSpure}
+result_AJPSpure <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
+  result <- map(pure_cls_ajps, function(aData){ # applying to the 1000 datasets
     eval(parse(text = aMod))
@@
 
-names(result_clsUncertainFull) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
-
-saveRDS(result_clsUncertainFull, file = here::here("output", "estimates_clsAJPSfullUncertain.RDS"))
+names(result_AJPSpure) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
+
+saveRDS(result_AJPSpure, file = here::here("output", "estimates_clsAJPSpure.RDS"))
 ```
@@
 result_cls <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
-result_clsUncertainFull <- readRDS(here("output", "estimates_clsAJPSfullUncertain.RDS"))
+result_AJPSpure <- readRDS(here("output", "estimates_clsAJPSfullUncertain.RDS"))
 result_dcpoUncertainFull <- readRDS(here("output", "estimates_dcpoAJPSfullUncertain.RDS"))
@@
   list(result_cls,
-       result_clsUncertainFull,
+       result_AJPSpure,
        result_dcpoUncertainFull) %>%
@@
 saveRDS(result_dcpoUncertainAPSR, file = here::here("output", "estimates_dcpoAPSR.RDS"))
+```
+
+# Replications of Full Pack of Models in Claassen 2020a,b
+
+```{r plot-fullpackAJPS, fig.cap= "The Effect of Public Support on Democracy", fig.width=7.5, fig.height=10, eval=TRUE}
+
+# Very weird phenomenon that the same type of rds files needs different ways to read
+# Suggesting using the qs or csv data type in future.
+result_cls <- readRDS(here::here("output", "estimates_clsMeanAJPS.RDS"))
+result_clsUncertain <- readRDS(here::here("output", "estimates_clsAJPS.RDS"))
+result_dcpoUncertain <- readRDS(here::here("output", "estimates_dcpoAJPS.RDS"))
+
+result_pooled <- bind_rows(
+  mutate(result_cls$pooled[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertain$pooled[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertain$pooled[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "Pooled")
+
+result_gmm <- bind_rows(
+  mutate(result_cls$gmm[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertain$gmm[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertain$gmm[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "GMM")
+
+result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democracy\n (t-1)",
+        "Democracy\n (t-2)",
+      "Support\n (t-1)",
+      "Log GDP\n per capita\n (t-1)",
+      "GDP per\n capita growth\n (t-1)",
+      "Regional\n democracy\n (t-1)",
+      "Percent\n Muslim\n (t-1)",
+      "Resource\n dependence\n (t-1)"),
+    time = 6), 
+    type = factor(type, levels = c("Pooled", "GMM")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
+
+terms <- factor(rev(c("Democracy[t-1]",
+        "Democracy[t-2]",
+      "Support[t-1]",
+      "Log~GDP~per~capita[t-1]",
+      "GDP~per~capita~growth[t-1]",
+      "Regional~democracy[t-1]",
+      "Percent~Muslim[t-1]",
+      "Resource~dependence[t-1]")), levels =
+      rev(c("Democracy[t-1]",
+        "Democracy[t-2]",
+      "Support[t-1]",
+      "Log~GDP~per~capita[t-1]",
+      "GDP~per~capita~growth[t-1]",
+      "Regional~democracy[t-1]",
+      "Percent~Muslim[t-1]",
+      "Resource~dependence[t-1]")))
+
+# ggplot produces reversed plot, and embarrassed to say, I can't fix, again. Any thought?
+# What I've tried
+# 1. using guide_legend(reverse = TRUE) will change the legend's order not the plot.
+# 2. ordering models with factor levels using the original names or even c("1", "2", "3")
+# 2. redefining the order of model in the dataframe or in dwplot 
+# 3. checking the dwplot codes, model works in line 453, but nothing looks helpful
+# 4. Every post online is to reverse
+
+plot_AJPS1 <- dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms))) +
+  scale_color_grey(start = 0.4, end = 0.8) +
+  labs(
+    title = "DV: V-Dem Liberal Democracy Index",
+    subtitle = "Regime Compacted"
+  ) +
+  facet_wrap(~type, scales = "free_x") + 
+  theme(legend.position = "none")
+
+# the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
+# The trick is  to use guide = guide_legend(reverse = TRUE) within scale_color_*(); see below in plotAJPS2. --FS
+
+result_regime <- bind_rows(
+  mutate(result_cls$`pooled-regime`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertain$`pooled-regime`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertain$`pooled-regime`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "Pooled")
+
+result_regimeGmm <- bind_rows(
+  mutate(result_cls$`gmm-regime`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertain$`gmm-regime`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertain$`gmm-regime`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "GMM")
+
+result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democracy\n (t-1)",
+        "Democracy\n (t-2)",
+      "Support\n demo only\n (t-1)",
+      "Support\n auto only\n (t-1)",
+      "Log GDP\n per capita\n (t-1)",
+      "GDP per\n capita growth\n (t-1)",
+      "Regional\n democracy\n (t-1)",
+      "Percent\n Muslim\n (t-1)",
+      "Resource\n dependence\n (t-1)"),
+    time = 6), 
+    type = factor(type, levels = c("Pooled", "GMM")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
+
+terms2 <- factor(rev(c("Democracy[t-1]",
+                       "Democracy[t-2]",
+                       "Support[t-1] (democracies~only)",
+                       "Support[t-1] (autocracies~only)",
+                       "Log~GDP~per~capita[t-1]",
+                       "GDP~per~capita~growth[t-1]",
+                       "Regional~democracy[t-1]",
+                       "Percent~Muslim[t-1]",
+                       "Resource~dependence[t-1]")), levels =
+                   rev(c("Democracy[t-1]",
+                         "Democracy[t-2]",
+                         "Support[t-1] (democracies~only)",
+                         "Support[t-1] (autocracies~only)",
+                         "Log~GDP~per~capita[t-1]",
+                         "GDP~per~capita~growth[t-1]",
+                         "Regional~democracy[t-1]",
+                         "Percent~Muslim[t-1]",
+                         "Resource~dependence[t-1]")))
+
+plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
+    scale_y_discrete(labels = parse(text = levels(terms2))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  labs(
+    title = "",
+    subtitle = "Regime Specific"
+  ) +
+  facet_wrap(~type, scales = "free_x") +
+  theme(legend.position = "bottom", 
+        legend.title = element_blank())
+
+legend <- get_legend(plot_AJPS2)
+
+plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
+
+grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
+
+```
+
+```{r plot-fullpackAJPSfull, fig.cap= "The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=7, eval=TRUE}
+
+# Very weird phenomenon that the same type of rds files needs different ways to read
+# Suggesting using the qs or csv data type in future.
+result_cls <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
+result_AJPSpure <- readRDS(here("output", "estimates_clsAJPSfullUncertain.RDS"))
+result_dcpoUncertainFull <- readRDS(here("output", "estimates_dcpoAJPSfullUncertain.RDS"))
+
+result_pooled <- bind_rows(
+  mutate(result_cls$pooled[[1]], model = "Claassen 2020a"),
+  mutate(result_AJPSpure$pooled[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertainFull$pooled[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "Pooled")
+
+result_gmm <- bind_rows(
+  mutate(result_cls$gmm[[1]], model = "Claassen 2020a"),
+  mutate(result_AJPSpure$gmm[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertainFull$gmm[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "GMM")
+
+result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democracy\n (t-1)",
+        "Democracy\n (t-2)",
+      "Support\n (t-1)",
+      "Log GDP\n per capita\n (t-1)",
+      "GDP per\n capita growth\n (t-1)",
+      "Regional\n democracy\n (t-1)",
+      "Percent\n Muslim\n (t-1)",
+      "Resource\n dependence\n (t-1)"),
+    time = 6), 
+    type = factor(type, levels = c("Pooled", "GMM")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
+
+terms <- factor(rev(c("Democracy[t-1]",
+        "Democracy[t-2]",
+      "Support[t-1]",
+      "Log~GDP~per~capita[t-1]",
+      "GDP~per~capita~growth[t-1]",
+      "Regional~democracy[t-1]",
+      "Percent~Muslim[t-1]",
+      "Resource~dependence[t-1]")), levels =
+      rev(c("Democracy[t-1]",
+        "Democracy[t-2]",
+      "Support[t-1]",
+      "Log~GDP~per~capita[t-1]",
+      "GDP~per~capita~growth[t-1]",
+      "Regional~democracy[t-1]",
+      "Percent~Muslim[t-1]",
+      "Resource~dependence[t-1]")))
+
+# ggplot produces reversed plot, and embarrassed to say, I can't fix, again. Any thought?
+# What I've tried
+# 1. using guide_legend(reverse = TRUE) will change the legend's order not the plot.
+# 2. ordering models with factor levels using the original names or even c("1", "2", "3")
+# 2. redefining the order of model in the dataframe or in dwplot 
+# 3. checking the dwplot codes, model works in line 453, but nothing looks helpful
+# 4. Every post online is to reverse
+
+plot_AJPS1 <- dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms))) +
+  scale_color_grey(start = 0.4, end = 0.8) +
+  labs(
+    title = "DV: V-Dem Liberal Democracy Index",
+    subtitle = "Regime Compacted"
+  ) +
+  facet_wrap(~type, scales = "free_x") + 
+  theme(legend.position = "none")
+
+# the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
+# The trick is  to use guide = guide_legend(reverse = TRUE) within scale_color_*(); see below in plotAJPS2. --FS
+
+result_regime <- bind_rows(
+  mutate(result_cls$`pooled-regime`[[1]], model = "Claassen 2020a"),
+  mutate(result_AJPSpure$`pooled-regime`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertainFull$`pooled-regime`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "Pooled")
+
+result_regimeGmm <- bind_rows(
+  mutate(result_cls$`gmm-regime`[[1]], model = "Claassen 2020a"),
+  mutate(result_AJPSpure$`gmm-regime`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertainFull$`gmm-regime`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "GMM")
+
+result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democracy\n (t-1)",
+        "Democracy\n (t-2)",
+      "Support\n demo only\n (t-1)",
+      "Support\n auto only\n (t-1)",
+      "Log GDP\n per capita\n (t-1)",
+      "GDP per\n capita growth\n (t-1)",
+      "Regional\n democracy\n (t-1)",
+      "Percent\n Muslim\n (t-1)",
+      "Resource\n dependence\n (t-1)"),
+    time = 6), 
+    type = factor(type, levels = c("Pooled", "GMM")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))
+
+terms2 <- factor(rev(c("Democracy[t-1]",
+                       "Democracy[t-2]",
+                       "Support[t-1] (democracies~only)",
+                       "Support[t-1] (autocracies~only)",
+                       "Log~GDP~per~capita[t-1]",
+                       "GDP~per~capita~growth[t-1]",
+                       "Regional~democracy[t-1]",
+                       "Percent~Muslim[t-1]",
+                       "Resource~dependence[t-1]")), levels =
+                   rev(c("Democracy[t-1]",
+                         "Democracy[t-2]",
+                         "Support[t-1] (democracies~only)",
+                         "Support[t-1] (autocracies~only)",
+                         "Log~GDP~per~capita[t-1]",
+                         "GDP~per~capita~growth[t-1]",
+                         "Regional~democracy[t-1]",
+                         "Percent~Muslim[t-1]",
+                         "Resource~dependence[t-1]")))
+
+plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
+    scale_y_discrete(labels = parse(text = levels(terms2))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  labs(
+    title = "",
+    subtitle = "Regime Specific"
+  ) +
+  facet_wrap(~type, scales = "free_x") +
+  theme(legend.position = "bottom", 
+        legend.title = element_blank())
+
+legend <- get_legend(plot_AJPS2)
+
+plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
+
+grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
+
+```
+
+```{r plot-fullpackAPSR, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO", fig.width=7.5, fig.height=10, eval=TRUE}
+
+result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
+result_clsUncertainAPSR <- readRDS(here("output", "estimates_clsAPSR.RDS"))
+result_dcpoUncertainAPSR <- readRDS(here("output", "estimates_dcpoAPSR.RDS"))
+
+# Regime compacted ####
+
+result_ecm1 <- bind_rows(
+  mutate(result_clsAPSR$pooled1[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainAPSR$pooled1[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertainAPSR$pooled1[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "ECM")
+
+result_fd1 <- bind_rows(
+  mutate(result_clsAPSR$fd1[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainAPSR$fd1[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertainAPSR$fd1[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "First Difference")
+
+result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+      "Liberal Democracy\n (Difference)",
+      "Liberal Democracy\n (t-1)",
+      "Log GDP\n per capita\n (Difference)",
+      "Log GDP\n (t-1)"),
+    time = 3),
+    rep(
+      c("Liberal Democracy\n (Difference)", 
+        "Log GDP\n per capita\n (Difference)"), 
+      time = 3
+    )),
+    type = factor(type, levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
+  )
+
+terms1 <- factor(rev(c("Support[t-1]",
+                      "Support[t-2]",
+                      "Delta~Liberal~democracy",
+                      "Liberal~democracy[t-1]",
+                      "Delta~Log~GDP~per~capita",
+                      "Log~GDP[t-1]")),
+                levels = rev(c("Support[t-1]",
+                               "Support[t-2]",
+                               "Delta~Liberal~democracy",
+                               "Liberal~democracy[t-1]",
+                               "Delta~Log~GDP~per~capita",
+                               "Log~GDP[t-1]")))
+
+plot_APSR1 <- dwplot(result_APSR1, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms1))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  # scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "DV: Public Support for Democracy",
+    subtitle = "Regime Compacted"
+  ) +
+  facet_wrap(~type, scales = "free_x") + 
+  theme(legend.position = "none")
+
+result_ecm2 <- bind_rows(
+  mutate(result_clsAPSR$pooled2[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainAPSR$pooled2[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertainAPSR$pooled2[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "ECM")
+
+result_fd2 <- bind_rows(
+  mutate(result_clsAPSR$fd2[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainAPSR$fd2[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertainAPSR$fd2[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "First Difference")
+
+result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+      "Liberal Democracy\n (Difference)",
+      "Liberal Democracy\n (t-1)",
+      "Log GDP\n per capita\n (Difference)",
+      "Log GDP\n (t-1)",
+      "Corruption\n (Difference)",
+      "Corruption\n (t-1)"
+      ),
+    time = 3),
+    rep(
+      c("Liberal Democracy\n (Difference)", 
+        "Log GDP\n per capita\n (Difference)",
+        "Corruption\n (Difference)"), 
+      time = 3
+    )),
+    type = factor(type, levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
+  )
+
+terms2 <- factor(rev(c("Support[t-1]",
+                      "Support[t-2]",
+                      "Delta~Liberal~democracy",
+                      "Liberal~democracy[t-1]",
+                      "Delta~Log~GDP~per~capita",
+                      "Log~GDP[t-1]",
+                      "Delta~Corruption",
+                      "Corruption[t-1]")),
+                levels = rev(c("Support[t-1]",
+                               "Support[t-2]",
+                               "Delta~Liberal~democracy",
+                               "Liberal~democracy[t-1]",
+                               "Delta~Log~GDP~per~capita",
+                               "Log~GDP[t-1]",
+                               "Delta~Corruption",
+                               "Corruption[t-1]")))
+
+plot_APSR2 <- dwplot(result_APSR2, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms2))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  # scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "",
+    subtitle = "W. Corruption"
+  ) +
+  facet_wrap(~type, scales = "free_x") +
+  theme(legend.position = "none")
+
+# Regime specified ####
+
+result_ecmReg1 <- bind_rows(
+  mutate(result_clsAPSR$`pooled-regime1`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainAPSR$`pooled-regime1`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertainAPSR$`pooled-regime1`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "ECM")
+
+result_fdReg1 <- bind_rows(
+  mutate(result_clsAPSR$`fd-regime1`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainAPSR$`fd-regime1`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertainAPSR$`fd-regime1`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "First Difference")
+
+result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+      "Electoral Democracy\n (Difference)",
+      "Electoral Democracy\n (t-1)",
+      "Minoritarian Democracy\n (Difference)",
+      "Minoritarian Democracy\n (t-1)",
+      "Log GDP\n per capita\n (Difference)",
+      "Log GDP\n (t-1)"),
+    time = 3),
+    rep(
+      c("Electoral Democracy\n (Difference)", 
+        "Minoritarian Democracy\n (Difference)",
+        "Log GDP\n per capita\n (Difference)"), 
+      time = 3
+    )),
+    type = factor(type, levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
+  )
+
+terms3 <- factor(rev(c("Support[t-1]",
+                      "Support[t-2]",
+                      "Delta~Electoral~democracy",
+                      "Electoral~democracy[t-1]",
+                      "Delta~Minoritarian~democracy",
+                      "Minoritarian~democracy[t-1]",
+                      "Delta~Log~GDP~per~capita",
+                      "Log~GDP[t-1]")),
+                levels = rev(c("Support[t-1]",
+                      "Support[t-2]",
+                      "Delta~Electoral~democracy",
+                      "Electoral~democracy[t-1]",
+                      "Delta~Minoritarian~democracy",
+                      "Minoritarian~democracy[t-1]",
+                      "Delta~Log~GDP~per~capita",
+                      "Log~GDP[t-1]")))
+
+plot_RegAPSR1 <- dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms3))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  # scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "",
+    subtitle = "Regime Specified"
+  ) +
+  facet_wrap(~type, scales = "free_x") + 
+  theme(legend.position = "none")
+
+result_ecmReg2 <- bind_rows(
+  mutate(result_clsAPSR$`pooled-regime2`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainAPSR$`pooled-regime2`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertainAPSR$`pooled-regime2`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "ECM")
+
+result_fdReg2 <- bind_rows(
+  mutate(result_clsAPSR$`fd-regime2`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsUncertainAPSR$`fd-regime2`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoUncertainAPSR$`fd-regime2`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "First Difference")
+
+result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+      "Electoral Democracy\n (Difference)",
+      "Electoral Democracy\n (t-1)",
+      "Minoritarian Democracy\n (Difference)",
+      "Minoritarian Democracy\n (t-1)",
+      "Log GDP\n per capita\n (Difference)",
+      "Log GDP\n (t-1)",
+      "Corruption\n (Difference)",
+      "Corruption\n (t-1)"
+      ),
+    time = 3),
+    rep(
+      c("Electoral Democracy\n (Difference)", 
+        "Minoritarian Democracy\n (Difference)",
+        "Log GDP\n per capita\n (Difference)",
+        "Corruption\n (Difference)"), 
+      time = 3
+    )),
+    type = factor(type, levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
+  )
+
+terms4 <- factor(rev(c("Support[t-1]",
+                      "Support[t-2]",
+                      "Delta~Electoral~democracy",
+                      "Electoral~democracy[t-1]",
+                      "Delta~Minoritarian~democracy",
+                      "Minoritarian~democracy[t-1]",
+                      "Delta~Log~GDP",
+                      "Log~GDP[t-1]",
+                      "Delta~Corruption",
+                      "Corruption[t-1]")),
+                levels = rev(c("Support[t-1]",
+                               "Support[t-2]",
+                               "Delta~Electoral~democracy",
+                               "Electoral~democracy[t-1]",
+                               "Delta~Minoritarian~democracy",
+                               "Minoritarian~democracy[t-1]",
+                               "Delta~Log~GDP",
+                               "Log~GDP[t-1]",
+                               "Delta~Corruption",
+                               "Corruption[t-1]")))
+
+plot_RegAPSR2 <- dwplot(result_RegAPSR2, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms4))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  # scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "",
+    subtitle = "Regime Specified w. Corruption"
+  ) +
+  facet_wrap(~type, scales = "free_x") +
+  theme(legend.position = "bottom", 
+        legend.title = element_blank())
+
+legend <- get_legend(plot_RegAPSR2)
+
+plot_RegAPSR2 <- plot_RegAPSR2 + theme(legend.position = "none")
+
+grid.arrange(plot_APSR1, plot_APSR2, plot_RegAPSR1, plot_RegAPSR2, legend, ncol = 1)
+```
+
+```{r plot-fullpackAPSRfull, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10, eval=TRUE}
+
+result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
+result_clsFullUncertainAPSR <- readRDS(here("output", "estimates_clsFullUncertainAPSR.RDS"))
+result_dcpoFullUncertainAPSR <- readRDS(here("output", "estimates_dcpoUncertainAPSR.RDS"))
+
+# Regime compacted ####
+
+result_ecm1 <- bind_rows(
+  mutate(result_clsAPSR$pooled1[[1]], model = "Claassen 2020a"),
+  mutate(result_clsFullUncertainAPSR$pooled1[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoFullUncertainAPSR$pooled1[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "ECM")
+
+result_fd1 <- bind_rows(
+  mutate(result_clsAPSR$fd1[[1]], model = "Claassen 2020a"),
+  mutate(result_clsFullUncertainAPSR$fd1[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoFullUncertainAPSR$fd1[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "First Difference")
+
+result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+      "Liberal Democracy\n (Difference)",
+      "Liberal Democracy\n (t-1)",
+      "Log GDP\n per capita\n (Difference)",
+      "Log GDP\n (t-1)"),
+    time = 3),
+    rep(
+      c("Liberal Democracy\n (Difference)", 
+        "Log GDP\n per capita\n (Difference)"), 
+      time = 3
+    )),
+    type = factor(type, levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
+  )
+
+terms1 <- factor(rev(c("Support[t-1]",
+                      "Support[t-2]",
+                      "Delta~Liberal~democracy",
+                      "Liberal~democracy[t-1]",
+                      "Delta~Log~GDP~per~capita",
+                      "Log~GDP[t-1]")),
+                levels = rev(c("Support[t-1]",
+                               "Support[t-2]",
+                               "Delta~Liberal~democracy",
+                               "Liberal~democracy[t-1]",
+                               "Delta~Log~GDP~per~capita",
+                               "Log~GDP[t-1]")))
+
+plot_APSR1 <- dwplot(result_APSR1, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms1))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  # scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "DV: Public Support for Democracy",
+    subtitle = "Regime Compacted"
+  ) +
+  facet_wrap(~type, scales = "free_x") + 
+  theme(legend.position = "none")
+
+result_ecm2 <- bind_rows(
+  mutate(result_clsAPSR$pooled2[[1]], model = "Claassen 2020a"),
+  mutate(result_clsFullUncertainAPSR$pooled2[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoFullUncertainAPSR$pooled2[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "ECM")
+
+result_fd2 <- bind_rows(
+  mutate(result_clsAPSR$fd2[[1]], model = "Claassen 2020a"),
+  mutate(result_clsFullUncertainAPSR$fd2[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoFullUncertainAPSR$fd2[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "First Difference")
+
+result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+      "Liberal Democracy\n (Difference)",
+      "Liberal Democracy\n (t-1)",
+      "Log GDP\n per capita\n (Difference)",
+      "Log GDP\n (t-1)",
+      "Corruption\n (Difference)",
+      "Corruption\n (t-1)"
+      ),
+    time = 3),
+    rep(
+      c("Liberal Democracy\n (Difference)", 
+        "Log GDP\n per capita\n (Difference)",
+        "Corruption\n (Difference)"), 
+      time = 3
+    )),
+    type = factor(type, levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
+  )
+
+terms2 <- factor(rev(c("Support[t-1]",
+                      "Support[t-2]",
+                      "Delta~Liberal~democracy",
+                      "Liberal~democracy[t-1]",
+                      "Delta~Log~GDP~per~capita",
+                      "Log~GDP[t-1]",
+                      "Delta~Corruption",
+                      "Corruption[t-1]")),
+                levels = rev(c("Support[t-1]",
+                               "Support[t-2]",
+                               "Delta~Liberal~democracy",
+                               "Liberal~democracy[t-1]",
+                               "Delta~Log~GDP~per~capita",
+                               "Log~GDP[t-1]",
+                               "Delta~Corruption",
+                               "Corruption[t-1]")))
+
+plot_APSR2 <- dwplot(result_APSR2, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms2))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  # scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "",
+    subtitle = "W. Corruption"
+  ) +
+  facet_wrap(~type, scales = "free_x") +
+  theme(legend.position = "none")
+
+# Regime specified ####
+
+result_ecmReg1 <- bind_rows(
+  mutate(result_clsAPSR$`pooled-regime1`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsFullUncertainAPSR$`pooled-regime1`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoFullUncertainAPSR$`pooled-regime1`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "ECM")
+
+result_fdReg1 <- bind_rows(
+  mutate(result_clsAPSR$`fd-regime1`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsFullUncertainAPSR$`fd-regime1`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoFullUncertainAPSR$`fd-regime1`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "First Difference")
+
+result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+      "Electoral Democracy\n (Difference)",
+      "Electoral Democracy\n (t-1)",
+      "Minoritarian Democracy\n (Difference)",
+      "Minoritarian Democracy\n (t-1)",
+      "Log GDP\n per capita\n (Difference)",
+      "Log GDP\n (t-1)"),
+    time = 3),
+    rep(
+      c("Electoral Democracy\n (Difference)", 
+        "Minoritarian Democracy\n (Difference)",
+        "Log GDP\n per capita\n (Difference)"), 
+      time = 3
+    )),
+    type = factor(type, levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
+  )
+
+terms3 <- factor(rev(c("Support[t-1]",
+                      "Support[t-2]",
+                      "Delta~Electoral~democracy",
+                      "Electoral~democracy[t-1]",
+                      "Delta~Minoritarian~democracy",
+                      "Minoritarian~democracy[t-1]",
+                      "Delta~Log~GDP~per~capita",
+                      "Log~GDP[t-1]")),
+                levels = rev(c("Support[t-1]",
+                      "Support[t-2]",
+                      "Delta~Electoral~democracy",
+                      "Electoral~democracy[t-1]",
+                      "Delta~Minoritarian~democracy",
+                      "Minoritarian~democracy[t-1]",
+                      "Delta~Log~GDP~per~capita",
+                      "Log~GDP[t-1]")))
+
+plot_RegAPSR1 <- dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms3))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  # scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "",
+    subtitle = "Regime Specified"
+  ) +
+  facet_wrap(~type, scales = "free_x") + 
+  theme(legend.position = "none")
+
+result_ecmReg2 <- bind_rows(
+  mutate(result_clsAPSR$`pooled-regime2`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsFullUncertainAPSR$`pooled-regime2`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoFullUncertainAPSR$`pooled-regime2`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "ECM")
+
+result_fdReg2 <- bind_rows(
+  mutate(result_clsAPSR$`fd-regime2`[[1]], model = "Claassen 2020a"),
+  mutate(result_clsFullUncertainAPSR$`fd-regime2`[[1]], model = "Claassen w/ Uncertainty"),
+  mutate(result_dcpoFullUncertainAPSR$`fd-regime2`[[1]], model = "DCPO")
+) %>% 
+  mutate(type = "First Difference")
+
+result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+      "Electoral Democracy\n (Difference)",
+      "Electoral Democracy\n (t-1)",
+      "Minoritarian Democracy\n (Difference)",
+      "Minoritarian Democracy\n (t-1)",
+      "Log GDP\n per capita\n (Difference)",
+      "Log GDP\n (t-1)",
+      "Corruption\n (Difference)",
+      "Corruption\n (t-1)"
+      ),
+    time = 3),
+    rep(
+      c("Electoral Democracy\n (Difference)", 
+        "Minoritarian Democracy\n (Difference)",
+        "Log GDP\n per capita\n (Difference)",
+        "Corruption\n (Difference)"), 
+      time = 3
+    )),
+    type = factor(type, levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
+  )
+
+terms4 <- factor(rev(c("Support[t-1]",
+                      "Support[t-2]",
+                      "Delta~Electoral~democracy",
+                      "Electoral~democracy[t-1]",
+                      "Delta~Minoritarian~democracy",
+                      "Minoritarian~democracy[t-1]",
+                      "Delta~Log~GDP",
+                      "Log~GDP[t-1]",
+                      "Delta~Corruption",
+                      "Corruption[t-1]")),
+                levels = rev(c("Support[t-1]",
+                               "Support[t-2]",
+                               "Delta~Electoral~democracy",
+                               "Electoral~democracy[t-1]",
+                               "Delta~Minoritarian~democracy",
+                               "Minoritarian~democracy[t-1]",
+                               "Delta~Log~GDP",
+                               "Log~GDP[t-1]",
+                               "Delta~Corruption",
+                               "Corruption[t-1]")))
+
+plot_RegAPSR2 <- dwplot(result_RegAPSR2, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms4))) +
+  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
+  # scale_color_uiowa(name = "", palette = "digitMixed") +
+  labs(
+    title = "",
+    subtitle = "Regime Specified w. Corruption"
+  ) +
+  facet_wrap(~type, scales = "free_x") +
+  theme(legend.position = "bottom", 
+        legend.title = element_blank())
+
+legend <- get_legend(plot_RegAPSR2)
+
+plot_RegAPSR2 <- plot_RegAPSR2 + theme(legend.position = "none")
+
+grid.arrange(plot_APSR1, plot_APSR2, plot_RegAPSR1, plot_RegAPSR2, legend, ncol = 1)
 ```
@@
 ```
-
->>>>>>> 7257990cf1c7c4951fc068aacaa22c22bc503a86

### 2021-07-07 paper/dcpo_demsupport.Rmd
update moc estimates @sammo3182

--- 2021-06-29 paper/dcpo_demsupport.Rmd
@@
 result_expAPSR <- readRDS(here("output", "estimates_clsExpAPSR.RDS"))
+
+mocresult_pureAJPS <- readRDS(here("output", "estimates_moc_pureAJPS.RDS"))
+mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expAJPS.RDS"))
+mocresult_pureAPSR <- readRDS(here("output", "estimates_moc_pureAPSR.RDS"))
+mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expAPSR.RDS"))
 
@@
     # Using expressions of underscore and greek letters
-    scale_color_gb(palette = "digitMixed") +
+    #scale_color_gb(palette = "digitMixed") +
     facet_wrap(~ type)
@@
     # Using expressions of underscore and greek letters
-    scale_color_gb(palette = "digitMixed") +
+   # scale_color_gb(palette = "digitMixed") +
     facet_wrap( ~ type)
@@
 # Replication with Alternative Methods Accounting for Uncertainty
-```{r MocclaassenUncertaintyAJPS}
-load(here("data","cls_ajps.rda"))
-
-df_cls <- purrr::map(1:900, function(anEntry) {
-  cls_ajps[[anEntry]] %>% 
-    plm::pdata.frame(index = c("country", "year"))
-})
+```{r moc_estimates}
+
+result_clsAJPS <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
+result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
+mocresult_pureAJPS <- readRDS(here("output", "estimates_moc_pureAJPS.RDS"))
+mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expAJPS.RDS"))
+mocresult_pureAPSR <- readRDS(here("output", "estimates_moc_pureAPSR.RDS"))
+mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expAPSR.RDS"))
+
+```
+
+```{r model-AJPS}
+
+#ls_iv <- c("plm::lag(theta, 1)", 
+#    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) ")
 
 ls_iv <- c("plm::lag(SupDem_trim, 1)", 
-           "plm::lag(theta_dem_trim, 1) + plm::lag(theta_aut_trim, 1) ") ##all use trim
+    "plm::lag(theta_dem_trim, 1) + plm::lag(theta_aut_trim, 1) ") #use trimmed data
+
 ls_method <- c("plm", "pgmm")
-ls_eq <- glue("Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + {ls_iv} + 
-              plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + 
-              plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)")
-
-ls_mod <- c(
+
+ls_eq <- glue("Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + {ls_iv} + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)")
+
+ls_mod_ajpsCLS <- c(
     glue("plm({ls_eq}, model = 'pooling', data = aData)"),
@@
 
-result_clsUncertain  <- map(ls_mod[1:2], function(aMod){
-  result <- methodComposition1(df_cls,aMod)
-})
-
-names(result_clsUncertain) <- c("pooled", "pooled-regime")
-
-result_clsUncertain_gmm  <- map(ls_mod[3:4], function(aMod){
-  result <- methodComposition2(df_cls,aMod)
-})
-names(result_clsUncertain_gmm) <- c("gmm", "gmm-regime")
-
-result_clsUncertain_whole <- append(result_clsUncertain, result_clsUncertain_gmm)
-
-saveRDS(result_clsUncertain_whole, file =here("output","clsAJPS_uncertainty.RDS"))
-
-```
-
-```{r MocdcpoUncertaintyAJPS}
-load(here("data","dcpo_ajps.rda"))
-
-df_dcpo <- purrr::map(1:900, function(anEntry) {
-  dcpo_ajps[[anEntry]] %>%     #original data has include theta_dem_trim
+```
+
+```{r mocresult-pureAJPS}
+
+df_pure_clsAjps <- purrr::map(1:900, function(anEntry) {
+  pure_cls_ajps[[anEntry]] %>% 
     plm::pdata.frame(index = c("country", "year"))
@@
 
-ls_iv <- c("plm::lag(theta_trim, 1)", 
-           "plm::lag(theta_dem_trim, 1) + plm::lag(theta_aut_trim, 1)") #use trimed data
-ls_method <- c("plm", "pgmm")
-ls_eq <- glue("Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + {ls_iv} + plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) + plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)")
-ls_mod <- c(
-  glue("plm({ls_eq}, model = 'pooling', data = aData)"),
-  glue(
-    "pgmm({ls_eq} | plm::lag(Vdem_libdem, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
-  )
-)
-
-result_dcpoUncertain  <- map(ls_mod[1:2], function(aMod){
-  result <- methodComposition1(df_dcpo,aMod)
-})
-
-names(result_dcpoUncertain) <- c("pooled", "pooled-regime")
-
-result_dcpoUncertain_gmm  <- map(ls_mod[3:4], function(aMod){
-  result <- methodComposition2(df_dcpo,aMod)
-})
-
-names(result_dcpoUncertain_gmm) <- c("gmm", "gmm-regime")
-
-result_dcpoUncertain_whole <- append(result_dcpoUncertain, result_dcpoUncertain_gmm)
-
-saveRDS(result_dcpoUncertain_whole, file =here("output","dcpoAJPS_uncertainty.RDS"))
-
-```
-
-```{r visualizedMocUncertainAJPS, fig.cap= "The Effect of Public Support on Democracy ", eval = TRUE, fig.width=7, fig.height=10}
-
-result_clsAJPS <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
-result_clsUncertain_whole <- readRDS(here("output", "clsAJPS_uncertainty.RDS"))
-result_dcpoUncertain_whole <- readRDS(here("output", "dcpoAJPS_uncertainty.RDS"))
+result_pure_clsUncertain  <- map(ls_mod_ajpsCLS[1:2], function(aMod){
+  result <- methodComposition1(df_pure_clsAjps,aMod)
+})
+
+names(result_pure_clsUncertain) <- c("pooled", "pooled-regime")
+
+result_pure_clsUncertain_gmm  <- map(ls_mod_ajpsCLS[3:4], function(aMod){
+  result <- methodComposition2(df_pure_clsAjps,aMod)
+})
+names(result_pure_clsUncertain_gmm) <- c("gmm", "gmm-regime")
+
+mocresult_pureAJPS <- append(result_pure_clsUncertain, result_pure_clsUncertain_gmm)
+
+saveRDS(mocresult_pureAJPS, file =here("output","estimates_moc_pureAJPS.RDS"))
+
+```
+
+```{r mocresult-expAJPS}
+
+df_exp_clsAjps <- purrr::map(1:900, function(anEntry) {
+  exp_cls_ajps[[anEntry]] %>% 
+    plm::pdata.frame(index = c("country", "year"))
+})
+
+result_exp_clsUncertain  <- map(ls_mod_ajpsCLS[1:2], function(aMod){
+  result <- methodComposition1(df_exp_clsAjps,aMod)
+})
+
+names(result_exp_clsUncertain) <- c("pooled", "pooled-regime")
+
+result_exp_clsUncertain_gmm  <- map(ls_mod_ajpsCLS[3:4], function(aMod){
+  result <- methodComposition2(df_exp_clsAjps,aMod)
+})
+names(result_exp_clsUncertain_gmm) <- c("gmm", "gmm-regime")
+
+mocresult_expAJPS <- append(result_exp_clsUncertain, result_exp_clsUncertain_gmm)
+
+saveRDS(mocresult_expAJPS, file =here("output","estimates_moc_expAJPS.RDS"))
+
+```
+
+```{r plot-mocAJPS, fig.cap= "The Effect of Public Support on Democracy ", eval = TRUE, fig.width=7, fig.height=10}
 
 result_pooled <- bind_rows(
-  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Claassen 2020a"),
-  mutate(MOCsumm(result_clsUncertain_whole[["pooled"]]), model = "Claassen w/uncertainty"),
-  mutate(MOCsumm(result_dcpoUncertain_whole[["pooled"]]), model = "DCPO")
+  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm(mocresult_pureAJPS[["pooled"]]), model = "Uncertainty"),
+  mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), model = "Uncertainty+Expanded Data")
 ) %>% 
@@
 result_gmm <- bind_rows(
-  mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Claassen 2020a"),
-  mutate(MOCsumm(result_clsUncertain_whole[["gmm"]]), model = "Claassen w/uncertainty"),
-  mutate(MOCsumm(result_dcpoUncertain_whole[["gmm"]]), model = "DCPO")
+  mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm(mocresult_pureAJPS[["gmm"]]), model = "Uncertainty"),
+  mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), model = "Uncertainty+Expanded Data")
 ) %>% 
@@
     type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Claassen 2020a", "Claassen w/uncertainty", "DCPO")))
+    model = factor(model, levels = c("Original", "Uncertainty", "Uncertainty+Expanded Data")))
 
@@
 result_regime <- bind_rows(
-  mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Claassen 2020a"),
-  mutate(MOCsumm(result_clsUncertain_whole[["pooled-regime"]]), model = "Claassen w/uncertainty"),
-  mutate(MOCsumm(result_dcpoUncertain_whole[["pooled-regime"]]), model = "DCPO")
+  mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm(mocresult_pureAJPS[["pooled-regime"]]), model = "Uncertainty"),
+  mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), model = "Uncertainty+Expanded Data")
 ) %>% 
@@
 result_regimeGmm <- bind_rows(
-  mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Claassen 2020a"),
-  mutate(MOCsumm(result_clsUncertain_whole[["gmm-regime"]]), model = "Claassen w/uncertainty"),
-    mutate(MOCsumm(result_dcpoUncertain_whole[["gmm-regime"]]), model = "DCPO")
+  mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm(mocresult_pureAJPS[["gmm-regime"]]), model = "Uncertainty"),
+ mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), model = "Uncertainty+Expanded Data")
 )%>% 
@@
     type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Claassen 2020a","Claassen w/uncertainty", "DCPO")))
+    model = factor(model, levels = c("Original","Uncertainty", "Uncertainty+Expanded Data")))
 terms2 <- factor(rev(c("Democracy[t-1]",
@@
 
-```{r claassenMocUncertaintyAPSR}
-load(here("data", "pure_cls_apsr.rda")) #use pure_cls_apsr instead of cls_apsr
-load(here("data", "exp_cls_apsr.rda")) #use exp_cls_apsr instead of cls_apsr
-
-df_clsAPSR <- purrr::map(1:900, function(anEntry) {
+```{r model-APSR}
+ls_ivECM <- c("diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)", 
+              "diff(Polyarchy_z, lag = 1) + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)")
+ls_ctrlECM <- c("", " + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1)")
+
+ls_eqECM <- glue("diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)") %>% 
+  outer(ls_ctrlECM, paste0) %>% 
+  as.vector()
+
+ls_ivFD <- c("Libdem_z",
+             "Polyarchy_z + Liberal_z")
+
+ls_ctrlFD <- c("", " + Corrup_TI_z")
+
+ls_eqFD <- glue("diff(SupDem_trim, lag = 1) ~ {ls_ivFD} + lnGDP_imp") %>% 
+  outer(ls_ctrlFD, paste0) %>% 
+  as.vector()
+
+ls_mod_apsrCLS <- c(
+  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
+  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
+)
+```
+
+```{r mocresult-pureAPSR}
+
+df_pure_clsAPSR <- purrr::map(1:900, function(anEntry) {
   pure_cls_apsr[[anEntry]] %>% 
@@
 
-df_our_clsAPSR <- purrr::map(1:900, function(anEntry) {
+mocresult_pureAPSR  <- map(ls_mod_apsrCLS, function(aMod){
+  result <- methodComposition3(df_pure_clsAPSR,aMod)
+})
+
+names(mocresult_pureAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
+                                "fd1", "fd-regime1", "fd2", "fd-regime2")
+
+saveRDS(mocresult_pureAPSR, file = here::here("ouput","estimates_moc_pureAPSR.RDS"))
+
+```
+
+```{r mocresult-expAPSR}
+
+df_exp_clsAPSR <- purrr::map(1:900, function(anEntry) {
   exp_cls_apsr[[anEntry]] %>% 
@@
 
-ls_ivECM <- c("diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)", 
-              "diff(Polyarchy_z, lag = 1) + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)")
-ls_ctrlECM <- c("", " + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1)")
-
-ls_eqECM <- glue("diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)") %>% 
-  outer(ls_ctrlECM, paste0) %>% 
-  as.vector() ##Change theta to SupDem_trim
-
-ls_ivFD <- c("Libdem_z",
-             "Polyarchy_z + Liberal_z")
-ls_ctrlFD <- c("", " + Corrup_TI_z")
-ls_eqFD <- glue("SupDem_trim ~ {ls_ivFD} + lnGDP_imp") %>% 
-  outer(ls_ctrlFD, paste0) %>% 
-  as.vector()
-ls_mod <- c(
-  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
-  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
-)
-
-result_clsUncertain  <- map(ls_mod, function(aMod){
-  result <- methodComposition3(df_clsAPSR,aMod)
-})  #claassen's data
-
-result_our_clsUncertain  <- map(ls_mod, function(aMod){
-  result <- methodComposition3(df_our_clsAPSR,aMod)
-})   ##our expanded data
-
-names(result_clsUncertain) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
+mocresult_expAPSR <- map(ls_mod_apsrCLS, function(aMod){
+  result <- methodComposition3(df_exp_clsAPSR,aMod)
+})
+
+names(mocresult_expAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
                                 "fd1", "fd-regime1", "fd2", "fd-regime2")
 
-names(result_our_clsUncertain) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
-                                "fd1", "fd-regime1", "fd2", "fd-regime2")
-
-saveRDS(result_clsUncertain, file = here::here("ouput","clsAPSR_uncertainty.RDS"))
-
-saveRDS(result_our_clsUncertain, file = here::here("ouput","our_clsAPSR_uncertainty.RDS"))
-
-```
-
-```{r  dcpoMocUncertaintyAPSR}
-load(here("data","dcpo_apsr.rda"))
-df_dcpoUncertainAPSR <- purrr::map(1:900, function(anEntry) {
-  dcpo_apsr[[anEntry]] %>% 
-    plm::pdata.frame(index = c("country", "year"))
-})
-
-ls_ivECM <- c("diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1)", 
-              "diff(Vdem_polyarchy_z, lag = 1) + plm::lag(Vdem_polyarchy_z, 1) + diff(Vdem_liberal_z, lag = 1) + plm::lag(Vdem_liberal_z, 1)")
-ls_ctrlECM <- c("", " + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1)")
-ls_eqECM <- glue("diff(theta_trim, lag = 1) ~ plm::lag(theta_trim, 1:2) + {ls_ivECM} + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1)") %>% 
-  outer(ls_ctrlECM, paste0) %>% 
-  as.vector()
-
-ls_ivFD <- c("Vdem_libdem_z",
-             "Vdem_polyarchy_z + Vdem_liberal_z")
-ls_ctrlFD <- c("", " + corruption_z")
-ls_eqFD <- glue("theta_trim ~ {ls_ivFD} + lg_imp_mdpgdp") %>% 
-  outer(ls_ctrlFD, paste0) %>% 
-  as.vector()
-
-ls_mod <- c(
-  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
-  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
-)
-
-result_dcpoUncertain  <- map(ls_mod, function(aMod){
-  result <- methodComposition3(df_dcpoUncertainAPSR,aMod)
-})
-
-names(result_dcpoUncertain) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
-                                "fd1", "fd-regime1", "fd2", "fd-regime2")
-
-saveRDS(result_dcpoUncertain, file =here("output","dcpoAPSR_uncertainty.RDS"))
-
-```
-
-```{r visualizedMocUncertainAPSR, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}
-
-#result_clsUncertain <- readRDS(here("output","clsAPSR_uncertainty.RDS"))
-result_clsUncertain <- readRDS(here("output","our_clsAPSR_uncertainty.RDS"))
-result_dcpoUncertain <- readRDS(here("output","dcpoAPSR_uncertainty.RDS"))
-result_clsAPSR <- readRDS(here("output","estimates_clsMeanAPSR.RDS"))
+saveRDS(mocresult_expAPSR, file = here::here("ouput","estimates_moc_expAPSR.RDS"))
+
+```
+
+```{r plot-mocAJPS, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}
 
 result_ecm1 <- bind_rows(
-  mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], model = "Claassen 2020b"),
-  mutate(MOCsumm2(result_clsUncertain[["pooled1"]]), model = "Claassen w/uncertainty"),
-  mutate(MOCsumm2(result_dcpoUncertain[["pooled1"]]), model = "DCPO")
+  mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm2(mocresult_pureAPSR[["pooled1"]]), model = "Uncertainty"),
+  mutate(MOCsumm2(mocresult_expAPSR[["pooled1"]]), model = "Uncertainty+Expanded Data")
 ) %>% 
@@
 result_fd1 <- bind_rows(
-  mutate(result_clsAPSR[["fd1"]][[1]][,1:3], model = "Claassen 2020b"),
-  mutate(MOCsumm2(result_clsUncertain[["fd1"]]), model = "Claassen w/uncertainty"),
-  mutate(MOCsumm2(result_dcpoUncertain[["fd1"]]), model = "DCPO")
+  mutate(result_clsAPSR[["fd1"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm2(mocresult_pureAPSR[["fd1"]]), model = "Uncertainty"),
+  mutate(MOCsumm2(mocresult_expAPSR[["fd1"]]), model = "Uncertainty+Expanded Data")
 ) %>% 
@@
     type = factor(type,  levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Claassen 2020b","Claassen w/uncertainty", "DCPO"))
+    model = factor(model, levels = c("Original","Uncertainty", "Uncertainty+Expanded Data"))
   )
@@
 ############################ Regime specified####
+
 result_ecmReg1 <- bind_rows(
-  mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], model = "Claassen 2020b"),
-  mutate(MOCsumm2(result_clsUncertain[["pooled-regime1"]]), model = "Claassen w/uncertainty"),
-  mutate(MOCsumm2(result_dcpoUncertain[["pooled-regime1"]]), model = "DCPO")
+  mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm2(mocresult_pureAPSR[["pooled-regime1"]]), model = "Uncertainty"),
+  mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime1"]]), model = "Uncertainty+Expanded Data")
 ) %>% 
@@
 result_fdReg1 <- bind_rows(
-  mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], model = "Claassen 2020b"),
-  mutate(MOCsumm2(result_clsUncertain[["fd-regime1"]]), model = "Claassen w/uncertainty"),
-  mutate(MOCsumm2(result_dcpoUncertain[["fd-regime1"]]), model = "DCPO")
+  mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm2(mocresult_pureAPSR[["fd-regime1"]]), model = "Uncertainty"),
+  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime1"]]), model = "Uncertainty+Expanded Data")
 ) %>% 
@@
 result_ecm2 <- bind_rows(
-  mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], model = "Claassen 2020b"),
-  mutate(MOCsumm2(result_clsUncertain[["pooled2"]]), model = "Claassen w/uncertainty"),
-  mutate(MOCsumm2(result_dcpoUncertain[["pooled2"]]), model = "DCPO")
+  mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm2(mocresult_pureAPSR[["pooled2"]]), model = "Uncertainty"),
+  mutate(MOCsumm2(mocresult_expAPSR[["pooled2"]]), model = "Uncertainty+Expanded Data")
 ) %>% 
@@
 result_fd2 <- bind_rows(
-  mutate(result_clsAPSR[["fd2"]][[1]][,1:3], model = "Claassen 2020b"),
-  mutate(MOCsumm2(result_clsUncertain[["fd2"]]), model = "Claassen w/uncertainty"),
-  mutate(MOCsumm2(result_dcpoUncertain[["fd2"]]), model = "DCPO")
+  mutate(result_clsAPSR[["fd2"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm2(mocresult_pureAPSR[["fd2"]]), model = "Uncertainty"),
+  mutate(MOCsumm2(mocresult_expAPSR[["fd2"]]), model = "Uncertainty+Expanded Data")
 ) %>% 
@@
     type = factor(type,  levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Claassen 2020b", "Claassen w/uncertainty","DCPO"))
+    model = factor(model, levels = c("Original","Uncertainty", "Uncertainty+Expanded Data"))
   )
@@
 result_ecmReg2 <- bind_rows(
-  mutate(result_clsAPSR[["pooled-regime2"]][[1]][,1:3], model = "Claassen 2020b"),
-  mutate(MOCsumm2(result_clsUncertain[["pooled-regime2"]]), model = "Claassen w/uncertainty"),
-  mutate(MOCsumm2(result_dcpoUncertain[["pooled-regime2"]]), model = "DCPO")) %>% 
+  mutate(result_clsAPSR[["pooled-regime2"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm2(mocresult_pureAPSR[["pooled-regime2"]]), model = "Uncertainty"),
+  mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime2"]]), model = "Uncertainty+Expanded Data")) %>% 
   mutate(type = "ECM")
@@
 result_fdReg2 <- bind_rows(
-  mutate(result_clsAPSR[["fd-regime2"]][[1]][,1:3], model = "Claassen 2020b"),
-  mutate(MOCsumm2(result_clsUncertain[["fd-regime2"]]), model = "Claassen w/uncertainty"),
-  mutate(MOCsumm2(result_dcpoUncertain[["fd-regime2"]]), model = "DCPO")) %>% 
+  mutate(result_clsAPSR[["fd-regime2"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm2(mocresult_pureAPSR[["fd-regime2"]]), model = "Uncertainty"),
+  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime2"]]), model = "Uncertainty+Expanded Data")) %>% 
   mutate(type = "First Difference")

### 2021-07-09 paper/dcpo_demsupport.Rmd
add sentences on MOC and overimputation

@@
 Although measurement uncertainty has yet not attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can bias coefficient estimates and standard errors.
-Especially when measurement error is correlated with the dependent variable, the resulting bias could either attentuate or exaggerate the magnitude of the estimated effects [see, e.g., @Blackwell2017, 360].
+Especially when measurement error is correlated with the dependent variable, the resulting bias could either attentuate or exaggerate the magnitude of the estimated effects [see, e.g., @Blackwell2017, 360; @caughey_policy_2018, 254].
 In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey_policy_2018, 254].
@@
 Then we perform each analysis repeatedly on its respective collection of datasets, and combine the results following the rules set out in @Rubin1987 [see, e.g., @Schnakenberg2014; @Crabtree2015].
-Our approach of incorporating uncertainty is similar in the logic of @Blackwell2017a's multiple overimputation, that is, creating multiple data set from the posterior distribution of the true latent value, applying analysis model for each dataset, and then averaging results by using Rubin's rule.
+Our approach of incorporating uncertainty is analogous to @Blackwell2017a's multiple overimputation which corrects the Between imputation variance. 
+We also employ one alternative technique known as “method of composition” [@treier_democracy_2008, 215) as robuestness check [see Supplementary Appendix xx].
 

### 2021-07-09 paper/dcpo_demsupport.Rmd
explain Rubin's rule in detail.

@@
 Then we perform each analysis repeatedly on its respective collection of datasets, and combine the results following the rules set out in @Rubin1987 [see, e.g., @Schnakenberg2014; @Crabtree2015].
-Our approach of incorporating uncertainty is analogous to @Blackwell2017a's multiple overimputation which corrects the Between imputation variance. 
+Our approach of incorporating uncertainty is analogous to @Blackwell2017a's multiple overimputation, that is, creating multiple data set from the posterior distribution of the true latent value, applying analysis model for each dataset, and then averaging results by correcting the Between imputation variance.
 We also employ one alternative technique known as “method of composition” [@treier_democracy_2008, 215) as robuestness check [see Supplementary Appendix xx].

### 2021-07-12 paper/dcpo_demsupport.Rmd
Add literature on democratic support and emancipative values. @sammo3182, the new version is ready!

--- 2021-07-09 paper/dcpo_demsupport.Rmd
@@
 From a theoretical perspective, the effect of democracy on public support may depend not on its mere existence but on its effectiveness [see @Magalhaes2014] and particularly with regard to redistribution [see @Krieckhaus2014].
-Similarly, the effect of public support on democracy may depend on the extent to which those who support democracy are also dissatisfied with the current regime's performance; that is, that it is not democratic support that is important to democratic change, but rather unsatisfied democratic demand [see @Qi2011].
+Similarly, the impact of public support on democracy may depend on the extent to which those who support democracy are also dissatisfied with the current regime's performance; that is, that it is not democratic support that is important to democratic change, but rather unsatisfied democratic demand [see @Qi2011].
+Culturally, whether the public democratic support has a pro-democratic or anti-authoritarian effect is bounded by emancipative value that, as a belief-anchored orientation, shapes the public's understanding of democracy [see @Brunkert2019; @Kirsch2019; @Kruse2019].
 Of course, it could in fact be that democratic change does not actually depend on public opinion of any sort at all but instead is an elite-driven phenomenon [see, e.g., @levitsky_how_2018].
@@
 Then we perform each analysis repeatedly on its respective collection of datasets, and combine the results following the rules set out in @Rubin1987 [see, e.g., @Schnakenberg2014; @Crabtree2015].
-Our approach of incorporating uncertainty is analogous to @Blackwell2017a's multiple overimputation which corrects the Between imputation variance. 
+Our approach of incorporating uncertainty is analogous to @Blackwell2017a's multiple overimputation, that is, creating multiple data set from the posterior distribution of the true latent value, applying analysis model for each dataset, and then averaging results by correcting both within and between imputation variance.
 We also employ one alternative technique known as “method of composition” [@treier_democracy_2008, 215) as robuestness check [see Supplementary Appendix xx].
@@
 Instead, that work contends, it is the combination of democratic support and dissatisfaction with current regime performance that generates demand for greater democracy.
+The effects of public support also have cultural-bound.
+@Brunkert2019 contends outspoken support for democracy is a "deceptive indicator of public's affinity to democracy" [423] and finds public support has neither pro-democratic nor anti-authoritarian effect without controlling emancipative values.
+Empirical results show that the meaning of support for democracy is dependent on emancipation values and is reversed to its own negation in a society with weak emancipative values [see, e.g.,@Kirsch2019, 83-85].
 And we must be open to the possibility that no theoretical elaboration, no respecification of these models will reveal relationships between public opinion and democracy.

### 2021-07-13 paper/dcpo_demsupport.Rmd

--- 2021-07-09 paper/dcpo_demsupport.Rmd
@@
 
-mocresult_pureAJPS <- readRDS(here("output", "estimates_moc_pureAJPS.RDS"))
-mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expAJPS.RDS"))
-mocresult_pureAPSR <- readRDS(here("output", "estimates_moc_pureAPSR.RDS"))
-mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expAPSR.RDS"))
-
 ```
@@
 Although measurement uncertainty has yet not attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can bias coefficient estimates and standard errors.
-Especially when measurement error is correlated with the dependent variable, the resulting bias could either attentuate or exaggerate the magnitude of the estimated effects [see, e.g., @Blackwell2017, 360; @caughey_policy_2018, 254].
+Especially when measurement error is correlated with the dependent variable, the resulting bias could either attentuate or exaggerate the magnitude of the estimated effects [see, e.g., @Blackwell2017, 360].
 In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey_policy_2018, 254].
@@
 Then we perform each analysis repeatedly on its respective collection of datasets, and combine the results following the rules set out in @Rubin1987 [see, e.g., @Schnakenberg2014; @Crabtree2015].
-Our approach of incorporating uncertainty is analogous to @Blackwell2017a's multiple overimputation which corrects the Between imputation variance. 
-We also employ one alternative technique known as “method of composition” [@treier_democracy_2008, 215) as robuestness check [see Supplementary Appendix xx].
+Our approach of incorporating uncertainty is similar in the logic of @Blackwell2017a's multiple overimputation, that is, creating multiple data set from the posterior distribution of the true latent value, applying analysis model for each dataset, and then averaging results by using Rubin's rule.
 
@@
     # Using expressions of underscore and greek letters
-    #scale_color_gb(palette = "digitMixed") +
+    scale_color_gb(palette = "digitMixed") +
     facet_wrap(~ type)
@@
     # Using expressions of underscore and greek letters
-   # scale_color_gb(palette = "digitMixed") +
+    scale_color_gb(palette = "digitMixed") +
     facet_wrap( ~ type)
@@
 # Replication with Alternative Methods Accounting for Uncertainty
-```{r moc_estimates}
-
-result_clsAJPS <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
-result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
-mocresult_pureAJPS <- readRDS(here("output", "estimates_moc_pureAJPS.RDS"))
-mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expAJPS.RDS"))
-mocresult_pureAPSR <- readRDS(here("output", "estimates_moc_pureAPSR.RDS"))
-mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expAPSR.RDS"))
-
-```
-
-```{r model-AJPS}
-
-#ls_iv <- c("plm::lag(theta, 1)", 
-#    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) ")
+```{r MocclaassenUncertaintyAJPS}
+load(here("data","cls_ajps.rda"))
+
+df_cls <- purrr::map(1:900, function(anEntry) {
+  cls_ajps[[anEntry]] %>% 
+    plm::pdata.frame(index = c("country", "year"))
+})
 
 ls_iv <- c("plm::lag(SupDem_trim, 1)",                         
-    "plm::lag(theta_dem_trim, 1) + plm::lag(theta_aut_trim, 1) ") #use trimmed data
-
+           "plm::lag(theta_dem_trim, 1) + plm::lag(theta_aut_trim, 1) ") ##all use trim
 ls_method <- c("plm", "pgmm")
-
-ls_eq <- glue("Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + {ls_iv} + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)")
-
-ls_mod_ajpsCLS <- c(
+ls_eq <- glue("Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + {ls_iv} + 
+              plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + 
+              plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)")
+
+ls_mod <- c(
   glue("plm({ls_eq}, model = 'pooling', data = aData)"),
@@
 
-```
-
-```{r mocresult-pureAJPS}
-
-df_pure_clsAjps <- purrr::map(1:900, function(anEntry) {
-  pure_cls_ajps[[anEntry]] %>% 
+result_clsUncertain  <- map(ls_mod[1:2], function(aMod){
+  result <- methodComposition1(df_cls,aMod)
+})
+
+names(result_clsUncertain) <- c("pooled", "pooled-regime")
+
+result_clsUncertain_gmm  <- map(ls_mod[3:4], function(aMod){
+  result <- methodComposition2(df_cls,aMod)
+})
+names(result_clsUncertain_gmm) <- c("gmm", "gmm-regime")
+
+result_clsUncertain_whole <- append(result_clsUncertain, result_clsUncertain_gmm)
+
+saveRDS(result_clsUncertain_whole, file =here("output","clsAJPS_uncertainty.RDS"))
+
+```
+
+```{r MocdcpoUncertaintyAJPS}
+load(here("data","dcpo_ajps.rda"))
+
+df_dcpo <- purrr::map(1:900, function(anEntry) {
+  dcpo_ajps[[anEntry]] %>%     #original data has include theta_dem_trim
     plm::pdata.frame(index = c("country", "year"))
@@
 
-result_pure_clsUncertain  <- map(ls_mod_ajpsCLS[1:2], function(aMod){
-  result <- methodComposition1(df_pure_clsAjps,aMod)
-})
-
-names(result_pure_clsUncertain) <- c("pooled", "pooled-regime")
-
-result_pure_clsUncertain_gmm  <- map(ls_mod_ajpsCLS[3:4], function(aMod){
-  result <- methodComposition2(df_pure_clsAjps,aMod)
-})
-names(result_pure_clsUncertain_gmm) <- c("gmm", "gmm-regime")
-
-mocresult_pureAJPS <- append(result_pure_clsUncertain, result_pure_clsUncertain_gmm)
-
-saveRDS(mocresult_pureAJPS, file =here("output","estimates_moc_pureAJPS.RDS"))
-
-```
-
-```{r mocresult-expAJPS}
-
-df_exp_clsAjps <- purrr::map(1:900, function(anEntry) {
-  exp_cls_ajps[[anEntry]] %>% 
-    plm::pdata.frame(index = c("country", "year"))
-})
-
-result_exp_clsUncertain  <- map(ls_mod_ajpsCLS[1:2], function(aMod){
-  result <- methodComposition1(df_exp_clsAjps,aMod)
-})
-
-names(result_exp_clsUncertain) <- c("pooled", "pooled-regime")
-
-result_exp_clsUncertain_gmm  <- map(ls_mod_ajpsCLS[3:4], function(aMod){
-  result <- methodComposition2(df_exp_clsAjps,aMod)
-})
-names(result_exp_clsUncertain_gmm) <- c("gmm", "gmm-regime")
-
-mocresult_expAJPS <- append(result_exp_clsUncertain, result_exp_clsUncertain_gmm)
-
-saveRDS(mocresult_expAJPS, file =here("output","estimates_moc_expAJPS.RDS"))
-
-```
-
-```{r plot-mocAJPS, fig.cap= "The Effect of Public Support on Democracy ", eval = TRUE, fig.width=7, fig.height=10}
+ls_iv <- c("plm::lag(theta_trim, 1)", 
+           "plm::lag(theta_dem_trim, 1) + plm::lag(theta_aut_trim, 1)") #use trimed data
+ls_method <- c("plm", "pgmm")
+ls_eq <- glue("Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + {ls_iv} + plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) + plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)")
+ls_mod <- c(
+  glue("plm({ls_eq}, model = 'pooling', data = aData)"),
+  glue(
+    "pgmm({ls_eq} | plm::lag(Vdem_libdem, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
+  )
+)
+
+result_dcpoUncertain  <- map(ls_mod[1:2], function(aMod){
+  result <- methodComposition1(df_dcpo,aMod)
+})
+
+names(result_dcpoUncertain) <- c("pooled", "pooled-regime")
+
+result_dcpoUncertain_gmm  <- map(ls_mod[3:4], function(aMod){
+  result <- methodComposition2(df_dcpo,aMod)
+})
+
+names(result_dcpoUncertain_gmm) <- c("gmm", "gmm-regime")
+
+result_dcpoUncertain_whole <- append(result_dcpoUncertain, result_dcpoUncertain_gmm)
+
+saveRDS(result_dcpoUncertain_whole, file =here("output","dcpoAJPS_uncertainty.RDS"))
+
+```
+
+```{r visualizedMocUncertainAJPS, fig.cap= "The Effect of Public Support on Democracy ", eval = TRUE, fig.width=7, fig.height=10}
+
+result_clsAJPS <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
+result_clsUncertain_whole <- readRDS(here("output", "clsAJPS_uncertainty.RDS"))
+result_dcpoUncertain_whole <- readRDS(here("output", "dcpoAJPS_uncertainty.RDS"))
 
 result_pooled <- bind_rows(
-  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_pureAJPS[["pooled"]]), model = "Uncertainty"),
-  mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), model = "Uncertainty+Expanded Data")
+  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Claassen 2020a"),
+  mutate(MOCsumm(result_clsUncertain_whole[["pooled"]]), model = "Claassen w/uncertainty"),
+  mutate(MOCsumm(result_dcpoUncertain_whole[["pooled"]]), model = "DCPO")
 ) %>% 
@@
 result_gmm <- bind_rows(
-  mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_pureAJPS[["gmm"]]), model = "Uncertainty"),
-  mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), model = "Uncertainty+Expanded Data")
+  mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Claassen 2020a"),
+  mutate(MOCsumm(result_clsUncertain_whole[["gmm"]]), model = "Claassen w/uncertainty"),
+  mutate(MOCsumm(result_dcpoUncertain_whole[["gmm"]]), model = "DCPO")
 ) %>% 
@@
     type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Original", "Uncertainty", "Uncertainty+Expanded Data")))
+    model = factor(model, levels = c("Claassen 2020a", "Claassen w/uncertainty", "DCPO")))
 
@@
 result_regime <- bind_rows(
-  mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_pureAJPS[["pooled-regime"]]), model = "Uncertainty"),
-  mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), model = "Uncertainty+Expanded Data")
+  mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Claassen 2020a"),
+  mutate(MOCsumm(result_clsUncertain_whole[["pooled-regime"]]), model = "Claassen w/uncertainty"),
+  mutate(MOCsumm(result_dcpoUncertain_whole[["pooled-regime"]]), model = "DCPO")
 ) %>% 
@@
 result_regimeGmm <- bind_rows(
-  mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_pureAJPS[["gmm-regime"]]), model = "Uncertainty"),
- mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), model = "Uncertainty+Expanded Data")
+  mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Claassen 2020a"),
+  mutate(MOCsumm(result_clsUncertain_whole[["gmm-regime"]]), model = "Claassen w/uncertainty"),
+    mutate(MOCsumm(result_dcpoUncertain_whole[["gmm-regime"]]), model = "DCPO")
 )%>% 
@@
     type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Original","Uncertainty", "Uncertainty+Expanded Data")))
+    model = factor(model, levels = c("Claassen 2020a","Claassen w/uncertainty", "DCPO")))
 terms2 <- factor(rev(c("Democracy[t-1]",
@@
 
-```{r model-APSR}
+```{r claassenMocUncertaintyAPSR}
+load(here("data", "pure_cls_apsr.rda")) #use pure_cls_apsr instead of cls_apsr
+load(here("data", "exp_cls_apsr.rda")) #use exp_cls_apsr instead of cls_apsr
+
+df_clsAPSR <- purrr::map(1:900, function(anEntry) {
+  pure_cls_apsr[[anEntry]] %>% 
+    plm::pdata.frame(index = c("country", "year"))
+}
+)
+
+df_our_clsAPSR <- purrr::map(1:900, function(anEntry) {
+  exp_cls_apsr[[anEntry]] %>% 
+    plm::pdata.frame(index = c("country", "year"))
+}
+)
+
 ls_ivECM <- c("diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)", 
@@
   outer(ls_ctrlECM, paste0) %>% 
-  as.vector()
+  as.vector() ##Change theta to SupDem_trim
 
@@
              "Polyarchy_z + Liberal_z")
-
 ls_ctrlFD <- c("", " + Corrup_TI_z")
-
-ls_eqFD <- glue("diff(SupDem_trim, lag = 1) ~ {ls_ivFD} + lnGDP_imp") %>% 
+ls_eqFD <- glue("SupDem_trim ~ {ls_ivFD} + lnGDP_imp") %>% 
   outer(ls_ctrlFD, paste0) %>% 
   as.vector()
-
-ls_mod_apsrCLS <- c(
+ls_mod <- c(
   glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
@@
 )
-```
-
-```{r mocresult-pureAPSR}
-
-df_pure_clsAPSR <- purrr::map(1:900, function(anEntry) {
-  pure_cls_apsr[[anEntry]] %>% 
+
+result_clsUncertain  <- map(ls_mod, function(aMod){
+  result <- methodComposition3(df_clsAPSR,aMod)
+})  #claassen's data
+
+result_our_clsUncertain  <- map(ls_mod, function(aMod){
+  result <- methodComposition3(df_our_clsAPSR,aMod)
+})   ##our expanded data
+
+names(result_clsUncertain) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
+                                "fd1", "fd-regime1", "fd2", "fd-regime2")
+
+names(result_our_clsUncertain) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
+                                "fd1", "fd-regime1", "fd2", "fd-regime2")
+
+saveRDS(result_clsUncertain, file = here::here("ouput","clsAPSR_uncertainty.RDS"))
+
+saveRDS(result_our_clsUncertain, file = here::here("ouput","our_clsAPSR_uncertainty.RDS"))
+
+```
+
+```{r  dcpoMocUncertaintyAPSR}
+load(here("data","dcpo_apsr.rda"))
+df_dcpoUncertainAPSR <- purrr::map(1:900, function(anEntry) {
+  dcpo_apsr[[anEntry]] %>% 
     plm::pdata.frame(index = c("country", "year"))
-}
-)
-
-mocresult_pureAPSR  <- map(ls_mod_apsrCLS, function(aMod){
-  result <- methodComposition3(df_pure_clsAPSR,aMod)
-})
-
-names(mocresult_pureAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
+})
+
+ls_ivECM <- c("diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1)", 
+              "diff(Vdem_polyarchy_z, lag = 1) + plm::lag(Vdem_polyarchy_z, 1) + diff(Vdem_liberal_z, lag = 1) + plm::lag(Vdem_liberal_z, 1)")
+ls_ctrlECM <- c("", " + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1)")
+ls_eqECM <- glue("diff(theta_trim, lag = 1) ~ plm::lag(theta_trim, 1:2) + {ls_ivECM} + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1)") %>% 
+  outer(ls_ctrlECM, paste0) %>% 
+  as.vector()
+
+ls_ivFD <- c("Vdem_libdem_z",
+             "Vdem_polyarchy_z + Vdem_liberal_z")
+ls_ctrlFD <- c("", " + corruption_z")
+ls_eqFD <- glue("theta_trim ~ {ls_ivFD} + lg_imp_mdpgdp") %>% 
+  outer(ls_ctrlFD, paste0) %>% 
+  as.vector()
+
+ls_mod <- c(
+  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
+  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
+)
+
+result_dcpoUncertain  <- map(ls_mod, function(aMod){
+  result <- methodComposition3(df_dcpoUncertainAPSR,aMod)
+})
+
+names(result_dcpoUncertain) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
                                 "fd1", "fd-regime1", "fd2", "fd-regime2")
 
-saveRDS(mocresult_pureAPSR, file = here::here("ouput","estimates_moc_pureAPSR.RDS"))
-
-```
-
-```{r mocresult-expAPSR}
-
-df_exp_clsAPSR <- purrr::map(1:900, function(anEntry) {
-  exp_cls_apsr[[anEntry]] %>% 
-    plm::pdata.frame(index = c("country", "year"))
-}
-)
-
-mocresult_expAPSR <- map(ls_mod_apsrCLS, function(aMod){
-  result <- methodComposition3(df_exp_clsAPSR,aMod)
-})
-
-names(mocresult_expAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
-                                "fd1", "fd-regime1", "fd2", "fd-regime2")
-
-saveRDS(mocresult_expAPSR, file = here::here("ouput","estimates_moc_expAPSR.RDS"))
-
-```
-
-```{r plot-mocAJPS, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}
+saveRDS(result_dcpoUncertain, file =here("output","dcpoAPSR_uncertainty.RDS"))
+
+```
+
+```{r visualizedMocUncertainAPSR, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}
+
+#result_clsUncertain <- readRDS(here("output","clsAPSR_uncertainty.RDS"))
+result_clsUncertain <- readRDS(here("output","our_clsAPSR_uncertainty.RDS"))
+result_dcpoUncertain <- readRDS(here("output","dcpoAPSR_uncertainty.RDS"))
+result_clsAPSR <- readRDS(here("output","estimates_clsMeanAPSR.RDS"))
 
 result_ecm1 <- bind_rows(
-  mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_pureAPSR[["pooled1"]]), model = "Uncertainty"),
-  mutate(MOCsumm2(mocresult_expAPSR[["pooled1"]]), model = "Uncertainty+Expanded Data")
+  mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], model = "Claassen 2020b"),
+  mutate(MOCsumm2(result_clsUncertain[["pooled1"]]), model = "Claassen w/uncertainty"),
+  mutate(MOCsumm2(result_dcpoUncertain[["pooled1"]]), model = "DCPO")
 ) %>% 
@@
 result_fd1 <- bind_rows(
-  mutate(result_clsAPSR[["fd1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_pureAPSR[["fd1"]]), model = "Uncertainty"),
-  mutate(MOCsumm2(mocresult_expAPSR[["fd1"]]), model = "Uncertainty+Expanded Data")
+  mutate(result_clsAPSR[["fd1"]][[1]][,1:3], model = "Claassen 2020b"),
+  mutate(MOCsumm2(result_clsUncertain[["fd1"]]), model = "Claassen w/uncertainty"),
+  mutate(MOCsumm2(result_dcpoUncertain[["fd1"]]), model = "DCPO")
 ) %>% 
@@
     type = factor(type,  levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Original","Uncertainty", "Uncertainty+Expanded Data"))
+    model = factor(model, levels = c("Claassen 2020b","Claassen w/uncertainty", "DCPO"))
   )
@@
 ############################ Regime specified####
-
 result_ecmReg1 <- bind_rows(
-  mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_pureAPSR[["pooled-regime1"]]), model = "Uncertainty"),
-  mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime1"]]), model = "Uncertainty+Expanded Data")
+  mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], model = "Claassen 2020b"),
+  mutate(MOCsumm2(result_clsUncertain[["pooled-regime1"]]), model = "Claassen w/uncertainty"),
+  mutate(MOCsumm2(result_dcpoUncertain[["pooled-regime1"]]), model = "DCPO")
 ) %>% 
@@
 result_fdReg1 <- bind_rows(
-  mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_pureAPSR[["fd-regime1"]]), model = "Uncertainty"),
-  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime1"]]), model = "Uncertainty+Expanded Data")
+  mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], model = "Claassen 2020b"),
+  mutate(MOCsumm2(result_clsUncertain[["fd-regime1"]]), model = "Claassen w/uncertainty"),
+  mutate(MOCsumm2(result_dcpoUncertain[["fd-regime1"]]), model = "DCPO")
 ) %>% 
@@
 result_ecm2 <- bind_rows(
-  mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_pureAPSR[["pooled2"]]), model = "Uncertainty"),
-  mutate(MOCsumm2(mocresult_expAPSR[["pooled2"]]), model = "Uncertainty+Expanded Data")
+  mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], model = "Claassen 2020b"),
+  mutate(MOCsumm2(result_clsUncertain[["pooled2"]]), model = "Claassen w/uncertainty"),
+  mutate(MOCsumm2(result_dcpoUncertain[["pooled2"]]), model = "DCPO")
 ) %>% 
@@
 result_fd2 <- bind_rows(
-  mutate(result_clsAPSR[["fd2"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_pureAPSR[["fd2"]]), model = "Uncertainty"),
-  mutate(MOCsumm2(mocresult_expAPSR[["fd2"]]), model = "Uncertainty+Expanded Data")
+  mutate(result_clsAPSR[["fd2"]][[1]][,1:3], model = "Claassen 2020b"),
+  mutate(MOCsumm2(result_clsUncertain[["fd2"]]), model = "Claassen w/uncertainty"),
+  mutate(MOCsumm2(result_dcpoUncertain[["fd2"]]), model = "DCPO")
 ) %>% 
@@
     type = factor(type,  levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Original","Uncertainty", "Uncertainty+Expanded Data"))
+    model = factor(model, levels = c("Claassen 2020b", "Claassen w/uncertainty","DCPO"))
   )
@@
 result_ecmReg2 <- bind_rows(
-  mutate(result_clsAPSR[["pooled-regime2"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_pureAPSR[["pooled-regime2"]]), model = "Uncertainty"),
-  mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime2"]]), model = "Uncertainty+Expanded Data")) %>% 
+  mutate(result_clsAPSR[["pooled-regime2"]][[1]][,1:3], model = "Claassen 2020b"),
+  mutate(MOCsumm2(result_clsUncertain[["pooled-regime2"]]), model = "Claassen w/uncertainty"),
+  mutate(MOCsumm2(result_dcpoUncertain[["pooled-regime2"]]), model = "DCPO")) %>% 
   mutate(type = "ECM")
@@
 result_fdReg2 <- bind_rows(
-  mutate(result_clsAPSR[["fd-regime2"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_pureAPSR[["fd-regime2"]]), model = "Uncertainty"),
-  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime2"]]), model = "Uncertainty+Expanded Data")) %>% 
+  mutate(result_clsAPSR[["fd-regime2"]][[1]][,1:3], model = "Claassen 2020b"),
+  mutate(MOCsumm2(result_clsUncertain[["fd-regime2"]]), model = "Claassen w/uncertainty"),
+  mutate(MOCsumm2(result_dcpoUncertain[["fd-regime2"]]), model = "DCPO")) %>% 
   mutate(type = "First Difference")

### 2021-07-13 paper/dcpo_demsupport.Rmd

--- 2021-07-12 paper/dcpo_demsupport.Rmd
@@
 Although measurement uncertainty has yet not attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can bias coefficient estimates and standard errors.
-Especially when measurement error is correlated with the dependent variable, the resulting bias could either attentuate or exaggerate the magnitude of the estimated effects [see, e.g., @Blackwell2017, 360; @caughey_policy_2018, 254].
+Especially when measurement error is correlated with the dependent variable, the resulting bias could either attentuate or exaggerate the magnitude of the estimated effects [see, e.g., @Blackwell2017, p.360; @caughey_policy_2018, p.254].
 In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey_policy_2018, 254].
@@
 # Replication with Alternative Methods Accounting for Uncertainty
-```{r moc_estimates}
+
+```{r moc-estimates}
 
@@
 mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expAPSR.RDS"))
-
-```
-
-```{r model-AJPS}
-
-#ls_iv <- c("plm::lag(theta, 1)", 
-#    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) ")
-
-ls_iv <- c("plm::lag(SupDem_trim, 1)", 
-    "plm::lag(theta_dem_trim, 1) + plm::lag(theta_aut_trim, 1) ") #use trimmed data
-
-ls_method <- c("plm", "pgmm")
-
-ls_eq <- glue("Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + {ls_iv} + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)")
-
-ls_mod_ajpsCLS <- c(
-    glue("plm({ls_eq}, model = 'pooling', data = aData)"),
-    glue(
-        "pgmm({ls_eq} | plm::lag(Libdem_VD, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
-    )
-)
 
@@
 grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
-
-```
-
-```{r model-APSR}
-ls_ivECM <- c("diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)", 
-              "diff(Polyarchy_z, lag = 1) + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)")
-ls_ctrlECM <- c("", " + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1)")
-
-ls_eqECM <- glue("diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)") %>% 
-  outer(ls_ctrlECM, paste0) %>% 
-  as.vector()
-
-ls_ivFD <- c("Libdem_z",
-             "Polyarchy_z + Liberal_z")
-
-ls_ctrlFD <- c("", " + Corrup_TI_z")
-
-ls_eqFD <- glue("diff(SupDem_trim, lag = 1) ~ {ls_ivFD} + lnGDP_imp") %>% 
-  outer(ls_ctrlFD, paste0) %>% 
-  as.vector()
-
-ls_mod_apsrCLS <- c(
-  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
-  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
-)
 ```
@@
 
-```{r plot-mocAJPS, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}
+```{r plot-mocAPSR, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}
 
@@
   scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  # scale_color_uiowa(name = "", palette = "digitMixed") +
   labs(

### 2021-07-13 paper/dcpo_demsupport.Rmd
cleanning the words of DCPO

@@
 But the evidence for either part of this claim has been decidedly mixed.
-Countries with greater democratic support have been found to become stronger and more stable democracies [e.g., @Inglehart2005, 251-254] and just the opposite [@Fails2010, 182-183].
-Similarly, studies have alternately found that more experience with democracy yields more democratic support [e.g., @Fails2010, 183; @Wuttke2020a, 5-6] or instead that long-established democracies are suffering from democratic fatigue [e.g., @Denemark2016; @Foa2017].
+Countries with greater democratic support have been found to become stronger and more stable democracies [e.g., @Inglehart2005, pp. 251-254] and just the opposite [@Fails2010, pp. 182-183].
+Similarly, studies have alternately found that more experience with democracy yields more democratic support [e.g., @Fails2010, p.
+183; @Wuttke2020a, pp.
+5-6] or instead that long-established democracies are suffering from democratic fatigue [e.g., @Denemark2016; @Foa2017].
 
@@
 A pair of prominent recent works took advantage of this latent variable approach to measure democratic support for over one hundred countries for up to nearly three decades and to then assess, respectively, its consequences for and roots in democratic change [@Claassen2020a; @Claassen2020b].
-These works concluded, first and supporting the classic argument, that mass support had a positive impact on democratic change, especially the endurance of democracy [@Claassen2020a, 127-130], and, second and directly contrary to it, democratic change has a thermostatic effect on public support, that is that, rather than generating its own support, deepening democracy provokes a backlash and it is instead democratic backsliding that calls forth greater public support [@Claassen2020b, 46-50].
+These works concluded, first and supporting the classic argument, that mass support had a positive impact on democratic change, especially the endurance of democracy [@Claassen2020a, pp.
+127-130], and, second and directly contrary to it, democratic change has a thermostatic effect on public support, that is that, rather than generating its own support, deepening democracy provokes a backlash and it is instead democratic backsliding that calls forth greater public support [@Claassen2020b, 46-50].
 
 The models employed in these studies' analyses, though, do not account for uncertainty in their measurement of democratic support.
-Measurement error challenges statistical analyses, especially when it is correlated with a dependent variable which is the case of democratic support, but it is often ignored in the analysis [@Blackwell2017; @Blackwell2017a].
+Measurement error challenges statistical analyses, especially when it is correlated with an outcome variable which is the case of democratic support, but it is often ignored in the analysis [@Blackwell2017; @Blackwell2017a].
 Because they are unobserved, latent variables are inherently accompanied by measurement uncertainty.
@@
 In this letter, we reexamine the classic arguments about support for democracy and democratic change tested in these two pieces while correcting this oversight.
-In addition to incorporating the measurement uncertainty, we also sought to reduce it by employing a superior model of public opinion, the Dynamic Comparative Public Opinion (DCPO) model developed by @Solt2020a, and more data to estimate democratic support for 144 countries for up to 33 years between 1988 and 2020.
-Our analyses reveal that the significant relationships between public support and democratic change disappear once measurement uncertainty is taken into account, both in replications with the studies' original data and in our extension DCPO analyses that incorporate additional data.
+In addition to incorporating the measurement uncertainty, we also sought to reduce it by expanding the estimated data to including 144 countries for up to 33 years between 1988 and 2020 (based on 26% more questions and 33% more survey sources).
+Our analyses reveal that the significant relationships between public support and democratic change disappear once measurement uncertainty is taken into account, both in replications with the studies' original data and with expanded data.
 That is, once measurement uncertainty is accounted for, there is no empirical support for either claim put forward in these two works: declining democratic support does not signal subsequent democratic backsliding, and changes in democracy do not spur a thermostatic response in democratic support.
@@
 As latent variable measurement models become more commonly used, it is absolutely necessary for researchers employing them to incorporate the associated uncertainty into analyses.
-And, at a time when democracy is seen as under threat around the world [e.g., @Diamond2015], taken together, Claassen [-@Claassen2020a; -@Claassen2020b] send what is ultimately a reassuring message: the fate of democracy rests with us, the public, and when democratic institutions are undermined, we will swing to their support and constitute "an obstacle to democratic backsliding" [@Claassen2020b, 51].
+And, at a time when democracy is seen as under threat around the world [e.g., @Diamond2015], taken together, Claassen [-@Claassen2020a; -@Claassen2020b] send what is ultimately a reassuring message: the fate of democracy rests with us, the public, and when democratic institutions are undermined, we will swing to their support and constitute "an obstacle to democratic backsliding" [@Claassen2020b, p.
+51].
 Both of these assertions may well be true, but the evidence we have, properly assessed, does not provide support for them.
@@
 # Method
+
 We proceed in three steps.
-In our first step, we reproduce the original analyses of Claassen [-@Claassen2020a; -@Claassen2020b], which included only the point estimates of the latent variable of democratic support and so exclude its measurement uncertainty.
-In the second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.
-As our third step, we collect even more survey data---increasing these source data observations by one-fourth---and re-estimate democratic support using the superior DCPO measurement model, then conduct the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.
+First, we reproduce the original analyses of Claassen [-@Claassen2020a; -@Claassen2020b], which included only the point estimates of the latent variable of democratic support and so exclude its measurement uncertainty.
+Second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.
+As the third step, we collect even more survey data---increasing these source data observations by one-fourth---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.
 
 ## Incorporating Uncertainty
-Although measurement uncertainty has yet not attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can bias coefficient estimates and standard errors.
-Especially when measurement error is correlated with the dependent variable, the resulting bias could either attentuate or exaggerate the magnitude of the estimated effects [see, e.g., @Blackwell2017, p.360; @caughey_policy_2018, p.254].
-In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey_policy_2018, 254].
-
-Therefore, after we replicate the original analyses that used only the point estimates of democratic support, we incorporate the full distribution of the latent variable estimates.
+
+Although measurement uncertainty has yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can bias coefficient estimates and standard errors.
+Especially when measurement error is correlated with the outcome variable, the resulting bias could either attenuate or exaggerate the magnitude of the estimated effects [see, e.g., @Blackwell2017, p.360; @caughey_policy_2018, p.254].
+In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, p.
+18; @Gandhi2020, p.
+1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, pp.
+791-792; @caughey_policy_2018, p.
+254].
+
+Following this line, after replicating the original analyses with point estimates, we incorporate the full distribution of the latent and control variables to the estimation.
+We follows the 
 To do this, we replicate the latent variable estimation from the original survey data, duplicate each article's analysis dataset 1,000 times, and assign to each a different random draw from the posterior distribution of public democratic support.
-Then we perform each analysis repeatedly on its respective collection of datasets, and combine the results following the rules set out in @Rubin1987 [see, e.g., @Schnakenberg2014; @Crabtree2015].
-Our approach of incorporating uncertainty is analogous to @Blackwell2017a's multiple overimputation, that is, creating multiple data set from the posterior distribution of the true latent value, applying analysis model for each dataset, and then averaging results by correcting both within and between imputation variance.
-We also employ one alternative technique known as “method of composition” [@treier_democracy_2008, 215) as robuestness check [see Supplementary Appendix xx].
+Then we perform each analysis repeatedly on its respective collection of the datasets, and combine the results following the rules set out in @Rubin1987 [see, e.g., @Schnakenberg2014; @Crabtree2015].
+This uncertainty-incorporation process is analogous to @Blackwell2017a's multiple overimputation (MO).
+We also employ one alternative technique known as “method of composition” [@treier_democracy_2008, p. 215) as a robustness check [see the Online Supplementary Material \@ref(moc)].
 
@@
 
-## Better Estimates of Democratic Support and More Data
-As a further test of the classic arguments on democracy and public support, we apply the superior DCPO model to a bigger data set.
-The DCPO model has several advantages over the @Claassen2019 model used in Claassen [-@Claassen2020a; -@Claassen2020b].
-First, while the @Claassen2019 model dichotomizes responses and so discards some information provided by 50 of the 52 survey items employed in Claassen [-@Claassen2020a; -@Claassen2020b], the DCPO model makes use of all of the information available from these ordinal items [@Solt2020a, 5].
-Second, as the DCPO model includes both parameters for the dispersion of each survey item and for the standard deviation of aggregate public opinion in each country-year, it is a complete population-level item-response model and so, unlike the @Claassen2019 model, is explicitly derived from an individual-level model of survey responses [@Solt2020a, 3-4; see also @McGann2014].
-Third, to produce more sensible estimates of uncertainty for observations at the extremes of the scale [see @Linzer2015, 229], the DCPO model places bounds on its estimates of public opinion [@Solt2020a, 8].
-Further commending the DCPO model to us---and demonstrating that its advantages make a difference---the validation tests in @Solt2020a [, 10-12] reveal that it fits survey data on democratic support better than the @Claassen2019 model does.
-
-In addition to applying the superior DCPO model, we also assembled as much available data on democratic support as possible.
+In addition to incorporating uncertainty, we also assembled as much available data on democratic support as possible. 
 We employed `r dcpo_input_ncyi` national opinions on democracy from `r dcpo_input_surv` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncy` opinions and `r supdem_surv` national surveys used in Claassen [-@Claassen2020a; -@Claassen2020b].^[These figures represent the survey data actually used in estimating public support for democracy; as in Claassen [-@Claassen2020a; -@Claassen2020b], countries for which two separate years of survey data were not available were excluded.]
-We used the `DCPO` package for R [@Solt2020b] to estimate the DCPO model on this expanded dataset.
+
+A noteworthy point is that MO method enables not only uncertainty incorporation of key explanatory and outcome variables but also control variables. 
+We fully utilize this strength to include the uncertainty of the measurement of
+.......
 
@@
 
-Figure&nbsp;\ref{fig:visualizeAJPS} presents the reanalyses of the hypothesis that public support influences the level of democracy, with democratic support pooled for all countries (Claassen's 2020$a$, 128, Model 1) in the left panel and democratic support separated by regime type (Model 2) on the right.
-The uppermost set of results replicate @Claassen2020a, including by excluding measurement uncertainty, and reproduce that article's findings.
-The middle results introduce a single change: the uncertainty in the measurement of public support is taken into account.
-In both models, the positive coefficients for democratic support are no longer statistically significant.
-The bottom results also incorporate uncertainty but additionally replace the @Claassen2019 estimates of support with those based on DCPO and the expanded dataset; this change works to increase the number of observations analyzed as well.
-Although the confidence intervals shrink considerably, the coefficient estimates move much closer to zero; the hypothesis remains unsupported.
+Figure \@ref(fig:plot-mainAJPS) presents the reanalyses of the hypothesis that public support influences the level of democracy, with democratic support pooled for all countries [@Claassen2020a, Model 1] in the left panel and separated by regime type (Model 2) on the right.
+The uppermost set of results replicate @Claassen2020a without uncertainty.
+The middle results introduce the uncertainty in the measurement of public support into the model.
+The lowermost set presents the results estimated with the expanded data.
+
+In comparison to the original result, the positive coefficients for democratic support in both model accounting for the uncertainty are no longer statistically significant.
+This result is robust when using separated regime types in the explanatory variable. 
+The estimation based on an alternative method of uncertainty incorporation, model of composition, yields identical conclusions [XXXX].
+
+At the same time, the results also shows that ignoring uncertainty may lead to misestimation of the point effect as well. 
+In the case here, the point estimates of democracy support are notably larger than the original estimate for both model settings. 
+With MO, we draw variable values from their distributions and estimate the coefficient first before combining through Rubin's rule.
+The deviation of the result from the original indicates the coefficient (point) estimates were not that consistent.
+In other words, the estimates based on the mean values of variables cannot fully reflect their characteristics and relations at all.
+Only when the uncertainty is accounted, their effect can be more properly estimated.
 
@@
 
+The importance of accounting for the measurement uncertainty appear more evident when the relevant variable plays as the outcome variable. 
+In Figure \@ref(fig:plot-mainAPSR), we examine the thermostatic model of democratic support per @Claassen2020b [p. 47, Models 1.1 and 1.2]. 
+The negative coefficient estimates of change in liberal democracy in the top set of results, which do not take uncertainty into account, imply that democratic mood decreases as democracy increases and vice versa.
+However, the middle and bottom results demonstrate that this thermostatic effect, too, does not hold after the measurement uncertainty is accounted for. 
+And again, we observe the point estimates slides to the zero line.
+
+[A discussion about the support t-1]
+
 ```{r pointAPSR, eval=TRUE}
@@
 
-The importance of accounting for the measurement uncertainty appear more evident when the relevant variable plays as the dependent variable. 
-In Figure&nbsp;\ref{fig:visualizedAPSR}, we examine the thermostatic model of democratic support per @Claassen2020b [, 47, Models 1.1 and 1.2]. 
-The negative coefficient estimates of change in liberal democracy in the top set of results, which do not take uncertainty into account, imply that democratic mood decreases as democracy increases and vice versa.
-However, the middle results demonstrate that this thermostatic effect, too, does not  hold after the measurement uncertainty is accounted for. 
-And again, the bottom results reveal that the additional data and superior DCPO measurement model of our extension do not provide support for the original conclusion.
-
 ```{r coefName-APSR, eval=TRUE}
@@
     `plm::lag(theta_trim, 1:2)2` = "Support[t-2]",
+    `diff(Libdem_z, lag = 1)` = "Delta~Liberal~democracy",
+    `diff(Vdem_libdem_z, lag = 1)` = "Delta~Liberal~democracy",
+    `plm::lag(Libdem_z, 1)` = "Liberal~democracy[t-1]",
+    `plm::lag(Vdem_libdem_z, 1)` = "Liberal~democracy[t-1]",
     `diff(Liberal_z, lag = 1)` = "Delta~Support(demo~only)",
@@
     `plm::lag(Vdem_polyarchy_z, 1)` = "Support[t-1](auto~only)",
-    `diff(Libdem_z, lag = 1)` = "Delta~Liberal~democracy",
-    `diff(Vdem_libdem_z, lag = 1)` = "Delta~Liberal~democracy",
-    `plm::lag(Libdem_z, 1)` = "Liberal~democracy[t-1]",
-    `plm::lag(Vdem_libdem_z, 1)` = "Liberal~democracy[t-1]",
     `diff(lnGDP_imp, lag = 1)` = "Delta~Log~GDP~per~capita",
@@
 # Discussion
-In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support has a positive effect on democracy and democracy a negative effect on support are not empirically supported once measurement uncertainty is taken into account, even when a superior estimate of public support and more data are used.
+
+In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support has a positive effect on democracy and democracy a negative effect on support are not empirically supported once measurement uncertainty is taken into account, even when more data are used.
 
@@
 # Conclusion
+
 In this letter, we reexamined the findings from Claassen [-@Claassen2020a; -@Claassen2020b], two articles that maintain that public support helps the survival of democracy and democratic development has a thermostatic effect on public support.
 We demonstrated the importance of incorporating measurement uncertainty in analyzing the relationship between public support and democracy.
-Taking uncertainty into account rendered both articles' conclusions without empirical support, even when we employed the more sophisticated DCPO measurement model and additional data.
+Taking uncertainty into account rendered both articles' conclusions without empirical support, even when we added considerable more data.
 
@@
 
-# Replication with Alternative Methods Accounting for Uncertainty
+# Replication with Alternative Methods Accounting for Uncertainty {#moc}
+
+To ensure the robustness of our analysis, we apply another method to account for uncertainty.
+In the
 

### 2021-07-15 paper/dcpo_demsupport.Rmd
writing out the moc vs mo; fixed #23; fixed #22; fixed #17; fixed #15

@@
 This uncertainty-incorporation process is analogous to @Blackwell2017a's multiple overimputation (MO).
-We also employ one alternative technique known as “method of composition” [@treier_democracy_2008, p. 215) as a robustness check [see the Online Supplementary Material \@ref(moc)].
+We also employ one alternative technique known as “method of composition” [@treier_democracy_2008, p. 215] as a robustness check [see the Online Supplementary Material \@ref(moc)].
 
@@
 We fully utilize this strength to include the uncertainty of the measurement of
-.......
+democracy and corruption. 
+[XXXX Cassandra, please fill in a tiny little bit of details here]
 
@@
     `plm::lag(lnGDP_imp, 1)` = "Log~GDP[t-1]",
-    `plm::lag(lg_imp_mdpgdp, 1)` = "Log~GDP[t-1]"
+    `plm::lag(lg_imp_mdpgdp, 1)` = "Log~GDP[t-1]",
+    `diff(Corrup_TI_z, lag = 1)`= "Delta~Corruption",
+    `plm::lag(Corrup_TI_z, 1)` = "Log~Corruption[t-1]",
+    `Corrup_TI_z` = "Log~Corruption[t-1]"
 )
@@
 To ensure the robustness of our analysis, we apply another method to account for uncertainty.
-In the
+The method we employ is "method of composition" (MOC).
+It is a common method for Monte Carlo integration, but can also be applied for addressing uncertainty [@treier_democracy_2008].
+To compare these two methods, let's denote `y` as a vector of the outcome variable [either institutional democracy in @Claassen2020a or the changes in mass support of democracy in @Claassen2020b]. 
+Let $x$ (variables without subscript are used to denote vectors of observations, viz., $x$ = ($x_1$,......, $x_i$)) be a vector of the explanatory variable (e.g., mass support or institutional democracy) and $\theta$ be the parameter of interest.
+In multiple overimputation (MO, the method used in the main article), the explanatory variable with measurement errors is regarded as missing data $x^{mis}$ with an observed proxy $w$ under the assumption of "Missing at Random" and "Ignorable Measurement Mechanism Assignment" [@Blackwell2017].
+The explanatory variables without error are denoted $x^{obs}$.
+The parameter likelihood is then
+
+\begin{equation}
+\mathcal{L}(\theta|y, x^{obs}) \propto \int\limit_{\chi} p(x|y, \theta)p(y|\theta)dx^{mis}.
+\end{equation}
+
+Given $x$ is unobservable, one can estimate it through the proxy $w$ together with the measurement error $a$:
+
+\begin{equation}
+E(w | x) = x + a.
+\end{equation}
+
+After gaining the parameter density based on the above functions, one can apply Rubin's Rule to combine the point estimates and standard errors into single values yet accounting for both within and between imputation variances [@Rubin1987].
+
+MOC addresses the same issue from a slightly different angle.
+The method assumes that the explanatory and outcome variables are samples from their estimate functions, and their paired sample follows a joint density [@Tanner1993, p.31].
+From the joint density, one can decomposite the likelihood of the explanatory variable and its parameter to a product of their own probabilities.
+When x is measured with errors $w$, the probability becomes conditional:
+
+\begin{equation}
+\mathcal{L}(\theta, x|y, w) = p(\theta|x,y)p(x|w).
+\end{equation}
+
+Based on this decomposition, one can estimate the marginal density for &\theta&:
+
+\begin{equation}
+\mathcal{L}(\theta|y, x) \propto \int\limit_{\chi} p(\theta|y, x)p(x|w)dx.
+\end{equation}
+
+Again, the gained parameter density can be combined into single values.
+A common way to do so is using the mean of $theta$ as the point estimate, and the variance from the density as the standard error.
 
@@
 ```
+
+Figure \@ref(fig:plot-mocAJPS) and \@ref(fig:plot-mocAPSR) presents the results of using MOC to engage measurement error. 
+The results are consistent as we gained from the MO method (cf. Figure \@ref(fig:plot-mainAJPS) and \@ref(fig:plot-mainAPSR)).

### 2021-07-15 paper/dcpo_demsupport.Rmd
elaborate more on Rubin's rule, uncertainty on dv and control variables,  and the process of incorporating uncertainty. + correct "observation" usage.

@@
 In this letter, we reexamine the classic arguments about support for democracy and democratic change tested in these two pieces while correcting this oversight.
-In addition to incorporating the measurement uncertainty, we also sought to reduce it by expanding the estimated data to including 144 countries for up to 33 years between 1988 and 2020 (based on 26% more questions and 33% more survey sources).
+In addition to incorporating the measurement uncertainty, we also sought to reduce it by expanding survey data to including 144 countries for up to 33 years between 1988 and 2020 (based on 26% more questions and 33% more survey sources).
 Our analyses reveal that the significant relationships between public support and democratic change disappear once measurement uncertainty is taken into account, both in replications with the studies' original data and with expanded data.
@@
 Second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.
-As the third step, we collect even more survey data---increasing these source data observations by one-fourth---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.
+As the third step, we collect even more survey data---increasing these source data by one-fourth---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.
 
@@
 
-Following this line, after replicating the original analyses with point estimates, we incorporate the full distribution of the latent and control variables to the estimation.
-We follows the 
-To do this, we replicate the latent variable estimation from the original survey data, duplicate each article's analysis dataset 1,000 times, and assign to each a different random draw from the posterior distribution of public democratic support.
-Then we perform each analysis repeatedly on its respective collection of the datasets, and combine the results following the rules set out in @Rubin1987 [see, e.g., @Schnakenberg2014; @Crabtree2015].
-This uncertainty-incorporation process is analogous to @Blackwell2017a's multiple overimputation (MO).
+Following this line, after replicating the original analyses with point estimates, we take the distribution of the latent variable, the dependent variable, and control variables to account for the uncertainty from the measurement model as well as dependent and control variables.
+To do this, we take 900 draws from the distribution of public democratic support and corruption index, duplicate each article's analysis dataset of variables without “measurement error” 900 times, and assign them to each a different random draw from the posterior distribution of democracy indices, electoral, polyarchy and liberal index, which are provided by V-DEM project.
+We estimate each analysis model repeatedly on its respective collection of the datasets, and then make inferences from the distribution of parameter estimates by accounting for both within model standard error and between model variance.
+This combine rule was set out in @Rubin1987 and employed in research of measurement errors [see, e.g., @Schnakenberg2014; @Crabtree2015].
+@Blackwell2017a's multiple overimputation (MO) uses the same logic to correct sampling variance.
 We also employ one alternative technique known as “method of composition” [@treier_democracy_2008, p. 215] as a robustness check [see the Online Supplementary Material \@ref(moc)].
@@
     # Using expressions of underscore and greek letters
-    scale_color_gb(palette = "digitMixed") +
+    # scale_color_gb(palette = "digitMixed") +
     facet_wrap(~ type)
@@
     # Using expressions of underscore and greek letters
-    scale_color_gb(palette = "digitMixed") +
+    # scale_color_gb(palette = "digitMixed") +
     facet_wrap( ~ type)

### 2021-07-15 paper/dcpo_demsupport.Rmd
added description for controling uncertainty on DV and Corruption.

@@
 Following this line, after replicating the original analyses with point estimates, we take the distribution of the latent variable, the dependent variable, and control variables to account for the uncertainty from the measurement model as well as dependent and control variables.
-To do this, we take 900 draws from the distribution of public democratic support and corruption index, duplicate each article's analysis dataset of variables without “measurement error” 900 times, and assign them to each a different random draw from the posterior distribution of democracy indices, electoral, polyarchy and liberal index, which are provided by V-DEM project.
+To do this, we take 900 draws from the distribution of public democratic support and corruption index, duplicate each article's analysis dataset of variables without “measurement error” 900 times, and assign them to each a different random draw from the posterior distribution of democracy indices.
 We estimate each analysis model repeatedly on its respective collection of the datasets, and then make inferences from the distribution of parameter estimates by accounting for both within model standard error and between model variance.
@@
 
-A noteworthy point is that MO method enables not only uncertainty incorporation of key explanatory and outcome variables but also control variables. 
-We fully utilize this strength to include the uncertainty of the measurement of
-democracy and corruption. 
-[XXXX Cassandra, please fill in a tiny little bit of details here]
+A noteworthy point is that in addition to account for uncertainty in latent variable estimates, we also include the measurement uncertainty in democracy indices and corruption index. 
+We extracted the posterior distributions of democratic indices, including electoral, polyarchy, and liberal index, which are provided by [@coppedge2018]. 
+We drew 900 samples from the distribution of the Corruption Perception Index.^[Since Corruption Perception Index does not provide standard error before 2011, we imputed the missing standard error using the  multiplication of a country's corruption index and the ratio of its available maximum standard error to its corresponding index.]
 

### 2021-07-16 paper/dcpo_demsupport.Rmd
add result description for MOC; change the title for APSR result figure.

@@
 @Blackwell2017a's multiple overimputation (MO) uses the same logic to correct sampling variance.
-We also employ one alternative technique known as “method of composition” [@treier_democracy_2008, p. 215] as a robustness check [see the Online Supplementary Material \@ref(moc)].
+We also employ one alternative technique known as “method of composition” (MOC)  [@treier_democracy_2008, p. 215] as a robustness check [see the Online Supplementary Material \@ref(moc)].
 
@@
 This result is robust when using separated regime types in the explanatory variable. 
-The estimation based on an alternative method of uncertainty incorporation, model of composition, yields identical conclusions [XXXX].
+The estimation based on MOC yields mixed results.
+In the OLS models, the public support from originial data with uncertainty is significant for both pooled data and split data for democracies but the support estimated from the expanded data is not.
+In GMM models which should yield more accurate results than OLS models, the coeffient of public support is not significant for pooled data but significant for split sample data with original data.
 
@@
 In the case here, the point estimates of democracy support are notably larger than the original estimate for both model settings. 
-With MO, we draw variable values from their distributions and estimate the coefficient first before combining through Rubin's rule.
-The deviation of the result from the original indicates the coefficient (point) estimates were not that consistent.
+We draw variable values from their distributions and estimate the coefficient first before combining through Rubin's rule.
+The deviation of the result from the original one indicates the coefficient (point) estimates were not that consistent.
 In other words, the estimates based on the mean values of variables cannot fully reflect their characteristics and relations at all.
@@
 result_pureAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
-  result <- map(pure_cls_apsr, function(aData){ # applying to the 1000 datasets
+  result <- map(pure_cls_apsr, function(aData){ # applying to the 900 datasets
     eval(parse(text = aMod))
@@
 
-```{r plot-mainAPSR, fig.cap= "The Effect of Democracy on Public Support", fig.width=7, fig.height=10, eval = TRUE}
+```{r plot-mainAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", fig.width=7, fig.height=10, eval = TRUE}
 result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
@@
     theme_minimal() +
-    ggtitle("DV: Public Support for Democracy") +
+    ggtitle("DV: The Change of Public Support for Democracy") +
     xlab("Coefficient Estimate") +
@@
 
-```{r plot-mocAPSR, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}
+```{r plot-mocAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", eval = TRUE, fig.width=7, fig.height=10}
 
@@
   labs(
-    title = "DV: Public Support for Democracy",
+    title = "DV: The Change of Public Support for Democracy",
     subtitle = "Regime Compacted"

### 2021-07-16 paper/memo/memo.Rmd
cls uncertain
two reponses in memo.

@@
 
+# Uncertainty in DV and Control Variables
+
+## Reviewer #1 
+[Issue 16](https://github.com/fsolt/dcpo_dem_mood/issues/16) First, I believe that the measurement error of variables included in the model should be factored in.
+Many of these variables (democracy, corruption, economic output) cannot be directly observed and are therefore prone to measurement error.
+If one believes that (a) estimating the effect of one variable on another requires incorporating measurement error; and (b) control variable Z needs to be included because it likely has an effect on both X and Y, then to accurately adjust for the effects of Z requires that X, Y and Z all have included measurement error.
+
+## Reviewer #2
+[Issue 16](https://github.com/fsolt/dcpo_dem_mood/issues/16) Despite the MS's assertion of the "absolute necessity" of accounting for measurement error, the MS does not do so for any of the other variables in the analysis.
+Given that Treier and Jackman's analysis focused on uncertainty in measures of democracy, the most obvious omission is the V-DEM democracy measure itself (which, according to the V-DEM documentation, does appear to have associated uncertainty estimates).
+
+## Response 
+A major concern raised by Reviewers 1 & 2 was regard to the omission of measurement errors of DV and control variables in our analysis.
+It is a good point.
+Many variables in the analysis cannot be observed directly and inherently contaminated by measurement errors.
+To address this concern, since Claassen used V-Dem Version 8 in his analyses, we incorporated measurement error for V-Dem democracy index, electoral index, polyarchy index, and liberal index, by using the posterior distribution of Version 8 provided by V-Dem.
+Regarding the data used to replicate Claassen' analyses, we simulated 900 data set for democracy index from V-Dem Version 10 which did not provide available posterior distribution yet but standard error.
+To account for measurement error in Corruption Perceptions Index, we simulated 900 draws from a distribution with the point estimate and standard error which provided by CPI for the year from 2012 to 2018.
+For the year before 2012, we estimated standard error by using the multiplication between country's maximum relative error (standard error/cpi index) and CPI index.
+We rerun the models following the same steps in our previous analysis but incorporating uncertainty in democracy index, democratic support, and corruption perception index.
+The relationship between public support and democracy development disappears when uncertainty is accounted for in models either using Claassen's original data or expanded data with 25% more country-year data.
+The updated results are presented in Figure XXX at Page xx.
+
+# Alternative Method for Incorporating uncertainty
+
 ## Reviewer #1
@@
 This is unfortunate because I have several concerns with the method as used and the results which are produced, as described below.
-
-[Issue 16](https://github.com/fsolt/dcpo_dem_mood/issues/16) First, I believe that the measurement error of variables included in the model should be factored in.
-Many of these variables (democracy, corruption, economic output) cannot be directly observed and are therefore prone to measurement error.
-If one believes that (a) estimating the effect of one variable on another requires incorporating measurement error; and (b) control variable Z needs to be included because it likely has an effect on both X and Y, then to accurately adjust for the effects of Z requires that X, Y and Z all have included measurement error.
-
-[Issue 24](https://github.com/fsolt/dcpo_dem_mood/issues/23) Second, the results in Figure 2, based on models using democratic support as a dependent variable, are puzzling.
-They appear to show that democratic support is entirely disconnected from such prominent features of the political environment as the level of democracy and economic development.
-Not only are these effects insignificant, but their point estimates are almost exactly zero in magnitude.
-The effects of lagged democratic support are also zero, which is even more implausible because it suggests that democratic support in one year is entirely disconnected from its levels in previous years.
-In other words, Denmark is as likely to have a low value next year as China is likely to have a high value.
-This stands in contrast with much of existing research on democratic support and political culture.
-
 [Issue 23](https://github.com/fsolt/dcpo_dem_mood/issues/23) Alternatively, the authors might use a different method for factoring in the error due to measurement: structural equation models, which, in essence, combine a measurement model and the subsequent regression model in one step.
@@
 
-[Issue 22](https://github.com/fsolt/dcpo_dem_mood/issues/22) I have two additional concerns with the paper.
-First, the authors have not replicated all of Claassen's main results.
-Claassen 2020a argues that within-country analyses are desirable and uses generalized method of moments (GMM) estimators to obtain these.
-Claassen (2020b) uses first difference models; he also focuses on the separate effects of the electoral and liberal components of democracy.
-I suggest that the authors replicate all the main results from Claassen (2020a; 2020b), rather than an ad hoc subset of these.
-
-[Issue 18](https://github.com/fsolt/dcpo_dem_mood/issues/18) Second, in addition to the results obtained from the latent variable model developed and used by Claassen, the authors present the results obtained from an entirely different latent variable model.
-Although intriguing, no evidence at all is presented to support the claim (repeated throughout) that this method is "superior" to Claassen's (reference is made to an unpublished working paper).
-Indeed, it would appear from the short summary of this model that it adds additional parameters to Claassen's model.
-Yet more complicated models may overfit the data and are not necessarily more accurate.
-I propose that evidence supporting the superiority of this method be supplied, or alternatively, the authors just focus on replicating Claassen's models.
-
 ## Reviewer #2
@@
 How does it perform when measurement error is strongly correlated across variables, as is likely to be the case in the models with lagged DVs?
+[Issue 23](https://github.com/fsolt/dcpo_dem_mood/issues/23) It would be useful to show that the critique still holds with an alternative measurement-error approach, such as Treier and Jackman's (2008) method of composition.
+## Reviewer #4
+[Issue 17](https://github.com/fsolt/dcpo_dem_mood/issues/17) We need more information on (1) how uncertainty is integrated into the models of Claassen, and (2) the DCPO models.
 
-[Issue 23](https://github.com/fsolt/dcpo_dem_mood/issues/23) It would be useful to show that the critique still holds with an alternative measurement-error approach, such as Treier and Jackman's (2008) method of composition.
+# The Change of Democratic Support and Lagged Support
 
-[Issue 16](https://github.com/fsolt/dcpo_dem_mood/issues/16) Despite the MS's assertion of the "absolute necessity" of accounting for measurement error, the MS does not do so for any of the other variables in the analysis.
-Given that Treier and Jackman's analysis focused on uncertainty in measures of democracy, the most obvious omission is the V-DEM democracy measure itself (which, according to the V-DEM documentation, does appear to have associated uncertainty estimates).
+## Reviewer #1
+[Issue 24](https://github.com/fsolt/dcpo_dem_mood/issues/23) Second, the results in Figure 2, based on models using democratic support as a dependent variable, are puzzling.
+They appear to show that democratic support is entirely disconnected from such prominent features of the political environment as the level of democracy and economic development.
+Not only are these effects insignificant, but their point estimates are almost exactly zero in magnitude.
+The effects of lagged democratic support are also zero, which is even more implausible because it suggests that democratic support in one year is entirely disconnected from its levels in previous years.
+In other words, Denmark is as likely to have a low value next year as China is likely to have a high value.
+This stands in contrast with much of existing research on democratic support and political culture.
 
+## Reviewer #2
 [Issue 24](https://github.com/fsolt/dcpo_dem_mood/issues/24) Also, I could not help but be struck by the extreme attenuation of the coefficient estimates in Figure 2, which almost suggest that the variables were generated from independent distributions.
@@
 
+## Reviewer #4
+[Issue 15](https://github.com/fsolt/dcpo_dem_mood/issues/15) Second, I was a bit confused by Figures 1 and 2.
+My understanding is that accounting for uncertainty should only affect the standard errors, but in the figures it also affects the point estimates.
+This is the case even in the models 'Claassen W/Uncertainty.'
+
+# Test Full Models 
+## Reviewer #1
+[Issue 22](https://github.com/fsolt/dcpo_dem_mood/issues/22) I have two additional concerns with the paper.
+First, the authors have not replicated all of Claassen's main results.
+Claassen 2020a argues that within-country analyses are desirable and uses generalized method of moments (GMM) estimators to obtain these.
+Claassen (2020b) uses first difference models; he also focuses on the separate effects of the electoral and liberal components of democracy.
+I suggest that the authors replicate all the main results from Claassen (2020a; 2020b), rather than an ad hoc subset of these.
+
+## Response
+Regarding Reviewer 1's request on replicating all specification in the original two studies, we added alternate specifications on the relationship between support and democracy, including GMM models, First Different Models, and sample split.
+Results do not change in all these models, presented in Page xxx, Figure xxx and xxx in SI. 
+As the editor suggested that this letter should focus on the core point, that is, the relationship between public support and democracy, we do not replicate specifications on other relationship.
+
+# Justification of DCPO 
+## Reviewer #1
+[Issue 18](https://github.com/fsolt/dcpo_dem_mood/issues/18) Second, in addition to the results obtained from the latent variable model developed and used by Claassen, the authors present the results obtained from an entirely different latent variable model.
+Although intriguing, no evidence at all is presented to support the claim (repeated throughout) that this method is "superior" to Claassen's (reference is made to an unpublished working paper).
+Indeed, it would appear from the short summary of this model that it adds additional parameters to Claassen's model.
+Yet more complicated models may overfit the data and are not necessarily more accurate.
+I propose that evidence supporting the superiority of this method be supplied, or alternatively, the authors just focus on replicating Claassen's models.
+## Reviewer #2
 [Issue 20](https://github.com/fsolt/dcpo_dem_mood/issues/20) Finally, I am concerned about the over-time smoothing induced by the random-walk prior in measurement model.
@@
 There is no magic fix for this problem, but readers should still be given more information on how much "work" the prior is doing—what proportion of country-years are missing data, how informative is the prior relative to the likelihood, and so on.
+## Reviewer #4
+[Issue 18](https://github.com/fsolt/dcpo_dem_mood/issues/18) Third, the author should provide more information on the differences between the models employed by Claassen and those that she/he employs (perhaps in an appendix).
 
+Thanks to editor's suggesions, we do agree that we should present and assess the effect of intermediate modification in an incremental way.
+To do this, in the revised manuscript, we replicated Claassen's measure for public democratic support by applying his measurement Model5 to  his original data file and used the posterior distribution of the public support estimates to incorporated uncertainty.
+Then, we added more survey data to improve the quality of source data and applied Model5 to this expanded data set, still keeping the full posterior distribution of estimates. 
+In this way, we isolate the effects of measurement uncertainty and more data. 
+In the APSR analyses, it is uncertainty that accounts for the disappearing significance of public support.
+
+# Substantive Discussion
+## Reviewer #4
+
+[Issue 19](https://github.com/fsolt/dcpo_dem_mood/issues/19) First, I found the 'Discussion' section somewhat underwhelming.
+The discussion is mainly about data issues that could explain the lack of a relationship, not the substantive question.
+If that is the case, the letter makes a negligible contribution because it only finds that the findings of two specific studies are not robust (not that there is no relationship between public support for democracy and regime survival).
+I would like the author to engage a bit more in substantive debates.
+
+# Compliement
 ## Reviewer #3
@@
 Although I am quite confident that policy preferences and policy change react thermostatically to each other in yearly rhythms, I find it hard to believe that such fundamental things as regime preferences and regime qualities underly such short-term cycles.
-Regime preferences and regime qualities are more enduring, inert and their changes are too glacial for a thermostatic model of short-term cycles to plausibly capture the underlying dynamic in the co-evolution of public opinion and regime qualities.
-Since Claassen uses V-Dem data to measure democratic regime qualities, which are entirely expert judgements, his models demonstrate at best that expert and lay assessments of democracy react thermostatically to each other.
+Regime preferences and regime qualities are more enduring, inert and their changes are too glacial for a thermostatic model of short-term cycles to *plausibly capture the underlying dynamic in the co-evolution of public opinion and regime qualities.
+Since Claassen uses V-Dem data to measure democratic regime qualities, which are entirely expert judgements, his models demonstrate at best that expert and lay assessments of democracy react thermostatically to each other.*
 
@@
 "A Tale of Culture-bound Regime Evolution: The Centennial Democratic Trend and Its Recent Reversal." Democratization 25: 1-23 (DOI: 10.1080/13510347.2018.1542430).
-
-## Reviewer #4
-
-[Issue 19](https://github.com/fsolt/dcpo_dem_mood/issues/19) First, I found the 'Discussion' section somewhat underwhelming.
-The discussion is mainly about data issues that could explain the lack of a relationship, not the substantive question.
-If that is the case, the letter makes a negligible contribution because it only finds that the findings of two specific studies are not robust (not that there is no relationship between public support for democracy and regime survival).
-I would like the author to engage a bit more in substantive debates.
-
-[Issue 15](https://github.com/fsolt/dcpo_dem_mood/issues/15) Second, I was a bit confused by Figures 1 and 2.
-My understanding is that accounting for uncertainty should only affect the standard errors, but in the figures it also affects the point estimates.
-This is the case even in the models 'Claassen W/Uncertainty.'
-
-[Issue 18](https://github.com/fsolt/dcpo_dem_mood/issues/18) Third, the author should provide more information on the differences between the models employed by Claassen and those that she/he employs (perhaps in an appendix).
-
-[Issue 17](https://github.com/fsolt/dcpo_dem_mood/issues/17) We need more information on (1) how uncertainty is integrated into the models of Claassen, and (2) the DCPO models.
 

### 2021-07-17 paper/dcpo_demsupport.Rmd
plotting with dotwhisker 0.7.0; fixed #27
Try to explain the implications from the significant results of MOC Ajps results.  @sammo3182 check whether make any sense or how to make it more sense.

@@
 A noteworthy point is that in addition to account for uncertainty in latent variable estimates, we also include the measurement uncertainty in democracy indices and corruption index. 
-We extracted the posterior distributions of democratic indices, including electoral, polyarchy, and liberal index, which are provided by [@coppedge2018]. 
+We extracted the posterior distributions of democratic indices, including Liberal Democracy,  polyarchy, and electoral democracy index, which are provided by [@coppedge2018]. 
 We drew 900 samples from the distribution of the Corruption Perception Index.^[Since Corruption Perception Index does not provide standard error before 2011, we imputed the missing standard error using the  multiplication of a country's corruption index and the ratio of its available maximum standard error to its corresponding index.]
@@
 The estimation based on MOC yields mixed results.
-In the OLS models, the public support from originial data with uncertainty is significant for both pooled data and split data for democracies but the support estimated from the expanded data is not.
-In GMM models which should yield more accurate results than OLS models, the coeffient of public support is not significant for pooled data but significant for split sample data with original data.
+In pooled OLS models, the public support estimated from the originial data with uncertainty is significant for the whole data and split databut the support estimated from the expanded data is not.
+In system GMM models which are more appropriate in this case than pooled OLS models, public support estimated from the original data reached the threshold of significance within democratic regimes. 
+The estimated support with the expanded data is not significant in GMM models.
+
+Using the same models and the measurement, the support estimate from a more qualified data yields insignificant results. 
+This undermines the reliability of significant results from the estimate using the original data.^[In fact, when we further improve the estimate and reduce the uncertainty by applying a more superior measurement model, the relationship between public support and democratic survival disappears.]
 
@@
 type_model <-
-  c("Claassen 2020", "Claassen Uncertainty", "DCPO Uncertainty")
+  c("Original", "Uncertainty", "Uncertainty+Expanded Data")
 
@@
 This points to the absolute necessity of incorporating measurement uncertainty into analyses that include latent variables.
+Measurement issues have never had a prominent place in comparative political studies because they need more time to estimate models, but they ground the quality of data and the basis of analysis [@stegmueller2011, 484].
 As the use of latent variables grows more common in political science, both researchers and readers should be aware that these variables' concomitant measurement uncertainty cannot be neglected.
@@
 The explanatory variables without error are denoted $x^{obs}$.
+*Personally, I think we should be careful to use MO since our approach is not MO. I will go back here later.* 
 The parameter likelihood is then

### 2021-07-20 paper/dcpo_demsupport.Rmd
label and output corrected

--- 2021-07-16 paper/dcpo_demsupport.Rmd
@@
     `plm::lag(Vdem_libdem_z, 1)` = "Liberal~democracy[t-1]",
-    `diff(Liberal_z, lag = 1)` = "Delta~Support(demo~only)",
-    `diff(Vdem_liberal_z, lag = 1)` = "Delta~Support(demo~only)",
-    `plm::lag(Liberal_z, 1)` = "Support[t-1](demo~only)",
-    `plm::lag(Vdem_liberal_z, 1)` = "Support[t-1](demo~only)",
-    `diff(Polyarchy_z, lag = 1)` = "Delta~Support(auto~only)",
-    `diff(Vdem_polyarchy_z, lag = 1)` = "Delta~Support(auto~only)",
-    `plm::lag(Polyarchy_z, 1)` = "Support[t-1](auto~only)",
-    `plm::lag(Vdem_polyarchy_z, 1)` = "Support[t-1](auto~only)",
+    `diff(Liberal_z, lag = 1)` = "Delta~Support(electoral)",
+    `diff(Vdem_liberal_z, lag = 1)` = "Delta~Support(electoral)",
+    `plm::lag(Liberal_z, 1)` = "Support[t-1](electoral)",
+    `plm::lag(Vdem_liberal_z, 1)` = "Support[t-1](electoral)",
+    `diff(Polyarchy_z, lag = 1)` = "Delta~Support(minoritarian)",
+    `diff(Vdem_polyarchy_z, lag = 1)` = "Delta~Support(minoritarian)",
+    `plm::lag(Polyarchy_z, 1)` = "Support[t-1](minoritarian)",
+    `plm::lag(Vdem_polyarchy_z, 1)` = "Support[t-1](minoritarian)",
     `diff(lnGDP_imp, lag = 1)` = "Delta~Log~GDP~per~capita",
@@
     `plm::lag(lnGDP_imp, 1)` = "Log~GDP[t-1]",
-    `plm::lag(lg_imp_mdpgdp, 1)` = "Log~GDP[t-1]",
-    `diff(Corrup_TI_z, lag = 1)`= "Delta~Corruption",
-    `plm::lag(Corrup_TI_z, 1)` = "Log~Corruption[t-1]",
-    `Corrup_TI_z` = "Log~Corruption[t-1]"
+    `plm::lag(lg_imp_mdpgdp, 1)` = "Log~GDP[t-1]"
+    # `diff(Corrup_TI_z, lag = 1)`= "Delta~Corruption",
+    # `plm::lag(Corrup_TI_z, 1)` = "Log~Corruption[t-1]",
+    # `Corrup_TI_z` = "Log~Corruption[t-1]"
 )
@@
   }) %>% 
-  mutate(type = "Regime Specified")
+  mutate(type = "Institution Specified")
 
@@
     mutate(term = index_coefName[term],
-           term = factor(term, levels = unique(index_coefName)))
+           term = factor(term, levels = unique(index_coefName)), 
+           type = factor(type, levels = c("Pooled", "Institution Specified")))
 
@@
                linetype = 2) +
-    theme_minimal() +
     ggtitle("DV: The Change of Public Support for Democracy") +
@@
     ) +
-    scale_y_discrete(labels = parse(text = rev(levels(df_plot$term)))) +
+    facet_wrap( ~ type) + 
+    scale_y_discrete(labels = parse(text = rev(levels(df_plot$term))))
     # Using expressions of underscore and greek letters
-    # scale_color_gb(palette = "digitMixed") +
-    facet_wrap( ~ type)
+    # scale_color_gb(palette = "digitMixed")
 
@@
 
-```{r num-labelAJPS}
+```{r num-labelAJPS, eval=TRUE}
 names_coef <- c(
@@
 
-```{r num-pointAJPS, results='asis'}
+```{r num-pointAJPS, results='asis', eval=TRUE}
 tb_result_cls <- map(result_clsAJPS, ~ {
@@
 
-```{r num-pureAJPS, results='asis'}
+```{r num-pureAJPS, results='asis', eval=TRUE}
 tb_result_pureAJPS <- map(result_pureAJPS, ~ {
@@
 
-```{r num-expAJPS, results='asis'}
+```{r num-expAJPS, results='asis', eval=TRUE}
 tb_result_expAJPS <- map(result_expAJPS, ~ {
@@
 
-```{r num-labelAPSR}
+```{r num-labelAPSR, eval=TRUE}
 names_coef <- c(
@@
 
-```{r num-pointAPSR, results='asis'}
+```{r num-pointAPSR, results='asis', eval=TRUE}
 tb_result_clsAPSR <- map(result_clsAPSR, ~ {
@@
 
-```{r num-pureAPSR, results='asis'}
+```{r num-pureAPSR, results='asis', eval=TRUE}
 tb_result_pureAPSR <- map(result_pureAPSR, ~ {
@@
 
-```{r num-expAPSR, results='asis'}
+```{r num-expAPSR, results='asis', eval=TRUE}
 tb_result_expAPSR <- map(result_expAPSR, ~ {
@@
 \begin{equation}
-\mathcal{L}(\theta|y, x^{obs}) \propto \int\limit_{\chi} p(x|y, \theta)p(y|\theta)dx^{mis}.
+\mathcal{L}(\theta|y, x^{obs}) \propto \int_{\chi} p(x|y, \theta)p(y|\theta)dx^{mis}.
 \end{equation}
@@
 \begin{equation}
-\mathcal{L}(\theta|y, x) \propto \int\limit_{\chi} p(\theta|y, x)p(x|w)dx.
+\mathcal{L}(\theta|y, x) \propto \int_{\chi} p(\theta|y,x)p(x|w)dx.
 \end{equation}
@@
 
-```{r moc-estimates}
+```{r moc-estimates, eval=TRUE}
 
@@
 
-```{r plot-mocAJPS, fig.cap= "The Effect of Public Support on Democracy ", eval = TRUE, fig.width=7, fig.height=10}
+```{r plot-mocAJPS, fig.cap= "The Effect of Public Support on Democracy ", eval = TRUE, fig.width=7, fig.height=10, eval=TRUE}
 
@@
 
-```{r plot-mocAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", eval = TRUE, fig.width=7, fig.height=10}
+```{r plot-mocAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", eval = TRUE, fig.width=7, fig.height=10, eval=TRUE}
 

### 2021-07-20 paper/memo/memo.Rmd
added response to alternative method and magnitude of coeffients.

@@
 
+## Response 
+Both Reviewers 1 & 2 concern about the validity of the approach which we used to incorporate measurement uncertainty.
+First, we added more explanations on how uncertainty is integrated into the models in Page xx of main text and also presented equations in Page xx in SI.
+It is ture that Rubin's rule is designed to address missing values by using multiple imputation(MI), but as Reviewer 2 has already pointed out, @Blackwell2017 applied the logic of MI and Rubin's rule in their Multiple Overimputation (P309) to address measurement error and missing data which is conceptulized as an extreme case of measurement error.
+
+The idea of our approach for propagating uncertainty is correcting both within and between imputation variance through Rubin's rule, and the idea of MOC is accounting for within imputation variance through drawing sample from the joint posterior distribution of the measurement and analysis model.
+
+To address the performance of the method we used, we employed "method of component" as an alternative way in SI.
+Our approach and MOC yield similar results from replicating APSR's analysis, that is, when uncertainty is allowed, the coefficients on the lagged public support and the change of democratic level are no longer distinguishable from zero in Page xx in MS and Page xx in SI.
+It is not surprising that the estimated effect of democracy is indistinguishable from zero given measurement errors in both democracy and democratic support measurements and cultural features of democratic values.
+As Reviewer3 pointed out, democratic value is formed and shaped by institution, history, and culture and the cultural feature of democratic value determines that it cannot be impacted swiftly by the change of democracy.
+
+Our approach and MOC yield mixed results for AJPS's analysis.
+
+In terms of the impact of measurement error on estimated effects, many studies have shown when taking measurement uncertainty into account, magnitude of coeffients of latent variables can be either attenuated or enlarged substantively [e.g., @treier_democracy_2008, p.
+211; @caughey_policy_2018,p.
+254].
+
 # The Change of Democratic Support and Lagged Support

### 2021-07-20 paper/dcpo_demsupport.Rmd
adjust citation.

@@
 @Blackwell2017a's multiple overimputation (MO) uses the same logic to correct sampling variance.
-We also employ one alternative technique known as “method of composition” (MOC)  [@treier_democracy_2008, p. 215] as a robustness check [see the Online Supplementary Material \@ref(moc)].
+We also employ one alternative technique known as “method of composition” (MOC)  [@Treier2008, p. 215] as a robustness check [see the Online Supplementary Material \@ref(moc)].
 
@@
 The method we employ is "method of composition" (MOC).
-It is a common method for Monte Carlo integration, but can also be applied for addressing uncertainty [@treier_democracy_2008].
+It is a common method for Monte Carlo integration, but can also be applied for addressing uncertainty [@Treier2008].
 To compare these two methods, let's denote `y` as a vector of the outcome variable [either institutional democracy in @Claassen2020a or the changes in mass support of democracy in @Claassen2020b]. 

### 2021-07-20 paper/memo/memo.Rmd
adjust citation

@@
 
-In terms of the impact of measurement error on estimated effects, many studies have shown when taking measurement uncertainty into account, magnitude of coeffients of latent variables can be either attenuated or enlarged substantively [e.g., @treier_democracy_2008, p.
+In terms of the impact of measurement error on estimated effects, many studies have shown when taking measurement uncertainty into account, magnitude of coeffients of latent variables can be either attenuated or enlarged substantively [e.g., @Treier2008, p.
 211; @caughey_policy_2018,p.

### 2021-07-20 paper/dcpo_demsupport.Rmd
var label updated

--- 2021-07-20 paper/dcpo_demsupport.Rmd
@@
     `plm::lag(theta_trim, 1:2)2` = "Support[t-2]",
+
     `diff(Libdem_z, lag = 1)` = "Delta~Liberal~democracy",
@@
     `plm::lag(Vdem_libdem_z, 1)` = "Liberal~democracy[t-1]",
-    `diff(Liberal_z, lag = 1)` = "Delta~Support(electoral)",
-    `diff(Vdem_liberal_z, lag = 1)` = "Delta~Support(electoral)",
-    `plm::lag(Liberal_z, 1)` = "Support[t-1](electoral)",
-    `plm::lag(Vdem_liberal_z, 1)` = "Support[t-1](electoral)",
-    `diff(Polyarchy_z, lag = 1)` = "Delta~Support(minoritarian)",
-    `diff(Vdem_polyarchy_z, lag = 1)` = "Delta~Support(minoritarian)",
-    `plm::lag(Polyarchy_z, 1)` = "Support[t-1](minoritarian)",
-    `plm::lag(Vdem_polyarchy_z, 1)` = "Support[t-1](minoritarian)",
+
+    `diff(Liberal_z, lag = 1)` = "Delta~Electoral~democracy",
+    `diff(Vdem_liberal_z, lag = 1)` = "Delta~Electoral~democracy",
+    `plm::lag(Liberal_z, 1)` = "Electoral~democracy[t-1]",
+    `plm::lag(Vdem_liberal_z, 1)` = "Electoral~democracy[t-1]",
+
+    `diff(Polyarchy_z, lag = 1)` = "Delta~Minoritarian~democracy",
+    `diff(Vdem_polyarchy_z, lag = 1)` = "Delta~Minoritarian~democracy",
+    `plm::lag(Polyarchy_z, 1)` = "Minoritarian~democracy[t-1]",
+    `plm::lag(Vdem_polyarchy_z, 1)` = "Minoritarian~democracy[t-1]",
+
     `diff(lnGDP_imp, lag = 1)` = "Delta~Log~GDP~per~capita",

### 2021-07-20 paper/memo/memo.Rmd
clarify the DV in fig2.

@@
 
+## Response
+First, we need to clarify the DV in Figure2 is the change of public support for democracy rather than current public support.
+Second, when DV is the change of public support, Claassen's original results wouldn't make any sense. 
+Claassen's original results indicate the change of public support in one year is positively changed by the public support in the previous one year and negatively shifted by the previous two years.
+However, should we expect that public support can produce its demand and especially a conflicting demand?
+Can high public support of this year ask for a change in next year but resist a change in the next two years?
+In the contrast, our null results of lagged support on change of support mood make more sense since the change of moods is supposed to be shaped by exogenous factors, such as democratic or economic environment, or especially a shock.
+Unfortunately, after acknowledging uncertainty, the estimated effect of the change of democracy is indistinguishable from zero and the magnitude of the coefficient also moves to zero.
+As @Treier2008 emphasized, only in applications where democracy has a strong effect on the quantity of interest and models are simple enough, it is rare that accounting of uncertainty renders the insignificant effect of democracy.
+However, even in Claassen's original results, the estimated effects of both the change of democracy and other social as well as economic factors are small.
+Given the measurement errors in both democratic indices and public support, it is not surprising to get the diminution of the estimated effects.
+
 # Test Full Models 

### 2021-07-21 paper/memo/memo.Rmd
response draft is almost done, not discuss substantive inference yet.

@@
 In terms of the impact of measurement error on estimated effects, many studies have shown when taking measurement uncertainty into account, magnitude of coeffients of latent variables can be either attenuated or enlarged substantively [e.g., @Treier2008, p.
-211; @caughey_policy_2018,p.
+211; @caughey2018,p.
 254].
@@
 
+## Response
 Thanks to editor's suggesions, we do agree that we should present and assess the effect of intermediate modification in an incremental way.
@@
 I would like the author to engage a bit more in substantive debates.
+
+## Response
+Since we do acknowledge uncertainty in extant measurements, we can not unambigously make a statement that there is no relationship between public support and regime survival although it is possible.
+Examing theories in different contexts overtime is a promising strategy for generalization [KKV].
+However, scholars' pursue on models usually lead to the ignorance for measurements which cost more time but determine the quality of data in analyses [@stegmueller2011].
+In this letter, we stress the necessity of incorporating measurement uncertainty in analyses with latent variables and encourage scholars to pay more attention on that.
 
@@
 
+## Response
+We did not do a simulation study, instead we employ MOC suggested by Review 1 and 2 as a robust check and present results in SI. 
+We also elaborate the imputation process in details in MS and clarify the equations in SI.
+Measurement errors in other variables have been included in our rexaminations. 
+As for the concerns on Fig2, the first thing needing to clarify is that the DV is not current public support but the change of public support. 
+We elaborate why our null results make more sense than Claassen's original results.
+
+## Editor
 Reviewers 1, 2, and 4 all ask why the results for Claassen's model but accounting for measurement error (second set of results) also yield different point estimates.
@@
 
+## Response
+It is a misunderstanding that incorporating uncertainty only changes standard error.
+First, incorporating uncertainty might or might not cause the changes of standard error.
+For example, standard errors did not change after accounting for uncerainty in [@caughey2018] but became smaller in [@Treier2008].
+Second, the propogation of uncertainty can either attentuate or magnify the magnitude of estimated effects.
+*We can cite more lit if neccessary*. 
+For transparcy and avoiding confusion, we only focus on uncertainty in revised version.
+
+## Editor
 Evidence to address these various methodological questions and issues issues may be included in the response to reviewers and/or the Supplemental Information (if it would help readers appreciate the methods used) as needed.
-For instance, I could imagine some readers benefitting from having the estimating equations included in the Supplemental Information in order to appreciate how measurement error is incorporated into the estimates as well as more information about the levels of measurement used (mentioned as an important difference by Reviewer 3).
+*For instance, I could imagine some readers benefitting from having the estimating equations included in the Supplemental Information in order to appreciate how measurement error is incorporated into the estimates as well as more information about the levels of measurement used (mentioned as an important difference by Reviewer 3)*.
 While Reviewer 1 asks for all results from the original two studies be replicated as well, these additional replications need only be included in the paper or SI to the extent that they are relevant to the relationship between support and democracy at the core of this Letter's focus.
@@
 
+## Response
+We might need to review the functions added in SI.
+
+## Editor
 Finally, Reviewers 2, 3, and 4 offer various suggestions for how to more effectively frame or discuss the substantive or theoretical (rather than measurement or methodological) implications of your contribution.
 We hope their feedback is useful as you revise your Letter.
+
+## Response
 

### 2021-07-21 paper/dcpo_demsupport.Rmd
adjust citation

--- 2021-07-20 paper/dcpo_demsupport.Rmd
@@
 Although measurement uncertainty has yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can bias coefficient estimates and standard errors.
-Especially when measurement error is correlated with the outcome variable, the resulting bias could either attenuate or exaggerate the magnitude of the estimated effects [see, e.g., @Blackwell2017, p.360; @caughey_policy_2018, p.254].
+Especially when measurement error is correlated with the outcome variable, the resulting bias could either attenuate or exaggerate the magnitude of the estimated effects [see, e.g., @Blackwell2017, p.360; @caughey2018, p.254].
 In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, p.
@@
 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, pp.
-791-792; @caughey_policy_2018, p.
+791-792; @caughey2018, p.
 254].

### 2021-07-21 paper/memo/memo.Rmd
draft

@@
 It is a good point.
-Many variables in the analysis cannot be observed directly and inherently contaminated by measurement errors.
-To address this concern, since Claassen used V-Dem Version 8 in his analyses, we incorporated measurement error for V-Dem democracy index, electoral index, polyarchy index, and liberal index, by using the posterior distribution of Version 8 provided by V-Dem.
-Regarding the data used to replicate Claassen' analyses, we simulated 900 data set for democracy index from V-Dem Version 10 which did not provide available posterior distribution yet but standard error.
-To account for measurement error in Corruption Perceptions Index, we simulated 900 draws from a distribution with the point estimate and standard error which provided by CPI for the year from 2012 to 2018.
-For the year before 2012, we estimated standard error by using the multiplication between country's maximum relative error (standard error/cpi index) and CPI index.
+Many variables in the analysis cannot be observed directly and are inherently contaminated by measurement errors.
+To address this concern, since Claassen used V-Dem Version 8 in his analyses, we incorporated measurement error for the V-Dem democracy index, electoral index, polyarchy index, and liberal index using the posterior distribution of Version 8 provided by V-Dem.
+Regarding the data used to replicate Claassen's analyses, we simulated 900 data set for democracy index from V-Dem Version 10, which did not provide available posterior distribution yet but standard error.
+To account for measurement error in Corruption Perceptions Index, we simulated 900 draws from a distribution with the point estimate and standard error provided by CPI for the year from 2012 to 2018.
+We estimated the standard error for the year before 2012 by using the multiplication between countries' maximum relative error (standard error/cpi index) and their CPI index.
 We rerun the models following the same steps in our previous analysis but incorporating uncertainty in democracy index, democratic support, and corruption perception index.
-The relationship between public support and democracy development disappears when uncertainty is accounted for in models either using Claassen's original data or expanded data with 25% more country-year data.
-The updated results are presented in Figure XXX at Page xx.
+The relationship between the change of public support and the change of democracy disappears when uncertainty is accounted for in models either using Claassen's original data or expanded data with 25% more country-year data.
+The updated results are presented in Figure XXX on Page xx.
+
+*Need to explain the different results in AJPS*
 
@@
 ## Response 
-Both Reviewers 1 & 2 concern about the validity of the approach which we used to incorporate measurement uncertainty.
-First, we added more explanations on how uncertainty is integrated into the models in Page xx of main text and also presented equations in Page xx in SI.
-It is ture that Rubin's rule is designed to address missing values by using multiple imputation(MI), but as Reviewer 2 has already pointed out, @Blackwell2017 applied the logic of MI and Rubin's rule in their Multiple Overimputation (P309) to address measurement error and missing data which is conceptulized as an extreme case of measurement error.
+Both Reviewers 1 & 2 concern the validity of the approach used to incorporate measurement uncertainty.
+First, we added more explanations of how uncertainty is integrated into the models on Page xx of the main text and presented equations on Page xx in SI.
+Rubin's rule is indeed designed to address missing values by using multiple imputations (MI).
+However, as Reviewer 2 has already pointed out, @Blackwell2017 applied the logic of MI and Rubin's rule in their Multiple Overimputation (P309) to address measurement error and missing data, which is conceptualized as an extreme case of measurement error.
 
-The idea of our approach for propagating uncertainty is correcting both within and between imputation variance through Rubin's rule, and the idea of MOC is accounting for within imputation variance through drawing sample from the joint posterior distribution of the measurement and analysis model.
+The idea of our approach for propagating uncertainty is correcting both within and between imputation variance through Rubin's rule, and the idea of MOC is accounting for within imputation variance through drawing samples from the joint posterior distribution of the measurement and analysis model.
 
-To address the performance of the method we used, we employed "method of component" as an alternative way in SI.
+To address the performance of the method we used, we employed the "method of component" as an alternative way in SI.
 Our approach and MOC yield similar results from replicating APSR's analysis, that is, when uncertainty is allowed, the coefficients on the lagged public support and the change of democratic level are no longer distinguishable from zero in Page xx in MS and Page xx in SI.
 It is not surprising that the estimated effect of democracy is indistinguishable from zero given measurement errors in both democracy and democratic support measurements and cultural features of democratic values.
-As Reviewer3 pointed out, democratic value is formed and shaped by institution, history, and culture and the cultural feature of democratic value determines that it cannot be impacted swiftly by the change of democracy.
+As Reviewer3 pointed out, democratic value is formed and shaped by institution, history, and culture, and the cultural feature of democratic value determines that it cannot be impacted swiftly by the change of democracy.
 
@@
 
-In terms of the impact of measurement error on estimated effects, many studies have shown when taking measurement uncertainty into account, magnitude of coeffients of latent variables can be either attenuated or enlarged substantively [e.g., @Treier2008, p.
+In terms of the impact of measurement error on estimated effects, many studies have shown that when taking measurement uncertainty into account, the magnitude of coefficients of latent variables can be either attenuated or enlarged substantively [e.g., @Treier2008, p.
 211; @caughey2018,p.
@@
 ## Response
-First, we need to clarify the DV in Figure2 is the change of public support for democracy rather than current public support.
-Second, when DV is the change of public support, Claassen's original results wouldn't make any sense. 
-Claassen's original results indicate the change of public support in one year is positively changed by the public support in the previous one year and negatively shifted by the previous two years.
+
+First, we need to clarify that the DV in Figure2 is the change of public support for democracy rather than current public support.
+Second, when DV is the change of public support, Claassen's original results would not make any sense. 
+Claassen's original results indicate the change of public support in one year is positively changed by the public support in the previous year and negatively shifted by the previous two years.
 However, should we expect that public support can produce its demand and especially a conflicting demand?
-Can high public support of this year ask for a change in next year but resist a change in the next two years?
-In the contrast, our null results of lagged support on change of support mood make more sense since the change of moods is supposed to be shaped by exogenous factors, such as democratic or economic environment, or especially a shock.
-Unfortunately, after acknowledging uncertainty, the estimated effect of the change of democracy is indistinguishable from zero and the magnitude of the coefficient also moves to zero.
-As @Treier2008 emphasized, only in applications where democracy has a strong effect on the quantity of interest and models are simple enough, it is rare that accounting of uncertainty renders the insignificant effect of democracy.
-However, even in Claassen's original results, the estimated effects of both the change of democracy and other social as well as economic factors are small.
-Given the measurement errors in both democratic indices and public support, it is not surprising to get the diminution of the estimated effects.
+Can high public support this year ask for a change next year but resist a change in the next two years?
+In contrast, our null results of lagged support on change of support mood make more sense since the change of moods is supposed to be shaped by exogenous factors, such as democratic or economic environment, or especially a shock.
+Unfortunately, after acknowledging uncertainty, the estimated effect of the change of democracy is indistinguishable from zero, and the magnitude of the coefficient also moves to zero.
+As @Treier2008 emphasized, only in applications where democracy has a strong effect on the quantity of interest and models are simple enough, accounting of uncertainty rarely renders the insignificant effect of democracy.
+However, even in Claassen's original results, the estimated effects of both the change of democracy and other social and economic factors are minor.
+Given the measurement errors in both democratic indices and public support, it is not surprising to see the diminution of the estimated effects.
 
@@
 ## Response
-Regarding Reviewer 1's request on replicating all specification in the original two studies, we added alternate specifications on the relationship between support and democracy, including GMM models, First Different Models, and sample split.
-Results do not change in all these models, presented in Page xxx, Figure xxx and xxx in SI. 
-As the editor suggested that this letter should focus on the core point, that is, the relationship between public support and democracy, we do not replicate specifications on other relationship.
+In contrast, our null results of lagged support on change of support mood make more sense since the change of moods is supposed to be shaped by exogenous factors, such as democratic or economic environment, or especially a shock.
+Unfortunately, after acknowledging uncertainty, the estimated effect of the change of democracy is indistinguishable from zero, and the magnitude of the coefficient also moves to zero.
+As @Treier2008 emphasized, only in applications where democracy has a strong effect on the quantity of interest and models are simple enough, accounting of uncertainty rarely renders the insignificant effect of democracy.
+However, even in Claassen's original results, the estimated effects of both the change of democracy and other social and economic factors are minor.
+Given the measurement errors in both democratic indices and public support, it is not surprising to see the diminution of the estimated effects.
 

### 2021-07-21 paper/memo/memo.Rmd
an item-style rough draft @fsolt. @sammo3182 please check and add more on full model part.

@@
 ## Response
-In contrast, our null results of lagged support on change of support mood make more sense since the change of moods is supposed to be shaped by exogenous factors, such as democratic or economic environment, or especially a shock.
-Unfortunately, after acknowledging uncertainty, the estimated effect of the change of democracy is indistinguishable from zero, and the magnitude of the coefficient also moves to zero.
-As @Treier2008 emphasized, only in applications where democracy has a strong effect on the quantity of interest and models are simple enough, accounting of uncertainty rarely renders the insignificant effect of democracy.
-However, even in Claassen's original results, the estimated effects of both the change of democracy and other social and economic factors are minor.
-Given the measurement errors in both democratic indices and public support, it is not surprising to see the diminution of the estimated effects.
+Regarding Reviewer 1's request on replicating all specifications in the original two studies, we added alternate specifications on the relationship between public support and democracy, including GMM models, First Different Models, and sample split.
+Results do not change in all these models, presented on Page xxx, Figure xxx, and xxx in SI. 
+As the editor suggested, this letter should focus on the core point: the relationship between public support and democracy. We do not replicate specifications on other relationships.
+
+*Need to add APSR models or more description on full models*
 
@@
 ## Response
-Thanks to editor's suggesions, we do agree that we should present and assess the effect of intermediate modification in an incremental way.
-To do this, in the revised manuscript, we replicated Claassen's measure for public democratic support by applying his measurement Model5 to his original data file and used the posterior distribution of the public support estimates to incorporated uncertainty.
-Then, we added more survey data to improve the quality of source data and applied Model5 to this expanded data set, still keeping the full posterior distribution of estimates. 
+Thanks to the editor's suggestions, we agree that we should present and assess the effect of intermediate modification in an incremental way.
+To do this, in the revised manuscript, we replicated Claassen's measure for public democratic support by applying his measurement Model5 to his original data file and used the posterior distribution of the public support estimates to incorporate uncertainty.
+Then, we added more survey data to improve source data quality and applied Model5 to this expanded data set, still keeping the full posterior distribution of estimates.
 In this way, we isolate the effects of measurement uncertainty and more data. 
@@
 ## Response
-Since we do acknowledge uncertainty in extant measurements, we can not unambigously make a statement that there is no relationship between public support and regime survival although it is possible.
-Examing theories in different contexts overtime is a promising strategy for generalization [KKV].
-However, scholars' pursue on models usually lead to the ignorance for measurements which cost more time but determine the quality of data in analyses [@stegmueller2011].
-In this letter, we stress the necessity of incorporating measurement uncertainty in analyses with latent variables and encourage scholars to pay more attention on that.
+Since we do acknowledge uncertainty in extant measurements, we can not unambiguously make a statement that there is no relationship between public support and regime survival, although it is possible.
+Examing theories in different contexts over time is a promising strategy for generalization [KKV].
+However, scholars' pursuit of models usually leads to ignorance for measurements that cost more time but determine the quality of data in analyses [@stegmueller2011].
+In this letter, we stress the necessity of incorporating measurement uncertainty in analyses with latent variables and encourage scholars to pay more attention to that.
+*need more on substantive discussion*
 
@@
 ## Response
-We did not do a simulation study, instead we employ MOC suggested by Review 1 and 2 as a robust check and present results in SI. 
-We also elaborate the imputation process in details in MS and clarify the equations in SI.
-Measurement errors in other variables have been included in our rexaminations. 
-As for the concerns on Fig2, the first thing needing to clarify is that the DV is not current public support but the change of public support. 
-We elaborate why our null results make more sense than Claassen's original results.
+We did not do a simulation study. Instead, we employ MOC suggested by Review 1 and 2 as a robust check and present results in SI. 
+We also elaborate on the imputation process in detail in MS and clarify the equations in SI.
+Measurement errors in other variables have been included in our reexaminations. 
+As for the concerns in Fig2, the first thing needing to clarify is that the DV is not current public support but the change of public support. 
+We elaborate on why our null results make more sense than Claassen's original results.
 
@@
 First, incorporating uncertainty might or might not cause the changes of standard error.
-For example, standard errors did not change after accounting for uncerainty in [@caughey2018] but became smaller in [@Treier2008].
-Second, the propogation of uncertainty can either attentuate or magnify the magnitude of estimated effects.
-*We can cite more lit if neccessary*. 
-For transparcy and avoiding confusion, we only focus on uncertainty in revised version.
+For example, standard errors did not change after accounting for uncertainty in [@caughey2018] but became smaller in [@Treier2008].
+Second, the propagation of uncertainty can either attenuate or magnify the magnitude of estimated effects.
+*We can cite more lit if necessary*. 
+To avoid confusion, we only focus on uncertainty in this revised version.
 

### 2021-07-22 R/cls_correct_ajpsapsr.R
codes for creating analysis data with corrected but not expanded cls's data. The expanded part is not done yet.

@@ -1,0 +1,363 @@
+if (!require(pacman)) install.packages("pacman")
+library(pacman)
+
+# load all the packages you will use below 
+p_load(
+    here,
+    purrr,
+    countrycode,
+    tidyverse,
+    rstan,
+    osfr
+) 
+
+#osf_retrieve_file("kg7z4") %>%
+#     osf_download(here::here("data"))  ##pure corrected
+
+
+# Functions preload
+set.seed(313)
+
+
+reformat_dcpo_output <- function(x, parameter_name) {
+    df_temp <- x %>% 
+        as_tibble(.name_repair = ~ls_country) %>% 
+        mutate(year = first_year + row_number() - 1) %>% 
+        pivot_longer(cols = all_of(ls_country),
+                     names_to = "country",
+                     values_to = parameter_name) %>%
+        arrange(country, year)
+    return(df_temp)
+}
+
+
+
+load(here("data", "claassen_m5_3k_07-05-11-16.rda")) 
+
+claassen_m5_theta <- rstan::extract(claassen_m5, pars = "theta")  ##derived from claassen_m5_3k_07-05-11-16
+##however, theta has 136 country instead of 137. 
+
+#cnt.names = as.character(sort(unique(sddem2$Country)))
+
+
+claassen_replication <- readRDS(here::here("data","claassen_replication.rds")) %>% 
+    janitor::clean_names() %>% 
+    DCPOtools::with_min_yrs(2) 
+##need to use claassen_replication.rds. remember to mention which country is missing
+
+length(unique(claassen_replication$country))
+
+ls_year <- 1988:2017
+ls_country <- claassen_replication$country %>% unique()
+first_year <- min(claassen_replication$year)
+
+correct_cls_theta_list <- purrr::map(1:900, function(anEntry) {
+    claassen_m5_theta$theta[anEntry,,] %>%
+        reformat_dcpo_output("theta") 
+}
+)
+#year 30, country 136
+save(correct_cls_theta_list,file = here("data","correct_cls_theta_list.rda"))
+
+################################################################
+######## Create lists for elements in analysis data  ###########
+########### AJPS: cls_libdem_ajps_list,correct_cls_ajps ############
+################################################################
+
+ 
[…]

### 2021-07-22 paper/dcpo_demsupport.Rmd
update moc models with corrected data.

@@
 
-load(here("data", "pure_cls_ajps.rda")) 
-load(here("data", "pure_cls_apsr.rda")) 
+#load(here("data", "pure_cls_ajps.rda")) 
+#load(here("data", "pure_cls_apsr.rda")) 
+load(here("data", "correct_cls_ajps.rda"))
+load(here("data", "correct_cls_apsr.rda")) 
 load(here("data", "exp_cls_ajps.rda"))
@@
 result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
-mocresult_pureAJPS <- readRDS(here("output", "estimates_moc_pureAJPS.RDS"))
+#mocresult_pureAJPS <- readRDS(here("output", "estimates_moc_pureAJPS.RDS"))
+mocresult_correctAJPS <- readRDS(here("output", "estimates_moc_correctAJPS.RDS"))
 mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expAJPS.RDS"))
-mocresult_pureAPSR <- readRDS(here("output", "estimates_moc_pureAPSR.RDS"))
+#mocresult_pureAPSR <- readRDS(here("output", "estimates_moc_pureAPSR.RDS"))
+mocresult_correctAPSR <- readRDS(here("output", "estimates_moc_correctAPSR.RDS"))
 mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expAPSR.RDS"))
@@
 
-df_pure_clsAjps <- purrr::map(1:900, function(anEntry) {
-  pure_cls_ajps[[anEntry]] %>% 
+#df_pure_clsAjps <- purrr::map(1:900, function(anEntry) {
+#  pure_cls_ajps[[anEntry]] %>% 
+#    plm::pdata.frame(index = c("country", "year"))
+#})
+
+#result_pure_clsUncertain  <- map(ls_mod_ajpsCLS[1:2], function(aMod){
+#  result <- methodComposition1(df_pure_clsAjps,aMod)
+#})
+
+#names(result_pure_clsUncertain) <- c("pooled", "pooled-regime")
+
+#result_pure_clsUncertain_gmm  <- map(ls_mod_ajpsCLS[3:4], function(aMod){
+#  result <- methodComposition2(df_pure_clsAjps,aMod)
+#})
+#names(result_pure_clsUncertain_gmm) <- c("gmm", "gmm-regime")
+
+#mocresult_pureAJPS <- append(result_pure_clsUncertain, result_pure_clsUncertain_gmm)
+
+#saveRDS(mocresult_pureAJPS, file =here("output","estimates_moc_pureAJPS.RDS"))
+
+df_correct_clsAjps <- purrr::map(1:900, function(anEntry) {
+  correct_cls_ajps[[anEntry]] %>% 
     plm::pdata.frame(index = c("country", "year"))
@@
 
-result_pure_clsUncertain  <- map(ls_mod_ajpsCLS[1:2], function(aMod){
-  result <- methodComposition1(df_pure_clsAjps,aMod)
-})
-
-names(result_pure_clsUncertain) <- c("pooled", "pooled-regime")
-
-result_pure_clsUncertain_gmm  <- map(ls_mod_ajpsCLS[3:4], function(aMod){
-  result <- methodComposition2(df_pure_clsAjps,aMod)
-})
-names(result_pure_clsUncertain_gmm) <- c("gmm", "gmm-regime")
-
-mocresult_pureAJPS <- append(result_pure_clsUncertain, result_pure_clsUncertain_gmm)
-
-saveRDS(mocresult_pureAJPS, file =here("output","estimates_moc_pureAJPS.RDS"))
+result_correct_clsUncertain  <- map(ls_mod_ajpsCLS[1:2], function(aMod){
+  result <- methodComposition1(df_correct_clsAjps,aMod)
+})
+
+names(result_correct_clsUncertain) <- c("pooled", "pooled-regime")
+
+result_correct_clsUncertain_gmm  <- map(ls_mod_ajpsCLS[3:4], function(aMod){
+  result <- methodComposition2(df_correct_clsAjps,aMod)
+})
+names(result_correct_clsUncertain_gmm) <- c("gmm", "gmm-regime")
+
+mocresult_correctAJPS <- append(result_correct_clsUncertain, result_correct_clsUncertain_gmm)
+
+saveRDS(mocresult_correctAJPS, file =here("output","estimates_moc_correctAJPS.RDS"))
 
@@
   mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_pureAJPS[["pooled"]]), model = "Uncertainty"),
+ # mutate(MOCsumm(mocresult_pureAJPS[["pooled"]]), model = "Uncertainty"),
+ mutate(MOCsumm(mocresult_correctAJPS[["pooled"]]), model = "Corrected"),
   mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), model = "Uncertainty+Expanded Data")
@@
   mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_pureAJPS[["gmm"]]), model = "Uncertainty"),
+  #mutate(MOCsumm(mocresult_pureAJPS[["gmm"]]), model = "Uncertainty"),
+  mutate(MOCsumm(mocresult_correctAJPS[["gmm"]]), model = "Corrected"),
   mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), model = "Uncertainty+Expanded Data")
@@
     type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Original", "Uncertainty", "Uncertainty+Expanded Data")))
+    model = factor(model, levels = c("Original", "Corrected", "Uncertainty+Expanded Data")))
 
@@
   mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_pureAJPS[["pooled-regime"]]), model = "Uncertainty"),
+  #mutate(MOCsumm(mocresult_pureAJPS[["pooled-regime"]]), model = "Uncertainty"),
+  mutate(MOCsumm(mocresult_correctAJPS[["pooled-regime"]]), model = "Corrected"),
   mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), model = "Uncertainty+Expanded Data")
@@
   mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_pureAJPS[["gmm-regime"]]), model = "Uncertainty"),
+  #mutate(MOCsumm(mocresult_pureAJPS[["gmm-regime"]]), model = "Uncertainty"),
+  mutate(MOCsumm(mocresult_correctAJPS[["gmm-regime"]]), model = "Corrected"),
  mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), model = "Uncertainty+Expanded Data")
@@
     type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Original","Uncertainty", "Uncertainty+Expanded Data")))
+    model = factor(model, levels = c("Original","Corrected", "Uncertainty+Expanded Data")))
 terms2 <- factor(rev(c("Democracy[t-1]",
@@
 
-df_pure_clsAPSR <- purrr::map(1:900, function(anEntry) {
-  pure_cls_apsr[[anEntry]] %>% 
+#df_pure_clsAPSR <- purrr::map(1:900, function(anEntry) {
+#  pure_cls_apsr[[anEntry]] %>% 
+#    plm::pdata.frame(index = c("country", "year"))
+#}
+#)
+
+#mocresult_pureAPSR  <- map(ls_mod_apsrCLS, function(aMod){
+#  result <- methodComposition3(df_pure_clsAPSR,aMod)
+#})
+
+#names(mocresult_pureAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
+#                                "fd1", "fd-regime1", "fd2", "fd-regime2")
+
+#saveRDS(mocresult_pureAPSR, file = here::here("ouput","estimates_moc_pureAPSR.RDS"))
+
+df_correct_clsAPSR <- purrr::map(1:900, function(anEntry) {
+  correct_cls_apsr[[anEntry]] %>% 
     plm::pdata.frame(index = c("country", "year"))
@@
 
-mocresult_pureAPSR  <- map(ls_mod_apsrCLS, function(aMod){
-  result <- methodComposition3(df_pure_clsAPSR,aMod)
-})
-
-names(mocresult_pureAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
+mocresult_correctAPSR  <- map(ls_mod_apsrCLS, function(aMod){
+  result <- methodComposition3(df_correct_clsAPSR,aMod)
+})
+
+names(mocresult_correctAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
                                 "fd1", "fd-regime1", "fd2", "fd-regime2")
 
-saveRDS(mocresult_pureAPSR, file = here::here("ouput","estimates_moc_pureAPSR.RDS"))
+saveRDS(mocresult_correctAPSR, file = here::here("ouput","estimates_moc_correctAPSR.RDS"))
+
+```
+
+```{r mocresult-expAPSR}
+
+#df_exp_clsAPSR <- purrr::map(1:900, function(anEntry) {
+#  exp_cls_apsr[[anEntry]] %>% 
+#    plm::pdata.frame(index = c("country", "year"))
+#}
+#)
+
+#mocresult_expAPSR <- map(ls_mod_apsrCLS, function(aMod){
+ # result <- methodComposition3(df_exp_clsAPSR,aMod)
+#})
+
+#names(mocresult_expAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
+#                                "fd1", "fd-regime1", "fd2", "fd-regime2")
+#saveRDS(mocresult_expAPSR, file = here::here("ouput","estimates_moc_expAPSR.RDS"))
 
@@
   mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_pureAPSR[["pooled1"]]), model = "Uncertainty"),
+  #mutate(MOCsumm2(mocresult_pureAPSR[["pooled1"]]), model = "Uncertainty"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["pooled1"]]), model = "Corrected"),
   mutate(MOCsumm2(mocresult_expAPSR[["pooled1"]]), model = "Uncertainty+Expanded Data")
@@
   mutate(result_clsAPSR[["fd1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_pureAPSR[["fd1"]]), model = "Uncertainty"),
+  #mutate(MOCsumm2(mocresult_pureAPSR[["fd1"]]), model = "Uncertainty"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["fd1"]]), model = "Corrected"),
   mutate(MOCsumm2(mocresult_expAPSR[["fd1"]]), model = "Uncertainty+Expanded Data")
@@
     type = factor(type,  levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Original","Uncertainty", "Uncertainty+Expanded Data"))
+    model = factor(model, levels = c("Original","Corrected", "Uncertainty+Expanded Data"))
   )
@@
   mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_pureAPSR[["pooled-regime1"]]), model = "Uncertainty"),
+  #mutate(MOCsumm2(mocresult_pureAPSR[["pooled-regime1"]]), model = "Uncertainty"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime1"]]), model = "Corrected"),
+
   mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime1"]]), model = "Uncertainty+Expanded Data")
@@
   mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_pureAPSR[["fd-regime1"]]), model = "Uncertainty"),
+  #mutate(MOCsumm2(mocresult_pureAPSR[["fd-regime1"]]), model = "Uncertainty"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime1"]]), model = "Corrected"),
   mutate(MOCsumm2(mocresult_expAPSR[["fd-regime1"]]), model = "Uncertainty+Expanded Data")
@@
   mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_pureAPSR[["pooled2"]]), model = "Uncertainty"),
+  #mutate(MOCsumm2(mocresult_pureAPSR[["pooled2"]]), model = "Uncertainty"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["pooled2"]]), model = "Corrected"),
+
   mutate(MOCsumm2(mocresult_expAPSR[["pooled2"]]), model = "Uncertainty+Expanded Data")
@@
   mutate(result_clsAPSR[["fd2"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_pureAPSR[["fd2"]]), model = "Uncertainty"),
+  #mutate(MOCsumm2(mocresult_pureAPSR[["fd2"]]), model = "Uncertainty"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["fd2"]]), model = "Corrected"),
   mutate(MOCsumm2(mocresult_expAPSR[["fd2"]]), model = "Uncertainty+Expanded Data")
@@
   mutate(result_clsAPSR[["pooled-regime2"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_pureAPSR[["pooled-regime2"]]), model = "Uncertainty"),
+ # mutate(MOCsumm2(mocresult_pureAPSR[["pooled-regime2"]]), model = "Uncertainty"),
+ mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime2"]]), model = "Corrected"),
+
   mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime2"]]), model = "Uncertainty+Expanded Data")) %>% 
@@
   mutate(result_clsAPSR[["fd-regime2"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_pureAPSR[["fd-regime2"]]), model = "Uncertainty"),
+  #mutate(MOCsumm2(mocresult_pureAPSR[["fd-regime2"]]), model = "Uncertainty"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime2"]]), model = "Corrected"),
   mutate(MOCsumm2(mocresult_expAPSR[["fd-regime2"]]), model = "Uncertainty+Expanded Data")) %>% 

### 2021-07-22 R/exp_claassen_input.R
add exp_claassen_input

@@ -1,0 +1,31 @@
+library(tidyverse)
+library(DCPOtools)
+
+# claassen_input_raw <- DCPOtools:::claassen_setup(vars = read_csv(here::here("data-raw", "mood_dem.csv"),
+#                                                                  col_types = "cccccc"),
+#                                                  file = "data/claassen_input_raw.csv")
+
+claassen_input_raw <- read_csv(here::here("data", "claassen_input_raw.csv"),
+                               col_types = "cdcddcd")
+
+claassen_input_raw1 <- claassen_input_raw %>% 
+    filter(!((str_detect(item, "army_wvs") & # WVS obs identified as problematic by Claassen 
+                  ((country=="Albania" & year==1998) |
+                       (country=="Indonesia" & (year==2001 | year==2006)) |
+                       (country=="Iran" & year==2000) |
+                       (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
+                       (country=="Vietnam" & year==2001))) |
+                 (str_detect(item, "strong_wvs") &
+                      ((country=="Egypt" & year==2012) |
+                           (country=="Iran" & (year==2000 | year==2007)) | # 2005 in Claassen
+                           (country=="India") |
+                           (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
+                           (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
+                           (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
+                           (country=="Vietnam" & year==2001))) |
+                 (country %in% c("Puerto Rico", "Northern Ireland", 
+                                 "SrpSka Republic", "Hong Kong SAR China")))) %>%
+    with_min_yrs(2)
+
+exp_claassen_input <- DCPOtools:::format_claassen(claassen_input_raw1)
+save(exp_claassen_input, file = here::here("data", "exp_claassen_input.rda"))

### 2021-07-22 paper/memo/memo.Rmd
draft

--- 2021-07-21 paper/memo/memo.Rmd
@@
 
-# Uncertainty in DV and Control Variables
+## Reviewer #1
+[Issue 17](https://github.com/fsolt/dcpo_dem_mood/issues/17) My primary concern is that the method by which measurement error is included / added is not sufficiently explicated and demonstrated to be valid (e.g., using Monte Carlo experiments), especially in the time-series, cross-sectional context which is of interest.
+The authors cite several applied articles - none of which appears to be methodological in nature - as well as a classic book by Rubin on multiple imputation in surveys - which is a distinct topic.
+This is unfortunate because I have several concerns with the method as used and the results which are produced, as described below.
 
-## Reviewer #1 
 [Issue 16](https://github.com/fsolt/dcpo_dem_mood/issues/16) First, I believe that the measurement error of variables included in the model should be factored in.
@@
 
-## Reviewer #2
-[Issue 16](https://github.com/fsolt/dcpo_dem_mood/issues/16) Despite the MS's assertion of the "absolute necessity" of accounting for measurement error, the MS does not do so for any of the other variables in the analysis.
-Given that Treier and Jackman's analysis focused on uncertainty in measures of democracy, the most obvious omission is the V-DEM democracy measure itself (which, according to the V-DEM documentation, does appear to have associated uncertainty estimates).
+[Issue 24](https://github.com/fsolt/dcpo_dem_mood/issues/23) Second, the results in Figure 2, based on models using democratic support as a dependent variable, are puzzling.
+They appear to show that democratic support is entirely disconnected from such prominent features of the political environment as the level of democracy and economic development.
+Not only are these effects insignificant, but their point estimates are almost exactly zero in magnitude.
+The effects of lagged democratic support are also zero, which is even more implausible because it suggests that democratic support in one year is entirely disconnected from its levels in previous years.
+In other words, Denmark is as likely to have a low value next year as China is likely to have a high value.
+This stands in contrast with much of existing research on democratic support and political culture.
 
-## Response 
-A major concern raised by Reviewers 1 & 2 was regard to the omission of measurement errors of DV and control variables in our analysis.
-It is a good point.
-Many variables in the analysis cannot be observed directly and are inherently contaminated by measurement errors.
-To address this concern, since Claassen used V-Dem Version 8 in his analyses, we incorporated measurement error for the V-Dem democracy index, electoral index, polyarchy index, and liberal index using the posterior distribution of Version 8 provided by V-Dem.
-Regarding the data used to replicate Claassen's analyses, we simulated 900 data set for democracy index from V-Dem Version 10, which did not provide available posterior distribution yet but standard error.
-To account for measurement error in Corruption Perceptions Index, we simulated 900 draws from a distribution with the point estimate and standard error provided by CPI for the year from 2012 to 2018.
-We estimated the standard error for the year before 2012 by using the multiplication between countries' maximum relative error (standard error/cpi index) and their CPI index.
-We rerun the models following the same steps in our previous analysis but incorporating uncertainty in democracy index, democratic support, and corruption perception index.
-The relationship between the change of public support and the change of democracy disappears when uncertainty is accounted for in models either using Claassen's original data or expanded data with 25% more country-year data.
-The updated results are presented in Figure XXX on Page xx.
-
-*Need to explain the different results in AJPS*
-
-# Alternative Method for Incorporating uncertainty
-
-## Reviewer #1
-[Issue 17](https://github.com/fsolt/dcpo_dem_mood/issues/17) My primary concern is that the method by which measurement error is included / added is not sufficiently explicated and demonstrated to be valid (e.g., using Monte Carlo experiments), especially in the time-series, cross-sectional context which is of interest.
-The authors cite several applied articles - none of which appears to be methodological in nature - as well as a classic book by Rubin on multiple imputation in surveys - which is a distinct topic.
-This is unfortunate because I have several concerns with the method as used and the results which are produced, as described below.
 [Issue 23](https://github.com/fsolt/dcpo_dem_mood/issues/23) Alternatively, the authors might use a different method for factoring in the error due to measurement: structural equation models, which, in essence, combine a measurement model and the subsequent regression model in one step.
@@
 
+[Issue 22](https://github.com/fsolt/dcpo_dem_mood/issues/22) I have two additional concerns with the paper.
+First, the authors have not replicated all of Claassen's main results.
+Claassen 2020a argues that within-country analyses are desirable and uses generalized method of moments (GMM) estimators to obtain these.
+Claassen (2020b) uses first difference models; he also focuses on the separate effects of the electoral and liberal components of democracy.
+I suggest that the authors replicate all the main results from Claassen (2020a; 2020b), rather than an ad hoc subset of these.
+
+[Issue 18](https://github.com/fsolt/dcpo_dem_mood/issues/18) Second, in addition to the results obtained from the latent variable model developed and used by Claassen, the authors present the results obtained from an entirely different latent variable model.
+Although intriguing, no evidence at all is presented to support the claim (repeated throughout) that this method is "superior" to Claassen's (reference is made to an unpublished working paper).
+Indeed, it would appear from the short summary of this model that it adds additional parameters to Claassen's model.
+Yet more complicated models may overfit the data and are not necessarily more accurate.
+I propose that evidence supporting the superiority of this method be supplied, or alternatively, the authors just focus on replicating Claassen's models.
+
 ## Reviewer #2
@@
 How does it perform when measurement error is strongly correlated across variables, as is likely to be the case in the models with lagged DVs?
+
 [Issue 23](https://github.com/fsolt/dcpo_dem_mood/issues/23) It would be useful to show that the critique still holds with an alternative measurement-error approach, such as Treier and Jackman's (2008) method of composition.
-## Reviewer #4
-[Issue 17](https://github.com/fsolt/dcpo_dem_mood/issues/17) We need more information on (1) how uncertainty is integrated into the models of Claassen, and (2) the DCPO models.
 
-## Response 
-Both Reviewers 1 & 2 concern the validity of the approach used to incorporate measurement uncertainty.
-First, we added more explanations of how uncertainty is integrated into the models on Page xx of the main text and presented equations on Page xx in SI.
-Rubin's rule is indeed designed to address missing values by using multiple imputations (MI).
-However, as Reviewer 2 has already pointed out, @Blackwell2017 applied the logic of MI and Rubin's rule in their Multiple Overimputation (P309) to address measurement error and missing data, which is conceptualized as an extreme case of measurement error.
+[Issue 16](https://github.com/fsolt/dcpo_dem_mood/issues/16) Despite the MS's assertion of the "absolute necessity" of accounting for measurement error, the MS does not do so for any of the other variables in the analysis.
+Given that Treier and Jackman's analysis focused on uncertainty in measures of democracy, the most obvious omission is the V-DEM democracy measure itself (which, according to the V-DEM documentation, does appear to have associated uncertainty estimates).
 
-The idea of our approach for propagating uncertainty is correcting both within and between imputation variance through Rubin's rule, and the idea of MOC is accounting for within imputation variance through drawing samples from the joint posterior distribution of the measurement and analysis model.
-
-To address the performance of the method we used, we employed the "method of component" as an alternative way in SI.
-Our approach and MOC yield similar results from replicating APSR's analysis, that is, when uncertainty is allowed, the coefficients on the lagged public support and the change of democratic level are no longer distinguishable from zero in Page xx in MS and Page xx in SI.
-It is not surprising that the estimated effect of democracy is indistinguishable from zero given measurement errors in both democracy and democratic support measurements and cultural features of democratic values.
-As Reviewer3 pointed out, democratic value is formed and shaped by institution, history, and culture, and the cultural feature of democratic value determines that it cannot be impacted swiftly by the change of democracy.
-
-Our approach and MOC yield mixed results for AJPS's analysis.
-
-In terms of the impact of measurement error on estimated effects, many studies have shown that when taking measurement uncertainty into account, the magnitude of coefficients of latent variables can be either attenuated or enlarged substantively [e.g., @Treier2008, p.
-211; @caughey2018,p.
-254].
-
-# The Change of Democratic Support and Lagged Support
-
-## Reviewer #1
-[Issue 24](https://github.com/fsolt/dcpo_dem_mood/issues/23) Second, the results in Figure 2, based on models using democratic support as a dependent variable, are puzzling.
-They appear to show that democratic support is entirely disconnected from such prominent features of the political environment as the level of democracy and economic development.
-Not only are these effects insignificant, but their point estimates are almost exactly zero in magnitude.
-The effects of lagged democratic support are also zero, which is even more implausible because it suggests that democratic support in one year is entirely disconnected from its levels in previous years.
-In other words, Denmark is as likely to have a low value next year as China is likely to have a high value.
-This stands in contrast with much of existing research on democratic support and political culture.
-
-## Reviewer #2
 [Issue 24](https://github.com/fsolt/dcpo_dem_mood/issues/24) Also, I could not help but be struck by the extreme attenuation of the coefficient estimates in Figure 2, which almost suggest that the variables were generated from independent distributions.
@@
 
-## Reviewer #4
-[Issue 15](https://github.com/fsolt/dcpo_dem_mood/issues/15) Second, I was a bit confused by Figures 1 and 2.
-My understanding is that accounting for uncertainty should only affect the standard errors, but in the figures it also affects the point estimates.
-This is the case even in the models 'Claassen W/Uncertainty.'
-
-## Response
-
-First, we need to clarify that the DV in Figure2 is the change of public support for democracy rather than current public support.
-Second, when DV is the change of public support, Claassen's original results would not make any sense. 
-Claassen's original results indicate the change of public support in one year is positively changed by the public support in the previous year and negatively shifted by the previous two years.
-However, should we expect that public support can produce its demand and especially a conflicting demand?
-Can high public support this year ask for a change next year but resist a change in the next two years?
-In contrast, our null results of lagged support on change of support mood make more sense since the change of moods is supposed to be shaped by exogenous factors, such as democratic or economic environment, or especially a shock.
-Unfortunately, after acknowledging uncertainty, the estimated effect of the change of democracy is indistinguishable from zero, and the magnitude of the coefficient also moves to zero.
-As @Treier2008 emphasized, only in applications where democracy has a strong effect on the quantity of interest and models are simple enough, accounting of uncertainty rarely renders the insignificant effect of democracy.
-However, even in Claassen's original results, the estimated effects of both the change of democracy and other social and economic factors are minor.
-Given the measurement errors in both democratic indices and public support, it is not surprising to see the diminution of the estimated effects.
-
-# Test Full Models 
-## Reviewer #1
-[Issue 22](https://github.com/fsolt/dcpo_dem_mood/issues/22) I have two additional concerns with the paper.
-First, the authors have not replicated all of Claassen's main results.
-Claassen 2020a argues that within-country analyses are desirable and uses generalized method of moments (GMM) estimators to obtain these.
-Claassen (2020b) uses first difference models; he also focuses on the separate effects of the electoral and liberal components of democracy.
-I suggest that the authors replicate all the main results from Claassen (2020a; 2020b), rather than an ad hoc subset of these.
-
-## Response
-In contrast, our null results of lagged support on change of support mood make more sense since the change of moods is supposed to be shaped by exogenous factors, such as democratic or economic environment, or especially a shock.
-Unfortunately, after acknowledging uncertainty, the estimated effect of the change of democracy is indistinguishable from zero, and the magnitude of the coefficient also moves to zero.
-As @Treier2008 emphasized, only in applications where democracy has a strong effect on the quantity of interest and models are simple enough, accounting of uncertainty rarely renders the insignificant effect of democracy.
-However, even in Claassen's original results, the estimated effects of both the change of democracy and other social and economic factors are minor.
-Given the measurement errors in both democratic indices and public support, it is not surprising to see the diminution of the estimated effects.
-
-# Justification of DCPO 
-## Reviewer #1
-[Issue 18](https://github.com/fsolt/dcpo_dem_mood/issues/18) Second, in addition to the results obtained from the latent variable model developed and used by Claassen, the authors present the results obtained from an entirely different latent variable model.
-Although intriguing, no evidence at all is presented to support the claim (repeated throughout) that this method is "superior" to Claassen's (reference is made to an unpublished working paper).
-Indeed, it would appear from the short summary of this model that it adds additional parameters to Claassen's model.
-Yet more complicated models may overfit the data and are not necessarily more accurate.
-I propose that evidence supporting the superiority of this method be supplied, or alternatively, the authors just focus on replicating Claassen's models.
-## Reviewer #2
 [Issue 20](https://github.com/fsolt/dcpo_dem_mood/issues/20) Finally, I am concerned about the over-time smoothing induced by the random-walk prior in measurement model.
@@
 There is no magic fix for this problem, but readers should still be given more information on how much "work" the prior is doing—what proportion of country-years are missing data, how informative is the prior relative to the likelihood, and so on.
-## Reviewer #4
-[Issue 18](https://github.com/fsolt/dcpo_dem_mood/issues/18) Third, the author should provide more information on the differences between the models employed by Claassen and those that she/he employs (perhaps in an appendix).
 
-## Response
-Thanks to editor's suggesions, we do agree that we should present and assess the effect of intermediate modification in an incremental way.
-To do this, in the revised manuscript, we replicated Claassen's measure for public democratic support by applying his measurement Model5 to his original data file and used the posterior distribution of the public support estimates to incorporated uncertainty.
-Then, we added more survey data to improve the quality of source data and applied Model5 to this expanded data set, still keeping the full posterior distribution of estimates. 
-In this way, we isolate the effects of measurement uncertainty and more data. 
-In the APSR analyses, it is uncertainty that accounts for the disappearing significance of public support.
-
-# Substantive Discussion
-## Reviewer #4
-
-[Issue 19](https://github.com/fsolt/dcpo_dem_mood/issues/19) First, I found the 'Discussion' section somewhat underwhelming.
-The discussion is mainly about data issues that could explain the lack of a relationship, not the substantive question.
-If that is the case, the letter makes a negligible contribution because it only finds that the findings of two specific studies are not robust (not that there is no relationship between public support for democracy and regime survival).
-I would like the author to engage a bit more in substantive debates.
-
-## Response
-Since we do acknowledge uncertainty in extant measurements, we can not unambigously make a statement that there is no relationship between public support and regime survival although it is possible.
-Examing theories in different contexts overtime is a promising strategy for generalization [KKV].
-However, scholars' pursue on models usually lead to the ignorance for measurements which cost more time but determine the quality of data in analyses [@stegmueller2011].
-In this letter, we stress the necessity of incorporating measurement uncertainty in analyses with latent variables and encourage scholars to pay more attention on that.
-
-# Compliement
 ## Reviewer #3
@@
 Although I am quite confident that policy preferences and policy change react thermostatically to each other in yearly rhythms, I find it hard to believe that such fundamental things as regime preferences and regime qualities underly such short-term cycles.
-Regime preferences and regime qualities are more enduring, inert and their changes are too glacial for a thermostatic model of short-term cycles to *plausibly capture the underlying dynamic in the co-evolution of public opinion and regime qualities.
-Since Claassen uses V-Dem data to measure democratic regime qualities, which are entirely expert judgements, his models demonstrate at best that expert and lay assessments of democracy react thermostatically to each other.*
+Regime preferences and regime qualities are more enduring, inert and their changes are too glacial for a thermostatic model of short-term cycles to plausibly capture the underlying dynamic in the co-evolution of public opinion and regime qualities.
+Since Claassen uses V-Dem data to measure democratic regime qualities, which are entirely expert judgements, his models demonstrate at best that expert and lay assessments of democracy react thermostatically to each other.
 
@@
 
+## Reviewer #4
+
+[Issue 19](https://github.com/fsolt/dcpo_dem_mood/issues/19) First, I found the 'Discussion' section somewhat underwhelming.
+The discussion is mainly about data issues that could explain the lack of a relationship, not the substantive question.
+If that is the case, the letter makes a negligible contribution because it only finds that the findings of two specific studies are not robust (not that there is no relationship between public support for democracy and regime survival).
+I would like the author to engage a bit more in substantive debates.
+
+[Issue 15](https://github.com/fsolt/dcpo_dem_mood/issues/15) Second, I was a bit confused by Figures 1 and 2.
+My understanding is that accounting for uncertainty should only affect the standard errors, but in the figures it also affects the point estimates.
+This is the case even in the models 'Claassen W/Uncertainty.'
+
+Reviewer 4 raised the question of whether accounting for uncertainty should affect the point estimates at all, rather than simply inflating the standard errors (a concern perhaps also raised indirectly by Reviewers 1 and 2).
+
+[Issue 18](https://github.com/fsolt/dcpo_dem_mood/issues/18) Third, the author should provide more information on the differences between the models employed by Claassen and those that she/he employs (perhaps in an appendix).
+
+[Issue 17](https://github.com/fsolt/dcpo_dem_mood/issues/17) We need more information on (1) how uncertainty is integrated into the models of Claassen, and (2) the DCPO models.
+
 ## Editor
@@
 
-## Response
-We did not do a simulation study, instead we employ MOC suggested by Review 1 and 2 as a robust check and present results in SI. 
-We also elaborate the imputation process in details in MS and clarify the equations in SI.
-Measurement errors in other variables have been included in our rexaminations. 
-As for the concerns on Fig2, the first thing needing to clarify is that the DV is not current public support but the change of public support. 
-We elaborate why our null results make more sense than Claassen's original results.
-
-## Editor
 Reviewers 1, 2, and 4 all ask why the results for Claassen's model but accounting for measurement error (second set of results) also yield different point estimates.
@@
 
-## Response
-It is a misunderstanding that incorporating uncertainty only changes standard error.
-First, incorporating uncertainty might or might not cause the changes of standard error.
-For example, standard errors did not change after accounting for uncerainty in [@caughey2018] but became smaller in [@Treier2008].
-Second, the propogation of uncertainty can either attentuate or magnify the magnitude of estimated effects.
-*We can cite more lit if neccessary*. 
-For transparcy and avoiding confusion, we only focus on uncertainty in revised version.
-
-## Editor
 Evidence to address these various methodological questions and issues issues may be included in the response to reviewers and/or the Supplemental Information (if it would help readers appreciate the methods used) as needed.
-*For instance, I could imagine some readers benefitting from having the estimating equations included in the Supplemental Information in order to appreciate how measurement error is incorporated into the estimates as well as more information about the levels of measurement used (mentioned as an important difference by Reviewer 3)*.
+For instance, I could imagine some readers benefitting from having the estimating equations included in the Supplemental Information in order to appreciate how measurement error is incorporated into the estimates as well as more information about the levels of measurement used (mentioned as an important difference by Reviewer 3).
 While Reviewer 1 asks for all results from the original two studies be replicated as well, these additional replications need only be included in the paper or SI to the extent that they are relevant to the relationship between support and democracy at the core of this Letter's focus.
@@
 
-## Response
-We might need to review the functions added in SI.
-
-## Editor
 Finally, Reviewers 2, 3, and 4 offer various suggestions for how to more effectively frame or discuss the substantive or theoretical (rather than measurement or methodological) implications of your contribution.
 We hope their feedback is useful as you revise your Letter.
-
-## Response
 

### 2021-07-24 R/cls_correct_ajpsapsr.R
create expanded and corrected cls's analysis data

@@ -14,6 +14,9 @@ p_load(
 #osf_retrieve_file("kg7z4") %>%
 #     osf_download(here::here("data"))  ##pure corrected
 
+osf_retrieve_file("gk7nu") %>%
+     osf_download(here::here("data"))  ##corrected + expanded
+
 
 # Functions preload
 set.seed(313)
@@ -206,158 +209,143 @@ osf_upload(demsup, c(here("data","correct_cls_ajps.rda")))
 
 
 ###############Expanded_Claassen and Analysis Data##################
-###############Input:  correctexp_claassen_m5 ############################
-##############Output: correctexp_cls_theta_list ############################
-exp_claassen_m5_theta <- rstan::extract(exp_claassen_m5, pars = "theta")
+###############Input:  exp_claassen_m5_3k_07-23-10-50.rda ############################
+##############Output: expcor_cls_theta_list ############################
 
-ls_year <- 1988:2017
-ls_country <- expanded_claassen_input$data$country %>% unique()
-first_year <- min(expanded_claassen_input$data$year)
+load(here("data", "exp_claassen_m5_3k_07-23-10-50.rda")) 
+load(here("data","exp_claassen_input.rda"))
+load(here("data","dcpo_ajps_cntrl.rda"))
+load(here("data","dcpo_apsr_cntrl.rda"))
+
+reformat_dcpo_output <- function(x, parameter_name) {
+    df_temp <- x %>% 
+        as_tibble(.name_repair = ~ls_country) %>%
+        mutate(year = first_year + row_number() - 1) %>% 
+        pivot_longer(cols = all_of(ls_country),
+                     names_to = "country",
+                     values_to = parameter_name) %>%
+        arrange(country, year)
+    return(df_temp)
+}
+
+exp_claassen_m5_theta <- rstan::extract(claassen_m5, pars = "theta")
+
+ls_year <- 1988:2020
+ls_country <- exp_claassen_input$data$country %>% unique() #145
+first_year <- min(exp_claassen_input$data$year) #1988
 
 
-exp_cls_theta_list <- purrr::map(1:900, function(anEntry) {
+expcor_cls_theta_list <- purrr::map(1:900, function(anEntry) {
     exp_claassen_m5_theta$theta[anEntry,,] %>%
         reformat_dcpo_output("theta") 
 }
 )
[…]

### 2021-07-24 R/cls_correct_ajpsapsr.R
adjust variable names in expanded data to be consistent with the names in models.

@@ -43,7 +43,8 @@ claassen_m5_theta <- rstan::extract(claassen_m5, pars = "theta")  ##derived from
 #cnt.names = as.character(sort(unique(sddem2$Country)))
 
 
-claassen_replication <- readRDS(here::here("data","claassen_replication.rds")) %>% 
+#claassen_replication <- readRDS(here::here("data","claassen_replication.rds")) %>% 
+claassen_replication <- readRDS(here::here("data","claassen_replication_input.rda")) %>%
     janitor::clean_names() %>% 
     DCPOtools::with_min_yrs(2) 
 ##need to use claassen_replication.rds. remember to mention which country is missing
@@ -274,6 +275,27 @@ expcor_cls_ajps <- purrr::map(1:900, function(anEntry) {
 }) 
 
 
+expcor_cls_ajps <- purrr::map(1:900, function(anEntry) {
+    expcor_cls_ajps[[anEntry]] %>% 
+            rename(SupDem_trim = theta_trim,
+                   Regime_VD = Vdem_regime,
+                   Pr_Muslim = muslism_prop_2010,
+                   Res_cp_WDI_di = dependence_pc_di,
+                   lnGDP_imp = lg_imp_mdpgdp,
+                   GDP_imp_grth = mdprgdp_grwth,
+                   Regime_VD = Vdem_regime,
+                   firstyear = first_year,
+                   Libdem_VD = Vdem_libdem,
+                   Libdem_m1 = Vdem_libdem_m1,
+                   Libdem_m2 = Vdem_libdem_m2,
+                   ChgDem = Chgdem,
+                   UpChgDem = upchgdem,
+                   DwnChgDem = downchgdem,
+                   Libdem_regUN = Region_libdem,
+                   Libdem_regUN_m1 = Region_libdem_m1,) 
+    })  ##adjust names to be consistent with correct_cls_ajps
+
+
 save(expcor_cls_ajps, file = here::here("data","expcor_cls_ajps.rda"))
 
 ################################################################
@@ -339,6 +361,23 @@ expcor_cls_apsr <- purrr::map(1:900, function(anEntry) {
         select(country, year, first_year,theta, theta_trim, contains("z"),everything())
 }) 
 
+colnames(correct_cls_apsr[[1]])
+colnames(expcor_cls_apsr[[1]])
+
[…]

### 2021-07-24 paper/dcpo_demsupport.Rmd
update moc models with expanded and corrected data.

@@
 load(here("data", "correct_cls_apsr.rda")) 
-load(here("data", "exp_cls_ajps.rda"))
-load(here("data", "exp_cls_apsr.rda"))
+#load(here("data", "exp_cls_ajps.rda"))
+#load(here("data", "exp_cls_apsr.rda")) 
+load(here("data", "expcor_cls_ajps.rda"))
+load(here("data", "expcor_cls_apsr.rda"))
 
@@
 
-mocresult_pureAJPS <- readRDS(here("output", "estimates_moc_pureAJPS.RDS"))
-mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expAJPS.RDS"))
-mocresult_pureAPSR <- readRDS(here("output", "estimates_moc_pureAPSR.RDS"))
-mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expAPSR.RDS"))
+#mocresult_pureAJPS <- readRDS(here("output", "estimates_moc_pureAJPS.RDS"))
+mocresult_correctAJPS <- readRDS(here("output", "estimates_moc_correctAJPS.RDS")) 
+#mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expAJPS.RDS"))
+mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expcorAJPS.RDS"))
+#mocresult_pureAPSR <- readRDS(here("output", "estimates_moc_pureAPSR.RDS"))
+mocresult_correctAPSR <- readRDS(here("output", "estimates_moc_correctAPSR.RDS"))
+#mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expAPSR.RDS"))
+mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expcorAPSR.RDS"))
 
@@
 df_exp_clsAjps <- purrr::map(1:900, function(anEntry) {
-  exp_cls_ajps[[anEntry]] %>% 
+  expcor_cls_ajps[[anEntry]] %>% 
     plm::pdata.frame(index = c("country", "year"))
@@
 
-saveRDS(mocresult_expAJPS, file =here("output","estimates_moc_expAJPS.RDS"))
+saveRDS(mocresult_expAJPS, file =here("output","estimates_moc_expcorAJPS.RDS"))
 
@@
 #df_exp_clsAPSR <- purrr::map(1:900, function(anEntry) {
-#  exp_cls_apsr[[anEntry]] %>% 
+#  expcor_cls_apsr[[anEntry]] %>% 
 #    plm::pdata.frame(index = c("country", "year"))
@@
 
-```
-
-```{r mocresult-expAPSR}
-
 df_exp_clsAPSR <- purrr::map(1:900, function(anEntry) {
-  exp_cls_apsr[[anEntry]] %>% 
+  expcor_cls_apsr[[anEntry]] %>% 
     plm::pdata.frame(index = c("country", "year"))
@@
 
-saveRDS(mocresult_expAPSR, file = here::here("ouput","estimates_moc_expAPSR.RDS"))
+saveRDS(mocresult_expAPSR, file = here::here("ouput","estimates_moc_expcorAPSR.RDS"))
 

### 2021-07-26 paper/dcpo_demsupport.Rmd
new output code revised

@@
 
-#load(here("data", "pure_cls_ajps.rda")) 
-#load(here("data", "pure_cls_apsr.rda")) 
 load(here("data", "correct_cls_ajps.rda"))
 load(here("data", "correct_cls_apsr.rda")) 
-#load(here("data", "exp_cls_ajps.rda"))
-#load(here("data", "exp_cls_apsr.rda")) 
 load(here("data", "expcor_cls_ajps.rda"))
@@
 result_expAJPS <- readRDS(here("output", "estimates_clsExpAJPS.RDS"))
-
 result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
@@
 
-#mocresult_pureAJPS <- readRDS(here("output", "estimates_moc_pureAJPS.RDS"))
 mocresult_correctAJPS <- readRDS(here("output", "estimates_moc_correctAJPS.RDS")) 
-#mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expAJPS.RDS"))
 mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expcorAJPS.RDS"))
-#mocresult_pureAPSR <- readRDS(here("output", "estimates_moc_pureAPSR.RDS"))
 mocresult_correctAPSR <- readRDS(here("output", "estimates_moc_correctAPSR.RDS"))
-#mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expAPSR.RDS"))
 mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expcorAPSR.RDS"))
@@
 
+[XXXX This paragraph should be revised]
 In addition to incorporating uncertainty, we also assembled as much available data on democratic support as possible. 
@@
 result_pureAJPS <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
-  result <- map(pure_cls_ajps, function(aData){ # applying to the 1000 datasets
+  result <- map(correct_cls_ajps, function(aData){ # applying to the 1000 datasets
     eval(parse(text = aMod))
@@
 result_expAJPS <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
-  result <- map(exp_cls_ajps, function(aData){ # applying to the 1000 datasets
+  result <- map(expcor_cls_ajps, function(aData){ # applying to the 1000 datasets
     eval(parse(text = aMod))
@@
 result_pureAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
-  result <- map(pure_cls_apsr, function(aData){ # applying to the 900 datasets
+  result <- map(correct_cls_apsr, function(aData){ # applying to the 900 datasets
     eval(parse(text = aMod))
@@
 result_expAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
-  result <- map(exp_cls_apsr, function(aData){ # applying to the 1000 datasets
+  result <- map(expcor_cls_apsr, function(aData){ # applying to the 1000 datasets
     eval(parse(text = aMod))
@@
   "plm::lag(SupDem_Autoc, 1)" = "Support in Autocracy",
-  "plm::lag(lnGDP_imp, 1)" = "Log~GDP~per~capita[t-1]",
-  "plm::lag(GDP_imp_grth, 1)"  = "GDP~per~capita~growth[t-1]",
-  "plm::lag(Libdem_regUN, 1)" = "Regional~democracy[t-1]",
-  "plm::lag(Pr_Muslim, 1)" = "Percent~Muslim[t-1]",
-  "plm::lag(Res_cp_WDI_di, 1)" = "Resource~dependence[t-1]"
+  "plm::lag(lnGDP_imp, 1)" = "Log GDP Per Capita[t-1]",
+  "plm::lag(GDP_imp_grth, 1)"  = "GDP Per Capita~growth[t-1]",
+  "plm::lag(Libdem_regUN, 1)" = "Regional Democracy[t-1]",
+  "plm::lag(Pr_Muslim, 1)" = "Percent Muslim[t-1]",
+  "plm::lag(Res_cp_WDI_di, 1)" = "Resource Dependence[t-1]"
 )
@@
   "(Intercept)" = "(Intercept)",
-  "plm::lag(SupDem_trim, 1:2)1" = "Democratic\n Mood\n (t-1)",
-  "plm::lag(SupDem_trim, 1:2)2" = "Democratic\n Mood\n (t-2)",
-  "diff(Libdem_z, lag = 1)" = "Liberal\n Democracy\n (Difference)",
-  "Libdem_z" = "Liberal\n Democracy\n (Difference)",
-  "plm::lag(Libdem_z, 1)" = "Liberal\n Democracy\n (t-1)",
-  "diff(Polyarchy_z, lag = 1)" = "Electoral\n Democracy\n (Difference)",
-  "Polyarchy_z" = "Electoral\n Democracy\n (Difference)",
-  "plm::lag(Polyarchy_z, 1)" = "Electoral\n Democracy\n (t-1)",
-  "diff(Liberal_z, lag = 1)" = "Minoritarian\n Democracy\n (Difference)",
-  "Liberal_z" = "Minoritarian\n Democracy\n (Difference)",
-  "plm::lag(Liberal_z, 1)" = "Minoritarian\n Democracy\n (t-1)",
-  "diff(lnGDP_imp, lag = 1)" = "Log GDP\n per capita\n (Difference)",
-  "lnGDP_imp" = "Log GDP\n per capita\n (Difference)",
-  "plm::lag(lnGDP_imp, 1)" = "Log GDP\n (t-1)",
-  "diff(Corrup_TI_z, lag = 1)" = "Corruption\n (Difference)",
-  "Corrup_TI_z" = "Corruption\n (Difference)",
-  "plm::lag(Corrup_TI_z, 1)" = "Corruption\n (t-1)"
+  "plm::lag(SupDem_trim, 1:2)1" = "Democratic Mood (t-1)",
+  "plm::lag(SupDem_trim, 1:2)2" = "Democratic Mood (t-2)",
+  "diff(Libdem_z, lag = 1)" = "Liberal Democracy (Difference)",
+  "Libdem_z" = "Liberal Democracy (Difference)",
+  "plm::lag(Libdem_z, 1)" = "Liberal Democracy (t-1)",
+  "diff(Polyarchy_z, lag = 1)" = "Electoral Democracy (Difference)",
+  "Polyarchy_z" = "Electoral Democracy (Difference)",
+  "plm::lag(Polyarchy_z, 1)" = "Electoral Democracy (t-1)",
+  "diff(Liberal_z, lag = 1)" = "Minoritarian Democracy (Difference)",
+  "Liberal_z" = "Minoritarian Democracy (Difference)",
+  "plm::lag(Liberal_z, 1)" = "Minoritarian Democracy (t-1)",
+  "diff(lnGDP_imp, lag = 1)" = "Log GDP per capita (Difference)",
+  "lnGDP_imp" = "Log GDP per capita (Difference)",
+  "plm::lag(lnGDP_imp, 1)" = "Log GDP (t-1)",
+  "diff(Corrup_TI_z, lag = 1)" = "Corruption (Difference)",
+  "Corrup_TI_z" = "Corruption (Difference)",
+  "plm::lag(Corrup_TI_z, 1)" = "Corruption (t-1)"
 )
@@
 #df_pure_clsAjps <- purrr::map(1:900, function(anEntry) {
-#  pure_cls_ajps[[anEntry]] %>% 
+#  correct_cls_ajps[[anEntry]] %>% 
 #    plm::pdata.frame(index = c("country", "year"))
@@
   scale_y_discrete(labels = parse(text = levels(terms))) +
-  scale_color_grey(start = 0.4, end = 0.8) +
   labs(
@@
   scale_y_discrete(labels = parse(text = levels(terms2))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
   labs(
@@
 #df_pure_clsAPSR <- purrr::map(1:900, function(anEntry) {
-#  pure_cls_apsr[[anEntry]] %>% 
+#  correct_cls_apsr[[anEntry]] %>% 
 #    plm::pdata.frame(index = c("country", "year"))
@@
 
-```{r plot-mocAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", eval = TRUE, fig.width=7, fig.height=10, eval=TRUE}
+```{r plot-mocAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", eval = TRUE, fig.width=7, fig.height=12, eval=TRUE}
 
@@
   scale_y_discrete(labels = parse(text = levels(terms1))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  # scale_color_uiowa(name = "", palette = "digitMixed") +
   labs(
@@
   scale_y_discrete(labels = parse(text = levels(terms3))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  # scale_color_uiowa(name = "", palette = "digitMixed") +
   labs(
@@
   scale_y_discrete(labels = parse(text = levels(terms2))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
-  # scale_color_uiowa(name = "", palette = "digitMixed") +
   labs(
@@
   scale_y_discrete(labels = parse(text = levels(terms4))) +
-  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
   labs(

### 2021-07-27 R/claassen_replication_input.R
claassen_replication_input (now) has 5 fewer observations than supdem (3 are no longer available and 2 seem to have never existed) and 1 more survey item (Claassen conflates two ArabBarometer items with different response categories) 👀@TyhCass

@@ -1,0 +1,200 @@
+library(tidyverse)
+library(DCPOtools)
+
+# dcpo_input_raw <- DCPOtools::dcpo_setup(vars = read_csv(here::here("data-raw", "mood_dem.csv"),
+#                                                         col_types = "cccccc"),
+#                                         file = "data/dcpo_input_raw.csv")
+
+dcpo_input_raw1 <- read_csv(here::here("data", "dcpo_input_raw.csv"), col_types = "cdcddcd") %>% 
+    filter(!(str_detect(survey, "army_wvs") & # WVS obs identified as problematic by Claassen 
+                 ((country=="Albania" & year==1998) |
+                      (country=="Indonesia" & (year==2001 | year==2006)) |
+                      (country=="Iran" & year==2000) |
+                      (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
+                      (country=="Vietnam" & year==2001)) |
+                 (str_detect(item, "strong_wvs") &
+                      ((country=="Egypt" & year==2012) |
+                           (country=="Iran" & (year==2000 | year==2007)) | # 2005 in Claassen
+                           (country=="India") |
+                           (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
+                           (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
+                           (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
+                           (country=="Vietnam" & year==2001))) |
+                 (country %in% c("Puerto Rico", "Northern Ireland", 
+                                 "SrpSka Republic", "Hong Kong SAR China")))) %>%
+    with_min_yrs(2)
+
+# Note that before running `dataverse::get_file()` below, one should set their personal token and server in their system environment first: 
+# Sys.setenv("DATAVERSE_KEY" = "exampleToken")
+# Sys.setenv("DATAVERSE_SERVER" = "dataverse.harvard.edu")
+# These values can be set to persist across R sessions using `usethis::edit_r_environ()`
+
+if (!file.exists(here::here("data", "supdem raw survey marginals.tab"))) {
+    tempfile <- dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") # AJPS replication file
+    
+    writeBin(tempfile, here::here("data", "supdem raw survey marginals.tab"))
+}
+
[…]

### 2021-07-27 paper/dcpo_demsupport.Rmd

@@
 
-Following this line, after replicating the original analyses with point estimates, we take the distribution of the latent variable, the dependent variable, and control variables to account for the uncertainty from the measurement model as well as dependent and control variables.
-To do this, we take 900 draws from the distribution of public democratic support and corruption index, duplicate each article's analysis dataset of variables without “measurement error” 900 times, and assign them to each a different random draw from the posterior distribution of democracy indices.
+Following this line, after replicating the original analyses with point estimates, we take the distribution of the latent (explanatory) variable, the outcome variable, and control variables to account for the uncertainty from the measurement model as well as outcome and control variables.
+We take 900 draws from the distribution of public democratic support, duplicate each article's analysis dataset of variables without "measurement error" 900 times, and assign them to each a different random draw from the posterior distribution of democracy indices.
 We estimate each analysis model repeatedly on its respective collection of the datasets, and then make inferences from the distribution of parameter estimates by accounting for both within model standard error and between model variance.
@@
 @Blackwell2017a's multiple overimputation (MO) uses the same logic to correct sampling variance.
-We also employ one alternative technique known as “method of composition” (MOC)  [@Treier2008, p. 215] as a robustness check [see the Online Supplementary Material \@ref(moc)].
+We also employ one alternative technique known as "method of composition" (MOC)  [@Treier2008, p. 215] as a robustness check [see Online Supplementary Material \@ref(moc)].
 
@@
 
-[XXXX This paragraph should be revised]
-In addition to incorporating uncertainty, we also assembled as much available data on democratic support as possible. 
-We employed `r dcpo_input_ncyi` national opinions on democracy from `r dcpo_input_surv` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncy` opinions and `r supdem_surv` national surveys used in Claassen [-@Claassen2020a; -@Claassen2020b].^[These figures represent the survey data actually used in estimating public support for democracy; as in Claassen [-@Claassen2020a; -@Claassen2020b], countries for which two separate years of survey data were not available were excluded.]
-
-A noteworthy point is that in addition to account for uncertainty in latent variable estimates, we also include the measurement uncertainty in democracy indices and corruption index. 
-We extracted the posterior distributions of democratic indices, including Liberal Democracy,  polyarchy, and electoral democracy index, which are provided by [@coppedge2018]. 
+<!-- This paragraph should be revised. -->
+In addition to incorporating uncertainty, we expanded Claassen's data pool assembling as much data on democratic support as possible from available opinion surveys around the world. 
+The expansion ended with `r dcpo_input_ncyi` national opinions on democracy from `r dcpo_input_surv` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncy` opinions and `r supdem_surv` national surveys used in Claassen [-@Claassen2020a; -@Claassen2020b].^[These figures represent the survey data actually used in estimating public support for democracy; as in Claassen [-@Claassen2020a; -@Claassen2020b], countries for which two separate years of survey data were not available were excluded.]
+
+Besides accounting for uncertainty in latent variable estimates, we also included the measurement uncertainty in democracy indices and corruption index. 
+We extracted the posterior distributions of democratic indices, including Liberal Democracy,polyarchy, and electoral democracy index, which are provided by [@coppedge2018]. 
 We drew 900 samples from the distribution of the Corruption Perception Index.^[Since Corruption Perception Index does not provide standard error before 2011, we imputed the missing standard error using the multiplication of a country's corruption index and the ratio of its available maximum standard error to its corresponding index.]
@@
 The middle results introduce the uncertainty in the measurement of public support into the model.
-The lowermost set presents the results estimated with the expanded data.
+And the lowermost set presents the results estimated with the expanded data.
 
@@
 This result is robust when using separated regime types in the explanatory variable. 
-The estimation based on MOC yields mixed results.
-In pooled OLS models, the public support estimated from the originial data with uncertainty is significant for the whole data and split databut the support estimated from the expanded data is not.
-In system GMM models which are more appropriate in this case than pooled OLS models, public support estimated from the original data reached the threshold of significance within democratic regimes. 
-The estimated support with the expanded data is not significant in GMM models.
-
-Using the same models and the measurement, the support estimate from a more qualified data yields insignificant results. 
-This undermines the reliability of significant results from the estimate using the original data.^[In fact, when we further improve the estimate and reduce the uncertainty by applying a more superior measurement model, the relationship between public support and democratic survival disappears.]
-
-At the same time, the results also shows that ignoring uncertainty may lead to misestimation of the point effect as well. 
-In the case here, the point estimates of democracy support are notably larger than the original estimate for both model settings. 
-We draw variable values from their distributions and estimate the coefficient first before combining through Rubin's rule.
-The deviation of the result from the original one indicates the coefficient (point) estimates were not that consistent.
-In other words, the estimates based on the mean values of variables cannot fully reflect their characteristics and relations at all.
-Only when the uncertainty is accounted, their effect can be more properly estimated.
+Nor do applying system GMM models and using alternative methods for uncertainty incorporation methods alters the conclusion (see Online Supplementary Material \@ref(fullAJPS), \@ref(fullAPSR), and \@ref(moc)).
+
+Adding more data is indeed helpful for increasing the certainty to the analytic estimates. 
+The confidence intervals of the explanatory variable (and some control variables) are considerably narrower than the cases just bringing the uncertainty back---or even the original case when uncertainty was completely ignored.
+Nonetheless, the insignificance remains and is robust across different model specifications.
+
+Moreover, the results also manfiest another risk of ignoring uncertainty: missestimation. 
+As shown in Figure \@ref(fig:plot-mainAJPS), besides the confidence intervals the (point) estimates also shift. 
+Methodologically, these shifts indicates that the 900 regressions of public support on democracy do not yield consistent results although the support opinions were drawn from the same distribution. 
+In this sense, the coefficient produced simply by the mean of the public support distribution is no more than a one-time guess of the true parameter and definitely not a robust one. 
+What this methodological issue lead to, however, is a substantively different conclusion of the relationship between public opinions and institutional democratization in both direction and magnitude.
+The replication results illustrate the uncertainty ignorance with mounting risk.
 
@@
 In Figure \@ref(fig:plot-mainAPSR), we examine the thermostatic model of democratic support per @Claassen2020b [p. 47, Models 1.1 and 1.2]. 
-The negative coefficient estimates of change in liberal democracy in the top set of results, which do not take uncertainty into account, imply that democratic mood decreases as democracy increases and vice versa.
-However, the middle and bottom results demonstrate that this thermostatic effect, too, does not hold after the measurement uncertainty is accounted for. 
-And again, we observe the point estimates slides to the zero line.
-
-[A discussion about the support t-1]
+When the uncertainty is ignored, the coefficient of $\Delta$liberal democracy (the uppermost set), the yearly changes of the institutional feature is negative inferring that democratic mood decreases as democracy increases and vice versa.
+However, when the measurement uncertainty is properly accounted (the middle set), the point estimate shifts towards zero and the coefficient is no longer significant.
+More data (the lowermost set), again, only adjusts the confidence intervals but not direction nor significance.
 
@@
 # (APPENDIX) Appendix {-}
-# Numeric Results for Replicating Claassen 2020a
+# Numeric Results for Replicating Claassen 2020a {#fullAJPS}
 
@@
 
-# Numeric Results for Replicating Claassen 2020b
+# Numeric Results for Replicating Claassen 2020b {#fullAPSR}
 

### 2021-07-28 paper/dcpo_demsupport.Rmd

@@
 #     osf_download(path = "../data", conflicts = "overwrite")
+
+# osf_retrieve_file("52u7n") %>%
+#     osf_download(path = "../data", conflicts = "overwrite") #corrected ajps
+# osf_retrieve_file("2hwqg") %>%
+#     osf_download(path = "../data", conflicts = "overwrite") #corrected apsr
 
@@
 result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
-#mocresult_pureAJPS <- readRDS(here("output", "estimates_moc_pureAJPS.RDS"))
 mocresult_correctAJPS <- readRDS(here("output", "estimates_moc_correctAJPS.RDS"))
 mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expAJPS.RDS"))
-#mocresult_pureAPSR <- readRDS(here("output", "estimates_moc_pureAPSR.RDS"))
 mocresult_correctAPSR <- readRDS(here("output", "estimates_moc_correctAPSR.RDS"))
@@
   mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Original"),
- # mutate(MOCsumm(mocresult_pureAJPS[["pooled"]]), model = "Uncertainty"),
- mutate(MOCsumm(mocresult_correctAJPS[["pooled"]]), model = "Corrected"),
+ mutate(MOCsumm(mocresult_correctAJPS[["pooled"]]), model = "Uncertainty+Corrected"),
  mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), model = "Uncertainty+Expanded Data")
@@
   mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Original"),
-  #mutate(MOCsumm(mocresult_pureAJPS[["gmm"]]), model = "Uncertainty"),
-  mutate(MOCsumm(mocresult_correctAJPS[["gmm"]]), model = "Corrected"),
+  mutate(MOCsumm(mocresult_correctAJPS[["gmm"]]), model = "Uncertainty+Corrected"),
   mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), model = "Uncertainty+Expanded Data")
@@
     type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Original", "Corrected", "Uncertainty+Expanded Data")))
+    model = factor(model, levels = c("Original", "Uncertainty+Corrected", "Uncertainty+Expanded Data")))
 
@@
   mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Original"),
-  #mutate(MOCsumm(mocresult_pureAJPS[["pooled-regime"]]), model = "Uncertainty"),
-  mutate(MOCsumm(mocresult_correctAJPS[["pooled-regime"]]), model = "Corrected"),
+  mutate(MOCsumm(mocresult_correctAJPS[["pooled-regime"]]), model = "Uncertainty+Corrected"),
   mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), model = "Uncertainty+Expanded Data")
@@
   mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Original"),
-  #mutate(MOCsumm(mocresult_pureAJPS[["gmm-regime"]]), model = "Uncertainty"),
-  mutate(MOCsumm(mocresult_correctAJPS[["gmm-regime"]]), model = "Corrected"),
+  mutate(MOCsumm(mocresult_correctAJPS[["gmm-regime"]]), model = "Uncertainty+Corrected"),
  mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), model = "Uncertainty+Expanded Data")
@@
     type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Original","Corrected", "Uncertainty+Expanded Data")))
+    model = factor(model, levels = c("Original","Uncertainty+Corrected", "Uncertainty+Expanded Data")))
 terms2 <- factor(rev(c("Democracy[t-1]",
@@
   mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], model = "Original"),
-  #mutate(MOCsumm2(mocresult_pureAPSR[["pooled1"]]), model = "Uncertainty"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["pooled1"]]), model = "Corrected"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["pooled1"]]), model = "Uncertainty+Corrected"),
   mutate(MOCsumm2(mocresult_expAPSR[["pooled1"]]), model = "Uncertainty+Expanded Data")
@@
   mutate(result_clsAPSR[["fd1"]][[1]][,1:3], model = "Original"),
-  #mutate(MOCsumm2(mocresult_pureAPSR[["fd1"]]), model = "Uncertainty"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["fd1"]]), model = "Corrected"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["fd1"]]), model = "Uncertainty+Corrected"),
   mutate(MOCsumm2(mocresult_expAPSR[["fd1"]]), model = "Uncertainty+Expanded Data")
@@
     type = factor(type,  levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Original","Corrected", "Uncertainty+Expanded Data"))
+    model = factor(model, levels = c("Original","Uncertainty+Corrected", "Uncertainty+Expanded Data"))
   )
@@
   mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], model = "Original"),
-  #mutate(MOCsumm2(mocresult_pureAPSR[["pooled-regime1"]]), model = "Uncertainty"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime1"]]), model = "Corrected"),
-
+  mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime1"]]), model = "Uncertainty+Corrected"),
   mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime1"]]), model = "Uncertainty+Expanded Data")
@@
   mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], model = "Original"),
-  #mutate(MOCsumm2(mocresult_pureAPSR[["fd-regime1"]]), model = "Uncertainty"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime1"]]), model = "Corrected"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime1"]]), model = "Uncertainty+Corrected"),
   mutate(MOCsumm2(mocresult_expAPSR[["fd-regime1"]]), model = "Uncertainty+Expanded Data")
@@
   mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], model = "Original"),
-  #mutate(MOCsumm2(mocresult_pureAPSR[["pooled2"]]), model = "Uncertainty"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["pooled2"]]), model = "Corrected"),
-
+  mutate(MOCsumm2(mocresult_correctAPSR[["pooled2"]]), model = "Uncertainty+Corrected"),
   mutate(MOCsumm2(mocresult_expAPSR[["pooled2"]]), model = "Uncertainty+Expanded Data")
@@
   mutate(result_clsAPSR[["fd2"]][[1]][,1:3], model = "Original"),
-  #mutate(MOCsumm2(mocresult_pureAPSR[["fd2"]]), model = "Uncertainty"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["fd2"]]), model = "Corrected"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["fd2"]]), model = "Uncertainty+Corrected"),
   mutate(MOCsumm2(mocresult_expAPSR[["fd2"]]), model = "Uncertainty+Expanded Data")
@@
   mutate(result_clsAPSR[["pooled-regime2"]][[1]][,1:3], model = "Original"),
- # mutate(MOCsumm2(mocresult_pureAPSR[["pooled-regime2"]]), model = "Uncertainty"),
- mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime2"]]), model = "Corrected"),
-
+ mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime2"]]), model = "Uncertainty+Corrected"),
   mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime2"]]), model = "Uncertainty+Expanded Data")) %>%
@@
   mutate(result_clsAPSR[["fd-regime2"]][[1]][,1:3], model = "Original"),
-  #mutate(MOCsumm2(mocresult_pureAPSR[["fd-regime2"]]), model = "Uncertainty"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime2"]]), model = "Corrected"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime2"]]), model = "Uncertainty+Corrected"),
   mutate(MOCsumm2(mocresult_expAPSR[["fd-regime2"]]), model = "Uncertainty+Expanded Data")) %>% 

### 2021-07-28 paper/dcpo_demsupport.Rmd

@@
 grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
+
 ```

### 2021-07-29 paper/dcpo_demsupport.Rmd
compile pdf @sammo3182

@@
 ```{r num-pointAJPS, results='asis', eval=TRUE}
-tb_result_cls <- map(result_clsAJPS, ~ {
+tb_result_cls <- purrr::map(result_clsAJPS, ~ {
   names(.) <- c("tidy", "glance")
@@
 ```{r num-pureAJPS, results='asis', eval=TRUE}
-tb_result_pureAJPS <- map(result_pureAJPS, ~ {
+tb_result_pureAJPS <- purrr::map(result_pureAJPS, ~ {
   names(.) <- c("tidy", "glance")
@@
 ```{r num-expAJPS, results='asis', eval=TRUE}
-tb_result_expAJPS <- map(result_expAJPS, ~ {
+tb_result_expAJPS <- purrr::map(result_expAJPS, ~ {
   names(.) <- c("tidy", "glance")
@@
 ```{r num-pureAPSR, results='asis', eval=TRUE}
-tb_result_pureAPSR <- map(result_pureAPSR, ~ {
+tb_result_pureAPSR <- purrr:::map(result_pureAPSR, ~ {
   names(.) <- c("tidy", "glance")
@@
 A common way to do so is using the mean of $theta$ as the point estimate, and the variance from the density as the standard error.
-
-```{r moc-estimates, eval=TRUE}
-
-result_clsAJPS <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
-result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
-mocresult_correctAJPS <- readRDS(here("output", "estimates_moc_correctAJPS.RDS"))
-mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expAJPS.RDS"))
-mocresult_correctAPSR <- readRDS(here("output", "estimates_moc_correctAPSR.RDS"))
-mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expAPSR.RDS"))
-
-```
 

### 2021-07-31 paper/dcpo_demsupport.Rmd
correct variable and model lables.

@@
 
-#df_pure_clsAjps <- purrr::map(1:900, function(anEntry) {
-#  correct_cls_ajps[[anEntry]] %>% 
-#    plm::pdata.frame(index = c("country", "year"))
-#})
-
-#result_pure_clsUncertain  <- map(ls_mod_ajpsCLS[1:2], function(aMod){
-#  result <- methodComposition1(df_pure_clsAjps,aMod)
-#})
-
-#names(result_pure_clsUncertain) <- c("pooled", "pooled-regime")
-
-#result_pure_clsUncertain_gmm  <- map(ls_mod_ajpsCLS[3:4], function(aMod){
-#  result <- methodComposition2(df_pure_clsAjps,aMod)
-#})
-#names(result_pure_clsUncertain_gmm) <- c("gmm", "gmm-regime")
-
-#mocresult_pureAJPS <- append(result_pure_clsUncertain, result_pure_clsUncertain_gmm)
-
-#saveRDS(mocresult_pureAJPS, file =here("output","estimates_moc_pureAJPS.RDS"))
-
 df_correct_clsAjps <- purrr::map(1:900, function(anEntry) {
@@
     title = "DV: V-Dem Liberal Democracy Index",
-    subtitle = "Regime Compacted"
+    subtitle = "Pooled"
   ) +
@@
     title = "",
-    subtitle = "Regime Specific"
+    subtitle = "Regime Specified"
   ) +
@@
 
-#df_pure_clsAPSR <- purrr::map(1:900, function(anEntry) {
-#  correct_cls_apsr[[anEntry]] %>% 
-#    plm::pdata.frame(index = c("country", "year"))
-#}
-#)
-
-#mocresult_pureAPSR  <- map(ls_mod_apsrCLS, function(aMod){
-#  result <- methodComposition3(df_pure_clsAPSR,aMod)
-#})
-
-#names(mocresult_pureAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
-#                                "fd1", "fd-regime1", "fd2", "fd-regime2")
-
-#saveRDS(mocresult_pureAPSR, file = here::here("ouput","estimates_moc_pureAPSR.RDS"))
-
 df_correct_clsAPSR <- purrr::map(1:900, function(anEntry) {
@@
 ```{r mocresult-expAPSR}
-
-#df_exp_clsAPSR <- purrr::map(1:900, function(anEntry) {
-#  expcor_cls_apsr[[anEntry]] %>% 
-#    plm::pdata.frame(index = c("country", "year"))
-#}
-#)
-
-#mocresult_expAPSR <- map(ls_mod_apsrCLS, function(aMod){
- # result <- methodComposition3(df_exp_clsAPSR,aMod)
-#})
-
-#names(mocresult_expAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
-#                                "fd1", "fd-regime1", "fd2", "fd-regime2")
-#saveRDS(mocresult_expAPSR, file = here::here("ouput","estimates_moc_expAPSR.RDS"))
 
@@
     title = "DV: The Change of Public Support for Democracy",
-    subtitle = "Regime Compacted"
+    subtitle = "Pooled"
   ) +
@@
     title = "",
-    subtitle = "Regime Specified"
+    subtitle = "Institution Specified"
   ) +
@@
     title = "",
-    subtitle = "Regime Specified w. Corruption"
+    subtitle = "Institution Specified w. Corruption"
   ) +

### 2021-07-31 paper/dcpo_demsupport.Rmd
Mildly adjust discussion on demo support and Rubin's rule.

@@
 In this letter, we reexamine the classic arguments about support for democracy and democratic change tested in these two pieces while correcting this oversight.
-In addition to incorporating the measurement uncertainty, we also sought to reduce it by expanding survey data to including 144 countries for up to 33 years between 1988 and 2020 (based on 26% more questions and 33% more survey sources).
+In addition to incorporating the measurement uncertainty, we also sought to reduce it by correcting and expanding survey data to including 144 countries for up to 33 years between 1988 and 2020 (based on 26% more questions and 33% more survey sources).
 Our analyses reveal that the significant relationships between public support and democratic change disappear once measurement uncertainty is taken into account, both in replications with the studies' original data and with expanded data.
@@
 
-There are many plausible explanations for these null results, both methodological and theoretical.
+There are many plausible explanations for these null results, both theoretical and methodological.
+From a theoretical perspective, the effect of democracy on public support may depend not on its mere existence but on its effectiveness [see @Magalhaes2014] and particularly with regard to redistribution [see @Krieckhaus2014].
+Similarly, the impact of public support on democracy may depend on the extent to which those who support democracy are also dissatisfied with the current regime's performance; that is, that it is not democratic support that is important to democratic change, but rather unsatisfied democratic demand [see @Qi2011].
+Whether the public support has a pro-democratic or anti-authoritarian effect is also bounded by the emancipative value that, as a belief-anchored orientation, shapes the public's understanding of democracy [see @Brunkert2019; @Kirsch2019; @Kruse2019].
+Moreover, the cultural and historical attributes of the emancipative value decide that it cannot be shifted shortly by institutional changes.
+Of course, it could in fact be that democratic change does not actually depend on public opinion of any sort at all but instead is an elite-driven phenomenon [see, e.g., @levitsky_how_2018].
+
 Methodologically, one possible issue is that support for democracy is multidimensional, and the survey questions used to measure it simply do not capture all of the dimensions relevant to democratic change, such as commitments to political equality and freedom of expression [see @Schedler2007; @Wuttke2020].
@@
 A third is that these survey questions do not ask respondents how they prioritize democracy relative to other values with which it may come into conflict, such as their partisanship, and so miss capturing the true extent of support democracy would find among the public when public support was actually needed [see @Carey2020; @graham_democracy_2020; @McCoy2020].
-
-From a theoretical perspective, the effect of democracy on public support may depend not on its mere existence but on its effectiveness [see @Magalhaes2014] and particularly with regard to redistribution [see @Krieckhaus2014].
-Similarly, the impact of public support on democracy may depend on the extent to which those who support democracy are also dissatisfied with the current regime's performance; that is, that it is not democratic support that is important to democratic change, but rather unsatisfied democratic demand [see @Qi2011].
-Culturally, whether the public democratic support has a pro-democratic or anti-authoritarian effect is bounded by emancipative value that, as a belief-anchored orientation, shapes the public's understanding of democracy [see @Brunkert2019; @Kirsch2019; @Kruse2019].
-Of course, it could in fact be that democratic change does not actually depend on public opinion of any sort at all but instead is an elite-driven phenomenon [see, e.g., @levitsky_how_2018].
 
@@
 We estimate each analysis model repeatedly on its respective collection of the datasets, and then make inferences from the distribution of parameter estimates by accounting for both within model standard error and between model variance.
-This combine rule was set out in @Rubin1987 and employed in research of measurement errors [see, e.g., @Schnakenberg2014; @Crabtree2015].
-@Blackwell2017a's multiple overimputation (MO) uses the same logic to correct sampling variance.
+This combine rule was set out in @Rubin1987, and has been employed in research of measurement errors [see, e.g., @Schnakenberg2014; @Crabtree2015] as well as incorporated in @Blackwell2017a's multiple overimputation (MO) to handle missing values and measurement uncertainty.
 We also employ one alternative technique known as "method of composition" (MOC)  [@Treier2008, p. 215] as a robustness check [see Online Supplementary Material \@ref(moc)].

### 2021-07-31 paper/dcpo_demsupport.Rmd
update codes and comparison between supdem and exp_data. @sammo3182 please check whether the updated data is consistent with numberic description.

@@
 
+load(here("data","claassen_replication_input.rda"))
+load(here("data","exp_claassen_input.rda"))
+
 # Removed the comments for the final replication file
@@
 
-## Incorporating Uncertainty
+## Data Recollection and Incorporating Uncertainty
+When we recollected the original data, we could not entirely achieve a primary replication [see @Grossman2020, p. 18] based @Claassen2020a's Dataverse materials.
+It turned out that we have differences in number of country-year surveys and in sample size.
+Specificially, our replication data has five fewer observations, three of which are no longer available in originial survey data and 2 seem to have never existed, and one more survey item which was conflated in original data [See more detail in Appendix].
+<!-- which 5? South Sudan arabb4; Dominican Rep lb 2003; Spain lb 2005. 2? -->
 
@@
 
-Following this line, after replicating the original analyses with point estimates, we take the distribution of the latent (explanatory) variable, the outcome variable, and control variables to account for the uncertainty from the measurement model as well as outcome and control variables.
+Following this line, after replicating the original analyses with point estimates, we incorportate uncertainty in analysis model using our replication data.
+We take the distribution of the latent (explanatory) variable, the outcome variable, and control variables to account for the uncertainty from the measurement model as well as outcome and control variables.
 We take 900 draws from the distribution of public democratic support, duplicate each article's analysis dataset of variables without "measurement error" 900 times, and assign them to each a different random draw from the posterior distribution of democracy indices.
@@
 ```{r compare_n, eval = TRUE}
-dcpo_input_raw1 <-
-    read_csv(here::here("data", "dcpo_input_raw.csv"), col_types = "cdcddcd") %>%
-    filter(!(
-        str_detect(survey, "army_wvs") &
-            # WVS obs identified as problematic by Claassen
-            ((country == "Albania" & year == 1998) |
-                 (country == "Indonesia" &
-                      (year == 2001 | year == 2006)) |
-                 (country == "Iran" & year == 2000) |
-                 (country == "Pakistan" &
-                      (year == 1997 | year == 2001)) | # 1996 in Claassen
-                 (country == "Vietnam" & year == 2001)
-            ) |
-            (str_detect(item, "strong_wvs") &
-                 ((country == "Egypt" & year == 2012) |
-                      (country == "Iran" &
-                           (year == 2000 | year == 2007)) | # 2005 in Claassen
-                      (country == "India") |
-                      (country == "Pakistan" &
-                           (year == 1997 | year == 2001)) | # 1996 in Claassen
-                      (country == "Kyrgyzstan" &
-                           (year == 2003 | year == 2011)) |
-                      (country == "Romania" &
-                           (year == 1998 | year == 2005 | year == 2012)) |
-                      (country == "Vietnam" & year == 2001)
-                 )) |
-            (
-                country %in% c(
-                    "Puerto Rico",
-                    "Northern Ireland",
-                    "SrpSka Republic",
-                    "Hong Kong SAR China"
-                )
-            )
-    )) %>%
-    DCPOtools::with_min_yrs(2)
 
@@
 
-dcpo_input_nc <- dcpo_input_raw1 %>% 
+dcpo_input_nc <- exp_claassen_input$data %>% 
   dplyr::select(country) %>% 
@@
 
-dcpo_input_surv <- dcpo_input_raw1 %>%
+dcpo_input_surv <- exp_claassen_input$data %>%
   dplyr::select(country, year, survey) %>%
@@
 
-dcpo_input_ncy <- dcpo_input_raw1 %>% 
+dcpo_input_ncy <- exp_claassen_input$data %>% 
   dplyr::select(country, year) %>% 
@@
 
-dcpo_input_ncyi <- dcpo_input_raw1 %>% 
+dcpo_input_ncyi <- exp_claassen_input$data %>% 
   dplyr::select(country, year, item, survey) %>% 
@@
 <!-- This paragraph should be revised. -->
-In addition to incorporating uncertainty, we expanded Claassen's data pool assembling as much data on democratic support as possible from available opinion surveys around the world. 
+We also expanded Claassen's data pool assembling as much data on democratic support as possible from available opinion surveys around the world. 
 The expansion ended with `r dcpo_input_ncyi` national opinions on democracy from `r dcpo_input_surv` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncy` opinions and `r supdem_surv` national surveys used in Claassen [-@Claassen2020a; -@Claassen2020b].^[These figures represent the survey data actually used in estimating public support for democracy; as in Claassen [-@Claassen2020a; -@Claassen2020b], countries for which two separate years of survey data were not available were excluded.]
 
-Besides accounting for uncertainty in latent variable estimates, we also included the measurement uncertainty in democracy indices and corruption index. 
+Besides accounting for uncertainty in latent variable estimates, we also included the measurement uncertainty in democracy indices and corruption index [See Appendix].
+
+<!-- put it into memo rather than in main context. -->
 We extracted the posterior distributions of democratic indices, including Liberal Democracy,polyarchy, and electoral democracy index, which are provided by [@coppedge2018]. 

### 2021-08-01 paper/dcpo_demsupport.Rmd
add information about differences between claassen's original data and our corrected data.

@@
 Specificially, our replication data has five fewer observations, three of which are no longer available in originial survey data and 2 seem to have never existed, and one more survey item which was conflated in original data [See more detail in Appendix].
-<!-- which 5? South Sudan arabb4; Dominican Rep lb 2003; Spain lb 2005. 2? -->
 
@@
 Besides accounting for uncertainty in latent variable estimates, we also included the measurement uncertainty in democracy indices and corruption index [See Appendix].
-
-<!-- put it into memo rather than in main context. -->
-We extracted the posterior distributions of democratic indices, including Liberal Democracy,polyarchy, and electoral democracy index, which are provided by [@coppedge2018]. 
-We drew 900 samples from the distribution of the Corruption Perception Index.^[Since Corruption Perception Index does not provide standard error before 2011, we imputed the missing standard error using the multiplication of a country's corruption index and the ratio of its available maximum standard error to its corresponding index.]
 
@@
 
+# Data Recollection and Control Uncertainty in Control Variables.
+
+Due to revisions to the underlying datasets (and, possibly, transcription errors), we were not able to achieve a primary replication [@Grossman2020] based on survey data summarized in @Claassen2020a and @Claassen2020b's Dataverse files.
+
+Specifically, we are not able to identify 5 cournty-year surveys, including South Sudan in Arab Barometer Wave 4, Dominican Republic in 2003 Latinobarometer, XXXX, and Spain in 2005 Latinobarometer. 
+In addition, we still have different sample size and number of respondents answering supportively by following approaches of cleanning data and treatment of non-responses described in @Claassen2020a's supplementatry materials.
+Specifically, we used Claassen's year coding to recode 85 unmatching country-year observations and added one more item "strong leader 2" in Arabbarometer which has different response categories but was conflated into "strong leader 1".
+
+V-Dem data was standardized in @Claassen2020b's analyses, but we did not figure out how the standardization was exactly performed.
+We standardized variables using Z-score, and the standardized values are different from Claassen's data.
+
+We also include measurement errors in control variables, including three democratic indices and corruption index.
+We extracted the posterior distributions of democratic indices, including Liberal Democracy,polyarchy, and electoral democracy index, which are provided by [@coppedge2018].
+We drew 900 samples from the distribution of the Corruption Perception Index.
+Since Corruption Perception Index does not provide standard error before 2011, we imputed the missing standard error using the multiplication of a country's corruption index and the ratio of its available maximum standard error to its corresponding index.
+
 # Replication with Alternative Methods Accounting for Uncertainty {#moc}
@@
 The explanatory variables without error are denoted $x^{obs}$.
-*Personally, I think we should be careful to use MO since our approach is not MO. I will go back here later.* 
+*Personally, I think we should be careful to use MO since our approach is not MO. I will go back here later. Instead, we might just write down Rubin's rule here. * 
 The parameter likelihood is then

### 2021-08-02 paper/memo/memo.Rmd
explain null result of lagged support in Figure 2.

--- 2021-07-21 paper/memo/memo.Rmd
@@
 
-*Need to explain the different results in AJPS*
-
 # Alternative Method for Incorporating uncertainty
@@
 
-First, we need to clarify that the DV in Figure2 is the change of public support for democracy rather than current public support.
-Second, when DV is the change of public support, Claassen's original results would not make any sense. 
+First, we need to clarify that the DV in Figure2 is the _change_ of public support for democracy rather than current public support.
+Second, when DV is the change of public support, Claassen's original results of lagged support do not make any sense. 
 Claassen's original results indicate the change of public support in one year is positively changed by the public support in the previous year and negatively shifted by the previous two years.
-However, should we expect that public support can produce its demand and especially a conflicting demand?
-Can high public support this year ask for a change next year but resist a change in the next two years?
-In contrast, our null results of lagged support on change of support mood make more sense since the change of moods is supposed to be shaped by exogenous factors, such as democratic or economic environment, or especially a shock.
-Unfortunately, after acknowledging uncertainty, the estimated effect of the change of democracy is indistinguishable from zero, and the magnitude of the coefficient also moves to zero.
-As @Treier2008 emphasized, only in applications where democracy has a strong effect on the quantity of interest and models are simple enough, accounting of uncertainty rarely renders the insignificant effect of democracy.
-However, even in Claassen's original results, the estimated effects of both the change of democracy and other social and economic factors are minor.
-Given the measurement errors in both democratic indices and public support, it is not surprising to see the diminution of the estimated effects.
+Claassen's results indicate that a high public support in 2020 leads to a bigger change in mood in 2021 but a high support in 2019 leads to a smaller change in mood in 2021.
+However, we do not have grounded theories to expect that public support can produce its positive demand in one year but backsliding demands in two years. 
+In contrast, our null results of lagged support on change of support mood indicate that the change of moods might not be dependent on its previous situation but might be shaped by exogenous factors, especially a shock in democratic or economic environment.
+
+In terms of the effects of social and economic environment on the change in mood, even in Claassen's original results (the uppermost results in Figure \@ref(fig:plot-mainAPSR)),  point estimates of the change in democracy,  economic growth, corruption index as well as their lagged level, are close to zero in magnitude.
+Except for the change in democracy, all other estimated effects are not distinguishable from zero. 
+After acknowledging uncertainty, the estimated effect of the change in democracy is indistinguishable from zero, and the magnitude of the coefficient moves further to zero.
+As @Treier2008 [p213] emphasized, accounting of uncertainty maintains the significant effect of democracy mainly in applications where democracy strongly affects the quantity of interest and models are simple enough.
+Given the measurement errors in public support, democratic indices, and corruption index, it is not surprising to see the diminution of the estimated effects.
 

### 2021-08-02 paper/dcpo_demsupport.Rmd
adjust disucssion on results.  @sammo3182 Table 2and 3 might need relable for variables. please check.

@@
 Second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.
-As the third step, we collect even more survey data---increasing these source data by one-fourth---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.
+As the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.
 
 ## Data Recollection and Incorporating Uncertainty
-When we recollected the original data, we could not entirely achieve a primary replication [see @Grossman2020, p. 18] based @Claassen2020a's Dataverse materials.
-It turned out that we have differences in number of country-year surveys and in sample size.
-Specificially, our replication data has five fewer observations, three of which are no longer available in originial survey data and 2 seem to have never existed, and one more survey item which was conflated in original data [See more detail in Appendix].
+Despite the great effort of collecting data and identifying differences, we could not entirely achieve a primary replication [see @Grossman2020, p. 18] based on @Claassen2020a's Dataverse materials.
+Our replication data has differences in number of country-year surveys and in sample size.
+Specificially, we have five fewer observations, three of which are no longer available in originial survey data and two seem to have never existed, and one more survey item which was conflated in original data [see Online Supplementary Material].
 
@@
 
-Following this line, after replicating the original analyses with point estimates, we incorportate uncertainty in analysis model using our replication data.
-We take the distribution of the latent (explanatory) variable, the outcome variable, and control variables to account for the uncertainty from the measurement model as well as outcome and control variables.
-We take 900 draws from the distribution of public democratic support, duplicate each article's analysis dataset of variables without "measurement error" 900 times, and assign them to each a different random draw from the posterior distribution of democracy indices.
+Following this line, after replicating the original analyses with point estimates, we incorportate uncertainty in analysis models using our replication data.
+We take the distribution of the latent (explanatory) variable, the outcome variable, and control variables to account for the uncertainty.
+We take 900 draws from the posterior distribution of democratic support, outcome, and control variables with errors.
+We then duplicate each article's analysis dataset of variables "without" measurement error 900 times, and assign them to each a different random draw from the distributions of variables with measurement error.
 We estimate each analysis model repeatedly on its respective collection of the datasets, and then make inferences from the distribution of parameter estimates by accounting for both within model standard error and between model variance.
@@
 
-<!-- This paragraph should be revised. -->
 We also expanded Claassen's data pool assembling as much data on democratic support as possible from available opinion surveys around the world. 
@@
 
-Besides accounting for uncertainty in latent variable estimates, we also included the measurement uncertainty in democracy indices and corruption index [See Appendix].
-
 # Results
@@
 The uppermost set of results replicate @Claassen2020a without uncertainty.
-The middle results introduce the uncertainty in the measurement of public support into the model.
-And the lowermost set presents the results estimated with the expanded data.
-
-In comparison to the original result, the positive coefficients for democratic support in both model accounting for the uncertainty are no longer statistically significant.
+The middle results introduce the uncertainty in the measurement of public support and democratic indices into the model.
+And the lowermost set presents the results estimated with the expanded data with uncertainty.
+
+In comparison to the original result, the positive coefficients for democratic support in both models accounting for the uncertainty are no longer statistically significant.
 This result is robust when using separated regime types in the explanatory variable. 
-Nor do applying system GMM models and using alternative methods for uncertainty incorporation methods alters the conclusion (see Online Supplementary Material \@ref(fullAJPS), \@ref(fullAPSR), and \@ref(moc)).
+Nor do applying system GMM models and using alternative method for uncertainty incorporation alters the conclusion (see Online Supplementary Material \@ref(fullAJPS), \@ref(fullAPSR), and \@ref(moc)).
 
@@
 In Figure \@ref(fig:plot-mainAPSR), we examine the thermostatic model of democratic support per @Claassen2020b [p. 47, Models 1.1 and 1.2]. 
-When the uncertainty is ignored, the coefficient of $\Delta$liberal democracy (the uppermost set), the yearly changes of the institutional feature is negative inferring that democratic mood decreases as democracy increases and vice versa.
+When the uncertainty is ignored, the coefficient of $\Delta$liberal democracy (the uppermost set), the yearly changes of the institutional feature is negative inferring that the change in democratic mood decreases as change in democracy increases and vice versa.
 However, when the measurement uncertainty is properly accounted (the middle set), the point estimate shifts towards zero and the coefficient is no longer significant.
@@
 
-In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support has a positive effect on democracy and democracy a negative effect on support are not empirically supported once measurement uncertainty is taken into account, even when more data are used.
-
-There are several potential methodological explanations for these null results.
-One issue is that the survey items employed---which ask respondents to assess the desirability or appropriateness of democracy, to compare democracy to some undemocratic alternative, or to assess one of these alternatives---may not capture every aspect of democratic support necessary for it to play its hypothesized roles in the classic theory.
-If only those who profess to prefer democracy to its alternatives _and also_ value freedom of expression, freedom of association, and pluralism of opinion will take appropriate action when democracy is threatened, then this measure is inadequate to its purpose [see, e.g., @Schedler2007].
-Moreover, given the multi-faceted nature of democratic attitudes, even the inclusion of such questions in unidimensional public opinion models such as those provided by @Claassen2019 or @Solt2020a are unlikely to be sufficient [see, e.g., @Wuttke2020].
-Another issue is that even if these survey questions do capture support for the generic concept of democracy, these measurement models might still be incapable of suitably capturing democratic support due to the variation in understanding the concept across countries or over time within countries [@Wuttke2021].
-Yet another is that this measure provides no assessment of the _relative_ importance the public affords democracy.
-It provides no information on the extent to which other values, such as policy preferences or partisanship, weigh more heavily---and there is growing evidence that, at least in the United States, there are many for whom these other considerations excuse substantial transgressions against democracy [see @bartels_ethnic_2020; @Carey2020; @graham_democracy_2020; @McCoy2020].
-
-There are theoretical explanations for the null results as well.
+In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support has a positive effect on democracy and change in democracy a negative effect on change in support are not empirically supported once measurement uncertainty is taken into account, even when more data are used.
+
+There are theoretical explanations for the null results.
 With regard to how levels of democracy affect public support, we note that even the proponents of the classic argument did not contend that the mere existence of democratic institutions, no matter how consistently feckless and ineffective, would generate support among the public: instead, they maintained, public support would be gained through experience with government performance that was generally effective [@lipset_social_1959, 86-89; @Easton1965, 119-120].
@@
 Democratic backsliding may simply be primarily a matter of elite decisionmaking [see, e.g., @levitsky_how_2018].
+
+There are several potential methodological explanations for these null results as well.
+One issue is that the survey items employed---which ask respondents to assess the desirability or appropriateness of democracy, to compare democracy to some undemocratic alternative, or to assess one of these alternatives---may not capture every aspect of democratic support necessary for it to play its hypothesized roles in the classic theory.
+If only those who profess to prefer democracy to its alternatives _and also_ value freedom of expression, freedom of association, and pluralism of opinion will take appropriate action when democracy is threatened, then this measure is inadequate to its purpose [see, e.g., @Schedler2007].
+Moreover, given the multi-faceted nature of democratic attitudes, even the inclusion of such questions in unidimensional public opinion models such as those provided by @Claassen2019 or @Solt2020a are unlikely to be sufficient [see, e.g., @Wuttke2020].
+Another issue is that even if these survey questions do capture support for the generic concept of democracy, these measurement models might still be incapable of suitably capturing democratic support due to the variation in understanding the concept across countries or over time within countries [@Wuttke2021].
+Yet another is that this measure provides no assessment of the _relative_ importance the public affords democracy.
+It provides no information on the extent to which other values, such as policy preferences or partisanship, weigh more heavily---and there is growing evidence that, at least in the United States, there are many for whom these other considerations excuse substantial transgressions against democracy [see @bartels_ethnic_2020; @Carey2020; @graham_democracy_2020; @McCoy2020].
 Regardless, these explanations indicate that there remains much work to be done in the empirical study of public support and democracy.
@@
 
-In this letter, we reexamined the findings from Claassen [-@Claassen2020a; -@Claassen2020b], two articles that maintain that public support helps the survival of democracy and democratic development has a thermostatic effect on public support.
-We demonstrated the importance of incorporating measurement uncertainty in analyzing the relationship between public support and democracy.
+In this letter, we reexamine the findings from Claassen [-@Claassen2020a; -@Claassen2020b], two articles that maintain that public support helps the survival of democracy and democratic development has a thermostatic effect on public support.
+We demonstrate the importance of incorporating measurement uncertainty in analyzing the relationship between public support and democracy.
 Taking uncertainty into account rendered both articles' conclusions without empirical support, even when we added considerable more data.
@@
 The null results reached in this letter could arise from several sources.
-We identified a number of potential shortcomings in the measurement of democratic support and ways in which the analysis models might be underspecified.
-All of these could and should be explored in future research, though there are also theoretically grounded reasons to suspect that the relationships are in fact negligible.
+There are theoretically grounded reasons of government effectiveness, democratic understanding, and generical-or-behavioral support to suspect that the relationships are in fact negligible.
+We also identified a number of potential shortcomings in the measurement of democratic support and ways in which the analysis models might be underspecified.
+All of these could and should be explored in future research.
 In any event, the sanguine assessment that readers may draw from Claassen [-@Claassen2020a; -@Claassen2020b]---that the fate of democracies depend on public support, and when eroded, their publics will rally to them---is not supported by the current evidence.

### 2021-08-03 paper/memo/memo.Rmd
add random walk discussion

@@
 In this way, we isolate the effects of measurement uncertainty and more data. 
-In the APSR analyses, it is uncertainty that accounts for the disappearing significance of public support.
+In replications for both AJPS and APSR analyses, it is uncertainty that accounts for the disappearing significance of public support and changes in democracy. 
+In Supplementatry material, we explained the methodology for addressing measurement uncerainty in this study and compared Rubin's Rules and Method of Composition.
+Both methods yield the similar results in significant and magnitude, though they address measurement errors in different angles.
+
+In terms of disappearing relationships between public support and democracy and the change in mood and the change in democracy, we have discussed theoretical reasons in our main text. 
+It is possbile that the relationship is negligible. 
+The incorporation of measurement error swamping the significant effects of democracy in a strong relationship is rare [@Treier2008].
+
+In addition to potential methodological explanations we have discussed, another potential reason is the over-time smoothing induced by the random-walk prior thanks to Reviwer 2's suggestion.
+At aggregated level, country-year data is super sparse. 
+Even in our expanded data, xx data is missing, compared to xxx missing in original data, which might cause the domination of priors in smoothing over-time changes.
+However, in our revised manuscript, we only employed Claassen's Model 5 to estimate public support using corrected original data and expanded data, seperately.
+Therefore, we isolate the effect of priors on estimates. 
+Since our expanded data added xxx country-year, the estimates from the expanded data should be influenced less by priors than original data by inputing more data. 
+The results render strong evidence that the coefficient estimates from expanded data are more certainty with narrow confident interval.
+However, since the temporal evoluation of latent public support is specificed as a simple dynamic linear model and variance of noise term is constant across countries, the actual changes in mood might not be accurately captured instead being smoothed over.
+That might explain why literally there is nothing significant when uncertainty is accounted in APSR replication.
 

### 2021-08-04 paper/dcpo_demsupport.Rmd
corrected table labels

@@
 This result is robust when using separated regime types in the explanatory variable. 
-Nor do applying system GMM models and using alternative method for uncertainty incorporation alters the conclusion (see Online Supplementary Material \@ref(fullAJPS), \@ref(fullAPSR), and \@ref(moc)).
+Nor do applying system GMM models and using MOC for uncertainty incorporation alters the conclusion (see Online Supplementary Material \@ref(fullAJPS), \@ref(fullAPSR), and \@ref(moc)).
 
@@
   "plm::lag(SupDem_Democ, 1)" = "Support in Democracy",
+  "plm::lag(theta_dem_trim, 1)" = "Support in Democracy",
   "plm::lag(SupDem_Autoc, 1)" = "Support in Autocracy",
+  "plm::lag(theta_aut_trim, 1)" = "Support in Autocracy",
   "plm::lag(lnGDP_imp, 1)" = "Log GDP Per Capita[t-1]",
@@
 
-names(tb_result_cls) <- c("Pooled", "Pooled-Regime", 
+names(tb_result_pureAJPS) <- c("Pooled", "Pooled-Regime", 
                           "GMM", "GMM-Regime")
@@
              output = "latex", 
-             title = "W. Uncertainty") %>% 
+             title = "W. Uncertainty and Expanded Data") %>% 
   kableExtra::kable_styling(latex_options = "HOLD_position")
@@
              coef_map = names_coef, 
-             output = "latex") %>% 
+             output = "latex", 
+             title = "Original") %>% 
   kableExtra::kable_styling(font_size = 7) %>% 
@@
              coef_map = names_coef, 
-             output = "latex") %>% 
+             output = "latex", 
+             title = "W. Uncertainty") %>% 
   kableExtra::kable_styling(font_size = 7) %>% 
@@
              coef_map = names_coef, 
-             output = "latex") %>% 
+             output = "latex", 
+             title = "W. Uncertainty and Expanded Data") %>% 
   kableExtra::kable_styling(font_size = 7) %>% 
@@
 Let $x$ (variables without subscript are used to denote vectors of observations, viz., $x$ = ($x_1$,......, $x_i$)) be a vector of the explanatory variable (e.g., mass support or institutional democracy) and $\theta$ be the parameter of interest.
-In multiple overimputation (MO, the method used in the main article), the explanatory variable with measurement errors is regarded as missing data $x^{mis}$ with an observed proxy $w$ under the assumption of "Missing at Random" and "Ignorable Measurement Mechanism Assignment" [@Blackwell2017].
-The explanatory variables without error are denoted $x^{obs}$.
-*Personally, I think we should be careful to use MO since our approach is not MO. I will go back here later. Instead, we might just write down Rubin's rule here. * 
-The parameter likelihood is then
+
+Rubin's Rules (RR, the method used in the main article) take variables with measurement error as missing value, and combine the point estimates and standard errors into single values yet accounting for both within and between imputation variances [@Rubin1987].
+
+Rubein's Rules is defined in the following formulas.
 
 \begin{equation}
-\mathcal{L}(\theta|y, x^{obs}) \propto \int_{\chi} p(x|y, \theta)p(y|\theta)dx^{mis}.
+\bar{\theta}_{m} = \frac{1}{m}\sum_{i=1}^{m} \theta_{i}.
 \end{equation}
 
-Given $x$ is unobservable, one can estimate it through the proxy $w$ together with the measurement error $a$:
-
 \begin{equation}
-E(w | x) = x + a.
+{V}_{B} = \frac{1}{m-1}\sum_{i=1}^{m} (\theta_{i}-\bar{\theta}_{m})^2.
 \end{equation}
 
-After gaining the parameter density based on the above functions, one can apply Rubin's Rule to combine the point estimates and standard errors into single values yet accounting for both within and between imputation variances [@Rubin1987].
+\begin{equation}
+{V}_{W} = \frac{1}{m}\sum_{i=1}^{m} SE_{i}^2.
+\end{equation}
+
+\begin{equation}
+{V}_{T} = {V}_{w} +(1+ \frac{1}{m})\frac{V_B}{m}.
+\end{equation}
+
+$\bar{\theta}_{M}$ is the pooled parameter estimate, $m$ is the number of imputed datasets, $V_{B}$ is between imputation variance, $V_{W}$ within imputation variance, $V_{T}$ is total variance.
+
+The general formula for confidence interval (CI) is defined as:
+
+\begin{equation}
+\bar{\theta} \pm t_{df,1-\alpha/2} *\sqrt{V_{T}}.
+\end{equation}
+
+$df$ is calculated by using $df_{Adjusted}$ [@barnard1999] and the Fraction of Missing information, lambda, is derived from between and total variance [@raghunathan2015, @van2018].
+
+\begin{equation}
+{df_{Adjusted}} = \frac{df_{Old}*df_{Observed}}{df_{Old}+df_{Observed}}.
+\end{equation}
+
+\begin{equation}
+{df_{Old}} = \frac{(n-k)+1}{(n-k)+3} * (n-k)(1-lambda).
+\end{equation}
+
+\begin{equation}
+{df_{Observed}} = \frac{(n-k)+1}{(n-k)+3} * (n-k)(1-lambda).
+\end{equation}
+
+\begin{equation}
+{Lambda} = \frac{V_{B}+\frac{V_{B}}{m}}{V_{T}}
+\end{equation}
+
+One main idea behind RR is to account for both within imputation variance and sample variance which is due to the missing data (measurement error in our case).
 

### 2021-08-04 paper/dcpo_demsupport.Rmd
removing the overstatement in the memo

@@
     class(.) <- "modelsummary_list"
-  return(.)})
+    return(.)
+})
 
@@
 modelsummary(tb_result_cls,
-             statistic = "conf.int",
+             # statistic = "conf.int",
              coef_map = names_coef,
@@
              title = "Original") %>%
-
     kableExtra::kable_styling(font_size = 8) %>%
@@
 tb_result_pureAJPS <- purrr::map(result_pureAJPS, ~ {
+    .[[1]] <- rename(.[[1]], std.error = se)
     names(.) <- c("tidy", "glance")
     class(.) <- "modelsummary_list"
-  return(.)})
+    return(.)
+})
 
@@
 
-modelsummary(tb_result_pureAJPS, 
-             statistic = "conf.int",
+modelsummary(
+    tb_result_pureAJPS,
+    # statistic = "conf.int",
     coef_map = names_coef,
     output = "latex",
-             title = "W. Uncertainty") %>% 
+    title = "W. Uncertainty"
+) %>%
     kableExtra::kable_styling(latex_options = "HOLD_position")
@@
 tb_result_expAJPS <- purrr::map(result_expAJPS, ~ {
+    .[[1]] <- rename(.[[1]], std.error = se)
     names(.) <- c("tidy", "glance")
     class(.) <- "modelsummary_list"
-  return(.)})
+    return(.)
+})
 
@@
 
-modelsummary(tb_result_expAJPS, 
-             statistic = "conf.int",
+modelsummary(
+    tb_result_expAJPS,
+    # statistic = "conf.int",
     coef_map = names_coef,
     output = "latex",
-             title = "W. Uncertainty and Expanded Data") %>% 
+    title = "W. Uncertainty and Expanded Data"
+) %>%
     kableExtra::kable_styling(latex_options = "HOLD_position")
@@
     class(.) <- "modelsummary_list"
-  return(.)}) %>% 
-  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
-      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]
-
-names(tb_result_clsAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
-
-modelsummary(tb_result_clsAPSR, 
-             stars = TRUE,
+    return(.)
+}) %>%
+    .[c(
+        "pooled1",
+        "pooled-regime1",
+        "fd1",
+        "fd-regime1",
+        "pooled2",
+        "pooled-regime2",
+        "fd2",
+        "fd-regime2"
+    )]
+
+names(tb_result_clsAPSR) <-
+    c(
+        "ECM",
+        "ECM-Regime",
+        "FD",
+        "FD-Regime",
+        "ECM Corrup",
+        "ECM Corrup-Regime",
+        "FD Corrup",
+        "FD Corrup-Regime"
+    )
+
+modelsummary(
+    tb_result_clsAPSR,
+    # statistic = "conf.int",
     coef_map = names_coef,
     output = "latex",
-             title = "Original") %>% 
+    title = "Original"
+) %>%
     kableExtra::kable_styling(font_size = 7) %>%
@@
 tb_result_pureAPSR <- purrr:::map(result_pureAPSR, ~ {
+    .[[1]] <- rename(.[[1]], std.error = se)
     names(.) <- c("tidy", "glance")
     class(.) <- "modelsummary_list"
-  return(.)}) %>% 
-  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
-      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]
-
-names(tb_result_pureAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
-
-modelsummary(tb_result_pureAPSR, 
-             statistic = "conf.int",
+    return(.)
+}) %>%
+    .[c(
+        "pooled1",
+        "pooled-regime1",
+        "fd1",
+        "fd-regime1",
+        "pooled2",
+        "pooled-regime2",
+        "fd2",
+        "fd-regime2"
+    )]
+
+names(tb_result_pureAPSR) <-
+    c(
+        "ECM",
+        "ECM-Regime",
+        "FD",
+        "FD-Regime",
+        "ECM Corrup",
+        "ECM Corrup-Regime",
+        "FD Corrup",
+        "FD Corrup-Regime"
+    )
+
+modelsummary(
+    tb_result_pureAPSR,
+    # statistic = "conf.int",
     coef_map = names_coef,
     output = "latex",
-             title = "W. Uncertainty") %>% 
+    title = "W. Uncertainty"
+) %>%
     kableExtra::kable_styling(font_size = 7) %>%
@@
 tb_result_expAPSR <- map(result_expAPSR, ~ {
+    .[[1]] <- rename(.[[1]], std.error = se)
     names(.) <- c("tidy", "glance")
     class(.) <- "modelsummary_list"
-  return(.)}) %>% 
-  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
-      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]
-
-names(tb_result_expAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
-
-modelsummary(tb_result_expAPSR, 
-             statistic = "conf.int",
+    return(.)
+}) %>%
+    .[c(
+        "pooled1",
+        "pooled-regime1",
+        "fd1",
+        "fd-regime1",
+        "pooled2",
+        "pooled-regime2",
+        "fd2",
+        "fd-regime2"
+    )]
+
+names(tb_result_expAPSR) <-
+    c(
+        "ECM",
+        "ECM-Regime",
+        "FD",
+        "FD-Regime",
+        "ECM Corrup",
+        "ECM Corrup-Regime",
+        "FD Corrup",
+        "FD Corrup-Regime"
+    )
+
+modelsummary(
+    tb_result_expAPSR,
+    # statistic = "conf.int",
     coef_map = names_coef,
     output = "latex",
-             title = "W. Uncertainty and Expanded Data") %>% 
+    title = "W. Uncertainty and Expanded Data"
+) %>%
     kableExtra::kable_styling(font_size = 7) %>%

### 2021-08-04 paper/memo/memo.Rmd
removing the overstatement in the memo

--- 2021-08-02 paper/memo/memo.Rmd
@@
     fig_caption: true
-    latex_engine: pdflatex
+    latex_engine: xelatex
     template: ../svm-latex-ms2.tex
@@
 Regarding Reviewer 1's request on replicating all specifications in the original two studies, we added alternate specifications on the relationship between public support and democracy, including GMM models, First Different Models, and sample split.
-Results do not change in all these models, presented on Page xxx, Figure xxx, and xxx in SI. 
-As the editor suggested, this letter should focus on the core point: the relationship between public support and democracy. We do not replicate specifications on other relationships.
-
-*Need to add APSR models or more description on full models*
+See Page xxx, Figure xxx, and xxx in SI.
 
@@
 In this way, we isolate the effects of measurement uncertainty and more data. 
-In the APSR analyses, it is uncertainty that accounts for the disappearing significance of public support.
+In replications for both AJPS and APSR analyses, it is uncertainty that accounts for the disappearing significance of public support and changes in democracy. 
+In Supplementatry material, we explained the methodology for addressing measurement uncerainty in this study and compared Rubin's Rules and Method of Composition.
+Both methods yield the similar results in significant, though they address measurement errors in different angles.
+
+In terms of disappearing relationships between public support and democracy and the change in mood and the change in democracy, we have discussed theoretical reasons in our main text. 
+It is possbile that the relationship is negligible, because the incorporation of measurement error swamping the significant effects of democracy in a strong relationship is rare [@Treier2008].
+
+In addition to potential methodological explanations we have discussed, another potential reason is the over-time smoothing induced by the random-walk prior thanks to Reviwer 2's suggestion.
+At aggregated level, country-year data is super sparse. 
+Even in our expanded data, xx data is missing, compared to xxx missing in original data.
+The sparse of raw data and the simple dynamic linear model used in measurement model to capture dynamic effect might make priors dominate in smoothing over-time changes. 
+However, in our revised manuscript, we only used Claassen's Model 5 to estimate public support using corrected original data and expanded data, seperately.
+Since our expanded data added xxx country-year, the estimates from the expanded data should be influenced less by priors than original data by inputing more data. 
+Still, the coefficient estimates from expanded data are indistinguishable from zero though with narrower confident interval.
+Therefore, it is the incorporation of uncertainty that changes the coefficient estimates in magnitude and significant.
 
@@
 Second, the propagation of uncertainty can either attenuate or magnify the magnitude of estimated effects.
-*We can cite more lit if necessary*. 
 To avoid confusion, we only focus on uncertainty in this revised version.
@@
 ## Response
-We might need to review the functions added in SI.
+In SI, we discussed methodology used in this article to address measurement errors, Rubin's Rules and MOC.
+We compared these two methods by introducing their fomulas and equations and highlighing their different approaches. 
+As results show, though they have different approaches, the results from two methods are similar with each other.
 

### 2021-08-05 paper/dcpo_demsupport.Rmd
using moc plots throughout the paper

--- 2021-08-04 paper/dcpo_demsupport.Rmd
@@
   warning = FALSE,
-  eval = FALSE,
   dpi = 300
@@
 
-load(here("data", "correct_cls_ajps.rda"))
-load(here("data", "correct_cls_apsr.rda")) 
-load(here("data", "expcor_cls_ajps.rda"))
-load(here("data", "expcor_cls_apsr.rda"))
-
-result_clsAJPS <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
-result_pureAJPS <- readRDS(here("output", "estimates_clsPureAJPS.RDS"))
-result_expAJPS <- readRDS(here("output", "estimates_clsExpAJPS.RDS"))
-result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
-result_pureAPSR <- readRDS(here("output", "estimates_clsPureAPSR.RDS"))
-result_expAPSR <- readRDS(here("output", "estimates_clsExpAPSR.RDS"))
+# load(here("data", "correct_cls_ajps.rda"))
+# load(here("data", "correct_cls_apsr.rda")) 
+# load(here("data", "expcor_cls_ajps.rda"))
+# load(here("data", "expcor_cls_apsr.rda"))
 
@@
 ## Data Recollection and Incorporating Uncertainty
+
 Despite the great effort of collecting data and identifying differences, we could not entirely achieve a primary replication [see @Grossman2020, p. 18] based on @Claassen2020a's Dataverse materials.
 Our replication data has differences in number of country-year surveys and in sample size.
-Specificially, we have five fewer observations, three of which are no longer available in originial survey data and two seem to have never existed, and one more survey item which was conflated in original data [see Online Supplementary Material].
+Specifically, we have five fewer observations, three of which are no longer available in original survey data and two seem to have never existed, and one more survey item which was conflated in original data [see Online Supplementary Material].
 
@@
 
-Following this line, after replicating the original analyses with point estimates, we incorportate uncertainty in analysis models using our replication data.
+Following this line, after replicating the original analyses with point estimates, we incorporate uncertainty in analysis models using our replication data.
 We take the distribution of the latent (explanatory) variable, the outcome variable, and control variables to account for the uncertainty.
@@
 
-```{r compare_n, eval = TRUE}
+```{r compare_n}
 
@@
 
-```{r pointAJPS, eval=TRUE}
+```{r pointAJPS}
 ls_iv <- c("plm::lag(SupDem_trim, 1)",
@@
 
-```{r result-pureAJPS}
-result_pureAJPS <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
-  result <- map(correct_cls_ajps, function(aData){ # applying to the 1000 datasets
-    eval(parse(text = aMod))
-  })
-
-  result_betas <- mitools::MIextract(result, fun = coef)
-
-  ## Not work with ifelse
-  if(class(result[[1]])[1] == "plm"){
-      result_vars <- mitools::MIextract(result, fun = vcovBK_se)
-  }else{
-      result_vars <- mitools::MIextract(result, fun = vcovHC_se)
-  }
-
-  tidy_clsUncertain <- summary(mitools::MIcombine(results = result_betas, 
-                             variance = result_vars)) %>% 
-    rownames_to_column(var = "term") %>%
-        rename(conf.low = `(lower`,
-               conf.high = `upper)`,
-               estimate = results) %>%
-        filter(!str_detect(term, "(Intercept)"))
-
-  if(class(result[[1]]) == "plm"){ 
-    glance_clsUncertain <- glance.plm(result[[1]]) # using the customized glance function
-  }else{
-    glance_clsUncertain <- glance(result[[1]])
-  }
-
-  result_apsrAJPS <- list(tidy_clsUncertain, glance_clsUncertain)
-})
-
-names(result_pureAJPS) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
-
-saveRDS(result_pureAJPS, file = here::here("output", "estimates_clsPureAJPS.RDS"))
-```
-
-```{r result-expAJPS}
-result_expAJPS <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
-  result <- map(expcor_cls_ajps, function(aData){ # applying to the 1000 datasets
-    eval(parse(text = aMod))
-  })
-
-  result_betas <- mitools::MIextract(result, fun = coef)
-
-  ## Not work with ifelse
-  if(class(result[[1]])[1] == "plm"){
-      result_vars <- mitools::MIextract(result, fun = vcovBK_se)
-  }else{
-      result_vars <- mitools::MIextract(result, fun = vcovHC_se)
-  }
-
-  tidy_dcpoUncertain <- summary(mitools::MIcombine(results = result_betas, 
-                             variance = result_vars)) %>% 
-    rownames_to_column(var = "term") %>%
-        rename(conf.low = `(lower`,
-               conf.high = `upper)`,
-               estimate = results) %>%
-        filter(!str_detect(term, "(Intercept)"))
-
-  if(class(result[[1]]) == "plm"){ 
-    glance_dcpoUncertain <- glance.plm(result[[1]]) # using the customized glance function
-  }else{
-    glance_dcpoUncertain <- glance(result[[1]])
-  }
-
-  result_expAJPS <- list(tidy_dcpoUncertain, glance_dcpoUncertain)
-})
-
-names(result_expAJPS) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
-
-saveRDS(result_expAJPS, file = here::here("output", "estimates_clsExpAJPS.RDS"))
-```
-
-```{r coefName-AJPS, eval=TRUE}
-index_coefName <- c(
-  `plm::lag(Libdem_VD, 1:2)1` = "Democracy[t-1]",
-  `plm::lag(Libdem_VD, 1:2)2` = "Democracy[t-2]",
-  `plm::lag(Vdem_libdem, 1:2)1` = "Democracy[t-1]",
-  `plm::lag(Vdem_libdem, 1:2)2` = "Democracy[t-2]",
-  `plm::lag(SupDem_trim, 1)` = "Support[t-1]",
-  `plm::lag(theta, 1)` = "Support[t-1]",
-  `plm::lag(SupDem_Democ, 1)` = "Support[t-1](demo~only)",
-  `plm::lag(SupDem_Autoc, 1)` = "Support[t-1](auto~only)",
-  `plm::lag(theta_dem_trim, 1)` = "Support[t-1](demo~only)",
-  `plm::lag(theta_aut_trim, 1)` = "Support[t-1](auto~only)",
-  `plm::lag(lnGDP_imp, 1)` = "Log~GDP~per~capita[t-1]",
-  `plm::lag(lg_imp_mdpgdp, 1)` = "Log~GDP~per~capita[t-1]",
-  `plm::lag(GDP_imp_grth, 1)` = "GDP~per~capita~growth[t-1]",
-  `plm::lag(mdprgdp_grwth, 1)` = "GDP~per~capita~growth[t-1]",
-  `plm::lag(Libdem_regUN, 1)` = "Regional~democracy[t-1]",
-  `plm::lag(Region_libdem, 1)` = "Regional~democracy[t-1]",
-  `plm::lag(Pr_Muslim, 1)` = "Percent~Muslim[t-1]",
-  `plm::lag(muslism_prop_2010, 1)` = "Percent~Muslim[t-1]",
-  `plm::lag(Res_cp_WDI_di, 1)` = "Resource~dependence[t-1]",
-  `plm::lag(dependence_pc_di, 1)` = "Resource~dependence[t-1]"
-)
-```
-
-```{r plot-mainAJPS, fig.cap= "The Effect of Public Support on Democracy with Uncertainty", fig.width=7, fig.height=10, fig.align='center', eval=TRUE}
-
-type_model <-
-  c("Original", "Uncertainty", "Uncertainty+Expanded Data")
-
-result_ajpsPooled <-
-  list(result_clsAJPS,
-       result_pureAJPS,
-       result_expAJPS) %>%
-  map2_df(type_model, ~ {
-    .x$pooled[[1]] %>%
-      filter(term != "(Intercept)") %>%
-      select(term, estimate, conf.low, conf.high) %>%
-      mutate(model = .y)
-  }) %>% 
-  mutate(type = "Pooled")
-
-result_ajpsRegime <-
-  list(result_clsAJPS,
-       result_pureAJPS,
-       result_expAJPS) %>%
-  map2_df(type_model, ~ {
-    .x$`pooled-regime`[[1]] %>%
-      filter(term != "(Intercept)") %>%
-      select(term, estimate, conf.low, conf.high) %>%
-      mutate(model = .y)
-  }) %>% 
-  mutate(type = "Regime Specified")
-
-df_plot <- bind_rows(result_ajpsPooled, result_ajpsRegime) %>% 
-    mutate(term = index_coefName[term],
-           term = factor(term, levels = unique(index_coefName)))
-
-dwplot(df_plot) +
-    geom_vline(xintercept = 0,
-               colour = "grey80",
-               linetype = 2) +
-    theme_minimal() +
-    ggtitle("DV: Liberal Democracy (Vdem)") +
-    xlab("Coefficient Estimate") +
-    theme(
-        axis.title.y = element_blank(),
-        legend.position = "bottom",
-      legend.title = element_blank()
-    ) +
-    scale_y_discrete(labels = parse(text = rev(levels(df_plot$term)))) +
-    # Using expressions of underscore and greek letters
-    # scale_color_gb(palette = "digitMixed") +
-    facet_wrap(~ type)
-
-```
-
-The importance of accounting for the measurement uncertainty appear more evident when the relevant variable plays as the outcome variable. 
-In Figure \@ref(fig:plot-mainAPSR), we examine the thermostatic model of democratic support per @Claassen2020b [p. 47, Models 1.1 and 1.2]. 
-When the uncertainty is ignored, the coefficient of $\Delta$liberal democracy (the uppermost set), the yearly changes of the institutional feature is negative inferring that the change in democratic mood decreases as change in democracy increases and vice versa.
-However, when the measurement uncertainty is properly accounted (the middle set), the point estimate shifts towards zero and the coefficient is no longer significant.
-More data (the lowermost set), again, only adjusts the confidence intervals but not direction nor significance.
-
-```{r pointAPSR, eval=TRUE}
-load(here::here("data", "dem_mood_apsr.RData"))
-sd.plm <- pdata.frame(x, index = c("Country", "Year"))
-
-ls_ivECM <- c("diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)", 
-              "diff(Polyarchy_z, lag = 1) + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)")
-ls_ctrlECM <- c("", " + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1)")
-
-ls_eqECM <- glue("diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)") %>% 
-  outer(ls_ctrlECM, paste0) %>% 
-  as.vector()
-
-ls_ivFD <- c("Libdem_z",
-             "Polyarchy_z + Liberal_z")
-
-ls_ctrlFD <- c("", " + Corrup_TI_z")
-
-ls_eqFD <- glue("SupDem_trim ~ {ls_ivFD} + lnGDP_imp") %>% 
-  outer(ls_ctrlFD, paste0) %>% 
-  as.vector()
-
-ls_mod <- c(
-  glue("plm({ls_eqECM}, model = 'pooling', data = sd.plm)"),
-  glue("plm({ls_eqFD}, model = 'fd', index = 'Country', data = sd.plm)")
-)
-
-df_result_clsAPSR <- map(ls_mod, function(mod) {
-  result <- eval(parse(text = mod))
-})
-
-result_clsAPSR <- map(df_result_clsAPSR, function(aResult) {
-  tidy_result <- tidy(aResult, conf.int = TRUE) %>% 
-    mutate(std.error = vcovHC_se(aResult))
-
-  glance_result <- glance.plm(aResult)
-
-  ls_result <- list(tidy_result, glance_result)
-})
-
-names(result_clsAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", 
-                           "fd1", "fd-regime1", "fd2", "fd-regime2")
-
-saveRDS(result_clsAPSR, file = here("output", "estimates_clsMeanAPSR.RDS"))
-```
-
-```{r model-APSR}
-ls_ivECM <- c("diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)", 
-              "diff(Polyarchy_z, lag = 1) + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)")
-ls_ctrlECM <- c("", " + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1)")
-
-ls_eqECM <- glue("diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)") %>% 
-  outer(ls_ctrlECM, paste0) %>% 
-  as.vector()
-
-ls_ivFD <- c("Libdem_z",
-             "Polyarchy_z + Liberal_z")
-
-ls_ctrlFD <- c("", " + Corrup_TI_z")
-
-ls_eqFD <- glue("diff(SupDem_trim, lag = 1) ~ {ls_ivFD} + lnGDP_imp") %>% 
-  outer(ls_ctrlFD, paste0) %>% 
-  as.vector()
-
-ls_mod_apsrCLS <- c(
-  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
-  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
-)
-```
-
-```{r result-pureAPSR}
-result_pureAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
-  result <- map(correct_cls_apsr, function(aData){ # applying to the 900 datasets
-    eval(parse(text = aMod))
-  })
-
-  result_betas <- mitools::MIextract(result, fun = coef)
-
-  result_vars <- mitools::MIextract(result, fun = vcovHC_se)
-
-  tidy_clsUncertainAPSR <- summary(mitools::MIcombine(results = result_betas, 
-                             variance = result_vars)) %>% 
-    rownames_to_column(var = "term") %>%
-        rename(conf.low = `(lower`,
-               conf.high = `upper)`,
-               estimate = results) %>%
-        filter(!str_detect(term, "(Intercept)"))
-
-  glance_clsUncertainAPSR <- glance.plm(result[[1]])
-
-  result_apsrAJPSAPSR <- list(tidy_clsUncertainAPSR, glance_clsUncertainAPSR)
-})
-
-names(result_pureAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", "fd1", "fd-regime1", "fd2", "fd-regime2")
-
-saveRDS(result_pureAPSR, file = here("output", "estimates_clsPureAPSR.RDS"))
-```
-
-```{r result-expAPSR}
-result_expAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
-  result <- map(expcor_cls_apsr, function(aData){ # applying to the 1000 datasets
-    eval(parse(text = aMod))
-  })
-
-  result_betas <- mitools::MIextract(result, fun = coef)
-
-  result_vars <- mitools::MIextract(result, fun = vcovHC_se)
-
-  tidy_dcpoUncertainAPSR <- summary(mitools::MIcombine(results = result_betas, 
-                             variance = result_vars)) %>% 
-    rownames_to_column(var = "term") %>%
-        rename(conf.low = `(lower`,
-               conf.high = `upper)`,
-               estimate = results) %>%
-        filter(!str_detect(term, "(Intercept)"))
-
-  glance_dcpoUncertainAPSR <- glance.plm(result[[1]])
-
-  result_expAPSR <- list(tidy_dcpoUncertainAPSR, glance_dcpoUncertainAPSR)
-})
-
-names(result_expAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",  "fd1", "fd-regime1", "fd2", "fd-regime2")
-
-saveRDS(result_expAPSR, file = here("output", "estimates_clsExpAPSR.RDS"))
-```
-
-```{r coefName-APSR, eval=TRUE}
-index_coefName <- c(
-    `plm::lag(SupDem_trim, 1:2)1` = "Support[t-1]",
-    `plm::lag(SupDem_trim, 1:2)2` = "Support[t-2]",
-    `plm::lag(theta_trim, 1:2)1` = "Support[t-1]",
-    `plm::lag(theta_trim, 1:2)2` = "Support[t-2]",
-
-    `diff(Libdem_z, lag = 1)` = "Delta~Liberal~democracy",
-    `diff(Vdem_libdem_z, lag = 1)` = "Delta~Liberal~democracy",
-    `plm::lag(Libdem_z, 1)` = "Liberal~democracy[t-1]",
-    `plm::lag(Vdem_libdem_z, 1)` = "Liberal~democracy[t-1]",
-
-    `diff(Liberal_z, lag = 1)` = "Delta~Electoral~democracy",
-    `diff(Vdem_liberal_z, lag = 1)` = "Delta~Electoral~democracy",
-    `plm::lag(Liberal_z, 1)` = "Electoral~democracy[t-1]",
-    `plm::lag(Vdem_liberal_z, 1)` = "Electoral~democracy[t-1]",
-
-    `diff(Polyarchy_z, lag = 1)` = "Delta~Minoritarian~democracy",
-    `diff(Vdem_polyarchy_z, lag = 1)` = "Delta~Minoritarian~democracy",
-    `plm::lag(Polyarchy_z, 1)` = "Minoritarian~democracy[t-1]",
-    `plm::lag(Vdem_polyarchy_z, 1)` = "Minoritarian~democracy[t-1]",
-
-    `diff(lnGDP_imp, lag = 1)` = "Delta~Log~GDP~per~capita",
-    `diff(lg_imp_mdpgdp, lag = 1)` = "Delta~Log~GDP~per~capita",
-    `plm::lag(lnGDP_imp, 1)` = "Log~GDP[t-1]",
-    `plm::lag(lg_imp_mdpgdp, 1)` = "Log~GDP[t-1]"
-    # `diff(Corrup_TI_z, lag = 1)`= "Delta~Corruption",
-    # `plm::lag(Corrup_TI_z, 1)` = "Log~Corruption[t-1]",
-    # `Corrup_TI_z` = "Log~Corruption[t-1]"
-)
-```
-
-```{r plot-mainAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", fig.width=7, fig.height=10, eval = TRUE}
-result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
-result_pureAPSR <- readRDS(here("output", "estimates_clsFullUncertainAPSR.RDS"))
-result_expAPSR <- readRDS(here("output", "estimates_clsExpAPSR.RDS"))
-
-type_model <-
-  c("Original", "Uncertainty", "Uncertainty+Expanded Data")
-
-result_apsrPooled <-
-  list(result_clsAPSR,
-       result_pureAPSR,
-       result_expAPSR) %>%
-  map2_df(type_model, ~ {
-    .x$pooled1[[1]] %>%
-      filter(term != "(Intercept)") %>%
-      select(term, estimate, conf.low, conf.high) %>%
-      mutate(model = .y)
-  }) %>% 
-  mutate(type = "Pooled")
-
-result_apsrRegime <-
-  list(result_clsAPSR,
-       result_pureAPSR,
-       result_expAPSR) %>%
-  map2_df(type_model, ~ {
-    .x$`pooled-regime1`[[1]] %>%
-      filter(term != "(Intercept)") %>%
-      select(term, estimate, conf.low, conf.high) %>%
-      mutate(model = .y)
-  }) %>% 
-  mutate(type = "Institution Specified")
-
-df_plot <- bind_rows(result_apsrPooled, result_apsrRegime) %>% 
-    mutate(term = index_coefName[term],
-           term = factor(term, levels = unique(index_coefName)), 
-           type = factor(type, levels = c("Pooled", "Institution Specified")))
-
-dwplot(df_plot) +
-    geom_vline(xintercept = 0,
-               colour = "grey80",
-               linetype = 2) +
-    ggtitle("DV: The Change of Public Support for Democracy") +
-    xlab("Coefficient Estimate") +
-    theme(
-        axis.title.y = element_blank(),
-        legend.position = "bottom",
-        legend.title = element_blank()
-    ) +
-    facet_wrap( ~ type) + 
-    scale_y_discrete(labels = parse(text = rev(levels(df_plot$term))))
-    # Using expressions of underscore and greek letters
-    # scale_color_gb(palette = "digitMixed")
-
-```
-
-# Discussion
-
-In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support has a positive effect on democracy and change in democracy a negative effect on change in support are not empirically supported once measurement uncertainty is taken into account, even when more data are used.
-
-There are theoretical explanations for the null results.
-With regard to how levels of democracy affect public support, we note that even the proponents of the classic argument did not contend that the mere existence of democratic institutions, no matter how consistently feckless and ineffective, would generate support among the public: instead, they maintained, public support would be gained through experience with government performance that was generally effective [@lipset_social_1959, 86-89; @Easton1965, 119-120].
-There is some empirical support for this, with government effectiveness positively related to public support among democracies and negatively related in non-democracies [@Magalhaes2014]. 
-The finding of @Krieckhaus2014 that income inequality is strongly negatively related to public support in democracies suggests that performance regarding redistribution is particularly important.
-Relatedly, on the reverse part of the classic argument, @Qi2011 suggests that democratic support alone cannot be expected to generate democratic change and oppose backsliding.
-Instead, that work contends, it is the combination of democratic support and dissatisfaction with current regime performance that generates demand for greater democracy.
-The effects of public support also have cultural-bound.
-@Brunkert2019 contends outspoken support for democracy is a "deceptive indicator of public's affinity to democracy" [423] and finds public support has neither pro-democratic nor anti-authoritarian effect without controlling emancipative values.
-Empirical results show that the meaning of support for democracy is dependent on emancipation values and is reversed to its own negation in a society with weak emancipative values [see, e.g.,@Kirsch2019, 83-85].
-And we must be open to the possibility that no theoretical elaboration, no respecification of these models will reveal relationships between public opinion and democracy.
-Democratic backsliding may simply be primarily a matter of elite decisionmaking [see, e.g., @levitsky_how_2018].
-
-There are several potential methodological explanations for these null results as well.
-One issue is that the survey items employed---which ask respondents to assess the desirability or appropriateness of democracy, to compare democracy to some undemocratic alternative, or to assess one of these alternatives---may not capture every aspect of democratic support necessary for it to play its hypothesized roles in the classic theory.
-If only those who profess to prefer democracy to its alternatives _and also_ value freedom of expression, freedom of association, and pluralism of opinion will take appropriate action when democracy is threatened, then this measure is inadequate to its purpose [see, e.g., @Schedler2007].
-Moreover, given the multi-faceted nature of democratic attitudes, even the inclusion of such questions in unidimensional public opinion models such as those provided by @Claassen2019 or @Solt2020a are unlikely to be sufficient [see, e.g., @Wuttke2020].
-Another issue is that even if these survey questions do capture support for the generic concept of democracy, these measurement models might still be incapable of suitably capturing democratic support due to the variation in understanding the concept across countries or over time within countries [@Wuttke2021].
-Yet another is that this measure provides no assessment of the _relative_ importance the public affords democracy.
-It provides no information on the extent to which other values, such as policy preferences or partisanship, weigh more heavily---and there is growing evidence that, at least in the United States, there are many for whom these other considerations excuse substantial transgressions against democracy [see @bartels_ethnic_2020; @Carey2020; @graham_democracy_2020; @McCoy2020].
-Regardless, these explanations indicate that there remains much work to be done in the empirical study of public support and democracy.
-
-# Conclusion
-
-In this letter, we reexamine the findings from Claassen [-@Claassen2020a; -@Claassen2020b], two articles that maintain that public support helps the survival of democracy and democratic development has a thermostatic effect on public support.
-We demonstrate the importance of incorporating measurement uncertainty in analyzing the relationship between public support and democracy.
-Taking uncertainty into account rendered both articles' conclusions without empirical support, even when we added considerable more data.
-
-This points to the absolute necessity of incorporating measurement uncertainty into analyses that include latent variables.
-Measurement issues have never had a prominent place in comparative political studies because they need more time to estimate models, but they ground the quality of data and the basis of analysis [@stegmueller2011, 484].
-As the use of latent variables grows more common in political science, both researchers and readers should be aware that these variables' concomitant measurement uncertainty cannot be neglected.
-
-The null results reached in this letter could arise from several sources.
-There are theoretically grounded reasons of government effectiveness, democratic understanding, and generical-or-behavioral support to suspect that the relationships are in fact negligible.
-We also identified a number of potential shortcomings in the measurement of democratic support and ways in which the analysis models might be underspecified.
-All of these could and should be explored in future research.
-In any event, the sanguine assessment that readers may draw from Claassen [-@Claassen2020a; -@Claassen2020b]---that the fate of democracies depend on public support, and when eroded, their publics will rally to them---is not supported by the current evidence.
-Those who would defend democracy have no grounds to be complacent.
-
-# References  {-}
-
-<div id = 'refs'></div>
-
-\pagebreak
-
-# Online Supplementary Materials {-}
-# (APPENDIX) Appendix {-}
-# Numeric Results for Replicating Claassen 2020a {#fullAJPS}
-
-```{r num-labelAJPS, eval=TRUE}
-names_coef <- c(
-  "(Intercept)" = "(Intercept)",
-  "plm::lag(Libdem_VD, 1:2)1" = "Democracy[t-1]",
-  "plm::lag(Libdem_VD, 1:2)2"  = "Democracy[t-2]",
-  "plm::lag(SupDem_trim, 1)" = "Support[t-1]",
-  "plm::lag(SupDem_Democ, 1)" = "Support in Democracy",
-  "plm::lag(theta_dem_trim, 1)" = "Support in Democracy",
-  "plm::lag(SupDem_Autoc, 1)" = "Support in Autocracy",
-  "plm::lag(theta_aut_trim, 1)" = "Support in Autocracy",
-  "plm::lag(lnGDP_imp, 1)" = "Log GDP Per Capita[t-1]",
-  "plm::lag(GDP_imp_grth, 1)"  = "GDP Per Capita~growth[t-1]",
-  "plm::lag(Libdem_regUN, 1)" = "Regional Democracy[t-1]",
-  "plm::lag(Pr_Muslim, 1)" = "Percent Muslim[t-1]",
-  "plm::lag(Res_cp_WDI_di, 1)" = "Resource Dependence[t-1]"
-)
-```
-
-```{r num-pointAJPS, results='asis', eval=TRUE}
-tb_result_cls <- purrr::map(result_clsAJPS, ~ {
-  names(.) <- c("tidy", "glance")
-  class(.) <- "modelsummary_list"
-  return(.)})
-
-names(tb_result_cls) <- c("Pooled", "Pooled-Regime", 
-                          "GMM", "GMM-Regime")
-
-modelsummary(tb_result_cls,  
-             statistic = "conf.int",
-             coef_map = names_coef, 
-             output = "latex", 
-             title = "Original") %>%
-
-  kableExtra::kable_styling(font_size = 8) %>% 
-  kableExtra::kable_styling(latex_options = "HOLD_position")
-```
-
-```{r num-pureAJPS, results='asis', eval=TRUE}
-tb_result_pureAJPS <- purrr::map(result_pureAJPS, ~ {
-  names(.) <- c("tidy", "glance")
-  class(.) <- "modelsummary_list"
-  return(.)})
-
-names(tb_result_pureAJPS) <- c("Pooled", "Pooled-Regime", 
-                          "GMM", "GMM-Regime")
-
-modelsummary(tb_result_pureAJPS, 
-             statistic = "conf.int",
-             coef_map = names_coef, 
-             output = "latex", 
-             title = "W. Uncertainty") %>% 
-  kableExtra::kable_styling(latex_options = "HOLD_position")
-```
-
-```{r num-expAJPS, results='asis', eval=TRUE}
-tb_result_expAJPS <- purrr::map(result_expAJPS, ~ {
-  names(.) <- c("tidy", "glance")
-  class(.) <- "modelsummary_list"
-  return(.)})
-
-names(tb_result_expAJPS) <- c("Pooled", "Pooled-Regime", 
-                          "GMM", "GMM-Regime")
-
-modelsummary(tb_result_expAJPS, 
-             statistic = "conf.int",
-             coef_map = names_coef, 
-             output = "latex", 
-             title = "W. Uncertainty and Expanded Data") %>% 
-  kableExtra::kable_styling(latex_options = "HOLD_position")
-```
-
-\blandscape
-
-# Numeric Results for Replicating Claassen 2020b {#fullAPSR}
-
-```{r num-labelAPSR, eval=TRUE}
-names_coef <- c(
-  "(Intercept)" = "(Intercept)",
-  "plm::lag(SupDem_trim, 1:2)1" = "Democratic Mood (t-1)",
-  "plm::lag(SupDem_trim, 1:2)2" = "Democratic Mood (t-2)",
-  "diff(Libdem_z, lag = 1)" = "Liberal Democracy (Difference)",
-  "Libdem_z" = "Liberal Democracy (Difference)",
-  "plm::lag(Libdem_z, 1)" = "Liberal Democracy (t-1)",
-  "diff(Polyarchy_z, lag = 1)" = "Electoral Democracy (Difference)",
-  "Polyarchy_z" = "Electoral Democracy (Difference)",
-  "plm::lag(Polyarchy_z, 1)" = "Electoral Democracy (t-1)",
-  "diff(Liberal_z, lag = 1)" = "Minoritarian Democracy (Difference)",
-  "Liberal_z" = "Minoritarian Democracy (Difference)",
-  "plm::lag(Liberal_z, 1)" = "Minoritarian Democracy (t-1)",
-  "diff(lnGDP_imp, lag = 1)" = "Log GDP per capita (Difference)",
-  "lnGDP_imp" = "Log GDP per capita (Difference)",
-  "plm::lag(lnGDP_imp, 1)" = "Log GDP (t-1)",
-  "diff(Corrup_TI_z, lag = 1)" = "Corruption (Difference)",
-  "Corrup_TI_z" = "Corruption (Difference)",
-  "plm::lag(Corrup_TI_z, 1)" = "Corruption (t-1)"
-)
-```
-
-```{r num-pointAPSR, results='asis', eval=TRUE}
-tb_result_clsAPSR <- map(result_clsAPSR, ~ {
-  names(.) <- c("tidy", "glance")
-  class(.) <- "modelsummary_list"
-  return(.)}) %>% 
-  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
-      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]
-
-names(tb_result_clsAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
-
-modelsummary(tb_result_clsAPSR, 
-             stars = TRUE,
-             coef_map = names_coef, 
-             output = "latex", 
-             title = "Original") %>% 
-  kableExtra::kable_styling(font_size = 7) %>% 
-  kableExtra::kable_styling(latex_options = "HOLD_position")
-```
-
-\elandscape
-
-\blandscape
-
-```{r num-pureAPSR, results='asis', eval=TRUE}
-tb_result_pureAPSR <- purrr:::map(result_pureAPSR, ~ {
-  names(.) <- c("tidy", "glance")
-  class(.) <- "modelsummary_list"
-  return(.)}) %>% 
-  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
-      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]
-
-names(tb_result_pureAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
-
-modelsummary(tb_result_pureAPSR, 
-             statistic = "conf.int",
-             coef_map = names_coef, 
-             output = "latex", 
-             title = "W. Uncertainty") %>% 
-  kableExtra::kable_styling(font_size = 7) %>% 
-  kableExtra::kable_styling(latex_options = "HOLD_position")
-```
-
-\elandscape
-
-\blandscape
-
-```{r num-expAPSR, results='asis', eval=TRUE}
-tb_result_expAPSR <- map(result_expAPSR, ~ {
-  names(.) <- c("tidy", "glance")
-  class(.) <- "modelsummary_list"
-  return(.)}) %>% 
-  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
-      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]
-
-names(tb_result_expAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
-
-modelsummary(tb_result_expAPSR, 
-             statistic = "conf.int",
-             coef_map = names_coef, 
-             output = "latex", 
-             title = "W. Uncertainty and Expanded Data") %>% 
-  kableExtra::kable_styling(font_size = 7) %>% 
-  kableExtra::kable_styling(latex_options = "HOLD_position")
-```
-
-\elandscape
-
-# Data Recollection and Control Uncertainty in Control Variables.
-
-Due to revisions to the underlying datasets (and, possibly, transcription errors), we were not able to achieve a primary replication [@Grossman2020] based on survey data summarized in @Claassen2020a and @Claassen2020b's Dataverse files.
-
-Specifically, we are not able to identify 5 cournty-year surveys, including South Sudan in Arab Barometer Wave 4, Dominican Republic in 2003 Latinobarometer, XXXX, and Spain in 2005 Latinobarometer. 
-In addition, we still have different sample size and number of respondents answering supportively by following approaches of cleanning data and treatment of non-responses described in @Claassen2020a's supplementatry materials.
-Specifically, we used Claassen's year coding to recode 85 unmatching country-year observations and added one more item "strong leader 2" in Arabbarometer which has different response categories but was conflated into "strong leader 1".
-
-V-Dem data was standardized in @Claassen2020b's analyses, but we did not figure out how the standardization was exactly performed.
-We standardized variables using Z-score, and the standardized values are different from Claassen's data.
-
-We also include measurement errors in control variables, including three democratic indices and corruption index.
-We extracted the posterior distributions of democratic indices, including Liberal Democracy,polyarchy, and electoral democracy index, which are provided by [@coppedge2018].
-We drew 900 samples from the distribution of the Corruption Perception Index.
-Since Corruption Perception Index does not provide standard error before 2011, we imputed the missing standard error using the multiplication of a country's corruption index and the ratio of its available maximum standard error to its corresponding index.
-
-# Replication with Alternative Methods Accounting for Uncertainty {#moc}
-
-To ensure the robustness of our analysis, we apply another method to account for uncertainty.
-The method we employ is "method of composition" (MOC).
-It is a common method for Monte Carlo integration, but can also be applied for addressing uncertainty [@Treier2008].
-To compare these two methods, let's denote `y` as a vector of the outcome variable [either institutional democracy in @Claassen2020a or the changes in mass support of democracy in @Claassen2020b]. 
-Let $x$ (variables without subscript are used to denote vectors of observations, viz., $x$ = ($x_1$,......, $x_i$)) be a vector of the explanatory variable (e.g., mass support or institutional democracy) and $\theta$ be the parameter of interest.
-
-Rubin's Rules (RR, the method used in the main article) take variables with measurement error as missing value, and combine the point estimates and standard errors into single values yet accounting for both within and between imputation variances [@Rubin1987].
-
-Rubein's Rules is defined in the following formulas.
-
-\begin{equation}
-\bar{\theta}_{m} = \frac{1}{m}\sum_{i=1}^{m} \theta_{i}.
-\end{equation}
-
-\begin{equation}
-{V}_{B} = \frac{1}{m-1}\sum_{i=1}^{m} (\theta_{i}-\bar{\theta}_{m})^2.
-\end{equation}
-
-\begin{equation}
-{V}_{W} = \frac{1}{m}\sum_{i=1}^{m} SE_{i}^2.
-\end{equation}
-
-\begin{equation}
-{V}_{T} = {V}_{w} +(1+ \frac{1}{m})\frac{V_B}{m}.
-\end{equation}
-
-$\bar{\theta}_{M}$ is the pooled parameter estimate, $m$ is the number of imputed datasets, $V_{B}$ is between imputation variance, $V_{W}$ within imputation variance, $V_{T}$ is total variance.
-
-The general formula for confidence interval (CI) is defined as:
-
-\begin{equation}
-\bar{\theta} \pm t_{df,1-\alpha/2} *\sqrt{V_{T}}.
-\end{equation}
-
-$df$ is calculated by using $df_{Adjusted}$ [@barnard1999] and the Fraction of Missing information, lambda, is derived from between and total variance [@raghunathan2015, @van2018].
-
-\begin{equation}
-{df_{Adjusted}} = \frac{df_{Old}*df_{Observed}}{df_{Old}+df_{Observed}}.
-\end{equation}
-
-\begin{equation}
-{df_{Old}} = \frac{(n-k)+1}{(n-k)+3} * (n-k)(1-lambda).
-\end{equation}
-
-\begin{equation}
-{df_{Observed}} = \frac{(n-k)+1}{(n-k)+3} * (n-k)(1-lambda).
-\end{equation}
-
-\begin{equation}
-{Lambda} = \frac{V_{B}+\frac{V_{B}}{m}}{V_{T}}
-\end{equation}
-
-One main idea behind RR is to account for both within imputation variance and sample variance which is due to the missing data (measurement error in our case).
-
-MOC addresses the same issue from a slightly different angle.
-The method assumes that the explanatory and outcome variables are samples from their estimate functions, and their paired sample follows a joint density [@Tanner1993, p.31].
-From the joint density, one can decomposite the likelihood of the explanatory variable and its parameter to a product of their own probabilities.
-When x is measured with errors $w$, the probability becomes conditional:
-
-\begin{equation}
-\mathcal{L}(\theta, x|y, w) = p(\theta|x,y)p(x|w).
-\end{equation}
-
-Based on this decomposition, one can estimate the marginal density for &\theta&:
-
-\begin{equation}
-\mathcal{L}(\theta|y, x) \propto \int_{\chi} p(\theta|y,x)p(x|w)dx.
-\end{equation}
-
-Again, the gained parameter density can be combined into single values.
-A common way to do so is using the mean of $theta$ as the point estimate, and the variance from the density as the standard error.
-
-```{r mocresult-pureAJPS}
+```{r mocresult-pureAJPS, eval=FALSE}
 
@@
 
-```{r mocresult-expAJPS}
+```{r mocresult-expAJPS, eval=FALSE}
 
@@
 
-```{r plot-mocAJPS, fig.cap= "The Effect of Public Support on Democracy ", eval = TRUE, fig.width=7, fig.height=10, eval=TRUE}
-
+```{r formatResult-AJPS}
 result_pooled <- bind_rows(
   mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Original"),
- mutate(MOCsumm(mocresult_correctAJPS[["pooled"]]), model = "Uncertainty+Corrected"),
+ mutate(MOCsumm(mocresult_correctAJPS[["pooled"]]), model = "W. Uncertainty"),
  mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), model = "Uncertainty+Expanded Data")
@@
   mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_correctAJPS[["gmm"]]), model = "Uncertainty+Corrected"),
+  mutate(MOCsumm(mocresult_correctAJPS[["gmm"]]), model = "W. Uncertainty"),
   mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), model = "Uncertainty+Expanded Data")
@@
     type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Original", "Uncertainty+Corrected", "Uncertainty+Expanded Data")))
-
-terms <- factor(rev(c("Democracy[t-1]",
-                      "Democracy[t-2]",
-                      "Support[t-1]",
-                      "Log~GDP~per~capita[t-1]",
-                      "GDP~per~capita~growth[t-1]",
-                      "Regional~democracy[t-1]",
-                      "Percent~Muslim[t-1]",
-                      "Resource~dependence[t-1]")), levels =
-                  rev(c("Democracy[t-1]",
-                        "Democracy[t-2]",
-                        "Support[t-1]",
-                        "Log~GDP~per~capita[t-1]",
-                        "GDP~per~capita~growth[t-1]",
-                        "Regional~democracy[t-1]",
-                        "Percent~Muslim[t-1]",
-                        "Resource~dependence[t-1]")))
-
-plot_AJPS1 <- dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms))) +
-  labs(
-    title = "DV: V-Dem Liberal Democracy Index",
-    subtitle = "Pooled"
-  ) +
-  facet_wrap(~type, scales = "free_x") + 
-  theme(legend.position = "none")
-
-###########Regime
+    model = factor(model, levels = c("Original", "W. Uncertainty", "Uncertainty+Expanded Data")))
+
+result_ajpsPooled <- result_pooledAJPS %>% 
+    filter(type == "Pooled")
+
 result_regime <- bind_rows(
   mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_correctAJPS[["pooled-regime"]]), model = "Uncertainty+Corrected"),
+  mutate(MOCsumm(mocresult_correctAJPS[["pooled-regime"]]), model = "W. Uncertainty"),
   mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), model = "Uncertainty+Expanded Data")
@@
   mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_correctAJPS[["gmm-regime"]]), model = "Uncertainty+Corrected"),
+  mutate(MOCsumm(mocresult_correctAJPS[["gmm-regime"]]), model = "W. Uncertainty"),
  mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), model = "Uncertainty+Expanded Data")
@@
     type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Original","Uncertainty+Corrected", "Uncertainty+Expanded Data")))
-terms2 <- factor(rev(c("Democracy[t-1]",
-                       "Democracy[t-2]",
-                       "Support[t-1] (democracies~only)",
-                       "Support[t-1] (autocracies~only)",
-                       "Log~GDP~per~capita[t-1]",
-                       "GDP~per~capita~growth[t-1]",
-                       "Regional~democracy[t-1]",
-                       "Percent~Muslim[t-1]",
-                       "Resource~dependence[t-1]")), levels =
-                   rev(c("Democracy[t-1]",
-                         "Democracy[t-2]",
-                         "Support[t-1] (democracies~only)",
-                         "Support[t-1] (autocracies~only)",
-                         "Log~GDP~per~capita[t-1]",
-                         "GDP~per~capita~growth[t-1]",
-                         "Regional~democracy[t-1]",
-                         "Percent~Muslim[t-1]",
-                         "Resource~dependence[t-1]")))
-plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms2))) +
-  labs(
-    title = "",
-    subtitle = "Regime Specified"
+    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data")))
+
+result_ajpsRegime <- result_regimeAJPS %>%
+    filter(type == "Pooled") %>% 
+    mutate(type = "Regime Specified")
+
+```
+
+```{r coefName-AJPS}
+index_coefName <- c(
+    `Democracy\n (t-1)` = "Democracy[t-1]",
+    `Democracy\n (t-2)` = "Democracy[t-2]",
+    `Support\n (t-1)` = "Support[t-1]",
+    `Support\n demo only\n (t-1)` = "Support[t-1](demo~only)",
+    `Support\n auto only\n (t-1)` = "Support[t-1](auto~only)",
+    `Log GDP\n per capita\n (t-1)` = "Log~GDP~per~capita[t-1]",
+    `GDP per\n capita growth\n (t-1)` = "GDP~per~capita~growth[t-1]",
+    `Regional\n democracy\n (t-1)` = "Regional~democracy[t-1]",
+    `Percent\n Muslim\n (t-1)` = "Percent~Muslim[t-1]",
+    `Resource\n dependence\n (t-1)` = "Resource~dependence[t-1]"
+)
+```
+
+```{r plot-mainAJPS, fig.cap= "The Effect of Public Support on Democracy with Uncertainty", fig.width=7, fig.height=10, fig.align='center'}
+
+type_model <-
+  c("Original", "W. Uncertainty", "Uncertainty+Expanded Data")
+
+df_plot <- bind_rows(result_ajpsPooled, result_ajpsRegime) %>% 
+    mutate(term = index_coefName[term],
+           term = factor(term, levels = unique(index_coefName)))
+
+dwplot(df_plot) +
+    geom_vline(xintercept = 0,
+               colour = "grey80",
+               linetype = 2) +
+    theme_minimal() +
+    ggtitle("DV: Liberal Democracy (Vdem)") +
+    xlab("Coefficient Estimate") +
+    theme(
+        axis.title.y = element_blank(),
+        legend.position = "bottom",
+      legend.title = element_blank()
     ) +
-  facet_wrap(~type, scales = "free_x") +
-  theme(legend.position = "bottom", 
-        legend.title = element_blank())
-legend <- get_legend(plot_AJPS2)
-plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
-grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
-
-```
-
-```{r mocresult-pureAPSR}
+    scale_color_gb(palette = "digitMixed") +
+    facet_wrap(~ type)
+
+```
+
+The importance of accounting for the measurement uncertainty appear more evident when the relevant variable plays as the outcome variable. 
+In Figure \@ref(fig:plot-mainAPSR), we examine the thermostatic model of democratic support per @Claassen2020b [p. 47, Models 1.1 and 1.2]. 
+When the uncertainty is ignored, the coefficient of $\Delta$liberal democracy (the uppermost set), the yearly changes of the institutional feature is negative inferring that the change in democratic mood decreases as change in democracy increases and vice versa.
+However, when the measurement uncertainty is properly accounted (the middle set), the point estimate shifts towards zero and the coefficient is no longer significant.
+More data (the lowermost set), again, only adjusts the confidence intervals but not direction nor significance.
+
+```{r pointAPSR}
+# Reusing the sd.plm object, thus input data here rather than earlier
+
+load(here::here("data", "dem_mood_apsr.RData"))
+sd.plm <- pdata.frame(x, index = c("Country", "Year"))
+
+ls_ivECM <- c("diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)", 
+              "diff(Polyarchy_z, lag = 1) + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)")
+ls_ctrlECM <- c("", " + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1)")
+
+ls_eqECM <- glue("diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)") %>% 
+  outer(ls_ctrlECM, paste0) %>% 
+  as.vector()
+
+ls_ivFD <- c("Libdem_z",
+             "Polyarchy_z + Liberal_z")
+
+ls_ctrlFD <- c("", " + Corrup_TI_z")
+
+ls_eqFD <- glue("SupDem_trim ~ {ls_ivFD} + lnGDP_imp") %>% 
+  outer(ls_ctrlFD, paste0) %>% 
+  as.vector()
+
+ls_mod <- c(
+  glue("plm({ls_eqECM}, model = 'pooling', data = sd.plm)"),
+  glue("plm({ls_eqFD}, model = 'fd', index = 'Country', data = sd.plm)")
+)
+
+df_result_clsAPSR <- map(ls_mod, function(mod) {
+  result <- eval(parse(text = mod))
+})
+
+result_clsAPSR <- map(df_result_clsAPSR, function(aResult) {
+  tidy_result <- tidy(aResult, conf.int = TRUE) %>% 
+    mutate(std.error = vcovHC_se(aResult))
+
+  glance_result <- glance.plm(aResult)
+
+  ls_result <- list(tidy_result, glance_result)
+})
+
+names(result_clsAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", 
+                           "fd1", "fd-regime1", "fd2", "fd-regime2")
+
+saveRDS(result_clsAPSR, file = here("output", "estimates_clsMeanAPSR.RDS"))
+```
+
+```{r model-APSR}
+ls_ivECM <- c("diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)", 
+              "diff(Polyarchy_z, lag = 1) + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)")
+ls_ctrlECM <- c("", " + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1)")
+
+ls_eqECM <- glue("diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)") %>% 
+  outer(ls_ctrlECM, paste0) %>% 
+  as.vector()
+
+ls_ivFD <- c("Libdem_z",
+             "Polyarchy_z + Liberal_z")
+
+ls_ctrlFD <- c("", " + Corrup_TI_z")
+
+ls_eqFD <- glue("diff(SupDem_trim, lag = 1) ~ {ls_ivFD} + lnGDP_imp") %>% 
+  outer(ls_ctrlFD, paste0) %>% 
+  as.vector()
+
+ls_mod_apsrCLS <- c(
+  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
+  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
+)
+```
+
+```{r mocresult-pureAPSR, eval=FALSE}
 
@@
 
-```{r mocresult-expAPSR}
+```{r mocresult-expAPSR, eval=FALSE}
 
@@
 
-```{r plot-mocAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", eval = TRUE, fig.width=7, fig.height=12, eval=TRUE}
+```{r formatResult-APSR}
+# Pooled---------------------------------------
 
@@
   mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["pooled1"]]), model = "Uncertainty+Corrected"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["pooled1"]]), model = "W. Uncertainty"),
   mutate(MOCsumm2(mocresult_expAPSR[["pooled1"]]), model = "Uncertainty+Expanded Data")
@@
   mutate(result_clsAPSR[["fd1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["fd1"]]), model = "Uncertainty+Corrected"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["fd1"]]), model = "W. Uncertainty"),
   mutate(MOCsumm2(mocresult_expAPSR[["fd1"]]), model = "Uncertainty+Expanded Data")
@@
     type = factor(type,  levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Original","Uncertainty+Corrected", "Uncertainty+Expanded Data"))
-  )
-
-terms1 <- factor(rev(c("Support[t-1]",
-                       "Support[t-2]",
-                       "Delta~Liberal~democracy",
-                       "Liberal~democracy[t-1]",
-                       "Delta~Log~GDP~per~capita",
-                       "Log~GDP[t-1]")),
-                 levels = rev(c("Support[t-1]",
-                                "Support[t-2]",
-                                "Delta~Liberal~democracy",
-                                "Liberal~democracy[t-1]",
-                                "Delta~Log~GDP~per~capita",
-                                "Log~GDP[t-1]")))
-plot_APSR1 <- dwplot(result_APSR1, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms1))) +
-  labs(
-    title = "DV: The Change of Public Support for Democracy",
-    subtitle = "Pooled"
-  ) +
-  facet_wrap(~type, drop=T,scales = "free_x") +
-  theme(legend.position = "none")
-
-############################ Regime specified####
+    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data"))
+  )
+
+result_apsrPooled <- result_APSR1 %>% 
+    filter(type == "ECM") %>% 
+    mutate(type = "Pooled")
+
+# Institution----------------------------------
 
@@
   mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime1"]]), model = "Uncertainty+Corrected"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime1"]]), model = "W. Uncertainty"),
   mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime1"]]), model = "Uncertainty+Expanded Data")
@@
   mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime1"]]), model = "Uncertainty+Corrected"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime1"]]), model = "W. Uncertainty"),
   mutate(MOCsumm2(mocresult_expAPSR[["fd-regime1"]]), model = "Uncertainty+Expanded Data")
@@
     type = factor(type,  levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Original","Uncertainty+Corrected", "Uncertainty+Expanded Data"))
-  )
-terms3 <- factor(rev(c("Support[t-1]",
-                       "Support[t-2]",
-                       "Delta~Electoral~democracy",
-                       "Electoral~democracy[t-1]",
-                       "Delta~Minoritarian~democracy",
-                       "Minoritarian~democracy[t-1]",
-                       "Delta~Log~GDP~per~capita",
-                       "Log~GDP[t-1]")),
-                 levels = rev(c("Support[t-1]",
-                                "Support[t-2]",
-                                "Delta~Electoral~democracy",
-                                "Electoral~democracy[t-1]",
-                                "Delta~Minoritarian~democracy",
-                                "Minoritarian~democracy[t-1]",
-                                "Delta~Log~GDP~per~capita",
-                                "Log~GDP[t-1]")))
-plot_RegAPSR1 <- dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms3))) +
-  labs(
-    title = "",
-    subtitle = "Institution Specified"
-  ) +
-  facet_wrap(~type, scales = "free_x") + 
-  theme(legend.position = "none")
-
-#########Corruption
+    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data"))
+  )
+
+result_apsrRegime <- result_RegAPSR1 %>% 
+    filter(type == "ECM") %>% 
+    mutate(type = "Institution Specified")
+
+# Pooled-corruption------------------------------
 
@@
   mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["pooled2"]]), model = "Uncertainty+Corrected"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["pooled2"]]), model = "W. Uncertainty"),
   mutate(MOCsumm2(mocresult_expAPSR[["pooled2"]]), model = "Uncertainty+Expanded Data")
@@
   mutate(result_clsAPSR[["fd2"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["fd2"]]), model = "Uncertainty+Corrected"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["fd2"]]), model = "W. Uncertainty"),
   mutate(MOCsumm2(mocresult_expAPSR[["fd2"]]), model = "Uncertainty+Expanded Data")
@@
     type = factor(type,  levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Original","Uncertainty+Corrected", "Uncertainty+Expanded Data"))
-  )
-terms2 <- factor(rev(c("Support[t-1]",
-                       "Support[t-2]",
-                       "Delta~Liberal~democracy",
-                       "Liberal~democracy[t-1]",
-                       "Delta~Log~GDP~per~capita",
-                       "Log~GDP[t-1]",
-                       "Delta~Corruption",
-                       "Corruption[t-1]")),
-                 levels = rev(c("Support[t-1]",
-                                "Support[t-2]",
-                                "Delta~Liberal~democracy",
-                                "Liberal~democracy[t-1]",
-                                "Delta~Log~GDP~per~capita",
-                                "Log~GDP[t-1]",
-                                "Delta~Corruption",
-                                "Corruption[t-1]")))
-plot_APSR2 <- dwplot(result_APSR2, dodge_size = 0.8, by_2sd = FALSE) +
-  scale_y_discrete(labels = parse(text = levels(terms2))) +
-  labs(
-    title = "",
-    subtitle = "W. Corruption"
-  ) +
-  facet_wrap(~type, scales = "free_x") +
-  theme(legend.position = "none")
-
-#########Regime + Corruption
+    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data"))
+  )
+
+# Institution Corruption--------------------------------
 
@@
   mutate(result_clsAPSR[["pooled-regime2"]][[1]][,1:3], model = "Original"),
- mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime2"]]), model = "Uncertainty+Corrected"),
+ mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime2"]]), model = "W. Uncertainty"),
   mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime2"]]), model = "Uncertainty+Expanded Data")) %>%
@@
   mutate(result_clsAPSR[["fd-regime2"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime2"]]), model = "Uncertainty+Corrected"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime2"]]), model = "W. Uncertainty"),
   mutate(MOCsumm2(mocresult_expAPSR[["fd-regime2"]]), model = "Uncertainty+Expanded Data")) %>% 
@@
     type = factor(type,  levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Original","Uncertainty+Corrected", "Uncertainty+Expanded Data"))
-  )
-terms4 <- factor(rev(c("Support[t-1]",
+    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data"))
+  )
+```
+
+```{r coefName-APSR}
+index_coefName <- c(
+    `Democratic Mood\n (t-1)` = "Support[t-1]",
+    `Democratic Mood\n (t-2)` = "Support[t-2]",
+    `Liberal Democracy\n (Difference)` = "Delta~Liberal~democracy",
+    `Liberal Democracy\n (t-1)` = "Liberal~democracy[t-1]",
+    `Electoral Democracy\n (Difference)` = "Delta~Electoral~democracy",
+    `Electoral Democracy\n (t-1)` = "Electoral~democracy[t-1]",
+    `Minoritarian Democracy\n (Difference)` = "Delta~Minoritarian~democracy",
+    `Minoritarian Democracy\n (t-1)` = "Minoritarian~democracy[t-1]",
+    `Log GDP\n per capita\n (Difference)` = "Delta~Log~GDP~per~capita",
+    `Log GDP\n (t-1)` = "Log~GDP[t-1]"
+)
+```
+
+```{r plot-mainAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", fig.width=7, fig.height=10}
+type_model <-
+    c("Original", "W. Uncertainty", "Uncertainty+Expanded Data")
+
+df_plot <- bind_rows(result_apsrPooled, result_apsrRegime) %>%
+    mutate(
+        term = index_coefName[term],
+        term = factor(term, levels = unique(index_coefName)),
+        type = factor(type, levels = c("Pooled", "Institution Specified"))
+    )
+
+dwplot(df_plot) +
+    geom_vline(xintercept = 0,
+               colour = "grey80",
+               linetype = 2) +
+    ggtitle("DV: The Change of Public Support for Democracy") +
+    xlab("Coefficient Estimate") +
+    theme(
+        axis.title.y = element_blank(),
+        legend.position = "bottom",
+        legend.title = element_blank()
+    ) +
+    facet_wrap(~ type) +
+    scale_color_gb(palette = "digitMixed")
+
+```
+
+# Discussion
+
+In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support has a positive effect on democracy and change in democracy a negative effect on change in support are not empirically supported once measurement uncertainty is taken into account, even when more data are used.
+
+There are theoretical explanations for the null results.
+With regard to how levels of democracy affect public support, we note that even the proponents of the classic argument did not contend that the mere existence of democratic institutions, no matter how consistently feckless and ineffective, would generate support among the public: instead, they maintained, public support would be gained through experience with government performance that was generally effective [@lipset_social_1959, 86-89; @Easton1965, 119-120].
+There is some empirical support for this, with government effectiveness positively related to public support among democracies and negatively related in non-democracies [@Magalhaes2014]. 
+The finding of @Krieckhaus2014 that income inequality is strongly negatively related to public support in democracies suggests that performance regarding redistribution is particularly important.
+Relatedly, on the reverse part of the classic argument, @Qi2011 suggests that democratic support alone cannot be expected to generate democratic change and oppose backsliding.
+Instead, that work contends, it is the combination of democratic support and dissatisfaction with current regime performance that generates demand for greater democracy.
+The effects of public support also have cultural-bound.
+@Brunkert2019 contends outspoken support for democracy is a "deceptive indicator of public's affinity to democracy" [423] and finds public support has neither pro-democratic nor anti-authoritarian effect without controlling emancipative values.
+Empirical results show that the meaning of support for democracy is dependent on emancipation values and is reversed to its own negation in a society with weak emancipative values [see, e.g.,@Kirsch2019, 83-85].
+And we must be open to the possibility that no theoretical elaboration, no respecification of these models will reveal relationships between public opinion and democracy.
+Democratic backsliding may simply be primarily a matter of elite decisionmaking [see, e.g., @levitsky_how_2018].
+
+There are several potential methodological explanations for these null results as well.
+One issue is that the survey items employed---which ask respondents to assess the desirability or appropriateness of democracy, to compare democracy to some undemocratic alternative, or to assess one of these alternatives---may not capture every aspect of democratic support necessary for it to play its hypothesized roles in the classic theory.
+If only those who profess to prefer democracy to its alternatives _and also_ value freedom of expression, freedom of association, and pluralism of opinion will take appropriate action when democracy is threatened, then this measure is inadequate to its purpose [see, e.g., @Schedler2007].
+Moreover, given the multi-faceted nature of democratic attitudes, even the inclusion of such questions in unidimensional public opinion models such as those provided by @Claassen2019 or @Solt2020a are unlikely to be sufficient [see, e.g., @Wuttke2020].
+Another issue is that even if these survey questions do capture support for the generic concept of democracy, these measurement models might still be incapable of suitably capturing democratic support due to the variation in understanding the concept across countries or over time within countries [@Wuttke2021].
+Yet another is that this measure provides no assessment of the _relative_ importance the public affords democracy.
+It provides no information on the extent to which other values, such as policy preferences or partisanship, weigh more heavily---and there is growing evidence that, at least in the United States, there are many for whom these other considerations excuse substantial transgressions against democracy [see @bartels_ethnic_2020; @Carey2020; @graham_democracy_2020; @McCoy2020].
+Regardless, these explanations indicate that there remains much work to be done in the empirical study of public support and democracy.
+
+# Conclusion
+
+In this letter, we reexamine the findings from Claassen [-@Claassen2020a; -@Claassen2020b], two articles that maintain that public support helps the survival of democracy and democratic development has a thermostatic effect on public support.
+We demonstrate the importance of incorporating measurement uncertainty in analyzing the relationship between public support and democracy.
+Taking uncertainty into account rendered both articles' conclusions without empirical support, even when we added considerable more data.
+
+This points to the absolute necessity of incorporating measurement uncertainty into analyses that include latent variables.
+Measurement issues have never had a prominent place in comparative political studies because they need more time to estimate models, but they ground the quality of data and the basis of analysis [@stegmueller2011, 484].
+As the use of latent variables grows more common in political science, both researchers and readers should be aware that these variables' concomitant measurement uncertainty cannot be neglected.
+
+The null results reached in this letter could arise from several sources.
+There are theoretically grounded reasons of government effectiveness, democratic understanding, and generical-or-behavioral support to suspect that the relationships are in fact negligible.
+We also identified a number of potential shortcomings in the measurement of democratic support and ways in which the analysis models might be underspecified.
+All of these could and should be explored in future research.
+In any event, the sanguine assessment that readers may draw from Claassen [-@Claassen2020a; -@Claassen2020b]---that the fate of democracies depend on public support, and when eroded, their publics will rally to them---is not supported by the current evidence.
+Those who would defend democracy have no grounds to be complacent.
+
+# References  {-}
+
+<div id = 'refs'></div>
+
+\pagebreak
+
+# Online Supplementary Materials {-}
+# (APPENDIX) Appendix {-}
+# Data Recollection and Control Uncertainty in Control Variables.
+
+Due to revisions to the underlying datasets (and, possibly, transcription errors), we were not able to achieve a primary replication [@Grossman2020] based on survey data summarized in @Claassen2020a and @Claassen2020b's Dataverse files.
+
+Specifically, we are not able to identify 5 cournty-year surveys, including South Sudan in Arab Barometer Wave 4, Dominican Republic in 2003 Latinobarometer, XXXX, and Spain in 2005 Latinobarometer. 
+In addition, we still have different sample size and number of respondents answering supportively by following approaches of cleanning data and treatment of non-responses described in @Claassen2020a's supplementatry materials.
+Specifically, we used Claassen's year coding to recode 85 unmatching country-year observations and added one more item "strong leader 2" in Arabbarometer which has different response categories but was conflated into "strong leader 1".
+
+V-Dem data was standardized in @Claassen2020b's analyses, but we did not figure out how the standardization was exactly performed.
+We standardized variables using Z-score, and the standardized values are different from Claassen's data.
+
+We also include measurement errors in control variables, including three democratic indices and corruption index.
+We extracted the posterior distributions of democratic indices, including Liberal Democracy,polyarchy, and electoral democracy index, which are provided by [@coppedge2018].
+We drew 900 samples from the distribution of the Corruption Perception Index.
+Since Corruption Perception Index does not provide standard error before 2011, we imputed the missing standard error using the multiplication of a country's corruption index and the ratio of its available maximum standard error to its corresponding index.
+
+# Replication with Alternative Methods Accounting for Uncertainty {#moc}
+
+To ensure the robustness of our analysis, we apply another method to account for uncertainty.
+The method we employ is "method of composition" (MOC).
+It is a common method for Monte Carlo integration, but can also be applied for addressing uncertainty [@Treier2008].
+To compare these two methods, let's denote `y` as a vector of the outcome variable [either institutional democracy in @Claassen2020a or the changes in mass support of democracy in @Claassen2020b]. 
+Let $x$ (variables without subscript are used to denote vectors of observations, viz., $x$ = ($x_1$,......, $x_i$)) be a vector of the explanatory variable (e.g., mass support or institutional democracy) and $\theta$ be the parameter of interest.
+
+Rubin's Rules (RR, the method used in the main article) take variables with measurement error as missing value, and combine the point estimates and standard errors into single values yet accounting for both within and between imputation variances [@Rubin1987].
+
+Rubein's Rules is defined in the following formulas.
+
+\begin{equation}
+\bar{\theta}_{m} = \frac{1}{m}\sum_{i=1}^{m} \theta_{i}.
+\end{equation}
+
+\begin{equation}
+{V}_{B} = \frac{1}{m-1}\sum_{i=1}^{m} (\theta_{i}-\bar{\theta}_{m})^2.
+\end{equation}
+
+\begin{equation}
+{V}_{W} = \frac{1}{m}\sum_{i=1}^{m} SE_{i}^2.
+\end{equation}
+
+\begin{equation}
+{V}_{T} = {V}_{w} +(1+ \frac{1}{m})\frac{V_B}{m}.
+\end{equation}
+
+$\bar{\theta}_{M}$ is the pooled parameter estimate, $m$ is the number of imputed datasets, $V_{B}$ is between imputation variance, $V_{W}$ within imputation variance, $V_{T}$ is total variance.
+
+The general formula for confidence interval (CI) is defined as:
+
+\begin{equation}
+\bar{\theta} \pm t_{df,1-\alpha/2} *\sqrt{V_{T}}.
+\end{equation}
+
+$df$ is calculated by using $df_{Adjusted}$ [@barnard1999] and the Fraction of Missing information, lambda, is derived from between and total variance [@raghunathan2015, @van2018].
+
+\begin{equation}
+{df_{Adjusted}} = \frac{df_{Old}*df_{Observed}}{df_{Old}+df_{Observed}}.
+\end{equation}
+
+\begin{equation}
+{df_{Old}} = \frac{(n-k)+1}{(n-k)+3} * (n-k)(1-lambda).
+\end{equation}
+
+\begin{equation}
+{df_{Observed}} = \frac{(n-k)+1}{(n-k)+3} * (n-k)(1-lambda).
+\end{equation}
+
+\begin{equation}
+{Lambda} = \frac{V_{B}+\frac{V_{B}}{m}}{V_{T}}
+\end{equation}
+
+One main idea behind RR is to account for both within imputation variance and sample variance which is due to the missing data (measurement error in our case).
+
+MOC addresses the same issue from a slightly different angle.
+The method assumes that the explanatory and outcome variables are samples from their estimate functions, and their paired sample follows a joint density [@Tanner1993, p.31].
+From the joint density, one can decomposite the likelihood of the explanatory variable and its parameter to a product of their own probabilities.
+When x is measured with errors $w$, the probability becomes conditional:
+
+\begin{equation}
+\mathcal{L}(\theta, x|y, w) = p(\theta|x,y)p(x|w).
+\end{equation}
+
+Based on this decomposition, one can estimate the marginal density for &\theta&:
+
+\begin{equation}
+\mathcal{L}(\theta|y, x) \propto \int_{\chi} p(\theta|y,x)p(x|w)dx.
+\end{equation}
+
+Again, the gained parameter density can be combined into single values.
+A common way to do so is using the mean of $theta$ as the point estimate, and the variance from the density as the standard error.
+
+```{r plot-mocAJPS, fig.cap= "The Effect of Public Support on Democracy ", eval = TRUE, fig.width=7, fig.height=10}
+terms <- factor(rev(
+    c(
+        "Democracy[t-1]",
+        "Democracy[t-2]",
+        "Support[t-1]",
+        "Log~GDP~per~capita[t-1]",
+        "GDP~per~capita~growth[t-1]",
+        "Regional~democracy[t-1]",
+        "Percent~Muslim[t-1]",
+        "Resource~dependence[t-1]"
+    )
+), levels =
+    rev(
+        c(
+            "Democracy[t-1]",
+            "Democracy[t-2]",
+            "Support[t-1]",
+            "Log~GDP~per~capita[t-1]",
+            "GDP~per~capita~growth[t-1]",
+            "Regional~democracy[t-1]",
+            "Percent~Muslim[t-1]",
+            "Resource~dependence[t-1]"
+        )
+    ))
+
+plot_AJPS1 <-
+    dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
+    scale_y_discrete(labels = parse(text = levels(terms))) +
+    labs(title = "DV: V-Dem Liberal Democracy Index",
+         subtitle = "Pooled") +
+    facet_wrap( ~ type, scales = "free_x") +
+    theme(legend.position = "none") +
+    scale_color_gb(palette = "digitMixed")
+
+terms2 <- factor(rev(
+    c(
+        "Democracy[t-1]",
+        "Democracy[t-2]",
+        "Support[t-1] (democracies~only)",
+        "Support[t-1] (autocracies~only)",
+        "Log~GDP~per~capita[t-1]",
+        "GDP~per~capita~growth[t-1]",
+        "Regional~democracy[t-1]",
+        "Percent~Muslim[t-1]",
+        "Resource~dependence[t-1]"
+    )
+), levels =
+    rev(
+        c(
+            "Democracy[t-1]",
+            "Democracy[t-2]",
+            "Support[t-1] (democracies~only)",
+            "Support[t-1] (autocracies~only)",
+            "Log~GDP~per~capita[t-1]",
+            "GDP~per~capita~growth[t-1]",
+            "Regional~democracy[t-1]",
+            "Percent~Muslim[t-1]",
+            "Resource~dependence[t-1]"
+        )
+    ))
+
+plot_AJPS2 <-
+    dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
+    scale_y_discrete(labels = parse(text = levels(terms2))) +
+    labs(title = "",
+         subtitle = "Regime Specified") +
+    facet_wrap( ~ type, scales = "free_x") +
+    theme(legend.position = "bottom",
+          legend.title = element_blank()) +
+    scale_color_gb(palette = "digitMixed")
+
+legend <- get_legend(plot_AJPS2)
+
+plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
+
+grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
+```
+
+\blandscape
+
+```{r plot-mocAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", eval = TRUE, fig.width=10, fig.height=10}
+terms1 <- factor(rev(
+    c(
+        "Support[t-1]",
+        "Support[t-2]",
+        "Delta~Liberal~democracy",
+        "Liberal~democracy[t-1]",
+        "Delta~Log~GDP~per~capita",
+        "Log~GDP[t-1]"
+    )
+),
+levels = rev(
+    c(
+        "Support[t-1]",
+        "Support[t-2]",
+        "Delta~Liberal~democracy",
+        "Liberal~democracy[t-1]",
+        "Delta~Log~GDP~per~capita",
+        "Log~GDP[t-1]"
+    )
+), 
+labels = rev(
+    c(
+        "Support[t-1]",
+        "Support[t-2]",
+        "Delta~Liberal~Dem",
+        "Liberal~Dem[t-1]",
+        "Delta~Log~GDP~per~capita",
+        "Log~GDP[t-1]"
+    )
+))
+
+plot_APSR1 <-
+    dwplot(result_APSR1, dodge_size = 0.8, by_2sd = FALSE) +
+    scale_y_discrete(labels = parse(text = levels(terms1))) +
+    labs(title = "DV: The Change of Public Support for Democracy",
+         subtitle = "Pooled") +
+    facet_wrap( ~ type, drop = T, scales = "free_x") +
+    theme(legend.position = "none") +
+    scale_color_gb(palette = "digitMixed")
+
+terms3 <- factor(rev(
+    c(
+        "Support[t-1]",
+        "Support[t-2]",
+        "Delta~Electoral~democracy",
+        "Electoral~democracy[t-1]",
+        "Delta~Minoritarian~democracy",
+        "Minoritarian~democracy[t-1]",
+        "Delta~Log~GDP~per~capita",
+        "Log~GDP[t-1]"
+    )
+),
+levels = rev(
+    c(
+        "Support[t-1]",
+        "Support[t-2]",
+        "Delta~Electoral~democracy",
+        "Electoral~democracy[t-1]",
+        "Delta~Minoritarian~democracy",
+        "Minoritarian~democracy[t-1]",
+        "Delta~Log~GDP~per~capita",
+        "Log~GDP[t-1]"
+    )
+),
+labels = rev(
+    c(
+        "Support[t-1]",
+        "Support[t-2]",
+        "Delta~Electoral",
+        "Electoral[t-1]",
+        "Delta~Minoritarian",
+        "Minoritarian[t-1]",
+        "Delta~Log~GDP~per~capita",
+        "Log~GDP[t-1]"
+    )
+)
+)
+
+plot_RegAPSR1 <-
+    dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
+    scale_y_discrete(labels = parse(text = levels(terms3))) +
+    labs(title = "",
+         subtitle = "Institution Specified") +
+    facet_wrap( ~ type, scales = "free_x") +
+    theme(legend.position = "none") +
+    scale_color_gb(palette = "digitMixed")
+
+terms2 <- factor(rev(
+    c(
+        "Support[t-1]",
+        "Support[t-2]",
+        "Delta~Liberal~democracy",
+        "Liberal~democracy[t-1]",
+        "Delta~Log~GDP~per~capita",
+        "Log~GDP[t-1]",
+        "Delta~Corruption",
+        "Corruption[t-1]"
+    )
+),
+levels = rev(
+    c(
+        "Support[t-1]",
+        "Support[t-2]",
+        "Delta~Liberal~democracy",
+        "Liberal~democracy[t-1]",
+        "Delta~Log~GDP~per~capita",
+        "Log~GDP[t-1]",
+        "Delta~Corruption",
+        "Corruption[t-1]"
+    )
+),
+labels = rev(
+    c(
+        "Support[t-1]",
+        "Support[t-2]",
+        "Delta~Liberal~Dem",
+        "Liberal~Dem[t-1]",
+        "Delta~Log~GDP~per~capita",
+        "Log~GDP[t-1]",
+        "Delta~Corruption",
+        "Corruption[t-1]"
+    )
+))
+
+plot_APSR2 <-
+    dwplot(result_APSR2, dodge_size = 0.8, by_2sd = FALSE) +
+    scale_y_discrete(labels = parse(text = levels(terms2))) +
+    labs(title = "",
+         subtitle = "W. Corruption") +
+    facet_wrap( ~ type, scales = "free_x") +
+    theme(legend.position = "none") +
+    scale_color_gb(palette = "digitMixed")
+
+terms4 <- factor(rev(
+    c(
+        "Support[t-1]",
         "Support[t-2]",
@@
         "Delta~Corruption",
-                       "Corruption[t-1]")),
-                 levels = rev(c("Support[t-1]",
+        "Corruption[t-1]"
+    )
+),
+levels = rev(
+    c(
+        "Support[t-1]",
         "Support[t-2]",
@@
         "Delta~Corruption",
-                                "Corruption[t-1]")))
-plot_RegAPSR2 <- dwplot(result_RegAPSR2, dodge_size = 0.8, by_2sd = FALSE) +
+        "Corruption[t-1]"
+    )
+),
+labels = rev(
+    c(
+        "Support[t-1]",
+        "Support[t-2]",
+        "Delta~Electoral",
+        "Electoral[t-1]",
+        "Delta~Minoritarian",
+        "Minoritarian[t-1]",
+        "Delta~Log~GDP",
+        "Log~GDP[t-1]",
+        "Delta~Corruption",
+        "Corruption[t-1]"
+    )
+))
+
+plot_RegAPSR2 <-
+    dwplot(result_RegAPSR2, dodge_size = 0.8, by_2sd = FALSE) +
     scale_y_discrete(labels = parse(text = levels(terms4))) +
-  labs(
-    title = "",
-    subtitle = "Institution Specified w. Corruption"
-  ) +
-  facet_wrap(~type, scales = "free_x") +
+    labs(title = "",
+         subtitle = "Institution Specified w. Corruption") +
+    facet_wrap( ~ type, scales = "free_x") +
     theme(legend.position = "bottom",
-        legend.title = element_blank())
+          legend.title = element_blank()) +
+    scale_color_gb(palette = "digitMixed")
 
@@
 
-grid.arrange(plot_APSR1, plot_APSR2, plot_RegAPSR1, plot_RegAPSR2, legend, ncol = 1)
-
-```
+grid.arrange(plot_APSR1,
+             plot_APSR2,
+             plot_RegAPSR1,
+             plot_RegAPSR2,
+             legend,
+             ncol = 2)
+```
+
+\elandscape
 

### 2021-08-05 paper/dcpo_demsupport.Rmd
Revised the content to match MOC

@@
 citation_package: natbib
-fontsize: 11pt
+fontsize: 12pt
+indent: true
 linestretch: 1.5 # double spacing using linestretch 1.5
@@
 Second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.
-As the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.
-
-## Data Recollection and Incorporating Uncertainty
-
-Despite the great effort of collecting data and identifying differences, we could not entirely achieve a primary replication [see @Grossman2020, p. 18] based on @Claassen2020a's Dataverse materials.
-Our replication data has differences in number of country-year surveys and in sample size.
-Specifically, we have five fewer observations, three of which are no longer available in original survey data and two seem to have never existed, and one more survey item which was conflated in original data [see Online Supplementary Material].
+In the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.
+
+It is worth to note that, despite the great effort of collecting data and identifying differences, we could not reach a completely primary replication of @Claassen2020a's Dataverse materials.
+Specifically, we have five fewer observations, three of which are no longer available in original survey data and two seem to have never existed, and one more survey item which was conflated in original data.
+(See more details in Online Supplementary Material \@ref(dgp).)
+Nevertheless, given there are over 2000 observations involved in the analysis, the five missing should not make a meaningful difference.
+
+## Uncertainty Incorporation
 
@@
 254].
-
 Following this line, after replicating the original analyses with point estimates, we incorporate uncertainty in analysis models using our replication data.
@@
 We then duplicate each article's analysis dataset of variables "without" measurement error 900 times, and assign them to each a different random draw from the distributions of variables with measurement error.
-We estimate each analysis model repeatedly on its respective collection of the datasets, and then make inferences from the distribution of parameter estimates by accounting for both within model standard error and between model variance.
-This combine rule was set out in @Rubin1987, and has been employed in research of measurement errors [see, e.g., @Schnakenberg2014; @Crabtree2015] as well as incorporated in @Blackwell2017a's multiple overimputation (MO) to handle missing values and measurement uncertainty.
-We also employ one alternative technique known as "method of composition" (MOC)  [@Treier2008, p. 215] as a robustness check [see Online Supplementary Material \@ref(moc)].
+We conduct inferences from the distributive data via a technique known as "method of composition" (MOC) [@Treier2008, p. 215].
+See more details of the method and the operational process in Online Supplementary Material \@ref(moc).
 
@@
 This result is robust when using separated regime types in the explanatory variable. 
-Nor do applying system GMM models and using MOC for uncertainty incorporation alters the conclusion (see Online Supplementary Material \@ref(fullAJPS), \@ref(fullAPSR), and \@ref(moc)).
+Nor do applying system GMM models or controlling for corruption alter the conclusion (see Online Supplementary Material \@ref(moc) for the the result of the full-pack analyses).
 
@@
 
-Moreover, the results also manfiest another risk of ignoring uncertainty: missestimation. 
+Moreover, the results expose another risk for ignoring uncertainty: missestimation. 
 As shown in Figure \@ref(fig:plot-mainAJPS), besides the confidence intervals the (point) estimates also shift. 
-Methodologically, these shifts indicates that the 900 regressions of public support on democracy do not yield consistent results although the support opinions were drawn from the same distribution. 
-In this sense, the coefficient produced simply by the mean of the public support distribution is no more than a one-time guess of the true parameter and definitely not a robust one. 
-What this methodological issue lead to, however, is a substantively different conclusion of the relationship between public opinions and institutional democratization in both direction and magnitude.
-The replication results illustrate the uncertainty ignorance with mounting risk.
+Methodologically, the shifts indicate that the 900 regressions of public support on democracy do not yield consistent results, although the explanatory and control variables were drawn from the same distribution.
+In this sense, the coefficients produced simply by the means of the variable distributions are no more than a one-time guess of the true parameters and apparently not a robust one. 
+More importantly, what this methodological difference leads to is a substantively opposite conclusion of the relationship between public opinions and institutional democratization.
+Our replication results manifest the uncertainty ignorance with mounting risk.
 
@@
 
-The importance of accounting for the measurement uncertainty appear more evident when the relevant variable plays as the outcome variable. 
+The importance for taking the measurement uncertainty into account appear more evident when the relevant variable plays as the outcome variable. 
 In Figure \@ref(fig:plot-mainAPSR), we examine the thermostatic model of democratic support per @Claassen2020b [p. 47, Models 1.1 and 1.2]. 
@@
 The effects of public support also have cultural-bound.
-@Brunkert2019 contends outspoken support for democracy is a "deceptive indicator of public's affinity to democracy" [423] and finds public support has neither pro-democratic nor anti-authoritarian effect without controlling emancipative values.
+@Brunkert2019[p.
+423] contends outspoken support for democracy is a "deceptive indicator of public's affinity to democracy"  and finds public support has neither pro-democratic nor anti-authoritarian effect without controlling emancipative values.
 Empirical results show that the meaning of support for democracy is dependent on emancipation values and is reversed to its own negation in a society with weak emancipative values [see, e.g.,@Kirsch2019, 83-85].
 And we must be open to the possibility that no theoretical elaboration, no respecification of these models will reveal relationships between public opinion and democracy.
-Democratic backsliding may simply be primarily a matter of elite decisionmaking [see, e.g., @levitsky_how_2018].
+Democratic backsliding may simply be primarily a matter of elite decision making [see, e.g., @levitsky_how_2018].
 
@@
 All of these could and should be explored in future research.
-In any event, the sanguine assessment that readers may draw from Claassen [-@Claassen2020a; -@Claassen2020b]---that the fate of democracies depend on public support, and when eroded, their publics will rally to them---is not supported by the current evidence.
+In any event, the sanguine assessment that readers may draw from Claassen [-@Claassen2020a; -@Claassen2020b]---that the fate of democracies depend on public support, and when eroded, their public will rally to them---is not supported by the current evidence.
 Those who would defend democracy have no grounds to be complacent.
@@
 # (APPENDIX) Appendix {-}
-# Data Recollection and Control Uncertainty in Control Variables.
+# Data Recollection and Uncertainty in Control Variables {#dgp}
 

### 2021-08-08 paper/dcpo_demsupport.Rmd
update moc

@@
 
+In analysis models, we have latent variables in both sides of equations, public suppport for democracy, democracy indices and corruption index (The latter one is included in APSR analyses).
+Since measurement uncertainty associated with these latent variables can propogate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing "Method of Composition" [@Tanner1996,p52], which has been applied in analyses with latent variables [@Trei2008;@Caughey2018;@K2015].
+As @Caughey2018 explained, the main idea of MOC is to estimate the marginal distribution of coefficient parameter vector $\beta$, intergrating over the uncertainty in latent variables $\theta$ (P A-15).
+More explicitly, we wish to integrate the joint density of $\beta$ and $\theta$ over the distribution of $\theta$.
+
+\begin{equation}
+p(\beta,\theta|w,y, Z) = p(\beta|\theta,w,y)p(\theta|Z).
+\end{equation}
+
+where $\theta$ is latent varibles with measurement errors conditional on data Z and a measurement model, $w$ is other predictors without errors, $Z$ is indicators for latent variables $X$, and $y$ is the outcome variable.
+In this way, we incorportate uncertainty in measuring predictor $\theta$, and uncertainty in the effects of latent variables $\theta$ and other variables $w$ on outcome variable $y$ [@Treie2008, 215].
+To sample from the conditional dentsity and the marginal density in the right side of the equation, we follow iterative Monte Carlo procdure described by @Treier2008, at iteration t,
+1. We sample $\theta^{s}$ from its posterior distribution $p(\theta|Z)$ and $y$ from $p(y|Z)$. 
+2.
+For each analysis model, we run the model with $y$, $\theta$, and $w$, and save the coefficient estimates $\beta^{s}$ and variance-covariance matrix of $\beta^{s}$, $V^{s}$, both of which change due to the uncertainty in $\theta^{s}$ and $y^{s}$.
+3. We sample $\tilde{\beta^{t}}$ from the multivariate normal density with mean vector $\beta{s}$ and variance-covariace matrix $V^{s}$.
+
+We incorporate uncertainty for five variables, public support for democracy, liberal democracy, electoral democracy, liberal component index, and corruption perceptions index.
+
 MOC addresses the same issue from a slightly different angle.

### 2021-08-08 paper/dcpo_demsupport.Rmd
update moc and corresponding bib

@@
 Following this line, after replicating the original analyses with point estimates, we incorporate uncertainty in analysis models using our replication data.
-We take the distribution of the latent (explanatory) variable, the outcome variable, and control variables to account for the uncertainty.
-We take 900 draws from the posterior distribution of democratic support, outcome, and control variables with errors.
-We then duplicate each article's analysis dataset of variables "without" measurement error 900 times, and assign them to each a different random draw from the distributions of variables with measurement error.
-We conduct inferences from the distributive data via a technique known as "method of composition" (MOC) [@Treier2008, p. 215].
+We conduct inferences from the distributive data via a technique known as "method of composition" (MOC) [@Tanner1996, p.52;@Treier2008, p. 215; @caughey2018,p.A15-16].
 See more details of the method and the operational process in Online Supplementary Material \@ref(moc).
@@
 
-# Replication with Alternative Methods Accounting for Uncertainty {#moc}
-
-To ensure the robustness of our analysis, we apply another method to account for uncertainty.
-The method we employ is "method of composition" (MOC).
-It is a common method for Monte Carlo integration, but can also be applied for addressing uncertainty [@Treier2008].
-To compare these two methods, let's denote `y` as a vector of the outcome variable [either institutional democracy in @Claassen2020a or the changes in mass support of democracy in @Claassen2020b]. 
-Let $x$ (variables without subscript are used to denote vectors of observations, viz., $x$ = ($x_1$,......, $x_i$)) be a vector of the explanatory variable (e.g., mass support or institutional democracy) and $\theta$ be the parameter of interest.
-
-Rubin's Rules (RR, the method used in the main article) take variables with measurement error as missing value, and combine the point estimates and standard errors into single values yet accounting for both within and between imputation variances [@Rubin1987].
-
-Rubein's Rules is defined in the following formulas.
-
-\begin{equation}
-\bar{\theta}_{m} = \frac{1}{m}\sum_{i=1}^{m} \theta_{i}.
-\end{equation}
-
-\begin{equation}
-{V}_{B} = \frac{1}{m-1}\sum_{i=1}^{m} (\theta_{i}-\bar{\theta}_{m})^2.
-\end{equation}
-
-\begin{equation}
-{V}_{W} = \frac{1}{m}\sum_{i=1}^{m} SE_{i}^2.
-\end{equation}
-
-\begin{equation}
-{V}_{T} = {V}_{w} +(1+ \frac{1}{m})\frac{V_B}{m}.
-\end{equation}
-
-$\bar{\theta}_{M}$ is the pooled parameter estimate, $m$ is the number of imputed datasets, $V_{B}$ is between imputation variance, $V_{W}$ within imputation variance, $V_{T}$ is total variance.
-
-The general formula for confidence interval (CI) is defined as:
-
-\begin{equation}
-\bar{\theta} \pm t_{df,1-\alpha/2} *\sqrt{V_{T}}.
-\end{equation}
-
-$df$ is calculated by using $df_{Adjusted}$ [@barnard1999] and the Fraction of Missing information, lambda, is derived from between and total variance [@raghunathan2015, @van2018].
-
-\begin{equation}
-{df_{Adjusted}} = \frac{df_{Old}*df_{Observed}}{df_{Old}+df_{Observed}}.
-\end{equation}
-
-\begin{equation}
-{df_{Old}} = \frac{(n-k)+1}{(n-k)+3} * (n-k)(1-lambda).
-\end{equation}
-
-\begin{equation}
-{df_{Observed}} = \frac{(n-k)+1}{(n-k)+3} * (n-k)(1-lambda).
-\end{equation}
-
-\begin{equation}
-{Lambda} = \frac{V_{B}+\frac{V_{B}}{m}}{V_{T}}
-\end{equation}
-
-One main idea behind RR is to account for both within imputation variance and sample variance which is due to the missing data (measurement error in our case).
+# Replication with MOC Accounting for Uncertainty {#moc}
 
 In analysis models, we have latent variables in both sides of equations, public suppport for democracy, democracy indices and corruption index (The latter one is included in APSR analyses).
-Since measurement uncertainty associated with these latent variables can propogate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing "Method of Composition" [@Tanner1996,p52], which has been applied in analyses with latent variables [@Trei2008;@Caughey2018;@K2015].
+Since measurement uncertainty associated with these latent variables can propogate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing "Method of Composition" [@Tanner1996,p52], which has been applied in analyses with latent variables [@Treier2008;@Caughey2018;@Kastellec2015].
+
 As @Caughey2018 explained, the main idea of MOC is to estimate the marginal distribution of coefficient parameter vector $\beta$, intergrating over the uncertainty in latent variables $\theta$ (P A-15).
@@
 We incorporate uncertainty for five variables, public support for democracy, liberal democracy, electoral democracy, liberal component index, and corruption perceptions index.
-
-MOC addresses the same issue from a slightly different angle.
-The method assumes that the explanatory and outcome variables are samples from their estimate functions, and their paired sample follows a joint density [@Tanner1993, p.31].
-From the joint density, one can decomposite the likelihood of the explanatory variable and its parameter to a product of their own probabilities.
-When x is measured with errors $w$, the probability becomes conditional:
-
-\begin{equation}
-\mathcal{L}(\theta, x|y, w) = p(\theta|x,y)p(x|w).
-\end{equation}
-
-Based on this decomposition, one can estimate the marginal density for &\theta&:
-
-\begin{equation}
-\mathcal{L}(\theta|y, x) \propto \int_{\chi} p(\theta|y,x)p(x|w)dx.
-\end{equation}
-
-Again, the gained parameter density can be combined into single values.
-A common way to do so is using the mean of $theta$ as the point estimate, and the variance from the density as the standard error.
+For each of these five latent variables, we take 900 draws from its posterior distribution.
+We duplicate the dataset of variables “without” measurement error 900 times, and assign them to each a different random draw from the distributions of variables with measurement error, which yields 900 dataset.
+In next step, we run each of analysis models with these 900 datesets independently and save the resulting estimates of coefficients and the matrix of variance-covariance for each run.
+We then draw one sample from the mulitivariate normal distribution with the mean vector of coefficient estimates and variance-covariance matrix produced from each run.
+This procedure finally yields 900 samples of estimated coefficients drawn from the joint density of $\beta$ and $\theta$.
+We calcluate point estimates and standard error based on these 900 samples.
 

### 2021-08-09 paper/memo/memo.Rmd
updating memo

@@
 ## Response 
-A major concern raised by Reviewers 1 & 2 was regard to the omission of measurement errors of DV and control variables in our analysis.
-It is a good point.
-Many variables in the analysis cannot be observed directly and are inherently contaminated by measurement errors.
-To address this concern, since Claassen used V-Dem Version 8 in his analyses, we incorporated measurement error for the V-Dem democracy index, electoral index, polyarchy index, and liberal index using the posterior distribution of Version 8 provided by V-Dem.
-Regarding the data used to replicate Claassen's analyses, we simulated 900 data set for democracy index from V-Dem Version 10, which did not provide available posterior distribution yet but standard error.
+A major concern raised by Reviewers 1 & 2 was regard to the omission of measurement errors of DV and control variables in our reanalysis.
+It is a good and reasonable suggestion.
+
+Many variables, dependent variable, key independent variables and control variables in original analysis, are latent variables, which cannot be observed directly and are inherently contaminated by measurement errors.
+To address this concern and justify the necessity of incorporating measurement uncertainty in latent variables, we take uncertainty into account for five variables, public support for democracy, liberal democracy index, electoral democracy index, liberal component index, and corruption perception index, in this version of manuscript.
+
+In respect of the key independent variable, public support for democracy, we used Claassen's Model 5 and recollected originalsource data to replicate the measure of public support and keep its posterior distrubtion.
+For expanded data, still, we used Model 5 and expanded source data to measure public support and perserve its posterior distribution. 
+In terms of three indices of democratic development, we incorporated measurement error using their posterior distribution from V-Dem Version 8 which covers 201 countries from 1789 to 2017 and is the version Claassen used in his analyses.
+The posterior distributions are provided by V-Dem Project Team.
+Regarding the expanded data used to replicate Claassen's analyses, we use the same three democratic indices from V-Dem Version 10 which covers 202 countries from 1789 to 2019.
+However, since V-Dem project has not released posterior distributions for indices in version 10, we simulated 900 data set for democracy indices using their standard error.
 To account for measurement error in Corruption Perceptions Index, we simulated 900 draws from a distribution with the point estimate and standard error provided by CPI for the year from 2012 to 2018.
-We estimated the standard error for the year before 2012 by using the multiplication between countries' maximum relative error (standard error/cpi index) and their CPI index.
-We rerun the models following the same steps in our previous analysis but incorporating uncertainty in democracy index, democratic support, and corruption perception index.
-The relationship between the change of public support and the change of democracy disappears when uncertainty is accounted for in models either using Claassen's original data or expanded data with 25% more country-year data.
-The updated results are presented in Figure XXX on Page xx.
+However, since CPI does not povide standard error for the years before 2012, we first estimated the standard error for these years by using the product of countries' maximum relative error (standard error/cpi index) and their CPI index, and then used the estimated standard error to simulate 900 draws.
+
+We used he posterior distributions of five variables in method of composition to address measurement errors. 
+By incorporating uncertainty in democracy indices, democratic support, and corruption perception index, the relationships between public support and democratic development and between the change of public support and the change of democracy disappear either using Claassen's original data or expanded data with one-third more source data.
+The results from models including measurement error for outcome, key independent and control variables again justify the importance of incorporating uncertainty in analysis.
 
@@
 ## Response 
-Both Reviewers 1 & 2 concern the validity of the approach used to incorporate measurement uncertainty.
-First, we added more explanations of how uncertainty is integrated into the models on Page xx of the main text and presented equations on Page xx in SI.
-Rubin's rule is indeed designed to address missing values by using multiple imputations (MI).
-However, as Reviewer 2 has already pointed out, @Blackwell2017 applied the logic of MI and Rubin's rule in their Multiple Overimputation (P309) to address measurement error and missing data, which is conceptualized as an extreme case of measurement error.
+Reviewers 1 & 2 & d concern the validity of the approach used to incorporate measurement uncertainty.
+We appreciate Reviewers' suggestion on method of composition [@Tanner1996] (MOC) to take into account measurement error.
+After reviewing the logic of MOC and its application in articles with latent variables [@Treier2008; @caughey2018;@Kastellec2015], we believe that MOC is the approach that has been justified theoretically and methodologically to address measurement error in latent variables.
+We follow reviewers' suggestion and employ MOC in our revised version.
 
-The idea of our approach for propagating uncertainty is correcting both within and between imputation variance through Rubin's rule, and the idea of MOC is accounting for within imputation variance through drawing samples from the joint posterior distribution of the measurement and analysis model.
+The idea of MOC is to account for uncertainty in both latent variables and effects of latent variables and other variables on outcome variable through drawing samples from the joint posterior distribution of the measurement and analysis model.
+Although MOC is known to methodologists, to approach a broader audiance and make MOC more accessible, we present each step in employing MOC in our reanalysis and provide R script for faciliating reproducibility and replication.
+We followed MOC precedure and the results from MOC demonstrated that when uncertainty is allowed, the coefficients on public support and the change of democratic level are no longer distinguishable from zero on Figure 1 page 8 and Figure 2 page 9.
+The null results hold in robust check models and models with more control variables in Figure xx Page xx in Online Supplementary material.
 
-To address the performance of the method we used, we employed the "method of component" as an alternative way in SI.
-Our approach and MOC yield similar results from replicating APSR's analysis, that is, when uncertainty is allowed, the coefficients on the lagged public support and the change of democratic level are no longer distinguishable from zero in Page xx in MS and Page xx in SI.
-It is not surprising that the estimated effect of democracy is indistinguishable from zero given measurement errors in both democracy and democratic support measurements and cultural features of democratic values.
-As Reviewer3 pointed out, democratic value is formed and shaped by institution, history, and culture, and the cultural feature of democratic value determines that it cannot be impacted swiftly by the change of democracy.
-
-Our approach and MOC yield mixed results for AJPS's analysis.
-
-In terms of the impact of measurement error on estimated effects, many studies have shown that when taking measurement uncertainty into account, the magnitude of coefficients of latent variables can be either attenuated or enlarged substantively [e.g., @Treier2008, p.
-211; @caughey2018,p.
-254].
+We appreciate reviewers' suggestions on MOC, and the results from MOC not only justify but also provide us more confidence in our conclusion that the importance of accounting for uncertainty.
 
@@
 
-First, we need to clarify that the DV in Figure2 is the _change_ of public support for democracy rather than current public support.
-Second, when DV is the change of public support, Claassen's original results of lagged support do not make any sense. 
-Claassen's original results indicate the change of public support in one year is positively changed by the public support in the previous year and negatively shifted by the previous two years.
-Claassen's results indicate that a high public support in 2020 leads to a bigger change in mood in 2021 but a high support in 2019 leads to a smaller change in mood in 2021.
+Thanks to reviewers' feedback on Figure 2, we first need to clarify that the DV in Figure 2 is the _change_ of public support for democracy rather than current public support.
+Claassen examined the thermostatic effect of the change of democratic level on the _change_ of public support in his original APSR analysis.
+In our replication of the APSR article, the DV is also the _change_ of public support for democracy.
+Therefore, the question is that is there any theoretical reasons to suppor a significant relationship between the current _change_ of pubic support and the lagged public support.
+
+Claassen's original results indicate the _change_ of public support in current year is positively changed by the public support in the previous year and negatively shifted by the previous two years.
+For example, Claassen's results indicate that a high public support in 2020 leads to a bigger _change_ (either upturn or downturn) in mood in 2021 but a high support in 2019 leads to a smaller _change_ (either upturn or downturn) in mood in 2021.
 However, we do not have grounded theories to expect that public support can produce its positive demand in one year but backsliding demands in two years. 
-In contrast, our null results of lagged support on change of support mood indicate that the change of moods might not be dependent on its previous situation but might be shaped by exogenous factors, especially a shock in democratic or economic environment.
+In contrast, our null results of lagged support on the _change_ of support mood indicate that the _change_ of moods might not be dependent on its previous situation.
 
-In terms of the effects of social and economic environment on the change in mood, even in Claassen's original results (the uppermost results in Figure \@ref(fig:plot-mainAPSR)),  point estimates of the change in democracy,  economic growth, corruption index as well as their lagged level, are close to zero in magnitude.
+Theoretically, we should expect the change of public support is more likely to be shaped by exogenous factors, especially a shock in democratic or economic environment.
+However, in terms of the effects of social and economic environment on the change in mood, even in Claassen's original results (the uppermost results in Figure \@ref(fig:plot-mainAPSR)),  point estimates of the change in democracy, economic growth, corruption index as well as their lagged level, are close to zero in magnitude.
 Except for the change in democracy, all other estimated effects are not distinguishable from zero. 
 After acknowledging uncertainty, the estimated effect of the change in democracy is indistinguishable from zero, and the magnitude of the coefficient moves further to zero.
-As @Treier2008 [p213] emphasized, accounting of uncertainty maintains the significant effect of democracy mainly in applications where democracy strongly affects the quantity of interest and models are simple enough.
-Given the measurement errors in public support, democratic indices, and corruption index, it is not surprising to see the diminution of the estimated effects.
+
+Methodologically, given the measurement errors in public support, democratic indices, and corruption index, it should not be surprising to see the diminution of the estimated effects.
+Although it is rare that accounting of uncertainty disappears the significant effect of democracy, @Treier2008 [p213] emphasized, after allowing uncertainty, the significant effect of democracy holds mainly in applications where democracy strongly affects the quantity of interest and models are simple enough.
+Our results demonstrate that there at least is no a strong relationship between democracy and public support.
+Theoretically, as Reviewer3 pointed out, democratic value is formed and shaped by institution, history, and culture, and the nature of democratic value determines that it cannot be impacted swiftly by the change of democratic level.
+Moreover, the understanding of democracy which shapes democratic value has cultural bounds [@Brunkert2019; @Kirsch2019; @Kruse2019] but not yet incorporated in most current measure of democratic support.
+
+The understand of democracy problem could be "misunderstanding" in both authoritarian countries and democratic countries. 
+In democracies, the "misunderstanding" is related to another issue which should attract more theoretical discussion, that is, the choice between generic support for democracy and other values especially in the long built democracies [see @bartels_ethnic_2020; @Carey2020; @graham_democracy_2020; @McCoy2020].
+The disparity between the public's generic support and their commitment to support lends light to the recent democracy crisis and the uprising of populism witnessed in well-developed democracies.
+
+<!--
+thanks to reviewer2's comments on random walk, we do think we should discuss more on problems caused by random walk, which actually provides us another powerful explanation for our results. 
+In terms of the impact of measurement error on estimated effects, many studies have shown that when taking measurement uncertainty into account, the magnitude of coefficients of latent variables can be either attenuated or enlarged substantively [e.g., @Treier2008, p.
+211; @caughey2018,p.
+254].
+-->
 
@@
 Therefore, it is the incorporation of uncertainty that changes the coefficient estimates in magnitude and significant. 
+<!--random walk,standards for dv -->
 
@@
 Instead, it is more promising to use value priorities to distinguish different types of democracy supporters and estimate their demographic distribution.
-
-Kirsch, H. & C. Welzel (2018). "Democracy Misunderstood: Authoritarian Notions of Democracy around the Globe." Social Forces 91: 1-33 (DOI: 10.1093/sf/soy114).
-
-Kruse, S., M.
-Ravlik & C.
-Welzel (2018).
-"Democracy Confused: When People Mistake the Absence of Democracy for Its Presence." Journal of Cross-Cultural Psychology 49: 1-21 (DOI: 10.1177/0022022118821437).
-
-Brunkert, L., S.
-Kruse & C.
-Welzel (2018).
-"A Tale of Culture-bound Regime Evolution: The Centennial Democratic Trend and Its Recent Reversal." Democratization 25: 1-23 (DOI: 10.1080/13510347.2018.1542430).
 

### 2021-08-09 paper/dcpo_demsupport.Rmd
updating SI.

@@
 The uppermost set of results replicate @Claassen2020a without uncertainty.
-The middle results introduce the uncertainty in the measurement of public support and democratic indices into the model.
+The middle results introduce the uncertainty in the measurement of public support and democracy indices into the model.
 And the lowermost set presents the results estimated with the expanded data with uncertainty.
@@
 
-We also include measurement errors in control variables, including three democratic indices and corruption index.
-We extracted the posterior distributions of democratic indices, including Liberal Democracy,polyarchy, and electoral democracy index, which are provided by [@coppedge2018].
+We also include measurement errors in control variables, including three democracy indices and corruption index.
+We extracted the posterior distributions of democracy indices, including Liberal Democracy,electoral democracy index and liberal component index, which are provided by [@coppedge2018].
 We drew 900 samples from the distribution of the Corruption Perception Index.

### 2021-08-11 paper/dcpo_demsupport.Rmd
updating memo on random walk.

--- 2021-08-08 paper/dcpo_demsupport.Rmd
@@
 citation_package: natbib
-fontsize: 12pt
-indent: true
+fontsize: 11pt
 linestretch: 1.5 # double spacing using linestretch 1.5
@@
   warning = FALSE,
+  eval = FALSE,
   dpi = 300
@@
 
-# load(here("data", "correct_cls_ajps.rda"))
-# load(here("data", "correct_cls_apsr.rda")) 
-# load(here("data", "expcor_cls_ajps.rda"))
-# load(here("data", "expcor_cls_apsr.rda"))
+load(here("data", "correct_cls_ajps.rda"))
+load(here("data", "correct_cls_apsr.rda")) 
+load(here("data", "expcor_cls_ajps.rda"))
+load(here("data", "expcor_cls_apsr.rda"))
+
+result_clsAJPS <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
+result_pureAJPS <- readRDS(here("output", "estimates_clsPureAJPS.RDS"))
+result_expAJPS <- readRDS(here("output", "estimates_clsExpAJPS.RDS"))
+result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
+result_pureAPSR <- readRDS(here("output", "estimates_clsPureAPSR.RDS"))
+result_expAPSR <- readRDS(here("output", "estimates_clsExpAPSR.RDS"))
 
@@
 Second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.
-In the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.
-
-It is worth to note that, despite the great effort of collecting data and identifying differences, we could not reach a completely primary replication of @Claassen2020a's Dataverse materials.
-Specifically, we have five fewer observations, three of which are no longer available in original survey data and two seem to have never existed, and one more survey item which was conflated in original data.
-(See more details in Online Supplementary Material \@ref(dgp).)
-Nevertheless, given there are over 2000 observations involved in the analysis, the five missing should not make a meaningful difference.
-
-## Uncertainty Incorporation
+As the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.
+
+## Data Recollection and Incorporating Uncertainty
+Despite the great effort of collecting data and identifying differences, we could not entirely achieve a primary replication [see @Grossman2020, p. 18] based on @Claassen2020a's Dataverse materials.
+Our replication data has differences in number of country-year surveys and in sample size.
+Specificially, we have five fewer observations, three of which are no longer available in originial survey data and two seem to have never existed, and one more survey item which was conflated in original data [see Online Supplementary Material].
 
@@
 254].
-Following this line, after replicating the original analyses with point estimates, we incorporate uncertainty in analysis models using our replication data.
+
+Following this line, after replicating the original analyses with point estimates, we incorportate uncertainty in analysis models using our replication data.
 We take the distribution of the latent (explanatory) variable, the outcome variable, and control variables to account for the uncertainty.
@@
 We then duplicate each article's analysis dataset of variables "without" measurement error 900 times, and assign them to each a different random draw from the distributions of variables with measurement error.
-We conduct inferences from the distributive data via a technique known as "method of composition" (MOC) [@Treier2008, p. 215].
-See more details of the method and the operational process in Online Supplementary Material \@ref(moc).
-
-```{r compare_n}
+We estimate each analysis model repeatedly on its respective collection of the datasets, and then make inferences from the distribution of parameter estimates by accounting for both within model standard error and between model variance.
+This combine rule was set out in @Rubin1987, and has been employed in research of measurement errors [see, e.g., @Schnakenberg2014; @Crabtree2015] as well as incorporated in @Blackwell2017a's multiple overimputation (MO) to handle missing values and measurement uncertainty.
+We also employ one alternative technique known as "method of composition" (MOC)  [@Treier2008, p. 215] as a robustness check [see Online Supplementary Material \@ref(moc)].
+
+```{r compare_n, eval = TRUE}
 
@@
 This result is robust when using separated regime types in the explanatory variable. 
-Nor do applying system GMM models or controlling for corruption alter the conclusion (see Online Supplementary Material \@ref(moc) for the the result of the full-pack analyses).
+Nor do applying system GMM models and using MOC for uncertainty incorporation alters the conclusion (see Online Supplementary Material \@ref(fullAJPS), \@ref(fullAPSR), and \@ref(moc)).
 
@@
 
-Moreover, the results expose another risk for ignoring uncertainty: missestimation. 
+Moreover, the results also manfiest another risk of ignoring uncertainty: missestimation. 
 As shown in Figure \@ref(fig:plot-mainAJPS), besides the confidence intervals the (point) estimates also shift. 
-Methodologically, the shifts indicate that the 900 regressions of public support on democracy do not yield consistent results, although the explanatory and control variables were drawn from the same distribution.
-In this sense, the coefficients produced simply by the means of the variable distributions are no more than a one-time guess of the true parameters and apparently not a robust one. 
-More importantly, what this methodological difference leads to is a substantively opposite conclusion of the relationship between public opinions and institutional democratization.
-Our replication results manifest the uncertainty ignorance with mounting risk.
-
-```{r pointAJPS}
+Methodologically, these shifts indicates that the 900 regressions of public support on democracy do not yield consistent results although the support opinions were drawn from the same distribution. 
+In this sense, the coefficient produced simply by the mean of the public support distribution is no more than a one-time guess of the true parameter and definitely not a robust one. 
+What this methodological issue lead to, however, is a substantively different conclusion of the relationship between public opinions and institutional democratization in both direction and magnitude.
+The replication results illustrate the uncertainty ignorance with mounting risk.
+
+```{r pointAJPS, eval=TRUE}
 ls_iv <- c("plm::lag(SupDem_trim, 1)",
@@
 
-```{r mocresult-pureAJPS, eval=FALSE}
+```{r result-pureAJPS}
+result_pureAJPS <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
+  result <- map(correct_cls_ajps, function(aData){ # applying to the 1000 datasets
+    eval(parse(text = aMod))
+  })
+
+  result_betas <- mitools::MIextract(result, fun = coef)
+
+  ## Not work with ifelse
+  if(class(result[[1]])[1] == "plm"){
+      result_vars <- mitools::MIextract(result, fun = vcovBK_se)
+  }else{
+      result_vars <- mitools::MIextract(result, fun = vcovHC_se)
+  }
+
+  tidy_clsUncertain <- summary(mitools::MIcombine(results = result_betas, 
+                             variance = result_vars)) %>% 
+    rownames_to_column(var = "term") %>%
+        rename(conf.low = `(lower`,
+               conf.high = `upper)`,
+               estimate = results) %>%
+        filter(!str_detect(term, "(Intercept)"))
+
+  if(class(result[[1]]) == "plm"){ 
+    glance_clsUncertain <- glance.plm(result[[1]]) # using the customized glance function
+  }else{
+    glance_clsUncertain <- glance(result[[1]])
+  }
+
+  result_apsrAJPS <- list(tidy_clsUncertain, glance_clsUncertain)
+})
+
+names(result_pureAJPS) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
+
+saveRDS(result_pureAJPS, file = here::here("output", "estimates_clsPureAJPS.RDS"))
+```
+
+```{r result-expAJPS}
+result_expAJPS <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
+  result <- map(expcor_cls_ajps, function(aData){ # applying to the 1000 datasets
+    eval(parse(text = aMod))
+  })
+
+  result_betas <- mitools::MIextract(result, fun = coef)
+
+  ## Not work with ifelse
+  if(class(result[[1]])[1] == "plm"){
+      result_vars <- mitools::MIextract(result, fun = vcovBK_se)
+  }else{
+      result_vars <- mitools::MIextract(result, fun = vcovHC_se)
+  }
+
+  tidy_dcpoUncertain <- summary(mitools::MIcombine(results = result_betas, 
+                             variance = result_vars)) %>% 
+    rownames_to_column(var = "term") %>%
+        rename(conf.low = `(lower`,
+               conf.high = `upper)`,
+               estimate = results) %>%
+        filter(!str_detect(term, "(Intercept)"))
+
+  if(class(result[[1]]) == "plm"){ 
+    glance_dcpoUncertain <- glance.plm(result[[1]]) # using the customized glance function
+  }else{
+    glance_dcpoUncertain <- glance(result[[1]])
+  }
+
+  result_expAJPS <- list(tidy_dcpoUncertain, glance_dcpoUncertain)
+})
+
+names(result_expAJPS) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
+
+saveRDS(result_expAJPS, file = here::here("output", "estimates_clsExpAJPS.RDS"))
+```
+
+```{r coefName-AJPS, eval=TRUE}
+index_coefName <- c(
+  `plm::lag(Libdem_VD, 1:2)1` = "Democracy[t-1]",
+  `plm::lag(Libdem_VD, 1:2)2` = "Democracy[t-2]",
+  `plm::lag(Vdem_libdem, 1:2)1` = "Democracy[t-1]",
+  `plm::lag(Vdem_libdem, 1:2)2` = "Democracy[t-2]",
+  `plm::lag(SupDem_trim, 1)` = "Support[t-1]",
+  `plm::lag(theta, 1)` = "Support[t-1]",
+  `plm::lag(SupDem_Democ, 1)` = "Support[t-1](demo~only)",
+  `plm::lag(SupDem_Autoc, 1)` = "Support[t-1](auto~only)",
+  `plm::lag(theta_dem_trim, 1)` = "Support[t-1](demo~only)",
+  `plm::lag(theta_aut_trim, 1)` = "Support[t-1](auto~only)",
+  `plm::lag(lnGDP_imp, 1)` = "Log~GDP~per~capita[t-1]",
+  `plm::lag(lg_imp_mdpgdp, 1)` = "Log~GDP~per~capita[t-1]",
+  `plm::lag(GDP_imp_grth, 1)` = "GDP~per~capita~growth[t-1]",
+  `plm::lag(mdprgdp_grwth, 1)` = "GDP~per~capita~growth[t-1]",
+  `plm::lag(Libdem_regUN, 1)` = "Regional~democracy[t-1]",
+  `plm::lag(Region_libdem, 1)` = "Regional~democracy[t-1]",
+  `plm::lag(Pr_Muslim, 1)` = "Percent~Muslim[t-1]",
+  `plm::lag(muslism_prop_2010, 1)` = "Percent~Muslim[t-1]",
+  `plm::lag(Res_cp_WDI_di, 1)` = "Resource~dependence[t-1]",
+  `plm::lag(dependence_pc_di, 1)` = "Resource~dependence[t-1]"
+)
+```
+
+```{r plot-mainAJPS, fig.cap= "The Effect of Public Support on Democracy with Uncertainty", fig.width=7, fig.height=10, fig.align='center', eval=TRUE}
+
+type_model <-
+  c("Original", "Uncertainty", "Uncertainty+Expanded Data")
+
+result_ajpsPooled <-
+  list(result_clsAJPS,
+       result_pureAJPS,
+       result_expAJPS) %>%
+  map2_df(type_model, ~ {
+    .x$pooled[[1]] %>%
+      filter(term != "(Intercept)") %>%
+      select(term, estimate, conf.low, conf.high) %>%
+      mutate(model = .y)
+  }) %>% 
+  mutate(type = "Pooled")
+
+result_ajpsRegime <-
+  list(result_clsAJPS,
+       result_pureAJPS,
+       result_expAJPS) %>%
+  map2_df(type_model, ~ {
+    .x$`pooled-regime`[[1]] %>%
+      filter(term != "(Intercept)") %>%
+      select(term, estimate, conf.low, conf.high) %>%
+      mutate(model = .y)
+  }) %>% 
+  mutate(type = "Regime Specified")
+
+df_plot <- bind_rows(result_ajpsPooled, result_ajpsRegime) %>% 
+    mutate(term = index_coefName[term],
+           term = factor(term, levels = unique(index_coefName)))
+
+dwplot(df_plot) +
+    geom_vline(xintercept = 0,
+               colour = "grey80",
+               linetype = 2) +
+    theme_minimal() +
+    ggtitle("DV: Liberal Democracy (Vdem)") +
+    xlab("Coefficient Estimate") +
+    theme(
+        axis.title.y = element_blank(),
+        legend.position = "bottom",
+      legend.title = element_blank()
+    ) +
+    scale_y_discrete(labels = parse(text = rev(levels(df_plot$term)))) +
+    # Using expressions of underscore and greek letters
+    # scale_color_gb(palette = "digitMixed") +
+    facet_wrap(~ type)
+
+```
+
+The importance of accounting for the measurement uncertainty appear more evident when the relevant variable plays as the outcome variable. 
+In Figure \@ref(fig:plot-mainAPSR), we examine the thermostatic model of democratic support per @Claassen2020b [p. 47, Models 1.1 and 1.2]. 
+When the uncertainty is ignored, the coefficient of $\Delta$liberal democracy (the uppermost set), the yearly changes of the institutional feature is negative inferring that the change in democratic mood decreases as change in democracy increases and vice versa.
+However, when the measurement uncertainty is properly accounted (the middle set), the point estimate shifts towards zero and the coefficient is no longer significant.
+More data (the lowermost set), again, only adjusts the confidence intervals but not direction nor significance.
+
+```{r pointAPSR, eval=TRUE}
+load(here::here("data", "dem_mood_apsr.RData"))
+sd.plm <- pdata.frame(x, index = c("Country", "Year"))
+
+ls_ivECM <- c("diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)", 
+              "diff(Polyarchy_z, lag = 1) + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)")
+ls_ctrlECM <- c("", " + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1)")
+
+ls_eqECM <- glue("diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)") %>% 
+  outer(ls_ctrlECM, paste0) %>% 
+  as.vector()
+
+ls_ivFD <- c("Libdem_z",
+             "Polyarchy_z + Liberal_z")
+
+ls_ctrlFD <- c("", " + Corrup_TI_z")
+
+ls_eqFD <- glue("SupDem_trim ~ {ls_ivFD} + lnGDP_imp") %>% 
+  outer(ls_ctrlFD, paste0) %>% 
+  as.vector()
+
+ls_mod <- c(
+  glue("plm({ls_eqECM}, model = 'pooling', data = sd.plm)"),
+  glue("plm({ls_eqFD}, model = 'fd', index = 'Country', data = sd.plm)")
+)
+
+df_result_clsAPSR <- map(ls_mod, function(mod) {
+  result <- eval(parse(text = mod))
+})
+
+result_clsAPSR <- map(df_result_clsAPSR, function(aResult) {
+  tidy_result <- tidy(aResult, conf.int = TRUE) %>% 
+    mutate(std.error = vcovHC_se(aResult))
+
+  glance_result <- glance.plm(aResult)
+
+  ls_result <- list(tidy_result, glance_result)
+})
+
+names(result_clsAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", 
+                           "fd1", "fd-regime1", "fd2", "fd-regime2")
+
+saveRDS(result_clsAPSR, file = here("output", "estimates_clsMeanAPSR.RDS"))
+```
+
+```{r model-APSR}
+ls_ivECM <- c("diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)", 
+              "diff(Polyarchy_z, lag = 1) + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)")
+ls_ctrlECM <- c("", " + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1)")
+
+ls_eqECM <- glue("diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)") %>% 
+  outer(ls_ctrlECM, paste0) %>% 
+  as.vector()
+
+ls_ivFD <- c("Libdem_z",
+             "Polyarchy_z + Liberal_z")
+
+ls_ctrlFD <- c("", " + Corrup_TI_z")
+
+ls_eqFD <- glue("diff(SupDem_trim, lag = 1) ~ {ls_ivFD} + lnGDP_imp") %>% 
+  outer(ls_ctrlFD, paste0) %>% 
+  as.vector()
+
+ls_mod_apsrCLS <- c(
+  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
+  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
+)
+```
+
+```{r result-pureAPSR}
+result_pureAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
+  result <- map(correct_cls_apsr, function(aData){ # applying to the 900 datasets
+    eval(parse(text = aMod))
+  })
+
+  result_betas <- mitools::MIextract(result, fun = coef)
+
+  result_vars <- mitools::MIextract(result, fun = vcovHC_se)
+
+  tidy_clsUncertainAPSR <- summary(mitools::MIcombine(results = result_betas, 
+                             variance = result_vars)) %>% 
+    rownames_to_column(var = "term") %>%
+        rename(conf.low = `(lower`,
+               conf.high = `upper)`,
+               estimate = results) %>%
+        filter(!str_detect(term, "(Intercept)"))
+
+  glance_clsUncertainAPSR <- glance.plm(result[[1]])
+
+  result_apsrAJPSAPSR <- list(tidy_clsUncertainAPSR, glance_clsUncertainAPSR)
+})
+
+names(result_pureAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", "fd1", "fd-regime1", "fd2", "fd-regime2")
+
+saveRDS(result_pureAPSR, file = here("output", "estimates_clsPureAPSR.RDS"))
+```
+
+```{r result-expAPSR}
+result_expAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
+  result <- map(expcor_cls_apsr, function(aData){ # applying to the 1000 datasets
+    eval(parse(text = aMod))
+  })
+
+  result_betas <- mitools::MIextract(result, fun = coef)
+
+  result_vars <- mitools::MIextract(result, fun = vcovHC_se)
+
+  tidy_dcpoUncertainAPSR <- summary(mitools::MIcombine(results = result_betas, 
+                             variance = result_vars)) %>% 
+    rownames_to_column(var = "term") %>%
+        rename(conf.low = `(lower`,
+               conf.high = `upper)`,
+               estimate = results) %>%
+        filter(!str_detect(term, "(Intercept)"))
+
+  glance_dcpoUncertainAPSR <- glance.plm(result[[1]])
+
+  result_expAPSR <- list(tidy_dcpoUncertainAPSR, glance_dcpoUncertainAPSR)
+})
+
+names(result_expAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",  "fd1", "fd-regime1", "fd2", "fd-regime2")
+
+saveRDS(result_expAPSR, file = here("output", "estimates_clsExpAPSR.RDS"))
+```
+
+```{r coefName-APSR, eval=TRUE}
+index_coefName <- c(
+    `plm::lag(SupDem_trim, 1:2)1` = "Support[t-1]",
+    `plm::lag(SupDem_trim, 1:2)2` = "Support[t-2]",
+    `plm::lag(theta_trim, 1:2)1` = "Support[t-1]",
+    `plm::lag(theta_trim, 1:2)2` = "Support[t-2]",
+
+    `diff(Libdem_z, lag = 1)` = "Delta~Liberal~democracy",
+    `diff(Vdem_libdem_z, lag = 1)` = "Delta~Liberal~democracy",
+    `plm::lag(Libdem_z, 1)` = "Liberal~democracy[t-1]",
+    `plm::lag(Vdem_libdem_z, 1)` = "Liberal~democracy[t-1]",
+
+    `diff(Liberal_z, lag = 1)` = "Delta~Electoral~democracy",
+    `diff(Vdem_liberal_z, lag = 1)` = "Delta~Electoral~democracy",
+    `plm::lag(Liberal_z, 1)` = "Electoral~democracy[t-1]",
+    `plm::lag(Vdem_liberal_z, 1)` = "Electoral~democracy[t-1]",
+
+    `diff(Polyarchy_z, lag = 1)` = "Delta~Minoritarian~democracy",
+    `diff(Vdem_polyarchy_z, lag = 1)` = "Delta~Minoritarian~democracy",
+    `plm::lag(Polyarchy_z, 1)` = "Minoritarian~democracy[t-1]",
+    `plm::lag(Vdem_polyarchy_z, 1)` = "Minoritarian~democracy[t-1]",
+
+    `diff(lnGDP_imp, lag = 1)` = "Delta~Log~GDP~per~capita",
+    `diff(lg_imp_mdpgdp, lag = 1)` = "Delta~Log~GDP~per~capita",
+    `plm::lag(lnGDP_imp, 1)` = "Log~GDP[t-1]",
+    `plm::lag(lg_imp_mdpgdp, 1)` = "Log~GDP[t-1]"
+    # `diff(Corrup_TI_z, lag = 1)`= "Delta~Corruption",
+    # `plm::lag(Corrup_TI_z, 1)` = "Log~Corruption[t-1]",
+    # `Corrup_TI_z` = "Log~Corruption[t-1]"
+)
+```
+
+```{r plot-mainAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", fig.width=7, fig.height=10, eval = TRUE}
+result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
+result_pureAPSR <- readRDS(here("output", "estimates_clsFullUncertainAPSR.RDS"))
+result_expAPSR <- readRDS(here("output", "estimates_clsExpAPSR.RDS"))
+
+type_model <-
+  c("Original", "Uncertainty", "Uncertainty+Expanded Data")
+
+result_apsrPooled <-
+  list(result_clsAPSR,
+       result_pureAPSR,
+       result_expAPSR) %>%
+  map2_df(type_model, ~ {
+    .x$pooled1[[1]] %>%
+      filter(term != "(Intercept)") %>%
+      select(term, estimate, conf.low, conf.high) %>%
+      mutate(model = .y)
+  }) %>% 
+  mutate(type = "Pooled")
+
+result_apsrRegime <-
+  list(result_clsAPSR,
+       result_pureAPSR,
+       result_expAPSR) %>%
+  map2_df(type_model, ~ {
+    .x$`pooled-regime1`[[1]] %>%
+      filter(term != "(Intercept)") %>%
+      select(term, estimate, conf.low, conf.high) %>%
+      mutate(model = .y)
+  }) %>% 
+  mutate(type = "Institution Specified")
+
+df_plot <- bind_rows(result_apsrPooled, result_apsrRegime) %>% 
+    mutate(term = index_coefName[term],
+           term = factor(term, levels = unique(index_coefName)), 
+           type = factor(type, levels = c("Pooled", "Institution Specified")))
+
+dwplot(df_plot) +
+    geom_vline(xintercept = 0,
+               colour = "grey80",
+               linetype = 2) +
+    ggtitle("DV: The Change of Public Support for Democracy") +
+    xlab("Coefficient Estimate") +
+    theme(
+        axis.title.y = element_blank(),
+        legend.position = "bottom",
+        legend.title = element_blank()
+    ) +
+    facet_wrap( ~ type) + 
+    scale_y_discrete(labels = parse(text = rev(levels(df_plot$term))))
+    # Using expressions of underscore and greek letters
+    # scale_color_gb(palette = "digitMixed")
+
+```
+
+# Discussion
+
+In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support has a positive effect on democracy and change in democracy a negative effect on change in support are not empirically supported once measurement uncertainty is taken into account, even when more data are used.
+
+There are theoretical explanations for the null results.
+With regard to how levels of democracy affect public support, we note that even the proponents of the classic argument did not contend that the mere existence of democratic institutions, no matter how consistently feckless and ineffective, would generate support among the public: instead, they maintained, public support would be gained through experience with government performance that was generally effective [@lipset_social_1959, 86-89; @Easton1965, 119-120].
+There is some empirical support for this, with government effectiveness positively related to public support among democracies and negatively related in non-democracies [@Magalhaes2014]. 
+The finding of @Krieckhaus2014 that income inequality is strongly negatively related to public support in democracies suggests that performance regarding redistribution is particularly important.
+Relatedly, on the reverse part of the classic argument, @Qi2011 suggests that democratic support alone cannot be expected to generate democratic change and oppose backsliding.
+Instead, that work contends, it is the combination of democratic support and dissatisfaction with current regime performance that generates demand for greater democracy.
+The effects of public support also have cultural-bound.
+@Brunkert2019 contends outspoken support for democracy is a "deceptive indicator of public's affinity to democracy" [423] and finds public support has neither pro-democratic nor anti-authoritarian effect without controlling emancipative values.
+Empirical results show that the meaning of support for democracy is dependent on emancipation values and is reversed to its own negation in a society with weak emancipative values [see, e.g.,@Kirsch2019, 83-85].
+And we must be open to the possibility that no theoretical elaboration, no respecification of these models will reveal relationships between public opinion and democracy.
+Democratic backsliding may simply be primarily a matter of elite decisionmaking [see, e.g., @levitsky_how_2018].
+
+There are several potential methodological explanations for these null results as well.
+One issue is that the survey items employed---which ask respondents to assess the desirability or appropriateness of democracy, to compare democracy to some undemocratic alternative, or to assess one of these alternatives---may not capture every aspect of democratic support necessary for it to play its hypothesized roles in the classic theory.
+If only those who profess to prefer democracy to its alternatives _and also_ value freedom of expression, freedom of association, and pluralism of opinion will take appropriate action when democracy is threatened, then this measure is inadequate to its purpose [see, e.g., @Schedler2007].
+Moreover, given the multi-faceted nature of democratic attitudes, even the inclusion of such questions in unidimensional public opinion models such as those provided by @Claassen2019 or @Solt2020a are unlikely to be sufficient [see, e.g., @Wuttke2020].
+Another issue is that even if these survey questions do capture support for the generic concept of democracy, these measurement models might still be incapable of suitably capturing democratic support due to the variation in understanding the concept across countries or over time within countries [@Wuttke2021].
+Yet another is that this measure provides no assessment of the _relative_ importance the public affords democracy.
+It provides no information on the extent to which other values, such as policy preferences or partisanship, weigh more heavily---and there is growing evidence that, at least in the United States, there are many for whom these other considerations excuse substantial transgressions against democracy [see @bartels_ethnic_2020; @Carey2020; @graham_democracy_2020; @McCoy2020].
+Regardless, these explanations indicate that there remains much work to be done in the empirical study of public support and democracy.
+
+# Conclusion
+
+In this letter, we reexamine the findings from Claassen [-@Claassen2020a; -@Claassen2020b], two articles that maintain that public support helps the survival of democracy and democratic development has a thermostatic effect on public support.
+We demonstrate the importance of incorporating measurement uncertainty in analyzing the relationship between public support and democracy.
+Taking uncertainty into account rendered both articles' conclusions without empirical support, even when we added considerable more data.
+
+This points to the absolute necessity of incorporating measurement uncertainty into analyses that include latent variables.
+Measurement issues have never had a prominent place in comparative political studies because they need more time to estimate models, but they ground the quality of data and the basis of analysis [@stegmueller2011, 484].
+As the use of latent variables grows more common in political science, both researchers and readers should be aware that these variables' concomitant measurement uncertainty cannot be neglected.
+
+The null results reached in this letter could arise from several sources.
+There are theoretically grounded reasons of government effectiveness, democratic understanding, and generical-or-behavioral support to suspect that the relationships are in fact negligible.
+We also identified a number of potential shortcomings in the measurement of democratic support and ways in which the analysis models might be underspecified.
+All of these could and should be explored in future research.
+In any event, the sanguine assessment that readers may draw from Claassen [-@Claassen2020a; -@Claassen2020b]---that the fate of democracies depend on public support, and when eroded, their publics will rally to them---is not supported by the current evidence.
+Those who would defend democracy have no grounds to be complacent.
+
+# References  {-}
+
+<div id = 'refs'></div>
+
+\pagebreak
+
+# Online Supplementary Materials {-}
+# (APPENDIX) Appendix {-}
+# Numeric Results for Replicating Claassen 2020a {#fullAJPS}
+
+```{r num-labelAJPS, eval=TRUE}
+names_coef <- c(
+  "(Intercept)" = "(Intercept)",
+  "plm::lag(Libdem_VD, 1:2)1" = "Democracy[t-1]",
+  "plm::lag(Libdem_VD, 1:2)2"  = "Democracy[t-2]",
+  "plm::lag(SupDem_trim, 1)" = "Support[t-1]",
+  "plm::lag(SupDem_Democ, 1)" = "Support in Democracy",
+  "plm::lag(SupDem_Autoc, 1)" = "Support in Autocracy",
+  "plm::lag(lnGDP_imp, 1)" = "Log GDP Per Capita[t-1]",
+  "plm::lag(GDP_imp_grth, 1)"  = "GDP Per Capita~growth[t-1]",
+  "plm::lag(Libdem_regUN, 1)" = "Regional Democracy[t-1]",
+  "plm::lag(Pr_Muslim, 1)" = "Percent Muslim[t-1]",
+  "plm::lag(Res_cp_WDI_di, 1)" = "Resource Dependence[t-1]"
+)
+```
+
+```{r num-pointAJPS, results='asis', eval=TRUE}
+tb_result_cls <- purrr::map(result_clsAJPS, ~ {
+  names(.) <- c("tidy", "glance")
+  class(.) <- "modelsummary_list"
+  return(.)})
+
+names(tb_result_cls) <- c("Pooled", "Pooled-Regime", 
+                          "GMM", "GMM-Regime")
+
+modelsummary(tb_result_cls,  
+             statistic = "conf.int",
+             coef_map = names_coef, 
+             output = "latex", 
+             title = "Original") %>%
+
+  kableExtra::kable_styling(font_size = 8) %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+```{r num-pureAJPS, results='asis', eval=TRUE}
+tb_result_pureAJPS <- purrr::map(result_pureAJPS, ~ {
+  names(.) <- c("tidy", "glance")
+  class(.) <- "modelsummary_list"
+  return(.)})
+
+names(tb_result_cls) <- c("Pooled", "Pooled-Regime", 
+                          "GMM", "GMM-Regime")
+
+modelsummary(tb_result_pureAJPS, 
+             statistic = "conf.int",
+             coef_map = names_coef, 
+             output = "latex", 
+             title = "W. Uncertainty") %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+```{r num-expAJPS, results='asis', eval=TRUE}
+tb_result_expAJPS <- purrr::map(result_expAJPS, ~ {
+  names(.) <- c("tidy", "glance")
+  class(.) <- "modelsummary_list"
+  return(.)})
+
+names(tb_result_expAJPS) <- c("Pooled", "Pooled-Regime", 
+                          "GMM", "GMM-Regime")
+
+modelsummary(tb_result_expAJPS, 
+             statistic = "conf.int",
+             coef_map = names_coef, 
+             output = "latex", 
+             title = "W. Uncertainty") %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+\blandscape
+
+# Numeric Results for Replicating Claassen 2020b {#fullAPSR}
+
+```{r num-labelAPSR, eval=TRUE}
+names_coef <- c(
+  "(Intercept)" = "(Intercept)",
+  "plm::lag(SupDem_trim, 1:2)1" = "Democratic Mood (t-1)",
+  "plm::lag(SupDem_trim, 1:2)2" = "Democratic Mood (t-2)",
+  "diff(Libdem_z, lag = 1)" = "Liberal Democracy (Difference)",
+  "Libdem_z" = "Liberal Democracy (Difference)",
+  "plm::lag(Libdem_z, 1)" = "Liberal Democracy (t-1)",
+  "diff(Polyarchy_z, lag = 1)" = "Electoral Democracy (Difference)",
+  "Polyarchy_z" = "Electoral Democracy (Difference)",
+  "plm::lag(Polyarchy_z, 1)" = "Electoral Democracy (t-1)",
+  "diff(Liberal_z, lag = 1)" = "Minoritarian Democracy (Difference)",
+  "Liberal_z" = "Minoritarian Democracy (Difference)",
+  "plm::lag(Liberal_z, 1)" = "Minoritarian Democracy (t-1)",
+  "diff(lnGDP_imp, lag = 1)" = "Log GDP per capita (Difference)",
+  "lnGDP_imp" = "Log GDP per capita (Difference)",
+  "plm::lag(lnGDP_imp, 1)" = "Log GDP (t-1)",
+  "diff(Corrup_TI_z, lag = 1)" = "Corruption (Difference)",
+  "Corrup_TI_z" = "Corruption (Difference)",
+  "plm::lag(Corrup_TI_z, 1)" = "Corruption (t-1)"
+)
+```
+
+```{r num-pointAPSR, results='asis', eval=TRUE}
+tb_result_clsAPSR <- map(result_clsAPSR, ~ {
+  names(.) <- c("tidy", "glance")
+  class(.) <- "modelsummary_list"
+  return(.)}) %>% 
+  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
+      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]
+
+names(tb_result_clsAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
+
+modelsummary(tb_result_clsAPSR, 
+             stars = TRUE,
+             coef_map = names_coef, 
+             output = "latex") %>% 
+  kableExtra::kable_styling(font_size = 7) %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+\elandscape
+
+\blandscape
+
+```{r num-pureAPSR, results='asis', eval=TRUE}
+tb_result_pureAPSR <- purrr:::map(result_pureAPSR, ~ {
+  names(.) <- c("tidy", "glance")
+  class(.) <- "modelsummary_list"
+  return(.)}) %>% 
+  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
+      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]
+
+names(tb_result_pureAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
+
+modelsummary(tb_result_pureAPSR, 
+             statistic = "conf.int",
+             coef_map = names_coef, 
+             output = "latex") %>% 
+  kableExtra::kable_styling(font_size = 7) %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+\elandscape
+
+\blandscape
+
+```{r num-expAPSR, results='asis', eval=TRUE}
+tb_result_expAPSR <- map(result_expAPSR, ~ {
+  names(.) <- c("tidy", "glance")
+  class(.) <- "modelsummary_list"
+  return(.)}) %>% 
+  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
+      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]
+
+names(tb_result_expAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
+
+modelsummary(tb_result_expAPSR, 
+             statistic = "conf.int",
+             coef_map = names_coef, 
+             output = "latex") %>% 
+  kableExtra::kable_styling(font_size = 7) %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+\elandscape
+
+# Data Recollection and Control Uncertainty in Control Variables.
+
+Due to revisions to the underlying datasets (and, possibly, transcription errors), we were not able to achieve a primary replication [@Grossman2020] based on survey data summarized in @Claassen2020a and @Claassen2020b's Dataverse files.
+
+Specifically, we are not able to identify 5 cournty-year surveys, including South Sudan in Arab Barometer Wave 4, Dominican Republic in 2003 Latinobarometer, XXXX, and Spain in 2005 Latinobarometer. 
+In addition, we still have different sample size and number of respondents answering supportively by following approaches of cleanning data and treatment of non-responses described in @Claassen2020a's supplementatry materials.
+Specifically, we used Claassen's year coding to recode 85 unmatching country-year observations and added one more item "strong leader 2" in Arabbarometer which has different response categories but was conflated into "strong leader 1".
+
+V-Dem data was standardized in @Claassen2020b's analyses, but we did not figure out how the standardization was exactly performed.
+We standardized variables using Z-score, and the standardized values are different from Claassen's data.
+
+We also include measurement errors in control variables, including three democratic indices and corruption index.
+We extracted the posterior distributions of democratic indices, including Liberal Democracy,polyarchy, and electoral democracy index, which are provided by [@coppedge2018].
+We drew 900 samples from the distribution of the Corruption Perception Index.
+Since Corruption Perception Index does not provide standard error before 2011, we imputed the missing standard error using the multiplication of a country's corruption index and the ratio of its available maximum standard error to its corresponding index.
+
+# Replication with Alternative Methods Accounting for Uncertainty {#moc}
+
+To ensure the robustness of our analysis, we apply another method to account for uncertainty.
+The method we employ is "method of composition" (MOC).
+It is a common method for Monte Carlo integration, but can also be applied for addressing uncertainty [@Treier2008].
+To compare these two methods, let's denote `y` as a vector of the outcome variable [either institutional democracy in @Claassen2020a or the changes in mass support of democracy in @Claassen2020b]. 
+Let $x$ (variables without subscript are used to denote vectors of observations, viz., $x$ = ($x_1$,......, $x_i$)) be a vector of the explanatory variable (e.g., mass support or institutional democracy) and $\theta$ be the parameter of interest.
+
+Rubin's Rules (RR, the method used in the main article) take variables with measurement error as missing value, and combine the point estimates and standard errors into single values yet accounting for both within and between imputation variances [@Rubin1987].
+
+Rubein's Rules is defined in the following formulas.
+
+\begin{equation}
+\bar{\theta}_{m} = \frac{1}{m}\sum_{i=1}^{m} \theta_{i}.
+\end{equation}
+
+\begin{equation}
+{V}_{B} = \frac{1}{m-1}\sum_{i=1}^{m} (\theta_{i}-\bar{\theta}_{m})^2.
+\end{equation}
+
+\begin{equation}
+{V}_{W} = \frac{1}{m}\sum_{i=1}^{m} SE_{i}^2.
+\end{equation}
+
+\begin{equation}
+{V}_{T} = {V}_{w} +(1+ \frac{1}{m})\frac{V_B}{m}.
+\end{equation}
+
+$\bar{\theta}_{M}$ is the pooled parameter estimate, $m$ is the number of imputed datasets, $V_{B}$ is between imputation variance, $V_{W}$ within imputation variance, $V_{T}$ is total variance.
+
+The general formula for confidence interval (CI) is defined as:
+
+\begin{equation}
+\bar{\theta} \pm t_{df,1-\alpha/2} *\sqrt{V_{T}}.
+\end{equation}
+
+$df$ is calculated by using $df_{Adjusted$ [@barnard1999] and the Fraction of Missing information, lambda, is derived from between and total variance [@raghunathan2015, @van2018].
+
+\begin{equation}
+{df_{Adjusted}} = \frac{df_{Old}*df_{Observed}}{df_{Old}+df_{Observed}}.
+\end{equation}
+
+\begin{equation}
+{df_{Old}} = \frac{(n-k)+1}{(n-k)+3} * (n-k)(1-lambda).
+\end{equation}
+
+\begin{equation}
+{df_{Observed}} = \frac{(n-k)+1}{(n-k)+3} * (n-k)(1-lambda).
+\end{equation}
+
+\begin{equation}
+{Lambda} = \frac{V_{B}+\frac{V_{B}}{m}}{V_{T}}
+\end{equation}
+
+One main idea behind RR is to account for both within imputation variance and sample variance which is due to the missing data (measurement error in our case).
+
+MOC addresses the same issue from a slightly different angle.
+The method assumes that the explanatory and outcome variables are samples from their estimate functions, and their paired sample follows a joint density [@Tanner1993, p.31].
+From the joint density, one can decomposite the likelihood of the explanatory variable and its parameter to a product of their own probabilities.
+When x is measured with errors $w$, the probability becomes conditional:
+
+\begin{equation}
+\mathcal{L}(\theta, x|y, w) = p(\theta|x,y)p(x|w).
+\end{equation}
+
+Based on this decomposition, one can estimate the marginal density for &\theta&:
+
+\begin{equation}
+\mathcal{L}(\theta|y, x) \propto \int_{\chi} p(\theta|y,x)p(x|w)dx.
+\end{equation}
+
+Again, the gained parameter density can be combined into single values.
+A common way to do so is using the mean of $theta$ as the point estimate, and the variance from the density as the standard error.
+
+```{r mocresult-pureAJPS}
 
@@
 
-```{r mocresult-expAJPS, eval=FALSE}
+```{r mocresult-expAJPS}
 
@@
 
-```{r formatResult-AJPS}
+```{r plot-mocAJPS, fig.cap= "The Effect of Public Support on Democracy ", eval = TRUE, fig.width=7, fig.height=10, eval=TRUE}
+
 result_pooled <- bind_rows(
   mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Original"),
- mutate(MOCsumm(mocresult_correctAJPS[["pooled"]]), model = "W. Uncertainty"),
+ mutate(MOCsumm(mocresult_correctAJPS[["pooled"]]), model = "Uncertainty+Corrected"),
  mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), model = "Uncertainty+Expanded Data")
@@
   mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_correctAJPS[["gmm"]]), model = "W. Uncertainty"),
+  mutate(MOCsumm(mocresult_correctAJPS[["gmm"]]), model = "Uncertainty+Corrected"),
   mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), model = "Uncertainty+Expanded Data")
@@
     type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Original", "W. Uncertainty", "Uncertainty+Expanded Data")))
-
-result_ajpsPooled <- result_pooledAJPS %>% 
-    filter(type == "Pooled")
-
+    model = factor(model, levels = c("Original", "Uncertainty+Corrected", "Uncertainty+Expanded Data")))
+
+terms <- factor(rev(c("Democracy[t-1]",
+                      "Democracy[t-2]",
+                      "Support[t-1]",
+                      "Log~GDP~per~capita[t-1]",
+                      "GDP~per~capita~growth[t-1]",
+                      "Regional~democracy[t-1]",
+                      "Percent~Muslim[t-1]",
+                      "Resource~dependence[t-1]")), levels =
+                  rev(c("Democracy[t-1]",
+                        "Democracy[t-2]",
+                        "Support[t-1]",
+                        "Log~GDP~per~capita[t-1]",
+                        "GDP~per~capita~growth[t-1]",
+                        "Regional~democracy[t-1]",
+                        "Percent~Muslim[t-1]",
+                        "Resource~dependence[t-1]")))
+
+plot_AJPS1 <- dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms))) +
+  labs(
+    title = "DV: V-Dem Liberal Democracy Index",
+    subtitle = "Pooled"
+  ) +
+  facet_wrap(~type, scales = "free_x") + 
+  theme(legend.position = "none")
+
+###########Regime
 result_regime <- bind_rows(
   mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_correctAJPS[["pooled-regime"]]), model = "W. Uncertainty"),
+  mutate(MOCsumm(mocresult_correctAJPS[["pooled-regime"]]), model = "Uncertainty+Corrected"),
   mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), model = "Uncertainty+Expanded Data")
@@
   mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_correctAJPS[["gmm-regime"]]), model = "W. Uncertainty"),
+  mutate(MOCsumm(mocresult_correctAJPS[["gmm-regime"]]), model = "Uncertainty+Corrected"),
  mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), model = "Uncertainty+Expanded Data")
@@
     type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data")))
-
-result_ajpsRegime <- result_regimeAJPS %>%
-    filter(type == "Pooled") %>% 
-    mutate(type = "Regime Specified")
-
-```
-
-```{r coefName-AJPS}
-index_coefName <- c(
-    `Democracy\n (t-1)` = "Democracy[t-1]",
-    `Democracy\n (t-2)` = "Democracy[t-2]",
-    `Support\n (t-1)` = "Support[t-1]",
-    `Support\n demo only\n (t-1)` = "Support[t-1](demo~only)",
-    `Support\n auto only\n (t-1)` = "Support[t-1](auto~only)",
-    `Log GDP\n per capita\n (t-1)` = "Log~GDP~per~capita[t-1]",
-    `GDP per\n capita growth\n (t-1)` = "GDP~per~capita~growth[t-1]",
-    `Regional\n democracy\n (t-1)` = "Regional~democracy[t-1]",
-    `Percent\n Muslim\n (t-1)` = "Percent~Muslim[t-1]",
-    `Resource\n dependence\n (t-1)` = "Resource~dependence[t-1]"
-)
-```
-
-```{r plot-mainAJPS, fig.cap= "The Effect of Public Support on Democracy with Uncertainty", fig.width=7, fig.height=10, fig.align='center'}
-
-type_model <-
-  c("Original", "W. Uncertainty", "Uncertainty+Expanded Data")
-
-df_plot <- bind_rows(result_ajpsPooled, result_ajpsRegime) %>% 
-    mutate(term = index_coefName[term],
-           term = factor(term, levels = unique(index_coefName)))
-
-dwplot(df_plot) +
-    geom_vline(xintercept = 0,
-               colour = "grey80",
-               linetype = 2) +
-    theme_minimal() +
-    ggtitle("DV: Liberal Democracy (Vdem)") +
-    xlab("Coefficient Estimate") +
-    theme(
-        axis.title.y = element_blank(),
-        legend.position = "bottom",
-      legend.title = element_blank()
+    model = factor(model, levels = c("Original","Uncertainty+Corrected", "Uncertainty+Expanded Data")))
+terms2 <- factor(rev(c("Democracy[t-1]",
+                       "Democracy[t-2]",
+                       "Support[t-1] (democracies~only)",
+                       "Support[t-1] (autocracies~only)",
+                       "Log~GDP~per~capita[t-1]",
+                       "GDP~per~capita~growth[t-1]",
+                       "Regional~democracy[t-1]",
+                       "Percent~Muslim[t-1]",
+                       "Resource~dependence[t-1]")), levels =
+                   rev(c("Democracy[t-1]",
+                         "Democracy[t-2]",
+                         "Support[t-1] (democracies~only)",
+                         "Support[t-1] (autocracies~only)",
+                         "Log~GDP~per~capita[t-1]",
+                         "GDP~per~capita~growth[t-1]",
+                         "Regional~democracy[t-1]",
+                         "Percent~Muslim[t-1]",
+                         "Resource~dependence[t-1]")))
+plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms2))) +
+  labs(
+    title = "",
+    subtitle = "Regime Specified"
   ) +
-    scale_color_gb(palette = "digitMixed") +
-    facet_wrap(~ type)
-
-```
-
-The importance for taking the measurement uncertainty into account appear more evident when the relevant variable plays as the outcome variable. 
-In Figure \@ref(fig:plot-mainAPSR), we examine the thermostatic model of democratic support per @Claassen2020b [p. 47, Models 1.1 and 1.2]. 
-When the uncertainty is ignored, the coefficient of $\Delta$liberal democracy (the uppermost set), the yearly changes of the institutional feature is negative inferring that the change in democratic mood decreases as change in democracy increases and vice versa.
-However, when the measurement uncertainty is properly accounted (the middle set), the point estimate shifts towards zero and the coefficient is no longer significant.
-More data (the lowermost set), again, only adjusts the confidence intervals but not direction nor significance.
-
-```{r pointAPSR}
-# Reusing the sd.plm object, thus input data here rather than earlier
-
-load(here::here("data", "dem_mood_apsr.RData"))
-sd.plm <- pdata.frame(x, index = c("Country", "Year"))
-
-ls_ivECM <- c("diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)", 
-              "diff(Polyarchy_z, lag = 1) + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)")
-ls_ctrlECM <- c("", " + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1)")
-
-ls_eqECM <- glue("diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)") %>% 
-  outer(ls_ctrlECM, paste0) %>% 
-  as.vector()
-
-ls_ivFD <- c("Libdem_z",
-             "Polyarchy_z + Liberal_z")
-
-ls_ctrlFD <- c("", " + Corrup_TI_z")
-
-ls_eqFD <- glue("SupDem_trim ~ {ls_ivFD} + lnGDP_imp") %>% 
-  outer(ls_ctrlFD, paste0) %>% 
-  as.vector()
-
-ls_mod <- c(
-  glue("plm({ls_eqECM}, model = 'pooling', data = sd.plm)"),
-  glue("plm({ls_eqFD}, model = 'fd', index = 'Country', data = sd.plm)")
-)
-
-df_result_clsAPSR <- map(ls_mod, function(mod) {
-  result <- eval(parse(text = mod))
-})
-
-result_clsAPSR <- map(df_result_clsAPSR, function(aResult) {
-  tidy_result <- tidy(aResult, conf.int = TRUE) %>% 
-    mutate(std.error = vcovHC_se(aResult))
-
-  glance_result <- glance.plm(aResult)
-
-  ls_result <- list(tidy_result, glance_result)
-})
-
-names(result_clsAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", 
-                           "fd1", "fd-regime1", "fd2", "fd-regime2")
-
-saveRDS(result_clsAPSR, file = here("output", "estimates_clsMeanAPSR.RDS"))
-```
-
-```{r model-APSR}
-ls_ivECM <- c("diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)", 
-              "diff(Polyarchy_z, lag = 1) + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)")
-ls_ctrlECM <- c("", " + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1)")
-
-ls_eqECM <- glue("diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)") %>% 
-  outer(ls_ctrlECM, paste0) %>% 
-  as.vector()
-
-ls_ivFD <- c("Libdem_z",
-             "Polyarchy_z + Liberal_z")
-
-ls_ctrlFD <- c("", " + Corrup_TI_z")
-
-ls_eqFD <- glue("diff(SupDem_trim, lag = 1) ~ {ls_ivFD} + lnGDP_imp") %>% 
-  outer(ls_ctrlFD, paste0) %>% 
-  as.vector()
-
-ls_mod_apsrCLS <- c(
-  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
-  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
-)
-```
-
-```{r mocresult-pureAPSR, eval=FALSE}
+  facet_wrap(~type, scales = "free_x") +
+  theme(legend.position = "bottom", 
+        legend.title = element_blank())
+legend <- get_legend(plot_AJPS2)
+plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
+grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
+
+```
+
+```{r mocresult-pureAPSR}
 
@@
 
-```{r mocresult-expAPSR, eval=FALSE}
+```{r mocresult-expAPSR}
 
@@
 
-```{r formatResult-APSR}
-# Pooled---------------------------------------
+```{r plot-mocAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", eval = TRUE, fig.width=7, fig.height=12, eval=TRUE}
 
@@
   mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["pooled1"]]), model = "W. Uncertainty"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["pooled1"]]), model = "Uncertainty+Corrected"),
   mutate(MOCsumm2(mocresult_expAPSR[["pooled1"]]), model = "Uncertainty+Expanded Data")
@@
   mutate(result_clsAPSR[["fd1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["fd1"]]), model = "W. Uncertainty"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["fd1"]]), model = "Uncertainty+Corrected"),
   mutate(MOCsumm2(mocresult_expAPSR[["fd1"]]), model = "Uncertainty+Expanded Data")
@@
     type = factor(type,  levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data"))
-  )
-
-result_apsrPooled <- result_APSR1 %>% 
-    filter(type == "ECM") %>% 
-    mutate(type = "Pooled")
-
-# Institution----------------------------------
+    model = factor(model, levels = c("Original","Uncertainty+Corrected", "Uncertainty+Expanded Data"))
+  )
+
+terms1 <- factor(rev(c("Support[t-1]",
+                       "Support[t-2]",
+                       "Delta~Liberal~democracy",
+                       "Liberal~democracy[t-1]",
+                       "Delta~Log~GDP~per~capita",
+                       "Log~GDP[t-1]")),
+                 levels = rev(c("Support[t-1]",
+                                "Support[t-2]",
+                                "Delta~Liberal~democracy",
+                                "Liberal~democracy[t-1]",
+                                "Delta~Log~GDP~per~capita",
+                                "Log~GDP[t-1]")))
+plot_APSR1 <- dwplot(result_APSR1, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms1))) +
+  labs(
+    title = "DV: The Change of Public Support for Democracy",
+    subtitle = "Pooled"
+  ) +
+  facet_wrap(~type, drop=T,scales = "free_x") +
+  theme(legend.position = "none")
+
+############################ Regime specified####
 
@@
   mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime1"]]), model = "W. Uncertainty"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime1"]]), model = "Uncertainty+Corrected"),
   mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime1"]]), model = "Uncertainty+Expanded Data")
@@
   mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime1"]]), model = "W. Uncertainty"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime1"]]), model = "Uncertainty+Corrected"),
   mutate(MOCsumm2(mocresult_expAPSR[["fd-regime1"]]), model = "Uncertainty+Expanded Data")
@@
     type = factor(type,  levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data"))
-  )
-
-result_apsrRegime <- result_RegAPSR1 %>% 
-    filter(type == "ECM") %>% 
-    mutate(type = "Institution Specified")
-
-# Pooled-corruption------------------------------
+    model = factor(model, levels = c("Original","Uncertainty+Corrected", "Uncertainty+Expanded Data"))
+  )
+terms3 <- factor(rev(c("Support[t-1]",
+                       "Support[t-2]",
+                       "Delta~Electoral~democracy",
+                       "Electoral~democracy[t-1]",
+                       "Delta~Minoritarian~democracy",
+                       "Minoritarian~democracy[t-1]",
+                       "Delta~Log~GDP~per~capita",
+                       "Log~GDP[t-1]")),
+                 levels = rev(c("Support[t-1]",
+                                "Support[t-2]",
+                                "Delta~Electoral~democracy",
+                                "Electoral~democracy[t-1]",
+                                "Delta~Minoritarian~democracy",
+                                "Minoritarian~democracy[t-1]",
+                                "Delta~Log~GDP~per~capita",
+                                "Log~GDP[t-1]")))
+plot_RegAPSR1 <- dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms3))) +
+  labs(
+    title = "",
+    subtitle = "Institution Specified"
+  ) +
+  facet_wrap(~type, scales = "free_x") + 
+  theme(legend.position = "none")
+
+#########Corruption
 
@@
   mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["pooled2"]]), model = "W. Uncertainty"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["pooled2"]]), model = "Uncertainty+Corrected"),
   mutate(MOCsumm2(mocresult_expAPSR[["pooled2"]]), model = "Uncertainty+Expanded Data")
@@
   mutate(result_clsAPSR[["fd2"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["fd2"]]), model = "W. Uncertainty"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["fd2"]]), model = "Uncertainty+Corrected"),
   mutate(MOCsumm2(mocresult_expAPSR[["fd2"]]), model = "Uncertainty+Expanded Data")
@@
     type = factor(type,  levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data"))
-  )
-
-# Institution Corruption--------------------------------
+    model = factor(model, levels = c("Original","Uncertainty+Corrected", "Uncertainty+Expanded Data"))
+  )
+terms2 <- factor(rev(c("Support[t-1]",
+                       "Support[t-2]",
+                       "Delta~Liberal~democracy",
+                       "Liberal~democracy[t-1]",
+                       "Delta~Log~GDP~per~capita",
+                       "Log~GDP[t-1]",
+                       "Delta~Corruption",
+                       "Corruption[t-1]")),
+                 levels = rev(c("Support[t-1]",
+                                "Support[t-2]",
+                                "Delta~Liberal~democracy",
+                                "Liberal~democracy[t-1]",
+                                "Delta~Log~GDP~per~capita",
+                                "Log~GDP[t-1]",
+                                "Delta~Corruption",
+                                "Corruption[t-1]")))
+plot_APSR2 <- dwplot(result_APSR2, dodge_size = 0.8, by_2sd = FALSE) +
+  scale_y_discrete(labels = parse(text = levels(terms2))) +
+  labs(
+    title = "",
+    subtitle = "W. Corruption"
+  ) +
+  facet_wrap(~type, scales = "free_x") +
+  theme(legend.position = "none")
+
+#########Regime + Corruption
 
@@
   mutate(result_clsAPSR[["pooled-regime2"]][[1]][,1:3], model = "Original"),
- mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime2"]]), model = "W. Uncertainty"),
+ mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime2"]]), model = "Uncertainty+Corrected"),
   mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime2"]]), model = "Uncertainty+Expanded Data")) %>%
@@
   mutate(result_clsAPSR[["fd-regime2"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime2"]]), model = "W. Uncertainty"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime2"]]), model = "Uncertainty+Corrected"),
   mutate(MOCsumm2(mocresult_expAPSR[["fd-regime2"]]), model = "Uncertainty+Expanded Data")) %>% 
@@
     type = factor(type,  levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data"))
-  )
-```
-
-```{r coefName-APSR}
-index_coefName <- c(
-    `Democratic Mood\n (t-1)` = "Support[t-1]",
-    `Democratic Mood\n (t-2)` = "Support[t-2]",
-    `Liberal Democracy\n (Difference)` = "Delta~Liberal~democracy",
-    `Liberal Democracy\n (t-1)` = "Liberal~democracy[t-1]",
-    `Electoral Democracy\n (Difference)` = "Delta~Electoral~democracy",
-    `Electoral Democracy\n (t-1)` = "Electoral~democracy[t-1]",
-    `Minoritarian Democracy\n (Difference)` = "Delta~Minoritarian~democracy",
-    `Minoritarian Democracy\n (t-1)` = "Minoritarian~democracy[t-1]",
-    `Log GDP\n per capita\n (Difference)` = "Delta~Log~GDP~per~capita",
-    `Log GDP\n (t-1)` = "Log~GDP[t-1]"
-)
-```
-
-```{r plot-mainAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", fig.width=7, fig.height=10}
-type_model <-
-    c("Original", "W. Uncertainty", "Uncertainty+Expanded Data")
-
-df_plot <- bind_rows(result_apsrPooled, result_apsrRegime) %>%
-    mutate(
-        term = index_coefName[term],
-        term = factor(term, levels = unique(index_coefName)),
-        type = factor(type, levels = c("Pooled", "Institution Specified"))
-    )
-
-dwplot(df_plot) +
-    geom_vline(xintercept = 0,
-               colour = "grey80",
-               linetype = 2) +
-    ggtitle("DV: The Change of Public Support for Democracy") +
-    xlab("Coefficient Estimate") +
-    theme(
-        axis.title.y = element_blank(),
-        legend.position = "bottom",
-        legend.title = element_blank()
-    ) +
-    facet_wrap(~ type) +
-    scale_color_gb(palette = "digitMixed")
-
-```
-
-# Discussion
-
-In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support has a positive effect on democracy and change in democracy a negative effect on change in support are not empirically supported once measurement uncertainty is taken into account, even when more data are used.
-
-There are theoretical explanations for the null results.
-With regard to how levels of democracy affect public support, we note that even the proponents of the classic argument did not contend that the mere existence of democratic institutions, no matter how consistently feckless and ineffective, would generate support among the public: instead, they maintained, public support would be gained through experience with government performance that was generally effective [@lipset_social_1959, 86-89; @Easton1965, 119-120].
-There is some empirical support for this, with government effectiveness positively related to public support among democracies and negatively related in non-democracies [@Magalhaes2014]. 
-The finding of @Krieckhaus2014 that income inequality is strongly negatively related to public support in democracies suggests that performance regarding redistribution is particularly important.
-Relatedly, on the reverse part of the classic argument, @Qi2011 suggests that democratic support alone cannot be expected to generate democratic change and oppose backsliding.
-Instead, that work contends, it is the combination of democratic support and dissatisfaction with current regime performance that generates demand for greater democracy.
-The effects of public support also have cultural-bound.
-@Brunkert2019[p.
-423] contends outspoken support for democracy is a "deceptive indicator of public's affinity to democracy"  and finds public support has neither pro-democratic nor anti-authoritarian effect without controlling emancipative values.
-Empirical results show that the meaning of support for democracy is dependent on emancipation values and is reversed to its own negation in a society with weak emancipative values [see, e.g.,@Kirsch2019, 83-85].
-And we must be open to the possibility that no theoretical elaboration, no respecification of these models will reveal relationships between public opinion and democracy.
-Democratic backsliding may simply be primarily a matter of elite decision making [see, e.g., @levitsky_how_2018].
-
-There are several potential methodological explanations for these null results as well.
-One issue is that the survey items employed---which ask respondents to assess the desirability or appropriateness of democracy, to compare democracy to some undemocratic alternative, or to assess one of these alternatives---may not capture every aspect of democratic support necessary for it to play its hypothesized roles in the classic theory.
-If only those who profess to prefer democracy to its alternatives _and also_ value freedom of expression, freedom of association, and pluralism of opinion will take appropriate action when democracy is threatened, then this measure is inadequate to its purpose [see, e.g., @Schedler2007].
-Moreover, given the multi-faceted nature of democratic attitudes, even the inclusion of such questions in unidimensional public opinion models such as those provided by @Claassen2019 or @Solt2020a are unlikely to be sufficient [see, e.g., @Wuttke2020].
-Another issue is that even if these survey questions do capture support for the generic concept of democracy, these measurement models might still be incapable of suitably capturing democratic support due to the variation in understanding the concept across countries or over time within countries [@Wuttke2021].
-Yet another is that this measure provides no assessment of the _relative_ importance the public affords democracy.
-It provides no information on the extent to which other values, such as policy preferences or partisanship, weigh more heavily---and there is growing evidence that, at least in the United States, there are many for whom these other considerations excuse substantial transgressions against democracy [see @bartels_ethnic_2020; @Carey2020; @graham_democracy_2020; @McCoy2020].
-Regardless, these explanations indicate that there remains much work to be done in the empirical study of public support and democracy.
-
-# Conclusion
-
-In this letter, we reexamine the findings from Claassen [-@Claassen2020a; -@Claassen2020b], two articles that maintain that public support helps the survival of democracy and democratic development has a thermostatic effect on public support.
-We demonstrate the importance of incorporating measurement uncertainty in analyzing the relationship between public support and democracy.
-Taking uncertainty into account rendered both articles' conclusions without empirical support, even when we added considerable more data.
-
-This points to the absolute necessity of incorporating measurement uncertainty into analyses that include latent variables.
-Measurement issues have never had a prominent place in comparative political studies because they need more time to estimate models, but they ground the quality of data and the basis of analysis [@stegmueller2011, 484].
-As the use of latent variables grows more common in political science, both researchers and readers should be aware that these variables' concomitant measurement uncertainty cannot be neglected.
-
-The null results reached in this letter could arise from several sources.
-There are theoretically grounded reasons of government effectiveness, democratic understanding, and generical-or-behavioral support to suspect that the relationships are in fact negligible.
-We also identified a number of potential shortcomings in the measurement of democratic support and ways in which the analysis models might be underspecified.
-All of these could and should be explored in future research.
-In any event, the sanguine assessment that readers may draw from Claassen [-@Claassen2020a; -@Claassen2020b]---that the fate of democracies depend on public support, and when eroded, their public will rally to them---is not supported by the current evidence.
-Those who would defend democracy have no grounds to be complacent.
-
-# References  {-}
-
-<div id = 'refs'></div>
-
-\pagebreak
-
-# Online Supplementary Materials {-}
-# (APPENDIX) Appendix {-}
-# Data Recollection and Uncertainty in Control Variables {#dgp}
-
-Due to revisions to the underlying datasets (and, possibly, transcription errors), we were not able to achieve a primary replication [@Grossman2020] based on survey data summarized in @Claassen2020a and @Claassen2020b's Dataverse files.
-
-Specifically, we are not able to identify 5 cournty-year surveys, including South Sudan in Arab Barometer Wave 4, Dominican Republic in 2003 Latinobarometer, XXXX, and Spain in 2005 Latinobarometer. 
-In addition, we still have different sample size and number of respondents answering supportively by following approaches of cleanning data and treatment of non-responses described in @Claassen2020a's supplementatry materials.
-Specifically, we used Claassen's year coding to recode 85 unmatching country-year observations and added one more item "strong leader 2" in Arabbarometer which has different response categories but was conflated into "strong leader 1".
-
-V-Dem data was standardized in @Claassen2020b's analyses, but we did not figure out how the standardization was exactly performed.
-We standardized variables using Z-score, and the standardized values are different from Claassen's data.
-
-We also include measurement errors in control variables, including three democratic indices and corruption index.
-We extracted the posterior distributions of democratic indices, including Liberal Democracy,polyarchy, and electoral democracy index, which are provided by [@coppedge2018].
-We drew 900 samples from the distribution of the Corruption Perception Index.
-Since Corruption Perception Index does not provide standard error before 2011, we imputed the missing standard error using the multiplication of a country's corruption index and the ratio of its available maximum standard error to its corresponding index.
-
-# Replication with Alternative Methods Accounting for Uncertainty {#moc}
-
-To ensure the robustness of our analysis, we apply another method to account for uncertainty.
-The method we employ is "method of composition" (MOC).
-It is a common method for Monte Carlo integration, but can also be applied for addressing uncertainty [@Treier2008].
-To compare these two methods, let's denote `y` as a vector of the outcome variable [either institutional democracy in @Claassen2020a or the changes in mass support of democracy in @Claassen2020b]. 
-Let $x$ (variables without subscript are used to denote vectors of observations, viz., $x$ = ($x_1$,......, $x_i$)) be a vector of the explanatory variable (e.g., mass support or institutional democracy) and $\theta$ be the parameter of interest.
-
-Rubin's Rules (RR, the method used in the main article) take variables with measurement error as missing value, and combine the point estimates and standard errors into single values yet accounting for both within and between imputation variances [@Rubin1987].
-
-Rubein's Rules is defined in the following formulas.
-
-\begin{equation}
-\bar{\theta}_{m} = \frac{1}{m}\sum_{i=1}^{m} \theta_{i}.
-\end{equation}
-
-\begin{equation}
-{V}_{B} = \frac{1}{m-1}\sum_{i=1}^{m} (\theta_{i}-\bar{\theta}_{m})^2.
-\end{equation}
-
-\begin{equation}
-{V}_{W} = \frac{1}{m}\sum_{i=1}^{m} SE_{i}^2.
-\end{equation}
-
-\begin{equation}
-{V}_{T} = {V}_{w} +(1+ \frac{1}{m})\frac{V_B}{m}.
-\end{equation}
-
-$\bar{\theta}_{M}$ is the pooled parameter estimate, $m$ is the number of imputed datasets, $V_{B}$ is between imputation variance, $V_{W}$ within imputation variance, $V_{T}$ is total variance.
-
-The general formula for confidence interval (CI) is defined as:
-
-\begin{equation}
-\bar{\theta} \pm t_{df,1-\alpha/2} *\sqrt{V_{T}}.
-\end{equation}
-
-$df$ is calculated by using $df_{Adjusted}$ [@barnard1999] and the Fraction of Missing information, lambda, is derived from between and total variance [@raghunathan2015, @van2018].
-
-\begin{equation}
-{df_{Adjusted}} = \frac{df_{Old}*df_{Observed}}{df_{Old}+df_{Observed}}.
-\end{equation}
-
-\begin{equation}
-{df_{Old}} = \frac{(n-k)+1}{(n-k)+3} * (n-k)(1-lambda).
-\end{equation}
-
-\begin{equation}
-{df_{Observed}} = \frac{(n-k)+1}{(n-k)+3} * (n-k)(1-lambda).
-\end{equation}
-
-\begin{equation}
-{Lambda} = \frac{V_{B}+\frac{V_{B}}{m}}{V_{T}}
-\end{equation}
-
-One main idea behind RR is to account for both within imputation variance and sample variance which is due to the missing data (measurement error in our case).
-
-In analysis models, we have latent variables in both sides of equations, public suppport for democracy, democracy indices and corruption index (The latter one is included in APSR analyses).
-Since measurement uncertainty associated with these latent variables can propogate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing "Method of Composition" [@Tanner1996,p52], which has been applied in analyses with latent variables [@Trei2008;@Caughey2018;@K2015].
-As @Caughey2018 explained, the main idea of MOC is to estimate the marginal distribution of coefficient parameter vector $\beta$, intergrating over the uncertainty in latent variables $\theta$ (P A-15).
-More explicitly, we wish to integrate the joint density of $\beta$ and $\theta$ over the distribution of $\theta$.
-
-\begin{equation}
-p(\beta,\theta|w,y, Z) = p(\beta|\theta,w,y)p(\theta|Z).
-\end{equation}
-
-where $\theta$ is latent varibles with measurement errors conditional on data Z and a measurement model, $w$ is other predictors without errors, $Z$ is indicators for latent variables $X$, and $y$ is the outcome variable.
-In this way, we incorportate uncertainty in measuring predictor $\theta$, and uncertainty in the effects of latent variables $\theta$ and other variables $w$ on outcome variable $y$ [@Treie2008, 215].
-To sample from the conditional dentsity and the marginal density in the right side of the equation, we follow iterative Monte Carlo procdure described by @Treier2008, at iteration t,
-1. We sample $\theta^{s}$ from its posterior distribution $p(\theta|Z)$ and $y$ from $p(y|Z)$. 
-2.
-For each analysis model, we run the model with $y$, $\theta$, and $w$, and save the coefficient estimates $\beta^{s}$ and variance-covariance matrix of $\beta^{s}$, $V^{s}$, both of which change due to the uncertainty in $\theta^{s}$ and $y^{s}$.
-3. We sample $\tilde{\beta^{t}}$ from the multivariate normal density with mean vector $\beta{s}$ and variance-covariace matrix $V^{s}$.
-
-We incorporate uncertainty for five variables, public support for democracy, liberal democracy, electoral democracy, liberal component index, and corruption perceptions index.
-
-MOC addresses the same issue from a slightly different angle.
-The method assumes that the explanatory and outcome variables are samples from their estimate functions, and their paired sample follows a joint density [@Tanner1993, p.31].
-From the joint density, one can decomposite the likelihood of the explanatory variable and its parameter to a product of their own probabilities.
-When x is measured with errors $w$, the probability becomes conditional:
-
-\begin{equation}
-\mathcal{L}(\theta, x|y, w) = p(\theta|x,y)p(x|w).
-\end{equation}
-
-Based on this decomposition, one can estimate the marginal density for &\theta&:
-
-\begin{equation}
-\mathcal{L}(\theta|y, x) \propto \int_{\chi} p(\theta|y,x)p(x|w)dx.
-\end{equation}
-
-Again, the gained parameter density can be combined into single values.
-A common way to do so is using the mean of $theta$ as the point estimate, and the variance from the density as the standard error.
-
-```{r plot-mocAJPS, fig.cap= "The Effect of Public Support on Democracy ", eval = TRUE, fig.width=7, fig.height=10}
-terms <- factor(rev(
-    c(
-        "Democracy[t-1]",
-        "Democracy[t-2]",
-        "Support[t-1]",
-        "Log~GDP~per~capita[t-1]",
-        "GDP~per~capita~growth[t-1]",
-        "Regional~democracy[t-1]",
-        "Percent~Muslim[t-1]",
-        "Resource~dependence[t-1]"
-    )
-), levels =
-    rev(
-        c(
-            "Democracy[t-1]",
-            "Democracy[t-2]",
-            "Support[t-1]",
-            "Log~GDP~per~capita[t-1]",
-            "GDP~per~capita~growth[t-1]",
-            "Regional~democracy[t-1]",
-            "Percent~Muslim[t-1]",
-            "Resource~dependence[t-1]"
-        )
-    ))
-
-plot_AJPS1 <-
-    dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms))) +
-    labs(title = "DV: V-Dem Liberal Democracy Index",
-         subtitle = "Pooled") +
-    facet_wrap( ~ type, scales = "free_x") +
-    theme(legend.position = "none") +
-    scale_color_gb(palette = "digitMixed")
-
-terms2 <- factor(rev(
-    c(
-        "Democracy[t-1]",
-        "Democracy[t-2]",
-        "Support[t-1] (democracies~only)",
-        "Support[t-1] (autocracies~only)",
-        "Log~GDP~per~capita[t-1]",
-        "GDP~per~capita~growth[t-1]",
-        "Regional~democracy[t-1]",
-        "Percent~Muslim[t-1]",
-        "Resource~dependence[t-1]"
-    )
-), levels =
-    rev(
-        c(
-            "Democracy[t-1]",
-            "Democracy[t-2]",
-            "Support[t-1] (democracies~only)",
-            "Support[t-1] (autocracies~only)",
-            "Log~GDP~per~capita[t-1]",
-            "GDP~per~capita~growth[t-1]",
-            "Regional~democracy[t-1]",
-            "Percent~Muslim[t-1]",
-            "Resource~dependence[t-1]"
-        )
-    ))
-
-plot_AJPS2 <-
-    dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms2))) +
-    labs(title = "",
-         subtitle = "Regime Specified") +
-    facet_wrap( ~ type, scales = "free_x") +
-    theme(legend.position = "bottom",
-          legend.title = element_blank()) +
-    scale_color_gb(palette = "digitMixed")
-
-legend <- get_legend(plot_AJPS2)
-
-plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
-
-grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
-```
-
-\blandscape
-
-```{r plot-mocAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", eval = TRUE, fig.width=10, fig.height=10}
-terms1 <- factor(rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Liberal~democracy",
-        "Liberal~democracy[t-1]",
-        "Delta~Log~GDP~per~capita",
-        "Log~GDP[t-1]"
-    )
-),
-levels = rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Liberal~democracy",
-        "Liberal~democracy[t-1]",
-        "Delta~Log~GDP~per~capita",
-        "Log~GDP[t-1]"
-    )
-), 
-labels = rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Liberal~Dem",
-        "Liberal~Dem[t-1]",
-        "Delta~Log~GDP~per~capita",
-        "Log~GDP[t-1]"
-    )
-))
-
-plot_APSR1 <-
-    dwplot(result_APSR1, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms1))) +
-    labs(title = "DV: The Change of Public Support for Democracy",
-         subtitle = "Pooled") +
-    facet_wrap( ~ type, drop = T, scales = "free_x") +
-    theme(legend.position = "none") +
-    scale_color_gb(palette = "digitMixed")
-
-terms3 <- factor(rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Electoral~democracy",
-        "Electoral~democracy[t-1]",
-        "Delta~Minoritarian~democracy",
-        "Minoritarian~democracy[t-1]",
-        "Delta~Log~GDP~per~capita",
-        "Log~GDP[t-1]"
-    )
-),
-levels = rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Electoral~democracy",
-        "Electoral~democracy[t-1]",
-        "Delta~Minoritarian~democracy",
-        "Minoritarian~democracy[t-1]",
-        "Delta~Log~GDP~per~capita",
-        "Log~GDP[t-1]"
-    )
-),
-labels = rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Electoral",
-        "Electoral[t-1]",
-        "Delta~Minoritarian",
-        "Minoritarian[t-1]",
-        "Delta~Log~GDP~per~capita",
-        "Log~GDP[t-1]"
-    )
-)
-)
-
-plot_RegAPSR1 <-
-    dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms3))) +
-    labs(title = "",
-         subtitle = "Institution Specified") +
-    facet_wrap( ~ type, scales = "free_x") +
-    theme(legend.position = "none") +
-    scale_color_gb(palette = "digitMixed")
-
-terms2 <- factor(rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Liberal~democracy",
-        "Liberal~democracy[t-1]",
-        "Delta~Log~GDP~per~capita",
-        "Log~GDP[t-1]",
-        "Delta~Corruption",
-        "Corruption[t-1]"
-    )
-),
-levels = rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Liberal~democracy",
-        "Liberal~democracy[t-1]",
-        "Delta~Log~GDP~per~capita",
-        "Log~GDP[t-1]",
-        "Delta~Corruption",
-        "Corruption[t-1]"
-    )
-),
-labels = rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Liberal~Dem",
-        "Liberal~Dem[t-1]",
-        "Delta~Log~GDP~per~capita",
-        "Log~GDP[t-1]",
-        "Delta~Corruption",
-        "Corruption[t-1]"
-    )
-))
-
-plot_APSR2 <-
-    dwplot(result_APSR2, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms2))) +
-    labs(title = "",
-         subtitle = "W. Corruption") +
-    facet_wrap( ~ type, scales = "free_x") +
-    theme(legend.position = "none") +
-    scale_color_gb(palette = "digitMixed")
-
-terms4 <- factor(rev(
-    c(
-        "Support[t-1]",
+    model = factor(model, levels = c("Original","Uncertainty+Corrected", "Uncertainty+Expanded Data"))
+  )
+terms4 <- factor(rev(c("Support[t-1]",
                        "Support[t-2]",
@@
                        "Delta~Corruption",
-        "Corruption[t-1]"
-    )
-),
-levels = rev(
-    c(
-        "Support[t-1]",
+                       "Corruption[t-1]")),
+                 levels = rev(c("Support[t-1]",
                                 "Support[t-2]",
@@
                                 "Delta~Corruption",
-        "Corruption[t-1]"
-    )
-),
-labels = rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Electoral",
-        "Electoral[t-1]",
-        "Delta~Minoritarian",
-        "Minoritarian[t-1]",
-        "Delta~Log~GDP",
-        "Log~GDP[t-1]",
-        "Delta~Corruption",
-        "Corruption[t-1]"
-    )
-))
-
-plot_RegAPSR2 <-
-    dwplot(result_RegAPSR2, dodge_size = 0.8, by_2sd = FALSE) +
+                                "Corruption[t-1]")))
+plot_RegAPSR2 <- dwplot(result_RegAPSR2, dodge_size = 0.8, by_2sd = FALSE) +
   scale_y_discrete(labels = parse(text = levels(terms4))) +
-    labs(title = "",
-         subtitle = "Institution Specified w. Corruption") +
-    facet_wrap( ~ type, scales = "free_x") +
+  labs(
+    title = "",
+    subtitle = "Institution Specified w. Corruption"
+  ) +
+  facet_wrap(~type, scales = "free_x") +
   theme(legend.position = "bottom", 
-          legend.title = element_blank()) +
-    scale_color_gb(palette = "digitMixed")
+        legend.title = element_blank())
 
@@
 
-grid.arrange(plot_APSR1,
-             plot_APSR2,
-             plot_RegAPSR1,
-             plot_RegAPSR2,
-             legend,
-             ncol = 2)
-```
-
-\elandscape
+grid.arrange(plot_APSR1, plot_APSR2, plot_RegAPSR1, plot_RegAPSR2, legend, ncol = 1)
+
+```
 

### 2021-08-11 paper/memo/memo.Rmd
updating memo on random walk.

--- 2021-08-04 paper/memo/memo.Rmd
@@
     fig_caption: true
-    latex_engine: xelatex
+    latex_engine: pdflatex
     template: ../svm-latex-ms2.tex
@@
 Regarding Reviewer 1's request on replicating all specifications in the original two studies, we added alternate specifications on the relationship between public support and democracy, including GMM models, First Different Models, and sample split.
-See Page xxx, Figure xxx, and xxx in SI.
+Results do not change in all these models, presented on Page xxx, Figure xxx, and xxx in SI. 
+As the editor suggested, this letter should focus on the core point: the relationship between public support and democracy. We do not replicate specifications on other relationships.
 

### 2021-08-11 paper/memo/memo.Rmd
updating memo

--- 2021-08-09 paper/memo/memo.Rmd
@@
 
-The understand of democracy problem could be "misunderstanding" in both authoritarian countries and democratic countries. 
-In democracies, the "misunderstanding" is related to another issue which should attract more theoretical discussion, that is, the choice between generic support for democracy and other values especially in the long built democracies [see @bartels_ethnic_2020; @Carey2020; @graham_democracy_2020; @McCoy2020].
-The disparity between the public's generic support and their commitment to support lends light to the recent democracy crisis and the uprising of populism witnessed in well-developed democracies.
+Thanks to reviewer2's comments on random walk, we do think we should discuss more on problems caused by random walk, which actually provides us another powerful explanation for our results.
+In order to isolate the effect of different priors on estimated measures, in revised version, we only employed Claassen's Model5 with original data, recollected data and expanded data, separately.
+A bigger size of observed data is expected to reduce the possible dominance of priors.
+However, even though we put efforts to collect as much data as possible.
+The expanded data is only xxx county-year.
+It is possible that the changes of public mood are "smooth" out by modeling the temporal evolution in a simple local-level dynamic linear.
+The smoothed time series data might fail to capture a sudden change which is caused by exogenous factors.
+Given the sparsed available data and effects from random walk prior, it is highly possible that we cannot detect any significant effect from institution changes and other economic and social factors.
+Futhermore, scholars should be careful of using estimated latent variable as a dependent variable when source data is sparsed.
+We are planning to carry out more work on figuring out at what rate the sparseness of source data will post severe problems in statistical inference, which will faciliate scholars' usage of latent variable measures.
 
-<!--
-thanks to reviewer2's comments on random walk, we do think we should discuss more on problems caused by random walk, which actually provides us another powerful explanation for our results. 
-In terms of the impact of measurement error on estimated effects, many studies have shown that when taking measurement uncertainty into account, the magnitude of coefficients of latent variables can be either attenuated or enlarged substantively [e.g., @Treier2008, p.
+In terms of the impact of measurement error on estimated effects, as we illustrated in Appendix, point estimates of coefficients are calculated from samples drawn from joint distribution of estimated latent variable and coefficients, which incorporate both uncertainty in latent variable measurements and the relationship between outcome variables and covariates.
+Given the big uncertainty in two parts, we should expect the estimated effects are different from point estimates from models without accounting uncertainty. 
+Many studies have already shown that when taking measurement uncertainty into account, the magnitude of coefficients of latent variables can be either attenuated or enlarged substantively [e.g., @Treier2008, p.
 211; @caughey2018,p.
 254].
--->
 

### 2021-08-11 paper/dcpo_demsupport.Rmd
add DCPO in SI.

--- 2021-08-09 paper/dcpo_demsupport.Rmd
@@
 load(here("data","exp_claassen_input.rda"))
+load(here("data","dcpo_apsr.rda"))
+load(here("data","dcpo_ajps.rda"))
 
@@
 
+result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
+result_clsAJPS <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
+
 mocresult_correctAJPS <- readRDS(here("output", "estimates_moc_correctAJPS.RDS")) 
@@
 mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expcorAPSR.RDS"))
-
+mocdcpo_APSR <- readRDS(here("ouput","estimates_moc_dcpoAPSR.RDS"))
+mocresult_dcpoAJPS <- readRDS(here("output","estimates_moc_dcpoAJPS.RDS"))
 ```
@@
   distinct() %>% 
-  nrow()
+  nrow() #1165
 
@@
 
-Specifically, we are not able to identify 5 cournty-year surveys, including South Sudan in Arab Barometer Wave 4, Dominican Republic in 2003 Latinobarometer, XXXX, and Spain in 2005 Latinobarometer. 
+Specifically, we are not able to identify 5 country-year surveys, including South Sudan in Arab Barometer Wave 4, Dominican Republic in 2003 Latinobarometer, XXXX, and Spain in 2005 Latinobarometer. 
 In addition, we still have different sample size and number of respondents answering supportively by following approaches of cleanning data and treatment of non-responses described in @Claassen2020a's supplementatry materials.
@@
 
+# DCPO Replication {#dcpo}
+
+```{r dcpo-APSR, eval=FALSE}
+
+dcpo_APSR <- purrr::map(1:900, function(anEntry) {
+  dcpo_apsr[[anEntry]] %>% 
+    plm::pdata.frame(index = c("country", "year")) %>%
+    rename(SupDem_trim = theta_trim,
+          First_yr = first_year,
+          Libdem_z = Vdem_libdem_z,
+          Polyarchy_z = Vdem_polyarchy_z,
+          Liberal_z = Vdem_liberal_z,
+          Corrup_TI_z = corruption_z,
+          lnGDP_imp = lg_imp_mdpgdp)
+}
+)
+
+mocdcpo_APSR  <- map(ls_mod_apsrCLS, function(aMod){
+  result <- methodComposition3(dcpo_APSR,aMod)
+})
+
+names(mocdcpo_APSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
+                                "fd1", "fd-regime1", "fd2", "fd-regime2")
+
+saveRDS(mocdcpo_APSR, file = here::here("ouput","estimates_moc_dcpoAPSR.RDS"))
+```
+
+```{r formatDCPOResult-APSR}
+# Pooled---------------------------------------
+
+result_ecm1 <- bind_rows(
+  mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm2(mocresult_expAPSR[["pooled1"]]), model = "Uncertianty+ExpData"),
+  mutate(MOCsumm2(mocdcpo_APSR[["pooled1"]]), model = "Uncertianty+DCPO+ExpData")
+) %>% 
+  mutate(type = "ECM")
+
+result_fd1 <- bind_rows(
+  mutate(result_clsAPSR[["fd1"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm2(mocresult_expAPSR[["fd1"]]), model = "Uncertianty+ExpData"),
+  mutate(MOCsumm2(mocdcpo_APSR[["fd1"]]), model = "Uncertianty+DCPO+ExpData")
+) %>% 
+  mutate(type = "First Difference")
+
+result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+        "Liberal Democracy\n (Difference)",
+        "Liberal Democracy\n (t-1)",
+        "Log GDP\n per capita\n (Difference)",
+        "Log GDP\n (t-1)"),
+      time = 3),
+      rep(
+        c("Liberal Democracy\n (Difference)", 
+          "Log GDP\n per capita\n (Difference)"), 
+        time = 3
+      )),
+    type = factor(type,  levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Original","Uncertianty+ExpData", "Uncertianty+DCPO+ExpData"))
+  )
+
+result_apsrPooled <- result_APSR1 %>% 
+    filter(type == "ECM") %>% 
+    mutate(type = "Pooled")
+
+# Institution----------------------------------
+
+result_ecmReg1 <- bind_rows(
+  mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime1"]]), model = "Uncertianty+ExpData"),
+  mutate(MOCsumm2(mocdcpo_APSR[["pooled-regime1"]]), model = "Uncertianty+DCPO+ExpData")
+) %>% 
+  mutate(type = "ECM")
+
+result_fdReg1 <- bind_rows(
+  mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime1"]]), model = "Uncertianty+ExpData"),
+  mutate(MOCsumm2(mocdcpo_APSR[["fd-regime1"]]), model = "Uncertianty+DCPO+ExpData")
+) %>% 
+  mutate(type = "First Difference")
+
+result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+        "Electoral Democracy\n (Difference)",
+        "Electoral Democracy\n (t-1)",
+        "Minoritarian Democracy\n (Difference)",
+        "Minoritarian Democracy\n (t-1)",
+        "Log GDP\n per capita\n (Difference)",
+        "Log GDP\n (t-1)"),
+      time = 3),
+      rep(
+        c("Electoral Democracy\n (Difference)", 
+          "Minoritarian Democracy\n (Difference)",
+          "Log GDP\n per capita\n (Difference)"), 
+        time = 3
+      )),
+    type = factor(type,  levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Original","Uncertianty+ExpData", "Uncertianty+DCPO+ExpData"))
+  )
+
+result_apsrRegime <- result_RegAPSR1 %>% 
+    filter(type == "ECM") %>% 
+    mutate(type = "Institution Specified")
+
+# Pooled-corruption------------------------------
+
+result_ecm2 <- bind_rows(
+  mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm2(mocresult_expAPSR[["pooled2"]]), model = "Uncertianty+ExpData"),
+  mutate(MOCsumm2(mocdcpo_APSR[["pooled2"]]), model = "Uncertianty+DCPO+ExpData")
+) %>% 
+  mutate(type = "ECM")
+
+result_fd2 <- bind_rows(
+  mutate(result_clsAPSR[["fd2"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm2(mocresult_expAPSR[["fd2"]]), model = "Uncertianty+ExpData"),
+  mutate(MOCsumm2(mocdcpo_APSR[["fd2"]]), model = "Uncertianty+DCPO+ExpData")
+) %>% 
+  mutate(type = "First Difference")
+
+result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+        "Liberal Democracy\n (Difference)",
+        "Liberal Democracy\n (t-1)",
+        "Log GDP\n per capita\n (Difference)",
+        "Log GDP\n (t-1)",
+        "Corruption\n (Difference)",
+        "Corruption\n (t-1)"
+      ),
+      time = 3),
+      rep(
+        c("Liberal Democracy\n (Difference)", 
+          "Log GDP\n per capita\n (Difference)",
+          "Corruption\n (Difference)"), 
+        time = 3
+      )),
+    type = factor(type,  levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Original","Uncertianty+ExpData", "Uncertianty+DCPO+ExpData"))
+  )
+
+# Institution Corruption--------------------------------
+
+result_ecmReg2 <- bind_rows(
+  mutate(result_clsAPSR[["pooled-regime2"]][[1]][,1:3], model = "Original"),
+ mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime2"]]), model = "Uncertianty+ExpData"),
+  mutate(MOCsumm2(mocdcpo_APSR[["pooled-regime2"]]), model = "Uncertianty+DCPO+ExpData")) %>%
+  mutate(type = "ECM")
+
+result_fdReg2 <- bind_rows(
+  mutate(result_clsAPSR[["fd-regime2"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime2"]]), model = "Uncertianty+ExpData"),
+  mutate(MOCsumm2(mocdcpo_APSR[["fd-regime2"]]), model = "Uncertianty+DCPO+ExpData")) %>% 
+  mutate(type = "First Difference")
+
+result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+        "Electoral Democracy\n (Difference)",
+        "Electoral Democracy\n (t-1)",
+        "Minoritarian Democracy\n (Difference)",
+        "Minoritarian Democracy\n (t-1)",
+        "Log GDP\n per capita\n (Difference)",
+        "Log GDP\n (t-1)",
+        "Corruption\n (Difference)",
+        "Corruption\n (t-1)"
+      ),
+      time = 3),
+      rep(
+        c("Electoral Democracy\n (Difference)", 
+          "Minoritarian Democracy\n (Difference)",
+          "Log GDP\n per capita\n (Difference)",
+          "Corruption\n (Difference)"), 
+        time = 3
+      )),
+    type = factor(type,  levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Original","Uncertianty+ExpData", "Uncertianty+DCPO+ExpData"))
+  )
+```
+
+```{r plot-mainDCPOAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", fig.width=7, fig.height=10}
+type_model <-
+    c("Original", "Uncertianty+ExpData", "Uncertianty+DCPO+ExpData")
+
+df_plot <- bind_rows(result_apsrPooled, result_apsrRegime) %>%
+    mutate(
+        term = index_coefName[term],
+        term = factor(term, levels = unique(index_coefName)),
+        type = factor(type, levels = c("Pooled", "Institution Specified"))
+    )
+
+dwplot(df_plot) +
+    geom_vline(xintercept = 0,
+               colour = "grey80",
+               linetype = 2) +
+    ggtitle("DV: The Change of Public Support for Democracy") +
+    xlab("Coefficient Estimate") +
+    theme(
+        axis.title.y = element_blank(),
+        legend.position = "bottom",
+        legend.title = element_blank()
+    ) +
+    facet_wrap(~ type)  +
+   scale_color_gb(palette = "digitMixed")
+
+```
+
+```{r moc-dcpoAJPS, eval=FALSE}
+
+dcpo_Ajps <- purrr::map(1:900, function(anEntry) {
+  dcpo_ajps[[anEntry]] %>% 
+    plm::pdata.frame(index = c("country", "year")) %>%
+    rename(SupDem_trim =theta_trim,
+           Regime_VD = Vdem_regime,
+           Pr_Muslim = muslism_prop_2010,
+           Res_cp_WDI_di = dependence_pc_di,
+           lnGDP_imp = lg_imp_mdpgdp,
+           GDP_imp_grth = mdprgdp_grwth,
+           firstyear = first_year,
+           Libdem_VD = Vdem_libdem,
+           Libdem_m1 = Vdem_libdem_m1,
+           Libdem_m2 = Vdem_libdem_m2,
+           ChgDem = Chgdem,
+           UpChgDem = upchgdem,
+           DwnChgDem = downchgdem,
+           Libdem_regUN = Region_libdem,
+           Libdem_regUN_m1 = Region_libdem_m1)
+})
+
+result_dcpoUncertain  <- map(ls_mod_ajpsCLS[1:2], function(aMod){
+  result <- methodComposition1(dcpo_Ajps,aMod)
+})
+
+names(result_dcpoUncertain) <- c("pooled", "pooled-regime")
+
+result_dcpoUncertain_gmm  <- map(ls_mod_ajpsCLS[3:4], function(aMod){
+  result <- methodComposition2(dcpo_Ajps,aMod)
+})
+names(result_dcpoUncertain_gmm) <- c("gmm", "gmm-regime")
+
+mocresult_dcpoAJPS <- append(result_dcpoUncertain, result_dcpoUncertain_gmm)
+saveRDS(mocresult_dcpoAJPS, file =here("output","estimates_moc_dcpoAJPS.RDS"))
+
+```
+
+```{r formatDCPOResult-AJPS}
+result_pooled <- bind_rows(
+  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Original"),
+ mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), model = "Uncertianty+ExpData"),
+ mutate(MOCsumm(mocresult_dcpoAJPS[["pooled"]]), model = "Uncertianty+DCPO+ExpData")
+) %>% 
+  mutate(type = "Pooled")
+
+result_gmm <- bind_rows(
+  mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), model = "Uncertianty+ExpData"),
+  mutate(MOCsumm(mocresult_dcpoAJPS[["gmm"]]), model = "Uncertianty+DCPO+ExpData")
+) %>% 
+  mutate(type = "GMM")
+
+result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democracy\n (t-1)",
+        "Democracy\n (t-2)",
+        "Support\n (t-1)",
+        "Log GDP\n per capita\n (t-1)",
+        "GDP per\n capita growth\n (t-1)",
+        "Regional\n democracy\n (t-1)",
+        "Percent\n Muslim\n (t-1)",
+        "Resource\n dependence\n (t-1)"),
+      time = 6), 
+    type = factor(type, levels = c("Pooled", "GMM")),
+    model = factor(model, levels = c("Original", "Uncertianty+ExpData", "Uncertianty+DCPO+ExpData")))
+
+result_ajpsPooled <- result_pooledAJPS %>% 
+    filter(type == "Pooled")
+
+result_regime <- bind_rows(
+  mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), model = "Uncertianty+ExpData"),
+  mutate(MOCsumm(mocresult_dcpoAJPS[["pooled-regime"]]), model = "Uncertianty+DCPO+ExpData")
+) %>% 
+  mutate(type = "Pooled")
+
+result_regimeGmm <- bind_rows(
+  mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), model = "Uncertianty+ExpData"),
+ mutate(MOCsumm(mocresult_dcpoAJPS[["gmm-regime"]]), model = "Uncertianty+DCPO+ExpData")
+)%>% 
+  mutate(type = "GMM")
+
+result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democracy\n (t-1)",
+        "Democracy\n (t-2)",
+        "Support\n demo only\n (t-1)",
+        "Support\n auto only\n (t-1)",
+        "Log GDP\n per capita\n (t-1)",
+        "GDP per\n capita growth\n (t-1)",
+        "Regional\n democracy\n (t-1)",
+        "Percent\n Muslim\n (t-1)",
+        "Resource\n dependence\n (t-1)"),
+      time = 6), 
+    type = factor(type, levels = c("Pooled", "GMM")),
+    model = factor(model, levels = c("Original","Uncertianty+ExpData", "Uncertianty+DCPO+ExpData")))
+
+result_ajpsRegime <- result_regimeAJPS %>%
+    filter(type == "Pooled") %>% 
+    mutate(type = "Regime Specified")
+
+```
+
+```{r plotdcpo-mainAJPS, fig.cap= "The Effect of Public Support on Democracy with Uncertainty", fig.width=7, fig.height=10, fig.align='center'}
+
+type_model <-
+  c("Original", "Uncertianty+ExpData", "Uncertianty+DCPO+ExpData")
+
+df_plot <- bind_rows(result_ajpsPooled, result_ajpsRegime) %>% 
+    mutate(term = index_coefName[term],
+           term = factor(term, levels = unique(index_coefName)))
+
+dwplot(df_plot) +
+    geom_vline(xintercept = 0,
+               colour = "grey80",
+               linetype = 2) +
+    theme_minimal() +
+    ggtitle("DV: Liberal Democracy (Vdem)") +
+    xlab("Coefficient Estimate") +
+    theme(
+        axis.title.y = element_blank(),
+        legend.position = "bottom",
+      legend.title = element_blank()
+    ) +
+    scale_color_gb(palette = "digitMixed") +
+    facet_wrap(~ type)
+
+```
+
 # Replication with MOC Accounting for Uncertainty {#moc}
@@
 In analysis models, we have latent variables in both sides of equations, public suppport for democracy, democracy indices and corruption index (The latter one is included in APSR analyses).
-Since measurement uncertainty associated with these latent variables can propogate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing "Method of Composition" [@Tanner1996,p52], which has been applied in analyses with latent variables [@Treier2008;@Caughey2018;@Kastellec2015].
-
-As @Caughey2018 explained, the main idea of MOC is to estimate the marginal distribution of coefficient parameter vector $\beta$, intergrating over the uncertainty in latent variables $\theta$ (P A-15).
+Since measurement uncertainty associated with these latent variables can propogate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing "Method of Composition" [@Tanner1996,p52], which has been applied in analyses with latent variables [@treier2008;@caughey2018;@Kastellec2015].
+
+As @caughey2018 explained, the main idea of MOC is to estimate the marginal distribution of coefficient parameter vector $\beta$, intergrating over the uncertainty in latent variables $\theta$ (P A-15).
 More explicitly, we wish to integrate the joint density of $\beta$ and $\theta$ over the distribution of $\theta$.
@@
 where $\theta$ is latent varibles with measurement errors conditional on data Z and a measurement model, $w$ is other predictors without errors, $Z$ is indicators for latent variables $X$, and $y$ is the outcome variable.
-In this way, we incorportate uncertainty in measuring predictor $\theta$, and uncertainty in the effects of latent variables $\theta$ and other variables $w$ on outcome variable $y$ [@Treie2008, 215].
+In this way, we incorportate uncertainty in measuring predictor $\theta$, and uncertainty in the effects of latent variables $\theta$ and other variables $w$ on outcome variable $y$ [@treie2008, 215].
 To sample from the conditional dentsity and the marginal density in the right side of the equation, we follow iterative Monte Carlo procdure described by @Treier2008, at iteration t,

### 2021-08-11 paper/dcpo_demsupport.Rmd
corrected the var labels; the expression needs a further look

@@
 
+if (!require(drhutools)) remotes::install_github("sammo3182/drhutools")
+
 # load all the packages you will use below 
@@
 mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expcorAPSR.RDS"))
-mocdcpo_APSR <- readRDS(here("ouput","estimates_moc_dcpoAPSR.RDS"))
+mocdcpo_APSR <- readRDS(here("output","estimates_moc_dcpoAPSR.RDS"))
 mocresult_dcpoAJPS <- readRDS(here("output","estimates_moc_dcpoAJPS.RDS"))
+
 ```
@@
 Following this line, after replicating the original analyses with point estimates, we incorporate uncertainty in analysis models using our replication data.
-We conduct inferences from the distributive data via a technique known as "method of composition" (MOC) [@Tanner1996, p.52;@Treier2008, p. 215; @caughey2018,p.A15-16].
+We conduct inferences from the distributive data via a technique known as "method of composition" (MOC) [@Tanner1993, p.52;@Treier2008, p. 215; @caughey2018,p.A15-16].
 See more details of the method and the operational process in Online Supplementary Material \@ref(moc).
@@
 
+```{r coefName-AJPS-dup}
+index_coefName <- c(
+    `Democracy\n (t-1)` = "Democracy[t-1]",
+    `Democracy\n (t-2)` = "Democracy[t-2]",
+    `Support\n (t-1)` = "Support[t-1]",
+    `Support\n demo only\n (t-1)` = "Support[t-1](demo~only)",
+    `Support\n auto only\n (t-1)` = "Support[t-1](auto~only)",
+    `Log GDP\n per capita\n (t-1)` = "Log~GDP~per~capita[t-1]",
+    `GDP per\n capita growth\n (t-1)` = "GDP~per~capita~growth[t-1]",
+    `Regional\n democracy\n (t-1)` = "Regional~democracy[t-1]",
+    `Percent\n Muslim\n (t-1)` = "Percent~Muslim[t-1]",
+    `Resource\n dependence\n (t-1)` = "Resource~dependence[t-1]"
+)
+```
+
 ```{r moc-dcpoAJPS, eval=FALSE}
@@
 In analysis models, we have latent variables in both sides of equations, public suppport for democracy, democracy indices and corruption index (The latter one is included in APSR analyses).
-Since measurement uncertainty associated with these latent variables can propogate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing "Method of Composition" [@Tanner1996,p52], which has been applied in analyses with latent variables [@treier2008;@caughey2018;@Kastellec2015].
+Since measurement uncertainty associated with these latent variables can propogate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing "Method of Composition" [@Tanner1993,p52], which has been applied in analyses with latent variables [@Treier2008;@caughey2018;@Kastellec2015].
 
@@
 where $\theta$ is latent varibles with measurement errors conditional on data Z and a measurement model, $w$ is other predictors without errors, $Z$ is indicators for latent variables $X$, and $y$ is the outcome variable.
-In this way, we incorportate uncertainty in measuring predictor $\theta$, and uncertainty in the effects of latent variables $\theta$ and other variables $w$ on outcome variable $y$ [@treie2008, 215].
+In this way, we incorportate uncertainty in measuring predictor $\theta$, and uncertainty in the effects of latent variables $\theta$ and other variables $w$ on outcome variable $y$ [@Treier2008, 215].
 To sample from the conditional dentsity and the marginal density in the right side of the equation, we follow iterative Monte Carlo procdure described by @Treier2008, at iteration t,

### 2021-08-12 paper/memo/memo.Rmd

@@
 
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, eval = FALSE, dpi = 300)
+knitr::opts_chunk$set(
+  echo = FALSE,
+  message = FALSE,
+  warning = FALSE,
+  dpi = 300)
 
@@
 library(pacman)
+library(patchwork)
+library(rsdmx)
 
@@
 In order to isolate the effect of different priors on estimated measures, in revised version, we only employed Claassen's Model5 with original data, recollected data and expanded data, separately.
-A bigger size of observed data is expected to reduce the possible dominance of priors.
-However, even though we put efforts to collect as much data as possible.
-The expanded data is only xxx county-year.
-It is possible that the changes of public mood are "smooth" out by modeling the temporal evolution in a simple local-level dynamic linear.
-The smoothed time series data might fail to capture a sudden change which is caused by exogenous factors.
+
+By using the same measurement model, we exclude the effects which might be brought by different priors and a bigger size of observed data should reduce the possible dominance of priors.
+
+```{r expdata_summary_stats}
+
+load(here::here("data","exp_claassen_input.rda"))
+
+supdem <- read_csv(here::here("data", "supdem raw survey marginals.tab"),
+                   col_types = "cdcddcdc") %>% 
+  janitor::clean_names() %>% 
+  DCPOtools::with_min_yrs(2)
+
+supdem_ncy <- supdem %>%
+  dplyr::select(country, year) %>% 
+  distinct() %>% 
+  nrow() #1165
+
+process_dcpo_input_raw <- function(dcpo_input_raw_df) {
+  dcpo_input_raw_df %>% 
+  with_min_yrs(2) %>% 
+  with_min_cy(5) %>% 
+  group_by(country) %>% 
+  mutate(cc_rank = n()) %>% 
+  ungroup() %>% 
+  arrange(-cc_rank)
+}
+
+exp_data <- process_dcpo_input_raw(exp_claassen_input[["data"]])
+
+n_surveys <- exp_data %>%
+  distinct(survey) %>% 
+  nrow()  #123
+
+n_items <- exp_data %>%
+  distinct(item) %>% 
+  nrow() #61 items
+
+n_countries <- exp_data %>%
+  distinct(country) %>% 
+  nrow()  #145
+
+n_cy <- exp_data %>%
+  distinct(country, year) %>% 
+  nrow() %>% 
+  scales::comma() #1443 country year
+
+n_years <- as.integer(summary(exp_data$year)[6]-summary(exp_data$year)[1]) #32 years
+
+spanned_cy <- exp_data %>% 
+  group_by(country) %>% 
+  summarize(years = max(year) - min(year) + 1) %>% 
+  summarize(n = sum(years)) %>% 
+  pull(n) %>% 
+  scales::comma() #2746
+
+total_cy <- {n_countries * n_years} %>% 
+  scales::comma()
+
+year_range <- paste("from",
+                    summary(exp_data$year)[1], 
+                    "to",
+                    summary(exp_data$year)[6]) 
+n_cyi <- exp_data %>% 
+  distinct(country, year, item) %>% 
+  nrow() %>% 
+  scales::comma()
+
+back_to_numeric <- function(string_number) {
+  string_number %>% 
+    str_replace(",", "") %>% 
+    as.numeric()
+}
+
+increase_cy <- back_to_numeric(n_cy) - back_to_numeric(supdem_ncy)
+
+```
+
+Since our expanded data added `r increase_cy` country-year, the estimates from the expanded data should be influenced less by priors than original data by inputing more data. 
+However, even though we put much effort to collect as much data as possible.
+At aggregated level, country-year data is super sparse.
+
+However, if we have observations for every year in each country surveyed, the number would be `r total_cy`, and a complete set of country-year-items would encompass `r {n_countries * n_years * n_items} %>% scales::comma()` observations.
+In fact, even collecting as many available national and cross-national data as possible, the current source data has `r n_cy` country-years and a total of `r n_cyi` country-year-item observations.
+The spareness is reflected from the complete-data perspective but also from the available data in the country-years span.
+Although we have the `r spanned_cy` country-years, only `r {back_to_numeric(n_cy)/back_to_numeric(spanned_cy) * 100} %>% round()`% of it has available information.
+
+The sparseness of available data makes it possible that the changes of public mood are "smooth" out by modeling the temporal evolution in a simple local-level dynamic linear, which is also referred to as the random walk plus noise model.
+With random noise, the smoothed time series data might fail to capture a sudden change which is caused by exogenous factors.
 Given the sparsed available data and effects from random walk prior, it is highly possible that we cannot detect any significant effect from institution changes and other economic and social factors.
@@
 211; @caughey2018,p.
-254].
+254; @Crabtree2015,p.
+6].
 
@@
 ## Response
-Regarding Reviewer 1's request on replicating all specifications in the original two studies, we added alternate specifications on the relationship between public support and democracy, including GMM models, First Different Models, and sample split.
-See Page xxx, Figure xxx, and xxx in SI.
+As the editor suggested, we should focus on our main point in this letter, that is, reanalyzing the relationship between democracy and public support.
+We replicate additional models which examine this main relationship.
+
+We replicate @Claassen2020a's results using generalized method of moments (GMM) estimators for both pooled data and split data (democracy only and authoritarian country only).
+The results hold and presented in Figure \@ref(fig:plot-mocAJPS).
+We also replicate @Claassen2020b's results using First Different Models, including corruption index, and examing the separate effects of the electoral and liberal components of democracy.
+Still, the results hold in these robustness check models and specifications in Figure \@ref(fig:plot-mocAPSR).
 
@@
 ## Response
-Thanks to the editor's suggestions, we agree that we should present and assess the effect of intermediate modification in an incremental way.
-To do this, in the revised manuscript, we replicated Claassen's measure for public democratic support by applying his measurement Model5 to his original data file and used the posterior distribution of the public support estimates to incorporate uncertainty.
-Then, we added more survey data to improve source data quality and applied Model5 to this expanded data set, still keeping the full posterior distribution of estimates.
-In this way, we isolate the effects of measurement uncertainty and more data. 
-In replications for both AJPS and APSR analyses, it is uncertainty that accounts for the disappearing significance of public support and changes in democracy. 
-In Supplementatry material, we explained the methodology for addressing measurement uncerainty in this study and compared Rubin's Rules and Method of Composition.
-Both methods yield the similar results in significant, though they address measurement errors in different angles.
+Thanks to editor's suggestion, we agree that we should present and assess the effect of intermediate modification in an incremental way, holding analytical transparency.
+To do this, in the revised manuscript, we focus on replication by only employing Claassen's measurement Model 5 to measure public support for democracy.
 
-In terms of disappearing relationships between public support and democracy and the change in mood and the change in democracy, we have discussed theoretical reasons in our main text. 
-It is possbile that the relationship is negligible, because the incorporation of measurement error swamping the significant effects of democracy in a strong relationship is rare [@Treier2008].
-
-In addition to potential methodological explanations we have discussed, another potential reason is the over-time smoothing induced by the random-walk prior thanks to Reviwer 2's suggestion.
-At aggregated level, country-year data is super sparse. 
-Even in our expanded data, xx data is missing, compared to xxx missing in original data.
-The sparse of raw data and the simple dynamic linear model used in measurement model to capture dynamic effect might make priors dominate in smoothing over-time changes. 
-However, in our revised manuscript, we only used Claassen's Model 5 to estimate public support using corrected original data and expanded data, seperately.
-Since our expanded data added xxx country-year, the estimates from the expanded data should be influenced less by priors than original data by inputing more data. 
-Still, the coefficient estimates from expanded data are indistinguishable from zero though with narrower confident interval.
-Therefore, it is the incorporation of uncertainty that changes the coefficient estimates in magnitude and significant. 
-<!--random walk,standards for dv -->
+We apply Model 5 to Claassen's original data file, recollected data based on his provided data source and expanded data. 
+In this way, the only two changed things are acccounting for uncertainty and adding more data.
+We incorporate uncertainty when using Model 5 estimated public support from recollected data to examine the effect of uncertainty.
+Then, we apply Model5 to the expanded data set which improves source data quality and should reduce the uncertainty.  
+In this way, we eliminate potential effects caused by different measurement models and make efforts to reduce the uncertainty caused by fragmented data. 
+Our results show that it is the incorporation of uncertainty that accounts for the differences between Claassen's original analyses and our reanalyses.
 
@@
 ## Response
-Since we do acknowledge uncertainty in extant measurements, we can not unambiguously make a statement that there is no relationship between public support and regime survival, although it is possible.
-Examing theories in different contexts over time is a promising strategy for generalization [KKV].
-However, scholars' pursuit of models usually leads to ignorance for measurements that cost more time but determine the quality of data in analyses [@stegmueller2011].
-In this letter, we stress the necessity of incorporating measurement uncertainty in analyses with latent variables and encourage scholars to pay more attention to that.
-*need more on substantive discussion*
+Although we do acknowledge uncertainty in extant measurements and we can not unambiguously make a statement that there is no relationship between public support and regime survival, the relationship, if exists, is probably negligible, because the incorporation of measurement error swamping the significant effects of democracy in a strong relationship is rare [@Treier2008].
+
+<!--- need DISUCSSION --->
 
@@
 ## Response
-We did not do a simulation study. Instead, we employ MOC suggested by Review 1 and 2 as a robust check and present results in SI. 
-We also elaborate on the imputation process in detail in MS and clarify the equations in SI.
-Measurement errors in other variables have been included in our reexaminations. 
-As for the concerns in Fig2, the first thing needing to clarify is that the DV is not current public support but the change of public support. 
+We did not do a simulation study. Instead, we employ MOC suggested by Review 1 and 2 in this revised version. 
+We illustrate MOC process in detail in SI.
+Measurement errors in other variables, including three democracy indices, public support and corruption perception index, have been included in our reexaminations. 
+As for the concerns in Fig2, the DV is not current public support but the change of public support. 
 We elaborate on why our null results make more sense than Claassen's original results.
@@
 ## Response
+We appreciate editor's suggestion on presenting each intermediate modificantion.
+Following this suggestion, we only focus on uncertainty in this revised version. 
 It is a misunderstanding that incorporating uncertainty only changes standard error.
 First, incorporating uncertainty might or might not cause the changes of standard error.
-For example, standard errors did not change after accounting for uncertainty in [@caughey2018] but became smaller in [@Treier2008].
-Second, the propagation of uncertainty can either attenuate or magnify the magnitude of estimated effects.
-To avoid confusion, we only focus on uncertainty in this revised version.
+For example, standard errors did not change after accounting for uncertainty in [@caughey2018] became smaller in [@Treier2008] and bigger in [@Crabtree2015].
+Second, the propagation of uncertainty can either attenuate or magnify the magnitude of estimated effects [see @Treier2008; @caughey2018;@Crabtree2015].
 
@@
 ## Response
-In SI, we discussed methodology used in this article to address measurement errors, Rubin's Rules and MOC.
-We compared these two methods by introducing their fomulas and equations and highlighing their different approaches. 
-As results show, though they have different approaches, the results from two methods are similar with each other.
+In SI, we discussed methodology used in this article to address measurement errors.
 

### 2021-08-12 paper/memo/response_memo.Rmd
initial commit

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: xelatex
    template: ../svm-latex-ms2.tex
title: |
    | Democracy, Public Support, and Measurement Uncertainty
    | Memo to Reviewers
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
spacing: double
bibliography: \dummy{`r file.path(file.path(getwd(), ".."), list.files(file.path(getwd(), ".."), ".bib$", recursive = TRUE))`}
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
---

```{r setup, include=FALSE}
options(tinytex.verbose = TRUE)

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  dpi = 300)

# If you haven't install `DCPOtools`
# remotes::install_github("fsolt/DCPOtools")

if (!require(pacman)) install.packages("pacman")
library(pacman)
library(patchwork)
library(rsdmx)

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools,
  boot, plm, # analysis
  flextable, kableExtra, modelsummary, # tabulation
  gridExtra,
  latex2exp, # visualization
  rstan, # Bayesian estimation
  broom, tidyverse, janitor, # data wrangling
  dotwhisker # visualization
)

# Functions preload
set.seed(313)

get_legend<-function(myggplot){
  tmp <- ggplot_gtable(ggplot_build(myggplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)
}

# Theme setup
theme_set(theme_minimal())
source(here::here("R", "uiowa_palette.R"))
```

Thank you for your helpful comments, as well as your general enthusiasm for this piece.
As you will see below, the reviews were each very constructive individually---and together usually so, as concerns raised by one review were often met by suggestions made in another.
Collectively, the reviews motivated us to ensure the piece, as a letter manuscript, was tightly focused on its twin main points: that, in general, researchers working with latent variables must take care to include in their analyses the uncertainty in these measures, and, specifically, taking uncertainty into account reveals that there is no evidence for the assertions that democracies' fates depend on public support and that their publics will rally to them if they are weakened.
Indeed, your comments (and those of the editor) gave us the courage to be truly ruthless in stripping out any and all extraneous material that distracted from these crucial points.

We set out a list of the specific points raised in the reviews and our responses to them below, roughly in the order they appear in the text:

1. **Method: Incorporating Uncertainty** Reviewer 1 and Reviewer 2 both raised the question of whether the approach for incorporating uncertainty we employed was the most appropriate for this application.
Although Reviewer 2 correctly noted that that approach is the same explicated by @Blackwell2017, [they](https://public.oed.com/blog/a-brief-history-of-singular-they/) also suggested we use the Method of Composition (MOC) that was first put forward by @Tanner1993 and introduced to political science by @Treier2008.
As the MOC has become the standard method used to incorporate uncertainty in the subnational comparative public opinion literature using Multilevel Regression and Poststratification [see, e.g., @Kastellec2015; @caughey2018], we were pleased to adopt this suggestion.
Further, to help ensure that incorporating uncertainty is as easy as possible for those working with latent variables of cross-national public opinion, we are including in our replication materials a suite of R functions implementing the MOC that are tailored to this application.

1.

\pagebreak

# References

<div id="refs"></div>

### 2021-08-12 paper/dcpo_demsupport.Rmd

@@
 
-# If you haven't install `DCPOtools`
-# remotes::install_github("fsolt/DCPOtools")
-
 if (!require(pacman)) install.packages("pacman")
@@
 
-if (!require(drhutools)) remotes::install_github("sammo3182/drhutools")
+p_install(janitor, force = FALSE)
+
+ls_pacGH <- c("fsolt/DCPOtools", "sammo3182/drhutools")
+remotes::install_github(ls_pacGH, force = FALSE)
 
@@
 p_load(
-  # data scrapping
-  dataverse, 
-  osfr,
-  DCPOtools,
-  mitools,
-  boot, 
-  here,
   # analysis
   plm, 
-  rstan, 
   # presentation
-  flextable, 
-  broomExtra, 
-  kableExtra, 
-  modelsummary, 
   gridExtra,
-  latex2exp,
   drhutools,
   dotwhisker, 
+  latex2exp,
   # data wrangling
+  here,
+  broom,
   tidyverse, 
-  janitor, 
-  glue, 
-  qs
+  glue
 )
@@
 
+load(here("data", "correct_cls_ajps.rda"))
+load(here("data", "correct_cls_apsr.rda"))
+load(here("data", "expcor_cls_ajps.rda"))
+load(here("data", "expcor_cls_apsr.rda"))
 load(here("data","claassen_replication_input.rda"))
@@
 load(here("data","dcpo_ajps.rda"))
-
-# Removed the comments for the final replication file
-## Claasseen and extend data
-# 
-# osf_retrieve_file("hczmf") %>%
-#     osf_download(path = "../data")
-# 
-# osf_retrieve_file("wbu6m") %>%
-#     osf_download(path = "../data")
-# 
-# osf_retrieve_file("2jhbc") %>%
-#     osf_download(path = "../data")
-# 
-# osf_retrieve_file("u96m8") %>%
-#     osf_download(path = "../data", conflicts = "overwrite")
-
-# osf_retrieve_file("52u7n") %>%
-#     osf_download(path = "../data", conflicts = "overwrite") #corrected ajps
-# osf_retrieve_file("2hwqg") %>%
-#     osf_download(path = "../data", conflicts = "overwrite") #corrected apsr
-
-# load(here("data", "correct_cls_ajps.rda"))
-# load(here("data", "correct_cls_apsr.rda")) 
-# load(here("data", "expcor_cls_ajps.rda"))
-# load(here("data", "expcor_cls_apsr.rda"))
 
@@
 
-saveRDS(mocresult_expAPSR, file = here::here("ouput","estimates_moc_expcorAPSR.RDS"))
+saveRDS(mocresult_expAPSR, file = here::here("output","estimates_moc_expcorAPSR.RDS"))
 
@@
 ```{r dcpo-APSR, eval=FALSE}
-
 dcpo_APSR <- purrr::map(1:900, function(anEntry) {
@@
     plm::pdata.frame(index = c("country", "year")) %>%
-    rename(SupDem_trim = theta_trim,
+    rename(
+      SupDem_trim = theta_trim,
       First_yr = first_year,
@@
       Corrup_TI_z = corruption_z,
-          lnGDP_imp = lg_imp_mdpgdp)
-}
-)
-
-mocdcpo_APSR  <- map(ls_mod_apsrCLS, function(aMod){
-  result <- methodComposition3(dcpo_APSR,aMod)
-})
-
-names(mocdcpo_APSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
-                                "fd1", "fd-regime1", "fd2", "fd-regime2")
-
-saveRDS(mocdcpo_APSR, file = here::here("ouput","estimates_moc_dcpoAPSR.RDS"))
+      lnGDP_imp = lg_imp_mdpgdp
+    )
+})
+
+mocdcpo_APSR  <- map(ls_mod_apsrCLS, function(aMod) {
+  result <- methodComposition3(dcpo_APSR, aMod)
+})
+
+names(mocdcpo_APSR) <-
+  c(
+    "pooled1",
+    "pooled-regime1",
+    "pooled2",
+    "pooled-regime2",
+    "fd1",
+    "fd-regime1",
+    "fd2",
+    "fd-regime2"
+  )
+
+saveRDS(mocdcpo_APSR,
+        file = here::here("output", "estimates_moc_dcpoAPSR.RDS"))
 ```

### 2021-08-13 paper/dcpo_demsupport.Rmd
avoid nested script calls by incorporating needed broom_utilities in tidy_pgmm

@@
 
-load(here("data", "correct_cls_ajps.rda"))
-load(here("data", "correct_cls_apsr.rda"))
-load(here("data", "expcor_cls_ajps.rda"))
-load(here("data", "expcor_cls_apsr.rda"))
+load(here("data", "correct_cls_ajps.rda")) # https://osf.io/52u7n/download
+load(here("data", "correct_cls_apsr.rda")) # https://osf.io/2hwqg/download
+load(here("data", "expcor_cls_ajps.rda"))  # https://osf.io/wfm3c/download
+load(here("data", "expcor_cls_apsr.rda"))  # https://osf.io/rvc92/download
 load(here("data","claassen_replication_input.rda"))
 load(here("data","exp_claassen_input.rda"))
-load(here("data","dcpo_apsr.rda"))
-load(here("data","dcpo_ajps.rda"))
+#load(here("data","dcpo_apsr.rda"))
+#load(here("data","dcpo_ajps.rda"))
 

### 2021-08-13 R/tidy_pgmm.r

@@ -1,4 +1,47 @@
-source("../R/broom_utilities.R")
+
+na_types_dict <- list("r" = NA_real_,
+                      "i" = rlang::na_int,
+                      "c" = NA_character_,
+                      "l" = rlang::na_lgl)
+
+# A function that converts a string to a vector of NA types.
+# e.g. "rri" -> c(NA_real_, NA_real_, rlang::na_int)
+parse_na_types <- function(s) {
+    
+    positions <- purrr::map(
+        stringr::str_split(s, pattern = ""), 
+        match,
+        table = names(na_types_dict)
+    ) %>%
+        unlist()
+    
+    na_types_dict[positions] %>%
+        unlist() %>%
+        unname()
+}
+
+# A function that, given named arguments, will make a one-row
+# tibble, switching out NULLs for the appropriate NA type.
+as_glance_tibble <- function(..., na_types) {
+    
+    cols <- list(...)
+    
+    if (length(cols) != stringr::str_length(na_types)) {
+        stop(
+            "The number of columns provided does not match the number of ",
+            "column types provided."
+        )
+    }
+    
+    na_types_long <- parse_na_types(na_types)
+    
+    entries <- purrr::map2(cols, 
+                           na_types_long, 
+                           function(.x, .y) {if (length(.x) == 0) .y else .x})
+    
+    tibble::as_tibble_row(entries)
+    
+}
 
 tidy.pgmm <- function(x,
                       conf.int = FALSE,

### 2021-08-13 paper/dcpo_demsupport.Rmd
fix misspelling of "Uncertainty" throughout

@@
   mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_expAPSR[["pooled1"]]), model = "Uncertianty+ExpData"),
-  mutate(MOCsumm2(mocdcpo_APSR[["pooled1"]]), model = "Uncertianty+DCPO+ExpData")
+  mutate(MOCsumm2(mocresult_expAPSR[["pooled1"]]), model = "Uncertainty+ExpData"),
+  mutate(MOCsumm2(mocdcpo_APSR[["pooled1"]]), model = "Uncertainty+DCPO+ExpData")
 ) %>% 
@@
   mutate(result_clsAPSR[["fd1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_expAPSR[["fd1"]]), model = "Uncertianty+ExpData"),
-  mutate(MOCsumm2(mocdcpo_APSR[["fd1"]]), model = "Uncertianty+DCPO+ExpData")
+  mutate(MOCsumm2(mocresult_expAPSR[["fd1"]]), model = "Uncertainty+ExpData"),
+  mutate(MOCsumm2(mocdcpo_APSR[["fd1"]]), model = "Uncertainty+DCPO+ExpData")
 ) %>% 
@@
     type = factor(type,  levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Original","Uncertianty+ExpData", "Uncertianty+DCPO+ExpData"))
+    model = factor(model, levels = c("Original","Uncertainty+ExpData", "Uncertainty+DCPO+ExpData"))
   )
@@
   mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime1"]]), model = "Uncertianty+ExpData"),
-  mutate(MOCsumm2(mocdcpo_APSR[["pooled-regime1"]]), model = "Uncertianty+DCPO+ExpData")
+  mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime1"]]), model = "Uncertainty+ExpData"),
+  mutate(MOCsumm2(mocdcpo_APSR[["pooled-regime1"]]), model = "Uncertainty+DCPO+ExpData")
 ) %>% 
@@
   mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime1"]]), model = "Uncertianty+ExpData"),
-  mutate(MOCsumm2(mocdcpo_APSR[["fd-regime1"]]), model = "Uncertianty+DCPO+ExpData")
+  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime1"]]), model = "Uncertainty+ExpData"),
+  mutate(MOCsumm2(mocdcpo_APSR[["fd-regime1"]]), model = "Uncertainty+DCPO+ExpData")
 ) %>% 
@@
   mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_expAPSR[["pooled2"]]), model = "Uncertianty+ExpData"),
-  mutate(MOCsumm2(mocdcpo_APSR[["pooled2"]]), model = "Uncertianty+DCPO+ExpData")
+  mutate(MOCsumm2(mocresult_expAPSR[["pooled2"]]), model = "Uncertainty+ExpData"),
+  mutate(MOCsumm2(mocdcpo_APSR[["pooled2"]]), model = "Uncertainty+DCPO+ExpData")
 ) %>% 
@@
   mutate(result_clsAPSR[["fd2"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_expAPSR[["fd2"]]), model = "Uncertianty+ExpData"),
-  mutate(MOCsumm2(mocdcpo_APSR[["fd2"]]), model = "Uncertianty+DCPO+ExpData")
+  mutate(MOCsumm2(mocresult_expAPSR[["fd2"]]), model = "Uncertainty+ExpData"),
+  mutate(MOCsumm2(mocdcpo_APSR[["fd2"]]), model = "Uncertainty+DCPO+ExpData")
 ) %>% 
@@
   mutate(result_clsAPSR[["pooled-regime2"]][[1]][,1:3], model = "Original"),
- mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime2"]]), model = "Uncertianty+ExpData"),
-  mutate(MOCsumm2(mocdcpo_APSR[["pooled-regime2"]]), model = "Uncertianty+DCPO+ExpData")) %>%
+ mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime2"]]), model = "Uncertainty+ExpData"),
+  mutate(MOCsumm2(mocdcpo_APSR[["pooled-regime2"]]), model = "Uncertainty+DCPO+ExpData")) %>%
   mutate(type = "ECM")
@@
   mutate(result_clsAPSR[["fd-regime2"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime2"]]), model = "Uncertianty+ExpData"),
-  mutate(MOCsumm2(mocdcpo_APSR[["fd-regime2"]]), model = "Uncertianty+DCPO+ExpData")) %>% 
+  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime2"]]), model = "Uncertainty+ExpData"),
+  mutate(MOCsumm2(mocdcpo_APSR[["fd-regime2"]]), model = "Uncertainty+DCPO+ExpData")) %>% 
   mutate(type = "First Difference")
@@
 type_model <-
-    c("Original", "Uncertianty+ExpData", "Uncertianty+DCPO+ExpData")
+    c("Original", "Uncertainty+ExpData", "Uncertainty+DCPO+ExpData")
 
@@
   mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Original"),
- mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), model = "Uncertianty+ExpData"),
- mutate(MOCsumm(mocresult_dcpoAJPS[["pooled"]]), model = "Uncertianty+DCPO+ExpData")
+ mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), model = "Uncertainty+ExpData"),
+ mutate(MOCsumm(mocresult_dcpoAJPS[["pooled"]]), model = "Uncertainty+DCPO+ExpData")
 ) %>% 
@@
   mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), model = "Uncertianty+ExpData"),
-  mutate(MOCsumm(mocresult_dcpoAJPS[["gmm"]]), model = "Uncertianty+DCPO+ExpData")
+  mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), model = "Uncertainty+ExpData"),
+  mutate(MOCsumm(mocresult_dcpoAJPS[["gmm"]]), model = "Uncertainty+DCPO+ExpData")
 ) %>% 
@@
     type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Original", "Uncertianty+ExpData", "Uncertianty+DCPO+ExpData")))
+    model = factor(model, levels = c("Original", "Uncertainty+ExpData", "Uncertainty+DCPO+ExpData")))
 
@@
   mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), model = "Uncertianty+ExpData"),
-  mutate(MOCsumm(mocresult_dcpoAJPS[["pooled-regime"]]), model = "Uncertianty+DCPO+ExpData")
+  mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), model = "Uncertainty+ExpData"),
+  mutate(MOCsumm(mocresult_dcpoAJPS[["pooled-regime"]]), model = "Uncertainty+DCPO+ExpData")
 ) %>% 
@@
   mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), model = "Uncertianty+ExpData"),
- mutate(MOCsumm(mocresult_dcpoAJPS[["gmm-regime"]]), model = "Uncertianty+DCPO+ExpData")
+  mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), model = "Uncertainty+ExpData"),
+ mutate(MOCsumm(mocresult_dcpoAJPS[["gmm-regime"]]), model = "Uncertainty+DCPO+ExpData")
 )%>% 
@@
     type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Original","Uncertianty+ExpData", "Uncertianty+DCPO+ExpData")))
+    model = factor(model, levels = c("Original","Uncertainty+ExpData", "Uncertainty+DCPO+ExpData")))
 
@@
 type_model <-
-  c("Original", "Uncertianty+ExpData", "Uncertianty+DCPO+ExpData")
+  c("Original", "Uncertainty+ExpData", "Uncertainty+DCPO+ExpData")
 

### 2021-08-13 paper/dcpo_demsupport.Rmd
split off and cache data-input chunk for speed; use less-intrusive section headers

@@
     toc: FALSE
+    number_sections: FALSE
     latex_engine: xelatex
@@
       - \newcommand{\elandscape}{\end{landscape}}
+      - \usepackage{titlesec}
+      - \titleformat*{\section}{\normalsize\bfseries}
+      - \titleformat*{\subsection}{\normalsize\itshape}
 ---
@@
 Similarly, the impact of public support on democracy may depend on the extent to which those who support democracy are also dissatisfied with the current regime's performance; that is, that it is not democratic support that is important to democratic change, but rather unsatisfied democratic demand [see @Qi2011].
-Whether the public support has a pro-democratic or anti-authoritarian effect is also bounded by the emancipative value that, as a belief-anchored orientation, shapes the public's understanding of democracy [see @Brunkert2019; @Kirsch2019; @Kruse2019].
-Moreover, the cultural and historical attributes of the emancipative value decide that it cannot be shifted shortly by institutional changes.
+_Whether the public support has a pro-democratic or anti-authoritarian effect is also bounded by the emancipative value that, as a belief-anchored orientation, shapes the public's understanding of democracy [see @Brunkert2019; @Kirsch2019; @Kruse2019].
+Moreover, the cultural and historical attributes of the emancipative value decide that it cannot be shifted shortly by institutional changes._
 Of course, it could in fact be that democratic change does not actually depend on public opinion of any sort at all but instead is an elite-driven phenomenon [see, e.g., @levitsky_how_2018].
@@
 theme_set(theme_minimal())
-
-# Data input
+```
+
+```{r data-input, include=FALSE, cache=TRUE}
 
@@
 In analysis models, we have latent variables in both sides of equations, public suppport for democracy, democracy indices and corruption index (The latter one is included in APSR analyses).
-Since measurement uncertainty associated with these latent variables can propogate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing "Method of Composition" [@Tanner1993,p52], which has been applied in analyses with latent variables [@Treier2008;@caughey2018;@Kastellec2015].
-
-As @caughey2018 explained, the main idea of MOC is to estimate the marginal distribution of coefficient parameter vector $\beta$, intergrating over the uncertainty in latent variables $\theta$ (P A-15).
+Since measurement uncertainty associated with these latent variables can propagate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing "Method of Composition" [@Tanner1993,p52], which has been applied in analyses with latent variables [@Treier2008;@caughey2018;@Kastellec2015].
+
+As @caughey2018 explained, the main idea of MOC is to estimate the marginal distribution of coefficient parameter vector $\beta$, integrating over the uncertainty in latent variables $\theta$ (P A-15).
 More explicitly, we wish to integrate the joint density of $\beta$ and $\theta$ over the distribution of $\theta$.

### 2021-08-13 paper/dcpo_demsupport.Rmd
revise text; add labels to appendices by hand

@@
 
-It is worth to note that, despite the great effort of collecting data and identifying differences, we could not reach a completely primary replication of @Claassen2020a's Dataverse materials.
+_It is worth to note that, despite the great effort of collecting data and identifying differences, we could not reach a completely primary replication of @Claassen2020a's Dataverse materials.
 Specifically, we have five fewer observations, three of which are no longer available in original survey data and two seem to have never existed, and one more survey item which was conflated in original data.
 (See more details in Online Supplementary Material \@ref(dgp).)
-Nevertheless, given there are over 2000 observations involved in the analysis, the five missing should not make a meaningful difference.
-
-## Uncertainty Incorporation
-
-Although measurement uncertainty has yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can bias coefficient estimates and standard errors.
-Especially when measurement error is correlated with the outcome variable, the resulting bias could either attenuate or exaggerate the magnitude of the estimated effects [see, e.g., @Blackwell2017, p.360; @caughey2018, p.254].
-In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, p.
-18; @Gandhi2020, p.
-1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, pp.
-791-792; @caughey2018, p.
-254].
+Nevertheless, given there are over 2000 observations involved in the analysis, the five missing should not make a meaningful difference._
+
+## Incorporating Uncertainty
+
+Although measurement uncertainty has yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can both attenuate or exaggerate coefficient estimates as well as bias standard errors [see, e.g., @Blackwell2017, 318-319; @Blackwell2017a, 360-361].
+In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey2018, 254].
 Following this line, after replicating the original analyses with point estimates, we incorporate uncertainty in analysis models using our replication data.
-We conduct inferences from the distributive data via a technique known as "method of composition" (MOC) [@Tanner1993, p.52;@Treier2008, p. 215; @caughey2018,p.A15-16].
-See more details of the method and the operational process in Online Supplementary Material \@ref(moc).
+We conduct inferences from the distributive data via a technique known as the "method of composition" (MOC) [@Tanner1993, 52; @Treier2008, 215; @caughey2018, A15-16].
+See more details of the method and the operational process in Online Appendix C.
 
@@
 
-We also expanded Claassen's data pool assembling as much data on democratic support as possible from available opinion surveys around the world. 
-The expansion ended with `r dcpo_input_ncyi` national opinions on democracy from `r dcpo_input_surv` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncy` opinions and `r supdem_surv` national surveys used in Claassen [-@Claassen2020a; -@Claassen2020b].^[These figures represent the survey data actually used in estimating public support for democracy; as in Claassen [-@Claassen2020a; -@Claassen2020b], countries for which two separate years of survey data were not available were excluded.]
+## Adding Data
+
+As a further test of the classic arguments on democracy and public support, we generated estimates of democratic support using the same procedure as in Claassen [-@Claassen2020a; -@Claassen2020b] on a bigger data set,  assembling as much survey data on democratic support as possible.
+We employed `r dcpo_input_ncyi` national opinions on democracy from `r dcpo_input_surv` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncy` opinions and `r supdem_surv` national surveys used in Claassen [-@Claassen2020a; -@Claassen2020b].^[These figures represent the survey data actually used in estimating public support for democracy; as in Claassen [-@Claassen2020a; -@Claassen2020b], countries for which two separate years of survey data were not available were excluded.]
 
@@
 
-Figure \@ref(fig:plot-mainAJPS) presents the reanalyses of the hypothesis that public support influences the level of democracy, with democratic support pooled for all countries [@Claassen2020a, Model 1] in the left panel and separated by regime type (Model 2) on the right.
+Figure \@ref(fig:plot-mainAJPS) presents the reanalyses of the hypothesis that public support influences the level of democracy, with democratic support pooled for all countries [@Claassen2020a, 128, Model 1] in the left panel and democratic support separated by regime type (Model 2) on the right.
+The uppermost set of results replicate the analysis of @Claassen2020a, including its exclusion of measurement uncertainty, and reproduce that article's findings.
+The middle results introduce a single change: the uncertainty in the measurement of public support is taken into account.
+In both models, the positive coefficients for democratic support are no longer statistically significant.
 The uppermost set of results replicate @Claassen2020a without uncertainty.
@@
 # (APPENDIX) Appendix {-}
+\setcounter{page}{1}
+\renewcommand{\thepage}{A\arabic{page}}
+\setcounter{figure}{0}
+\renewcommand{\thefigure}{A.\arabic{figure}}
+
 # Data Recollection and Uncertainty in Control Variables {#dgp}
@@
 We also include measurement errors in control variables, including three democracy indices and corruption index.
-We extracted the posterior distributions of democracy indices, including Liberal Democracy,electoral democracy index and liberal component index, which are provided by [@coppedge2018].
+We extracted the posterior distributions of democracy indices, including Liberal Democracy, electoral democracy index and liberal component index, which are provided by [@coppedge2018].
 We drew 900 samples from the distribution of the Corruption Perception Index.
@@
 
-# DCPO Replication {#dcpo}
+# Appendix B: DCPO Replication {#dcpo}
 
@@
 
-# Replication with MOC Accounting for Uncertainty {#moc}
-
-In analysis models, we have latent variables in both sides of equations, public suppport for democracy, democracy indices and corruption index (The latter one is included in APSR analyses).
+# Appendix C: The Method of Composition {#moc}
+
+In analysis models, we have latent variables in both sides of equations, public suppport for democracy, democracy indices, and corruption index (The latter one is included in APSR analyses).
 Since measurement uncertainty associated with these latent variables can propagate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing "Method of Composition" [@Tanner1993,p52], which has been applied in analyses with latent variables [@Treier2008;@caughey2018;@Kastellec2015].
@@
 This procedure finally yields 900 samples of estimated coefficients drawn from the joint density of $\beta$ and $\theta$.
-We calcluate point estimates and standard error based on these 900 samples.
+We calculate point estimates and standard error based on these 900 samples.
+
+# Appendix D: Secondary Models from Claassen (2020$a$, 2020$b$)
 

### 2021-08-14 paper/dcpo_demsupport.Rmd
correct Figures of secondary models and dcpo

@@
 
-# Data Recollection and Uncertainty in Control Variables {#dgp}
+# Data Recollection and Uncertainty in Dependent and Control Variables {#dgp}
 
@@
 
-We also include measurement errors in control variables, including three democracy indices and corruption index.
-We extracted the posterior distributions of democracy indices, including Liberal Democracy, electoral democracy index and liberal component index, which are provided by [@coppedge2018].
-We drew 900 samples from the distribution of the Corruption Perception Index.
-Since Corruption Perception Index does not provide standard error before 2011, we imputed the missing standard error using the multiplication of a country's corruption index and the ratio of its available maximum standard error to its corresponding index.
+Since many variables, dependent variables, key independent variables, and control variables in the original analysis are latent variables, which cannot be observed directly and are inherently contaminated by measurement errors.
+We include measurement errors in five variables, public support for democracy, liberal democracy index, electoral democracy index, liberal component index, and corruption perception index.
+
+In respect of the key independent variable, public support for democracy, we preserve its posterior distribution from Model 5 using recollected and expanded data, separately.
+
+For the three indices of democratic development, we take two strategies.
+Regarding original data and recollected data, we use three democratic indices from V-Dem Version 8 which covers 201 countries from 1789 to 2017 and is the version Claassen used in his analyses.
+We use their posterior distribution provided by @coppedge2018.
+Regarding the expanded data used to replicate Claassen's analyses, we use the same three democratic indices but from V-Dem Version 10 because its year range from 1789 to 2019 is compatible with the expanded data.
+However, since V-Dem project has not released posterior distributions for indices in version 10, we simulated 900 data set for each democracy index using their standard error.
+
+Finally, to account for measurement error in Corruption Perceptions Index, we simulated 900 draws from a distribution with the point estimate and standard error provided by CPI for the year from 2012 to 2018.
+However, CPI does not provide standard error for the years before 2012.
+To simulate "posterior distribution", we first estimated the standard error for the country-year index.
+For each country, we identified its maximum relative standard error (standard error/cpi index) during these years and then calculated the estimated country-year standard error by multiplying the country's maximum relative error and its year CPI index.
+We used this estimated standard error to simulate 900 draws for each country-year.
+
+In the following section, we illustrate how we utilize these simulated distributions to take uncertainty into account in analysis models.
+
+# Appendix C: The Method of Composition {#moc}
+
+In analysis models, we have latent variables in both sides of equations, public suppport for democracy, democracy indices, and corruption index (The latter one is included in APSR analyses).
+Since measurement uncertainty associated with these latent variables can propagate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing "Method of Composition" [@Tanner1993,p52], which has been applied in analyses with latent variables [@Treier2008;@caughey2018;@Kastellec2015].
+
+As @caughey2018 explained, the main idea of MOC is to estimate the marginal distribution of coefficient parameter vector $\beta$, integrating over the uncertainty in latent variables $\theta$ (P A-15).
+More explicitly, we wish to integrate the joint density of $\beta$ and $\theta$ over the distribution of $\theta$.
+
+\begin{equation}
+p(\beta,\theta|w,y, Z) = p(\beta|\theta,w,y)p(\theta|Z).
+\end{equation}
+
+where $\theta$ is latent varibles with measurement errors conditional on data Z and a measurement model, $w$ is other predictors without errors, $Z$ is indicators for latent variables $X$, and $y$ is the outcome variable.
+In this way, we incorportate uncertainty in measuring predictor $\theta$, and uncertainty in the effects of latent variables $\theta$ and other variables $w$ on outcome variable $y$ [@Treier2008, 215].
+To sample from the conditional dentsity and the marginal density in the right side of the equation, we follow iterative Monte Carlo procdure described by @Treier2008, at iteration t,
+
+1. We sample $\theta^{s}$ from its posterior distribution $p(\theta|Z)$ and $y$ from $p(y|Z)$.
+
+2.
+For each analysis model, we run the model with $y$, $\theta$, and $w$, and save the coefficient estimates $\beta^{s}$ and variance-covariance matrix of $\beta^{s}$, $V^{s}$, both of which change due to the uncertainty in $\theta^{s}$ and $y^{s}$.
+
+3. We sample $\tilde{\beta^{t}}$ from the multivariate normal density with mean vector $\beta{s}$ and variance-covariace matrix $V^{s}$.
+
+We incorporate uncertainty for five variables, public support for democracy, liberal democracy, electoral democracy, liberal component index, and corruption perceptions index.
+For each of these five latent variables, we take 900 draws from its posterior distribution.
+We duplicate the dataset of variables “without” measurement error 900 times, and assign them to each a different random draw from the distributions of variables with measurement error, which yields 900 dataset.
+In next step, we run each of analysis models with these 900 datesets independently and save the resulting estimates of coefficients and the matrix of variance-covariance for each run.
+We then draw one sample from the mulitivariate normal distribution with the mean vector of coefficient estimates and variance-covariance matrix produced from each run.
+This procedure finally yields 900 samples of estimated coefficients drawn from the joint density of $\beta$ and $\theta$.
+We calculate point estimates and standard error based on these 900 samples.
+
+# Appendix D: Secondary Models from Claassen (2020$a$, 2020$b$)
+
+```{r formatResult-AJPS-dup}
+result_pooled <- bind_rows(
+  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Original"),
+ mutate(MOCsumm(mocresult_correctAJPS[["pooled"]]), model = "W. Uncertainty"),
+ mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), model = "Uncertainty+Expanded Data")
+) %>% 
+  mutate(type = "Pooled")
+
+result_gmm <- bind_rows(
+  mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm(mocresult_correctAJPS[["gmm"]]), model = "W. Uncertainty"),
+  mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), model = "Uncertainty+Expanded Data")
+) %>% 
+  mutate(type = "GMM")
+
+result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democracy\n (t-1)",
+        "Democracy\n (t-2)",
+        "Support\n (t-1)",
+        "Log GDP\n per capita\n (t-1)",
+        "GDP per\n capita growth\n (t-1)",
+        "Regional\n democracy\n (t-1)",
+        "Percent\n Muslim\n (t-1)",
+        "Resource\n dependence\n (t-1)"),
+      time = 6), 
+    type = factor(type, levels = c("Pooled", "GMM")),
+    model = factor(model, levels = c("Original", "W. Uncertainty", "Uncertainty+Expanded Data")))
+
+result_ajpsPooled <- result_pooledAJPS %>% 
+    filter(type == "Pooled")
+
+result_regime <- bind_rows(
+  mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm(mocresult_correctAJPS[["pooled-regime"]]), model = "W. Uncertainty"),
+  mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), model = "Uncertainty+Expanded Data")
+) %>% 
+  mutate(type = "Pooled")
+
+result_regimeGmm <- bind_rows(
+  mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm(mocresult_correctAJPS[["gmm-regime"]]), model = "W. Uncertainty"),
+ mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), model = "Uncertainty+Expanded Data")
+)%>% 
+  mutate(type = "GMM")
+
+result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democracy\n (t-1)",
+        "Democracy\n (t-2)",
+        "Support\n demo only\n (t-1)",
+        "Support\n auto only\n (t-1)",
+        "Log GDP\n per capita\n (t-1)",
+        "GDP per\n capita growth\n (t-1)",
+        "Regional\n democracy\n (t-1)",
+        "Percent\n Muslim\n (t-1)",
+        "Resource\n dependence\n (t-1)"),
+      time = 6), 
+    type = factor(type, levels = c("Pooled", "GMM")),
+    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data")))
+
+result_ajpsRegime <- result_regimeAJPS %>%
+    filter(type == "Pooled") %>% 
+    mutate(type = "Regime Specified")
+
+```
+
+```{r coefName-AJPS-dup}
+index_coefName <- c(
+    `Democracy\n (t-1)` = "Democracy[t-1]",
+    `Democracy\n (t-2)` = "Democracy[t-2]",
+    `Support\n (t-1)` = "Support[t-1]",
+    `Support\n demo only\n (t-1)` = "Support[t-1](demo~only)",
+    `Support\n auto only\n (t-1)` = "Support[t-1](auto~only)",
+    `Log GDP\n per capita\n (t-1)` = "Log~GDP~per~capita[t-1]",
+    `GDP per\n capita growth\n (t-1)` = "GDP~per~capita~growth[t-1]",
+    `Regional\n democracy\n (t-1)` = "Regional~democracy[t-1]",
+    `Percent\n Muslim\n (t-1)` = "Percent~Muslim[t-1]",
+    `Resource\n dependence\n (t-1)` = "Resource~dependence[t-1]"
+)
+```
+
+```{r plot-mocAJPS, fig.cap= "The Effect of Public Support on Democracy ", eval = TRUE, fig.width=7, fig.height=10}
+terms <- factor(rev(
+    c(
+        "Democracy[t-1]",
+        "Democracy[t-2]",
+        "Support[t-1]",
+        "Log~GDP~per~capita[t-1]",
+        "GDP~per~capita~growth[t-1]",
+        "Regional~democracy[t-1]",
+        "Percent~Muslim[t-1]",
+        "Resource~dependence[t-1]"
+    )
+), levels =
+    rev(
+        c(
+            "Democracy[t-1]",
+            "Democracy[t-2]",
+            "Support[t-1]",
+            "Log~GDP~per~capita[t-1]",
+            "GDP~per~capita~growth[t-1]",
+            "Regional~democracy[t-1]",
+            "Percent~Muslim[t-1]",
+            "Resource~dependence[t-1]"
+        )
+    ))
+
+plot_AJPS1 <-
+    dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
+    scale_y_discrete(labels = parse(text = levels(terms))) +
+    labs(title = "DV: V-Dem Liberal Democracy Index",
+         subtitle = "Pooled") +
+    facet_wrap( ~ type, scales = "free_x") +
+    theme(legend.position = "none")  +
+    scale_color_gb(palette = "digitMixed")
+
+terms2 <- factor(rev(
+    c(
+        "Democracy[t-1]",
+        "Democracy[t-2]",
+        "Support[t-1] (democracies~only)",
+        "Support[t-1] (autocracies~only)",
+        "Log~GDP~per~capita[t-1]",
+        "GDP~per~capita~growth[t-1]",
+        "Regional~democracy[t-1]",
+        "Percent~Muslim[t-1]",
+        "Resource~dependence[t-1]"
+    )
+), levels =
+    rev(
+        c(
+            "Democracy[t-1]",
+            "Democracy[t-2]",
+            "Support[t-1] (democracies~only)",
+            "Support[t-1] (autocracies~only)",
+            "Log~GDP~per~capita[t-1]",
+            "GDP~per~capita~growth[t-1]",
+            "Regional~democracy[t-1]",
+            "Percent~Muslim[t-1]",
+            "Resource~dependence[t-1]"
+        )
+    ))
+
+plot_AJPS2 <-
+    dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
+    scale_y_discrete(labels = parse(text = levels(terms2))) +
+    labs(title = "",
+         subtitle = "Regime Specified") +
+    facet_wrap( ~ type, scales = "free_x") +
+    theme(legend.position = "bottom",
+          legend.title = element_blank())  +
+   scale_color_gb(palette = "digitMixed")
+
+legend <- get_legend(plot_AJPS2)
+
+plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
+
+grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
+```
+
+\blandscape
+
+```{r formatResult-APSR-dup}
+# Pooled---------------------------------------
+
+result_ecm1 <- bind_rows(
+  mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["pooled1"]]), model = "W. Uncertainty"),
+  mutate(MOCsumm2(mocresult_expAPSR[["pooled1"]]), model = "Uncertainty+Expanded Data")
+) %>% 
+  mutate(type = "ECM")
+
+result_fd1 <- bind_rows(
+  mutate(result_clsAPSR[["fd1"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["fd1"]]), model = "W. Uncertainty"),
+  mutate(MOCsumm2(mocresult_expAPSR[["fd1"]]), model = "Uncertainty+Expanded Data")
+) %>% 
+  mutate(type = "First Difference")
+
+result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+        "Liberal Democracy\n (Difference)",
+        "Liberal Democracy\n (t-1)",
+        "Log GDP\n per capita\n (Difference)",
+        "Log GDP\n (t-1)"),
+      time = 3),
+      rep(
+        c("Liberal Democracy\n (Difference)", 
+          "Log GDP\n per capita\n (Difference)"), 
+        time = 3
+      )),
+    type = factor(type,  levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data"))
+  )
+
+result_apsrPooled <- result_APSR1 %>% 
+    filter(type == "ECM") %>% 
+    mutate(type = "Pooled")
+
+# Institution----------------------------------
+
+result_ecmReg1 <- bind_rows(
+  mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime1"]]), model = "W. Uncertainty"),
+  mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime1"]]), model = "Uncertainty+Expanded Data")
+) %>% 
+  mutate(type = "ECM")
+
+result_fdReg1 <- bind_rows(
+  mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime1"]]), model = "W. Uncertainty"),
+  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime1"]]), model = "Uncertainty+Expanded Data")
+) %>% 
+  mutate(type = "First Difference")
+
+result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+        "Electoral Democracy\n (Difference)",
+        "Electoral Democracy\n (t-1)",
+        "Minoritarian Democracy\n (Difference)",
+        "Minoritarian Democracy\n (t-1)",
+        "Log GDP\n per capita\n (Difference)",
+        "Log GDP\n (t-1)"),
+      time = 3),
+      rep(
+        c("Electoral Democracy\n (Difference)", 
+          "Minoritarian Democracy\n (Difference)",
+          "Log GDP\n per capita\n (Difference)"), 
+        time = 3
+      )),
+    type = factor(type,  levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data"))
+  )
+
+result_apsrRegime <- result_RegAPSR1 %>% 
+    filter(type == "ECM") %>% 
+    mutate(type = "Institution Specified")
+
+# Pooled-corruption------------------------------
+
+result_ecm2 <- bind_rows(
+  mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["pooled2"]]), model = "W. Uncertainty"),
+  mutate(MOCsumm2(mocresult_expAPSR[["pooled2"]]), model = "Uncertainty+Expanded Data")
+) %>% 
+  mutate(type = "ECM")
+
+result_fd2 <- bind_rows(
+  mutate(result_clsAPSR[["fd2"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["fd2"]]), model = "W. Uncertainty"),
+  mutate(MOCsumm2(mocresult_expAPSR[["fd2"]]), model = "Uncertainty+Expanded Data")
+) %>% 
+  mutate(type = "First Difference")
+
+result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+        "Liberal Democracy\n (Difference)",
+        "Liberal Democracy\n (t-1)",
+        "Log GDP\n per capita\n (Difference)",
+        "Log GDP\n (t-1)",
+        "Corruption\n (Difference)",
+        "Corruption\n (t-1)"
+      ),
+      time = 3),
+      rep(
+        c("Liberal Democracy\n (Difference)", 
+          "Log GDP\n per capita\n (Difference)",
+          "Corruption\n (Difference)"), 
+        time = 3
+      )),
+    type = factor(type,  levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data"))
+  )
+
+# Institution Corruption--------------------------------
+
+result_ecmReg2 <- bind_rows(
+  mutate(result_clsAPSR[["pooled-regime2"]][[1]][,1:3], model = "Original"),
+ mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime2"]]), model = "W. Uncertainty"),
+  mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime2"]]), model = "Uncertainty+Expanded Data")) %>%
+  mutate(type = "ECM")
+
+result_fdReg2 <- bind_rows(
+  mutate(result_clsAPSR[["fd-regime2"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime2"]]), model = "W. Uncertainty"),
+  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime2"]]), model = "Uncertainty+Expanded Data")) %>% 
+  mutate(type = "First Difference")
+
+result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = c(rep(
+      c("Democratic Mood\n (t-1)",
+        "Democratic Mood\n (t-2)",
+        "Electoral Democracy\n (Difference)",
+        "Electoral Democracy\n (t-1)",
+        "Minoritarian Democracy\n (Difference)",
+        "Minoritarian Democracy\n (t-1)",
+        "Log GDP\n per capita\n (Difference)",
+        "Log GDP\n (t-1)",
+        "Corruption\n (Difference)",
+        "Corruption\n (t-1)"
+      ),
+      time = 3),
+      rep(
+        c("Electoral Democracy\n (Difference)", 
+          "Minoritarian Democracy\n (Difference)",
+          "Log GDP\n per capita\n (Difference)",
+          "Corruption\n (Difference)"), 
+        time = 3
+      )),
+    type = factor(type,  levels = c("ECM", "First Difference")),
+    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data"))
+  )
+```
+
+```{r coefName-APSR-dup}
+index_coefName <- c(
+    `Democratic Mood\n (t-1)` = "Support[t-1]",
+    `Democratic Mood\n (t-2)` = "Support[t-2]",
+    `Liberal Democracy\n (Difference)` = "Delta~Liberal~democracy",
+    `Liberal Democracy\n (t-1)` = "Liberal~democracy[t-1]",
+    `Electoral Democracy\n (Difference)` = "Delta~Electoral~democracy",
+    `Electoral Democracy\n (t-1)` = "Electoral~democracy[t-1]",
+    `Minoritarian Democracy\n (Difference)` = "Delta~Minoritarian~democracy",
+    `Minoritarian Democracy\n (t-1)` = "Minoritarian~democracy[t-1]",
+    `Log GDP\n per capita\n (Difference)` = "Delta~Log~GDP~per~capita",
+    `Log GDP\n (t-1)` = "Log~GDP[t-1]"
+)
+```
+
+```{r plot-mocAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", eval = TRUE, fig.width=10, fig.height=10}
+terms1 <- factor(rev(
+    c(
+        "Support[t-1]",
+        "Support[t-2]",
+        "Delta~Liberal~democracy",
+        "Liberal~democracy[t-1]",
+        "Delta~Log~GDP~per~capita",
+        "Log~GDP[t-1]"
+    )
+),
+levels = rev(
+    c(
+        "Support[t-1]",
+        "Support[t-2]",
+        "Delta~Liberal~democracy",
+        "Liberal~democracy[t-1]",
+        "Delta~Log~GDP~per~capita",
+        "Log~GDP[t-1]"
+    )
+), 
+labels = rev(
+    c(
+        "Support[t-1]",
+        "Support[t-2]",
+        "Delta~Liberal~Dem",
+        "Liberal~Dem[t-1]",
+        "Delta~Log~GDP~per~capita",
+        "Log~GDP[t-1]"
+    )
+))
+
+plot_APSR1 <-
+    dwplot(result_APSR1, dodge_size = 0.8, by_2sd = FALSE) +
+    scale_y_discrete(labels = parse(text = levels(terms1))) +
+    labs(title = "DV: The Change of Public Support for Democracy",
+         subtitle = "Pooled") +
+    facet_wrap( ~ type, drop = T, scales = "free_x") +
+    theme(legend.position = "none")  +
+   scale_color_gb(palette = "digitMixed")
+
+terms3 <- factor(rev(
+    c(
+        "Support[t-1]",
+        "Support[t-2]",
+        "Delta~Electoral~democracy",
+        "Electoral~democracy[t-1]",
+        "Delta~Minoritarian~democracy",
+        "Minoritarian~democracy[t-1]",
+        "Delta~Log~GDP~per~capita",
+        "Log~GDP[t-1]"
+    )
+),
+levels = rev(
+    c(
+        "Support[t-1]",
+        "Support[t-2]",
+        "Delta~Electoral~democracy",
+        "Electoral~democracy[t-1]",
+        "Delta~Minoritarian~democracy",
+        "Minoritarian~democracy[t-1]",
+        "Delta~Log~GDP~per~capita",
+        "Log~GDP[t-1]"
+    )
+),
+labels = rev(
+    c(
+        "Support[t-1]",
+        "Support[t-2]",
+        "Delta~Electoral",
+        "Electoral[t-1]",
+        "Delta~Minoritarian",
+        "Minoritarian[t-1]",
+        "Delta~Log~GDP~per~capita",
+        "Log~GDP[t-1]"
+    )
+)
+)
+
+plot_RegAPSR1 <-
+    dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
+    scale_y_discrete(labels = parse(text = levels(terms3))) +
+    labs(title = "",
+         subtitle = "Institution Specified") +
+    facet_wrap( ~ type, scales = "free_x") +
+    theme(legend.position = "none")  +
+    scale_color_gb(palette = "digitMixed")
+
+terms2 <- factor(rev(
+    c(
+        "Support[t-1]",
+        "Support[t-2]",
+        "Delta~Liberal~democracy",
+        "Liberal~democracy[t-1]",
+        "Delta~Log~GDP~per~capita",
+        "Log~GDP[t-1]",
+        "Delta~Corruption",
+        "Corruption[t-1]"
+    )
+),
+levels = rev(
+    c(
+        "Support[t-1]",
+        "Support[t-2]",
+        "Delta~Liberal~democracy",
+        "Liberal~democracy[t-1]",
+        "Delta~Log~GDP~per~capita",
+        "Log~GDP[t-1]",
+        "Delta~Corruption",
+        "Corruption[t-1]"
+    )
+),
+labels = rev(
+    c(
+        "Support[t-1]",
+        "Support[t-2]",
+        "Delta~Liberal~Dem",
+        "Liberal~Dem[t-1]",
+        "Delta~Log~GDP~per~capita",
+        "Log~GDP[t-1]",
+        "Delta~Corruption",
+        "Corruption[t-1]"
+    )
+))
+
+plot_APSR2 <-
+    dwplot(result_APSR2, dodge_size = 0.8, by_2sd = FALSE) +
+    scale_y_discrete(labels = parse(text = levels(terms2))) +
+    labs(title = "",
+         subtitle = "W. Corruption") +
+    facet_wrap( ~ type, scales = "free_x") +
+    theme(legend.position = "none")  +
+    scale_color_gb(palette = "digitMixed")
+
+terms4 <- factor(rev(
+    c(
+        "Support[t-1]",
+        "Support[t-2]",
+        "Delta~Electoral~democracy",
+        "Electoral~democracy[t-1]",
+        "Delta~Minoritarian~democracy",
+        "Minoritarian~democracy[t-1]",
+        "Delta~Log~GDP",
+        "Log~GDP[t-1]",
+        "Delta~Corruption",
+        "Corruption[t-1]"
+    )
+),
+levels = rev(
+    c(
+        "Support[t-1]",
+        "Support[t-2]",
+        "Delta~Electoral~democracy",
+        "Electoral~democracy[t-1]",
+        "Delta~Minoritarian~democracy",
+        "Minoritarian~democracy[t-1]",
+        "Delta~Log~GDP",
+        "Log~GDP[t-1]",
+        "Delta~Corruption",
+        "Corruption[t-1]"
+    )
+),
+labels = rev(
+    c(
+        "Support[t-1]",
+        "Support[t-2]",
+        "Delta~Electoral",
+        "Electoral[t-1]",
+        "Delta~Minoritarian",
+        "Minoritarian[t-1]",
+        "Delta~Log~GDP",
+        "Log~GDP[t-1]",
+        "Delta~Corruption",
+        "Corruption[t-1]"
+    )
+))
+
+plot_RegAPSR2 <-
+    dwplot(result_RegAPSR2, dodge_size = 0.8, by_2sd = FALSE) +
+    scale_y_discrete(labels = parse(text = levels(terms4))) +
+    labs(title = "",
+         subtitle = "Institution Specified w. Corruption") +
+    facet_wrap( ~ type, scales = "free_x") +
+    theme(legend.position = "bottom",
+          legend.title = element_blank())  +
+    scale_color_gb(palette = "digitMixed")
+
+legend <- get_legend(plot_RegAPSR2)
+
+plot_RegAPSR2 <- plot_RegAPSR2 + theme(legend.position = "none")
+
+grid.arrange(plot_APSR1,
+             plot_APSR2,
+             plot_RegAPSR1,
+             plot_RegAPSR2,
+             legend,
+             ncol = 2)
+```
+
+\elandscape
+
+Figure \@ref(fig:plot-mocAJPS) and \@ref(fig:plot-mocAPSR) presents the results of using MOC to engage measurement error. 
+The results are consistent as we gained from the MO method (cf. Figure \@ref(fig:plot-mainAJPS) and \@ref(fig:plot-mainAPSR)).
 
 # Appendix B: DCPO Replication {#dcpo}
+
+As a further test of the classic arguments on democracy and public support, we apply the superior DCPO model to a bigger data set.
+The DCPO model has several advantages over the @Claassen2019 model used in Claassen [-@Claassen2020a; -@Claassen2020b].
+First, while the @Claassen2019 model dichotomizes responses and so discards some information provided by 50 of the 52 survey items employed in Claassen [-@Claassen2020a; -@Claassen2020b], the DCPO model makes use of all of the information available from these ordinal items [@Solt2020a, 5].
+Second, as the DCPO model includes both parameters for the dispersion of each survey item and for the standard deviation of aggregate public opinion in each country-year, it is a complete population-level item-response model and so, unlike the @Claassen2019 model, is explicitly derived from an individual-level model of survey responses [@Solt2020a, 3-4; see also @McGann2014].
+Third, to produce more sensible estimates of uncertainty for observations at the extremes of the scale [see @Linzer2015, 229], the DCPO model places bounds on its estimates of public opinion [@Solt2020a, 8].
+Further commending the DCPO model to us---and demonstrating that its advantages make a difference---the validation tests in @Solt2020a [, 10-12] reveal that it fits survey data on democratic support better than the @Claassen2019 model does.
+
+We employed the superior DCPO model to the expanded data using the `DCPO` package for R [@Solt2020b].
+
+```{r moc-dcpoAJPS, eval=FALSE}
+
+dcpo_Ajps <- purrr::map(1:900, function(anEntry) {
+  dcpo_ajps[[anEntry]] %>% 
+    plm::pdata.frame(index = c("country", "year")) %>%
+    rename(SupDem_trim =theta_trim,
+           Regime_VD = Vdem_regime,
+           Pr_Muslim = muslism_prop_2010,
+           Res_cp_WDI_di = dependence_pc_di,
+           lnGDP_imp = lg_imp_mdpgdp,
+           GDP_imp_grth = mdprgdp_grwth,
+           firstyear = first_year,
+           Libdem_VD = Vdem_libdem,
+           Libdem_m1 = Vdem_libdem_m1,
+           Libdem_m2 = Vdem_libdem_m2,
+           ChgDem = Chgdem,
+           UpChgDem = upchgdem,
+           DwnChgDem = downchgdem,
+           Libdem_regUN = Region_libdem,
+           Libdem_regUN_m1 = Region_libdem_m1)
+})
+
+result_dcpoUncertain  <- map(ls_mod_ajpsCLS[1:2], function(aMod){
+  result <- methodComposition1(dcpo_Ajps,aMod)
+})
+
+names(result_dcpoUncertain) <- c("pooled", "pooled-regime")
+
+result_dcpoUncertain_gmm  <- map(ls_mod_ajpsCLS[3:4], function(aMod){
+  result <- methodComposition2(dcpo_Ajps,aMod)
+})
+names(result_dcpoUncertain_gmm) <- c("gmm", "gmm-regime")
+
+mocresult_dcpoAJPS <- append(result_dcpoUncertain, result_dcpoUncertain_gmm)
+saveRDS(mocresult_dcpoAJPS, file =here("output","estimates_moc_dcpoAJPS.RDS"))
+
+```
+
+```{r formatDCPOResult-AJPS}
+result_pooled <- bind_rows(
+  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Original"),
+ mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), model = "Uncertainty+ExpData"),
+ mutate(MOCsumm(mocresult_dcpoAJPS[["pooled"]]), model = "Uncertainty+DCPO+ExpData")
+) %>% 
+  mutate(type = "Pooled")
+
+result_gmm <- bind_rows(
+  mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), model = "Uncertainty+ExpData"),
+  mutate(MOCsumm(mocresult_dcpoAJPS[["gmm"]]), model = "Uncertainty+DCPO+ExpData")
+) %>% 
+  mutate(type = "GMM")
+
+result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democracy\n (t-1)",
+        "Democracy\n (t-2)",
+        "Support\n (t-1)",
+        "Log GDP\n per capita\n (t-1)",
+        "GDP per\n capita growth\n (t-1)",
+        "Regional\n democracy\n (t-1)",
+        "Percent\n Muslim\n (t-1)",
+        "Resource\n dependence\n (t-1)"),
+      time = 6), 
+    type = factor(type, levels = c("Pooled", "GMM")),
+    model = factor(model, levels = c("Original", "Uncertainty+ExpData", "Uncertainty+DCPO+ExpData")))
+
+result_ajpsPooled <- result_pooledAJPS %>% 
+    filter(type == "Pooled")
+
+result_regime <- bind_rows(
+  mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), model = "Uncertainty+ExpData"),
+  mutate(MOCsumm(mocresult_dcpoAJPS[["pooled-regime"]]), model = "Uncertainty+DCPO+ExpData")
+) %>% 
+  mutate(type = "Pooled")
+
+result_regimeGmm <- bind_rows(
+  mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), model = "Uncertainty+ExpData"),
+ mutate(MOCsumm(mocresult_dcpoAJPS[["gmm-regime"]]), model = "Uncertainty+DCPO+ExpData")
+)%>% 
+  mutate(type = "GMM")
+
+result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democracy\n (t-1)",
+        "Democracy\n (t-2)",
+        "Support\n demo only\n (t-1)",
+        "Support\n auto only\n (t-1)",
+        "Log GDP\n per capita\n (t-1)",
+        "GDP per\n capita growth\n (t-1)",
+        "Regional\n democracy\n (t-1)",
+        "Percent\n Muslim\n (t-1)",
+        "Resource\n dependence\n (t-1)"),
+      time = 6), 
+    type = factor(type, levels = c("Pooled", "GMM")),
+    model = factor(model, levels = c("Original","Uncertainty+ExpData", "Uncertainty+DCPO+ExpData")))
+
+result_ajpsRegime <- result_regimeAJPS %>%
+    filter(type == "Pooled") %>% 
+    mutate(type = "Regime Specified")
+
+```
+
+```{r coefName-dcpoAJPS-dup}
+index_coefName <- c(
+    `Democracy\n (t-1)` = "Democracy[t-1]",
+    `Democracy\n (t-2)` = "Democracy[t-2]",
+    `Support\n (t-1)` = "Support[t-1]",
+    `Support\n demo only\n (t-1)` = "Support[t-1](demo~only)",
+    `Support\n auto only\n (t-1)` = "Support[t-1](auto~only)",
+    `Log GDP\n per capita\n (t-1)` = "Log~GDP~per~capita[t-1]",
+    `GDP per\n capita growth\n (t-1)` = "GDP~per~capita~growth[t-1]",
+    `Regional\n democracy\n (t-1)` = "Regional~democracy[t-1]",
+    `Percent\n Muslim\n (t-1)` = "Percent~Muslim[t-1]",
+    `Resource\n dependence\n (t-1)` = "Resource~dependence[t-1]"
+)
+```
+
+```{r plotdcpo-mocAJPS, fig.cap= "The Effect of Public Support on Democracy ", eval = TRUE, fig.width=7, fig.height=10}
+terms <- factor(rev(
+    c(
+        "Democracy[t-1]",
+        "Democracy[t-2]",
+        "Support[t-1]",
+        "Log~GDP~per~capita[t-1]",
+        "GDP~per~capita~growth[t-1]",
+        "Regional~democracy[t-1]",
+        "Percent~Muslim[t-1]",
+        "Resource~dependence[t-1]"
+    )
+), levels =
+    rev(
+        c(
+            "Democracy[t-1]",
+            "Democracy[t-2]",
+            "Support[t-1]",
+            "Log~GDP~per~capita[t-1]",
+            "GDP~per~capita~growth[t-1]",
+            "Regional~democracy[t-1]",
+            "Percent~Muslim[t-1]",
+            "Resource~dependence[t-1]"
+        )
+    ))
+
+plot_AJPS1 <-
+    dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
+    scale_y_discrete(labels = parse(text = levels(terms))) +
+    labs(title = "DV: V-Dem Liberal Democracy Index",
+         subtitle = "Pooled") +
+    facet_wrap( ~ type, scales = "free_x") +
+    theme(legend.position = "none")  +
+    scale_color_gb(palette = "digitMixed")
+
+terms2 <- factor(rev(
+    c(
+        "Democracy[t-1]",
+        "Democracy[t-2]",
+        "Support[t-1] (democracies~only)",
+        "Support[t-1] (autocracies~only)",
+        "Log~GDP~per~capita[t-1]",
+        "GDP~per~capita~growth[t-1]",
+        "Regional~democracy[t-1]",
+        "Percent~Muslim[t-1]",
+        "Resource~dependence[t-1]"
+    )
+), levels =
+    rev(
+        c(
+            "Democracy[t-1]",
+            "Democracy[t-2]",
+            "Support[t-1] (democracies~only)",
+            "Support[t-1] (autocracies~only)",
+            "Log~GDP~per~capita[t-1]",
+            "GDP~per~capita~growth[t-1]",
+            "Regional~democracy[t-1]",
+            "Percent~Muslim[t-1]",
+            "Resource~dependence[t-1]"
+        )
+    ))
+
+plot_AJPS2 <-
+    dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
+    scale_y_discrete(labels = parse(text = levels(terms2))) +
+    labs(title = "",
+         subtitle = "Regime Specified") +
+    facet_wrap( ~ type, scales = "free_x") +
+    theme(legend.position = "bottom",
+          legend.title = element_blank())  +
+   scale_color_gb(palette = "digitMixed")
+
+legend <- get_legend(plot_AJPS2)
+
+plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
+
+grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
+```
 
@@
 
-```{r plot-mainDCPOAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", fig.width=7, fig.height=10}
-type_model <-
-    c("Original", "Uncertainty+ExpData", "Uncertainty+DCPO+ExpData")
-
-df_plot <- bind_rows(result_apsrPooled, result_apsrRegime) %>%
-    mutate(
-        term = index_coefName[term],
-        term = factor(term, levels = unique(index_coefName)),
-        type = factor(type, levels = c("Pooled", "Institution Specified"))
-    )
-
-dwplot(df_plot) +
-    geom_vline(xintercept = 0,
-               colour = "grey80",
-               linetype = 2) +
-    ggtitle("DV: The Change of Public Support for Democracy") +
-    xlab("Coefficient Estimate") +
-    theme(
-        axis.title.y = element_blank(),
-        legend.position = "bottom",
-        legend.title = element_blank()
-    ) +
-    facet_wrap(~ type)  +
-   scale_color_gb(palette = "digitMixed")
-
-```
-
-```{r coefName-AJPS-dup}
+```{r coefName-dcpoAPSR-dup}
 index_coefName <- c(
-    `Democracy\n (t-1)` = "Democracy[t-1]",
-    `Democracy\n (t-2)` = "Democracy[t-2]",
-    `Support\n (t-1)` = "Support[t-1]",
-    `Support\n demo only\n (t-1)` = "Support[t-1](demo~only)",
-    `Support\n auto only\n (t-1)` = "Support[t-1](auto~only)",
-    `Log GDP\n per capita\n (t-1)` = "Log~GDP~per~capita[t-1]",
-    `GDP per\n capita growth\n (t-1)` = "GDP~per~capita~growth[t-1]",
-    `Regional\n democracy\n (t-1)` = "Regional~democracy[t-1]",
-    `Percent\n Muslim\n (t-1)` = "Percent~Muslim[t-1]",
-    `Resource\n dependence\n (t-1)` = "Resource~dependence[t-1]"
-)
-```
-
-```{r moc-dcpoAJPS, eval=FALSE}
-
-dcpo_Ajps <- purrr::map(1:900, function(anEntry) {
-  dcpo_ajps[[anEntry]] %>% 
-    plm::pdata.frame(index = c("country", "year")) %>%
-    rename(SupDem_trim =theta_trim,
-           Regime_VD = Vdem_regime,
-           Pr_Muslim = muslism_prop_2010,
-           Res_cp_WDI_di = dependence_pc_di,
-           lnGDP_imp = lg_imp_mdpgdp,
-           GDP_imp_grth = mdprgdp_grwth,
-           firstyear = first_year,
-           Libdem_VD = Vdem_libdem,
-           Libdem_m1 = Vdem_libdem_m1,
-           Libdem_m2 = Vdem_libdem_m2,
-           ChgDem = Chgdem,
-           UpChgDem = upchgdem,
-           DwnChgDem = downchgdem,
-           Libdem_regUN = Region_libdem,
-           Libdem_regUN_m1 = Region_libdem_m1)
-})
-
-result_dcpoUncertain  <- map(ls_mod_ajpsCLS[1:2], function(aMod){
-  result <- methodComposition1(dcpo_Ajps,aMod)
-})
-
-names(result_dcpoUncertain) <- c("pooled", "pooled-regime")
-
-result_dcpoUncertain_gmm  <- map(ls_mod_ajpsCLS[3:4], function(aMod){
-  result <- methodComposition2(dcpo_Ajps,aMod)
-})
-names(result_dcpoUncertain_gmm) <- c("gmm", "gmm-regime")
-
-mocresult_dcpoAJPS <- append(result_dcpoUncertain, result_dcpoUncertain_gmm)
-saveRDS(mocresult_dcpoAJPS, file =here("output","estimates_moc_dcpoAJPS.RDS"))
-
-```
-
-```{r formatDCPOResult-AJPS}
-result_pooled <- bind_rows(
-  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Original"),
- mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), model = "Uncertainty+ExpData"),
- mutate(MOCsumm(mocresult_dcpoAJPS[["pooled"]]), model = "Uncertainty+DCPO+ExpData")
-) %>% 
-  mutate(type = "Pooled")
-
-result_gmm <- bind_rows(
-  mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), model = "Uncertainty+ExpData"),
-  mutate(MOCsumm(mocresult_dcpoAJPS[["gmm"]]), model = "Uncertainty+DCPO+ExpData")
-) %>% 
-  mutate(type = "GMM")
-
-result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = rep(
-      c("Democracy\n (t-1)",
-        "Democracy\n (t-2)",
-        "Support\n (t-1)",
-        "Log GDP\n per capita\n (t-1)",
-        "GDP per\n capita growth\n (t-1)",
-        "Regional\n democracy\n (t-1)",
-        "Percent\n Muslim\n (t-1)",
-        "Resource\n dependence\n (t-1)"),
-      time = 6), 
-    type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Original", "Uncertainty+ExpData", "Uncertainty+DCPO+ExpData")))
-
-result_ajpsPooled <- result_pooledAJPS %>% 
-    filter(type == "Pooled")
-
-result_regime <- bind_rows(
-  mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), model = "Uncertainty+ExpData"),
-  mutate(MOCsumm(mocresult_dcpoAJPS[["pooled-regime"]]), model = "Uncertainty+DCPO+ExpData")
-) %>% 
-  mutate(type = "Pooled")
-
-result_regimeGmm <- bind_rows(
-  mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), model = "Uncertainty+ExpData"),
- mutate(MOCsumm(mocresult_dcpoAJPS[["gmm-regime"]]), model = "Uncertainty+DCPO+ExpData")
-)%>% 
-  mutate(type = "GMM")
-
-result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = rep(
-      c("Democracy\n (t-1)",
-        "Democracy\n (t-2)",
-        "Support\n demo only\n (t-1)",
-        "Support\n auto only\n (t-1)",
-        "Log GDP\n per capita\n (t-1)",
-        "GDP per\n capita growth\n (t-1)",
-        "Regional\n democracy\n (t-1)",
-        "Percent\n Muslim\n (t-1)",
-        "Resource\n dependence\n (t-1)"),
-      time = 6), 
-    type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Original","Uncertainty+ExpData", "Uncertainty+DCPO+ExpData")))
-
-result_ajpsRegime <- result_regimeAJPS %>%
-    filter(type == "Pooled") %>% 
-    mutate(type = "Regime Specified")
-
-```
-
-```{r plotdcpo-mainAJPS, fig.cap= "The Effect of Public Support on Democracy with Uncertainty", fig.width=7, fig.height=10, fig.align='center'}
-
-type_model <-
-  c("Original", "Uncertainty+ExpData", "Uncertainty+DCPO+ExpData")
-
-df_plot <- bind_rows(result_ajpsPooled, result_ajpsRegime) %>% 
-    mutate(term = index_coefName[term],
-           term = factor(term, levels = unique(index_coefName)))
-
-dwplot(df_plot) +
-    geom_vline(xintercept = 0,
-               colour = "grey80",
-               linetype = 2) +
-    theme_minimal() +
-    ggtitle("DV: Liberal Democracy (Vdem)") +
-    xlab("Coefficient Estimate") +
-    theme(
-        axis.title.y = element_blank(),
-        legend.position = "bottom",
-      legend.title = element_blank()
-    ) +
-    scale_color_gb(palette = "digitMixed") +
-    facet_wrap(~ type)
-
-```
-
-# Appendix C: The Method of Composition {#moc}
-
-In analysis models, we have latent variables in both sides of equations, public suppport for democracy, democracy indices, and corruption index (The latter one is included in APSR analyses).
-Since measurement uncertainty associated with these latent variables can propagate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing "Method of Composition" [@Tanner1993,p52], which has been applied in analyses with latent variables [@Treier2008;@caughey2018;@Kastellec2015].
-
-As @caughey2018 explained, the main idea of MOC is to estimate the marginal distribution of coefficient parameter vector $\beta$, integrating over the uncertainty in latent variables $\theta$ (P A-15).
-More explicitly, we wish to integrate the joint density of $\beta$ and $\theta$ over the distribution of $\theta$.
-
-\begin{equation}
-p(\beta,\theta|w,y, Z) = p(\beta|\theta,w,y)p(\theta|Z).
-\end{equation}
-
-where $\theta$ is latent varibles with measurement errors conditional on data Z and a measurement model, $w$ is other predictors without errors, $Z$ is indicators for latent variables $X$, and $y$ is the outcome variable.
-In this way, we incorportate uncertainty in measuring predictor $\theta$, and uncertainty in the effects of latent variables $\theta$ and other variables $w$ on outcome variable $y$ [@Treier2008, 215].
-To sample from the conditional dentsity and the marginal density in the right side of the equation, we follow iterative Monte Carlo procdure described by @Treier2008, at iteration t,
-1. We sample $\theta^{s}$ from its posterior distribution $p(\theta|Z)$ and $y$ from $p(y|Z)$. 
-2.
-For each analysis model, we run the model with $y$, $\theta$, and $w$, and save the coefficient estimates $\beta^{s}$ and variance-covariance matrix of $\beta^{s}$, $V^{s}$, both of which change due to the uncertainty in $\theta^{s}$ and $y^{s}$.
-3. We sample $\tilde{\beta^{t}}$ from the multivariate normal density with mean vector $\beta{s}$ and variance-covariace matrix $V^{s}$.
-
-We incorporate uncertainty for five variables, public support for democracy, liberal democracy, electoral democracy, liberal component index, and corruption perceptions index.
-For each of these five latent variables, we take 900 draws from its posterior distribution.
-We duplicate the dataset of variables “without” measurement error 900 times, and assign them to each a different random draw from the distributions of variables with measurement error, which yields 900 dataset.
-In next step, we run each of analysis models with these 900 datesets independently and save the resulting estimates of coefficients and the matrix of variance-covariance for each run.
-We then draw one sample from the mulitivariate normal distribution with the mean vector of coefficient estimates and variance-covariance matrix produced from each run.
-This procedure finally yields 900 samples of estimated coefficients drawn from the joint density of $\beta$ and $\theta$.
-We calculate point estimates and standard error based on these 900 samples.
-
-# Appendix D: Secondary Models from Claassen (2020$a$, 2020$b$)
-
-```{r plot-mocAJPS, fig.cap= "The Effect of Public Support on Democracy ", eval = TRUE, fig.width=7, fig.height=10}
-terms <- factor(rev(
-    c(
-        "Democracy[t-1]",
-        "Democracy[t-2]",
-        "Support[t-1]",
-        "Log~GDP~per~capita[t-1]",
-        "GDP~per~capita~growth[t-1]",
-        "Regional~democracy[t-1]",
-        "Percent~Muslim[t-1]",
-        "Resource~dependence[t-1]"
-    )
-), levels =
-    rev(
-        c(
-            "Democracy[t-1]",
-            "Democracy[t-2]",
-            "Support[t-1]",
-            "Log~GDP~per~capita[t-1]",
-            "GDP~per~capita~growth[t-1]",
-            "Regional~democracy[t-1]",
-            "Percent~Muslim[t-1]",
-            "Resource~dependence[t-1]"
-        )
-    ))
-
-plot_AJPS1 <-
-    dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms))) +
-    labs(title = "DV: V-Dem Liberal Democracy Index",
-         subtitle = "Pooled") +
-    facet_wrap( ~ type, scales = "free_x") +
-    theme(legend.position = "none")  +
-    scale_color_gb(palette = "digitMixed")
-
-terms2 <- factor(rev(
-    c(
-        "Democracy[t-1]",
-        "Democracy[t-2]",
-        "Support[t-1] (democracies~only)",
-        "Support[t-1] (autocracies~only)",
-        "Log~GDP~per~capita[t-1]",
-        "GDP~per~capita~growth[t-1]",
-        "Regional~democracy[t-1]",
-        "Percent~Muslim[t-1]",
-        "Resource~dependence[t-1]"
-    )
-), levels =
-    rev(
-        c(
-            "Democracy[t-1]",
-            "Democracy[t-2]",
-            "Support[t-1] (democracies~only)",
-            "Support[t-1] (autocracies~only)",
-            "Log~GDP~per~capita[t-1]",
-            "GDP~per~capita~growth[t-1]",
-            "Regional~democracy[t-1]",
-            "Percent~Muslim[t-1]",
-            "Resource~dependence[t-1]"
-        )
-    ))
-
-plot_AJPS2 <-
-    dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms2))) +
-    labs(title = "",
-         subtitle = "Regime Specified") +
-    facet_wrap( ~ type, scales = "free_x") +
-    theme(legend.position = "bottom",
-          legend.title = element_blank())  +
-   scale_color_gb(palette = "digitMixed")
-
-legend <- get_legend(plot_AJPS2)
-
-plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
-
-grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
-```
-
-\blandscape
-
-```{r plot-mocAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", eval = TRUE, fig.width=10, fig.height=10}
+    `Democratic Mood\n (t-1)` = "Support[t-1]",
+    `Democratic Mood\n (t-2)` = "Support[t-2]",
+    `Liberal Democracy\n (Difference)` = "Delta~Liberal~democracy",
+    `Liberal Democracy\n (t-1)` = "Liberal~democracy[t-1]",
+    `Electoral Democracy\n (Difference)` = "Delta~Electoral~democracy",
+    `Electoral Democracy\n (t-1)` = "Electoral~democracy[t-1]",
+    `Minoritarian Democracy\n (Difference)` = "Delta~Minoritarian~democracy",
+    `Minoritarian Democracy\n (t-1)` = "Minoritarian~democracy[t-1]",
+    `Log GDP\n per capita\n (Difference)` = "Delta~Log~GDP~per~capita",
+    `Log GDP\n (t-1)` = "Log~GDP[t-1]"
+)
+```
+
+```{r plotdcpo-mocAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", eval = TRUE, fig.width=10, fig.height=10}
 terms1 <- factor(rev(
@@
 ```
-
-\elandscape
-
-Figure \@ref(fig:plot-mocAJPS) and \@ref(fig:plot-mocAPSR) presents the results of using MOC to engage measurement error. 
-The results are consistent as we gained from the MO method (cf. Figure \@ref(fig:plot-mainAJPS) and \@ref(fig:plot-mainAPSR)).

### 2021-08-14 paper/memo/memo.Rmd
adjust memo

@@
 
-Many variables, dependent variable, key independent variables and control variables in original analysis, are latent variables, which cannot be observed directly and are inherently contaminated by measurement errors.
-To address this concern and justify the necessity of incorporating measurement uncertainty in latent variables, we take uncertainty into account for five variables, public support for democracy, liberal democracy index, electoral democracy index, liberal component index, and corruption perception index, in this version of manuscript.
+Many variables, dependent variables, key independent variables, and control variables in the original analysis, are latent variables, which cannot be observed directly and are inherently contaminated by measurement errors.
+To address this concern and justify the necessity of incorporating measurement uncertainty in latent variables, we take uncertainty into account for five variables, public support for democracy, liberal democracy index, electoral democracy index, liberal component index, and corruption perception index, in the revised version.
 
-In respect of the key independent variable, public support for democracy, we used Claassen's Model 5 and recollected originalsource data to replicate the measure of public support and keep its posterior distrubtion.
-For expanded data, still, we used Model 5 and expanded source data to measure public support and perserve its posterior distribution. 
+In respect of the key independent variable, public support for democracy, we used Claassen's Model 5 and recollected original source data to replicate the measure of public support and keep its posterior distribution.
+For expanded data, still, we used Model 5 and expanded source data to measure public support and preserve its posterior distribution. 
 In terms of three indices of democratic development, we incorporated measurement error using their posterior distribution from V-Dem Version 8 which covers 201 countries from 1789 to 2017 and is the version Claassen used in his analyses.
@@
 To account for measurement error in Corruption Perceptions Index, we simulated 900 draws from a distribution with the point estimate and standard error provided by CPI for the year from 2012 to 2018.
-However, since CPI does not povide standard error for the years before 2012, we first estimated the standard error for these years by using the product of countries' maximum relative error (standard error/cpi index) and their CPI index, and then used the estimated standard error to simulate 900 draws.
+However, since CPI does not provide standard error for the years before 2012, we first estimated the standard error for these years by using the product of countries' maximum relative error (standard error/cpi index) and their CPI index and then used the estimated standard error to simulate 900 draws.
 
-We used he posterior distributions of five variables in method of composition to address measurement errors. 
+We used the posterior distributions of five variables in method of composition to address measurement errors. 
 By incorporating uncertainty in democracy indices, democratic support, and corruption perception index, the relationships between public support and democratic development and between the change of public support and the change of democracy disappear either using Claassen's original data or expanded data with one-third more source data.
-The results from models including measurement error for outcome, key independent and control variables again justify the importance of incorporating uncertainty in analysis.
+The results from models including measurement error for outcome, key independent, and control variables again justify the importance of incorporating uncertainty in analyses.
 

### 2021-08-14 paper/dcpo_demsupport.Rmd
add dcpo description in Appendix

@@
 
-# Appendix C: The Method of Composition {#moc}
+# Appendix B: The Method of Composition {#moc}
 
@@
 
-# Appendix D: Secondary Models from Claassen (2020$a$, 2020$b$)
+# Appendix C: Secondary Models from Claassen (2020$a$, 2020$b$)
 
@@
 
-# Appendix B: DCPO Replication {#dcpo}
+# Appendix D: DCPO Replication {#dcpo}
 
@@
 
-We employed the superior DCPO model to the expanded data using the `DCPO` package for R [@Solt2020b].
+We employ the superior DCPO model to the expanded data using the `DCPO` package for R [@Solt2020b].
+We use the estimated public support from DCPO model to replicate analyses by following the same steps.
+Then, we compare the DCPO results with two types of replication results from Model 5: estimation of original data and without uncertainty and estimation of expanded data and with uncertainty.
+
+The comparison is presented in Appendix B.
+Still, even with the superior DCPO model and expanded data, there is no evidence to support that public support can sustain democratic development or public support responds thermostatically to changes in democracy.
 

### 2021-08-14 paper/dcpo_demsupport.Rmd
revise abstract, revise text up to #Results

--- 2021-08-13 paper/dcpo_demsupport.Rmd
@@
 
-title: "Democracy, Public Support, and Measurement Uncertainty"
-thanks: "The authors contributed equally to this work.  Corresponding author: [yuehu@mail.tsinghua.edu.cn](mailto:yuehu@mail.tsinghua.edu.cn).  Current version: `r format(Sys.time(), '%B %d, %Y')`."
+title: |
+  | Democracy, Public Support, 
+  | and Measurement Uncertainty
+# thanks: "The authors contributed equally to this work.  Corresponding author: [yuehu@mail.tsinghua.edu.cn](mailto:yuehu@mail.tsinghua.edu.cn).  Current version: `r format(Sys.time(), '%B %d, %Y')`."
 
@@
 But such approaches come with concomitant measurement uncertainty, and neither study incorporated this uncertainty into its analyses.
-In this letter, we correctly take this uncertainty in account and show that there is no support for the conclusion of either study.
-We then work to minimize the measurement uncertainty in public support by bringing additional survey data and a superior model of public opinion.
-Even with these improvements, however, our analyses fail to yield evidence in support of either hypothesis, underscoring the necessity of accounting for measurement uncertainty.
-[149/150 words]"
-keywords: "Democratization, public support, regime survival, measurement uncertainty, IRT."
+In this letter, we correctly take measurement uncertainty in account and show that there is no support for the conclusion of either study.
+We then work to minimize the measurement uncertainty in public support by incorporating additional survey data.
+Even with this expanded evidentiary base, however, our analyses fail to yield evidence in support of either hypothesis, underscoring the necessity of accounting for measurement uncertainty.
+[144/150 words]"
+keywords: "Democratization, public support, regime survival, measurement uncertainty, latent variables"
 
@@
 Second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.
+As democracy is also a latent variable in these analyses, we include the uncertainty in its estimates as well, along with that for corruption in the second analysis of @Claassen2020b.
 In the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.
 
-_It is worth to note that, despite the great effort of collecting data and identifying differences, we could not reach a completely primary replication of @Claassen2020a's Dataverse materials.
-Specifically, we have five fewer observations, three of which are no longer available in original survey data and two seem to have never existed, and one more survey item which was conflated in original data.
-(See more details in Online Supplementary Material \@ref(dgp).)
-Nevertheless, given there are over 2000 observations involved in the analysis, the five missing should not make a meaningful difference._
-
 ## Incorporating Uncertainty
 
-Although measurement uncertainty has yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can both attenuate or exaggerate coefficient estimates as well as bias standard errors [see, e.g., @Blackwell2017, 318-319; @Blackwell2017a, 360-361].
+Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can both attenuate or exaggerate coefficient estimates as well as bias standard errors [see, e.g., @Blackwell2017, 318-319; @Blackwell2017a, 360-361; @caughey2018, 254].
 In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey2018, 254].
 Following this line, after replicating the original analyses with point estimates, we incorporate uncertainty in analysis models using our replication data.
-We conduct inferences from the distributive data via a technique known as the "method of composition" (MOC) [@Tanner1993, 52; @Treier2008, 215; @caughey2018, A15-16].
-See more details of the method and the operational process in Online Appendix C.
+We conduct inferences from the distributive data via the technique known as the "method of composition" [@Tanner1993, 52; @Treier2008, 215; @caughey2018, A15-16].
+See more details of the method and the operational process in the Supplementary Materials.
 
@@
 
-As a further test of the classic arguments on democracy and public support, we generated estimates of democratic support using the same procedure as in Claassen [-@Claassen2020a; -@Claassen2020b] on a bigger data set,  assembling as much survey data on democratic support as possible.
+To provide a further test of the classic arguments on democracy and public support, we generated estimates of democratic support using the same procedure as in Claassen [-@Claassen2020a; -@Claassen2020b] on a bigger data set, assembling as much survey data on democratic support as possible.
 We employed `r dcpo_input_ncyi` national opinions on democracy from `r dcpo_input_surv` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncy` opinions and `r supdem_surv` national surveys used in Claassen [-@Claassen2020a; -@Claassen2020b].^[These figures represent the survey data actually used in estimating public support for democracy; as in Claassen [-@Claassen2020a; -@Claassen2020b], countries for which two separate years of survey data were not available were excluded.]
@@
 The middle results introduce a single change: the uncertainty in the measurement of public support is taken into account.
-In both models, the positive coefficients for democratic support are no longer statistically significant.
-The uppermost set of results replicate @Claassen2020a without uncertainty.
-The middle results introduce the uncertainty in the measurement of public support and democracy indices into the model.
-And the lowermost set presents the results estimated with the expanded data with uncertainty.
-
-In comparison to the original result, the positive coefficients for democratic support in both models accounting for the uncertainty are no longer statistically significant.
+<!-- In both models, the positive coefficients for democratic support are no longer statistically significant. -->
+The bottom results also incorporate uncertainty but additionally replace the estimates of democratic support with those based on the expanded dataset; this change works to increase the number of observations analyzed as well.
+<!-- Although the confidence intervals shrink considerably, the coefficient estimates move much closer to zero; the hypothesis remains unsupported.  -->
+
+_In comparison to the original result, the positive coefficients for democratic support in both models accounting for the uncertainty are no longer statistically significant.
 This result is robust when using separated regime types in the explanatory variable. 
-Nor do applying system GMM models or controlling for corruption alter the conclusion (see Online Supplementary Material \@ref(moc) for the the result of the full-pack analyses).
+Nor do applying system GMM models or controlling for corruption alter the conclusion (see the Supplementary Materials)._
 
@@
 
-# Data Recollection and Uncertainty in Control Variables {#dgp}
+# Supplementary Appendix A: Data Recollection and Uncertainty in Control Variables {#dgp}
 
@@
 
-# Appendix B: DCPO Replication {#dcpo}
+# Supplementary Appendix B: DCPO Replication {#dcpo}
 
@@
 
-# Appendix C: The Method of Composition {#moc}
+# Supplementary Appendix C: The Method of Composition {#moc}
 
@@
 
-# Appendix D: Secondary Models from Claassen (2020$a$, 2020$b$)
+# Supplementary Appendix D: Secondary Models from Claassen (2020$a$, 2020$b$)
 

### 2021-08-14 paper/dcpo_demsupport.Rmd

--- 2021-08-14 paper/dcpo_demsupport.Rmd
@@
 
-# Data Recollection and Uncertainty in Dependent and Control Variables {#dgp}
+# Supplementary Appendix A: Data Recollection and Uncertainty in Control Variables {#dgp}
 

### 2021-08-14 paper/memo/memo.Rmd

@@
 We followed MOC precedure and the results from MOC demonstrated that when uncertainty is allowed, the coefficients on public support and the change of democratic level are no longer distinguishable from zero on Figure 1 page 8 and Figure 2 page 9.
-The null results hold in robust check models and models with more control variables in Figure xx Page xx in Online Supplementary material.
+The null results hold in robust check models and models with more control variables in Appendix C in Online Supplementary material.
 
@@
 Thanks to editor's suggestion, we agree that we should present and assess the effect of intermediate modification in an incremental way, holding analytical transparency.
-To do this, in the revised manuscript, we focus on replication by only employing Claassen's measurement Model 5 to measure public support for democracy.
+To do this, in revised manuscript, we focus on replication by only employing Claassen's measurement Model 5 to measure public support for democracy.
+We take DCPO results as a robust check and discuss it in Appendix.
 

### 2021-08-14 paper/memo/response_memo.Rmd
responses on #16 (error in all vars), #17 & #23 (method of composition), #18 & #20 (no DCPO), #25 (more data), #24 (coef of lagged support), #22 (all models)

@@
 Thank you for your helpful comments, as well as your general enthusiasm for this piece.
-As you will see below, the reviews were each very constructive individually---and together usually so, as concerns raised by one review were often met by suggestions made in another.
+As you will see below, the reviews were each very constructive individually---and together usually so, as concerns raised by one review were often met by suggestions offered in another.
 Collectively, the reviews motivated us to ensure the piece, as a letter manuscript, was tightly focused on its twin main points: that, in general, researchers working with latent variables must take care to include in their analyses the uncertainty in these measures, and, specifically, taking uncertainty into account reveals that there is no evidence for the assertions that democracies' fates depend on public support and that their publics will rally to them if they are weakened.
-Indeed, your comments (and those of the editor) gave us the courage to be truly ruthless in stripping out any and all extraneous material that distracted from these crucial points.
+Indeed, your comments (and those of the editor) gave us the courage to be truly ruthless in stripping out any and all extraneous material that distracted from these two crucial points.
 
@@
 1.
-**Method: Incorporating Uncertainty** Reviewer 1 and Reviewer 2 both raised the question of whether the approach for incorporating uncertainty we employed was the most appropriate for this application.
-Although Reviewer 2 correctly noted that that approach is the same explicated by @Blackwell2017, [they](https://public.oed.com/blog/a-brief-history-of-singular-they/) also suggested we use the Method of Composition (MOC) that was first put forward by @Tanner1993 and introduced to political science by @Treier2008.
-As the MOC has become the standard method used to incorporate uncertainty in the subnational comparative public opinion literature using Multilevel Regression and Poststratification [see, e.g., @Kastellec2015; @caughey2018], we were pleased to adopt this suggestion.
-Further, to help ensure that incorporating uncertainty is as easy as possible for those working with latent variables of cross-national public opinion, we are including in our replication materials a suite of R functions implementing the MOC that are tailored to this application.
+**Method** A key omission in our original submission, given our goal of underscoring the "absolute necessity" of taking quantified measurement error into account, is that we ourselves neglected the measurement error in the V-Dem democracy data and the Transparency International corruption data.
+We are extremely grateful to R1 and R2 for alerting us to the beam in our own eye while we still had opportunity to pluck it out.
 
 1.
+**Method: Incorporating Uncertainty** R1 and R2 both raised the question of whether the approach for incorporating uncertainty we employed was the most appropriate for this application, and R4 asked for additional detail on how uncertainty was incorporated.
+Although R2 correctly (and helpfully!) noted that the approach we had employed is the same one explicated by @Blackwell2017, [they](https://public.oed.com/blog/a-brief-history-of-singular-they/) also suggested we use the Method of Composition (MOC) that was first put forward by @Tanner1993 and introduced to political science by @Treier2008.
+As this technique has become the standard method for incorporating uncertainty in the Americanist literature using Multilevel Regression and Poststratification [see, e.g., @Kastellec2015; @caughey2018], which is after all also a latent variable model of public opinion, we were pleased to adopt this suggestion.
+We provide a full description of the MOC technique in the Supplementary Materials.
+Further, to help ensure that incorporating uncertainty is as easy as possible for scholars working with latent variables of cross-national public opinion, we are including in our replication materials a suite of R functions implementing the MOC that are tailored to this application.
+
+1.
+**Method: ~~Better Estimates of Public Support and More Data~~ Adding Data** R1 and R4 asked for more detail on the differences between the DCPO model and the latent variable model used by Claassen.
+R2 indirectly raised the same issue, asking about the consequences for thermostatic models of employing a random-walk prior in the DCPO model of democratic support---when actually both DCPO and the Claassen model use the same random-walk prior.
+Given that the DCPO model's advantages ultimately do not have a payoff in this case, we concluded that its inclusion in this 4000-word letter is an unnecessary distraction from our main points.
+So we took the _other_ suggestion from R1 on this topic to simply drop DCPO from the text entirely and moved the analyses with the DCPO estimates to the Supplementary Materials.
+
+1.
+**Method: Adding Data** Not directly related to a specific comment, but the opportunity to revise and resubmit allowed us to incorporate even more survey data that was released since our original submission (most notably from the ongoing release of Wave 7 of the World Values Survey).
+
+1.
+**Results** R1 and R2 expressed concern about the results of the models of democratic support presented in Figure 2, and specifically that the coefficients for the lags of democratic support in the models incorporating uncertainty were approximately zero.
+R1 wrote, "The effects of lagged democratic support are also zero, which is even more implausible because it suggests that democratic support in one year is entirely disconnected from its levels in previous years.
+In other words, Denmark is as likely to have a low value next year as China is likely to have a high value."
+R2 summarized the issue even more pithily, "some explanation is required, or else readers will think that some mistake has been made."
+The explanation is that the analyses from @Claassen2020b are error correction models, and so the dependent variable is not the level of democratic support but the _change_ in democratic support; in other words, the mistake was that our caption to the figure was badly misleading, and there was nothing in our discussion to bring readers back on track.
+It is not the case that Denmark is as likely to have a low value as China is to have a high one, but rather that Denmark is as likely to have a decline as China is to have a gain.
+We have labeled the plot correctly now.
+These results, we note, give grounds for R2's concern for random-walk priors in latent variable models of public opinion when the estimates are then used in  thermostatic models: much of the year-to-year change in democratic support is simply random---only 44% of the country-years in Claassen's sample are estimated from survey data, leaving most with only the prior---so it is not surprising that these changes are not well predicted by the variables in Claassen's model.
+Ignoring the uncertainty in the estimates averages away this randomness and may, as here, yield conclusions that cannot be supported.
+
+1.
+**Results** R1 noted that in addition to the pooled OLS models we present in Figure 1 and the ECMs we present in Figure 2, @Claassen2020a includes a pair of system GMM models and @Claassen2020b includes a pair of first-difference models.
+We include the results of our three-tiered replication and extension for Claassen's secondary models in the Supplementary Materials; these additional analyses yield the same substantive conclusions as those we present in the text.
+
+[need #15, #19, #21]
 

### 2021-08-14 paper/memo/response_memo.Rmd
fuss

@@
 Thank you for your helpful comments, as well as your general enthusiasm for this piece.
-As you will see below, the reviews were each very constructive individually---and together usually so, as concerns raised by one review were often met by suggestions offered in another.
+As you will see below, the reviews were each individually very constructive---and together usually so, as concerns raised by one review were often met by suggestions offered in another.
 Collectively, the reviews motivated us to ensure the piece, as a letter manuscript, was tightly focused on its twin main points: that, in general, researchers working with latent variables must take care to include in their analyses the uncertainty in these measures, and, specifically, taking uncertainty into account reveals that there is no evidence for the assertions that democracies' fates depend on public support and that their publics will rally to them if they are weakened.
@@
 1.
-**Method: Incorporating Uncertainty** R1 and R2 both raised the question of whether the approach for incorporating uncertainty we employed was the most appropriate for this application, and R4 asked for additional detail on how uncertainty was incorporated.
+**Method: Incorporating Uncertainty** R1 and R2 both raised the question of whether the approach for incorporating uncertainty we used was the most appropriate for this application, and R4 asked for additional detail on how uncertainty was incorporated.
 Although R2 correctly (and helpfully!) noted that the approach we had employed is the same one explicated by @Blackwell2017, [they](https://public.oed.com/blog/a-brief-history-of-singular-they/) also suggested we use the Method of Composition (MOC) that was first put forward by @Tanner1993 and introduced to political science by @Treier2008.
@@
 **Method: Adding Data** Not directly related to a specific comment, but the opportunity to revise and resubmit allowed us to incorporate even more survey data that was released since our original submission (most notably from the ongoing release of Wave 7 of the World Values Survey).
+Thanks!
 
 1.
-**Results** R1 and R2 expressed concern about the results of the models of democratic support presented in Figure 2, and specifically that the coefficients for the lags of democratic support in the models incorporating uncertainty were approximately zero.
+**Results** R1 and R2 expressed concern about the results of the models of democratic support presented in Figure 2, and especially that the coefficients for the lags of democratic support in the models incorporating uncertainty were approximately zero.
 R1 wrote, "The effects of lagged democratic support are also zero, which is even more implausible because it suggests that democratic support in one year is entirely disconnected from its levels in previous years.
@@
 R2 summarized the issue even more pithily, "some explanation is required, or else readers will think that some mistake has been made."
-The explanation is that the analyses from @Claassen2020b are error correction models, and so the dependent variable is not the level of democratic support but the _change_ in democratic support; in other words, the mistake was that our caption to the figure was badly misleading, and there was nothing in our discussion to bring readers back on track.
-It is not the case that Denmark is as likely to have a low value as China is to have a high one, but rather that Denmark is as likely to have a decline as China is to have a gain.
+The explanation is that the analyses from @Claassen2020b are error correction models, and so the dependent variable is not the level of democratic support but the _change_ in democratic support; in other words, the mistake was that our captioning to the figure was badly misleading (it read simply, "DV: Public Support for Democracy" and "The Effect of Democracy on Public Support"), and there was nothing in our discussion to bring readers back on track.
+So: it is not the case that Denmark is as likely to have a low value as China is to have a high one, but rather that Denmark is as likely to have a decline as China is to have a gain.
 We have labeled the plot correctly now.
-These results, we note, give grounds for R2's concern for random-walk priors in latent variable models of public opinion when the estimates are then used in  thermostatic models: much of the year-to-year change in democratic support is simply random---only 44% of the country-years in Claassen's sample are estimated from survey data, leaving most with only the prior---so it is not surprising that these changes are not well predicted by the variables in Claassen's model.
+These results, we note, give further grounds for R2's concern about random-walk priors in latent variable models of public opinion when the estimates are then used in  thermostatic models: much of the year-to-year change in democratic support is simply random---only 44% of the country-years in Claassen's sample are estimated from survey data, leaving most with only the prior---so it is not surprising that these changes are not well predicted by the variables in Claassen's model.
 Ignoring the uncertainty in the estimates averages away this randomness and may, as here, yield conclusions that cannot be supported.

### 2021-08-15 paper/memo/response_memo.Rmd
response on #15

@@
 1.
+**Method: Incorporating Uncertainty** R4 suggested that it would be helpful to provide citations for the point that neglecting to include uncertainty can bias coefficients along with standard errors.
+We agree and so drop cites here to @Blackwell2017 [, 318-319] and @Blackwell2017a [, 360-361], who present simulations that, while aimed at other issues, nonetheless illustrate the point neatly.
+We also cite to @caughey2018 [, 254], who, like others familiar with the problem, simply state the fact and move on.
+
+1.
 **Method: ~~Better Estimates of Public Support and More Data~~ Adding Data** R1 and R4 asked for more detail on the differences between the DCPO model and the latent variable model used by Claassen.
@@
 **Method: Adding Data** Not directly related to a specific comment, but the opportunity to revise and resubmit allowed us to incorporate even more survey data that was released since our original submission (most notably from the ongoing release of Wave 7 of the World Values Survey).
-Thanks!
+Thanks again!
 
@@
 
-[need #15, #19, #21]
+[need #19, #21]
 

### 2021-08-15 paper/dcpo_demsupport.Rmd
fuss

@@
 51].
-Both of these assertions may well be true, but the evidence we have, properly assessed, does not provide support for them.
+Both of these assertions may well be true, but the evidence we have, properly assessed, does not support them.
 There is no room for complacency.
@@
 In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey2018, 254].
-Following this line, after replicating the original analyses with point estimates, we incorporate uncertainty in analysis models using our replication data.
+
+Therefore, after replicating the original analyses that use only the point estimates for public support and the other variables included in the model, we perform the analyses again only this time incorporating uncertainty in analysis models using our replication data.
 We conduct inferences from the distributive data via the technique known as the "method of composition" [@Tanner1993, 52; @Treier2008, 215; @caughey2018, A15-16].
-See more details of the method and the operational process in the Supplementary Materials.
+For additional detail on this technique, see the Supplementary Materials.
 
@@
 
-## Adding Data
+## Adding More Data
 

### 2021-08-15 R/apsr_plots.R
initial commit

@@ -1,0 +1,443 @@
+
+```{r formatResult-APSR-dup}
+# Pooled---------------------------------------
+
+result_ecm1 <- bind_rows(
+    mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], submodel = "Original"),
+    mutate(MOCsumm2(mocresult_correctAPSR[["pooled1"]]), submodel = "Uncertainty"),
+    mutate(MOCsumm2(mocresult_expAPSR[["pooled1"]]), submodel = "Uncertainty & More Data")
+) %>% 
+    mutate(type = "Error-Correction Model",
+           model = "Model 1.1")
+
+
+result_fd1 <- bind_rows(
+    mutate(result_clsAPSR[["fd1"]][[1]][,1:3], submodel = "Original"),
+    mutate(MOCsumm2(mocresult_correctAPSR[["fd1"]]), submodel = "Uncertainty"),
+    mutate(MOCsumm2(mocresult_expAPSR[["fd1"]]), submodel = "Uncertainty & More Data")
+) %>% 
+    mutate(type = "First-Difference Model",
+           model = "Model 1.3")
+
+result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
+    filter(term != "(Intercept)") %>%
+    mutate(
+        term0 = c(rep(
+            c("Democratic Mood\n (t-1)",
+              "Democratic Mood\n (t-2)",
+              "Liberal Democracy\n (Difference)",
+              "Liberal Democracy\n (t-1)",
+              "Log GDP\n per capita\n (Difference)",
+              "Log GDP\n (t-1)"),
+            time = 3),
+            rep(
+                c("Liberal Democracy\n (Difference)", 
+                  "Log GDP\n per capita\n (Difference)"), 
+                time = 3
+            )),
+        type = factor(type,  levels = c("Error-Correction Model", "First-Difference Model")),
+        submodel = factor(submodel, levels = c("Original","Uncertainty", "Uncertainty & More Data")),
+        model = factor(model, levels = paste0("Model ", rep(1:2, each = 4), ".", rep(1:4, 2)))
+    )
+
+# result_apsrPooled <- result_APSR1 %>% 
+#     filter(type == "Error-Correction Model") %>% 
+#     mutate(type = "Pooled")
+
+
+
+# Institution----------------------------------
+
+result_ecmReg1 <- bind_rows(
[…]

### 2021-08-15 R/apsr_plots.R
include all models; label models by type

@@ -8,7 +8,7 @@ result_ecm1 <- bind_rows(
     mutate(MOCsumm2(mocresult_expAPSR[["pooled1"]]), submodel = "Uncertainty & More Data")
 ) %>% 
     mutate(type = "Error-Correction Model",
-           model = "Model 1.1")
+           model = "Model 1.1 (ECM)")
 
 
 result_fd1 <- bind_rows(
@@ -17,7 +17,7 @@ result_fd1 <- bind_rows(
     mutate(MOCsumm2(mocresult_expAPSR[["fd1"]]), submodel = "Uncertainty & More Data")
 ) %>% 
     mutate(type = "First-Difference Model",
-           model = "Model 1.3")
+           model = "Model 1.3 (FD)")
 
 result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
     filter(term != "(Intercept)") %>%
@@ -37,7 +37,11 @@ result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
             )),
         type = factor(type,  levels = c("Error-Correction Model", "First-Difference Model")),
         submodel = factor(submodel, levels = c("Original","Uncertainty", "Uncertainty & More Data")),
-        model = factor(model, levels = paste0("Model ", rep(1:2, each = 4), ".", rep(1:4, 2)))
+        model = factor(model, levels = paste0("Model ", 
+                                              rep(1:2, each = 4), ".", rep(1:4, 2),
+                                              " (",
+                                              rep(c("ECM", "ECM", "FD", "FD"), 2),
+                                              ")"))
     )
 
 # result_apsrPooled <- result_APSR1 %>% 
@@ -54,7 +58,7 @@ result_ecmReg1 <- bind_rows(
     mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime1"]]), submodel = "Uncertainty & More Data")
 ) %>% 
     mutate(type = "Error-Correction Model",
-           model = "Model 2.1")
+           model = "Model 2.1 (ECM)")
 
 
 result_fdReg1 <- bind_rows(
@@ -63,7 +67,7 @@ result_fdReg1 <- bind_rows(
     mutate(MOCsumm2(mocresult_expAPSR[["fd-regime1"]]), submodel = "Uncertainty & More Data")
 ) %>% 
     mutate(type = "First-Difference Model",
-           model = "Model 2.3")
+           model = "Model 2.3 (FD)")
 
 
[…]

### 2021-08-15 paper/dcpo_demsupport.Rmd
include dotwhisker::small_multiple() hacks

@@
 
-# Theme setup
-theme_set(theme_minimal())
+# dotwhisker::small_multiple() hacks
+body(small_multiple)[[17]] <- substitute(
+    p <- ggplot(df, aes(y = estimate, ymin = conf.low, ymax = conf.high, 
+                        x = as.factor(model), colour = submodel)) +
+        do.call(geom_pointrange, point_args) + ylab("") + xlab("") + 
+        facet_grid(term ~ .,
+                   scales = "free_y",
+                   labeller = label_parsed,    # enable LaTeX facet labels
+                   switch = "y") +             # put facet labels on left
+        scale_y_continuous(position = "right") # put axis label on right
+)
 ```

### 2021-08-15 R/ajps_plots.R
initial commit

@@ -1,0 +1,114 @@
+```{r formatResult-AJPS-dup}
+result_pooled <- bind_rows(
+    mutate(result_clsAJPS[["pooled"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(MOCsumm(mocresult_correctAJPS[["pooled"]]), submodel = "With Uncertainty"),
+    mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), submodel = "Uncertainty & Expanded Data")
+) %>% 
+    mutate(type = "Pooled OLS",
+           model = "Model 1 (Pooled OLS)")
+
+
+result_gmm <- bind_rows(
+    mutate(result_clsAJPS[["gmm"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(MOCsumm(mocresult_correctAJPS[["gmm"]]), submodel = "With Uncertainty"),
+    mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), submodel = "Uncertainty & Expanded Data")
+) %>% 
+    mutate(type = "System GMM",
+           model = "Model 3 (System GMM)")
+
+result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
+    filter(term != "(Intercept)") %>%
+    mutate(
+        term0 = rep(
+            c("Democracy\n (t-1)",
+              "Democracy\n (t-2)",
+              "Support\n (t-1)",
+              "Log GDP\n per capita\n (t-1)",
+              "GDP per\n capita growth\n (t-1)",
+              "Regional\n democracy\n (t-1)",
+              "Percent\n Muslim\n (t-1)",
+              "Resource\n dependence\n (t-1)"),
+            time = 6), 
+        type = factor(type, levels = c("Pooled OLS", "System GMM")),
+        submodel = factor(submodel, levels = c("Point Estimates Only", "With Uncertainty", "Uncertainty & Expanded Data")),
+        model = factor(model, levels = paste0("Model ", rep(1:4), rep(c(" (Pooled OLS)", " (System GMM)"), each = 2)))
+    )
+
+
+
+result_regime <- bind_rows(
+    mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(MOCsumm(mocresult_correctAJPS[["pooled-regime"]]), submodel = "With Uncertainty"),
[…]

### 2021-08-16 paper/dcpo_demsupport.Rmd
use dotwhisker::small_multiple() to display AJPS results

--- 2021-08-15 paper/dcpo_demsupport.Rmd
@@
 
-# Theme setup
-theme_set(theme_minimal())
+# dotwhisker::small_multiple() hacks
+body(small_multiple)[[17]] <- substitute(
+  p <- ggplot(df, aes(y = estimate, ymin = conf.low, ymax = conf.high, 
+                      x = as.factor(model), colour = submodel)) +
+    do.call(geom_pointrange, point_args) + 
+    ylab("") + xlab("") + 
+    facet_grid(term ~ .,
+               scales = "free",
+               labeller = label_parsed,    # enable LaTeX facet labels
+               switch = "y") +             # put facet labels on left
+    scale_y_continuous(position = "right") # put axis label on right
+)
 ```
@@
 result_pooled <- bind_rows(
-  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Original"),
- mutate(MOCsumm(mocresult_correctAJPS[["pooled"]]), model = "W. Uncertainty"),
- mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), model = "Uncertainty+Expanded Data")
-) %>% 
-  mutate(type = "Pooled")
+    mutate(result_clsAJPS[["pooled"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(MOCsumm(mocresult_correctAJPS[["pooled"]]), submodel = "With Uncertainty"),
+    mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), submodel = "Uncertainty & More Data")
+) %>% 
+    mutate(type = "Pooled~OLS",
+           model = "Model 1 (Pooled OLS)")
 
 result_gmm <- bind_rows(
-  mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_correctAJPS[["gmm"]]), model = "W. Uncertainty"),
-  mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), model = "Uncertainty+Expanded Data")
-) %>% 
-  mutate(type = "GMM")
+    mutate(result_clsAJPS[["gmm"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(MOCsumm(mocresult_correctAJPS[["gmm"]]), submodel = "With Uncertainty"),
+    mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), submodel = "Uncertainty & More Data")
+) %>% 
+    mutate(type = "System~GMM",
+           model = "Model 3 (System GMM)")
 
@@
     mutate(
-    term = rep(
+        term0 = rep(
             c("Democracy\n (t-1)",
@@
             time = 6), 
-    type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Original", "W. Uncertainty", "Uncertainty+Expanded Data")))
-
-result_ajpsPooled <- result_pooledAJPS %>% 
-    filter(type == "Pooled")
+        type = factor(type, levels = c("Pooled~OLS", "System~GMM")),
+        submodel = factor(submodel, levels = c("Point Estimates Only", "With Uncertainty", "Uncertainty & More Data")),
+        model = factor(model, levels = paste0("Model ", rep(1:4), rep(c(" (Pooled OLS)", " (System GMM)"), each = 2)))
+    )
 
 result_regime <- bind_rows(
-  mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_correctAJPS[["pooled-regime"]]), model = "W. Uncertainty"),
-  mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), model = "Uncertainty+Expanded Data")
-) %>% 
-  mutate(type = "Pooled")
+    mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(MOCsumm(mocresult_correctAJPS[["pooled-regime"]]), submodel = "With Uncertainty"),
+    mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), submodel = "Uncertainty & More Data")
+) %>% 
+    mutate(type = "Pooled~OLS",
+           model = "Model 2 (Pooled OLS)")
 
 result_regimeGmm <- bind_rows(
-  mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_correctAJPS[["gmm-regime"]]), model = "W. Uncertainty"),
- mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), model = "Uncertainty+Expanded Data")
+    mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(MOCsumm(mocresult_correctAJPS[["gmm-regime"]]), submodel = "With Uncertainty"),
+    mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), submodel = "Uncertainty & More Data")
 )%>% 
-  mutate(type = "GMM")
+    mutate(type = "System~GMM",
+           model = "Model 4 (System GMM)")
 
@@
             time = 6), 
-    type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data")))
-
-result_ajpsRegime <- result_regimeAJPS %>%
-    filter(type == "Pooled") %>% 
-    mutate(type = "Regime Specified")
-
-```
-
-```{r coefName-AJPS}
-index_coefName <- c(
-    `Democracy\n (t-1)` = "Democracy[t-1]",
-    `Democracy\n (t-2)` = "Democracy[t-2]",
-    `Support\n (t-1)` = "Support[t-1]",
-    `Support\n demo only\n (t-1)` = "Support[t-1](demo~only)",
-    `Support\n auto only\n (t-1)` = "Support[t-1](auto~only)",
-    `Log GDP\n per capita\n (t-1)` = "Log~GDP~per~capita[t-1]",
-    `GDP per\n capita growth\n (t-1)` = "GDP~per~capita~growth[t-1]",
-    `Regional\n democracy\n (t-1)` = "Regional~democracy[t-1]",
-    `Percent\n Muslim\n (t-1)` = "Percent~Muslim[t-1]",
-    `Resource\n dependence\n (t-1)` = "Resource~dependence[t-1]"
-)
-```
-
-```{r plot-mainAJPS, fig.cap= "The Effect of Public Support on Democracy with Uncertainty", fig.width=7, fig.height=10, fig.align='center'}
-
-type_model <-
-  c("Original", "W. Uncertainty", "Uncertainty+Expanded Data")
-
-df_plot <- bind_rows(result_ajpsPooled, result_ajpsRegime) %>% 
-    mutate(term = index_coefName[term],
-           term = factor(term, levels = unique(index_coefName)))
-
-dwplot(df_plot) +
-    geom_vline(xintercept = 0,
-               colour = "grey80",
-               linetype = 2) +
-    theme_minimal() +
-    ggtitle("DV: Liberal Democracy (Vdem)") +
-    xlab("Coefficient Estimate") +
-    theme(
-        axis.title.y = element_blank(),
-        legend.position = "bottom",
-      legend.title = element_blank()
-    ) +
-    scale_color_gb(palette = "digitMixed") +
-    facet_wrap(~ type)
+        type = factor(type, levels = c("Pooled~OLS", "System~GMM")),
+        submodel = factor(submodel, levels = c("Point Estimates Only","With Uncertainty", "Uncertainty & More Data")),
+        model = factor(model, levels = paste0("Model ", rep(1:4), rep(c(" (Pooled OLS)", " (System GMM)"), each = 2))))
+
+```
+
+# ```{r coefName-AJPS}
+# index_coefName <- c(
+#     `Democracy\n (t-1)` = "Democracy[t-1]",
+#     `Democracy\n (t-2)` = "Democracy[t-2]",
+#     `Support\n (t-1)` = "Support[t-1]",
+#     `Support\n demo only\n (t-1)` = "Support[t-1](demo~only)",
+#     `Support\n auto only\n (t-1)` = "Support[t-1](auto~only)",
+#     `Log GDP\n per capita\n (t-1)` = "Log~GDP~per~capita[t-1]",
+#     `GDP per\n capita growth\n (t-1)` = "GDP~per~capita~growth[t-1]",
+#     `Regional\n democracy\n (t-1)` = "Regional~democracy[t-1]",
+#     `Percent\n Muslim\n (t-1)` = "Percent~Muslim[t-1]",
+#     `Resource\n dependence\n (t-1)` = "Resource~dependence[t-1]"
+# )
+# ```
+
+```{r plot-mainAJPS, fig.cap= "The Effect of Public Support on Democracy with Uncertainty", fig.width=5, fig.height=10, fig.align='center'}
+
+df_plot <- bind_rows(result_pooledAJPS, result_regimeAJPS) %>% 
+    mutate(term = case_when(term0 == 'Democracy\n (t-1)' ~ "Democracy[t-1]",
+                            term0 == 'Democracy\n (t-2)' ~ "Democracy[t-2]",
+                            term0 == 'Support\n (t-1)' ~ "Democratic~Support[t-1]",
+                            term0 == 'Support\n demo only\n (t-1)' ~ "Democratic~Support[t-1]~(democracies)",
+                            term0 == 'Support\n auto only\n (t-1)' ~ "Democratic~Support[t-1]~(autocracies)",
+                            term0 == 'Log GDP\n per capita\n (t-1)' ~ "Log~GDP~per~capita[t-1]",
+                            term0 == 'GDP per\n capita growth\n (t-1)' ~ "GDP~per~capita~growth[t-1]",
+                            term0 == 'Regional\n democracy\n (t-1)' ~ "Regional~Democracy[t-1]",
+                            term0 == 'Percent\n Muslim\n (t-1)' ~ "Percent~Muslim[t-1]",
+                            term0 == 'Resource\n dependence\n (t-1)' ~ "Resource~Dependence[t-1]",
+                            TRUE ~ str_replace(term0, " ", "~")), 
+           term = factor(term, levels =  c(
+               "Democracy[t-1]",
+               "Democracy[t-2]",
+               "Democratic~Support[t-1]",
+               "Democratic~Support[t-1]~(democracies)",
+               "Democratic~Support[t-1]~(autocracies)",
+               "Log~GDP~per~capita[t-1]",
+               "GDP~per~capita~growth[t-1]",
+               "Regional~Democracy[t-1]",
+               "Percent~Muslim[t-1]",
+               "Resource~Dependence[t-1]")))
+
+small_multiple(df_plot, dot_args = list(size = .9, fatten = 1)) +
+    theme_bw() +
+    geom_hline(yintercept = 0, colour = "grey50", linetype = 2) +
+    scale_color_grey(start = 0.8, end = 0.4, 
+                     name = "Replication",
+                     breaks=c("Point Estimates Only", "With Uncertainty", "Uncertainty & More Data"),
+                     labels=c("Point Estimates Only", "With Uncertainty", "Uncertainty & More Data")) +
+    theme(axis.text.x  = element_text(angle = 90, hjust = .5),
+          strip.text.y.left = element_text(angle = 0),
+          legend.position = c(-0.115, -.01),
+          legend.justification = c(1, 1), 
+          legend.title = element_text(size = 9, face = "bold"),
+          legend.title.align = 0.5,
+          legend.text = element_text(size = 9),
+          legend.background = element_rect(color="gray90"),
+          legend.spacing = unit(-3, "pt"),
+          legend.key.size = unit(9, "mm"))
 
@@
 
-result_ajpsPooled <- result_pooledAJPS %>% 
-    filter(type == "Pooled")
-
 result_regime <- bind_rows(

### 2021-08-16 paper/dcpo_demsupport.Rmd
use dotwhisker::small_multiple for APSR plot (but legend); add title to AJPS plot; clean up

@@
 
-# ```{r coefName-AJPS}
-# index_coefName <- c(
-#     `Democracy\n (t-1)` = "Democracy[t-1]",
-#     `Democracy\n (t-2)` = "Democracy[t-2]",
-#     `Support\n (t-1)` = "Support[t-1]",
-#     `Support\n demo only\n (t-1)` = "Support[t-1](demo~only)",
-#     `Support\n auto only\n (t-1)` = "Support[t-1](auto~only)",
-#     `Log GDP\n per capita\n (t-1)` = "Log~GDP~per~capita[t-1]",
-#     `GDP per\n capita growth\n (t-1)` = "GDP~per~capita~growth[t-1]",
-#     `Regional\n democracy\n (t-1)` = "Regional~democracy[t-1]",
-#     `Percent\n Muslim\n (t-1)` = "Percent~Muslim[t-1]",
-#     `Resource\n dependence\n (t-1)` = "Resource~dependence[t-1]"
-# )
-# ```
+```{r coefName-AJPS}
+index_coefName <- c(
+    `Democracy\n (t-1)` = "Democracy[t-1]",
+    `Democracy\n (t-2)` = "Democracy[t-2]",
+    `Support\n (t-1)` = "Democratic~Support[t-1]",
+    `Support\n demo only\n (t-1)` = "Democratic~Support[t-1]~(democracies)",
+    `Support\n auto only\n (t-1)` = "Democratic~Support[t-1]~(autocracies)",
+    `Log GDP\n per capita\n (t-1)` = "Log~GDP~per~capita[t-1]",
+    `GDP per\n capita growth\n (t-1)` = "GDP~per~capita~Growth[t-1]",
+    `Regional\n democracy\n (t-1)` = "Regional~Democracy[t-1]",
+    `Percent\n Muslim\n (t-1)` = "Percent~Muslim[t-1]",
+    `Resource\n dependence\n (t-1)` = "Resource~Dependence[t-1]"
+)
+```
 
@@
 df_plot <- bind_rows(result_pooledAJPS, result_regimeAJPS) %>% 
-    mutate(term = case_when(term0 == 'Democracy\n (t-1)' ~ "Democracy[t-1]",
-                            term0 == 'Democracy\n (t-2)' ~ "Democracy[t-2]",
-                            term0 == 'Support\n (t-1)' ~ "Democratic~Support[t-1]",
-                            term0 == 'Support\n demo only\n (t-1)' ~ "Democratic~Support[t-1]~(democracies)",
-                            term0 == 'Support\n auto only\n (t-1)' ~ "Democratic~Support[t-1]~(autocracies)",
-                            term0 == 'Log GDP\n per capita\n (t-1)' ~ "Log~GDP~per~capita[t-1]",
-                            term0 == 'GDP per\n capita growth\n (t-1)' ~ "GDP~per~capita~growth[t-1]",
-                            term0 == 'Regional\n democracy\n (t-1)' ~ "Regional~Democracy[t-1]",
-                            term0 == 'Percent\n Muslim\n (t-1)' ~ "Percent~Muslim[t-1]",
-                            term0 == 'Resource\n dependence\n (t-1)' ~ "Resource~Dependence[t-1]",
-                            TRUE ~ str_replace(term0, " ", "~")), 
-           term = factor(term, levels =  c(
-               "Democracy[t-1]",
-               "Democracy[t-2]",
-               "Democratic~Support[t-1]",
-               "Democratic~Support[t-1]~(democracies)",
-               "Democratic~Support[t-1]~(autocracies)",
-               "Log~GDP~per~capita[t-1]",
-               "GDP~per~capita~growth[t-1]",
-               "Regional~Democracy[t-1]",
-               "Percent~Muslim[t-1]",
-               "Resource~Dependence[t-1]")))
+  mutate(term = index_coefName[term0], 
+           term = factor(term, levels = unique(index_coefName)))
 
@@
           legend.spacing = unit(-3, "pt"),
-          legend.key.size = unit(9, "mm"))
+          legend.key.size = unit(9, "mm")) +
+  ggtitle("DV: V-Dem Liberal Democracy Index")
 
@@
 ```{r formatResult-APSR}
+# Pooled---------------------------------------
+
+result_ecm1 <- bind_rows(
+    mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(MOCsumm2(mocresult_correctAPSR[["pooled1"]]), submodel = "With Uncertainty"),
+    mutate(MOCsumm2(mocresult_expAPSR[["pooled1"]]), submodel = "Uncertainty & More Data")
+) %>% 
+    mutate(type = "Error-Correction Model",
+           model = "Model 1.1 (ECM)")
+
+result_fd1 <- bind_rows(
+    mutate(result_clsAPSR[["fd1"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(MOCsumm2(mocresult_correctAPSR[["fd1"]]), submodel = "With Uncertainty"),
+    mutate(MOCsumm2(mocresult_expAPSR[["fd1"]]), submodel = "Uncertainty & More Data")
+) %>% 
+    mutate(type = "First-Difference Model",
+           model = "Model 1.3 (FD)")
+
+result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
+    filter(term != "(Intercept)") %>%
+    mutate(
+        term0 = c(rep(
+            c("Democratic Mood\n (t-1)",
+              "Democratic Mood\n (t-2)",
+              "Liberal Democracy\n (Difference)",
+              "Liberal Democracy\n (t-1)",
+              "Log GDP\n per capita\n (Difference)",
+              "Log GDP\n (t-1)"),
+            time = 3),
+            rep(
+                c("Liberal Democracy\n (Difference)", 
+                  "Log GDP\n per capita\n (Difference)"), 
+                time = 3
+            )),
+        type = factor(type,  levels = c("Error-Correction Model", "First-Difference Model")),
+        submodel = factor(submodel, levels = c("Point Estimates Only","With Uncertainty", "Uncertainty & More Data")),
+        model = factor(model, levels = paste0("Model ", 
+                                              rep(1:2, each = 4), ".", rep(1:4, 2),
+                                              " (",
+                                              rep(c("ECM", "ECM", "FD", "FD"), 2),
+                                              ")"))
+    )
+
+# result_apsrPooled <- result_APSR1 %>% 
+#     filter(type == "Error-Correction Model") %>% 
+#     mutate(type = "Pooled")
+
+# Institution----------------------------------
+
+result_ecmReg1 <- bind_rows(
+    mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime1"]]), submodel = "With Uncertainty"),
+    mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime1"]]), submodel = "Uncertainty & More Data")
+) %>% 
+    mutate(type = "Error-Correction Model",
+           model = "Model 2.1 (ECM)")
+
+result_fdReg1 <- bind_rows(
+    mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime1"]]), submodel = "With Uncertainty"),
+    mutate(MOCsumm2(mocresult_expAPSR[["fd-regime1"]]), submodel = "Uncertainty & More Data")
+) %>% 
+    mutate(type = "First-Difference Model",
+           model = "Model 2.3 (FD)")
+
+result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
+    filter(term != "(Intercept)") %>%
+    mutate(
+        term0 = c(rep(
+            c("Democratic Mood\n (t-1)",
+              "Democratic Mood\n (t-2)",
+              "Electoral Democracy\n (Difference)",
+              "Electoral Democracy\n (t-1)",
+              "Minoritarian Democracy\n (Difference)",
+              "Minoritarian Democracy\n (t-1)",
+              "Log GDP\n per capita\n (Difference)",
+              "Log GDP\n (t-1)"),
+            time = 3),
+            rep(
+                c("Electoral Democracy\n (Difference)", 
+                  "Minoritarian Democracy\n (Difference)",
+                  "Log GDP\n per capita\n (Difference)"), 
+                time = 3
+            )),
+        type = factor(type,  levels = c("Error-Correction Model", "First-Difference Model")),
+        submodel = factor(submodel, levels = c("Point Estimates Only","With Uncertainty", "Uncertainty & More Data")),
+        model = factor(model, levels = paste0("Model ", 
+                                              rep(1:2, each = 4), ".", rep(1:4, 2),
+                                              " (",
+                                              rep(c("ECM", "ECM", "FD", "FD"), 2),
+                                              ")"))
+    )
+
+# result_apsrRegime <- result_RegAPSR1 %>% 
+#     filter(type == "Error-Correction Model") %>% 
+#     mutate(type = "Institution Specified")
+
+# Pooled-corruption------------------------------
+
+result_ecm2 <- bind_rows(
+    mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(MOCsumm2(mocresult_correctAPSR[["pooled2"]]), submodel = "With Uncertainty"),
+    mutate(MOCsumm2(mocresult_expAPSR[["pooled2"]]), submodel = "Uncertainty & More Data")
+) %>% 
+    mutate(type = "Error-Correction Model",
+           model = "Model 1.2 (ECM)")
+
+result_fd2 <- bind_rows(
+    mutate(result_clsAPSR[["fd2"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(MOCsumm2(mocresult_correctAPSR[["fd2"]]), submodel = "With Uncertainty"),
+    mutate(MOCsumm2(mocresult_expAPSR[["fd2"]]), submodel = "Uncertainty & More Data")
+) %>% 
+    mutate(type = "First-Difference Model",
+           model = "Model 1.4 (FD)")
+
+result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
+    filter(term != "(Intercept)") %>%
+    mutate(
+        term0 = c(rep(
+            c("Democratic Mood\n (t-1)",
+              "Democratic Mood\n (t-2)",
+              "Liberal Democracy\n (Difference)",
+              "Liberal Democracy\n (t-1)",
+              "Log GDP\n per capita\n (Difference)",
+              "Log GDP\n (t-1)",
+              "Corruption\n (Difference)",
+              "Corruption\n (t-1)"
+            ),
+            time = 3),
+            rep(
+                c("Liberal Democracy\n (Difference)", 
+                  "Log GDP\n per capita\n (Difference)",
+                  "Corruption\n (Difference)"), 
+                time = 3
+            )),
+        type = factor(type,  levels = c("Error-Correction Model", "First-Difference Model")),
+        submodel = factor(submodel, levels = c("Point Estimates Only","With Uncertainty", "Uncertainty & More Data")),
+        model = factor(model, levels = paste0("Model ", 
+                                                      rep(1:2, each = 4), ".", rep(1:4, 2),
+                                                      " (",
+                                                      rep(c("ECM", "ECM", "FD", "FD"), 2),
+                                                      ")"))
+    )
+
+# Institution Corruption--------------------------------
+
+result_ecmReg2 <- bind_rows(
+    mutate(result_clsAPSR[["pooled-regime2"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime2"]]), submodel = "With Uncertainty"),
+    mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime2"]]), submodel = "Uncertainty & More Data")) %>%
+    mutate(type = "Error-Correction Model",
+           model = "Model 2.2 (ECM)")
+
+result_fdReg2 <- bind_rows(
+    mutate(result_clsAPSR[["fd-regime2"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime2"]]), submodel = "With Uncertainty"),
+    mutate(MOCsumm2(mocresult_expAPSR[["fd-regime2"]]), submodel = "Uncertainty & More Data")) %>% 
+    mutate(type = "First-Difference Model",
+           model = "Model 2.4 (FD)")
+
+result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
+    filter(term != "(Intercept)") %>%
+    mutate(
+        term0 = c(rep(
+            c("Democratic Mood\n (t-1)",
+              "Democratic Mood\n (t-2)",
+              "Electoral Democracy\n (Difference)",
+              "Electoral Democracy\n (t-1)",
+              "Minoritarian Democracy\n (Difference)",
+              "Minoritarian Democracy\n (t-1)",
+              "Log GDP\n per capita\n (Difference)",
+              "Log GDP\n (t-1)",
+              "Corruption\n (Difference)",
+              "Corruption\n (t-1)"
+            ),
+            time = 3),
+            rep(
+                c("Electoral Democracy\n (Difference)", 
+                  "Minoritarian Democracy\n (Difference)",
+                  "Log GDP\n per capita\n (Difference)",
+                  "Corruption\n (Difference)"), 
+                time = 3
+            )),
+        type = factor(type,  levels = c("Error-Correction Model", "First-Difference Model")),
+        submodel = factor(submodel, levels = c("Point Estimates Only","With Uncertainty", "Uncertainty & More Data")),
+        model = factor(model, levels = paste0("Model ", 
+                                              rep(1:2, each = 4), ".", rep(1:4, 2),
+                                              " (",
+                                              rep(c("ECM", "ECM", "FD", "FD"), 2),
+                                              ")"))
+    )
+```
+
+```{r coefName-APSR}
+index_coefName <- c(
+    `Democratic Mood\n (t-1)` = "Democratic~Support[t-1]",
+    `Democratic Mood\n (t-2)` = "Democratic~Support[t-2]",
+    `Liberal Democracy\n (Difference)` = "Delta~Liberal~democracy",
+    `Liberal Democracy\n (t-1)` = "Liberal~Democracy[t-1]",
+    `Electoral Democracy\n (Difference)` = "Delta~Electoral~Democracy",
+    `Electoral Democracy\n (t-1)` = "Electoral~Democracy[t-1]",
+    `Minoritarian Democracy\n (Difference)` = "Delta~Minoritarian~Democracy",
+    `Minoritarian Democracy\n (t-1)` = "Minoritarian~Democracy[t-1]",
+    `Log GDP\n per capita\n (Difference)` = "Delta~Log~GDP~per~capita",
+    `Log GDP\n (t-1)` = "Log~GDP[t-1]",
+    `Corruption\n (Difference)` = "Delta~Corruption",
+    `Corruption\n (t-1)` = "Corruption[t-1]"
+)
+```
+
+```{r plot-mainAPSR, fig.cap= "The Effect of Democracy on Change in Public Support with Uncertainty", fig.width=7, fig.height=10}
+df_plot <- bind_rows(result_APSR1, result_APSR2,
+                     result_RegAPSR1, result_RegAPSR2) %>% 
+    mutate(term = index_coefName[term0], 
+           term = factor(term, levels = unique(index_coefName)))
+
+small_multiple(df_plot, dot_args = list(size = .9, fatten = 1)) +
+    theme_bw() +
+    geom_hline(yintercept = 0, colour = "grey50", linetype = 2) +
+    scale_color_grey(start = 0.8, end = 0.4, 
+                     name = "Replication",
+                     breaks=c("Point Estimates Only",
+                              "With Uncertainty",
+                              "Uncertainty & More Data"),
+                     labels=c("Point Estimates Only",
+                              "With Uncertainty",
+                              "Uncertainty & More Data")) +
+    theme(axis.text.x  = element_text(angle = 90, hjust = .5),
+          strip.text.y.left = element_text(angle = 0),
+          legend.position = c(0, -.01),
+          legend.justification = c(1, 1), 
+          legend.title = element_text(size = 9, face = "bold"),
+          legend.title.align = 0.5,
+          legend.text = element_text(size = 8),
+          legend.background = element_rect(color="gray90"),
+          legend.spacing = unit(-3, "pt"),
+          legend.key.size = unit(7, "mm")) +
+    ggtitle("DV: Change in Public Support for Democracy")
+
+```
+
+# Discussion
+
+In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support has a positive effect on democracy and change in democracy a negative effect on change in support are not empirically supported once measurement uncertainty is taken into account, even when more data are used.
+
+There are theoretical explanations for the null results.
+With regard to how levels of democracy affect public support, we note that even the proponents of the classic argument did not contend that the mere existence of democratic institutions, no matter how consistently feckless and ineffective, would generate support among the public: instead, they maintained, public support would be gained through experience with government performance that was generally effective [@lipset_social_1959, 86-89; @Easton1965, 119-120].
+There is some empirical support for this, with government effectiveness positively related to public support among democracies and negatively related in non-democracies [@Magalhaes2014]. 
+The finding of @Krieckhaus2014 that income inequality is strongly negatively related to public support in democracies suggests that performance regarding redistribution is particularly important.
+Relatedly, on the reverse part of the classic argument, @Qi2011 suggests that democratic support alone cannot be expected to generate democratic change and oppose backsliding.
+Instead, that work contends, it is the combination of democratic support and dissatisfaction with current regime performance that generates demand for greater democracy.
+The effects of public support also have cultural-bound.
+@Brunkert2019[p.
+423] contends outspoken support for democracy is a "deceptive indicator of public's affinity to democracy"  and finds public support has neither pro-democratic nor anti-authoritarian effect without controlling emancipative values.
+Empirical results show that the meaning of support for democracy is dependent on emancipation values and is reversed to its own negation in a society with weak emancipative values [see, e.g.,@Kirsch2019, 83-85].
+And we must be open to the possibility that no theoretical elaboration, no respecification of these models will reveal relationships between public opinion and democracy.
+Democratic backsliding may simply be primarily a matter of elite decision making [see, e.g., @levitsky_how_2018].
+
+There are several potential methodological explanations for these null results as well.
+One issue is that the survey items employed---which ask respondents to assess the desirability or appropriateness of democracy, to compare democracy to some undemocratic alternative, or to assess one of these alternatives---may not capture every aspect of democratic support necessary for it to play its hypothesized roles in the classic theory.
+If only those who profess to prefer democracy to its alternatives _and also_ value freedom of expression, freedom of association, and pluralism of opinion will take appropriate action when democracy is threatened, then this measure is inadequate to its purpose [see, e.g., @Schedler2007].
+Moreover, given the multi-faceted nature of democratic attitudes, even the inclusion of such questions in unidimensional public opinion models such as those provided by @Claassen2019 or @Solt2020a are unlikely to be sufficient [see, e.g., @Wuttke2020].
+Another issue is that even if these survey questions do capture support for the generic concept of democracy, these measurement models might still be incapable of suitably capturing democratic support due to the variation in understanding the concept across countries or over time within countries [@Wuttke2021].
+Yet another is that this measure provides no assessment of the _relative_ importance the public affords democracy.
+It provides no information on the extent to which other values, such as policy preferences or partisanship, weigh more heavily---and there is growing evidence that, at least in the United States, there are many for whom these other considerations excuse substantial transgressions against democracy [see @bartels_ethnic_2020; @Carey2020; @graham_democracy_2020; @McCoy2020].
+Regardless, these explanations indicate that there remains much work to be done in the empirical study of public support and democracy.
+
+# Conclusion
+
+In this letter, we reexamine the findings from Claassen [-@Claassen2020a; -@Claassen2020b], two articles that maintain that public support helps the survival of democracy and democratic development has a thermostatic effect on public support.
+We demonstrate the importance of incorporating measurement uncertainty in analyzing the relationship between public support and democracy.
+Taking uncertainty into account rendered both articles' conclusions without empirical support, even when we added considerable more data.
+
+This points to the absolute necessity of incorporating measurement uncertainty into analyses that include latent variables.
+Measurement issues have never had a prominent place in comparative political studies because they need more time to estimate models, but they ground the quality of data and the basis of analysis [@stegmueller2011, 484].
+As the use of latent variables grows more common in political science, both researchers and readers should be aware that these variables' concomitant measurement uncertainty cannot be neglected.
+
+The null results reached in this letter could arise from several sources.
+There are theoretically grounded reasons of government effectiveness, democratic understanding, and generical-or-behavioral support to suspect that the relationships are in fact negligible.
+We also identified a number of potential shortcomings in the measurement of democratic support and ways in which the analysis models might be underspecified.
+All of these could and should be explored in future research.
+In any event, the sanguine assessment that readers may draw from Claassen [-@Claassen2020a; -@Claassen2020b]---that the fate of democracies depend on public support, and when eroded, their public will rally to them---is not supported by the current evidence.
+Those who would defend democracy have no grounds to be complacent.
+
+# References  {-}
+
+<div id = 'refs'></div>
+
+\pagebreak
+
+# Online Supplementary Materials {-}
+# (APPENDIX) Appendix {-}
+\setcounter{page}{1}
+\renewcommand{\thepage}{A\arabic{page}}
+\setcounter{figure}{0}
+\renewcommand{\thefigure}{A.\arabic{figure}}
+
+# Supplementary Appendix A: Data Recollection and Uncertainty in Control Variables {#dgp}
+
+Due to revisions to the underlying datasets (and, possibly, transcription errors), we were not able to achieve a primary replication [@Grossman2020] based on survey data summarized in @Claassen2020a and @Claassen2020b's Dataverse files.
+
+Specifically, we are not able to identify 5 country-year surveys, including South Sudan in Arab Barometer Wave 4, Dominican Republic in 2003 Latinobarometer, XXXX, and Spain in 2005 Latinobarometer. 
+In addition, we still have different sample size and number of respondents answering supportively by following approaches of cleanning data and treatment of non-responses described in @Claassen2020a's supplementatry materials.
+Specifically, we used Claassen's year coding to recode 85 unmatching country-year observations and added one more item "strong leader 2" in Arabbarometer which has different response categories but was conflated into "strong leader 1".
+
+V-Dem data was standardized in @Claassen2020b's analyses, but we did not figure out how the standardization was exactly performed.
+We standardized variables using Z-score, and the standardized values are different from Claassen's data.
+
+Since many variables, dependent variables, key independent variables, and control variables in the original analysis are latent variables, which cannot be observed directly and are inherently contaminated by measurement errors.
+We include measurement errors in five variables, public support for democracy, liberal democracy index, electoral democracy index, liberal component index, and corruption perception index.
+
+In respect of the key independent variable, public support for democracy, we preserve its posterior distribution from Model 5 using recollected and expanded data, separately.
+
+For the three indices of democratic development, we take two strategies.
+Regarding original data and recollected data, we use three democratic indices from V-Dem Version 8 which covers 201 countries from 1789 to 2017 and is the version Claassen used in his analyses.
+We use their posterior distribution provided by @coppedge2018.
+Regarding the expanded data used to replicate Claassen's analyses, we use the same three democratic indices but from V-Dem Version 10 because its year range from 1789 to 2019 is compatible with the expanded data.
+However, since V-Dem project has not released posterior distributions for indices in version 10, we simulated 900 data set for each democracy index using their standard error.
+
+Finally, to account for measurement error in Corruption Perceptions Index, we simulated 900 draws from a distribution with the point estimate and standard error provided by CPI for the year from 2012 to 2018.
+However, CPI does not provide standard error for the years before 2012.
+To simulate "posterior distribution", we first estimated the standard error for the country-year index.
+For each country, we identified its maximum relative standard error (standard error/cpi index) during these years and then calculated the estimated country-year standard error by multiplying the country's maximum relative error and its year CPI index.
+We used this estimated standard error to simulate 900 draws for each country-year.
+
+In the following section, we illustrate how we utilize these simulated distributions to take uncertainty into account in analysis models.
+
+# Appendix B: The Method of Composition {#moc}
+
+In analysis models, we have latent variables in both sides of equations, public suppport for democracy, democracy indices, and corruption index (The latter one is included in APSR analyses).
+Since measurement uncertainty associated with these latent variables can propagate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing "Method of Composition" [@Tanner1993,p52], which has been applied in analyses with latent variables [@Treier2008;@caughey2018;@Kastellec2015].
+
+As @caughey2018 explained, the main idea of MOC is to estimate the marginal distribution of coefficient parameter vector $\beta$, integrating over the uncertainty in latent variables $\theta$ (P A-15).
+More explicitly, we wish to integrate the joint density of $\beta$ and $\theta$ over the distribution of $\theta$.
+
+\begin{equation}
+p(\beta,\theta|w,y, Z) = p(\beta|\theta,w,y)p(\theta|Z).
+\end{equation}
+
+where $\theta$ is latent varibles with measurement errors conditional on data Z and a measurement model, $w$ is other predictors without errors, $Z$ is indicators for latent variables $X$, and $y$ is the outcome variable.
+In this way, we incorportate uncertainty in measuring predictor $\theta$, and uncertainty in the effects of latent variables $\theta$ and other variables $w$ on outcome variable $y$ [@Treier2008, 215].
+To sample from the conditional dentsity and the marginal density in the right side of the equation, we follow iterative Monte Carlo procdure described by @Treier2008, at iteration t,
+
+1. We sample $\theta^{s}$ from its posterior distribution $p(\theta|Z)$ and $y$ from $p(y|Z)$.
+
+2.
+For each analysis model, we run the model with $y$, $\theta$, and $w$, and save the coefficient estimates $\beta^{s}$ and variance-covariance matrix of $\beta^{s}$, $V^{s}$, both of which change due to the uncertainty in $\theta^{s}$ and $y^{s}$.
+
+3. We sample $\tilde{\beta^{t}}$ from the multivariate normal density with mean vector $\beta{s}$ and variance-covariace matrix $V^{s}$.
+
+We incorporate uncertainty for five variables, public support for democracy, liberal democracy, electoral democracy, liberal component index, and corruption perceptions index.
+For each of these five latent variables, we take 900 draws from its posterior distribution.
+We duplicate the dataset of variables “without” measurement error 900 times, and assign them to each a different random draw from the distributions of variables with measurement error, which yields 900 dataset.
+In next step, we run each of analysis models with these 900 datesets independently and save the resulting estimates of coefficients and the matrix of variance-covariance for each run.
+We then draw one sample from the mulitivariate normal distribution with the mean vector of coefficient estimates and variance-covariance matrix produced from each run.
+This procedure finally yields 900 samples of estimated coefficients drawn from the joint density of $\beta$ and $\theta$.
+We calculate point estimates and standard error based on these 900 samples.
+
+# Appendix C: Secondary Models from Claassen (2020$a$, 2020$b$)
+
+```{r formatResult-AJPS-dup}
+result_pooled <- bind_rows(
+  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Original"),
+ mutate(MOCsumm(mocresult_correctAJPS[["pooled"]]), model = "W. Uncertainty"),
+ mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), model = "Uncertainty+Expanded Data")
+) %>% 
+  mutate(type = "Pooled")
+
+result_gmm <- bind_rows(
+  mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm(mocresult_correctAJPS[["gmm"]]), model = "W. Uncertainty"),
+  mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), model = "Uncertainty+Expanded Data")
+) %>% 
+  mutate(type = "GMM")
+
+result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democracy\n (t-1)",
+        "Democracy\n (t-2)",
+        "Support\n (t-1)",
+        "Log GDP\n per capita\n (t-1)",
+        "GDP per\n capita growth\n (t-1)",
+        "Regional\n democracy\n (t-1)",
+        "Percent\n Muslim\n (t-1)",
+        "Resource\n dependence\n (t-1)"),
+      time = 6), 
+    type = factor(type, levels = c("Pooled", "GMM")),
+    model = factor(model, levels = c("Original", "W. Uncertainty", "Uncertainty+Expanded Data")))
+
+result_regime <- bind_rows(
+  mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm(mocresult_correctAJPS[["pooled-regime"]]), model = "W. Uncertainty"),
+  mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), model = "Uncertainty+Expanded Data")
+) %>% 
+  mutate(type = "Pooled")
+
+result_regimeGmm <- bind_rows(
+  mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Original"),
+  mutate(MOCsumm(mocresult_correctAJPS[["gmm-regime"]]), model = "W. Uncertainty"),
+ mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), model = "Uncertainty+Expanded Data")
+)%>% 
+  mutate(type = "GMM")
+
+result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
+  filter(term != "(Intercept)") %>%
+  mutate(
+    term = rep(
+      c("Democracy\n (t-1)",
+        "Democracy\n (t-2)",
+        "Support\n demo only\n (t-1)",
+        "Support\n auto only\n (t-1)",
+        "Log GDP\n per capita\n (t-1)",
+        "GDP per\n capita growth\n (t-1)",
+        "Regional\n democracy\n (t-1)",
+        "Percent\n Muslim\n (t-1)",
+        "Resource\n dependence\n (t-1)"),
+      time = 6), 
+    type = factor(type, levels = c("Pooled", "GMM")),
+    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data")))
+
+result_ajpsRegime <- result_regimeAJPS %>%
+    filter(type == "Pooled") %>% 
+    mutate(type = "Regime Specified")
+
+```
+
+```{r coefName-AJPS-dup}
+index_coefName <- c(
+    `Democracy\n (t-1)` = "Democracy[t-1]",
+    `Democracy\n (t-2)` = "Democracy[t-2]",
+    `Support\n (t-1)` = "Support[t-1]",
+    `Support\n demo only\n (t-1)` = "Support[t-1](demo~only)",
+    `Support\n auto only\n (t-1)` = "Support[t-1](auto~only)",
+    `Log GDP\n per capita\n (t-1)` = "Log~GDP~per~capita[t-1]",
+    `GDP per\n capita growth\n (t-1)` = "GDP~per~capita~growth[t-1]",
+    `Regional\n democracy\n (t-1)` = "Regional~democracy[t-1]",
+    `Percent\n Muslim\n (t-1)` = "Percent~Muslim[t-1]",
+    `Resource\n dependence\n (t-1)` = "Resource~dependence[t-1]"
+)
+```
+
+```{r plot-mocAJPS, fig.cap= "The Effect of Public Support on Democracy ", eval = TRUE, fig.width=7, fig.height=10}
+terms <- factor(rev(
+    c(
+        "Democracy[t-1]",
+        "Democracy[t-2]",
+        "Support[t-1]",
+        "Log~GDP~per~capita[t-1]",
+        "GDP~per~capita~growth[t-1]",
+        "Regional~democracy[t-1]",
+        "Percent~Muslim[t-1]",
+        "Resource~dependence[t-1]"
+    )
+), levels =
+    rev(
+        c(
+            "Democracy[t-1]",
+            "Democracy[t-2]",
+            "Support[t-1]",
+            "Log~GDP~per~capita[t-1]",
+            "GDP~per~capita~growth[t-1]",
+            "Regional~democracy[t-1]",
+            "Percent~Muslim[t-1]",
+            "Resource~dependence[t-1]"
+        )
+    ))
+
+plot_AJPS1 <-
+    dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
+    scale_y_discrete(labels = parse(text = levels(terms))) +
+    labs(title = "DV: V-Dem Liberal Democracy Index",
+         subtitle = "Pooled") +
+    facet_wrap( ~ type, scales = "free_x") +
+    theme(legend.position = "none")  +
+    scale_color_gb(palette = "digitMixed")
+
+terms2 <- factor(rev(
+    c(
+        "Democracy[t-1]",
+        "Democracy[t-2]",
+        "Support[t-1] (democracies~only)",
+        "Support[t-1] (autocracies~only)",
+        "Log~GDP~per~capita[t-1]",
+        "GDP~per~capita~growth[t-1]",
+        "Regional~democracy[t-1]",
+        "Percent~Muslim[t-1]",
+        "Resource~dependence[t-1]"
+    )
+), levels =
+    rev(
+        c(
+            "Democracy[t-1]",
+            "Democracy[t-2]",
+            "Support[t-1] (democracies~only)",
+            "Support[t-1] (autocracies~only)",
+            "Log~GDP~per~capita[t-1]",
+            "GDP~per~capita~growth[t-1]",
+            "Regional~democracy[t-1]",
+            "Percent~Muslim[t-1]",
+            "Resource~dependence[t-1]"
+        )
+    ))
+
+plot_AJPS2 <-
+    dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
+    scale_y_discrete(labels = parse(text = levels(terms2))) +
+    labs(title = "",
+         subtitle = "Regime Specified") +
+    facet_wrap( ~ type, scales = "free_x") +
+    theme(legend.position = "bottom",
+          legend.title = element_blank())  +
+   scale_color_gb(palette = "digitMixed")
+
+legend <- get_legend(plot_AJPS2)
+
+plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
+
+grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
+```
+
+\blandscape
+
+```{r formatResult-APSR-dup}
 # Pooled---------------------------------------
@@
 
-```{r coefName-APSR}
-index_coefName <- c(
-    `Democratic Mood\n (t-1)` = "Support[t-1]",
-    `Democratic Mood\n (t-2)` = "Support[t-2]",
-    `Liberal Democracy\n (Difference)` = "Delta~Liberal~democracy",
-    `Liberal Democracy\n (t-1)` = "Liberal~democracy[t-1]",
-    `Electoral Democracy\n (Difference)` = "Delta~Electoral~democracy",
-    `Electoral Democracy\n (t-1)` = "Electoral~democracy[t-1]",
-    `Minoritarian Democracy\n (Difference)` = "Delta~Minoritarian~democracy",
-    `Minoritarian Democracy\n (t-1)` = "Minoritarian~democracy[t-1]",
-    `Log GDP\n per capita\n (Difference)` = "Delta~Log~GDP~per~capita",
-    `Log GDP\n (t-1)` = "Log~GDP[t-1]"
-)
-```
-
-```{r plot-mainAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", fig.width=7, fig.height=10}
-type_model <-
-    c("Original", "W. Uncertainty", "Uncertainty+Expanded Data")
-
-df_plot <- bind_rows(result_apsrPooled, result_apsrRegime) %>%
-    mutate(
-        term = index_coefName[term],
-        term = factor(term, levels = unique(index_coefName)),
-        type = factor(type, levels = c("Pooled", "Institution Specified"))
-    )
-
-dwplot(df_plot) +
-    geom_vline(xintercept = 0,
-               colour = "grey80",
-               linetype = 2) +
-    ggtitle("DV: The Change of Public Support for Democracy") +
-    xlab("Coefficient Estimate") +
-    theme(
-        axis.title.y = element_blank(),
-        legend.position = "bottom",
-        legend.title = element_blank()
-    ) +
-    facet_wrap(~ type)  +
-    scale_color_gb(palette = "digitMixed")
-
-```
-
-# Discussion
-
-In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support has a positive effect on democracy and change in democracy a negative effect on change in support are not empirically supported once measurement uncertainty is taken into account, even when more data are used.
-
-There are theoretical explanations for the null results.
-With regard to how levels of democracy affect public support, we note that even the proponents of the classic argument did not contend that the mere existence of democratic institutions, no matter how consistently feckless and ineffective, would generate support among the public: instead, they maintained, public support would be gained through experience with government performance that was generally effective [@lipset_social_1959, 86-89; @Easton1965, 119-120].
-There is some empirical support for this, with government effectiveness positively related to public support among democracies and negatively related in non-democracies [@Magalhaes2014]. 
-The finding of @Krieckhaus2014 that income inequality is strongly negatively related to public support in democracies suggests that performance regarding redistribution is particularly important.
-Relatedly, on the reverse part of the classic argument, @Qi2011 suggests that democratic support alone cannot be expected to generate democratic change and oppose backsliding.
-Instead, that work contends, it is the combination of democratic support and dissatisfaction with current regime performance that generates demand for greater democracy.
-The effects of public support also have cultural-bound.
-@Brunkert2019[p.
-423] contends outspoken support for democracy is a "deceptive indicator of public's affinity to democracy"  and finds public support has neither pro-democratic nor anti-authoritarian effect without controlling emancipative values.
-Empirical results show that the meaning of support for democracy is dependent on emancipation values and is reversed to its own negation in a society with weak emancipative values [see, e.g.,@Kirsch2019, 83-85].
-And we must be open to the possibility that no theoretical elaboration, no respecification of these models will reveal relationships between public opinion and democracy.
-Democratic backsliding may simply be primarily a matter of elite decision making [see, e.g., @levitsky_how_2018].
-
-There are several potential methodological explanations for these null results as well.
-One issue is that the survey items employed---which ask respondents to assess the desirability or appropriateness of democracy, to compare democracy to some undemocratic alternative, or to assess one of these alternatives---may not capture every aspect of democratic support necessary for it to play its hypothesized roles in the classic theory.
-If only those who profess to prefer democracy to its alternatives _and also_ value freedom of expression, freedom of association, and pluralism of opinion will take appropriate action when democracy is threatened, then this measure is inadequate to its purpose [see, e.g., @Schedler2007].
-Moreover, given the multi-faceted nature of democratic attitudes, even the inclusion of such questions in unidimensional public opinion models such as those provided by @Claassen2019 or @Solt2020a are unlikely to be sufficient [see, e.g., @Wuttke2020].
-Another issue is that even if these survey questions do capture support for the generic concept of democracy, these measurement models might still be incapable of suitably capturing democratic support due to the variation in understanding the concept across countries or over time within countries [@Wuttke2021].
-Yet another is that this measure provides no assessment of the _relative_ importance the public affords democracy.
-It provides no information on the extent to which other values, such as policy preferences or partisanship, weigh more heavily---and there is growing evidence that, at least in the United States, there are many for whom these other considerations excuse substantial transgressions against democracy [see @bartels_ethnic_2020; @Carey2020; @graham_democracy_2020; @McCoy2020].
-Regardless, these explanations indicate that there remains much work to be done in the empirical study of public support and democracy.
-
-# Conclusion
-
-In this letter, we reexamine the findings from Claassen [-@Claassen2020a; -@Claassen2020b], two articles that maintain that public support helps the survival of democracy and democratic development has a thermostatic effect on public support.
-We demonstrate the importance of incorporating measurement uncertainty in analyzing the relationship between public support and democracy.
-Taking uncertainty into account rendered both articles' conclusions without empirical support, even when we added considerable more data.
-
-This points to the absolute necessity of incorporating measurement uncertainty into analyses that include latent variables.
-Measurement issues have never had a prominent place in comparative political studies because they need more time to estimate models, but they ground the quality of data and the basis of analysis [@stegmueller2011, 484].
-As the use of latent variables grows more common in political science, both researchers and readers should be aware that these variables' concomitant measurement uncertainty cannot be neglected.
-
-The null results reached in this letter could arise from several sources.
-There are theoretically grounded reasons of government effectiveness, democratic understanding, and generical-or-behavioral support to suspect that the relationships are in fact negligible.
-We also identified a number of potential shortcomings in the measurement of democratic support and ways in which the analysis models might be underspecified.
-All of these could and should be explored in future research.
-In any event, the sanguine assessment that readers may draw from Claassen [-@Claassen2020a; -@Claassen2020b]---that the fate of democracies depend on public support, and when eroded, their public will rally to them---is not supported by the current evidence.
-Those who would defend democracy have no grounds to be complacent.
-
-# References  {-}
-
-<div id = 'refs'></div>
-
-\pagebreak
-
-# Online Supplementary Materials {-}
-# (APPENDIX) Appendix {-}
-\setcounter{page}{1}
-\renewcommand{\thepage}{A\arabic{page}}
-\setcounter{figure}{0}
-\renewcommand{\thefigure}{A.\arabic{figure}}
-
-# Supplementary Appendix A: Data Recollection and Uncertainty in Control Variables {#dgp}
-
-Due to revisions to the underlying datasets (and, possibly, transcription errors), we were not able to achieve a primary replication [@Grossman2020] based on survey data summarized in @Claassen2020a and @Claassen2020b's Dataverse files.
-
-Specifically, we are not able to identify 5 country-year surveys, including South Sudan in Arab Barometer Wave 4, Dominican Republic in 2003 Latinobarometer, XXXX, and Spain in 2005 Latinobarometer. 
-In addition, we still have different sample size and number of respondents answering supportively by following approaches of cleanning data and treatment of non-responses described in @Claassen2020a's supplementatry materials.
-Specifically, we used Claassen's year coding to recode 85 unmatching country-year observations and added one more item "strong leader 2" in Arabbarometer which has different response categories but was conflated into "strong leader 1".
-
-V-Dem data was standardized in @Claassen2020b's analyses, but we did not figure out how the standardization was exactly performed.
-We standardized variables using Z-score, and the standardized values are different from Claassen's data.
-
-Since many variables, dependent variables, key independent variables, and control variables in the original analysis are latent variables, which cannot be observed directly and are inherently contaminated by measurement errors.
-We include measurement errors in five variables, public support for democracy, liberal democracy index, electoral democracy index, liberal component index, and corruption perception index.
-
-In respect of the key independent variable, public support for democracy, we preserve its posterior distribution from Model 5 using recollected and expanded data, separately.
-
-For the three indices of democratic development, we take two strategies.
-Regarding original data and recollected data, we use three democratic indices from V-Dem Version 8 which covers 201 countries from 1789 to 2017 and is the version Claassen used in his analyses.
-We use their posterior distribution provided by @coppedge2018.
-Regarding the expanded data used to replicate Claassen's analyses, we use the same three democratic indices but from V-Dem Version 10 because its year range from 1789 to 2019 is compatible with the expanded data.
-However, since V-Dem project has not released posterior distributions for indices in version 10, we simulated 900 data set for each democracy index using their standard error.
-
-Finally, to account for measurement error in Corruption Perceptions Index, we simulated 900 draws from a distribution with the point estimate and standard error provided by CPI for the year from 2012 to 2018.
-However, CPI does not provide standard error for the years before 2012.
-To simulate "posterior distribution", we first estimated the standard error for the country-year index.
-For each country, we identified its maximum relative standard error (standard error/cpi index) during these years and then calculated the estimated country-year standard error by multiplying the country's maximum relative error and its year CPI index.
-We used this estimated standard error to simulate 900 draws for each country-year.
-
-In the following section, we illustrate how we utilize these simulated distributions to take uncertainty into account in analysis models.
-
-# Appendix B: The Method of Composition {#moc}
-
-In analysis models, we have latent variables in both sides of equations, public suppport for democracy, democracy indices, and corruption index (The latter one is included in APSR analyses).
-Since measurement uncertainty associated with these latent variables can propagate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing "Method of Composition" [@Tanner1993,p52], which has been applied in analyses with latent variables [@Treier2008;@caughey2018;@Kastellec2015].
-
-As @caughey2018 explained, the main idea of MOC is to estimate the marginal distribution of coefficient parameter vector $\beta$, integrating over the uncertainty in latent variables $\theta$ (P A-15).
-More explicitly, we wish to integrate the joint density of $\beta$ and $\theta$ over the distribution of $\theta$.
-
-\begin{equation}
-p(\beta,\theta|w,y, Z) = p(\beta|\theta,w,y)p(\theta|Z).
-\end{equation}
-
-where $\theta$ is latent varibles with measurement errors conditional on data Z and a measurement model, $w$ is other predictors without errors, $Z$ is indicators for latent variables $X$, and $y$ is the outcome variable.
-In this way, we incorportate uncertainty in measuring predictor $\theta$, and uncertainty in the effects of latent variables $\theta$ and other variables $w$ on outcome variable $y$ [@Treier2008, 215].
-To sample from the conditional dentsity and the marginal density in the right side of the equation, we follow iterative Monte Carlo procdure described by @Treier2008, at iteration t,
-
-1. We sample $\theta^{s}$ from its posterior distribution $p(\theta|Z)$ and $y$ from $p(y|Z)$.
-
-2.
-For each analysis model, we run the model with $y$, $\theta$, and $w$, and save the coefficient estimates $\beta^{s}$ and variance-covariance matrix of $\beta^{s}$, $V^{s}$, both of which change due to the uncertainty in $\theta^{s}$ and $y^{s}$.
-
-3. We sample $\tilde{\beta^{t}}$ from the multivariate normal density with mean vector $\beta{s}$ and variance-covariace matrix $V^{s}$.
-
-We incorporate uncertainty for five variables, public support for democracy, liberal democracy, electoral democracy, liberal component index, and corruption perceptions index.
-For each of these five latent variables, we take 900 draws from its posterior distribution.
-We duplicate the dataset of variables “without” measurement error 900 times, and assign them to each a different random draw from the distributions of variables with measurement error, which yields 900 dataset.
-In next step, we run each of analysis models with these 900 datesets independently and save the resulting estimates of coefficients and the matrix of variance-covariance for each run.
-We then draw one sample from the mulitivariate normal distribution with the mean vector of coefficient estimates and variance-covariance matrix produced from each run.
-This procedure finally yields 900 samples of estimated coefficients drawn from the joint density of $\beta$ and $\theta$.
-We calculate point estimates and standard error based on these 900 samples.
-
-# Appendix C: Secondary Models from Claassen (2020$a$, 2020$b$)
-
-```{r formatResult-AJPS-dup}
-result_pooled <- bind_rows(
-  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Original"),
- mutate(MOCsumm(mocresult_correctAJPS[["pooled"]]), model = "W. Uncertainty"),
- mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), model = "Uncertainty+Expanded Data")
-) %>% 
-  mutate(type = "Pooled")
-
-result_gmm <- bind_rows(
-  mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_correctAJPS[["gmm"]]), model = "W. Uncertainty"),
-  mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), model = "Uncertainty+Expanded Data")
-) %>% 
-  mutate(type = "GMM")
-
-result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = rep(
-      c("Democracy\n (t-1)",
-        "Democracy\n (t-2)",
-        "Support\n (t-1)",
-        "Log GDP\n per capita\n (t-1)",
-        "GDP per\n capita growth\n (t-1)",
-        "Regional\n democracy\n (t-1)",
-        "Percent\n Muslim\n (t-1)",
-        "Resource\n dependence\n (t-1)"),
-      time = 6), 
-    type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Original", "W. Uncertainty", "Uncertainty+Expanded Data")))
-
-result_regime <- bind_rows(
-  mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_correctAJPS[["pooled-regime"]]), model = "W. Uncertainty"),
-  mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), model = "Uncertainty+Expanded Data")
-) %>% 
-  mutate(type = "Pooled")
-
-result_regimeGmm <- bind_rows(
-  mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_correctAJPS[["gmm-regime"]]), model = "W. Uncertainty"),
- mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), model = "Uncertainty+Expanded Data")
-)%>% 
-  mutate(type = "GMM")
-
-result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = rep(
-      c("Democracy\n (t-1)",
-        "Democracy\n (t-2)",
-        "Support\n demo only\n (t-1)",
-        "Support\n auto only\n (t-1)",
-        "Log GDP\n per capita\n (t-1)",
-        "GDP per\n capita growth\n (t-1)",
-        "Regional\n democracy\n (t-1)",
-        "Percent\n Muslim\n (t-1)",
-        "Resource\n dependence\n (t-1)"),
-      time = 6), 
-    type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data")))
-
-result_ajpsRegime <- result_regimeAJPS %>%
-    filter(type == "Pooled") %>% 
-    mutate(type = "Regime Specified")
-
-```
-
-```{r coefName-AJPS-dup}
-index_coefName <- c(
-    `Democracy\n (t-1)` = "Democracy[t-1]",
-    `Democracy\n (t-2)` = "Democracy[t-2]",
-    `Support\n (t-1)` = "Support[t-1]",
-    `Support\n demo only\n (t-1)` = "Support[t-1](demo~only)",
-    `Support\n auto only\n (t-1)` = "Support[t-1](auto~only)",
-    `Log GDP\n per capita\n (t-1)` = "Log~GDP~per~capita[t-1]",
-    `GDP per\n capita growth\n (t-1)` = "GDP~per~capita~growth[t-1]",
-    `Regional\n democracy\n (t-1)` = "Regional~democracy[t-1]",
-    `Percent\n Muslim\n (t-1)` = "Percent~Muslim[t-1]",
-    `Resource\n dependence\n (t-1)` = "Resource~dependence[t-1]"
-)
-```
-
-```{r plot-mocAJPS, fig.cap= "The Effect of Public Support on Democracy ", eval = TRUE, fig.width=7, fig.height=10}
-terms <- factor(rev(
-    c(
-        "Democracy[t-1]",
-        "Democracy[t-2]",
-        "Support[t-1]",
-        "Log~GDP~per~capita[t-1]",
-        "GDP~per~capita~growth[t-1]",
-        "Regional~democracy[t-1]",
-        "Percent~Muslim[t-1]",
-        "Resource~dependence[t-1]"
-    )
-), levels =
-    rev(
-        c(
-            "Democracy[t-1]",
-            "Democracy[t-2]",
-            "Support[t-1]",
-            "Log~GDP~per~capita[t-1]",
-            "GDP~per~capita~growth[t-1]",
-            "Regional~democracy[t-1]",
-            "Percent~Muslim[t-1]",
-            "Resource~dependence[t-1]"
-        )
-    ))
-
-plot_AJPS1 <-
-    dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms))) +
-    labs(title = "DV: V-Dem Liberal Democracy Index",
-         subtitle = "Pooled") +
-    facet_wrap( ~ type, scales = "free_x") +
-    theme(legend.position = "none")  +
-    scale_color_gb(palette = "digitMixed")
-
-terms2 <- factor(rev(
-    c(
-        "Democracy[t-1]",
-        "Democracy[t-2]",
-        "Support[t-1] (democracies~only)",
-        "Support[t-1] (autocracies~only)",
-        "Log~GDP~per~capita[t-1]",
-        "GDP~per~capita~growth[t-1]",
-        "Regional~democracy[t-1]",
-        "Percent~Muslim[t-1]",
-        "Resource~dependence[t-1]"
-    )
-), levels =
-    rev(
-        c(
-            "Democracy[t-1]",
-            "Democracy[t-2]",
-            "Support[t-1] (democracies~only)",
-            "Support[t-1] (autocracies~only)",
-            "Log~GDP~per~capita[t-1]",
-            "GDP~per~capita~growth[t-1]",
-            "Regional~democracy[t-1]",
-            "Percent~Muslim[t-1]",
-            "Resource~dependence[t-1]"
-        )
-    ))
-
-plot_AJPS2 <-
-    dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms2))) +
-    labs(title = "",
-         subtitle = "Regime Specified") +
-    facet_wrap( ~ type, scales = "free_x") +
-    theme(legend.position = "bottom",
-          legend.title = element_blank())  +
-   scale_color_gb(palette = "digitMixed")
-
-legend <- get_legend(plot_AJPS2)
-
-plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
-
-grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
-```
-
-\blandscape
-
-```{r formatResult-APSR-dup}
-# Pooled---------------------------------------
-
-result_ecm1 <- bind_rows(
-  mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["pooled1"]]), model = "W. Uncertainty"),
-  mutate(MOCsumm2(mocresult_expAPSR[["pooled1"]]), model = "Uncertainty+Expanded Data")
-) %>% 
-  mutate(type = "ECM")
-
-result_fd1 <- bind_rows(
-  mutate(result_clsAPSR[["fd1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["fd1"]]), model = "W. Uncertainty"),
-  mutate(MOCsumm2(mocresult_expAPSR[["fd1"]]), model = "Uncertainty+Expanded Data")
-) %>% 
-  mutate(type = "First Difference")
-
-result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-        "Liberal Democracy\n (Difference)",
-        "Liberal Democracy\n (t-1)",
-        "Log GDP\n per capita\n (Difference)",
-        "Log GDP\n (t-1)"),
-      time = 3),
-      rep(
-        c("Liberal Democracy\n (Difference)", 
-          "Log GDP\n per capita\n (Difference)"), 
-        time = 3
-      )),
-    type = factor(type,  levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data"))
-  )
-
-result_apsrPooled <- result_APSR1 %>% 
-    filter(type == "ECM") %>% 
-    mutate(type = "Pooled")
-
-# Institution----------------------------------
-
-result_ecmReg1 <- bind_rows(
-  mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime1"]]), model = "W. Uncertainty"),
-  mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime1"]]), model = "Uncertainty+Expanded Data")
-) %>% 
-  mutate(type = "ECM")
-
-result_fdReg1 <- bind_rows(
-  mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime1"]]), model = "W. Uncertainty"),
-  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime1"]]), model = "Uncertainty+Expanded Data")
-) %>% 
-  mutate(type = "First Difference")
-
-result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-        "Electoral Democracy\n (Difference)",
-        "Electoral Democracy\n (t-1)",
-        "Minoritarian Democracy\n (Difference)",
-        "Minoritarian Democracy\n (t-1)",
-        "Log GDP\n per capita\n (Difference)",
-        "Log GDP\n (t-1)"),
-      time = 3),
-      rep(
-        c("Electoral Democracy\n (Difference)", 
-          "Minoritarian Democracy\n (Difference)",
-          "Log GDP\n per capita\n (Difference)"), 
-        time = 3
-      )),
-    type = factor(type,  levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data"))
-  )
-
-result_apsrRegime <- result_RegAPSR1 %>% 
-    filter(type == "ECM") %>% 
-    mutate(type = "Institution Specified")
-
-# Pooled-corruption------------------------------
-
-result_ecm2 <- bind_rows(
-  mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["pooled2"]]), model = "W. Uncertainty"),
-  mutate(MOCsumm2(mocresult_expAPSR[["pooled2"]]), model = "Uncertainty+Expanded Data")
-) %>% 
-  mutate(type = "ECM")
-
-result_fd2 <- bind_rows(
-  mutate(result_clsAPSR[["fd2"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["fd2"]]), model = "W. Uncertainty"),
-  mutate(MOCsumm2(mocresult_expAPSR[["fd2"]]), model = "Uncertainty+Expanded Data")
-) %>% 
-  mutate(type = "First Difference")
-
-result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-        "Liberal Democracy\n (Difference)",
-        "Liberal Democracy\n (t-1)",
-        "Log GDP\n per capita\n (Difference)",
-        "Log GDP\n (t-1)",
-        "Corruption\n (Difference)",
-        "Corruption\n (t-1)"
-      ),
-      time = 3),
-      rep(
-        c("Liberal Democracy\n (Difference)", 
-          "Log GDP\n per capita\n (Difference)",
-          "Corruption\n (Difference)"), 
-        time = 3
-      )),
-    type = factor(type,  levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data"))
-  )
-
-# Institution Corruption--------------------------------
-
-result_ecmReg2 <- bind_rows(
-  mutate(result_clsAPSR[["pooled-regime2"]][[1]][,1:3], model = "Original"),
- mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime2"]]), model = "W. Uncertainty"),
-  mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime2"]]), model = "Uncertainty+Expanded Data")) %>%
-  mutate(type = "ECM")
-
-result_fdReg2 <- bind_rows(
-  mutate(result_clsAPSR[["fd-regime2"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime2"]]), model = "W. Uncertainty"),
-  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime2"]]), model = "Uncertainty+Expanded Data")) %>% 
-  mutate(type = "First Difference")
-
-result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-        "Electoral Democracy\n (Difference)",
-        "Electoral Democracy\n (t-1)",
-        "Minoritarian Democracy\n (Difference)",
-        "Minoritarian Democracy\n (t-1)",
-        "Log GDP\n per capita\n (Difference)",
-        "Log GDP\n (t-1)",
-        "Corruption\n (Difference)",
-        "Corruption\n (t-1)"
-      ),
-      time = 3),
-      rep(
-        c("Electoral Democracy\n (Difference)", 
-          "Minoritarian Democracy\n (Difference)",
-          "Log GDP\n per capita\n (Difference)",
-          "Corruption\n (Difference)"), 
-        time = 3
-      )),
-    type = factor(type,  levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data"))
-  )
-```
-
 ```{r coefName-APSR-dup}

### 2021-08-16 paper/dcpo_demsupport.Rmd
polish legends

@@
           strip.text.y.left = element_text(angle = 0),
-          legend.position = c(-0.115, -.01),
+          legend.position = c(-0.06, -.01),
           legend.justification = c(1, 1), 
@@
           legend.background = element_rect(color="gray90"),
-          legend.spacing = unit(-3, "pt"),
-          legend.key.size = unit(9, "mm")) +
+          legend.spacing = unit(-5, "pt"),
+          legend.key.size = unit(8, "mm")) +
+  guides(color = guide_legend(override.aes = list(size=.3))) +
   ggtitle("DV: V-Dem Liberal Democracy Index")
@@
     )
-
-# result_apsrPooled <- result_APSR1 %>% 
-#     filter(type == "Error-Correction Model") %>% 
-#     mutate(type = "Pooled")
 
@@
           strip.text.y.left = element_text(angle = 0),
-          legend.position = c(0, -.01),
+          legend.position = c(0.006, -.01),
           legend.justification = c(1, 1), 
@@
           legend.background = element_rect(color="gray90"),
-          legend.spacing = unit(-3, "pt"),
-          legend.key.size = unit(7, "mm")) +
+          legend.spacing = unit(-5, "pt"),
+          legend.key.width = unit(4.5, "mm"),
+          legend.key.height = unit(7, "mm")) +
+  guides(color = guide_legend(override.aes = list(size=.3))) +
   ggtitle("DV: Change in Public Support for Democracy")

### 2021-08-16 paper/memo/response_memo.Rmd
fuss; revise discussion of add'l models #22 in light of https://github.com/fsolt/dcpo_dem_mood/commit/13cd643e4a1ef715b798f6d6949837e62c3b9266#diff-382635c9325bf3273d195ff1b8a44e5b11afd7d97addeb8863ea35feb98c1a07

@@
 As this technique has become the standard method for incorporating uncertainty in the Americanist literature using Multilevel Regression and Poststratification [see, e.g., @Kastellec2015; @caughey2018], which is after all also a latent variable model of public opinion, we were pleased to adopt this suggestion.
-We provide a full description of the MOC technique in the Supplementary Materials.
+We provide a full description of the MOC technique in the Supplementary Information.
 Further, to help ensure that incorporating uncertainty is as easy as possible for scholars working with latent variables of cross-national public opinion, we are including in our replication materials a suite of R functions implementing the MOC that are tailored to this application.
@@
 
-1.
-**Method: ~~Better Estimates of Public Support and More Data~~ Adding Data** R1 and R4 asked for more detail on the differences between the DCPO model and the latent variable model used by Claassen.
+1. **Method: ~~Better Estimates of Public Support and~~ Adding More Data** R1 and R4 asked for more detail on the differences between the DCPO model and the latent variable model used by Claassen.
 R2 indirectly raised the same issue, asking about the consequences for thermostatic models of employing a random-walk prior in the DCPO model of democratic support---when actually both DCPO and the Claassen model use the same random-walk prior.
 Given that the DCPO model's advantages ultimately do not have a payoff in this case, we concluded that its inclusion in this 4000-word letter is an unnecessary distraction from our main points.
-So we took the _other_ suggestion from R1 on this topic to simply drop DCPO from the text entirely and moved the analyses with the DCPO estimates to the Supplementary Materials.
+So we took the _other_ suggestion from R1 on this topic to simply drop DCPO from the text entirely and moved the analyses with the DCPO estimates to the Supplementary Information.
 
 1.
-**Method: Adding Data** Not directly related to a specific comment, but the opportunity to revise and resubmit allowed us to incorporate even more survey data that was released since our original submission (most notably from the ongoing release of Wave 7 of the World Values Survey).
+**Method: Adding More Data** Not directly related to a specific comment, but the opportunity to revise and resubmit allowed us to incorporate even more survey data that was released since our original submission (most notably from the ongoing release of Wave 7 of the World Values Survey).
 Thanks again!
@@
 R2 summarized the issue even more pithily, "some explanation is required, or else readers will think that some mistake has been made."
-The explanation is that the analyses from @Claassen2020b are error correction models, and so the dependent variable is not the level of democratic support but the _change_ in democratic support; in other words, the mistake was that our captioning to the figure was badly misleading (it read simply, "DV: Public Support for Democracy" and "The Effect of Democracy on Public Support"), and there was nothing in our discussion to bring readers back on track.
-So: it is not the case that Denmark is as likely to have a low value as China is to have a high one, but rather that Denmark is as likely to have a decline as China is to have a gain.
+The explanation is that the analyses from @Claassen2020b are error correction models, and so the dependent variable is not the level of democratic support but the _change_ in democratic support; the mistake was that our captioning to the figure was badly misleading (it read simply, "DV: Public Support for Democracy" and "The Effect of Democracy on Public Support"), and there was nothing in our discussion to bring readers back on track.
+In other words, it is not the case that Denmark is as likely to have a low value as China is to have a high one, but rather that Denmark is as likely to have a decline as China is to have a gain.
 We have labeled the plot correctly now.
@@
 1.
-**Results** R1 noted that in addition to the pooled OLS models we present in Figure 1 and the ECMs we present in Figure 2, @Claassen2020a includes a pair of system GMM models and @Claassen2020b includes a pair of first-difference models.
-We include the results of our three-tiered replication and extension for Claassen's secondary models in the Supplementary Materials; these additional analyses yield the same substantive conclusions as those we present in the text.
+**Results** R1 noted that in addition to the pooled OLS models we had presented in Figure 1 and the ECMs we had present in Figure 2, @Claassen2020a includes a pair of system GMM models and @Claassen2020b includes an additional specification that examines different aspects of democracy and a set of first-difference models.
+We now present the results of all of these secondary models as well.
+(As the analyses presented in Table 2 of @Claassen2020a consider the relative strengths of the performances of democratic support and democratic satisfaction, rather than the relationship between democracy and democratic support that we focus on here, we followed the APSR editor's advice and did not replicate those.)
+
+1. **Discussion**
 

### 2021-08-16 paper/dcpo_demsupport.Rmd
add plot captions; fuss with plot titles

--- 2021-08-16 paper/dcpo_demsupport.Rmd
@@
 We conduct inferences from the distributive data via the technique known as the "method of composition" [@Tanner1993, 52; @Treier2008, 215; @caughey2018, A15-16].
-For additional detail on this technique, see the Supplementary Materials.
+For additional detail on this technique, see the Supplementary Information.
 
@@
 This result is robust when using separated regime types in the explanatory variable. 
-Nor do applying system GMM models or controlling for corruption alter the conclusion (see the Supplementary Materials)._
+Nor do applying system GMM models or controlling for corruption alter the conclusion (see the Supplementary Information)._
 
@@
     `Democracy\n (t-2)` = "Democracy[t-2]",
-    `Support\n (t-1)` = "Democratic~Support[t-1]",
+    `Support\n (t-1)` = "Democratic~Support[t-1]~(all~regimes)",
     `Support\n demo only\n (t-1)` = "Democratic~Support[t-1]~(democracies)",
@@
            term = factor(term, levels = unique(index_coefName)))
+
+ajps_caption <- "Replications of Claassen (2020a), Table 1, 128."
 
@@
           legend.background = element_rect(color="gray90"),
-          legend.spacing = unit(-3, "pt"),
-          legend.key.size = unit(9, "mm")) +
-  ggtitle("DV: V-Dem Liberal Democracy Index")
+          legend.spacing = unit(-5, "pt"),
+          legend.key.size = unit(8, "mm"),
+          plot.title = element_text(hjust = 1.4),
+          plot.caption = element_text(size = 10, hjust = 0.2, margin = margin(t=15))) +
+  guides(color = guide_legend(override.aes = list(size=.3))) +
+  ggtitle("Dependent Variable: Level of Democracy") +
+  labs(caption = ajps_caption)
 
@@
 
+apsr_caption <- "Replications of Claassen (2020b), Table 1, 47, and Table 2, 49.  Models denoted 'ECM' are error-correction models; those marked 'FD' are first-difference models." %>% 
+  strwrap(85) %>% 
+  paste0(sep="", collapse="\n")
+
 small_multiple(df_plot, dot_args = list(size = .9, fatten = 1)) +
@@
           legend.background = element_rect(color="gray90"),
-          legend.spacing = unit(-3, "pt"),
-          legend.key.size = unit(7, "mm")) +
-    ggtitle("DV: Change in Public Support for Democracy")
+          legend.spacing = unit(-5, "pt"),
+          legend.key.width = unit(4.5, "mm"),
+          legend.key.height = unit(7, "mm"),
+          plot.caption = element_text(size = 10, hjust = 0.2, margin = margin(t=15))) +
+  guides(color = guide_legend(override.aes = list(size=.3))) +
+  ggtitle("Dependent Variable: Change in Public Democratic Support") +
+  labs(caption = apsr_caption)
 
@@
 
-# Online Supplementary Materials {-}
+# Online Supplementary Information {-}
 # (APPENDIX) Appendix {-}

### 2021-08-17 paper/dcpo_demsupport.Rmd
revise results, discussion, conclusion #19; discussion & conclusion not done; #21 not done

@@
 
-Figure \@ref(fig:plot-mainAJPS) presents the reanalyses of the hypothesis that public support influences the level of democracy, with democratic support pooled for all countries [@Claassen2020a, 128, Model 1] in the left panel and democratic support separated by regime type (Model 2) on the right.
-The uppermost set of results replicate the analysis of @Claassen2020a, including its exclusion of measurement uncertainty, and reproduce that article's findings.
+Figure \@ref(fig:plot-mainAJPS) presents the reanalyses of the hypothesis that public support influences the level of democracy [@Claassen2020a, Table 1, 128].
+The lighter, lefthand set of results replicate the analysis of @Claassen2020a, including its exclusion of measurement uncertainty by using only the point estimates of public democratic support and the other variables measured with quantified error (democracy and corruption), and they reproduce that article's findings.
 The middle results introduce a single change: the uncertainty in the measurement of public support is taken into account.
-<!-- In both models, the positive coefficients for democratic support are no longer statistically significant. -->
-The bottom results also incorporate uncertainty but additionally replace the estimates of democratic support with those based on the expanded dataset; this change works to increase the number of observations analyzed as well.
-<!-- Although the confidence intervals shrink considerably, the coefficient estimates move much closer to zero; the hypothesis remains unsupported.  -->
-
-_In comparison to the original result, the positive coefficients for democratic support in both models accounting for the uncertainty are no longer statistically significant.
-This result is robust when using separated regime types in the explanatory variable. 
-Nor do applying system GMM models or controlling for corruption alter the conclusion (see the Supplementary Information)._
-
-Adding more data is indeed helpful for increasing the certainty to the analytic estimates. 
-The confidence intervals of the explanatory variable (and some control variables) are considerably narrower than the cases just bringing the uncertainty back---or even the original case when uncertainty was completely ignored.
-Nonetheless, the insignificance remains and is robust across different model specifications.
-
-Moreover, the results expose another risk for ignoring uncertainty: missestimation. 
-As shown in Figure \@ref(fig:plot-mainAJPS), besides the confidence intervals the (point) estimates also shift. 
-Methodologically, the shifts indicate that the 900 regressions of public support on democracy do not yield consistent results, although the explanatory and control variables were drawn from the same distribution.
-In this sense, the coefficients produced simply by the means of the variable distributions are no more than a one-time guess of the true parameters and apparently not a robust one. 
-More importantly, what this methodological difference leads to is a substantively opposite conclusion of the relationship between public opinions and institutional democratization.
-Our replication results manifest the uncertainty ignorance with mounting risk.
+In all four models, the positive coefficients for democratic support are no longer statistically significant.
+The darker, righthand results also incorporate uncertainty but additionally replace the estimates of democratic support with those based on our expanded dataset; this change works to increase the number of observations analyzed as well.
+Although the confidence intervals shrink considerably, the coefficient estimates move much closer to zero; the hypothesis remains unsupported.
 
@@
 
-The importance for taking the measurement uncertainty into account appear more evident when the relevant variable plays as the outcome variable. 
-In Figure \@ref(fig:plot-mainAPSR), we examine the thermostatic model of democratic support per @Claassen2020b [p. 47, Models 1.1 and 1.2]. 
-When the uncertainty is ignored, the coefficient of $\Delta$liberal democracy (the uppermost set), the yearly changes of the institutional feature is negative inferring that the change in democratic mood decreases as change in democracy increases and vice versa.
-However, when the measurement uncertainty is properly accounted (the middle set), the point estimate shifts towards zero and the coefficient is no longer significant.
-More data (the lowermost set), again, only adjusts the confidence intervals but not direction nor significance.
+In Figure \@ref(fig:plot-mainAPSR), we examine the thermostatic model of democratic support per @Claassen2020b [47, Table 1, 49, Table 2].
+The negative coefficient estimates for change in liberal democracy in the lefthand set of results, which do not take uncertainty into account, imply that the immediate effect of a increase in the level of democracy is a decline in public support for democracy and of a decrease in democracy an expansion of support---that democratic support indeed does respond thermostatically to democracy.
+However, the middle results demonstrate that this thermostatic effect, too, does not  hold after the measurement uncertainty is accounted for. 
+And again, the righthand results reveal that the additional data of our extension do not provide support for the original conclusion.
+<!-- In fact, once uncertainty is taken into account, the models of @Claassen2020b detect very little pattern in the year-to-year changes of public support for democracy at all. -->
 
@@
     `Log GDP\n per capita\n (Difference)` = "Delta~Log~GDP~per~capita",
-    `Log GDP\n (t-1)` = "Log~GDP[t-1]",
+    `Log GDP\n (t-1)` = "Log~GDP~per~capita[t-1]",
     `Corruption\n (Difference)` = "Delta~Corruption",
@@
 In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support has a positive effect on democracy and change in democracy a negative effect on change in support are not empirically supported once measurement uncertainty is taken into account, even when more data are used.
-
-There are theoretical explanations for the null results.
-With regard to how levels of democracy affect public support, we note that even the proponents of the classic argument did not contend that the mere existence of democratic institutions, no matter how consistently feckless and ineffective, would generate support among the public: instead, they maintained, public support would be gained through experience with government performance that was generally effective [@lipset_social_1959, 86-89; @Easton1965, 119-120].
-There is some empirical support for this, with government effectiveness positively related to public support among democracies and negatively related in non-democracies [@Magalhaes2014]. 
+These null results have a number of important substantive implications.
+
+First, they underscore that recognizing the conditional aspects of the classic argument regarding democracy and democratic support is crucial.
+With regard to how levels of democracy affect public support, even the early proponents of the classic argument did not contend that the mere existence of democratic institutions, no matter how consistently feckless and ineffective, would generate support among the public: instead, they maintained, public support would be gained through experience with government performance that was generally effective [@lipset_social_1959, 86-89; @Easton1965, 119-120].
+There is some empirical evidence for this, with government effectiveness positively related to public support among democracies and negatively related in non-democracies [@Magalhaes2014]. 
 The finding of @Krieckhaus2014 that income inequality is strongly negatively related to public support in democracies suggests that performance regarding redistribution is particularly important.
-Relatedly, on the reverse part of the classic argument, @Qi2011 suggests that democratic support alone cannot be expected to generate democratic change and oppose backsliding.
+On the reverse part of the classic argument, @Qi2011 suggests that democratic support alone cannot be expected to generate democratic change and oppose backsliding.
 Instead, that work contends, it is the combination of democratic support and dissatisfaction with current regime performance that generates demand for greater democracy.
-The effects of public support also have cultural-bound.
-@Brunkert2019[p.
-423] contends outspoken support for democracy is a "deceptive indicator of public's affinity to democracy"  and finds public support has neither pro-democratic nor anti-authoritarian effect without controlling emancipative values.
-Empirical results show that the meaning of support for democracy is dependent on emancipation values and is reversed to its own negation in a society with weak emancipative values [see, e.g.,@Kirsch2019, 83-85].
-And we must be open to the possibility that no theoretical elaboration, no respecification of these models will reveal relationships between public opinion and democracy.
-Democratic backsliding may simply be primarily a matter of elite decision making [see, e.g., @levitsky_how_2018].
-
-There are several potential methodological explanations for these null results as well.
-One issue is that the survey items employed---which ask respondents to assess the desirability or appropriateness of democracy, to compare democracy to some undemocratic alternative, or to assess one of these alternatives---may not capture every aspect of democratic support necessary for it to play its hypothesized roles in the classic theory.
-If only those who profess to prefer democracy to its alternatives _and also_ value freedom of expression, freedom of association, and pluralism of opinion will take appropriate action when democracy is threatened, then this measure is inadequate to its purpose [see, e.g., @Schedler2007].
-Moreover, given the multi-faceted nature of democratic attitudes, even the inclusion of such questions in unidimensional public opinion models such as those provided by @Claassen2019 or @Solt2020a are unlikely to be sufficient [see, e.g., @Wuttke2020].
-Another issue is that even if these survey questions do capture support for the generic concept of democracy, these measurement models might still be incapable of suitably capturing democratic support due to the variation in understanding the concept across countries or over time within countries [@Wuttke2021].
-Yet another is that this measure provides no assessment of the _relative_ importance the public affords democracy.
-It provides no information on the extent to which other values, such as policy preferences or partisanship, weigh more heavily---and there is growing evidence that, at least in the United States, there are many for whom these other considerations excuse substantial transgressions against democracy [see @bartels_ethnic_2020; @Carey2020; @graham_democracy_2020; @McCoy2020].
+Whether these conditional relationships exist among the newly available latent-variable data on democracy and democratic support is a promising avenue for future research.
+
+Further, these null results suggest a careful reconsideration of the relationship between concept and measure for those seeking to construct latent-variable measures of democratic support.
+The most concerning issue is that the survey items employed---which ask respondents to assess the desirability or appropriateness of democracy, to compare democracy to some undemocratic alternative, or to assess one of these alternatives---may not capture every aspect of democratic support necessary for it to play its hypothesized roles in the classic theory.
+One possibility is that only those who profess to prefer democracy to its alternatives _and also_ value freedom of expression, freedom of association, and pluralism of opinion will take appropriate action when democracy is threatened [see, e.g., @Schedler2007].
+Another is that respondents' other values, such as their policy preferences or partisanship, may weigh more heavily than their support for democracy: there is growing evidence that, at least in the United States, there are many for whom these other considerations excuse substantial transgressions against democracy [see @bartels_ethnic_2020; @Carey2020; @graham_democracy_2020; @McCoy2020].
+Yet another is that the answers to the above items reflect actual support for democracy only when respondents also hold a robust understanding of what democracy means: otherwise, positive responses indicate support for autocracy instead [see, e.g., @Brunkert2019, @Kirsch2019, @Wuttke2021].
+Taking any or all of these into account requires considering the _combination_ of attitudes: even the inclusion of additional questions in a unidimensional public opinion model such as that provided by @Claassen2019 will not be sufficient [see, e.g., @Wuttke2020].
+
+Finally, by failing to provide evidence for a straightforward relationship between democratic support and democracy, these null findings lend additional support to rival understandings of regime change.
+There are compelling arguments that democratic transitions [see, e.g., @ODonnell1986; @Karl1987] and backsliding [see, e.g., @levitsky_how_2018, @Haggard2021] are primarily a matter of elite decision making.
+<!-- [But Norris critique] -->
+
 Regardless, these explanations indicate that there remains much work to be done in the empirical study of public support and democracy.
@@
 
-In this letter, we reexamine the findings from Claassen [-@Claassen2020a; -@Claassen2020b], two articles that maintain that public support helps the survival of democracy and democratic development has a thermostatic effect on public support.
-We demonstrate the importance of incorporating measurement uncertainty in analyzing the relationship between public support and democracy.
-Taking uncertainty into account rendered both articles' conclusions without empirical support, even when we added considerable more data.
+In this letter, we reexamined the findings from Claassen [-@Claassen2020a; -@Claassen2020b], two articles that maintain that public support helps the survival of democracy and democratic development has a thermostatic effect on public support.
+We demonstrated the importance of incorporating measurement uncertainty in analyzing the relationship between public support and democracy.
+Taking uncertainty into account rendered both articles' conclusions without empirical support, even when we added considerable additional data.
 
 This points to the absolute necessity of incorporating measurement uncertainty into analyses that include latent variables.
-Measurement issues have never had a prominent place in comparative political studies because they need more time to estimate models, but they ground the quality of data and the basis of analysis [@stegmueller2011, 484].
 As the use of latent variables grows more common in political science, both researchers and readers should be aware that these variables' concomitant measurement uncertainty cannot be neglected.
 
-The null results reached in this letter could arise from several sources.
-There are theoretically grounded reasons of government effectiveness, democratic understanding, and generical-or-behavioral support to suspect that the relationships are in fact negligible.
-We also identified a number of potential shortcomings in the measurement of democratic support and ways in which the analysis models might be underspecified.
-All of these could and should be explored in future research.
+The null results reached in this letter have several implications.
+<!-- There are theoretically grounded reasons of government effectiveness, democratic understanding, and generical-or-behavioral support to suspect that the relationships are in fact negligible. -->
+<!-- We also identified a number of potential shortcomings in the measurement of democratic support and ways in which the analysis models might be underspecified. -->
+<!-- All of these could and should be explored in future research. -->
+
 In any event, the sanguine assessment that readers may draw from Claassen [-@Claassen2020a; -@Claassen2020b]---that the fate of democracies depend on public support, and when eroded, their public will rally to them---is not supported by the current evidence.

### 2021-08-17 paper/dcpo_demsupport.Rmd
revise discussion and conclusion #19, #21

@@
 
+In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that democratic support has a positive effect on democracy and change in democracy a negative effect on change in support are not empirically supported once measurement uncertainty is taken into account, even when more data are used.
+
 ```{r pointAPSR}
@@
 
-In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support has a positive effect on democracy and change in democracy a negative effect on change in support are not empirically supported once measurement uncertainty is taken into account, even when more data are used.
 These null results have a number of important substantive implications.
-
 First, they underscore that recognizing the conditional aspects of the classic argument regarding democracy and democratic support is crucial.
@@
 Instead, that work contends, it is the combination of democratic support and dissatisfaction with current regime performance that generates demand for greater democracy.
-Whether these conditional relationships exist among the newly available latent-variable data on democracy and democratic support is a promising avenue for future research.
-
-Further, these null results suggest a careful reconsideration of the relationship between concept and measure for those seeking to construct latent-variable measures of democratic support.
-The most concerning issue is that the survey items employed---which ask respondents to assess the desirability or appropriateness of democracy, to compare democracy to some undemocratic alternative, or to assess one of these alternatives---may not capture every aspect of democratic support necessary for it to play its hypothesized roles in the classic theory.
+Whether these conditional relationships exist among the newly available latent-variable data on democracy and democratic support remain questions for future research.
+
+Further, these null results recommend building recent and more refined conceptualizations of democratic support into our measures.
+In other words, the survey items employed by Claassen [-@Claassen2020a; -@Claassen2020b]---which ask respondents to assess the desirability or appropriateness of democracy, to compare democracy to some undemocratic alternative, or to assess one of these alternatives---although often used by researchers, may not capture every aspect of democratic support necessary for it to play its hypothesized roles in the classic theory.
 One possibility is that only those who profess to prefer democracy to its alternatives _and also_ value freedom of expression, freedom of association, and pluralism of opinion will take appropriate action when democracy is threatened [see, e.g., @Schedler2007].
 Another is that respondents' other values, such as their policy preferences or partisanship, may weigh more heavily than their support for democracy: there is growing evidence that, at least in the United States, there are many for whom these other considerations excuse substantial transgressions against democracy [see @bartels_ethnic_2020; @Carey2020; @graham_democracy_2020; @McCoy2020].
-Yet another is that the answers to the above items reflect actual support for democracy only when respondents also hold a robust understanding of what democracy means: otherwise, positive responses indicate support for autocracy instead [see, e.g., @Brunkert2019, @Kirsch2019, @Wuttke2021].
+Yet another is that the answers to the above items reflect actual support for democracy only when respondents also hold a robust understanding of what liberal democracy means: otherwise, positive responses indicate support for autocracy instead [see, e.g., @Brunkert2019, @Kirsch2019, @Wuttke2021].
 Taking any or all of these into account requires considering the _combination_ of attitudes: even the inclusion of additional questions in a unidimensional public opinion model such as that provided by @Claassen2019 will not be sufficient [see, e.g., @Wuttke2020].
 
-Finally, by failing to provide evidence for a straightforward relationship between democratic support and democracy, these null findings lend additional support to rival understandings of regime change.
-There are compelling arguments that democratic transitions [see, e.g., @ODonnell1986; @Karl1987] and backsliding [see, e.g., @levitsky_how_2018, @Haggard2021] are primarily a matter of elite decision making.
-<!-- [But Norris critique] -->
-
-Regardless, these explanations indicate that there remains much work to be done in the empirical study of public support and democracy.
+Finally, by failing to provide evidence for a short-term relationship between democratic support and democracy, these null findings can be seen to lend additional support to other theories of regime change.
+There are compelling arguments that episodes of democratic transition [see, e.g., @ODonnell1986a; @Karl1987] and backsliding [see, e.g., @levitsky_how_2018; @Haggard2021] are best understood as products of elite decision making.
+With regard to the latter, critics have charged that these claims overlook the extent of demand for authoritarian rule among the public [see, e.g., @Norris2021].
+The null results reported here, by finding that year-to-year changes in democratic support bear little relationship to changes in democracy, highlight that levels of public support appear to play this role only over the long run [see also @Welzel2017], leaving elite decisions as a powerful explanation for when and how short-term developments unfold.
 
@@
 We demonstrated the importance of incorporating measurement uncertainty in analyzing the relationship between public support and democracy.
-Taking uncertainty into account rendered both articles' conclusions without empirical support, even when we added considerable additional data.
+Taking uncertainty into account rendered both articles' conclusions without empirical support, even when we added a considerable quantity of additional data.
 
@@
 
-The null results reached in this letter have several implications.
-<!-- There are theoretically grounded reasons of government effectiveness, democratic understanding, and generical-or-behavioral support to suspect that the relationships are in fact negligible. -->
-<!-- We also identified a number of potential shortcomings in the measurement of democratic support and ways in which the analysis models might be underspecified. -->
-<!-- All of these could and should be explored in future research. -->
-
-In any event, the sanguine assessment that readers may draw from Claassen [-@Claassen2020a; -@Claassen2020b]---that the fate of democracies depend on public support, and when eroded, their public will rally to them---is not supported by the current evidence.
+The null results reached in this letter have several substantive implications.
+They highlight theoretical arguments that maintain that levels of democratic support undergird democracy only over the long term and so lend indirect support to other explanations for short-run changes in regime.
+They also draw attention to the conditional nature of the classic argument on democracy and democratic support as well as to challenges in measuring the concept of democratic support that remain unmet by existing time-series cross-sectional latent-variable models.
+Most importantly, the sanguine assessment that readers may draw from Claassen [-@Claassen2020a; -@Claassen2020b]---that the fate of democracies depend on public support, and when eroded, their publics will rally to them---is not supported by the current evidence.
 Those who would defend democracy have no grounds to be complacent.

### 2021-08-17 paper/dcpo_demsupport.Rmd
fix cite

@@
 Another is that respondents' other values, such as their policy preferences or partisanship, may weigh more heavily than their support for democracy: there is growing evidence that, at least in the United States, there are many for whom these other considerations excuse substantial transgressions against democracy [see @bartels_ethnic_2020; @Carey2020; @graham_democracy_2020; @McCoy2020].
-Yet another is that the answers to the above items reflect actual support for democracy only when respondents also hold a robust understanding of what liberal democracy means: otherwise, positive responses indicate support for autocracy instead [see, e.g., @Brunkert2019, @Kirsch2019, @Wuttke2021].
+Yet another is that the answers to the above items reflect actual support for democracy only when respondents also hold a robust understanding of what liberal democracy means: otherwise, positive responses indicate support for autocracy instead [see, e.g., @Brunkert2019; @Kirsch2019; @Wuttke2021].
 Taking any or all of these into account requires considering the _combination_ of attitudes: even the inclusion of additional questions in a unidimensional public opinion model such as that provided by @Claassen2019 will not be sufficient [see, e.g., @Wuttke2020].

### 2021-08-17 paper/dcpo_demsupport.Rmd
fuss with discussion re #21

@@
 Another is that respondents' other values, such as their policy preferences or partisanship, may weigh more heavily than their support for democracy: there is growing evidence that, at least in the United States, there are many for whom these other considerations excuse substantial transgressions against democracy [see @bartels_ethnic_2020; @Carey2020; @graham_democracy_2020; @McCoy2020].
-Yet another is that the answers to the above items reflect actual support for democracy only when respondents also hold a robust understanding of what liberal democracy means: otherwise, positive responses indicate support for autocracy instead [see, e.g., @Brunkert2019; @Kirsch2019; @Wuttke2021].
+Yet another is that the answers to the above items reflect actual support for democracy only when respondents also either hold a robust understanding of what liberal democracy means or anchor their support in emancipative values of universal freedoms.
+If they do not, their positive responses to these items indicate support for autocracy instead [see, e.g., @Brunkert2019; @Kirsch2019; @Wuttke2021].
 Taking any or all of these into account requires considering the _combination_ of attitudes: even the inclusion of additional questions in a unidimensional public opinion model such as that provided by @Claassen2019 will not be sufficient [see, e.g., @Wuttke2020].

### 2021-08-17 paper/memo/response_memo.Rmd
single space; responses to #19 & #21; fuss

@@
 fontsize: 11pt
-spacing: double
+spacing: single
 bibliography: \dummy{`r file.path(file.path(getwd(), ".."), list.files(file.path(getwd(), ".."), ".bib$", recursive = TRUE))`}
@@
 As you will see below, the reviews were each individually very constructive---and together usually so, as concerns raised by one review were often met by suggestions offered in another.
-Collectively, the reviews motivated us to ensure the piece, as a letter manuscript, was tightly focused on its twin main points: that, in general, researchers working with latent variables must take care to include in their analyses the uncertainty in these measures, and, specifically, taking uncertainty into account reveals that there is no evidence for the assertions that democracies' fates depend on public support and that their publics will rally to them if they are weakened.
+Collectively, the reviews motivated us to ensure the piece, as a letter manuscript, was tightly focused on its twin main points: that, in general, researchers working with latent variables must take care to include in their analyses the uncertainty in these measures, and, specifically, taking uncertainty into account reveals that there is no evidence for the assertions in Claassen [-@Claassen2020a; -@Claassen2020b] that democracies' fates depend on public support and that their publics will rally to them if they are weakened.
 Indeed, your comments (and those of the editor) gave us the courage to be truly ruthless in stripping out any and all extraneous material that distracted from these two crucial points.
@@
 **Method** A key omission in our original submission, given our goal of underscoring the "absolute necessity" of taking quantified measurement error into account, is that we ourselves neglected the measurement error in the V-Dem democracy data and the Transparency International corruption data.
-We are extremely grateful to R1 and R2 for alerting us to the beam in our own eye while we still had opportunity to pluck it out.
+We are extremely grateful to R1 and R2 for alerting us to the beam in our own eye while we still had the opportunity to pluck it out.
+All of the replications that include uncertainty now do so for _all_ of the variables for which quantified error is available, not just democratic support.
 
@@
 **Method: Incorporating Uncertainty** R1 and R2 both raised the question of whether the approach for incorporating uncertainty we used was the most appropriate for this application, and R4 asked for additional detail on how uncertainty was incorporated.
-Although R2 correctly (and helpfully!) noted that the approach we had employed is the same one explicated by @Blackwell2017, [they](https://public.oed.com/blog/a-brief-history-of-singular-they/) also suggested we use the Method of Composition (MOC) that was first put forward by @Tanner1993 and introduced to political science by @Treier2008.
+Although R2 correctly (and helpfully!) noted that the approach we had employed is the same explicated by @Blackwell2017, [they](https://public.oed.com/blog/a-brief-history-of-singular-they/) also suggested we use the Method of Composition (MOC) that was first put forward by @Tanner1993 and introduced to political science by @Treier2008.
 As this technique has become the standard method for incorporating uncertainty in the Americanist literature using Multilevel Regression and Poststratification [see, e.g., @Kastellec2015; @caughey2018], which is after all also a latent variable model of public opinion, we were pleased to adopt this suggestion.
 We provide a full description of the MOC technique in the Supplementary Information.
-Further, to help ensure that incorporating uncertainty is as easy as possible for scholars working with latent variables of cross-national public opinion, we are including in our replication materials a suite of R functions implementing the MOC that are tailored to this application.
 
@@
 **Method: Incorporating Uncertainty** R4 suggested that it would be helpful to provide citations for the point that neglecting to include uncertainty can bias coefficients along with standard errors.
-We agree and so drop cites here to @Blackwell2017 [, 318-319] and @Blackwell2017a [, 360-361], who present simulations that, while aimed at other issues, nonetheless illustrate the point neatly.
-We also cite to @caughey2018 [, 254], who, like others familiar with the problem, simply state the fact and move on.
+We agree and so drop cites here to Blackwell, Honaker, and King [-@Blackwell2017, 318-319; -@Blackwell2017a, 360-361]---who present simulations that, while aimed at other issues, nonetheless illustrate the point neatly---as well as to @caughey2018 [, 254].
 
-1. **Method: ~~Better Estimates of Public Support and~~ Adding More Data** R1 and R4 asked for more detail on the differences between the DCPO model and the latent variable model used by Claassen.
+1.
+**Method: ~~Better Estimates of Public Support and~~ Adding More Data** R1 and R4 asked for more detail on the differences between Solt's [-@Solt2020b] DCPO model and the latent variable model used by Claassen.
 R2 indirectly raised the same issue, asking about the consequences for thermostatic models of employing a random-walk prior in the DCPO model of democratic support---when actually both DCPO and the Claassen model use the same random-walk prior.
 Given that the DCPO model's advantages ultimately do not have a payoff in this case, we concluded that its inclusion in this 4000-word letter is an unnecessary distraction from our main points.
-So we took the _other_ suggestion from R1 on this topic to simply drop DCPO from the text entirely and moved the analyses with the DCPO estimates to the Supplementary Information.
+So we took the _other_ suggestion from R1 on this topic, hinted at by R2 as well, to simply drop DCPO from the text entirely and move the analyses with the DCPO estimates to the Supplementary Information.
 
@@
 R2 summarized the issue even more pithily, "some explanation is required, or else readers will think that some mistake has been made."
-The explanation is that the analyses from @Claassen2020b are error correction models, and so the dependent variable is not the level of democratic support but the _change_ in democratic support; the mistake was that our captioning to the figure was badly misleading (it read simply, "DV: Public Support for Democracy" and "The Effect of Democracy on Public Support"), and there was nothing in our discussion to bring readers back on track.
+The explanation is that the analyses from @Claassen2020b are error-correction models, and so the dependent variable is not the level of democratic support but the _change_ in democratic support; the mistake was that our captioning to the figure was badly misleading (it read simply, "DV: Public Support for Democracy" and "The Effect of Democracy on Public Support"), and there was nothing in our discussion to bring readers back on track.
 In other words, it is not the case that Denmark is as likely to have a low value as China is to have a high one, but rather that Denmark is as likely to have a decline as China is to have a gain.
-We have labeled the plot correctly now.
-These results, we note, give further grounds for R2's concern about random-walk priors in latent variable models of public opinion when the estimates are then used in  thermostatic models: much of the year-to-year change in democratic support is simply random---only 44% of the country-years in Claassen's sample are estimated from survey data, leaving most with only the prior---so it is not surprising that these changes are not well predicted by the variables in Claassen's model.
+We label the plot correctly now.
+These results, we note, give further grounds for R2's concern about random-walk priors in latent variable models of public opinion when the estimates are then used in  thermostatic models: many of the year-to-year changes in democratic support are simply random---only 44% of the country-years in Claassen's sample are estimated from survey data, leaving most with only the prior---so it is not surprising that these changes are not well predicted by the variables in Claassen's model.
 Ignoring the uncertainty in the estimates averages away this randomness and may, as here, yield conclusions that cannot be supported.
@@
 1.
-**Results** R1 noted that in addition to the pooled OLS models we had presented in Figure 1 and the ECMs we had present in Figure 2, @Claassen2020a includes a pair of system GMM models and @Claassen2020b includes an additional specification that examines different aspects of democracy and a set of first-difference models.
+**Results** R1 noted that in addition to the pooled OLS models we had presented in Figure 1 and the ECMs we had presented in Figure 2, @Claassen2020a includes a pair of system GMM models and @Claassen2020b includes an additional specification that examines different aspects of democracy and also first-difference models for both specifications.
 We now present the results of all of these secondary models as well.
-(As the analyses presented in Table 2 of @Claassen2020a consider the relative strengths of the performances of democratic support and democratic satisfaction, rather than the relationship between democracy and democratic support that we focus on here, we followed the APSR editor's advice and did not replicate those.)
+(As the analyses presented in Table 2 of @Claassen2020a consider the relative strengths of the performances of democratic support and democratic satisfaction, rather than the relationship between democracy and democratic support that we focus on here, we followed the _APSR_ editor's advice and did not replicate those models---gratefully, too, because  reproducing the measure of democratic satisfaction would have been a ton of additional work.)
 
-1. **Discussion**
+1. **Discussion** R4 wrote the discussion section was "somewhat underwhelming," with too much attention to data issues and not enough engagement with substantive debates.
+This critique struck home.
+We rewrote this section (and the introduction and conclusion) to be sure to emphasize the substantive implications of our findings.
 
-[need #19, #21]
+1.
+**Discussion** R3 raised the point that Claassen's [-@Claassen2020a; -@Claassen2020b] measure of democratic support neglects that many people embrace authoritarian notions of democracy, and therefore the support for 'democracy' indicated by many of the items the measure incorporates often actually represents support for autocracy instead.
+We gladly incorporate this observation.
 
-\pagebreak
+1.
+**Discussion** R3 also pointed out that the relationship between democratic support and democracy is likely best understood to unfold on a much longer time scale than Claassen's [-@Claassen2020a] analysis implies.
+This is an excellent point, and we work it in here.
+
+Thank you once more for the opportunity to make revisions.
+We think the paper is much stronger as a result of your comments; in fact, with your assistance, we think it lives up to R3's assessment as an "exemplary demonstration" of the role of replication in scientific progress.
+We hope you all agree.
 

### 2021-08-17 paper/dcpo_demsupport.Rmd
revise intro

@@
 
-There are many plausible explanations for these null results, both theoretical and methodological.
-From a theoretical perspective, the effect of democracy on public support may depend not on its mere existence but on its effectiveness [see @Magalhaes2014] and particularly with regard to redistribution [see @Krieckhaus2014].
-Similarly, the impact of public support on democracy may depend on the extent to which those who support democracy are also dissatisfied with the current regime's performance; that is, that it is not democratic support that is important to democratic change, but rather unsatisfied democratic demand [see @Qi2011].
-_Whether the public support has a pro-democratic or anti-authoritarian effect is also bounded by the emancipative value that, as a belief-anchored orientation, shapes the public's understanding of democracy [see @Brunkert2019; @Kirsch2019; @Kruse2019].
-Moreover, the cultural and historical attributes of the emancipative value decide that it cannot be shifted shortly by institutional changes._
-Of course, it could in fact be that democratic change does not actually depend on public opinion of any sort at all but instead is an elite-driven phenomenon [see, e.g., @levitsky_how_2018].
-
-Methodologically, one possible issue is that support for democracy is multidimensional, and the survey questions used to measure it simply do not capture all of the dimensions relevant to democratic change, such as commitments to political equality and freedom of expression [see @Schedler2007; @Wuttke2020].
-Another is that the relationships among these survey items have varied substantially over time [see @Wuttke2021]; this would violate the assumptions of the public opinion models used and would yield faulty estimates of democratic support.
-A third is that these survey questions do not ask respondents how they prioritize democracy relative to other values with which it may come into conflict, such as their partisanship, and so miss capturing the true extent of support democracy would find among the public when public support was actually needed [see @Carey2020; @graham_democracy_2020; @McCoy2020].
+There are several important implications of these null results.
+They point to a need for closer attention to the conditional aspects of the classic theory [see @lipset_social_1959, 86-89; @Easton1965, 119-20].
+On the one side, the effect of democracy on public support may depend not on its mere existence but on its effectiveness [see @Magalhaes2014] and particularly with regard to redistribution [see @Krieckhaus2014].
+On the other, the impact of public support on democracy may depend on the extent to which those who support democracy are also dissatisfied with the current regime's performance; that is, that it is not democratic support that is important to democratic change, but rather unsatisfied democratic demand [see @Qi2011].
+
+Similarly, the results presented here are further evidence that the survey items commonly employed to measure democratic support are inadequate to the task.
+Without additional information on respondents' support for democracy relative to other values with which it may come into conflict, such as their partisanship [see, e.g., @Carey2020; @graham_democracy_2020; @McCoy2020]---or on whether respondents even understand the meaning of the democracy they are claiming to support [see, e.g., @Kirsch2019; @Wuttke2020]---these questions appear to miss capturing the true extent of support democracy would find among the public when public support was actually needed [see @Carey2020; @graham_democracy_2020; @McCoy2020].
+
+Our results also reinforce the views that relationships between democracy and public support unfold only over the long term [see, e.g., @Welzel2017] and that democratic change in the short-term is instead best understood as an elite-driven phenomenon [see, e.g., @levitsky_how_2018; @Haggard2021].
 
@@
 As democracy is also a latent variable in these analyses, we include the uncertainty in its estimates as well, along with that for corruption in the second analysis of @Claassen2020b.
-In the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.
+In the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.^[We also attempted to make fuller use of the available survey data by employing Solt's [-@Solt2020a; -@Solt2020b] DCPO model, which unlike Claassen's [-@Claassen2019] model does not dichotomize ordinal responses.
+The better fit of the DCPO model to these data [see @Solt2020a, 10-12] and the additional information it incorporates, however, did not yield substantively different results; see the Supplemental Information.]
 
@@
 With regard to the latter, critics have charged that these claims overlook the extent of demand for authoritarian rule among the public [see, e.g., @Norris2021].
-The null results reported here, by finding that year-to-year changes in democratic support bear little relationship to changes in democracy, highlight that levels of public support appear to play this role only over the long run [see also @Welzel2017], leaving elite decisions as a powerful explanation for when and how short-term developments unfold.
+The null results reported here, by finding that year-to-year changes in democratic support bear little relationship to changes in democracy, highlight that levels of public support appear to relate to regime only over the long run [see also @Welzel2017], leaving elite decisions as a powerful explanation for when and how short-term developments unfold.
 

### 2021-08-18 paper/dcpo_demsupport.Rmd
revise intro

@@
 The models employed in these studies' analyses, though, do not account for uncertainty in their measurement of democratic support.
-Measurement error challenges statistical analyses, especially when it is correlated with an outcome variable which is the case of democratic support, but it is often ignored in the analysis [@Blackwell2017; @Blackwell2017a].
 Because they are unobserved, latent variables are inherently accompanied by measurement uncertainty.
@@
 In this letter, we reexamine the classic arguments about support for democracy and democratic change tested in these two pieces while correcting this oversight.
-In addition to incorporating the measurement uncertainty, we also sought to reduce it by correcting and expanding survey data to including 144 countries for up to 33 years between 1988 and 2020 (based on 26% more questions and 33% more survey sources).
-Our analyses reveal that the significant relationships between public support and democratic change disappear once measurement uncertainty is taken into account, both in replications with the studies' original data and with expanded data.
+In addition to incorporating the measurement uncertainty, we also sought to reduce it by expanding considerably the survey data drawn upon and re-estimating democratic support for 144 countries for up to 33 years between 1988 and 2020.
+Our analyses reveal that the significant relationships between public support and democratic change disappear once measurement uncertainty is taken into account, both in replications with the studies' original data and in our extension analyses that incorporate the additional data.
 That is, once measurement uncertainty is accounted for, there is no empirical support for either claim put forward in these two works: declining democratic support does not signal subsequent democratic backsliding, and changes in democracy do not spur a thermostatic response in democratic support.
@@
 On the other, the impact of public support on democracy may depend on the extent to which those who support democracy are also dissatisfied with the current regime's performance; that is, that it is not democratic support that is important to democratic change, but rather unsatisfied democratic demand [see @Qi2011].
-
 Similarly, the results presented here are further evidence that the survey items commonly employed to measure democratic support are inadequate to the task.
-Without additional information on respondents' support for democracy relative to other values with which it may come into conflict, such as their partisanship [see, e.g., @Carey2020; @graham_democracy_2020; @McCoy2020]---or on whether respondents even understand the meaning of the democracy they are claiming to support [see, e.g., @Kirsch2019; @Wuttke2020]---these questions appear to miss capturing the true extent of support democracy would find among the public when public support was actually needed [see @Carey2020; @graham_democracy_2020; @McCoy2020].
-
-Our results also reinforce the views that relationships between democracy and public support unfold only over the long term [see, e.g., @Welzel2017] and that democratic change in the short-term is instead best understood as an elite-driven phenomenon [see, e.g., @levitsky_how_2018; @Haggard2021].
+Without additional information on respondents' support for democracy relative to other values with which it may come into conflict, such as their partisanship [see, e.g., @Carey2020; @graham_democracy_2020; @McCoy2020]---or on whether respondents even understand the meaning of the democracy they are claiming to support [see, e.g., @Kirsch2019; @Wuttke2020]---these questions appear to miss capturing the true extent of support democracy would find among the public when public support was actually needed.
+Our results also reinforce arguments that relationships between democracy and public support unfold only over the long term [see, e.g., @Welzel2017] and that democratic change in the short-term is instead best understood as an elite-driven phenomenon [see, e.g., @levitsky_how_2018; @Haggard2021].
 
@@
 As latent variable measurement models become more commonly used, it is absolutely necessary for researchers employing them to incorporate the associated uncertainty into analyses.
-And, at a time when democracy is seen as under threat around the world [e.g., @Diamond2015], taken together, Claassen [-@Claassen2020a; -@Claassen2020b] send what is ultimately a reassuring message: the fate of democracy rests with us, the public, and when democratic institutions are undermined, we will swing to their support and constitute "an obstacle to democratic backsliding" [@Claassen2020b, p.
-51].
+And, at a time when democracy is seen as under threat around the world [e.g., @Diamond2015], taken together, Claassen [-@Claassen2020a; -@Claassen2020b] send what is ultimately a reassuring message: the fate of democracy rests with us, the public, and when democratic institutions are undermined, we will swing to their support and constitute "an obstacle to democratic backsliding" [@Claassen2020b, 51].
 Both of these assertions may well be true, but the evidence we have, properly assessed, does not support them.
@@
 Second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.
-As democracy is also a latent variable in these analyses, we include the uncertainty in its estimates as well, along with that for corruption in the second analysis of @Claassen2020b.
-In the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.^[We also attempted to make fuller use of the available survey data by employing Solt's [-@Solt2020a; -@Solt2020b] DCPO model, which unlike Claassen's [-@Claassen2019] model does not dichotomize ordinal responses.
+As democracy is also a latent variable in these analyses, we include the uncertainty in its estimates as well, along with that for corruption in the models of @Claassen2020b.
+In the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.^[We also attempted to make fuller use of the available survey data by employing the DCPO model [@Solt2020a; @Solt2020b], which unlike the [@Claassen2019] model does not dichotomize ordinal responses.
 The better fit of the DCPO model to these data [see @Solt2020a, 10-12] and the additional information it incorporates, however, did not yield substantively different results; see the Supplemental Information.]
@@
 These null results have a number of important substantive implications.
-First, they underscore that recognizing the conditional aspects of the classic argument regarding democracy and democratic support is crucial.
+First, they underscore that it is crucial to recognize the conditional aspects of the classic argument regarding democracy and democratic support.
 With regard to how levels of democracy affect public support, even the early proponents of the classic argument did not contend that the mere existence of democratic institutions, no matter how consistently feckless and ineffective, would generate support among the public: instead, they maintained, public support would be gained through experience with government performance that was generally effective [@lipset_social_1959, 86-89; @Easton1965, 119-120].

### 2021-08-18 paper/dcpo_demsupport.Rmd
start revising Appendix A

@@
 These null results have a number of important substantive implications.
-First, they underscore that it is crucial to recognize the conditional aspects of the classic argument regarding democracy and democratic support.
+First, they underscore that it is crucial to recognize the conditional aspects of the classic theory regarding democracy and democratic support.
 With regard to how levels of democracy affect public support, even the early proponents of the classic argument did not contend that the mere existence of democratic institutions, no matter how consistently feckless and ineffective, would generate support among the public: instead, they maintained, public support would be gained through experience with government performance that was generally effective [@lipset_social_1959, 86-89; @Easton1965, 119-120].
@@
 
-# Supplementary Appendix A: Data Recollection and Uncertainty in Control Variables {#dgp}
-
-Due to revisions to the underlying datasets (and, possibly, transcription errors), we were not able to achieve a primary replication [@Grossman2020] based on survey data summarized in @Claassen2020a and @Claassen2020b's Dataverse files.
-
-Specifically, we are not able to identify 5 country-year surveys, including South Sudan in Arab Barometer Wave 4, Dominican Republic in 2003 Latinobarometer, XXXX, and Spain in 2005 Latinobarometer. 
+# Supplementary Appendix A: Replication Notes {#dgp}
+
+Replicating the analyses of @Claassen2020a and @Claassen2020b while incorporating the quantified uncertainty in their variables was not possible from those article's Dataverse files.
+Instead, it required re-collecting all of the data employed in those articles directly from their original sources, that is, in the terminology of @Grossman2020, it required a primary replication rather than a secondary one.
+We describe this process here.
+
+First, we identified the variable names of each survey item in each survey dataset as well as their corresponding values. 
+We then used the `DCPOtools` R package to automate the process of generating a dataset of survey marginals.
+Due to revisions to the underlying datasets (and, possibly, transcription errors), we were not able to locate 5 country-year-items: including South Sudan in Arab Barometer Wave 4, Dominican Republic in 2003 Latinobarometer, XXXX, and Spain in 2005 Latinobarometer.
 In addition, we still have different sample size and number of respondents answering supportively by following approaches of cleanning data and treatment of non-responses described in @Claassen2020a's supplementatry materials.

### 2021-08-18 paper/dcpo_demsupport.Rmd

--- 2021-08-17 paper/dcpo_demsupport.Rmd
@@
     keep_tex: yes
-    toc: FALSE
-    number_sections: FALSE
+    toc: no
+    number_sections: yes
     latex_engine: xelatex
@@
 
-ls_pacGH <- c("fsolt/DCPOtools", "sammo3182/drhutools")
-remotes::install_github(ls_pacGH, force = FALSE)
+# ls_pacGH <- c("fsolt/DCPOtools", "sammo3182/drhutools")
+# remotes::install_github(ls_pacGH, force = FALSE)
 
@@
   gridExtra,
-  drhutools,
+  # drhutools, # for colorful plots
   dotwhisker, 
@@
 )
+
+theme_set(theme_bw())
 ```
@@
 
-# Method
+# Method {-}
 
@@
 
-## Incorporating Uncertainty
+## Incorporating Uncertainty {-}
 
@@
 
-## Adding More Data
+## Adding More Data {-}
 
@@
 
-# Results
+# Results {-}
 
@@
 
-```{r mocresult-pureAJPS, eval=FALSE}
+```{r mocResult-pureAJPS, eval=FALSE}
 
@@
 
-```{r mocresult-expAJPS, eval=FALSE}
+```{r mocResult-expAJPS, eval=FALSE}
 
@@
 
-```{r formatResult-AJPS}
+```{r mocFormatResult-AJPS}
 result_pooled <- bind_rows(
@@
 
-```{r coefName-AJPS}
+```{r mocCoefName-AJPS}
 index_coefName <- c(
@@
 
-```{r plot-mainAJPS, fig.cap= "The Effect of Public Support on Democracy with Uncertainty", fig.width=5, fig.height=10, fig.align='center'}
+```{r plot-fullAJPS, fig.cap= "The Effect of Public Support on Democracy with Uncertainty", fig.width=5, fig.height=10, fig.align='center'}
 
@@
 small_multiple(df_plot, dot_args = list(size = .9, fatten = 1)) +
-    theme_bw() +
     geom_hline(yintercept = 0, colour = "grey50", linetype = 2) +
@@
                      name = "Replication",
-                     breaks=c("Point Estimates Only", "With Uncertainty", "Uncertainty & More Data"),
-                     labels=c("Point Estimates Only", "With Uncertainty", "Uncertainty & More Data")) +
+                     breaks=c("Point Estimates Only", "Uncertainty & More Data", "Uncertainty & DCPO"),
+                     labels=c("Point Estimates Only", "Uncertainty & More Data", "Uncertainty & DCPO")) +
     theme(axis.text.x  = element_text(angle = 90, hjust = .5),
@@
 
-```{r mocresult-pureAPSR, eval=FALSE}
+```{r mocResult-pureAPSR, eval=FALSE}
 
@@
 
-```{r mocresult-expAPSR, eval=FALSE}
+```{r mocResult-expAPSR, eval=FALSE}
 
@@
 
-```{r formatResult-APSR}
+```{r mocFormatResult-APSR}
 # Pooled---------------------------------------
@@
 
-```{r coefName-APSR}
+```{r mocCoefName-APSR}
 index_coefName <- c(
@@
 
-```{r plot-mainAPSR, fig.cap= "The Effect of Democracy on Change in Public Support with Uncertainty", fig.width=7, fig.height=10}
+```{r plot-fullAPSR, fig.cap= "The Effect of Democracy on Change in Public Support with Uncertainty", fig.width=7, fig.height=10}
 df_plot <- bind_rows(result_APSR1, result_APSR2,
@@
 
-# Discussion
+# Discussion {-}
 
@@
 
-# Conclusion
+# Conclusion {-}
 
@@
 # (APPENDIX) Appendix {-}
+
 \setcounter{page}{1}
@@
 
-# Supplementary Appendix A: Data Recollection and Uncertainty in Control Variables {#dgp}
+# Data Recollection and Uncertainty in Control Variables {#dgp}
 
@@
 
-# Appendix B: The Method of Composition {#moc}
-
-In analysis models, we have latent variables in both sides of equations, public suppport for democracy, democracy indices, and corruption index (The latter one is included in APSR analyses).
+# The Method of Composition {#moc}
+
+In analysis models, we have latent variables in both sides of equations, public support for democracy, democracy indices, and corruption index (The latter one is included in APSR analyses).
 Since measurement uncertainty associated with these latent variables can propagate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing "Method of Composition" [@Tanner1993,p52], which has been applied in analyses with latent variables [@Treier2008;@caughey2018;@Kastellec2015].
@@
 
-# Appendix C: Secondary Models from Claassen (2020$a$, 2020$b$)
-
-```{r formatResult-AJPS-dup}
+# DCPO Replication {#dcpo}
+
+As a further test of the classic arguments on democracy and public support, we apply the superior DCPO model to a bigger data set.
+The DCPO model has several advantages over the @Claassen2019 model used in Claassen [-@Claassen2020a; -@Claassen2020b].
+First, while the @Claassen2019 model dichotomizes responses and so discards some information provided by 50 of the 52 survey items employed in Claassen [-@Claassen2020a; -@Claassen2020b], the DCPO model makes use of all of the information available from these ordinal items [@Solt2020a, p.5].
+Second, as the DCPO model includes both parameters for the dispersion of each survey item and for the standard deviation of aggregate public opinion in each country-year, it is a complete population-level item-response model and so, unlike the @Claassen2019 model, is explicitly derived from an individual-level model of survey responses [@Solt2020a, pp.3-4; see also @McGann2014].
+Third, to produce more sensible estimates of uncertainty for observations at the extremes of the scale [see @Linzer2015, p.229], the DCPO model places bounds on its estimates of public opinion [@Solt2020a, p.8].
+Further commending the DCPO model to us---and demonstrating that its advantages make a difference---the validation tests in @Solt2020a [, pp.10-12] reveal that it fits survey data on democratic support better than the @Claassen2019 model does.
+
+We employ the superior DCPO model to the expanded data using the `DCPO` package for R [@Solt2020b].
+We use the estimated public support from DCPO model to replicate analyses by following the same steps.
+Then, we compare the DCPO results with two types of replication results from Model 5: estimation of original data and without uncertainty and estimation of expanded data and with uncertainty.
+
+The comparison is presented in Appendix B.
+Still, even with the superior DCPO model and expanded data, there is no evidence to support that public support can sustain democratic development or public support responds thermostatically to changes in democracy.
+
+```{r dcpo-AJPS, eval=FALSE}
+
+dcpo_Ajps <- purrr::map(1:900, function(anEntry) {
+  dcpo_ajps[[anEntry]] %>% 
+    plm::pdata.frame(index = c("country", "year")) %>%
+    rename(SupDem_trim =theta_trim,
+           Regime_VD = Vdem_regime,
+           Pr_Muslim = muslism_prop_2010,
+           Res_cp_WDI_di = dependence_pc_di,
+           lnGDP_imp = lg_imp_mdpgdp,
+           GDP_imp_grth = mdprgdp_grwth,
+           firstyear = first_year,
+           Libdem_VD = Vdem_libdem,
+           Libdem_m1 = Vdem_libdem_m1,
+           Libdem_m2 = Vdem_libdem_m2,
+           ChgDem = Chgdem,
+           UpChgDem = upchgdem,
+           DwnChgDem = downchgdem,
+           Libdem_regUN = Region_libdem,
+           Libdem_regUN_m1 = Region_libdem_m1)
+})
+
+result_dcpoUncertain  <- map(ls_mod_ajpsCLS[1:2], function(aMod){
+  result <- methodComposition1(dcpo_Ajps,aMod)
+})
+
+names(result_dcpoUncertain) <- c("pooled", "pooled-regime")
+
+result_dcpoUncertain_gmm  <- map(ls_mod_ajpsCLS[3:4], function(aMod){
+  result <- methodComposition2(dcpo_Ajps,aMod)
+})
+names(result_dcpoUncertain_gmm) <- c("gmm", "gmm-regime")
+
+mocresult_dcpoAJPS <- append(result_dcpoUncertain, result_dcpoUncertain_gmm)
+saveRDS(mocresult_dcpoAJPS, file =here("output","estimates_moc_dcpoAJPS.RDS"))
+
+```
+
+```{r dcpoFormatResult-AJPS}
 result_pooled <- bind_rows(
-  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Original"),
- mutate(MOCsumm(mocresult_correctAJPS[["pooled"]]), model = "W. Uncertainty"),
- mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), model = "Uncertainty+Expanded Data")
-) %>% 
-  mutate(type = "Pooled")
+    mutate(result_clsAJPS[["pooled"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), submodel = "Uncertainty & More Data"),
+    mutate(MOCsumm(mocresult_dcpoAJPS[["pooled"]]), submodel = "Uncertainty & DCPO")
+) %>% 
+    mutate(type = "Pooled~OLS",
+           model = "Model 1 (Pooled OLS)")
 
 result_gmm <- bind_rows(
-  mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_correctAJPS[["gmm"]]), model = "W. Uncertainty"),
-  mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), model = "Uncertainty+Expanded Data")
-) %>% 
-  mutate(type = "GMM")
+    mutate(result_clsAJPS[["gmm"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), submodel = "Uncertainty & More Data"),
+    mutate(MOCsumm(mocresult_dcpoAJPS[["gmm"]]), submodel = "Uncertainty & DCPO")
+) %>% 
+    mutate(type = "System~GMM",
+           model = "Model 3 (System GMM)")
 
@@
             time = 6), 
-    type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Original", "W. Uncertainty", "Uncertainty+Expanded Data")))
+        type = factor(type, levels = c("Pooled~OLS", "System~GMM")),
+        submodel = factor(submodel, levels = c("Point Estimates Only", "Uncertainty & More Data", "Uncertainty & DCPO")),
+        model = factor(model, levels = paste0("Model ", rep(1:4), rep(c(" (Pooled OLS)", " (System GMM)"), each = 2)))
+    )
 
 result_regime <- bind_rows(
-  mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_correctAJPS[["pooled-regime"]]), model = "W. Uncertainty"),
-  mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), model = "Uncertainty+Expanded Data")
-) %>% 
-  mutate(type = "Pooled")
+    mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), submodel = "Uncertainty & More Data"),
+  mutate(MOCsumm(mocresult_dcpoAJPS[["pooled-regime"]]), submodel = "Uncertainty & DCPO")
+) %>% 
+    mutate(type = "Pooled~OLS",
+           model = "Model 2 (Pooled OLS)")
 
 result_regimeGmm <- bind_rows(
-  mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_correctAJPS[["gmm-regime"]]), model = "W. Uncertainty"),
- mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), model = "Uncertainty+Expanded Data")
+    mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), submodel = "Uncertainty & More Data"),
+ mutate(MOCsumm(mocresult_dcpoAJPS[["gmm-regime"]]), submodel = "Uncertainty & DCPO")
 )%>% 
-  mutate(type = "GMM")
+    mutate(type = "System~GMM",
+           model = "Model 4 (System GMM)")
 
@@
             time = 6), 
-    type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data")))
-
-result_ajpsRegime <- result_regimeAJPS %>%
-    filter(type == "Pooled") %>% 
-    mutate(type = "Regime Specified")
-
-```
-
-```{r coefName-AJPS-dup}
+        type = factor(type, levels = c("Pooled~OLS", "System~GMM")),
+        submodel = factor(submodel, levels = c("Point Estimates Only", "Uncertainty & More Data", "Uncertainty & DCPO")),
+        model = factor(model, levels = paste0("Model ", rep(1:4), rep(c(" (Pooled OLS)", " (System GMM)"), each = 2))))
+
+```
+
+```{r dcopCoefName-AJPS}
 index_coefName <- c(
@@
     `Democracy\n (t-2)` = "Democracy[t-2]",
-    `Support\n (t-1)` = "Support[t-1]",
-    `Support\n demo only\n (t-1)` = "Support[t-1](demo~only)",
-    `Support\n auto only\n (t-1)` = "Support[t-1](auto~only)",
+    `Support\n (t-1)` = "Democratic~Support[t-1]~(all~regimes)",
+    `Support\n demo only\n (t-1)` = "Democratic~Support[t-1]~(democracies)",
+    `Support\n auto only\n (t-1)` = "Democratic~Support[t-1]~(autocracies)",
     `Log GDP\n per capita\n (t-1)` = "Log~GDP~per~capita[t-1]",
-    `GDP per\n capita growth\n (t-1)` = "GDP~per~capita~growth[t-1]",
-    `Regional\n democracy\n (t-1)` = "Regional~democracy[t-1]",
+    `GDP per\n capita growth\n (t-1)` = "GDP~per~capita~Growth[t-1]",
+    `Regional\n democracy\n (t-1)` = "Regional~Democracy[t-1]",
     `Percent\n Muslim\n (t-1)` = "Percent~Muslim[t-1]",
-    `Resource\n dependence\n (t-1)` = "Resource~dependence[t-1]"
-)
-```
-
-```{r plot-mocAJPS, fig.cap= "The Effect of Public Support on Democracy ", eval = TRUE, fig.width=7, fig.height=10}
-terms <- factor(rev(
+    `Resource\n dependence\n (t-1)` = "Resource~Dependence[t-1]"
+)
+```
+
+```{r plot-dcpoAJPS, fig.cap= "The Effect of Public Support on Democracy", fig.width=5, fig.height=10, fig.align='center'}
+df_plot <- bind_rows(result_pooledAJPS, result_regimeAJPS) %>% 
+  mutate(term = index_coefName[term0], 
+           term = factor(term, levels = unique(index_coefName)))
+
+ajps_caption <- "Replications of Claassen (2020a), Table 1, 128, with DCPO."
+
+small_multiple(df_plot, dot_args = list(size = .9, fatten = 1)) +
+    geom_hline(yintercept = 0, colour = "grey50", linetype = 2) +
+    scale_color_grey(start = 0.8, end = 0.4, 
+                     name = "Replication",
+                     breaks=c("Point Estimates Only", "With Uncertainty", "Uncertainty & More Data"),
+                     labels=c("Point Estimates Only", "With Uncertainty", "Uncertainty & More Data")) +
+    theme(axis.text.x  = element_text(angle = 90, hjust = .5),
+          strip.text.y.left = element_text(angle = 0),
+          legend.position = c(-0.06, -.01),
+          legend.justification = c(1, 1), 
+          legend.title = element_text(size = 9, face = "bold"),
+          legend.title.align = 0.5,
+          legend.text = element_text(size = 9),
+          legend.background = element_rect(color="gray90"),
+          legend.spacing = unit(-5, "pt"),
+          legend.key.size = unit(8, "mm"),
+          plot.title = element_text(hjust = 1.4),
+          plot.caption = element_text(size = 10, hjust = 0.7, margin = margin(t=15))) +
+  guides(color = guide_legend(override.aes = list(size=.3))) +
+  ggtitle("Dependent Variable: Level of Democracy") +
+  labs(caption = ajps_caption)
+```
+
+```{r dcpo-APSR, eval=FALSE}
+dcpo_APSR <- purrr::map(1:900, function(anEntry) {
+  dcpo_apsr[[anEntry]] %>%
+    plm::pdata.frame(index = c("country", "year")) %>%
+    rename(
+      SupDem_trim = theta_trim,
+      First_yr = first_year,
+      Libdem_z = Vdem_libdem_z,
+      Polyarchy_z = Vdem_polyarchy_z,
+      Liberal_z = Vdem_liberal_z,
+      Corrup_TI_z = corruption_z,
+      lnGDP_imp = lg_imp_mdpgdp
+    )
+})
+
+mocdcpo_APSR  <- map(ls_mod_apsrCLS, function(aMod) {
+  result <- methodComposition3(dcpo_APSR, aMod)
+})
+
+names(mocdcpo_APSR) <-
   c(
-        "Democracy[t-1]",
-        "Democracy[t-2]",
-        "Support[t-1]",
-        "Log~GDP~per~capita[t-1]",
-        "GDP~per~capita~growth[t-1]",
-        "Regional~democracy[t-1]",
-        "Percent~Muslim[t-1]",
-        "Resource~dependence[t-1]"
-    )
-), levels =
-    rev(
-        c(
-            "Democracy[t-1]",
-            "Democracy[t-2]",
-            "Support[t-1]",
-            "Log~GDP~per~capita[t-1]",
-            "GDP~per~capita~growth[t-1]",
-            "Regional~democracy[t-1]",
-            "Percent~Muslim[t-1]",
-            "Resource~dependence[t-1]"
-        )
-    ))
-
-plot_AJPS1 <-
-    dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms))) +
-    labs(title = "DV: V-Dem Liberal Democracy Index",
-         subtitle = "Pooled") +
-    facet_wrap( ~ type, scales = "free_x") +
-    theme(legend.position = "none")  +
-    scale_color_gb(palette = "digitMixed")
-
-terms2 <- factor(rev(
-    c(
-        "Democracy[t-1]",
-        "Democracy[t-2]",
-        "Support[t-1] (democracies~only)",
-        "Support[t-1] (autocracies~only)",
-        "Log~GDP~per~capita[t-1]",
-        "GDP~per~capita~growth[t-1]",
-        "Regional~democracy[t-1]",
-        "Percent~Muslim[t-1]",
-        "Resource~dependence[t-1]"
-    )
-), levels =
-    rev(
-        c(
-            "Democracy[t-1]",
-            "Democracy[t-2]",
-            "Support[t-1] (democracies~only)",
-            "Support[t-1] (autocracies~only)",
-            "Log~GDP~per~capita[t-1]",
-            "GDP~per~capita~growth[t-1]",
-            "Regional~democracy[t-1]",
-            "Percent~Muslim[t-1]",
-            "Resource~dependence[t-1]"
-        )
-    ))
-
-plot_AJPS2 <-
-    dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms2))) +
-    labs(title = "",
-         subtitle = "Regime Specified") +
-    facet_wrap( ~ type, scales = "free_x") +
-    theme(legend.position = "bottom",
-          legend.title = element_blank())  +
-   scale_color_gb(palette = "digitMixed")
-
-legend <- get_legend(plot_AJPS2)
-
-plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
-
-grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
-```
-
-\blandscape
-
-```{r formatResult-APSR-dup}
+    "pooled1",
+    "pooled-regime1",
+    "pooled2",
+    "pooled-regime2",
+    "fd1",
+    "fd-regime1",
+    "fd2",
+    "fd-regime2"
+  )
+
+saveRDS(mocdcpo_APSR,
+        file = here::here("output", "estimates_moc_dcpoAPSR.RDS"))
+```
+
+```{r dcpoFormatResult-APSR}
 # Pooled---------------------------------------
@@
 result_ecm1 <- bind_rows(
-  mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["pooled1"]]), model = "W. Uncertainty"),
-  mutate(MOCsumm2(mocresult_expAPSR[["pooled1"]]), model = "Uncertainty+Expanded Data")
-) %>% 
-  mutate(type = "ECM")
+    mutate(result_clsAPSR[["pooled1"]][[1]][, 1:3], submodel = "Point Estimates Only"),
+    mutate(MOCsumm2(mocresult_expAPSR[["pooled1"]]), submodel = "Uncertainty & More Data"),
+    mutate(MOCsumm2(mocdcpo_APSR[["pooled1"]]), submodel = "Uncertainty & DCPO")
+) %>%
+    mutate(type = "Error-Correction Model",
+           model = "Model 1.1 (ECM)")
 
 result_fd1 <- bind_rows(
-  mutate(result_clsAPSR[["fd1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["fd1"]]), model = "W. Uncertainty"),
-  mutate(MOCsumm2(mocresult_expAPSR[["fd1"]]), model = "Uncertainty+Expanded Data")
-) %>% 
-  mutate(type = "First Difference")
+    mutate(result_clsAPSR[["fd1"]][[1]][, 1:3], submodel = "Point Estimates Only"),
+    mutate(MOCsumm2(mocresult_expAPSR[["fd1"]]), submodel = "Uncertainty & More Data"),
+    mutate(MOCsumm2(mocdcpo_APSR[["fd1"]]), submodel = "Uncertainty & DCPO")
+) %>%
+    mutate(type = "First-Difference Model",
+           model = "Model 1.3 (FD)")
 
@@
     mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
+        term0 = c(rep(
+            c(
+                "Democratic Mood\n (t-1)",
                 "Democratic Mood\n (t-2)",
@@
                 "Log GDP\n per capita\n (Difference)",
-        "Log GDP\n (t-1)"),
-      time = 3),
+                "Log GDP\n (t-1)"
+            ),
+            time = 3
+        ),
         rep(
-        c("Liberal Democracy\n (Difference)", 
-          "Log GDP\n per capita\n (Difference)"), 
+            c(
+                "Liberal Democracy\n (Difference)",
+                "Log GDP\n per capita\n (Difference)"
+            ),
             time = 3
         )),
-    type = factor(type,  levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data"))
-  )
-
-result_apsrPooled <- result_APSR1 %>% 
-    filter(type == "ECM") %>% 
-    mutate(type = "Pooled")
+        type = factor(
+            type,
+            levels = c("Error-Correction Model", "First-Difference Model")
+        ),
+        submodel = factor(
+            submodel,
+            levels = c(
+                "Point Estimates Only",
+                "Uncertainty & More Data",
+                "Uncertainty & DCPO"
+            )
+        ),
+        model = factor(model, levels = paste0(
+            "Model ",
+            rep(1:2, each = 4), ".", rep(1:4, 2),
+            " (",
+            rep(c("ECM", "ECM", "FD", "FD"), 2),
+            ")"
+        ))
+    )
 
@@
 result_ecmReg1 <- bind_rows(
-  mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime1"]]), model = "W. Uncertainty"),
-  mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime1"]]), model = "Uncertainty+Expanded Data")
-) %>% 
-  mutate(type = "ECM")
+    mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime1"]]), submodel = "Uncertainty & More Data"),
+  mutate(MOCsumm2(mocdcpo_APSR[["pooled-regime1"]]), submodel = "Uncertainty & DCPO")
+) %>% 
+    mutate(type = "Error-Correction Model",
+           model = "Model 2.1 (ECM)")
 
 result_fdReg1 <- bind_rows(
-  mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime1"]]), model = "W. Uncertainty"),
-  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime1"]]), model = "Uncertainty+Expanded Data")
-) %>% 
-  mutate(type = "First Difference")
+    mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(MOCsumm2(mocresult_expAPSR[["fd-regime1"]]), submodel = "Uncertainty & More Data"),
+  mutate(MOCsumm2(mocdcpo_APSR[["fd-regime1"]]), submodel = "Uncertainty & DCPO")
+) %>% 
+    mutate(type = "First-Difference Model",
+           model = "Model 2.3 (FD)")
 
@@
     mutate(
-    term = c(rep(
+        term0 = c(rep(
             c("Democratic Mood\n (t-1)",
@@
             )),
-    type = factor(type,  levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data"))
-  )
-
-result_apsrRegime <- result_RegAPSR1 %>% 
-    filter(type == "ECM") %>% 
-    mutate(type = "Institution Specified")
+        type = factor(type,  levels = c("Error-Correction Model", "First-Difference Model")),
+        submodel = factor(submodel, levels = c("Point Estimates Only", "Uncertainty & More Data", "Uncertainty & DCPO")),
+        model = factor(model, levels = paste0("Model ", 
+                                              rep(1:2, each = 4), ".", rep(1:4, 2),
+                                              " (",
+                                              rep(c("ECM", "ECM", "FD", "FD"), 2),
+                                              ")"))
+    )
 
@@
 result_ecm2 <- bind_rows(
-  mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["pooled2"]]), model = "W. Uncertainty"),
-  mutate(MOCsumm2(mocresult_expAPSR[["pooled2"]]), model = "Uncertainty+Expanded Data")
-) %>% 
-  mutate(type = "ECM")
+    mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(MOCsumm2(mocresult_expAPSR[["pooled2"]]), submodel = "Uncertainty & More Data"),
+  mutate(MOCsumm2(mocdcpo_APSR[["pooled2"]]), submodel = "Uncertainty & DCPO")
+) %>% 
+    mutate(type = "Error-Correction Model",
+           model = "Model 1.2 (ECM)")
 
 result_fd2 <- bind_rows(
-  mutate(result_clsAPSR[["fd2"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["fd2"]]), model = "W. Uncertainty"),
-  mutate(MOCsumm2(mocresult_expAPSR[["fd2"]]), model = "Uncertainty+Expanded Data")
-) %>% 
-  mutate(type = "First Difference")
+    mutate(result_clsAPSR[["fd2"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(MOCsumm2(mocresult_expAPSR[["fd2"]]), submodel = "Uncertainty & More Data"),
+  mutate(MOCsumm2(mocdcpo_APSR[["fd2"]]), submodel = "Uncertainty & DCPO")
+) %>% 
+    mutate(type = "First-Difference Model",
+           model = "Model 1.4 (FD)")
 
@@
             )),
-    type = factor(type,  levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data"))
+        type = factor(type,  levels = c("Error-Correction Model", "First-Difference Model")),
+        submodel = factor(submodel, levels = c("Point Estimates Only", "Uncertainty & More Data","Uncertainty & DCPO")),
+        model = factor(model, levels = paste0("Model ", 
+                                                      rep(1:2, each = 4), ".", rep(1:4, 2),
+                                                      " (",
+                                                      rep(c("ECM", "ECM", "FD", "FD"), 2),
+                                                      ")"))
     )
@@
 result_ecmReg2 <- bind_rows(
-  mutate(result_clsAPSR[["pooled-regime2"]][[1]][,1:3], model = "Original"),
- mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime2"]]), model = "W. Uncertainty"),
-  mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime2"]]), model = "Uncertainty+Expanded Data")) %>%
-  mutate(type = "ECM")
+    mutate(result_clsAPSR[["pooled-regime2"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime2"]]), submodel = "Uncertainty & More Data"),
+  mutate(MOCsumm2(mocdcpo_APSR[["pooled-regime2"]]), submodel = "Uncertainty & DCPO")) %>%
+    mutate(type = "Error-Correction Model",
+           model = "Model 2.2 (ECM)")
 
 result_fdReg2 <- bind_rows(
-  mutate(result_clsAPSR[["fd-regime2"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime2"]]), model = "W. Uncertainty"),
-  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime2"]]), model = "Uncertainty+Expanded Data")) %>% 
-  mutate(type = "First Difference")
+    mutate(result_clsAPSR[["fd-regime2"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(MOCsumm2(mocresult_expAPSR[["fd-regime2"]]), submodel = "Uncertainty & More Data"),
+  mutate(MOCsumm2(mocdcpo_APSR[["fd-regime2"]]), submodel = "Uncertainty & DCPO")) %>% 
+    mutate(type = "First-Difference Model",
+           model = "Model 2.4 (FD)")
 
@@
             )),
-    type = factor(type,  levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data"))
-  )
-```
-
-```{r coefName-APSR-dup}
+        type = factor(type,  levels = c("Error-Correction Model", "First-Difference Model")),
+        submodel = factor(submodel, levels = c("Point Estimates Only", "Uncertainty & More Data", "Uncertainty & DCPO")),
+        model = factor(model, levels = paste0("Model ", 
+                                              rep(1:2, each = 4), ".", rep(1:4, 2),
+                                              " (",
+                                              rep(c("ECM", "ECM", "FD", "FD"), 2),
+                                              ")"))
+    )
+```
+
+```{r dcpoCoefName-APSR}
 index_coefName <- c(
-    `Democratic Mood\n (t-1)` = "Support[t-1]",
-    `Democratic Mood\n (t-2)` = "Support[t-2]",
+    `Democratic Mood\n (t-1)` = "Democratic~Support[t-1]",
+    `Democratic Mood\n (t-2)` = "Democratic~Support[t-2]",
     `Liberal Democracy\n (Difference)` = "Delta~Liberal~democracy",
-    `Liberal Democracy\n (t-1)` = "Liberal~democracy[t-1]",
-    `Electoral Democracy\n (Difference)` = "Delta~Electoral~democracy",
-    `Electoral Democracy\n (t-1)` = "Electoral~democracy[t-1]",
-    `Minoritarian Democracy\n (Difference)` = "Delta~Minoritarian~democracy",
-    `Minoritarian Democracy\n (t-1)` = "Minoritarian~democracy[t-1]",
+    `Liberal Democracy\n (t-1)` = "Liberal~Democracy[t-1]",
+    `Electoral Democracy\n (Difference)` = "Delta~Electoral~Democracy",
+    `Electoral Democracy\n (t-1)` = "Electoral~Democracy[t-1]",
+    `Minoritarian Democracy\n (Difference)` = "Delta~Minoritarian~Democracy",
+    `Minoritarian Democracy\n (t-1)` = "Minoritarian~Democracy[t-1]",
     `Log GDP\n per capita\n (Difference)` = "Delta~Log~GDP~per~capita",
-    `Log GDP\n (t-1)` = "Log~GDP[t-1]"
-)
-```
-
-```{r plot-mocAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", eval = TRUE, fig.width=10, fig.height=10}
-terms1 <- factor(rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Liberal~democracy",
-        "Liberal~democracy[t-1]",
-        "Delta~Log~GDP~per~capita",
-        "Log~GDP[t-1]"
-    )
-),
-levels = rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Liberal~democracy",
-        "Liberal~democracy[t-1]",
-        "Delta~Log~GDP~per~capita",
-        "Log~GDP[t-1]"
-    )
-), 
-labels = rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Liberal~Dem",
-        "Liberal~Dem[t-1]",
-        "Delta~Log~GDP~per~capita",
-        "Log~GDP[t-1]"
-    )
-))
-
-plot_APSR1 <-
-    dwplot(result_APSR1, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms1))) +
-    labs(title = "DV: The Change of Public Support for Democracy",
-         subtitle = "Pooled") +
-    facet_wrap( ~ type, drop = T, scales = "free_x") +
-    theme(legend.position = "none")  +
-   scale_color_gb(palette = "digitMixed")
-
-terms3 <- factor(rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Electoral~democracy",
-        "Electoral~democracy[t-1]",
-        "Delta~Minoritarian~democracy",
-        "Minoritarian~democracy[t-1]",
-        "Delta~Log~GDP~per~capita",
-        "Log~GDP[t-1]"
-    )
-),
-levels = rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Electoral~democracy",
-        "Electoral~democracy[t-1]",
-        "Delta~Minoritarian~democracy",
-        "Minoritarian~democracy[t-1]",
-        "Delta~Log~GDP~per~capita",
-        "Log~GDP[t-1]"
-    )
-),
-labels = rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Electoral",
-        "Electoral[t-1]",
-        "Delta~Minoritarian",
-        "Minoritarian[t-1]",
-        "Delta~Log~GDP~per~capita",
-        "Log~GDP[t-1]"
-    )
-)
-)
-
-plot_RegAPSR1 <-
-    dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms3))) +
-    labs(title = "",
-         subtitle = "Institution Specified") +
-    facet_wrap( ~ type, scales = "free_x") +
-    theme(legend.position = "none")  +
-    scale_color_gb(palette = "digitMixed")
-
-terms2 <- factor(rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Liberal~democracy",
-        "Liberal~democracy[t-1]",
-        "Delta~Log~GDP~per~capita",
-        "Log~GDP[t-1]",
-        "Delta~Corruption",
-        "Corruption[t-1]"
-    )
-),
-levels = rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Liberal~democracy",
-        "Liberal~democracy[t-1]",
-        "Delta~Log~GDP~per~capita",
-        "Log~GDP[t-1]",
-        "Delta~Corruption",
-        "Corruption[t-1]"
-    )
-),
-labels = rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Liberal~Dem",
-        "Liberal~Dem[t-1]",
-        "Delta~Log~GDP~per~capita",
-        "Log~GDP[t-1]",
-        "Delta~Corruption",
-        "Corruption[t-1]"
-    )
-))
-
-plot_APSR2 <-
-    dwplot(result_APSR2, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms2))) +
-    labs(title = "",
-         subtitle = "W. Corruption") +
-    facet_wrap( ~ type, scales = "free_x") +
-    theme(legend.position = "none")  +
-    scale_color_gb(palette = "digitMixed")
-
-terms4 <- factor(rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Electoral~democracy",
-        "Electoral~democracy[t-1]",
-        "Delta~Minoritarian~democracy",
-        "Minoritarian~democracy[t-1]",
-        "Delta~Log~GDP",
-        "Log~GDP[t-1]",
-        "Delta~Corruption",
-        "Corruption[t-1]"
-    )
-),
-levels = rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Electoral~democracy",
-        "Electoral~democracy[t-1]",
-        "Delta~Minoritarian~democracy",
-        "Minoritarian~democracy[t-1]",
-        "Delta~Log~GDP",
-        "Log~GDP[t-1]",
-        "Delta~Corruption",
-        "Corruption[t-1]"
-    )
-),
-labels = rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Electoral",
-        "Electoral[t-1]",
-        "Delta~Minoritarian",
-        "Minoritarian[t-1]",
-        "Delta~Log~GDP",
-        "Log~GDP[t-1]",
-        "Delta~Corruption",
-        "Corruption[t-1]"
-    )
-))
-
-plot_RegAPSR2 <-
-    dwplot(result_RegAPSR2, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms4))) +
-    labs(title = "",
-         subtitle = "Institution Specified w. Corruption") +
-    facet_wrap( ~ type, scales = "free_x") +
-    theme(legend.position = "bottom",
-          legend.title = element_blank())  +
-    scale_color_gb(palette = "digitMixed")
-
-legend <- get_legend(plot_RegAPSR2)
-
-plot_RegAPSR2 <- plot_RegAPSR2 + theme(legend.position = "none")
-
-grid.arrange(plot_APSR1,
-             plot_APSR2,
-             plot_RegAPSR1,
-             plot_RegAPSR2,
-             legend,
-             ncol = 2)
-```
-
-\elandscape
-
-Figure \@ref(fig:plot-mocAJPS) and \@ref(fig:plot-mocAPSR) presents the results of using MOC to engage measurement error. 
-The results are consistent as we gained from the MO method (cf. Figure \@ref(fig:plot-mainAJPS) and \@ref(fig:plot-mainAPSR)).
-
-# Appendix D: DCPO Replication {#dcpo}
-
-As a further test of the classic arguments on democracy and public support, we apply the superior DCPO model to a bigger data set.
-The DCPO model has several advantages over the @Claassen2019 model used in Claassen [-@Claassen2020a; -@Claassen2020b].
-First, while the @Claassen2019 model dichotomizes responses and so discards some information provided by 50 of the 52 survey items employed in Claassen [-@Claassen2020a; -@Claassen2020b], the DCPO model makes use of all of the information available from these ordinal items [@Solt2020a, 5].
-Second, as the DCPO model includes both parameters for the dispersion of each survey item and for the standard deviation of aggregate public opinion in each country-year, it is a complete population-level item-response model and so, unlike the @Claassen2019 model, is explicitly derived from an individual-level model of survey responses [@Solt2020a, 3-4; see also @McGann2014].
-Third, to produce more sensible estimates of uncertainty for observations at the extremes of the scale [see @Linzer2015, 229], the DCPO model places bounds on its estimates of public opinion [@Solt2020a, 8].
-Further commending the DCPO model to us---and demonstrating that its advantages make a difference---the validation tests in @Solt2020a [, 10-12] reveal that it fits survey data on democratic support better than the @Claassen2019 model does.
-
-We employ the superior DCPO model to the expanded data using the `DCPO` package for R [@Solt2020b].
-We use the estimated public support from DCPO model to replicate analyses by following the same steps.
-Then, we compare the DCPO results with two types of replication results from Model 5: estimation of original data and without uncertainty and estimation of expanded data and with uncertainty.
-
-The comparison is presented in Appendix B.
-Still, even with the superior DCPO model and expanded data, there is no evidence to support that public support can sustain democratic development or public support responds thermostatically to changes in democracy.
-
-```{r moc-dcpoAJPS, eval=FALSE}
-
-dcpo_Ajps <- purrr::map(1:900, function(anEntry) {
-  dcpo_ajps[[anEntry]] %>% 
-    plm::pdata.frame(index = c("country", "year")) %>%
-    rename(SupDem_trim =theta_trim,
-           Regime_VD = Vdem_regime,
-           Pr_Muslim = muslism_prop_2010,
-           Res_cp_WDI_di = dependence_pc_di,
-           lnGDP_imp = lg_imp_mdpgdp,
-           GDP_imp_grth = mdprgdp_grwth,
-           firstyear = first_year,
-           Libdem_VD = Vdem_libdem,
-           Libdem_m1 = Vdem_libdem_m1,
-           Libdem_m2 = Vdem_libdem_m2,
-           ChgDem = Chgdem,
-           UpChgDem = upchgdem,
-           DwnChgDem = downchgdem,
-           Libdem_regUN = Region_libdem,
-           Libdem_regUN_m1 = Region_libdem_m1)
-})
-
-result_dcpoUncertain  <- map(ls_mod_ajpsCLS[1:2], function(aMod){
-  result <- methodComposition1(dcpo_Ajps,aMod)
-})
-
-names(result_dcpoUncertain) <- c("pooled", "pooled-regime")
-
-result_dcpoUncertain_gmm  <- map(ls_mod_ajpsCLS[3:4], function(aMod){
-  result <- methodComposition2(dcpo_Ajps,aMod)
-})
-names(result_dcpoUncertain_gmm) <- c("gmm", "gmm-regime")
-
-mocresult_dcpoAJPS <- append(result_dcpoUncertain, result_dcpoUncertain_gmm)
-saveRDS(mocresult_dcpoAJPS, file =here("output","estimates_moc_dcpoAJPS.RDS"))
-
-```
-
-```{r formatDCPOResult-AJPS}
-result_pooled <- bind_rows(
-  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Original"),
- mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), model = "Uncertainty+ExpData"),
- mutate(MOCsumm(mocresult_dcpoAJPS[["pooled"]]), model = "Uncertainty+DCPO+ExpData")
-) %>% 
-  mutate(type = "Pooled")
-
-result_gmm <- bind_rows(
-  mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), model = "Uncertainty+ExpData"),
-  mutate(MOCsumm(mocresult_dcpoAJPS[["gmm"]]), model = "Uncertainty+DCPO+ExpData")
-) %>% 
-  mutate(type = "GMM")
-
-result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = rep(
-      c("Democracy\n (t-1)",
-        "Democracy\n (t-2)",
-        "Support\n (t-1)",
-        "Log GDP\n per capita\n (t-1)",
-        "GDP per\n capita growth\n (t-1)",
-        "Regional\n democracy\n (t-1)",
-        "Percent\n Muslim\n (t-1)",
-        "Resource\n dependence\n (t-1)"),
-      time = 6), 
-    type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Original", "Uncertainty+ExpData", "Uncertainty+DCPO+ExpData")))
-
-result_ajpsPooled <- result_pooledAJPS %>% 
-    filter(type == "Pooled")
-
-result_regime <- bind_rows(
-  mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), model = "Uncertainty+ExpData"),
-  mutate(MOCsumm(mocresult_dcpoAJPS[["pooled-regime"]]), model = "Uncertainty+DCPO+ExpData")
-) %>% 
-  mutate(type = "Pooled")
-
-result_regimeGmm <- bind_rows(
-  mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), model = "Uncertainty+ExpData"),
- mutate(MOCsumm(mocresult_dcpoAJPS[["gmm-regime"]]), model = "Uncertainty+DCPO+ExpData")
-)%>% 
-  mutate(type = "GMM")
-
-result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = rep(
-      c("Democracy\n (t-1)",
-        "Democracy\n (t-2)",
-        "Support\n demo only\n (t-1)",
-        "Support\n auto only\n (t-1)",
-        "Log GDP\n per capita\n (t-1)",
-        "GDP per\n capita growth\n (t-1)",
-        "Regional\n democracy\n (t-1)",
-        "Percent\n Muslim\n (t-1)",
-        "Resource\n dependence\n (t-1)"),
-      time = 6), 
-    type = factor(type, levels = c("Pooled", "GMM")),
-    model = factor(model, levels = c("Original","Uncertainty+ExpData", "Uncertainty+DCPO+ExpData")))
-
-result_ajpsRegime <- result_regimeAJPS %>%
-    filter(type == "Pooled") %>% 
-    mutate(type = "Regime Specified")
-
-```
-
-```{r coefName-dcpoAJPS-dup}
-index_coefName <- c(
-    `Democracy\n (t-1)` = "Democracy[t-1]",
-    `Democracy\n (t-2)` = "Democracy[t-2]",
-    `Support\n (t-1)` = "Support[t-1]",
-    `Support\n demo only\n (t-1)` = "Support[t-1](demo~only)",
-    `Support\n auto only\n (t-1)` = "Support[t-1](auto~only)",
-    `Log GDP\n per capita\n (t-1)` = "Log~GDP~per~capita[t-1]",
-    `GDP per\n capita growth\n (t-1)` = "GDP~per~capita~growth[t-1]",
-    `Regional\n democracy\n (t-1)` = "Regional~democracy[t-1]",
-    `Percent\n Muslim\n (t-1)` = "Percent~Muslim[t-1]",
-    `Resource\n dependence\n (t-1)` = "Resource~dependence[t-1]"
-)
-```
-
-```{r plotdcpo-mocAJPS, fig.cap= "The Effect of Public Support on Democracy ", eval = TRUE, fig.width=7, fig.height=10}
-terms <- factor(rev(
-    c(
-        "Democracy[t-1]",
-        "Democracy[t-2]",
-        "Support[t-1]",
-        "Log~GDP~per~capita[t-1]",
-        "GDP~per~capita~growth[t-1]",
-        "Regional~democracy[t-1]",
-        "Percent~Muslim[t-1]",
-        "Resource~dependence[t-1]"
-    )
-), levels =
-    rev(
-        c(
-            "Democracy[t-1]",
-            "Democracy[t-2]",
-            "Support[t-1]",
-            "Log~GDP~per~capita[t-1]",
-            "GDP~per~capita~growth[t-1]",
-            "Regional~democracy[t-1]",
-            "Percent~Muslim[t-1]",
-            "Resource~dependence[t-1]"
-        )
-    ))
-
-plot_AJPS1 <-
-    dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms))) +
-    labs(title = "DV: V-Dem Liberal Democracy Index",
-         subtitle = "Pooled") +
-    facet_wrap( ~ type, scales = "free_x") +
-    theme(legend.position = "none")  +
-    scale_color_gb(palette = "digitMixed")
-
-terms2 <- factor(rev(
-    c(
-        "Democracy[t-1]",
-        "Democracy[t-2]",
-        "Support[t-1] (democracies~only)",
-        "Support[t-1] (autocracies~only)",
-        "Log~GDP~per~capita[t-1]",
-        "GDP~per~capita~growth[t-1]",
-        "Regional~democracy[t-1]",
-        "Percent~Muslim[t-1]",
-        "Resource~dependence[t-1]"
-    )
-), levels =
-    rev(
-        c(
-            "Democracy[t-1]",
-            "Democracy[t-2]",
-            "Support[t-1] (democracies~only)",
-            "Support[t-1] (autocracies~only)",
-            "Log~GDP~per~capita[t-1]",
-            "GDP~per~capita~growth[t-1]",
-            "Regional~democracy[t-1]",
-            "Percent~Muslim[t-1]",
-            "Resource~dependence[t-1]"
-        )
-    ))
-
-plot_AJPS2 <-
-    dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms2))) +
-    labs(title = "",
-         subtitle = "Regime Specified") +
-    facet_wrap( ~ type, scales = "free_x") +
-    theme(legend.position = "bottom",
-          legend.title = element_blank())  +
-   scale_color_gb(palette = "digitMixed")
-
-legend <- get_legend(plot_AJPS2)
-
-plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
-
-grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
-```
-
-```{r dcpo-APSR, eval=FALSE}
-dcpo_APSR <- purrr::map(1:900, function(anEntry) {
-  dcpo_apsr[[anEntry]] %>%
-    plm::pdata.frame(index = c("country", "year")) %>%
-    rename(
-      SupDem_trim = theta_trim,
-      First_yr = first_year,
-      Libdem_z = Vdem_libdem_z,
-      Polyarchy_z = Vdem_polyarchy_z,
-      Liberal_z = Vdem_liberal_z,
-      Corrup_TI_z = corruption_z,
-      lnGDP_imp = lg_imp_mdpgdp
-    )
-})
-
-mocdcpo_APSR  <- map(ls_mod_apsrCLS, function(aMod) {
-  result <- methodComposition3(dcpo_APSR, aMod)
-})
-
-names(mocdcpo_APSR) <-
-  c(
-    "pooled1",
-    "pooled-regime1",
-    "pooled2",
-    "pooled-regime2",
-    "fd1",
-    "fd-regime1",
-    "fd2",
-    "fd-regime2"
-  )
-
-saveRDS(mocdcpo_APSR,
-        file = here::here("output", "estimates_moc_dcpoAPSR.RDS"))
-```
-
-```{r formatDCPOResult-APSR}
-# Pooled---------------------------------------
-
-result_ecm1 <- bind_rows(
-  mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_expAPSR[["pooled1"]]), model = "Uncertainty+ExpData"),
-  mutate(MOCsumm2(mocdcpo_APSR[["pooled1"]]), model = "Uncertainty+DCPO+ExpData")
-) %>% 
-  mutate(type = "ECM")
-
-result_fd1 <- bind_rows(
-  mutate(result_clsAPSR[["fd1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_expAPSR[["fd1"]]), model = "Uncertainty+ExpData"),
-  mutate(MOCsumm2(mocdcpo_APSR[["fd1"]]), model = "Uncertainty+DCPO+ExpData")
-) %>% 
-  mutate(type = "First Difference")
-
-result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-        "Liberal Democracy\n (Difference)",
-        "Liberal Democracy\n (t-1)",
-        "Log GDP\n per capita\n (Difference)",
-        "Log GDP\n (t-1)"),
-      time = 3),
-      rep(
-        c("Liberal Democracy\n (Difference)", 
-          "Log GDP\n per capita\n (Difference)"), 
-        time = 3
-      )),
-    type = factor(type,  levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Original","Uncertainty+ExpData", "Uncertainty+DCPO+ExpData"))
-  )
-
-result_apsrPooled <- result_APSR1 %>% 
-    filter(type == "ECM") %>% 
-    mutate(type = "Pooled")
-
-# Institution----------------------------------
-
-result_ecmReg1 <- bind_rows(
-  mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime1"]]), model = "Uncertainty+ExpData"),
-  mutate(MOCsumm2(mocdcpo_APSR[["pooled-regime1"]]), model = "Uncertainty+DCPO+ExpData")
-) %>% 
-  mutate(type = "ECM")
-
-result_fdReg1 <- bind_rows(
-  mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime1"]]), model = "Uncertainty+ExpData"),
-  mutate(MOCsumm2(mocdcpo_APSR[["fd-regime1"]]), model = "Uncertainty+DCPO+ExpData")
-) %>% 
-  mutate(type = "First Difference")
-
-result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-        "Electoral Democracy\n (Difference)",
-        "Electoral Democracy\n (t-1)",
-        "Minoritarian Democracy\n (Difference)",
-        "Minoritarian Democracy\n (t-1)",
-        "Log GDP\n per capita\n (Difference)",
-        "Log GDP\n (t-1)"),
-      time = 3),
-      rep(
-        c("Electoral Democracy\n (Difference)", 
-          "Minoritarian Democracy\n (Difference)",
-          "Log GDP\n per capita\n (Difference)"), 
-        time = 3
-      )),
-    type = factor(type,  levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Original","Uncertainty+ExpData", "Uncertainty+DCPO+ExpData"))
-  )
-
-result_apsrRegime <- result_RegAPSR1 %>% 
-    filter(type == "ECM") %>% 
-    mutate(type = "Institution Specified")
-
-# Pooled-corruption------------------------------
-
-result_ecm2 <- bind_rows(
-  mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_expAPSR[["pooled2"]]), model = "Uncertainty+ExpData"),
-  mutate(MOCsumm2(mocdcpo_APSR[["pooled2"]]), model = "Uncertainty+DCPO+ExpData")
-) %>% 
-  mutate(type = "ECM")
-
-result_fd2 <- bind_rows(
-  mutate(result_clsAPSR[["fd2"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_expAPSR[["fd2"]]), model = "Uncertainty+ExpData"),
-  mutate(MOCsumm2(mocdcpo_APSR[["fd2"]]), model = "Uncertainty+DCPO+ExpData")
-) %>% 
-  mutate(type = "First Difference")
-
-result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-        "Liberal Democracy\n (Difference)",
-        "Liberal Democracy\n (t-1)",
-        "Log GDP\n per capita\n (Difference)",
-        "Log GDP\n (t-1)",
-        "Corruption\n (Difference)",
-        "Corruption\n (t-1)"
-      ),
-      time = 3),
-      rep(
-        c("Liberal Democracy\n (Difference)", 
-          "Log GDP\n per capita\n (Difference)",
-          "Corruption\n (Difference)"), 
-        time = 3
-      )),
-    type = factor(type,  levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Original","Uncertainty+ExpData", "Uncertainty+DCPO+ExpData"))
-  )
-
-# Institution Corruption--------------------------------
-
-result_ecmReg2 <- bind_rows(
-  mutate(result_clsAPSR[["pooled-regime2"]][[1]][,1:3], model = "Original"),
- mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime2"]]), model = "Uncertainty+ExpData"),
-  mutate(MOCsumm2(mocdcpo_APSR[["pooled-regime2"]]), model = "Uncertainty+DCPO+ExpData")) %>%
-  mutate(type = "ECM")
-
-result_fdReg2 <- bind_rows(
-  mutate(result_clsAPSR[["fd-regime2"]][[1]][,1:3], model = "Original"),
-  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime2"]]), model = "Uncertainty+ExpData"),
-  mutate(MOCsumm2(mocdcpo_APSR[["fd-regime2"]]), model = "Uncertainty+DCPO+ExpData")) %>% 
-  mutate(type = "First Difference")
-
-result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
-  filter(term != "(Intercept)") %>%
-  mutate(
-    term = c(rep(
-      c("Democratic Mood\n (t-1)",
-        "Democratic Mood\n (t-2)",
-        "Electoral Democracy\n (Difference)",
-        "Electoral Democracy\n (t-1)",
-        "Minoritarian Democracy\n (Difference)",
-        "Minoritarian Democracy\n (t-1)",
-        "Log GDP\n per capita\n (Difference)",
-        "Log GDP\n (t-1)",
-        "Corruption\n (Difference)",
-        "Corruption\n (t-1)"
-      ),
-      time = 3),
-      rep(
-        c("Electoral Democracy\n (Difference)", 
-          "Minoritarian Democracy\n (Difference)",
-          "Log GDP\n per capita\n (Difference)",
-          "Corruption\n (Difference)"), 
-        time = 3
-      )),
-    type = factor(type,  levels = c("ECM", "First Difference")),
-    model = factor(model, levels = c("Original","Uncertainty+ExpData", "Uncertainty+DCPO+ExpData"))
-  )
-```
-
-```{r coefName-dcpoAPSR-dup}
-index_coefName <- c(
-    `Democratic Mood\n (t-1)` = "Support[t-1]",
-    `Democratic Mood\n (t-2)` = "Support[t-2]",
-    `Liberal Democracy\n (Difference)` = "Delta~Liberal~democracy",
-    `Liberal Democracy\n (t-1)` = "Liberal~democracy[t-1]",
-    `Electoral Democracy\n (Difference)` = "Delta~Electoral~democracy",
-    `Electoral Democracy\n (t-1)` = "Electoral~democracy[t-1]",
-    `Minoritarian Democracy\n (Difference)` = "Delta~Minoritarian~democracy",
-    `Minoritarian Democracy\n (t-1)` = "Minoritarian~democracy[t-1]",
-    `Log GDP\n per capita\n (Difference)` = "Delta~Log~GDP~per~capita",
-    `Log GDP\n (t-1)` = "Log~GDP[t-1]"
-)
-```
-
-```{r plotdcpo-mocAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", eval = TRUE, fig.width=10, fig.height=10}
-terms1 <- factor(rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Liberal~democracy",
-        "Liberal~democracy[t-1]",
-        "Delta~Log~GDP~per~capita",
-        "Log~GDP[t-1]"
-    )
-),
-levels = rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Liberal~democracy",
-        "Liberal~democracy[t-1]",
-        "Delta~Log~GDP~per~capita",
-        "Log~GDP[t-1]"
-    )
-), 
-labels = rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Liberal~Dem",
-        "Liberal~Dem[t-1]",
-        "Delta~Log~GDP~per~capita",
-        "Log~GDP[t-1]"
-    )
-))
-
-plot_APSR1 <-
-    dwplot(result_APSR1, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms1))) +
-    labs(title = "DV: The Change of Public Support for Democracy",
-         subtitle = "Pooled") +
-    facet_wrap( ~ type, drop = T, scales = "free_x") +
-    theme(legend.position = "none")  +
-   scale_color_gb(palette = "digitMixed")
-
-terms3 <- factor(rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Electoral~democracy",
-        "Electoral~democracy[t-1]",
-        "Delta~Minoritarian~democracy",
-        "Minoritarian~democracy[t-1]",
-        "Delta~Log~GDP~per~capita",
-        "Log~GDP[t-1]"
-    )
-),
-levels = rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Electoral~democracy",
-        "Electoral~democracy[t-1]",
-        "Delta~Minoritarian~democracy",
-        "Minoritarian~democracy[t-1]",
-        "Delta~Log~GDP~per~capita",
-        "Log~GDP[t-1]"
-    )
-),
-labels = rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Electoral",
-        "Electoral[t-1]",
-        "Delta~Minoritarian",
-        "Minoritarian[t-1]",
-        "Delta~Log~GDP~per~capita",
-        "Log~GDP[t-1]"
-    )
-)
-)
-
-plot_RegAPSR1 <-
-    dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms3))) +
-    labs(title = "",
-         subtitle = "Institution Specified") +
-    facet_wrap( ~ type, scales = "free_x") +
-    theme(legend.position = "none")  +
-    scale_color_gb(palette = "digitMixed")
-
-terms2 <- factor(rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Liberal~democracy",
-        "Liberal~democracy[t-1]",
-        "Delta~Log~GDP~per~capita",
-        "Log~GDP[t-1]",
-        "Delta~Corruption",
-        "Corruption[t-1]"
-    )
-),
-levels = rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Liberal~democracy",
-        "Liberal~democracy[t-1]",
-        "Delta~Log~GDP~per~capita",
-        "Log~GDP[t-1]",
-        "Delta~Corruption",
-        "Corruption[t-1]"
-    )
-),
-labels = rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Liberal~Dem",
-        "Liberal~Dem[t-1]",
-        "Delta~Log~GDP~per~capita",
-        "Log~GDP[t-1]",
-        "Delta~Corruption",
-        "Corruption[t-1]"
-    )
-))
-
-plot_APSR2 <-
-    dwplot(result_APSR2, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms2))) +
-    labs(title = "",
-         subtitle = "W. Corruption") +
-    facet_wrap( ~ type, scales = "free_x") +
-    theme(legend.position = "none")  +
-    scale_color_gb(palette = "digitMixed")
-
-terms4 <- factor(rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Electoral~democracy",
-        "Electoral~democracy[t-1]",
-        "Delta~Minoritarian~democracy",
-        "Minoritarian~democracy[t-1]",
-        "Delta~Log~GDP",
-        "Log~GDP[t-1]",
-        "Delta~Corruption",
-        "Corruption[t-1]"
-    )
-),
-levels = rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Electoral~democracy",
-        "Electoral~democracy[t-1]",
-        "Delta~Minoritarian~democracy",
-        "Minoritarian~democracy[t-1]",
-        "Delta~Log~GDP",
-        "Log~GDP[t-1]",
-        "Delta~Corruption",
-        "Corruption[t-1]"
-    )
-),
-labels = rev(
-    c(
-        "Support[t-1]",
-        "Support[t-2]",
-        "Delta~Electoral",
-        "Electoral[t-1]",
-        "Delta~Minoritarian",
-        "Minoritarian[t-1]",
-        "Delta~Log~GDP",
-        "Log~GDP[t-1]",
-        "Delta~Corruption",
-        "Corruption[t-1]"
-    )
-))
-
-plot_RegAPSR2 <-
-    dwplot(result_RegAPSR2, dodge_size = 0.8, by_2sd = FALSE) +
-    scale_y_discrete(labels = parse(text = levels(terms4))) +
-    labs(title = "",
-         subtitle = "Institution Specified w. Corruption") +
-    facet_wrap( ~ type, scales = "free_x") +
-    theme(legend.position = "bottom",
-          legend.title = element_blank())  +
-    scale_color_gb(palette = "digitMixed")
-
-legend <- get_legend(plot_RegAPSR2)
-
-plot_RegAPSR2 <- plot_RegAPSR2 + theme(legend.position = "none")
-
-grid.arrange(plot_APSR1,
-             plot_APSR2,
-             plot_RegAPSR1,
-             plot_RegAPSR2,
-             legend,
-             ncol = 2)
-```
+    `Log GDP\n (t-1)` = "Log~GDP~per~capita[t-1]",
+    `Corruption\n (Difference)` = "Delta~Corruption",
+    `Corruption\n (t-1)` = "Corruption[t-1]"
+)
+```
+
+```{r plot-dcpoAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", fig.width=7, fig.height=10}
+df_plot <- bind_rows(result_APSR1, result_APSR2,
+                     result_RegAPSR1, result_RegAPSR2) %>% 
+    mutate(term = index_coefName[term0], 
+           term = factor(term, levels = unique(index_coefName)))
+
+apsr_caption <- "Replications of Claassen (2020b), Table 1-2, 47-49 with DCPO.  Models denoted 'ECM' are error-correction models; those marked 'FD' are first-difference models." %>% 
+  strwrap(85) %>% 
+  paste0(sep="", collapse="\n")
+
+small_multiple(df_plot, dot_args = list(size = .9, fatten = 1)) +
+    theme_bw() +
+    geom_hline(yintercept = 0, colour = "grey50", linetype = 2) +
+    scale_color_grey(start = 0.8, end = 0.4, 
+                     name = "Replication",
+                     breaks=c("Point Estimates Only",
+                              "Uncertainty & More Data",
+                              "Uncertainty & DCPO"),
+                     labels=c("Point Estimates Only",
+                              "Uncertainty & More Data",
+                              "Uncertainty & DCPO")) +
+    theme(axis.text.x  = element_text(angle = 90, hjust = .5),
+          strip.text.y.left = element_text(angle = 0),
+          legend.position = c(0.006, -.01),
+          legend.justification = c(1, 1), 
+          legend.title = element_text(size = 9, face = "bold"),
+          legend.title.align = 0.5,
+          legend.text = element_text(size = 8),
+          legend.background = element_rect(color="gray90"),
+          legend.spacing = unit(-5, "pt"),
+          legend.key.width = unit(4.5, "mm"),
+          legend.key.height = unit(7, "mm"),
+          plot.caption = element_text(size = 10, hjust = 0.2, margin = margin(t=15))) +
+  guides(color = guide_legend(override.aes = list(size=.3))) +
+  ggtitle("Dependent Variable: Change in Public Democratic Support") +
+  labs(caption = apsr_caption)
+```

### 2021-08-18 paper/dcpo_demsupport.Rmd
fuss

--- 2021-08-18 paper/dcpo_demsupport.Rmd
@@
 As democracy is also a latent variable in these analyses, we include the uncertainty in its estimates as well, along with that for corruption in the models of @Claassen2020b.
-In the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.^[We also attempted to make fuller use of the available survey data by employing the DCPO model [@Solt2020a; @Solt2020b], which unlike the [@Claassen2019] model does not dichotomize ordinal responses.
+In the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.^[We also attempted to make fuller use of the available survey data by employing the DCPO model [@Solt2020a], which unlike the [@Claassen2019] model does not dichotomize ordinal responses.
 The better fit of the DCPO model to these data [see @Solt2020a, 10-12] and the additional information it incorporates, however, did not yield substantively different results; see the Supplemental Information.]

### 2021-08-18 paper/dcpo_demsupport.Rmd
corrected the legend and cross-reference of the plots

--- 2021-08-18 paper/dcpo_demsupport.Rmd
@@
 Second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.
-As democracy is also a latent variable in these analyses, we include the uncertainty in its estimates as well, along with that for corruption in the second analysis of @Claassen2020b.
-In the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.^[We also attempted to make fuller use of the available survey data by employing Solt's [-@Solt2020a; -@Solt2020b] DCPO model, which unlike Claassen's [-@Claassen2019] model does not dichotomize ordinal responses.
+As democracy is also a latent variable in these analyses, we include the uncertainty in its estimates as well, along with that for corruption in the models of @Claassen2020b.
+In the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.^[We also attempted to make fuller use of the available survey data by employing the DCPO model [@Solt2020a], which unlike the [@Claassen2019] model does not dichotomize ordinal responses.
 The better fit of the DCPO model to these data [see @Solt2020a, 10-12] and the additional information it incorporates, however, did not yield substantively different results; see the Supplemental Information.]
@@
 
-Figure \@ref(fig:plot-mainAJPS) presents the reanalyses of the hypothesis that public support influences the level of democracy [@Claassen2020a, Table 1, 128].
+Figure \@ref(fig:plot-fullAJPS) presents the reanalyses of the hypothesis that public support influences the level of democracy [@Claassen2020a, Table 1, 128].
 The lighter, lefthand set of results replicate the analysis of @Claassen2020a, including its exclusion of measurement uncertainty by using only the point estimates of public democratic support and the other variables measured with quantified error (democracy and corruption), and they reproduce that article's findings.
@@
            model = "Model 1 (Pooled OLS)")
-
 result_gmm <- bind_rows(
@@
            model = "Model 3 (System GMM)")
-
 result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
@@
     )
-
 result_regime <- bind_rows(
@@
            model = "Model 2 (Pooled OLS)")
-
 result_regimeGmm <- bind_rows(
@@
            model = "Model 4 (System GMM)")
-
 result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
@@
            term = factor(term, levels = unique(index_coefName)))
-
 ajps_caption <- "Replications of Claassen (2020a), Table 1, 128."
-
 small_multiple(df_plot, dot_args = list(size = .9, fatten = 1)) +
+    theme_bw() +
     geom_hline(yintercept = 0, colour = "grey50", linetype = 2) +
@@
                      name = "Replication",
-                     breaks=c("Point Estimates Only", "Uncertainty & More Data", "Uncertainty & DCPO"),
-                     labels=c("Point Estimates Only", "Uncertainty & More Data", "Uncertainty & DCPO")) +
+                     breaks=c("Point Estimates Only", "With Uncertainty", "Uncertainty & More Data"),
+                     labels=c("Point Estimates Only", "With Uncertainty", "Uncertainty & More Data")) +
     theme(axis.text.x  = element_text(angle = 90, hjust = .5),
@@
 
-In Figure \@ref(fig:plot-mainAPSR), we examine the thermostatic model of democratic support per @Claassen2020b [47, Table 1, 49, Table 2].
+In Figure \@ref(fig:plot-fullAPSR), we examine the thermostatic model of democratic support per @Claassen2020b [47, Table 1, 49, Table 2].
 The negative coefficient estimates for change in liberal democracy in the lefthand set of results, which do not take uncertainty into account, imply that the immediate effect of a increase in the level of democracy is a decline in public support for democracy and of a decrease in democracy an expansion of support---that democratic support indeed does respond thermostatically to democracy.
@@
 These null results have a number of important substantive implications.
-First, they underscore that recognizing the conditional aspects of the classic argument regarding democracy and democratic support is crucial.
+First, they underscore that it is crucial to recognize the conditional aspects of the classic theory regarding democracy and democratic support.
 With regard to how levels of democracy affect public support, even the early proponents of the classic argument did not contend that the mere existence of democratic institutions, no matter how consistently feckless and ineffective, would generate support among the public: instead, they maintained, public support would be gained through experience with government performance that was generally effective [@lipset_social_1959, 86-89; @Easton1965, 119-120].
@@
 
-# Data Recollection and Uncertainty in Control Variables {#dgp}
-
-Due to revisions to the underlying datasets (and, possibly, transcription errors), we were not able to achieve a primary replication [@Grossman2020] based on survey data summarized in @Claassen2020a and @Claassen2020b's Dataverse files.
-
-Specifically, we are not able to identify 5 country-year surveys, including South Sudan in Arab Barometer Wave 4, Dominican Republic in 2003 Latinobarometer, XXXX, and Spain in 2005 Latinobarometer. 
+# Replication Notes {#dgp}
+
+Replicating the analyses of @Claassen2020a and @Claassen2020b while incorporating the quantified uncertainty in their variables was not possible from those article's Dataverse files.
+Instead, it required re-collecting all of the data employed in those articles directly from their original sources, that is, in the terminology of @Grossman2020, it required a primary replication rather than a secondary one.
+We describe this process here.
+
+First, we identified the variable names of each survey item in each survey dataset as well as their corresponding values. 
+We then used the `DCPOtools` R package to automate the process of generating a dataset of survey marginals.
+Due to revisions to the underlying datasets (and, possibly, transcription errors), we were not able to locate 5 country-year-items: including South Sudan in Arab Barometer Wave 4, Dominican Republic in 2003 Latinobarometer, XXXX, and Spain in 2005 Latinobarometer.
 In addition, we still have different sample size and number of respondents answering supportively by following approaches of cleanning data and treatment of non-responses described in @Claassen2020a's supplementatry materials.

### 2021-08-18 paper/dcpo_demsupport.Rmd
correctly cross-ref appendices

@@
 First, we reproduce the original analyses of Claassen [-@Claassen2020a; -@Claassen2020b], which included only the point estimates of the latent variable of democratic support and so exclude its measurement uncertainty.
-Second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.
+Second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.^[Additional details on this data replication process are found in Supplementary Information Appendix \@ref(dgp).]
 As democracy is also a latent variable in these analyses, we include the uncertainty in its estimates as well, along with that for corruption in the models of @Claassen2020b.
 In the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.^[We also attempted to make fuller use of the available survey data by employing the DCPO model [@Solt2020a], which unlike the [@Claassen2019] model does not dichotomize ordinal responses.
-The better fit of the DCPO model to these data [see @Solt2020a, 10-12] and the additional information it incorporates, however, did not yield substantively different results; see the Supplemental Information.]
+The better fit of the DCPO model to these data [see @Solt2020a, 10-12] and the additional information it incorporates, however, did not yield substantively different results; see Supplementary Information Appendix \@ref(dcpo).]
 
@@
 Therefore, after replicating the original analyses that use only the point estimates for public support and the other variables included in the model, we perform the analyses again only this time incorporating uncertainty in analysis models using our replication data.
-We conduct inferences from the distributive data via the technique known as the "method of composition" [@Tanner1993, 52; @Treier2008, 215; @caughey2018, A15-16].
-For additional detail on this technique, see the Supplementary Information.
+We conduct inferences from the distributive data via the technique known as the "method of composition" [@Tanner1993, 52; @Treier2008, 215; @caughey2018, A15-16].^[For additional details on this technique, see Supplementary Information Appendix \@ref(moc).]
 
@@
 Due to revisions to the underlying datasets (and, possibly, transcription errors), we were not able to locate 5 country-year-items: including South Sudan in Arab Barometer Wave 4, Dominican Republic in 2003 Latinobarometer, XXXX, and Spain in 2005 Latinobarometer.
-In addition, we still have different sample size and number of respondents answering supportively by following approaches of cleanning data and treatment of non-responses described in @Claassen2020a's supplementatry materials.
+In addition, we still have different sample size and number of respondents answering supportively by following approaches of cleanning data and treatment of non-responses described in @Claassen2020a's supplementary materials.
 Specifically, we used Claassen's year coding to recode 85 unmatching country-year observations and added one more item "strong leader 2" in Arabbarometer which has different response categories but was conflated into "strong leader 1".

### 2021-08-18 paper/memo/response_memo.Rmd
identify appendices by letter

@@
 As this technique has become the standard method for incorporating uncertainty in the Americanist literature using Multilevel Regression and Poststratification [see, e.g., @Kastellec2015; @caughey2018], which is after all also a latent variable model of public opinion, we were pleased to adopt this suggestion.
-We provide a full description of the MOC technique in the Supplementary Information.
+We provide a full description of the MOC technique in Supplementary Information Appendix B.
 
 1.
-**Method: Incorporating Uncertainty** R4 suggested that it would be helpful to provide citations for the point that neglecting to include uncertainty can bias coefficients along with standard errors.
-We agree and so drop cites here to Blackwell, Honaker, and King [-@Blackwell2017, 318-319; -@Blackwell2017a, 360-361]---who present simulations that, while aimed at other issues, nonetheless illustrate the point neatly---as well as to @caughey2018 [, 254].
+**Method: Incorporating Uncertainty** R4's comments suggested that it would be helpful to provide citations for the point that neglecting to include uncertainty can bias coefficients along with standard errors.
+We drop cites here to Blackwell, Honaker, and King [-@Blackwell2017, 318-319; -@Blackwell2017a, 360-361]---who present simulations that, while aimed at other issues, nonetheless illustrate the point neatly---as well as to @caughey2018 [254].
 
 1.
-**Method: ~~Better Estimates of Public Support and~~ Adding More Data** R1 and R4 asked for more detail on the differences between Solt's [-@Solt2020b] DCPO model and the latent variable model used by Claassen.
+**Method: ~~Better Estimates of Public Support and~~ Adding More Data** R1 and R4 asked for more detail on the differences between Solt's [-@Solt2020a] DCPO model and the latent variable model used by Claassen.
 R2 indirectly raised the same issue, asking about the consequences for thermostatic models of employing a random-walk prior in the DCPO model of democratic support---when actually both DCPO and the Claassen model use the same random-walk prior.
 Given that the DCPO model's advantages ultimately do not have a payoff in this case, we concluded that its inclusion in this 4000-word letter is an unnecessary distraction from our main points.
-So we took the _other_ suggestion from R1 on this topic, hinted at by R2 as well, to simply drop DCPO from the text entirely and move the analyses with the DCPO estimates to the Supplementary Information.
+So we took the _other_ suggestion from R1 on this topic, hinted at by R2 as well, to simply drop DCPO from the text entirely and move the analyses with the DCPO estimates to Appendix C in the Supplementary Information.
 

### 2021-08-18 paper/dcpo_demsupport.Rmd
revise appendices

@@
 In the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.^[We also attempted to make fuller use of the available survey data by employing the DCPO model [@Solt2020a], which unlike the [@Claassen2019] model does not dichotomize ordinal responses.
-The better fit of the DCPO model to these data [see @Solt2020a, 10-12] and the additional information it incorporates, however, did not yield substantively different results; see Supplementary Information Appendix \@ref(dcpo).]
+The better fit of the DCPO model to the data on democratic support [see @Solt2020a, 10-12] and the additional information it incorporates, however, did not yield substantively different results; see Supplementary Information Appendix \@ref(dcpo).]
 
@@
 
-Replicating the analyses of @Claassen2020a and @Claassen2020b while incorporating the quantified uncertainty in their variables was not possible from those article's Dataverse files.
+Because the Dataverse replication files for @Claassen2020a and @Claassen2020b included only the point estimates of their variables, replicating those articles' analyses while incorporating the quantified uncertainty in their latent variables was not possible using only those files.
 Instead, it required re-collecting all of the data employed in those articles directly from their original sources, that is, in the terminology of @Grossman2020, it required a primary replication rather than a secondary one.
-We describe this process here.
-
-First, we identified the variable names of each survey item in each survey dataset as well as their corresponding values. 
-We then used the `DCPOtools` R package to automate the process of generating a dataset of survey marginals.
-Due to revisions to the underlying datasets (and, possibly, transcription errors), we were not able to locate 5 country-year-items: including South Sudan in Arab Barometer Wave 4, Dominican Republic in 2003 Latinobarometer, XXXX, and Spain in 2005 Latinobarometer.
-In addition, we still have different sample size and number of respondents answering supportively by following approaches of cleanning data and treatment of non-responses described in @Claassen2020a's supplementary materials.
-Specifically, we used Claassen's year coding to recode 85 unmatching country-year observations and added one more item "strong leader 2" in Arabbarometer which has different response categories but was conflated into "strong leader 1".
-
-V-Dem data was standardized in @Claassen2020b's analyses, but we did not figure out how the standardization was exactly performed.
-We standardized variables using Z-score, and the standardized values are different from Claassen's data.
-
-Since many variables, dependent variables, key independent variables, and control variables in the original analysis are latent variables, which cannot be observed directly and are inherently contaminated by measurement errors.
-We include measurement errors in five variables, public support for democracy, liberal democracy index, electoral democracy index, liberal component index, and corruption perception index.
-
-In respect of the key independent variable, public support for democracy, we preserve its posterior distribution from Model 5 using recollected and expanded data, separately.
-
-For the three indices of democratic development, we take two strategies.
-Regarding original data and recollected data, we use three democratic indices from V-Dem Version 8 which covers 201 countries from 1789 to 2017 and is the version Claassen used in his analyses.
-We use their posterior distribution provided by @coppedge2018.
-Regarding the expanded data used to replicate Claassen's analyses, we use the same three democratic indices but from V-Dem Version 10 because its year range from 1789 to 2019 is compatible with the expanded data.
-However, since V-Dem project has not released posterior distributions for indices in version 10, we simulated 900 data set for each democracy index using their standard error.
-
-Finally, to account for measurement error in Corruption Perceptions Index, we simulated 900 draws from a distribution with the point estimate and standard error provided by CPI for the year from 2012 to 2018.
-However, CPI does not provide standard error for the years before 2012.
-To simulate "posterior distribution", we first estimated the standard error for the country-year index.
-For each country, we identified its maximum relative standard error (standard error/cpi index) during these years and then calculated the estimated country-year standard error by multiplying the country's maximum relative error and its year CPI index.
-We used this estimated standard error to simulate 900 draws for each country-year.
-
-In the following section, we illustrate how we utilize these simulated distributions to take uncertainty into account in analysis models.
-
+We describe this process for the latent variables here.
+
+## Democratic Support {-}
+
+First, for each item used in the two articles' measure of democratic support, we identified the original variable names and corresponding values in each survey dataset. 
+We then used the `dcpo_setup` and `format_claassen` functions of the `DCPOtools` R package to automate the process of generating a dataset of survey marginals.
+These survey marginals were then used to generate estimates of democratic support in Stan using the `supdem.stan.mod5.stan` script from the @Claassen2020a Dataverse materials.
+Draws from the posterior distribution quantify the uncertainty in the estimates.
+
+## Democracy {-}
+
+The democracy variables in the two articles are drawn from Version 8 of the V-Dem Dataset [@coppedge2018].
+This version of the dataset includes draws from the posterior distribution of the estimates to quantify their uncertainty.
+In our extension (the rightmost replication of each model in our Figures 1 and 2), we are able to extend the time series beyond the last year of Version 8, 2017, so we use the updated Version 10 instead.
+Version 10, however, does not include posterior draws of the estimates, but rather standard errors.
+For the purposes of incorporating this uncertainty into our analyses, we assumed a normal distribution around the point estimates.
+
+## Corruption {-}
+
+The corruption variable used in @Claassen2020b is the Corruption Perceptions Index, which provides point estimates and standard errors for the years from 2012 to 2018.
+For country-years beyond that range, we estimated standard errors for by first identifying the country's maximum relative standard error (standard error/point estimate) during 2012-2018 and then multiplying this quantity by the country-year's point estimate.
+For the purposes of incorporating this uncertainty into our analyses, we again assumed a normal distribution around the point estimates.
+
+In Appendix \@ref(moc), we illustrate how we employed these simulated distributions to take uncertainty into account in our analysis models.
+
+\pagebreak
 # The Method of Composition {#moc}
 
-In analysis models, we have latent variables in both sides of equations, public support for democracy, democracy indices, and corruption index (The latter one is included in APSR analyses).
-Since measurement uncertainty associated with these latent variables can propagate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing "Method of Composition" [@Tanner1993,p52], which has been applied in analyses with latent variables [@Treier2008;@caughey2018;@Kastellec2015].
-
-As @caughey2018 explained, the main idea of MOC is to estimate the marginal distribution of coefficient parameter vector $\beta$, integrating over the uncertainty in latent variables $\theta$ (P A-15).
+In our analysis models, we have latent variables in both sides of the equations: public democratic support, democracy, and corruption.
+Since measurement uncertainty associated with these latent variables can propagate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing the "Method of Composition" [@Tanner1993, 52], which has often been applied in analyses with latent variables in political science [see, e.g., @Treier2008; @caughey2018; @Kastellec2015].
+
+As @caughey2018 [A-15] explained, the main idea of MOC is to estimate the marginal distribution of coefficient parameter vector $\beta$, integrating over the uncertainty in latent variables $\theta$.
 More explicitly, we wish to integrate the joint density of $\beta$ and $\theta$ over the distribution of $\theta$.
@@
 
-We incorporate uncertainty for five variables, public support for democracy, liberal democracy, electoral democracy, liberal component index, and corruption perceptions index.
+We incorporate uncertainty for five variables, public support for democracy, liberal democracy, electoral democracy, the liberal component index, and the corruption perceptions index.
 For each of these five latent variables, we take 900 draws from its posterior distribution.
@@
 
+\pagebreak
 # DCPO Replication {#dcpo}
 
-As a further test of the classic arguments on democracy and public support, we apply the superior DCPO model to a bigger data set.
+To make fuller use of the available survey data, we also replicated the tests of the classic arguments on democracy and public support using the DCPO model put forward in @Solt2020a on our expanded data set.
 The DCPO model has several advantages over the @Claassen2019 model used in Claassen [-@Claassen2020a; -@Claassen2020b].
-First, while the @Claassen2019 model dichotomizes responses and so discards some information provided by 50 of the 52 survey items employed in Claassen [-@Claassen2020a; -@Claassen2020b], the DCPO model makes use of all of the information available from these ordinal items [@Solt2020a, p.5].
-Second, as the DCPO model includes both parameters for the dispersion of each survey item and for the standard deviation of aggregate public opinion in each country-year, it is a complete population-level item-response model and so, unlike the @Claassen2019 model, is explicitly derived from an individual-level model of survey responses [@Solt2020a, pp.3-4; see also @McGann2014].
-Third, to produce more sensible estimates of uncertainty for observations at the extremes of the scale [see @Linzer2015, p.229], the DCPO model places bounds on its estimates of public opinion [@Solt2020a, p.8].
-Further commending the DCPO model to us---and demonstrating that its advantages make a difference---the validation tests in @Solt2020a [, pp.10-12] reveal that it fits survey data on democratic support better than the @Claassen2019 model does.
-
-We employ the superior DCPO model to the expanded data using the `DCPO` package for R [@Solt2020b].
-We use the estimated public support from DCPO model to replicate analyses by following the same steps.
-Then, we compare the DCPO results with two types of replication results from Model 5: estimation of original data and without uncertainty and estimation of expanded data and with uncertainty.
-
-The comparison is presented in Appendix B.
-Still, even with the superior DCPO model and expanded data, there is no evidence to support that public support can sustain democratic development or public support responds thermostatically to changes in democracy.
+First, while the @Claassen2019 model dichotomizes responses and so discards some information provided by 50 of the 52 survey items employed in Claassen [-@Claassen2020a; -@Claassen2020b], the DCPO model makes use of all of the information available from these ordinal items [@Solt2020a, 5].
+Second, as the DCPO model includes both parameters for the dispersion of each survey item and for the standard deviation of aggregate public opinion in each country-year, it is a complete population-level item-response model and so, unlike the @Claassen2019 model, is explicitly derived from an individual-level model of survey responses [@Solt2020a, 3-4; see also @McGann2014].
+Third, to produce more sensible estimates of uncertainty for observations at the extremes of the scale [see @Linzer2015, 229], the DCPO model places bounds on its estimates of public opinion [@Solt2020a, 8].
+Further commending the DCPO model to us---and demonstrating that its advantages make a difference---the validation tests in @Solt2020a [, 10-12] reveal that it fits survey data on democratic support better than the @Claassen2019 model does.
+
+We employ the superior DCPO model to our expanded dataset using the `DCPO` package for R [@Solt2020b].
+We then use the estimated public support from the DCPO model to replicate all of the analyses presented in the text.
+Figures A.1 and A.2 display these results as the righthand set of results, with the replication of the articles' original results based only on point estimates on the left and our extension with uncertainty and more data, but the articles' original, @Claassen2019, model in the middle for comparison.
+
+Even with the advantages of the DCPO model, there is no evidence to support the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support sustains democratic regimes or public support responds thermostatically to changes in democracy.
 

### 2021-08-18 paper/memo/response_memo.Rmd
add separate bibliographies for text and SI; cut down to <4k words
Ready to go, I think! @sammo3182 @Tyhcass

@@
 spacing: single
-bibliography: \dummy{`r file.path(file.path(getwd(), ".."), list.files(file.path(getwd(), ".."), ".bib$", recursive = TRUE))`}
+bibliography: ../dcpo-demsupport.bib
 biblio-style: apsr
@@
 **Method: Incorporating Uncertainty** R4's comments suggested that it would be helpful to provide citations for the point that neglecting to include uncertainty can bias coefficients along with standard errors.
-We drop cites here to Blackwell, Honaker, and King [-@Blackwell2017, 318-319; -@Blackwell2017a, 360-361]---who present simulations that, while aimed at other issues, nonetheless illustrate the point neatly---as well as to @caughey2018 [254].
+We drop cites here to @Blackwell2017 [, 318-319]---who present a simulation that, while aimed at other issues, nonetheless illustrates the point neatly---as well as to @caughey2018 [254].
 

### 2021-08-18 paper/dcpo_demsupport.Rmd
add separate bibliographies for text and SI; cut down to <4k words
Ready to go, I think! @sammo3182 @Tyhcass

@@
     latex_engine: xelatex
+    pandoc_args: --lua-filter=multiple-bibliographies.lua
 
@@
 
-date: "`r format(Sys.time(), '%B %d, %Y')`"
+date: " "
 editor_options: 
@@
 linestretch: 1.5 # double spacing using linestretch 1.5
-bibliography: dcpo_demsupport.bib
-# bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
-# csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl
+bibliography_text: 
+  - dcpo_demsupport_text.bib
+bibliography_app: 
+  - dcpo_demsupport_app.bib
 biblio-style: apsr
@@
 
-(Word count: 3628)
+(Word count: 3986)
 
@@
 But the evidence for either part of this claim has been decidedly mixed.
-Countries with greater democratic support have been found to become stronger and more stable democracies [e.g., @Inglehart2005, pp. 251-254] and just the opposite [@Fails2010, pp. 182-183].
-Similarly, studies have alternately found that more experience with democracy yields more democratic support [e.g., @Fails2010, p.
-183; @Wuttke2020a, pp.
-5-6] or instead that long-established democracies are suffering from democratic fatigue [e.g., @Denemark2016; @Foa2017].
+Countries with greater democratic support have been found to become stronger and more stable democracies [e.g., @Inglehart2005, 251-254] and just the opposite [@Fails2010, 182-183].
+Similarly, studies have alternately found that more experience with democracy yields more democratic support [e.g., @Fails2010, 183; @Wuttke2020a, 5-6] or instead that long-established democracies are suffering from democratic fatigue [e.g., @Denemark2016; @Foa2017].
 
@@
 A pair of prominent recent works took advantage of this latent variable approach to measure democratic support for over one hundred countries for up to nearly three decades and to then assess, respectively, its consequences for and roots in democratic change [@Claassen2020a; @Claassen2020b].
-These works concluded, first and supporting the classic argument, that mass support had a positive impact on democratic change, especially the endurance of democracy [@Claassen2020a, pp.
-127-130], and, second and directly contrary to it, democratic change has a thermostatic effect on public support, that is that, rather than generating its own support, deepening democracy provokes a backlash and it is instead democratic backsliding that calls forth greater public support [@Claassen2020b, 46-50].
+These works concluded, first and supporting the classic argument, that mass support had a positive impact on democratic change, especially the endurance of democracy [@Claassen2020a, 127-130], and, second and directly contrary to it, democratic change has a thermostatic effect on public support, that is that, rather than generating its own support, deepening democracy provokes a backlash and it is instead democratic backsliding that calls forth greater public support [@Claassen2020b, 46-50].
 
@@
 On the one side, the effect of democracy on public support may depend not on its mere existence but on its effectiveness [see @Magalhaes2014] and particularly with regard to redistribution [see @Krieckhaus2014].
-On the other, the impact of public support on democracy may depend on the extent to which those who support democracy are also dissatisfied with the current regime's performance; that is, that it is not democratic support that is important to democratic change, but rather unsatisfied democratic demand [see @Qi2011].
+On the other, the impact of public support on democracy may depend on the extent to which those who support democracy are also dissatisfied with the current regime's performance [see @Qi2011].
 Similarly, the results presented here are further evidence that the survey items commonly employed to measure democratic support are inadequate to the task.
-Without additional information on respondents' support for democracy relative to other values with which it may come into conflict, such as their partisanship [see, e.g., @Carey2020; @graham_democracy_2020; @McCoy2020]---or on whether respondents even understand the meaning of the democracy they are claiming to support [see, e.g., @Kirsch2019; @Wuttke2020]---these questions appear to miss capturing the true extent of support democracy would find among the public when public support was actually needed.
+Without additional information on respondents' support for democracy relative to other values with which it may come into conflict, such as their partisanship [see, e.g., @Carey2020; @McCoy2020]---or on whether respondents even understand the meaning of the democracy they are claiming to support [see, e.g., @Kirsch2019; @Wuttke2020]---these questions appear to miss capturing the true extent of support democracy would find among the public when public support was actually needed.
 Our results also reinforce arguments that relationships between democracy and public support unfold only over the long term [see, e.g., @Welzel2017] and that democratic change in the short-term is instead best understood as an elite-driven phenomenon [see, e.g., @levitsky_how_2018; @Haggard2021].
@@
 
-Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can both attenuate or exaggerate coefficient estimates as well as bias standard errors [see, e.g., @Blackwell2017, 318-319; @Blackwell2017a, 360-361; @caughey2018, 254].
+Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can both attenuate or exaggerate coefficient estimates as well as bias standard errors [see, e.g., @Blackwell2017, 318-319; @caughey2018, 254].
 In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey2018, 254].
@@
 One possibility is that only those who profess to prefer democracy to its alternatives _and also_ value freedom of expression, freedom of association, and pluralism of opinion will take appropriate action when democracy is threatened [see, e.g., @Schedler2007].
-Another is that respondents' other values, such as their policy preferences or partisanship, may weigh more heavily than their support for democracy: there is growing evidence that, at least in the United States, there are many for whom these other considerations excuse substantial transgressions against democracy [see @bartels_ethnic_2020; @Carey2020; @graham_democracy_2020; @McCoy2020].
+Another is that respondents' other values, such as their policy preferences or partisanship, may weigh more heavily than their support for democracy: there is growing evidence that, at least in the United States, there are many for whom these other considerations excuse substantial transgressions against democracy [see @Carey2020; @graham_democracy_2020; @McCoy2020].
 Yet another is that the answers to the above items reflect actual support for democracy only when respondents also either hold a robust understanding of what liberal democracy means or anchor their support in emancipative values of universal freedoms.
@@
 
+\pagebreak
 # References  {-}
 
-<div id = 'refs'></div>
+<div id = 'refs_text'></div>
 
@@
 ```
+
+# References  {-}
+
+<div id = 'refs_app'></div>

### 2021-08-18 paper/make_separate_bibliographies.R

@@ -1,0 +1,21 @@
+source_url("https://raw.githubusercontent.com/paulcbauer/flex_bib/master/replace_bib_braces.R")
+source_url("https://raw.githubusercontent.com/paulcbauer/flex_bib/master/merge_bib_lines.R")
+x <- stringi::stri_read_lines("dcpo_demsupport.bib")
+x <- replace_bib_braces(x = x) # Replace (non-existent) quotes by braces
+x  <- merge_bib_lines(x = x) # merge line breaks
+stringi::stri_write_lines(x, "references_test.bib")
+
+devtools::source_url("https://raw.githubusercontent.com/paulcbauer/flex_bib/master/flex_bib.R")
+flex_bib(
+    rmarkdown_file = "dcpo_demsupport.Rmd",
+    bib_input = "references_test.bib",
+    bib_output = "dcpo_demsupport.bib",
+    by_sections = c("<!--- flex_bib appendix split -->"),
+    repair = TRUE,
+    removeISSN = TRUE,
+    removeISBN = TRUE,
+    removeDOI = TRUE,
+    removeURL = TRUE
+)
+
+# some hand-editing still left to do *sigh*

### 2021-08-19 paper/memo/response_memo.Rmd
add page numbers per @sammo3182 https://github.com/fsolt/dcpo_dem_mood/commit/3e5de0329e715b17630de103d57662f0695ccbb5#commitcomment-55104092

@@
 All of the replications that include uncertainty now do so for _all_ of the variables for which quantified error is available, not just democratic support.
+We make note of this at page 4.
 
@@
 As this technique has become the standard method for incorporating uncertainty in the Americanist literature using Multilevel Regression and Poststratification [see, e.g., @Kastellec2015; @caughey2018], which is after all also a latent variable model of public opinion, we were pleased to adopt this suggestion.
-We provide a full description of the MOC technique in Supplementary Information Appendix B.
+We mention our use of the MOC at page 5 and provide a full description of the technique in Supplementary Information Appendix B.
 
@@
 **Method: Incorporating Uncertainty** R4's comments suggested that it would be helpful to provide citations for the point that neglecting to include uncertainty can bias coefficients along with standard errors.
-We drop cites here to @Blackwell2017 [, 318-319]---who present a simulation that, while aimed at other issues, nonetheless illustrates the point neatly---as well as to @caughey2018 [254].
+We add cites to @Blackwell2017 [, 318-319]---who present a simulation that, while aimed at other issues, nonetheless illustrates the point neatly---as well as to @caughey2018 [254] at page 5.
 
@@
 Given that the DCPO model's advantages ultimately do not have a payoff in this case, we concluded that its inclusion in this 4000-word letter is an unnecessary distraction from our main points.
-So we took the _other_ suggestion from R1 on this topic, hinted at by R2 as well, to simply drop DCPO from the text entirely and move the analyses with the DCPO estimates to Appendix C in the Supplementary Information.
+So we took the _other_ suggestion from R1 on this topic, hinted at by R2 as well, to simply drop DCPO from the text entirely and move the analyses with the DCPO estimates to Appendix C in the Supplementary Information (and point to it in footnote 2 on page 4).
 
@@
 Thanks again!
+We discuss our expanded dataset at page 5.
 
@@
 In other words, it is not the case that Denmark is as likely to have a low value as China is to have a high one, but rather that Denmark is as likely to have a decline as China is to have a gain.
-We label the plot correctly now.
+We label the plot correctly now; it's on page 8.
 These results, we note, give further grounds for R2's concern about random-walk priors in latent variable models of public opinion when the estimates are then used in  thermostatic models: many of the year-to-year changes in democratic support are simply random---only 44% of the country-years in Claassen's sample are estimated from survey data, leaving most with only the prior---so it is not surprising that these changes are not well predicted by the variables in Claassen's model.
@@
 **Results** R1 noted that in addition to the pooled OLS models we had presented in Figure 1 and the ECMs we had presented in Figure 2, @Claassen2020a includes a pair of system GMM models and @Claassen2020b includes an additional specification that examines different aspects of democracy and also first-difference models for both specifications.
-We now present the results of all of these secondary models as well.
+We now present the results of all of these secondary models as well in Figures 1 and 2.
 (As the analyses presented in Table 2 of @Claassen2020a consider the relative strengths of the performances of democratic support and democratic satisfaction, rather than the relationship between democracy and democratic support that we focus on here, we followed the _APSR_ editor's advice and did not replicate those models---gratefully, too, because  reproducing the measure of democratic satisfaction would have been a ton of additional work.)
@@
 This critique struck home.
-We rewrote this section (and the introduction and conclusion) to be sure to emphasize the substantive implications of our findings.
+We rewrote the whole section (and the relevant parts of the introduction and conclusion) to be sure to emphasize the substantive implications of our findings.
 
@@
 **Discussion** R3 raised the point that Claassen's [-@Claassen2020a; -@Claassen2020b] measure of democratic support neglects that many people embrace authoritarian notions of democracy, and therefore the support for 'democracy' indicated by many of the items the measure incorporates often actually represents support for autocracy instead.
-We gladly incorporate this observation.
+We gladly incorporate this observation at the top of page 10.
 
@@
 **Discussion** R3 also pointed out that the relationship between democratic support and democracy is likely best understood to unfold on a much longer time scale than Claassen's [-@Claassen2020a] analysis implies.
-This is an excellent point, and we work it in here.
+This is an excellent point, and we work it into the final paragraph of the section, on page 10.
 

### 2021-08-19 paper/dcpo_demsupport.Rmd
removed the pagebreak to keep appendix into 8 ps; corrected the word count

@@
 
-(Word count: 3986)
+(Word count: 3888)
 
@@
 
-\pagebreak
 # The Method of Composition {#moc}
@@
 
-\pagebreak
 # DCPO Replication {#dcpo}
@@
 The DCPO model has several advantages over the @Claassen2019 model used in Claassen [-@Claassen2020a; -@Claassen2020b].
-First, while the @Claassen2019 model dichotomizes responses and so discards some information provided by 50 of the 52 survey items employed in Claassen [-@Claassen2020a; -@Claassen2020b], the DCPO model makes use of all of the information available from these ordinal items [@Solt2020a, 5].
-Second, as the DCPO model includes both parameters for the dispersion of each survey item and for the standard deviation of aggregate public opinion in each country-year, it is a complete population-level item-response model and so, unlike the @Claassen2019 model, is explicitly derived from an individual-level model of survey responses [@Solt2020a, 3-4; see also @McGann2014].
+First, while the @Claassen2019 model dichotomizes responses and so discards some information provided by 50 of the 52 survey items employed in Claassen [-@Claassen2020a; -@Claassen2020b], the DCPO model makes use of all of the information available from these ordinal items [@Solt2020a, p.5].
+Second, as the DCPO model includes both parameters for the dispersion of each survey item and for the standard deviation of aggregate public opinion in each country-year, it is a complete population-level item-response model and so, unlike the @Claassen2019 model, is explicitly derived from an individual-level model of survey responses [@Solt2020a, pp.3-4; see also @McGann2014].
 Third, to produce more sensible estimates of uncertainty for observations at the extremes of the scale [see @Linzer2015, 229], the DCPO model places bounds on its estimates of public opinion [@Solt2020a, 8].
-Further commending the DCPO model to us---and demonstrating that its advantages make a difference---the validation tests in @Solt2020a [, 10-12] reveal that it fits survey data on democratic support better than the @Claassen2019 model does.
+Further commending the DCPO model to us---and demonstrating that its advantages make a difference---the validation tests in @Solt2020a [pp.10-12] reveal that it fits survey data on democratic support better than the @Claassen2019 model does.
 
@@
 We then use the estimated public support from the DCPO model to replicate all of the analyses presented in the text.
-Figures A.1 and A.2 display these results as the righthand set of results, with the replication of the articles' original results based only on point estimates on the left and our extension with uncertainty and more data, but the articles' original, @Claassen2019, model in the middle for comparison.
+Figures \@ref(fig:plot-dcpoAJPS) and Figures \@ref(fig:plot-dcpoAPSR) display these results as the righthand set of results, with the replication of the articles' original results based only on point estimates on the left and our extension with uncertainty and more data, but the articles' original, @Claassen2019, model in the middle for comparison.
 

### 2021-08-27 paper/dcpo_demsupport.Rmd
the submitted version for RR
include names

--- 2021-08-18 paper/dcpo_demsupport.Rmd
@@
   | and Measurement Uncertainty
-# thanks: "The authors contributed equally to this work.  Corresponding author: [yuehu@mail.tsinghua.edu.cn](mailto:yuehu@mail.tsinghua.edu.cn).  Current version: `r format(Sys.time(), '%B %d, %Y')`."
-
-# author:
-# - name: Yuehong 'Cassandra' Tai
-#   affiliation: University of Iowa
-# - name: Yue Hu
-#   affiliation: Tsinghua University
-# - name: Frederick Solt
-#   affiliation: University of Iowa
+thanks: "The authors contributed equally to this work.  Corresponding author: [yuehu@mail.tsinghua.edu.cn](mailto:yuehu@mail.tsinghua.edu.cn).  Current version: August 20, 2021."
+
+author: "Yuehong 'Cassandra' Tai^[University of Iowa], Yue Hu^[Tsinghua University], and Frederick Solt$^{\\dagger}$"
 
@@
 
-date: " "
+date: "August 20, 2021"
 editor_options: 

### 2021-09-16 paper/dcpo_demsupport.Rmd

@@
 We then work to minimize the measurement uncertainty in public support by incorporating additional survey data.
-Even with this expanded evidentiary base, however, our analyses fail to yield evidence in support of either hypothesis, underscoring the necessity of accounting for measurement uncertainty.
-[144/150 words]"
+Even with this expanded evidentiary base, however, our analyses fail to yield evidence in support of either hypothesis, underscoring the necessity of accounting for measurement uncertainty."
 keywords: "Democratization, public support, regime survival, measurement uncertainty, latent variables"
@@
 
-(Word count: 3986)
-
 It has long been argued that democratic regimes and public support for them are mutually reinforcing: that high levels of public support ensure democracies remain strong, and that experience with democratic governance generates robust public support [see, e.g., @lipset_social_1959; @Easton1965].

### 2021-10-31 paper/dcpo_demsupport.Rmd
correct MOC's indice

@@
 
-where $\theta$ is latent varibles with measurement errors conditional on data Z and a measurement model, $w$ is other predictors without errors, $Z$ is indicators for latent variables $X$, and $y$ is the outcome variable.
+where $\theta$ is latent varibles with measurement errors conditional on data Z and a measurement model, $w$ is other predictors without errors, $Z$ is indicators for latent variables $\theta$, and $y$ is the outcome variable.
 In this way, we incorportate uncertainty in measuring predictor $\theta$, and uncertainty in the effects of latent variables $\theta$ and other variables $w$ on outcome variable $y$ [@Treier2008, 215].
-To sample from the conditional dentsity and the marginal density in the right side of the equation, we follow iterative Monte Carlo procdure described by @Treier2008, at iteration t,
-
-1. We sample $\theta^{s}$ from its posterior distribution $p(\theta|Z)$ and $y$ from $p(y|Z)$.
+To sample from the conditional density and the marginal density in the right side of the equation, we follow iterative Monte Carlo procedure described by @Treier2008, at iteration t,
+
+1. We sample $\theta^{t}$ from its posterior distribution $p(\theta|Z)$.
 
 2.
-For each analysis model, we run the model with $y$, $\theta$, and $w$, and save the coefficient estimates $\beta^{s}$ and variance-covariance matrix of $\beta^{s}$, $V^{s}$, both of which change due to the uncertainty in $\theta^{s}$ and $y^{s}$.
-
-3. We sample $\tilde{\beta^{t}}$ from the multivariate normal density with mean vector $\beta{s}$ and variance-covariace matrix $V^{s}$.
-
-We incorporate uncertainty for five variables, public support for democracy, liberal democracy, electoral democracy, the liberal component index, and the corruption perceptions index.
+For each analysis model, we run the model with $\theta^{t}$, and $w$, and save the coefficient estimates $\beta^{t}$ and variance-covariance matrix of $\hat{\beta^{t}}$, $\hat{V^{t}}$, both of which change due to the uncertainty in $\theta$.
+
+3. We sample $\tilde{\beta^{t}}$ from the multivariate normal density with mean vector $\beta{t}$ and variance-covariance matrix $V^{t}$.
+
+In the step 3, the marginal distribution of a parameter vector $\beta$ was estimated, intergrating over $p(\theta|Z)$:
+
+\begin{equation}
+p(\beta|w,y) = \[ \int_{\theta} p(\beta|\theta,w,y)p(\theta|Z) \,d\theta\]
+\end{equation}
+
+In our re-analyses, we incorporate uncertainty for five variables, public support for democracy, liberal democracy, electoral democracy, the liberal component index, and the corruption perceptions index.
 For each of these five latent variables, we take 900 draws from its posterior distribution.
@@
 In next step, we run each of analysis models with these 900 datesets independently and save the resulting estimates of coefficients and the matrix of variance-covariance for each run.
-We then draw one sample from the mulitivariate normal distribution with the mean vector of coefficient estimates and variance-covariance matrix produced from each run.
+We then draw one sample from the multivariate normal distribution with the mean vector of coefficient estimates and variance-covariance matrix produced from each run.
 This procedure finally yields 900 samples of estimated coefficients drawn from the joint density of $\beta$ and $\theta$.

### 2021-11-01 paper/dcpo_demsupport.Rmd
preparing for the tables

--- 2021-08-27 paper/dcpo_demsupport.Rmd
@@
   | and Measurement Uncertainty
-thanks: "The authors contributed equally to this work.  Corresponding author: [yuehu@mail.tsinghua.edu.cn](mailto:yuehu@mail.tsinghua.edu.cn).  Current version: August 20, 2021."
-
-author: "Yuehong 'Cassandra' Tai^[University of Iowa], Yue Hu^[Tsinghua University], and Frederick Solt$^{\\dagger}$"
+# thanks: "The authors contributed equally to this work.  Corresponding author: [yuehu@mail.tsinghua.edu.cn](mailto:yuehu@mail.tsinghua.edu.cn).  Current version: `r format(Sys.time(), '%B %d, %Y')`."
+
+# author:
+# - name: Yuehong 'Cassandra' Tai
+#   affiliation: University of Iowa
+# - name: Yue Hu
+#   affiliation: Tsinghua University
+# - name: Frederick Solt
+#   affiliation: University of Iowa
 
@@
 
-date: "August 20, 2021"
+date: " "
 editor_options: 
@@
   gridExtra,
+  modelsummary,
   # drhutools, # for colorful plots
@@
 # dotwhisker::small_multiple() hacks
-body(small_multiple)[[17]] <- substitute(
+body(small_multiple)[[19]] <- substitute(
   p <- ggplot(df, aes(y = estimate, ymin = conf.low, ymax = conf.high, 
@@
 
-# Online Supplementary Information {-}
+# Online Supplementary Information Appendix {-}
 # (APPENDIX) Appendix {-}
@@
 \pagebreak
+
 # The Method of Composition {#moc}
@@
 \pagebreak
+
 # DCPO Replication {#dcpo}

### 2021-11-01 paper/dcpo_demsupport.Rmd

@@
 
+## Numeric Results for Replicating Claassen 2020a {#fullAJPS}
+
+```{r num-labelAJPS, eval=TRUE}
+names_coef <- c(
+  "(Intercept)" = "(Intercept)",
+  "plm::lag(Libdem_VD, 1:2)1" = "Democracy[t-1]",
+  "plm::lag(Libdem_VD, 1:2)2"  = "Democracy[t-2]",
+  "plm::lag(SupDem_trim, 1)" = "Support[t-1]",
+  "plm::lag(SupDem_Democ, 1)" = "Support in Democracy",
+  "plm::lag(theta_dem_trim, 1)" = "Support in Democracy",
+  "plm::lag(SupDem_Autoc, 1)" = "Support in Autocracy",
+  "plm::lag(theta_aut_trim, 1)" = "Support in Autocracy",
+  "plm::lag(lnGDP_imp, 1)" = "Log GDP Per Capita[t-1]",
+  "plm::lag(GDP_imp_grth, 1)"  = "GDP Per Capita Growth[t-1]",
+  "plm::lag(Libdem_regUN, 1)" = "Regional Democracy[t-1]",
+  "plm::lag(Pr_Muslim, 1)" = "Percent Muslim[t-1]",
+  "plm::lag(Res_cp_WDI_di, 1)" = "Resource Dependence[t-1]"
+)
+```
+
+```{r num-pointAJPS, results='asis', eval=TRUE}
+tb_result_cls <- purrr::map(result_clsAJPS, ~ {
+  names(.) <- c("tidy", "glance")
+  class(.) <- "modelsummary_list"
+  return(.)})
+names(tb_result_cls) <- c("Pooled", "Pooled-Regime", 
+                          "GMM", "GMM-Regime")
+modelsummary(tb_result_cls,  
+             statistic = "conf.int",
+             coef_map = names_coef, 
+             output = "latex", 
+             title = "Original") %>%
+
+  kableExtra::kable_styling(font_size = 8) %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+\blandscape
+
+## Numeric Results of Figure \@ref(fig:plot-fullAPSR) {#fullAPSR}
+
+```{r num-labelAPSR, eval=TRUE}
+names_coef <- c(
+  "(Intercept)" = "(Intercept)",
+  "plm::lag(SupDem_trim, 1:2)1" = "Democratic Mood (t-1)",
+  "plm::lag(SupDem_trim, 1:2)2" = "Democratic Mood (t-2)",
+  "diff(Libdem_z, lag = 1)" = "Liberal Democracy (Difference)",
+  "Libdem_z" = "Liberal Democracy (Difference)",
+  "plm::lag(Libdem_z, 1)" = "Liberal Democracy (t-1)",
+  "diff(Polyarchy_z, lag = 1)" = "Electoral Democracy (Difference)",
+  "Polyarchy_z" = "Electoral Democracy (Difference)",
+  "plm::lag(Polyarchy_z, 1)" = "Electoral Democracy (t-1)",
+  "diff(Liberal_z, lag = 1)" = "Minoritarian Democracy (Difference)",
+  "Liberal_z" = "Minoritarian Democracy (Difference)",
+  "plm::lag(Liberal_z, 1)" = "Minoritarian Democracy (t-1)",
+  "diff(lnGDP_imp, lag = 1)" = "Log GDP Per Capita (Difference)",
+  "lnGDP_imp" = "Log GDP per capita (Difference)",
+  "plm::lag(lnGDP_imp, 1)" = "Log GDP (t-1)",
+  "diff(Corrup_TI_z, lag = 1)" = "Corruption (Difference)",
+  "Corrup_TI_z" = "Corruption (Difference)",
+  "plm::lag(Corrup_TI_z, 1)" = "Corruption (t-1)"
+)
+```
+
+```{r num-pointAPSR, results='asis', eval=TRUE}
+tb_result_clsAPSR <- map(result_clsAPSR, ~ {
+  names(.) <- c("tidy", "glance")
+  class(.) <- "modelsummary_list"
+  return(.)}) %>% 
+  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
+      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]
+names(tb_result_clsAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
+modelsummary(tb_result_clsAPSR, 
+             stars = TRUE,
+             coef_map = names_coef, 
+             output = "latex", 
+             title = "The Effect of Public Support on Democracy with Uncertainty (Original)") %>% 
+  kableExtra::kable_styling(font_size = 7) %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+\elandscape
+
 # The Method of Composition {#moc}
@@
 
+where $\theta$ is latent variables with measurement errors conditional on data Z and a measurement model, $w$ is other predictors without errors, $Z$ is indicators for latent variables $\theta$, and $y$ is the outcome variable.
+In this way, we incorporate uncertainty in measuring predictor $\theta$, and uncertainty in the effects of latent variables $\theta$ and other variables $w$ on outcome variable $y$ [@Treier2008, 215].
+To sample from the conditional density and the marginal density in the right side of the equation, we follow iterative Monte Carlo procedure described by @Treier2008, at iteration t,
+
+1. We sample $\theta^{t}$ from its posterior distribution $p(\theta|Z)$.
+
+2.
+For each analysis model, we run the model with $\theta^{t}$, and $w$, and save the coefficient estimates $\beta^{t}$ and variance-covariance matrix of $\hat{\beta^{t}}$, $\hat{V^{t}}$, both of which change due to the uncertainty in $\theta$.
+
+3. We sample $\tilde{\beta^{t}}$ from the multivariate normal density with mean vector $\beta{t}$ and variance-covariance matrix $V^{t}$.
+
+In the step 3, the marginal distribution of a parameter vector $\beta$ was estimated, intergrating over $p(\theta|Z)$:
+
+\begin{equation}
+p(\beta|w,y) = \int_{\theta} p(\beta|\theta,w,y)p(\theta|Z) \,d\theta
+\end{equation}
+
+In our re-analyses, we incorporate uncertainty for five variables, public support for democracy, liberal democracy, electoral democracy, the liberal component index, and the corruption perceptions index.
 where $\theta$ is latent varibles with measurement errors conditional on data Z and a measurement model, $w$ is other predictors without errors, $Z$ is indicators for latent variables $X$, and $y$ is the outcome variable.

### 2021-11-07 paper/dcpo_demsupport.Rmd
table ready

--- 2021-11-01 paper/dcpo_demsupport.Rmd
@@
 ```{r data-input, include=FALSE, cache=TRUE}
-
-supdem <- read.csv(here("data", "Support_democracy_ajps.csv"))
-sd.plm <- pdata.frame(supdem, index = c("Country", "Year"))
-
 load(here("data", "correct_cls_ajps.rda")) # https://osf.io/52u7n/download
@@
 mocresult_dcpoAJPS <- readRDS(here("output","estimates_moc_dcpoAJPS.RDS"))
-
 ```
@@
 ```{r pointAJPS}
+supdem <- read.csv(here("data", "Support_democracy_ajps.csv"))
+sd.plm <- pdata.frame(supdem, index = c("Country", "Year"))
+
 ls_iv <- c("plm::lag(SupDem_trim, 1)",
@@
     )
+
 result_regime <- bind_rows(
@@
            model = "Model 4 (System GMM)")
+
 result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
@@
 \renewcommand{\thefigure}{A.\arabic{figure}}
+\setcounter{table}{0}
+\renewcommand{\thetable}{A.\arabic{table}}
 
@@
 
+## Numeric Results for Figure \@ref(fig:plot-fullAJPS) and Figure \@ref(fig:plot-fullAPSR)
+
+Note that, for the GMM models, the original publication presented the observation number based on the trimmed data, i.e., "2435", while the tabulating function in the replication file (line 86) uses the full used-observation number, "4735."
+We follow the replication file in the following tables.
+
+```{r num-labelAJPS}
+names_coef <- c(
+  "(Intercept)" = "(Intercept)",
+  "plm::lag(Libdem_VD, 1:2)1" = "Democracy (t-1)",
+  "plm::lag(Libdem_VD, 1:2)2"  = "Democracy (t-2)",
+  "plm::lag(SupDem_trim, 1)" = "Support (t-1)",
+  "plm::lag(SupDem_Democ, 1)" = "Support in Democracy",
+  "plm::lag(theta_dem_trim, 1)" = "Support in Democracy",
+  "plm::lag(SupDem_Autoc, 1)" = "Support in Autocracy",
+  "plm::lag(theta_aut_trim, 1)" = "Support in Autocracy",
+  "plm::lag(lnGDP_imp, 1)" = "Log GDP Per Capita (t-1)",
+  "plm::lag(GDP_imp_grth, 1)"  = "GDP Per Capita Growth (t-1)",
+  "plm::lag(Libdem_regUN, 1)" = "Regional Democracy (t-1)",
+  "plm::lag(Pr_Muslim, 1)" = "Percent Muslim (t-1)",
+  "plm::lag(Res_cp_WDI_di, 1)" = "Resource Dependence (t-1)"
+)
+
+names_gof <- tibble::tribble(
+         ~raw,           ~clean, ~fmt,
+       "nobs", "N observations",    0,
+  "n.country",    "N countries",    0,
+     "n.inst",  "N instruments",    0
+  )
+```
+
+```{r num-pointAJPS, results='asis'}
+tb_result_cls <- purrr::map(result_clsAJPS, ~ {
+  names(.) <- c("tidy", "glance")
+  class(.) <- "modelsummary_list"
+  return(.)})
+names(tb_result_cls) <- c("Pooled", "Pooled-Regime", 
+                          "GMM", "GMM-Regime")
+modelsummary(tb_result_cls,  
+             coef_map = names_coef,
+             gof_map = names_gof,
+             output = "latex", 
+             title = "The Effect of Democracy on Change in Public Support (Original Results)") %>%
+  kableExtra::kable_styling(font_size = 8) %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+```{r tabulatingFun-AJPS}
+# function to extract statistics of MOC models
+extract_statsAJPS <- function(input_data) {
+    # Reproducing the chunk `pointAJPS` with updated data
+    sd.plm <- pdata.frame(input_data, index = c("country", "year"))
+
+    ls_iv <- c(
+        "plm::lag(SupDem_trim, 1)",
+        "plm::lag(theta_dem_trim, 1) + plm::lag(theta_dem_trim, 1)"
+    )
+
+    ls_method <- c("plm", "pgmm")
+
+    ls_eq <-
+        glue(
+            "Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + {ls_iv} + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)"
+        )
+
+    ls_mod <- c(
+        glue("plm({ls_eq}, model = 'pooling', data = sd.plm)"),
+        glue(
+            "pgmm({ls_eq} | plm::lag(Libdem_VD, 3:5), data = sd.plm, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
+        )
+    )
+
+    df_result_cls <- map(ls_mod, function(mod) {
+        result <- eval(parse(text = mod))
+        glance_result <- glance(result)
+        return(glance_result)
+    })
+
+    names(df_result_cls) <-
+        c("pooled", "pooled-regime", "gmm", "gmm-regime")
+
+    return(df_result_cls)
+}
+
+# function to produce data formated to fit `modelsummary`
+format_resultAJPS <- function(condition, input_data) {
+    tidy_mocPooled <-
+        filter(result_pooledAJPS, submodel == condition)
+    tidy_mocRegime <-
+        filter(result_regimeAJPS, submodel == condition)
+    tidy_mocAJPS <- bind_rows(tidy_mocPooled, tidy_mocRegime)
+
+    vec_names <- levels(tidy_mocAJPS$model)
+
+    tidy_mocAJPS <- group_split(tidy_mocAJPS, model)
+    names(tidy_mocAJPS) <- vec_names
+
+    glance_mocAJPS <- extract_statsAJPS(input_data)
+
+    tb_resultAJPS <- map2(tidy_mocAJPS, glance_mocAJPS, ~ {
+        result <- list(tidy = .x,
+                       glance = .y)
+        class(result) <- "modelsummary_list"
+        return(result)
+    })
+
+    names(tb_resultAJPS) <- c("Pooled", "Pooled-Regime",
+                              "GMM", "GMM-Regime")
+    return(tb_resultAJPS)
+}
+```
+
+```{r num-pureAJPS, results='asis'}
+tb_pureAJPS <- format_resultAJPS(condition = "With Uncertainty",
+                                      input_data = correct_cls_ajps[[1]])
+
+modelsummary(tb_pureAJPS,
+             coef_map = names_coef,
+             gof_map = names_gof,
+             output = "latex",
+             title = "The Effect of Democracy on Change in Public Support (With Uncertainty)") %>%
+    kableExtra::kable_styling(font_size = 8) %>%
+    kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+```{r num-expAJPS, results='asis'}
+tb_expAJPS <- format_resultAJPS(condition = "Uncertainty & More Data",
+                                      input_data = expcor_cls_ajps[[1]])
+
+modelsummary(tb_expAJPS, 
+             coef_map = names_coef,
+             gof_map = names_gof,
+             output = "latex", 
+             title = "The Effect of Democracy on Change in Public Support (Uncertainty \\& More Data)") %>%
+  kableExtra::kable_styling(font_size = 8) %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+\blandscape
+
+```{r num-labelAPSR}
+names_coef <- c(
+  "(Intercept)" = "(Intercept)",
+  "plm::lag(SupDem_trim, 1:2)1" = "Democratic Mood (t-1)",
+  "plm::lag(SupDem_trim, 1:2)2" = "Democratic Mood (t-2)",
+  "diff(Libdem_z, lag = 1)" = "Liberal Democracy (Difference)",
+  "Libdem_z" = "Liberal Democracy (Difference)",
+  "plm::lag(Libdem_z, 1)" = "Liberal Democracy (t-1)",
+  "diff(Polyarchy_z, lag = 1)" = "Electoral Democracy (Difference)",
+  "Polyarchy_z" = "Electoral Democracy (Difference)",
+  "plm::lag(Polyarchy_z, 1)" = "Electoral Democracy (t-1)",
+  "diff(Liberal_z, lag = 1)" = "Minoritarian Democracy (Difference)",
+  "Liberal_z" = "Minoritarian Democracy (Difference)",
+  "plm::lag(Liberal_z, 1)" = "Minoritarian Democracy (t-1)",
+  "diff(lnGDP_imp, lag = 1)" = "Log GDP Per Capita (Difference)",
+  "lnGDP_imp" = "Log GDP per capita (Difference)",
+  "plm::lag(lnGDP_imp, 1)" = "Log GDP (t-1)",
+  "diff(Corrup_TI_z, lag = 1)" = "Corruption (Difference)",
+  "Corrup_TI_z" = "Corruption (Difference)",
+  "plm::lag(Corrup_TI_z, 1)" = "Corruption (t-1)"
+)
+```
+
+```{r num-pointAPSR, results='asis'}
+tb_result_clsAPSR <- map(result_clsAPSR, ~ {
+  names(.) <- c("tidy", "glance")
+  class(.) <- "modelsummary_list"
+  return(.)}) %>% 
+  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
+      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]
+names(tb_result_clsAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")
+
+modelsummary(tb_result_clsAPSR, 
+             stars = FALSE,
+             coef_map = names_coef,
+             gof_map = names_gof, 
+             coef_omit = "Int",
+             output = "latex", 
+             title = "The Effect of Public Support on Democracy with Uncertainty (Original)") %>% 
+  kableExtra::kable_styling(font_size = 7) %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+```{r tabulatingFun-APSR}
+## function to extract statistics of MOC models
+extract_statsAPSR <- function(input_data){
+    # Reproducing the chunk `pointAPSR` with updated data
+    sd.plm <- pdata.frame(input_data, index = c("country", "year"))
+
+    ls_ivECM <- c("diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)", 
+                  "diff(Polyarchy_z, lag = 1) + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)")
+    ls_ctrlECM <- c("", " + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1)")
+
+    ls_eqECM <- glue("diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)") %>% 
+      outer(ls_ctrlECM, paste0) %>% 
+      as.vector()
+
+    ls_ivFD <- c("Libdem_z",
+                 "Polyarchy_z + Liberal_z")
+
+    ls_ctrlFD <- c("", " + Corrup_TI_z")
+
+    ls_eqFD <- glue("SupDem_trim ~ {ls_ivFD} + lnGDP_imp") %>% 
+      outer(ls_ctrlFD, paste0) %>% 
+      as.vector()
+
+    ls_mod <- c(
+      glue("plm({ls_eqECM}, model = 'pooling', data = sd.plm)"),
+      glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = sd.plm)")
+    )
+
+    df_result_clsAPSR <- map(ls_mod, function(mod) {
+      result <- eval(parse(text = mod))
+      glance_result <- glance.plm(result)
+      return(glance_result)
+    })
+
+    names(df_result_clsAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", "fd1", "fd-regime1", "fd2", "fd-regime2")
+
+    return(df_result_clsAPSR)
+}
+
+# function to produce data formated to fit `modelsummary`
+format_resultAPSR <- function(condition, input_data){
+    tidy_mocAPSR1 <-
+        filter(result_APSR1, submodel == condition)
+    tidy_mocRegAPSR1 <-
+        filter(result_RegAPSR1, submodel == condition)
+    tidy_mocAPSR2 <-
+        filter(result_APSR2, submodel == condition)
+    tidy_mocRegAPSR2 <-
+        filter(result_RegAPSR2, submodel == condition)
+
+    tidy_mocAPSR <-
+        bind_rows(tidy_mocAPSR1,
+                  tidy_mocRegAPSR1,
+                  tidy_mocAPSR2,
+                  tidy_mocRegAPSR2)
+
+    vec_names <- levels(tidy_mocAPSR$model)
+
+    tidy_mocAPSR <- group_split(tidy_mocAPSR, model)
+    names(tidy_mocAPSR) <- vec_names
+    tidy_mocAPSR <-
+        tidy_mocAPSR[c(
+            "Model 1.1 (ECM)",
+            "Model 2.1 (ECM)",
+            "Model 1.3 (FD)",
+            "Model 2.3 (FD)",
+            "Model 1.2 (ECM)",
+            "Model 2.2 (ECM)",
+            "Model 1.4 (FD)",
+            "Model 2.4 (FD)"
+        )]
+
+    glance_mocAPSR <- extract_statsAPSR(input_data)
+    glance_mocAPSR <-
+        glance_mocAPSR[c(
+            "pooled1",
+            "pooled-regime1",
+            "fd1",
+            "fd-regime1",
+            "pooled2",
+            "pooled-regime2",
+            "fd2",
+            "fd-regime2"
+        )]
+
+    tb_pureAPSR <- map2(tidy_mocAPSR, glance_mocAPSR, ~ {
+        result <- list(tidy = .x,
+                       glance = .y)
+        class(result) <- "modelsummary_list"
+        return(result)
+    })
+
+    names(tb_pureAPSR) <-
+        c(
+            "ECM",
+            "ECM-Regime",
+            "FD",
+            "FD-Regime",
+            "ECM Corrup",
+            "ECM Corrup-Regime",
+            "FD Corrup",
+            "FD Corrup-Regime"
+        )
+
+    return(tb_pureAPSR)
+}
+```
+
+```{r num-pureAPSR, results='asis'}
+tb_pureAPSR <- format_resultAPSR(condition = "With Uncertainty",
+                                      input_data = correct_cls_apsr[[1]])
+
+modelsummary(tb_pureAPSR, 
+             stars = FALSE,
+             coef_map = names_coef,
+             gof_map = names_gof,
+             output = "latex", 
+             title = "The Effect of Public Support on Democracy (With Uncertainty)") %>% 
+  kableExtra::kable_styling(font_size = 7) %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+```{r num-expAPSR, results='asis'}
+tb_expAPSR <- format_resultAPSR(condition = "Uncertainty & More Data",
+                                      input_data = expcor_cls_apsr[[1]])
+
+modelsummary(tb_expAPSR, 
+             stars = FALSE,
+             coef_map = names_coef,
+             gof_map = names_gof,
+             output = "latex", 
+             title = "The Effect of Public Support on Democracy (Uncertainty \\& More Data)") %>% 
+  kableExtra::kable_styling(font_size = 7) %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+\elandscape
+
 # The Method of Composition {#moc}

### 2021-11-07 R/tidy_pgmm.r

@@ -70,8 +70,7 @@ tidy.pgmm <- function(x,
     result
 }
 
-
-glance.pgmm <- function(x, ...) {
+glance.plm <- function(x, ...) {
     s <- summary(x)
     as_glance_tibble(
         # chisq.sargan = unname(s$sargan$statistic),
@@ -89,7 +88,8 @@ glance.pgmm <- function(x, ...) {
     )
 }
 
-glance.plm <- function(x, ...) {
+
+glance.pgmm <- function(x, ...) {
     s <- summary(x)
     as_glance_tibble(
         # chisq.sargan = unname(s$sargan$statistic),
@@ -102,7 +102,7 @@ glance.plm <- function(x, ...) {
         # arellano.bond2 = unname(x$m2$statistic[1,]),
         nobs = stats::nobs(x),
         n.country = pdim(x)$nT$n,
-        # n.inst = dim(x$W[[1]])[2],
-        na_types = "ii"
+        n.inst = dim(x$W[[1]])[2],
+        na_types = "iii"
     )
 }

### 2021-11-08 paper/dcpo_demsupport.Rmd
adding corrected data descriptions for #34; cleaning the setup chunk for #29

@@
 
-if (!require(pacman)) install.packages("pacman")
+if (!require(pacman))
+    install.packages("pacman")
 library(pacman)
-
-p_install(janitor, force = FALSE)
 
@@
 # remotes::install_github(ls_pacGH, force = FALSE)
+
+p_install(janitor, force = FALSE)
 
@@
     plm,
+
     # presentation
@@
     modelsummary,
-  # drhutools, # for colorful plots
+    drhutools, ## for colorful plots
     dotwhisker,
     latex2exp,
+
     # data wrangling
@@
     tidyverse,
-  glue
-)
+    glue)
 
@@
 
-source(here("R", "tidy_pgmm.r"))
-source(here("R", "moc_function.R")) 
-source(here("R", "moc_summary.R")) 
-source(here("R", "customFunctions.R"))
-
-# dotwhisker::small_multiple() hacks
+source(here("R", "customFunctions.R")) ## analyzing and presenting functions
+
+theme_set(theme_bw())
+
+## dotwhisker::small_multiple() hacks
 body(small_multiple)[[19]] <- substitute(
-  p <- ggplot(df, aes(y = estimate, ymin = conf.low, ymax = conf.high, 
-                      x = as.factor(model), colour = submodel)) +
+    p <-
+        ggplot(
+            df,
+            aes(
+                y = estimate,
+                ymin = conf.low,
+                ymax = conf.high,
+                x = as.factor(model),
+                colour = submodel
+            )
+        ) +
         do.call(geom_pointrange, point_args) +
         ylab("") + xlab("") +
-    facet_grid(term ~ .,
+        facet_grid(
+            term ~ .,
             scales = "free",
-               labeller = label_parsed,    # enable LaTeX facet labels
-               switch = "y") +             # put facet labels on left
+            labeller = label_parsed,
+            # enable LaTeX facet labels
+            switch = "y"
+        ) +             # put facet labels on left
         scale_y_continuous(position = "right") # put axis label on right
@@
 
-theme_set(theme_bw())
 ```
@@
 ```{r data-input, include=FALSE, cache=TRUE}
+## Replication data
 load(here("data", "correct_cls_ajps.rda")) # https://osf.io/52u7n/download
@@
 load(here("data", "expcor_cls_apsr.rda"))  # https://osf.io/rvc92/download
-load(here("data","claassen_replication_input.rda"))
-load(here("data","exp_claassen_input.rda"))
-#load(here("data","dcpo_apsr.rda"))
-#load(here("data","dcpo_ajps.rda"))
-
-result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
-result_clsAJPS <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
-
-mocresult_correctAJPS <- readRDS(here("output", "estimates_moc_correctAJPS.RDS")) 
-mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expcorAJPS.RDS"))
-mocresult_correctAPSR <- readRDS(here("output", "estimates_moc_correctAPSR.RDS"))
-mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expcorAPSR.RDS"))
-mocdcpo_APSR <- readRDS(here("output","estimates_moc_dcpoAPSR.RDS"))
-mocresult_dcpoAJPS <- readRDS(here("output","estimates_moc_dcpoAJPS.RDS"))
+load(here("data", "exp_claassen_input.rda")) # Source???
+
+## Preload chunk-produced results to speed up the compiling
+## One can find how they were created by locating the corresponding chunks
+
+result_clsAPSR <-
+    readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
+result_clsAJPS <-
+    readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
+
+mocresult_correctAJPS <-
+    readRDS(here("output", "estimates_moc_correctAJPS.RDS"))
+mocresult_expAJPS <-
+    readRDS(here("output", "estimates_moc_expcorAJPS.RDS"))
+mocresult_correctAPSR <-
+    readRDS(here("output", "estimates_moc_correctAPSR.RDS"))
+mocresult_expAPSR <-
+    readRDS(here("output", "estimates_moc_expcorAPSR.RDS"))
+mocdcpo_APSR <- readRDS(here("output", "estimates_moc_dcpoAPSR.RDS"))
+mocresult_dcpoAJPS <-
+    readRDS(here("output", "estimates_moc_dcpoAJPS.RDS"))
 ```
@@
 
-Note that, for the GMM models, the original publication presented the observation number based on the trimmed data, i.e., "2435", while the tabulating function in the replication file (line 86) uses the full used-observation number, "4735."
+During the replications of @Claassen2020a;@Claassen2020b, we found several miscoding across the original data.
+For example, in @Claassen2020b that the author coded the option "Necesitamos un líder fuerte que no tenga que ser elegid" as "strong_lapop_2" for the question:
+
+> Hay gente que dice que necesitamos un líder fuerte que no tenga que ser elegido a través del voto.
+AUT1 Otros dicen que aunque las cosas no funcionen, la democracia electoral, o sea el voto popular, es siempre
+lo mejor. ¿Qué piensa usted? [Leer alternativas]
+
+But according to the description of the question, this ought to be "strong_amb_1."
+Another example involves a miscount of the midpoint of its three-point scale as a positive, democracy-supporting response, when the original work coded "evdemoc_asiab" in the Asian Barometer.
+In a separate ongoing research project, we will identify the main types of miscoding and evaluate the extent to which they affect on the inferences.
+In this work, we use the corrected data for the replications with uncertainty to ensure that the data quality would not distort the results.
+
+Moreover, for the GMM models, the original publication presented the observation number based on the trimmed data, i.e., "2435", while the tabulating function in the replication file (line 86) uses the full used-observation number, "4735."
 We follow the replication file in the following tables.

### 2021-11-08 R/customFunctions.R

@@ -1,4 +1,7 @@
+# Variance Calculation ------------------------------------------------------------------
+
 ## Beck-Katz panel-corrected standard errors
+
 vcovBK_se <- function(x) {
     plm::vcovBK(x, cluster = "time") %>% 
         diag() %>% 
@@ -31,4 +34,243 @@ get_legend<-function(myggplot){
     leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
     legend <- tmp$grobs[[leg]]
     return(legend)
+}
+
+
+# Method of composition ------------------------------------------------------------
+
+vcovBK <- function(mod) {
+    plm::vcovBK(mod, cluster = "time") 
+}
+
+plmHC <- function (mod) {
+    plm::vcovHC(mod, method="arellano", cluster="group")
+}
+
+
+## For Ajps pooled ols, using vcov=vcovBK
+methodComposition1 <- function (data, model, vcov=vcovBK, rsq=TRUE) {
+    aData <- data[[1]]
+    aMod <- eval(parse(text = model))
+    
+    coefdf <- as.data.frame(matrix(nrow=length(data), ncol=length(coef(aMod))))
+    R2 <- data.frame(rsq=rep(NA, length(data)), adjrsq=rep(NA, length(data)))
+    
+    for (s in seq_along(data)) {
+        ## (1) Sample from p(x)
+        data_sample <- data[[s]]
+        ## (2) Sample from p(B|x,y):
+        ##     (a) Estimate B_s and Cov(B_s) conditional on x_s.
+        mod_sample <- update(aMod, data=data_sample)
+        hatB_sample <- coef(mod_sample)
+        hatV_sample <- vcov(mod_sample)
+        ##     (b) Sample \data_sample{B_s} from MV(\hat{B_sample}, \hat{Cov(B_sample)}).
+        coefdf[s, ] <- MASS::mvrnorm(n = 1, mu = hatB_sample, Sigma = hatV_sample)
+        if (rsq) {
+            R2$rsq[s] <- summary(mod_sample)$r.squared["rsq"]
+            R2$adjrsq[s] <- summary(mod_sample)$r.squared["adjrsq"]
+        }
+    }
+    names(coefdf) <- names(coef(aMod))
+    if (rsq) {
+        coefdf$rsq <- R2$rsq
+        coefdf$adjrsq <- R2$adjrsq
+    }
+    return(coefdf)
+}
+
+
[…]

### 2021-11-08 paper/dcpo_demsupport.Rmd
colorful plots :P

@@
 
-# ls_pacGH <- c("fsolt/DCPOtools", "sammo3182/drhutools")
-# remotes::install_github(ls_pacGH, force = FALSE)
-
 p_install(janitor, force = FALSE)
+p_install_gh(c("fsolt/DCPOtools", "sammo3182/drhutools"), force = FALSE)
 
@@
 
-## Preload chunk-produced results to speed up the compiling
+## Preloading chunk-produced results to speed up the compiling
 ## One can find how they were created by locating the corresponding chunks
@@
 
-ls_eq <- glue("Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + {ls_iv} + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)")
+ls_eq <-
+    glue(
+        "Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + {ls_iv} + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)"
+    )
 
@@
 
-glance_cls <- map(df_result_cls, function(aResult){
-  if(class(aResult) == "plm"){ 
+glance_cls <- map(df_result_cls, function(aResult) {
+    if (class(aResult) == "plm") {
         glance.plm(aResult) # using the customized glance function
-  }else{
+    } else{
         glance(aResult)
@@
 result_clsAJPS <- map2(tidy_cls, glance_cls, ~ list(.x, .y))
-names(result_clsAJPS) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")
-
-saveRDS(result_clsAJPS, file = here::here("output", "estimates_clsMeanAJPS.RDS"))  
+names(result_clsAJPS) <-
+    c("pooled", "pooled-regime", "gmm", "gmm-regime")
+
+saveRDS(result_clsAJPS,
+        file = here::here("output", "estimates_clsMeanAJPS.RDS"))  
 ```
@@
 ```{r model-AJPS}
-
-#ls_iv <- c("plm::lag(theta, 1)", 
-#    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) ")
-
-ls_iv <- c("plm::lag(SupDem_trim, 1)", 
-    "plm::lag(theta_dem_trim, 1) + plm::lag(theta_aut_trim, 1) ") #use trimmed data
+ls_iv <- c(
+    "plm::lag(SupDem_trim, 1)",
+    "plm::lag(theta_dem_trim, 1) + plm::lag(theta_aut_trim, 1) "
+) #use trimmed data
 
@@
 )
-
 ```
@@
 ```{r mocResult-pureAJPS, eval=FALSE}
-
 df_correct_clsAjps <- purrr::map(1:900, function(anEntry) {
@@
 
-result_correct_clsUncertain  <- map(ls_mod_ajpsCLS[1:2], function(aMod){
-  result <- methodComposition1(df_correct_clsAjps,aMod)
+result_correct_clsUncertain  <-
+    map(ls_mod_ajpsCLS[1:2], function(aMod) {
+        result <- methodComposition1(df_correct_clsAjps, aMod)
     })
@@
 
-result_correct_clsUncertain_gmm  <- map(ls_mod_ajpsCLS[3:4], function(aMod){
-  result <- methodComposition2(df_correct_clsAjps,aMod)
+result_correct_clsUncertain_gmm  <-
+    map(ls_mod_ajpsCLS[3:4], function(aMod) {
+        result <- methodComposition2(df_correct_clsAjps, aMod)
     })
@@
 
-mocresult_correctAJPS <- append(result_correct_clsUncertain, result_correct_clsUncertain_gmm)
-
-saveRDS(mocresult_correctAJPS, file =here("output","estimates_moc_correctAJPS.RDS"))
-
+mocresult_correctAJPS <-
+    append(result_correct_clsUncertain,
+           result_correct_clsUncertain_gmm)
+
+saveRDS(mocresult_correctAJPS,
+        file = here("output", "estimates_moc_correctAJPS.RDS"))
 ```
@@
 ```{r mocResult-expAJPS, eval=FALSE}
-
 df_exp_clsAjps <- purrr::map(1:900, function(anEntry) {
@@
 result_pooled <- bind_rows(
-    mutate(result_clsAJPS[["pooled"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(result_clsAJPS[["pooled"]][[1]][, 1:3], submodel = "Point Estimates Only"),
     mutate(MOCsumm(mocresult_correctAJPS[["pooled"]]), submodel = "With Uncertainty"),
@@
 result_gmm <- bind_rows(
-    mutate(result_clsAJPS[["gmm"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(result_clsAJPS[["gmm"]][[1]][, 1:3], submodel = "Point Estimates Only"),
     mutate(MOCsumm(mocresult_correctAJPS[["gmm"]]), submodel = "With Uncertainty"),
@@
         term0 = rep(
-            c("Democracy\n (t-1)",
+            c(
+                "Democracy\n (t-1)",
                 "Democracy\n (t-2)",
@@
                 "Percent\n Muslim\n (t-1)",
-              "Resource\n dependence\n (t-1)"),
-            time = 6), 
+                "Resource\n dependence\n (t-1)"
+            ),
+            time = 6
+        ),
         type = factor(type, levels = c("Pooled~OLS", "System~GMM")),
-        submodel = factor(submodel, levels = c("Point Estimates Only", "With Uncertainty", "Uncertainty & More Data")),
-        model = factor(model, levels = paste0("Model ", rep(1:4), rep(c(" (Pooled OLS)", " (System GMM)"), each = 2)))
+        submodel = factor(
+            submodel,
+            levels = c(
+                "Point Estimates Only",
+                "With Uncertainty",
+                "Uncertainty & More Data"
+            )
+        ),
+        model = factor(model, levels = paste0("Model ", rep(1:4), rep(
+            c(" (Pooled OLS)", " (System GMM)"), each = 2
+        )))
     )
@@
 result_regime <- bind_rows(
-    mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(result_clsAJPS[["pooled-regime"]][[1]][, 1:3], submodel = "Point Estimates Only"),
     mutate(MOCsumm(mocresult_correctAJPS[["pooled-regime"]]), submodel = "With Uncertainty"),
@@
 result_regimeGmm <- bind_rows(
-    mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(result_clsAJPS[["gmm-regime"]][[1]][, 1:3], submodel = "Point Estimates Only"),
     mutate(MOCsumm(mocresult_correctAJPS[["gmm-regime"]]), submodel = "With Uncertainty"),
     mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), submodel = "Uncertainty & More Data")
-)%>% 
+) %>%
     mutate(type = "System~GMM",
@@
                 "Percent\n Muslim\n (t-1)",
-              "Resource\n dependence\n (t-1)"),
-            time = 6), 
+                "Resource\n dependence\n (t-1)"
+            ),
+            time = 6
+        ),
         type = factor(type, levels = c("Pooled~OLS", "System~GMM")),
-        submodel = factor(submodel, levels = c("Point Estimates Only","With Uncertainty", "Uncertainty & More Data")),
-        model = factor(model, levels = paste0("Model ", rep(1:4), rep(c(" (Pooled OLS)", " (System GMM)"), each = 2))))
-
+        submodel = factor(
+            submodel,
+            levels = c(
+                "Point Estimates Only",
+                "With Uncertainty",
+                "Uncertainty & More Data"
+            )
+        ),
+        model = factor(model, levels = paste0("Model ", rep(1:4), rep(
+            c(" (Pooled OLS)", " (System GMM)"), each = 2
+        )))
+    )
 ```
@@
 ajps_caption <- "Replications of Claassen (2020a), Table 1, 128."
+
 small_multiple(df_plot, dot_args = list(size = .9, fatten = 1)) +
     theme_bw() +
-    geom_hline(yintercept = 0, colour = "grey50", linetype = 2) +
-    scale_color_grey(start = 0.8, end = 0.4, 
+    geom_hline(yintercept = 0,
+               colour = "grey50",
+               linetype = 2) +
+    scale_color_gb(
+        palette = "digitMixed",
         name = "Replication",
-                     breaks=c("Point Estimates Only", "With Uncertainty", "Uncertainty & More Data"),
-                     labels=c("Point Estimates Only", "With Uncertainty", "Uncertainty & More Data")) +
-    theme(axis.text.x  = element_text(angle = 90, hjust = .5),
+        breaks = c(
+            "Point Estimates Only",
+            "With Uncertainty",
+            "Uncertainty & More Data"
+        ),
+        labels = c(
+            "Point Estimates Only",
+            "With Uncertainty",
+            "Uncertainty & More Data"
+        )
+    ) + 
+    theme(
+        axis.text.x  = element_text(angle = 90, hjust = .5),
         strip.text.y.left = element_text(angle = 0),
@@
         legend.text = element_text(size = 9),
-          legend.background = element_rect(color="gray90"),
+        legend.background = element_rect(color = "gray90"),
         legend.spacing = unit(-5, "pt"),
@@
         plot.title = element_text(hjust = 1.4),
-          plot.caption = element_text(size = 10, hjust = 0.2, margin = margin(t=15))) +
-  guides(color = guide_legend(override.aes = list(size=.3))) +
-  ggtitle("Dependent Variable: Level of Democracy") +
+        plot.caption = element_text(
+            size = 10,
+            hjust = 0.2,
+            margin = margin(t = 15)
+        )
+    ) +
+    guides(color = guide_legend(override.aes = list(size = .3))) +
+    ggtitle("Outcome Variable: Level of Democracy") +
     labs(caption = ajps_caption)
@@
 And again, the righthand results reveal that the additional data of our extension do not provide support for the original conclusion.
-<!-- In fact, once uncertainty is taken into account, the models of @Claassen2020b detect very little pattern in the year-to-year changes of public support for democracy at all. -->
 
@@
 
-ls_ivECM <- c("diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)", 
-              "diff(Polyarchy_z, lag = 1) + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)")
-ls_ctrlECM <- c("", " + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1)")
-
-ls_eqECM <- glue("diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)") %>% 
+ls_ivECM <- c(
+    "diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)",
+    "diff(Polyarchy_z, lag = 1) + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)"
+)
+ls_ctrlECM <-
+    c("", " + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1)")
+
+ls_eqECM <-
+    glue(
+        "diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)"
+    ) %>%
     outer(ls_ctrlECM, paste0) %>%
@@
 
-names(result_clsAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", 
-                           "fd1", "fd-regime1", "fd2", "fd-regime2")
+names(result_clsAPSR) <-
+    c(
+        "pooled1",
+        "pooled-regime1",
+        "pooled2",
+        "pooled-regime2",
+        "fd1",
+        "fd-regime1",
+        "fd2",
+        "fd-regime2"
+    )
 
@@
 ```{r model-APSR}
-ls_ivECM <- c("diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)", 
-              "diff(Polyarchy_z, lag = 1) + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)")
-ls_ctrlECM <- c("", " + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1)")
-
-ls_eqECM <- glue("diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)") %>% 
+ls_ivECM <- c(
+    "diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)",
+    "diff(Polyarchy_z, lag = 1) + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)"
+)
+ls_ctrlECM <-
+    c("", " + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1)")
+
+ls_eqECM <-
+    glue(
+        "diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)"
+    ) %>%
     outer(ls_ctrlECM, paste0) %>%
@@
 
-ls_eqFD <- glue("diff(SupDem_trim, lag = 1) ~ {ls_ivFD} + lnGDP_imp") %>% 
+ls_eqFD <-
+    glue("diff(SupDem_trim, lag = 1) ~ {ls_ivFD} + lnGDP_imp") %>%
     outer(ls_ctrlFD, paste0) %>%
@@
 ```{r mocResult-pureAPSR, eval=FALSE}
-
 df_correct_clsAPSR <- purrr::map(1:900, function(anEntry) {
@@
         plm::pdata.frame(index = c("country", "year"))
-}
-)
-
-mocresult_correctAPSR  <- map(ls_mod_apsrCLS, function(aMod){
-  result <- methodComposition3(df_correct_clsAPSR,aMod)
-})
-
-names(mocresult_correctAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
-                                "fd1", "fd-regime1", "fd2", "fd-regime2")
-
-saveRDS(mocresult_correctAPSR, file = here::here("ouput","estimates_moc_correctAPSR.RDS"))
-
+})
+
+mocresult_correctAPSR  <- map(ls_mod_apsrCLS, function(aMod) {
+    result <- methodComposition3(df_correct_clsAPSR, aMod)
+})
+
+names(mocresult_correctAPSR) <-
+    c(
+        "pooled1",
+        "pooled-regime1",
+        "pooled2",
+        "pooled-regime2",
+        "fd1",
+        "fd-regime1",
+        "fd2",
+        "fd-regime2"
+    )
+
+saveRDS(mocresult_correctAPSR,
+        file = here::here("ouput", "estimates_moc_correctAPSR.RDS"))
 ```
@@
 ```{r mocResult-expAPSR, eval=FALSE}
-
 df_exp_clsAPSR <- purrr::map(1:900, function(anEntry) {
@@
         plm::pdata.frame(index = c("country", "year"))
-}
-)
-
-mocresult_expAPSR <- map(ls_mod_apsrCLS, function(aMod){
-  result <- methodComposition3(df_exp_clsAPSR,aMod)
-})
-
-names(mocresult_expAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
-                                "fd1", "fd-regime1", "fd2", "fd-regime2")
-
-saveRDS(mocresult_expAPSR, file = here::here("output","estimates_moc_expcorAPSR.RDS"))
-
+})
+
+mocresult_expAPSR <- map(ls_mod_apsrCLS, function(aMod) {
+    result <- methodComposition3(df_exp_clsAPSR, aMod)
+})
+
+names(mocresult_expAPSR) <-
+    c(
+        "pooled1",
+        "pooled-regime1",
+        "pooled2",
+        "pooled-regime2",
+        "fd1",
+        "fd-regime1",
+        "fd2",
+        "fd-regime2"
+    )
+
+saveRDS(mocresult_expAPSR,
+        file = here::here("output", "estimates_moc_expcorAPSR.RDS"))
 ```
@@
 result_ecm1 <- bind_rows(
-    mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(result_clsAPSR[["pooled1"]][[1]][, 1:3], submodel = "Point Estimates Only"),
     mutate(MOCsumm2(mocresult_correctAPSR[["pooled1"]]), submodel = "With Uncertainty"),
@@
 result_fd1 <- bind_rows(
-    mutate(result_clsAPSR[["fd1"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(result_clsAPSR[["fd1"]][[1]][, 1:3], submodel = "Point Estimates Only"),
     mutate(MOCsumm2(mocresult_correctAPSR[["fd1"]]), submodel = "With Uncertainty"),
@@
         term0 = c(rep(
-            c("Democratic Mood\n (t-1)",
+            c(
+                "Democratic Mood\n (t-1)",
                 "Democratic Mood\n (t-2)",
@@
                 "Log GDP\n per capita\n (Difference)",
-              "Log GDP\n (t-1)"),
-            time = 3),
+                "Log GDP\n (t-1)"
+            ),
+            time = 3
+        ),
         rep(
-                c("Liberal Democracy\n (Difference)", 
-                  "Log GDP\n per capita\n (Difference)"), 
+            c(
+                "Liberal Democracy\n (Difference)",
+                "Log GDP\n per capita\n (Difference)"
+            ),
             time = 3
         )),
-        type = factor(type,  levels = c("Error-Correction Model", "First-Difference Model")),
-        submodel = factor(submodel, levels = c("Point Estimates Only","With Uncertainty", "Uncertainty & More Data")),
-        model = factor(model, levels = paste0("Model ", 
+        type = factor(
+            type,
+            levels = c("Error-Correction Model", "First-Difference Model")
+        ),
+        submodel = factor(
+            submodel,
+            levels = c(
+                "Point Estimates Only",
+                "With Uncertainty",
+                "Uncertainty & More Data"
+            )
+        ),
+        model = factor(model, levels = paste0(
+            "Model ",
             rep(1:2, each = 4), ".", rep(1:4, 2),
@@
             rep(c("ECM", "ECM", "FD", "FD"), 2),
-                                              ")"))
+            ")"
+        ))
     )
@@
 result_ecmReg1 <- bind_rows(
-    mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(result_clsAPSR[["pooled-regime1"]][[1]][, 1:3], submodel = "Point Estimates Only"),
     mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime1"]]), submodel = "With Uncertainty"),
@@
 result_fdReg1 <- bind_rows(
-    mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(result_clsAPSR[["fd-regime1"]][[1]][, 1:3], submodel = "Point Estimates Only"),
     mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime1"]]), submodel = "With Uncertainty"),
@@
                 "Log GDP\n per capita\n (Difference)",
-              "Log GDP\n (t-1)"),
-            time = 3),
+                "Log GDP\n (t-1)"
+            ),
+            time = 3
+        ),
         rep(
-                c("Electoral Democracy\n (Difference)", 
+            c(
+                "Electoral Democracy\n (Difference)",
                 "Minoritarian Democracy\n (Difference)",
-                  "Log GDP\n per capita\n (Difference)"), 
+                "Log GDP\n per capita\n (Difference)"
+            ),
             time = 3
         )),
-        type = factor(type,  levels = c("Error-Correction Model", "First-Difference Model")),
-        submodel = factor(submodel, levels = c("Point Estimates Only","With Uncertainty", "Uncertainty & More Data")),
-        model = factor(model, levels = paste0("Model ", 
+        type = factor(
+            type,
+            levels = c("Error-Correction Model", "First-Difference Model")
+        ),
+        submodel = factor(
+            submodel,
+            levels = c(
+                "Point Estimates Only",
+                "With Uncertainty",
+                "Uncertainty & More Data"
+            )
+        ),
+        model = factor(model, levels = paste0(
+            "Model ",
             rep(1:2, each = 4), ".", rep(1:4, 2),
@@
 result_ecm2 <- bind_rows(
-    mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(result_clsAPSR[["pooled2"]][[1]][, 1:3], submodel = "Point Estimates Only"),
     mutate(MOCsumm2(mocresult_correctAPSR[["pooled2"]]), submodel = "With Uncertainty"),
@@
 result_fd2 <- bind_rows(
-    mutate(result_clsAPSR[["fd2"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(result_clsAPSR[["fd2"]][[1]][, 1:3], submodel = "Point Estimates Only"),
     mutate(MOCsumm2(mocresult_correctAPSR[["fd2"]]), submodel = "With Uncertainty"),
@@
             ),
-            time = 3),
+            time = 3
+        ),
         rep(
-                c("Liberal Democracy\n (Difference)", 
+            c(
+                "Liberal Democracy\n (Difference)",
                 "Log GDP\n per capita\n (Difference)",
-                  "Corruption\n (Difference)"), 
+                "Corruption\n (Difference)"
+            ),
             time = 3
         )),
-        type = factor(type,  levels = c("Error-Correction Model", "First-Difference Model")),
-        submodel = factor(submodel, levels = c("Point Estimates Only","With Uncertainty", "Uncertainty & More Data")),
-        model = factor(model, levels = paste0("Model ", 
+        type = factor(
+            type,
+            levels = c("Error-Correction Model", "First-Difference Model")
+        ),
+        submodel = factor(
+            submodel,
+            levels = c(
+                "Point Estimates Only",
+                "With Uncertainty",
+                "Uncertainty & More Data"
+            )
+        ),
+        model = factor(model, levels = paste0(
+            "Model ",
             rep(1:2, each = 4), ".", rep(1:4, 2),
@@
             rep(c("ECM", "ECM", "FD", "FD"), 2),
-                                                      ")"))
+            ")"
+        ))
     )
@@
 result_ecmReg2 <- bind_rows(
-    mutate(result_clsAPSR[["pooled-regime2"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(result_clsAPSR[["pooled-regime2"]][[1]][, 1:3], submodel = "Point Estimates Only"),
     mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime2"]]), submodel = "With Uncertainty"),
-    mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime2"]]), submodel = "Uncertainty & More Data")) %>%
+    mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime2"]]), submodel = "Uncertainty & More Data")
+) %>%
     mutate(type = "Error-Correction Model",
@@
 result_fdReg2 <- bind_rows(
-    mutate(result_clsAPSR[["fd-regime2"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(result_clsAPSR[["fd-regime2"]][[1]][, 1:3], submodel = "Point Estimates Only"),
     mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime2"]]), submodel = "With Uncertainty"),
-    mutate(MOCsumm2(mocresult_expAPSR[["fd-regime2"]]), submodel = "Uncertainty & More Data")) %>% 
+    mutate(MOCsumm2(mocresult_expAPSR[["fd-regime2"]]), submodel = "Uncertainty & More Data")
+) %>%
     mutate(type = "First-Difference Model",
@@
             ),
-            time = 3),
+            time = 3
+        ),
         rep(
-                c("Electoral Democracy\n (Difference)", 
+            c(
+                "Electoral Democracy\n (Difference)",
                 "Minoritarian Democracy\n (Difference)",
                 "Log GDP\n per capita\n (Difference)",
-                  "Corruption\n (Difference)"), 
+                "Corruption\n (Difference)"
+            ),
             time = 3
         )),
-        type = factor(type,  levels = c("Error-Correction Model", "First-Difference Model")),
-        submodel = factor(submodel, levels = c("Point Estimates Only","With Uncertainty", "Uncertainty & More Data")),
-        model = factor(model, levels = paste0("Model ", 
+        type = factor(
+            type,
+            levels = c("Error-Correction Model", "First-Difference Model")
+        ),
+        submodel = factor(
+            submodel,
+            levels = c(
+                "Point Estimates Only",
+                "With Uncertainty",
+                "Uncertainty & More Data"
+            )
+        ),
+        model = factor(model, levels = paste0(
+            "Model ",
             rep(1:2, each = 4), ".", rep(1:4, 2),
@@
 ```{r plot-fullAPSR, fig.cap= "The Effect of Democracy on Change in Public Support with Uncertainty", fig.width=7, fig.height=10}
+
 df_plot <- bind_rows(result_APSR1, result_APSR2,
@@
 
-apsr_caption <- "Replications of Claassen (2020b), Table 1, 47, and Table 2, 49.  Models denoted 'ECM' are error-correction models; those marked 'FD' are first-difference models." %>% 
+apsr_caption <-
+    "Replications of Claassen (2020b), Table 1, 47, and Table 2, 49.  Models denoted 'ECM' are error-correction models; those marked 'FD' are first-difference models." %>%
     strwrap(85) %>%
-  paste0(sep="", collapse="\n")
+    paste0(sep = "", collapse = "\n")
 
 small_multiple(df_plot, dot_args = list(size = .9, fatten = 1)) +
-    geom_hline(yintercept = 0, colour = "grey50", linetype = 2) +
-    scale_color_grey(start = 0.8, end = 0.4, 
+    geom_hline(yintercept = 0,
+               colour = "grey50",
+               linetype = 2) +
+    scale_color_gb(
+        palette = "digitMixed",
         name = "Replication",
-                     breaks=c("Point Estimates Only",
+        breaks = c(
+            "Point Estimates Only",
             "With Uncertainty",
-                              "Uncertainty & More Data"),
-                     labels=c("Point Estimates Only",
+            "Uncertainty & More Data"
+        ),
+        labels = c(
+            "Point Estimates Only",
             "With Uncertainty",
-                              "Uncertainty & More Data")) +
-    theme(axis.text.x  = element_text(angle = 90, hjust = .5),
+            "Uncertainty & More Data"
+        )
+    ) + 
+    theme(
+        axis.text.x  = element_text(angle = 90, hjust = .5),
         strip.text.y.left = element_text(angle = 0),
@@
         legend.text = element_text(size = 8),
-          legend.background = element_rect(color="gray90"),
+        legend.background = element_rect(color = "gray90"),
         legend.spacing = unit(-5, "pt"),
@@
         legend.key.height = unit(7, "mm"),
-          plot.caption = element_text(size = 10, hjust = 0.2, margin = margin(t=15))) +
-  guides(color = guide_legend(override.aes = list(size=.3))) +
-  ggtitle("Dependent Variable: Change in Public Democratic Support") +
+        plot.caption = element_text(
+            size = 10,
+            hjust = 0.2,
+            margin = margin(t = 15)
+        )
+    ) +
+    guides(color = guide_legend(override.aes = list(size = .3))) +
+    ggtitle("Outcome Variable: Change in Public Democratic Support") +
     labs(caption = apsr_caption)
@@
 ```{r dcpo-AJPS, eval=FALSE}
-
 dcpo_Ajps <- purrr::map(1:900, function(anEntry) {
@@
         plm::pdata.frame(index = c("country", "year")) %>%
-    rename(SupDem_trim =theta_trim,
+        rename(
+            SupDem_trim = theta_trim,
             Regime_VD = Vdem_regime,
@@
             Libdem_regUN = Region_libdem,
-           Libdem_regUN_m1 = Region_libdem_m1)
-})
-
-result_dcpoUncertain  <- map(ls_mod_ajpsCLS[1:2], function(aMod){
-  result <- methodComposition1(dcpo_Ajps,aMod)
+            Libdem_regUN_m1 = Region_libdem_m1
+        )
+})
+
+result_dcpoUncertain  <- map(ls_mod_ajpsCLS[1:2], function(aMod) {
+    result <- methodComposition1(dcpo_Ajps, aMod)
 })
@@
 
-result_dcpoUncertain_gmm  <- map(ls_mod_ajpsCLS[3:4], function(aMod){
-  result <- methodComposition2(dcpo_Ajps,aMod)
+result_dcpoUncertain_gmm  <-
+    map(ls_mod_ajpsCLS[3:4], function(aMod) {
+        result <- methodComposition2(dcpo_Ajps, aMod)
     })
@@
 
-mocresult_dcpoAJPS <- append(result_dcpoUncertain, result_dcpoUncertain_gmm)
-saveRDS(mocresult_dcpoAJPS, file =here("output","estimates_moc_dcpoAJPS.RDS"))
+mocresult_dcpoAJPS <-
+    append(result_dcpoUncertain, result_dcpoUncertain_gmm)
+
+saveRDS(mocresult_dcpoAJPS,
+        file = here("output", "estimates_moc_dcpoAJPS.RDS"))
 
@@
 result_pooled <- bind_rows(
-    mutate(result_clsAJPS[["pooled"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(result_clsAJPS[["pooled"]][[1]][, 1:3], submodel = "Point Estimates Only"),
     mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), submodel = "Uncertainty & More Data"),
@@
 result_gmm <- bind_rows(
-    mutate(result_clsAJPS[["gmm"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(result_clsAJPS[["gmm"]][[1]][, 1:3], submodel = "Point Estimates Only"),
     mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), submodel = "Uncertainty & More Data"),
@@
                 "Percent\n Muslim\n (t-1)",
-              "Resource\n dependence\n (t-1)"),
-            time = 6), 
+                "Resource\n dependence\n (t-1)"
+            ),
+            time = 6
+        ),
         type = factor(type, levels = c("Pooled~OLS", "System~GMM")),
-        submodel = factor(submodel, levels = c("Point Estimates Only", "Uncertainty & More Data", "Uncertainty & DCPO")),
-        model = factor(model, levels = paste0("Model ", rep(1:4), rep(c(" (Pooled OLS)", " (System GMM)"), each = 2)))
+        submodel = factor(
+            submodel,
+            levels = c(
+                "Point Estimates Only",
+                "Uncertainty & More Data",
+                "Uncertainty & DCPO"
+            )
+        ),
+        model = factor(model, levels = paste0("Model ", rep(1:4), rep(
+            c(" (Pooled OLS)", " (System GMM)"), each = 2
+        )))
     )
@@
 result_regime <- bind_rows(
-    mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(result_clsAJPS[["pooled-regime"]][[1]][, 1:3], submodel = "Point Estimates Only"),
     mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), submodel = "Uncertainty & More Data"),
@@
 result_regimeGmm <- bind_rows(
-    mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(result_clsAJPS[["gmm-regime"]][[1]][, 1:3], submodel = "Point Estimates Only"),
     mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), submodel = "Uncertainty & More Data"),
     mutate(MOCsumm(mocresult_dcpoAJPS[["gmm-regime"]]), submodel = "Uncertainty & DCPO")
-)%>% 
+) %>%
     mutate(type = "System~GMM",
@@
                 "Percent\n Muslim\n (t-1)",
-              "Resource\n dependence\n (t-1)"),
-            time = 6), 
+                "Resource\n dependence\n (t-1)"
+            ),
+            time = 6
+        ),
         type = factor(type, levels = c("Pooled~OLS", "System~GMM")),
-        submodel = factor(submodel, levels = c("Point Estimates Only", "Uncertainty & More Data", "Uncertainty & DCPO")),
-        model = factor(model, levels = paste0("Model ", rep(1:4), rep(c(" (Pooled OLS)", " (System GMM)"), each = 2))))
+        submodel = factor(
+            submodel,
+            levels = c(
+                "Point Estimates Only",
+                "Uncertainty & More Data",
+                "Uncertainty & DCPO"
+            )
+        ),
+        model = factor(model, levels = paste0("Model ", rep(1:4), rep(
+            c(" (Pooled OLS)", " (System GMM)"), each = 2
+        )))
+    )
 
@@
 
-ajps_caption <- "Replications of Claassen (2020a), Table 1, 128, with DCPO."
+ajps_caption <-
+    "Replications of Claassen (2020a), Table 1, 128, with DCPO."
 
 small_multiple(df_plot, dot_args = list(size = .9, fatten = 1)) +
-    geom_hline(yintercept = 0, colour = "grey50", linetype = 2) +
-    scale_color_grey(start = 0.8, end = 0.4, 
+    geom_hline(yintercept = 0,
+               colour = "grey50",
+               linetype = 2) +
+    scale_color_gb(
+        palette = "digitMixed",
         name = "Replication",
-                     breaks=c("Point Estimates Only", "Uncertainty & More Data", "Uncertainty & DCPO"),
-                     labels=c("Point Estimates Only", "Uncertainty & More Data", "Uncertainty & DCPO")) +
-    theme(axis.text.x  = element_text(angle = 90, hjust = .5),
+        breaks = c(
+            "Point Estimates Only",
+            "Uncertainty & More Data",
+            "Uncertainty & DCPO"
+        ),
+        labels = c(
+            "Point Estimates Only",
+            "Uncertainty & More Data",
+            "Uncertainty & DCPO"
+        )
+    ) + 
+    theme(
+        axis.text.x  = element_text(angle = 90, hjust = .5),
         strip.text.y.left = element_text(angle = 0),
@@
         plot.title = element_text(hjust = 1.4),
-          plot.caption = element_text(size = 10, hjust = 0.7, margin = margin(t=15))) +
-  guides(color = guide_legend(override.aes = list(size=.3))) +
-  ggtitle("Dependent Variable: Level of Democracy") +
+        plot.caption = element_text(
+            size = 10,
+            hjust = 0.7,
+            margin = margin(t = 15)
+        )
+    ) +
+    guides(color = guide_legend(override.aes = list(size = .3))) +
+    ggtitle("Outcome Variable: Level of Democracy") +
     labs(caption = ajps_caption)
@@
 result_ecmReg1 <- bind_rows(
-    mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(result_clsAPSR[["pooled-regime1"]][[1]][, 1:3], submodel = "Point Estimates Only"),
     mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime1"]]), submodel = "Uncertainty & More Data"),
@@
 result_fdReg1 <- bind_rows(
-    mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(result_clsAPSR[["fd-regime1"]][[1]][, 1:3], submodel = "Point Estimates Only"),
     mutate(MOCsumm2(mocresult_expAPSR[["fd-regime1"]]), submodel = "Uncertainty & More Data"),
@@
                 "Log GDP\n per capita\n (Difference)",
-              "Log GDP\n (t-1)"),
-            time = 3),
+                "Log GDP\n (t-1)"
+            ),
+            time = 3
+        ),
         rep(
-                c("Electoral Democracy\n (Difference)", 
+            c(
+                "Electoral Democracy\n (Difference)",
                 "Minoritarian Democracy\n (Difference)",
-                  "Log GDP\n per capita\n (Difference)"), 
+                "Log GDP\n per capita\n (Difference)"
+            ),
             time = 3
         )),
-        type = factor(type,  levels = c("Error-Correction Model", "First-Difference Model")),
-        submodel = factor(submodel, levels = c("Point Estimates Only", "Uncertainty & More Data", "Uncertainty & DCPO")),
-        model = factor(model, levels = paste0("Model ", 
+        type = factor(
+            type,
+            levels = c("Error-Correction Model", "First-Difference Model")
+        ),
+        submodel = factor(
+            submodel,
+            levels = c(
+                "Point Estimates Only",
+                "Uncertainty & More Data",
+                "Uncertainty & DCPO"
+            )
+        ),
+        model = factor(model, levels = paste0(
+            "Model ",
             rep(1:2, each = 4), ".", rep(1:4, 2),
@@
 result_ecm2 <- bind_rows(
-    mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(result_clsAPSR[["pooled2"]][[1]][, 1:3], submodel = "Point Estimates Only"),
     mutate(MOCsumm2(mocresult_expAPSR[["pooled2"]]), submodel = "Uncertainty & More Data"),
@@
 result_fd2 <- bind_rows(
-    mutate(result_clsAPSR[["fd2"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(result_clsAPSR[["fd2"]][[1]][, 1:3], submodel = "Point Estimates Only"),
     mutate(MOCsumm2(mocresult_expAPSR[["fd2"]]), submodel = "Uncertainty & More Data"),
@@
             ),
-            time = 3),
+            time = 3
+        ),
         rep(
-                c("Liberal Democracy\n (Difference)", 
+            c(
+                "Liberal Democracy\n (Difference)",
                 "Log GDP\n per capita\n (Difference)",
-                  "Corruption\n (Difference)"), 
+                "Corruption\n (Difference)"
+            ),
             time = 3
         )),
-        type = factor(type,  levels = c("Error-Correction Model", "First-Difference Model")),
-        submodel = factor(submodel, levels = c("Point Estimates Only", "Uncertainty & More Data","Uncertainty & DCPO")),
-        model = factor(model, levels = paste0("Model ", 
+        type = factor(
+            type,
+            levels = c("Error-Correction Model", "First-Difference Model")
+        ),
+        submodel = factor(
+            submodel,
+            levels = c(
+                "Point Estimates Only",
+                "Uncertainty & More Data",
+                "Uncertainty & DCPO"
+            )
+        ),
+        model = factor(model, levels = paste0(
+            "Model ",
             rep(1:2, each = 4), ".", rep(1:4, 2),
@@
 result_ecmReg2 <- bind_rows(
-    mutate(result_clsAPSR[["pooled-regime2"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(result_clsAPSR[["pooled-regime2"]][[1]][, 1:3], submodel = "Point Estimates Only"),
     mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime2"]]), submodel = "Uncertainty & More Data"),
-  mutate(MOCsumm2(mocdcpo_APSR[["pooled-regime2"]]), submodel = "Uncertainty & DCPO")) %>%
+    mutate(MOCsumm2(mocdcpo_APSR[["pooled-regime2"]]), submodel = "Uncertainty & DCPO")
+) %>%
     mutate(type = "Error-Correction Model",
@@
 result_fdReg2 <- bind_rows(
-    mutate(result_clsAPSR[["fd-regime2"]][[1]][,1:3], submodel = "Point Estimates Only"),
+    mutate(result_clsAPSR[["fd-regime2"]][[1]][, 1:3], submodel = "Point Estimates Only"),
     mutate(MOCsumm2(mocresult_expAPSR[["fd-regime2"]]), submodel = "Uncertainty & More Data"),
-  mutate(MOCsumm2(mocdcpo_APSR[["fd-regime2"]]), submodel = "Uncertainty & DCPO")) %>% 
+    mutate(MOCsumm2(mocdcpo_APSR[["fd-regime2"]]), submodel = "Uncertainty & DCPO")
+) %>%
     mutate(type = "First-Difference Model",
@@
             ),
-            time = 3),
+            time = 3
+        ),
         rep(
-                c("Electoral Democracy\n (Difference)", 
+            c(
+                "Electoral Democracy\n (Difference)",
                 "Minoritarian Democracy\n (Difference)",
                 "Log GDP\n per capita\n (Difference)",
-                  "Corruption\n (Difference)"), 
+                "Corruption\n (Difference)"
+            ),
             time = 3
         )),
-        type = factor(type,  levels = c("Error-Correction Model", "First-Difference Model")),
-        submodel = factor(submodel, levels = c("Point Estimates Only", "Uncertainty & More Data", "Uncertainty & DCPO")),
-        model = factor(model, levels = paste0("Model ", 
+        type = factor(
+            type,
+            levels = c("Error-Correction Model", "First-Difference Model")
+        ),
+        submodel = factor(
+            submodel,
+            levels = c(
+                "Point Estimates Only",
+                "Uncertainty & More Data",
+                "Uncertainty & DCPO"
+            )
+        ),
+        model = factor(model, levels = paste0(
+            "Model ",
             rep(1:2, each = 4), ".", rep(1:4, 2),
@@
 
-apsr_caption <- "Replications of Claassen (2020b), Table 1-2, 47-49 with DCPO.  Models denoted 'ECM' are error-correction models; those marked 'FD' are first-difference models." %>% 
+apsr_caption <-
+    "Replications of Claassen (2020b), Table 1-2, 47-49 with DCPO.  Models denoted 'ECM' are error-correction models; those marked 'FD' are first-difference models." %>%
     strwrap(85) %>%
-  paste0(sep="", collapse="\n")
+    paste0(sep = "", collapse = "\n")
 
 small_multiple(df_plot, dot_args = list(size = .9, fatten = 1)) +
-    geom_hline(yintercept = 0, colour = "grey50", linetype = 2) +
-    scale_color_grey(start = 0.8, end = 0.4, 
+    geom_hline(yintercept = 0,
+               colour = "grey50",
+               linetype = 2) +
+    scale_color_gb(
+        palette = "digitMixed",
         name = "Replication",
-                     breaks=c("Point Estimates Only",
+        breaks = c(
+            "Point Estimates Only",
             "Uncertainty & More Data",
-                              "Uncertainty & DCPO"),
-                     labels=c("Point Estimates Only",
+            "Uncertainty & DCPO"
+        ),
+        labels = c(
+            "Point Estimates Only",
             "Uncertainty & More Data",
-                              "Uncertainty & DCPO")) +
-    theme(axis.text.x  = element_text(angle = 90, hjust = .5),
+            "Uncertainty & DCPO"
+        )
+    ) +
+    theme(
+        axis.text.x  = element_text(angle = 90, hjust = .5),
         strip.text.y.left = element_text(angle = 0),

### 2021-11-08 paper/dcpo_demsupport.Rmd
table for appendix figures; fixed #34

@@
 
+```{r num-dcpoAJPS, results='asis'}
+names_coef <- c(
+  "(Intercept)" = "(Intercept)",
+  "plm::lag(Libdem_VD, 1:2)1" = "Democracy (t-1)",
+  "plm::lag(Libdem_VD, 1:2)2"  = "Democracy (t-2)",
+  "plm::lag(SupDem_trim, 1)" = "Support (t-1)",
+  "plm::lag(SupDem_Democ, 1)" = "Support in Democracy",
+  "plm::lag(theta_dem_trim, 1)" = "Support in Democracy",
+  "plm::lag(SupDem_Autoc, 1)" = "Support in Autocracy",
+  "plm::lag(theta_aut_trim, 1)" = "Support in Autocracy",
+  "plm::lag(lnGDP_imp, 1)" = "Log GDP Per Capita (t-1)",
+  "plm::lag(GDP_imp_grth, 1)"  = "GDP Per Capita Growth (t-1)",
+  "plm::lag(Libdem_regUN, 1)" = "Regional Democracy (t-1)",
+  "plm::lag(Pr_Muslim, 1)" = "Percent Muslim (t-1)",
+  "plm::lag(Res_cp_WDI_di, 1)" = "Resource Dependence (t-1)"
+)
+
+tb_dcpoAJPS <- format_resultAJPS(condition = "Uncertainty & DCPO",
+                                      input_data = expcor_cls_ajps[[1]])
+modelsummary(tb_dcpoAJPS, 
+             coef_map = names_coef,
+             gof_map = names_gof,
+             output = "latex", 
+             title = "The Effect of Democracy on Change in Public Support (Uncertainty \\& DCPO)") %>%
+  kableExtra::kable_styling(font_size = 8) %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
 ```{r dcpo-APSR, eval=FALSE}
@@
 
+\blandscape
+
+```{r num-dcpoAPSR, results='asis'}
+names_coef <- c(
+  "(Intercept)" = "(Intercept)",
+  "plm::lag(SupDem_trim, 1:2)1" = "Democratic Mood (t-1)",
+  "plm::lag(SupDem_trim, 1:2)2" = "Democratic Mood (t-2)",
+  "diff(Libdem_z, lag = 1)" = "Liberal Democracy (Difference)",
+  "Libdem_z" = "Liberal Democracy (Difference)",
+  "plm::lag(Libdem_z, 1)" = "Liberal Democracy (t-1)",
+  "diff(Polyarchy_z, lag = 1)" = "Electoral Democracy (Difference)",
+  "Polyarchy_z" = "Electoral Democracy (Difference)",
+  "plm::lag(Polyarchy_z, 1)" = "Electoral Democracy (t-1)",
+  "diff(Liberal_z, lag = 1)" = "Minoritarian Democracy (Difference)",
+  "Liberal_z" = "Minoritarian Democracy (Difference)",
+  "plm::lag(Liberal_z, 1)" = "Minoritarian Democracy (t-1)",
+  "diff(lnGDP_imp, lag = 1)" = "Log GDP Per Capita (Difference)",
+  "lnGDP_imp" = "Log GDP per capita (Difference)",
+  "plm::lag(lnGDP_imp, 1)" = "Log GDP (t-1)",
+  "diff(Corrup_TI_z, lag = 1)" = "Corruption (Difference)",
+  "Corrup_TI_z" = "Corruption (Difference)",
+  "plm::lag(Corrup_TI_z, 1)" = "Corruption (t-1)"
+)
+
+tb_dcpoAPSR <- format_resultAPSR(condition = "Uncertainty & DCPO",
+                                      input_data = expcor_cls_apsr[[1]])
+
+modelsummary(tb_dcpoAPSR, 
+             stars = FALSE,
+             coef_map = names_coef,
+             gof_map = names_gof,
+             output = "latex", 
+             title = "The Effect of Public Support on Democracy (Uncertainty \\& DCPO)") %>% 
+  kableExtra::kable_styling(font_size = 7) %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+\elandscape
+
 # References  {-}

### 2021-11-08 R/cls_correct_ajpsapsr.R
add number of obs

@@ -322,3 +322,39 @@ osf_retrieve_user("me") %>%
 demsup <- osf_retrieve_node("tnp2a")
 osf_upload(demsup, c(here("data","expcor_cls_apsr.rda")),conflicts = "overwrite")
 osf_upload(demsup, c(here("data","expcor_cls_ajps.rda")),conflicts = "overwrite")
+
+####num.of observation
+cor_cls_ajps_trim <- correct_cls_ajps[[1]] %>%
+    group_by(country) %>% 
+    arrange(year, .by_group = TRUE) %>% 
+    mutate(SupDem_m1 = lag(SupDem_trim))
+
+cor_cls_ajps_trim %>%
+    filter(!is.na(Libdem_VD) & !is.na(SupDem_m1)) %>%
+    nrow()
+#2435
+length(unique(cor_cls_ajps_trim$country))
+#137
+cor_cls_ajps_trim %>%
+    filter(!is.na(Libdem_VD) & !is.na(SupDem_m1)) %>%
+    distinct(country) %>%
+    nrow()
+#135
+
+expcor_cls_ajps_trim <- expcor_cls_ajps[[1]] %>%
+    group_by(country) %>% 
+    arrange(year, .by_group = TRUE) %>% 
+    mutate(SupDem_m1 = lag(SupDem_trim))
+
+expcor_cls_ajps_trim %>%
+    filter(!is.na(Libdem_VD) & !is.na(SupDem_m1)) %>%
+    nrow()
+#2787
+length(unique(expcor_cls_ajps_trim$country))
+#145
+
+expcor_cls_ajps_trim %>%
+    filter(!is.na(Libdem_VD) & !is.na(SupDem_m1)) %>%
+    distinct(country) %>%
+    nrow()
+#140

### 2021-11-08 paper/dcpo_demsupport.Rmd
update MOC

--- 2021-11-08 paper/dcpo_demsupport.Rmd
@@
 As @caughey2018 [A-15] explained, the main idea of MOC is to estimate the marginal distribution of coefficient parameter vector $\beta$, integrating over the uncertainty in latent variables $\theta$.
-More explicitly, we wish to integrate the joint density of $\beta$ and $\theta$ over the distribution of $\theta$.
+More explicitly, MOC integrates the joint density of $\beta$ and $\theta$ over the distribution of $\theta$.
 
@@
 In this way, we incorporate uncertainty in measuring predictor $\theta$, and uncertainty in the effects of latent variables $\theta$ and other variables $w$ on outcome variable $y$ [@Treier2008, 215].
+
 To sample from the conditional density and the marginal density in the right side of the equation, we follow iterative Monte Carlo procedure described by @Treier2008, at iteration t,
@@
 
-In the step 3, the marginal distribution of a parameter vector $\beta$ was estimated, intergrating over $p(\theta|Z)$:
+In the step 3, the marginal distribution of a parameter vector $\beta$ was estimated, integrating over $p(\theta|Z)$:
 
@@
 In our re-analyses, we incorporate uncertainty for five variables, public support for democracy, liberal democracy, electoral democracy, the liberal component index, and the corruption perceptions index.
-where $\theta$ is latent varibles with measurement errors conditional on data Z and a measurement model, $w$ is other predictors without errors, $Z$ is indicators for latent variables $X$, and $y$ is the outcome variable.
-In this way, we incorportate uncertainty in measuring predictor $\theta$, and uncertainty in the effects of latent variables $\theta$ and other variables $w$ on outcome variable $y$ [@Treier2008, 215].
-To sample from the conditional dentsity and the marginal density in the right side of the equation, we follow iterative Monte Carlo procdure described by @Treier2008, at iteration t,
-
-1. We sample $\theta^{s}$ from its posterior distribution $p(\theta|Z)$ and $y$ from $p(y|Z)$.
-
-2.
-For each analysis model, we run the model with $y$, $\theta$, and $w$, and save the coefficient estimates $\beta^{s}$ and variance-covariance matrix of $\beta^{s}$, $V^{s}$, both of which change due to the uncertainty in $\theta^{s}$ and $y^{s}$.
-
-3. We sample $\tilde{\beta^{t}}$ from the multivariate normal density with mean vector $\beta{s}$ and variance-covariace matrix $V^{s}$.
-
-We incorporate uncertainty for five variables, public support for democracy, liberal democracy, electoral democracy, the liberal component index, and the corruption perceptions index.
 For each of these five latent variables, we take 900 draws from its posterior distribution.
 We duplicate the dataset of variables “without” measurement error 900 times, and assign them to each a different random draw from the distributions of variables with measurement error, which yields 900 dataset.
-In next step, we run each of analysis models with these 900 datesets independently and save the resulting estimates of coefficients and the matrix of variance-covariance for each run.
-We then draw one sample from the mulitivariate normal distribution with the mean vector of coefficient estimates and variance-covariance matrix produced from each run.
+In next step, we run each of analysis models with these 900 datasets independently and save the resulting estimates of coefficients and the matrix of variance-covariance for each run.
+We then draw one sample from the multivariate normal distribution with the mean vector of coefficient estimates and variance-covariance matrix produced from each run.
 This procedure finally yields 900 samples of estimated coefficients drawn from the joint density of $\beta$ and $\theta$.

### 2021-11-08 paper/dcpo_demsupport.Rmd
address TSCS approach.

@@
 Therefore, after replicating the original analyses that use only the point estimates for public support and the other variables included in the model, we perform the analyses again only this time incorporating uncertainty in analysis models using our replication data.
-We conduct inferences from the distributive data via the technique known as the "method of composition" [@Tanner1993, 52; @Treier2008, 215; @caughey2018, A15-16].^[For additional details on this technique, see Supplementary Information Appendix \@ref(moc).]
+We conduct inferences from the distributive data via the technique known as the "method of composition" (MOC) [@Tanner1993, 52].
+MOC accounts for uncertainty from opinion estimates and analysis models through each modeling stage.
+In analysis stage, uncertainty is incorporated through simulation based on variance-covariance matrix of a given model, regardless of the structures of the given model.
+Therefore MOC can adapt any different types of models, including but not limited to different specifications for a Time-Series-Cross-Sectional approach [@caughey2018, A15-16], a Cox proportional hazards model [@Treier2008, 215], or individual level roll call voting model [@Kastellec2015, 791].^[For additional details on this technique, see Supplementary Information Appendix \@ref(moc).]
 

### 2021-11-08 paper/dcpo_demsupport.Rmd
address appropriateness of MOC for TSCS approach and data.

--- 2021-11-08 paper/dcpo_demsupport.Rmd
@@
 Therefore, after replicating the original analyses that use only the point estimates for public support and the other variables included in the model, we perform the analyses again only this time incorporating uncertainty in analysis models using our replication data.
-We conduct inferences from the distributive data via the technique known as the "method of composition" [@Tanner1993, 52; @Treier2008, 215; @caughey2018, A15-16].^[For additional details on this technique, see Supplementary Information Appendix \@ref(moc).]
+We conduct inferences from the distributive data via the technique known as the "method of composition" (MOC) [@Tanner1993, 52].
+MOC accounts for uncertainty from opinion estimates and analysis models through each modeling stage.
+In analysis stage, uncertainty is incorporated through simulation based on variance-covariance matrix of a given model, regardless of the structures or features of the given model.
+Therefore MOC can adapt any different types of models, including but not limited to different specifications for a Time-Series-Cross-Sectional approach for TSCS data [@caughey2018, A15-16], a Cox proportional hazards model [@Treier2008, 215], or individual level roll call voting model [@Kastellec2015, 791].^[For additional details on this technique, see Supplementary Information Appendix \@ref(moc).]
 

### 2021-11-08 paper/dcpo_demsupport.Rmd
addressing a3bf5b5f840c34a0419cefccf524bf26321179c9 and 5823f7abf51015ef6d8b2d39a8098be894cd0826

@@
 As @caughey2018 [A-15] explained, the main idea of MOC is to estimate the marginal distribution of coefficient parameter vector $\beta$, integrating over the uncertainty in latent variables $\theta$.
-More explicitly, MOC integrates the joint density of $\beta$ and $\theta$ over the distribution of $\theta$.
+More explicitly, we wish to integrate the joint density of $\beta$ and $\theta$ over the distribution of $\theta$.
 
@@
 In this way, we incorporate uncertainty in measuring predictor $\theta$, and uncertainty in the effects of latent variables $\theta$ and other variables $w$ on outcome variable $y$ [@Treier2008, 215].
-
 To sample from the conditional density and the marginal density in the right side of the equation, we follow iterative Monte Carlo procedure described by @Treier2008, at iteration t,
@@
 
-In the step 3, the marginal distribution of a parameter vector $\beta$ was estimated, integrating over $p(\theta|Z)$:
+In the step 3, the marginal distribution of a parameter vector $\beta$ was estimated, intergrating over $p(\theta|Z)$:
 
@@
 In our re-analyses, we incorporate uncertainty for five variables, public support for democracy, liberal democracy, electoral democracy, the liberal component index, and the corruption perceptions index.
+where $\theta$ is latent varibles with measurement errors conditional on data Z and a measurement model, $w$ is other predictors without errors, $Z$ is indicators for latent variables $X$, and $y$ is the outcome variable.
+In this way, we incorportate uncertainty in measuring predictor $\theta$, and uncertainty in the effects of latent variables $\theta$ and other variables $w$ on outcome variable $y$ [@Treier2008, 215].
+To sample from the conditional dentsity and the marginal density in the right side of the equation, we follow iterative Monte Carlo procdure described by @Treier2008, at iteration t,
+
+1. We sample $\theta^{s}$ from its posterior distribution $p(\theta|Z)$ and $y$ from $p(y|Z)$.
+
+2.
+For each analysis model, we run the model with $y$, $\theta$, and $w$, and save the coefficient estimates $\beta^{s}$ and variance-covariance matrix of $\beta^{s}$, $V^{s}$, both of which change due to the uncertainty in $\theta^{s}$ and $y^{s}$.
+
+3. We sample $\tilde{\beta^{t}}$ from the multivariate normal density with mean vector $\beta{s}$ and variance-covariace matrix $V^{s}$.
+
+We incorporate uncertainty for five variables, public support for democracy, liberal democracy, electoral democracy, the liberal component index, and the corruption perceptions index.
 For each of these five latent variables, we take 900 draws from its posterior distribution.
 We duplicate the dataset of variables “without” measurement error 900 times, and assign them to each a different random draw from the distributions of variables with measurement error, which yields 900 dataset.
-In next step, we run each of analysis models with these 900 datasets independently and save the resulting estimates of coefficients and the matrix of variance-covariance for each run.
-We then draw one sample from the multivariate normal distribution with the mean vector of coefficient estimates and variance-covariance matrix produced from each run.
+In next step, we run each of analysis models with these 900 datesets independently and save the resulting estimates of coefficients and the matrix of variance-covariance for each run.
+We then draw one sample from the mulitivariate normal distribution with the mean vector of coefficient estimates and variance-covariance matrix produced from each run.
 This procedure finally yields 900 samples of estimated coefficients drawn from the joint density of $\beta$ and $\theta$.

### 2021-11-10 paper/dcpo_demsupport.Rmd
based on new data
address the comparison of SEM and MOC.

--- 2021-11-08 paper/dcpo_demsupport.Rmd
@@
 
+A simultaneous equation model which incorporates measurement model and structural links between variables together accounts for bias caused by simultaneity between variables and measurement models.
+However, we are reluctant to use a structural equation model (SEM) because SEM is a method to test the match between the model and the data.
+In other words, SEM tests whether the assumed model can be validated by the observed data, with the assumption is that the model is correct.
+Therefore, SEM is subject to confirmation bias due to the existing of competing theories which we have in the theory on democracy and public opinion, omitted variables, linear causal relationship assumption, the sensitivity to the estimator choice when both endogenous and  endogenous are contaminated by measurement errors [@Edith2019], among others [@Tomarken2005].
+
+More importantly, SEM becomes more complicated by increasing equations, demanding more from researchers on specific projects, but our main idea is to demonstrate the importance of incorporating uncertainty in a broader context but also provide a practical technique for scholars to deal with a model with multiple latent variables in both sides of the model.
+
+The advantage of MOC is that it can accommodate multiple layers of uncertainty in both opinion estimates and substantive models [@Kastellec2015, 792] and can be used very handily.
+
 ```{r compare_n}
@@
 # References  {-}
-
-<div id = 'refs_app'></div>

### 2021-11-14 paper/dcpo_demsupport.Rmd
update lit on the effects of measurement errors.

@@
 
-Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can both attenuate or exaggerate coefficient estimates as well as bias standard errors [see, e.g., @Blackwell2017, 318-319; @caughey2018, 254].
+Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can change the sign of coefficients[@Bound2001; @Saccenti2020], both attenuate or exaggerate coefficient estimates as well as bias standard errors [see, e.g., @Blackwell2017, 318-319; @caughey2018, 254].
 In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey2018, 254].
@@
 
-saveRDS(mocresult_correctAPSR,
-        file = here::here("ouput", "estimates_moc_correctAPSR.RDS"))
+saveRDS(mocresult_correctAPSR, file = here("ouput", "estimates_moc_correctAPSR.RDS"))
+
 ```

### 2021-11-14 R/v10_posterior.R
correct the cntrl variables in terms of Region_UN

@@ -58,6 +58,7 @@ cntrl_ajps_error <- left_join(cntrl_ajps_postse,cntrl_ajps_poly_postse, by = c("
 cntrl_ajps_uncertainty <- left_join(cntrl_ajps_error,cntrl_ajps_se, by = c("country", "year")) %>%
   select(country, year, starts_with("Vdem"),everything())
 
+libdem_cntrl_list
 
 cntrl_ajps_uncertainty_region <- cntrl_ajps_uncertainty %>%
   group_by(country, iter_se) %>%

### 2021-11-15 paper/dcpo_demsupport.Rmd

--- 2021-11-10 paper/dcpo_demsupport.Rmd
@@
 
-```{r mocResult-pureAJPS, eval=FALSE}
+```{r mocResult-pureAJPS}
 df_correct_clsAjps <- purrr::map(1:900, function(anEntry) {
@@
 saveRDS(mocresult_correctAPSR,
-        file = here::here("ouput", "estimates_moc_correctAPSR.RDS"))
+        file = here::here("output", "estimates_moc_correctAPSR.RDS"))
 ```
@@
 
+\blandscape
+
+```{r num-dcpoAPSR, results='asis'}
+names_coef <- c(
+  "(Intercept)" = "(Intercept)",
+  "plm::lag(SupDem_trim, 1:2)1" = "Democratic Mood (t-1)",
+  "plm::lag(SupDem_trim, 1:2)2" = "Democratic Mood (t-2)",
+  "diff(Libdem_z, lag = 1)" = "Liberal Democracy (Difference)",
+  "Libdem_z" = "Liberal Democracy (Difference)",
+  "plm::lag(Libdem_z, 1)" = "Liberal Democracy (t-1)",
+  "diff(Polyarchy_z, lag = 1)" = "Electoral Democracy (Difference)",
+  "Polyarchy_z" = "Electoral Democracy (Difference)",
+  "plm::lag(Polyarchy_z, 1)" = "Electoral Democracy (t-1)",
+  "diff(Liberal_z, lag = 1)" = "Minoritarian Democracy (Difference)",
+  "Liberal_z" = "Minoritarian Democracy (Difference)",
+  "plm::lag(Liberal_z, 1)" = "Minoritarian Democracy (t-1)",
+  "diff(lnGDP_imp, lag = 1)" = "Log GDP Per Capita (Difference)",
+  "lnGDP_imp" = "Log GDP per capita (Difference)",
+  "plm::lag(lnGDP_imp, 1)" = "Log GDP (t-1)",
+  "diff(Corrup_TI_z, lag = 1)" = "Corruption (Difference)",
+  "Corrup_TI_z" = "Corruption (Difference)",
+  "plm::lag(Corrup_TI_z, 1)" = "Corruption (t-1)"
+)
+
+tb_dcpoAPSR <- format_resultAPSR(condition = "Uncertainty & DCPO",
+                                      input_data = expcor_cls_apsr[[1]])
+
+modelsummary(tb_dcpoAPSR, 
+             stars = FALSE,
+             coef_map = names_coef,
+             gof_map = names_gof,
+             output = "latex", 
+             title = "The Effect of Public Support on Democracy (Uncertainty \\& DCPO)") %>% 
+  kableExtra::kable_styling(font_size = 7) %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+\elandscape
+
 # References  {-}
+
+<div id = 'refs_app'></div>

### 2021-11-15 paper/dcpo_demsupport.Rmd

@@
 
-```{r mocResult-pureAJPS}
+```{r mocResult-pureAJPS, eval=FALSE}
 df_correct_clsAjps <- purrr::map(1:900, function(anEntry) {

### 2021-12-01 paper/dcpo_demsupport.Rmd
highlight method contribution

@@
 We draw two conclusions, one methodological and one substantive.
+Many constructs in social science are latent variables, including but not limited to corruption, polarization, public attitudes, policy preference, social norms, and economic behaviors. 
 As latent variable measurement models become more commonly used, it is absolutely necessary for researchers employing them to incorporate the associated uncertainty into analyses.
-And, at a time when democracy is seen as under threat around the world [e.g., @Diamond2015], taken together, Claassen [-@Claassen2020a; -@Claassen2020b] send what is ultimately a reassuring message: the fate of democracy rests with us, the public, and when democratic institutions are undermined, we will swing to their support and constitute "an obstacle to democratic backsliding" [@Claassen2020b, 51].
+The technique and codes used in this study can be handily applied to empirical studies with latent variables and address the uncertainty for models with only one or multiple latent variables in both sides of the models without any further requirements for models.
+This letter contributes to the recent methodological development in measurement models by emphasizing the necessity of incorporating uncertainty. 
+It highlights a necessary procedure and provides a practicable approach for examining theory generalization in comparative studies.
+And, at a time when democracy is seen as under threat around the world [e.g., @Diamond2015; @IDEA2021], taken together, Claassen [-@Claassen2020a; -@Claassen2020b] send what is ultimately a reassuring message: the fate of democracy rests with us, the public, and when democratic institutions are undermined, we will swing to their support and constitute "an obstacle to democratic backsliding" [@Claassen2020b, 51].
 Both of these assertions may well be true, but the evidence we have, properly assessed, does not support them.

### 2021-12-01 paper/dcpo_demsupport.Rmd
Modify the part about SEM and adverse effect of measurement errors on coef

@@
 As democracy is also a latent variable in these analyses, we include the uncertainty in its estimates as well, along with that for corruption in the models of @Claassen2020b.
+We also include the uncertainty for GDP and Resource Dependence variables by using multiple imputation.
 In the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.^[We also attempted to make fuller use of the available survey data by employing the DCPO model [@Solt2020a], which unlike the [@Claassen2019] model does not dichotomize ordinal responses.
@@
 
-Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can both attenuate or exaggerate coefficient estimates as well as bias standard errors [see, e.g., @Blackwell2017, 318-319; @caughey2018, 254].
+Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement errors, and measurement errors can reverse the sign of estimation of coefficients [@Bound2001, 3709; @Saccenti2020, 8], attenuate or exaggerate coefficient estimates as well as bias standard errors [see, e.g., @Blackwell2017, 318-319; @caughey2018, 254].
 In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey2018, 254].
@@
 
-A simultaneous equation model which incorporates measurement model and structural links between variables together accounts for bias caused by simultaneity between variables and measurement models.
-However, we are reluctant to use a structural equation model (SEM) because SEM is a method to test the match between the model and the data.
-In other words, SEM tests whether the assumed model can be validated by the observed data, with the assumption is that the model is correct.
-Therefore, SEM is subject to confirmation bias due to the existing of competing theories which we have in the theory on democracy and public opinion, omitted variables, linear causal relationship assumption, the sensitivity to the estimator choice when both endogenous and  endogenous are contaminated by measurement errors [@Edith2019], among others [@Tomarken2005].
-
-More importantly, SEM becomes more complicated by increasing equations, demanding more from researchers on specific projects, but our main idea is to demonstrate the importance of incorporating uncertainty in a broader context but also provide a practical technique for scholars to deal with a model with multiple latent variables in both sides of the model.
-
-The advantage of MOC is that it can accommodate multiple layers of uncertainty in both opinion estimates and substantive models [@Kastellec2015, 792] and can be used very handily.
+As an alternative way, a structural equation model(SEM) which incorporates measurement model and structural links between variables together can also account for bias caused by simultaneity between variables and measurement models.
+However, SEM is a method to test the match between the model and the data, subject to confirmation bias due to the existing of competing theories which we have in the theory on democracy and public opinion, omitted variables, linear causal relationship assumption, the sensitivity to the estimator choice when both endogenous and endogenous are contaminated by measurement errors [@Umeh2019], among others [@Tomarken2005].
+
+In contrast, MOC is flexible to accommodate not only various models but also multiple layers of uncertainty in both opinion estimates and substantive models [@Kastellec2015, 792] where the model and joint distribution of the error and all the variables in the model determine the bias introduced by measurement errors [@Bound2001, 3708].
 

### 2021-12-01 paper/dcpo_demsupport.Rmd
add method contribution in discussion.
correct Tables' titles.

@@
 In all four models, the positive coefficients for democratic support are no longer statistically significant.
-The darker, righthand results also incorporate uncertainty but additionally replace the estimates of democratic support with those based on our expanded dataset; this change works to increase the number of observations analyzed as well.
+The darker, righth and results also incorporate uncertainty but additionally replace the estimates of democratic support with those based on our expanded dataset; this change works to increase the number of observations analyzed as well.
 Although the confidence intervals shrink considerably, the coefficient estimates move much closer to zero; the hypothesis remains unsupported.
@@
 As the use of latent variables grows more common in political science, both researchers and readers should be aware that these variables' concomitant measurement uncertainty cannot be neglected.
+Since measurement uncertainty distorts both statistical and substantive inferences with unknown directions on the sign and size of coefficients [@Bound2001;@Blackwell2017; @caughey2018], it is not only a methodological concern but also has substantive implications [@juhl_measurement_2019].
 
@@
              output = "latex", 
-             title = "The Effect of Democracy on Change in Public Support (Original Results)") %>%
+             title = "The Effect of Public Support on Democracy (Original Results)") %>%
   kableExtra::kable_styling(font_size = 8) %>% 
@@
              output = "latex",
-             title = "The Effect of Democracy on Change in Public Support (With Uncertainty)") %>%
+             title = "The Effect of Public Support on Democracy (With Uncertainty)") %>%
     kableExtra::kable_styling(font_size = 8) %>%
@@
              output = "latex", 
-             title = "The Effect of Democracy on Change in Public Support (Uncertainty \\& More Data)") %>%
+             title = "The Effect of Public Support on Democracy (Uncertainty \\& More Data)") %>%
   kableExtra::kable_styling(font_size = 8) %>% 
@@
              output = "latex", 
-             title = "The Effect of Public Support on Democracy with Uncertainty (Original)") %>% 
+             title = "The Effect of Democracy on Change in Public Support (Original)") %>% 
   kableExtra::kable_styling(font_size = 7) %>% 
@@
              output = "latex", 
-             title = "The Effect of Public Support on Democracy (With Uncertainty)") %>% 
+             title = "The Effect of Democracy on Change in Public Support (With Uncertainty)") %>% 
   kableExtra::kable_styling(font_size = 7) %>% 
@@
              output = "latex", 
-             title = "The Effect of Public Support on Democracy (Uncertainty \\& More Data)") %>% 
+             title = "The Effect of Democracy on Change in Public Support (Uncertainty \\& More Data)") %>% 
   kableExtra::kable_styling(font_size = 7) %>% 

### 2021-12-03 paper/dcpo_demsupport.Rmd
confirmed the new datasets

@@
 
-```{r data-input, include=FALSE, cache=TRUE}
+```{r data-input, include=FALSE, cache=TRUE, cache.extra = tools::md5sum(here::here("output", "estimates_moc_correctAJPS.RDS"))}
 ## Replication data

### 2021-12-16 paper/dcpo_demsupport.Rmd
tablek caption and figure color correction

@@
 citation_package: natbib
+citeproc: false
 fontsize: 12pt
@@
                linetype = 2) +
-    scale_color_gb(
-        palette = "digitMixed",
+    scale_color_grey(
+        start = 0.8, end = 0.4, 
         name = "Replication",
@@
             "Point Estimates Only",
-            "Uncertainty & More Data",
-            "Uncertainty & DCPO"
+            "With Uncertainty",
+            "Uncertainty & More Data"
         ),
@@
             "Point Estimates Only",
-            "Uncertainty & More Data",
-            "Uncertainty & DCPO"
+            "With Uncertainty",
+            "Uncertainty & More Data"
         )
@@
              output = "latex", 
-             title = "The Effect of Democracy on Change in Public Support (Uncertainty \\& DCPO)") %>%
+             title = "The Effect of Public Support on Democracy (Uncertainty \\& DCPO)") %>%
   kableExtra::kable_styling(font_size = 8) %>% 

### 2021-12-19 paper/dcpo_demsupport.Rmd
update osf links in comments

@@
 load(here("data", "correct_cls_ajps.rda")) # https://osf.io/52u7n/download
-load(here("data", "correct_cls_apsr.rda")) # https://osf.io/2hwqg/download
-load(here("data", "expcor_cls_ajps.rda"))  # https://osf.io/wfm3c/download
-load(here("data", "expcor_cls_apsr.rda"))  # https://osf.io/rvc92/download
+load(here("data", "correct_cls_apsr.rda")) # https://osf.io/cws59/download
+load(here("data", "expcor_cls_ajps.rda"))  # https://osf.io/cgxjd/download
+load(here("data", "expcor_cls_apsr.rda"))  # https://osf.io/uka5g/download
 load(here("data", "exp_claassen_input.rda")) # Source???

### 2021-12-19 paper/dcpo_demsupport.Rmd
revisions to intro for clarity.  Closes #35

@@
 A pair of prominent recent works took advantage of this latent variable approach to measure democratic support for over one hundred countries for up to nearly three decades and to then assess, respectively, its consequences for and roots in democratic change [@Claassen2020a; @Claassen2020b].
-These works concluded, first and supporting the classic argument, that mass support had a positive impact on democratic change, especially the endurance of democracy [@Claassen2020a, 127-130], and, second and directly contrary to it, democratic change has a thermostatic effect on public support, that is that, rather than generating its own support, deepening democracy provokes a backlash and it is instead democratic backsliding that calls forth greater public support [@Claassen2020b, 46-50].
+The first of these works concluded, supporting the classic argument, that mass support had a positive impact on democratic change, especially the endurance of democracy [@Claassen2020a, 127-130].
+The second directly contradicted the classic argument, concluding that democratic change has a thermostatic effect on public support, that is, that rather than generating its own support, deepening democracy provokes a backlash and it is instead democratic backsliding that calls forth greater public support [@Claassen2020b, 46-50].
 
@@
 Similarly, the results presented here are further evidence that the survey items commonly employed to measure democratic support are inadequate to the task.
-Without additional information on respondents' support for democracy relative to other values with which it may come into conflict, such as their partisanship [see, e.g., @Carey2020; @McCoy2020]---or on whether respondents even understand the meaning of the democracy they are claiming to support [see, e.g., @Kirsch2019; @Wuttke2020]---these questions appear to miss capturing the true extent of support democracy would find among the public when public support was actually needed.
+Because these questions contain no information on respondents' support for democracy relative to other values with which it may come into conflict, such as their partisanship [see, e.g., @Carey2020; @McCoy2020]---or on whether respondents even understand the meaning of the democracy they are claiming to support [see, e.g., @Kirsch2019; @Wuttke2020]---these questions appear to miss capturing, when public support is in fact needed, the true extent of the support among the public that democracy will actually find.
 Our results also reinforce arguments that relationships between democracy and public support unfold only over the long term [see, e.g., @Welzel2017] and that democratic change in the short-term is instead best understood as an elite-driven phenomenon [see, e.g., @levitsky_how_2018; @Haggard2021].
@@
 As latent variable measurement models become more commonly used, it is absolutely necessary for researchers employing them to incorporate the associated uncertainty into analyses.
-The technique and codes used in this study can be handily applied to empirical studies with latent variables and address the uncertainty for models with only one or multiple latent variables in both sides of the models without any further requirements for models.
+The technique and codes used in this study can be handily applied to empirical studies with latent variables and address the uncertainty for models with only one or multiple latent variables on both sides of the models without any further change in modeling strategy.
 This letter contributes to the recent methodological development in measurement models by emphasizing the necessity of incorporating uncertainty. 

### 2021-12-23 paper/dcpo_demsupport.Rmd
corrected the legend of dcpo in the appendix

@@
 [144/150 words]"
-keywords: "Democratization, public support, regime survival, measurement uncertainty, latent variables"
+keywords: "Democratization, public support, regime survival, measurement uncertainty, latent variables."
 
@@
             "Point Estimates Only",
-            "With Uncertainty",
-            "Uncertainty & More Data"
+            "Uncertainty & More Data",
+            "Uncertainty & DCPO"
         ),
@@
             "Point Estimates Only",
-            "With Uncertainty",
-            "Uncertainty & More Data"
+            "Uncertainty & More Data",
+            "Uncertainty & DCPO"
         )

### 2021-12-23 R/cls_correct_ajpsapsr.R

@@ -9,6 +9,7 @@ p_load(
     rstan,
     osfr
 ) 
+
 #osf_retrieve_file("kg7z4") %>%
 #     osf_download(here::here("data"))  ##pure corrected
 
@@ -57,9 +58,10 @@ correct_cls_theta_list <- purrr::map(1:900, function(anEntry) {
 #year 30, country 137
 save(correct_cls_theta_list,file = here("data","correct_cls_theta_list.rda"))
 
+
 ################################################################
 ######## Create lists for elements in analysis data  ###########
-########### AJPS: cls_libdem_ajps_list,correct_cls_ajps ############
+########### AJPS: cls_libdem_ajps_list,correct_cls_ajps ########
 ################################################################
 
 load(here("data","cls_libdem_list.rda"))  #vdem8 libdem list
@@ -108,10 +110,13 @@ correct_cls_ajps <- purrr::map(1:900, function(anEntry) {
 }) 
 #merge with correct_cls_theta and create trim variables. 
 save(correct_cls_ajps, file = here("data","correct_cls_ajps.rda"))
+
+
 ################################################################
 ######## Create lists for elements in analysis data  ###########
-########### APSR: cls_libdem_apsr_list,correct_cls_apsr  ###########
+########### APSR: cls_libdem_apsr_list,correct_cls_apsr  #######
 ################################################################
+
 load(here("data","cls_libdem_list.rda"))  #vdem8 libdem list
 load(here("data","cls_apsr_cntrl.rda"))
 load(here("data","cls_poly_list.rda"))
@@ -179,9 +184,13 @@ demsup <- osf_retrieve_node("tnp2a")
 osf_upload(demsup, c(here("data","correct_cls_ajps.rda")),conflicts = "overwrite")
 osf_upload(demsup, c(here("data","correct_cls_apsr.rda")),conflicts = "overwrite")
 
-###############Expanded_Claassen and Analysis Data##################
-###############Input:  exp_claassen_m5_3k_07-23-10-50.rda ############################
-##############Output: expcor_cls_theta_list ############################
+
+################################################################
+###############Expanded_Claassen and Analysis Data##############
+###############Input:  exp_claassen_m5_3k_07-23-10-50.rda ######
+##############Output: expcor_cls_theta_list ####################
+################################################################
+
 load(here("data", "exp_claassen_m5_3k_07-23-10-50.rda")) 
 load(here("data","exp_claassen_input.rda"))
 load(here("data","dcpo_ajps_cntrl.rda"))
[…]

### 2021-12-23 R/dcpo_ajps_apsr_uncertainty.R

@@ -23,7 +23,7 @@ set.seed(313)
 ########### theta_sigma_list,lib_list.rda, cpi_list  ###########
 ################    libdem_list,  poly_list    #################
 ####################### libdem_cntrl_list     ##################
-
+################################################################
 
 load(here("data","dcpo_input.rda"))
 load(here("data","dcpo_theta.rda"))

### 2021-12-23 paper/dcpo_demsupport.Rmd
revise abstract for #33

@@
 Two prominent recent studies (Claassen 2020a, 2020b) reinvigorated the classic hypothesis on the positive relationship between public support for democracy and regime survival---and challenged its reciprocal counterpart---by using a latent variable approach to measure mass democratic support from cross-national survey data.
-But such approaches come with concomitant measurement uncertainty, and neither study incorporated this uncertainty into its analyses.
-In this letter, we correctly take measurement uncertainty in account and show that there is no support for the conclusion of either study.
-We then work to minimize the measurement uncertainty in public support by incorporating additional survey data.
-Even with this expanded evidentiary base, however, our analyses fail to yield evidence in support of either hypothesis, underscoring the necessity of accounting for measurement uncertainty.
-[144/150 words]"
+Such approaches come with concomitant measurement uncertainty that should be taken into account, however, and neither study incorporated this uncertainty into its analyses.
+Correcting this oversight reveals that there is no support for either study's conclusion.
+Efforts to minimize the uncertainty by incorporating additional survey data still fail to yield evidence in support of either hypothesis.
+These results underscore the need both for more nuanced analyses of the relationships between public support and democracy and of accounting for measurement uncertainty when working with latent variables.
+[150/150 words]"
 keywords: "Democratization, public support, regime survival, measurement uncertainty, latent variables."

### 2021-12-23 paper/dcpo_demsupport.Rmd
revise intro for method contribution #33

@@
 Similarly, the results presented here are further evidence that the survey items commonly employed to measure democratic support are inadequate to the task.
-Because these questions contain no information on respondents' support for democracy relative to other values with which it may come into conflict, such as their partisanship [see, e.g., @Carey2020; @McCoy2020]---or on whether respondents even understand the meaning of the democracy they are claiming to support [see, e.g., @Kirsch2019; @Wuttke2020]---these questions appear to miss capturing, when public support is in fact needed, the true extent of the support among the public that democracy will actually find.
-Our results also reinforce arguments that relationships between democracy and public support unfold only over the long term [see, e.g., @Welzel2017] and that democratic change in the short-term is instead best understood as an elite-driven phenomenon [see, e.g., @levitsky_how_2018; @Haggard2021].
+Because these questions contain no information on respondents' support for democracy relative to other values with which it may come into conflict, such as their partisanship [see, e.g., @Carey2020; @McCoy2020]---or on whether respondents even understand the meaning of the democracy they are claiming to support [see, e.g., @Kirsch2019; @Wuttke2020]---these questions appear to miss capturing the true extent of the support among the public that democracy will actually find when public support is in fact most needed.
+Our results also reinforce arguments that relationships between democracy and public support unfold only over the long term [see, e.g., @Welzel2017] and that democratic change in the short term is instead best understood as an elite-driven phenomenon [see, e.g., @levitsky_how_2018; @Haggard2021].
 
 We draw two conclusions, one methodological and one substantive.
-Many constructs in social science are latent variables, including but not limited to corruption, polarization, public attitudes, policy preference, social norms, and economic behaviors. 
-As latent variable measurement models become more commonly used, it is absolutely necessary for researchers employing them to incorporate the associated uncertainty into analyses.
-The technique and codes used in this study can be handily applied to empirical studies with latent variables and address the uncertainty for models with only one or multiple latent variables on both sides of the models without any further change in modeling strategy.
-This letter contributes to the recent methodological development in measurement models by emphasizing the necessity of incorporating uncertainty. 
-It highlights a necessary procedure and provides a practicable approach for examining theory generalization in comparative studies.
-And, at a time when democracy is seen as under threat around the world [e.g., @Diamond2015; @IDEA2021], taken together, Claassen [-@Claassen2020a; -@Claassen2020b] send what is ultimately a reassuring message: the fate of democracy rests with us, the public, and when democratic institutions are undermined, we will swing to their support and constitute "an obstacle to democratic backsliding" [@Claassen2020b, 51].
+Many constructs in social science---from democracy to corruption to public opinion---are latent variables, and recent advances have made estimating them much more practicable.
+As latent variable measurement models become more commonly used, it is absolutely necessary for researchers employing them to incorporate the associated uncertainty into their analyses.
+As demonstrated here, this can be done straightforwardly using the method of composition [see @Tanner1993, 52; @Treier2008, 215], without requiring any further change in modeling strategy.
+
+And, at a time when democracy is seen as under threat around the world [e.g., @Diamond2015], taken together, Claassen [-@Claassen2020a; -@Claassen2020b] send what is ultimately a reassuring message: the fate of democracy rests with us, the public, and when democratic institutions are undermined, we will swing to their support and constitute "an obstacle to democratic backsliding" [@Claassen2020b, 51].
 Both of these assertions may well be true, but the evidence we have, properly assessed, does not support them.
@@
 Second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.^[Additional details on this data replication process are found in Supplementary Information Appendix \@ref(dgp).]
-As democracy is also a latent variable in these analyses, we include the uncertainty in its estimates as well, along with that for corruption in the models of @Claassen2020b.
-We also include the uncertainty for GDP and Resource Dependence variables by using multiple imputation.
-In the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.^[We also attempted to make fuller use of the available survey data by employing the DCPO model [@Solt2020a], which unlike the [@Claassen2019] model does not dichotomize ordinal responses.
+As democracy is also a latent variable in these analyses, we include the quantified uncertainty in its estimates as well, along with that for corruption in the models of @Claassen2020b.^[
+We also include the uncertainty in GDP per capita and resource dependence by using multiple imputation of missing observations rather than the single imputation employed in the original analyses.]
+In the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.^[
+We attempted to make fuller use of the available survey data by employing the DCPO model [@Solt2020a], which unlike the @Claassen2019 model does not dichotomize ordinal responses.
 The better fit of the DCPO model to the data on democratic support [see @Solt2020a, 10-12] and the additional information it incorporates, however, did not yield substantively different results; see Supplementary Information Appendix \@ref(dcpo).]
@@
 
-Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement errors, and measurement errors can reverse the sign of estimation of coefficients [@Bound2001, 3709; @Saccenti2020, 8], attenuate or exaggerate coefficient estimates as well as bias standard errors [see, e.g., @Blackwell2017, 318-319; @caughey2018, 254].
+Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement error, and measurement error can reverse the sign of estimation of coefficients [@Bound2001, 3709; @Saccenti2020, 8], attenuate or exaggerate coefficient estimates as well as bias standard errors [see, e.g., @Blackwell2017, 318-319; @caughey2018, 254].
 In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey2018, 254].
-
 Therefore, after replicating the original analyses that use only the point estimates for public support and the other variables included in the model, we perform the analyses again only this time incorporating uncertainty in analysis models using our replication data.

### 2021-12-23 paper/dcpo_demsupport.Rmd
polish discussion of MOC

@@
 As latent variable measurement models become more commonly used, it is absolutely necessary for researchers employing them to incorporate the associated uncertainty into their analyses.
-As demonstrated here, this can be done straightforwardly using the method of composition [see @Tanner1993, 52; @Treier2008, 215], without requiring any further change in modeling strategy.
+As demonstrated here, this can be done straightforwardly using the method of composition [see @Tanner1993, 52; @Treier2008, 215], without requiring any further change in model specification.
 
@@
 
-Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement error, and measurement error can reverse the sign of estimation of coefficients [@Bound2001, 3709; @Saccenti2020, 8], attenuate or exaggerate coefficient estimates as well as bias standard errors [see, e.g., @Blackwell2017, 318-319; @caughey2018, 254].
+Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are always estimated with a quantifiable amount of measurement error, and ignoring measurement error in analyses can attenuate, exaggerate, or even reverse coefficient estimates as well as bias standard errors [see, e.g., @Bound2001, 3709; @Blackwell2017, 318-319; @caughey2018, 254; @Saccenti2020, 8].
 In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey2018, 254].
 Therefore, after replicating the original analyses that use only the point estimates for public support and the other variables included in the model, we perform the analyses again only this time incorporating uncertainty in analysis models using our replication data.
-We conduct inferences from the distributive data via the technique known as the "method of composition" (MOC) [@Tanner1993, 52].
+We conduct inferences from the distributive data via the technique known as the "method of composition"  [MOC, @Tanner1993, 52].
 MOC accounts for uncertainty from opinion estimates and analysis models through each modeling stage.
-In analysis stage, uncertainty is incorporated through simulation based on variance-covariance matrix of a given model, regardless of the structures or features of the given model.
-Therefore MOC can adapt any different types of models, including but not limited to different specifications for a Time-Series-Cross-Sectional approach for TSCS data [@caughey2018, A15-16], a Cox proportional hazards model [@Treier2008, 215], or individual level roll call voting model [@Kastellec2015, 791].^[For additional details on this technique, see Supplementary Information Appendix \@ref(moc).]
-
-As an alternative way, a structural equation model(SEM) which incorporates measurement model and structural links between variables together can also account for bias caused by simultaneity between variables and measurement models.
-However, SEM is a method to test the match between the model and the data, subject to confirmation bias due to the existing of competing theories which we have in the theory on democracy and public opinion, omitted variables, linear causal relationship assumption, the sensitivity to the estimator choice when both endogenous and endogenous are contaminated by measurement errors [@Umeh2019], among others [@Tomarken2005].
+In analysis stage, uncertainty is incorporated through simulation based on the variance-covariance matrix of a given model, regardless of its structure or features.
+This allows MOC to adapt to many different types of models, including but not limited to different time-series-cross-sectional specifications [@caughey2018, A15-16], Cox proportional hazards models [@Treier2008, 215], or models of individual-level roll call voting [@Kastellec2015, 791].^[For additional details on the MOC technique, see Supplementary Information Appendix \@ref(moc).]
+
+As an alternative way, a structural equation model (SEM) which incorporates measurement model and structural links between variables together can also account for bias caused by simultaneity between variables and measurement models.
+However, SEM is a method to test the match between the model and the data, subject to confirmation bias due to the existing of competing theories which we have in the theory on democracy and public opinion, omitted variables, linear causal relationship assumption, the sensitivity to the estimator choice when both endogenous and endogenous are contaminated by measurement errors, among others [@Tomarken2005].
 

### 2021-12-24 paper/dcpo_demsupport.Rmd
revise conclusion for method contribution #33

@@
 This points to the absolute necessity of incorporating measurement uncertainty into analyses that include latent variables.
-As the use of latent variables grows more common in political science, both researchers and readers should be aware that these variables' concomitant measurement uncertainty cannot be neglected.
-Since measurement uncertainty distorts both statistical and substantive inferences with unknown directions on the sign and size of coefficients [@Bound2001;@Blackwell2017; @caughey2018], it is not only a methodological concern but also has substantive implications [@juhl_measurement_2019].
-
-The null results reached in this letter have several substantive implications.
+As the use of latent variables grows more common, political scientists should be aware that these variables' concomitant measurement uncertainty cannot be neglected.
+Recent cross-national time-series measures of, for example, European policy ideology [developed in @Caughey2019], immigration mood and immigration concern [presented in @Claassen2022], and public gender egalitarianism [introduced in @Woo2022], make possible a host of previously infeasible analyses, but the resulting research cannot be considered robust if it does not also incorporate these measures' quantified uncertainty.
+
+The results reached in this letter also have several substantive implications.
 They highlight theoretical arguments that maintain that levels of democratic support undergird democracy only over the long term and so lend indirect support to other explanations for short-run changes in regime.

### 2021-12-24 paper/dcpo_demsupport.Rmd
drop SEM discussion

@@
 As the use of latent variables grows more common, political scientists should be aware that these variables' concomitant measurement uncertainty cannot be neglected.
-Recent cross-national time-series measures of, for example, European policy ideology [developed in @Caughey2019], immigration mood and immigration concern [presented in @Claassen2022], and public gender egalitarianism [introduced in @Woo2022], make possible a host of previously infeasible analyses, but the resulting research cannot be considered robust if it does not also incorporate these measures' quantified uncertainty.
+Recent cross-national time-series measures of, for example, policy ideology in Europe [developed in @Caughey2019], immigration attitudes across Europe [presented in @Claassen2022], and public gender egalitarianism worldwide [introduced in @Woo2022], make possible a host of previously infeasible analyses, but the resulting research cannot be considered robust if it does not also incorporate these measures' quantified uncertainty.
 

### 2021-12-24 paper/dcpo_demsupport.Rmd
drop SEM discussion

--- 2021-12-24 paper/dcpo_demsupport.Rmd
@@
 
-As an alternative way, a structural equation model (SEM) which incorporates measurement model and structural links between variables together can also account for bias caused by simultaneity between variables and measurement models.
-However, SEM is a method to test the match between the model and the data, subject to confirmation bias due to the existing of competing theories which we have in the theory on democracy and public opinion, omitted variables, linear causal relationship assumption, the sensitivity to the estimator choice when both endogenous and endogenous are contaminated by measurement errors, among others [@Tomarken2005].
-
-In contrast, MOC is flexible to accommodate not only various models but also multiple layers of uncertainty in both opinion estimates and substantive models [@Kastellec2015, 792] where the model and joint distribution of the error and all the variables in the model determine the bias introduced by measurement errors [@Bound2001, 3708].
-
 ```{r compare_n}
@@
 As the use of latent variables grows more common, political scientists should be aware that these variables' concomitant measurement uncertainty cannot be neglected.
-Recent cross-national time-series measures of, for example, European policy ideology [developed in @Caughey2019], immigration mood and immigration concern [presented in @Claassen2022], and public gender egalitarianism [introduced in @Woo2022], make possible a host of previously infeasible analyses, but the resulting research cannot be considered robust if it does not also incorporate these measures' quantified uncertainty.
+Recent cross-national time-series measures of, for example, policy ideology across Europe [developed in @Caughey2019], immigration attitudes in Europe [presented in @Claassen2022], and public gender egalitarianism worldwide [introduced in @Woo2022], make possible a host of previously infeasible analyses, but the resulting research cannot be considered robust if it does not also incorporate these measures' quantified uncertainty.
 
@@
 During the replications of @Claassen2020a;@Claassen2020b, we found several miscoding across the original data.
-For example, in @Claassen2020b that the author coded the option "Necesitamos un líder fuerte que no tenga que ser elegid" as "strong_lapop_2" for the question:
+For example, in @Claassen2020b that the author coded the option "necesitamos un líder fuerte que no tenga que ser eligido" as "strong_lapop_2" for the question:
 

### 2021-12-24 paper/dcpo_demsupport.Rmd
highlight that MOC requires no change in model specification.  Closes #31

@@
 
-In this letter, we reexamine the classic arguments about support for democracy and democratic change tested in these two pieces while correcting this oversight.
+Here, we reexamine the classic arguments about support for democracy and democratic change tested in these two pieces while correcting this oversight.
 In addition to incorporating the measurement uncertainty, we also sought to reduce it by expanding considerably the survey data drawn upon and re-estimating democratic support for 144 countries for up to 33 years between 1988 and 2020.
-Our analyses reveal that the significant relationships between public support and democratic change disappear once measurement uncertainty is taken into account, both in replications with the studies' original data and in our extension analyses that incorporate the additional data.
-That is, once measurement uncertainty is accounted for, there is no empirical support for either claim put forward in these two works: declining democratic support does not signal subsequent democratic backsliding, and changes in democracy do not spur a thermostatic response in democratic support.
+Our analyses reveal that the significant relationships between public support and democratic change disappear once measurement uncertainty is taken into account, both in replications with the studies' original data and in our extension analyses that incorporate additional data.
+That is, simply taking into account measurement uncertainty---making no change to the specification of the models---reveals there is no empirical support for either claim put forward in these two works: declining democratic support does not signal subsequent democratic backsliding, and changes in democracy do not spur a thermostatic response in democratic support.
 
@@
 
-Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are always estimated with a quantifiable amount of measurement error, and ignoring measurement error in analyses can attenuate, exaggerate, or even reverse coefficient estimates as well as bias standard errors [see, e.g., @Bound2001, 3709; @Blackwell2017, 318-319; @caughey2018, 254; @Saccenti2020, 8].
+Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are always estimated with a quantifiable amount of measurement error, and ignoring measurement error in analyses can attenuate, exaggerate, or even reverse coefficient estimates as well as bias standard errors [see, e.g., @Bound2001, 3709; @caughey2018, 254; @Saccenti2020, 8].
 In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey2018, 254].
@@
 MOC accounts for uncertainty from opinion estimates and analysis models through each modeling stage.
-In analysis stage, uncertainty is incorporated through simulation based on the variance-covariance matrix of a given model, regardless of its structure or features.
-This allows MOC to adapt to many different types of models, including but not limited to different time-series-cross-sectional specifications [@caughey2018, A15-16], Cox proportional hazards models [@Treier2008, 215], or models of individual-level roll call voting [@Kastellec2015, 791].^[For additional details on the MOC technique, see Supplementary Information Appendix \@ref(moc).]
+In analysis stage, uncertainty is incorporated through simulation based on the variance-covariance matrix of a model without requiring any change to its specification.
+This allows MOC to adapt to many different types of models, including but not limited to many different time-series-cross-sectional specifications [@caughey2018, A15-16], Cox proportional hazards models [@Treier2008, 215], or models of individual-level roll call voting [@Kastellec2015, 791].^[For additional details on the MOC technique, see Supplementary Information Appendix \@ref(moc).]
 
@@
 
-In this letter, we reexamined the findings from Claassen [-@Claassen2020a; -@Claassen2020b], two articles that maintain that public support helps the survival of democracy and democratic development has a thermostatic effect on public support.
+In this piece, we reexamined the findings from Claassen [-@Claassen2020a; -@Claassen2020b], two articles that maintain that public support helps the survival of democracy and democratic development has a thermostatic effect on public support.
 We demonstrated the importance of incorporating measurement uncertainty in analyzing the relationship between public support and democracy.

### 2021-12-24 paper/dcpo_demsupport.Rmd
clean up Appendix B

@@
 In our analysis models, we have latent variables in both sides of the equations: public democratic support, democracy, and corruption.
-Since measurement uncertainty associated with these latent variables can propagate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing the "Method of Composition" [@Tanner1993, 52], which has often been applied in analyses with latent variables in political science [see, e.g., @Treier2008; @caughey2018; @Kastellec2015].
+Since measurement uncertainty associated with these latent variables can propagate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing the "Method of Composition" [@Tanner1993, 52], which has often been applied in analyses with latent variables in political science [see, e.g., @Treier2008; @Kastellec2015; @caughey2018].
 
@@
 
-To sample from the conditional density and the marginal density in the right side of the equation, we follow iterative Monte Carlo procedure described by @Treier2008, at iteration t,
+To sample from the conditional density and the marginal density in the right side of the equation, we follow iterative Monte Carlo procedure described by @Treier2008, at iteration $t$,
 
@@
 
-3. We sample $\tilde{\beta^{t}}$ from the multivariate normal density with mean vector $\beta{t}$ and variance-covariance matrix $V^{t}$.
+3. We sample $\tilde{\beta^{t}}$ from the multivariate normal density with mean vector $\beta^{t}$ and variance-covariance matrix $V^{t}$.
 
@@
 For each of these five latent variables, we take 900 draws from its posterior distribution.
-We duplicate the dataset of variables “without” measurement error 900 times, and assign them to each a different random draw from the distributions of variables with measurement error, which yields 900 dataset.
-In next step, we run each of analysis models with these 900 datasets independently and save the resulting estimates of coefficients and the matrix of variance-covariance for each run.
+We duplicate the dataset of variables "without" measurement error 900 times, and assign them to each a different random draw from the distributions of variables with measurement error, which yields 900 datasets.
+In the next step, we run each of analysis models with these 900 datasets independently and save the resulting estimates of coefficients and the matrix of variance-covariance for each run.
 We then draw one sample from the multivariate normal distribution with the mean vector of coefficient estimates and variance-covariance matrix produced from each run.
 This procedure finally yields 900 samples of estimated coefficients drawn from the joint density of $\beta$ and $\theta$.
-We calculate point estimates and standard error based on these 900 samples.
+We calculate point estimates and standard errors based on these 900 samples.
 

### 2021-12-24 paper/dcpo_demsupport.Rmd
clean up Appendix C

@@
 The DCPO model has several advantages over the @Claassen2019 model used in Claassen [-@Claassen2020a; -@Claassen2020b].
-First, while the @Claassen2019 model dichotomizes responses and so discards some information provided by 50 of the 52 survey items employed in Claassen [-@Claassen2020a; -@Claassen2020b], the DCPO model makes use of all of the information available from these ordinal items [@Solt2020a, p.5].
+First, while the @Claassen2019 model dichotomizes responses and so discards some information provided by the 50 ordinal survey items (of 52 total) employed in Claassen [-@Claassen2020a; -@Claassen2020b], the DCPO model makes use of all of the information available from these ordinal items [@Solt2020a, p.5].
 Second, as the DCPO model includes both parameters for the dispersion of each survey item and for the standard deviation of aggregate public opinion in each country-year, it is a complete population-level item-response model and so, unlike the @Claassen2019 model, is explicitly derived from an individual-level model of survey responses [@Solt2020a, pp.3-4; see also @McGann2014].
@@
 
-Even with the advantages of the DCPO model, there is no evidence to support the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support sustains democratic regimes or public support responds thermostatically to changes in democracy.
+Even with the advantages of the DCPO model, there is no evidence to support the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support sustains democratic regimes or that public support responds thermostatically to changes in democracy.
 

### 2021-12-24 paper/dcpo_demsupport.Rmd
clean up Appendix A

@@
 First, for each item used in the two articles' measure of democratic support, we identified the original variable names and corresponding values in each survey dataset. 
-We then used the `dcpo_setup` and `format_claassen` functions of the `DCPOtools` R package to automate the process of generating a dataset of survey marginals.
+We then used the `dcpo_setup` and `format_claassen` functions of the `DCPOtools` R package [@Solt2019] to automate the process of generating a dataset of survey marginals.
 These survey marginals were then used to generate estimates of democratic support in Stan using the `supdem.stan.mod5.stan` script from the @Claassen2020a Dataverse materials.
@@
 Version 10, however, does not include posterior draws of the estimates, but rather standard errors.
-For the purposes of incorporating this uncertainty into our analyses, we assumed a normal distribution around the point estimates.
+For the purposes of incorporating this uncertainty into our analyses, we assumed these errors were normally distributed around the point estimates.
 
@@
 The corruption variable used in @Claassen2020b is the Corruption Perceptions Index, which provides point estimates and standard errors for the years from 2012 to 2018.
-For country-years beyond that range, we estimated standard errors for by first identifying the country's maximum relative standard error (standard error/point estimate) during 2012-2018 and then multiplying this quantity by the country-year's point estimate.
+For country-years beyond that range, we conservatively estimated standard errors by first identifying the country's maximum relative standard error (standard error/point estimate) during 2012-2018 and then multiplying this quantity by the country-year's point estimate.
 For the purposes of incorporating this uncertainty into our analyses, we again assumed a normal distribution around the point estimates.
 
-In Appendix \@ref(moc), we illustrate how we employed these simulated distributions to take uncertainty into account in our analysis models.
+In Appendix \@ref(moc), we illustrate how we employed these simulated distributions to take uncertainty into account in the models replicating the analyses of [@Claassen2020a; @Claassen2020b].
 
@@
 
-## Numeric Results for Figure \@ref(fig:plot-fullAJPS) and Figure \@ref(fig:plot-fullAPSR)
-
-During the replications of @Claassen2020a;@Claassen2020b, we found several miscoding across the original data.
-For example, in @Claassen2020b that the author coded the option "necesitamos un líder fuerte que no tenga que ser eligido" as "strong_lapop_2" for the question:
+## Numeric Results for Figure \@ref(fig:plot-fullAJPS) and Figure \@ref(fig:plot-fullAPSR) {-}
+
+During the replications of [@Claassen2020a;@Claassen2020b], we encountered a number of miscodings in the original data that we corrected.
+For example, the item "necesitamos un líder fuerte que no tenga que ser eligido" was coded as `strong_lapop_2`, although according to the AmericasBarometer codebooks, this question and that coded as `strong_lapop_1` employed the identical language:
 
@@
 
-But according to the description of the question, this ought to be "strong_amb_1."
-Another example involves a miscount of the midpoint of its three-point scale as a positive, democracy-supporting response, when the original work coded "evdemoc_asiab" in the Asian Barometer.
-In a separate ongoing research project, we will identify the main types of miscoding and evaluate the extent to which they affect on the inferences.
-In this work, we use the corrected data for the replications with uncertainty to ensure that the data quality would not distort the results.
-
-Moreover, for the GMM models, the original publication presented the observation number based on the trimmed data, i.e., "2435", while the tabulating function in the replication file (line 86) uses the full used-observation number, "4735."
-We follow the replication file in the following tables.
+We therefore coded both as `strong_lapop_1`.
+Other examples include inconsistent coding regarding what constitutes a "democracy-supporting" response and the inconsistent application of the stated rule regarding "don't know" and other nonresponses.
+Here we use the corrected data for the replications with uncertainty to ensure that issues of data quality did not distort the results presented.
+
+Finally, for the GMM models, the original publication presented the observation number based on the trimmed data, i.e., "2435", while the tabulating function in the replication file (line 86) uses the full used-observation number, "4735."
+We follow the replication file in the tables below.
 

### 2021-12-24 paper/dcpo_demsupport.Rmd
clean up method section

@@
 As latent variable measurement models become more commonly used, it is absolutely necessary for researchers employing them to incorporate the associated uncertainty into their analyses.
-As demonstrated here, this can be done straightforwardly using the method of composition [see @Tanner1993, 52; @Treier2008, 215], without requiring any further change in model specification.
+As demonstrated here, this can be done straightforwardly using the method of composition [see @Tanner1993, 52; @Treier2008, 215] without requiring any further change in model specification.
 
@@
 
-Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are always estimated with a quantifiable amount of measurement error, and ignoring measurement error in analyses can attenuate, exaggerate, or even reverse coefficient estimates as well as bias standard errors [see, e.g., @Bound2001, 3709; @caughey2018, 254; @Saccenti2020, 8].
+Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019; @Claassen2022], latent variables are always estimated with a quantifiable amount of measurement error, and ignoring measurement error in analyses can attenuate, exaggerate, or even reverse coefficient estimates as well as bias standard errors [see, e.g., @Bound2001, 3709; @caughey2018, 254; @Saccenti2020, 8].
 In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey2018, 254].
-Therefore, after replicating the original analyses that use only the point estimates for public support and the other variables included in the model, we perform the analyses again only this time incorporating uncertainty in analysis models using our replication data.
+Therefore, after replicating the original analyses that use only the point estimates for public support and the other variables included in the model, we perform the analyses again only this time incorporating uncertainty in the articles' models using our replicated data.
 We conduct inferences from the distributive data via the technique known as the "method of composition"  [MOC, @Tanner1993, 52].
 MOC accounts for uncertainty from opinion estimates and analysis models through each modeling stage.
-In analysis stage, uncertainty is incorporated through simulation based on the variance-covariance matrix of a model without requiring any change to its specification.
+In the analysis stage, uncertainty is incorporated through simulation based on the variance-covariance matrix of a model without requiring any change to its specification.
 This allows MOC to adapt to many different types of models, including but not limited to many different time-series-cross-sectional specifications [@caughey2018, A15-16], Cox proportional hazards models [@Treier2008, 215], or models of individual-level roll call voting [@Kastellec2015, 791].^[For additional details on the MOC technique, see Supplementary Information Appendix \@ref(moc).]

### 2021-12-24 paper/dcpo_demsupport.Rmd
clean up results section

@@
 In all four models, the positive coefficients for democratic support are no longer statistically significant.
-The darker, righth and results also incorporate uncertainty but additionally replace the estimates of democratic support with those based on our expanded dataset; this change works to increase the number of observations analyzed as well.
-Although the confidence intervals shrink considerably, the coefficient estimates move much closer to zero; the hypothesis remains unsupported.
+The darker, righthand results also incorporate uncertainty but additionally replace the estimates of democratic support with those based on our expanded dataset; this change works to increase the number of observations analyzed as well.
+Although the confidence intervals shrink considerably, the coefficient estimates move much closer to zero: the hypothesis remains unsupported.
 

### 2021-12-24 paper/dcpo_demsupport.Rmd
trim citations in discussion

@@
 Because these questions contain no information on respondents' support for democracy relative to other values with which it may come into conflict, such as their partisanship [see, e.g., @Carey2020; @McCoy2020]---or on whether respondents even understand the meaning of the democracy they are claiming to support [see, e.g., @Kirsch2019; @Wuttke2020]---these questions appear to miss capturing the true extent of the support among the public that democracy will actually find when public support is in fact most needed.
-Our results also reinforce arguments that relationships between democracy and public support unfold only over the long term [see, e.g., @Welzel2017] and that democratic change in the short term is instead best understood as an elite-driven phenomenon [see, e.g., @levitsky_how_2018; @Haggard2021].
+Our results also reinforce arguments that relationships between democracy and public support unfold only over the long term [see, e.g., @Welzel2017] and that democratic change in the short term is instead best understood as an elite-driven phenomenon [see, e.g., @Haggard2021].
 
@@
 Yet another is that the answers to the above items reflect actual support for democracy only when respondents also either hold a robust understanding of what liberal democracy means or anchor their support in emancipative values of universal freedoms.
-If they do not, their positive responses to these items indicate support for autocracy instead [see, e.g., @Brunkert2019; @Kirsch2019; @Wuttke2021].
+If they do not, their positive responses to these items indicate support for autocracy instead [see, e.g., @Kirsch2019; @Wuttke2021].
 Taking any or all of these into account requires considering the _combination_ of attitudes: even the inclusion of additional questions in a unidimensional public opinion model such as that provided by @Claassen2019 will not be sufficient [see, e.g., @Wuttke2020].
@@
 Finally, by failing to provide evidence for a short-term relationship between democratic support and democracy, these null findings can be seen to lend additional support to other theories of regime change.
-There are compelling arguments that episodes of democratic transition [see, e.g., @ODonnell1986a; @Karl1987] and backsliding [see, e.g., @levitsky_how_2018; @Haggard2021] are best understood as products of elite decision making.
+There are compelling arguments that episodes of democratic transition [see, e.g., @ODonnell1986a] and backsliding [see, e.g., @Haggard2021] are best understood as products of elite decision making.
 With regard to the latter, critics have charged that these claims overlook the extent of demand for authoritarian rule among the public [see, e.g., @Norris2021].

### 2021-12-24 paper/dcpo_demsupport.Rmd
trim citations for word count

@@
 Countries with greater democratic support have been found to become stronger and more stable democracies [e.g., @Inglehart2005, 251-254] and just the opposite [@Fails2010, 182-183].
-Similarly, studies have alternately found that more experience with democracy yields more democratic support [e.g., @Fails2010, 183; @Wuttke2020a, 5-6] or instead that long-established democracies are suffering from democratic fatigue [e.g., @Denemark2016; @Foa2017].
+Similarly, studies have alternately found that more experience with democracy yields more democratic support [e.g., @Fails2010, 183] or instead that long-established democracies are suffering from democratic fatigue [e.g., @Foa2017].
 
@@
 Because they are unobserved, latent variables are inherently accompanied by measurement uncertainty.
-To leave this uncertainty unacknowledged is to make the implausible assumption that the latent variables are measured perfectly, an assumption which distorts both statistical and substantive inference [see, e.g., @Crabtree2015; @juhl_measurement_2019].
+To leave this uncertainty unacknowledged is to make the implausible assumption that the latent variables are measured perfectly, an assumption which distorts both statistical and substantive inference [see, e.g., @Crabtree2015].
 
@@
 Similarly, the results presented here are further evidence that the survey items commonly employed to measure democratic support are inadequate to the task.
-Because these questions contain no information on respondents' support for democracy relative to other values with which it may come into conflict, such as their partisanship [see, e.g., @Carey2020; @McCoy2020]---or on whether respondents even understand the meaning of the democracy they are claiming to support [see, e.g., @Kirsch2019; @Wuttke2020]---these questions appear to miss capturing the true extent of the support among the public that democracy will actually find when public support is in fact most needed.
+Because these questions contain no information on respondents' support for democracy relative to other values with which it may come into conflict, such as their partisanship [see, e.g., @graham_democracy_2020; @McCoy2020]---or on whether respondents even understand the meaning of the democracy they are claiming to support [see, e.g., @Kirsch2019; @Wuttke2020]---these questions appear to miss capturing the true extent of the support among the public that democracy will actually find when public support is in fact most needed.
 Our results also reinforce arguments that relationships between democracy and public support unfold only over the long term [see, e.g., @Welzel2017] and that democratic change in the short term is instead best understood as an elite-driven phenomenon [see, e.g., @Haggard2021].
@@
 First, we reproduce the original analyses of Claassen [-@Claassen2020a; -@Claassen2020b], which included only the point estimates of the latent variable of democratic support and so exclude its measurement uncertainty.
-Second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.^[Additional details on this data replication process are found in Supplementary Information Appendix \@ref(dgp).]
+Second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.^[
+Additional details on this data replication process are found in Supplementary Information Appendix \@ref(dgp).]
 As democracy is also a latent variable in these analyses, we include the quantified uncertainty in its estimates as well, along with that for corruption in the models of @Claassen2020b.^[
-We also include the uncertainty in GDP per capita and resource dependence by using multiple imputation of missing observations rather than the single imputation employed in the original analyses.]
+We also include the uncertainty in GDP per capita and resource dependence due to missing data by using multiple imputation rather than the single imputation employed in the original analyses.]
 In the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.^[
@@
 
-Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019; @Claassen2022], latent variables are always estimated with a quantifiable amount of measurement error, and ignoring measurement error in analyses can attenuate, exaggerate, or even reverse coefficient estimates as well as bias standard errors [see, e.g., @Bound2001, 3709; @caughey2018, 254; @Saccenti2020, 8].
+Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion, latent variables are always estimated with a quantifiable amount of measurement error, and ignoring measurement error in analyses can attenuate, exaggerate, or even reverse coefficient estimates as well as bias standard errors [see, e.g., @Bound2001, 3709; @caughey2018, 254; @Saccenti2020, 8].
 In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey2018, 254].
@@
 In the analysis stage, uncertainty is incorporated through simulation based on the variance-covariance matrix of a model without requiring any change to its specification.
-This allows MOC to adapt to many different types of models, including but not limited to many different time-series-cross-sectional specifications [@caughey2018, A15-16], Cox proportional hazards models [@Treier2008, 215], or models of individual-level roll call voting [@Kastellec2015, 791].^[For additional details on the MOC technique, see Supplementary Information Appendix \@ref(moc).]
 
@@
 To provide a further test of the classic arguments on democracy and public support, we generated estimates of democratic support using the same procedure as in Claassen [-@Claassen2020a; -@Claassen2020b] on a bigger data set, assembling as much survey data on democratic support as possible.
-We employed `r dcpo_input_ncyi` national opinions on democracy from `r dcpo_input_surv` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncy` opinions and `r supdem_surv` national surveys used in Claassen [-@Claassen2020a; -@Claassen2020b].^[These figures represent the survey data actually used in estimating public support for democracy; as in Claassen [-@Claassen2020a; -@Claassen2020b], countries for which two separate years of survey data were not available were excluded.]
+We employed `r dcpo_input_ncyi` national opinions on democracy from `r dcpo_input_surv` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncy` opinions and `r supdem_surv` national surveys used in Claassen [-@Claassen2020a; -@Claassen2020b].^[
+These figures represent the survey data actually used in estimating public support for democracy; as in Claassen [-@Claassen2020a; -@Claassen2020b], countries for which two separate years of survey data were not available were excluded.]
 
@@
 
-Further, these null results recommend building recent and more refined conceptualizations of democratic support into our measures.
+Further, these results recommend building recent and more refined conceptualizations of democratic support into our measures.
 In other words, the survey items employed by Claassen [-@Claassen2020a; -@Claassen2020b]---which ask respondents to assess the desirability or appropriateness of democracy, to compare democracy to some undemocratic alternative, or to assess one of these alternatives---although often used by researchers, may not capture every aspect of democratic support necessary for it to play its hypothesized roles in the classic theory.
 One possibility is that only those who profess to prefer democracy to its alternatives _and also_ value freedom of expression, freedom of association, and pluralism of opinion will take appropriate action when democracy is threatened [see, e.g., @Schedler2007].
-Another is that respondents' other values, such as their policy preferences or partisanship, may weigh more heavily than their support for democracy: there is growing evidence that, at least in the United States, there are many for whom these other considerations excuse substantial transgressions against democracy [see @Carey2020; @graham_democracy_2020; @McCoy2020].
+Another is that respondents' other values, such as their policy preferences or partisanship, may weigh more heavily than their support for democracy: there is growing evidence that, at least in the United States, there are many for whom these other considerations excuse substantial transgressions against democracy [see @graham_democracy_2020; @McCoy2020].
 Yet another is that the answers to the above items reflect actual support for democracy only when respondents also either hold a robust understanding of what liberal democracy means or anchor their support in emancipative values of universal freedoms.
@@
 
-In this piece, we reexamined the findings from Claassen [-@Claassen2020a; -@Claassen2020b], two articles that maintain that public support helps the survival of democracy and democratic development has a thermostatic effect on public support.
-We demonstrated the importance of incorporating measurement uncertainty in analyzing the relationship between public support and democracy.
-Taking uncertainty into account rendered both articles' conclusions without empirical support, even when we added a considerable quantity of additional data.
-
-This points to the absolute necessity of incorporating measurement uncertainty into analyses that include latent variables.
+Simply taking measurement uncertainty into account, while making no changes to model specification, rendered the conclusions of both articles examined here without empirical support, even when we added a considerable quantity of additional data.
+Methodologically, these results point to the absolute necessity of incorporating measurement uncertainty into analyses that include latent variables.
 As the use of latent variables grows more common, political scientists should be aware that these variables' concomitant measurement uncertainty cannot be neglected.
@@
 
-The results reached in this letter also have several substantive implications.
+Our results also have several substantive implications.
 They highlight theoretical arguments that maintain that levels of democratic support undergird democracy only over the long term and so lend indirect support to other explanations for short-run changes in regime.

### 2021-12-24 paper/dcpo_demsupport.Rmd
fuss with abstract

@@
 Correcting this oversight reveals that there is no support for either study's conclusion.
-Efforts to minimize the uncertainty by incorporating additional survey data still fail to yield evidence in support of either hypothesis.
-These results underscore the need both for more nuanced analyses of the relationships between public support and democracy and of accounting for measurement uncertainty when working with latent variables.
+Efforts to minimize the uncertainty by incorporating additional data still fail to yield evidence in support of either hypothesis.
+These results underscore the need both for more nuanced analyses of the relationships between public support and democracy and for taking measurement uncertainty into account when working with latent variables.
 [150/150 words]"

### 2021-12-24 paper/dcpo_demsupport.Rmd
fuss with intro for wc

@@
 Further, the survey data available across countries and over time on support for democracy---or indeed most topics in public opinion---are sparse and incomparable, greatly hindering broadly comparative research.
-Recently, a few pioneering studies have sought to overcome the hurdle of sparse and incomparable data by developing latent variable measurement models of public opinion [see @Caughey2019; @Claassen2019; @Solt2020a].
-A pair of prominent recent works took advantage of this latent variable approach to measure democratic support for over one hundred countries for up to nearly three decades and to then assess, respectively, its consequences for and roots in democratic change [@Claassen2020a; @Claassen2020b].
+Recent pioneering studies have sought to overcome the hurdle of sparse and incomparable data by developing latent variable measurement models of public opinion [see @Caughey2019; @Claassen2019; @Solt2020a].
+A pair of prominent recent works took advantage of this latent variable approach to measure democratic support for over one hundred countries for up to nearly three decades and assess, respectively, its consequences for and roots in democratic change [@Claassen2020a; @Claassen2020b].
 The first of these works concluded, supporting the classic argument, that mass support had a positive impact on democratic change, especially the endurance of democracy [@Claassen2020a, 127-130].

### 2021-12-24 paper/dcpo_demsupport.Rmd
fuss with intro; update word count

@@
 
-(Word count: 3888)
+(Word count: 3973)
 
@@
 Countries with greater democratic support have been found to become stronger and more stable democracies [e.g., @Inglehart2005, 251-254] and just the opposite [@Fails2010, 182-183].
-Similarly, studies have alternately found that more experience with democracy yields more democratic support [e.g., @Fails2010, 183] or instead that long-established democracies are suffering from democratic fatigue [e.g., @Foa2017].
+Similarly, studies have alternately found that more experience with democracy yields more democratic support [e.g., @Fails2010, 183; @Wuttke2020a, 5-6] or instead that long-established democracies are suffering from democratic fatigue [e.g., @Foa2017].
 

### 2021-12-24 paper/dcpo_demsupport.Rmd
clean up appendices

@@
 We then used the `dcpo_setup` and `format_claassen` functions of the `DCPOtools` R package [@Solt2019] to automate the process of generating a dataset of survey marginals.
+We encountered a number of miscodings in the original data that we corrected.
+For example, the item "necesitamos un líder fuerte que no tenga que ser eligido" was coded as `strong_lapop_2`, although according to the AmericasBarometer codebooks, this question and that coded as `strong_lapop_1` employed the identical language:
+
+> Hay gente que dice que necesitamos un líder fuerte que no tenga que ser elegido a través del voto.
+AUT1 Otros dicen que aunque las cosas no funcionen, la democracia electoral, o sea el voto popular, es siempre
+lo mejor. ¿Qué piensa usted? [Leer alternativas]
+
+We therefore coded both as `strong_lapop_1`.
+Other examples include inconsistent coding regarding what constitutes a "democracy-supporting" response and the inconsistent application of the stated rule regarding "don't know" and other nonresponses.
+Here we use the corrected data for the replications with uncertainty to ensure that issues of data quality did not distort the results presented.
 These survey marginals were then used to generate estimates of democratic support in Stan using the `supdem.stan.mod5.stan` script from the @Claassen2020a Dataverse materials.
 Draws from the posterior distribution quantify the uncertainty in the estimates.
+Finally, for the GMM models, the original publication presented the observation number based on the trimmed data, i.e., "2435", while the tabulating function in the replication file (line 86) uses the full used-observation number, "4735."
+We follow the replication file in the tables of Appendix \@ref(tables_not_plots) below.
 
@@
 
-In Appendix \@ref(moc), we illustrate how we employed these simulated distributions to take uncertainty into account in the models replicating the analyses of [@Claassen2020a; @Claassen2020b].
-
 \pagebreak
 
-## Numeric Results for Figure \@ref(fig:plot-fullAJPS) and Figure \@ref(fig:plot-fullAPSR) {-}
-
-During the replications of [@Claassen2020a;@Claassen2020b], we encountered a number of miscodings in the original data that we corrected.
-For example, the item "necesitamos un líder fuerte que no tenga que ser eligido" was coded as `strong_lapop_2`, although according to the AmericasBarometer codebooks, this question and that coded as `strong_lapop_1` employed the identical language:
-
-> Hay gente que dice que necesitamos un líder fuerte que no tenga que ser elegido a través del voto.
-AUT1 Otros dicen que aunque las cosas no funcionen, la democracia electoral, o sea el voto popular, es siempre
-lo mejor. ¿Qué piensa usted? [Leer alternativas]
-
-We therefore coded both as `strong_lapop_1`.
-Other examples include inconsistent coding regarding what constitutes a "democracy-supporting" response and the inconsistent application of the stated rule regarding "don't know" and other nonresponses.
-Here we use the corrected data for the replications with uncertainty to ensure that issues of data quality did not distort the results presented.
-
-Finally, for the GMM models, the original publication presented the observation number based on the trimmed data, i.e., "2435", while the tabulating function in the replication file (line 86) uses the full used-observation number, "4735."
-We follow the replication file in the tables below.
+# Numeric Results for Figures \@ref(fig:plot-fullAJPS) and \@ref(fig:plot-fullAPSR) {#tables_not_plots}
 

### 2021-12-24 paper/dcpo_demsupport.Rmd
modify notation of beta and variance in MOC. @fsolt @sammo3182

@@
 2.
-For each analysis model, we run the model with $\theta^{t}$, and $w$, and save the coefficient estimates $\beta^{t}$ and variance-covariance matrix of $\hat{\beta^{t}}$, $\hat{V^{t}}$, both of which change due to the uncertainty in $\theta$.
-
-3. We sample $\tilde{\beta^{t}}$ from the multivariate normal density with mean vector $\beta^{t}$ and variance-covariance matrix $V^{t}$.
+For each analysis model, we run the model with $\theta^{t}$, and $w$, and save the coefficient estimates $\hat{\beta^{t}}$ and variance-covariance matrix of $\hat{\beta^{t}}$, $\hat{V^{t}}$, both of which change due to the uncertainty in $\theta$.
+
+3. We sample $\tilde{\beta^{t}}$ from the multivariate normal density with mean vector $\hat{\beta^{t}}$ and variance-covariance matrix $\hat{V^{t}}$.
 

### 2021-12-24 paper/dcpo_demsupport.Rmd
ugh. revisions specifically to address comments @Tyhcass @sammo3182.  Will need another to again cut to <4k words

--- 2021-12-24 paper/dcpo_demsupport.Rmd
@@
 Two prominent recent studies (Claassen 2020a, 2020b) reinvigorated the classic hypothesis on the positive relationship between public support for democracy and regime survival---and challenged its reciprocal counterpart---by using a latent variable approach to measure mass democratic support from cross-national survey data.
-Such approaches come with concomitant measurement uncertainty that should be taken into account, however, and neither study incorporated this uncertainty into its analyses.
-Correcting this oversight reveals that there is no support for either study's conclusion.
-Efforts to minimize the uncertainty by incorporating additional data still fail to yield evidence in support of either hypothesis.
+Both studies, however, used only the point estimates of democratic support; we show that incorporating the concomitant measurement uncertainty into these analyses reveals that there is no support for either study's conclusion.
+Efforts to minimize the uncertainty by incorporating additional survey data still fail to yield evidence in support of either hypothesis.
 These results underscore the need both for more nuanced analyses of the relationships between public support and democracy and for taking measurement uncertainty into account when working with latent variables.
-[150/150 words]"
+[147/150 words]"
 keywords: "Democratization, public support, regime survival, measurement uncertainty, latent variables."
@@
 Countries with greater democratic support have been found to become stronger and more stable democracies [e.g., @Inglehart2005, 251-254] and just the opposite [@Fails2010, 182-183].
-Similarly, studies have alternately found that more experience with democracy yields more democratic support [e.g., @Fails2010, 183; @Wuttke2020a, 5-6] or instead that long-established democracies are suffering from democratic fatigue [e.g., @Foa2017].
+Similarly, studies have alternately found that more experience with democracy yields more democratic support [e.g., @Fails2010, 183] or instead that long-established democracies are suffering from democratic fatigue [e.g., @Foa2017].
 
@@
 Similarly, the results presented here are further evidence that the survey items commonly employed to measure democratic support are inadequate to the task.
-Because these questions contain no information on respondents' support for democracy relative to other values with which it may come into conflict, such as their partisanship [see, e.g., @graham_democracy_2020; @McCoy2020]---or on whether respondents even understand the meaning of the democracy they are claiming to support [see, e.g., @Kirsch2019; @Wuttke2020]---these questions appear to miss capturing the true extent of the support among the public that democracy will actually find when public support is in fact most needed.
+Because these questions contain no information on respondents' support for democracy relative to other values with which it may come into conflict [see, e.g., @graham_democracy_2020; @McCoy2020] or on whether respondents even understand the meaning of the democracy they are claiming to support [see, e.g., @Kirsch2019; @Wuttke2020], these questions appear to miss capturing the true extent of the support among the public that democracy will actually find when public support is in fact most needed.
 Our results also reinforce arguments that relationships between democracy and public support unfold only over the long term [see, e.g., @Welzel2017] and that democratic change in the short term is instead best understood as an elite-driven phenomenon [see, e.g., @Haggard2021].
@@
 
-Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion, latent variables are always estimated with a quantifiable amount of measurement error, and ignoring measurement error in analyses can attenuate, exaggerate, or even reverse coefficient estimates as well as bias standard errors [see, e.g., @Bound2001, 3709; @caughey2018, 254; @Saccenti2020, 8].
+Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion, latent variables are always estimated with a quantifiable amount of measurement error, and ignoring measurement error in analyses can attenuate, exaggerate, or even reverse coefficient estimates as well as bias standard errors [see, e.g., @Bound2001, 3709; @caughey2018, 254].
 In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey2018, 254].
@@
 In the analysis stage, uncertainty is incorporated through simulation based on the variance-covariance matrix of a model without requiring any change to its specification.
+This allows MOC to be broadly applicable adapt to many different types of models, including time-series-cross-sectional models [@caughey2018, A15-16], Cox proportional hazards models [@Treier2008, 215], or models of individual-level roll call voting [@Kastellec2015, 791].^[For additional details on the MOC technique, see Supplementary Information Appendix \@ref(moc).]
 
@@
 Figure \@ref(fig:plot-fullAJPS) presents the reanalyses of the hypothesis that public support influences the level of democracy [@Claassen2020a, Table 1, 128].
-The lighter, lefthand set of results replicate the analysis of @Claassen2020a, including its exclusion of measurement uncertainty by using only the point estimates of public democratic support and the other variables measured with quantified error (democracy and corruption), and they reproduce that article's findings.
-The middle results introduce a single change: the uncertainty in the measurement of public support is taken into account.
+The lighter, lefthand set of results replicate the analysis of @Claassen2020a, including its exclusion of measurement uncertainty by using only the point estimates of public democratic support and the other variables measured with quantified error (i.e., democracy and corruption), and they reproduce that article's findings.
+The middle results introduce a single change: the uncertainty in the measurement of public support and these other variables is taken into account.
 In all four models, the positive coefficients for democratic support are no longer statistically significant.

### 2021-12-24 paper/memo/response_memo2.Rmd
initial commit

---
output: 
  bookdown::pdf_document2:
    fig_caption: yes
    keep_tex: yes
    toc: no
    number_sections: yes
    latex_engine: xelatex
title: |
    | Democracy, Public Support, and Measurement Uncertainty
    | Memo to Reviewers
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
spacing: single
bibliography: ../dcpo-demsupport.bib
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
---

```{r setup, include=FALSE}
options(tinytex.verbose = TRUE)

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  dpi = 300)

# If you haven't install `DCPOtools`
# remotes::install_github("fsolt/DCPOtools")

if (!require(pacman)) install.packages("pacman")
library(pacman)
library(patchwork)
library(rsdmx)

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools,
  boot, plm, # analysis
  flextable, kableExtra, modelsummary, # tabulation
  gridExtra,
  latex2exp, # visualization
  rstan, # Bayesian estimation
  broom, tidyverse, janitor, # data wrangling
  dotwhisker # visualization
)

# Functions preload
set.seed(313)

get_legend<-function(myggplot){
  tmp <- ggplot_gtable(ggplot_build(myggplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)
}

# Theme setup
theme_set(theme_minimal())
source(here::here("R", "uiowa_palette.R"))
```

Thank you for your helpful comments, as well as your enthusiasm for this piece.
We set out a list of the specific points raised in the reviews and our responses to them below, roughly in the order they appear in the text:

1. **Abstract** The editor pointed out that, in responding to R4's desire for more discussion of our substantive point, we had allowed the balance of our attention toward our substantive and methodological contributions to become skewed too far toward the former. She suggested revising the abstract to "emphasize more clearly the contribution" on the methods side.  We revised the abstract to better highlight our methodological point.  (At her suggestion, we carried this thought through to the conclusion as well.)

1. **Introduction** The sentence flagged for revision for clarity on page 2 was split in two, and the one on page 3 was rewritten.

1. **Method** R1 asked for a justification of the method of composition (MOC) approach in the TSCS context.  We include citations to the literature establishing the broad applicability of MOC, including specifically to TSCS, at page 5.

1. **Method** R1 again raises the question of structural equation models as an alternative approach.  While SEM is a potentially appropriate technique for the examination of these questions, it has the distinct disadvantage of requiring a change in model specification to test both hypotheses simultaneously, as demonstrated by the working paper/response that R1 referenced.  (Had we pursued this approach from the outset, we surmise, R1 would have justifiably considered the altered specification to be a point of concern.)  While not specifically addressing SEM, we now stress throughout the piece the advantage of MOC in allowing us to incorporate measurement uncertainty without changing at all the original articles' model specifications.

1. **Method** R1 again raises the point that many of the estimates in Figure 2 are near zero.  As we pointed out in our previous memo, that is not particularly surprising: it merely suggests that the change in Claassen's estimates of democratic support---some 56% of which are simply random walks---is very poorly predicted by the democracy variables.  We note that the GDP and corruption variables are not particularly near zero in the figure, and that, of course, none of the estimated coefficients are really "exactly zero" as R1 claims (see Tables A.5 and A.6).  R1's reference to ADL specifications is puzzling (surely they know that "the ECM and ADL specifications are interchangeable," @Claassen2020b, 46).  If they meant to refer to the FD specifications, our point still stands: the dependent variable is the _change_ in Claassen's estimates of democratic support, which is---when uncertainty is taken into account---more often than not just random.

1. **Conclusion** The editor pointed out the conclusion was "a bit repetitive."  We cut down this section to minimize repeating ourselves.

1. **Conclusion** The editor encouraged us to engage "researchers who might not be interested in this specific substantive debate but who use similar aggregate public opinion measures in cross-national analyses are able to connect your approach to their substantive areas of interest," particularly by "revising the conclusion to incorporate a discussion of the implications for other literatures."  We added a discussion of other specific nascent comparative public opinion literatures where our methodological point is apt.

1. **Supplemental Materials** At the editor's request, we have added tables of all results to the Supplemental Materials, with Figure 1 in Tables A.1-A.3, Figure 2 in Tables A.4-A.6, Figure A.1 in Table A.7, and Figure A.2 in Table A.8.

Thank you once more for the opportunity to make revisions.
We think the paper is much stronger as a result of your comments and hope you agree.

# References

<div id="refs"></div>

### 2021-12-24 paper/memo/response_memo2.Rmd
clean up

@@
 Thank you for your helpful comments, as well as your enthusiasm for this piece.
-We set out a list of the specific points raised in the reviews and our responses to them below, roughly in the order they appear in the text:
+We set out a list of the specific points raised in the reviews and by the editor with our responses to them below, roughly in the order they appear in the text:
 
@@
 
-1. **Introduction** The sentence flagged for revision for clarity on page 2 was split in two, and the one on page 3 was rewritten.
+1. **Introduction** The sentence the editor flagged for revision for clarity on page 2 was split in two, and the one on page 3 was rewritten.
 
@@
 As we pointed out in our previous memo, that is not particularly surprising: it merely suggests that the change in Claassen's estimates of democratic support---some 56% of which are simply random walks---is very poorly predicted by the democracy variables.
-We note that the GDP and corruption variables are not particularly near zero in the figure, and that, of course, none of the estimated coefficients are really "exactly zero" as R1 claims (see Tables A.5 and A.6).
-R1's reference to ADL specifications is puzzling (surely they know that "the ECM and ADL specifications are interchangeable," @Claassen2020b, 46).
-If they meant to refer to the FD specifications, our point still stands: the dependent variable is the _change_ in Claassen's estimates of democratic support, which is---when uncertainty is taken into account---more often than not just random.
+We note that the GDP and corruption variables are not particularly near zero in the figure, and that, of course, none of the estimated coefficients are really "exactly zero" as R1 suggests (see Tables A.5 and A.6).
+R1's reference to ADL specifications is puzzling [surely they know that "the ECM and ADL specifications are interchangeable," @Claassen2020b, 46].
+If they meant to refer to the FD first-difference specifications, our point still stands: the dependent variable is the _change_ in Claassen's estimates of democratic support, which is---when uncertainty is taken into account---more often than not just random.
 
@@
 
-# References
+# References {-}
 

### 2022-02-18 paper/dcpo_demsupport.Rmd
corrected the bib, #36; fixed #43

@@
 
-(Word count: 3973)
-
-It has long been argued that democratic regimes and public support for them are mutually reinforcing: that high levels of public support ensure democracies remain strong, and that experience with democratic governance generates robust public support [see, e.g., @lipset_social_1959; @Easton1965].
-But the evidence for either part of this claim has been decidedly mixed.
-Countries with greater democratic support have been found to become stronger and more stable democracies [e.g., @Inglehart2005, 251-254] and just the opposite [@Fails2010, 182-183].
-Similarly, studies have alternately found that more experience with democracy yields more democratic support [e.g., @Fails2010, 183] or instead that long-established democracies are suffering from democratic fatigue [e.g., @Foa2017].
-
-One important reason for these mixed results is the difficulty in measuring democratic support over time and across many countries.
-Public support for democracy cannot be directly observed, and its incorrect measurement will limit inferences about the relationships between public opinion and institutional development.
-Further, the survey data available across countries and over time on support for democracy---or indeed most topics in public opinion---are sparse and incomparable, greatly hindering broadly comparative research.
-Recent pioneering studies have sought to overcome the hurdle of sparse and incomparable data by developing latent variable measurement models of public opinion [see @Caughey2019; @Claassen2019; @Solt2020a].
-A pair of prominent recent works took advantage of this latent variable approach to measure democratic support for over one hundred countries for up to nearly three decades and assess, respectively, its consequences for and roots in democratic change [@Claassen2020a; @Claassen2020b].
-The first of these works concluded, supporting the classic argument, that mass support had a positive impact on democratic change, especially the endurance of democracy [@Claassen2020a, 127-130].
-The second directly contradicted the classic argument, concluding that democratic change has a thermostatic effect on public support, that is, that rather than generating its own support, deepening democracy provokes a backlash and it is instead democratic backsliding that calls forth greater public support [@Claassen2020b, 46-50].
-
-The models employed in these studies' analyses, though, do not account for uncertainty in their measurement of democratic support.
-Because they are unobserved, latent variables are inherently accompanied by measurement uncertainty.
-To leave this uncertainty unacknowledged is to make the implausible assumption that the latent variables are measured perfectly, an assumption which distorts both statistical and substantive inference [see, e.g., @Crabtree2015].
-
-Here, we reexamine the classic arguments about support for democracy and democratic change tested in these two pieces while correcting this oversight.
-In addition to incorporating the measurement uncertainty, we also sought to reduce it by expanding considerably the survey data drawn upon and re-estimating democratic support for 144 countries for up to 33 years between 1988 and 2020.
-Our analyses reveal that the significant relationships between public support and democratic change disappear once measurement uncertainty is taken into account, both in replications with the studies' original data and in our extension analyses that incorporate additional data.
-That is, simply taking into account measurement uncertainty---making no change to the specification of the models---reveals there is no empirical support for either claim put forward in these two works: declining democratic support does not signal subsequent democratic backsliding, and changes in democracy do not spur a thermostatic response in democratic support.
-
-There are several important implications of these null results.
-They point to a need for closer attention to the conditional aspects of the classic theory [see @lipset_social_1959, 86-89; @Easton1965, 119-20].
-On the one side, the effect of democracy on public support may depend not on its mere existence but on its effectiveness [see @Magalhaes2014] and particularly with regard to redistribution [see @Krieckhaus2014].
-On the other, the impact of public support on democracy may depend on the extent to which those who support democracy are also dissatisfied with the current regime's performance [see @Qi2011].
-Similarly, the results presented here are further evidence that the survey items commonly employed to measure democratic support are inadequate to the task.
-Because these questions contain no information on respondents' support for democracy relative to other values with which it may come into conflict [see, e.g., @graham_democracy_2020; @McCoy2020] or on whether respondents even understand the meaning of the democracy they are claiming to support [see, e.g., @Kirsch2019; @Wuttke2020], these questions appear to miss capturing the true extent of the support among the public that democracy will actually find when public support is in fact most needed.
-Our results also reinforce arguments that relationships between democracy and public support unfold only over the long term [see, e.g., @Welzel2017] and that democratic change in the short term is instead best understood as an elite-driven phenomenon [see, e.g., @Haggard2021].
-
-We draw two conclusions, one methodological and one substantive.
-Many constructs in social science---from democracy to corruption to public opinion---are latent variables, and recent advances have made estimating them much more practicable.
-As latent variable measurement models become more commonly used, it is absolutely necessary for researchers employing them to incorporate the associated uncertainty into their analyses.
-As demonstrated here, this can be done straightforwardly using the method of composition [see @Tanner1993, 52; @Treier2008, 215] without requiring any further change in model specification.
-
-And, at a time when democracy is seen as under threat around the world [e.g., @Diamond2015], taken together, Claassen [-@Claassen2020a; -@Claassen2020b] send what is ultimately a reassuring message: the fate of democracy rests with us, the public, and when democratic institutions are undermined, we will swing to their support and constitute "an obstacle to democratic backsliding" [@Claassen2020b, 51].
-Both of these assertions may well be true, but the evidence we have, properly assessed, does not support them.
-There is no room for complacency.
-
 ```{r setup, include=FALSE}
@@
     warning = FALSE,
-    dpi = 300
+    dpi = 1000
 )
@@
 p_install(janitor, force = FALSE)
-p_install_gh(c("fsolt/DCPOtools", "sammo3182/drhutools"), force = FALSE)
+p_install_gh(c("fsolt/DCPOtools"), force = FALSE)
 
@@
     modelsummary,
-    drhutools, ## for colorful plots
     dotwhisker,
@@
 
-```{r data-input, include=FALSE, cache=TRUE, cache.extra = tools::md5sum(here::here("output", "estimates_moc_correctAJPS.RDS"))}
+It has long been argued that democratic regimes and public support for them are mutually reinforcing: that high levels of public support ensure democracies remain strong, and that experience with democratic governance generates robust public support [see, e.g., @Lipset1959a; @Easton1965].
+But the evidence for either part of this claim has been decidedly mixed.
+Countries with greater democratic support have been found to become stronger and more stable democracies [e.g., @InglehartWelzel2005a, pp.
+251-254] and just the opposite [@FailsPierce2010, pp.182-183].
+Similarly, studies have alternately found that more experience with democracy yields more democratic support [e.g., @FailsPierce2010, 183] or instead that long-established democracies are suffering from democratic fatigue [e.g., @FoaMounk2017].
+
+One important reason for these mixed results is the difficulty in measuring democratic support over time and across many countries.
+Public support for democracy cannot be directly observed, and its incorrect measurement will limit inferences about the relationships between public opinion and institutional development.
+Further, the survey data available across countries and over time on support for democracy---or indeed most topics in public opinion---are sparse and incomparable, greatly hindering broadly comparative research.
+Recent pioneering studies have sought to overcome the hurdle of sparse and incomparable data by developing latent variable measurement models of public opinion [see @CaugheyEtAl2019; @Claassen2019; @Solt2020a].
+A pair of prominent recent works took advantage of this latent variable approach to measure democratic support for over one hundred countries for up to nearly three decades and assess, respectively, its consequences for and roots in democratic change [@Claassen2020a; @Claassen2020].
+The first of these works concluded, supporting the classic argument, that mass support had a positive impact on democratic change, especially the endurance of democracy [@Claassen2020a, 127-130].
+The second directly contradicted the classic argument, concluding that democratic change has a thermostatic effect on public support, that is, that rather than generating its own support, deepening democracy provokes a backlash and it is instead democratic backsliding that calls forth greater public support [@Claassen2020, 46-50].
+
+The models employed in these studies' analyses, though, do not account for uncertainty in their measurement of democratic support.
+Because they are unobserved, latent variables are inherently accompanied by measurement uncertainty.
+To leave this uncertainty unacknowledged is to make the implausible assumption that the latent variables are measured perfectly, an assumption which distorts both statistical and substantive inference [see, e.g., @CrabtreeFariss2015].
+
+Here, we reexamine the classic arguments about support for democracy and democratic change tested in these two pieces while correcting this oversight.
+In addition to incorporating the measurement uncertainty, we also sought to reduce it by expanding considerably the survey data drawn upon and re-estimating democratic support for 144 countries for up to 33 years between 1988 and 2020.
+Our analyses reveal that the significant relationships between public support and democratic change disappear once measurement uncertainty is taken into account, both in replications with the studies' original data and in our extension analyses that incorporate additional data.
+That is, simply taking into account measurement uncertainty---making no change to the specification of the models---reveals there is no empirical support for either claim put forward in these two works: declining democratic support does not signal subsequent democratic backsliding, and changes in democracy do not spur a thermostatic response in democratic support.
+
+There are several important implications of these null results.
+They point to a need for closer attention to the conditional aspects of the classic theory [see @Lipset1959a, 86-89; @Easton1965, 119-20].
+On the one side, the effect of democracy on public support may depend not on its mere existence but on its effectiveness [see @Magalhaes2014] and particularly with regard to redistribution [see @KrieckhausEtAl2014].
+On the other, the impact of public support on democracy may depend on the extent to which those who support democracy are also dissatisfied with the current regime's performance [see @QiShin2011].
+Similarly, the results presented here are further evidence that the survey items commonly employed to measure democratic support are inadequate to the task.
+Because these questions contain no information on respondents' support for democracy relative to other values with which it may come into conflict [see, e.g., @GrahamSvolik2020; @SimonovitsEtAl2022] or on whether respondents even understand the meaning of the democracy they are claiming to support [see, e.g., @KirschWelzel2019; @WuttkeEtAl2020], these questions appear to miss capturing the true extent of the support among the public that democracy will actually find when public support is in fact most needed.
+Our results also reinforce arguments that relationships between democracy and public support unfold only over the long term [see, e.g., @WelzelEtAl2017] and that democratic change in the short term is instead best understood as an elite-driven phenomenon [see, e.g., @HaggardKaufman2021].
+
+We draw two conclusions, one methodological and one substantive.
+Many constructs in social science---from democracy to corruption to public opinion---are latent variables, and recent advances have made estimating them much more practicable.
+As latent variable measurement models become more commonly used, it is absolutely necessary for researchers employing them to incorporate the associated uncertainty into their analyses.
+As demonstrated here, this can be done straightforwardly using the method of composition [see @Tanner1993, p.52; @TreierJackman2008, p.215] without requiring any further change in model specification.
+
+And, at a time when democracy is seen as under threat around the world [e.g., @Diamond2015], taken together, Claassen [-@Claassen2020a; -@Claassen2020] send what is ultimately a reassuring message: the fate of democracy rests with us, the public, and when democratic institutions are undermined, we will swing to their support and constitute "an obstacle to democratic backsliding" [@Claassen2020, 51].
+Both of these assertions may well be true, but the evidence we have, properly assessed, does not support them.
+There is no room for complacency.
+
+```{r data-input, include=FALSE}
 ## Replication data
@@
 We proceed in three steps.
-First, we reproduce the original analyses of Claassen [-@Claassen2020a; -@Claassen2020b], which included only the point estimates of the latent variable of democratic support and so exclude its measurement uncertainty.
+First, we reproduce the original analyses of Claassen [-@Claassen2020a; -@Claassen2020], which included only the point estimates of the latent variable of democratic support and so exclude its measurement uncertainty.
 Second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.^[
-Additional details on this data replication process are found in Supplementary Information Appendix \@ref(dgp).]
-As democracy is also a latent variable in these analyses, we include the quantified uncertainty in its estimates as well, along with that for corruption in the models of @Claassen2020b.^[
+Additional details on this data replication process are found in the Online Supplementary Materials (OSM) \@ref(dgp).]
+As democracy is also a latent variable in these analyses, we include the quantified uncertainty in its estimates as well, along with that for corruption in the models of @Claassen2020.^[
 We also include the uncertainty in GDP per capita and resource dependence due to missing data by using multiple imputation rather than the single imputation employed in the original analyses.]
@@
 We attempted to make fuller use of the available survey data by employing the DCPO model [@Solt2020a], which unlike the @Claassen2019 model does not dichotomize ordinal responses.
-The better fit of the DCPO model to the data on democratic support [see @Solt2020a, 10-12] and the additional information it incorporates, however, did not yield substantively different results; see Supplementary Information Appendix \@ref(dcpo).]
+The better fit of the DCPO model to the data on democratic support [see @Solt2020a, 10-12] and the additional information it incorporates, however, did not yield substantively different results; see OSM \@ref(dcpo).]
 
@@
 
-Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion, latent variables are always estimated with a quantifiable amount of measurement error, and ignoring measurement error in analyses can attenuate, exaggerate, or even reverse coefficient estimates as well as bias standard errors [see, e.g., @Bound2001, 3709; @caughey2018, 254].
-In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey2018, 254].
+Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion, latent variables are always estimated with a quantifiable amount of measurement error, and ignoring measurement error in analyses can attenuate, exaggerate, or even reverse coefficient estimates as well as bias standard errors [see, e.g., @BoundEtAl2001, 3709; @CaugheyWarshaw2018a, 254].
+In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @SolisWaggoner2021, 18; @GandhiSumner2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @KastellecEtAl2015, 791-792; @CaugheyWarshaw2018a, 254].
 Therefore, after replicating the original analyses that use only the point estimates for public support and the other variables included in the model, we perform the analyses again only this time incorporating uncertainty in the articles' models using our replicated data.
@@
 In the analysis stage, uncertainty is incorporated through simulation based on the variance-covariance matrix of a model without requiring any change to its specification.
-This allows MOC to be broadly applicable adapt to many different types of models, including time-series-cross-sectional models [@caughey2018, A15-16], Cox proportional hazards models [@Treier2008, 215], or models of individual-level roll call voting [@Kastellec2015, 791].^[For additional details on the MOC technique, see Supplementary Information Appendix \@ref(moc).]
+This allows MOC to be broadly applicable adapt to many different types of models, including time-series-cross-sectional models [@CaugheyWarshaw2018a, A15-16], Cox proportional hazards models [@TreierJackman2008, 215], or models of individual-level roll call voting [@KastellecEtAl2015, 791].^[For additional details on the MOC technique, see  OSM \@ref(moc).]
 
@@
 
-To provide a further test of the classic arguments on democracy and public support, we generated estimates of democratic support using the same procedure as in Claassen [-@Claassen2020a; -@Claassen2020b] on a bigger data set, assembling as much survey data on democratic support as possible.
-We employed `r dcpo_input_ncyi` national opinions on democracy from `r dcpo_input_surv` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncy` opinions and `r supdem_surv` national surveys used in Claassen [-@Claassen2020a; -@Claassen2020b].^[
-These figures represent the survey data actually used in estimating public support for democracy; as in Claassen [-@Claassen2020a; -@Claassen2020b], countries for which two separate years of survey data were not available were excluded.]
+To provide a further test of the classic arguments on democracy and public support, we generated estimates of democratic support using the same procedure as in Claassen [-@Claassen2020a; -@Claassen2020] on a bigger data set, assembling as much survey data on democratic support as possible.
+We employed `r dcpo_input_ncyi` national opinions on democracy from `r dcpo_input_surv` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncy` opinions and `r supdem_surv` national surveys used in Claassen [-@Claassen2020a; -@Claassen2020].^[
+These figures represent the survey data actually used in estimating public support for democracy; as in Claassen [-@Claassen2020a; -@Claassen2020], countries for which two separate years of survey data were not available were excluded.]
 
@@
 
-Figure \@ref(fig:plot-fullAJPS) presents the reanalyses of the hypothesis that public support influences the level of democracy [@Claassen2020a, Table 1, 128].
+Figure \@ref(fig:plot-fullAJPS) presents the reanalyses of the hypothesis that public support influences the level of democracy [@Claassen2020a, Table 1].
 The lighter, lefthand set of results replicate the analysis of @Claassen2020a, including its exclusion of measurement uncertainty by using only the point estimates of public democratic support and the other variables measured with quantified error (i.e., democracy and corruption), and they reproduce that article's findings.
@@
 
-In Figure \@ref(fig:plot-fullAPSR), we examine the thermostatic model of democratic support per @Claassen2020b [47, Table 1, 49, Table 2].
+In Figure \@ref(fig:plot-fullAPSR), we examine the thermostatic model of democratic support per @Claassen2020 [47, Table 1, 49, Table 2].
 The negative coefficient estimates for change in liberal democracy in the lefthand set of results, which do not take uncertainty into account, imply that the immediate effect of a increase in the level of democracy is a decline in public support for democracy and of a decrease in democracy an expansion of support---that democratic support indeed does respond thermostatically to democracy.
@@
 
-In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that democratic support has a positive effect on democracy and change in democracy a negative effect on change in support are not empirically supported once measurement uncertainty is taken into account, even when more data are used.
+In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020] that democratic support has a positive effect on democracy and change in democracy a negative effect on change in support are not empirically supported once measurement uncertainty is taken into account, even when more data are used.
 
@@
 First, they underscore that it is crucial to recognize the conditional aspects of the classic theory regarding democracy and democratic support.
-With regard to how levels of democracy affect public support, even the early proponents of the classic argument did not contend that the mere existence of democratic institutions, no matter how consistently feckless and ineffective, would generate support among the public: instead, they maintained, public support would be gained through experience with government performance that was generally effective [@lipset_social_1959, 86-89; @Easton1965, 119-120].
+With regard to how levels of democracy affect public support, even the early proponents of the classic argument did not contend that the mere existence of democratic institutions, no matter how consistently feckless and ineffective, would generate support among the public: instead, they maintained, public support would be gained through experience with government performance that was generally effective [@Lipset1959a, 86-89; @Easton1965, 119-120].
 There is some empirical evidence for this, with government effectiveness positively related to public support among democracies and negatively related in non-democracies [@Magalhaes2014]. 
-The finding of @Krieckhaus2014 that income inequality is strongly negatively related to public support in democracies suggests that performance regarding redistribution is particularly important.
-On the reverse part of the classic argument, @Qi2011 suggests that democratic support alone cannot be expected to generate democratic change and oppose backsliding.
+The finding of @KrieckhausEtAl2014 that income inequality is strongly negatively related to public support in democracies suggests that performance regarding redistribution is particularly important.
+On the reverse part of the classic argument, @QiShin2011 suggests that democratic support alone cannot be expected to generate democratic change and oppose backsliding.
 Instead, that work contends, it is the combination of democratic support and dissatisfaction with current regime performance that generates demand for greater democracy.
@@
 Further, these results recommend building recent and more refined conceptualizations of democratic support into our measures.
-In other words, the survey items employed by Claassen [-@Claassen2020a; -@Claassen2020b]---which ask respondents to assess the desirability or appropriateness of democracy, to compare democracy to some undemocratic alternative, or to assess one of these alternatives---although often used by researchers, may not capture every aspect of democratic support necessary for it to play its hypothesized roles in the classic theory.
-One possibility is that only those who profess to prefer democracy to its alternatives _and also_ value freedom of expression, freedom of association, and pluralism of opinion will take appropriate action when democracy is threatened [see, e.g., @Schedler2007].
-Another is that respondents' other values, such as their policy preferences or partisanship, may weigh more heavily than their support for democracy: there is growing evidence that, at least in the United States, there are many for whom these other considerations excuse substantial transgressions against democracy [see @graham_democracy_2020; @McCoy2020].
+In other words, the survey items employed by Claassen [-@Claassen2020a; -@Claassen2020]---which ask respondents to assess the desirability or appropriateness of democracy, to compare democracy to some undemocratic alternative, or to assess one of these alternatives---although often used by researchers, may not capture every aspect of democratic support necessary for it to play its hypothesized roles in the classic theory.
+One possibility is that only those who profess to prefer democracy to its alternatives _and also_ value freedom of expression, freedom of association, and pluralism of opinion will take appropriate action when democracy is threatened [see, e.g., @SchedlerSarsfield2007].
+Another is that respondents' other values, such as their policy preferences or partisanship, may weigh more heavily than their support for democracy: there is growing evidence that, at least in the United States, there are many for whom these other considerations excuse substantial transgressions against democracy [see @GrahamSvolik2020; @SimonovitsEtAl2022].
 Yet another is that the answers to the above items reflect actual support for democracy only when respondents also either hold a robust understanding of what liberal democracy means or anchor their support in emancipative values of universal freedoms.
-If they do not, their positive responses to these items indicate support for autocracy instead [see, e.g., @Kirsch2019; @Wuttke2021].
-Taking any or all of these into account requires considering the _combination_ of attitudes: even the inclusion of additional questions in a unidimensional public opinion model such as that provided by @Claassen2019 will not be sufficient [see, e.g., @Wuttke2020].
+If they do not, their positive responses to these items indicate support for autocracy instead [see, e.g., @KirschWelzel2019; @WuttkeEtAl2022].
+Taking any or all of these into account requires considering the _combination_ of attitudes: even the inclusion of additional questions in a unidimensional public opinion model such as that provided by @Claassen2019 will not be sufficient [see, e.g., @WuttkeEtAl2020].
 
 Finally, by failing to provide evidence for a short-term relationship between democratic support and democracy, these null findings can be seen to lend additional support to other theories of regime change.
-There are compelling arguments that episodes of democratic transition [see, e.g., @ODonnell1986a] and backsliding [see, e.g., @Haggard2021] are best understood as products of elite decision making.
+There are compelling arguments that episodes of democratic transition [see, e.g., @ODonnellEtAl1986] and backsliding [see, e.g., @HaggardKaufman2021] are best understood as products of elite decision making.
 With regard to the latter, critics have charged that these claims overlook the extent of demand for authoritarian rule among the public [see, e.g., @Norris2021].
-The null results reported here, by finding that year-to-year changes in democratic support bear little relationship to changes in democracy, highlight that levels of public support appear to relate to regime only over the long run [see also @Welzel2017], leaving elite decisions as a powerful explanation for when and how short-term developments unfold.
+The null results reported here, by finding that year-to-year changes in democratic support bear little relationship to changes in democracy, highlight that levels of public support appear to relate to regime only over the long run [see also @WelzelEtAl2017], leaving elite decisions as a powerful explanation for when and how short-term developments unfold.
 
@@
 As the use of latent variables grows more common, political scientists should be aware that these variables' concomitant measurement uncertainty cannot be neglected.
-Recent cross-national time-series measures of, for example, policy ideology across Europe [developed in @Caughey2019], immigration attitudes in Europe [presented in @Claassen2022], and public gender egalitarianism worldwide [introduced in @Woo2022], make possible a host of previously infeasible analyses, but the resulting research cannot be considered robust if it does not also incorporate these measures' quantified uncertainty.
+Recent cross-national time-series measures of, for example, policy ideology across Europe [developed in @CaugheyEtAl2019], immigration attitudes in Europe [presented in @ClaassenMcLaren2021], and public gender egalitarianism worldwide [introduced in @WooEtAl2022], make possible a host of previously infeasible analyses, but the resulting research cannot be considered robust if it does not also incorporate these measures' quantified uncertainty.
 
@@
 They also draw attention to the conditional nature of the classic argument on democracy and democratic support as well as to challenges in measuring the concept of democratic support that remain unmet by existing time-series cross-sectional latent-variable models.
-Most importantly, the sanguine assessment that readers may draw from Claassen [-@Claassen2020a; -@Claassen2020b]---that the fate of democracies depend on public support, and when eroded, their publics will rally to them---is not supported by the current evidence.
+Most importantly, the sanguine assessment that readers may draw from Claassen [-@Claassen2020a; -@Claassen2020]---that the fate of democracies depend on public support, and when eroded, their publics will rally to them---is not supported by the current evidence.
 Those who would defend democracy have no grounds to be complacent.
@@
 
-# Online Supplementary Information Appendix {-}
+# Online Supplementary Materials {-}
 # (APPENDIX) Appendix {-}
@@
 
-Because the Dataverse replication files for @Claassen2020a and @Claassen2020b included only the point estimates of their variables, replicating those articles' analyses while incorporating the quantified uncertainty in their latent variables was not possible using only those files.
-Instead, it required re-collecting all of the data employed in those articles directly from their original sources, that is, in the terminology of @Grossman2020, it required a primary replication rather than a secondary one.
+Because the Dataverse replication files for @Claassen2020a and @Claassen2020 included only the point estimates of their variables, replicating those articles' analyses while incorporating the quantified uncertainty in their latent variables was not possible using only those files.
+Instead, it required re-collecting all of the data employed in those articles directly from their original sources, that is, in the terminology of @GrossmanPedahzur2021, it required a primary replication rather than a secondary one.
 We describe this process for the latent variables here.
@@
 First, for each item used in the two articles' measure of democratic support, we identified the original variable names and corresponding values in each survey dataset. 
-We then used the `dcpo_setup` and `format_claassen` functions of the `DCPOtools` R package [@Solt2019] to automate the process of generating a dataset of survey marginals.
+We then used the `dcpo_setup` and `format_claassen` functions of the `DCPOtools` R package [@SoltEtAl2019] to automate the process of generating a dataset of survey marginals.
 We encountered a number of miscodings in the original data that we corrected.
@@
 
-The democracy variables in the two articles are drawn from Version 8 of the V-Dem Dataset [@coppedge2018].
+The democracy variables in the two articles are drawn from Version 8 of the V-Dem Dataset [@CoppedgeEtAl2018].
 This version of the dataset includes draws from the posterior distribution of the estimates to quantify their uncertainty.
@@
 
-The corruption variable used in @Claassen2020b is the Corruption Perceptions Index, which provides point estimates and standard errors for the years from 2012 to 2018.
+The corruption variable used in @Claassen2020 is the Corruption Perceptions Index, which provides point estimates and standard errors for the years from 2012 to 2018.
 For country-years beyond that range, we conservatively estimated standard errors by first identifying the country's maximum relative standard error (standard error/point estimate) during 2012-2018 and then multiplying this quantity by the country-year's point estimate.
@@
 In our analysis models, we have latent variables in both sides of the equations: public democratic support, democracy, and corruption.
-Since measurement uncertainty associated with these latent variables can propagate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing the "Method of Composition" [@Tanner1993, 52], which has often been applied in analyses with latent variables in political science [see, e.g., @Treier2008; @Kastellec2015; @caughey2018].
-
-As @caughey2018 [A-15] explained, the main idea of MOC is to estimate the marginal distribution of coefficient parameter vector $\beta$, integrating over the uncertainty in latent variables $\theta$.
+Since measurement uncertainty associated with these latent variables can propagate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing the "Method of Composition" [@Tanner1993, 52], which has often been applied in analyses with latent variables in political science [see, e.g., @TreierJackman2008; @KastellecEtAl2015; @CaugheyWarshaw2018a].
+
+As @CaugheyWarshaw2018a [A-15] explained, the main idea of MOC is to estimate the marginal distribution of coefficient parameter vector $\beta$, integrating over the uncertainty in latent variables $\theta$.
 More explicitly, MOC integrates the joint density of $\beta$ and $\theta$ over the distribution of $\theta$.
@@
 where $\theta$ is latent variables with measurement errors conditional on data Z and a measurement model, $w$ is other predictors without errors, $Z$ is indicators for latent variables $\theta$, and $y$ is the outcome variable.
-In this way, we incorporate uncertainty in measuring predictor $\theta$, and uncertainty in the effects of latent variables $\theta$ and other variables $w$ on outcome variable $y$ [@Treier2008, 215].
-
-To sample from the conditional density and the marginal density in the right side of the equation, we follow iterative Monte Carlo procedure described by @Treier2008, at iteration $t$,
+In this way, we incorporate uncertainty in measuring predictor $\theta$, and uncertainty in the effects of latent variables $\theta$ and other variables $w$ on outcome variable $y$ [@TreierJackman2008, 215].
+
+To sample from the conditional density and the marginal density in the right side of the equation, we follow iterative Monte Carlo procedure described by @TreierJackman2008, at iteration $t$,
 
@@
 To make fuller use of the available survey data, we also replicated the tests of the classic arguments on democracy and public support using the DCPO model put forward in @Solt2020a on our expanded data set.
-The DCPO model has several advantages over the @Claassen2019 model used in Claassen [-@Claassen2020a; -@Claassen2020b].
-First, while the @Claassen2019 model dichotomizes responses and so discards some information provided by the 50 ordinal survey items (of 52 total) employed in Claassen [-@Claassen2020a; -@Claassen2020b], the DCPO model makes use of all of the information available from these ordinal items [@Solt2020a, p.5].
+The DCPO model has several advantages over the @Claassen2019 model used in Claassen [-@Claassen2020a; -@Claassen2020].
+First, while the @Claassen2019 model dichotomizes responses and so discards some information provided by the 50 ordinal survey items (of 52 total) employed in Claassen [-@Claassen2020a; -@Claassen2020], the DCPO model makes use of all of the information available from these ordinal items [@Solt2020a, p.5].
 Second, as the DCPO model includes both parameters for the dispersion of each survey item and for the standard deviation of aggregate public opinion in each country-year, it is a complete population-level item-response model and so, unlike the @Claassen2019 model, is explicitly derived from an individual-level model of survey responses [@Solt2020a, pp.3-4; see also @McGann2014].
-Third, to produce more sensible estimates of uncertainty for observations at the extremes of the scale [see @Linzer2015, 229], the DCPO model places bounds on its estimates of public opinion [@Solt2020a, 8].
+Third, to produce more sensible estimates of uncertainty for observations at the extremes of the scale [see @LinzerStaton2015a, 229], the DCPO model places bounds on its estimates of public opinion [@Solt2020a, 8].
 Further commending the DCPO model to us---and demonstrating that its advantages make a difference---the validation tests in @Solt2020a [pp.10-12] reveal that it fits survey data on democratic support better than the @Claassen2019 model does.
 
-We employ the superior DCPO model to our expanded dataset using the `DCPO` package for R [@Solt2020b].
+We employ the superior DCPO model to our expanded dataset using the `DCPO` package for R [@Solt2020].
 We then use the estimated public support from the DCPO model to replicate all of the analyses presented in the text.
@@
 
-Even with the advantages of the DCPO model, there is no evidence to support the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support sustains democratic regimes or that public support responds thermostatically to changes in democracy.
+Even with the advantages of the DCPO model, there is no evidence to support the conclusions of Claassen [-@Claassen2020a; -@Claassen2020] that public support sustains democratic regimes or that public support responds thermostatically to changes in democracy.
 

### 2022-02-19 paper/dcpo_demsupport.Rmd
clean up

@@
 In the analysis stage, uncertainty is incorporated through simulation based on the variance-covariance matrix of a model without requiring any change to its specification.
-This allows MOC to be broadly applicable adapt to many different types of models, including time-series-cross-sectional models [@CaugheyWarshaw2018a, A15-16], Cox proportional hazards models [@TreierJackman2008, 215], or models of individual-level roll call voting [@KastellecEtAl2015, 791].^[For additional details on the MOC technique, see  OSM \@ref(moc).]
+This allows MOC to be broadly applicable to many different types of models, including time-series-cross-sectional models [@CaugheyWarshaw2018a, A15-16], Cox proportional hazards models [@TreierJackman2008, 215], or models of individual-level roll call voting [@KastellecEtAl2015, 791].^[For additional details on the MOC technique, see  OSM \@ref(moc).]
 

### 2022-02-19 R/dcpo_input.R
format dcpo_input

@@ -1,0 +1,15 @@
+library(tidyverse)
+library(DCPOtools)
+
+# dcpo_input_raw <- DCPOtools::dcpo_setup(vars = read_csv(here::here("data-raw", "mood_dem.csv"),
+#                                                         col_types = "cccccc"),
+#                                         file = "data/dcpo_input_raw.csv")
+
+dcpo_input_raw1 <- read_csv(here::here("data", "dcpo_input_raw.csv"), 
+                            col_types = "cdcddcd") %>%
+                            with_min_yrs(2)
+
+dcpo_input_update22 <- DCPOtools::format_dcpo(dcpo_input_raw1,
+                                              scale_q = "church_wvs",
+                                              scale_cp = 2)
+save(dcpo_input_update22, file = here::here("data", "dcpo_input_update22.rda"))

### 2022-02-22 paper/dcpo_demsupport.Rmd
prepare for merging

@@
   | and Measurement Uncertainty
-# thanks: "The authors contributed equally to this work.  Corresponding author: [yuehu@mail.tsinghua.edu.cn](mailto:yuehu@mail.tsinghua.edu.cn).  Current version: `r format(Sys.time(), '%B %d, %Y')`."
-
-# author:
-# - name: Yuehong 'Cassandra' Tai
-#   affiliation: University of Iowa
-# - name: Yue Hu
-#   affiliation: Tsinghua University
-# - name: Frederick Solt
-#   affiliation: University of Iowa
-
-abstract: "Do democratic regimes depend on public support to avoid backsliding?
+
+# abstract: "Do democratic regimes depend on public support to avoid backsliding?
 Does public support, in turn, respond thermostatically to changes in democracy?
@@
 [147/150 words]"
-keywords: "Democratization, public support, regime survival, measurement uncertainty, latent variables."
+# keywords: "Democratization, public support, regime survival, measurement uncertainty, latent variables."
 
@@
 
+# Authors {-}
+
+- Yuehong 'Cassandra' Tai, Ph.D. Candidate, Department of Political Science, University of Iowa, yuehong-tai@uiowa.edu.
+- Yue Hu, corresponding author, ORCID: https://orcid.org/0000-0002-2829-3971, Associate Professor, Department of Political Science, Tsinghua University, yuehu@tsinghua.edu.cn
+- Frederick Solt, ORCID: https://orcid.org/0000-0002-3154-6132, Associate Professor, Department of Political Science, University of Iowa, frederick-solt@uiowa.edu."
+
+# Acknowledgement {-}
+
+The three authors contributed equally to this work. 
+We thank the editors and anonymous reviewers for their helpful comments. 
+All errors remain our own.
+
+# Funding {-}
+Yue Hu acknowledges the support from the National Natural Science Foundation of China (Grant No. 72004109).
+
+\pagebreak
+
+# Abstract {-}
+
+Do democratic regimes depend on public support to avoid backsliding?
+Does public support, in turn, respond thermostatically to changes in democracy?
+Two prominent recent studies (Claassen 2020a, 2020b) reinvigorated the classic hypothesis on the positive relationship between public support for democracy and regime survival---and challenged its reciprocal counterpart---by using a latent variable approach to measure mass democratic support from cross-national survey data.
+Both studies, however, used only the point estimates of democratic support; we show that incorporating the concomitant measurement uncertainty into these analyses reveals that there is no support for either study's conclusion.
+Efforts to minimize the uncertainty by incorporating additional survey data still fail to yield evidence in support of either hypothesis.
+These results underscore the need both for more nuanced analyses of the relationships between public support and democracy and for taking measurement uncertainty into account when working with latent variables.
+
+\pagebreak
+
 ```{r setup, include=FALSE}
@@
 251-254] and just the opposite [@FailsPierce2010, pp.182-183].
-Similarly, studies have alternately found that more experience with democracy yields more democratic support [e.g., @FailsPierce2010, 183] or instead that long-established democracies are suffering from democratic fatigue [e.g., @FoaMounk2017].
+Similarly, studies have alternately found that more experience with democracy yields more democratic support [e.g., @FailsPierce2010, p.
+183] or instead that long-established democracies are suffering from democratic fatigue [e.g., @FoaMounk2017].
 
@@
 A pair of prominent recent works took advantage of this latent variable approach to measure democratic support for over one hundred countries for up to nearly three decades and assess, respectively, its consequences for and roots in democratic change [@Claassen2020a; @Claassen2020].
-The first of these works concluded, supporting the classic argument, that mass support had a positive impact on democratic change, especially the endurance of democracy [@Claassen2020a, 127-130].
-The second directly contradicted the classic argument, concluding that democratic change has a thermostatic effect on public support, that is, that rather than generating its own support, deepening democracy provokes a backlash and it is instead democratic backsliding that calls forth greater public support [@Claassen2020, 46-50].
+The first of these works concluded, supporting the classic argument, that mass support had a positive impact on democratic change, especially the endurance of democracy [@Claassen2020a, pp.
+127-130].
+The second directly contradicted the classic argument, concluding that democratic change has a thermostatic effect on public support, that is, that rather than generating its own support, deepening democracy provokes a backlash and it is instead democratic backsliding that calls forth greater public support [@Claassen2020, pp.
+46-50].
 
@@
 There are several important implications of these null results.
-They point to a need for closer attention to the conditional aspects of the classic theory [see @Lipset1959a, 86-89; @Easton1965, 119-20].
+They point to a need for closer attention to the conditional aspects of the classic theory [see @Lipset1959a, pp. 86-89; @Easton1965, pp. 119-20].
 On the one side, the effect of democracy on public support may depend not on its mere existence but on its effectiveness [see @Magalhaes2014] and particularly with regard to redistribution [see @KrieckhausEtAl2014].
@@
 
-And, at a time when democracy is seen as under threat around the world [e.g., @Diamond2015], taken together, Claassen [-@Claassen2020a; -@Claassen2020] send what is ultimately a reassuring message: the fate of democracy rests with us, the public, and when democratic institutions are undermined, we will swing to their support and constitute "an obstacle to democratic backsliding" [@Claassen2020, 51].
+And, at a time when democracy is seen as under threat around the world [e.g., @Diamond2015], taken together, Claassen [-@Claassen2020a; -@Claassen2020] send what is ultimately a reassuring message: the fate of democracy rests with us, the public, and when democratic institutions are undermined, we will swing to their support and constitute "an obstacle to democratic backsliding" [@Claassen2020, p.
+51].
 Both of these assertions may well be true, but the evidence we have, properly assessed, does not support them.
@@
 
-Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion, latent variables are always estimated with a quantifiable amount of measurement error, and ignoring measurement error in analyses can attenuate, exaggerate, or even reverse coefficient estimates as well as bias standard errors [see, e.g., @BoundEtAl2001, 3709; @CaugheyWarshaw2018a, 254].
-In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @SolisWaggoner2021, 18; @GandhiSumner2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @KastellecEtAl2015, 791-792; @CaugheyWarshaw2018a, 254].
+Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion, latent variables are always estimated with a quantifiable amount of measurement error, and ignoring measurement error in analyses can attenuate, exaggerate, or even reverse coefficient estimates as well as bias standard errors [see, e.g., @BoundEtAl2001, p.
+3709; @CaugheyWarshaw2018a, p.
+254].
+In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @SolisWaggoner2021, p.
+18; @GandhiSumner2020, p.
+1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @KastellecEtAl2015, pp.
+791-792; @CaugheyWarshaw2018a, p.
+254].
 Therefore, after replicating the original analyses that use only the point estimates for public support and the other variables included in the model, we perform the analyses again only this time incorporating uncertainty in the articles' models using our replicated data.
-We conduct inferences from the distributive data via the technique known as the "method of composition"  [MOC, @Tanner1993, 52].
+We conduct inferences from the distributive data via the technique known as the "method of composition"  [MOC, @Tanner1993, p. 52].
 MOC accounts for uncertainty from opinion estimates and analysis models through each modeling stage.
 In the analysis stage, uncertainty is incorporated through simulation based on the variance-covariance matrix of a model without requiring any change to its specification.
-This allows MOC to be broadly applicable to many different types of models, including time-series-cross-sectional models [@CaugheyWarshaw2018a, A15-16], Cox proportional hazards models [@TreierJackman2008, 215], or models of individual-level roll call voting [@KastellecEtAl2015, 791].^[For additional details on the MOC technique, see  OSM \@ref(moc).]
+This allows MOC to be broadly applicable to many different types of models, including time-series-cross-sectional models [@CaugheyWarshaw2018a, p.
+A15-16], Cox proportional hazards models [@TreierJackman2008, p.
+215], or models of individual-level roll call voting [@KastellecEtAl2015, p.
+791].^[For additional details on the MOC technique, see  OSM \@ref(moc).]
 
@@
 
-In Figure \@ref(fig:plot-fullAPSR), we examine the thermostatic model of democratic support per @Claassen2020 [47, Table 1, 49, Table 2].
+In Figure \@ref(fig:plot-fullAPSR), we examine the thermostatic model of democratic support per @Claassen2020 [p. 47, Table 1, 49, Table 2].
 The negative coefficient estimates for change in liberal democracy in the lefthand set of results, which do not take uncertainty into account, imply that the immediate effect of a increase in the level of democracy is a decline in public support for democracy and of a decrease in democracy an expansion of support---that democratic support indeed does respond thermostatically to democracy.
@@
 First, they underscore that it is crucial to recognize the conditional aspects of the classic theory regarding democracy and democratic support.
-With regard to how levels of democracy affect public support, even the early proponents of the classic argument did not contend that the mere existence of democratic institutions, no matter how consistently feckless and ineffective, would generate support among the public: instead, they maintained, public support would be gained through experience with government performance that was generally effective [@Lipset1959a, 86-89; @Easton1965, 119-120].
+With regard to how levels of democracy affect public support, even the early proponents of the classic argument did not contend that the mere existence of democratic institutions, no matter how consistently feckless and ineffective, would generate support among the public: instead, they maintained, public support would be gained through experience with government performance that was generally effective [@Lipset1959a, pp.
+86-89; @Easton1965, pp.
+119-120].
 There is some empirical evidence for this, with government effectiveness positively related to public support among democracies and negatively related in non-democracies [@Magalhaes2014]. 
@@
 In our analysis models, we have latent variables in both sides of the equations: public democratic support, democracy, and corruption.
-Since measurement uncertainty associated with these latent variables can propagate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing the "Method of Composition" [@Tanner1993, 52], which has often been applied in analyses with latent variables in political science [see, e.g., @TreierJackman2008; @KastellecEtAl2015; @CaugheyWarshaw2018a].
-
-As @CaugheyWarshaw2018a [A-15] explained, the main idea of MOC is to estimate the marginal distribution of coefficient parameter vector $\beta$, integrating over the uncertainty in latent variables $\theta$.
+Since measurement uncertainty associated with these latent variables can propagate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing the "Method of Composition" [@Tanner1993, p.
+52], which has often been applied in analyses with latent variables in political science [see, e.g., @TreierJackman2008; @KastellecEtAl2015; @CaugheyWarshaw2018a].
+
+As @CaugheyWarshaw2018a [p.
+A-15] explained, the main idea of MOC is to estimate the marginal distribution of coefficient parameter vector $\beta$, integrating over the uncertainty in latent variables $\theta$.
 More explicitly, MOC integrates the joint density of $\beta$ and $\theta$ over the distribution of $\theta$.
@@
 where $\theta$ is latent variables with measurement errors conditional on data Z and a measurement model, $w$ is other predictors without errors, $Z$ is indicators for latent variables $\theta$, and $y$ is the outcome variable.
-In this way, we incorporate uncertainty in measuring predictor $\theta$, and uncertainty in the effects of latent variables $\theta$ and other variables $w$ on outcome variable $y$ [@TreierJackman2008, 215].
+In this way, we incorporate uncertainty in measuring predictor $\theta$, and uncertainty in the effects of latent variables $\theta$ and other variables $w$ on outcome variable $y$ [@TreierJackman2008, p.
+215].
 
@@
 First, while the @Claassen2019 model dichotomizes responses and so discards some information provided by the 50 ordinal survey items (of 52 total) employed in Claassen [-@Claassen2020a; -@Claassen2020], the DCPO model makes use of all of the information available from these ordinal items [@Solt2020a, p.5].
-Second, as the DCPO model includes both parameters for the dispersion of each survey item and for the standard deviation of aggregate public opinion in each country-year, it is a complete population-level item-response model and so, unlike the @Claassen2019 model, is explicitly derived from an individual-level model of survey responses [@Solt2020a, pp.3-4; see also @McGann2014].
-Third, to produce more sensible estimates of uncertainty for observations at the extremes of the scale [see @LinzerStaton2015a, 229], the DCPO model places bounds on its estimates of public opinion [@Solt2020a, 8].
-Further commending the DCPO model to us---and demonstrating that its advantages make a difference---the validation tests in @Solt2020a [pp.10-12] reveal that it fits survey data on democratic support better than the @Claassen2019 model does.
+Second, as the DCPO model includes both parameters for the dispersion of each survey item and for the standard deviation of aggregate public opinion in each country-year, it is a complete population-level item-response model and so, unlike the @Claassen2019 model, is explicitly derived from an individual-level model of survey responses [@Solt2020a, pp.
+3-4; see also @McGann2014].
+Third, to produce more sensible estimates of uncertainty for observations at the extremes of the scale [see @LinzerStaton2015a, p.
+229], the DCPO model places bounds on its estimates of public opinion [@Solt2020a, p.
+8].
+Further commending the DCPO model to us---and demonstrating that its advantages make a difference---the validation tests in @Solt2020a [pp.
+10-12] reveal that it fits survey data on democratic support better than the @Claassen2019 model does.
 
@@
 <div id = 'refs_app'></div>
+
+\pagebreak
+
+# Declarations {-}
+
+The authors affirm this research did not involve human subjects.
+
+The authors declare no ethical issues or conflicts of interest in this research.
+Yue Hu was funded by the National Natural Science Foundation of China (Grant No. 72004109).
+
+Research documentation and data that support the findings of this study are openly available in the APSR Dataverse at [DOI].

### 2022-02-23 R/argon/dcpo_demsupport/R/processing.R
use `iter <- 2000`

@@ -6,7 +6,7 @@ download.file("https://github.com/fsolt/dcpo_dem_mood/raw/master/data/dcpo_input
 
 load("data/dcpo_input.rda")
 
-iter <- 3000
+iter <- 2000
 
 dcpo_output <- dcpo(dcpo_input,
                     iter = iter,

### 2022-02-23 R/argon/dcpo_demsupport/R/processing.R
update to use `dcpo_input_update22.rda` 😬

@@ -2,9 +2,10 @@ library(tidyverse)
 if (!require("DCPO")) install.packages("DCPO", repos = "https://cloud.r-project.org/"); library(DCPO)
 
 
-download.file("https://github.com/fsolt/dcpo_dem_mood/raw/master/data/dcpo_input.rda", "data/dcpo_input.rda")
+download.file("https://github.com/fsolt/dcpo_dem_mood/raw/master/data/dcpo_input_update22.rda", "data/dcpo_input.rda")
 
 load("data/dcpo_input.rda")
+dcpo_input <- dcpo_input_update22
 
 iter <- 2000
 

### 2022-02-23 R/analysisData.R
update codes for creating analysis data

@@ -1,6 +1,24 @@
+
+#### R version 4.1.1 (2021-08-10)
+###  Input Data:claassen_m5_3k_07-27-15-40.rda, claassen_replication_input
+###             cls_libdem_list.rda,  cls_poly_list.rda,cls_liberal_list.rda   
+###             cls_cntrl.rda
+###             exp_claassen_m5_3k_07-23-10-50.rda, exp_claassen_input.rda
+###             libdem_list.rda, poly_list.rda, lib_list.rda 
+###             exp_cntrl.rda      
+###             dcpo_cntrl.rda
+###             vdem8_regime.rda,vdem10_regime.rda
+###             country_regionUN.rda
+###             cpi_list
+###  Output Data:     
+###             correct_cls_theta_list,    correct_cls_ajps.rda,correct_cls_apsr.rda
+###             expcor_cls_theta_list.rda, expcor_cls_ajps.rda, expcor_cls_apsr.rda 
+###             dcpo_theta_list.rda, dcpo_ajps.rda, dcpo_apsr.rda
+                         
+
+###Load packages
 if (!require(pacman)) install.packages("pacman")
 library(pacman)
-# load all the packages you will use below 
 p_load(
     here,
     purrr,
@@ -10,12 +28,7 @@ p_load(
     osfr
 )
 
-osf_retrieve_file("uvn4g") %>%
-    osf_download(here::here("data"))  ##claassen_m5_3k_07-27-15-40.rda
-
-
-# Functions preload
-set.seed(313)
+###Load Function
 reformat_dcpo_output <- function(x, parameter_name) {
     df_temp <- x %>% 
         as_tibble(.name_repair = ~ls_country) %>% 
@@ -28,13 +41,17 @@ reformat_dcpo_output <- function(x, parameter_name) {
 }
 
 
+set.seed(313)
+
+
 ####################################################
 ################Creating Correct Data ##############
 ####################################################
 
 
 ######Creating Correct_theta_list################
-
+osf_retrieve_file("uvn4g") %>%
+    osf_download(here::here("data"))  ##claassen_m5_3k_07-27-15-40.rda
 load(here("data", "claassen_m5_3k_07-27-15-40.rda")) 
 load(here::here("data","claassen_replication_input.rda"))
[…]

### 2022-02-24 paper/dcpo_demsupport.Rmd
update dcpo

@@
 
-- Yuehong 'Cassandra' Tai, Ph.D. Candidate, Department of Political Science, University of Iowa, yuehong-tai@uiowa.edu.
+- Yuehong 'Cassandra' Tai, ORCID: https://orcid.org/0000-0001-7303-7443, Ph.D. Candidate, Department of Political Science, University of Iowa, yuehong-tai@uiowa.edu.
 - Yue Hu, corresponding author, ORCID: https://orcid.org/0000-0002-2829-3971, Associate Professor, Department of Political Science, Tsinghua University, yuehu@tsinghua.edu.cn
@@
 
+```{r dcpodata-input, include=FALSE}
+## Replication data
+load(here("data", "dcpo_ajps.rda"))  # https://osf.io/xxxx/download
+load(here("data", "dcpo_apsr.rda"))  # https://osf.io/xxxx/download
+load(here("data", "dcpo_input_update22.rda"))  # https://osf.io/xxxx/download
+
+## Preloading chunk-produced results to speed up the compiling
+## One can find how they were created by locating the corresponding chunks
+
+mocdcpo_APSR <- readRDS(here("output", "estimates_moc_dcpoAPSR.RDS"))
+mocresult_dcpoAJPS <-
+    readRDS(here("output", "estimates_moc_dcpoAJPS.RDS"))
+```
+
 ```{r dcpo-AJPS, eval=FALSE}
@@
     dcpo_ajps[[anEntry]] %>%
-        plm::pdata.frame(index = c("country", "year")) %>%
-        rename(
-            SupDem_trim = theta_trim,
-            Regime_VD = Vdem_regime,
-            Pr_Muslim = muslism_prop_2010,
-            Res_cp_WDI_di = dependence_pc_di,
-            lnGDP_imp = lg_imp_mdpgdp,
-            GDP_imp_grth = mdprgdp_grwth,
-            firstyear = first_year,
-            Libdem_VD = Vdem_libdem,
-            Libdem_m1 = Vdem_libdem_m1,
-            Libdem_m2 = Vdem_libdem_m2,
-            ChgDem = Chgdem,
-            UpChgDem = upchgdem,
-            DwnChgDem = downchgdem,
-            Libdem_regUN = Region_libdem,
-            Libdem_regUN_m1 = Region_libdem_m1
-        )
+        plm::pdata.frame(index = c("country", "year")) 
 })
@@
     dcpo_apsr[[anEntry]] %>%
-        plm::pdata.frame(index = c("country", "year")) %>%
-        rename(
-            SupDem_trim = theta_trim,
-            First_yr = first_year,
-            Libdem_z = Vdem_libdem_z,
-            Polyarchy_z = Vdem_polyarchy_z,
-            Liberal_z = Vdem_liberal_z,
-            Corrup_TI_z = corruption_z,
-            lnGDP_imp = lg_imp_mdpgdp
-        )
+        plm::pdata.frame(index = c("country", "year")) 
 })

### 2022-02-24 R/argon/dcpo_demsupport_cls_exp/R/exp_claassen_m5.sh
add dcpo_demsupport_cls_exp

@@ -1,0 +1,4 @@
+#!/bin/sh
+
+module load R/3.5.1_gcc-5.4.0
+Rscript R/exp_claassen_m5.R

### 2022-02-26 R/analysisData.R
combining vdem_control, control and analysisData.R

@@ -1,19 +1,38 @@
-
 #### R version 4.1.1 (2021-08-10)
-###  Input Data:claassen_m5_3k_07-27-15-40.rda, claassen_replication_input
-###             cls_libdem_list.rda,  cls_poly_list.rda,cls_liberal_list.rda   
-###             cls_cntrl.rda
-###             exp_claassen_m5_3k_07-23-10-50.rda, exp_claassen_input.rda
-###             libdem_list.rda, poly_list.rda, lib_list.rda 
-###             exp_cntrl.rda      
-###             dcpo_cntrl.rda
-###             vdem8_regime.rda,vdem10_regime.rda
-###             country_regionUN.rda
-###             cpi_list
-###  Output Data:     
-###             correct_cls_theta_list,    correct_cls_ajps.rda,correct_cls_apsr.rda
-###             expcor_cls_theta_list.rda, expcor_cls_ajps.rda, expcor_cls_apsr.rda 
-###             dcpo_theta_list.rda, dcpo_ajps.rda, dcpo_apsr.rda
+#### Input Data: raw_data_controls.RData which includes 
+####             vdem8_post            Vdem8 with posterior distribution from The Varieties of Democracy Project
+####             vdem10_1985           Vdem10 with standard errors from The Varieties of Democracy Project
+####             cpi_95_19_error       from Corruption Perception Index 
+####             muslism_prop_2010     from http://globalreligiousfutures.org/
+####             WDIData               from World Development Indicators 
+####             resource_dep          from Haber and Menaldo (2011) 
+####             WEOApr2020all         from IMF 
+####             pwt100                from World Table Penn World Table Version.10. 
+####             country_regionUN      
+
+####             Data for Measures of Public Support: 
+####             claassen_replication_input.rda  
+####             exp_claassen_input.rda
+####             exp_dcpo_input.rda
+####             claassen_replication_output.rda
+####             exp_claassen_output.rda
+####             exp_dcpo_output.rda
+
+
+####  Output Data:
+####             vdem8_1985_post.rds       V-Dem8
+####             vdem10_1985_post.rds      V-Dem10
[…]

### 2022-02-26 paper/dcpo_demsupport.Rmd
citation updated, #36

--- 2022-02-22 paper/dcpo_demsupport.Rmd
@@
 
-- Yuehong 'Cassandra' Tai, Ph.D. Candidate, Department of Political Science, University of Iowa, yuehong-tai@uiowa.edu.
+- Yuehong 'Cassandra' Tai, ORCID: https://orcid.org/0000-0001-7303-7443, Ph.D. Candidate, Department of Political Science, University of Iowa, yuehong-tai@uiowa.edu.
 - Yue Hu, corresponding author, ORCID: https://orcid.org/0000-0002-2829-3971, Associate Professor, Department of Political Science, Tsinghua University, yuehu@tsinghua.edu.cn
-- Frederick Solt, ORCID: https://orcid.org/0000-0002-3154-6132, Associate Professor, Department of Political Science, University of Iowa, frederick-solt@uiowa.edu."
+- Frederick Solt, ORCID: https://orcid.org/0000-0002-3154-6132, Associate Professor, Department of Political Science, University of Iowa, frederick-solt@uiowa.edu.
 
@@
 All errors remain our own.
+Replication files are available at the American Political
+Science Review Dataverse: https://doi.org/XXXX.
 
@@
 p_load(
+    # data
+    dataverse,
+
     # analysis
@@
 
-    # data wrangling
+    # wrangling
     here,
@@
     glue)
+
+Sys.setenv("DATAVERSE_SERVER" = "dataverse.harvard.edu")
 
@@
 ```{r compare_n}
-
-# if (!file.exists(here::here("data", "supdem raw survey marginals.tab"))) {
-#   dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>% 
-#     read_csv(col_types = "cdcddcdc") %>% 
-#     write_csv("data/supdem raw survey marginals.tab")
-# }
-
-supdem <- read_csv(here::here("data", "supdem raw survey marginals.tab"),
+if (!file.exists(here("data", "supdem raw survey marginals.tab"))) {
+  dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>%
+    read_csv(col_types = "cdcddcdc") %>%
+    write_csv("data/supdem raw survey marginals.tab")
+}
+
+supdem <- read_csv(here("data", "supdem raw survey marginals.tab"),
                    col_types = "cdcddcdc") %>% 
@@
 ```{r pointAJPS}
+if (!file.exists(here("data", "Support_democracy_ajps.csv"))) {
+  get_file_by_doi(filedoi = "10.7910/DVN/HWLW0J/MVXNFC") %>%
+    read_csv(col_types = "cdcddcdc") %>%
+    write_csv(here("data", "Support_democracy_ajps.csv"))
+}
+
 supdem <- read.csv(here("data", "Support_democracy_ajps.csv"))
@@
 # Reusing the sd.plm object, thus input data here rather than earlier
+if (!file.exists(here("data", "dem_mood_apsr.RData"))) {
+  get_dataframe_by_doi(filedoi = "10.7910/DVN/FECIO3/ACMGQG") %>%
+    save(file = here("data", "dem_mood_apsr.RData"))
+}
 
@@
 
-Research documentation and data that support the findings of this study are openly available in the APSR Dataverse at [DOI].
+Research documentation and data that support the findings of this study are openly available in the APSR Dataverse at https://doi.org/XXXX.

### 2022-02-27 R/argon/dcpo_demsupport/R/claassen_m5.R
clean files for measurement

@@ -1,25 +1,0 @@
-library(tidyverse)
-library(rstan)
-
-download.file("https://github.com/fsolt/dcpo_dem_mood/raw/master/data/claassen_input.rda", "data/claassen_input.rda")
-
-load("data/claassen_input.rda")
-
-iter <- 3000
-
-claassen_m5 <- stan(file = 'R/supdem.stan.mod5.stan',
-                    data = claassen_input,
-                    iter = iter,
-                    chains= 4,
-                    cores = 4,
-                    thin = iter/500,
-                    pars = c("mu_lambda","sigma_lambda","sigma_delta","sigma_theta","phi","lambda","delta","theta",
-                             "x_pred","log_lik"),
-                    control = list(adapt_delta=0.99, stepsize=0.02, max_treedepth=11))
-
-save(claassen_input, claassen_m5,
-     file = str_c("data/claassen_m5_", round(iter/1000), "k_",
-                  str_replace_all(Sys.time(), "[ :]", "-") %>%
-                      str_replace("20\\d{2}-", "") %>%
-                      str_replace("-\\d{2}$", ""),
-                  ".rda"))

### 2022-02-27 R/argon/dcpo_demsupport/R/processing.R

@@ -1,23 +1,0 @@
-library(tidyverse)
-if (!require("DCPO")) install.packages("DCPO", repos = "https://cloud.r-project.org/"); library(DCPO)
-
-
-download.file("https://github.com/fsolt/dcpo_dem_mood/raw/master/data/dcpo_input_update22.rda", "data/dcpo_input.rda")
-
-load("data/dcpo_input.rda")
-dcpo_input <- dcpo_input_update22
-
-iter <- 2000
-
-dcpo_output <- dcpo(dcpo_input,
-                    iter = iter,
-                    chains = 4,
-                    thin = iter/500, # this yields 250 draws per chain, 1000 draws total
-                    pars = c("sd_delta","sd_theta_evolve", "sd_sigma_evolve", "sigma","phi","beta","alpha","delta","theta","y_r_pred","log_lik"))
-
-save(dcpo_input, dcpo_output,
-     file = str_c("data/church_lb2_", round(iter/1000), "k_",
-                  str_replace_all(Sys.time(), "[ :]", "-") %>%
-                      str_replace("20\\d{2}-", "") %>%
-                      str_replace("-\\d{2}$", ""),
-                  ".rda"))

### 2022-02-27 R/argon/dcpo_demsupport/R/processing_con.R

@@ -1,22 +1,0 @@
-library(tidyverse)
-if (!require("DCPO")) install.packages("DCPO", repos = "https://cloud.r-project.org/"); library(DCPO)
-
-
-download.file("https://github.com/fsolt/dcpo_dem_mood/raw/master/data/dcpo_input_con.rda", "data/dcpo_input_con.rda")
-
-load("data/dcpo_input_con.rda")
-
-iter <- 3000
-
-dcpo_output_con <- dcpo(dcpo_input_con,
-                    iter = iter,
-                    chains = 4,
-                    thin = iter/500,
-                    pars = c("sd_delta","sd_theta_evolve", "sd_sigma_evolve", "sigma","phi","beta","alpha","delta","theta","y_r_pred","log_lik"))
-
-save(dcpo_input_con, dcpo_output_con,
-     file = str_c("data/church4_", round(iter/1000), "k_",
-                  str_replace_all(Sys.time(), "[ :]", "-") %>%
-                      str_replace("20\\d{2}-", "") %>%
-                      str_replace("-\\d{2}$", ""),
-                  ".rda"))

### 2022-02-27 R/argon/dcpo_demsupport/R/processing_con.sh

@@ -1,4 +1,0 @@
-#!/bin/sh
-
-module load R/3.5.1_gcc-5.4.0
-Rscript R/processing_con.R

### 2022-02-27 R/argon/dcpo_demsupport/R/claassen_m5_rep.R
combine dcposetup files and stan files

@@ -1,0 +1,236 @@
+##### Working Environment ####
+## The script for creating output was run on the University of Iowa's high-performance computing cluster.
+## The working environment requires R version 3.5.1,Rcpp_1.0.0, and rstan_2.18.2. 
+
+library(tidyverse)
+library(rstan)
+library(DCPOtools)
+
+# Creating claassen_replication_input
+
+# Note that to setup input raw data, one needs raw survey datasets.
+# See details at https://github.com/fsolt/DCPOtools
+
+# claassen_input_raw <- DCPOtools:::claassen_setup(vars = read_csv(here::here("data-raw", "mood_dem.csv"),
+#                                                                 col_types = "cccccc"),
+#                                                 file = "data/claassen_input_raw.csv")
+
+# dcpo_input_raw <- DCPOtools::dcpo_setup(vars = read_csv(here::here("data-raw", "mood_dem.csv"),
+#                                                         col_types = "cccccc"),
+#                                         file = "data/dcpo_input_raw.csv")
+
+dcpo_input_raw1 <- read_csv(here::here("data", "dcpo_input_raw.csv"), col_types = "cdcddcd") %>% 
+    filter(!(str_detect(survey, "army_wvs") & # WVS obs identified as problematic by Claassen 
+                 ((country=="Albania" & year==1998) |
+                      (country=="Indonesia" & (year==2001 | year==2006)) |
+                      (country=="Iran" & year==2000) |
+                      (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
+                      (country=="Vietnam" & year==2001)) |
+                 (str_detect(item, "strong_wvs") &
+                      ((country=="Egypt" & year==2012) |
+                           (country=="Iran" & (year==2000 | year==2007)) | # 2005 in Claassen
+                           (country=="India") |
+                           (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
+                           (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
+                           (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
+                           (country=="Vietnam" & year==2001))) |
+                 (country %in% c("Puerto Rico", "Northern Ireland", 
+                                 "SrpSka Republic", "Hong Kong SAR China")))) %>%
+    with_min_yrs(2)
+
[…]

### 2022-02-27 R/argon/dcpo_demsupport/R/exp_claassen_m5.R

@@ -1,0 +1,63 @@
+##### Working Environment ####
+## The script for creating output was run on the University of Iowa's high-performance computing cluster.
+## The working environment requires R version 3.5.1,Rcpp_1.0.0, and rstan_2.18.2. 
+
+library(tidyverse)
+library(rstan)
+library(DCPOtools)
+
+
+# Creating exp_claassen_input by using expanded data
+# Note that to setup input raw data, one needs raw survey datasets.
+# See details at https://github.com/fsolt/DCPOtools
+
+
+# claassen_input_raw <- DCPOtools:::claassen_setup(vars = read_csv(here::here("data-raw", "mood_dem.csv"),
+#                                                                  col_types = "cccccc"),
+#                                                  file = "data/claassen_input_raw.csv") 
+#Note that claassen_input_raw.csv should be in data folder if one run claassen_m5_rep.R first.
+
+claassen_input_raw <- read_csv(here::here("data", "claassen_input_raw.csv"),
+                               col_types = "cdcddcd")
+
+claassen_input_raw1 <- claassen_input_raw %>% 
+    filter(!((str_detect(item, "army_wvs") & # WVS obs identified as problematic by Claassen 
+                  ((country=="Albania" & year==1998) |
+                       (country=="Indonesia" & (year==2001 | year==2006)) |
+                       (country=="Iran" & year==2000) |
+                       (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
+                       (country=="Vietnam" & year==2001))) |
+                 (str_detect(item, "strong_wvs") &
+                      ((country=="Egypt" & year==2012) |
+                           (country=="Iran" & (year==2000 | year==2007)) | # 2005 in Claassen
+                           (country=="India") |
+                           (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
+                           (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
+                           (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
+                           (country=="Vietnam" & year==2001))) |
+                 (country %in% c("Puerto Rico", "Northern Ireland", 
+                                 "SrpSka Republic", "Hong Kong SAR China")))) %>%
+    with_min_yrs(2)
+
+exp_claassen_input <- DCPOtools:::format_claassen(claassen_input_raw1)
[…]

### 2022-02-27 R/analysisData.R
make file names consistent

@@ -84,12 +84,12 @@ load(here("data", "exp_dcpo_output.rda"))
 #load(here("data","cls_libdem_list.rda"))  
 #load(here("data","cls_liberal_list.rda"))
 #load(here("data","cls_poly_list.rda"))
-#load(here("data","cls_cntrl.rda")) 
 #load(here("data","libdem_list.rda"))  
 #load(here("data","poly_list.rda"))
 #load(here("data","lib_list.rda"))
-#load(here("data","exp_cntrl.rda")) 
 #load(here("data","cpi_list.rda"))
+#load(here("data","cls_cntrl.rda")) 
+#load(here("data","exp_cntrl.rda")) 
 #load(here("data","dcpo_cntrl.rda")) 
 
 ################################### Vdem8 variables ##########################
@@ -1143,11 +1143,11 @@ save(exp_cntrl,file = here("data","exp_cntrl.rda"))
 
 #### DCPO Expanded Data
 
-min(dcpo_input_update22[["data"]]$year) #1988
-max(dcpo_input_update22[["data"]]$year) #2020
-length(unique(dcpo_input_update22[["data"]]$country))   #148
+min(exp_dcpo_input[["data"]]$year) #1988
+max(exp_dcpo_input[["data"]]$year) #2020
+length(unique(exp_dcpo_input[["data"]]$country))   #148
 
-dcpo_cntry_firstyr <- dcpo_input_update22[["data"]] %>%
+dcpo_cntry_firstyr <- exp_dcpo_input[["data"]] %>%
     select(c("country","year")) %>%
     unique()  %>% 
     group_by(country) %>%
@@ -1320,7 +1320,7 @@ save(correct_cls_apsr, file = here("data","correct_cls_apsr.rda"))
 
 #### Creating Expanded Correct theta list ####
 
-exp_claassen_m5_theta <- rstan::extract(claassen_m5, pars = "theta")
+exp_claassen_m5_theta <- rstan::extract(exp_claassen_m5, pars = "theta")
 ls_year <- 1988:2020
 ls_country <- exp_claassen_input$data$country %>% unique() #145
 first_year <- min(exp_claassen_input$data$year) #1988

### 2022-02-27 paper/dcpo_demsupport.Rmd
add osf source for dcpo_ajps, apsr, input, and exp_claassen_input @sammo3182

@@
 load(here("data", "expcor_cls_apsr.rda"))  # https://osf.io/uka5g/download
-load(here("data", "exp_claassen_input.rda")) # Source???
+load(here("data", "exp_claassen_input.rda")) # https://osf.io/fcyn3/download
 
@@
 ## Replication data
-load(here("data", "dcpo_ajps.rda"))  # https://osf.io/xxxx/download
-load(here("data", "dcpo_apsr.rda"))  # https://osf.io/xxxx/download
-load(here("data", "dcpo_input_update22.rda"))  # https://osf.io/xxxx/download
+load(here("data", "dcpo_ajps.rda"))  # https://osf.io/xw9fr/download
+load(here("data", "dcpo_apsr.rda"))  # https://osf.io/j7kn3/download
+load(here("data", "exp_dcpo_input.rda"))  # https://osf.io/r2pe8/download
 

### 2022-02-27 R/analysisData.R
add comments for output data.

@@ -78,6 +78,13 @@ load(here("data", "exp_claassen_output.rda"))
 load(here("data","exp_dcpo_input.rda"))
 load(here("data", "exp_dcpo_output.rda")) 
 
+
+# The following files will be created by codes in this file. 
+# Loading these files, you can skip data clean part and 
+# create final analysis data, which includes
+# correct_cls_ajps.rda,correct_cls_apsr.rda expcor_cls_ajps.rda, 
+# expcor_cls_apsr.rda, dcpo_ajps.rda, and dcpo_apsr, directly. 
+
 #load(here("data","correct_cls_theta_list.rda"))
 #load(here("data","expcor_cls_theta_list.rda"))
 #load(here("data","dcpo_theta_list.rda"))

### 2022-02-27 R/analysisData.R
add raw data source

@@ -2,13 +2,13 @@
 #### Input Data: raw_data_controls.RData which includes 
 ####             vdem8_post            Vdem8 with posterior distribution from The Varieties of Democracy Project
 ####             vdem10_1985           Vdem10 with standard errors from The Varieties of Democracy Project
-####             cpi_95_19_error       from Corruption Perception Index 
+####             cpi_95_19_error       from Corruption Perceptions Index - CPI transparency 
 ####             muslism_prop_2010     from http://globalreligiousfutures.org/
 ####             WDIData               from World Development Indicators 
 ####             resource_dep          from Haber and Menaldo (2011) 
 ####             WEOApr2020all         from IMF 
 ####             pwt100                from World Table Penn World Table Version.10. 
-####             country_regionUN      
+####             country_regionUN      based on UN region code https://unstats.un.org/unsd/methodology/m49/  
 
 ####             Data for Measures of Public Support: 
 ####             claassen_replication_input.rda  

### 2022-02-28 paper/dcpo_demsupport.Rmd
replication data updated; fixed #42, fixed #40; relate with #36

--- 2022-02-27 paper/dcpo_demsupport.Rmd
@@
 Replication files are available at the American Political
-Science Review Dataverse: https://doi.org/XXXX.
+Science Review Dataverse: https://doi.org/10.7910/DVN/YM67QE.
 
@@
     tidyverse,
-    glue)
+    glue,
+    janitor,
+    purrr,
+    tibble,
+
+    # compiling
+    rmarkdown,
+    bookdown)
 
@@
 
-source(here("R", "customFunctions.R")) ## analyzing and presenting functions
+source(here("customFunctions.R")) ## analyzing and presenting functions
 
@@
 ```{r data-input, include=FALSE}
-## Replication data
+## Data relocation
+
+if(!dir.exists("data")) {
+    dir.create("data")
+    file.copy(
+        c(
+            "correct_cls_ajps.rda",
+            "correct_cls_apsr.rda",
+            "expcor_cls_ajps.rda",
+            "expcor_cls_apsr.rda",
+            "exp_claassen_input.rda"
+        ),
+        "data"
+    )
+}
+
+if (!dir.exists("output")) {
+    dir.create("output")
+    file.copy(
+        c(
+            "estimates_clsMeanAPSR.RDS",
+            "estimates_clsMeanAJPS.RDS",
+            "estimates_moc_correctAJPS.RDS",
+            "estimates_moc_expcorAJPS.RDS",
+            "estimates_moc_correctAPSR.RDS",
+            "estimates_moc_expcorAPSR.RDS",
+            "estimates_moc_dcpoAPSR.RDS",
+            "estimates_moc_dcpoAJPS.RDS"
+        ),
+        "output"
+    )
+}
+
+## Loading replication data
 load(here("data", "correct_cls_ajps.rda")) # https://osf.io/52u7n/download
@@
 saveRDS(result_clsAJPS,
-        file = here::here("output", "estimates_clsMeanAJPS.RDS"))  
+        file = here("output", "estimates_clsMeanAJPS.RDS"))  
 ```
@@
 
-load(here::here("data", "dem_mood_apsr.RData"))
+load(here("data", "dem_mood_apsr.RData"))
 sd.plm <- pdata.frame(x, index = c("Country", "Year"))
@@
 saveRDS(mocresult_correctAPSR,
-        file = here::here("output", "estimates_moc_correctAPSR.RDS"))
+        file = here("output", "estimates_moc_correctAPSR.RDS"))
 ```
@@
 saveRDS(mocresult_expAPSR,
-        file = here::here("output", "estimates_moc_expcorAPSR.RDS"))
+        file = here("output", "estimates_moc_expcorAPSR.RDS"))
 ```
@@
 ```{r dcpodata-input, include=FALSE}
+file.copy(
+        c(
+            "dcpo_ajps.rda",
+            "dcpo_apsr.rda",
+            "exp_dcpo_input.rda"
+        ),
+        "data"
+    )
+
+file.copy(
+        c(
+            "estimates_moc_dcpoAPSR.RDS",
+            "estimates_moc_dcpoAJPS.RDS"
+        ),
+        "output"
+    )
+
 ## Replication data
-load(here("data", "dcpo_ajps.rda"))  # https://osf.io/xxxx/download
-load(here("data", "dcpo_apsr.rda"))  # https://osf.io/xxxx/download
-load(here("data", "dcpo_input_update22.rda"))  # https://osf.io/xxxx/download
+load(here("data", "dcpo_ajps.rda"))  # https://osf.io/xw9fr/download
+load(here("data", "dcpo_apsr.rda"))  # https://osf.io/j7kn3/download
+load(here("data", "exp_dcpo_input.rda"))  # https://osf.io/r2pe8/download
 
@@
 saveRDS(mocdcpo_APSR,
-        file = here::here("output", "estimates_moc_dcpoAPSR.RDS"))
+        file = here("output", "estimates_moc_dcpoAPSR.RDS"))
 ```
@@
 
-Research documentation and data that support the findings of this study are openly available in the APSR Dataverse at https://doi.org/XXXX.
+Research documentation and data that support the findings of this study are openly available in the APSR Dataverse at https://doi.org/10.7910/DVN/YM67QE.

### 2022-02-28 R/analysisData.R

@@ -70,8 +70,8 @@ set.seed(313)
 
 #Load input data
 
-load(here::here("data","raw_data_controls.RData"))
-load(here::here("data","claassen_replication_input.rda"))
+load(here("data","raw_data_controls.RData"))
+load(here("data","claassen_replication_input.rda"))
 load(here("data", "claassen_replication_output.rda")) 
 load(here("data","exp_claassen_input.rda"))
 load(here("data", "exp_claassen_output.rda")) 
@@ -934,7 +934,7 @@ pwt100_gdp <- pwt100 %>%
 
 #### Clean Dependence Data from Haberand Menaldo (2011)
 
-resource_dep %>% resource_dep
+resource_dep %>%
     mutate( cnamehabmen = ifelse(cnamehabmen == "Pakisan", "Pakistan",cnamehabmen),
             country = countrycode(cnamehabmen, origin = 'country.name', destination = 'country.name'),) %>%
     select("country", "year", "Total_Resources_Income_PC") %>%

### 2022-02-28 R/analysisData.R
correct resouce_dep

@@ -934,7 +934,7 @@ pwt100_gdp <- pwt100 %>%
 
 #### Clean Dependence Data from Haberand Menaldo (2011)
 
-resource_dep %>%
+resource_dep <- resource_dep %>%
     mutate( cnamehabmen = ifelse(cnamehabmen == "Pakisan", "Pakistan",cnamehabmen),
             country = countrycode(cnamehabmen, origin = 'country.name', destination = 'country.name'),) %>%
     select("country", "year", "Total_Resources_Income_PC") %>%

### 2022-02-28 paper/dcpo_demsupport.Rmd
rmd updated for replication

@@
 
-p_install(janitor, force = FALSE)
-p_install_gh(c("fsolt/DCPOtools"), force = FALSE)
+if(!require(janitor)) p_install(janitor, force = FALSE)
+if(!require(gesisdata)) remotes::install_github("fsolt/gesisdata") # dependent package for DCPOtools
+if(!require(DCPOtools)) remotes::install_github("fsolt/DCPOtools")
 
@@
     # data
-    dataverse,
+    # dataverse,
 
@@
     plm,
+    DCPOtools,
 
@@
 Sys.setenv("DATAVERSE_SERVER" = "dataverse.harvard.edu")
+# Sys.setenv("DATAVERSE_KEY" = "your_keys") # replace your_keys with true API keys
 
@@
 ```{r compare_n}
-if (!file.exists(here("data", "supdem raw survey marginals.tab"))) {
-  dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>%
-    read_csv(col_types = "cdcddcdc") %>%
-    write_csv("data/supdem raw survey marginals.tab")
-}
+# One can download the original data of the AJPS paper with the following codes AFTER set Sys.setenv("DATAVERSE_KEY" = "your_keys")
+# if (!file.exists(here("data", "supdem raw survey marginals.tab"))) {
+#   dataverse::get_file("supdem raw survey marginals.tab", "10.7910/DVN/HWLW0J") %>%
+#     read_csv(col_types = "cdcddcdc") %>%
+#     write_csv("data/supdem raw survey marginals.tab")
+# }
 
@@
 ```{r pointAJPS}
-if (!file.exists(here("data", "Support_democracy_ajps.csv"))) {
-  get_file_by_doi(filedoi = "10.7910/DVN/HWLW0J/MVXNFC") %>%
-    read_csv(col_types = "cdcddcdc") %>%
-    write_csv(here("data", "Support_democracy_ajps.csv"))
-}
+# One can download the original data of the AJPS paper with the following codes AFTER set Sys.setenv("DATAVERSE_KEY" = "your_keys")
+# if (!file.exists(here("data", "Support_democracy_ajps.csv"))) {
+#   get_file_by_doi(filedoi = "10.7910/DVN/HWLW0J/MVXNFC") %>%
+#     read_csv(col_types = "cdcddcdc") %>%
+#     write_csv(here("data", "Support_democracy_ajps.csv"))
+# }
 
@@
 # Reusing the sd.plm object, thus input data here rather than earlier
-if (!file.exists(here("data", "dem_mood_apsr.RData"))) {
-  get_dataframe_by_doi(filedoi = "10.7910/DVN/FECIO3/ACMGQG") %>%
-    save(file = here("data", "dem_mood_apsr.RData"))
-}
+# One can download the original data of the AJPS paper with the following codes AFTER set Sys.setenv("DATAVERSE_KEY" = "your_keys")
+# if (!file.exists(here("data", "dem_mood_apsr.RData"))) {
+#   get_dataframe_by_doi(filedoi = "10.7910/DVN/FECIO3/ACMGQG") %>%
+#     save(file = here("data", "dem_mood_apsr.RData"))
+# }
 

### 2022-03-01 R/renvSet.R
adding the renv package

@@ -1,0 +1,5 @@
+# The file is used to setup a replicable R environment
+
+if(!require(renv)) install.packages("renv")
+renv::init()
+renv::snapshot()

### 2022-03-02 paper/dcpo_demsupport.Rmd
apsr submission

@@
 
-date: " "
 editor_options: 
@@
     # data
-    # dataverse,
+    dataverse,
 
@@
 \renewcommand{\thetable}{A.\arabic{table}}
+
+Yuehong 'Cassandra' Tai, Yue Hu, and Frederick Solt, "Democracy, Public Support, and Measurement Uncertainty," American Political Science Review.
 

### 2022-03-03 paper/dcpo_demsupport.Rmd
corrected the dataset doi

@@
 Replication files are available at the American Political
-Science Review Dataverse: https://doi.org/10.7910/DVN/YM67QE.
+Science Review Dataverse: https://doi.org/10.7910/DVN/XAUF3H.
 
@@
 
-We proceed in three steps.
+We proceed in three steps.^[The replication files are available at @TaiEtAl2022a.]
 First, we reproduce the original analyses of Claassen [-@Claassen2020a; -@Claassen2020], which included only the point estimates of the latent variable of democratic support and so exclude its measurement uncertainty.
@@
 
-Research documentation and data that support the findings of this study are openly available in the APSR Dataverse at https://doi.org/10.7910/DVN/YM67QE.
+Research documentation and data that support the findings of this study are openly available in the APSR Dataverse at https://doi.org/10.7910/DVN/XAUF3H.

### 2023-06-06 replication_materials/dcpo_demsupport.Rmd
update replication materials

--- 2022-02-28 paper/dcpo_demsupport.Rmd
@@
 load(here("data", "expcor_cls_apsr.rda"))  # https://osf.io/uka5g/download
-load(here("data", "exp_claassen_input.rda")) # https://osf.io/fcyn3/download
+exp_claassen_input <- rio::import(here("data", "exp_claassen_input.rds")) # https://osf.io/fcyn3/download
 
@@
 # One can download the original data of the AJPS paper with the following codes AFTER set Sys.setenv("DATAVERSE_KEY" = "your_keys")
-# if (!file.exists(here("data", "supdem raw survey marginals.tab"))) {
-#   dataverse::get_file("supdem raw survey marginals.tab", "10.7910/DVN/HWLW0J") %>%
-#     read_csv(col_types = "cdcddcdc") %>%
-#     write_csv("data/supdem raw survey marginals.tab")
-# }
+if (!file.exists(here("data", "supdem raw survey marginals.tab"))) {
+    tempfile <- dataverse::get_file_by_doi("doi:10.7910/DVN/HWLW0J/RA8IJC") # AJPS replication file
+
+    writeBin(tempfile, here("data", "supdem raw survey marginals.tab"))
+}
 
@@
 
-dcpo_input_nc <- exp_claassen_input$data %>% 
+dcpo_input_nc <- exp_claassen_input$mar$data %>% 
   dplyr::select(country) %>% 
@@
 
-dcpo_input_surv <- exp_claassen_input$data %>%
+dcpo_input_surv <- exp_claassen_input$mar$data %>%
   dplyr::select(country, year, survey) %>%
@@
 
-dcpo_input_ncy <- exp_claassen_input$data %>% 
+dcpo_input_ncy <- exp_claassen_input$mar$data %>% 
   dplyr::select(country, year) %>% 
@@
 
-dcpo_input_ncyi <- exp_claassen_input$data %>% 
+dcpo_input_ncyi <- exp_claassen_input$mar$data %>% 
   dplyr::select(country, year, item, survey) %>% 
@@
 
-increase_cy <- sprintf("%2.1f", (dcpo_input_ncy/supdem_ncy - 1) * 100, 1)
-increase_cyi <- sprintf("%2.1f", (dcpo_input_ncyi/supdem_ncyi - 1) * 100, 1)
-increase_surv <- sprintf("%2.1f", (dcpo_input_surv/supdem_surv - 1) * 100, 1)
+increase_cy <- sprintf("%2.1f", (dcpo_input_ncy/supdem_ncy - 1) * 100)
+increase_cyi <- sprintf("%2.1f", (dcpo_input_ncyi/supdem_ncyi - 1) * 100)
+increase_surv <- sprintf("%2.1f", (dcpo_input_surv/supdem_surv - 1) * 100)
 ```
@@
 To provide a further test of the classic arguments on democracy and public support, we generated estimates of democratic support using the same procedure as in Claassen [-@Claassen2020a; -@Claassen2020] on a bigger data set, assembling as much survey data on democratic support as possible.
-We employed `r dcpo_input_ncyi` national opinions on democracy from `r dcpo_input_surv` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncy` opinions and `r supdem_surv` national surveys used in Claassen [-@Claassen2020a; -@Claassen2020].^[
+We employed `r dcpo_input_ncyi %>% formatC(big.mark=",")` national opinions on democracy from `r dcpo_input_surv %>% formatC(big.mark=",")` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncyi %>% formatC(big.mark=",")` opinions and `r supdem_surv %>% formatC(big.mark=",")` national surveys used in Claassen [-@Claassen2020a; -@Claassen2020].^[
 These figures represent the survey data actually used in estimating public support for democracy; as in Claassen [-@Claassen2020a; -@Claassen2020], countries for which two separate years of survey data were not available were excluded.]
@@
 # One can download the original data of the AJPS paper with the following codes AFTER set Sys.setenv("DATAVERSE_KEY" = "your_keys")
-# if (!file.exists(here("data", "Support_democracy_ajps.csv"))) {
-#   get_file_by_doi(filedoi = "10.7910/DVN/HWLW0J/MVXNFC") %>%
-#     read_csv(col_types = "cdcddcdc") %>%
-#     write_csv(here("data", "Support_democracy_ajps.csv"))
-# }
+if (!file.exists(here("data", "Support_democracy_ajps.csv"))) {
+  tempfile <- get_file_by_doi(filedoi = "10.7910/DVN/HWLW0J/MVXNFC")
+
+  writeBin(tempfile, here("data", "Support_democracy_ajps.csv"))
+}
 
@@
 
-    if (class(result) == "plm") {
+    if (any(str_detect("plm", class(result)))) {
         mutate(df_result, std.error = vcovBK_se(result))
@@
 glance_cls <- map(df_result_cls, function(aResult) {
-    if (class(aResult) == "plm") {
+    if (any(str_detect("plm", class(aResult)))) {
         glance.plm(aResult) # using the customized glance function
@@
            model = "Model 1 (Pooled OLS)")
+
 result_gmm <- bind_rows(
@@
            model = "Model 3 (System GMM)")
+
 result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
@@
            model = "Model 2 (Pooled OLS)")
+
 result_regimeGmm <- bind_rows(
@@
 We therefore coded both as `strong_lapop_1`.
-Other examples include inconsistent coding regarding what constitutes a "democracy-supporting" response and the inconsistent application of the stated rule regarding "don't know" and other nonresponses.
+Other examples include inconsistent coding regarding what constitutes a "democracy-supporting" response. 
 Here we use the corrected data for the replications with uncertainty to ensure that issues of data quality did not distort the results presented.
-These survey marginals were then used to generate estimates of democratic support in Stan using the `supdem.stan.mod5.stan` script from the @Claassen2020a Dataverse materials.
-Draws from the posterior distribution quantify the uncertainty in the estimates.
+
+Another coding problem involves "don't know" and other survey non-responses. 
+In Claassen [-@Claassen2020a; -@Claassen2020] all respondents who did not respond to a survey item are assumed to not support democracy and an undemocratic response is singly imputed to them.
+We found this rule was sometimes inconsistently applied, but in any event, single imputation has long been well understood to incorporate overly strong assumptions and understate measurement error [see, e.g., @Rubin1987].
+Therefore, we instead used multiple imputation.^[
+In rare cases, non-responses that were imputed undemocratic responses in Claassen [-@Claassen2020a; -@Claassen2020] are the result of split samples, where respondents were not even presented with the survey item in question.
+We exclude these explicitly 'missing at random' responses from the sample.]
+As the more familiar model-based multiple imputation technique is infeasible across thousands of national surveys, we proceeded as follows to generate four imputations.
+A first imputation assumes that attitudes among those who did not respond to an item are actually similar to the attitudes of those who did; that is, that the data are missing at random and so non-responses are excluded from the sample.
+The second imputation follows Claassen [-@Claassen2020a; -@Claassen2020] in coding non-responses as a lack of support and so sets a lower bound on the proportion of the population who support democracy as evidenced by a particular survey item.
+The third imputation, conversely, establishes an upper bound on democratic support indicated by an item by coding all non-responses as _support_ for democracy.
+The last imputation is theoretically derived: it assumes that non-response in democratic contexts reflects social desirability bias and so a lack of support for democracy, while non-response in non-democratic contexts reflects fear of reprisal and so democratic support.
+These four sets of survey marginals were then used to generate estimates of democratic support in Stan using the `supdem.stan.mod5.stan` script from the @Claassen2020a Dataverse materials.
+Finally, the draws from the resulting posterior distributions were combined as in a model-based multiple imputation routine [see, e.g., @Rubin1987]; together, the draws quantify the uncertainty in the estimates of democratic support.
+
 Finally, for the GMM models, the original publication presented the observation number based on the trimmed data, i.e., "2435", while the tabulating function in the replication file (line 86) uses the full used-observation number, "4735."
-We follow the replication file in the tables of Appendix \@ref(tables_not_plots) below.
+We follow the replication file in the tables of Appendix B below.
 
@@
              output = "latex", 
-             title = "The Effect of Public Support on Democracy (Uncertainty \\& More Data)") %>%
+             title = "The Effect of Public Support on Democracy (Uncertainty & More Data)") %>%
   kableExtra::kable_styling(font_size = 8) %>% 
@@
              output = "latex", 
-             title = "The Effect of Democracy on Change in Public Support (Uncertainty \\& More Data)") %>% 
+             title = "The Effect of Democracy on Change in Public Support (Uncertainty & More Data)") %>% 
   kableExtra::kable_styling(font_size = 7) %>% 
@@
 
-To sample from the conditional density and the marginal density in the right side of the equation, we follow iterative Monte Carlo procedure described by @TreierJackman2008, at iteration $t$,
+To sample from the conditional density and the marginal density in the right side of the equation, we follow the iterative Monte Carlo procedure described by @TreierJackman2008, at iteration $t$,
 
@@
 load(here("data", "dcpo_apsr.rda"))  # https://osf.io/j7kn3/download
-load(here("data", "exp_dcpo_input.rda"))  # https://osf.io/r2pe8/download
 
@@
              output = "latex", 
-             title = "The Effect of Public Support on Democracy (Uncertainty \\& DCPO)") %>%
+             title = "The Effect of Public Support on Democracy (Uncertainty & DCPO)") %>%
   kableExtra::kable_styling(font_size = 8) %>% 
@@
              output = "latex", 
-             title = "The Effect of Public Support on Democracy (Uncertainty \\& DCPO)") %>% 
+             title = "The Effect of Public Support on Democracy (Uncertainty & DCPO)") %>% 
   kableExtra::kable_styling(font_size = 7) %>% 

### 2023-06-06 replication_materials/data_replication/data_replication.Rmd
update data_replication

---
title: "Data Replication Script for Democracy, Public Support, and Measurement Uncertainty"
output:
    - pdf_document
date: "2023-06-01"
---

This file generates the latent variable estimates of support for democracy employed in the article, "Democracy, Public Support, and Measurement Uncertainty."  It then combines these estimates with data on the control variables to create the analysis datasets.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE) # comment this line to run all code
# knitr::opts_chunk$set(echo = TRUE)             # uncomment this line to run all code

library(tidyverse)
library(cmdstanr)
library(DCPOtools)
library(here)
library(furrr)
```

# Data Replication Files
There are 14 data files in the `data_replication` directory:

| Type         | Filename 
|--------------|---------------------------------
| Input        | mood_dem.csv
| Intermediate | claassen_input_raw.rds
| Intermediate | claassen_replication_input.rda
| Intermediate | exp_claassen_input.rds
| Intermediate | claassen_replication_theta.rds
| Intermediate | exp_theta.rds
| Intermediate | exp_dcpo_theta.rds
| Input        | cls_ajps_cntrl_list.rds
| Output       | correct_cls_ajps.rda
| Input        | cls_apsr_cntrl_list.rds
| Output       | correct_cls_apsr.rda
| Input        | exp_ajps_cntrl_list.rds
| Output       | expcor_cls_ajps.rda
| Output       | dcpo_ajps.rda
| Input        | exp_apsr_cntrl_list.rds
| Output       | expcor_cls_apsr.rda
| Output       | dcpo_apsr.rda

"Input" files are exogenous.  "Intermediate" files are generated by input files (and other intermediate files) and are used to generate output files; all of these processes are included in this document.  "Output" files are generated by input and intermediate files, and are used in the analyses scripted in the `dcpo_demsupport.Rmd` file (as is the `exp_claassen_input.rds` intermediate file).

# Source Data for Latent Variable Estimates

This section generates the source data needed to estimate the latent variable.
The first chunk starts from the original surveys; it generates the file `claassen_input_raw.rds`.  Collecting all of the needed survey datasets is labor-intensive (see https://github.com/fsolt/DCPOtools), so by default this code chunk is not evaluated and the next chunk simply uses the `claassen_input_raw.rds` file included in the replication materials.

```{r claassen_input_raw, eval=FALSE}
claassen_input_raw <- DCPOtools:::claassen_setup(
    vars = read_csv(here("data_replication",
                         "mood_dem.csv"),
                    col_types = "cccccc"),
    file = here::here("data_replication",
                      "claassen_input_raw.rds"),
    datapath = "../../data/dcpo_surveys")
```

The object `claassen_input_raw` contains many more observations than the dataset employed in Claassen (2020a,b), and that dataset misidentifies the survey year in ~8% the observations it does include.  The next chunk reproduces the sample of countries and years included in those data and saves it as `claassen_replication_input.rds`.  The expanded dataset labeled "more data" in our work is saved as `exp_claassen_input.rds`.

```{r claassen_replication_input}
claassen_input_raw <- rio::import(here::here("data_replication",
                      "claassen_input_raw.rds"))

dem <- readRDS(here("data_replication", "exp_ajps_cntrl_list.rds")) %>% 
    first() %>% 
    transmute(country, year, dem = as.numeric(Regime_VD > 1))

claassen_input_raw$scared <- claassen_input_raw %>% 
    pluck("lower") %>% 
    left_join(dem, by = join_by(country, year)) %>% 
    mutate(r = case_when(r == -1 & dem == 0 ~ 999, # code non-respondents in 
                         TRUE ~ r)) %>%  # autocracies as supporting democracy
    select(-dem)

remove_bad_items <- function(x) {
    x %>% 
    filter(!(str_detect(survey, "army_wvs") & # WVS obs identified as problematic by Claassen 
                     ((country=="Albania" & year==1998) |
                          (country=="Indonesia" & (year==2001 | year==2006)) |
                          (country=="Iran" & year==2000) |
                          (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
                          (country=="Vietnam" & year==2001)) |
                     (str_detect(item, "strong_wvs") &
                          ((country=="Egypt" & year==2012) |
                               (country=="Iran" & (year==2000 | year==2007)) | # 2005 in Claassen
                               (country=="India") |
                               (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
                               (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
                               (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
                               (country=="Vietnam" & year==2001))) |
                     (country %in% c("Puerto Rico", "Northern Ireland", 
                                     "SrpSka Republic", "Hong Kong SAR China"))))
}

claassen_input_raw1 <- map(claassen_input_raw, function(df) { 
    df %>%
        remove_bad_items() %>%
        with_min_yrs(2)
})

exp_claassen_input <- format_claassen(claassen_input_raw1)

rio::export(exp_claassen_input, file = here::here("data_replication",
                                           "exp_claassen_input.rds"))

dir.create("data", showWarnings = FALSE)
rio::export(exp_claassen_input, file = here::here("data",
                                           "exp_claassen_input.rds"))

# Note that before running `dataverse::get_file()` below, one should set their personal token and server in their system environment first: 
# Sys.setenv("DATAVERSE_KEY" = "exampleToken")
# Sys.setenv("DATAVERSE_SERVER" = "dataverse.harvard.edu")
# These values can be set to persist across R sessions using `usethis::edit_r_environ()`

if (!file.exists(here("data_replication", "supdem raw survey marginals.tab"))) {
    tempfile <- dataverse::get_file_by_doi("doi:10.7910/DVN/HWLW0J/RA8IJC") # AJPS replication file

    writeBin(tempfile, here("data_replication",
                                  "supdem raw survey marginals.tab"))
}

supdem <- read_csv(here::here("data_replication", "supdem raw survey marginals.tab"),
                   col_types = "cdcddcdc")

supdem1 <- supdem %>%                                             # 1390 obs
    janitor::clean_names() %>% 
    mutate(old_country = country,
           country = countrycode::countrycode(old_country, "country.name", "country.name"),
           i_claassen0 = tolower(item),
           i_claassen = case_when(str_detect(i_claassen0, "strong_arb") ~ "strong_arb",
                                  str_detect(i_claassen0, "strong_lapop") ~ "strong_lapop",
                                  str_detect(i_claassen0, "strong_pew") ~ "strong_pew",
                                  TRUE ~ i_claassen0),
           year = if_else(c_abb == "INS" & year == 2010 & i_claassen0 == "strong_pew",
                          2011,
                          year)) %>% 
    with_min_yrs(2)

supdem_cy <- supdem1 %>%                                   # 1376 obs
    select(country, year, project) %>% 
    distinct()

claassen_replication_input <- map(claassen_input_raw, function(df) {
    claassen_input_cy <- df %>%           # 1868 obs
        mutate(p_dcpo = str_extract(survey, "^[a-z]+"), 
               project = case_when(p_dcpo == "afrob" ~ "afb",
                                   p_dcpo == "amb" ~ "lapop",
                                   p_dcpo == "arabb" ~ "arb",
                                   p_dcpo == "asiab" ~ "asb",
                                   p_dcpo == "asianb" ~ "asnb",
                                   p_dcpo == "neb" ~ "ndb",
                                   p_dcpo == "sasianb" ~ "sab",
                                   TRUE ~ p_dcpo),
               y_dcpo = year) %>%
        select(country, year, y_dcpo, survey, project) %>% 
        unique()

    no_problems <- inner_join(supdem_cy, claassen_input_cy,
                              by = join_by(country, year, project))     # 1283 obs

    needed <- anti_join(supdem_cy, claassen_input_cy,
                        by = join_by(country, year, project))           # 93 obs

    available <- anti_join(claassen_input_cy, supdem_cy,
                           by = join_by(country, year, project))        # 585 obs

    year_fixes <- left_join(needed, available, 
                            by = c("country", "project"),
                            relationship = "many-to-many") %>% # 89 obs
        mutate(diff = year.x - year.y) %>% 
        group_by(country, project, year.x) %>% 
        mutate(closest_to_claassen = min(abs(diff))) %>% 
        ungroup() %>% 
        group_by(country, project, year.y) %>% 
        mutate(closest_to_dcpo = min(abs(diff))) %>% 
        ungroup() %>% 
        filter(closest_to_claassen == abs(diff) & closest_to_dcpo == abs(diff) & abs(diff) <= 3) %>% 
        filter(!(country == "Egypt" & year.x == 2014 & survey == "afrob5")) # double match (it's really afrob6)

    cys_crosswalk <- year_fixes %>% 
        select(country, y_dcpo, y_claassen = year.x, survey)

    missing_cyps <- anti_join(needed, year_fixes,  
                              by = c("country", "year" = "year.x", "project")) # 4 obs; listed in issue #5 (Bahrain now in) plus two unrepresentative Pakistan surveys

    cys_to_drop <- anti_join(available, year_fixes, 
                             by = c("country",
                                    "year" = "year.y",
                                    "project")) %>% # 496 obs
        select(-y_dcpo)

    cri <- df %>% #3705
        remove_bad_items() %>% 
        mutate(p_dcpo = str_extract(survey, "^[a-z]+"), 
               project = case_when(p_dcpo == "afrob" ~ "afb",
                                   p_dcpo == "amb" ~ "lapop",
                                   p_dcpo == "arabb" ~ "arb",
                                   p_dcpo == "asiab" ~ "asb",
                                   p_dcpo == "asianb" ~ "asnb",
                                   p_dcpo == "neb" ~ "ndb",
                                   p_dcpo == "sasianb" ~ "sab",
                                   TRUE ~ p_dcpo),
               i_dcpo = item,
               i_claassen = paste(str_replace(item, "_.*", "_"), p_dcpo)) %>% 
        left_join(cys_crosswalk, by = c("country", "year" = "y_dcpo", "survey")) %>% 
        anti_join(cys_to_drop, by = c("country", "year", "survey")) %>% # surveys unused by Claassen
        mutate(year = if_else(!is.na(y_claassen), y_claassen, year)) %>% # use Claassen's year codings
        mutate(item = if_else(item == "strong_amb_1" & year == 2004, "strong_amb_2", item)) %>% # items conflated in amb_combo file
        with_min_yrs(2) %>% 
        # DCPOtools::format_claassen() %>% 
        # pluck("data") %>% 
        mutate(p_dcpo = str_extract(survey, "^[a-z]+"), 
               project = case_when(p_dcpo == "afrob" ~ "afb",
                                   p_dcpo == "amb" ~ "lapop",
                                   p_dcpo == "arabb" ~ "arb",
                                   p_dcpo == "asiab" ~ "asb",
                                   p_dcpo == "asianb" ~ "asnb",
                                   p_dcpo == "neb" ~ "ndb",
                                   p_dcpo == "sasianb" ~ "sab",
                                   TRUE ~ p_dcpo),
               i_dcpo = item,
               i_claassen0 = paste0(str_replace(item, "_.*", "_"), project),
               i_claassen = case_when(i_claassen0 == "army_afb" ~ "army_afrob",
                                      i_claassen0 == "strong_afb" ~ "strong_afrob",
                                      i_claassen0 == "threestate_afb" ~ "threestate_afrob",
                                      i_claassen0 == "party_afb" ~ "party_afrob",
                                      i_claassen0 == "election_sab" ~ "elec_sab",
                                      TRUE ~ i_claassen0)) %>%
        inner_join(supdem1,
                   by = join_by(country, year, i_claassen)) %>% 
        select(country, year, item = item.x, r, n, survey) %>% 
        format_claassen()

    return(cri)
})

# each element of claassen_replication_input0 is missing 11 country-year-item observations included in supdem1 (6 are apparently no longer available, 2 seem to have never existed, and 3 are unrepresentative and should not have ever been included) and it has 1 more survey item (Claassen conflates two Arabbarometer items with different response categories)

rio::export(claassen_replication_input, 
            file = here("data_replication",
                        "claassen_replication_input.rds"))
```

# Estimating Democratic Support
Below, the inputs created above are used to generate the latent variable estimates of democratic support.  This requires a working installation of [`cmdstanr`](https://mc-stan.org/cmdstanr/index.html).  Generating each set of estimates takes 5 to 10 minutes to run on a M1 MacBook Pro.

## Original sample
```{r claassen_replication_output}
claassen_replication_input <- rio::import(here("data_replication", "claassen_replication_input.rds"))

if (!file.exists(here("data_replication", "supdem.stan.mod5.stan"))) {
    tempfile <- dataverse::get_file_by_doi("doi:10.7910/DVN/HWLW0J/MKBL9E") # AJPS replication file

    writeBin(tempfile, here("data_replication", "supdem.stan.mod5.stan"))
}

cm5 <- cmdstan_model(here("data_replication", "supdem.stan.mod5.stan"))

warmup <- 250; sampling = 75

plan(multisession, workers = 12)
future_options <- furrr_options(seed = 324)

claassen_replication_output <- future_map(claassen_replication_input,
                                          \(cri_df) {
                                              cm5$sample(
                                                  data = cri_df, 
                                                  max_treedepth = 14,
                                                  adapt_delta = 0.99,
                                                  step_size = 0.005,
                                                  seed = 324, 
                                                  chains = 3, 
                                                  parallel_chains = 3,
                                                  iter_warmup = warmup,
                                                  iter_sampling = sampling,
                                                  refresh = warmup/25
                                              )
                                          },
                                          .options = future_options
)

dat <- claassen_replication_input[["mar"]]$data %>% 
    mutate(kk = claassen_replication_input[["mar"]]$jj,
           tt = claassen_replication_input[["mar"]]$tt)

kcodes <- dat %>%
    group_by(country) %>%
    summarize(kk = first(kk) %>% 
                         as.numeric())

tcodes <- dat %>%
    group_by(year) %>%
    summarize(tt = first(tt))

ktcodes <- dat %>%
    group_by(country) %>%
    summarize(first_yr = min(year), 
                     last_yr = max(year))

claassen_replication_theta <- 
    imap(claassen_replication_output,
        \(res, idx) {
            res$draws("theta",
                      format = "df") %>% 
                pivot_longer(starts_with("theta"), values_to = "theta") %>% 
                mutate(tt = as.numeric(gsub("theta\\[(\\d+),\\d+\\]", 
                                            "\\1", name)), 
                       kk = as.numeric(gsub("theta\\[\\d+,(\\d+)\\]", 
                                            "\\1", name))) %>%
                left_join(kcodes, 
                          by = "kk") %>%
                left_join(tcodes, by = "tt") %>%
                mutate(year = if_else(tt == 1,
                                      as.integer(year),
                                      as.integer(min(year, na.rm = TRUE)
                                                 + tt - 1)),
                       set = idx) %>%
                left_join(ktcodes, by = "country") %>%
                arrange(kk, tt) %>%
                group_by(kk, tt) %>% 
                mutate(draw = case_when(idx == "mar" ~ 0,
                                        idx == "lower" ~ n(),
                                        idx == "upper" ~ 2*n(),
                                        idx == "scared" ~ 3*n())
                           + 1:n()) %>% 
                ungroup() %>% 
                select(country, year, theta, set, draw) 
        }) %>% 
    list_rbind() %>% 
    group_split(draw)

saveRDS(claassen_replication_theta, 
        file = here("data_replication", "claassen_replication_theta.rds"))
```

## Expanded 'More Data' Sample
```{r exp_output}
exp_claassen_input <- rio::import(here("data_replication", "exp_claassen_input.rds"))

cm5 <- cmdstan_model(here("data_replication", "supdem.stan.mod5.stan"))

warmup <- 250; sampling = 75

plan(multisession, workers = 12)
future_options <- furrr_options(seed = 324)

exp_output <- future_map(exp_claassen_input,
                         \(cri_df) {
                             cm5$sample(
                                 data = cri_df, 
                                 max_treedepth = 14,
                                 adapt_delta = 0.99,
                                 step_size = 0.005,
                                 seed = 324, 
                                 chains = 3, 
                                 parallel_chains = 3,
                                 iter_warmup = warmup,
                                 iter_sampling = sampling,
                                 refresh = warmup/25
                             )
                         },
                         .options = future_options
)

dat <- exp_claassen_input[["mar"]]$data %>% 
    mutate(kk = exp_claassen_input[["mar"]]$jj,
           tt = exp_claassen_input[["mar"]]$tt)

kcodes <- dat %>%
    group_by(country) %>%
    summarize(kk = first(kk) %>% 
                         as.numeric())

tcodes <- dat %>%
    group_by(year) %>%
    summarize(tt = first(tt))

ktcodes <- dat %>%
    group_by(country) %>%
    summarize(first_yr = min(year), 
                     last_yr = max(year))

exp_theta <- 
    imap(exp_output,
        \(res, idx) {
            res$draws("theta",
                      format = "df") %>% 
                pivot_longer(starts_with("theta"), values_to = "theta") %>% 
                mutate(tt = as.numeric(gsub("theta\\[(\\d+),\\d+\\]", 
                                            "\\1", name)), 
                       kk = as.numeric(gsub("theta\\[\\d+,(\\d+)\\]", 
                                            "\\1", name))) %>%
                left_join(kcodes, 
                          by = "kk") %>%
                left_join(tcodes, by = "tt") %>%
                mutate(year = if_else(tt == 1,
                                      as.integer(year),
                                      as.integer(min(year, na.rm = TRUE)
                                                 + tt - 1)),
                       set = idx) %>%
                left_join(ktcodes, by = "country") %>%
                arrange(kk, tt) %>%
                group_by(kk, tt) %>% 
                mutate(draw = case_when(idx == "mar" ~ 0,
                                        idx == "lower" ~ n(),
                                        idx == "upper" ~ 2*n(),
                                        idx == "scared" ~ 3*n())
                           + 1:n()) %>% 
                ungroup() %>% 
                select(country, year, theta, set, draw) 
        }) %>% 
    list_rbind() %>% 
    group_split(draw)

saveRDS(exp_theta, 
        file = here("data_replication", "exp_theta.rds"))
```

# Merging Data

The output of the next four chunks are the four files used in the (1) 'uncertainty' AJPS replication, (2) 'uncertainty' APSR replication, (3) 'uncertainty & more data AJPS replication', and (4) 'uncertainty & more data' APSR replication.

## AJPS replication, Claassen sample
```{r correct_cls_ajps}
# If latent-variable estimates were not just generated, load them now
if (!exists("claassen_replication_theta")) {
    claassen_replication_theta <- readRDS(file = here("data_replication", "claassen_replication_theta.rds"))
}

# Download controls from osf if file not present
if (!file.exists(here("data_replication",
                      "exp_apsr_cntrl_list.rds"))) { 
    osf_retrieve_file("hf2t4") %>% 
        osf_download(here("data_replication"))
}

cls_ajps_cntrl_list <- readRDS(here("data_replication", "cls_ajps_cntrl_list.rds"))

correct_cls_ajps <- map2(cls_ajps_cntrl_list,
                         claassen_replication_theta,
                         \(controls, theta) {
                             controls %>% 
                                 left_join(theta, by = c("country", "year")) %>% 
                                 mutate(SupDem_trim = ifelse(year < firstyear,
                                                             NA,
                                                             theta),
                                        theta_dem_trim = case_when(
                                            is.na(SupDem_trim) ~ NA,
                                            Regime_VD > 1 & !is.na(SupDem_trim) ~ theta,
                                            TRUE ~ 0),
                                        theta_aut_trim = case_when(
                                            is.na(SupDem_trim) ~ NA,
                                            Regime_VD <= 1 & !is.na(SupDem_trim) ~ theta,
                                            TRUE ~ 0)
                                        ) %>%
                                 select(country, year, theta, contains("trim"),
                                        everything())
                         })

dir.create("data", showWarnings = FALSE)
save(correct_cls_ajps, file = here("data","correct_cls_ajps.rda"))
```

## APSR replication, Claassen sample
```{r correct_cls_apsr}
# If latent-variable estimates were not just generated, load them now
if (!exists("claassen_replication_theta")) {
    claassen_replication_theta <- readRDS(file = here("data_replication", "claassen_replication_theta.rds"))
}

# Download controls from osf if file not present
if (!file.exists(here("data_replication",
                      "exp_apsr_cntrl_list.rds"))) { 
    osf_retrieve_file("fsk96") %>% 
        osf_download(here("data_replication"))
}

cls_apsr_cntrl_list <- readRDS(here("data_replication", "cls_apsr_cntrl_list.rds"))

correct_cls_apsr <- map2(cls_apsr_cntrl_list,
                         claassen_replication_theta,
                         \(controls, theta) {
    controls %>% 
        left_join(theta, by = c("year", "country"))  %>% 
        mutate(SupDem_trim = ifelse(year < firstyear, NA, theta)) %>%
        select(country, year, firstyear, theta, SupDem_trim,
               contains("z"), everything())
})

save(correct_cls_apsr, file = here("data","correct_cls_apsr.rda"))
```

## AJPS replication, expanded sample
```{r expcor_cls_ajps}
# If latent-variable estimates were not just generated, load them now
if (!exists("exp_theta")) {
    exp_theta <- readRDS(file = here("data_replication", "exp_theta.rds"))
}

# Download controls from osf if file not present
if (!file.exists(here("data_replication",
                      "exp_ajps_cntrl_list.rds"))) {
    osf_retrieve_file("etp7a") %>% 
        osf_download(here("data_replication"))
}

exp_ajps_cntrl_list <- readRDS(here("data_replication", "exp_ajps_cntrl_list.rds"))

expcor_cls_ajps <- map2(exp_ajps_cntrl_list,
                 exp_theta,
                 \(controls, theta) {
                     controls %>% 
                         left_join(theta, by = c("country", "year")) %>% 
                         mutate(SupDem_trim = ifelse(year < firstyear, NA, theta),
                                theta_dem_trim = case_when(
                                    is.na(SupDem_trim) ~ NA,
                                    Regime_VD > 1 & !is.na(SupDem_trim) ~ theta,
                                    TRUE ~ 0),
                                theta_aut_trim = case_when(
                                    is.na(SupDem_trim) ~ NA,
                                    Regime_VD <= 1 & !is.na(SupDem_trim) ~ theta,
                                    TRUE ~ 0)) %>%
                         select(country, year, theta, contains("trim"), everything())
                 })

save(expcor_cls_ajps, file = here("data",
                                  "expcor_cls_ajps.rda"))
```

## APSR replication, expanded sample
```{r expcor_cls_apsr}
# If latent-variable estimates were not just generated, load them now
if (!exists("exp_theta")) {
    exp_theta <- readRDS(file = here("data_replication", "exp_theta.rds"))
}

# Download from osf if file not present
if (!file.exists(here("data_replication",
                      "exp_apsr_cntrl_list.rds"))) { 
    osf_retrieve_file("kqtyv") %>% 
        osf_download(here("data_replication"))
}

exp_apsr_cntrl_list <- readRDS(here("data_replication", "exp_apsr_cntrl_list.rds"))

expcor_cls_apsr <- map2(exp_apsr_cntrl_list,
                        claassen_replication_theta,
                        \(controls, theta) {
                            controls %>% 
                                left_join(theta, by = c("year", "country"))  %>% 
                                mutate(SupDem_trim = ifelse(year < firstyear,
                                                            NA, 
                                                            theta)) %>%
                                select(country, year, firstyear, theta, SupDem_trim,
                                       contains("z"), everything())
                        })

save(expcor_cls_apsr, file = here("data",
                                  "expcor_cls_apsr.rda"))
```

# Estimating Democratic Support with the DCPO Model (OSM D)

Online Supplementary Materials D presents, for comparison, the 'Uncertainty & More Data' models when the superior DCPO model is used to estimate the latent variable of democratic support.

## Expanded 'More Data' Sample, DCPO Estimates
```{r dcpo_exp_output}
exp_dcpo_input <- format_dcpo(claassen_input_raw1,
                              scale_q = "threestate_lb",
                              scale_cp = 2)

if (!file.exists(here("data_replication", "dcpo.stan"))) {
    download.file("https://raw.githubusercontent.com/fsolt/DCPO/master/inst/stan/dcpo.stan", here("data_replication", "dcpo.stan"))
}

dcpo <- cmdstan_model(here("data_replication", "dcpo.stan"))

warmup <- 250; sampling = 75

plan(multisession, workers = 12)
future_options <- furrr_options(seed = 324)

exp_dcpo_output <- future_map(exp_dcpo_input,
                         \(edi_df) {
                             dcpo$sample(
                                 data = edi_df[1:14], 
                                 max_treedepth = 14,
                                 adapt_delta = 0.99,
                                 step_size = 0.005,
                                 seed = 324, 
                                 chains = 3, 
                                 parallel_chains = 3,
                                 iter_warmup = warmup,
                                 iter_sampling = sampling,
                                 refresh = warmup/25
                             )
                         },
                         .options = future_options
)

dat <- exp_dcpo_input[["mar"]]$data %>% 
    mutate(kk = exp_dcpo_input[["mar"]]$kk,
           tt = exp_dcpo_input[["mar"]]$tt)

kcodes <- dat %>%
    group_by(country) %>%
    summarize(kk = first(kk) %>% 
                         as.numeric())

tcodes <- dat %>%
    group_by(year) %>%
    summarize(tt = first(tt))

ktcodes <- dat %>%
    group_by(country) %>%
    summarize(first_yr = min(year), 
                     last_yr = max(year))

exp_dcpo_theta <- 
    imap(exp_dcpo_output,
        \(res, idx) {
            res$draws("theta",
                      format = "df") %>% 
                pivot_longer(starts_with("theta"), values_to = "theta") %>% 
                mutate(tt = as.numeric(gsub("theta\\[(\\d+),\\d+\\]", 
                                            "\\1", name)), 
                       kk = as.numeric(gsub("theta\\[\\d+,(\\d+)\\]", 
                                            "\\1", name))) %>%
                left_join(kcodes, 
                          by = "kk") %>%
                left_join(tcodes, by = "tt") %>%
                mutate(year = if_else(tt == 1,
                                      as.integer(year),
                                      as.integer(min(year, na.rm = TRUE)
                                                 + tt - 1)),
                       set = idx) %>%
                left_join(ktcodes, by = "country") %>%
                arrange(kk, tt) %>%
                filter(year >= first_yr & year <= last_yr) %>%
                arrange(kk, tt) %>%
                group_by(kk, tt) %>% 
                mutate(set = idx,
                       draw = case_when(idx == "mar" ~ 0,
                                        idx == "lower" ~ n(),
                                        idx == "upper" ~ 2*n(),
                                        idx == "scared" ~ 3*n())
                           + 1:n()) %>% 
                ungroup() %>% 
                select(country, year, theta, set, draw) 
        }) %>% 
    list_rbind() %>% 
    group_split(draw)

saveRDS(exp_dcpo_theta, 
        file = here("data_replication", "exp_dcpo_theta.rds"))
```

## AJPS replication, DCPO model, expanded sample
```{r expcor_cls_ajps}
# If latent-variable estimates were not just generated, load them now
if (!exists("exp_dcpo_theta")) {
    exp_dcpo_theta <- readRDS(file = here("data_replication", "exp_dcpo_theta.rds"))
}
# If controls not present already, load them now
if (!exists("exp_ajps_cntrl_list")) {
    # download from osf if needed
    if (!file.exists(here("data_replication",
                          "exp_ajps_cntrl_list.rds"))) {
        osf_retrieve_file("etp7a") %>% 
            osf_download(here("data_replication"))
    }

    exp_ajps_cntrl_list <- readRDS(here("data_replication",
                                        "exp_ajps_cntrl_list.rds"))
}

dcpo_ajps <- map2(exp_ajps_cntrl_list,
                 exp_dcpo_theta,
                 \(controls, theta) {
                     controls %>% 
                         left_join(theta, by = c("country", "year")) %>% 
                         mutate(SupDem_trim = ifelse(year < firstyear,
                                                      NA, 
                                                      theta),
                                theta_dem_trim = case_when(
                                    is.na(SupDem_trim) ~ NA,
                                    Regime_VD > 1 & !is.na(SupDem_trim) ~ theta,
                                    TRUE ~ 0),
                                theta_aut_trim = case_when(
                                    is.na(SupDem_trim) ~ NA,
                                    Regime_VD <= 1 & !is.na(SupDem_trim) ~ theta,
                                    TRUE ~ 0)) %>%
                         select(country, year, theta, contains("trim"), everything())
                 })

save(dcpo_ajps, file = here("data",
                            "dcpo_ajps.rda"))
```

## APSR replication, DCPO model, expanded sample
```{r expcor_cls_apsr}
# If latent-variable estimates were not just generated, load them now
if (!exists("exp_dcpo_theta")) {
    exp_dcpo_theta <- readRDS(file = here("data_replication", "exp_dcpo_theta.rds"))
}
# If controls not present already, load them now 
if (!exists("exp_ajps_cntrl_list")) {
    # download from osf if needed
    if (!file.exists(here("data_replication",
                          "exp_apsr_cntrl_list.rds"))) { 
        osf_retrieve_file("kqtyv") %>% 
            osf_download(here("data_replication"))
    }

    exp_apsr_cntrl_list <- readRDS(here("data_replication",
                                        "exp_apsr_cntrl_list.rds"))
}

dcpo_apsr <- map2(exp_apsr_cntrl_list,
                  exp_dcpo_theta,
                  \(controls, theta) {
                      controls %>% 
                          left_join(theta, by = c("year", "country"))  %>% 
                          mutate(SupDem_trim = ifelse(year < firstyear,
                                                      NA, 
                                                      theta)) %>%
                          select(country, year, firstyear, theta, SupDem_trim,
                                 contains("z"), everything())
                  })

save(dcpo_apsr, file = here("data",
                            "dcpo_apsr.rda"))
```

### 2023-06-06 replication_materials/dcpo_demsupport.Rmd
add osf links

@@
 ## Loading replication data
-load(here("data", "correct_cls_ajps.rda")) # https://osf.io/52u7n/download
-load(here("data", "correct_cls_apsr.rda")) # https://osf.io/cws59/download
-load(here("data", "expcor_cls_ajps.rda"))  # https://osf.io/cgxjd/download
-load(here("data", "expcor_cls_apsr.rda"))  # https://osf.io/uka5g/download
-exp_claassen_input <- rio::import(here("data", "exp_claassen_input.rds")) # https://osf.io/fcyn3/download
-
-## Preloading chunk-produced results to speed up the compiling
-## One can find how they were created by locating the corresponding chunks
-
+# Download from osf if files not present 
+# (can also be generated by compiling /data_replication/data_replication.Rmd)
+if (!file.exists(here("data",
+                      "correct_cls_ajps.rda"))) { 
+    osf_retrieve_file("5xyvt") %>% 
+        osf_download(here("data"))
+}
+if (!file.exists(here("data",
+                      "correct_cls_apsr.rda"))) { 
+    osf_retrieve_file("8xgm4") %>% 
+        osf_download(here("data"))
+}
+if (!file.exists(here("data",
+                      "expcor_cls_ajps.rda"))) { 
+    osf_retrieve_file("rj9g5") %>% 
+        osf_download(here("data"))
+}
+if (!file.exists(here("data",
+                      "expcor_cls_apsr.rda"))) { 
+    osf_retrieve_file("bxt7m") %>% 
+        osf_download(here("data"))
+}
+if (!file.exists(here("data",
+                      "exp_claassen_input.rds"))) { 
+    osf_retrieve_file("rfamx") %>% 
+        osf_download(here("data"))
+}
+if (!file.exists(here("data",
+                      "dcpo_ajps.rda"))) { 
+    osf_retrieve_file("sbp5a") %>% 
+        osf_download(here("data"))
+}
+if (!file.exists(here("data",
+                      "dcpo_apsr.rda"))) { 
+    osf_retrieve_file("9yh5z") %>% 
+        osf_download(here("data"))
+}
+
+## Loading replication data
+load(here("data", "correct_cls_ajps.rda"))
+load(here("data", "correct_cls_apsr.rda"))
+load(here("data", "expcor_cls_ajps.rda")) 
+load(here("data", "expcor_cls_apsr.rda")) 
+exp_claassen_input <- rio::import(here("data", "exp_claassen_input.rds")) 
+load(here("data", "dcpo_ajps.rda"))
+load(here("data", "dcpo_apsr.rda"))
+
+## Preloading chunk-produced results to speed up the document compiling
+# Download from osf if files not present 
+# (can also be generated by compiling the appropriate eval=FALSE chunks below)
+if (!file.exists(here("output",
+                      "estimates_clsMeanAJPS.RDS"))) { 
+    osf_retrieve_file("s36h2") %>% 
+        osf_download(here("output"))
+}
+if (!file.exists(here("output",
+                      "estimates_clsMeanAPSR.RDS"))) { 
+    osf_retrieve_file("cuj63") %>% 
+        osf_download(here("output"))
+}
+if (!file.exists(here("output",
+                      "estimates_moc_correctAJPS.RDS"))) { 
+    osf_retrieve_file("nbt4j") %>% 
+        osf_download(here("output"))
+}
+if (!file.exists(here("output",
+                      "estimates_moc_expcorAJPS.RDS"))) { 
+    osf_retrieve_file("hd874") %>% 
+        osf_download(here("output"))
+}
+if (!file.exists(here("output",
+                      "estimates_moc_correctAPSR.RDS"))) { 
+    osf_retrieve_file("fv3qz") %>% 
+        osf_download(here("output"))
+}
+if (!file.exists(here("output",
+                      "estimates_moc_expcorAPSR.RDS"))) { 
+    osf_retrieve_file("td5nr") %>% 
+        osf_download(here("output"))
+}
+if (!file.exists(here("output",
+                      "estimates_moc_dcpoAJPS.RDS"))) { 
+    osf_retrieve_file("8avpt") %>% 
+        osf_download(here("output"))
+}
+if (!file.exists(here("output",
+                      "estimates_moc_dcpoAPSR.RDS"))) { 
+    osf_retrieve_file("e2ys3") %>% 
+        osf_download(here("output"))
+}
+
+result_clsAJPS <-
+    readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
 result_clsAPSR <-
     readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
-result_clsAJPS <-
-    readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
-
 mocresult_correctAJPS <-
@@
     readRDS(here("output", "estimates_moc_expcorAPSR.RDS"))
-mocdcpo_APSR <- readRDS(here("output", "estimates_moc_dcpoAPSR.RDS"))
 mocresult_dcpoAJPS <-
     readRDS(here("output", "estimates_moc_dcpoAJPS.RDS"))
+mocdcpo_APSR <- readRDS(here("output", "estimates_moc_dcpoAPSR.RDS"))
+
 ```
@@
     )
-
-## Replication data
-load(here("data", "dcpo_ajps.rda"))  # https://osf.io/xw9fr/download
-load(here("data", "dcpo_apsr.rda"))  # https://osf.io/j7kn3/download
-
-## Preloading chunk-produced results to speed up the compiling
-## One can find how they were created by locating the corresponding chunks
-
-mocdcpo_APSR <- readRDS(here("output", "estimates_moc_dcpoAPSR.RDS"))
-mocresult_dcpoAJPS <-
-    readRDS(here("output", "estimates_moc_dcpoAJPS.RDS"))
 ```

### 2023-07-19 paper/dcpo_demsupport.Rmd
update

@@
 ## Loading replication data
+# Download from osf if files not present 
+# (can also be generated by compiling /data_replication/data_replication.Rmd)
+if (!file.exists(here("data",
+                      "correct_cls_ajps.rda"))) { 
+    osf_retrieve_file("5xyvt") %>% 
+        osf_download(here("data"))
+}
+if (!file.exists(here("data",
+                      "correct_cls_apsr.rda"))) { 
+    osf_retrieve_file("8xgm4") %>% 
+        osf_download(here("data"))
+}
+if (!file.exists(here("data",
+                      "expcor_cls_ajps.rda"))) { 
+    osf_retrieve_file("rj9g5") %>% 
+        osf_download(here("data"))
+}
+if (!file.exists(here("data",
+                      "expcor_cls_apsr.rda"))) { 
+    osf_retrieve_file("bxt7m") %>% 
+        osf_download(here("data"))
+}
+
 load(here("data", "correct_cls_ajps.rda")) # https://osf.io/52u7n/download

### 2023-07-19 paper/correction_memo.Rmd
add correction_memo

---
title: |
    | Correction Memo:
    | Democracy, Public Support, and Measurement Uncertainty
output: pdf_document
author: "Yuehong Cassandra Tai, Yue Hu, and Frederick Solt"
date: "2023-06-05"
bibliography: 
  - dcpo-demsupport-app.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Thank you for the opportunity to address the issues of (1) the inclusion of nonrepresentative surveys in the expanded dataset, (2) the treatment of non-responses, and (3) the lack of standardization of survey weights.
It is perhaps worth noting that, soon after our letter was published last spring, Christopher Claassen shared with us via email that he had identified these issues.
He offered no evidence or indication that he believed that any or all of them were of consequence, and we did not think they were either; as both he and our team are continuing to work in this area, we understood our exchange as instead a friendly effort to ensure these points would be adequately addressed in the future research both he and we conduct.
At your prompting, we have now attended to these concerns specifically in the context of our letter, and we can confirm that they are inconsequential to its conclusions.
They do suggest, however, that revisions would be warranted to the replication materials, to the online supplemental materials, and to both plots and a few numbers in the text of the letter itself.

## Nonrepresentative Surveys
**The Issue**. In the 2002 and 2005 Pew Global Attitudes Surveys, the codebooks identify a total of nineteen national surveys with samples that are biased toward urban areas.
Although Claassen [-@Claassen2020a; -@Claassen2020] identified and excluded seventeen of the nineteen (inadvertently, apparently, including two), we did not catch this issue at all and included all of these national surveys in our expanded sample.

**Resolution**. Data from these nineteen national surveys---including the two that were included in the sample used in Claassen [-@Claassen2020a; -@Claassen2020]---are now excluded from our data.

## Non-Responses
**The Issue**. In Claassen [-@Claassen2020a; -@Claassen2020], all respondents who did not respond to a survey item are assumed to not support democracy and an undemocratic response is (usually but not always, as we noted in the OSM at page A2; see also @Hu2022 at 4) singly imputed to them.
Single imputation has long been well understood to incorporate overly strong assumptions and understate measurement error [see, e.g., @Rubin1987].
In our letter, we treated these non-responses as 'missing at random'---that is, that the distribution of attitudes among those who did not respond was similar to that among those who did---and applied listwise deletion, excluding the non-responses from the sample.
This was a mistake: like single imputation, listwise deletion is known to understate measurement error [again see @Rubin1987 and many others]. 
So neither approach is suitable, especially not in a letter on the importance of avoiding understating measurement error.

**Resolution**. In some cases (for example, the Americas Barometer survey of Canada in 2010; see @Hu2022 at 5), non-responses are the result of split samples, where many respondents were not even presented with the survey item in question.
In such cases, imputing undemocratic responses to these respondents is clearly inapt.
Instead, they are missing at random---respondents were explicitly randomly assigned to the split samples that excluded the relevant item---and so listwise deletion is appropriate.
We therefore continue to exclude from the sample those respondents who were not even asked the relevant question.
These cases are rare, though; most non-responses in these surveys are the result of refusal, 'don't know', and other non-responsive answers.

For these remaining cases, it is _multiple_, not single, imputation that is the preferred method for addressing such missing data and the measurement error that results [see, e.g., @Rubin1987].
Typically, multiple imputation of survey non-response involves building a model of the missing data with the other variables of interest from the survey.
This preserves the relationships among these survey variables and allows the measurement uncertainty that remains after modeling to propagate to the quantity of interest [see, e.g., @King2001; @Blackwell2017].
Here, however, there is only one variable of interest (or, sometimes, a few) in each of thousands of national surveys, and building such an MI model for every survey is not practicable.

The single-imputation approach employed in Claassen [-@Claassen2020a; -@Claassen2020] is inappropriate on its own, but it points the way to a feasible solution that, unlike either single imputation or listwise deletion, incorporates measurement uncertainty in the proportion of the population that supports democracy.
To assume that all respondents who did not answer an item do not support democracy is not theoretically grounded: indeed, it is often argued that non-response to such politically sensitive items in nondemocracies reflects a fear of government reprisal for holding _pro-democratic_ views [see, e.g., @Shen2021].
Nevertheless, the Claassen assumption sets a lower bound on the proportion of the population who support democracy as evidenced by a particular survey item.
Conversely, assuming that all non-responses reflect unvoiced _support_ for democracy establishes an upper bound on democratic support indicated by an item.
A more theoretically-driven assumption than either of these is that non-response in democratic contexts reflects social desirability bias and so a lack of support for democracy, while non-response in non-democratic contexts reflects fear of reprisal (or perhaps again social desirability bias, only yielding different results in a different political setting) and so democratic support.
An intermediate possibility, of course, is that attitudes among those who did not respond to an item are actually similar to the attitudes of those who did; that is, that the data are missing at random and non-responses are appropriately listwise deleted.

We therefore now incorporate the measurement uncertainty due to non-response as follows.
The number of democracy-supporting responses and the total sample size was imputed four times---that is, using in turn each of these four assumptions about the distribution of non-responses described above---for each country-year-item in the source survey data.
The latent variable was then estimated using each of these imputations, and the resulting draws combined as in model-based multiple imputation.
The result is a distribution of draws that reflects the measurement uncertainty in the latent variable, avoiding the strong assumptions of either single imputation or listwise deletion.

## Survey Weights
**The Issue**.  Claassen [-@Claassen2020a; -@Claassen2020] ignored survey weights (well, again usually but not always; see @Hu2022 at 4-5), instead using the unweighted survey data.
This is problematic, of course, as the unweighted data may not be representative of the underlying population.
In our data collection, we corrected this by employing each survey's weights, but did not appreciate that some surveys' weights are not standardized; that is, applying them caused (occasionally dramatic) changes in the sample size.
As the sample size is an important input in the latent variable model---smaller samples yield larger uncertainty in the population mean, which then propagates into the estimate of democratic support---this is undesirable.

**Resolution**. We now standardize survey weights to have a mean of one before applying them and so ensure that these weights preserve the sample size.

# Conclusions
Applying these corrections does not yield substantive differences in the results of our analyses and so does not affect the conclusions reached.
But "no substantive differences" does not mean "no differences." 
As one would anticipate, all of the regression results change marginally, and the few numbers we included in our description of the expanded dataset are no longer accurate either.
Updating the replication materials to reflect these corrections (and, as a bonus, make them more user friendly); revising the tables in OSM B and the figures and tables in OSM D; adding a discussion of non-responses to OSM A; and updating Figure 1, Figure 2, and the specific numbers reported under "Adding More Data" in the text itself would be warranted.
Drafts of the revised text and OSM are attached, and we have prepared the updated replication materials for upload to the Dataverse.
Please let us know how you would like us to proceed.

# References

### 2023-07-25 paper/correction/corrigenda.qmd
corrigenda drafted

--- 2023-07-19 paper/correction_memo.Rmd
@@
 ---
-title: |
-    | Correction Memo:
-    | Democracy, Public Support, and Measurement Uncertainty
-output: pdf_document
-author: "Yuehong Cassandra Tai, Yue Hu, and Frederick Solt"
-date: "2023-06-05"
-bibliography: 
-  - dcpo-demsupport-app.bib
+format:
+  pdf:
+    number-sections: true
+    papersize: a4
+crossref:
+  sec-prefix: OSM
+  sec-labels: alpha A
+
+author:
+  - name: Yuehong 'Cassandra' Tai
+    affiliations:
+      - ref: ui
+    orcid: 0000-0001-7303-7443
+    email: yuehong-tai@uiowa.edu
+    equal-contributor: true
+  - name: Yue Hu
+    affiliations:
+      - ref: tsu
+    orcid: 0000-0002-2829-3971
+    email: yuehu@tsinghua.edu.cn
+    url: https://sammo3182.github.io
+    equal-contributor: true
+    corresponding: true
+  - name: Frederick Solt
+    affiliations:
+      - ref: ui
+    orcid: 0000-0002-3154-6132
+    email: frederick-solt@uiowa.edu
+    url: https://fsolt.org/
+    equal-contributor: true
+
+affiliations:
+  - id: ui
+    name: Department of Political Science, University of Iowa, Iowa, U.S.A.
+  - id: tsu
+    name: Department of Political Science, Tsinghua University, Beijing, China
+
+filters:
+    - authors-block
+
+tables: true # enable longtable and booktabs
+fontsize: 12pt
+indent: true
+geometry: margin=1in
+linestretch: 1.5 # double spacing using linestretch 1.5
+colorlinks: true
+bibliography: p_dcpo_demsupport_corrigenda.bib
+citation_package: natbib
+link-citations: true
+execute:
+  echo: false
+  message: false
+  warning: false
+  dpi: 300
+
+title: "Corrigendum"
+subtitle: |
+  | Democracy, Public Support, and Measurement Uncertainty--CORRIGENDUM
+  | doi:10.1017/S0003055422000429. Published in *American Political Science Review*: First View.
+
+editor_options: 
+  chunk_output_type: console
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
+\newline
+\newline
 
-Thank you for the opportunity to address the issues of (1) the inclusion of nonrepresentative surveys in the expanded dataset, (2) the treatment of non-responses, and (3) the lack of standardization of survey weights.
-It is perhaps worth noting that, soon after our letter was published last spring, Christopher Claassen shared with us via email that he had identified these issues.
-He offered no evidence or indication that he believed that any or all of them were of consequence, and we did not think they were either; as both he and our team are continuing to work in this area, we understood our exchange as instead a friendly effort to ensure these points would be adequately addressed in the future research both he and we conduct.
-At your prompting, we have now attended to these concerns specifically in the context of our letter, and we can confirm that they are inconsequential to its conclusions.
-They do suggest, however, that revisions would be warranted to the replication materials, to the online supplemental materials, and to both plots and a few numbers in the text of the letter itself.
+The authors regret that three operations raise controversies, and thus make the following updates:
 
-## Nonrepresentative Surveys
-**The Issue**. In the 2002 and 2005 Pew Global Attitudes Surveys, the codebooks identify a total of nineteen national surveys with samples that are biased toward urban areas.
+# Nonrepresentative Surveys
+**The Issue**: In the 2002 and 2005 Pew Global Attitudes Surveys, the codebooks identify a total of nineteen national surveys with samples that are biased toward urban areas.
 Although Claassen [-@Claassen2020a; -@Claassen2020] identified and excluded seventeen of the nineteen (inadvertently, apparently, including two), we did not catch this issue at all and included all of these national surveys in our expanded sample.
 
-**Resolution**. Data from these nineteen national surveys---including the two that were included in the sample used in Claassen [-@Claassen2020a; -@Claassen2020]---are now excluded from our data.
+**Resolution**: Data from these nineteen national surveys---including the two that were included in the sample used in Claassen [-@Claassen2020a; -@Claassen2020]---are now excluded from our data.
 
-## Non-Responses
-**The Issue**.
-In Claassen [-@Claassen2020a; -@Claassen2020], all respondents who did not respond to a survey item are assumed to not support democracy and an undemocratic response is (usually but not always, as we noted in the OSM at page A2; see also @Hu2022 at 4) singly imputed to them.
+# Non-Responses
+**The Issue**: In Claassen [-@Claassen2020a; -@Claassen2020], all respondents who did not respond to a survey item are assumed to not support democracy and an undemocratic response is (usually but not always, as we noted in the OSM at page A2; see also @HuEtAl2022a at 4) singly imputed to them.
 Single imputation has long been well understood to incorporate overly strong assumptions and understate measurement error [see, e.g., @Rubin1987].
-In our letter, we treated these non-responses as 'missing at random'---that is, that the distribution of attitudes among those who did not respond was similar to that among those who did---and applied listwise deletion, excluding the non-responses from the sample.
+In the original paper, we treated these non-responses as 'missing at random'---that is, that the distribution of attitudes among those who did not respond was similar to that among those who did---and applied listwise deletion, excluding the non-responses from the sample.
 This was a mistake: like single imputation, listwise deletion is known to understate measurement error [again see @Rubin1987 and many others]. 
-So neither approach is suitable, especially not in a letter on the importance of avoiding understating measurement error.
+So neither approach is suitable, especially not in a research on the importance of avoiding understating measurement error.
 
-**Resolution**.
-In some cases (for example, the Americas Barometer survey of Canada in 2010; see @Hu2022 at 5), non-responses are the result of split samples, where many respondents were not even presented with the survey item in question.
+**Resolution**: In some cases (for example, the Americas Barometer survey of Canada in 2010; see @HuEtAl2022a at 5), non-responses are the result of split samples, where many respondents were not even presented with the survey item in question.
 In such cases, imputing undemocratic responses to these respondents is clearly inapt.
@@
 
-For these remaining cases, it is _multiple_, not single, imputation that is the preferred method for addressing such missing data and the measurement error that results [see, e.g., @Rubin1987].
+For these remaining cases, it is _multiple_, not single, imputations that is the preferred method for addressing such missing data and the measurement error that results [see, e.g., @Rubin1987].
 Typically, multiple imputation of survey non-response involves building a model of the missing data with the other variables of interest from the survey.
-This preserves the relationships among these survey variables and allows the measurement uncertainty that remains after modeling to propagate to the quantity of interest [see, e.g., @King2001; @Blackwell2017].
+This preserves the relationships among these survey variables and allows the measurement uncertainty that remains after modeling to propagate to the quantity of interest [see, e.g., @KingEtAl2001; @BlackwellEtAl2017b].
 Here, however, there is only one variable of interest (or, sometimes, a few) in each of thousands of national surveys, and building such an MI model for every survey is not practicable.
@@
 The single-imputation approach employed in Claassen [-@Claassen2020a; -@Claassen2020] is inappropriate on its own, but it points the way to a feasible solution that, unlike either single imputation or listwise deletion, incorporates measurement uncertainty in the proportion of the population that supports democracy.
-To assume that all respondents who did not answer an item do not support democracy is not theoretically grounded: indeed, it is often argued that non-response to such politically sensitive items in nondemocracies reflects a fear of government reprisal for holding _pro-democratic_ views [see, e.g., @Shen2021].
+To assume that all respondents who did not answer an item do not support democracy is not theoretically grounded: indeed, it is often argued that non-response to such politically sensitive items in nondemocracies reflects a fear of government reprisal for holding _pro-democratic_ views [see, e.g., @ShenTruex2021].
 Nevertheless, the Claassen assumption sets a lower bound on the proportion of the population who support democracy as evidenced by a particular survey item.
@@
 
-## Survey Weights
-**The Issue**.  Claassen [-@Claassen2020a; -@Claassen2020] ignored survey weights (well, again usually but not always; see @Hu2022 at 4-5), instead using the unweighted survey data.
+# Survey Weights
+**The Issue**:  Claassen [-@Claassen2020a; -@Claassen2020] ignored survey weights (well, again usually but not always; see @HuEtAl2022a at 4--5), instead using the unweighted survey data.
 This is problematic, of course, as the unweighted data may not be representative of the underlying population.
@@
 
-**Resolution**. We now standardize survey weights to have a mean of one before applying them and so ensure that these weights preserve the sample size.
+**Resolution**: We now standardize survey weights to have a mean of one before applying them and so ensure that these weights preserve the sample size.
 
-# Conclusions
-Applying these corrections does not yield substantive differences in the results of our analyses and so does not affect the conclusions reached.
-But "no substantive differences" does not mean "no differences." 
-As one would anticipate, all of the regression results change marginally, and the few numbers we included in our description of the expanded dataset are no longer accurate either.
+# Results after the operation updates
+
 Updating the replication materials to reflect these corrections (and, as a bonus, make them more user friendly); revising the tables in OSM B and the figures and tables in OSM D; adding a discussion of non-responses to OSM A; and updating Figure 1, Figure 2, and the specific numbers reported under "Adding More Data" in the text itself would be warranted.
-Drafts of the revised text and OSM are attached, and we have prepared the updated replication materials for upload to the Dataverse.
-Please let us know how you would like us to proceed.
+Applying these corrections *does not* yield substantive differences in the results of our analyses and so does not affect the conclusions reached.
 

### 2023-11-01 paper/correction/corrigenda.qmd
revised the corrigendum; #45 fixed; #46 fixed

@@
     number-sections: true
+    keep-tex: true
     papersize: a4
@@
     equal-contributor: true
-
 affiliations:
@@
   - id: tsu
-    name: Department of Political Science, Tsinghua University, Beijing, China
-
+    name: Department of Political Science, Tsinghua University, Beijing, China.
 filters:
     - authors-block
-
 tables: true # enable longtable and booktabs
@@
   | doi:10.1017/S0003055422000429. Published in *American Political Science Review*: First View.
-
 editor_options: 
@@
 
-\newline
-\newline
+\hfill \break
+\hfill \break
 
@@
 # Nonrepresentative Surveys
-**The Issue**: In the 2002 and 2005 Pew Global Attitudes Surveys, the codebooks identify a total of nineteen national surveys with samples that are biased toward urban areas.
-Although Claassen [-@Claassen2020a; -@Claassen2020] identified and excluded seventeen of the nineteen (inadvertently, apparently, including two), we did not catch this issue at all and included all of these national surveys in our expanded sample.
 
-**Resolution**: Data from these nineteen national surveys---including the two that were included in the sample used in Claassen [-@Claassen2020a; -@Claassen2020]---are now excluded from our data.
+In the 2002 and 2005 Pew Global Attitudes Surveys, the codebooks identify a total of nineteen national surveys with samples that are biased toward urban areas.
+We included all of these national surveys in our expanded sample.
+Data from these nineteen national surveys---including the two that were included in the sample used in Claassen [-@Claassen2020a; -@Claassen2020]---are now excluded from our data.
 
 # Non-Responses
-**The Issue**: In Claassen [-@Claassen2020a; -@Claassen2020], all respondents who did not respond to a survey item are assumed to not support democracy and an undemocratic response is (usually but not always, as we noted in the OSM at page A2; see also @HuEtAl2022a at 4) singly imputed to them.
-Single imputation has long been well understood to incorporate overly strong assumptions and understate measurement error [see, e.g., @Rubin1987].
+
+In Claassen [-@Claassen2020a; -@Claassen2020], all respondents who did not respond to a survey item are assumed to not support democracy and an undemocratic response is usually (but not always) singly imputed to them.
 In the original paper, we treated these non-responses as 'missing at random'---that is, that the distribution of attitudes among those who did not respond was similar to that among those who did---and applied listwise deletion, excluding the non-responses from the sample.
-This was a mistake: like single imputation, listwise deletion is known to understate measurement error [again see @Rubin1987 and many others]. 
-So neither approach is suitable, especially not in a research on the importance of avoiding understating measurement error.
 
-**Resolution**: In some cases (for example, the Americas Barometer survey of Canada in 2010; see @HuEtAl2022a at 5), non-responses are the result of split samples, where many respondents were not even presented with the survey item in question.
-In such cases, imputing undemocratic responses to these respondents is clearly inapt.
-Instead, they are missing at random---respondents were explicitly randomly assigned to the split samples that excluded the relevant item---and so listwise deletion is appropriate.
+In some cases (for example, the Americas Barometer survey of Canada in 2010; see @HuEtAl2022a at 5), non-responses are the result of split samples, where many respondents were not even presented with the survey item in question.
+In such cases, they are missing at random---respondents were explicitly randomly assigned to the split samples that excluded the relevant item---and so listwise deletion is appropriate.
 We therefore continue to exclude from the sample those respondents who were not even asked the relevant question.
@@
 
-For these remaining cases, it is _multiple_, not single, imputations that is the preferred method for addressing such missing data and the measurement error that results [see, e.g., @Rubin1987].
-Typically, multiple imputation of survey non-response involves building a model of the missing data with the other variables of interest from the survey.
-This preserves the relationships among these survey variables and allows the measurement uncertainty that remains after modeling to propagate to the quantity of interest [see, e.g., @KingEtAl2001; @BlackwellEtAl2017b].
-Here, however, there is only one variable of interest (or, sometimes, a few) in each of thousands of national surveys, and building such an MI model for every survey is not practicable.
-
-The single-imputation approach employed in Claassen [-@Claassen2020a; -@Claassen2020] is inappropriate on its own, but it points the way to a feasible solution that, unlike either single imputation or listwise deletion, incorporates measurement uncertainty in the proportion of the population that supports democracy.
-To assume that all respondents who did not answer an item do not support democracy is not theoretically grounded: indeed, it is often argued that non-response to such politically sensitive items in nondemocracies reflects a fear of government reprisal for holding _pro-democratic_ views [see, e.g., @ShenTruex2021].
-Nevertheless, the Claassen assumption sets a lower bound on the proportion of the population who support democracy as evidenced by a particular survey item.
-Conversely, assuming that all non-responses reflect unvoiced _support_ for democracy establishes an upper bound on democratic support indicated by an item.
-A more theoretically-driven assumption than either of these is that non-response in democratic contexts reflects social desirability bias and so a lack of support for democracy, while non-response in non-democratic contexts reflects fear of reprisal (or perhaps again social desirability bias, only yielding different results in a different political setting) and so democratic support.
-An intermediate possibility, of course, is that attitudes among those who did not respond to an item are actually similar to the attitudes of those who did; that is, that the data are missing at random and non-responses are appropriately listwise deleted.
-
-We therefore now incorporate the measurement uncertainty due to non-response as follows.
+For these remaining cases, we now incorporate the measurement uncertainty due to non-response as follows.
 The number of democracy-supporting responses and the total sample size was imputed four times---that is, using in turn each of these four assumptions about the distribution of non-responses described above---for each country-year-item in the source survey data.
@@
 # Survey Weights
-**The Issue**:  Claassen [-@Claassen2020a; -@Claassen2020] ignored survey weights (well, again usually but not always; see @HuEtAl2022a at 4--5), instead using the unweighted survey data.
-This is problematic, of course, as the unweighted data may not be representative of the underlying population.
-In our data collection, we corrected this by employing each survey's weights, but did not appreciate that some surveys' weights are not standardized; that is, applying them caused (occasionally dramatic) changes in the sample size.
+
+Claassen [-@Claassen2020a; -@Claassen2020] again usually but not always use the unweighted survey data.
+In our data collection, we employ each survey's weights, but did not appreciate that some surveys' weights are not standardized; that is, applying them caused (occasionally dramatic) changes in the sample size.
 As the sample size is an important input in the latent variable model---smaller samples yield larger uncertainty in the population mean, which then propagates into the estimate of democratic support---this is undesirable.
-
-**Resolution**: We now standardize survey weights to have a mean of one before applying them and so ensure that these weights preserve the sample size.
+We now standardize survey weights to have a mean of one before applying them and so ensure that these weights preserve the sample size.
 
@@
 
-Updating the replication materials to reflect these corrections (and, as a bonus, make them more user friendly); revising the tables in OSM B and the figures and tables in OSM D; adding a discussion of non-responses to OSM A; and updating Figure 1, Figure 2, and the specific numbers reported under "Adding More Data" in the text itself would be warranted.
+@fig-fullAJPS and @fig-fullAPSR represent the results of the main analysis of the article with the corrected data.
 Applying these corrections *does not* yield substantive differences in the results of our analyses and so does not affect the conclusions reached.
 
+In particular, @fig-fullAJPS presents the reanalyses of the hypothesis that public support influences the level of democracy [@Claassen2020a, Table 1].
+The lighter, lefthand set of results replicate the analysis of @Claassen2020a, including its exclusion of measurement uncertainty by using only the point estimates of public democratic support and the other variables measured with quantified error (i.e., democracy and corruption), and they reproduce that article's findings.
+The middle results introduce a single change: the uncertainty in the measurement of public support and these other variables is taken into account.
+In all four models, the positive coefficients for democratic support are no longer statistically significant.
+The darker, righthand results also incorporate uncertainty but additionally replace the estimates of democratic support with those based on our expanded dataset; this change works to increase the number of observations analyzed as well.
+Although the confidence intervals shrink considerably, the coefficient estimates move much closer to zero: the hypothesis remains unsupported.
+
+![The Effect of Public Support on Democracy with Uncertainty](../../output/plot_fullAJPS.png){#fig-fullAJPS fig-align="center" height=num}
+
+@fig-fullAPSR examine the thermostatic model of democratic support per @Claassen2020 [p. 47, Table 1, 49, Table 2].
+The negative coefficient estimates for change in liberal democracy in the lefthand set of results, which do not take uncertainty into account, imply that the immediate effect of a increase in the level of democracy is a decline in public support for democracy and of a decrease in democracy an expansion of support---that democratic support indeed does respond thermostatically to democracy.
+However, the middle results demonstrate that this thermostatic effect, too, does not  hold after the measurement uncertainty is accounted for. 
+And again, the righthand results reveal that the additional data of our extension do not provide support for the original conclusion.
+
+![The Effect of Democracy on Change in Public Support with Uncertainty](../../output/plot_fullAPSR.png){#fig-fullAPSR fig-align="center" height=num}
+
 # References

### 2023-11-01 replication_materials/dcpo_demsupport.Rmd
revised the corrigendum; #45 fixed; #46 fixed

@@
     fig_caption: yes
-    keep_tex: yes
     toc: no
@@
 if (!file.exists(here("data",
-                      "exp_claassen_input.rds"))) { 
+                      "exp_claassen_input.rda"))) { 
     osf_retrieve_file("rfamx") %>% 
@@
 load(here("data", "expcor_cls_apsr.rda")) 
-exp_claassen_input <- rio::import(here("data", "exp_claassen_input.rds")) 
+load(here("data", "exp_claassen_input.rda")) 
 load(here("data", "dcpo_ajps.rda"))
@@
 
-dcpo_input_nc <- exp_claassen_input$mar$data %>% 
+dcpo_input_nc <- exp_claassen_input$data %>% 
   dplyr::select(country) %>% 
@@
 
-dcpo_input_surv <- exp_claassen_input$mar$data %>%
+dcpo_input_surv <- exp_claassen_input$data %>%
   dplyr::select(country, year, survey) %>%
@@
 
-dcpo_input_ncy <- exp_claassen_input$mar$data %>% 
+dcpo_input_ncy <- exp_claassen_input$data %>% 
   dplyr::select(country, year) %>% 
@@
 
-dcpo_input_ncyi <- exp_claassen_input$mar$data %>% 
+dcpo_input_ncyi <- exp_claassen_input$data %>% 
   dplyr::select(country, year, item, survey) %>% 
@@
 
+ggsave(here("output","plot_fullAJPS.png"))
 ```
@@
 
+ggsave(here("output","plot_fullAPSR.png"))
 ```

### 2023-11-01 paper/correction/corrigenda.qmd
adding CORRECTED in SM and citations in corrigendum; #47

@@
 The darker, righthand results also incorporate uncertainty but additionally replace the estimates of democratic support with those based on our expanded dataset; this change works to increase the number of observations analyzed as well.
-Although the confidence intervals shrink considerably, the coefficient estimates move much closer to zero: the hypothesis remains unsupported.
+Although the confidence intervals shrink considerably, the coefficient estimates move much closer to zero: the hypothesis git.
 
@@
 
+The associated supplementary materials and replication data are already updated in the Dataverse [@TaiEtAl2022].
+
 # References

### 2024-08-30 paper/dcpo_demsupport.Rmd

@@
     fig_caption: yes
-    keep_tex: yes
+    keep_md: yes
     toc: no
